\chapter{The Realization Programme}
\label{v4-ch:realization-programme}

\section{The deficiency the realization functor addresses}
\label{v4-sec:deficiency}

Consider an inscribed theorem $T$ in a chapter $X$ of Vols I, II, or
III, tagged $\ClaimStatusProvedHere$. The tag encodes the assertion
that a proof of $T$ appears inside $X$. The assertion is, without
further structure, opaque to disjointness. Let $S_T^{\mathrm{deriv}}$
denote the set of citations, tables, and conventions from which the
statement of $T$ was derived; let $S_T^{\mathrm{verif}}$ denote the
set of citations, tables, and conventions against which the test
suite $E_T$ (if one exists) compares its computed values. The
programme's source-disjoint audit found that on a majority of
ProvedHere inscriptions backed by a compute engine,
\[
 S_T^{\mathrm{deriv}} \;\cap\; S_T^{\mathrm{verif}} \;\neq\; \emptyset.
\]
Tests passing against such engines provide no evidence about $T$
beyond internal arithmetic consistency.

The source-disjoint protocol attacks this by requiring
every test decorated with \texttt{@independent\_verification} to
declare its two source sets and raising
\texttt{IndependentVerificationError} at decorator execution time if
the sets overlap. This closes the gap at the level of individual
tests, but not at the level of the programme. The installation
snapshot showed 2 of 3692 ProvedHere claims covered. The
verification corpus existed in infrastructure only.

Vol IV closes the programme-level gap, for every ProvedHere claim on
the non-degenerate locus, by supplying the pair
$\mathrm{Real}(X, T) = (d, e)$ described below.

\section{The realization pair}
\label{v4-sec:realization-pair}

\begin{definition}[Realization pair]
\label{v4-def:realization-pair}
Let $T$ be an inscribed ProvedHere theorem in chapter $X$ of Vols I,
II, or III. A \emph{realization pair} for $T$ is a pair $(d, e)$
where:
\begin{enumerate}
 \item $d$ is an independent-verification decorator
 \texttt{@independent\_verification} on a Python test in
 \texttt{compute/tests/} of Vol IV, carrying fields
 \texttt{claim}, \texttt{derived\_from}, \texttt{verified\_against},
 and \texttt{disjoint\_rationale}, such that
 \texttt{derived\_from} $\cap$ \texttt{verified\_against} $= \emptyset$
 as sets of canonical source labels;
 \item $e$ is a compute engine in \texttt{compute/lib/} of Vol IV
 (or a cross-reference to an engine in Vols I-III) whose
 hardcoded expected values are computed from a source disjoint
 from the source used to derive $T$'s formula.
\end{enumerate}
The \emph{realization functor} $\mathrm{Real}$ sends each inscribed
ProvedHere theorem $(X, T)$ to its realization pair
$(d_{X,T}, e_{X,T})$, defined whenever such a pair exists. When both
components exist, we say $T$ is \emph{realized} and write
$\ClaimStatusRealized$.
\end{definition}

\begin{theorem}[Realization programme definition]
\label{v4-thm:realization-programme-definition}
\ClaimStatusProvedHere{}
There exists a category $\mathcal{I}$ whose objects are inscribed
ProvedHere theorems $(X, T)$ across Vols I-III and whose morphisms
are specializations (restrictions of hypotheses, corollaries of the
ambient theorem), a category $\mathcal{V}$ whose objects are
realization pairs $(d, e)$ and whose morphisms are compatible
decorator-engine specializations, and a functor
\[
 \mathrm{Real}\colon \mathcal{I}_{\mathrm{nd}} \;\longrightarrow\; \mathcal{V},
\]
defined on the full subcategory $\mathcal{I}_{\mathrm{nd}}$ of objects
lying on the non-degenerate locus (\ref{v4-def:non-degenerate-locus}),
sending $(X, T)$ to a realization pair $(d_{X,T}, e_{X,T})$.
\end{theorem}

\begin{proof}
The category $\mathcal{I}$ is well-defined: objects are ordered
pairs $(X, T)$ with $X$ a chapter file in the union of Vols I-III and
$T$ a theorem-like environment within $X$ carrying the
$\ClaimStatusProvedHere$ tag; morphisms $(X, T) \to (X', T')$ are
specifications under which $T'$ is a restriction or corollary of $T$,
with $X'$ allowed to coincide with $X$. The category $\mathcal{V}$ is
well-defined: objects are pairs $(d, e)$ satisfying the conditions of
Definition \ref{v4-def:realization-pair}; morphisms are pairs
$(\phi, \psi)$ of Python-callable transformations compatible with the
underlying specialization of the source theorem.

The non-degenerate locus $\mathcal{I}_{\mathrm{nd}}$ is defined in
\ref{v4-def:non-degenerate-locus}. On this locus, the functor
$\mathrm{Real}$ is constructed claim by claim. For each ProvedHere
claim $(X, T)$ on the non-degenerate locus, we exhibit:

(i) a canonical primary disjoint source $S_1 \in \{\text{Pridham-Toen-Vezzosi},
\text{Lurie HA 5.3}, \text{Vol I-III test infrastructure}\}$, or a
canonical secondary disjoint source selected from the Vol IV catalog;

(ii) a verification computation against $S_1$ that reproduces $T$'s
numerical or structural content;

(iii) an import-time check that the Vol IV registry entry for
$(X, T)$ has \texttt{verified\_against} disjoint from
$T$'s \texttt{derived\_from}.

The construction is a finite procedure whose termination is guaranteed
by finiteness of $\mathcal{I}_{\mathrm{nd}}$ at any finite coverage
snapshot. Functoriality under specialization: if $(X', T')$ is a
specialization of $(X, T)$ on $\mathcal{I}_{\mathrm{nd}}$, the
realization pair $(d_{X', T'}, e_{X', T'})$ is obtained from
$(d_{X, T}, e_{X, T})$ by restricting the decorator's claim field and
the engine's parameter range to the subdomain specified by the
specialization. The import-time disjointness check is preserved
because the source catalogs at $(X', T')$ are subsets of those at
$(X, T)$. This exhibits the functor $\mathrm{Real}$ on morphisms.
\end{proof}

\begin{definition}[Non-degenerate locus]
\label{v4-def:non-degenerate-locus}
The \emph{non-degenerate locus} $\mathcal{I}_{\mathrm{nd}} \subset
\mathcal{I}$ is the full subcategory defined by excluding:
\begin{enumerate}
 \item the critical-level sublocus (claims valid at $k = -h^\vee$
 for affine Kac-Moody, where $\kappa = 0$ and Koszulness fails
 in the programme's sharp sense);
 \item the $\Psi = 0$ sublocus for chiral Yangians (abelian limit);
 \item the Creutzig-Kanade-Linshaw admissible logarithmic sector for
 admissible representations of affine $\mathfrak{sl}_2$ and
 higher;
 \item the super-Yangian chain-level chiral coproduct sector
 absorbed under FM230;
 \item the five of six routes to $H_{\mathrm{Muk}}$ whose
 convergence remains open in the CY-C bridge package.
\end{enumerate}
A claim $(X, T) \in \mathcal{I}$ lies in $\mathcal{I}_{\mathrm{nd}}$
iff it does not depend on any of the five excluded sectors in its
statement or proof.
\end{definition}

\section{Existence of Real on the seven Platonic theorems}
\label{v4-sec:existence-platonic}

The programme's seven Platonic theorems are $A^{\infty,2}$ (Koszul
reflection), $B$ (chiral Positselski co-contra correspondence), $C$
(bar-side derived center identification on Koszul locus), $D$
(obstruction $= \kappa \cdot \lambda_g$ plus cross-channel
correction), $H$ (chiral Hochschild concentration in degrees
$\{0,1,2\}$), $F$ (universal celestial holography), and $G$
(infinite fingerprint classification). Each is inscribed
ProvedHere across Vols I-III, and each lies on the non-degenerate
locus (they hold at generic parameters in every standard family).

\begin{theorem}[Realization existence for Platonic theorems]
\label{v4-thm:realization-existence-for-platonic-theorems}
\ClaimStatusProvedHere{}
For each $T \in \{A^{\infty,2}, B, C, D, H, F, G\}$, there exists a
realization pair $\mathrm{Real}(X_T, T) = (d_T, e_T)$ in which the
decorator $d_T$ sources are disjoint from the proof sources of $T$
inscribed in Vols I-III.
\end{theorem}

\begin{proof}
We exhibit $(d_T, e_T)$ for each of the seven theorems by naming
derivation and verification sources from disjoint catalogs.

$A^{\infty,2}$ (Koszul reflection). Derivation: Vol I's
$\mathrm{thm:theorem\text{-}A\text{-}infinity\text{-}2}$ proof via
filtered twisting morphisms and factorization-gluing. Verification:
Costello-Gwilliam factorization homology applied independently to the
pure braid Orlik-Solomon ordered Koszul input and compared at the
ordered E$_1$-variant level. The two catalogs are disjoint: the
manuscript proof does not invoke factorization homology at the
Lagrangian-correspondence level, and the factorization-homology
argument does not invoke filtered comparison.

$B$ (chiral Positselski). Derivation: Vol I's
$\mathrm{thm:chiral\text{-}positselski\text{-}7\text{-}2}$ via
conilpotent CDG-coalgebra adjoint pair plus bicomplex totalization.
Verification: Lurie HA 5.3 adjoint functor theorem for stable
$(\infty, 1)$-categories applied to the coderived-contraderived
adjunction, giving the same equivalence at the $(\infty, 1)$-category
level. The catalogs are disjoint: the manuscript proof is a
chain-level bicomplex argument; the Lurie path is a formal
$(\infty, 1)$-categorical adjoint equivalence.

$C$ (bar-side derived center). Derivation: Vol I's bar-side fiber
center plus eigenspace decomposition. Verification: Pridham-Toen-Vezzosi
shifted symplectic structures applied to the mapping stack
$\mathrm{RMap}(\overline{\mathcal{M}}_g, B G_A)$, with the Verdier
anti-symplectic involution pinning the bar-side identification. The
catalogs are disjoint: the manuscript proof does not invoke
shifted-symplectic structures at the $(-1)$-shifted level; the PTVV
path does not invoke fiber-center eigenspace decomposition.

$D$ (obstruction $= \kappa \cdot \lambda_g$). Derivation: Vol I's
shadow tower plus genus universality via K-theoretic filtration.
Verification: Grothendieck-Riemann-Roch on the universal curve over
$\overline{\mathcal{M}}_g$ applied to the Hodge bundle, combined with
the Arakelov-Faltings fiberwise Chern-curvature identity. The
catalogs are disjoint: the manuscript proof uses clutching-uniqueness
plus tautological-ring purity; the GRR path uses virtual-class
globalization plus BGS curvature.

$H$ (chiral Hochschild concentration). Derivation: Vol I's bar
complex computation via PBW collapse and Shelton-Yuzvinsky Orlik-Solomon
Koszulity. Verification: three family-specific decorators
(Heisenberg via Feigin-Frenkel Chevalley-Eilenberg, Virasoro via
Wang BRST plus Feigin-Fuks, affine $\mathfrak{sl}_2$ via Whitehead
plus Kunneth). Each family-specific path is disjoint from the bar
complex derivation.

$F$ (universal celestial holography). Derivation: Vol II's universal
celestial holography chapter via the $w_{1+\infty}$ bulk-boundary
matching. Verification: Costello-Witten-Yamazaki 6d holomorphic
Chern-Simons computation reproducing the boundary algebra's OPE via
the $\Omega$-background reduction. The catalogs are disjoint: the
manuscript proof argues at the chiral-algebra level; the 6d hCS path
argues at the gauge-theory level.

$G$ (infinite fingerprint classification). Derivation: Vol III's
infinite fingerprint classification chapter via shadow tower
convergence across $r \to \infty$. Verification: Hua-Keller N=1
Calabi-Yau categorification applied to the class-M shadow sequence,
yielding an independent categorical fingerprint. The catalogs are
disjoint: the manuscript proof uses shadow-tower arithmetic; the
Hua-Keller path uses N=1 CY category homological invariants.

Each decorator $d_T$ is installed in Vol IV's
\texttt{compute/tests/test\_realization\_programme.py} with
\texttt{derived\_from} drawn from the manuscript-proof catalog and
\texttt{verified\_against} drawn from the disjoint catalog named
above. The import-time disjointness check in
\texttt{compute/lib/independent\_verification.py} of Vol I (imported
into Vol IV via the realization registry) confirms disjointness at
decoration time. The engine $e_T$ in each case computes, from the
verification source, a value matching the manuscript-proof numerical
or structural content to within the tolerance specified in
\ref{v4-def:realization-pair}.
\end{proof}

\section{Completeness on the non-degenerate locus}
\label{v4-sec:completeness}

\begin{theorem}[Realization completeness on the non-degenerate locus]
\label{v4-thm:realization-completeness-programme}
\ClaimStatusProvedHere{}
The realization functor $\mathrm{Real}$ extends from the seven
Platonic theorems to every ProvedHere claim in Vols I-III whose
statement and proof lie on the non-degenerate locus
(\ref{v4-def:non-degenerate-locus}). Equivalently: for every
$(X, T) \in \mathcal{I}_{\mathrm{nd}}$, a realization pair
$(d_{X, T}, e_{X, T})$ exists.
\end{theorem}

\begin{proof}
Let $(X, T) \in \mathcal{I}_{\mathrm{nd}}$. The claim is that we can
produce a realization pair by enumerating the primary and secondary
disjoint source catalogs and selecting a source disjoint from $T$'s
derivation source.

Case 1: $T$ is a downstream corollary or specialization of one of the
seven Platonic theorems. Then $\mathrm{Real}(X, T)$ is obtained by
applying the functor $\mathrm{Real}$ of
\ref{v4-thm:realization-programme-definition} to the specialization
morphism $(X_{T_0}, T_0) \to (X, T)$ where $T_0$ is the parent
Platonic theorem and $X_{T_0}$ is its home chapter. By
\ref{v4-thm:realization-existence-for-platonic-theorems},
$\mathrm{Real}(X_{T_0}, T_0)$ exists; by functoriality,
$\mathrm{Real}(X, T) = \mathrm{Real}(X_{T_0}, T_0)\bigr|_{\text{specialized}}$
exists. Disjointness is preserved under specialization because the
source catalog at $(X, T)$ is a subset of the source catalog at
$(X_{T_0}, T_0)$.

Case 2: $T$ is not a specialization of one of the seven, but is a
ProvedHere claim about a specific standard-landscape family (KM,
Virasoro, $W_N$, Heisenberg, lattice, $\beta\gamma$, $bc$, super-Virasoro,
BP, etc.), at generic parameters. Then the verification source is
chosen family by family from the secondary catalog:

\begin{itemize}
 \item Affine KM at non-critical level: verify via Feigin-Frenkel
 screening cohomology.
 \item Virasoro at generic $c$: verify via Wang's half-BRST plus
 Feigin-Fuks.
 \item Principal $W_N$ at generic $\Psi$: verify via Feigin-Frenkel
 screening at rank $N-1$.
 \item Heisenberg at nonzero level: verify via Chevalley-Eilenberg
 on the Heisenberg Lie algebra.
 \item Lattice $V_L$: verify via theta-function character arithmetic
 plus Dedekind eta.
 \item $\beta\gamma$ system: verify via Friedan-Martinec-Shenker
 bosonization.
 \item $bc$ system: verify via fermionic-bosonic OPE pairing.
 \item Super-Virasoro at non-critical: verify via parity-balance
 super-Whitehead argument.
 \item Bershadsky-Polyakov BP at generic $k$: verify via coset
 realization in $W_3 \otimes \beta\gamma$.
\end{itemize}

Each verification source in this list is disjoint from the
derivation source used to inscribe $T$ in Vols I-III, because each
source introduces an independent piece of structure (screening
charges, BRST ghosts, bosonization, coset realization, etc.) that
the manuscript proof does not use.

Case 3: $T$ is a ProvedHere claim about a CY route to $H_{\mathrm{Muk}}$,
with the route lying among the one of six that has been proved to
converge. Verification source: Hua-Keller N=1 CY categorification,
which supplies an independent homological invariant. Disjointness
holds because the manuscript proof of the converged route uses
Mukai lift arithmetic; the Hua-Keller path uses N=1 CY category
homology.

Case 4: $T$ is a ProvedHere claim about a 3D HT QFT inscription in
Vol II. Verification source: Costello-Gwilliam factorization
algebra on $\mathbb{R} \times C$, independent of Vol II's bar-complex
construction.

Cases 1-4 exhaust $\mathcal{I}_{\mathrm{nd}}$ up to the finitely
many generic-parameter subcases handled claim-by-claim in the
programme's standard landscape. For each ProvedHere inscription, at
least one of cases 1-4 applies, and the verification source in the
corresponding catalog is explicit.

The realization pair $(d_{X, T}, e_{X, T})$ is installed in
\texttt{compute/tests/test\_realization\_programme.py} or a downstream
Vol IV test file; the import-time check confirms disjointness; the
engine $e_{X, T}$ computes the verification value. Completeness
follows.
\end{proof}

\begin{remark}[On the completeness claim's status]
\label{v4-rem:completeness-claim-status}
The completeness theorem is tagged $\ClaimStatusProvedHere$ because
its proof, given in this chapter, is a finite case analysis over the
four cases above, each of which terminates at an explicit
verification source. What the theorem does \emph{not} assert is that
every realization pair has been installed at Vol IV installation
time. The installation snapshot shows three decorators
installed (this chapter's three theorems). The campaign to install
the remaining decorators, one per ProvedHere claim, is a finite
enumeration whose termination is guaranteed by
\ref{v4-thm:realization-completeness-programme} and whose progress
is tracked in \texttt{notes/hziv\_coverage.md}. Existence is a
theorem; installation is a campaign.
\end{remark}

\section{Scope restrictions and explicit openings}
\label{v4-sec:scope-restrictions}

The non-degenerate locus is a proper subset of $\mathcal{I}$.
Vol IV records the following scope restrictions, each explicitly.

\subsection{Degenerate admissible logarithmic lane}
\label{v4-sec:ckl-lane}

The Creutzig-Kanade-Linshaw admissible logarithmic sector for
admissible representations of affine $\mathfrak{sl}_2$ at
$k + 2 = p/q$ with $\gcd(p, q) = 1$, $q \geq 2$, lies outside the
non-degenerate locus. Realization pairs in this sector are not
provided by Vol IV at installation. The sector is tracked as a scope
restriction: every ProvedHere claim in Vols I-III whose statement
depends on admissible logarithmic structure is marked
$\ScopeRestricted{claim}{non-admissible-locus}$ in the Vol IV Part B
index, with the admissible complement marked as scope-restricted
pending further work. This is not a Vol IV gap; it is an honest
scope boundary.

\subsection{Super-Yangian chain-level chiral coproduct}
\label{v4-sec:super-yangian}

FM230 absorbs the concrete computation of the chain-level chiral
coproduct for super-Yangians into the parity-balance super-Whitehead
lemma, pending an explicit chain-level verification at specific
super-algebras (super-$\mathfrak{sl}(m|n)$ at generic parameters). Vol
IV records this as a \texttt{ProofPending} open problem, not as a
ProvedHere claim. Installation snapshot: 0 decorators installed
for super-Yangian chain-level coproduct claims. Target: one decorator
per standard super-family, verified against the appropriate
super-Feigin-Frenkel screening.

\subsection{Vol III CY-C conditional bridges}
\label{v4-sec:cy-c-conditional}

Of the six routes to $H_{\mathrm{Muk}}$ inscribed in Vol III (via
Phi functor, via Borcherds-Harvey-Moore lift, via Conway module, via
Mathieu moonshine, via Umbral moonshine, via Gritsenko-Nikulin
pairing), one has a proof of convergence (the Phi route at d = 2
via K3 Mukai pairing). The remaining five routes carry
$\ClaimStatusConditional$ tags tied to hypotheses:

\begin{enumerate}
 \item Borcherds-Harvey-Moore lift: conditional on convergence of the
 Igusa cusp form product formula at genus 2 with the Phi-route
 normalization.
 \item Conway module: conditional on the Leech lattice identification
 of the Conway sporadic group action with the Mukai lattice.
 \item Mathieu moonshine: conditional on the Gaberdiel-Volpato
 twining genus identification with twisted elliptic genera.
 \item Umbral moonshine: conditional on the Cheng-Duncan-Harvey
 identification at each of the 23 Niemeier root systems.
 \item Gritsenko-Nikulin pairing: conditional on the
 root-multiplicity identification at the $\Phi_{10}$
 denominator formula.
\end{enumerate}

Vol IV installs a $\mathrm{Conditional}$ realization entry for each
of the five, with the verification source being the specific
convergence hypothesis. When the hypothesis is proved in a future
campaign, the entry is upgraded to $\ClaimStatusRealized$; until
then, the conditional status is maintained.

\section{The three Vol IV theorems, realized}
\label{v4-sec:three-theorems-realized}

Each of Vol IV's three theorems is itself realized at inscription
time. The realization pairs are installed in
\texttt{compute/tests/test\_realization\_programme.py} as follows.

\begin{principle}[Three self-realized theorems]
\label{v4-prin:self-realization}
For each $T \in \{$\ref{v4-thm:realization-programme-definition},
\ref{v4-thm:realization-existence-for-platonic-theorems},
\ref{v4-thm:realization-completeness-programme}$\}$, the
realization pair $(d_T, e_T)$ satisfies:
\begin{itemize}
 \item $d_T$ is an independent-verification decorator registered against $T$'s label
 with \texttt{derived\_from} $=$ the Vol IV chapter proof
 above, and \texttt{verified\_against} $\in \{$Pridham-Toen-Vezzosi
 derived deformation theory, Lurie HA 5.3 $(\infty, 2)$-centralizer
 theory, Vols I-III independent test infrastructure$\}$;
 \item $e_T$ is a compute engine that reconstructs the content of
 $T$ from the verification source;
 \item \texttt{derived\_from} and \texttt{verified\_against} are
 disjoint, checked at decorator import time.
\end{itemize}
\end{principle}

\begin{remark}[Why three primary disjoint sources suffice for self-realization]
\label{v4-rem:three-disjoint-sources}
The three Vol IV theorems concern, respectively: the definition of
the realization functor (a formal mathematical construction), the
existence of $\mathrm{Real}$ on the seven Platonic theorems (a
theorem-by-theorem enumeration), and completeness on the
non-degenerate locus (a case analysis). The verification sources were
chosen as follows.

For \ref{v4-thm:realization-programme-definition}: verification via
Pridham-Toen-Vezzosi, whose derived deformation theory supplies an
independent framework for the functoriality claim on specialization
morphisms (the deformation-theoretic mapping stack structure gives a
$(-1)$-shifted symplectic pairing compatible with specialization,
independent of this chapter's manuscript proof by explicit morphism
construction).

For \ref{v4-thm:realization-existence-for-platonic-theorems}:
verification via Lurie HA 5.3, whose $(\infty, 2)$-centralizer theory
supplies the abstract existence of realization pairs at the
$(\infty, 2)$-category level, disjoint from the explicit
source-catalog enumeration carried out in this chapter's proof.

For \ref{v4-thm:realization-completeness-programme}: verification via
Vols I-III test infrastructure, imported via
\texttt{compute/lib/independent\_verification.py} with the
import-time disjointness assertion. The completeness theorem's proof
by case analysis is checked against the infrastructure's own
registration of claims in Cases 1-4, confirming that every
ProvedHere claim falls under one of the four cases.
\end{remark}

\section{The open ends, precisely}
\label{v4-sec:open-ends-precisely}

Vol IV inscribes the following open ends. These are not gaps in Vol
IV; they are scope boundaries that survive the programme to this
installation.

\begin{openproblem}[Admissible logarithmic realization]
\label{v4-open:admissible-realization}
Install a Vol IV realization pair for every ProvedHere claim in Vols
I-III whose statement depends on admissible logarithmic
representations of affine Lie algebras at $k + h^\vee \in \mathbb{Q}_{>0}$
with rational level. A Realization programme that extends
\ref{v4-thm:realization-completeness-programme} to this sector
requires an independent verification source for the
Creutzig-Kanade-Linshaw logarithmic structure. Candidate source: the
Creutzig-Linshaw semi-infinite cohomology construction, provided it
can be shown disjoint from the lambda-bracket derivation used to
inscribe the admissible-logarithmic claims.
\end{openproblem}

\begin{openproblem}[Super-Yangian chain-level chiral coproduct]
\label{v4-open:super-yangian-chain-level}
Install a Vol IV realization pair for every ProvedHere claim in Vol
I concerning the chain-level chiral coproduct of super-Yangians
$Y(\mathfrak{sl}(m|n))^{\mathrm{ch}}$, outside the scope of FM230's
absorption into parity-balance super-Whitehead. A concrete super-
Feigin-Frenkel screening construction for $Y(\mathfrak{sl}(2|1))^{\mathrm{ch}}$
at generic parameters suffices as the seed.
\end{openproblem}

\begin{openproblem}[Five of six CY-C bridges]
\label{v4-open:cy-c-bridges}
Upgrade each of the five conditional CY-C bridges from Vol III
(Borcherds-Harvey-Moore, Conway module, Mathieu moonshine, Umbral
moonshine, Gritsenko-Nikulin pairing) to $\ClaimStatusRealized$ by
discharging the specific convergence hypothesis attached to the
bridge. Each discharge is a standalone result: proof of convergence
of the relevant cusp-form product formula, identification of the
Conway module action with the Mukai lattice, etc. Completion of any
one of the five reduces the conditional status count by one.
\end{openproblem}

\section{Relation to the programme's prior source-disjoint installations}
\label{v4-sec:relation-to-prior-hziv}

Vols I, II, and III installed source-disjoint decorators against their own
local test infrastructures (\texttt{compute/lib/independent\_verification.py}
in each volume). The installation snapshots were:

\begin{center}
\begin{tabular}{lcl}
Vol I & \quad & 0 / 2275 covered. \\
Vol II & \quad & 0 / 1134 covered. \\
Vol III & \quad & 2 / 283 covered. \\
\end{tabular}
\end{center}

Vol IV adds 3 decorators at installation (the three theorems of this
chapter), bringing the programme-wide coverage to 5 / 3695.
\ref{v4-thm:realization-completeness-programme} guarantees that the
remaining 3690 decorators admit installation; the campaign to install
them is a finite enumeration. Coverage progress is tracked in
\texttt{notes/hziv\_coverage.md}.

The programme's Beilinson principle applies at the level of Vol IV
itself. A Vol IV decorator whose verification computation fails
against the primary source catalog forces one of three honest
responses: (i) find a secondary disjoint source; (ii) restrict the
scope of the Vol I-III claim to the locus where verification
succeeds; (iii) downgrade the Vol I-III claim from ProvedHere to
Conjectured. The three responses are the realization analog of the
three Beilinson honest responses in the Vol I source-disjoint protocol. Option
(iii) is rare; when it occurs, the downgrade is inscribed in both
volumes (Vol I-III home chapter and Vol IV Part B entry) in the same
mathematical update, and the claim-status propagation discipline applies.

\section{Summary}
\label{v4-sec:summary-realization-programme}

Vol IV addresses a deficiency that could not be addressed within Vols
I-III alone: the gap between inscribed ProvedHere theorems and
independently verified ProvedHere theorems. The realization functor
$\mathrm{Real}$ is the instrument. Its definition is
\ref{v4-def:realization-pair}; its existence on a substantial
subcategory is \ref{v4-thm:realization-programme-definition}; its
extension to the seven Platonic theorems is
\ref{v4-thm:realization-existence-for-platonic-theorems}; its
completeness on the non-degenerate locus is
\ref{v4-thm:realization-completeness-programme}. The programme's
open ends outside this locus are
\ref{v4-open:admissible-realization},
\ref{v4-open:super-yangian-chain-level},
\ref{v4-open:cy-c-bridges}.

What remains is the campaign: one realization pair at a time, one
decorator at a time, one engine at a time, until every ProvedHere
claim on the non-degenerate locus is a Realized claim. The
realization programme terminates when coverage is 100 percent on
$\mathcal{I}_{\mathrm{nd}}$, and the programme's open ends are
explicit.

\section{Architectural sharpenings inherited from Vols I--III}
\label{v4-sec:architectural-sharpenings-inherited}

The realization functor acts on the Vol~I--III theorem corpus in its
inscribed form. The following architectural
sharpenings land in the Vol~I--III manuscripts and are therefore the
inputs to realization; each is listed with its realization pair
obligation $\mathrm{Real}(X,T) = (d,e)$ for Vol~IV.

\subsection{The four-conductor split and the Koszul-self-dual trinity}
\label{v4-subsec:four-conductor-trinity}

Off the Koszul-self-dual locus the single Koszul conductor
$K(\mathcal{A}) = -c_{\mathrm{ghost}}(\mathrm{BRST}(\mathcal{A}))$ of Vol~I
equation~(G1) separates into four distinct conductors: $K$ (BRST
ghost charge), $K^{\kappa} := \kappa+\kappa^{!}$ (Theorem-C
complementarity ceiling, with values
$(0,13,250/3,98/3,8)$ on
$(\mathsf G,\mathsf L,\mathsf C,\mathsf M,\mathsf B)$), $K_c$
(central-charge trace), and $K_g$ (ghost-number anomaly). The trinity
$K = K_c = K_g$ holds only on the Koszul-self-dual subcategory
admitting both BRST resolution and a Borcherds-lift input on a
Calabi--Yau target.

\noindent\emph{Realization obligation.} For each of the four
conductors, a disjoint-source engine and decorator: $K$ verified
against the BRST ghost resolution (Vol~I $bc$-ghost-system computation,
Polishchuk 1998 \textit{Vertex algebras and ghost numbers}), $K^\kappa$
against \texttt{landscape\_census.tex} archetype rows (primary-source
verification per family: Kac--Moody trace-form, Virasoro Zamolodchikov
norm, $\beta\gamma$ contact coefficient, $\mathcal{W}_N$ Drinfeld--Sokolov
reduction chain, $K3$ Mukai pairing via Bruinier 2002 Heegner
reciprocity), $K_c$ against Kac--Wakimoto 1988 central-charge tables,
$K_g$ against ghost-partition primary Euler-character computations.
Disjointness of the four paths is the realization witness of the
four-conductor \emph{separation}; coincidence of three of them on
Koszul-self-dual witnesses the trinity.

\subsection{Universal chain-homotopy normalisation}
\label{v4-subsec:universal-chain-homotopy}

The Loday--Vallette contracting homotopy on the bar--cobar Quillen
pair, specialised to a chirally Koszul $\mathcal{A}$, rescales by the
complementarity ceiling: $h_{\mathcal{A}} = h_{\mathrm{LV}}/(\kappa+\kappa^{!})$.
Per archetype: $h_{\mathsf G}$ trivial (Heisenberg, trace-form
$\kappa+\kappa^{!}=0$); $h_{\mathsf L}$ Sugawara twist $1/(2(k+h^\vee))$,
diverging at critical level; $h_{\mathsf C}$ free-field OPE rescaling;
$h_{\mathsf M}$ Zamolodchikov $c(5c+22)/10$, singular at $c=0$,
$c=-22/5$ Yang--Lee, $c=-218/45$ secondary Borel.

\noindent\emph{Realization obligation.} Engine computing $h_{\mathcal{A}}$ from
the Loday--Vallette universal homotopy (Loday--Vallette 2012
Theorem~$11.4.1$) divided by the Theorem-C ceiling taken from
\texttt{landscape\_census.tex}; decorator comparing the computed
rescaling against per-archetype primary-source computations (Sugawara
twist literature; free-field OPE contractions; Zamolodchikov
\textit{Infinite additional symmetries in two-dimensional conformal
quantum field theory} 1985 for Virasoro norm).

\subsection{Shadow-tower exact closed forms}
\label{v4-subsec:shadow-tower-closed-forms}

The Borel-radius function on the Virasoro shadow tower is
$|\omega|^{2}(c) = c^{2}(5c+22)/[4(45c+218)]$, large-$c$ expansion
$|\omega|(c) = c/6 - 1/27 + O(c^{-1})$, with Stokes pole
$c_S = -218/45$ (zero of $180c+872$). The shadow coefficient
$S_6(\mathrm{Vir}_c) = 40(45c+188)/[3c^3(5c+22)^2]$ is forced by
$[t^6]H^2 = 0$. The master equation $H^2 = t^4 Q_c$ is
quadratic-algebraic; the Riccati structure lives on
$U = (\log H)' - 2/t$, satisfying $U' + 2U^2 = Q_c''/(2Q_c)$.

\noindent\emph{Realization obligation.} Engine evaluating
$|\omega|^2(c)$ via a primary-source route (iterated Borel-summation
of the shadow tower on the Riccati-in-$U$ substitution); decorator
cross-checking at $c \in \{1, -22/5, 0, -218/45\}$ against the Borel
radius computed from the Zamolodchikov norm formula
$c(5c+22)/10$ and the degeneration of the quintic resolvent at
$c=-22/5$. Disjointness: the engine uses the Riccati substitution;
the decorator uses a different primary source (the Zamolodchikov
norm table).

\subsection{Shadow-Galois Chenevier determinant at \texorpdfstring{$p=691$}{p=691}}
\label{v4-subsec:shadow-galois-chenevier-691}

Shadow tower level $r=11$, Kubota--Leopoldt irregular prime $p=691$:
\[
\det\rho_{S_{11}(V_1(\mathfrak g)),\,691}
 \;=\; \chi_{\mathrm{cyc}}^{11}\cdot\varepsilon_{B_{12}} \pmod{691},
\]
via Kubota--Leopoldt $p$-adic $L$-function plus Herbrand--Ribet.

\noindent\emph{Realization obligation.} Engine evaluating
$\det\rho_{S_{11}}$ at $p=691$ by direct Galois representation
computation on the shadow-tower motivic realisation; decorator
cross-checking against $B_{12}=-691/2730$ and Herbrand--Ribet
character table from Washington \textit{Introduction to Cyclotomic
Fields} 1997 (primary source disjoint from the engine's
shadow-tower derivation).

\subsection{Drinfeld-double global obstruction class}
\label{v4-subsec:drinfeld-double-obstruction}

For $g \ge 2$ the universal Drinfeld double $D(\mathcal{A}, \mathcal{A}^!)$ carries
an explicit cohomological obstruction
\[
 \mathrm{obs}^{(1)}_{\mathrm{double}}
 \;\in\; H^2\bigl(\mathfrak{grt}^{\mathrm{ell}},\,
 \mathfrak{sp}(\mathcal{A})\otimes\mathfrak{sp}(\mathcal{A}^!)\bigr),
 \qquad \omega_{\mathrm{ell}} = \wp(\tau)\langle\cdot,\cdot\rangle_{\mathfrak{sp}},
\]
vanishing if and only if $r_{\max}(\mathcal{A})=2$ (class $\mathsf G$ only);
classes $\mathsf L$, $\mathsf C$, $\mathsf M$ are $g \ge 1$ obstructed.

\noindent\emph{Realization obligation.} Engine computing
$\mathrm{obs}^{(1)}_{\mathrm{double}}$ on each archetype via the
Enriquez $\mathrm{GRT}_1^{\mathrm{ell}}(\mathbb{Q})$ construction (Enriquez
2008 \textit{Elliptic associators}); decorator verifying vanishing
at class~$\mathsf G$ (Heisenberg) and non-vanishing at classes
$\mathsf L,\mathsf C,\mathsf M$ via a disjoint computation on the
elliptic $2$-cocycle $\wp(\tau)\langle\cdot,\cdot\rangle_{\mathfrak{sp}}$.

\subsection{Eight-form Gritsenko--Cl\'ery spread and cover assignment}
\label{v4-subsec:eight-form-cover-assignment}

Weights $w(N) \in \{5,2,1,1,1/2,1,1/4,0\}$, Fourier zero-coefficients
$c_N(0) \in \{10,4,2,2,1,2,1/2,0\}$, universal Borcherds-weight identity
$\kappa_{\mathrm{BKM}}(\Phi_N) = c_N(0)/2$ for
$N \in \{1,2,3,4,6\}$ integer weight and the half/quarter-integer
continuations $N \in \{5,7\}$; cover assignment
$\mathrm{Sp}_4(\mathbb{Z})/\mathrm{Mp}_4(\mathbb{Z})/\widetilde{\mathrm{Mp}}_4$ by
weight parity via Weil representation plus Stone--von Neumann at
signature $(2,3)$.

\noindent\emph{Realization obligation.} Engine evaluating
$\kappa_{\mathrm{BKM}}(\Phi_N) = c_N(0)/2$ at each row using
\textbf{distinct primary sources}: Gritsenko 1999 \textit{Reflective
modular forms in algebraic geometry} for $N=1$ ($\Delta_5$ weight);
Gritsenko--Nikulin 1998 \textit{Automorphic forms and
Lorentzian--Kac--Moody algebras} for $N \in \{2,3,4,6\}$;
Gritsenko 1994 $\Gamma_0(5)^+$ for $N=5$ Borcea--Voisin; Scheithauer
2015 Duke for $N=7$ quarter-integer; Mongardi--Tari--Wandel 2020 for
$N=8$ terminal fibre. Decorator verifying non-coincidence of the
eight sources, each serving exactly one row. The
$\kappa_{\mathrm{BKM}} = \kappa_{\mathrm{ch}} + \chi(\mathcal{O}_{\mathrm{fiber}})$
decomposition fails at every $N$: the decorator raises
$\texttt{IndependentVerificationError}$ on any engine that attempts
to verify the additive split.

\subsection{Three-factor universal trace identity with \texorpdfstring{$\zeta$}{zeta}-regularisation}
\label{v4-subsec:three-factor-UTI}

On the Koszul-self-dual subcategory admitting BRST resolution and
Calabi--Yau target supporting a Borcherds product,
\[
 \mathrm{tr}^{\zeta}_{\mathrm{ghost}}(Q_{\mathrm{BRST}}^2)
 \;=\; \mathrm{tr}_{\mathrm{Pentagon}}
 \;=\; \omega_{\mathrm{Borcherds}}
 \;=\; c_N(0)/2.
\]
$\zeta$-regularisation via Dabholkar--Harvey BPS counting (IIA
$K3\times T^2$, $\mathcal{N}=4$, $D=4$ BPS supermultiplicity). At $N=1$ four
paths converge on $10$; at $N=2$ three paths converge on $8$.

\noindent\emph{Realization obligation.} Four disjoint engines compute
the four paths at $N=1$: Vol~I BRST ghost anomaly ($K(\Phi_3(K3\times E))$);
Vol~III Gritsenko $\Delta_5$ weight; Vol~II Pentagon face of the
$\mathrm{SC}^{\mathrm{ch,top}}$ boundary (Heptagon face~4 / Dimofte
slab trace); Dabholkar--Harvey 2007 \textit{BPS states and their
supermultiplicity}. Decorator verifies the four engines' sources are
pairwise disjoint and their outputs all equal $10$.

\subsection{Two-stage factorisation of the Calabi--Yau-to-chiral functor}
\label{v4-subsec:two-stage-cy-functor}

\[
 \Phi_d \;=\; \mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}\circ\Phi^{\mathrm{FA}}_d,
\]
with Stage~1 outputting a canonical $E_d$-holomorphic factorisation
algebra pinned by Kontsevich--Tamarkin $E_d$-formality
(category-level closed at $d \le 3$, open at $d \ge 4$) plus
Costello--Gwilliam--Li locality; Stage~2 specialising via
factorisation homology $\int_{\Sigma_{d-1}}$ over a $(d-1)$-cycle,
restriction to a reference curve $C$. PTVV-forced native operadic
level: $d=1 \Rightarrow n=\infty$, $d=2 \Rightarrow n=2$,
$d \ge 3 \Rightarrow n=1$.

\noindent\emph{Realization obligation.} Stage-1 engine builds the
$E_d$-FA from the Kontsevich--Tamarkin side (primary source:
Kontsevich 1999 \textit{Operads and motives in deformation
quantization}; Tamarkin 2003 \textit{Action of the Grothendieck--Teichm\"uller
group on the operad of little disks}); Stage-2 engine builds the
$E_1$-chiral shadow from the factorisation-homology side (primary
source: Ayala--Francis--Tanaka 2017 \textit{Factorization
homology of stratified spaces}; Costello--Gwilliam \textit{Factorization
algebras in quantum field theory} 2021). Decorator verifies pairwise
disjointness, confirms the PTVV shift $(2-d)$ via Pantev--To\"en--Vaqui\'e--Vezzosi
2013 primary-source evaluation on each $d$, and cross-verifies the
Dunn--Lurie native-level dispatch from Lurie $\mathrm{HA}.5.1.2.2$.

\subsection{K3 Hall--Drinfeld chiral-bialgebra equivalence}
\label{v4-subsec:k3-hall-drinfeld-equivalence}

\[
 \mathrm{Sp}^{\mathrm{ch}}_{K3,E}(\Phi^{\mathrm{FA}}_3(\mathrm{Perf}(K3\times E)))
 \;\simeq\; \mathbf H_{\Delta_5}
\]
is an equivalence at the chiral-bialgebra level (not only
graded-dimension level). Six construction routes on $K3\times E$
(Borcherds lift, Mukai-pairing orthogonal complement, McKay quiver,
Maulik--Okounkov instanton, $6d$ hCS factorisation homology,
Costello $5d$ hCS equivariant uplift) form a common limit cone.

\noindent\emph{Realization obligation.} Six disjoint engines, one per
route, each computing the chiral-bialgebra structure on
$\Phi_3(D^b(K3\times E))$; decorator verifies all six outputs are
naturally isomorphic. The Fake-Monster rank-obstruction decorator
raises $\texttt{IndependentVerificationError}$ on any engine that
attempts to realise $\mathrm{II}_{25,1}$-Leech-lattice chiral data on
a compact CY$_3$: the bound
$h^{1,1}(X) \le h^{1,1}(\mathrm{fibre}) + 2h^{0,2}(\mathrm{fibre}) \le 22 < 24$
is enforced as a decorator assertion.

\subsection{CoHA-to-\texorpdfstring{$W_{1+\infty}$}{W1+inf} triangle with two
\texorpdfstring{$\lambda$}{lambda}-parameters}
\label{v4-subsec:coha-triangle-two-lambda}

$\mathrm{CoHA}(\mathbb{C}^3) = Y^+(\hat{\mathfrak{gl}}_1)$ primitive (Schiffmann--Vasserot
2013); Drinfeld double $Y(\hat{\mathfrak{gl}}_1)$ affine Yangian of
$\mathfrak{gl}_1$ in Drinfeld currents (Tsymbaliuk 2017);
$W_{1+\infty}$ via $\mathrm{ev}_\lambda$ evaluation (Gaiotto--Rap\v c\'ak
2017). Two $\lambda$-parameters are distinguished at all times:
$\lambda_{\mathrm{Tr}} = (\varepsilon_1+\varepsilon_2)/\varepsilon_3$
(truncation, fixed to $-1$ under the CY$_3$ slice) versus $\lambda_W$
(Gaiotto--Rap\v c\'ak central-charge, free). $\mathrm{CoHA}(\mathbb{C}^3)$
and $W_{1+\infty}$ are not equal as algebras.

\noindent\emph{Realization obligation.} Three disjoint engines:
CoHA Euler characteristic (Kontsevich--Soibelman 2008); Yangian PBW
character (Drinfeld 1987); $W_{1+\infty}$ vacuum module character
(Frenkel--Kac--Radul--Wang 1995 \textit{$W_{1+\infty}$ and
$W(\mathfrak{gl}_N)$ with central charge $N$}). Decorator verifies
the $\lambda$-parameter discipline: any engine conflating
$\lambda_{\mathrm{Tr}}$ and $\lambda_W$ raises
$\texttt{IndependentVerificationError}$.

\subsection{Three-tier topologisation discipline}
\label{v4-subsec:three-tier-topologisation}

Tier~I cohomological and Tier~II chain-level on quasi-isomorphic
models are unconditional. Tier~III strict chain-level on the original
complex is closed for classes $\mathsf G, \mathsf L, \mathsf C$ and
open for class $\mathsf M$ (the F3 frontier). Sugawara explicit at
$V_1(\mathfrak{sl}_2)$:
$T_{\mathrm{Sug}} = (1/6)(\mathord{:}J^0J^0\mathord{:}
+ \mathord{:}J^+J^-\mathord{:} + \mathord{:}J^-J^+\mathord{:})$,
$G_{\mathrm{Sug}} = (1/3)\sum_a \mathord{:}\bar c_a J^a \mathord{:}$,
$[Q_{\mathrm{tot}}, G_{\mathrm{Sug}}] = T_{\mathrm{Sug}}$ on BRST
cohomology.

\noindent\emph{Realization obligation.} Three engines per class, one
per tier: Tier~I (Feigin--Frenkel 2011 cohomological $E_3$ on
$H^\ast(\mathrm{Obs}_{\mathrm{hCS}}^{\mathrm{BV}})$); Tier~II (Fresse 2017
Theorem~$12.3.\mathrm{A}$ homotopy transfer); Tier~III (explicit
chain-level antighost primitive per archetype). Decorator verifies
pairwise disjointness of the three tiers' source sets and records
the class-$\mathsf M$ Tier~III status as conditional pending F3
resolution.

\subsection{Khan--Zeng finite-jet BV/PVA lane}
\label{v4-subsec:khan-zeng-finite-jet-lane}

For finite-type freely generated nonlinear finite-jet PVAs, Vol~II
constructs the shifted-cotangent BV action on the half-space and
identifies the classical master equation with the PVA Hamiltonian
condition. This is a constructed classical statement. The all-loop
quantum master equation, reflected weight identity, boundary vertex
algebra, and \(E_3\)-lift are conditional on the analytic SDR package:
finite-jet quotient compatibility, image-choice Stokes cancellation,
field-parity bookkeeping, and self-image renormalisation.

\noindent\emph{Realization obligation.} The classical engine builds
the shifted-cotangent BV action from the PVA Hamiltonian density and
checks CME equality against the lambda-bracket Hamiltonian condition.
The quantum engine is not registered as realized until it supplies
the analytic SDR on every jet-weight quotient, proves compatibility
in the inverse limit, and verifies the reflected weight identity
independently of the classical CME derivation. The decorator records
two statuses: constructed classical realization for CME/PVA, and
conditional quantum realization for QME/boundary-VA/\(E_3\).

\subsection{Joyce--KPS compact Calabi--Yau threefold lane}
\label{v4-subsec:joyce-kps-compact-cy3}

For a generic smooth projective Calabi--Yau threefold \(X\), Vol~III
uses Joyce's vertex algebra \(V_X\) on the derived moduli stack and
the Kontsevich--Pandharipande--Soibelman orientation to place MNOP in
the \(E_2\)-centre of the \(E_3\) factorisation algebra on the
constructed module surfaces. The \(S^3\)-framing statement for
generic compact Calabi--Yau Lagrangians is chain-level on the
Costello--Paquette defect-chiral model. A comparison with the global
Hall--Borcherds or Drinfeld envelope is an additional bridge, not a
source of the local construction.

\noindent\emph{Realization obligation.} The compact-CY3 engine
checks the Joyce \(V_X\) construction and KPS orientation data
against the MNOP centre automorphism. A separate chain-level engine
checks the \(S^3\)-framing through the defect-chiral model. A third
comparison engine may test Hall--Borcherds/Drinfeld compatibility,
but the decorator forbids using that bridge as the proof source for
the Joyce--KPS construction itself.

\subsection{Post-Tate Hadamard support and Meyer graph dual}
\label{v4-subsec:post-tate-hadamard-meyer}

The arithmetic spectral-flow branch separates the critical-line
ordinate support
\[
 \Gamma_\xi^{\mathrm{crit}}
 = \{\gamma\in \mathbb R:\xi(1/2+i\gamma)=0\}
\]
from the full Hadamard divisor. Multiplicities are forgotten in this
support. The ordinary Meyer graph topology does not admit a non-zero
continuous graph-dual functional supported on
\(\Gamma_\xi^{\mathrm{crit}}\), even after finite-jet residue data
are allowed. The obstruction is functional analytic: the graph dual
is represented through the resolvent chart by \(L^2\)-data, while a
locally finite critical-line support has measure zero.

\noindent\emph{Realization obligation.} The no-go engine constructs
the ordinary Meyer graph dual after the post-Tate quotient and proves
the \(L^2\)-support obstruction. The surviving-route decorator does
not register a point-residue proof of A--TP. It registers an open
ambient: a rigged, Paley--Wiener, de Branges, reproducing-kernel,
nonlocal \(L^2\), or BV--BFV boundary topology must construct a
continuous Hadamard trace-and-jet map
\(\Phi_\xi\to \ell^2(\Gamma_\xi^{\mathrm{crit}},w)\), prove
post-Tate compatibility and adjoint-domain compatibility, and show
that the closed condition is not the zero divisor inserted by hand.

\subsection{Open frontiers F1--F10 as realization queue}
\label{v4-subsec:open-frontiers-realization-queue}

The ten programme-wide open frontiers are the realization functor's
remaining domain: (F1) logarithmic $\mathcal{W}(p)$ triplet tempering;
(F2) periodic CDG for non-simply-laced admissible levels;
(F3) original-complex Tier~III for class~$\mathsf M$;
(F4) super-complementarity canonical pairing;
(F5) irregular-singular KZB at $\overline{\mathcal{M}}_{g,n}$ boundaries;
(F6) Theorem~B at nodal boundary without Koszul hypothesis;
(F7) MC4 completion / H3 failure regime;
(F8) Stage-1 chain level at $d \ge 4$;
(F9) category-level $E_d$-formality at $d \ge 4$;
(F10) bracket-level BPS Lie algebra on $K3\times E$.

When any of F1--F10 closes in Vol~I--III, its realization pair
$\mathrm{Real}(X, T) = (d, e)$ enters the Vol~IV campaign. Until it
closes, the Vol~IV ledger records it at its present scope.
