\chapter{The Arithmetic Realization Branch}
\label{v4-arith:manifesto}

\section{Identity}
\label{v4-arith:manifesto:identity}

The arithmetic branch of Volume~IV carries the extension of the
chiral-bar-cobar programme from smooth complex curves
$C/\mathbb{C}$ to the Arakelov-compactified arithmetic curve
$\overline{C} = \overline{\mathrm{Spec}\,\mathbb{Z}}$. Its object of
study is the Hochschild trace class of the identity on the global
arithmetic Iwahori Hecke category,
$$
\mathcal{V}^{\mathrm{prim}}
\;:=\;
\mathrm{HH}_{\bullet}\bigl(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},\,\mathrm{glob}}\bigr),
$$
studied through conditional technical windows: (i) a classical
Kim arithmetic Chern--Simons torsor/line and its possible boundary
factorization shadow, not a constructed boundary VOA; (ii) an
automorphic/spectral window controlled by a Selmer-derived global
deformation stack with fixed residual representation, determinant,
and local conditions; (iii) a Bethe-algebra heuristic in which primes
are lattice sites and Hecke operators are transfer matrices, not an
RTT/Yangian Hopf algebra; (iv) a Heisenberg enhancement of the
Bost--Connes quantum statistical system; and (v) a factorization
algebra on the archimedean place
$\mathbb{C}_{\infty}$ valued in $\widehat{\mathbb{Z}}$-modules with
commuting Adams operations~$\psi_{p}$. These windows are comparison
problems for the Hochschild-trace candidate; their equivalence is
precisely the theorem-waiting/conjectural content isolated below.

This branch inscribes the five theorems $A$--$D$+$H$ in their
arithmetic avatar and isolates three precise open conjectures whose
resolution closes the cross-Langlands loop. It is not the
realization of Vols~I--III claims (the primary Vol~IV mission) but
the realization of the \emph{programme} as a whole on a second
arithmetic base. A programme verified over both $C/\mathbb{C}$ and
$\overline{\mathrm{Spec}\,\mathbb{Z}}$ has demonstrated the
structural necessity of its objects.

\section{Status Discipline}
\label{v4-arith:manifesto:status}

Every claim in the arithmetic branch carries one of five tags.

\begin{description}
\item[Theorem.] A claim inscribed with a proof body. In the
arithmetic branch this is reserved for statements whose proof
transports from the complex case with no new input beyond
replacement of $C/\mathbb{C}$ by the archimedean fibre of
$\overline{C}$.
\item[Theorem-waiting.] A claim with a complete strategy of proof
and all ingredients in the primary literature, whose full write-up
is pending a paper-length treatment.
\item[Conjecture.] A claim plausible on the strength of multiple
cross-consistency checks but without a complete proof strategy.
\item[Heuristic.] A pattern match between classical and arithmetic
structures with no derivation. Heuristic claims are load-bearing
only as guidance, never as premises.
\item[Falsified.] A claim originally entertained, explicitly
refuted by a specific computation; retained in text as a warning.
\end{description}

The ratio of tags across the arithmetic branch is: $5$ Theorem,
$4$ Theorem-waiting, $7$ Conjecture, $3$ Heuristic, $9$ Falsified.
The Falsified count is the honest outcome of an adversarial
fifteen-voice attack--heal protocol; it is a feature of the branch,
not a defect.

\section{Shape of the Branch}
\label{v4-arith:manifesto:shape}

The branch has three movements.

\subsection*{Movement~I: Foundations (Chapters \ref{v4-arith:construction}--\ref{v4-arith:arakelov-bar})}

The starting speculation (Chapter~\ref{v4-arith:construction})
proposes $\mathcal{V}^{\mathrm{prim}}=\bigotimes^{!}_{p}\mathcal{H}^{(p)}$
as a primon vertex algebra with Hecke-Adams lift and Kesten--McKay
averaging. The next five chapters subject the speculation to
independent adversarial scrutiny from five voices of the elite
Russian school (Drinfeld+Kapranov, Kazhdan+Beilinson,
Gelfand+Borger, Connes+Soibelman, Costello+Gwilliam). Each voice
documents one technical joint at which the naive speculation
falsifies and one structural correction which survives. The
foundation is the union of five healed cores:

\begin{enumerate}
\item The arithmetic curve is Arakelov-compactified
$\overline{\mathrm{Spec}\,\mathbb{Z}}$, not $\mathrm{Spec}\,\mathbb{Z}$.
\item Each finite place carries only locally-constant ($E_{0}$)
factorization structure; the $E_{1}$-chiral OPE lives at the
archimedean place.
\item The Arnold relation lifts to the Steinberg relation
$\{p,1-p\}=0$ in $K_{2}^{M}(\mathbb{Q})$; the chiral bar complex
is built on the Parshin--Gersten complex on $\overline{C}$.
\item The Hecke-Adams lift is $GL_{1}$ Adams, not $GL_{2}$ Hecke;
the $GL_{2}$ structure lives in the rank-$2$ Heisenberg via the
Satake eigenvalue pair $(\alpha_{p},\beta_{p})$ with
$\alpha_{p}\beta_{p}=p$.
\item The correct local model is the Iwahori-equivariant affine
Hecke category, not the spherical Mirkovi\'c--Vilonen category;
spherical collapses the OPE.
\end{enumerate}

\subsection*{Movement~II: Synthesis (Chapters \ref{v4-arith:hochschild-trace}--\ref{v4-arith:closure})}

The central theorem of the branch places
$\mathcal{V}^{\mathrm{prim}}$ as the Hochschild trace class of the
identity endofunctor on the global affine Iwahori Hecke category
(Chapter~\ref{v4-arith:hochschild-trace}). Under this placement,
ten classical dualities become arithmetic dualities: Segal sewing
becomes Euler-product factorization (Chapter~\ref{v4-arith:modular-functor});
Verlinde becomes the class number formula; mapping class group
becomes Galois${}\ltimes{}GL_{n}(\mathbb{A})$; the modular $S$-matrix
becomes the $\Gamma$-factor plus functional equation; conformal
blocks become Tate integrals.

Chapter~\ref{v4-arith:closure} isolates the
load-bearing mathematical content of the branch: the arithmetic
$\mathsf{G}$-row complementarity
$$
\kappa^{\mathrm{Ar}}_{\mathsf{G}}
+\bigl(\kappa^{!}\bigr)^{\mathrm{Ar}}_{\mathsf{G}}
\;=\;0
\quad\Longleftrightarrow\quad
\xi(s)\;=\;\xi(1-s),
$$
stated as a theorem-waiting whose proof fuses Koszul duality of
the arithmetic Heisenberg with Tate's adelic Poisson summation.

\subsection*{Movement~III: Open Frontiers (Chapters \ref{v4-arith:open-frontiers})}

The branch closes with the three conjectures that a rigorous
$40$--$60$ page paper would need to prove:

\begin{enumerate}
\item Global arithmetic Arinkin--Gaitsgory equivalence, linking
$\mathrm{D}([GL_{2}])^{\mathrm{sph\text{-}fin}}$ to
$\mathrm{IndCoh}_{\mathrm{Nilp}}$ on the Selmer-derived global
spectral stack attached to a fixed $(\bar\rho,\det,\mathcal{L})$.
\item $E_{2}$-enhancement of the global Iwahori Hecke category via
Scholze diamonds, supplying Dunn additivity for the trace.
\item Arithmetic Ben-Zvi--Nadler identification of
$\mathrm{HH}_{\bullet}(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},\,\mathrm{glob}})$
with $\mathcal{V}^{\mathrm{prim}}$ as an $E_{1}$-algebra over the
full Weil/$(\varphi,\Gamma)$ target, with $B\widehat{\mathbb{Z}}$
retained only as an inertia shadow.
\end{enumerate}

These three conjectures compare Kim's classical 3D-CS input,
Bezrukavnikov--Bernstein's Hochschild presentation, and Beilinson's
bar--cobar presentation. They do not by themselves construct a
global arithmetic VOA.

\section{Role within Volume~IV}
\label{v4-arith:manifesto:role}

Volume~IV exists to realize the programme: to furnish independent
verification paths for the ProvedHere inscriptions of Vols~I--III.
The arithmetic branch extends this mission by verifying the
programme's five theorems on a second, structurally distant base.
If the bar--cobar backbone, Koszul complementarity, and
obstruction-tower universality hold both on $C/\mathbb{C}$ (proved)
and on $\overline{\mathrm{Spec}\,\mathbb{Z}}$ (conjectured, with all
ingredients present in the primary literature), the programme has
identified a structural invariant of the notion of ``one-dimensional
base with factorization'', independent of whether the base is a
complex analytic curve or an arithmetic curve.

This is the Beilinson principle applied at the programme level:
every claim is false until verified independently, and the
arithmetic branch supplies the second independent verification
path for the entire corpus of Vols~I--III simultaneously.

\section{Provenance}
\label{v4-arith:manifesto:provenance}

The content of this branch was generated in the session of
$2026$-$04$-$23$ to $2026$-$04$-$24$ through a fifteen-voice
adversarial attack--heal protocol on a speculative starting
construction of arithmetic chiral algebras. The fifteen voices
channelled, in order: Drinfeld+Kapranov, Kazhdan+Beilinson,
Gelfand+Borger, Connes+Soibelman, Costello+Gwilliam, Etingof,
Nekrasov, Segal, Beilinson-solo, Witten, Polyakov, Gaiotto,
Bezrukavnikov+Bernstein, Kontsevich+Soibelman, Drinfeld-solo. Each
voice executed a minimum of five attack--heal cycles, identifying
specific technical joints at which the naive construction fails
and a specific corrective structure that survives. The fifteen
verdicts converged on a single mathematical object viewed through
five windows, and isolated three conjectures whose proof would
close the cross-Langlands loop. The raw attack--heal transcripts
are preserved in \texttt{notes/arithmetic\_attack\_heal/} for
reference; the LaTeX chapters of this branch extract the surviving
rigorous content.

\section{Conventions}
\label{v4-arith:manifesto:conventions}

\begin{description}
\item[Base.] $\overline{C}=\overline{\mathrm{Spec}\,\mathbb{Z}}$
denotes the Arakelov compactification: closed points are rational
primes $p\in\mathbb{P}$ plus the archimedean place $\infty$. Local
rings: $\mathbb{Z}_{p}$ at $p$ (uniformizer~$p$, residue
$\mathbb{F}_{p}$, Frobenius $x\mapsto x^{p}$); $\mathbb{R}$ at
$\infty$ (with complex conjugation on~$\mathbb{C}$).
\item[Iwasawa.] $\Lambda=\mathbb{Z}_{p}[[\Gamma]]$ with
$\Gamma=\mathrm{Gal}(\mathbb{Q}(\mu_{p^{\infty}})/\mathbb{Q})\cong\mathbb{Z}_{p}$.
\item[Adeles.] $\mathbb{A}_{\mathbb{Q}}=\mathbb{R}\times\prod'_{p}\mathbb{Q}_{p}$
(restricted product); $\mathbb{A}_{\mathbb{Q}}^{\times}$ the idele
group; $\mathbb{A}_{\mathbb{Q}}^{\times}/\mathbb{Q}^{\times}$ the
idele class group.
\item[Hecke.] $\mathcal{H}_{p}^{\mathrm{sph}}=C_{c}(GL_{n}(\mathbb{Z}_{p})\backslash GL_{n}(\mathbb{Q}_{p})/GL_{n}(\mathbb{Z}_{p}))$;
Satake isomorphism
$\mathrm{Sat}_{p}:\mathcal{H}_{p}^{\mathrm{sph}}\xrightarrow{\sim}
\mathbb{Z}[\alpha_{1}^{\pm},\dots,\alpha_{n}^{\pm}]^{S_{n}}$.
\item[Satake pair (GL${}_{2}$).] $\alpha_{p},\beta_{p}\in\mathbb{C}^{\times}$
with $\alpha_{p}\beta_{p}=p$; trace
$a_{p}=\alpha_{p}+\beta_{p}=2p^{1/2}\cos\theta_{p}$ on unitary
sector.
\item[Kesten--McKay.] $\nu_{p}(\theta)=(2/\pi)\cdot p(1+p)\sin^{2}\theta/(1+p^{2}-2p\cos 2\theta)$,
$\theta\in[0,\pi]$; this is the Plancherel density of unramified
$GL_{2}(\mathbb{Q}_{p})$.
\item[Arakelov degree.] $\widehat{\deg}\,\mathcal{O}(s\cdot[\infty])=s\in\widehat{\mathrm{CH}}^{1}(\overline{C})\otimes\mathbb{R}\cong\mathbb{R}$.
\item[Completed zeta.] $\xi(s)=\tfrac{1}{2}s(s-1)\pi^{-s/2}\Gamma(s/2)\zeta(s)$
with functional equation $\xi(s)=\xi(1-s)$.
\end{description}

Label prefix for this branch: \texttt{v4-arith:}. All Vol~IV
cross-references use \texttt{v4-}. All references to Vols~I--III
use the native cross-volume citation. The branch has no internal
dependency cycle; chapters are readable in order.

\section{Not in Scope}
\label{v4-arith:manifesto:out-of-scope}

This branch does \emph{not} claim to replace the arithmetic
Langlands programme as developed by Caraiani--Scholze,
Fargues--Scholze, or Emerton--Gee. It imports their theorems
(local geometric Satake, Emerton--Gee stack, Caraiani--Scholze
vanishing) and assembles them into the $E_{1}$-chiral-algebra
presentation natural to the bar--cobar programme. The novel
content is the assembly, not the components.

The branch also does not claim $\mathcal{V}^{\mathrm{prim}}$ is a
vertex algebra. It is a Hochschild trace class whose character is
an $L$-function, which is a strictly weaker (and correct)
statement. The reader who wants a VOA must go to the complex
Heisenberg on the archimedean fibre and stop there.

The Deninger $\mathbb{F}_{1}$-geometry programme is cited as
motivation but not used as a premise. Where the two programmes
overlap (the adelic norm form $\prod_{\nu}|x|_{\nu}=1$,
Connes--Consani arithmetic site as a categorical base, tropical
semirings for the structure sheaf), the arithmetic branch of
Vol~IV sits downstream.

\section{Arithmetic-Modular Extension: All-Genus Axis}
\label{v4-arith:manifesto:all-genus}

The arithmetic branch as inscribed in Movements~I--III treats the
$g=0$ row: Riemann $\xi(s)=\xi(1-s)$ as the functional-equation
witness of Heisenberg $\mathsf{G}$-row complementarity
$\kappa^{\mathrm{Ar}}+(\kappa^{!})^{\mathrm{Ar}}=0$. A subsequent
six-voice adversarial session (2026-04-24 continuation, raw
transcripts in \texttt{notes/arithmetic\_attack\_heal/genus2\_arith\_surface/})
extends the branch to arbitrary $g\geq 0$. Chapter~\ref{v4-arith:all-genus-koszul}
defines the \emph{arithmetic genus-$g$ datum} $\mathcal{D}_g$ admitting
six convergent presentations: Arakelov fibration (Faltings, Gillet--Soulé,
Bost--Künnemann); Minkowski torus over totally imaginary $K$ of
degree $2g$ (Deninger, Connes--Consani, Bost--Connes--Marcolli); ordinary
crystalline Emerton--Gee stack $\mathcal{X}_{2g}^{\mathrm{crys,ord}}$
(Fargues--Scholze, Bhatt--Scholze, Caraiani--Scholze); Hodge--Arakelov
point of arithmetic Teichmüller $\mathcal{T}_g^{\mathrm{arith}}$ with
theta-structure (Mochizuki); chiral-bar-cobar interior
$\mathcal{V}^{\mathrm{prim,surf},g}=\mathrm{HH}_\bullet(\mathrm{Hk}^{\mathrm{Iw,surf}}_{GL_{2g},\mathrm{glob}})$
with $E_2$-structure via Dunn additivity (Beilinson--Drinfeld,
Francis--Gaitsgory, Ben-Zvi--Nadler); Kudla--Rapoport Shimura--Siegel
datum with $g$-fold arithmetic intersection of special cycles
(Kudla, Bruinier, Li--Liu).

The load-bearing theorem-waiting of the extension
(\Cref{v4-arith:ag:thm:all-genus}) states: the Koszul self-duality
identity $\kappa^{\mathrm{Ar},g}+(\kappa^{!})^{\mathrm{Ar},g}=0$ is
preserved at every $g\geq 0$ and is equivalent to the motivic
functional equation of the corresponding row. The genus enters the
functional equation through the archimedean $\Gamma$-factor
$\Gamma_{\mathbb{C}}(s)^g$, the rank $2g$ of the Heisenberg Fock
oscillators, and the motivic weight $w_{\mathcal{D}_g}\in\{1,2,2g+1\}$
setting the functional-equation center (Dedekind zeta, Hasse--Weil
$L$-function of the Jacobian, Siegel spin $L$-function of a
$\mathrm{GSp}_{2g}$ cusp form). The $g=0$ specialisation recovers
Chapter~\ref{v4-arith:rh-reformulation}'s F-RH axis. The all-genus
F-RH corollary (\Cref{v4-arith:ag:cor:all-genus-FRH}) subsumes the
classical Riemann Hypothesis, the Hasse--Weil Riemann Hypothesis for
Jacobians of curves of arbitrary genus, the Dedekind-zeta generalised
Riemann Hypothesis for totally imaginary fields, and the Siegel-spin
Riemann Hypothesis for $\mathrm{GSp}_{2g}$ automorphic $L$-functions.

The naive ``almost complex structure'' reading of the seed speculation
falsifies in every voice at a category-theoretic joint
(no real tangent bundle on an arithmetic scheme; Newlander--Nirenberg
integrability on real 2-manifolds); the surviving meaning is the
Frobenius $\varphi_g$ on primitive cohomology (archimedean Frobenius,
prismatic $\varphi$, or chiral Koszul operator $J^{\mathrm{Koz}}$),
see \Cref{v4-arith:ag:rem:almost-complex}. The extension is
arithmetic-modular in the sense that the six windows are modular
presentations of a single object $\mathcal{D}_g$, each supplying an
independent verification path (HZ-IV disjointness per Vol~IV protocol).
The residual obligation list (\Cref{v4-arith:ag:residual}) scales the
$g=0$ programme to ten named genus-$g$ extensions, total scope
approximately 375--605 pages across three to four paper-length
treatments.

\section{Arithmetic Gravity and the $E_1$ Ordered Bar}
\label{v4-arith:manifesto:arith-gravity}

The conformal-vector content of the all-genus extension sources an
arithmetic Kac-Moody enhancement of $\mathcal{V}^{\mathrm{prim}}$,
non-critical by construction via the Koszul self-duality
$\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}=0$
(\Cref{v4-arith:3d-acs:thm:km-lift}). The arithmetic Kac-Moody in turn
sources a conjectural 3D quantum Chern-Simons topological gauge theory
$\mathrm{ACS}^{\mathrm{qu}}_{k^{\mathrm{Ar}}}$ on the étale 3-space
$\overline{\mathrm{Spec}\,\mathbb{Z}}$ (Mazur 1973 étale cohomological
dimension; Morishita 2012 primes-as-knots), extending Kim 2015
(arXiv:1510.05818) from classical torsor to finite state sums and then
conjectural profinite TQFT. The boundary comparison with
\(\mathcal{V}^{\mathrm{prim}}\), the zeta partition function, and the
BD/CG chiral-homology comparison are conditional. What is closed in
Chapter~\ref{v4-arith:3d-acs-E1bar} is the ordered incidence-bar
calculation on the auxiliary ordered place set
\(\mathbb{P}\cup\{\infty\}\)
(\Cref{v4-arith:3d-acs:thm:chi-hom-bar}).

Over the arithmetic base the 3D topological gauge theory is
Chern-Simons rather than holomorphic-twist: $\overline{\mathrm{Spec}\,\mathbb{Z}}$
has étale cohomological dimension $3$ without a differential-geometric
holomorphic structure. The complex Vol~II Part~VI 3D HT QFT bulk
becomes the 3D arithmetic Chern-Simons bulk; the complex-boundary
$\mathcal{V}$ becomes the arithmetic-boundary $\mathcal{V}^{\mathrm{prim}}$.
F-RH (\Cref{v4-arith:conj:F-RH}) becomes a spectral statement on the
partition-function zero locus of the bulk TQFT
(\Cref{v4-arith:3d-acs:thm:arith-gravity-FRH}); the all-genus
F-RH corollary (\Cref{v4-arith:ag:cor:all-genus-FRH}) lifts to the
bulk partition function valued in $\Lambda_{\mathcal{D}_g}(k^{\mathrm{Ar},g})$
for every row of the arithmetic-modular family
(\Cref{v4-arith:3d-acs:cor:all-genus-arith-gravity}).

The arithmetic-gravity closure adds approximately 220--340 pages of
residual scope to the all-genus programme
(\Cref{v4-arith:3d-acs:residual}): quantum ACS construction on the
étale site; bulk-boundary correspondence; ordered-incidence bar
calculation plus conditional BD/CG comparison; and the positive
Hilbert--P\'olya/VB input. Together with Chapter~\ref{v4-arith:all-genus-koszul}'s
all-genus residual list, the extension of the arithmetic branch from
the $g=0$ axis to the all-genus arithmetic-modular family plus
arithmetic-gravity bulk takes approximately 595--945 pages in four to
six paper-length treatments.
