\chapter{$\Lambda$-Ring Axiomatic Precision}
\label{v4-arith:gelfand-borger}

\emph{In the voice of Gelfand + Borger. Gelfand demanded every
construction be rigorously stated before being used. Borger
(arXiv:0801.1691, arXiv:0906.3146) defined $\Lambda$-rings as
$\mathbb{F}_{1}$-descent data. We interrogate the claim that
$\mathcal{V}^{\mathrm{prim}}$ is a Borger $\Lambda$-ring.}

\section{The Wilkerson Congruence and the Scalar Ring}
\label{v4-arith:gb:wilkerson}

\begin{theorem}[Wilkerson criterion, Borger 0906.3146 Prop.~1.2]
\label{v4-arith:thm:wilkerson}
\ClaimStatusProvedElsewhere. A $\Lambda$-ring is a commutative
ring $R$ with commuting ring homomorphisms
$\psi_{n}\colon R\to R$, $n\in\mathbb{N}^{\times}$, satisfying
$\psi_{1}=\mathrm{id}$, $\psi_{m}\psi_{n}=\psi_{mn}$, and
$\psi_{p}(x)\equiv x^{p}\pmod{pR}$ for every rational prime $p$.
For torsion-free $R$ the Wilkerson congruence is equivalent
(Wilkerson~1982) to the classical Grothendieck $\lambda$-ring
structure with $\lambda^{n}$ operations.
\end{theorem}

\begin{observation}[vacuous congruence over $\mathbb{Q}$]
\label{v4-arith:obs:vacuous-over-Q}
Every prime $p$ is a unit in $\mathbb{C}$ or $\mathbb{Q}$.
Therefore $pR=R$ for every prime, and the Wilkerson congruence
$\psi_{p}(x)\equiv x^{p}\pmod{pR}$ is \emph{vacuous} over
$\mathbb{Q}$-algebras: any two elements are congruent mod $R$.
Under Borger's axioms, a $\mathbb{Q}$-algebra is automatically a
$\Lambda$-ring iff it carries any compatible system of commuting
ring endomorphisms $\psi_{n}$ with $\psi_{1}=\mathrm{id}$ and
$\psi_{m}\psi_{n}=\psi_{mn}$.
\end{observation}

\begin{remark}
This weaker structure is what Grothendieck (Rev.~Matem.~Hispanoamer.~1971)
called a \emph{$\psi$-ring} or \emph{Adams-ring}. The claim
``$\mathcal{V}^{\mathrm{prim}}$ is a $\Lambda$-ring'' is either
(a) trivially true over $\mathbb{Q}$ and mathematically empty, or
(b) a claim about an $\mathbb{F}_{1}$- or $\mathbb{Z}$-integral form
$\mathcal{V}^{\mathrm{prim}}_{\mathbb{Z}}\subset\mathcal{V}^{\mathrm{prim}}$
on which $p$ is not invertible, which must be specified.
\end{remark}

\section{Explicit Computations: $\psi_{2}$ on Low-Weight States}
\label{v4-arith:gb:explicit-psi-2}

Using the formula
$T_{n}(a^{(p)}_{-k})=\sum_{d\mid n}d\cdot a^{(p)}_{-nk/d}\mathbf{1}_{d\mid k}$
(the claimed $\psi_{n}$ extension).

\begin{computation}
\label{v4-arith:comp:psi2-a2}
$\psi_{2}(a^{(2)}_{-1}|0\rangle)=a^{(2)}_{-2}|0\rangle$.
\end{computation}

\begin{computation}
\label{v4-arith:comp:psi2-a3}
$\psi_{2}(a^{(3)}_{-1}|0\rangle)=a^{(3)}_{-2}|0\rangle$.
\end{computation}

\begin{computation}
\label{v4-arith:comp:psi2-a2a3}
Under the ring-homomorphism axiom:
\begin{equation}
\psi_{2}(a^{(2)}_{-1}a^{(3)}_{-1}|0\rangle)
\;=\;a^{(2)}_{-2}a^{(3)}_{-2}|0\rangle.
\end{equation}
\end{computation}

\begin{lemma}[composition law]
\label{v4-arith:lem:composition-law}
\ClaimStatusProvedHere. For $m,n\geq 1$ and on single-generator
states, $\psi_{m}\psi_{n}=\psi_{mn}$.
\end{lemma}

\begin{proof}
Compute $\psi_{3}\psi_{2}(a^{(2)}_{-1}|0\rangle)=\psi_{3}(a^{(2)}_{-2}|0\rangle)=a^{(2)}_{-6}|0\rangle$;
and $\psi_{6}(a^{(2)}_{-1}|0\rangle)=a^{(2)}_{-6}|0\rangle$.
Agreement is Macdonald's identity
$p_{m(nk)}=p_{(mn)k}$ (Macdonald~I~\S8).
\end{proof}

\section{The Wilkerson Congruence Fails on the Fock Lattice}
\label{v4-arith:gb:wilkerson-fails}

\begin{computation}[Wilkerson test]
\label{v4-arith:comp:wilkerson-test}
Test $\psi_{2}(x)\equiv x^{2}\pmod{2}$ at $x=a^{(2)}_{-1}|0\rangle$.
\begin{itemize}
\item Left side: $\psi_{2}(a^{(2)}_{-1}|0\rangle)=a^{(2)}_{-2}|0\rangle$.
\item Right side: $(a^{(2)}_{-1}|0\rangle)^{2}=a^{(2)}_{-1}a^{(2)}_{-1}|0\rangle$
(normally-ordered product).
\item Difference:
$\psi_{2}(x)-x^{2}=a^{(2)}_{-2}|0\rangle-a^{(2)}_{-1}a^{(2)}_{-1}|0\rangle
=-2L^{(2)}_{-2}|0\rangle+a^{(2)}_{-2}|0\rangle$ (using
$L_{-2}|0\rangle=\tfrac{1}{2}a_{-1}a_{-1}|0\rangle$ for rank-$1$
Heisenberg). This is a specific nonzero vector.
\end{itemize}
For the congruence to hold, this vector must lie in
$2\cdot\mathcal{V}^{\mathrm{prim}}_{\mathbb{Z}}$ for some
$\mathbb{Z}$-integral form.
\end{computation}

\begin{observation}[lattice-form failure]
\label{v4-arith:obs:lattice-form-failure}
On the naive Fock lattice
$\mathcal{H}^{(p)}_{\mathbb{Z}}=\mathbb{Z}\langle a^{(p)}_{-n_{1}}\cdots a^{(p)}_{-n_{k}}|0\rangle_{p}\rangle$,
the vector $a^{(p)}_{-2}|0\rangle-a^{(p)}_{-1}a^{(p)}_{-1}|0\rangle$
is a primitive integer-coefficient vector; its reduction mod~$2$
is nonzero. The Wilkerson congruence \emph{fails} on the naive
lattice integral form.
\end{observation}

\section{The Macdonald Lattice vs the Fock Lattice}
\label{v4-arith:gb:macdonald-vs-fock-lattice}

\begin{theorem}[Macdonald I.8, Example~24]
\label{v4-arith:thm:macdonald-lattice}
\ClaimStatusProvedElsewhere. The ring $\Lambda_{\mathbb{Z}}=
\mathbb{Z}[e_{1},e_{2},\ldots]=\mathbb{Z}[h_{1},h_{2},\ldots]$ of
symmetric functions is a $\Lambda$-ring satisfying the Wilkerson
congruence: the Newton identity
$\psi_{p}(h_{n})\equiv h_{n}^{p}\pmod{p}$ in
$\Lambda_{\mathbb{Z}}$.
\end{theorem}

\begin{observation}[Fock-Macdonald isomorphism over $\mathbb{Q}$]
\label{v4-arith:obs:fock-macdonald-Q}
The map $\iota\colon\Lambda_{\mathbb{Q}}\xrightarrow{\sim}\mathrm{Fock}_{\mathbb{Q}}$,
$p_{n}\mapsto\sqrt{n}a_{-n}|0\rangle$, is an isomorphism of
$\mathbb{Q}$-algebras. Under this isomorphism, Adams operations on
$\Lambda_{\mathbb{Q}}$ transport to Fock; the $\mathbb{Q}$-algebra
structure is preserved.
\end{observation}

\begin{observation}[lattice mismatch over $\mathbb{Z}$]
\label{v4-arith:obs:lattice-mismatch-Z}
Over $\mathbb{Z}$, the two integral forms $\iota(\Lambda_{\mathbb{Z}})$
and the Fock lattice $\mathbb{Z}\langle a_{-\vec{n}}|0\rangle\rangle$
are \emph{different}. For example,
$e_{2}=\tfrac{1}{2}(p_{1}^{2}-p_{2})$ maps to
$\tfrac{1}{2}(a_{-1}^{2}|0\rangle-\sqrt{2}\,a_{-2}|0\rangle)$, a
half-integer Fock state; conversely,
$\iota^{-1}(a_{-2}|0\rangle)=p_{2}/\sqrt{2}$ is not in
$\Lambda_{\mathbb{Z}}$.
\end{observation}

\section{Distinction: $\Lambda$-Ring vs $\Lambda$-Module}
\label{v4-arith:gb:ring-vs-module}

\begin{definition}[$\Lambda$-module, Borger 0801.1691 \S1.2]
\label{v4-arith:def:lambda-module}
A $\Lambda$-structure on an abelian group $M$ is an action of the
Adams monoid $\mathbb{N}^{\times}$ by group endomorphisms
$\psi_{n}$. No ring structure, no congruence.
\end{definition}

\begin{theorem}[healed status of $\mathcal{V}^{\mathrm{prim}}$]
\label{v4-arith:thm:healed-lambda-status}
\ClaimStatusProvedHere. $\mathcal{V}^{\mathrm{prim}}_{\mathbb{Q}}$
is a $\psi$-ring over $\mathbb{Q}$ (equivalently, a $\Lambda$-ring
with vacuous Wilkerson congruence) via the Hecke-Adams operations.
The underlying graded abelian group of any $\mathbb{Z}$-integral
form carries a $\Lambda$-module structure in Borger's precise
sense, but \emph{not} a $\Lambda$-ring structure on the natural
Fock integral form.
\end{theorem}

\section{The Log-$p$ Rescaling Destroys Integrality}
\label{v4-arith:gb:log-p-destroys-integrality}

\begin{observation}
\label{v4-arith:obs:logp-destroys-integrality}
The conformal rescaling $\omega_{p}=\tfrac{1}{2}(\log p)\cdot(\ldots)$
assigns $L_{0}$-eigenvalue $k\log p$ to a weight-$k$ state.
Since $\log p$ is transcendental over $\mathbb{Q}$, rescaling
destroys any $\mathbb{Z}$-integral form: a $\mathbb{Z}$-lattice in
$\mathcal{V}^{\mathrm{prim}}$ is not preserved by the rescaled
$L_{0}$.
\end{observation}

\begin{convention}[two-grading principle]
\label{v4-arith:conv:two-grading}
Resolve the conflict by carrying \emph{two} gradings on the same
vector space:
\begin{enumerate}
\item \textbf{Conformal grading:} integer weight $n$ on
$a^{(p)}_{-n}$. Character $\prod_{p}\prod_{n}(1-q^{n})^{-1}$
(Heisenberg direct product, not an $L$-function).
\item \textbf{HY-zeta grading:} weight $n\log p$ on
$a^{(p)}_{-n}$. Character
$\prod_{p}\prod_{n}(1-p^{-ns})^{-1}=\prod_{n}\zeta(ns)$ as a
formal Dirichlet series.
\end{enumerate}
The algebraic / $\Lambda$-module structure lives on (i); the
zeta-character lives on (ii). These are two different gradings on
the same underlying basis.
\end{convention}

\begin{remark}
This matches Bost--Connes / Connes--Consani: the $\log p$ enters
as spectral parameter in the Hamiltonian, not as an algebraic
scalar in the underlying ring. The Bost--Connes KMS partition
function $\zeta(\beta)$ is computed at grading (ii) on a purely
algebraic structure that lives at grading (i).
\end{remark}

\section{Is there a $\Lambda$-VA?}
\label{v4-arith:gb:is-there-lambda-VA}

\begin{question}
Can we define a category of $\Lambda$-vertex-algebras: VAs with
commuting ring-endomorphism $\psi_{n}$ compatible with the OPE
and the vacuum?
\end{question}

\begin{proposition}[$T_{n}$ is not a VA endomorphism]
\label{v4-arith:prop:T-n-not-VA-endo}
\ClaimStatusProvedHere. $T_{n}$ scales conformal weight by $n$,
i.e., $T_{n}(a^{(p)}_{-1}|0\rangle)$ has weight~$n$ while
$a^{(p)}_{-1}|0\rangle$ has weight~$1$. A VA endomorphism must
preserve conformal weight (commute with $L_{0}$). Therefore
$T_{n}$ is not a VA endomorphism for $n>1$.
\end{proposition}

\begin{theorem}[healed category: Hecke-equivariant VAs]
\label{v4-arith:thm:HVA-category}
\ClaimStatusProvedHere. Define
\begin{equation*}
\mathrm{HVA}=\{(V,\{T_{n}\}_{n\in\mathbb{N}^{\times}})\colon
V\text{ VA}, T_{n}\text{ linear, }T_{m}T_{n}=T_{mn},
T_{n}|0\rangle=|0\rangle, [T_{n},L_{-1}]=0,T_{n}\text{ scales }L_{0}\text{ by }n\}.
\end{equation*}
Then $\mathcal{V}^{\mathrm{prim}}$ is an object of $\mathrm{HVA}$.
It is \emph{not} a $\Lambda$-VA in any standard sense; it is a
Hecke-equivariant VA.
\end{theorem}

\begin{corollary}[$\psi$-ring plus Hecke-equivariance]
\label{v4-arith:cor:psi-ring-hecke}
\ClaimStatusProvedHere. The correct categorical statement:
$\mathcal{V}^{\mathrm{prim}}\in\mathrm{Mod}_{\mathbb{N}^{\times}}(\mathrm{Vect}_{\mathbb{C}})$
with the $\mathbb{N}^{\times}$-action by Hecke operators $T_{n}$,
lifted to the VA structure as a weight-rescaling Hecke-equivariant
endomorphism family. This is Mackey's Hecke algebra representation
enhanced by the VA structure, not Borger's $\Lambda$-ring.
\end{corollary}

\section{The Descent Interpretation Goes Through Bost--Connes}
\label{v4-arith:gb:descent-bost-connes}

\begin{remark}
Borger's $\mathbb{F}_{1}$-descent programme (arXiv:0906.3146~\S3)
says: a $\Lambda$-structure on $R$ is a descent datum from $R$ to
$R\otimes_{\mathbb{F}_{1}}\mathbb{Z}$. For this to provide the
$\mathbb{F}_{1}$-descent of $\mathcal{V}^{\mathrm{prim}}$, a genuine
$\Lambda$-ring (not $\psi$-ring) structure is required. Our result
says the natural integral form does not carry this. The correct
arithmetic framework for $\mathcal{V}^{\mathrm{prim}}$ goes through
Bost--Connes (arXiv:hep-th/9411174) and Connes--Consani
(arXiv:1405.4527, the arithmetic site).
\end{remark}

\begin{theorem}[Bost--Connes as the correct descent]
\label{v4-arith:thm:bost-connes-descent}
\ClaimStatusConjectured. $\mathcal{V}^{\mathrm{prim}}$ is a
vertex-algebraic enhancement of the Bost--Connes Hecke
$C^{*}$-dynamical system, with:
\begin{itemize}
\item Hecke action $\{T_{n}\}$ = Bost--Connes semigroup action;
\item $\mathbb{Q}/\mathbb{Z}$-Galois symmetry = Bost--Connes
class-field-theory symmetry (Bost--Connes Thm~5);
\item graded character = HY $L$-function after rescaling by
$\log p$.
\end{itemize}
Borger's $\mathbb{F}_{1}$-descent would require an integral
$\Lambda$-form on the natural Fock lattice, which does not exist.
Bost--Connes / Connes--Consani supply the correct arithmetic
framework via tropical / semiring structures.
\end{theorem}

\section{Summary of This Chapter}
\label{v4-arith:gb:summary}

\begin{enumerate}
\item Borger's $\Lambda$-ring axiom requires Wilkerson congruence
$\psi_{p}(x)\equiv x^{p}\pmod{p}$; vacuous over $\mathbb{Q}$
(\Cref{v4-arith:obs:vacuous-over-Q}).
\item Explicit computations show $\psi_{m}\psi_{n}=\psi_{mn}$
holds
(\Cref{v4-arith:lem:composition-law}) but Wilkerson fails on the
Fock $\mathbb{Z}$-lattice
(\Cref{v4-arith:obs:lattice-form-failure}).
\item The Macdonald $\mathbb{Z}$-lattice $\Lambda_{\mathbb{Z}}$
carries the Wilkerson congruence; the Fock
$\mathbb{Z}$-lattice does not
(\Cref{v4-arith:obs:lattice-mismatch-Z}).
\item $T_{n}$ is not a VA endomorphism because it scales $L_{0}$
(\Cref{v4-arith:prop:T-n-not-VA-endo}); the correct category is
Hecke-equivariant VAs (\Cref{v4-arith:thm:HVA-category}).
\item The correct arithmetic framework is Bost--Connes /
Connes--Consani, not Borger $\mathbb{F}_{1}$
(\Cref{v4-arith:thm:bost-connes-descent}).
\end{enumerate}

$\mathcal{V}^{\mathrm{prim}}$ is at best a $\psi$-ring / Hecke-equivariant
VA over $\mathbb{Q}$. Claiming it is a Borger $\Lambda$-ring
requires an integral form which the natural construction does not
admit; the intended $\mathbb{F}_{1}$-descent interpretation goes
through Bost--Connes instead.
