\chapter{Arithmetic $E_{n}$ Formality and CoHA}
\label{v4-arith:kontsevich-soibelman}

\emph{In the voice of Kontsevich + Soibelman. Kontsevich proved
$E_{n}$ formality over $\mathbb{Q}$ (arXiv:q-alg/9709040,
arXiv:math/9904055); Soibelman co-built the cohomological Hall
algebra programme (arXiv:1006.2706). We test arithmetic
$E_{n}$ formality status and the CoHA identification of
$\mathcal{V}^{\mathrm{prim}}$.}

\section{$E_{1}$-Formality Is Automatic over $\mathbb{Z}$}
\label{v4-arith:ks:E1-automatic}

\begin{theorem}[Fresse \emph{Homotopy of Operads}, Vol.~II, Thm~I.4.1.6]
\label{v4-arith:thm:E1-formality-automatic}
\ClaimStatusProvedElsewhere. For any commutative ring $R$,
$H_{\bullet}(E_{1};R)\cong\mathrm{Ass}_{R}$ and the canonical map
$C_{\bullet}(E_{1};R)\to\mathrm{Ass}_{R}$ is an operadic
quasi-isomorphism. $E_{1}$-formality is automatic over $\mathbb{Z}$.
\end{theorem}

\begin{corollary}[ordered $E_{1}$-chiral survives over $\mathbb{Z}$]
\label{v4-arith:cor:ordered-E1-survives}
\ClaimStatusProvedHere. The ordered $E_{1}$-chiral structure on
$\mathcal{V}^{\mathrm{prim}}$; the strict associative product
from the ordered factorization-algebra product; is defined
integrally; no Massey obstruction.
\end{corollary}

\section{$E_{2}$-Formality Fails Integrally}
\label{v4-arith:ks:E2-fails}

\begin{theorem}[Salvatore--Wahl; Cohen LNM~533; Fresse--Willwacher arXiv:1503.08699]
\label{v4-arith:thm:E2-fails-integrally}
\ClaimStatusProvedElsewhere. $H_{\bullet}(E_{2};\mathbb{F}_{p})$
carries non-trivial Dyer--Lashof operations; these obstruct
formality because they vanish on any cohomology-operadic target
but survive on the chain-level operad. Over $\mathbb{Q}$, Tamarkin's
theorem (arXiv:math/9803025) establishes $C_{\bullet}(E_{2};\mathbb{Q})\xrightarrow{\sim}H_{\bullet}(E_{2};\mathbb{Q})=\mathrm{Ger}_{\mathbb{Q}}$,
a $\mathrm{GRT}_{1}(\mathbb{Q})$-torsor.
\end{theorem}

\begin{corollary}[no integral $E_{2}$-enhancement]
\label{v4-arith:cor:no-integral-E2}
\ClaimStatusProvedHere. The $E_{2}$-chiral-centre enhancement of
$\mathcal{V}^{\mathrm{prim}}$ (Drinfeld-centre or Swiss-cheese)
does not extend to $\mathrm{Spec}\,\mathbb{Z}$. It lifts to
$\mathbb{Q}$ as a $\mathrm{GRT}_{1}(\mathbb{Q})$-torsor and to
$\mathbb{Z}[1/N]$ for some finite $N$ determined by the torsion in
$H_{\bullet}(E_{2};\mathbb{Z})$, but not to
$\mathrm{Spec}\,\mathbb{Z}$ itself.
\end{corollary}

\begin{remark}[Kaledin Japanese cocycle]
Kaledin isolates the arithmetic obstruction: for
an associative $\mathbb{Z}$-algebra $A$, the reduction
$A\otimes\mathbb{F}_{p}$ may carry a non-trivial Hochschild
$A_{\infty}$-deformation class; the ``Japanese cocycle''; in
$\mathrm{HH}^{2}(A\otimes\mathbb{F}_{p})/\mathrm{HH}^{2}(A)\otimes\mathbb{F}_{p}$.
This is the first-order obstruction to integral strictification of
the $E_{2}$-enhancement.
\end{remark}

\section{Higher Products Vanish}
\label{v4-arith:ks:higher-products-vanish}

\begin{theorem}
\label{v4-arith:thm:mk-vanish}
\ClaimStatusProvedHere. $A_{\infty}$-higher products $m_{k}$
($k\geq 3$) vanish on $\mathcal{V}^{\mathrm{prim}}$ over
$\mathbb{Z}$, because $H_{\bullet}(E_{1};\mathbb{Z})$ is
torsion-free.
\end{theorem}

\begin{corollary}[strict associativity over $\mathbb{Z}$]
\label{v4-arith:cor:strict-associativity-Z}
\ClaimStatusProvedHere. $\mathcal{V}^{\mathrm{prim}}$ is strictly
associative over $\mathbb{Z}$; not merely $A_{\infty}$. This does
\emph{not} extend to the $E_{2}$-level, where $A_{\infty}$ (or
even $E_{\infty}$) obstructions survive.
\end{corollary}

\section{The Chiral Bracket via Adelic Residue}
\label{v4-arith:ks:chiral-bracket-adelic}

\begin{definition}[arithmetic $\lambda$-bracket]
\label{v4-arith:def:arith-lambda-bracket}
The chiral bracket on $\mathcal{V}^{\mathrm{prim}}$ over
$\overline{C}$ is the Beilinson--Drinfeld $\lambda$-bracket on
$\mathrm{Conf}_{2}(\overline{C})=\overline{C}\times\overline{C}\setminus\Delta$:
\begin{equation}
\{a,b\}_{\mathrm{arith}}(p,q)\;=\;\mathrm{Res}_{p=q}f(p,q)\cdot\log|p-q|_{\infty}^{-1}.
\end{equation}
Each finite prime contributes a discrete residue; the archimedean
place contributes the $|\cdot|_{\infty}$ normalisation. This is
the Lorenzini--Kontsevich adelic-residue package
(Kontsevich--Soibelman arXiv:1303.3253, \S2.4).
\end{definition}

\begin{theorem}[chiral bracket descends adelically]
\label{v4-arith:thm:chiral-bracket-adelic}
\ClaimStatusConjectured. The arithmetic $\lambda$-bracket on
$\mathcal{V}^{\mathrm{prim}}$ is a well-defined adelic residue,
interpreted via Arakelov completion: the $1$-form bundle
$\mathrm{Cot}^{*}_{\mathrm{arith}}$ on
$\mathrm{Conf}_{2}(\overline{C})$ restricted to the punctured
diagonal supports the pairing
$\{\mathcal{V}^{\mathrm{prim}},\mathcal{V}^{\mathrm{prim}}\}_{\mathrm{arith}}\subset\mathcal{V}^{\mathrm{prim}}\otimes_{\mathbb{Z}}\mathrm{Cot}^{*}_{\mathrm{arith}}$.
\end{theorem}

\section{The CoHA Identification Is Conjectural}
\label{v4-arith:ks:CoHA-conjectural}

\begin{theorem}[Kontsevich--Soibelman 1006.2706]
\label{v4-arith:thm:KS-CoHA}
\ClaimStatusProvedElsewhere. For a quiver $Q$ and potential
$W\in\mathbb{C}\langle Q\rangle_{\mathrm{cyc}}$:
\begin{equation*}
\mathrm{CoHA}(Q,W)\;:=\;\bigoplus_{\mathbf{d}}H^{\bullet}_{G_{\mathbf{d}}}(\mathrm{Rep}(Q,\mathbf{d}),\varphi_{W_{\mathbf{d}}}).
\end{equation*}
\end{theorem}

\begin{theorem}[Davison integrality arXiv:1601.02479]
\label{v4-arith:thm:davison-integrality}
\ClaimStatusProvedElsewhere. For symmetric $(Q,W)$ in the CY-3
setting,
\begin{equation*}
\mathrm{CoHA}(Q,W)\;\cong\;\mathrm{Sym}(\mathrm{BPS}(Q,W)\otimes H^{\bullet}(B\mathbb{C}^{\times})),
\end{equation*}
with $\mathrm{BPS}(Q,W)$ the BPS Lie algebra (primitive generator
lattice, in Davison's sense).
\end{theorem}

\begin{theorem}[conjectural arithmetic CoHA identification]
\label{v4-arith:thm:arithmetic-CoHA-conjectural}
\ClaimStatusConjectured. $\mathcal{V}^{\mathrm{prim}}$ is \emph{not}
$\mathrm{CoHA}(Q,W)$ for any single quiver-with-potential; it is
the \emph{BPS sub-object}
\begin{equation*}
\mathcal{V}^{\mathrm{prim}}\;\stackrel{?}{\cong}\;\mathrm{BPS}(Q^{\mathrm{arith}},W^{\mathrm{arith}}),
\end{equation*}
with candidate data
\begin{itemize}
\item $Q^{\mathrm{arith}}_{0}=\mathbb{P}\cup\{\infty\}$;
\item $Q^{\mathrm{arith}}_{1}=$ Hecke correspondences (one edge per
automorphism of a local completion);
\item $W^{\mathrm{arith}}\in\mathrm{HC}_{0}(\mathbb{Z}\langle Q^{\mathrm{arith}}\rangle)$
= the cyclic cohomology class of the Connes--Consani motivic lift
of the global $\zeta$-function (arXiv:1006.4810, \S5).
\end{itemize}
\end{theorem}

\begin{remark}[why Bost--Connes quiver alone is insufficient]
The Bost--Connes quiver (vertex set $\mathbb{P}$, free commutative
monoid on primes) is acyclic: trivial potential, CoHA is a
polynomial algebra $\bigotimes_{p}\mathbb{Z}[e_{p}]$. This is not
the structure of $\mathcal{V}^{\mathrm{prim}}$; the identification
requires adding the cyclic-cohomology-lifted potential.
\end{remark}

\section{$\log L$ Is Not a Cyclic Polynomial}
\label{v4-arith:ks:logL-not-cyclic}

\begin{observation}
\label{v4-arith:obs:logL-not-cyclic}
$\log L=\sum_{p}\sum_{k\geq 1}p^{-ks}/k$ is a formal Dirichlet
series with transcendental coefficients $\log p$; it is not a
cyclic polynomial in the path algebra $\mathbb{Z}\langle Q\rangle_{\mathrm{cyc}}$.
Its appearance in a CoHA must go through Connes' cyclic
cohomology ($\mathrm{HC}_{0}$), not directly as a potential.
\end{observation}

\begin{remark}[role of exponential Hodge structure]
Kontsevich--Soibelman \emph{Cohomological Hall algebra,
exponential Hodge structures, and motivic DT invariants}
(arXiv:1006.2706, \S7) provides the setting in which $\zeta$-value
periods appear as CoHA data. The arithmetic CoHA identification
requires this exponential Hodge structure machinery.
\end{remark}

\section{Summary of This Chapter}
\label{v4-arith:ks:summary}

\begin{enumerate}
\item $E_{1}$-formality automatic over $\mathbb{Z}$
(\Cref{v4-arith:thm:E1-formality-automatic}). Ordered
$E_{1}$-chiral structure extends integrally
(\Cref{v4-arith:cor:ordered-E1-survives}).
\item $E_{2}$-formality fails integrally (Dyer--Lashof,
Japanese cocycle); $E_{2}$-enhancement exists only over $\mathbb{Q}$
(\Cref{v4-arith:cor:no-integral-E2}).
\item Higher $A_{\infty}$-products vanish over $\mathbb{Z}$ because
$H_{\bullet}(E_{1};\mathbb{Z})$ is torsion-free
(\Cref{v4-arith:cor:strict-associativity-Z}).
\item Chiral bracket $=$ adelic residue (Kontsevich--Soibelman)
on Arakelov completion
(\Cref{v4-arith:def:arith-lambda-bracket}).
\item CoHA identification: conjectural, via Davison
$\mathrm{BPS}(Q^{\mathrm{arith}},W^{\mathrm{arith}})$ with cyclic
cohomology lift of $\log L$
(\Cref{v4-arith:thm:arithmetic-CoHA-conjectural}).
\end{enumerate}

Arithmetic formality is subtler than it looks: the $E_{1}$-lane is
mercifully free, the $E_{2}$-lane costs $\mathbb{Q}$, and the CoHA
identification costs both a quiver nobody has written down and a
potential requiring exponential Hodge structure machinery.
