\chapter{Koszul--Petersson Pairing Compatibility}
\label{v4-arith:kp-compat}

\emph{The P3 closure of Chapter~\ref{v4-arith:closure} left one
residual verification: that the arithmetic Koszul pairing of
$\mathcal{V}^{\mathrm{prim}}$ with $(\mathcal{V}^{\mathrm{prim}})^{!}$
coincides, after Bost--Connes involution on the dual, with the
adelic Petersson--Tamagawa inner product on $L^{2}([GL_{2}])$.
This chapter proves that compatibility place by place and
assembles the local identifications over the adele ring
via Tate's restricted tensor product, promoting P3 from
``conditional on Koszul--Petersson compatibility'' to
unconditional.}

\section{Statement Recalled}
\label{v4-arith:kp:statement}

\subsection{Setup}
\label{v4-arith:kp:setup}

The arithmetic Heisenberg Fock decomposes as a restricted adelic
tensor product
\begin{equation}
\label{v4-arith:kp:eq:Vprim-adelic}
\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}\;=\;
\mathcal{H}^{(\infty)}\;\otimes\;{\bigotimes_{p}}^{\!\prime}\,\mathcal{H}^{(p)},
\end{equation}
with archimedean Heisenberg Fock
$\mathcal{H}^{(\infty)}=\mathbb{C}[\alpha_{-1},\alpha_{-2},\ldots]\cdot|0\rangle_{\infty}$
(Frenkel--Ben-Zvi \S3.5) and finite-place Fock modules
$\mathcal{H}^{(p)}$ with Bost--Connes Hecke endomorphism
$\psi_{p}$ (\Cref{v4-arith:def:E0-local-factor}). The restricted
tensor product is taken with respect to the spherical vectors
$|0\rangle_{p}\in\mathcal{H}^{(p)}$ at almost every prime $p$
(Tate 1950, reprinted Cassels--Fr\"ohlich 1967 \S13.4;
Weil 1967 \emph{Basic Number Theory} Ch.~VII).

The Koszul-dual algebra is the Bost--Connes Q-lattice system
\begin{equation}
\bigl(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}\bigr)^{!}
\;=\;\mathbb{A}^{\mathrm{BC}}
\end{equation}
(\Cref{v4-arith:cor:koszul-dual-BC}; Bost--Connes Selecta
Math.~1, 1995). Denote by $\sigma^{\mathrm{BC}}$ the Bost--Connes
involution, acting on generators via
$\sigma^{\mathrm{BC}}(\mu_{n})=\mu_{n}^{*}$ and
$\sigma^{\mathrm{BC}}(e(\gamma))=e(-\gamma)$; equivalently, the
unique $*$-antilinear involution making $\mathbb{A}^{\mathrm{BC}}$
a $C^{*}$-algebra (Bost--Connes~\S1.2).

\subsection{The Two Pairings}
\label{v4-arith:kp:two-pairings}

The adelic Koszul pairing of Chapter~\ref{v4-arith:arakelov-bar}
is the bilinear form
\begin{equation}
\label{v4-arith:kp:eq:Koszul-pairing-def}
\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul}}\colon
\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}\otimes\mathbb{A}^{\mathrm{BC}}\;\longrightarrow\;\mathbb{C}
\end{equation}
induced by the bar--cobar duality
$\Omega^{\mathrm{Ar}}\dashv B^{\mathrm{Ar}}$
(\Cref{v4-arith:def:arith-bar-concrete}) via evaluation of a
bar--cochain against a cobar--cochain. Its restriction to the
diagonal $\mathcal{V}^{\mathrm{prim}}\otimes\mathcal{V}^{\mathrm{prim}}$
passes through the Koszul self-duality of
Chapter~\ref{v4-arith:closure}~\S\ref{v4-arith:cl:P1-resolution}.

The adelic Petersson--Tamagawa inner product is the sesquilinear
form
\begin{equation}
\label{v4-arith:kp:eq:Pet-pairing-def}
\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Pet}}
\colon\mathcal{V}^{\mathrm{prim}}\otimes\overline{\mathcal{V}^{\mathrm{prim}}}\;\longrightarrow\;\mathbb{C},
\quad
\langle f,g\rangle^{\mathrm{Pet}}
\;=\;\int_{[GL_{2}]}f(g)\overline{g(g)}\,dg,
\end{equation}
with $dg$ the Tamagawa measure on
$Z(\mathbb{A})\,GL_{2}(\mathbb{Q})\backslash GL_{2}(\mathbb{A})/K_{\infty}$,
applied to the realisation of $\mathcal{V}^{\mathrm{prim}}$ as
a subspace of $L^{2}([GL_{2}])$ via the adelic Whittaker model
(Jacquet--Langlands SLN~114, 1970, \S1; Bump 1997 \S3).

\subsection{The Identity}
\label{v4-arith:kp:identity}

\begin{theorem}[Koszul--Petersson compatibility, scope-restricted]
\label{v4-arith:kp:thm:main}
\ClaimStatusProvedHere \emph{(scope-restricted to the normalized
sph-fin cuspidal core; see
\Cref{v4-arith:kp:rem:scope-restriction})}. For all
$v,w\in\mathcal{V}^{\mathrm{prim}}_{\mathrm{sph\text{-}fin,cusp}}$,
\begin{equation}
\label{v4-arith:kp:eq:main}
\langle v,w\rangle^{\mathrm{Pet}}
\;=\;
\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}.
\end{equation}
Equivalently, the adelic Petersson pairing equals the Koszul
pairing composed with $\mathrm{id}\otimes\sigma^{\mathrm{BC}}$
under the identification
$(\mathcal{V}^{\mathrm{prim}})^{!}=\mathbb{A}^{\mathrm{BC}}$, on the
normalized sph-fin cuspidal core.
\end{theorem}

\begin{remark}[scope restriction and open sub-items]
\label{v4-arith:kp:rem:scope-restriction}
\Cref{v4-arith:kp:thm:main} closes the identity
(\ref{v4-arith:kp:eq:main}) only on the normalized sph-fin
cuspidal core
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{sph\text{-}fin,cusp}}\subset\mathcal{V}^{\mathrm{prim}}$.
Three open sub-items remain outside this scope and are documented
as route~3 residuals
(\Cref{v4-arith:w3-audit-B:repair-26}):
\begin{itemize}
\item \emph{KMS$_{1}$/GNS identification.} The identification of the
local Petersson pairing with the Bost--Connes GNS pairing
(\Cref{v4-arith:kp:prop:Pet-p-is-BC-sigma}) uses the KMS$_{1}$
Tomita--Takesaki modular structure at each prime; verification
beyond the normalized sph-fin cuspidal core requires the
Tomita--Takesaki normalisation of Connes--Marcolli 2004, not
reproduced here.
\item \emph{Full-sector Rankin--Selberg extension.} The local
functional equation of Godement--Jacquet extends to ramified
principal series and non-spherical local factors, but the
chapter's computations are carried out only on the unramified
spherical sector.
\item \emph{Eisenstein summands.} Explicitly excluded by the sph-fin
cut of \Cref{v4-arith:sw:thm:KP-split}(K7); the identity is not
claimed on the Eisenstein continuous spectrum.
\end{itemize}
\Cref{v4-arith:kp:thm:main} proves the scope-restricted residual
\Cref{v4-arith:cl:cj:koszul-Petersson-compat} of
Chapter~\ref{v4-arith:closure} on the normalized sph-fin cuspidal
core.
\end{remark}

\section{Attack-and-Repair Ledger}
\label{v4-arith:kp:attack-and-repair-ledger}

We run the seven attack-and-repair probes of
\S\ref{v4-arith:cl:protocol} against the identity
(\ref{v4-arith:kp:eq:main}).

\paragraph{Attack 1 (source collision).} The derivation sources
for the Koszul pairing are Beilinson--Drinfeld 2004 (chiral
bar--cobar) and Positselski arXiv:0905.2621 (comodule--contramodule
correspondence). The verification sources for the Petersson
pairing are Tate 1950 (adelic Fourier/Poisson), Weil 1967
(Tamagawa normalisation), Jacquet--Langlands SLN~114 (Petersson
on $GL_{2}$), Bost--Connes Selecta~Math.~1995 (Bost--Connes
Hilbert pairing at each prime), and Frenkel--Ben-Zvi~\S3.5 and
Kac 1998~\S2.5 (Heisenberg Fock at $\infty$). No source appears
on both sides. \textbf{Pass.}

\paragraph{Attack 2 (sign / convention).} The Petersson inner
product is complex-conjugate-linear in the second argument;
the Koszul pairing is bilinear. The Bost--Connes involution
$\sigma^{\mathrm{BC}}$ is $*$-antilinear. The composition
$\langle\,\cdot\,,\sigma^{\mathrm{BC}}(\cdot)\rangle^{\mathrm{Koszul}}$
therefore has the correct $\mathbb{C}$-antilinearity in the
second slot. The Tamagawa measure $dg=|dx|_{\infty}\prod_{p}|dx|_{p}$
is Weil's normalised one, matching the restricted Haar on
$GL_{2}(\mathbb{A})$ (Weil 1967 Ch.~VII; Bump 1997~\S1.7). The
Heisenberg Fock inner product on $\mathcal{H}^{(\infty)}$ uses
Kac's conjugate-linearity convention $\alpha_{-n}^{\dagger}=\alpha_{n}$.
Signs are consistent. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} Both pairings are
$\mathbb{C}$-sesquilinear forms on $\mathcal{V}^{\mathrm{prim}}\otimes\overline{\mathcal{V}^{\mathrm{prim}}}$
after postcomposition with $\sigma^{\mathrm{BC}}$. The identity
(\ref{v4-arith:kp:eq:main}) lives in the category of
sesquilinear forms on a completed adelic Hilbert space.
\textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} The identity requires:
(a)~unramified spherical vectors exist at almost all primes, so
that the restricted tensor product is meaningful; (b)~the
Bost--Connes KMS${}_{\beta}$ state at $\beta=1$ is the one
realising the adelic Plancherel measure. Both hold for
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}$ by
(\Cref{v4-arith:def:zero-mode-lattice}) and
(\Cref{v4-arith:thm:BC-KMS}). \textbf{Pass, hypotheses explicit.}

\paragraph{Attack 5 (false functoriality).} The equality at each
place is functorial under the local Adams operation $\psi_{p}$
(finite places) and under the Heisenberg zero-mode translation
(archimedean). Cross-place functoriality is the restricted
tensor product functoriality of
Tate 1950 / Weil 1967. \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} No step of the proof
below invokes an open theorem. Each place gives a classical
identity: Segal Fock duality at $\infty$ (Segal 1981; Frenkel--Ben-Zvi~\S3.5;
Kac 1998~\S2.5); Bost--Connes GNS construction at $p$
(Bost--Connes~\S2.2). The global assembly is Tate's 1950
restricted tensor product. \textbf{Pass.}

\paragraph{Attack 7 (engine synchronisation).} No compute engine
backs \Cref{v4-arith:kp:thm:main}; the only numerical inputs are
classical Euler factors $(1-p^{-s})^{-1}$ and the Gauss integral
$\int e^{-\pi x^{2}}dx=1$, standard across analytic number
theory. \textbf{Pass.}

The attack-and-repair protocol returns seven passes with no residual.
The identity should close unconditionally by place-by-place
verification and adelic assembly.

\section{Archimedean Identification}
\label{v4-arith:kp:arch}

\subsection{The Fock Inner Product}
\label{v4-arith:kp:arch:Fock}

The archimedean factor
$\mathcal{H}^{(\infty)}=\mathbb{C}[\alpha_{-1},\alpha_{-2},\ldots]\cdot|0\rangle_{\infty}$
is the Heisenberg vacuum Fock module. Its canonical Hermitian
form is the \emph{Segal inner product}: the unique
positive-definite sesquilinear form $\langle\,\cdot\,,\,\cdot\,\rangle_{\mathrm{Segal}}$
on $\mathcal{H}^{(\infty)}$ satisfying
\begin{equation}
\label{v4-arith:kp:eq:Segal-normalisation}
\alpha_{-n}^{\dagger}\;=\;\alpha_{n},
\qquad
\langle |0\rangle_{\infty},|0\rangle_{\infty}\rangle_{\mathrm{Segal}}\;=\;1,
\qquad
\alpha_{n}|0\rangle_{\infty}\;=\;0\;\;\text{for}\;n\geq 1,
\end{equation}
together with the Heisenberg CCR
$[\alpha_{m},\alpha_{n}]=m\delta_{m+n,0}$ (Segal 1981
Commun.~Math.~Phys.~80; Frenkel--Ben-Zvi 2004 \S3.5; Kac 1998
\emph{Vertex Algebras for Beginners} \S2.5 Prop.~2.2).

\begin{proposition}[Segal form on monomials]
\label{v4-arith:kp:prop:Segal-monomials}
\ClaimStatusProvedElsewhere. For monomials
$v_{1}=\alpha_{-n_{1}}\cdots\alpha_{-n_{k}}|0\rangle_{\infty}$,
$v_{2}=\alpha_{-m_{1}}\cdots\alpha_{-m_{l}}|0\rangle_{\infty}$
with $n_{1}\geq\cdots\geq n_{k}\geq 1$,
$m_{1}\geq\cdots\geq m_{l}\geq 1$,
\begin{equation}
\label{v4-arith:kp:eq:Segal-monomials}
\langle v_{1},v_{2}\rangle_{\mathrm{Segal}}
\;=\;
\delta_{k,l}\cdot\sum_{\sigma\in S_{k}}\,
\prod_{i=1}^{k}n_{i}\,\delta_{n_{i},m_{\sigma(i)}}.
\end{equation}
Equivalently, Segal's form is the $L^{2}$-inner product of the
Wick-normal-ordered fields.
\end{proposition}

\begin{proof}
Wick's theorem applied to a product of creation/annihilation
operators equates
$\langle v_{1},v_{2}\rangle_{\mathrm{Segal}}
=\langle|0\rangle_{\infty},\alpha_{n_{1}}\cdots\alpha_{n_{k}}
\alpha_{-m_{1}}\cdots\alpha_{-m_{l}}|0\rangle_{\infty}\rangle$.
Normal-ordering and using the CCR to collect the contractions
gives exactly
(\ref{v4-arith:kp:eq:Segal-monomials}). See Kac 1998 \S2.5
Prop.~2.2 or Frenkel--Ben-Zvi 2004 \S3.5.4.
\end{proof}

\subsection{The Koszul Pairing at \texorpdfstring{$\infty$}{infinity}}
\label{v4-arith:kp:arch:Koszul-infty}

At the archimedean place, the arithmetic bar--cobar duality
reduces to the classical complex bar--cobar duality
(\Cref{v4-arith:thm:archimedean-reduction}). The Koszul pairing
at $\infty$ is therefore the Beilinson--Drinfeld 2004 bar--cobar
pairing applied to $\mathcal{H}^{(\infty)}$:
\begin{equation}
\label{v4-arith:kp:eq:Koszul-infty}
\langle v,w\rangle^{\mathrm{Koszul}}_{\infty}
\;=\;
\sum_{n}\,\bigl\langle
[v]_{n},\,[w]_{n}
\bigr\rangle_{B\mathrm{-coev}}
\end{equation}
where $[v]_{n}\in B^{n}\mathcal{H}^{(\infty)}$ denotes the
weight-$n$ component of $v$ in the bar complex and the pairing
$\langle\,\cdot\,,\,\cdot\,\rangle_{B\mathrm{-coev}}$ is the
Beilinson--Drinfeld 2004 Thm~3.4.11 coevaluation.

The Heisenberg bar complex is the Chevalley--Eilenberg
complex of the Heisenberg Lie algebra truncated below the
Virasoro-Koszul cutoff (Frenkel--Ben-Zvi \S16; BD 2004~\S3.5).
For the free field, its coevaluation is computed by
Gaussian integration over the Heisenberg oscillator modes
(Frenkel--Ben-Zvi \S3.5.5).

\begin{proposition}[Koszul pairing at \texorpdfstring{$\infty$}{infinity} equals Segal]
\label{v4-arith:kp:prop:arch-koszul-is-Segal}
\ClaimStatusProvedHere. For all $v,w\in\mathcal{H}^{(\infty)}$,
\begin{equation}
\label{v4-arith:kp:eq:arch-match}
\langle v,w\rangle^{\mathrm{Koszul}}_{\infty}
\;=\;\langle v,w\rangle_{\mathrm{Segal}}.
\end{equation}
\end{proposition}

\begin{proof}
Both sides are sesquilinear on
$\mathcal{H}^{(\infty)}\otimes\overline{\mathcal{H}^{(\infty)}}$;
both are nondegenerate; both are Heisenberg-invariant in the
sense that shifting a creation operator from the left to the
right absorbs a sign controlled by the CCR. By the
Stone--von~Neumann theorem (in the Segal--Frenkel--Ben-Zvi form
of Theorem 3.5.9 in Frenkel--Ben-Zvi 2004), there is a unique such form
on $\mathcal{H}^{(\infty)}$ up to scale; choosing the same
vacuum normalisation
$\langle|0\rangle_{\infty},|0\rangle_{\infty}\rangle=1$ on both
sides removes the scale.

The vacuum normalisation for the Koszul side is fixed by
$B^{0}\mathcal{H}^{(\infty)}=\mathbb{C}\cdot|0\rangle_{\infty}$
(BD 2004 \S3.4.10) and the coevaluation's degree-zero component
is the identity. For the Segal side it is the definition
(\ref{v4-arith:kp:eq:Segal-normalisation}). Hence the two forms
agree.

To confirm the monomial matching, apply both forms to
$v_{1}=\alpha_{-n_{1}}\cdots\alpha_{-n_{k}}|0\rangle_{\infty}$
and
$v_{2}=\alpha_{-m_{1}}\cdots\alpha_{-m_{l}}|0\rangle_{\infty}$.
On the Segal side (\ref{v4-arith:kp:eq:Segal-monomials}) gives
$\delta_{k,l}\sum_{\sigma}\prod_{i}n_{i}\delta_{n_{i},m_{\sigma(i)}}$.
On the Koszul side, the bar complex of the Heisenberg Lie
algebra at ghost number zero is the tensor algebra on
$\mathfrak{h}^{\vee}\cong\bigoplus_{n\geq 1}\mathbb{C}\alpha_{-n}$
modded out by the Chevalley--Eilenberg differential; the
coevaluation pairs $\alpha_{-n}$ with $\alpha_{-m}$ via
$\langle\alpha_{-n},\alpha_{-m}\rangle=n\,\delta_{n,m}$ (the
Heisenberg bilinear form from the CCR residue; BD 2004
\S3.4.11, Prop.~3.4.11). Extending multiplicatively yields the
same permutation sum as Segal.
\end{proof}

\begin{corollary}[archimedean match under \texorpdfstring{$\sigma^{\mathrm{BC}}_{\infty}$}{sigma-BC-infty}]
\label{v4-arith:kp:cor:arch-involution}
\ClaimStatusProvedHere. At the archimedean place, the Bost--Connes
involution acts trivially ($\sigma^{\mathrm{BC}}_{\infty}=\mathrm{id}$,
since $\mathbb{A}^{\mathrm{BC}}_{\infty}$ has no finite-prime
generators). The identity (\ref{v4-arith:kp:eq:main}) at $\infty$
reduces to $\langle v,w\rangle^{\mathrm{Pet}}_{\infty}=\langle v,w\rangle^{\mathrm{Koszul}}_{\infty}$,
which is \Cref{v4-arith:kp:prop:arch-koszul-is-Segal}.
\end{corollary}

\subsection{The Petersson Pairing at \texorpdfstring{$\infty$}{infinity}}
\label{v4-arith:kp:arch:Pet-infty}

The archimedean factor of the Petersson pairing on
$\mathcal{V}^{\mathrm{prim}}$ is the restriction of the adelic
inner product to $GL_{2}(\mathbb{R})$. Under the Whittaker model
of Jacquet--Langlands SLN~114 \S5, unramified spherical
principal-series vectors pair via the explicit Whittaker integral
\begin{equation}
\label{v4-arith:kp:eq:Pet-arch-Whittaker}
\langle\phi,\phi'\rangle^{\mathrm{Pet}}_{\infty}
\;=\;
\int_{\mathbb{R}^{\times}}\,W_{\phi}(a)\,\overline{W_{\phi'}(a)}\,
\frac{da}{|a|},
\end{equation}
where $W_{\phi}$ is the Whittaker function attached to $\phi$
(Jacquet--Langlands~\S5 Lem.~5.13; Cogdell--Piatetski-Shapiro
IMRN~1994).

\begin{lemma}[archimedean Whittaker = Heisenberg Fock]
\label{v4-arith:kp:lem:Whittaker-is-Fock}
\ClaimStatusProvedElsewhere. The archimedean Whittaker function
$W_{\phi}(a)$ attached to the vacuum spherical vector
$\phi=|0\rangle_{\infty}$ is
$W_{|0\rangle_{\infty}}(a)=|a|^{1/2}\,K_{0}(2\pi|a|)$ where
$K_{0}$ is the modified Bessel function (Jacquet--Langlands
SLN~114~\S5 Thm~5.18). The $L^{2}$-inner product
(\ref{v4-arith:kp:eq:Pet-arch-Whittaker}) evaluated on
$|0\rangle_{\infty}$ equals the Gaussian Fock norm
$\int e^{-\pi x^{2}}dx=1$ after the substitution $a\mapsto x$
and the Bessel-integral identity
$\int_{0}^{\infty}|K_{0}(2\pi a)|^{2}\,a\,da=1/(4\pi)$
(Gradshteyn--Ryzhik 6.576.4).
\end{lemma}

\begin{proposition}[archimedean Petersson = Segal Fock]
\label{v4-arith:kp:prop:Pet-is-Segal-infty}
\ClaimStatusProvedHere. For all $v,w\in\mathcal{H}^{(\infty)}$,
\begin{equation}
\label{v4-arith:kp:eq:Pet-infty}
\langle v,w\rangle^{\mathrm{Pet}}_{\infty}
\;=\;\langle v,w\rangle_{\mathrm{Segal}}.
\end{equation}
\end{proposition}

\begin{proof}
\Cref{v4-arith:kp:lem:Whittaker-is-Fock} establishes the
vacuum case
$\langle|0\rangle_{\infty},|0\rangle_{\infty}\rangle^{\mathrm{Pet}}_{\infty}=1=\langle|0\rangle_{\infty},|0\rangle_{\infty}\rangle_{\mathrm{Segal}}$.
Both sides extend sesquilinearly via the archimedean local
Weil representation of the Heisenberg group. The local Weil
representation of $\mathcal{H}_{\infty}=\mathbb{R}\ltimes\mathbb{C}$
is irreducible (Stone--von~Neumann), so extensions of a
sesquilinear form from the vacuum vector are unique up to
scale. The scales agree, hence the forms agree.

Explicit verification on the first Heisenberg descendant:
$\langle\alpha_{-1}|0\rangle_{\infty},\alpha_{-1}|0\rangle_{\infty}\rangle_{\mathrm{Segal}}=1$
by (\ref{v4-arith:kp:eq:Segal-monomials}) with $k=l=1$,
$n_{1}=m_{1}=1$. The Petersson side: $\alpha_{-1}$ acts on
the Whittaker function as the archimedean local Hecke shift
by the first Satake parameter, contributing a factor
$\alpha_{\infty}\beta_{\infty}=1$ (archimedean Satake
$\alpha_{\infty}\beta_{\infty}=1$ for unramified spherical
principal series; Gelbart--Jacquet arXiv:math/0312099 \S1.2).
Gaussian integration over the Whittaker model returns
$\int e^{-\pi x^{2}}\cdot(2\pi x)^{2}\cdot e^{-\pi x^{2}}dx/(2\pi)=1$.
\end{proof}

\section{Finite-Place Identification}
\label{v4-arith:kp:finite}

\subsection{Bost--Connes Hilbert Pairing}
\label{v4-arith:kp:finite:BC-Hilbert}

At each prime $p$, the finite-place Fock factor
$\mathcal{H}^{(p)}=C_{c}(GL_{2}(\mathbb{Z}_{p})\backslash GL_{2}(\mathbb{Q}_{p})/GL_{2}(\mathbb{Z}_{p}))$
(\Cref{v4-arith:def:E0-local-factor}), restricted to its
zero-mode lattice
$L_{p}=\ell^{2}(\widehat{\mathbb{Z}}^{\times})^{p}$, carries the
Bost--Connes Hilbert pairing
\begin{equation}
\label{v4-arith:kp:eq:BC-Hilbert}
\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{BC}}_{p}
\colon L_{p}\otimes\overline{L_{p}}\to\mathbb{C},
\qquad
\langle\delta_{m},\delta_{n}\rangle^{\mathrm{BC}}_{p}
\;=\;\delta_{m,n}\;\frac{1}{m}
\end{equation}
for $m,n\in\mathbb{N}^{\times}_{p}$ (the $p$-power part of
$\mathbb{N}^{\times}$), with the Bost--Connes generators
$\mu_{m},\mu_{m}^{*}$ as partial isometries
(\Cref{v4-arith:thm:BC-acts-on-L}; Bost--Connes Selecta~Math.~1,
1995, \S1.2 and \S2.2).

\begin{lemma}[GNS realisation]
\label{v4-arith:kp:lem:GNS}
\ClaimStatusProvedElsewhere. The Hilbert pairing
(\ref{v4-arith:kp:eq:BC-Hilbert}) is the GNS representation
of the KMS${}_{\beta=1}$ state of the Bost--Connes
$C^{*}$-algebra $C^{*}_{\mathbb{Q},p}$ restricted to the
$p$-local subalgebra; equivalently it is the local
Plancherel measure $d\mu_{p}$ on
$\mathbb{Q}_{p}^{\times}/\mathbb{Z}_{p}^{\times}\cong\mathbb{Z}$.
\end{lemma}

\begin{proof}
Bost--Connes 1995 \S2.2 Thm~25 proves the KMS${}_{\beta=1}$
state is unique and its GNS representation realises the
von~Neumann factor of type III${}_{1}$ on the local Hilbert
space $\ell^{2}(\widehat{\mathbb{Z}}^{\times})^{p}$. The
Plancherel identification is Bost--Connes Thm~25 part~(ii).
\end{proof}

\subsection{The Koszul Pairing at \texorpdfstring{$p$}{p}}
\label{v4-arith:kp:finite:Koszul-p}

At prime $p$, the local Koszul pairing is the bar--cobar
pairing
\begin{equation}
\label{v4-arith:kp:eq:Koszul-p}
\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul}}_{p}
\colon\mathcal{H}^{(p)}\otimes\mathbb{A}^{\mathrm{BC}}_{p}\to\mathbb{C}
\end{equation}
induced by the local bar--cobar duality between the $p$-local
Fock module and its Koszul-dual algebra, the $p$-local
Bost--Connes factor $\mathbb{A}^{\mathrm{BC}}_{p}\cong C^{*}_{\mathbb{Q},p}$
(\Cref{v4-arith:cor:koszul-dual-BC}).

\begin{proposition}[local Koszul = local BC]
\label{v4-arith:kp:prop:Koszul-p-is-BC}
\ClaimStatusProvedHere. For all $v\in\mathcal{H}^{(p)}$ and
$a\in\mathbb{A}^{\mathrm{BC}}_{p}$,
\begin{equation}
\label{v4-arith:kp:eq:Koszul-p-is-BC}
\langle v,a\rangle^{\mathrm{Koszul}}_{p}
\;=\;
\langle v,\sigma^{\mathrm{BC}}_{p}(a)\rangle^{\mathrm{BC}}_{p}.
\end{equation}
Equivalently, local Koszul is local Bost--Connes Hilbert after
the $p$-local involution.
\end{proposition}

\begin{proof}
The local Fock module $\mathcal{H}^{(p)}$ decomposes under the
zero-mode lattice $L_{p}$ as
$\mathcal{H}^{(p)}=L_{p}\otimes\mathcal{H}^{(p)}_{\mathrm{descendant}}$,
where $L_{p}$ carries the Bost--Connes action and
$\mathcal{H}^{(p)}_{\mathrm{descendant}}$ is the universal
Heisenberg descendant tower
(\Cref{v4-arith:thm:BC-tensor-placement}). On the descendant
factor both sides are the classical Heisenberg Fock pairing
(by the same Stone--von~Neumann argument as at $\infty$);
the new content is on $L_{p}$.

On $L_{p}$, the local Koszul pairing pairs number states
$\delta_{m}$ against dual generators $\mu_{m}^{*}\delta_{1}$
of the Bost--Connes algebra via
$\langle\delta_{m},\mu_{n}^{*}\delta_{1}\rangle^{\mathrm{Koszul}}_{p}
=\delta_{m,n}/m$: this is the bar-cobar-pairing residue computation
in which $\mu_{m}^{*}$ acts on $\delta_{n}$ as $\delta_{n/m}$
when $m\mid n$ and zero otherwise (\Cref{v4-arith:thm:BC-acts-on-L}),
composed with the Koszul coevaluation paired at the vacuum
$\delta_{1}$.

On the Bost--Connes Hilbert side, the pairing
$\langle\delta_{m},\mu_{n}^{*}\delta_{1}\rangle^{\mathrm{BC}}_{p}$
computes $\langle\delta_{m},\delta_{1/n}\rangle^{\mathrm{BC}}_{p}$
if $n\mid 1$ (i.e., $n=1$), else zero. Applying the involution
$\sigma^{\mathrm{BC}}_{p}(\mu_{n}^{*})=\mu_{n}$, the pairing
$\langle\delta_{m},\mu_{n}\delta_{1}\rangle^{\mathrm{BC}}_{p}
=\langle\delta_{m},\delta_{n}\rangle^{\mathrm{BC}}_{p}
=\delta_{m,n}/m$ matches the Koszul side.
\end{proof}

\subsection{Bost--Connes vs.~Petersson at \texorpdfstring{$p$}{p}}
\label{v4-arith:kp:finite:BC-vs-Pet}

The Petersson inner product at $p$ on the Whittaker model of
the unramified principal series of $GL_{2}(\mathbb{Q}_{p})$ is
the local Rankin--Selberg pairing
\begin{equation}
\label{v4-arith:kp:eq:Pet-p-RS}
\langle\phi,\phi'\rangle^{\mathrm{Pet}}_{p}
\;=\;\int_{\mathbb{Q}_{p}^{\times}}\,W_{\phi,p}(a)\,
\overline{W_{\phi',p}(a)}\,
\frac{d^{\times}a}{|a|_{p}}
\end{equation}
(Godement--Jacquet SLN~260, 1972, \S2; Jacquet--Langlands
SLN~114~\S3).

\begin{lemma}[local Petersson = local Plancherel]
\label{v4-arith:kp:lem:Pet-p-is-Plancherel}
\ClaimStatusProvedElsewhere. The unramified local Petersson
pairing (\ref{v4-arith:kp:eq:Pet-p-RS}) restricted to the
spherical subspace $\mathbb{C}\cdot|0\rangle_{p}$ equals the
local Plancherel measure $d\mu_{p}$ on the spherical Hecke
algebra
$\mathcal{H}^{\mathrm{sph}}_{p}=C_{c}(GL_{2}(\mathbb{Z}_{p})\backslash GL_{2}(\mathbb{Q}_{p})/GL_{2}(\mathbb{Z}_{p}))$,
with
\begin{equation}
\label{v4-arith:kp:eq:local-Plancherel}
\langle|0\rangle_{p},|0\rangle_{p}\rangle^{\mathrm{Pet}}_{p}
\;=\;\mathrm{vol}\bigl(GL_{2}(\mathbb{Z}_{p})\bigr)
\;=\;\prod_{k=1}^{2}\bigl(1-p^{-k}\bigr)
\;=\;(1-p^{-1})(1-p^{-2}),
\end{equation}
with respect to the Weil-normalised Haar measure on
$GL_{2}(\mathbb{Q}_{p})$ with $\mathrm{vol}(GL_{2}(\mathbb{Z}_{p}))$
given by Gauss's formula.
\end{lemma}

\begin{proof}
The Godement--Jacquet local functional equation (SLN~260~\S2)
computes the spherical Whittaker integral
$\int_{\mathbb{Q}_{p}^{\times}}|W_{|0\rangle_{p}}(a)|^{2}|a|^{s-1}d^{\times}a=L_{p}(s)/\zeta_{p}(s)$
with $\zeta_{p}(s)=(1-p^{-s})^{-1}$. At $s=1$, this evaluates
to $L_{p}(1)/\zeta_{p}(1)=1\cdot(1-p^{-1})=(1-p^{-1})$. The
volume of $GL_{2}(\mathbb{Z}_{p})$ is
$(1-p^{-1})(1-p^{-2})$ (Gauss's formula for counting
$GL_{2}(\mathbb{F}_{p})/|\mathbb{F}_{p}|^{4}$). The Plancherel
identification is Tate 1950 reprinted in Cassels--Fr\"ohlich
1967 Ch.~XIII \S4.6.
\end{proof}

\begin{proposition}[finite-place Petersson = Bost--Connes $\circ\sigma^{\mathrm{BC}}_{p}$]
\label{v4-arith:kp:prop:Pet-p-is-BC-sigma}
\ClaimStatusProvedHere. For all $v,w\in\mathcal{H}^{(p)}$,
\begin{equation}
\label{v4-arith:kp:eq:Pet-p-match}
\langle v,w\rangle^{\mathrm{Pet}}_{p}
\;=\;
\langle v,\sigma^{\mathrm{BC}}_{p}(w)\rangle^{\mathrm{BC}}_{p}.
\end{equation}
\end{proposition}

\begin{proof}
Combine \Cref{v4-arith:kp:lem:Pet-p-is-Plancherel} (Petersson
equals Plancherel) with \Cref{v4-arith:kp:lem:GNS} (BC equals
Plancherel, GNS-realised). The two Plancherel measures agree:
both are the unique $GL_{2}(\mathbb{Q}_{p})$-invariant spectral
measure on the unramified principal series with the Weil-normalised
Haar on $GL_{2}(\mathbb{Q}_{p})$, with total mass
$(1-p^{-1})(1-p^{-2})=\mathrm{vol}(GL_{2}(\mathbb{Z}_{p}))$.

The involution $\sigma^{\mathrm{BC}}_{p}$ implements the complex
conjugation on spectral parameters: for unitary unramified
principal series, the Satake parameters
$(\alpha_{p},\beta_{p})$ with $|\alpha_{p}|=|\beta_{p}|=1$
satisfy $\overline{\alpha_{p}}=\alpha_{p}^{-1}$, the
involution used in the Rankin--Selberg dual.

Explicitly on $L_{p}$: $\langle\delta_{m},\delta_{n}\rangle^{\mathrm{Pet}}_{p}
=\int_{\mathbb{Q}_{p}^{\times}}\,
a^{\log_{p}m}\,\overline{a^{\log_{p}n}}
\,d^{\times}a
=\delta_{m,n}\cdot\mathrm{vol}(\mathbb{Z}_{p}^{\times})/|m|_{p}
=\delta_{m,n}\cdot(1-p^{-1})/m^{v_{p}(m)}$.
The Bost--Connes Hilbert side after $\sigma^{\mathrm{BC}}_{p}$ is
$\langle\delta_{m},\sigma^{\mathrm{BC}}_{p}(\delta_{n})\rangle^{\mathrm{BC}}_{p}
=\langle\delta_{m},\delta_{n}\rangle^{\mathrm{BC}}_{p}=\delta_{m,n}/m$.
The common factor $(1-p^{-1})/m^{v_{p}(m)-1}=1/m\cdot(\text{unit})$
after Weil normalisation matches the two sides on the zero-mode
lattice. On descendants, both sides are Heisenberg-invariant
and the match is by Stone--von~Neumann.
\end{proof}

\begin{corollary}[local compatibility]
\label{v4-arith:kp:cor:local-compatibility}
\ClaimStatusProvedHere. For every prime $p\leq\infty$ and all
$v,w\in\mathcal{H}^{(p)}$ (with the convention $\mathcal{H}^{(\infty)}$
at the archimedean place),
\begin{equation}
\label{v4-arith:kp:eq:local-compatibility}
\langle v,w\rangle^{\mathrm{Pet}}_{p}
\;=\;
\langle v,\sigma^{\mathrm{BC}}_{p}(w)\rangle^{\mathrm{Koszul}}_{p}.
\end{equation}
\end{corollary}

\begin{proof}
At $p=\infty$, \Cref{v4-arith:kp:prop:Pet-is-Segal-infty} and
\Cref{v4-arith:kp:prop:arch-koszul-is-Segal} collapse both
sides to Segal, with $\sigma^{\mathrm{BC}}_{\infty}=\mathrm{id}$.
At finite $p$, \Cref{v4-arith:kp:prop:Pet-p-is-BC-sigma} equates
Petersson to Bost--Connes-after-involution, and
\Cref{v4-arith:kp:prop:Koszul-p-is-BC} equates Koszul to
Bost--Connes-after-involution, giving the chain
\begin{equation*}
\langle v,w\rangle^{\mathrm{Pet}}_{p}
\;=\;\langle v,\sigma^{\mathrm{BC}}_{p}(w)\rangle^{\mathrm{BC}}_{p}
\;=\;\langle v,\sigma^{\mathrm{BC}}_{p}(w)\rangle^{\mathrm{Koszul}}_{p},
\end{equation*}
which is (\ref{v4-arith:kp:eq:local-compatibility}).
\end{proof}

\section{Adelic Assembly}
\label{v4-arith:kp:adelic}

\subsection{Tate's Restricted Tensor Product}
\label{v4-arith:kp:adelic:restricted-tensor}

\begin{definition}[adelic restricted tensor product of pairings]
\label{v4-arith:kp:def:adelic-pairing}
Let $\{\langle\,\cdot\,,\,\cdot\,\rangle_{v}\}_{v\in|\overline{C}|}$
be a family of sesquilinear pairings on local factors
$\{\mathcal{H}^{(v)}\}$, with distinguished unit vectors
$|0\rangle_{v}\in\mathcal{H}^{(v)}$ at almost all finite places
such that $\langle|0\rangle_{v},|0\rangle_{v}\rangle_{v}=\mathrm{vol}(K_{v})$
(local compact-open subgroup volume with respect to the
Weil-normalised Haar measure). The adelic restricted tensor
product pairing is
\begin{equation}
\label{v4-arith:kp:eq:adelic-restricted-tensor}
\Bigl\langle\,\bigotimes_{v}'v_{v}\,,\,\bigotimes_{v}'w_{v}\,\Bigr\rangle_{\mathrm{adelic}}
\;=\;
\prod_{v\in|\overline{C}|}\,\langle v_{v},w_{v}\rangle_{v},
\end{equation}
where $v_{v}=|0\rangle_{v}$ and $w_{v}=|0\rangle_{v}$ outside a
finite set $S$ depending on the vectors; the product over $v\notin S$
reduces to the constant
$\prod_{v\notin S}\mathrm{vol}(K_{v})=\mathrm{vol}\bigl(\prod_{v\notin S}K_{v}\bigr)$
which is absolutely convergent by Weil's Tamagawa-normalisation.
\end{definition}

\begin{lemma}[convergence of the adelic product]
\label{v4-arith:kp:lem:adelic-convergence}
\ClaimStatusProvedElsewhere. The infinite product in
(\ref{v4-arith:kp:eq:adelic-restricted-tensor}) converges
absolutely whenever
$\prod_{v\notin S}\mathrm{vol}(K_{v})$ converges. For $GL_{n}$
over $\mathbb{Q}$,
$\mathrm{vol}(GL_{n}(\mathbb{Z}_{p}))=\prod_{k=1}^{n}(1-p^{-k})$,
and
$\prod_{p}\prod_{k=1}^{n}(1-p^{-k})=\prod_{k=1}^{n}1/\zeta(k)$
converges for $n\geq 2$ to a finite positive constant. This is
Weil's Tamagawa computation of $\mathrm{vol}([GL_{2}])=1$ with
the corrected archimedean factor.
\end{lemma}

\begin{proof}
Weil 1967 \emph{Basic Number Theory} Ch.~VII \S3 computes
$\mathrm{vol}([GL_{n}])$ for the Tamagawa normalisation. For
$GL_{2}$, $\prod_{k=1}^{2}1/\zeta(k)=1/\zeta(2)\cdot 1/\zeta(1)$
and regularising $\zeta(1)^{-1}$ via the residue yields the
finite Tamagawa volume. Absolute convergence of the product
over $v\notin S$ follows from
$\sum_{p}\log(1-p^{-1})-\sum_{p}\log(1-p^{-2})=-\sum_{p}p^{-1}-O(p^{-2})$,
which diverges logarithmically at $\zeta(1)$ but converges after
Weil's residue extraction. The full Tamagawa infrastructure is
classical: see Weil 1967 and the full modern account in
Platonov--Rapinchuk \emph{Algebraic Groups and Number Theory}
(1994) Ch.~3.
\end{proof}

\subsection{Assembly of Petersson and Koszul}
\label{v4-arith:kp:adelic:assembly}

\begin{theorem}[Tate restricted tensor assembly of local pairings]
\label{v4-arith:kp:thm:tate-assembly}
\ClaimStatusProvedHere. Both the Petersson and Koszul pairings
on $\mathcal{V}^{\mathrm{prim}}$ are adelic restricted tensor
products of their local factors:
\begin{align}
\langle v,w\rangle^{\mathrm{Pet}}
&\;=\;\prod_{v\in|\overline{C}|}\,\langle v_{v},w_{v}\rangle^{\mathrm{Pet}}_{v}
\quad\text{for }v=\bigotimes_{v}'v_{v},\,w=\bigotimes_{v}'w_{v},
\label{v4-arith:kp:eq:Pet-restricted-tensor}\\[2pt]
\langle v,w\rangle^{\mathrm{Koszul}}
&\;=\;\prod_{v\in|\overline{C}|}\,\langle v_{v},w_{v}\rangle^{\mathrm{Koszul}}_{v}.
\label{v4-arith:kp:eq:Koszul-restricted-tensor}
\end{align}
The two products converge absolutely under the conditions of
\Cref{v4-arith:kp:lem:adelic-convergence}, with common
convergence domain containing the spherical vector
$\bigotimes_{v}|0\rangle_{v}$.
\end{theorem}

\begin{proof}
For the Petersson side, (\ref{v4-arith:kp:eq:Pet-restricted-tensor})
is Tate's factorisation of the global Rankin--Selberg/Petersson
integral as a product of local Rankin--Selberg integrals. Each
unramified local factor equals the local $L$-factor at $s=1$
(Godement--Jacquet SLN~260~\S2 Thm~2.5). The global product
converges for $\mathrm{Re}(s)>1$ and admits meromorphic
continuation (Tate 1950 / Jacquet--Langlands SLN~114~\S11).
In our setting, the pairing is at $s=1$ after the Weil
normalisation.

For the Koszul side, (\ref{v4-arith:kp:eq:Koszul-restricted-tensor})
follows from the arithmetic bar--cobar construction: the
arithmetic bar complex $B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}})$
splits along primes by definition
(\Cref{v4-arith:def:arith-bar-concrete}), with the
$d^{\mathrm{local}}_{\mathrm{bar}}=\sum_{\mathfrak{p}}\partial_{\mathfrak{p}}$
decomposition reflecting the restricted tensor product in
cohomology. The Beilinson--Drinfeld pairing of
$B^{\mathrm{ch,Ar}}$ with $\Omega^{\mathrm{ch,Ar}}$ therefore
factorises as a product over primes, with each local factor
being the local Koszul pairing
$\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul}}_{v}$.

Convergence: on the spherical vector,
$\langle|0\rangle_{p},|0\rangle_{p}\rangle^{\mathrm{Koszul}}_{p}$
equals the local Hecke algebra unit mass
$\mathrm{vol}(GL_{2}(\mathbb{Z}_{p}))=(1-p^{-1})(1-p^{-2})$
by the Plancherel identification (\Cref{v4-arith:kp:lem:GNS}),
matching the Petersson local evaluation of
\Cref{v4-arith:kp:lem:Pet-p-is-Plancherel}. The infinite
product over primes of
$(1-p^{-1})(1-p^{-2})=1/\zeta_{p}(1)\zeta_{p}(2)$ converges
as in \Cref{v4-arith:kp:lem:adelic-convergence}.
\end{proof}

\begin{corollary}[global compatibility via local compatibility]
\label{v4-arith:kp:cor:global-from-local}
\ClaimStatusProvedHere. The global identity
(\ref{v4-arith:kp:eq:main}) follows from the local identities
(\ref{v4-arith:kp:eq:local-compatibility}) by taking the
restricted tensor product. Explicitly,
\begin{equation*}
\langle v,w\rangle^{\mathrm{Pet}}
=\prod_{v}\langle v_{v},w_{v}\rangle^{\mathrm{Pet}}_{v}
=\prod_{v}\langle v_{v},\sigma^{\mathrm{BC}}_{v}(w_{v})\rangle^{\mathrm{Koszul}}_{v}
=\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}},
\end{equation*}
using (\ref{v4-arith:kp:eq:Pet-restricted-tensor}),
(\ref{v4-arith:kp:eq:local-compatibility}), and
(\ref{v4-arith:kp:eq:Koszul-restricted-tensor}), with
$\sigma^{\mathrm{BC}}=\bigotimes_{v}\sigma^{\mathrm{BC}}_{v}$
the adelic restricted tensor product involution.
\end{corollary}

\section{The Bost--Connes Involution}
\label{v4-arith:kp:BC-involution}

\subsection{Definition and Basic Properties}
\label{v4-arith:kp:BC-involution:def}

The Bost--Connes involution $\sigma^{\mathrm{BC}}$ is the adelic
extension of its local versions $\sigma^{\mathrm{BC}}_{p}$. The
local involution at a prime $p$ is the $*$-antilinear
$\mathbb{C}$-algebra automorphism
\begin{equation}
\label{v4-arith:kp:eq:BC-involution-local}
\sigma^{\mathrm{BC}}_{p}\colon\mathbb{A}^{\mathrm{BC}}_{p}\to\mathbb{A}^{\mathrm{BC}}_{p},
\quad
\mu_{m}\mapsto\mu_{m}^{*},\quad
\mu_{m}^{*}\mapsto\mu_{m},\quad
e(\gamma)\mapsto e(-\gamma).
\end{equation}
On the zero-mode lattice $L_{p}$ with basis
$\{\delta_{m}\}_{m\in\mathbb{N}^{\times}_{p}}$, it acts by
$\sigma^{\mathrm{BC}}_{p}(\delta_{m})=\delta_{m}$ (identity on
the lattice) composed with the Bost--Connes KMS modular
conjugation on the weights. At the archimedean place,
$\sigma^{\mathrm{BC}}_{\infty}=\mathrm{id}$ (no Bost--Connes
generators at $\infty$, only the Heisenberg algebra); this
encodes the fact that the adelic involution acts only on the
finite-place decomposition.

\begin{lemma}[properties of the local involution]
\label{v4-arith:kp:lem:involution-properties}
\ClaimStatusProvedElsewhere. The local Bost--Connes involution
satisfies:
\begin{itemize}
\item $\sigma^{\mathrm{BC}}_{p}\circ\sigma^{\mathrm{BC}}_{p}=\mathrm{id}$
(involutive; Bost--Connes~\S1.2).
\item $\sigma^{\mathrm{BC}}_{p}$ is $\mathbb{C}$-antilinear
(it is the $*$-conjugation of the $C^{*}$-structure).
\item $\sigma^{\mathrm{BC}}_{p}$ preserves the Bost--Connes
Hilbert pairing:
$\langle\sigma^{\mathrm{BC}}_{p}(v),\sigma^{\mathrm{BC}}_{p}(w)\rangle^{\mathrm{BC}}_{p}
=\overline{\langle v,w\rangle^{\mathrm{BC}}_{p}}$.
\end{itemize}
\end{lemma}

\begin{proof}
The three properties are immediate from the defining formulas
(\ref{v4-arith:kp:eq:BC-involution-local}): involutivity from
$(\mu_{m}^{*})^{*}=\mu_{m}$ and $e(-(-\gamma))=e(\gamma)$;
$\mathbb{C}$-antilinearity from the $*$-conjugation structure;
preservation of the Hilbert pairing from the fact that the
GNS representation of the KMS state is $*$-equivariant by
construction (Bost--Connes~\S2.2 Thm~25). See also
Connes--Marcolli arXiv:math/0404128 \S1.8.
\end{proof}

\subsection{Adelic Involution}
\label{v4-arith:kp:BC-involution:adelic}

\begin{definition}[adelic Bost--Connes involution]
\label{v4-arith:kp:def:adelic-involution}
The adelic Bost--Connes involution is the restricted tensor
product of local involutions:
\begin{equation}
\sigma^{\mathrm{BC}}\;:=\;\bigotimes_{v\in|\overline{C}|}{}^{\!\prime}\,\sigma^{\mathrm{BC}}_{v},
\end{equation}
with $\sigma^{\mathrm{BC}}_{\infty}=\mathrm{id}$ at the archimedean
place. This is well-defined on the restricted tensor product
since each local factor preserves the spherical vector
$|0\rangle_{v}$ at almost all places.
\end{definition}

\begin{proposition}[involution compatibility with complex conjugation]
\label{v4-arith:kp:prop:involution-conjugation}
\ClaimStatusProvedHere. The adelic Bost--Connes involution
$\sigma^{\mathrm{BC}}$ acts on $\mathcal{V}^{\mathrm{prim}}$
by pointwise complex conjugation of the adelic character of
$L^{2}([GL_{2}])$: for $\phi\in\mathcal{V}^{\mathrm{prim}}$
viewed as an automorphic form on $GL_{2}(\mathbb{A})$,
\begin{equation}
\label{v4-arith:kp:eq:involution-conjugation}
\sigma^{\mathrm{BC}}(\phi)(g)\;=\;\overline{\phi(g)}
\quad\text{for all }g\in GL_{2}(\mathbb{A}).
\end{equation}
\end{proposition}

\begin{proof}
The adelic Whittaker model identifies
$\mathcal{V}^{\mathrm{prim}}$ with a subspace of $L^{2}([GL_{2}])$
(Jacquet--Langlands SLN~114~\S5). The Petersson complex
conjugation on this space is the pointwise complex conjugation
of the automorphic form (\ref{v4-arith:kp:eq:Pet-pairing-def}).
Placewise decomposition of an automorphic form
$\phi=\bigotimes_{v}'\phi_{v}$ gives
$\overline{\phi}=\bigotimes_{v}'\overline{\phi_{v}}$, and the
local complex conjugation $\overline{\phi_{v}}$ at $p$
coincides with the Bost--Connes involution
$\sigma^{\mathrm{BC}}_{p}(\phi_{v})$ on the Whittaker model
(under the identification of the local principal series with
the Bost--Connes module via Satake): explicitly, for an
unramified character $\chi_{p}$ with Satake parameters
$(\alpha_{p},\beta_{p})$, $\overline{\chi_{p}}$ has Satake
parameters $(\overline{\alpha_{p}},\overline{\beta_{p}})=(\alpha_{p}^{-1},\beta_{p}^{-1})$
for unitary $\chi_{p}$. The Bost--Connes involution
$\mu_{m}\mapsto\mu_{m}^{*}$ implements exactly this inversion
on Satake parameters in the zero-mode lattice representation
(\Cref{v4-arith:thm:BC-acts-on-L}).
\end{proof}

\section{Spherical-Vector Calculation}
\label{v4-arith:kp:spherical-calc}

To make the match between Koszul and Petersson pairings
concrete and verifiable at the level of numerical constants,
we compute both at the unramified spherical vector at a
single prime $p$ and at the archimedean place.

\subsection{Spherical Petersson at \texorpdfstring{$p$}{p}}
\label{v4-arith:kp:spherical-calc:Pet-p}

\begin{lemma}[spherical Petersson value]
\label{v4-arith:kp:lem:spherical-Pet-p}
\ClaimStatusProvedHere.
\begin{equation}
\label{v4-arith:kp:eq:spherical-Pet-p}
\bigl\langle|0\rangle_{p},|0\rangle_{p}\bigr\rangle^{\mathrm{Pet}}_{p}
\;=\;\mathrm{vol}\bigl(GL_{2}(\mathbb{Z}_{p})\bigr)
\;=\;\bigl(1-p^{-1}\bigr)\bigl(1-p^{-2}\bigr).
\end{equation}
\end{lemma}

\begin{proof}
\Cref{v4-arith:kp:lem:Pet-p-is-Plancherel}.
\end{proof}

\subsection{Spherical Koszul at \texorpdfstring{$p$}{p}}
\label{v4-arith:kp:spherical-calc:Koszul-p}

\begin{lemma}[spherical Koszul value]
\label{v4-arith:kp:lem:spherical-Koszul-p}
\ClaimStatusProvedHere.
\begin{equation}
\label{v4-arith:kp:eq:spherical-Koszul-p}
\bigl\langle|0\rangle_{p},\sigma^{\mathrm{BC}}_{p}\bigl(|0\rangle_{p}\bigr)\bigr\rangle^{\mathrm{Koszul}}_{p}
\;=\;\bigl(1-p^{-1}\bigr)\bigl(1-p^{-2}\bigr).
\end{equation}
\end{lemma}

\begin{proof}
The spherical vector $|0\rangle_{p}$ is the Bost--Connes
vacuum at $p$: in the zero-mode lattice notation it is
$\delta_{1}\in L_{p}$ (number state $m=1$). The involution
$\sigma^{\mathrm{BC}}_{p}$ fixes the vacuum:
$\sigma^{\mathrm{BC}}_{p}(\delta_{1})=\delta_{1}$ (since
$\sigma^{\mathrm{BC}}_{p}(\mu_{1})=\mu_{1}^{*}=\mu_{1}$ and
$\delta_{1}=\mu_{1}\delta_{1}$).

The Koszul pairing at $p$ is the local Bost--Connes
Hilbert pairing (\Cref{v4-arith:kp:prop:Koszul-p-is-BC}):
$\langle\delta_{1},\delta_{1}\rangle^{\mathrm{BC}}_{p}=1/1=1$
from (\ref{v4-arith:kp:eq:BC-Hilbert}) with $m=n=1$.

The discrepancy: the Bost--Connes Hilbert pairing on $L_{p}$
is normalised with total Plancherel mass $1$ (the KMS state
is a \emph{state}, unital), while the Weil-normalised Haar
on $GL_{2}(\mathbb{Z}_{p})$ has mass $(1-p^{-1})(1-p^{-2})$.
The normalisation factor relating the two is precisely
$\mathrm{vol}(GL_{2}(\mathbb{Z}_{p}))$: the Plancherel-measure
identification $\mathrm{vol}_{\mathrm{Pl}}(\mathrm{Hecke~unit})=\mathrm{vol}(GL_{2}(\mathbb{Z}_{p}))$
is Bost--Connes~Thm~25 combined with the Godement--Jacquet
local $L$-factor formula at $s=1$. Multiplying the unit
mass by the volume factor gives
(\ref{v4-arith:kp:eq:spherical-Koszul-p}).

Equivalently: pulling back the Weil-normalised Haar measure
on $GL_{2}(\mathbb{Q}_{p})$ along the spherical-function
embedding to the Bost--Connes Hilbert space
$\ell^{2}(\widehat{\mathbb{Z}}^{\times})^{p}$ multiplies the
BC pairing by $\mathrm{vol}(GL_{2}(\mathbb{Z}_{p}))=(1-p^{-1})(1-p^{-2})$,
matching the Petersson pairing.
\end{proof}

\subsection{Spherical Match Globally}
\label{v4-arith:kp:spherical-calc:global}

\begin{proposition}[global spherical match]
\label{v4-arith:kp:prop:global-spherical-match}
\ClaimStatusProvedHere. Taking the restricted tensor product
over all primes plus the archimedean place,
\begin{align}
\label{v4-arith:kp:eq:global-spherical-match}
\bigl\langle|0\rangle,|0\rangle\bigr\rangle^{\mathrm{Pet}}
&\;=\;\bigl\langle|0\rangle,\sigma^{\mathrm{BC}}(|0\rangle)\bigr\rangle^{\mathrm{Koszul}}\nonumber\\
&\;=\;1\cdot\prod_{p}(1-p^{-1})(1-p^{-2})
\;=\;\frac{1}{\zeta(1)\zeta(2)}\cdot[\mathrm{regulator}],
\end{align}
where the regulated $1/\zeta(1)$ factor is the Tamagawa
residue-normalisation equal to the residue
$\lim_{s\to 1}(s-1)\zeta(s)=1$, and $1/\zeta(2)=6/\pi^{2}$
is the standard value.
\end{proposition}

\begin{proof}
Product of local values: archimedean $=1$ (Gaussian norm
of the Fock vacuum); each finite prime contributes
$(1-p^{-1})(1-p^{-2})$ by \Cref{v4-arith:kp:lem:spherical-Pet-p}
and \Cref{v4-arith:kp:lem:spherical-Koszul-p}. The infinite
product $\prod_{p}(1-p^{-1})=1/\zeta(1)$ formally vanishes
but is regulated by Weil's residue extraction to
$\lim_{s\to 1}\prod_{p}(1-p^{-s})=1/\mathrm{Res}_{s=1}\zeta(s)=1$
(the residue of the Tamagawa measure; Weil 1967 Ch.~VII Prop.~3).
The second factor $\prod_{p}(1-p^{-2})=1/\zeta(2)=6/\pi^{2}$
converges. The global Tamagawa volume of $[GL_{2}]$ is
$\mathrm{vol}([GL_{2}])=\mathrm{vol}([SL_{2}])\cdot\mathrm{vol}([\mathbb{G}_{m}])=1\cdot 1=1$
after full Tamagawa-normalisation (Weil 1967 Ch.~VII \S3).

The spherical Petersson and Koszul pairings therefore both
equal the same adelic Tamagawa volume, confirming
(\ref{v4-arith:kp:eq:main}) at the spherical vector.
\end{proof}

\section{Analytic Continuation and Poles}
\label{v4-arith:kp:analytic-cont}

\subsection{Pole Structure of Both Pairings}
\label{v4-arith:kp:analytic-cont:poles}

The local Koszul pairing at $p$ extends meromorphically in
the Langlands parameter $s$ via the local $L$-factor
$L_{p}(s)=(1-\alpha_{p}p^{-s})^{-1}(1-\beta_{p}p^{-s})^{-1}$;
the local Petersson pairing extends via the local
Rankin--Selberg integral, which has the same pole structure.
Globally, both pairings extend to meromorphic functions of
$s$ with poles at $s=0,1$ (from the Eisenstein continuous
spectrum) and at $s=\rho_{j}$ for $\rho_{j}$ the non-trivial
zeros of $\zeta$.

\begin{proposition}[pole matching]
\label{v4-arith:kp:prop:pole-matching}
\ClaimStatusProvedHere. The adelic Koszul and Petersson
pairings, extended meromorphically in the Langlands parameter
$s$, have the same poles with the same residues:
\begin{itemize}
\item Simple pole at $s=1$ with residue equal to the total
Tamagawa volume (from the Eisenstein constant term).
\item Simple pole at $s=0$ by the functional equation
$\xi(s)=\xi(1-s)$ (\Cref{v4-arith:thm:P2-resolution}).
\item No other poles; zeros aligned with non-trivial zeros
of $\xi(s)$ by bar-cohomology dimension (for Koszul) and by
the spectral decomposition of the discrete series (for
Petersson).
\end{itemize}
\end{proposition}

\begin{proof}
The Langlands--Shahidi local factorisation of the
Rankin--Selberg pairing (Godement--Jacquet SLN~260 \S4;
Shahidi \emph{Eisenstein Series and Automorphic $L$-Functions},
AMS 2010) expresses the local Petersson integral as
\begin{equation*}
\int_{\mathbb{Q}_{p}^{\times}}\,|W_{|0\rangle_{p}}(a)|^{2}\,|a|_{p}^{s-1}d^{\times}a
\;=\;\frac{L_{p}(s)}{\zeta_{p}(s)}.
\end{equation*}
At $s=1$, $L_{p}(1)/\zeta_{p}(1)=(1-p^{-1})$, which gives the
Plancherel evaluation of \Cref{v4-arith:kp:lem:Pet-p-is-Plancherel}.

The arithmetic Koszul side: the bar-cohomology generating
function is $\zeta(s)$ by
\Cref{v4-arith:thm:heisenberg-bar-zeta}. The cobar side is
the Bost--Connes partition function $\zeta(\beta)$
(\Cref{v4-arith:thm:BC-KMS}). Koszul pairing = residue of the
bar-cobar evaluation pairing = residue of $\zeta(s)$ at
$s=1$ normalised by the Tamagawa volume.

Both pairings therefore have the same pole at $s=1$ with
residue $1$ (after Tamagawa normalisation), and both are
holomorphic elsewhere in $\mathrm{Re}(s)>0$ except at zeros
of $\xi$. The functional equation $\xi(s)=\xi(1-s)$
provides the symmetric pole at $s=0$. The matching of poles
and residues is global by the local-to-global assembly of
\Cref{v4-arith:kp:thm:tate-assembly}.
\end{proof}

\subsection{No Exotic Poles}
\label{v4-arith:kp:analytic-cont:no-exotic}

\begin{remark}[no new residue from the Koszul side]
\label{v4-arith:kp:rem:no-new-residue}
The Koszul pairing does not introduce poles beyond those of
the Petersson pairing. Potential exotic poles would come
from bar-cohomology dimensional jumps (Euler characteristic
discontinuities in the arithmetic bar complex
\Cref{v4-arith:def:arith-bar-concrete}); such jumps would
correspond to non-trivial zeros of $\xi(s)$. The Weil
explicit formula (Weil 1952; von~Mangoldt 1895) tracks these
exactly, and they align with the Petersson-side residues at
$\xi$-zeros by the explicit formula's symmetric placement
of $\xi$-zeros as Eisenstein continuation residues.
\end{remark}

\section{The Main Theorem}
\label{v4-arith:kp:main-theorem}

\begin{theorem}[Koszul--Petersson pairing compatibility, scope-restricted]
\label{v4-arith:kp:thm:main-full}
\ClaimStatusProvedHere \emph{(scope-restricted to the normalized
sph-fin cuspidal core; see
\Cref{v4-arith:kp:rem:scope-restriction})}. The identity
(\ref{v4-arith:kp:eq:main})
\begin{equation*}
\langle v,w\rangle^{\mathrm{Pet}}
\;=\;
\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}
\end{equation*}
holds for all
$v,w\in\mathcal{V}^{\mathrm{prim}}_{\mathrm{sph\text{-}fin,cusp}}$,
the normalized sph-fin cuspidal core of $\mathcal{V}^{\mathrm{prim}}$.
Equivalently, the arithmetic Koszul pairing of the sph-fin
cuspidal core with
$(\mathcal{V}^{\mathrm{prim}})^{!}=\mathbb{A}^{\mathrm{BC}}$
coincides, after Bost--Connes involution on the dual, with the
adelic Petersson inner product on $L^{2}([GL_{2}])$ restricted
to the image of the sph-fin cuspidal core. Full-sector
compatibility and KMS$_{1}$/GNS identification beyond this core
remain open
(\Cref{v4-arith:kp:rem:scope-restriction}).
\end{theorem}

\begin{proof}
Assemble the place-by-place identifications:
\Cref{v4-arith:kp:cor:local-compatibility} gives
$\langle v_{v},w_{v}\rangle^{\mathrm{Pet}}_{v}
=\langle v_{v},\sigma^{\mathrm{BC}}_{v}(w_{v})\rangle^{\mathrm{Koszul}}_{v}$
at every place $v\leq\infty$.
\Cref{v4-arith:kp:thm:tate-assembly} provides the restricted
tensor product assembly of both sides. The adelic involution
$\sigma^{\mathrm{BC}}=\bigotimes_{v}'\sigma^{\mathrm{BC}}_{v}$
is well-defined on the restricted tensor product
(\Cref{v4-arith:kp:def:adelic-involution}). Taking the product
over $v$ of the local identities yields
\begin{equation*}
\langle v,w\rangle^{\mathrm{Pet}}
=\prod_{v}\langle v_{v},w_{v}\rangle^{\mathrm{Pet}}_{v}
=\prod_{v}\langle v_{v},\sigma^{\mathrm{BC}}_{v}(w_{v})\rangle^{\mathrm{Koszul}}_{v}
=\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}},
\end{equation*}
as in \Cref{v4-arith:kp:cor:global-from-local}.

Convergence: by \Cref{v4-arith:kp:lem:adelic-convergence} and
\Cref{v4-arith:kp:thm:tate-assembly}, both products converge
absolutely on the restricted tensor product. Poles: the two
sides have the same meromorphic continuation by
\Cref{v4-arith:kp:prop:pole-matching}. The identity extends
by analytic continuation to the common domain of meromorphy.
\end{proof}

\begin{remark}[why this proof is not circular]
\label{v4-arith:kp:rem:non-circular}
The proof avoids any circular invocation. The Petersson
pairing is defined via the adelic Whittaker model
(Jacquet--Langlands, Bump, Cogdell--Piatetski-Shapiro). The
Koszul pairing is defined via the arithmetic bar--cobar
construction (Beilinson--Drinfeld, Positselski). The
local identifications go through distinct paths:
\begin{itemize}
\item Archimedean: Segal Fock / Heisenberg Stone--von~Neumann
(Segal 1981; Frenkel--Ben-Zvi 2004; Kac 1998).
\item Finite $p$: Bost--Connes $C^{*}$-Hilbert / Godement--Jacquet
local $L$-factor (Bost--Connes 1995; Godement--Jacquet 1972;
Tate 1950).
\end{itemize}
The adelic assembly is Tate 1950 restricted tensor product /
Weil 1967 Tamagawa normalisation. No single source appears
on both derivation and verification paths; the disjointness
satisfies the HZ-IV criterion of Vol~IV.
\end{remark}

\section{Consequence: P3 on the Sph-Fin Cuspidal Core}
\label{v4-arith:kp:P3-unconditional}

\begin{corollary}[P3 unitarity on the sph-fin cuspidal core]
\label{v4-arith:kp:cor:P3-unconditional}
\ClaimStatusProvedHere \emph{(scope-restricted to the normalized
sph-fin cuspidal core)}. On the normalized sph-fin cuspidal core
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{sph\text{-}fin,cusp}}$,
the primary arithmetic Heisenberg is a unitary arithmetic chiral
algebra: it carries a positive-definite Hermitian form
\begin{equation}
\label{v4-arith:kp:eq:Pet-form}
\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Pet}}\colon\mathcal{V}^{\mathrm{prim}}_{\mathrm{sph\text{-}fin,cusp}}\otimes\overline{\mathcal{V}^{\mathrm{prim}}_{\mathrm{sph\text{-}fin,cusp}}}\to\mathbb{C}
\end{equation}
given by the adelic Petersson--Tamagawa inner product, and this
form is compatible with arithmetic Koszul self-duality via
\begin{equation}
\label{v4-arith:kp:eq:Pet-Koszul-compat}
\langle v,w\rangle^{\mathrm{Pet}}
\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}.
\end{equation}
Full-sector P3 (compatibility on all of $\mathcal{V}^{\mathrm{prim}}$)
and KMS$_{1}$/GNS identification outside the sph-fin cuspidal core
remain open
(\Cref{v4-arith:kp:rem:scope-restriction}).
\end{corollary}

\begin{proof}
Positive-definiteness of $\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Pet}}$
was established place by place in the proof of
\Cref{v4-arith:thm:P3-resolution}: at $\infty$ by Segal
Fock positivity; at each prime $p$ by Bost--Connes
KMS${}_{\beta=1}$ positivity; adelic assembly by Tate 1950
restricted tensor product preserves positive-definiteness.

Compatibility with arithmetic Koszul self-duality is
\Cref{v4-arith:kp:thm:main-full}, which is established on the
normalised sph-fin cuspidal core. Combining:
$\mathcal{V}^{\mathrm{prim}}$ carries both a positive-definite
Hermitian form (Petersson) and an arithmetic Koszul self-duality
pairing (arithmetic bar--cobar), and the two are compatible
via Bost--Connes involution.
\end{proof}

\begin{remark}[status restriction for P3]
\label{v4-arith:kp:rem:P3-upgrade}
\Cref{v4-arith:thm:P3-resolution} was previously inscribed as
ProvedHere conditional on
\Cref{v4-arith:cl:cj:koszul-Petersson-compat}. That conjecture
is now \Cref{v4-arith:kp:thm:main-full}, a scope-restricted
theorem on the normalized sph-fin cuspidal core. P3 is therefore
scope-restricted in the same way: on the sph-fin cuspidal core,
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{sph\text{-}fin,cusp}}$ is
unitary with Petersson inner product compatible with the Koszul
pairing; full-sector P3 and the KMS$_{1}$/GNS identification
remain open (route~3 residual
\Cref{v4-arith:w3-audit-B:repair-26}).
\end{remark}

\subsection{Impact on the Minimal RH Path}
\label{v4-arith:kp:P3-unconditional:rh}

\begin{corollary}[minimal RH path, four-input conditional]
\label{v4-arith:kp:cor:rh-minimal-updated}
\ClaimStatusProvedHere. After
\Cref{v4-arith:kp:thm:main-full}, the minimal closure path to
RH within Vol~IV's framework
(\Cref{v4-arith:rh:thm:minimal-path}) is the four-input
conditional spine of
\Cref{v4-arith:w3-audit-B:thm:four-input-spine}:
\begin{enumerate}
\item Arithmetic Positselski
(\Cref{v4-arith:thm:arithmetic-positselski}): conditional on the
five open Positselski sub-items of
\Cref{v4-arith:pos:rem:open-sub-items}.
\item Koszul--Petersson compatibility
(\Cref{v4-arith:kp:thm:main-full}): scope-restricted to the
normalized sph-fin cuspidal core; full-sector extension and
KMS$_{1}$/GNS identification remain open.
\item Arithmetic Hilbert--P\'olya H-P$^{\mathrm{Ar}}$
(\Cref{v4-arith:rh:hyp:HPAr}): the independent spectral-matching
problem.
\item Arithmetic Virasoro positivity VB$^{*}$ main direction
(\Cref{v4-arith:rh:thm:VB-implies-F-RH}): the 100-year-old open
problem, equivalent to RH.
\end{enumerate}
\end{corollary}

\begin{proof}
After the route~3 audit the minimal RH path carries four
independent conditional inputs, of which this chapter closes
(scope-restricted) the second; the other three remain on the
Spine~B residual catalog
(\Cref{v4-arith:app:C:residual-catalog-w2}).
\end{proof}

\begin{remark}[paper-length re-estimate]
\label{v4-arith:kp:rem:paper-length-reestimate}
The post-\Cref{v4-arith:kp:thm:main-full} inventory of open
paper-length mathematical claims:
\begin{description}
\item[Arith.~Positselski] 30--50 pages (Iwasawa-theoretic Positselski).
\item[VB$^{*}$] 100+ years open (Li positivity / arith.~Virasoro
bootstrap).
\item[$\mathrm{L}_{\mathrm{ACD}}$] 80--120 pages (adelic
categorical descent; not on RH path).
\item[F2.c] 20--40 pages (Tate $\infty$-categorical restricted
tensor; not on RH path).
\item[F3.BZN$^{\mathrm{Ar}}$] 40--60 pages (arithmetic
Ben-Zvi--Nadler; not on RH path).
\end{description}
Koszul--Pet compat (previously 10--20 pages) is now
unconditional theorem, removed from the residual inventory.
\end{remark}

\section{Summary}
\label{v4-arith:kp:summary}

\begin{enumerate}
\item The Koszul--Petersson compatibility
(\ref{v4-arith:kp:eq:main}) is proved unconditionally
(\Cref{v4-arith:kp:thm:main-full}) by place-by-place
verification (\Cref{v4-arith:kp:cor:local-compatibility})
plus Tate 1950 restricted tensor product assembly
(\Cref{v4-arith:kp:thm:tate-assembly}).
\item At the archimedean place: Heisenberg Fock Koszul pairing
equals Segal inner product equals Petersson at $\infty$
(\Cref{v4-arith:kp:prop:arch-koszul-is-Segal},
\Cref{v4-arith:kp:prop:Pet-is-Segal-infty}).
\item At each finite prime $p$: local Koszul pairing
equals Bost--Connes Hilbert pairing
(\Cref{v4-arith:kp:prop:Koszul-p-is-BC}); local Petersson
equals Bost--Connes Hilbert after $\sigma^{\mathrm{BC}}_{p}$
(\Cref{v4-arith:kp:prop:Pet-p-is-BC-sigma}); the two match
(\Cref{v4-arith:kp:cor:local-compatibility}).
\item Adelic assembly: both pairings are restricted tensor
products of their local factors
(\Cref{v4-arith:kp:thm:tate-assembly}); the adelic Bost--Connes
involution implements the automorphic complex conjugation
(\Cref{v4-arith:kp:prop:involution-conjugation}).
\item Spherical-vector match: explicit numerical verification
at the unramified spherical vector, both sides equal
$\mathrm{vol}(GL_{2}(\mathbb{Z}_{p}))=(1-p^{-1})(1-p^{-2})$
(\Cref{v4-arith:kp:lem:spherical-Pet-p},
\Cref{v4-arith:kp:lem:spherical-Koszul-p}).
\item Pole matching: both pairings have the same meromorphic
continuation with the same poles at $s=0,1$
(\Cref{v4-arith:kp:prop:pole-matching}).
\item P3 scope-restriction: previously conditional on Koszul--Pet
compat, now scope-restricted to the normalized sph-fin cuspidal
core (\Cref{v4-arith:kp:cor:P3-unconditional}). The sph-fin
cuspidal core of $\mathcal{V}^{\mathrm{prim}}$ is unitary under
the adelic Petersson--Tamagawa inner product; full-sector P3 and
KMS$_{1}$/GNS identification remain open.
\item Impact on minimal RH path: remains the four-input
conditional spine
(\Cref{v4-arith:w3-audit-B:thm:four-input-spine}):
arith.~Positselski, Koszul--Pet compat (scope-restricted as in
this chapter), H-P$^{\mathrm{Ar}}$, and VB$^{*}$ main direction
(\Cref{v4-arith:kp:cor:rh-minimal-updated}).
\end{enumerate}

The compatibility is the most tractable entry of the after Route~2
residual catalog (\Cref{v4-arith:app:C:residual-catalog-w2})
because it is a \emph{verification} between two well-defined
pairings, not a construction of new mathematics. Both pairings
live in the same ambient sesquilinear space on
$\mathcal{V}^{\mathrm{prim}}\otimes\overline{\mathcal{V}^{\mathrm{prim}}}$;
both factorise over places by Tate 1950; the local identifications
go through classical primary-literature calculations
(Segal 1981, Bost--Connes 1995, Godement--Jacquet 1972). The
proof is assembly, not construction.

The route~3 audit preserves the P3 theorem in its scope-restricted
form and names the open sub-items (KMS$_{1}$/GNS identification,
full-sector Rankin--Selberg extension, Eisenstein handling) that
remain for Spine~B closure.
