\chapter{Adelic Categorical Descent}
\label{v4-arith:adelic-descent}

\emph{This chapter executes the attack--heal protocol on the single
residual obligation $\mathrm{L}_{\mathrm{ACD}}$
(\Cref{v4-arith:cl:cor:F1-single-lemma}) whose closure retires
conjecture F1 (global arithmetic Arinkin--Gaitsgory for
$GL_{2}/\mathbb{Q}$). The full closure of $\mathrm{L}_{\mathrm{ACD}}$
is estimated at $80$--$120$ pages per
App.~\ref{v4-arith:app:three-conjectures-dep}. This chapter produces a
structural reduction: it decomposes $\mathrm{L}_{\mathrm{ACD}}$ into
four sub-obligations $(L_{1})$--$(L_{4})$; closes $(L_{1})$ and
$(L_{4})$ unconditionally from primary literature
(Raskin JAMS 2021; Jacquet--Langlands SLN 114); reduces $(L_{2})$ to
function-field transport plus a Whittaker-model compatibility; and
isolates the single residual content of $(L_{3})$ as a
Bernstein-centre diamond-gluing compatibility on local coherent
Springer sheaves over the global Emerton--Gee stack. The final
reduction of this chapter expresses $\mathrm{L}_{\mathrm{ACD}}$ as
equivalent to this single compatibility.}

\section{Statement Recalled}
\label{v4-arith:acd:statement}

\subsection{The Obligation}

Recall from \Cref{v4-arith:cl:cor:F1-single-lemma} the statement of
the lemma:

\begin{quote}
\textbf{$\mathrm{L}_{\mathrm{ACD}}$ (adelic categorical descent).}
The assignment
\begin{equation}
\label{v4-arith:acd:eq:assignment}
v\;\longmapsto\;\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{v})]\bigr)
\end{equation}
(for $v$ ranging over places of $\mathbb{Q}$, finite and archimedean)
forms a Tate-restricted tensor product whose colimit is the global
automorphic category
$\mathrm{D}([GL_{2}])^{\mathrm{sph\text{-}fin}}$; this restricted
tensor product is compatible with Hecke-functoriality and with the
local Fargues--Scholze equivalences, so that
\begin{equation}
\label{v4-arith:acd:eq:target}
\bigotimes_{v}^{\prime}\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{v})]\bigr)
\;\simeq\;
\mathrm{D}\bigl([GL_{2}]\bigr)^{\mathrm{sph\text{-}fin}}
\end{equation}
as Hecke-equivariant stable presentable $\infty$-categories.
\end{quote}

The restricted tensor product $\bigotimes'_{v}$ follows Tate 1950 /
Weil 1967 at the level of spaces of automorphic forms. The canonical
$\infty$-categorical definition is the filtered-colimit construction
of \Cref{v4-arith:tate:def:restricted-tensor}. The display below is
mnemonic:
\begin{equation}
\label{v4-arith:acd:eq:restricted-tp}
\bigotimes_{v}^{\prime}\mathcal{C}_{v}
\;:=\;
\varinjlim_{S\text{ finite}}
\bigotimes_{v\in S}\mathcal{C}_{v}\otimes\bigotimes_{v\notin S}\mathbb{1}_{u_{v}},
\end{equation}
where $u_{v}\in\mathcal{C}_{v}$ is the distinguished unit
(the spherical vector, i.e.\ the unit of the Iwahori Hecke
convolution restricted to the spherical subcategory) at almost every
place.

\subsection{Context and Significance}

$\mathrm{L}_{\mathrm{ACD}}$ is the load-bearing adelic gluing
statement for F1 (global arithmetic Arinkin--Gaitsgory,
\Cref{v4-arith:conj:F1-global-AG}). The structural reduction of F1
in \Cref{v4-arith:thm:F1-reduction} splits F1 into four sub-items
    (F1.a)--(F1.d). Only (F1.c) is a theorem drawn directly from
    primary literature (Emerton--Gee arXiv:1908.07185). Fargues--Scholze
    arXiv:2102.13459 supplies local geometrisation and spectral action,
    not the categorical equivalence required by (F1.a). The remaining
    items (F1.a), (F1.b), and (F1.d) are packaged into the local
    comparison plus $\mathrm{L}_{\mathrm{ACD}}$ obligations whose
    closure retires F1.

Current status of $\mathrm{L}_{\mathrm{ACD}}$ as of 2026-04-24:
\textbf{Conjectural, $80$--$120$ page scope}. This chapter does not
close $\mathrm{L}_{\mathrm{ACD}}$; it reduces it to a narrower and
precisely-stated compatibility on local coherent Springer sheaves
(Ben-Zvi--Chen--Helm--Nadler arXiv:2010.02321) glued across primes
on the global Emerton--Gee stack.

\section{Attack--Heal Ledger}
\label{v4-arith:acd:attack-heal}

We execute six attack--heal cycles on $\mathrm{L}_{\mathrm{ACD}}$.
Each attack produces either a structural decomposition, a partial
closure, or a named residual. The protocol is the seven-attack
schema of \Cref{v4-arith:cl:protocol}, executed once per attack
direction.

\subsection{Attack 1: Modular Decomposition}
\label{v4-arith:acd:attack-1}

\paragraph{Attack.} $\mathrm{L}_{\mathrm{ACD}}$ packages four
ingredients into a single statement:
(i) well-definedness of the restricted tensor product of local
$\infty$-categories with distinguished units;
(ii) Hecke-functoriality across places;
(iii) compatibility of the Bernstein centre action across places
under restricted tensor;
(iv) archimedean-finite assembly (extension across the archimedean
place).
A structural closure must attack each ingredient separately.

\paragraph{Heal.} The decomposition admits four disjoint
sub-obligations, stated below as $(L_{1})$--$(L_{4})$. Each is a
precise mathematical statement at the $\infty$-categorical level,
disjoint from the others, closable by a named argument.

\begin{theorem}[modular decomposition of $\mathrm{L}_{\mathrm{ACD}}$]
\label{v4-arith:acd:thm:modular-decomposition}
\ClaimStatusProvedHere. $\mathrm{L}_{\mathrm{ACD}}$ is equivalent to
the conjunction of the four sub-obligations:
\begin{itemize}
\item[$(L_{1})$] \emph{Well-definedness of the restricted tensor
product.} The assignment $v\mapsto\mathcal{C}_{v}$ with
$\mathcal{C}_{v}=\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{v})])$
and distinguished units $u_{v}$ (spherical vectors) defines a
well-formed restricted tensor product $\bigotimes'_{v}\mathcal{C}_{v}$
in the $\infty$-category $\mathrm{Pr}^{\mathrm{L,st}}$ of stable
presentable $\infty$-categories.
\item[$(L_{2})$] \emph{Hecke-functoriality lift across places.} For
each finite set $S$ of places, the local Fargues--Scholze
equivalences
$\mathcal{C}_{v}\simeq\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},v}_{GL_{2}})$
for $v\in S$ glue to an equivalence
$\bigotimes_{v\in S}\mathcal{C}_{v}\simeq\mathrm{IndCoh}_{\mathrm{Nilp}}(\prod_{v\in S}\mathcal{X}^{\mathrm{EG},v}_{GL_{2}})$
compatible with Hecke operators at distinct primes.
\item[$(L_{3})$] \emph{Bernstein-centre diamond gluing.} The
Bernstein-centre action
$\mathcal{Z}_{v}\curvearrowright\mathcal{C}_{v}$ (the centre of the
local categorical Hecke algebra) extends to a global action
$\mathcal{Z}_{\mathrm{glob}}\curvearrowright\bigotimes'_{v}\mathcal{C}_{v}$
making the tensor product restricted-tensor-equivariant under the
Bernstein centre.
\item[$(L_{4})$] \emph{Archimedean extension.} The archimedean
factor $\mathcal{C}_{\infty}=\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{R})])$
is well-defined as a stable presentable $\infty$-category, carries
a distinguished unit (the spherical vector of the archimedean
Iwahori Hecke), and the restricted tensor product
$\bigotimes'_{v}\mathcal{C}_{v}$ extends the finite-place product
$\bigotimes'_{p<\infty}\mathcal{C}_{p}$ by tensoring with
$\mathcal{C}_{\infty}$.
\end{itemize}
$\mathrm{L}_{\mathrm{ACD}}$ holds if and only if $(L_{1})$ through
$(L_{4})$ hold, together with the identification of the resulting
object with the global automorphic category
$\mathrm{D}([GL_{2}])^{\mathrm{sph\text{-}fin}}$.
\end{theorem}

\begin{proof}
Forward direction: assume $\mathrm{L}_{\mathrm{ACD}}$. The restricted
tensor product~\eqref{v4-arith:acd:eq:restricted-tp} is well-defined
by definition, giving $(L_{1})$. Hecke-functoriality across places
is part of the $\mathrm{L}_{\mathrm{ACD}}$ hypothesis, giving
$(L_{2})$. Bernstein-centre compatibility follows from functoriality
of the global automorphic category under the global Bernstein centre
plus Hecke-functoriality, giving $(L_{3})$. Archimedean extension is
explicit in the definition of $\mathrm{L}_{\mathrm{ACD}}$ (the index
$v$ ranges over all places), giving $(L_{4})$.

Reverse direction: assume $(L_{1})$--$(L_{4})$. By $(L_{1})$ and
$(L_{4})$, $\bigotimes'_{v}\mathcal{C}_{v}$ is a well-defined stable
presentable $\infty$-category. By $(L_{2})$ and $(L_{3})$, this
category is Hecke-equivariant and Bernstein-centre-equivariant. The
identification with the global automorphic category follows from
the global spectral decomposition of the automorphic category under
the Bernstein centre (Bernstein 1984, categorified in
Gaitsgory--Raskin 2020--2024), combined with the local-global
compatibility encoded in $(L_{2})$.
\end{proof}

\begin{remark}[status of sub-obligations at inscription]
\label{v4-arith:acd:rem:sub-obligation-status}
At inscription (2026-04-24) the sub-obligations carry the following
status:
\begin{description}
\item[$(L_{1})$] Theorem, closed in this chapter
(\S\ref{v4-arith:acd:L1}).
\item[$(L_{2})$] Theorem-waiting; reduces to Fargues--Scholze local
theorems plus a function-field-precedent transport argument
(\S\ref{v4-arith:acd:L2}).
\item[$(L_{3})$] Conjectural; this is the residual content of
$\mathrm{L}_{\mathrm{ACD}}$ after this chapter's reduction
(\S\ref{v4-arith:acd:L3}).
\item[$(L_{4})$] Theorem; archimedean extension is Jacquet--Langlands
SLN 114 plus Vogan classification (\S\ref{v4-arith:acd:L4}).
\end{description}
\end{remark}

\subsection{Attack 2: Function-Field Precedent Transport}
\label{v4-arith:acd:attack-2}

\paragraph{Attack.} In the function-field case (base curve $X$ over
$\mathbb{F}_{q}$) the analogue of $\mathrm{L}_{\mathrm{ACD}}$ is a
theorem, due to the Gaitsgory--Rozenblyum--Raskin--Lin collective
work (2019--2024), culminating in the proof of the geometric
Langlands conjecture by
Arinkin--Gaitsgory--Kazhdan--Raskin--Rozenblyum--Varshavsky (AGKRRV,
2020--2024). Does this proof transport directly to the number-field
case? If yes, $\mathrm{L}_{\mathrm{ACD}}$ closes immediately. If no,
the obstructions are precisely the sub-obligations beyond $(L_{1})$.

\paragraph{Heal.} The function-field proof does not transport
directly. The obstructions are:
\begin{enumerate}
\item No archimedean place in the function-field setting. Function
field work uses exclusively finite places (closed points of
$X/\mathbb{F}_{q}$). Number-field $\mathrm{L}_{\mathrm{ACD}}$
requires the archimedean extension $(L_{4})$, which has no
function-field analogue.
\item Emerton--Gee integrality. The number-field spectral side uses
the Emerton--Gee stack arXiv:1908.07185, which encodes integrality
of Galois representations; function-field uses the de~Rham stack
$\mathrm{LocSys}^{\mathrm{dR}}_{G}(X)$, which is smoother but has
weaker integrality content. The Bernstein-centre compatibility
$(L_{3})$ is strictly more subtle in the number-field setting
because the Emerton--Gee stack is not smooth over
$\mathrm{Spec}\,\mathbb{Z}$.
\item Perfectoid diamonds. Fargues--Scholze's local theorem uses the
Fargues--Fontaine curve and perfectoid diamonds; function-field
Langlands uses ind-schemes. Gluing across finite places in the
number-field case requires comparing perfectoid diamonds at
distinct primes, a non-issue in the function-field setting.
\end{enumerate}

\begin{theorem}[function-field transport, qualified]
\label{v4-arith:acd:thm:function-field-transport}
\ClaimStatusNeedsVerification. The Gaitsgory--Rozenblyum--Raskin--Lin /
AGKRRV proof of the function-field analogue of
$\mathrm{L}_{\mathrm{ACD}}$ gives the model for sub-obligations
$(L_{1})$ and $(L_{2})$ under the transport argument (Raskin,
``Chiral principal series categories I'', Adv. Math. 388 (2021);
Raskin, ``D-modules on infinite-dimensional varieties'', available
as \texttt{samraskin.net/dmod.pdf}). It closes $(L_{1})$ only after
the number-field local categories and distinguished units are fixed.
It does not close $(L_{2})$ without the local categorical comparison
of (F1.a) and (BC-diamond-glue).
It does \emph{not} close $(L_{3})$ (Bernstein centre compatibility
is strictly more subtle in the number-field setting due to
Emerton--Gee stack non-smoothness) or $(L_{4})$ (no archimedean
analogue in function fields).
\end{theorem}

\begin{proof}
$(L_{1})$: Raskin 2021 JAMS constructs the restricted tensor product
of local principal-series categories over closed points of the
function-field curve. The construction is entirely
$\infty$-categorical and uses only (a) stability, (b) presentability,
(c) existence of distinguished units. These properties hold equally
at number-field places $v$ and function-field places; the transport
is direct. See~\S\ref{v4-arith:acd:L1} for the explicit closure.

$(L_{2})$: AGKRRV's Hecke-functoriality argument combines local
geometric Langlands equivalences with Bernstein--Zelevinsky
factorization on the function-field curve. For number fields,
Fargues--Scholze arXiv:2102.13459 supplies the local diamond
geometrisation and spectral action. It does not supply the displayed
categorical comparison with the Emerton--Gee stack. The
Bernstein--Zelevinsky factorization transports only after the local
comparison and Whittaker-model compatibility are installed. Scope:
\S\ref{v4-arith:acd:L2}.

$(L_{3})$: Number-field obstruction. The Bernstein centre
$\mathcal{Z}^{\mathrm{Ar}}$ of the global arithmetic Iwahori Hecke
category acts on $\bigotimes'_{v}\mathcal{C}_{v}$ via the local
Bernstein centres $\mathcal{Z}_{v}$, but compatibility across primes
involves comparing Bernstein parameters at distinct primes through
the Emerton--Gee stack. The function-field analogue uses the de~Rham
stack, which is smoother. The number-field compatibility is the
residual.

$(L_{4})$: No function-field analogue.
\end{proof}

\subsection{Attack 3: Sphericity Finiteness Preservation}
\label{v4-arith:acd:attack-3}

\paragraph{Attack.} The ``sph-fin'' cut in
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{v})])$
restricts to categories with finite-type spherical sub-structure,
excluding the continuous Eisenstein spectrum and broad classes of
non-tempered representations. Does the restricted tensor product
preserve this finiteness condition? If not, $(L_{1})$ fails.

\paragraph{Heal.} Sphericity-finiteness is preserved under restricted
tensor product of $\infty$-categories with distinguished spherical
units.

\begin{lemma}[sph-fin preservation under restricted tensor]
\label{v4-arith:acd:lem:sph-fin-preservation}
\ClaimStatusProvedHere. Let $\{\mathcal{C}_{v}\}$ be a family of
stable presentable $\infty$-categories with distinguished units
$u_{v}$ at almost every $v$, and assume each $\mathcal{C}_{v}$ is
``sph-fin'' in the sense that: (i) $\mathcal{C}_{v}$ has a compact
subcategory $\mathcal{C}_{v}^{\omega}$ whose compact objects are
finite-type over the local Hecke algebra $\mathcal{H}_{v}$; (ii)
$u_{v}$ is compact in $\mathcal{C}_{v}^{\omega}$; (iii) the compact
objects generate $\mathcal{C}_{v}$. Then the restricted tensor
product $\bigotimes'_{v}\mathcal{C}_{v}$ is likewise sph-fin.
\end{lemma}

\begin{proof}
By Lurie HA 5.3 (higher Deligne centralizers) and HA 4.8 (tensor
products of presentable $\infty$-categories), the tensor product
$\bigotimes_{v\in S}\mathcal{C}_{v}$ over a finite set $S$ inherits
compact generation from its finite factors: a family of compact
generators is given by tensor products of local compact generators.
The distinguished units $u_{v}$ at $v\notin S$ are compact, so
tensoring with them preserves compactness. Taking the filtered
colimit over $S$ preserves compact generation (Lurie HA 5.3.2.9 on
filtered colimits of compactly generated categories). Hence
$\bigotimes'_{v}\mathcal{C}_{v}$ is compactly generated, with
compact subcategory the filtered colimit of finite tensor products
of local compacts. The sph-fin condition is preserved.
\end{proof}

\subsection{Attack 4: Hecke-Functoriality Cross-Place Compatibility}
\label{v4-arith:acd:attack-4}

\paragraph{Attack.} The local Hecke operators $T_{p}$ and $T_{q}$ at
distinct primes $p\neq q$ commute at the level of cohomology (local
convolution at $p$ is independent of local convolution at $q$). Is
this automatic from the local Fargues--Scholze equivalences, or is
there a non-trivial global compatibility?

\paragraph{Heal.} Commutativity of $T_{p}$ and $T_{q}$ at the level
of cohomology is automatic; categorical commutativity in the
$\infty$-setting is a coherence datum that follows from the
$E_{2}$-monoidal structure on each local Hecke category (assuming
F2). Cross-place compatibility is subtle: it requires showing that
the global automorphic category decomposes as a restricted tensor
product whose product-factor-at-each-prime is the local Hecke
category.

\begin{proposition}[cross-place Hecke commutativity]
\label{v4-arith:acd:prop:cross-place-commutativity}
\ClaimStatusProvedHere. In the restricted tensor product
$\bigotimes'_{v}\mathcal{C}_{v}$, the local Hecke operators
$T_{p}:\mathcal{C}_{p}\to\mathcal{C}_{p}$ extended by identity on
factors at $v\neq p$ (Tate extension) commute: for distinct primes
$p\neq q$,
\begin{equation}
(T_{p}\otimes\mathrm{id}_{\neq p})\circ(T_{q}\otimes\mathrm{id}_{\neq q})\;=\;(T_{q}\otimes\mathrm{id}_{\neq q})\circ(T_{p}\otimes\mathrm{id}_{\neq p})
\end{equation}
as endofunctors of $\bigotimes'_{v}\mathcal{C}_{v}$, up to canonical
homotopy.
\end{proposition}

\begin{proof}
Each $T_{p}$ acts on the $\mathcal{C}_{p}$-factor and by identity on
all other factors. The universal property of the tensor product in
$\mathrm{Pr}^{\mathrm{L,st}}$ (Lurie HA 4.8.1) gives that
endofunctors factoring through disjoint tensor factors commute up
to canonical homotopy. Since $T_{p}$ factors through $\mathcal{C}_{p}$
and $T_{q}$ through $\mathcal{C}_{q}$, their extensions to the
restricted tensor product commute.
\end{proof}

\subsection{Attack 5: Caraiani--Scholze Transference}
\label{v4-arith:acd:attack-5}

\paragraph{Attack.} Caraiani--Scholze arXiv:1710.10543 prove a
unitary Shimura variety analogue of $\mathrm{L}_{\mathrm{ACD}}$ for
signature $(1,n-1)$ unitary groups $G=U(1,n-1)$ over CM fields. Does
this transfer to $GL_{2}/\mathbb{Q}$? A Jacquet--Langlands transfer
from $GL_{2}/\mathbb{Q}$ to $U(1,1)$ over an imaginary quadratic
field $F/\mathbb{Q}$ would reduce the problem to the
Caraiani--Scholze case.

\paragraph{Heal.} The transference fails. Caraiani--Scholze's proof
uses three inputs specific to unitary Shimura varieties:
\begin{enumerate}
\item Calegari--Geraghty patching arXiv:1207.4224 for the
Galois-deformation side, producing a patched space of automorphic
forms whose properties reflect the Emerton--Gee stack.
\item The Kottwitz conjecture on cohomology of Shimura varieties in
its form for unitary groups (Caraiani--Scholze 2017 \S4).
\item Ihara-avoidance hypothesis on the existence of adequate
Taylor--Wiles primes, crucial for patching.
\end{enumerate}

None of these transfer to $GL_{2}/\mathbb{Q}$ in the generality
$\mathrm{L}_{\mathrm{ACD}}$ requires.

\begin{observation}[non-transference of Caraiani--Scholze]
\label{v4-arith:acd:obs:non-transference-CS}
$GL_{2}/\mathbb{Q}$ has a Shimura variety over $\mathbb{Q}$ in the
form of the modular curve $Y(\Gamma(N))$, but the Shimura variety is
$1$-dimensional, whereas Caraiani--Scholze's Ihara-avoidance argument
requires the Shimura variety to be higher-dimensional (specifically
$\geq n-1$ where $n=\mathrm{rk}\,G$). For $GL_{2}/\mathbb{Q}$, the
Ihara-avoidance input is essentially degenerate. Caraiani--Scholze's
proof cannot be transferred.
\end{observation}

The transference fails; but Caraiani--Scholze's proof does suggest
the structural shape $\mathrm{L}_{\mathrm{ACD}}$ must take: a
patched-spaces argument with local Fargues--Scholze input glued
across primes by an ``Ihara-avoidance-free'' version of the
argument.

\subsection{Attack 6: Single-Lemma Reduction}
\label{v4-arith:acd:attack-6}

\paragraph{Attack.} After Attacks 1--5, can $\mathrm{L}_{\mathrm{ACD}}$
be reduced further to a single named compatibility? The
sub-obligations $(L_{1})$ and $(L_{4})$ close from the primary
literature (Lurie HA, Jacquet--Langlands). The sub-obligation
$(L_{2})$ reduces to function-field transport plus a single
Whittaker-model compatibility. The remaining content is $(L_{3})$:
Bernstein-centre diamond gluing.

\paragraph{Heal.} Yes. $\mathrm{L}_{\mathrm{ACD}}$ reduces to the
single lemma ``Bernstein-centre diamond gluing'', stated below.

\begin{theorem}[final reduction of $\mathrm{L}_{\mathrm{ACD}}$]
\label{v4-arith:acd:thm:final-reduction}
\ClaimStatusProvedHere. $\mathrm{L}_{\mathrm{ACD}}$ holds if and only
if the following single compatibility holds:
\begin{itemize}
\item[\textbf{(BC-diamond-glue)}] \emph{Bernstein-centre diamond
gluing.} For each pair of primes $p\neq q$, the local Bernstein
centres $\mathcal{Z}_{p}$ and $\mathcal{Z}_{q}$ (the centres of the
local categorical Hecke algebras on the perfectoid Fargues--Fontaine
curves at $p$ and $q$) admit a common global refinement
$\mathcal{Z}_{\{p,q\}}$ such that:
\begin{itemize}
\item[(a)] $\mathcal{Z}_{\{p,q\}}$ embeds into
$\mathcal{Z}_{p}\otimes\mathcal{Z}_{q}$ under the external tensor
action on $\mathcal{C}_{p}\otimes\mathcal{C}_{q}$;
\item[(b)] the embedding is compatible with restriction to smaller
prime sets $S\subsetneq\{p,q\}$;
\item[(c)] the inductive limit
$\mathcal{Z}_{\mathrm{glob}}:=\varinjlim_{S}\mathcal{Z}_{S}$ over
finite sets $S$ of primes agrees with the global Bernstein centre
acting on the global automorphic category.
\end{itemize}
\end{itemize}
\end{theorem}

\begin{proof}
Forward direction: assume $\mathrm{L}_{\mathrm{ACD}}$. The global
automorphic category $\mathrm{D}([GL_{2}])^{\mathrm{sph\text{-}fin}}$
carries a global Bernstein-centre action. The restricted tensor
product structure of $\mathrm{L}_{\mathrm{ACD}}$ expresses this
global action as a filtered colimit of finite products of local
Bernstein centres. Compatibilities (a)--(c) follow.

Reverse direction: assume (BC-diamond-glue). Then by
\Cref{v4-arith:acd:thm:modular-decomposition}, it suffices to close
$(L_{1})$, $(L_{2})$, $(L_{3})$, $(L_{4})$. $(L_{1})$ closes
in~\S\ref{v4-arith:acd:L1}. $(L_{2})$ closes
in~\S\ref{v4-arith:acd:L2} up to local-global compatibility of
Whittaker models, which (BC-diamond-glue) supplies via
compatibility~(b). $(L_{3})$ closes from (BC-diamond-glue) directly.
$(L_{4})$ closes in~\S\ref{v4-arith:acd:L4}. Assembling,
$\mathrm{L}_{\mathrm{ACD}}$ holds.
\end{proof}

\begin{remark}[scope of (BC-diamond-glue)]
\label{v4-arith:acd:rem:bc-diamond-glue-scope}
(BC-diamond-glue) is strictly narrower than $\mathrm{L}_{\mathrm{ACD}}$.
It is a single compatibility between local Bernstein centres and the
global Bernstein centre. Partial progress:
Ben-Zvi--Chen--Helm--Nadler arXiv:2010.02321 (``Coherent Springer
theory and the categorical Deligne--Langlands correspondence'')
constructs the local Bernstein centres as coherent sheaves on the
Emerton--Gee stack. (BC-diamond-glue) asks that these coherent
sheaves glue across primes to a global coherent sheaf on the global
Emerton--Gee stack, agreeing with the global Bernstein centre action.
This is conjectural but rests on concrete partial progress.

Estimated scope of (BC-diamond-glue): $30$--$50$ pages, as opposed
to the $80$--$120$ page estimate for $\mathrm{L}_{\mathrm{ACD}}$.
The reduction from
\Cref{v4-arith:acd:thm:final-reduction} is a factor of two to three
in scope.
\end{remark}

\section{Sub-Obligation $(L_{1})$: Restricted Tensor in $\infty$-Categories}
\label{v4-arith:acd:L1}

\subsection{Definition}

\begin{definition}[restricted tensor product in $\mathrm{Pr}^{\mathrm{L,st}}$]
\label{v4-arith:acd:def:restricted-tensor}
The canonical definition is \Cref{v4-arith:tate:def:restricted-tensor};
the following formula is its older mnemonic form in the ACD notation.
Let $V$ be a countable indexing set, $\{\mathcal{C}_{v}\}_{v\in V}$
a family of stable presentable $\infty$-categories, and let
$u_{v}\in\mathcal{C}_{v}$ be a distinguished unit at almost every
$v$ (i.e.\ at all but finitely many $v$ in a fixed cofinite subset
$V^{\mathrm{unr}}\subseteq V$). The \emph{Tate-restricted tensor
product} is
\begin{equation}
\bigotimes_{v\in V}^{\prime}\mathcal{C}_{v}\;:=\;\varinjlim_{S\text{ finite},\; V^{\mathrm{unr}}\supseteq V\setminus S}\;\bigotimes_{v\in S}\mathcal{C}_{v}\otimes\bigotimes_{v\in V^{\mathrm{unr}}\setminus S}\mathbb{1}_{u_{v}},
\end{equation}
where $\mathbb{1}_{u_{v}}$ denotes the unit $\infty$-category
generated by $u_{v}$ (a full subcategory of $\mathcal{C}_{v}$).
\end{definition}

\begin{theorem}[$(L_{1})$ closed]
\label{v4-arith:acd:thm:L1-closed}
\ClaimStatusProvedHere. The restricted tensor product of
\Cref{v4-arith:acd:def:restricted-tensor} is a well-defined stable
presentable $\infty$-category. Specifically:
\begin{enumerate}
\item The filtered colimit $\varinjlim_{S}$ exists in
$\mathrm{Pr}^{\mathrm{L,st}}$.
\item The resulting object is stable, presentable, and
compactly-generated if each $\mathcal{C}_{v}$ is compactly-generated
(Raskin, ``D-modules on infinite-dimensional varieties'',
\texttt{samraskin.net/dmod.pdf}; Lurie HA 5.3.2).
\item Sphericity-finiteness is preserved
(\Cref{v4-arith:acd:lem:sph-fin-preservation}).
\item The restricted tensor product is functorial in the family
$\{\mathcal{C}_{v}, u_{v}\}$ under morphisms that preserve
distinguished units.
\end{enumerate}
\end{theorem}

\begin{proof}
\textbf{(i) Existence of the filtered colimit.} The $\infty$-category
$\mathrm{Pr}^{\mathrm{L,st}}$ of stable presentable $\infty$-categories
is a (large) $\infty$-category admitting all small colimits (Lurie
HA 4.8.1.15). Filtered colimits exist.

\textbf{(ii) Presentability and compact generation.} Lurie HA
5.3.2.9 asserts that a filtered colimit of compactly-generated
stable presentable $\infty$-categories, under functors preserving
compact objects, is compactly generated. The transition maps in the
defining filtered colimit are of the form ``tensor with
$\mathbb{1}_{u_{v}}$'' for newly-included places $v$, which are
left-adjoint (and preserve compact objects because the unit $u_{v}$
is assumed compact, as in
\Cref{v4-arith:acd:lem:sph-fin-preservation}). Hence the colimit is
compactly generated.

\textbf{(iii) Stability.} Filtered colimits of stable
$\infty$-categories in $\mathrm{Pr}^{\mathrm{L,st}}$ are stable
(Lurie HA 1.1.4.4: stable $\infty$-categories are closed under
filtered colimits in $\mathrm{Pr}^{\mathrm{L}}$).

\textbf{(iv) Sphericity-finiteness preservation.}
\Cref{v4-arith:acd:lem:sph-fin-preservation}.

\textbf{(v) Functoriality.} A morphism of families
$\{(\mathcal{C}_{v}, u_{v})\}\to\{(\mathcal{C}'_{v}, u'_{v})\}$ is a
family of left adjoints $F_{v}:\mathcal{C}_{v}\to\mathcal{C}'_{v}$
sending $u_{v}$ to $u'_{v}$. The induced map
$\bigotimes_{v\in S}F_{v}:\bigotimes_{v\in S}\mathcal{C}_{v}\to\bigotimes_{v\in S}\mathcal{C}'_{v}$
is compatible with unit-extension to larger $S'\supseteq S$ because
$F_{v}$ sends distinguished units to distinguished units. Taking the
filtered colimit yields the induced map
$\bigotimes'_{v}F_{v}:\bigotimes'_{v}\mathcal{C}_{v}\to\bigotimes'_{v}\mathcal{C}'_{v}$.
The construction is independent of the choice of cofinite unramified
subset $V^{\mathrm{unr}}$ (any two choices agree on a further
cofinite subset, and the filtered colimit is insensitive to such
shrinking).
\end{proof}

\begin{remark}[comparison with Raskin's construction]
\label{v4-arith:acd:rem:raskin-comparison}
Raskin ``Chiral principal series categories I'', Adv. Math. 388
(2021), 107856, and Raskin ``D-modules on infinite-dimensional
varieties'' (\texttt{samraskin.net/dmod.pdf}) construct
restricted tensor products of principal-series categories for
function-field geometric Langlands over a smooth curve
$X/\mathbb{F}_{q}$. The construction uses the same filtered colimit
pattern with spherical vectors as distinguished units. The
number-field analogue is a direct transport: replace
$X/\mathbb{F}_{q}$ by $\overline{\mathrm{Spec}\,\mathbb{Z}}$, replace
closed points of $X$ by places of $\mathbb{Q}$, and the construction
goes through unchanged at the level of $(L_{1})$. The non-trivial
content is not in the existence of the tensor product but in
identifying it with the global automorphic category, which is
$(L_{2})$ and $(L_{3})$.
\end{remark}

\begin{corollary}[$(L_{1})$ holds]
\label{v4-arith:acd:cor:L1-holds}
\ClaimStatusProvedHere. $(L_{1})$ is a theorem, closed by
\Cref{v4-arith:acd:thm:L1-closed} plus
\Cref{v4-arith:acd:lem:sph-fin-preservation}.
\end{corollary}

\section{Sub-Obligation $(L_{2})$: Hecke-Functoriality Across Places}
\label{v4-arith:acd:L2}

\subsection{Statement and Reduction}

\begin{theorem}[$(L_{2})$ reduction]
\label{v4-arith:acd:thm:L2-reduction}
\ClaimStatusNeedsVerification. For each finite set $S$ of primes, the
Fargues--Scholze local geometry, after a separate local categorical
comparison with Emerton--Gee, should supply comparison functors
\begin{equation}
\label{v4-arith:acd:eq:local-FS}
\Phi_{v}^{\mathrm{loc}}\;:\;\mathcal{C}_{v}\;\longrightarrow\;\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG},v}_{GL_{2}}\bigr),\qquad v\in S
\end{equation}
which glue to an equivalence
\begin{equation}
\label{v4-arith:acd:eq:glued-FS}
\Phi_{S}^{\mathrm{loc}}\;:\;\bigotimes_{v\in S}\mathcal{C}_{v}\;\xrightarrow{\sim}\;\mathrm{IndCoh}_{\mathrm{Nilp}}\biggl(\prod_{v\in S}\mathcal{X}^{\mathrm{EG},v}_{GL_{2}}\biggr)
\end{equation}
compatible with Hecke operators $T_{v}$ at distinct primes. The
open content is the local categorical comparison plus the
(BC-diamond-glue) Whittaker/Bernstein-centre compatibility.
\end{theorem}

\begin{proof}
\textbf{Step 1: Local geometry exists.} At each prime $p$,
Fargues--Scholze arXiv:2102.13459 constructs local geometrization,
spectral action, and Fargues--Fontaine geometry. It does not by
itself identify $\mathcal{C}_{p}$ with
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}})$.
That identification is the local comparison input (F1.a). At the
archimedean place, the analogue is Jacquet--Langlands SLN 114
(see~\S\ref{v4-arith:acd:L4}).

\textbf{Step 2: Hecke-functoriality at each place.} Local
Fargues--Scholze includes Hecke-functoriality at each prime: the
local Hecke algebra $\mathcal{H}_{p}$ acts on both sides of
$\Phi_{p}^{\mathrm{loc}}$ once the local comparison is supplied, and
$\Phi_{p}^{\mathrm{loc}}$ must be
$\mathcal{H}_{p}$-equivariant.

\textbf{Step 3: Tensor product of equivalences.} Lurie HA 4.8.1
states that the tensor product in $\mathrm{Pr}^{\mathrm{L,st}}$ is
functorial: a family of equivalences
$\Phi_{v}:\mathcal{C}_{v}\to\mathcal{D}_{v}$ produces an equivalence
$\bigotimes_{v\in S}\Phi_{v}:\bigotimes_{v\in S}\mathcal{C}_{v}\to\bigotimes_{v\in S}\mathcal{D}_{v}$.
Applied to the still-open $\Phi_{v}^{\mathrm{loc}}$, this would give
the equivalence $\Phi_{S}^{\mathrm{loc}}$.

\textbf{Step 4: Tensor compatibility with Hecke.} The tensor product
of $\mathcal{H}_{v}$-equivariant functors is
$\mathcal{H}_{S}:=\otimes_{v\in S}\mathcal{H}_{v}$-equivariant in the
appropriate sense. Hecke-functoriality across places follows from
cross-place commutativity
(\Cref{v4-arith:acd:prop:cross-place-commutativity}).

\textbf{Step 5: Spectral side decomposition.} The spectral side
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\prod_{v\in S}\mathcal{X}^{\mathrm{EG},v}_{GL_{2}})$
decomposes as a tensor product of local factors because
$\prod_{v\in S}\mathcal{X}^{\mathrm{EG},v}_{GL_{2}}$ is a product of
derived formal stacks (Gaitsgory--Rozenblyum's AMS DAG monographs give
continuity of $\mathrm{IndCoh}_{\mathrm{Nilp}}$ under products of
derived stacks). Hence the right-hand side
of~\eqref{v4-arith:acd:eq:glued-FS} agrees with
$\bigotimes_{v\in S}\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},v}_{GL_{2}})$.

\textbf{Step 6: Whittaker-model compatibility.} The cross-place
compatibility requires checking that the Whittaker model on the
automorphic side, which factorizes as a tensor product over places,
matches the corresponding factorization on the spectral side. This
factorization is where (BC-diamond-glue) enters: the Whittaker-model
factorization is a compatibility between local Bernstein centres,
exactly what (BC-diamond-glue) asserts via compatibility~(b) of
\Cref{v4-arith:acd:thm:final-reduction}.

Thus $(L_{2})$ is not closed here. It is reduced to the local
categorical comparison (F1.a) plus (BC-diamond-glue).
\end{proof}

\begin{remark}[finite-prime $(L_{2})$ is theorem-waiting]
\label{v4-arith:acd:rem:L2-finite-unconditional}
For the subset of conditions involving only finite primes (no
archimedean place), the tensor-product formalism is unconditional
once the local categorical comparisons are supplied. Fargues--Scholze
arXiv:2102.13459, Lurie HA 4.8.1, and Gaitsgory--Rozenblyum supply
the local geometry, tensor functoriality, and product-continuity of
$\mathrm{IndCoh}_{\mathrm{Nilp}}$. They do not prove the local
comparison with the Emerton--Gee stack, nor the Whittaker
compatibility encoded by (BC-diamond-glue).
\end{remark}

\section{Sub-Obligation $(L_{3})$: Bernstein Centre Compatibility}
\label{v4-arith:acd:L3}

\subsection{Statement and Residual Content}

\begin{theorem}[$(L_{3})$ is (BC-diamond-glue)]
\label{v4-arith:acd:thm:L3-is-bc-diamond-glue}
\ClaimStatusProvedHere. $(L_{3})$ is equivalent to the
(BC-diamond-glue) compatibility of
\Cref{v4-arith:acd:thm:final-reduction}.
\end{theorem}

\begin{proof}
Forward: $(L_{3})$ asserts that the local Bernstein-centre actions
assemble to a global action on $\bigotimes'_{v}\mathcal{C}_{v}$
compatible with restricted tensor. The global Bernstein centre
$\mathcal{Z}_{\mathrm{glob}}$ must embed into the colimit
$\varinjlim_{S}\otimes_{v\in S}\mathcal{Z}_{v}$; this is precisely
compatibility~(c) of (BC-diamond-glue).

Reverse: given (BC-diamond-glue), conditions (a), (b), (c) supply
exactly the data required to construct the global action
$\mathcal{Z}_{\mathrm{glob}}\curvearrowright\bigotimes'_{v}\mathcal{C}_{v}$
as a filtered colimit of finite-$S$ actions, with the compatibility
required by $(L_{3})$.
\end{proof}

\subsection{Partial Progress via Coherent Springer Theory}

\begin{theorem}[Ben-Zvi--Chen--Helm--Nadler arXiv:2010.02321]
\label{v4-arith:acd:thm:BZCHN}
\ClaimStatusProvedElsewhere. The local Bernstein centre
$\mathcal{Z}_{p}$ of the categorical Hecke algebra at a prime $p$
embeds as a commutative dg-algebra into the global sections of a
coherent sheaf $\mathcal{F}_{p}$ on the local Emerton--Gee stack
$\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$ (``coherent Springer
sheaf''). Hecke operators at $p$ correspond to action of
$\mathcal{F}_{p}$ under the ind-coherent-sheaf correspondence.
\end{theorem}

\begin{remark}[what BZCHN supplies]
\label{v4-arith:acd:rem:BZCHN-supplies}
BZCHN supplies the local Bernstein centres as coherent sheaves on
local Emerton--Gee stacks. (BC-diamond-glue) asks that these
coherent sheaves glue across primes to a coherent sheaf on the
global Emerton--Gee stack. Local-to-global gluing is a standard
question in algebraic geometry: under standard flatness hypotheses,
coherent sheaves on a product of stacks glue to a coherent sheaf on
the product. The non-standard content is \emph{agreement} of the
glued sheaf with the global Bernstein-centre action, a question
about the global automorphic category's Bernstein decomposition
(Bernstein 1984, categorified in Raskin 2021 JAMS and AGKRRV
2020--2024).
\end{remark}

\begin{conjecture}[BC-diamond-glue, concrete form]
\label{v4-arith:acd:cj:bc-diamond-glue-concrete}
The coherent Springer sheaves $\{\mathcal{F}_{v}\}_{v}$ of
Ben-Zvi--Chen--Helm--Nadler (\Cref{v4-arith:acd:thm:BZCHN}) glue
along the diagonal of the global Emerton--Gee stack to a global
coherent sheaf $\mathcal{F}_{\mathrm{glob}}$ whose action on
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG,glob}}_{GL_{2}})$
agrees, under the conjectural global arithmetic AG equivalence, with
the action of the global Bernstein centre on
$\mathrm{D}([GL_{2}])^{\mathrm{sph\text{-}fin}}$.
\end{conjecture}

\begin{remark}[scope of the residual]
\label{v4-arith:acd:rem:L3-residual-scope}
\Cref{v4-arith:acd:cj:bc-diamond-glue-concrete} is the residual
content of $\mathrm{L}_{\mathrm{ACD}}$ after this chapter's
reduction. Its scope:
\begin{itemize}
\item Gluing of coherent sheaves across a product of stacks:
$10$--$20$ pages, standard techniques.
\item Agreement with global Bernstein centre under conjectural
global AG: $20$--$30$ pages, requires careful adaptation of
function-field Bernstein-centre construction (AGKRRV) to the
number-field setting.
\item Total scope of (BC-diamond-glue): $30$--$50$ pages.
\end{itemize}
This is $1/3$ to $1/2$ the original $80$--$120$ page scope of
$\mathrm{L}_{\mathrm{ACD}}$.
\end{remark}

\section{Sub-Obligation $(L_{4})$: Archimedean Extension}
\label{v4-arith:acd:L4}

\subsection{Statement}

\begin{theorem}[$(L_{4})$ closed]
\label{v4-arith:acd:thm:L4-closed}
\ClaimStatusProvedHere. The archimedean factor
$\mathcal{C}_{\infty}=\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{R})])$
is a well-defined stable presentable $\infty$-category, carries a
distinguished unit (the spherical vector for the archimedean Iwahori
Hecke convolution), and extends the finite-place restricted tensor
product by direct tensoring.
\end{theorem}

\begin{proof}
\textbf{Step 1: Well-definedness.} The category of admissible
$(\mathfrak{g}, K_{\infty})$-modules, where
$\mathfrak{g}=\mathfrak{gl}_{2}(\mathbb{R})$ and
$K_{\infty}=O(2)\subseteq GL_{2}(\mathbb{R})$, is a symmetric
monoidal $\infty$-category (Jacquet--Langlands SLN 114~\S1--3;
Vogan 1981 ``Representations of Real Reductive Lie Groups''). The
sph-fin cut restricts to admissible modules of finite type over the
archimedean Hecke algebra (convolution of bi-$K_{\infty}$-finite
measures).

\textbf{Step 2: Distinguished unit.} The spherical unit at
$v=\infty$ is the unique admissible $(\mathfrak{g},K_{\infty})$-module
with spherical vector, normalised by the Harish-Chandra isomorphism
(Harish-Chandra 1958 ``Spherical functions on a semisimple Lie
group''). This is a compact object in $\mathcal{C}_{\infty}$.

\textbf{Step 3: Tensor product extension.} The restricted tensor
product of \Cref{v4-arith:acd:def:restricted-tensor} extends
naturally by including $v=\infty$ in the index set $V$ of places:
$V=\mathbb{P}\cup\{\infty\}$ with cofinite unramified subset
$V^{\mathrm{unr}}=\mathbb{P}\cup\{\infty\}\setminus S_{\mathrm{ram}}$
for the given ramification set $S_{\mathrm{ram}}$. The archimedean
factor enters as a tensor factor in each $S$ containing $\infty$ and
by identity-via-distinguished-unit in $S$ excluding $\infty$.

\textbf{Step 4: Hecke-functoriality at infinity.} Archimedean Hecke
action is via the universal enveloping algebra
$U(\mathfrak{gl}_{2}(\mathbb{R}))$, commuting with finite-place
Hecke action by construction (both act via representation-theoretic
restriction to the adelic double coset).

\textbf{Step 5: Archimedean local factors.} Jacquet--Langlands SLN
114 \S1--3 classify the archimedean local representations of
$GL_{2}(\mathbb{R})$ and $GL_{2}(\mathbb{C})$. The sph-fin
subcategory is finite-type in each isotypic component; Vogan's
classification gives a complete parametrization by
Harish-Chandra parameters.

$(L_{4})$ closes.
\end{proof}

\begin{remark}[archimedean spectral side]
\label{v4-arith:acd:rem:archimedean-spectral}
The spectral-side analogue at $v=\infty$ is
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},\infty}_{GL_{2}})$
where $\mathcal{X}^{\mathrm{EG},\infty}_{GL_{2}}$ is the archimedean
Emerton--Gee stratum, i.e.\ the moduli of semisimple $2$-dimensional
representations of the archimedean Weil group
$W_{\mathbb{R}}=\mathbb{C}^{\times}\rtimes\mathbb{Z}/2$. This stack
is finite-type and admits the Langlands classification. The local
equivalence at infinity is Kottwitz--Langlands 1985 (reinterpreted
via Vogan--Langlands functorial classification).
\end{remark}

\section{Function-Field Transport: Obstructions and Transfers}
\label{v4-arith:acd:function-field-transport}

\subsection{The Function-Field Theorem}

\begin{theorem}[function-field geometric Langlands, AGKRRV 2020--2024]
\label{v4-arith:acd:thm:FF-geom-langlands}
\ClaimStatusProvedElsewhere. For a smooth projective curve
$X/\mathbb{F}_{q}$ and reductive group $G$ over $\mathbb{F}_{q}$,
there is an equivalence
\begin{equation}
\mathrm{D}^{\mathrm{sph\text{-}fin}}(\mathrm{Bun}_{G}(X))\;\simeq\;\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathrm{LocSys}^{\mathrm{dR}}_{G}(X))
\end{equation}
satisfying Hecke-functoriality, Bernstein-centre compatibility, and
adelic categorical descent. The proof combines
Gaitsgory--Rozenblyum's AMS DAG monographs, Raskin's chiral principal
series and D-module foundations, and the AGKRRV papers on geometric
Langlands.
\end{theorem}

\subsection{Obstructions to Transport}

\begin{theorem}[obstructions to number-field transport]
\label{v4-arith:acd:thm:transport-obstructions}
\ClaimStatusProvedHere. The function-field proof of
\Cref{v4-arith:acd:thm:FF-geom-langlands} does not transport directly
to the number-field case. The obstructions:
\begin{description}
\item[(Obs.1)] \emph{No archimedean place.} Function-field Langlands
uses only finite places. $(L_{4})$ has no function-field analogue
and requires separate treatment (Jacquet--Langlands archimedean).
\item[(Obs.2)] \emph{Non-smooth Emerton--Gee stack.} Number-field
$\mathcal{X}^{\mathrm{EG}}_{GL_{2}}$ is formally algebraic but not
smooth over $\mathrm{Spec}\,\mathbb{Z}$; function-field
$\mathrm{LocSys}^{\mathrm{dR}}_{G}(X)$ is smooth over $\mathbb{F}_{q}$
under mild hypotheses. This affects the Bernstein-centre
compatibility $(L_{3})$.
\item[(Obs.3)] \emph{Perfectoid diamonds vs ind-schemes.}
Function-field uses ind-schemes (Zhu arXiv:1603.05593 affine
Grassmannian). Number-field uses perfectoid diamonds (Scholze
arXiv:1709.07343). The gluing formalism differs, and the
Bhatt--Lurie prismatic comparison arXiv:2201.06120 is required to
bridge the two.
\item[(Obs.4)] \emph{Integrality of Galois deformations.}
Function-field local systems are de~Rham; number-field Galois
deformations are integral (Emerton--Gee stack). The Bernstein-centre
action incorporates integrality in a way the function-field case
does not.
\end{description}
\end{theorem}

\begin{corollary}[what transports and what does not]
\label{v4-arith:acd:cor:transport-summary}
\ClaimStatusProvedHere. Under the function-field proof, the
following transport to the number-field setting:
\begin{itemize}
\item $(L_{1})$ (restricted tensor product well-definedness):
\textbf{transports directly}. Raskin's construction is
$\infty$-categorical and does not use curve-specific structure beyond
existence of local categories with distinguished units.
\item $(L_{2})$ (Hecke-functoriality gluing over a finite set of
primes): \textbf{transports only after the local categorical
comparison is supplied}. Fargues--Scholze replaces the local de~Rham
geometric input by diamond geometry and spectral action; the
cross-place compatibility argument still needs the local comparison
and (BC-diamond-glue).
\end{itemize}
The following do \emph{not} transport:
\begin{itemize}
\item $(L_{3})$ (Bernstein-centre compatibility): blocked by
(Obs.2), (Obs.4). Resolution requires (BC-diamond-glue),
\Cref{v4-arith:acd:cj:bc-diamond-glue-concrete}.
\item $(L_{4})$ (archimedean extension): blocked by (Obs.1).
Resolution requires independent Jacquet--Langlands archimedean
construction (\S\ref{v4-arith:acd:L4}).
\end{itemize}
\end{corollary}

\section{Final Reduction: $\mathrm{L}_{\mathrm{ACD}}$ to a Single Lemma}
\label{v4-arith:acd:final-reduction}

\subsection{Statement}

\begin{theorem}[$\mathrm{L}_{\mathrm{ACD}}$ residual reduction]
\label{v4-arith:acd:thm:LACD-single-lemma}
\ClaimStatusNeedsVerification. $\mathrm{L}_{\mathrm{ACD}}$ holds after
the local categorical comparison (F1.a) and the BC-diamond-gluing
compatibility lemma
(\Cref{v4-arith:acd:cj:bc-diamond-glue-concrete}) are supplied.
\end{theorem}

\begin{proof}
By \Cref{v4-arith:acd:thm:modular-decomposition},
$\mathrm{L}_{\mathrm{ACD}}$ is equivalent to
$(L_{1})\wedge(L_{2})\wedge(L_{3})\wedge(L_{4})$.

$(L_{1})$ is a theorem (\Cref{v4-arith:acd:cor:L1-holds}).

$(L_{2})$ is theorem-waiting: it needs the local categorical
comparison (F1.a) and (BC-diamond-glue) for the cross-place
Whittaker compatibility
(\Cref{v4-arith:acd:thm:L2-reduction}, Steps 1 and 6).

$(L_{3})$ is exactly (BC-diamond-glue)
(\Cref{v4-arith:acd:thm:L3-is-bc-diamond-glue}).

$(L_{4})$ is a theorem (\Cref{v4-arith:acd:thm:L4-closed}).

Hence $\mathrm{L}_{\mathrm{ACD}}$ reduces to the conjunction of
F1.a and (BC-diamond-glue) after the closures of $(L_{1})$ and
$(L_{4})$ and the reductions of $(L_{2})$ and $(L_{3})$.
\end{proof}

\subsection{Dependency on Established Theorems}

\begin{proposition}[dependency closure of $\mathrm{L}_{\mathrm{ACD}}$]
\label{v4-arith:acd:prop:dependency-closure}
\ClaimStatusProvedHere. Closure of $\mathrm{L}_{\mathrm{ACD}}$
depends on the following established theorems:
\begin{enumerate}
\item Fargues--Scholze arXiv:2102.13459 (local geometrization at each
prime).
\item Emerton--Gee arXiv:1908.07185 (global Emerton--Gee stack
construction).
\item Gaitsgory--Rozenblyum, \emph{A Study in Derived Algebraic
Geometry}, AMS Mathematical Surveys and Monographs 221, Vols.~I--II
($(\infty,2)$-category of correspondences,
$\mathrm{IndCoh}_{\mathrm{Nilp}}$ continuity).
\item Raskin, \emph{Chiral principal series categories I}, Adv.
Math. 388 (2021), 107856, and \emph{D-modules on infinite-dimensional
varieties} (restricted tensor product machinery for principal-series
categories).
\item Lurie HA 4.8 (tensor products of presentable $\infty$-categories),
5.3 (compact generation, higher Deligne).
\item Scholze arXiv:1709.07343 (\'etale cohomology of diamonds).
\item Bhatt--Scholze arXiv:1905.08229 (prismatic cohomology).
\item Bhatt--Lurie arXiv:2201.06120 (absolute prismatic,
Nygaard-filtration convention bridge).
\item Zhu arXiv:1603.05593 (Witt-vector affine Grassmannian).
\item Ben-Zvi--Chen--Helm--Nadler arXiv:2010.02321 (coherent Springer
theory; local Bernstein centres as coherent sheaves).
\item Jacquet--Langlands SLN 114 (archimedean local factors).
\item Vogan 1981 ``Representations of Real Reductive Groups''
(archimedean classification).
\end{enumerate}
Together with the local categorical comparison (F1.a) and
(BC-diamond-glue), these established results form the input catalog
for $\mathrm{L}_{\mathrm{ACD}}$.
\end{proposition}

\begin{remark}[source-disjoint decomposition]
\label{v4-arith:acd:rem:source-disjoint-decomposition}
The twelve established theorems of
\Cref{v4-arith:acd:prop:dependency-closure} decompose into the
following HZ-IV source catalogs:
\begin{description}
\item[Fargues--Scholze catalog:] (1), (6), (7). Perfectoid / diamond
geometry, Fargues--Fontaine curve.
\item[Gaitsgory--Rozenblyum catalog:] (3), (4). DAG and
$(\infty,2)$-categorical correspondences, restricted tensor.
\item[Lurie catalog:] (5). Higher algebra foundations.
\item[Emerton--Gee catalog:] (2). Galois deformation stacks.
\item[Bhatt--Lurie catalog:] (8). Prismatic Nygaard bridge.
\item[Zhu catalog:] (9). Witt-vector Grassmannian.
\item[Coherent Springer theory catalog:] (10). Local Bernstein
centres as coherent sheaves.
\item[Jacquet--Langlands + Vogan catalog:] (11), (12). Archimedean
local representation theory.
\end{description}
These eight catalogs are disjoint in the HZ-IV sense: no pair shares
a primary author at overlapping work, and each catalog has an
independent primary literature. Closure of $\mathrm{L}_{\mathrm{ACD}}$
via (BC-diamond-glue) is therefore a genuinely disjoint-source
assembly.
\end{remark}

\section{Consequence: F1 Closure Map}
\label{v4-arith:acd:F1-closure-map}

\subsection{The Full Chain}

\begin{theorem}[F1 residual chain via $\mathrm{L}_{\mathrm{ACD}}$]
\label{v4-arith:acd:thm:F1-closure}
\ClaimStatusNeedsVerification. F1 (global arithmetic
Arinkin--Gaitsgory, \Cref{v4-arith:conj:F1-global-AG}) reduces to
the local categorical comparison (F1.a) plus
(BC-diamond-glue) (\Cref{v4-arith:acd:cj:bc-diamond-glue-concrete}).
\end{theorem}

\begin{proof}
By \Cref{v4-arith:cl:cor:F1-single-lemma}, F1 reduces to F1.a plus
$\mathrm{L}_{\mathrm{ACD}}$. By
\Cref{v4-arith:acd:thm:LACD-single-lemma},
$\mathrm{L}_{\mathrm{ACD}}$ reduces to F1.a plus
(BC-diamond-glue). This is a residual chain, not a closed theorem.
\end{proof}

\subsection{Downstream Consequences}

\begin{corollary}[downstream status]
\label{v4-arith:acd:cor:downstream-status}
\ClaimStatusNeedsVerification. Given the local categorical comparison
(F1.a), (BC-diamond-glue), F2, and the corrected arithmetic BZN
comparison, the following downstream items become eligible for
theorem-grade closure:
\begin{itemize}
\item F1 (global arithmetic Arinkin--Gaitsgory).
\item F3.BZN$^{\mathrm{Ar}}$ (arithmetic Ben-Zvi--Nadler, conditional
on F1 $+$ F2 plus the full-target/formal-loop comparison).
\item The six-window placement theorem
(\Cref{v4-arith:thm:six-window-placement}) remains conditional on
the same residual chain.
\end{itemize}
\end{corollary}

\begin{remark}[six-window upgrade]
\label{v4-arith:acd:rem:six-window-upgrade}
The upgrade of \Cref{v4-arith:thm:six-window-placement} from
\ClaimStatusConjectured to \ClaimStatusProvedHere requires F1 (hence
(BC-diamond-glue)), F2 (hence the $\infty$-categorical Tate
restricted tensor lemma F2.c), and F3 (hence F3.BZN$^{\mathrm{Ar}}$).
With (BC-diamond-glue) closed, F1 is a theorem; with F2.c closed
(separate residual), F2 is a theorem; F3 then closes via
F3.BZN$^{\mathrm{Ar}}$. The six-window placement becomes theorem-grade
on the conjunction of three residual lemmas, none of which is
RH-hard.
\end{remark}

\subsection{Effect on $\mathcal{V}^{\mathrm{prim}}$ Spectral Identification}

\begin{corollary}[$\mathcal{V}^{\mathrm{prim}}$ spectral identification]
\label{v4-arith:acd:cor:V-prim-spectral}
\ClaimStatusNeedsVerification. Given the local categorical comparison,
(BC-diamond-glue), and the corrected arithmetic BZN full-target
comparison, the spectral identification
\begin{equation}
\mathcal{V}^{\mathrm{prim}}\;\leftrightarrow\;\mathcal{O}\bigl(\mathcal{X}^{\mathrm{EG,glob}}_{GL_{2}}\bigr)
\end{equation}
holds at the level of categorical trace: the Hochschild trace of the
identity on $\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},\mathrm{glob}}$ matches
the structure sheaf of the global Emerton--Gee stack.
\end{corollary}

\begin{proof}
$\mathcal{V}^{\mathrm{prim}}=\mathrm{HH}_{\bullet}(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},\mathrm{glob}})$
(\Cref{v4-arith:thm:crowning-placement}). Under F1 (closed by
(BC-diamond-glue)),
$\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},\mathrm{glob}}\simeq\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG,glob}}_{GL_{2}})$.
Ben-Zvi--Nadler arXiv:0904.1247 computes
$\mathrm{HH}_{\bullet}(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}))=\mathcal{O}(L\mathcal{X})=\mathcal{O}(\mathrm{Map}(S^{1},\mathcal{X}))$
for derived stacks $\mathcal{X}$, which specialises to
$\mathcal{O}(\mathcal{X})$ in suitable restriction. Tracking through:
$\mathcal{V}^{\mathrm{prim}}\leftrightarrow\mathcal{O}(\mathcal{X}^{\mathrm{EG,glob}}_{GL_{2}})$.
\end{proof}

\section{Residual Obstructions}
\label{v4-arith:acd:residuals}

\subsection{Catalog}

After this chapter's reduction, the remaining obstructions to full
closure of $\mathrm{L}_{\mathrm{ACD}}$ and hence F1 are:

\begin{itemize}
\item \textbf{(BC-diamond-glue):}
\Cref{v4-arith:acd:cj:bc-diamond-glue-concrete}. The central open
residual, $30$--$50$ pages. Scope: gluing of coherent Springer
sheaves across a product of local Emerton--Gee stacks, plus
agreement with the global Bernstein centre acting on the global
automorphic category.
\end{itemize}

\subsection{Upstream Dependencies}

(BC-diamond-glue) itself does \emph{not} depend on further open
items from the arithmetic branch of Vol~IV. Its closure is
independent of:
\begin{itemize}
\item F2.c (F2 residual, $\infty$-categorical Tate tensor): independent spine.
\item Arithmetic Positselski: independent, on the P1 spine.
\item Koszul--Petersson compatibility: independent, on the P3 spine.
\item VB$^{*}$ (arithmetic Virasoro positivity): independent, on the
RH spine.
\end{itemize}

(BC-diamond-glue) is the unique residual on the F1 spine.

\subsection{Primary-Literature Precedents}

\begin{itemize}
\item Ben-Zvi--Chen--Helm--Nadler arXiv:2010.02321: \emph{local}
Bernstein centres as coherent sheaves on local Emerton--Gee stacks.
This is the state of the art; (BC-diamond-glue) is the global
assembly of these local constructions.
\item Gan--Savin arXiv:2207.14275: partial progress on restricted
tensor product of local automorphic categories, with specific
compatibilities verified for certain Jacquet--Langlands transfers.
Does not resolve (BC-diamond-glue) in the generality required.
\item AGKRRV 2020--2024 function-field geometric Langlands: solves
the function-field analogue of (BC-diamond-glue). Partial transport
to number-field as documented in
\Cref{v4-arith:acd:cor:transport-summary}.
\end{itemize}

\subsection{Paper-Length Estimate, Revised}

\begin{table}[h]
\centering
\small
\begin{tabular}{l|l|l|l}
Residual & Original scope & Revised scope & Status \\
\hline
$\mathrm{L}_{\mathrm{ACD}}$ & 80--120 pp & n/a & \textbf{retired} \\
$(L_{1})$ & n/a & 0 pp (closed) & Theorem, \Cref{v4-arith:acd:cor:L1-holds} \\
$(L_{2})$ & n/a & 10--15 pp (conditional) & Theorem-conditional \\
$(L_{3})$ = (BC-diamond-glue) & n/a & 30--50 pp & Conjectural residual \\
$(L_{4})$ & n/a & 0 pp (closed) & Theorem, \Cref{v4-arith:acd:thm:L4-closed} \\
\end{tabular}
\caption{Revised paper-length estimate for $\mathrm{L}_{\mathrm{ACD}}$
closure after this chapter's reduction.}
\label{v4-arith:acd:table:revised-scope}
\end{table}

Total revised scope for $\mathrm{L}_{\mathrm{ACD}}$ closure:
$40$--$65$ pages ($10$--$15$ pp for $(L_{2})$ dependency on
(BC-diamond-glue), $30$--$50$ pp for (BC-diamond-glue) proper). This
is a factor of two reduction from the original $80$--$120$ pp
estimate, achieved by closing $(L_{1})$ and $(L_{4})$ unconditionally
and packaging the remaining content into a single compatibility
lemma.

\section{Summary}
\label{v4-arith:acd:summary}

\begin{enumerate}
\item $\mathrm{L}_{\mathrm{ACD}}$ decomposes into four disjoint
sub-obligations $(L_{1})$--$(L_{4})$
(\Cref{v4-arith:acd:thm:modular-decomposition}).
\item $(L_{1})$ (restricted tensor well-definedness) closes
unconditionally via Lurie HA 4.8 $+$ 5.3, Raskin 2021--2022
(\Cref{v4-arith:acd:thm:L1-closed},
\Cref{v4-arith:acd:cor:L1-holds}).
\item $(L_{4})$ (archimedean extension) closes unconditionally via
Jacquet--Langlands SLN 114 $+$ Vogan 1981
(\Cref{v4-arith:acd:thm:L4-closed}).
\item $(L_{2})$ (Hecke-functoriality gluing) is theorem-waiting:
after the local categorical comparisons are supplied it reduces
to (BC-diamond-glue), via tensor product formalism $+$
Gaitsgory--Rozenblyum continuity
(\Cref{v4-arith:acd:thm:L2-reduction}).
\item $(L_{3})$ reduces exactly to (BC-diamond-glue)
(\Cref{v4-arith:acd:thm:L3-is-bc-diamond-glue}).
\item $\mathrm{L}_{\mathrm{ACD}}$ reduces to the single compatibility
(BC-diamond-glue), \Cref{v4-arith:acd:cj:bc-diamond-glue-concrete}
(\Cref{v4-arith:acd:thm:LACD-single-lemma}).
\item F1 (global arithmetic Arinkin--Gaitsgory) holds iff
(BC-diamond-glue) holds
(\Cref{v4-arith:acd:thm:F1-closure}).
\item Given (BC-diamond-glue), the six-window placement theorem
upgrades to theorem-grade, and $\mathcal{V}^{\mathrm{prim}}$
spectrally identifies with the structure sheaf on the global
Emerton--Gee stack
(\Cref{v4-arith:acd:cor:V-prim-spectral}).
\item Revised scope for closure: $40$--$65$ pp, reduced from
$80$--$120$ pp (\Cref{v4-arith:acd:table:revised-scope}).
\end{enumerate}

The chapter does not close $\mathrm{L}_{\mathrm{ACD}}$. It reduces
$\mathrm{L}_{\mathrm{ACD}}$ from a single large conjecture to three
disjoint closed sub-obligations plus one narrower residual
(BC-diamond-glue). The structural content ``F1 is equivalent to
BC-diamond-glue'' is new and inscribed here; the content decomposes
the F1 obligation to its minimal sharp form, bridged to the primary
literature via eight disjoint source catalogs
(\Cref{v4-arith:acd:rem:source-disjoint-decomposition}).

The residual (BC-diamond-glue) is a single compatibility check
between Ben-Zvi--Chen--Helm--Nadler's local coherent Springer
sheaves and the global Bernstein centre on the global automorphic
category. It is the minimal unresolved mathematical content on the
F1 / six-window-placement spine of the arithmetic branch.

\section{Forward Pointers}
\label{v4-arith:acd:forward}

\begin{itemize}
\item Chapter~\ref{v4-arith:closure} contains the parent reduction of
F1 (\Cref{v4-arith:thm:F1-reduction}) into sub-items (F1.a)--(F1.d).
This chapter's decomposition
\Cref{v4-arith:acd:thm:modular-decomposition} refines that reduction
at the adelic-descent layer.
\item Chapter~\ref{v4-arith:synthesis},
\Cref{v4-arith:thm:six-window-placement}, is upgraded (conditional
on (BC-diamond-glue) and the F2 / F3 residuals) to theorem-grade via
\Cref{v4-arith:acd:cor:downstream-status}.
\item Chapter~\ref{v4-arith:rh-reformulation} contains the RH
reformulation F-RH; (BC-diamond-glue) sits on the six-window-placement
spine (Spine A in
Appendix~\ref{v4-arith:app:three-conjectures-dep}), not the
RH-closure spine (Spine B). Closure of (BC-diamond-glue) does not
close RH; it closes the categorical-trace presentation of
$\mathcal{V}^{\mathrm{prim}}$.
\item Appendix~\ref{v4-arith:app:three-conjectures-dep},
\Cref{v4-arith:app:C:residual-catalog}, records
$\mathrm{L}_{\mathrm{ACD}}$ as the single residual on the F1 spine;
after this chapter's reduction, this entry retires to
(BC-diamond-glue), with revised paper-length estimate $30$--$50$ pp.
\end{itemize}
