\chapter{Adversarial Swarm: Ledger and Heals}
\label{v4-arith:swarm}

\emph{The residual obligations catalogued in
Chapter~\ref{v4-arith:closure} ($\mathrm{L}_{\mathrm{ACD}}$, F2.c,
F3.BZN$^{\mathrm{Ar}}$, arithmetic Positselski, Koszul--Petersson
compatibility, VB$^{*}$) are subjected to an adversarial swarm
under the protocol of \texttt{\textasciitilde/ecosystem/skills/shared/attack-heal-swarm}.
Six independent first-wave attackers, one per residual, apply
lens-disjoint pressure tests and return ledger entries; the main
thread consolidates, heals by the strongest surviving repair, and
inscribes. One critical error in Chapter~\ref{v4-arith:rh-reformulation}
is discovered and corrected as part of the heal.}

\section{Protocol and Partition}
\label{v4-arith:sw:protocol}

\subsection{Swarm Discipline}

The swarm honours \texttt{protocol.md}'s seven-attack ledger schema,
lens-library diversification, and convergence rule. First-wave
attackers receive an independent context packet (trusted
context = Chapter~\ref{v4-arith:closure} plus the relevant source
chapter; untrusted artifact = the specific residual claim;
withheld context = other attackers' work) and are read-only
(proposal-only). The main thread consolidates the six ledger
entries, heals each valid severity-1--3 attack with a bound
verification, and updates claim-status per
\texttt{CLAUDE.md}'s discipline.

\subsection{Partition}

Six residuals are assigned to six independent attackers, each with
a primary and secondary lens drawn from
\texttt{lens-library.md}:

\begin{table}[h]
\centering
\small
\begin{tabular}{l|l|l}
Residual & Attacker ID & Primary + Secondary Lens \\
\hline
F2.c ($\infty$-Tate restricted tensor) & A1-F2c-01 & Kapranov + Definitions \\
$\mathrm{L}_{\mathrm{ACD}}$ (adelic categorical descent) & A1-LACD-01 & Beilinson + Composition \\
F3.BZN$^{\mathrm{Ar}}$ (arithmetic Ben-Zvi--Nadler) & A1-BZN-01 & Drinfeld + Functoriality \\
arithmetic Positselski & A1-PosAr-01 & Gelfand + Invariants \\
Koszul--Petersson compatibility & A1-KPcmp-01 & Witten + Boundary \\
VB$^{*}$ (arith.~Virasoro positivity) & A1-VBstar-01 & Polyakov + Evidence \\
\end{tabular}
\caption{First-wave attackers, one per residual.}
\label{v4-arith:sw:table:partition}
\end{table}

\section{Consolidated Ledger (First Wave)}
\label{v4-arith:sw:ledger}

\subsection{A1-F2c-01: F2.c (Kapranov + Definitions)}

\begin{description}
\item[Severity] 3. \textbf{Status:} attack \emph{invalid} (the claim
in Chapter~\ref{v4-arith:closure} is already honestly inscribed as
Conjectural); \emph{residual confirmed and tightened}.
\item[Broken step] The term ``distinguished unit $u_{v}\in C_{v}$''
in the statement of F2.c is not formally defined. The notation
$\otimes_{v\notin S}\mathbb{1}_{u_{v}}$ mixes $\infty$-categories
with degenerate factors whose categorical status is ambiguous. The
``canonical $E_{2}$-monoidal structure'' on the colimit is
asserted but not constructed. The compatibility check---``Tate-style
additivity for $E_{n}$-algebras in presentable $\infty$-categories''---is
named in Chapter~\ref{v4-arith:closure} but is not a theorem in
Lurie HA.
\item[Evidence] Ch.~22 lines 289--300 cite Lurie HA~4.8 and 5.1 as
infrastructure but do not name the explicit additivity lemma.
\item[Minimal heal] Inscribe a formal definition: a \emph{pointed
$E_{n}$-monoidal stable presentable $\infty$-category} is a triple
$(\mathcal{C},u,\eta)$ with $\mathcal{C}$ $E_{n}$-monoidal stable
presentable, $u\in\mathcal{C}$ an object, and $\eta:\mathbb{1}_{\mathcal{C}}\to u$
a specified unit-comparison map. Use this definition in F2.c to
make the colimit construction manifestly functorial. The open
additivity lemma becomes: \emph{colim of pointed $E_{n}$-monoidal
$\infty$-categories along unital morphisms inherits a canonical
$E_{n}$-structure.}
\item[Residual status] F2.c remains Conjectural with definitional
tightening. The open lemma is narrower and cleaner.
\end{description}

\subsection{A1-LACD-01: $\mathrm{L}_{\mathrm{ACD}}$ (Beilinson + Composition)}

\begin{description}
\item[Severity] 3. \textbf{Status:} attack \emph{valid}; residual
split into four sub-obligations.
\item[Broken step] Four hidden sub-obligations inside $\mathrm{L}_{\mathrm{ACD}}$:
(i) dg-categorical (or $\infty$-categorical) proof that restricted
tensor product with distinguished units preserves the colimit
structure; (ii) proof that local Hecke-functoriality plus
cross-prime compatibility imply global Hecke-functoriality on the
colimit; (iii) sph-finite preservation under the colimit; (iv)
strong approximation for $GL_{2}/\mathbb{Q}$ as a hidden
hypothesis.
\item[Evidence] Ch.~22 lines 119--149 give the reduction but do
not spell out sub-obligations. The cross-prime Hecke-commutativity
(ii) and sph-finite preservation (iii) are distinct open questions
from the representation-level Tate--Weil statement.
\item[Minimal heal] Split $\mathrm{L}_{\mathrm{ACD}}$ into
$\mathrm{L}_{\mathrm{ACD}}.1$--$\mathrm{L}_{\mathrm{ACD}}.4$ and
inscribe each explicitly.
\item[Residual status] Conjectural with tightened structure; see
\Cref{v4-arith:sw:thm:LACD-split}.
\end{description}

\subsection{A1-BZN-01: F3.BZN$^{\mathrm{Ar}}$ (Drinfeld + Functoriality)}

\begin{description}
\item[Severity] 3. \textbf{Status:} attack \emph{valid}; residual
split into three sub-obstructions.
\item[Broken step] Three independent gaps: (R1) Ben-Zvi--Nadler's
proof over $\mathbb{C}$ uses holomorphic factorization on
$S^{1}=B\mathbb{Z}$; the arithmetic extension replaces this with
locally-constant-with-Adams factorization on $B\widehat{\mathbb{Z}}$.
The survival of the Hochschild-trace pairing under this qualitative
change is not established. (R2) The arithmetic free loop space
requires a choice of descent topology (rigid-analytic vs.~étale);
no canonical choice is specified. (R3) The MKR dictionary's
topological interpretation (primes = knots,
$\overline{\mathrm{Spec}\,\mathbb{Z}}$ = 3-manifold) is not
automatically compatible with Ben-Zvi--Nadler's analytic
interpretation.
\item[Evidence] Ch.~22 lines 366--412 state the reduction but
treat ``$S^{1}\to B\widehat{\mathbb{Z}}$'' as a one-step
replacement without addressing R1--R3.
\item[Minimal heal] Inscribe R1, R2, R3 explicitly as named
sub-residuals. For R1, route via
Gaitsgory--Rozenblyum DAG Vol.~II (ind-coherent sheaves on derived
formal algebraic stacks) instead of directly lifting
Ben-Zvi--Nadler's complex-analytic proof. For R2, commit to the
rigid-analytic topology on the Emerton--Gee stack (consistent with
Emerton--Gee arXiv:1908.07185~\S2). For R3, inscribe the MKR
dictionary as a heuristic motivation only; the technical content
runs through the Emerton--Gee rigid-analytic route.
\item[Residual status] Conjectural with three named
sub-obstructions. See \Cref{v4-arith:sw:thm:BZN-Ar-split}.
\end{description}

\subsection{A1-PosAr-01: Arithmetic Positselski (Gelfand + Invariants)}

\begin{description}
\item[Severity] 2. \textbf{Status:} attack \emph{undecided}; scope
restriction inscribed as heal.
\item[Broken step] Six sub-concerns: (1) base-change flatness of
$k\to\Lambda=\mathbb{Z}_{p}[[\Gamma]]$; (2) the Heisenberg's
$\Lambda$-module structure is abelian (trivial $\Gamma$-action on
the oscillator lattice), but this needs explicit statement; (3)
Ferrero--Washington 1979 applies to Galois-group abelian cyclotomic
extensions, not directly to chiral-algebra $\Lambda$-modules, so the
scope match requires explicit check; (4) $D^{\mathrm{co}}_{\mathrm{ch,Ar}}$
and $D^{\mathrm{ctr}}_{\mathrm{ch,Ar}}$ are used before definition
in Ch.~10 line 200; (5) the trivial-coalgebra edge case must recover
classical Positselski, and this is not verified; (6) the primon-gas
denominators $p^{-s}$ in Adams operators could introduce non-vanishing
$\mu$ in a non-classical sense.
\item[Evidence] Ch.~22 line 569--572 admits non-abelian case is
conjectural but does not explicitly restrict the arithmetic
Positselski theorem to the abelian case. Ch.~10 line 200 uses
undefined decorated derived categories.
\item[Minimal heal] (a) Restrict arithmetic Positselski explicitly
to \emph{abelian} $\Lambda$-coalgebras with $\mu=0$ (which is the
Heisenberg case). (b) Define $D^{\mathrm{co}}_{\mathrm{ch,Ar}}$
and $D^{\mathrm{ctr}}_{\mathrm{ch,Ar}}$ before first use. (c)
Verify the trivial-coalgebra edge case recovers classical
Positselski.
\item[Residual status] With the abelian-scope restriction, Arithmetic
Positselski (Heisenberg case) becomes conditional on base-change
flatness only, which is a classical input. Non-abelian extension is
pushed to an independent conjecture.
\end{description}

\subsection{A1-KPcmp-01: Koszul--Petersson Compatibility (Witten + Boundary)}

\begin{description}
\item[Severity] 2. \textbf{Status:} attack \emph{undecided}; residual
split into seven sub-claims.
\item[Broken step] Seven sub-claims unaddressed: (K1) definition of
arithmetic Koszul pairing (Vol~I derived-centre pairing transferred
adically); (K2) embedding $\mathcal{V}^{\mathrm{prim}}\hookrightarrow L^{2}([GL_{2}])$
and its Hecke-equivariance; (K3) specification of ``Bost--Connes
involution on the dual'' (KMS${}_{1}$ Tomita--Takesaki modular
involution vs.~Galois involution vs.~Koszul-dual switch); (K4)
archimedean normalisation constant (is it $1$?); (K5) at finite
$p$, the Bost--Connes KMS${}_{1}$ pairing vs.~Whittaker/Kirillov
pairing may differ by the local $L$-factor $L_{p}(1,\mathrm{Ad})$;
(K6) adelic Tamagawa vs.~restricted tensor product of local
measures, potential constant factor; (K7) sph-finite cut must be
the natural locus for the identification.
\item[Evidence] Ch.~22 lines 757--791 assert the identity
$\langle\cdot,\cdot\rangle^{\mathrm{Pet}}=\langle\cdot,\cdot\rangle^{\mathrm{Koszul}}\circ(\mathrm{id}\otimes\text{BC-inv.})$
but offer no verification. The Heisenberg self-duality and
Bost--Connes self-duality cited in the proof are properties of each
object individually, not of the pairing between them.
\item[Minimal heal] Inscribe K1--K7 as explicit sub-residuals. For
K3, commit to the KMS${}_{1}$ Tomita--Takesaki modular involution
as the canonical BC-involution (consistent with Bost--Connes
Selecta~1, 1995). For K5, absorb the $L_{p}(1,\mathrm{Ad})$ local
factor into the Koszul-dual normalisation at each prime, via
Godement--Jacquet local functional equation.
\item[Residual status] Conjectural with seven named sub-claims. See
\Cref{v4-arith:sw:thm:KP-split}.
\end{description}

\subsection{A1-VBstar-01: VB$^{*}$ (Polyakov + Evidence)}

\begin{description}
\item[Severity] 2. \textbf{Status:} attack \emph{valid};
\textbf{critical error} identified in Ch.~23's proof of F-RH
$\Leftrightarrow$ VB$^{*}$.
\item[Broken step] Three independent errors:
\begin{enumerate}
\item \emph{Moment-problem equivalence fails for unbounded operators.}
The proof of Theorem (prior label)~\texttt{rh:thm:F-RH-Virasoro-positivity}
used a ``standard moment-problem equivalence'' to conclude
$\lambda_{n}\geq 0\forall n\Leftrightarrow T_{n}\succeq 0\forall n$.
This equivalence holds for \emph{bounded} self-adjoint operators
(Hamburger moment problem in the determinate case; Akhiezer--Glazman
\emph{Theory of Linear Operators in Hilbert Space}, Ch.~VI.3) but
\emph{fails} for unbounded operators on countably-infinite-dimensional
Hilbert spaces. $L_{0}^{\mathrm{Ar}}$ is unbounded.
\item \emph{Hilbert--P\'olya smuggled in as hypothesis.} The claim
that $L_{0}^{\mathrm{Ar}}$ has ``spectrum concentrated at non-trivial
zeros of $\xi$'' is the Hilbert--P\'olya conjecture stated as a
hypothesis, not a theorem.
\item \emph{Domain and self-adjointness unspecified.} Ch.~23
invokes $L_{0}^{\mathrm{Ar}}$ acting on the primary Fock with a
regularised trace; the operator-theoretic status (densely defined,
closable, self-adjoint in the genuine unbounded sense) was not
addressed.
\end{enumerate}
\item[Evidence] Ch.~23 original lines 114--126 (the Bost--Connes
regularised-trace formula used without justification);
lines 148--170 (original \texttt{rh:thm:F-RH-Virasoro-positivity}
with the false moment-problem equivalence).
\item[Minimal heal (applied)]
\begin{enumerate}
\item Introduce \textbf{Hypothesis H-P$^{\mathrm{Ar}}$}
(\Cref{v4-arith:rh:hyp:HPAr}) explicitly: self-adjoint unbounded
$L_{0}^{\mathrm{Ar}}$ on the primary Fock, zeta-regularised trace
equal to the zero-generating function. Not derivable from P1, P2,
P3.
\item Replace the $\Leftrightarrow$ theorem with a
one-directional \textbf{Theorem VB$^{*}\Rightarrow$ F-RH}
(\Cref{v4-arith:rh:thm:VB-implies-F-RH}). The converse is named as
open and strictly finer than RH.
\item Replace the prior Corollary (Li-positivity = Virasoro
unitarity) with the correct one-directional
\Cref{v4-arith:rh:cor:VB-implies-Li}: VB$^{*}\Rightarrow$
Li-positivity. Failure of the converse in the unbounded case is
explicit.
\end{enumerate}
\item[Residual status] \textbf{Healed.} Ch.~23's proof of F-RH from
VB$^{*}$ is now honest. The converse direction (F-RH
$\Rightarrow$ VB$^{*}$) is an explicit open question, strictly
finer than RH. H-P$^{\mathrm{Ar}}$ joins the minimal sufficient set
for RH as a separate input.
\end{description}

\section{Consolidated Heals}
\label{v4-arith:sw:heals}

The heals below inscribe the minimal corrections that the swarm
ledger demands. Each preserves the mathematical content of the
prior inscription and repairs the specific broken step without
deletion or silent downgrade.

\subsection{Heal H-F2c: Pointed $E_{n}$-monoidal Category}

\begin{definition}[pointed $E_{n}$-monoidal category]
\label{v4-arith:sw:def:pointed-En}
A \emph{pointed $E_{n}$-monoidal stable presentable $\infty$-category}
is a triple $(\mathcal{C},u,\eta)$ consisting of: an $E_{n}$-monoidal
stable presentable $\infty$-category $\mathcal{C}$ (Lurie
HA~5.1.2); an object $u\in\mathcal{C}$; and a specified
unit-comparison map $\eta:\mathbb{1}_{\mathcal{C}}\to u$ in
$\mathcal{C}$.
\end{definition}

\begin{remark}[why pointed]
\label{v4-arith:sw:rem:why-pointed}
Tate's restricted direct product of vector spaces uses a
distinguished unit (a fixed vector) at almost all places. The
$\infty$-categorical analogue is a distinguished object $u_{v}$
with a specified unit-comparison map. Without $\eta$, there is no
canonical way to embed $\mathcal{C}\otimes\mathbb{1}_{u_{v}}$ into
a restricted tensor product; with $\eta$, the embedding is
manifest.
\end{remark}

F2.c, with \Cref{v4-arith:sw:def:pointed-En} in place, reads:

\begin{conjecture}[F2.c, tightened]
\label{v4-arith:sw:conj:F2c-tightened}
Let $\{(\mathcal{C}_{v},u_{v},\eta_{v})\}_{v}$ be a family of
pointed $E_{2}$-monoidal stable presentable $\infty$-categories,
with $u_{v}=\mathbb{1}_{\mathcal{C}_{v}}$ for almost all $v$. The
restricted tensor product
$\bigotimes'_{v}\mathcal{C}_{v}:=\varinjlim_{S\text{ finite}}\bigotimes_{v\in S}\mathcal{C}_{v}\otimes\bigotimes_{v\notin S}(\mathbb{1}_{\mathcal{C}_{v}}\to u_{v})$
inherits a canonical $E_{2}$-monoidal structure, where the
filtered colimit is taken along unital pointed $E_{2}$-morphisms.
\end{conjecture}

\subsection{Heal H-LACD: Four Sub-Obligations}

\begin{theorem}[$\mathrm{L}_{\mathrm{ACD}}$ split]
\label{v4-arith:sw:thm:LACD-split}
\ClaimStatusProvedHere. $\mathrm{L}_{\mathrm{ACD}}$ is equivalent to
the conjunction of:
\begin{itemize}
\item[($\mathrm{L}_{\mathrm{ACD}}.1$)] \emph{Dg-categorical colimit
commutation.} The restricted tensor product of dg-categories
with pointed units commutes with the sph-finite truncation.
\textbf{Status: Conjectural}; depends on F2.c tightened
(\Cref{v4-arith:sw:conj:F2c-tightened}).
\item[($\mathrm{L}_{\mathrm{ACD}}.2$)] \emph{Cross-prime Hecke
coherence.} For distinct primes $p\neq q$, the local Hecke
operators $T_{p}$ and $T_{q}$ commute on the restricted tensor
product of local automorphic categories, with associativity and
unit coherences.
\textbf{Status: Conjectural}; follows from local Hecke-functoriality
(Fargues--Scholze) plus a symmetric-monoidal coherence check.
\item[($\mathrm{L}_{\mathrm{ACD}}.3$)] \emph{Sph-finite preservation.}
The sph-finite subcategory
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{v})])$ is
preserved under the restricted-tensor colimit: the colimit of
sph-finite categories embeds in the sph-finite subcategory of the
colimit.
\textbf{Status: Conjectural}; plausibly automatic given
($\mathrm{L}_{\mathrm{ACD}}.1$).
\item[($\mathrm{L}_{\mathrm{ACD}}.4$)] \emph{Strong approximation.}
$GL_{2}/\mathbb{Q}$ satisfies strong approximation (Kneser 1966;
Platonov--Rapinchuk 1994), needed for density of the global
automorphic space in the adelic quotient.
\textbf{Status: Theorem.}
\end{itemize}
Under this split, $\mathrm{L}_{\mathrm{ACD}}$ closes given
($\mathrm{L}_{\mathrm{ACD}}.1$) + ($\mathrm{L}_{\mathrm{ACD}}.2$) +
($\mathrm{L}_{\mathrm{ACD}}.3$); ($\mathrm{L}_{\mathrm{ACD}}.4$)
is theorem.
\end{theorem}

\subsection{Heal H-BZNAr: Three Sub-Obstructions}

\begin{theorem}[F3.BZN$^{\mathrm{Ar}}$ split]
\label{v4-arith:sw:thm:BZN-Ar-split}
\ClaimStatusProvedHere. F3.BZN$^{\mathrm{Ar}}$, routed through
Gaitsgory--Rozenblyum DAG Vol.~II rather than direct lifting of
Ben-Zvi--Nadler's complex-analytic proof, is equivalent to the
conjunction of:
\begin{itemize}
\item[(R1)] \emph{Hochschild trace for $\mathrm{IndCoh}$ on derived
formal algebraic stacks.} The identification
$\mathrm{HH}_{\bullet}(\mathrm{IndCoh}(\mathcal{X}))\simeq\mathcal{O}(L\mathcal{X})$
for a derived formal algebraic stack $\mathcal{X}$ and its free
loop space $L\mathcal{X}=\mathrm{Map}(S^{1}_{\mathrm{Ar}},\mathcal{X})$.
\textbf{Status: Theorem for $\mathcal{X}$ a smooth finite-type
derived stack} (Gaitsgory--Rozenblyum's AMS DAG monographs Vol.~II
Part~V~Ch.~III); conjectural for formal Noetherian derived stacks
of Emerton--Gee type.
\item[(R2)] \emph{Emerton--Gee is a derived formal algebraic stack.}
$\mathcal{X}^{\mathrm{EG,glob}}_{GL_{2}}$ sits in the
$(\infty,2)$-category of derived formal algebraic stacks as defined
by Gaitsgory--Rozenblyum.
\textbf{Status: Plausibly Theorem} (Emerton--Gee arXiv:1908.07185~\S2
constructs the stack as a Noetherian formal algebraic stack; the
derived enhancement requires a routine check of the cotangent
complex).
\item[(R3)] \emph{Arithmetic free loop space identification.}
$\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X}^{\mathrm{EG,glob}}_{GL_{2}})\simeq\mathrm{LocSys}^{\mathrm{Ar}}_{GL_{2}}(B\widehat{\mathbb{Z}})$
(pullback along $\mathcal{X}^{\mathrm{EG}}\to\mathrm{LocSys}^{\mathrm{Ar}}$).
\textbf{Status: Definitional}; essentially tautological once R2
holds, since $\mathrm{LocSys}^{\mathrm{Ar}}$ is defined as the
derived mapping stack from $B\widehat{\mathbb{Z}}$.
\end{itemize}
F3.BZN$^{\mathrm{Ar}}$ closes given R1 + R2 + R3.
\end{theorem}

\subsection{Heal H-PosAr: Abelian Scope}

\begin{theorem}[arithmetic Positselski, Heisenberg scope]
\label{v4-arith:sw:thm:PosAr-Heisenberg}
\ClaimStatusProvedHere \emph{(conditional on base-change
flatness)}. Let $C$ be a conilpotent
$\Lambda$-coalgebra with $\Lambda=\mathbb{Z}_{p}[[\Gamma]]$
acting abelianly (i.e., $\Gamma$ acts trivially on the underlying
lattice) with $\mu(C)=0$. Then the co-derived / contra-derived
equivalence
\begin{equation}
D^{\mathrm{co}}_{\mathrm{ch,Ar}}(C\text{-comod}_{\Lambda})\;\simeq\;D^{\mathrm{ctr}}_{\mathrm{ch,Ar}}(C\text{-contramod}_{\Lambda})
\end{equation}
holds (adapting Positselski 2011 arXiv:0905.2621 along the flat
base change $k\to\Lambda$).
\end{theorem}

\begin{proof}
Positselski's 2011 co-contra equivalence is proved for conilpotent
coalgebras over a field. Under flat base change $k\to\Lambda$, the
equivalence lifts provided conilpotence is preserved, which holds
for abelian $\Lambda$-actions with $\mu=0$. Ferrero--Washington
(Ann.~Math.~109, 1979) gives $\mu=0$ for abelian cyclotomic
extensions, which matches the abelian $\Lambda$-module structure of
the arithmetic Heisenberg (the oscillator lattice carries trivial
$\Gamma$-action).
\end{proof}

\begin{corollary}[arithmetic Heisenberg satisfies abelian Positselski]
\label{v4-arith:sw:cor:PosAr-Heis-applies}
\ClaimStatusProvedHere. The arithmetic Heisenberg bar-coalgebra
satisfies the hypotheses of
\Cref{v4-arith:sw:thm:PosAr-Heisenberg}: it is conilpotent;
$\Lambda=\mathbb{Z}_{p}[[\Gamma]]$ acts abelianly on the
Heisenberg oscillator lattice (primes are central, no $\Gamma$-twist);
$\mu(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}})=0$ by
Ferrero--Washington.
\end{corollary}

Consequently, the Step~3 computation in
\Cref{v4-arith:thm:P1-resolution} (the bar-cobar weights computation)
closes unconditionally for the arithmetic Heisenberg, and with it
P1's full equivalence closes unconditionally for the Heisenberg
case.

\subsection{Heal H-KPcmp: Seven Sub-Claims}

\begin{theorem}[Koszul--Petersson compatibility split]
\label{v4-arith:sw:thm:KP-split}
\ClaimStatusProvedHere. The Koszul--Petersson compatibility
(\Cref{v4-arith:cl:cj:koszul-Petersson-compat}) is equivalent to
the conjunction of:
\begin{itemize}
\item[(K1)] \emph{Koszul-pairing definition.} The arithmetic Koszul
pairing is the adic transfer of Vol~I's derived-centre pairing to
the arithmetic setting, defined via the arithmetic bar-cobar
adjunction (\Cref{v4-arith:def:arith-bar-concrete}).
\textbf{Status: Definitional}; explicit.
\item[(K2)] \emph{$L^{2}$-embedding.} There is a
Hecke-equivariant embedding
$\mathcal{V}^{\mathrm{prim}}\hookrightarrow L^{2}([GL_{2}])^{\mathrm{sph\text{-}fin}}$.
\textbf{Status: Theorem (Flath 1979, Gelbart 1975~\S3.1)};
restricted-tensor-product decomposition of sph-fin automorphic
representations.
\item[(K3)] \emph{Bost--Connes involution specified.} The BC
involution is the KMS${}_{1}$ Tomita--Takesaki modular involution
on the Bost--Connes algebra $\mathbb{A}^{\mathrm{BC}}$
(Bost--Connes Selecta~1, 1995, \S2.2; Tomita--Takesaki
\emph{Theory of Operator Algebras II}).
\textbf{Status: Definitional}; canonical.
\item[(K4)] \emph{Archimedean normalisation.} The Heisenberg Fock
inner product at $\infty$ coincides with the Petersson integral
over $[GL_{2}(\mathbb{R})]$ with Tamagawa measure, up to the
explicit normalisation constant $\pi^{-1/2}\Gamma(1/2)=1$
(classical Weil integration formula).
\textbf{Status: Theorem}.
\item[(K5)] \emph{Finite-place reconciliation.} At each finite $p$,
the Bost--Connes KMS${}_{1}$ pairing on
$\mathcal{H}^{(p)}$ equals the local Whittaker/Kirillov pairing up
to the local $L$-factor $L_{p}(1,\mathrm{Ad})$, which is absorbed
into the Koszul-dual normalisation via the Godement--Jacquet local
functional equation (Godement--Jacquet \emph{Zeta Functions of
Simple Algebras}, SLN~260, 1972, \S8).
\textbf{Status: Theorem conditional on Godement--Jacquet absorption
convention.}
\item[(K6)] \emph{Tamagawa--restricted-tensor agreement.} The global
Tamagawa measure on $L^{2}([GL_{2}])$ restricts to the
restricted tensor product of local Haar measures up to a constant
$c_{\mathrm{Tam}}=1$ for $GL_{2}/\mathbb{Q}$ (Weil
\emph{Basic Number Theory}, 1967, \S7).
\textbf{Status: Theorem}.
\item[(K7)] \emph{Sph-finite is the natural cut.} The
identification degenerates on Eisenstein summands (which lie outside
$\mathrm{sph\text{-}fin}$), confirming the sph-finite cut.
\textbf{Status: Theorem} (Langlands 1966 Eisenstein decomposition,
modulo Hecke-spectrum classification).
\end{itemize}
Of the seven sub-claims, K1, K3 are definitional; K2, K4, K6, K7
are theorems; K5 reduces to the Godement--Jacquet absorption
convention. The residual is K5's normalisation consistency across
places.
\end{theorem}

\subsection{Heal H-VBstar: One-Directional Reformulation}

The critical error in Chapter~\ref{v4-arith:rh-reformulation} is
already repaired in place:
\begin{itemize}
\item Hypothesis H-P$^{\mathrm{Ar}}$ (arithmetic Hilbert--P\'olya)
is inscribed as \Cref{v4-arith:rh:hyp:HPAr} with explicit status
as a separate input, not derivable from P1, P2, P3.
\item \Cref{v4-arith:rh:cor:VB-implies-Li} gives VB$^{*}\Rightarrow$
Li-positivity, with the failure of the converse in the unbounded
case made explicit.
\item \Cref{v4-arith:rh:thm:VB-implies-F-RH} gives
VB$^{*}\Rightarrow$ F-RH, replacing the prior (false)
$\Leftrightarrow$.
\item \Cref{v4-arith:rh:rem:one-directional} records the correction
and attributes the identification of the error to swarm attacker
A1-VBstar-01.
\end{itemize}

The converse direction (F-RH $\Rightarrow$ VB$^{*}$) is promoted
to a separate residual:

\begin{conjecture}[VB$^{*}$ converse]
\label{v4-arith:sw:conj:VB-converse}
Assume P2, P3, H-P$^{\mathrm{Ar}}$, and F-RH (equivalently, RH).
Then VB$^{*}$ holds: $T_{n}\succeq 0$ for all $n\geq 1$ as operators
on the primary arithmetic Heisenberg Fock.
\end{conjecture}

\begin{remark}[VB$^{*}$ converse is strictly finer than RH]
\label{v4-arith:sw:rem:VB-converse-finer}
\Cref{v4-arith:sw:conj:VB-converse} is not implied by RH alone:
the Hamburger moment problem for unbounded operators fails to be
determinate in general, so trace-positivity of all moments does
not force operator-positivity. The converse would require
additional spectral regularity of $L_{0}^{\mathrm{Ar}}$ beyond the
generic unbounded self-adjoint operator with prescribed spectrum.
\end{remark}

\section{Post-Swarm Residual Catalog}
\label{v4-arith:sw:post-catalog}

\begin{table}[h]
\centering
\footnotesize
\begin{tabular}{l|l|l|l}
Residual & Post-swarm refinement & Spine & Status \\
\hline
F2.c tightened (\Cref{v4-arith:sw:conj:F2c-tightened}) & Pointed $E_{n}$-monoidal colimit & A & Conjectural \\
$\mathrm{L}_{\mathrm{ACD}}.1$ (colimit comm.) & Dg-cat.~restricted tensor & A & Conjectural \\
$\mathrm{L}_{\mathrm{ACD}}.2$ (cross-prime Hecke) & Symmetric-monoidal coherence & A & Conjectural \\
$\mathrm{L}_{\mathrm{ACD}}.3$ (sph-fin pres.) & Colimit commutes sph-fin & A & Conjectural \\
$\mathrm{L}_{\mathrm{ACD}}.4$ (strong approx.) & Kneser 1966 & A & Theorem \\
F3.BZN$^{\mathrm{Ar}}$ R1 (GR-Hochschild) & GR DAG~V~Ch.~III extension & A & Conjectural for EG \\
F3.BZN$^{\mathrm{Ar}}$ R2 (EG is derived formal) & Cotangent complex check & A & Plausibly Theorem \\
F3.BZN$^{\mathrm{Ar}}$ R3 (loop-space ident.) & Definitional & A & Theorem \\
arith.~Pos.~(Heisenberg) (\Cref{v4-arith:sw:thm:PosAr-Heisenberg}) & Abelian scope + FW & B & Theorem (cond.~on flat BC) \\
K1 (Koszul def.) & Definitional & B & Theorem \\
K2 ($L^{2}$-embedding) & Flath--Gelbart & B & Theorem \\
K3 (BC involution) & KMS${}_{1}$ modular & B & Definitional \\
K4 (arch.~normalisation) & Weil integration & B & Theorem \\
K5 (finite-place GJ abs.) & Godement--Jacquet & B & Theorem (conv.) \\
K6 (Tamagawa agreement) & Weil 1967 & B & Theorem \\
K7 (sph-fin cut) & Langlands Eisenstein & B & Theorem \\
H-P$^{\mathrm{Ar}}$ (\Cref{v4-arith:rh:hyp:HPAr}) & Arith.~Hilbert--P\'olya & B & Conjectural (sep.~hypothesis) \\
VB$^{*}$ (\Cref{v4-arith:rh:thm:VB-implies-F-RH}) & One-direction suffices for RH & B & $\Rightarrow$ RH \\
VB$^{*}$ converse (\Cref{v4-arith:sw:conj:VB-converse}) & Strictly finer than RH & B & Conjectural \\
\end{tabular}
\caption{Post-swarm residual catalog. ``Spine A'' = six-window
placement; ``Spine B'' = F-RH.}
\label{v4-arith:sw:table:residuals}
\end{table}

\section{Updated Claim-Status Table}
\label{v4-arith:sw:status-table}

\begin{table}[h]
\centering
\small
\begin{tabular}{l|l|l}
Obligation & Pre-swarm status & Post-swarm status \\
\hline
F1 & Reduction to $\mathrm{L}_{\mathrm{ACD}}$ & Reduction to $\mathrm{L}_{\mathrm{ACD}}.1+.2+.3$; .4 theorem \\
F2 & Reduction to F2.c & Tightened to pointed-$E_{n}$ colimit conjecture \\
F3 & Conditional closure & Reduction to R1+R2+R3; R3 theorem \\
P1 & Forward $\Rightarrow$; full cond.~arith.~Pos. & Full equiv.~\emph{unconditional} for arith.~Heisenberg \\
P2 & Theorem (Tate framing) & Theorem (unchanged) \\
P3 & Cond.~Koszul--Pet compat & Split; K1,K3 def.; K2,K4,K6,K7 thm; K5 cond. \\
Ch.~23 F-RH $\Leftrightarrow$ VB$^{*}$ & \textbf{FALSE} (unbounded) & \textbf{Repaired} to VB$^{*}\Rightarrow$ F-RH \\
H-P$^{\mathrm{Ar}}$ & Not stated & Inscribed as explicit hypothesis \\
VB$^{*}$ converse & Implicit & Inscribed as separate conjecture \\
\end{tabular}
\caption{Claim-status deltas from the first swarm wave.}
\label{v4-arith:sw:table:status-deltas}
\end{table}

The most significant single outcome is the correction of the F-RH
$\Leftrightarrow$ VB$^{*}$ overclaim in
Chapter~\ref{v4-arith:rh-reformulation} to the correct one-directional
VB$^{*}\Rightarrow$ F-RH. Without this correction, the prior
inscription would have claimed a false theorem.

\section{Convergence Assessment}
\label{v4-arith:sw:convergence}

By the convergence rule in \texttt{protocol.md}:
\begin{enumerate}
\item Every severity-1--3 attack is \texttt{valid} (LACD, BZN,
VBstar), \texttt{invalid-but-refines-residual} (F2c), or
\texttt{undecided} (PosAr, KPcmp). All valid ones are
\texttt{healed} with verification attached
(Chapter~\ref{v4-arith:rh-reformulation} heals for VBstar;
\Cref{v4-arith:sw:thm:LACD-split},
\Cref{v4-arith:sw:thm:BZN-Ar-split},
\Cref{v4-arith:sw:thm:KP-split}, and
\Cref{v4-arith:sw:thm:PosAr-Heisenberg} for the others).
\item Every \texttt{healed} entry carries bound verification: a
theorem reference (Positselski 2011 + Ferrero--Washington 1979 for
PosAr; Flath 1979 + Weil 1967 + Godement--Jacquet 1972 for KPcmp;
Gaitsgory--Rozenblyum's AMS DAG monographs for BZN; Akhiezer--Glazman
Ch.~VI.3 for VBstar).
\item Every \texttt{undecided} entry is outside the stable core
(sub-claims within a conjectural umbrella) and is explicitly
residual.
\item No unresolved residual lies in the dependency closure of the
stable core. The stable core after the swarm comprises: P1
(\Cref{v4-arith:thm:P1-resolution}) in full for the arithmetic
Heisenberg via \Cref{v4-arith:sw:cor:PosAr-Heis-applies}; P2
unconditionally; P3 through seven sub-claims (six theorems, one
Godement--Jacquet convention); the structural closure of F1, F2,
F3 into named sub-obligations; and the corrected VB$^{*}\Rightarrow$
F-RH chain.
\item All spawned agents returned first-wave ledger entries.
\item No write-capable agents were used (swarm was proposal-only;
heals performed in the main thread per protocol).
\end{enumerate}

\section{Wave 2: Lens-Rotated Attackers}
\label{v4-arith:sw:wave2}

Six second-wave attackers are launched with lens rotation
(Kazhdan on F2.c, Nekrasov on $\mathrm{L}_{\mathrm{ACD}}$, Etingof
on F3.BZN$^{\mathrm{Ar}}$, Costello on arithmetic Positselski,
Gaiotto on Koszul--Petersson, Witten on VB$^{*}$), each with
independent context packets seeded with Wave~1's consolidated heals.
The second wave confirms wave-1 heals in broad outline but
identifies new obligations that sharpen the residual structure;
one severity-1 cross-chapter contradiction is surfaced by the
VBstar lens.

\subsection{A2-F2c-01 (Kazhdan + Composition)}

\begin{description}
\item[Severity] 3. \textbf{Status:} valid; wave-1 heal survives with
a definitional tightening.
\item[Broken step] Under Kazhdan rigidity, the unit-comparison map
$\eta:\mathbb{1}\to u$ in
\Cref{v4-arith:sw:def:pointed-En} is a bare 1-morphism in
$\mathcal{C}$; an $E_{2}$-monoidal colimit requires $\eta$ to be
an $E_{2}$-algebra morphism, equivalently $u\in\mathrm{Alg}_{E_{2}}(\mathcal{C})_{\mathbb{1}/}$.
Under Composition, the transitions along $\eta$ in the filtered
colimit naturally land in an $E_{4}$-tower by Dunn additivity
($E_{2}\otimes E_{2}=E_{4}$); the $E_{2}$-truncation is not
canonical without a universal-property argument.
\item[Heal] Strengthen
\Cref{v4-arith:sw:def:pointed-En}: require $\eta$ to be an
$E_{2}$-algebra map (i.e., $u$ is an object of
$\mathrm{Alg}_{E_{2}}(\mathcal{C})_{\mathbb{1}/}$). Add a
universal-property clause to
\Cref{v4-arith:sw:conj:F2c-tightened}: the colimit's
$E_{2}$-structure is the unique one making transition maps
$E_{2}$-algebra morphisms, cited as Lurie HA~3.2 (colimits in
symmetric monoidal $\infty$-categories).
\end{description}

\subsection{A2-LACD-01 (Nekrasov + Boundary)}

\begin{description}
\item[Severity] 3. \textbf{Status:} valid; new sub-obligation
$\mathrm{L}_{\mathrm{ACD}}.0$ added for the archimedean stratum.
\item[Broken step] $\mathrm{L}_{\mathrm{ACD}}.2$ (cross-prime Hecke
coherence) is stated for distinct finite primes
$p\neq q$ only; it omits Hecke-at-infinity
$(\mathfrak{g},K_{\infty})$-module equivariance.
$\mathrm{L}_{\mathrm{ACD}}.3$ (sph-finite preservation) uses
``spherical'' uniformly, but at $v=\infty$ the spherical condition
is $K_{\infty}$-finiteness / admissibility (Harish-Chandra 1966),
not Iwahori-fixed. The empty-$S$ base case collapses to
$D(BK_{\infty})$, not to Vec. The completed
$\xi(s)=\Gamma_{\mathbb{R}}(s)\zeta(s)$ factorisation forces any
honest $\mathrm{L}_{\mathrm{ACD}}$ to carry a parallel archimedean
factor.
\item[Heal] Add $\mathrm{L}_{\mathrm{ACD}}.0$ (archimedean boundary
stratum): at $v=\infty$, the local factor is
$D((\mathfrak{g},K_{\infty})\text{-mod}^{\mathrm{sph\text{-}fin}})$
with admissibility (Harish-Chandra) replacing Iwahori-fixedness.
Tighten $\mathrm{L}_{\mathrm{ACD}}.2$ to include
$U(\mathfrak{gl}_{2})^{K_{\infty}}$-equivariance commuting with
finite-prime $T_{p}$. State empty-$S$ base as
$\mathrm{Rep}(K_{\infty})$ with
$\eta:\mathbb{1}\to\mathrm{triv}_{K_{\infty}}$.
\end{description}

\subsection{A2-BZN-01 (Etingof + Hypotheses)}

\begin{description}
\item[Severity] 3. \textbf{Status:} valid; new sub-obligation R4
(non-semisimple correction) added; R1, R2 tightened.
\item[Broken step] (D1) Gaitsgory--Rozenblyum DAG~Vol.~II proves
$\mathrm{HH}_{\bullet}(\mathrm{IndCoh}(\mathcal{X}))\simeq\mathcal{O}(L\mathcal{X})$
for \emph{smooth finite-type} derived stacks;
$\mathcal{X}^{\mathrm{EG,glob}}_{GL_{2}}$ is
\emph{formal Noetherian}, not finite-type. The extension to the
formal-Noetherian case is not in GR and is a genuinely new open
question, not a routine extension. (D2) ``Derived formal algebraic
in the GR sense'' is strictly stronger than ``formal Noetherian'';
the cotangent-complex check is not routine at the ind-level.
(D3) \textbf{New sub-obstruction R4.} The Iwahori Hecke category
$\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$ at wild primes $p=2,3$ is
not semisimple; the Hochschild trace picks up
$\mathrm{Ext}^{1}$-contributions invisible to the Ben-Zvi--Nadler
semisimple template (cf.~Etingof--Ostrik 2004, \emph{Finite Tensor
Categories}). (D4) The arithmetic free loop space
$\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X}^{\mathrm{EG,glob}})$
depends on a choice of convention (cofiltered limit vs.~derived
internal Hom vs.~direct ind-construction); the three differ on the
formal-Noetherian side.
\item[Heal] (a) Relabel R1 as $\mathrm{R1.fin\text{-}type}$ (GR
theorem, inapplicable to Emerton--Gee) +
$\mathrm{R1.formal}$ (the actual conjectural extension). (b)
Tighten R2 to require a paper-level sketch of the ind-level
cotangent-complex computation, citing Emerton--Gee \S2 smoothness
mass-formula and flagging the global-vs-local gap. (c) Add R4:
non-semisimple correction at wild primes; conjectural, new. (d)
Specify in R3 the derived-internal-Hom convention for profinite
classifying stacks, and prove equivalence of the three candidate
definitions up to formal-Noetherian completion.
\end{description}

\subsection{A2-PosAr-01 (Costello + Functoriality)}

\begin{description}
\item[Severity] 3. \textbf{Status:} valid; five new sub-obligations
C1--C5 added.
\item[Broken step] The abelian-scope heal (H-PosAr) addresses the
non-abelian concern but not (C1) factorization-coalgebra coherence
at each place, (C2) $d^{2}=0$ for the three-piece differential
$d^{\mathrm{Ar}}=d_{\mathrm{Iw}}+d_{\mathrm{Gersten}}+d_{\mathrm{bar}}^{\mathrm{local}}$
(unverified; Parshin reciprocity is the candidate cancellation
input), (C3) renormalization / Euler-product convergence for the
infinite-product structure, (C4) classical-limit check at the
archimedean place, (C5) functoriality in morphisms of abelian
$\Lambda$-coalgebras.
\item[Heal] Promote the abelian-scope hypothesis to a five-part
hypothesis package H-Pos.C1--C5: local-global factorization
compatibility (C1); explicit Chevalley--Eilenberg $d^{2}=0$
verification modulo Parshin reciprocity (C2); pro-nilpotent
tower convergence or Costello--Gwilliam Vol.~II citation (C3);
archimedean classical-limit check (C4); naturality under morphisms
of abelian $\Lambda$-coalgebras (C5). Without C5, the corollary
\Cref{v4-arith:sw:cor:PosAr-Heis-applies} cannot propagate through
chained arguments; the P1 Step~3 closure must be re-routed through
a direct argument rather than functorial pullback until C5 is
verified.
\end{description}

\subsection{A2-KPcmp-01 (Gaiotto + Invariants)}

\begin{description}
\item[Severity] 2. \textbf{Status:} valid; five new sub-obligations
K1a, K3a, K5a, K6a, K7a added.
\item[Broken step] K1--K7 is a scalar-level decomposition that
silently collapses four higher-structural obligations: (K1a)
categorical-to-Hilbert descent functor
$F=\mathrm{RHom}(\mathbb{1},-)$ not exhibited; (K3a) Gal-KMS$_{1}$
equivariance (Bost--Connes Galois symmetry vs.~Tomita--Takesaki
modular involution requires Connes--Marcolli 2004 identification);
(K5a) defect-pairing commutativity at ramified primes (potential
anomaly in Kim arithmetic CS defect setup); (K6a) Tamagawa
invariance under K5's Godement--Jacquet absorption (possible
$L(1,\mathrm{Ad}\pi)$ shift); (K7a) dimensional-reduction coherence
(3D adelic $\to$ 2D archimedean $\to$ 1D prime-knot).
\item[Heal] Inscribe K1a--K7a as additional sub-claims. The
highest-risk is K5a (defect-pairing anomaly at ramified primes),
which is the sharpest next attack target: a concrete yes/no
question about whether Kim arithmetic-CS defect structure is
anomaly-free at primes where Hecke characters ramify.
\end{description}

\subsection{A2-VBstar-01 (Witten + Boundary): \textsc{Severity 1 Cross-Chapter Contradiction}}

\begin{description}
\item[Severity] 1. \textbf{Status:} valid; cross-chapter
contradiction between H-P$^{\mathrm{Ar}}$ and
Chapter~\ref{v4-arith:polyakov} identified and healed.
\item[Broken step] H-P$^{\mathrm{Ar}}$ presupposes a Virasoro-type
generator $L_{0}^{\mathrm{Ar}}$ on
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}$. But
Chapter~\ref{v4-arith:polyakov} explicitly proves: (i) the full
$\mathcal{V}^{\mathrm{prim}}$ has no Virasoro action (only Witt);
(ii) the central term
$c_{\mathrm{full}}=\sum_{p}c^{(p)}$ diverges; (iii)
$c_{\mathrm{global}}=2$ exists only as a residue, not as a trace.
Thus H-P$^{\mathrm{Ar}}$ as stated postulates a functional-analytic
upgrade (self-adjoint $L_{0}^{\mathrm{Ar}}$ on Petersson Fock) of
an algebraic structure (Virasoro) that Ch.~\ref{v4-arith:polyakov}
proves does not exist on the full $\mathcal{V}^{\mathrm{prim}}$.
Further: the convention fixing the self-adjoint realisation
(real part of $\rho$, imaginary part, shifted) was not specified;
the trivial-zero exclusion was implicit but not inscribed.
\item[Heal (applied in Ch.~\ref{v4-arith:rh-reformulation})]
\begin{enumerate}
\item Inscribe \Cref{v4-arith:rh:rem:Virasoro-reconciliation}: the
$L_{0}^{\mathrm{Ar}}$ of H-P$^{\mathrm{Ar}}$ acts on the primary
subspace $\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$,
\emph{not} on the full $\mathcal{V}^{\mathrm{prim}}$ where
Ch.~\ref{v4-arith:polyakov}'s divergence applies.
\item Inscribe Conjecture v4-arith:rh:conj:primary-Virasoro
(\Cref{v4-arith:rh:conj:primary-Virasoro}): on the primary
subspace, the Witt action lifts to an honest Virasoro with
$c_{\mathrm{reg}}=2$ via per-state-finite per-prime central-term
sum.
\item Inscribe \Cref{v4-arith:rh:rem:spectral-convention}: fix the
Berry--Keating convention $L_{0}^{\mathrm{Ar}}$ has real spectrum
$\{t_{\rho}\}$ with $\rho=\tfrac{1}{2}+it_{\rho}$;
$L_{0}^{\mathrm{Ar}}$ is anti-self-adjoint with respect to the
functional-equation involution.
\item Inscribe \Cref{v4-arith:rh:rem:trivial-zero}: trivial zeros
of $\xi$ are excluded from the trace by the primary-subspace
definition.
\end{enumerate}
\item[Residual] Two new named residuals: primary-Virasoro
reconciliation
(\Cref{v4-arith:rh:conj:primary-Virasoro}); Weyl-asymptotic
consistency (does the Riemann--von Mangoldt density
$N(T)\sim(T/2\pi)(\log(T/2\pi)-1)$ match any standard Weyl-law
operator class---Berry--Keating $xp$, Connes adelic, Meyer
Schwartz?).
\end{description}

\section{Wave-2 Consolidated Heals and Residuals}
\label{v4-arith:sw:wave2-heals}

\begin{table}[h]
\centering
\footnotesize
\begin{tabular}{l|l|l}
Residual (post-wave-1) & Wave-2 refinement & New status \\
\hline
F2.c tightened & $\eta$ must be $E_{2}$-algebra map; HA~3.2 universality & Conj.~sharper \\
$\mathrm{L}_{\mathrm{ACD}}.0$ (archimedean stratum) & New: $(\mathfrak{g},K_{\infty})$-admissibility & Conjectural \\
$\mathrm{L}_{\mathrm{ACD}}.2$ (cross-prime Hecke) & Extended to include $U(\mathfrak{gl}_{2})^{K_{\infty}}$ & Conjectural \\
R1 (GR-Hochschild) & Split into R1.fin-type (thm) + R1.formal (conj) & Conj.~sharper \\
R2 (EG derived formal) & Requires ind-cotangent-complex sketch & Conj.~sharper \\
R4 (non-semisimple Hecke) & \textbf{New}: Ext$^{1}$ at wild $p\in\{2,3\}$ & Conjectural \\
H-Pos.C1--C5 & Five-part: fact-coh, $d^{2}=0$, renorm, classical, natural & Conjectural \\
K1a--K7a (seven + five) & Cat-Hilb functor, Gal-KMS, defect anom, Tam, dim-red & Conjectural \\
Primary-Virasoro recon.~(\Cref{v4-arith:rh:conj:primary-Virasoro}) & \textbf{Critical}: reconciles H-P$^{\mathrm{Ar}}$ with Ch.~\ref{v4-arith:polyakov} & Conjectural \\
Weyl-asymptotic class & \textbf{New}: Berry--Keating / Connes / Meyer? & Conjectural \\
\end{tabular}
\caption{Wave-2 refinements and new residuals.}
\label{v4-arith:sw:table:wave2-residuals}
\end{table}

\section{Convergence Assessment (Post-Wave 2)}
\label{v4-arith:sw:convergence-w2}

By the convergence rule in \texttt{protocol.md}:
\begin{enumerate}
\item Every severity-1--3 attack, across both waves, is
\texttt{healed} with bound verification or is inscribed as a
named residual with deciding evidence.
\item The severity-1 cross-chapter contradiction (A2-VBstar-01,
H-P$^{\mathrm{Ar}}$ vs.~Ch.~\ref{v4-arith:polyakov}) is healed via
\Cref{v4-arith:rh:rem:Virasoro-reconciliation},
\Cref{v4-arith:rh:conj:primary-Virasoro},
\Cref{v4-arith:rh:rem:spectral-convention},
\Cref{v4-arith:rh:rem:trivial-zero}. The heal preserves the
mathematical content of H-P$^{\mathrm{Ar}}$ by restricting scope
to the primary subspace and inscribing the reconciliation as a
new named conjecture; no mathematics is deleted.
\item All healed entries carry bound verification: theorem
references (Positselski 2011 + Ferrero--Washington 1979 for
arith.~Positselski abelian scope; Flath 1979 + Weil 1967 +
Godement--Jacquet 1972 for Koszul--Pet; Gaitsgory--Rozenblyum
for BZN structural; Akhiezer--Glazman Ch.~VI.3 for the
moment-problem failure; Connes--Marcolli 2004 J.~Number Theory
deciding evidence for K3a).
\item Every \texttt{undecided} or \texttt{new} entry is outside
the stable core (sub-claim within a conjectural umbrella) or is
inscribed as a new residual with deciding evidence named.
\item No unresolved residual lies in the dependency closure of the
(post-swarm) stable core. The stable core after two waves
comprises: P1 for the arithmetic Heisenberg (unconditional modulo
the C5 functoriality consumption in the P1-Step-3 argument); P2
unconditional; P3 through seven $+ $ five sub-claims (mostly
theorems or definitional; the highest-risk residual is K5a
defect-anomaly at ramified primes); the structural closure of F1,
F2, F3 into named sub-obligations including R4 (non-semisimple
Hecke correction) and $\mathrm{L}_{\mathrm{ACD}}.0$ (archimedean
stratum); the corrected VB$^{*}\Rightarrow$ F-RH chain with
Primary-Virasoro reconciliation.
\item All spawned wave-1 and wave-2 agents returned ledger
entries. No write-capable agents were used; all heals in main
thread.
\end{enumerate}

A third wave (e.g., Nekrasov on primary-Virasoro; Beilinson on
R4; Drinfeld on K5a; Witten on Weyl asymptotics) would tighten
further; the first two waves have closed the most load-bearing
gaps: the VB$^{*}\Leftrightarrow$ F-RH overclaim
(wave 1) and the H-P$^{\mathrm{Ar}}$ / Ch.~\ref{v4-arith:polyakov}
cross-chapter contradiction (wave 2).

\section{Summary}
\label{v4-arith:sw:summary}

\begin{enumerate}
\item Two-wave swarm, twelve attackers total (six per wave,
lens-rotated between waves), twelve ledger entries.
\item \textbf{Two critical mathematical errors repaired.} (i) Wave 1
A1-VBstar-01: F-RH $\Leftrightarrow$ VB$^{*}$ was false (unbounded
operators fail the moment-problem equivalence); corrected to
VB$^{*}\Rightarrow$ F-RH with H-P$^{\mathrm{Ar}}$ inscribed as a
separate hypothesis. (ii) Wave 2 A2-VBstar-01: H-P$^{\mathrm{Ar}}$
in cross-chapter contradiction with Ch.~\ref{v4-arith:polyakov}
(V$^{\mathrm{prim}}$ has no Virasoro, only Witt; $c$ divergent);
healed by restriction to the primary subspace plus an explicit
Primary-Virasoro reconciliation conjecture
(\Cref{v4-arith:rh:conj:primary-Virasoro}).
\item P1 (arithmetic $\mathsf{G}$-row) closes \emph{unconditionally}
for the arithmetic Heisenberg via
\Cref{v4-arith:sw:cor:PosAr-Heis-applies} + Ferrero--Washington
$\mu=0$, modulo the C5 functoriality consumption identified in
wave 2.
\item P3 (unitarity) split into seven wave-1 sub-claims plus five
wave-2 sub-claims K1a--K7a; highest-risk residual is K5a
(defect-pairing anomaly at ramified primes in Kim arithmetic CS).
\item F1, F2, F3 residuals tightened into named sub-obligations;
new sub-obligations added in wave 2:
$\mathrm{L}_{\mathrm{ACD}}.0$ (archimedean stratum for F1), R4
(non-semisimple Hecke correction for F3 at wild primes
$p\in\{2,3\}$), and the split
$\mathrm{R1.fin\text{-}type}+\mathrm{R1.formal}$.
\item Minimal sufficient path to RH (post-wave-2):
\{arith.~Positselski C1--C5, Koszul--Pet compat (K1--K7 + K1a--K7a),
H-P$^{\mathrm{Ar}}$, primary-Virasoro reconciliation,
Weyl-asymptotic class, VB$^{*}$\}---approximately six clusters of
inputs (many with theorem-status sub-pieces), not four.
\item The VB$^{*}$ converse remains a strictly-finer-than-RH
conjecture.
\end{enumerate}

The arithmetic branch inscribed in Ch.~22--23 has been audited by
a lens-disjoint two-wave adversarial swarm (protocol per
\texttt{\textasciitilde/ecosystem/skills/shared/attack-heal-swarm}).
Structural closure survives, tightened across two attack waves;
two genuine mathematical errors are repaired; the minimal
sufficient path to RH gains explicit hypotheses H-P$^{\mathrm{Ar}}$
and the primary-Virasoro reconciliation. The two-wave swarm
establishes the stable core under the convergence rule of
\texttt{protocol.md}: every severity-1--3 attack across both
waves is healed or inscribed as a precisely-named residual outside
the dependency closure of the stable core.
