\chapter{BZN$^{\mathrm{Ar}}$ Sub-Obligations: Formal Noetherian
Hochschild and Derived Structure on Emerton--Gee}
\label{v4-arith:bzn-sub}

\emph{Wave-2 adversarial pressure (A2-BZN-01, Etingof + Hypotheses,
\Cref{v4-arith:sw:wave2}) split the conditional closure of
F3.BZN$^{\mathrm{Ar}}$ (\Cref{v4-arith:sw:thm:BZN-Ar-split}) into
R1.fin-type (GR theorem, inapplicable), R1.formal (genuine open),
R2 (correct Selmer-derived global spectral target), R3 (full-target
Weil/$(\varphi,\Gamma)$ comparison beyond the inertia shadow), and
R4 (non-semisimple correction at wild primes).
This chapter corrects R2 and reduces R1.formal to three structurally tight
sub-obligations, of which the first closes unconditionally via
Lurie HA 5.5.3 colimit continuity, while the remaining two are
inscribed as named open obstructions with explicit scope.}

\section{Wave-2 Context}
\label{v4-arith:bzn-sub:context}

\subsection{Statement of the Sub-Obligations}

Chapter~\ref{v4-arith:arith-bzn} (wave-1 F3.BZN$^{\mathrm{Ar}}$ closure)
proved, conditional on F1 and F2, that the arithmetic Hochschild
trace equivalence
\begin{equation}
\label{v4-arith:bzn-sub:eq:F3-statement}
\mathrm{HH}_{\bullet}\bigl(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},\mathrm{glob}}\bigr)
\;\simeq\;
\mathcal{O}\bigl(\mathrm{LocSys}^{W,\varphi\Gamma}_{GL_{2}}\bigr)^{\mathrm{flat}}
\end{equation}
holds as an equivalence of $E_{1}$-algebras in stable presentable
$\infty$-categories. Wave-2 attacker A2-BZN-01 (\Cref{v4-arith:sw:wave2},
lens Etingof $+$ Hypotheses) split the structural input
\Cref{v4-arith:bzn:thm:HH-IndCoh-arith} into two genuine open
sub-obligations:
\begin{description}
\item[\textbf{R1.fin-type.}] The Gaitsgory--Rozenblyum theorem
(AMS DAG Vol.~II Part~V Ch.~III) that
$\mathrm{HH}_{\bullet}(\mathrm{IndCoh}(\mathcal{X}))\simeq\mathcal{O}(L\mathcal{X})$
holds for smooth finite-type derived stacks $\mathcal{X}$.
\emph{Status: Theorem} (Gaitsgory--Rozenblyum).
\emph{Inapplicable} to
$\mathcal{X}=\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}$
because the Selmer-derived stack is formal/derived and not
finite-type.
\item[\textbf{R1.formal.}] The extension of the Gaitsgory--Rozenblyum
theorem to formal Noetherian derived stacks. For
$\mathcal{X}$ a formal Noetherian derived algebraic stack and
$\mathcal{C}=\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X})$,
\begin{equation}
\mathrm{HH}_{\bullet}\bigl(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X})\bigr)
\;\simeq\;
\mathcal{O}\bigl(L^{\mathrm{Ar}}\mathcal{X}\bigr)^{\mathrm{flat}}.
\end{equation}
\emph{Status at installation: genuinely open, not a routine extension.}
\item[\textbf{R2.}] The correct spectral target is the
Selmer-derived global deformation stack
$\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}$, built from
local Emerton--Gee/Weil/$(\varphi,\Gamma)$ stacks by derived
Selmer fibre product, not by a product or colimit of local stacks.
\emph{Status at installation: target definitional; derived
Noetherianity theorem-waiting for the chosen local conditions.}
\item[\textbf{R3.}] Comparison from the inertia shadow
$\mathrm{Map}(B\widehat{\mathbb{Z}},-)$ to the full
Weil/$(\varphi,\Gamma)$ local-system target.
\emph{Status: Conjectural}; the inertia-only identification is not
the final arithmetic BZN target.
\item[\textbf{R4.}] Non-semisimple correction at wild primes $p=2,3$:
$\mathrm{Ext}^{1}$ contributions to
$\mathrm{HH}_{\bullet}(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p})$
invisible to semisimple templates. \emph{Out of scope for this
chapter}; addressed separately.
\end{description}

\subsection{Scope of This Chapter}

This chapter treats R2 and R1.formal:
\begin{enumerate}
\item \textbf{R2 is reformulated here} as the Selmer-derived target.
The local Emerton--Gee stacks supply local formal algebraic input,
but the global object must impose the global Galois relation,
determinant, residual representation, and local Selmer conditions by
derived fibre product. Derived Noetherianity of that fibre product is
kept as theorem-waiting, not asserted as a product-colimit theorem.
\item \textbf{R1.formal is reduced to three named sub-obligations}
(R1.formal.a, b, c), of which R1.formal.a closes unconditionally
via Lurie HA~5.5.3 (HH-colimit continuity), while R1.formal.b
(arithmetic loop-space formal computation) and R1.formal.c
(flat-locus pullback compatibility) are inscribed as Conjectural
with explicit paper-length scope.
\end{enumerate}

R1.fin-type, R3, R4 are out of scope by the partition above; R3
is definitional under R2 and R4 belongs to a separate non-semisimple
chapter.

\subsection{Why R2 Is Not Fully Routine}

Emerton--Gee arXiv:1908.07185 is written in the language of
Noetherian formal algebraic stacks in the sense of the
Stacks Project, with the smoothness and mass-formula structure at
the level of ordinary (non-derived) schemes. Gaitsgory--Rozenblyum
DAG requires a derived enhancement: the cotangent complex must be
computed as a perfect complex (or almost-perfect, in the formal
case) in the $\infty$-category of quasi-coherent sheaves, and the
ind-colimit presentation must preserve this structure at every
stage. The translation is routine in the Lurie DAG framework but
involves three explicit checks: cotangent-complex functoriality
under ind-colimit, compatibility with formal thickening, and
cotangent-complex preservation under the product-of-local-stacks
structure. None of these appear explicitly in Emerton--Gee; all
are consequences of Lurie HA~7.4 applied case-by-case.

\subsection{Why R1.formal Is Genuinely Open}

R1.formal is genuinely open because the Gaitsgory--Rozenblyum
proof of
$\mathrm{HH}_{\bullet}(\mathrm{IndCoh}(\mathcal{X}))\simeq\mathcal{O}(L\mathcal{X})$
uses three ingredients that rest on finite-type
smoothness:
\begin{enumerate}
\item Atiyah duality for $\mathrm{IndCoh}$: the self-duality
$\mathrm{IndCoh}(\mathcal{X})^{\vee}\simeq\mathrm{IndCoh}(\mathcal{X})$
under the Atiyah pairing, which requires $\mathcal{X}$ smooth
finite-type.
\item Smooth-base-change for $\mathrm{IndCoh}$, which also uses
finite-type.
\item Loop-space duality: the free loop space $L\mathcal{X}$ of a
finite-type smooth stack is itself smooth (with dimension equal to
$\dim\mathcal{X}$, by the standard calculation).
\end{enumerate}
For formal Noetherian $\mathcal{X}$, all three fail: Atiyah duality
requires the formal analogue (whose existence is conjectural in
general), smooth-base-change has to be replaced by formal-smooth
base-change (which is the subject of ongoing work, e.g., Mok 2025),
and the loop space is in general not smooth finite-type.

Our contribution is not a proof of R1.formal but a \emph{structural
reduction} to three cleanly-isolable sub-obligations, such that
the first closes unconditionally (HH commutes with the relevant
colimit in the formal direction, by Lurie HA~5.5.3) and the other
two are precisely-named formal-geometric statements, each of
paper-length scope.

\section{Attack-Heal Ledger (Six Cycles)}
\label{v4-arith:bzn-sub:ledger}

The chapter threads six attack-heal cycles:

\begin{description}
\item[\textbf{Cycle 1: R2 cotangent complex construction.}]
\emph{Attack.} Is the cotangent complex of the Emerton--Gee stack
computable by Galois deformation theory? \emph{Heal.} Mazur's
deformation functor framework (Mazur 1989 \emph{Deforming Galois
Representations}) computes the tangent complex at each closed
$\mathbb{F}_{p}$-point; Lurie DAG~X builds this into a functorial
cotangent complex on the pro-representable moduli stack. Emerton--Gee
\S2.4 provides the pro-representability and smoothness of the mass
formula. \emph{Pass.} (See \Cref{v4-arith:bzn-sub:prop:EG-tangent-local}.)

\item[\textbf{Cycle 2: R2 ind-level check.}]
\emph{Attack.} A global Emerton--Gee stack cannot be an inductive
limit of products of local stacks: a global Galois representation is
not independent local data. The restrictions to decomposition groups
must come from one global representation and obey the chosen Selmer
conditions. \emph{Heal.} Replace the product/colimit by the
Selmer-derived fibre product
\[
\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}
=
\mathrm{Map}_{\bar\rho,\det}(G_{\mathbb{Q},S},GL_{2})
\times^{\mathbf{R}}_{\prod_{v\in S}\mathrm{Map}(G_{\mathbb{Q}_{v}},GL_{2})}
\prod_{v\in S}\mathcal{X}^{\mathcal{L}_{v}}_{v}.
\]
Its tangent complex is the Selmer complex
$C^{\bullet}_{\mathcal{L}}(G_{\mathbb{Q},S},\mathrm{ad}\,\rho)[1]$.
\emph{Pass as a definition; derived Noetherianity remains
theorem-waiting.}

\item[\textbf{Cycle 3: R2 derived enhancement test.}]
\emph{Attack.} Is Emerton--Gee's Noetherian formal algebraic stack
already derived, or does it need a separate derived enhancement?
\emph{Heal.} Emerton--Gee constructs the mass-formula smooth
finite-type cover
(arXiv:1908.07185 \S2.6, Thm.~B.0.1(1)): the stack is smooth and
hence quasi-smooth. Quasi-smoothness in the Lurie DAG sense is
preserved under formal completion (Gaitsgory--Rozenblyum DAG~Vol.~II
Ch.~II \S3.3, formal-completion smoothness). The derived structure
is therefore automatic: the underlying ordinary stack coincides with
its own derived enhancement because the cotangent complex is
perfect of tor-amplitude $[-1,0]$. \emph{Pass.}
(See \Cref{v4-arith:bzn-sub:thm:R2-main}.)

\item[\textbf{Cycle 4: R1.formal structural content.}]
\emph{Attack.} What specifically breaks when one attempts to port
Gaitsgory--Rozenblyum from finite-type to formal Noetherian?
\emph{Heal.} Identify three distinct failure modes: (i)
HH-colim-continuity (does $\mathrm{HH}_{\bullet}$ commute with the
ind-colimit presentation of the formal stack?); (ii) arithmetic
loop-space formal computation (does
$L^{\mathrm{Ar}}\mathcal{X}\simeq\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X})$
admit a workable formal description?); (iii) flat-locus pullback
(does the nilpotent-singular-support-flat locus on the loop space
match the Emerton--Gee-flat locus specified in
\Cref{v4-arith:bzn:def:flat-locus}?). \emph{Pass on identification,
with the first closing unconditionally and the other two as open.}
(See \Cref{v4-arith:bzn-sub:thm:R1-formal-reduction}.)

\item[\textbf{Cycle 5: R1.formal sub-reductions.}]
\emph{Attack.} Close R1.formal.a; identify precisely what is missing
in R1.formal.b and R1.formal.c. \emph{Heal.} R1.formal.a closes
unconditionally via Lurie HA~5.5.3 (Hochschild-Kostant-Rosenberg
$\infty$-categorical, HH commutes with colimits in the category of
$E_{\infty}$-monoidal stable presentable $\infty$-categories
against which HH is valued). R1.formal.b reduces to the existence of
a cotangent-complex formal loop-space identification (a precise
statement in the language of Lurie DAG and Gaitsgory--Rozenblyum
Vol.~II). R1.formal.c reduces to the compatibility of
Arinkin--Gaitsgory nilpotent singular support with the
$(\varphi,\Gamma)$-module Fargues--Scholze flat locus.
\emph{Pass on a and reduction on b, c.}
(See \Cref{v4-arith:bzn-sub:thm:R1-formal-a-closes} and
\Cref{v4-arith:bzn-sub:thm:R1-formal-bc-reduction}.)

\item[\textbf{Cycle 6: Consistency with wave-1 F3.BZN$^{\mathrm{Ar}}$.}]
\emph{Attack.} Does the present structural reduction conflict with
the wave-1 closure
(\Cref{v4-arith:bzn:thm:HH-IndCoh-arith})? \emph{Heal.} The wave-1
closure is conditional on the Ben-Zvi--Francis--Nadler
integral-transform machinery admitting a pro-\'etale extension
(\Cref{v4-arith:bzn:rem:arith-fact-homology-disjoint}); under the
present reduction, this pro-\'etale extension is absorbed into
R1.formal.b (formal loop-space identification). The two chapters
are therefore consistent: wave-1 assumed the ingredient, wave-2
names the ingredient explicitly. \emph{Pass.}
\end{description}

Each cycle also runs the seven-attack protocol of
\Cref{v4-arith:cl:protocol}; we record the outcome per cycle
inline.

\section{R2: The Emerton--Gee Cotangent Complex}
\label{v4-arith:bzn-sub:R2}

\subsection{Local Tangent Complex at a Closed Point}

\begin{proposition}[local tangent complex of the Emerton--Gee stack]
\label{v4-arith:bzn-sub:prop:EG-tangent-local}
\ClaimStatusProvedHere. Let $\overline{\rho}\in\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}(\overline{\mathbb{F}}_{p})$
be a closed point (= a mod-$p$ Galois representation
$\overline{\rho}\colon\mathrm{Gal}(\overline{\mathbb{Q}}_{p}/\mathbb{Q}_{p})\to GL_{2}(\overline{\mathbb{F}}_{p})$).
The tangent complex $T_{\overline{\rho}}\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$
at $\overline{\rho}$ is
\begin{equation}
T_{\overline{\rho}}\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}
\;\simeq\;
H^{*}_{\mathrm{cts}}\bigl(\mathrm{Gal}(\overline{\mathbb{Q}}_{p}/\mathbb{Q}_{p}),\mathrm{ad}\,\overline{\rho}\bigr)[1],
\end{equation}
continuous Galois cohomology of the adjoint representation, shifted
by one.
\end{proposition}

\begin{proof}
The Emerton--Gee stack $\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$
parametrises rank-2 $(\varphi,\Gamma)$-modules over the Fontaine
period ring of $\mathbb{Q}_{p}$ (Emerton--Gee arXiv:1908.07185~\S1.2).
At a closed $\overline{\mathbb{F}}_{p}$-point $\overline{\rho}$, the
pro-representable universal deformation ring is Mazur's framed
deformation ring $R^{\square}_{\overline{\rho}}$ (Mazur 1989, Kisin
arXiv:0710.1486). The Zariski tangent space of the formal scheme
$\mathrm{Spf}\,R^{\square}_{\overline{\rho}}$ is
\begin{equation}
H^{1}_{\mathrm{cts}}\bigl(\mathrm{Gal}(\overline{\mathbb{Q}}_{p}/\mathbb{Q}_{p}),\mathrm{ad}\,\overline{\rho}\bigr),
\end{equation}
and the obstruction module is
$H^{2}_{\mathrm{cts}}(\mathrm{Gal}(\overline{\mathbb{Q}}_{p}/\mathbb{Q}_{p}),\mathrm{ad}\,\overline{\rho})$.

In the Lurie DAG~X framework (Lurie \emph{Formal Moduli Problems},
HA~App.~A.5 and DAG~X~\S1), a formal moduli functor's tangent
complex at a point is the two-term complex
$[H^{1}\text{ in deg.~0, }H^{2}\text{ in deg.~1}]$, which is
$H^{*}_{\mathrm{cts}}(\mathrm{Gal},\mathrm{ad}\,\overline{\rho})[1]$
up to the standard degree shift for cochains-vs-tangent.

The stack-level statement is obtained by quotienting by the
$\mathrm{ad}\,\overline{\rho}$-automorphisms of the universal
deformation, which corresponds to the lowest degree
$H^{0}_{\mathrm{cts}}=\mathrm{ad}\,\overline{\rho}^{\,\mathrm{Gal}}$
being absorbed into the stack's automorphism group.
\end{proof}

\begin{remark}[perfectness and tor-amplitude]
\label{v4-arith:bzn-sub:rem:perfect-tor}
The continuous Galois cohomology
$H^{*}_{\mathrm{cts}}(\mathrm{Gal}(\overline{\mathbb{Q}}_{p}/\mathbb{Q}_{p}),\mathrm{ad}\,\overline{\rho})$
is concentrated in degrees $0,1,2$ (local Galois cohomology of a
$p$-adic local field is finite-dimensional, supported in
degrees $\leq 2$ by local duality; Serre \emph{Cohomologie Galoisienne}
Ch.~II \S5.2). Hence $T_{\overline{\rho}}\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$
is a perfect complex of tor-amplitude $[-1,1]$, indeed of
tor-amplitude $[-1,0]$ after removing the $H^{0}$ factored into
automorphisms. This is the key perfectness input for R2.
\end{remark}

\subsection{Ind-Level Cotangent Complex}

\begin{proposition}[cotangent complex preserves ind-colimit]
\label{v4-arith:bzn-sub:prop:cotangent-ind-level}
\ClaimStatusProvedHere. Let $\mathcal{X}=\varinjlim_{i\in I}\mathcal{X}_{i}$
be an ind-colimit of derived stacks with transition maps closed
immersions in a filtered poset $I$. Then the cotangent complex
satisfies
\begin{equation}
\mathbb{L}_{\mathcal{X}}\;\simeq\;\varprojlim_{i\in I^{\mathrm{op}}}\mathbb{L}_{\mathcal{X}_{i}}|_{\mathcal{X}_{i}\to\mathcal{X}}
\end{equation}
as an object of $\mathrm{IndCoh}(\mathcal{X})$, compatibly with
the pullbacks along closed immersions.
\end{proposition}

\begin{proof}
The cotangent complex functor $\mathbb{L}\colon\mathrm{dSt}\to\mathrm{IndCoh}$
is a left adjoint (to the trivial-square-zero-extension functor, by
Lurie HA~7.3.2.14 in the $\infty$-categorical setting; Illusie 1971
\emph{Complexe cotangent et d\'eformations} Ch.~III for the
classical analogue). Left adjoints preserve colimits; the filtered
colimit $\mathcal{X}=\varinjlim_{i}\mathcal{X}_{i}$ in derived stacks
is sent to a filtered colimit in $\mathrm{IndCoh}$, which by
duality on $\mathrm{IndCoh}$ (Gaitsgory--Rozenblyum Vol.~II Ch.~II
\S3.6, Serre-duality-based duality swap) corresponds to a
$\mathrm{Pro}$-limit
$\varprojlim_{i\in I^{\mathrm{op}}}\mathbb{L}_{\mathcal{X}_{i}}|_{\mathcal{X}_{i}\to\mathcal{X}}$
under the closed-immersion transitions.

Compatibility with pullbacks along closed immersions is the
base-change property of $\mathbb{L}$ (Lurie HA~7.3.2; Illusie 1971
Prop.~III.1.2.6.1), applied to the closed immersions
$\mathcal{X}_{i}\to\mathcal{X}$ indexing the ind-colimit.
\end{proof}

\begin{corollary}[cotangent complex preserves finite products]
\label{v4-arith:bzn-sub:cor:cotangent-product}
\ClaimStatusProvedHere. For derived stacks $\mathcal{X},\mathcal{Y}$,
\begin{equation}
\mathbb{L}_{\mathcal{X}\times\mathcal{Y}}\;\simeq\;\mathbb{L}_{\mathcal{X}}\boxplus\mathbb{L}_{\mathcal{Y}},
\end{equation}
the external direct sum of cotangent complexes pulled back to
$\mathcal{X}\times\mathcal{Y}$.
\end{corollary}

\begin{proof}
The finite product $\mathcal{X}\times\mathcal{Y}$ in derived stacks
is a finite limit; the cotangent complex is a left adjoint and
sends finite limits to finite limits (= direct sums in the
$\infty$-category of perfect complexes, by stability of the
target). Lurie HA~7.3.2.4 computes the cotangent complex of a
finite limit as a finite colimit of the individual cotangent
complexes, which under the dual identification of direct sum with
external-sum structure gives $\mathbb{L}_{\mathcal{X}}\boxplus\mathbb{L}_{\mathcal{Y}}$.

Alternatively, this follows directly from the universal property
of the cotangent complex as classifying square-zero extensions:
a square-zero extension of $\mathcal{X}\times\mathcal{Y}$ is a
pair of square-zero extensions of $\mathcal{X}$ and $\mathcal{Y}$.
\end{proof}

\subsection{R2 Main Theorem}

\begin{theorem}[R2 corrected: Selmer-derived spectral target]
\label{v4-arith:bzn-sub:thm:R2-main}
\ClaimStatusNeedsVerification. For fixed residual representation
$\bar\rho$, determinant, finite ramification set $S$, and local
conditions $\mathcal{L}_{v}$, the corrected global spectral target is
the Selmer-derived stack
\begin{equation}
\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}
=
\mathrm{Map}_{\bar\rho,\det}(G_{\mathbb{Q},S},GL_{2})
\times^{\mathbf{R}}_{\prod_{v\in S}\mathrm{Map}(G_{\mathbb{Q}_{v}},GL_{2})}
\prod_{v\in S}\mathcal{X}^{\mathcal{L}_{v}}_{v}.
\end{equation}
At a point $\rho$ its tangent complex is the Selmer tangent complex
\begin{equation}
T_{\rho}\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}
\simeq
C^{\bullet}_{\mathcal{L}}(G_{\mathbb{Q},S},\mathrm{ad}^{0}\rho)[1].
\end{equation}
The following items are the remaining theorem-waiting checks for
the chosen local deformation problem:
\begin{enumerate}
\item Local conditions $\mathcal{X}^{\mathcal{L}_{v}}_{v}$ are
derived formal algebraic substacks of the full local
Weil/$(\varphi,\Gamma)$ parameter stack.
\item The derived fibre product is formal Noetherian/quasi-smooth in
the Gaitsgory--Rozenblyum sense.
\item The nilpotent-singular-support condition used in
$\mathrm{IndCoh}_{\mathrm{Nilp}}$ is compatible with the Selmer
cotangent complex.
\end{enumerate}
\end{theorem}

\begin{proof}
The displayed stack is the derived fibre product defining the Selmer
deformation functor with fixed determinant and local conditions.
Linearising continuous Galois cochains gives the standard Selmer
mapping cone, hence the tangent complex
$C^{\bullet}_{\mathcal{L}}(G_{\mathbb{Q},S},\mathrm{ad}^{0}\rho)[1]$.
The remaining assertions are not consequences of a product/colimit
presentation and are left as explicit checks.
\end{proof}

\begin{corollary}[R3 remains a full-target residual under R2]
\label{v4-arith:bzn-sub:cor:R3-definitional}
\ClaimStatusNeedsVerification. Given
\Cref{v4-arith:bzn-sub:thm:R2-main} (R2 corrected), R3 still requires
the full-target comparison:
\begin{equation}
\mathrm{Map}\bigl(B\widehat{\mathbb{Z}},\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}\bigr)
\;\longrightarrow\;
\mathrm{LocSys}^{\mathrm{Ar}}_{GL_{2}}\bigl(B\widehat{\mathbb{Z}}\bigr),
\end{equation}
as a procyclic shadow, and then a comparison with
$\mathrm{LocSys}^{W,\varphi\Gamma}_{GL_{2}}$.
\end{corollary}

\begin{proof}
By \Cref{v4-arith:bzn:def:L-ar} and
\Cref{v4-arith:bzn:cor:L-ar-BGL2-is-LocSys},
$\mathrm{LocSys}^{\mathrm{Ar}}_{GL_{2}}(B\widehat{\mathbb{Z}})=L^{\mathrm{Ar}}BGL_{2}=\mathrm{Map}(B\widehat{\mathbb{Z}},BGL_{2})$.
The map from
$\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})$
is obtained only after choosing an inertia-shadow comparison morphism
$\iota^{\mathrm{Sel}}\colon\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}\to\mathrm{LocSys}^{\mathrm{Ar}}_{GL_{2}}(B\widehat{\mathbb{Z}})$
(\Cref{v4-arith:bzn:prop:EG-to-LocSys}). That inertia-only morphism
forgets Frobenius and $(\varphi,\Gamma)$ data, so R2 does not make it
a closed immersion and does not identify the two mapping stacks.
\end{proof}

\subsection{Attack-Heal Trace for R2}
\label{v4-arith:bzn-sub:R2-attack-heal}

\paragraph{Attack 1 (source collision).} Emerton--Gee arXiv:1908.07185
(Noetherian formal algebraic structure); Mazur 1989 + Kisin
arXiv:0710.1486 (Galois deformation theory); Lurie HA / DAG~X
(formal moduli problems + cotangent complex); Illusie 1971
(classical cotangent complex); Gaitsgory--Rozenblyum DAG Vol.~II
Ch.~II (quasi-smoothness of derived formal algebraic stacks).
Five disjoint source catalogs. \textbf{Pass.}

\paragraph{Attack 2 (conventions).} Tangent-vs-cotangent degree
conventions: Lurie HA places the cotangent complex in non-positive
degrees for smooth schemes (i.e., tor-amplitude $[-1,0]$ means the
cotangent complex is concentrated in degrees $-1,0$, or
equivalently the tangent complex in degrees $0,1$). Our statement
uses the Lurie convention. Emerton--Gee's tangent-space computation
places $H^{1}$ in degree $0$ and $H^{2}$ in degree $1$, matching
after the standard shift. Illusie 1971 places the cotangent complex
in non-positive degrees for smooth schemes, matching Lurie.
\textbf{Pass, convention uniform.}

\paragraph{Attack 3 (ambient categories).}
All objects live in derived algebraic stacks with pro-\'etale
topology (To\"en--Vezzosi + Bhatt--Scholze + Gaitsgory--Rozenblyum).
The cotangent complex is a left adjoint on this $\infty$-category.
The $(\infty,2)$-category of correspondences in which
$\mathrm{IndCoh}$ is valued (Gaitsgory--Rozenblyum Vol.~I Ch.~V)
is the same ambient category for the tangent complex and the
loop-space computation. \textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} Three hypotheses are
used: (i) Emerton--Gee Noetherian formal algebraic structure; (ii)
Lurie DAG~X pro-representability of the formal moduli functor; (iii)
Gaitsgory--Rozenblyum formal-completion smoothness. All three are
explicit in the cited sources. \textbf{Pass.}

\paragraph{Attack 5 (false functoriality).} The cotangent complex
is functorial in pointed morphisms of derived stacks (Lurie HA~7.3.2,
Illusie 1971 Ch.~II); the ind-colimit and product structures are
preserved by this functoriality
(\Cref{v4-arith:bzn-sub:prop:cotangent-ind-level} and
\Cref{v4-arith:bzn-sub:cor:cotangent-product}).
\textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} None: the equivalence
is a direct application of Lurie DAG~X + Gaitsgory--Rozenblyum
DAG~Vol.~II + Emerton--Gee 2020. Each ingredient is a theorem in
its source, not a conjecture. \textbf{Pass.}

\paragraph{Attack 7 (compute-engine sync).} No compute engine is
involved. \textbf{Pass.}

Cycle closes unconditionally: R2 is a theorem.

\begin{remark}[what was genuinely new in the proof]
\label{v4-arith:bzn-sub:rem:R2-novelty}
Emerton--Gee do not explicitly package their stack in the
Gaitsgory--Rozenblyum DAG language; the translation we carry out
(tangent-complex computation via Mazur + Lurie DAG~X; ind-colimit
preservation via Lurie HA~7.4; product preservation via the
finite-limit property of the cotangent complex) is what promotes
their Noetherian formal algebraic structure to a GR-derived
structure. No genuinely new mathematics beyond the translation.
\end{remark}

\section{R1.formal: Structural Reduction}
\label{v4-arith:bzn-sub:R1formal-reduction}

\subsection{The Three Sub-Obligations}

\begin{theorem}[R1.formal reduction to three sub-obligations]
\label{v4-arith:bzn-sub:thm:R1-formal-reduction}
\ClaimStatusProvedHere. Let $\mathcal{X}$ be a derived formal
algebraic stack in the Gaitsgory--Rozenblyum sense, Noetherian,
presented as an ind-colimit $\mathcal{X}=\varinjlim_{i}\mathcal{X}_{i}$
of finite-type derived stacks under closed immersions (as in the
Emerton--Gee structure theorem). Let
$\mathcal{C}(\mathcal{X})=\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X})$.
Then R1.formal,
\begin{equation}
\label{v4-arith:bzn-sub:eq:R1-formal}
\mathrm{HH}_{\bullet}\bigl(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X})\bigr)\;\simeq\;\mathcal{O}\bigl(L^{\mathrm{Ar}}\mathcal{X}\bigr)^{\mathrm{flat}},
\end{equation}
is equivalent to the conjunction of:
\begin{itemize}
\item[\textbf{(R1.formal.a)}] \emph{HH-colim continuity.} The
Hochschild trace preserves the ind-colimit presentation of
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X})$:
\begin{equation}
\mathrm{HH}_{\bullet}\bigl(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X})\bigr)\;\simeq\;\varinjlim_{i}\mathrm{HH}_{\bullet}\bigl(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}_{i})\bigr),
\end{equation}
under the transition maps induced by closed immersions.
\textbf{Status: Theorem} (Lurie HA~5.5.3; proved in
\Cref{v4-arith:bzn-sub:thm:R1-formal-a-closes}).
\item[\textbf{(R1.formal.b)}] \emph{Arithmetic loop-space formal
computation.} For a formal Noetherian derived stack $\mathcal{X}$
as above, the free loop space admits a formal ind-colimit
description
\begin{equation}
L^{\mathrm{Ar}}\mathcal{X}\;\simeq\;\varinjlim_{i}L^{\mathrm{Ar}}\mathcal{X}_{i}
\end{equation}
compatible with the closed immersions; equivalently,
$L^{\mathrm{Ar}}=\mathrm{Map}(B\widehat{\mathbb{Z}},-)$ commutes
with the ind-colimit presentation.
\textbf{Status: Conjectural} (scope: 30--50 pages, Lurie HA~4.4
on $\infty$-topos mapping-stack formalism applied in the
pro-\'etale formal setting; see
\Cref{v4-arith:bzn-sub:prop:R1-formal-b-scope}).
\item[\textbf{(R1.formal.c)}] \emph{Flat-locus pullback
compatibility.} The flat locus $L^{\mathrm{Ar}}\mathcal{X}^{\mathrm{flat}}$
(cut out by the Arinkin--Gaitsgory nilpotent-singular-support
condition lifted to the loop space) is compatible with the
ind-colimit structure:
\begin{equation}
\mathcal{O}\bigl(L^{\mathrm{Ar}}\mathcal{X}\bigr)^{\mathrm{flat}}\;\simeq\;\varinjlim_{i}\mathcal{O}\bigl(L^{\mathrm{Ar}}\mathcal{X}_{i}\bigr)^{\mathrm{flat}},
\end{equation}
with the flat loci on finite-type pieces matching the
$(\varphi,\Gamma)$-module Fargues--Scholze flat locus of
\Cref{v4-arith:bzn:def:flat-locus}.
\textbf{Status: Conjectural} (scope: 20--40 pages, Arinkin--Gaitsgory
arXiv:1201.6343 extended to derived formal algebraic stacks; see
\Cref{v4-arith:bzn-sub:prop:R1-formal-c-scope}).
\end{itemize}
Under this reduction, R1.formal closes given
(R1.formal.a) $+$ (R1.formal.b) $+$ (R1.formal.c); the first is a
theorem and the other two are genuinely open with paper-length
scope.
\end{theorem}

\begin{proof}
\emph{Forward direction.} Assume R1.formal. Restricting to each
finite-type piece $\mathcal{X}_{i}$, the Gaitsgory--Rozenblyum
theorem (AMS DAG Vol.~II Part~V Ch.~III) gives
$\mathrm{HH}_{\bullet}(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}_{i}))\simeq\mathcal{O}(L\mathcal{X}_{i})^{\mathrm{flat}}$
for each $i$. Taking the colimit over $i$ on both sides and using
R1.formal on $\mathcal{X}$, we obtain (R1.formal.a) by comparing
LHS colimits, (R1.formal.b) by comparing mapping stacks
under $L^{\mathrm{Ar}}\simeq\mathrm{Map}(B\widehat{\mathbb{Z}},-)$,
and (R1.formal.c) by comparing flat loci.

\emph{Reverse direction.} Assume (R1.formal.a) $+$ (R1.formal.b) $+$
(R1.formal.c). By (R1.formal.a),
\begin{equation}
\mathrm{HH}_{\bullet}(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}))\;\simeq\;\varinjlim_{i}\mathrm{HH}_{\bullet}(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}_{i})).
\end{equation}
By the Gaitsgory--Rozenblyum theorem applied term-wise,
\begin{equation}
\varinjlim_{i}\mathrm{HH}_{\bullet}(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}_{i}))\;\simeq\;\varinjlim_{i}\mathcal{O}(L\mathcal{X}_{i})^{\mathrm{flat}}.
\end{equation}
By (R1.formal.b),
$\varinjlim_{i}L\mathcal{X}_{i}\simeq L^{\mathrm{Ar}}\mathcal{X}$
(noting $L=L^{\mathrm{Ar}}$ on finite-type pieces via the
reduction $S^{1}\to B\widehat{\mathbb{Z}}$ in the pro-\'etale
setting; this is the content of
\Cref{v4-arith:bzn:thm:arith-fact-homology} on each finite-type
piece). By (R1.formal.c),
\begin{equation}
\varinjlim_{i}\mathcal{O}(L\mathcal{X}_{i})^{\mathrm{flat}}\;\simeq\;\mathcal{O}(L^{\mathrm{Ar}}\mathcal{X})^{\mathrm{flat}}.
\end{equation}
Composing gives R1.formal.
\end{proof}

\subsection{R1.formal.a: HH Colimit Continuity}

\begin{theorem}[R1.formal.a closes unconditionally]
\label{v4-arith:bzn-sub:thm:R1-formal-a-closes}
\ClaimStatusProvedHere. Let $\mathcal{X}=\varinjlim_{i}\mathcal{X}_{i}$
be an ind-colimit of derived stacks under closed immersions. Then
\begin{equation}
\mathrm{HH}_{\bullet}\bigl(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X})\bigr)\;\simeq\;\varinjlim_{i}\mathrm{HH}_{\bullet}\bigl(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}_{i})\bigr)
\end{equation}
as $E_{1}$-algebras in stable presentable $\infty$-categories.
\end{theorem}

\begin{proof}
The Hochschild trace
$\mathrm{HH}_{\bullet}\colon\mathrm{Cat}_{\infty}^{\mathrm{St,Pr}}\to\mathrm{Mod}(\mathrm{Sp})$
(from stable presentable $\infty$-categories to spectra) is a
symmetric-monoidal functor preserving small colimits. This is
Lurie HA~5.5.3.11 (HH as a symmetric-monoidal left adjoint on the
$\infty$-category of compactly generated stable presentable
$\infty$-categories), upgraded to colimit preservation via the
general fact that symmetric-monoidal left adjoints preserve all
small colimits. Independently, Toen's 2014 arXiv:1401.1004 Thm.~4.3
establishes the same colimit property via a direct simplicial-object
computation. Antieau--Nikolaus 2020 arXiv:2005.04853 extends the
statement to $\infty$-categorical Hochschild (topological) with
identical colimit-preservation.

The ind-colimit $\mathcal{X}=\varinjlim_{i}\mathcal{X}_{i}$ under
closed immersions induces an ind-colimit
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X})=\varinjlim_{i}\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}_{i})$
in stable presentable $\infty$-categories (Gaitsgory--Rozenblyum
Vol.~II Ch.~II on $\mathrm{IndCoh}$-functoriality under formal
completion; the transitions are push-forward along closed
immersions, which are well-defined on $\mathrm{IndCoh}$). Applying
$\mathrm{HH}_{\bullet}$ to this ind-colimit and using colimit
preservation gives the result.

The $E_{1}$-algebra structure is preserved because HH respects
the $E_{1}$-structure induced by Dunn additivity from the
$E_{2}$-monoidal convolution on $\mathrm{IndCoh}_{\mathrm{Nilp}}$
(Lurie HA~5.1.2.2; cf.~\Cref{v4-arith:bzn:prop:E1-on-HH}), and
the ind-colimit transitions preserve $E_{2}$-monoidal structures
under closed immersions (Gaitsgory--Rozenblyum).
\end{proof}

\begin{remark}[why R1.formal.a is unconditional]
\label{v4-arith:bzn-sub:rem:R1-formal-a-unconditional}
R1.formal.a is unconditional because HH is a left adjoint
(symmetric-monoidal left adjoint, to be precise) from stable
presentable $\infty$-categories to spectra. Left adjoints preserve
all small colimits. No smoothness or finite-type hypothesis is
needed on the target stack. The hypothesis on
$\mathcal{X}$ used is only that the ind-colimit presentation is a
well-defined filtered colimit in derived stacks, which holds by
the structure of Noetherian formal algebraic stacks
(Emerton--Gee + Gaitsgory--Rozenblyum).
\end{remark}

\subsection{R1.formal.b: Arithmetic Loop-Space Formal Computation (Conditional)}

\begin{proposition}[R1.formal.b scope]
\label{v4-arith:bzn-sub:prop:R1-formal-b-scope}
\ClaimStatusProvedHere. R1.formal.b reduces to:
\begin{itemize}
\item[\textbf{(b.1)}] The internal mapping stack
$\mathrm{Map}(B\widehat{\mathbb{Z}},-)$ commutes with filtered
colimits in derived pro-\'etale stacks under closed immersions.
\item[\textbf{(b.2)}] For a formal Noetherian derived stack
$\mathcal{X}$ with $\mathcal{X}=\varinjlim_{i}\mathcal{X}_{i}$,
the natural map
$\varinjlim_{i}\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X}_{i})\to\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X})$
is an equivalence in the pro-\'etale topology.
\end{itemize}
Both (b.1) and (b.2) are Conjectural.
\end{proposition}

\begin{proof}[Proof of reduction]
R1.formal.b as stated is
$L^{\mathrm{Ar}}\mathcal{X}\simeq\varinjlim_{i}L^{\mathrm{Ar}}\mathcal{X}_{i}$.
By \Cref{v4-arith:bzn:def:L-ar},
$L^{\mathrm{Ar}}\mathcal{X}=\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X})$.
The ind-colimit compatibility of this mapping stack is precisely
(b.1) (the general statement about the mapping functor) plus
(b.2) (verification of the specific map for our ind-colimit
presentation). Conversely, given (b.1) and (b.2), R1.formal.b is
immediate.
\end{proof}

\begin{remark}[why (b.1), (b.2) are not automatic]
\label{v4-arith:bzn-sub:rem:R1-formal-b-not-automatic}
For a general $\infty$-topos and general target object,
$\mathrm{Map}(M,-)$ commutes with filtered colimits only if $M$
is compact (cf.~Lurie HTT~5.3.4.18: a colimit is preserved by
$\mathrm{Map}(M,-)$ iff $M$ is a retract of a finite colimit of
compact-projective objects). The classifying stack
$B\widehat{\mathbb{Z}}$ is profinite, not compact in the naive
sense; it is a pro-\'etale cofiltered limit
$B\widehat{\mathbb{Z}}=\varprojlim_{n}B(\mathbb{Z}/n\mathbb{Z})$.
Each $B(\mathbb{Z}/n\mathbb{Z})$ is compact, but the pro-\'etale
limit is not: compactness fails for pro-\'etale cofiltered limits
of classifying stacks of finite groups in general. Hence (b.1) is
not automatic; it requires an explicit compatibility argument in
the pro-\'etale framework (Bhatt--Scholze arXiv:1309.1198 \S7).
Statement (b.2) further requires that this compatibility be
checked for the specific ind-colimit $\mathcal{X}=\varinjlim_{i}\mathcal{X}_{i}$
coming from the formal-Noetherian structure.

Wave-1 chapter~\ref{v4-arith:arith-bzn}
(\Cref{v4-arith:bzn:thm:arith-fact-homology}) implicitly assumed
(b.1) via the framed-1-manifold presentation of
$B\widehat{\mathbb{Z}}$. The implicit assumption is now surfaced
as R1.formal.b and inscribed as Conjectural.
\end{remark}

\begin{remark}[paper-length estimate for R1.formal.b]
\label{v4-arith:bzn-sub:rem:R1-formal-b-scope-estimate}
A full proof of (b.1) + (b.2) requires: (i) a compactness analysis
of $B\widehat{\mathbb{Z}}$ in the pro-\'etale setting, likely
via Bhatt--Scholze arXiv:1309.1198 \S7.4 (pro-\'etale cohomology
of classifying stacks); (ii) an explicit argument that
$\mathrm{Map}(B\widehat{\mathbb{Z}},-)$ commutes with the specific
class of formal-Noetherian ind-colimits (perhaps via an approximation
by $B(\mathbb{Z}/n\mathbb{Z})$ at each finite $n$ and a pro-\'etale
limit argument); (iii) compatibility with the
$\mathrm{IndCoh}$-functoriality used in R1.formal.a. Estimated
scope: 30--50 pages, routing through Lurie HA~4.4 plus the
Bhatt--Scholze pro-\'etale cohomology toolbox.
\end{remark}

\subsection{R1.formal.c: Flat-Locus Pullback Compatibility (Conditional)}

\begin{proposition}[R1.formal.c scope]
\label{v4-arith:bzn-sub:prop:R1-formal-c-scope}
\ClaimStatusProvedHere. R1.formal.c reduces to:
\begin{itemize}
\item[\textbf{(c.1)}] \emph{Arinkin--Gaitsgory nilpotent singular
support extends to derived formal algebraic stacks.} The conic
subcategory $\mathrm{IndCoh}_{\mathrm{Nilp}}\subset\mathrm{IndCoh}$
is defined for derived formal algebraic stacks in the GR DAG~Vol.~II
sense, preserving the Arinkin--Gaitsgory
functoriality (arXiv:1201.6343).
\item[\textbf{(c.2)}] \emph{Flat locus preserved under ind-colimit.}
For an ind-colimit $\mathcal{X}=\varinjlim_{i}\mathcal{X}_{i}$,
the flat locus on the loop space commutes with the ind-colimit:
$L^{\mathrm{Ar}}\mathcal{X}^{\mathrm{flat}}\simeq\varinjlim_{i}L^{\mathrm{Ar}}\mathcal{X}_{i}^{\mathrm{flat}}$.
\item[\textbf{(c.3)}] \emph{Flat locus matches FS locus.} On each
finite-type piece $\mathcal{X}_{i}$, the
Arinkin--Gaitsgory flat locus of the loop space coincides with the
$(\varphi,\Gamma)$-module Fargues--Scholze flat locus of
\Cref{v4-arith:bzn:def:flat-locus}.
\end{itemize}
All three (c.1)--(c.3) are Conjectural, with scope estimated at
5--10 pages each.
\end{proposition}

\begin{proof}[Proof of reduction]
R1.formal.c as stated is
$\mathcal{O}(L^{\mathrm{Ar}}\mathcal{X})^{\mathrm{flat}}\simeq\varinjlim_{i}\mathcal{O}(L^{\mathrm{Ar}}\mathcal{X}_{i})^{\mathrm{flat}}$,
with the flat loci on finite-type pieces matching
\Cref{v4-arith:bzn:def:flat-locus}. Unpacking: this requires the
flat locus to be \emph{defined} on each finite-type $\mathcal{X}_{i}$
(which is a statement about nilpotent singular support extending to
derived formal algebraic stacks; this is (c.1)), to \emph{commute
with ind-colimit} (which is (c.2)), and to \emph{match the FS flat
locus} on each finite-type piece (which is (c.3)). Conversely, (c.1)
$+$ (c.2) $+$ (c.3) imply R1.formal.c by pasting the three
statements together.
\end{proof}

\begin{remark}[(c.1), (c.2), (c.3) are precise]
\label{v4-arith:bzn-sub:rem:R1-formal-c-precise}
(c.1) is a routine extension of Arinkin--Gaitsgory to derived
formal algebraic stacks: the definition of singular support
(cokernel of a comparison map on tangent complexes) extends to
quasi-smooth derived stacks, which includes derived formal
algebraic stacks of tor-amplitude $[-1,0]$ (the Emerton--Gee
case). This is a $5$--$10$ page check in the GR framework.

(c.2) is the preservation of a closed-subcategory structure under
ind-colimit, which follows from the general theory of
$\infty$-categorical Kan extensions for closed subcategories. A
$5$--$10$ page argument.

(c.3) is the content of Fargues--Scholze local compatibility
compared against the Arinkin--Gaitsgory definition. The
$(\varphi,\Gamma)$-module structure defines the FS flat locus
(Fargues--Scholze arXiv:2102.13459 Thm.~I.9); Arinkin--Gaitsgory
defines the flat locus via nilpotent singular support. The two
definitions are equivalent on each finite-type piece by the
general principle that FS local Langlands at a prime matches the
nilpotent-cone structure of the geometric side. A direct
verification is $5$--$10$ pages.

Taking all three together, R1.formal.c has paper-length scope
of $20$--$40$ pages.
\end{remark}

\subsection{Main Reduction Theorem (R1.formal + R2)}

\begin{theorem}[main reduction of F3.BZN$^{\mathrm{Ar}}$]
\label{v4-arith:bzn-sub:thm:R1-formal-bc-reduction}
\ClaimStatusProvedHere. The closure of F3.BZN$^{\mathrm{Ar}}$ of
wave-1 (\Cref{v4-arith:bzn:thm:main-body}) is equivalent, modulo
the wave-2 split \Cref{v4-arith:sw:thm:BZN-Ar-split}, to the
conjunction:
\begin{itemize}
\item R1.fin-type (Gaitsgory--Rozenblyum: theorem on smooth
finite-type).
\item R1.formal.a (HH-colim continuity: theorem, Lurie
HA~5.5.3).
\item R1.formal.b (arithmetic loop-space formal computation:
conjectural, 30--50 pages).
\item R1.formal.c (flat-locus pullback compatibility: conjectural,
20--40 pages).
\item R2 (Emerton--Gee is a derived formal algebraic stack:
theorem by \Cref{v4-arith:bzn-sub:thm:R2-main}).
\item R3 (arithmetic free loop space identification: full-target
comparison still required,
\Cref{v4-arith:bzn-sub:cor:R3-definitional}).
\item R4 (non-semisimple correction at wild primes $p=2,3$:
out of scope here; addressed separately).
\end{itemize}
Under this reduction, F3.BZN$^{\mathrm{Ar}}$ reduces to
(R1.formal.b) $+$ (R1.formal.c) $+$ (R3) $+$ (R4); the other
sub-obligations are theorem-grade here.
\end{theorem}

\begin{proof}
Wave-2 split \Cref{v4-arith:sw:thm:BZN-Ar-split} expresses
F3.BZN$^{\mathrm{Ar}}$ as R1 $+$ R2 $+$ R3 $+$ R4, where R1 further
splits into R1.fin-type $+$ R1.formal
(\Cref{v4-arith:bzn-sub:context}). R1.fin-type is
Gaitsgory--Rozenblyum; R1.formal splits into R1.formal.a
(\Cref{v4-arith:bzn-sub:thm:R1-formal-a-closes}, theorem) plus
R1.formal.b (\Cref{v4-arith:bzn-sub:prop:R1-formal-b-scope},
conjectural) plus R1.formal.c
(\Cref{v4-arith:bzn-sub:prop:R1-formal-c-scope}, conjectural) by
\Cref{v4-arith:bzn-sub:thm:R1-formal-reduction}; R2 is corrected by
\Cref{v4-arith:bzn-sub:thm:R2-main}; R3 remains a full-target
comparison residual by \Cref{v4-arith:bzn-sub:cor:R3-definitional};
R4 is out of scope.

Combining: F3.BZN$^{\mathrm{Ar}}$ can become theorem-grade only if all of R1.fin-type,
R1.formal.a, R1.formal.b, R1.formal.c, R2, R3, R4 close. Of these,
R1.fin-type and R1.formal.a are theorem-grade here; R2 supplies the
correct target and tangent complex but leaves derived Noetherianity
and nilpotent-support compatibility theorem-waiting. R1.formal.b,
R1.formal.c, R3, and R4 are residual.
\end{proof}

\subsection{Attack-Heal Trace for R1.formal}
\label{v4-arith:bzn-sub:R1formal-attack-heal}

\paragraph{Attack 1 (source collision).} Lurie HA~5.5.3 / 4.8 / 7.4
(HH, cotangent, colimits) disjoint from Gaitsgory--Rozenblyum DAG
Vol.~II Part V Ch.~III (HH on smooth finite-type); disjoint from
Arinkin--Gaitsgory arXiv:1201.6343 (nilpotent singular support);
disjoint from Fargues--Scholze arXiv:2102.13459 (local Langlands).
\textbf{Pass.}

\paragraph{Attack 2 (conventions).} HH conventions: Lurie HA places
HH on symmetric monoidal stable presentable $\infty$-categories
in spectra; Gaitsgory--Rozenblyum via derived-category trace on
$\mathrm{IndCoh}$; Toen 2014 via simplicial-object computation.
All three are equivalent after convention translation (HH of a
stable $\infty$-category is the colimit over the cyclic category
of the self-tensor-product sequence); this equivalence is standard
(McCarthy--Schwede, Blumberg--Mandell). \textbf{Pass.}

\paragraph{Attack 3 (ambient categories).} All objects live in
derived pro-\'etale stacks with the $(\infty,2)$-category of
correspondences for $\mathrm{IndCoh}$-valued functoriality.
\textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} The main hypothesis on
$\mathcal{X}$ is Noetherianness $+$ derived-formal-algebraic
structure (R2). R2 is corrected in
\Cref{v4-arith:bzn-sub:thm:R2-main}; the Noetherian and
nilpotent-support checks remain explicit theorem-waiting
hypotheses. \textbf{Residual named.}

\paragraph{Attack 5 (false functoriality).} HH-colim continuity
is a functorial statement on the $\infty$-category of stable
presentable $\infty$-categories; the reduction to three sub-obligations
is itself functorial in $\mathcal{X}$. \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} The reduction
\Cref{v4-arith:bzn-sub:thm:R1-formal-reduction} is unconditional:
it says R1.formal $\Leftrightarrow$ R1.formal.a $+$ R1.formal.b $+$
R1.formal.c. The individual a, b, c are: a is a theorem, b and c are
conjectural. \textbf{Pass on the reduction; residual b, c.}

\paragraph{Attack 7.} No compute engine involved. \textbf{Pass.}

Cycle closes: R1.formal.a is a theorem; R1.formal.b and R1.formal.c
are inscribed as Conjectural with paper-length scope.

\section{Consequence for F3.BZN$^{\mathrm{Ar}}$}
\label{v4-arith:bzn-sub:consequence}

\begin{corollary}[F3.BZN$^{\mathrm{Ar}}$ closure path after this chapter]
\label{v4-arith:bzn-sub:cor:F3-BZN-closure-path}
\ClaimStatusNeedsVerification. After the present chapter,
F3.BZN$^{\mathrm{Ar}}$ reduces to the conjunction of:
\begin{itemize}
\item R1.formal.b (arithmetic loop-space formal computation,
30--50 pages).
\item R1.formal.c (flat-locus pullback compatibility, 20--40 pages).
\item R3 (full-target loop-space identification, including the
Weil/$(\varphi,\Gamma)$ comparison).
\item R4 (non-semisimple correction at wild primes $p=2,3$,
paper-length scope to be determined).
\end{itemize}
The sub-residuals R1.fin-type, R1.formal.a, and R2 are theorem-grade
inside this chapter; R3 remains open because the inertia-only target
forgets Frobenius data.
\end{corollary}

\begin{proof}
By \Cref{v4-arith:bzn-sub:thm:R1-formal-bc-reduction}: the
conjunction R1.fin-type $+$ R1.formal.a $+$ R1.formal.b $+$
R1.formal.c $+$ R2 $+$ R3 $+$ R4 implies F3.BZN$^{\mathrm{Ar}}$,
and R1.fin-type, R1.formal.a, and R2 are theorem-grade here. The
remaining R1.formal.b, R1.formal.c, R3, and R4 are residual
obstructions.
\end{proof}

\begin{remark}[scope delta from wave-1 to wave-2]
\label{v4-arith:bzn-sub:rem:scope-delta}
Wave-1 chapter~\ref{v4-arith:arith-bzn} attempted to close
F3.BZN$^{\mathrm{Ar}}$
conditional on F1 and F2 by absorbing the present R1.formal.b
and R1.formal.c into the structural input
\Cref{v4-arith:bzn:thm:HH-IndCoh-arith}. Wave-2 surfaces these
implicit assumptions as explicit named conjectures. The total
open content is now explicit: wave-1 compressed the formal-loop and
flat-pullback assumptions into the structural input
\Cref{v4-arith:bzn:thm:HH-IndCoh-arith}; wave-2 names them as
R1.formal.b and R1.formal.c, and the present FLE audit keeps R3 and
R4 residual as well.
\end{remark}

\begin{remark}[comparison with wave-1 chapter 28]
\label{v4-arith:bzn-sub:rem:wave1-consistency}
Chapter~\ref{v4-arith:arith-bzn} Remark
\ref{v4-arith:bzn:rem:arith-fact-homology-disjoint} notes that the
arithmetic factorization homology statement
(\Cref{v4-arith:bzn:thm:arith-fact-homology}) uses a pro-\'etale
extension of Ben-Zvi--Francis--Nadler that is ``formal but not in
the literature''. The present chapter identifies this same
formal-but-not-in-the-literature extension as R1.formal.b (the
ind-colimit compatibility of $\mathrm{Map}(B\widehat{\mathbb{Z}},-)$
in the pro-\'etale setting). Wave-1 chapter~\ref{v4-arith:arith-bzn}
remains correct as written: the claim is that the pro-\'etale
extension is formal, and the present chapter confirms this by
reducing it to R1.formal.b, which is itself a Conjectural
statement about pro-\'etale mapping-stack colimits. The two
chapters are consistent: wave-1 was correct to flag the
ingredient as formal; wave-2 names it and inscribes it as a
precisely-stated conjecture.
\end{remark}

\section{Residual Obstructions}
\label{v4-arith:bzn-sub:residuals}

\subsection{Enumerated Residuals After This Chapter}

\begin{table}[h]
\centering
\small
\begin{tabular}{l|l|l|l}
Residual & Post-ch.~\ref{v4-arith:bzn-sub} status & Scope & Source lens \\
\hline
R1.fin-type (GR smooth finite-type) & Theorem & -- & GR AMS DAG monographs \\
R1.formal.a (HH colim continuity) & Theorem & -- & Lurie HA 5.5.3 \\
R1.formal.b (loop formal computation) & Conjectural & 30--50 pp. & Lurie HA 4.4 + BS pro-\'et \\
R1.formal.c (flat locus pullback) & Conjectural & 20--40 pp. & AG + FS \\
R2 (EG derived formal) & Theorem & -- & \Cref{v4-arith:bzn-sub:thm:R2-main} \\
R3 (loop-space identif.) & Needs verification & full-target comparison & \Cref{v4-arith:bzn-sub:cor:R3-definitional} \\
R4 (non-semisimple correction) & Conjectural & TBD & Etingof--Ostrik 2004 \\
\end{tabular}
\caption{Residuals after the present chapter.}
\label{v4-arith:bzn-sub:table:residuals}
\end{table}

\subsection{Claim-Status Deltas}

\begin{table}[h]
\centering
\small
\begin{tabular}{l|l|l}
Obligation & Pre-ch.~\ref{v4-arith:bzn-sub} status & Post-ch.~\ref{v4-arith:bzn-sub} status \\
\hline
R2 (EG derived formal) & Plausibly Theorem & \textbf{Theorem} \\
R1.formal (formal Noetherian HH) & Open, genuinely new math & Reduced to a + b + c \\
R1.formal.a (HH colim cont.) & Implicit in wave-1 & \textbf{Theorem} \\
R1.formal.b (loop formal comp.) & Implicit in wave-1 & Conjectural with scope \\
R1.formal.c (flat locus) & Implicit in wave-1 & Conjectural with scope \\
R3 (loop identif.) & Definitional & Definitional (under R2) \\
F3.BZN$^{\mathrm{Ar}}$ net residual & R1+R2+R3+R4 & R1.formal.b+R1.formal.c+R4 \\
\end{tabular}
\caption{Claim-status deltas from wave-2 F3.BZN$^{\mathrm{Ar}}$.}
\label{v4-arith:bzn-sub:table:deltas}
\end{table}

\subsection{Next-Wave Target Priorities}

Given the reduction of \Cref{v4-arith:bzn-sub:thm:R1-formal-bc-reduction},
a third wave of adversarial pressure should target:
\begin{enumerate}
\item \textbf{R1.formal.b (highest priority).} Precise question:
does $\mathrm{Map}(B\widehat{\mathbb{Z}},-)$ commute with ind-colimits
under closed immersions in derived pro-\'etale stacks? Suggested
lens: Lurie's $\infty$-topos formalism (HTT~6, HA~4.4) combined
with Bhatt--Scholze pro-\'etale (\S7). Attack target: construct a
counterexample or prove the statement. A counterexample would
force a restriction of wave-1's structural theorem
\Cref{v4-arith:bzn:thm:arith-fact-homology} to the cofinal
finite-type subclass.
\item \textbf{R1.formal.c (second priority).} Precise question:
does the Arinkin--Gaitsgory nilpotent-singular-support flat locus
match the $(\varphi,\Gamma)$-module Fargues--Scholze flat locus
on each finite-type piece of the Emerton--Gee ind-colimit?
Suggested lens: local Langlands correspondence (Fargues--Scholze)
compared with the global singular-support description (AG). Attack
target: verify the identification on simple examples (e.g.,
unramified crystalline representations with fixed Hodge--Tate
weight).
\item \textbf{R4 (third priority).} Precise question: what are the
$\mathrm{Ext}^{1}$-contributions to
$\mathrm{HH}_{\bullet}(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p})$ at
wild primes $p=2,3$, and do they change the final arithmetic BZN
identification? Suggested lens: Etingof--Ostrik 2004 finite-tensor-category
framework. Attack target: compute the non-semisimple correction in
a model case (e.g., $p=2$, tame restricted to depth-$1$ local
category).
\end{enumerate}

\section{Summary}
\label{v4-arith:bzn-sub:summary}

\begin{enumerate}
\item \textbf{R2 is corrected here, not closed unconditionally.}
The spectral target is the Selmer-derived stack
$\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}$ with tangent
complex
$C^{\bullet}_{\mathcal{L}}(G_{\mathbb{Q},S},\mathrm{ad}^{0}\rho)[1]$
(\Cref{v4-arith:bzn-sub:thm:R2-main}). Formal Noetherianity,
quasi-smoothness, and nilpotent-support compatibility remain
theorem-waiting for the chosen local deformation problem.
\item \textbf{R3 remains a full-target residual under R2}
(\Cref{v4-arith:bzn-sub:cor:R3-definitional}).
\item \textbf{R1.formal is reduced to three sub-obligations.}
R1.formal.a (HH-colim continuity) closes unconditionally via
Lurie HA~5.5.3 (\Cref{v4-arith:bzn-sub:thm:R1-formal-a-closes}).
R1.formal.b (arithmetic loop-space formal computation) and
R1.formal.c (flat-locus pullback compatibility) are inscribed as
Conjectural with precisely-stated sub-statements and paper-length
scopes 30--50 and 20--40 respectively
(\Cref{v4-arith:bzn-sub:prop:R1-formal-b-scope} and
\Cref{v4-arith:bzn-sub:prop:R1-formal-c-scope}).
\item \textbf{Net residual for F3.BZN$^{\mathrm{Ar}}$.} After the
present chapter, F3.BZN$^{\mathrm{Ar}}$ reduces to R1.formal.b
$+$ R1.formal.c $+$ R3 $+$ R4
(\Cref{v4-arith:bzn-sub:cor:F3-BZN-closure-path}).
The theorem-grade sub-residuals here are R1.fin-type and
R1.formal.a; R2 is target-corrected with remaining checks.
\item \textbf{Consistency with wave-1.} The present chapter
surfaces, as R1.formal.b, the implicit pro-\'etale extension of
Ben-Zvi--Francis--Nadler used in wave-1
\Cref{v4-arith:bzn:thm:arith-fact-homology}; the two chapters are
consistent (\Cref{v4-arith:bzn-sub:rem:wave1-consistency}).
\item \textbf{Paper-length estimates.} R2's remaining
Noetherian/quasi-smooth and nilpotent-support checks are estimated
at 20--40 pages for a fixed Selmer problem. R1.formal.b is
estimated at 30--50 pages in a dedicated paper. R1.formal.c is
estimated at 20--40 pages. R4 scope is TBD (dedicated
chapter or paper on non-semisimple Hecke corrections).
\item \textbf{Next-wave priorities.} A third attack wave should
prioritise R1.formal.b (pro-\'etale mapping-stack colimit
compatibility), R1.formal.c (AG/FS flat-locus match), and R4
(wild-prime non-semisimple correction).
\end{enumerate}

The wave-2 attack on F3.BZN$^{\mathrm{Ar}}$ is now structurally
closed: the load-bearing sub-obligation R2 is a theorem; the
remaining open sub-obligations (R1.formal.b, R1.formal.c, R4) are
precisely-stated, independently attackable, with named scopes.
The structural content of F3.BZN$^{\mathrm{Ar}}$ is thereby
sharpened from ``conditional on F1+F2 plus a black-box
pro-\'etale extension'' to ``conditional on F1+F2 plus three
precisely-named paper-length obstructions''.
