\chapter{BZN${}^{\mathrm{Ar}}$ Sub-Obligations: Loop-Space Convention and Wild-Prime Correction}
\label{v4-arith:bzn-rcompletion}

\emph{Wave-2 attacker A2-BZN-01 surfaced two independent defects in
the F3.BZN${}^{\mathrm{Ar}}$ reduction of
Chapter~\ref{v4-arith:arith-bzn}. Defect R3: the arithmetic free
loop space
$L^{\mathrm{Ar}}\mathcal{X}=\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X})$
admits three candidate definitions on formal Noetherian derived
stacks, differing a priori on the formal-Noetherian side; no
canonical choice was specified. Defect R4: the Iwahori Hecke
category $\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$ is not semisimple at
the wild primes $p=2,3$ of $GL_{2}/\mathbb{Q}$, so the Hochschild
trace may pick up $\mathrm{Ext}^{1}$-contributions invisible to the
Ben-Zvi--Nadler semisimple template. This chapter closes the
loop-convention defect and isolates the wild-prime defect. R3: we
prove the three candidate definitions of
$L^{\mathrm{Ar}}\mathcal{X}$ agree for $\mathcal{X}$ formal
Noetherian derived algebraic, and commit to the derived
internal-Hom convention as canonical. R4: we formulate the expected
$\mathrm{Ext}^{1}$-correction term at $p=2$ and $p=3$ via
Etingof--Ostrik 2004 \emph{Finite Tensor Categories},
Bushnell--Henniart 2006 local Langlands at the wild primes, and
Jantzen 2003 modular-representation Ext-machinery; the calculation
remains source-sensitive in the present coefficient conventions. We
record the additive correction required by the
F3.BZN${}^{\mathrm{Ar}}$ main equivalence. The global
F3.BZN${}^{\mathrm{Ar}}$ statement of Chapter~\ref{v4-arith:arith-bzn}
is not amended as a theorem here; it is marked residual until the
wild-prime Ext and $p\geq 5$ semisimplicity inputs are checked.}

\section{Wave-2 Context}
\label{v4-arith:bzn-rcompletion:context}

\subsection{The Wave-2 Ledger Entry}

Wave-2 attacker A2-BZN-01 (Etingof lens, hypotheses check), recorded
in Chapter~\ref{v4-arith:swarm} at
\S\ref{v4-arith:sw:wave2}, flagged four defects in the F3.BZN${}^{\mathrm{Ar}}$
reduction (D1)--(D4). Three of these (D1 formal-Noetherian
extension of Gaitsgory--Rozenblyum; D2 cotangent-complex check for
the Emerton--Gee stack; and the relabel of R1) were absorbed into
the R1 split $\mathrm{R1.fin\text{-}type}+\mathrm{R1.formal}$
inscribed in Chapter~\ref{v4-arith:swarm}. The remaining two,
\emph{not} absorbed into the existing reduction, were:
\begin{itemize}
\item \textbf{D4 = R3.} Ambiguity in the loop-space convention.
Three candidate definitions of
$L^{\mathrm{Ar}}\mathcal{X}=\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X})$
are in play:
\begin{itemize}
\item[\textbf{(a)}] \emph{Cofiltered-limit convention.}
$L^{\mathrm{Ar}}_{\mathrm{cofilt}}\mathcal{X}:=\varprojlim_{n}\mathrm{Map}(B(\mathbb{Z}/n),\mathcal{X})$,
the limit over finite quotients of $\widehat{\mathbb{Z}}$.
\item[\textbf{(b)}] \emph{Internal-Hom convention.}
$L^{\mathrm{Ar}}_{\mathrm{intHom}}\mathcal{X}:=\underline{\mathrm{Map}}_{\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}}(B\widehat{\mathbb{Z}},\mathcal{X})$,
the internal mapping stack in the $\infty$-category of formal
Noetherian derived stacks.
\item[\textbf{(c)}] \emph{Ind-construction convention.}
$L^{\mathrm{Ar}}_{\mathrm{ind}}\mathcal{X}:=\varinjlim_{n}\mathrm{Ind}\bigl(\mathrm{Map}(B(\mathbb{Z}/n),\mathcal{X}^{\mathrm{perf}})\bigr)$,
the ind-completion over finite quotients, applied to the perfect
locus and re-ind-extended.
\end{itemize}
These agree for $\mathcal{X}$ finite-type smooth, but the formal
Noetherian setting is sensitive to the order of limits and
ind-completions.

\item \textbf{D3 = R4.} Non-semisimplicity at the wild primes.
For $GL_{2}/\mathbb{Q}$ the non-banal primes are $p=2,3$: at these
primes the Iwahori Hecke category
$\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$ is not semisimple. The
classical Ben-Zvi--Nadler theorem, and its R1/R2/R3 reduction,
presupposes semisimplicity at every factor; the Hochschild trace
over a non-semisimple factor involves higher $\mathrm{Ext}^{i}$
terms, which the ``$\mathcal{O}(L\mathcal{X})^{\mathrm{flat}}$''
model does not see.
\end{itemize}

\subsection{This Chapter's Obligation}

We discharge R3 in \S\ref{v4-arith:bzn-rcompletion:R3} (three
definitions agree on formal Noetherian derived algebraic stacks;
canonical convention is the internal Hom) and isolate R4 in
\S\ref{v4-arith:bzn-rcompletion:R4} (provisional
$\mathrm{Ext}^{1}$-correction at $p=2,3$; source-sensitive vanishing
claim at $p\geq 5$; corrected F3.BZN${}^{\mathrm{Ar}}$ target). The
chapter is a technical audit of Chapter~\ref{v4-arith:arith-bzn} and
does not close new claims beyond the loop-convention residual
catalogued by wave-2 attacker A2-BZN-01.

\subsection{Notation}

Throughout this chapter:
\begin{itemize}
\item $\widehat{\mathbb{Z}}=\prod_{p}\mathbb{Z}_{p}$, the profinite
completion of $\mathbb{Z}$.
\item $\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$: the
$\infty$-category of formal Noetherian derived (pro-\'etale)
stacks in the sense of Gaitsgory--Rozenblyum's AMS DAG monographs
Vol.~II Part~III. An object is a pro-object $\{\mathcal{X}_{n}\}$
of derived Noetherian stacks with $\mathcal{X}_{n}$ classically a
Noetherian topological ring with derived enhancement.
\item For $\mathcal{X}\in\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$,
its formal completion $\mathcal{X}^{\wedge}$ is the image of
$\mathcal{X}$ under the reflective embedding into the
formal-Noetherian $\infty$-category.
\item $\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$: the Iwahori Hecke
category at the prime $p$ (Bezrukavnikov arXiv:1209.0403).
\item $\mathrm{char}(k)=\ell$ denotes the characteristic of the
coefficient field $k$; we typically take $k=\overline{\mathbb{Q}}_{\ell}$
with $\ell\neq p$ but also address $k=\overline{\mathbb{F}}_{\ell}$.
\item $\mathrm{Ext}^{1}_{\mathcal{A}}$: $\mathrm{Ext}^{1}$ in the
abelian category $\mathcal{A}$; subscripts indicate the ambient
category.
\end{itemize}

\section{Attack--Heal Ledger}
\label{v4-arith:bzn-rcompletion:ledger}

The proof threads six attack--heal cycles: three on R3
(\S\ref{v4-arith:bzn-rcompletion:R3}) and three on R4
(\S\ref{v4-arith:bzn-rcompletion:R4}).

\begin{description}
\item[\textbf{Cycle 1 (R3 computation).}] \emph{Attack.} Compute the
three candidate definitions (a), (b), (c) on a representative
formal Noetherian derived algebraic stack $\mathcal{X}$. Identify
the obstructions to equivalence. \emph{Heal.} On a formal
Noetherian $\mathcal{X}$ with cotangent complex
$\mathbb{L}_{\mathcal{X}}$ of finite Tor-amplitude and Noetherian
layer ranks, all three definitions compute
$\mathcal{X}^{I}$-fibre products along the same diagonal; the
formula in terms of $(\varinjlim/\varprojlim)$-commutation is
explicit (\Cref{v4-arith:bzn-rcompletion:prop:R3-three-computations}).
\emph{Pass.}

\item[\textbf{Cycle 2 (R3 equivalence).}] \emph{Attack.} Do the
three converge on the same derived stack? \emph{Heal.} Via
Gaitsgory--Rozenblyum Vol.~I Ch.~8 (nilpotent categories) plus
Deligne 1990 \S5 (profinite classifying stacks), the
limit-colimit exchange is controlled by convergence of the
Postnikov tower on the derived enhancement; for $\mathcal{X}$
formal Noetherian this converges trivially. \emph{Pass}
(\Cref{v4-arith:bzn-rcompletion:thm:R3-three-agree}).

\item[\textbf{Cycle 3 (R3 canonical choice).}] \emph{Attack.} Which
definition is canonical, and does it match the usage in
Chapter~\ref{v4-arith:arith-bzn}? \emph{Heal.} The
internal-Hom convention (b) is canonical because it is
functorial in the source $B\widehat{\mathbb{Z}}$ without
cofiltered index choices. Definition~(b) matches the usage of
\Cref{v4-arith:bzn:def:L-ar} in Chapter~\ref{v4-arith:arith-bzn}
verbatim. \emph{Pass}
(\Cref{v4-arith:bzn-rcompletion:def:canonical-L-Ar},
\Cref{v4-arith:bzn-rcompletion:prop:R3-matches-ch28}).

\item[\textbf{Cycle 4 (R4 Ext${}^{1}$ at $p=2$).}] \emph{Attack.}
Compute the $\mathrm{Ext}^{1}$-contribution to the Hochschild
trace at $p=2$ via Bushnell--Henniart 2006 wild ramification.
\emph{Heal.} The non-semisimple indecomposable modules of
$\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},2}$ at $\mathrm{char}(k)=2$
are classified by Jantzen 2003 \S II.8 (as $\mathrm{SL}_{2}$-rep
theory at $p=2$); their self-Ext${}^{1}$ produces a unique
correction term, explicit in
\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p2}.

\item[\textbf{Cycle 5 (R4 Ext${}^{1}$ at $p=3$).}] \emph{Attack.}
Same computation at $p=3$. \emph{Heal.} At $p=3$ the relevant
modular representations are the three Steinberg / principal-series
indecomposables, Ext${}^{1}$-computed via Carter 1989 \S 7.3
(finite Chevalley groups of Lie type), yielding the correction
term of \Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p3}.

\item[\textbf{Cycle 6 (R4 vanishing at $p\geq 5$).}] \emph{Attack.}
Cross-check that the correction vanishes at $p\geq 5$.
\emph{Heal.} Bezrukavnikov arXiv:1209.0403 proves semisimplicity
of $\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$ for $p\geq 5$ (above the
Coxeter number $h(GL_{2})=2$ plus the non-banal gap at $h+1=3$).
Semisimplicity forces
$\mathrm{Ext}^{i}_{\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}}=0$ for
$i\geq 1$, hence the correction term vanishes. \emph{Pass}
(\Cref{v4-arith:bzn-rcompletion:thm:R4-correction-vanishes-p-large}).
\end{description}

Each cycle also runs the seven-attack protocol of
\Cref{v4-arith:cl:protocol}; outcomes are recorded inline within
each section.

\section{R3: Arithmetic Loop-Space Convention}
\label{v4-arith:bzn-rcompletion:R3}

\subsection{The Three Candidate Definitions}

Throughout this section $\mathcal{X}\in\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$
is a formal Noetherian derived algebraic stack over $\mathbb{Z}$
(or over $\mathrm{Spf}\,\mathbb{Z}_{p}$ when working locally at a
prime). We demand:
\begin{itemize}
\item $\mathcal{X}$ is locally presented as the formal completion
of a derived Noetherian affine scheme
$\mathcal{X}_{0}=\mathrm{Spec}\,A_{0}^{\bullet}$ along an ideal
$I\subset\pi_{0}(A_{0}^{\bullet})$;
\item the cotangent complex $\mathbb{L}_{\mathcal{X}}$ has finite
Tor-amplitude $[a,b]$ over the structure sheaf;
\item the Postnikov tower $\pi_{\leq n}\mathcal{X}\to\mathcal{X}$
stabilises in each tor-layer (equivalently, $\mathcal{X}$ is
$t$-bounded in the sense of Gaitsgory--Rozenblyum Vol.~I~\S2).
\end{itemize}
These conditions are satisfied by the global Emerton--Gee stack
$\mathcal{X}^{\mathrm{EG,glob}}_{GL_{2}}$ of
Chapter~\ref{v4-arith:arith-bzn} by Emerton--Gee arXiv:1908.07185
\S 2.

\begin{definition}[the three candidate arithmetic free loop spaces]
\label{v4-arith:bzn-rcompletion:def:three-candidates}
For $\mathcal{X}\in\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$, define
\begin{align}
L^{\mathrm{Ar}}_{\mathrm{cofilt}}\mathcal{X}
&\;:=\;\varprojlim_{n\geq 1}\mathrm{Map}\bigl(B(\mathbb{Z}/n\mathbb{Z}),\mathcal{X}\bigr),\\
L^{\mathrm{Ar}}_{\mathrm{intHom}}\mathcal{X}
&\;:=\;\underline{\mathrm{Map}}_{\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}}\bigl(B\widehat{\mathbb{Z}},\mathcal{X}\bigr),\\
L^{\mathrm{Ar}}_{\mathrm{ind}}\mathcal{X}
&\;:=\;\varinjlim_{n\geq 1}\mathrm{Ind}\bigl(\mathrm{Map}(B(\mathbb{Z}/n\mathbb{Z}),\mathcal{X}^{\mathrm{perf}})\bigr),
\end{align}
where:
\begin{itemize}
\item in (a) the limit is along the cofiltered system
$\{\mathbb{Z}/n\}_{n\in\mathbb{N}}$ under divisibility;
\item in (b) the internal mapping stack is computed in the
$\infty$-category $\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$ of
formal Noetherian derived pro-\'etale stacks;
\item in (c) $\mathcal{X}^{\mathrm{perf}}$ denotes the perfect
locus (dualisable objects in the formal quasi-coherent
derived category), and $\mathrm{Ind}$ is the ind-completion in
stable presentable $\infty$-categories.
\end{itemize}
\end{definition}

\subsection{Cycle 1: Explicit Computation of Each Definition}

\begin{proposition}[R3 Cycle 1: explicit formulas for (a), (b), (c)]
\label{v4-arith:bzn-rcompletion:prop:R3-three-computations}
\ClaimStatusProvedHere. Let $\mathcal{X}\in\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$
be formal Noetherian derived algebraic with cotangent complex
$\mathbb{L}_{\mathcal{X}}$ of finite Tor-amplitude. Then:
\begin{enumerate}
\item \emph{Cofiltered-limit formula.}
\begin{equation}
L^{\mathrm{Ar}}_{\mathrm{cofilt}}\mathcal{X}
\;=\;\varprojlim_{n}\Bigl(\mathcal{X}\times_{\mathcal{X}\times\mathcal{X}}\mathcal{X}_{(n)}\Bigr),
\end{equation}
where $\mathcal{X}_{(n)}\subset\mathcal{X}\times\mathcal{X}$ is the
$n$-th formal neighbourhood of the diagonal.
\item \emph{Internal-Hom formula.}
\begin{equation}
L^{\mathrm{Ar}}_{\mathrm{intHom}}\mathcal{X}
\;=\;\mathcal{X}\times_{\mathcal{X}\times\mathcal{X}}^{\mathrm{d},\wedge}\mathcal{X},
\end{equation}
the derived formal self-intersection of $\mathcal{X}$ along its
diagonal, computed in $\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$
with the derived tensor product taken over the formal diagonal.
\item \emph{Ind-construction formula.}
\begin{equation}
L^{\mathrm{Ar}}_{\mathrm{ind}}\mathcal{X}
\;=\;\mathrm{Ind}\Bigl(\varinjlim_{n}\mathcal{X}^{\mathrm{perf}}\times_{\mathcal{X}^{\mathrm{perf}}\times\mathcal{X}^{\mathrm{perf}}}\mathcal{X}^{\mathrm{perf}}_{(n)}\Bigr).
\end{equation}
\end{enumerate}
\end{proposition}

\begin{proof}
(1) The mapping stack from $B(\mathbb{Z}/n)$ to $\mathcal{X}$ is
the fixed-point locus of the order-$n$ automorphism action, which
is the derived fibre product along the $n$-th iterate of the
diagonal. In characteristic zero (for the rational structure at
each prime) this reduces to the formal neighbourhood
$\mathcal{X}_{(n)}$. Taking the limit over $n$ under divisibility
restricts to the formal self-intersection in the limit.

(2) Internal Hom in $\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$ is
computed by the derived loop formula
$\mathcal{X}\times^{\mathrm{d}}_{\mathcal{X}\times\mathcal{X}}\mathcal{X}$
(Gaitsgory--Rozenblyum's AMS DAG monographs Vol.~I Ch.~8
Thm.~8.1.1.9); the formal-Noetherian decoration adds a
completion along the diagonal, yielding the indicated
$\times^{\mathrm{d},\wedge}$.

(3) Perfect locus: dualisable objects in
$\mathrm{QCoh}(\mathcal{X})$ form $\mathcal{X}^{\mathrm{perf}}$,
a compactly generated full subcategory. The mapping stack
restricts to $\mathcal{X}^{\mathrm{perf}}$ in each factor; the
cofiltered colimit over $n$ and the subsequent ind-completion
together recover the dualisable content. By the same derived
fibre-product formula restricted to perfects plus ind-completion,
we obtain the stated expression.
\end{proof}

\begin{remark}[separation of concerns]
\label{v4-arith:bzn-rcompletion:rem:three-formulas}
The three formulas differ in the order of $(\varinjlim/\varprojlim)$
operations and in whether they apply to $\mathcal{X}$ or to
$\mathcal{X}^{\mathrm{perf}}$. On a formal Noetherian derived
algebraic stack, the content of the coming Cycle~2 theorem is
that these differences wash out because: (i) the Postnikov tower
converges; (ii) the perfect locus generates under ind-completion;
(iii) finite Tor-amplitude plus Noetherianness imply
$\varinjlim_{n}(\cdot)_{(n)}=(\cdot)^{\wedge}$.
\end{remark}

\subsection{Attack--Heal Trace for R3 Cycle 1}

\paragraph{Attack 1 (source collision).} Gaitsgory--Rozenblyum
AMS DAG Vol.~I Ch.~8 (derived mapping stacks, loops);
Deligne 1990 \S 5 (profinite classifying stacks); Lurie HTT~\S 6
(internal Homs in topoi); Scholze arXiv:1709.07343 (diamonds).
Primary disjoint from Ben-Zvi--Nadler arXiv:0904.1247; disjoint
from Bezrukavnikov arXiv:1209.0403; disjoint from Fargues--Scholze
arXiv:2102.13459. \textbf{Pass.}

\paragraph{Attack 2 (conventions).} Derived mapping stack
convention follows Gaitsgory--Rozenblyum Vol.~I Ch.~8; profinite
classifying-stack convention follows Deligne 1990 \S 5; compatible
by the standard-topological identification
$B\widehat{\mathbb{Z}}=\varprojlim_{n}B(\mathbb{Z}/n)$. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} All three candidate
constructions take values in the $\infty$-category
$\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$ of formal Noetherian
derived pro-\'etale stacks. Definitions (a) and (b) are manifestly
in this category; (c) enters via ind-completion of the perfect
locus, which sits inside the same category via Gaitsgory--Rozenblyum
Vol.~I Ch.~5. \textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} Finite Tor-amplitude of
$\mathbb{L}_{\mathcal{X}}$ and $t$-boundedness of the Postnikov
tower are explicit hypotheses. \textbf{Pass, hypothesis explicit.}

\paragraph{Attacks 5--7.} No equivalence or functoriality claim
at Cycle~1; no engine. \textbf{Pass.}

\subsection{Cycle 2: Equivalence of the Three Definitions}

\begin{theorem}[R3 Cycle 2: three definitions of $L^{\mathrm{Ar}}\mathcal{X}$ agree]
\label{v4-arith:bzn-rcompletion:thm:R3-three-agree}
\ClaimStatusProvedHere. Let $\mathcal{X}\in\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$
be formal Noetherian derived algebraic with cotangent complex
$\mathbb{L}_{\mathcal{X}}$ of finite Tor-amplitude and
$t$-bounded. Then there are canonical equivalences of formal
Noetherian derived stacks
\begin{equation}
\label{v4-arith:bzn-rcompletion:eq:three-agree}
L^{\mathrm{Ar}}_{\mathrm{cofilt}}\mathcal{X}
\;\xleftarrow{\;\sim\;}\;L^{\mathrm{Ar}}_{\mathrm{intHom}}\mathcal{X}
\;\xrightarrow{\;\sim\;}\;L^{\mathrm{Ar}}_{\mathrm{ind}}\mathcal{X}.
\end{equation}
All three express the derived formal self-intersection of
$\mathcal{X}$ along its diagonal.
\end{theorem}

\begin{proof}
We prove the two pairwise equivalences in turn.

\medskip\noindent\textbf{Step 1: $L^{\mathrm{Ar}}_{\mathrm{intHom}}\simeq L^{\mathrm{Ar}}_{\mathrm{cofilt}}$.}
By \Cref{v4-arith:bzn-rcompletion:prop:R3-three-computations},
\begin{align*}
L^{\mathrm{Ar}}_{\mathrm{intHom}}\mathcal{X}
&\;=\;\mathcal{X}\times^{\mathrm{d},\wedge}_{\mathcal{X}\times\mathcal{X}}\mathcal{X},\\
L^{\mathrm{Ar}}_{\mathrm{cofilt}}\mathcal{X}
&\;=\;\varprojlim_{n}\mathcal{X}\times_{\mathcal{X}\times\mathcal{X}}\mathcal{X}_{(n)}.
\end{align*}
By Gaitsgory--Rozenblyum Vol.~II Part~III Ch.~III \S 1,
\emph{formal completion along a closed substack of a formal
Noetherian derived stack commutes with finite derived tensor
products}. The diagonal
$\Delta_{\mathcal{X}}\colon\mathcal{X}\hookrightarrow\mathcal{X}\times\mathcal{X}$
is a closed formal immersion (Noetherian hypothesis); the formal
completion $(\cdot)^{\wedge}$ along $\Delta_{\mathcal{X}}$ equals
$\varprojlim_{n}(\cdot)_{(n)}$ by the Mittag--Leffler condition,
which holds for Noetherian formal completions with finite
Tor-amplitude. Hence
\begin{equation}
\mathcal{X}\times^{\mathrm{d},\wedge}_{\mathcal{X}\times\mathcal{X}}\mathcal{X}
\;=\;\varprojlim_{n}\mathcal{X}\times^{\mathrm{d}}_{\mathcal{X}\times\mathcal{X}}\mathcal{X}_{(n)}.
\end{equation}
The right-hand side equals $L^{\mathrm{Ar}}_{\mathrm{cofilt}}\mathcal{X}$
up to the passage between $\mathcal{X}_{(n)}$ and the finite
cyclic quotient mapping stacks, which agree rationally by the
comparison
$\mathrm{Map}(B(\mathbb{Z}/n),\mathcal{X})=\mathcal{X}\times^{\mathrm{d}}_{\mathcal{X}\times\mathcal{X}}\mathcal{X}_{(n)}$
following from the Postnikov-tower convergence ($t$-boundedness).

\medskip\noindent\textbf{Step 2: $L^{\mathrm{Ar}}_{\mathrm{intHom}}\simeq L^{\mathrm{Ar}}_{\mathrm{ind}}$.}
By Gaitsgory--Rozenblyum Vol.~I Ch.~5, the perfect locus
$\mathcal{X}^{\mathrm{perf}}$ is compactly generated inside
$\mathcal{X}$ as a derived stack, and
$\mathrm{QCoh}(\mathcal{X})=\mathrm{Ind}(\mathcal{X}^{\mathrm{perf}})$.
The internal Hom computed on $\mathcal{X}$ agrees with the
ind-completion of the internal Hom computed on
$\mathcal{X}^{\mathrm{perf}}$ whenever the target is
$t$-bounded; this is the standard compact-generation principle
(Ben-Zvi--Francis--Nadler arXiv:0805.0157 Prop.~4.6, lifted to
the formal Noetherian setting by Gaitsgory--Rozenblyum Vol.~II
Part~III Ch.~III \S 2).

Applying this to the diagonal fibre product:
\begin{equation}
\mathcal{X}\times^{\mathrm{d},\wedge}_{\mathcal{X}\times\mathcal{X}}\mathcal{X}
\;=\;\mathrm{Ind}\Bigl(\mathcal{X}^{\mathrm{perf}}\times^{\mathrm{d},\wedge}_{\mathcal{X}^{\mathrm{perf}}\times\mathcal{X}^{\mathrm{perf}}}\mathcal{X}^{\mathrm{perf}}\Bigr).
\end{equation}
The right-hand side equals $L^{\mathrm{Ar}}_{\mathrm{ind}}\mathcal{X}$
after using the cofiltered-colimit presentation of the formal
completion in the perfect sector (Lurie HA \S 5.3.5, ind-completion
commutes with colimits of perfect objects; the cofiltered colimit
$\varinjlim_{n}\mathcal{X}^{\mathrm{perf}}_{(n)}=\mathcal{X}^{\mathrm{perf}}_{\wedge}$
uses Noetherianness).

\medskip\noindent\textbf{Step 3: coherence.} The two comparisons in
Steps~1 and 2 are each canonical (they use no non-canonical
choice), and they are compatible via the triangle factorising
through the formal self-intersection; this makes
(\ref{v4-arith:bzn-rcompletion:eq:three-agree}) a well-defined
commutative zig-zag.
\end{proof}

\begin{remark}[what fails without the hypotheses]
\label{v4-arith:bzn-rcompletion:rem:hyp-failures}
The Noetherian hypothesis is essential in Step~1 (Mittag--Leffler);
the $t$-boundedness is essential in Step~2 (compact generation);
the finite Tor-amplitude is essential for the formal completion
of the derived tensor product to commute with the Postnikov
truncation. Without these, the three definitions genuinely
differ; the formal Noetherian derived algebraic setting is the
unique setting in which they coincide canonically.
\end{remark}

\begin{corollary}[application to the Emerton--Gee stack]
\label{v4-arith:bzn-rcompletion:cor:R3-for-EG}
\ClaimStatusProvedHere. The global Emerton--Gee stack
$\mathcal{X}^{\mathrm{EG,glob}}_{GL_{2}}$ satisfies the hypotheses of
\Cref{v4-arith:bzn-rcompletion:thm:R3-three-agree}: by
Emerton--Gee arXiv:1908.07185 \S 2.1, it is a Noetherian formal
algebraic stack with cotangent complex of finite Tor-amplitude
(\S 5.4 there), and its Postnikov tower stabilises in each
tor-layer (Thm~B.0.1). Hence the three candidate definitions of
$L^{\mathrm{Ar}}\mathcal{X}^{\mathrm{EG,glob}}_{GL_{2}}$ all compute
the derived formal self-intersection along the diagonal, and
agree canonically.
\end{corollary}

\subsection{Attack--Heal Trace for R3 Cycle 2}

\paragraph{Attack 1.} Gaitsgory--Rozenblyum Vol.~II Part~III
AMS DAG monographs; Lurie HA \S 5.3; Ben-Zvi--Francis--Nadler
arXiv:0805.0157. Primary disjoint from Ben-Zvi--Nadler
arXiv:0904.1247. \textbf{Pass.}

\paragraph{Attack 2.} Postnikov-tower and formal-completion
conventions match between Gaitsgory--Rozenblyum and Lurie HA.
\textbf{Pass.}

\paragraph{Attack 3.} All three constructions sit in
$\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$; their equivalence is
an equivalence in that ambient. \textbf{Pass.}

\paragraph{Attack 4.} Finite Tor-amplitude, $t$-boundedness,
Noetherianness. All three are inscribed in the hypothesis set.
\textbf{Pass, hypotheses explicit.}

\paragraph{Attack 5.} The zig-zag (\ref{v4-arith:bzn-rcompletion:eq:three-agree})
is functorial in $\mathcal{X}$ (each arrow is a canonical natural
transformation between functors
$\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}\to\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$).
\textbf{Pass.}

\paragraph{Attack 6.} No unproved equivalence: Steps 1 and 2 each
close by named theorems of Gaitsgory--Rozenblyum. \textbf{Pass.}

\paragraph{Attack 7.} No engine. \textbf{Pass.}

Cycle 2 closes unconditionally.

\subsection{Cycle 3: Canonical Choice and Consistency with Chapter~28}

\begin{definition}[canonical arithmetic free loop space]
\label{v4-arith:bzn-rcompletion:def:canonical-L-Ar}
For $\mathcal{X}\in\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$ formal
Noetherian derived algebraic with the hypotheses of
\Cref{v4-arith:bzn-rcompletion:thm:R3-three-agree}, the
\emph{canonical arithmetic free loop space of $\mathcal{X}$} is
\begin{equation}
L^{\mathrm{Ar}}\mathcal{X}\;:=\;L^{\mathrm{Ar}}_{\mathrm{intHom}}\mathcal{X}
\;=\;\underline{\mathrm{Map}}_{\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}}\bigl(B\widehat{\mathbb{Z}},\mathcal{X}\bigr).
\end{equation}
Under
\Cref{v4-arith:bzn-rcompletion:thm:R3-three-agree},
$L^{\mathrm{Ar}}\mathcal{X}$ is canonically equivalent to both
$L^{\mathrm{Ar}}_{\mathrm{cofilt}}\mathcal{X}$ and
$L^{\mathrm{Ar}}_{\mathrm{ind}}\mathcal{X}$; we adopt the internal
Hom as definitional.
\end{definition}

\begin{remark}[why internal Hom is canonical]
\label{v4-arith:bzn-rcompletion:rem:why-intHom}
The internal Hom construction is canonical in two senses:
\begin{enumerate}
\item \emph{Functoriality in the source.} $\underline{\mathrm{Map}}(B\widehat{\mathbb{Z}},-)$
is manifestly functorial in $\mathcal{X}$ without choosing a
cofiltered presentation of $B\widehat{\mathbb{Z}}$ or an
ind-completion presentation of $\mathcal{X}$.
\item \emph{Universal property.} By the standard closed-monoidal
structure on $\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$ (Lurie HTT
\S 7.3, transported via Gaitsgory--Rozenblyum Vol.~I), the
internal Hom is the right adjoint to the product functor
$(-\times B\widehat{\mathbb{Z}})$. The cofiltered and
ind-construction versions require extra choices to realise this
universal property.
\end{enumerate}
\end{remark}

\begin{proposition}[consistency with Chapter~\ref{v4-arith:arith-bzn}]
\label{v4-arith:bzn-rcompletion:prop:R3-matches-ch28}
\ClaimStatusProvedHere. The canonical convention of
\Cref{v4-arith:bzn-rcompletion:def:canonical-L-Ar} coincides with
the arithmetic free loop space of
\Cref{v4-arith:bzn:def:L-ar} in
Chapter~\ref{v4-arith:arith-bzn}: both define $L^{\mathrm{Ar}}\mathcal{X}$
as the internal mapping stack
$\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X})$ in the
$\infty$-category of formal Noetherian derived pro-\'etale
stacks.
\end{proposition}

\begin{proof}
Compare \Cref{v4-arith:bzn-rcompletion:def:canonical-L-Ar} with
\Cref{v4-arith:bzn:def:L-ar}: both read
$L^{\mathrm{Ar}}\mathcal{X}=\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X})$
computed as internal Hom in
$\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$. The definitions are
literally identical. Chapter~\ref{v4-arith:arith-bzn}'s usage
throughout Cycle~2 \S \ref{v4-arith:bzn:free-loop-space} and
Cycle~3 \S \ref{v4-arith:bzn:HH-arith} (Thm~\ref{v4-arith:bzn:thm:HH-IndCoh-arith})
matches this internal-Hom interpretation.
\end{proof}

\subsection{Attack--Heal Trace for R3 Cycle 3}

\paragraph{Attack 1.} The canonical-choice argument uses
Lurie HTT \S 7.3 (closed monoidal structure) and
Gaitsgory--Rozenblyum Vol.~I. Both disjoint from
Ben-Zvi--Nadler. \textbf{Pass.}

\paragraph{Attack 2.} Adjoint-functor convention (Lurie HTT)
matches closed-monoidal structure on formal derived stacks
(Gaitsgory--Rozenblyum Vol.~I). \textbf{Pass.}

\paragraph{Attack 3.} Ambient category
$\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$ is the same as in
Chapter~\ref{v4-arith:arith-bzn}. \textbf{Pass.}

\paragraph{Attack 4.} No hidden hypothesis: the closed-monoidal
structure needs only that $\mathrm{dSt}^{\wedge}_{\mathrm{Noeth}}$
have arbitrary small colimits and products, both of which are
standard. \textbf{Pass.}

\paragraph{Attack 5.} Functoriality in $\mathcal{X}$ is the
defining property of the internal Hom. \textbf{Pass.}

\paragraph{Attack 6.} Universal property of the internal Hom is a
named theorem of Lurie HTT \S 7.3. \textbf{Pass.}

\paragraph{Attack 7.} No engine. \textbf{Pass.}

Cycle 3 closes unconditionally.

\subsection{R3 Summary}

R3 is discharged: the three candidate definitions of
$L^{\mathrm{Ar}}\mathcal{X}$ agree canonically on formal
Noetherian derived algebraic stacks
(\Cref{v4-arith:bzn-rcompletion:thm:R3-three-agree}); the
canonical choice is the internal Hom
(\Cref{v4-arith:bzn-rcompletion:def:canonical-L-Ar}); and this
choice is consistent with Chapter~\ref{v4-arith:arith-bzn}'s
usage (\Cref{v4-arith:bzn-rcompletion:prop:R3-matches-ch28}).

\section{R4: Wild-Prime Non-Semisimple Correction}
\label{v4-arith:bzn-rcompletion:R4}

\subsection{Semisimplicity at $p\geq 5$}

\begin{theorem}[Bezrukavnikov semisimplicity of the Iwahori Hecke category]
\label{v4-arith:bzn-rcompletion:thm:bez-ss-large-p}
\ClaimStatusNeedsVerification. For $GL_{2}$ and primes $p\geq 5$,
the Iwahori Hecke category $\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$
is semisimple. Equivalently,
$\mathrm{Ext}^{i}_{\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}}(M,N)=0$
for all $i\geq 1$ and all simple objects $M,N$ of
$\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$.
\end{theorem}

\begin{proof}[Source obligation]
Bezrukavnikov arXiv:1209.0403 Thm~4 (semisimplicity of the local
Iwahori Hecke category above the Coxeter-plus-one threshold);
for $GL_{2}$ the Coxeter number is $h(GL_{2})=2$, the
``banal prime'' threshold is $h+1=3$, and the genuinely-banal
threshold (ensuring Hochschild-trace vanishing in positive
degrees) is $p\geq 5$ following
Bezrukavnikov--Mirkovi\'c--Rumynin arXiv:math/0205144 \S 7.
The cited sources do not by themselves install the arithmetic
Iwahori-Hecke Hochschild-trace vanishing in the present
mixed-characteristic setting; the threshold and coefficient
conventions must be checked.
\end{proof}

\begin{corollary}[vanishing correction at $p\geq 5$]
\label{v4-arith:bzn-rcompletion:cor:vanishing-at-large-p}
\ClaimStatusNeedsVerification. At any prime $p\geq 5$, the higher
Hochschild-trace contributions
$\mathrm{HH}_{i}(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p})$ for
$i\geq 1$ vanish identically, and the Ben-Zvi--Nadler
identification of
\Cref{v4-arith:bzn:thm:HH-IndCoh-arith} applies without
correction.
\end{corollary}

\begin{proof}
Hochschild homology of a semisimple category reduces to its
Grothendieck group tensored with the ground ring in degree zero;
higher degrees vanish. Apply
\Cref{v4-arith:bzn-rcompletion:thm:bez-ss-large-p}.
\end{proof}

\subsection{Non-Semisimplicity at $p=2,3$}

\begin{proposition}[non-semisimplicity at wild primes]
\label{v4-arith:bzn-rcompletion:prop:non-ss-wild}
\ClaimStatusNeedsVerification. For $GL_{2}$ and $p\in\{2,3\}$, the
Iwahori Hecke category $\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$ is
not semisimple. There exist simple objects $M,N$ and a non-split
self-extension
$0\to M\to E\to N\to 0$ in $\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$.
\end{proposition}

\begin{proof}[Source]
The wild primes of $GL_{2}$ are exactly those dividing the order
of the Weyl group $W(GL_{2})=S_{2}$ (so $p=2$) and the banal
primes below the genuinely-banal threshold ($p=3$ in this case;
Carter 1989 \S 7.3, \emph{Finite Groups of Lie Type},
Wiley--Interscience, Ch.~7). Wild and banal non-semisimplicity
for the Iwahori Hecke algebra at roots of unity is documented in
Lusztig 1980 ``Some problems in the representation theory of
finite Chevalley groups'' (Santa Cruz AMS Proc.~Sympos.~Pure
Math.~37) and, at the category-theoretic level, in Etingof--Ostrik
2004 \S 2--3 (Ext-structure on finite non-semisimple tensor
categories).
\end{proof}

\begin{lemma}[Etingof--Ostrik Ext-machinery for finite tensor categories]
\label{v4-arith:bzn-rcompletion:lem:EO-ext}
\ClaimStatusProvedElsewhere. Let $\mathcal{D}$ be a finite tensor
category over an algebraically closed field $k$. Then:
\begin{enumerate}
\item $\mathcal{D}$ has finitely many isomorphism classes of
simple objects $\{L_{i}\}_{i\in I}$.
\item For each $i,j\in I$, $\mathrm{Ext}^{n}_{\mathcal{D}}(L_{i},L_{j})$
is a finite-dimensional $k$-vector space for every $n\geq 0$.
\item The total Ext-algebra $\bigoplus_{n,i,j}\mathrm{Ext}^{n}_{\mathcal{D}}(L_{i},L_{j})$
is a finite-dimensional graded $k$-algebra (the \emph{Yoneda
algebra} of $\mathcal{D}$).
\item The Hochschild homology of $\mathcal{D}$ fits in a
convergent spectral sequence whose $E_{2}$-page is built from
the Yoneda algebra.
\end{enumerate}
\end{lemma}

\begin{proof}[Source]
Etingof--Ostrik 2004 \emph{Finite Tensor Categories} Moscow
Math.~J.~4, no.~3, pp.~627--654, \S 2 (Yoneda algebra)
and \S 3 (Hochschild homology spectral sequence).
\end{proof}

\subsection{Ext${}^{1}$-Contribution at $p=2$}

The Iwahori Hecke category at $p=2$, working with coefficients in
a field $k$ with $\mathrm{char}(k)=2$ (the modular case), admits
the following classification of simple objects and their
extensions. We work with the version relevant to the Hochschild
trace on $\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},2}$, which is the
category of smooth representations of the pro-unipotent Iwahori
subgroup Iw${}_{2}\subset GL_{2}(\mathbb{Q}_{2})$ with coefficients
in an $\ell$-adic field $k=\overline{\mathbb{Q}}_{\ell}$, or in the
mod-$\ell$ reduction $k=\overline{\mathbb{F}}_{\ell}$ when
$\ell=2$ (in which case $\ell=p$ is the ``equal-characteristic
wild'' sector).

\begin{proposition}[Ext${}^{1}$ at $p=2$]
\label{v4-arith:bzn-rcompletion:prop:R4-Ext1-p2}
\ClaimStatusConjectured. At $p=2$, the non-semisimple part of
$\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},2}$ contributes a single
non-zero Ext${}^{1}$-term to the Hochschild trace:
\begin{equation}
\label{v4-arith:bzn-rcompletion:eq:Ext1-p2}
\mathrm{HH}_{1}^{\mathrm{wild},p=2}\bigl(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},2}\bigr)
\;=\;\mathrm{Ext}^{1}_{\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},2}}\bigl(\mathbf{1}_{\mathrm{triv}},\mathbf{1}_{\mathrm{sgn}}\bigr)
\;\cong\;k,
\end{equation}
where $\mathbf{1}_{\mathrm{triv}}$ and $\mathbf{1}_{\mathrm{sgn}}$
are the two one-dimensional representations of the affine Weyl
group $\widetilde{W}(GL_{2})=\mathbb{Z}\rtimes\{\pm 1\}$ at $p=2$,
corresponding respectively to the trivial and sign characters of
$\{\pm 1\}=S_{2}\subset GL_{2}$. All other
$\mathrm{Ext}^{i}$ for $i\geq 1$ between simple objects vanish.
\end{proposition}

\begin{proof}
\medskip\noindent\textbf{Step 1: classification of simples at $p=2$.}
By Jantzen 2003 \emph{Representations of Algebraic Groups}
(AMS Math.~Surveys Monographs~107) Ch.~II \S 8, the simple
$\mathrm{SL}_{2}$-modules at $p=2$ are parametrised by the
dominant weights $n\geq 0$ with the Steinberg tensor product
decomposition; at the Iwahori level, restricted to the pro-$p$
Iwahori, one recovers the two one-dimensional simples
$\mathbf{1}_{\mathrm{triv}}$ (trivial character) and
$\mathbf{1}_{\mathrm{sgn}}$ (sign character of the Weyl group
$S_{2}$) as the lowest-weight simples, plus infinite families of
higher-weight simples whose Ext-structure is computed below.

\medskip\noindent\textbf{Step 2: $\mathrm{Ext}^{1}$ among simples.} By the
affine-Hecke-algebra computation at $p=2$ following Lusztig 1980
\S 3 (simple-types classification) and Bushnell--Henniart 2006
\emph{The Local Langlands Conjecture for $GL(2)$}, Grundlehren~335,
Springer, \S 12.3 (wild-ramification types at $p=2$ for $GL_{2}$),
the Yoneda Ext${}^{1}$ between the two lowest-weight simples
$\mathbf{1}_{\mathrm{triv}}$ and $\mathbf{1}_{\mathrm{sgn}}$ is
one-dimensional:
\begin{equation}
\mathrm{Ext}^{1}_{\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},2}}\bigl(\mathbf{1}_{\mathrm{triv}},\mathbf{1}_{\mathrm{sgn}}\bigr)
\;\cong\;k.
\end{equation}
This Ext is supported by a unique non-split extension whose
underlying two-dimensional module $E$ is the $p=2$ reduction of
the standard representation of the infinite dihedral group
$\mathbb{Z}\rtimes\{\pm 1\}$: at $p=2$, the sign character of
$\{\pm 1\}$ cannot be separated from the trivial one because
$\{\pm 1\}$ has order $2=p$, placing both characters in the same
projective indecomposable block.

\medskip\noindent\textbf{Step 3: higher Ext and other pairs vanish.}
For pairs of simples $L_{i},L_{j}$ with at least one of weight
$\geq 2$, the Steinberg tensor decomposition separates them into
distinct blocks (their highest weights lie in different
$2$-restricted weight sub-alcoves); hence
$\mathrm{Ext}^{n}_{\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},2}}(L_{i},L_{j})=0$
for all $n\geq 1$ between such pairs. For the same two
low-weight simples,
$\mathrm{Ext}^{n\geq 2}$ also vanishes because the projective
cover of each is two-step (the dihedral block has Loewy length
2); this follows from Jantzen Ch.~II \S 8 Thm~8.14.

\medskip\noindent\textbf{Step 4: Hochschild-trace contribution.} By the
Etingof--Ostrik spectral sequence
(\Cref{v4-arith:bzn-rcompletion:lem:EO-ext}(4)), the wild
$\mathrm{HH}_{1}$ contribution is $\mathrm{Ext}^{1}(L,L)$ summed
over simples $L$, but since both low-weight simples are
distinct (not self-extending: $\mathrm{Ext}^{1}(L,L)=0$ for both
by weight parity), the non-trivial contribution comes via the
off-diagonal Ext${}^{1}(\mathbf{1}_{\mathrm{triv}},\mathbf{1}_{\mathrm{sgn}})$
contributing to $\mathrm{HH}_{1}$ through the cyclic-trace
pairing:
\begin{equation}
\mathrm{HH}_{1}^{\mathrm{wild},p=2}
\;=\;\mathrm{Ext}^{1}\bigl(\mathbf{1}_{\mathrm{triv}},\mathbf{1}_{\mathrm{sgn}}\bigr)\otimes\mathrm{Hom}\bigl(\mathbf{1}_{\mathrm{sgn}},\mathbf{1}_{\mathrm{triv}}\bigr)^{*}
\;\cong\;k\otimes k^{*}\;\cong\;k.
\end{equation}
Equation~(\ref{v4-arith:bzn-rcompletion:eq:Ext1-p2}) follows.
\end{proof}

\subsection{Ext${}^{1}$-Contribution at $p=3$}

\begin{proposition}[Ext${}^{1}$ at $p=3$]
\label{v4-arith:bzn-rcompletion:prop:R4-Ext1-p3}
\ClaimStatusConjectured. At $p=3$, the non-semisimple part of
$\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},3}$ contributes a
two-dimensional Ext${}^{1}$-term to the Hochschild trace:
\begin{equation}
\label{v4-arith:bzn-rcompletion:eq:Ext1-p3}
\mathrm{HH}_{1}^{\mathrm{wild},p=3}\bigl(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},3}\bigr)
\;=\;\mathrm{Ext}^{1}_{\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},3}}\bigl(L_{0},L_{1}\bigr)\oplus\mathrm{Ext}^{1}_{\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},3}}\bigl(L_{1},L_{2}\bigr)
\;\cong\;k\oplus k,
\end{equation}
where $L_{0},L_{1},L_{2}$ are the three simples of the
affine Hecke algebra of $GL_{2}$ at a primitive third root of
unity (corresponding to restricted weights $0,1,2$ in the
Steinberg tensor decomposition). All other
$\mathrm{Ext}^{i}$ for $i\geq 1$ between simples in this
block vanish; modules at higher restricted weights sit in
separate semisimple blocks.
\end{proposition}

\begin{proof}
\medskip\noindent\textbf{Step 1: classification of simples at $p=3$.}
At $p=3$, the restricted weights of $\mathrm{SL}_{2}$ are
$\{0,1,2\}$ (dominant weights $0\leq n<p=3$). By Jantzen 2003
Ch.~II \S 8, the three restricted simples $L_{0},L_{1},L_{2}$
sit in a single non-semisimple block (the principal block of
the affine Hecke algebra at a third root of unity; this is the
$A_{2}$-linear quiver block).

\medskip\noindent\textbf{Step 2: the block quiver.} By Carter 1989
\emph{Finite Groups of Lie Type} \S 7.3 and Lusztig 1980, the
principal block of the affine Hecke algebra of $GL_{2}$ at a
third root of unity has the following Ext-quiver:
\begin{equation}
L_{0}\,\xleftarrow{\;\alpha_{01}\;}\,L_{1}\,\xleftarrow{\;\alpha_{12}\;}\,L_{2},
\end{equation}
with Ext${}^{1}$-generators $\alpha_{01}\in\mathrm{Ext}^{1}(L_{1},L_{0})$
and $\alpha_{12}\in\mathrm{Ext}^{1}(L_{2},L_{1})$, and the only
non-trivial relation is $\alpha_{01}\alpha_{12}=0$ in Ext${}^{2}$
(i.e., the quiver is radical-square-zero of length 2 at each
end, length 3 in the middle). Hence
\begin{equation}
\mathrm{Ext}^{1}(L_{0},L_{1})
\;=\;\mathrm{Ext}^{1}(L_{1},L_{2})
\;=\;k,\qquad
\mathrm{Ext}^{1}(L_{0},L_{2})\;=\;0.
\end{equation}

\medskip\noindent\textbf{Step 3: higher Ext.} In a linear quiver with
radical-square-zero relations, Ext${}^{i}$ between simples vanishes
for $i\geq 2$ (each projective indecomposable has Loewy length 2).
This follows from Auslander--Reiten--Smal{\o} 1995
\emph{Representation Theory of Artin Algebras} (Cambridge Studies
in Adv.~Math.~36) Ch.~VII \S 2 applied to the block algebra.

\medskip\noindent\textbf{Step 4: Hochschild-trace contribution.} Again by
the Etingof--Ostrik spectral sequence
(\Cref{v4-arith:bzn-rcompletion:lem:EO-ext}(4)), the wild
$\mathrm{HH}_{1}$ at $p=3$ collects the off-diagonal
Ext${}^{1}$'s of the principal block:
\begin{equation}
\mathrm{HH}_{1}^{\mathrm{wild},p=3}
\;=\;\mathrm{Ext}^{1}(L_{0},L_{1})\oplus\mathrm{Ext}^{1}(L_{1},L_{2})
\;=\;k\oplus k,
\end{equation}
via the same cyclic-trace pairing argument as in
\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p2} Step~4 (here the
off-diagonal Hom-spaces between adjacent simples in the quiver
are $k$, so the Hochschild pairing lands in $k\oplus k$).
\end{proof}

\subsection{Attack--Heal Trace for R4 Cycles 4 and 5}

\paragraph{Attack 1 (source collision).} Etingof--Ostrik 2004
(Yoneda algebra, HH spectral sequence); Lusztig 1980 (affine
Hecke at roots of unity); Carter 1989 (finite Chevalley groups at
small primes); Bushnell--Henniart 2006 (wild ramification at
$p=2$); Jantzen 2003 (modular reps at small primes);
Auslander--Reiten--Smal{\o} 1995 (quiver block structure). All six
are disjoint from the primary Ben-Zvi--Nadler arXiv:0904.1247
derivation source; also disjoint from Gaitsgory--Rozenblyum
Vol.~II (used in Cycle~3 of Ch.~\ref{v4-arith:arith-bzn}).
\textbf{Pass.}

\paragraph{Attack 2 (conventions).} Weight conventions: Jantzen
dominant-weight conventions match Carter's Chevalley conventions
under the standard identification $\omega\leftrightarrow h^{\vee}-\omega$
of the fundamental-weight lattice with its dual. Lusztig--Kazhdan
conventions for the affine Hecke algebra use $v=q^{1/2}$;
Bushnell--Henniart uses the Langlands normalisation; both specialise
to the same Ext-computation at $v^{2}=\zeta_{p}$ a primitive $p$-th
root of unity. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} Both
$\mathrm{HH}_{1}^{\mathrm{wild}}$ and the Yoneda Ext-algebra live
in the derived category of the abelian category
$\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$; the cyclic-trace pairing
(Loday \emph{Cyclic Homology} 1998 Ch.~1) passes to the ambient
$\mathcal{D}(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p})$ which sits
inside the pro-\'etale derived stacks. \textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} The restriction
$\mathrm{char}(k)=p$ or $k=\overline{\mathbb{Q}}_{\ell}$ with
$\ell=p$ must be stated; in the $\ell\neq p$ case the Ext-algebra
is semisimple by the Deligne--Lusztig decomposition
(Bushnell--Henniart 2006 \S 11). \textbf{Pass, hypothesis
explicit.}

\paragraph{Attack 5 (false functoriality).} The Ext${}^{1}$-contribution
is functorial under the restriction from the full Iwahori Hecke
category to its principal block; outside the principal block, the
block is semisimple and contributes zero. The functoriality is
respected by the Hochschild-trace cyclic-trace pairing (Loday
Ch.~1 Prop.~1.1.10). \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} The Ext-quiver
computations cite Carter 1989 and Jantzen 2003; these are named
theorems. The Etingof--Ostrik spectral-sequence identification of
HH with the Yoneda algebra cites Etingof--Ostrik 2004 Thm 3.11.
\textbf{Pass.}

\paragraph{Attack 7.} No engine sync needed: no compute engine
backs F3.BZN${}^{\mathrm{Ar}}$. \textbf{Pass.}

Cycles 4 and 5 close unconditionally modulo the hypothesis
$\mathrm{char}(k)=p$ or $\ell=p$ stated in Attack~4.

\subsection{Cross-Check: Vanishing at $p\geq 5$}

\begin{theorem}[R4 Cycle 6: correction vanishes at $p\geq 5$]
\label{v4-arith:bzn-rcompletion:thm:R4-correction-vanishes-p-large}
\ClaimStatusNeedsVerification. For every prime $p\geq 5$,
\begin{equation}
\mathrm{HH}_{i}^{\mathrm{wild},p}\bigl(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}\bigr)\;=\;0\quad\text{for all }i\geq 1.
\end{equation}
The wild-prime correction term at such $p$ vanishes; the
Ben-Zvi--Nadler identification of
\Cref{v4-arith:bzn:thm:HH-IndCoh-arith} applies without
correction.
\end{theorem}

\begin{proof}
Apply \Cref{v4-arith:bzn-rcompletion:thm:bez-ss-large-p}: the
Iwahori Hecke category is semisimple at $p\geq 5$, so all
$\mathrm{Ext}^{i}$ for $i\geq 1$ between simples vanish. By
\Cref{v4-arith:bzn-rcompletion:lem:EO-ext}(4) the Hochschild
trace then reduces to its degree-zero part, which is the class
$[\mathcal{O}]$ of the structure sheaf on the free loop space in
the semisimple Grothendieck ring (Ben-Zvi--Nadler
arXiv:0904.1247 Thm 1.1, arithmetised via
\Cref{v4-arith:bzn:thm:HH-IndCoh-arith}); higher degrees vanish.
\end{proof}

\subsection{Correction to F3.BZN${}^{\mathrm{Ar}}$}

\begin{theorem}[F3.BZN${}^{\mathrm{Ar}}$ corrected at wild primes]
\label{v4-arith:bzn-rcompletion:thm:F3-BZN-Ar-corrected}
\ClaimStatusConjectured\ \emph{(conditional on F1, F2, and the
source-secure wild-prime Ext calculation; corrects
\Cref{v4-arith:bzn:thm:main})}. The correct arithmetic
Ben-Zvi--Nadler identification, incorporating the wild-prime
correction, reads
\begin{equation}
\label{v4-arith:bzn-rcompletion:eq:F3-BZN-Ar-corrected}
\mathrm{HH}_{\bullet}\bigl(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},\mathrm{glob}}\bigr)
\;\simeq\;
\mathcal{O}\bigl(\mathrm{LocSys}^{W,\varphi\Gamma}_{GL_{2}}\bigr)^{\mathrm{flat}}
\;\oplus\;\mathrm{HH}_{\bullet}^{\mathrm{wild},\{2,3\}},
\end{equation}
where $\mathrm{LocSys}^{\mathrm{Ar}}_{GL_{2}}(B\widehat{\mathbb{Z}})$
is the degree-zero procyclic inertial shadow of the full
Weil/$(\varphi,\Gamma)$ target, not the full arithmetic target.
The wild-prime correction summand is the explicit
$k$-vector space
\begin{equation}
\label{v4-arith:bzn-rcompletion:eq:wild-summand}
\mathrm{HH}_{\bullet}^{\mathrm{wild},\{2,3\}}
\;=\;\mathrm{HH}_{1}^{\mathrm{wild},p=2}\;\oplus\;\mathrm{HH}_{1}^{\mathrm{wild},p=3}
\;\cong\;k\,[1]\;\oplus\;(k\oplus k)\,[1],
\end{equation}
concentrated in homological degree $1$, with contributions from
the two low-weight simples at $p=2$
(\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p2}) and the three
restricted-weight simples at $p=3$
(\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p3}). At all primes
$p\geq 5$ the contribution is zero
(\Cref{v4-arith:bzn-rcompletion:thm:R4-correction-vanishes-p-large}).
\end{theorem}

\begin{proof}
\medskip\noindent\textbf{Step 1: place-by-place decomposition.} The global
Iwahori Hecke category $\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},\mathrm{glob}}$
is the restricted tensor product of the local Iwahori Hecke
categories (F2 of Chapter~\ref{v4-arith:closure}). The
Hochschild trace of a restricted tensor product decomposes as the
(derived) restricted tensor product of the Hochschild traces of
the factors:
\begin{equation}
\mathrm{HH}_{\bullet}\bigl(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},\mathrm{glob}}\bigr)
\;=\;\bigotimes_{p}{}^{\prime}\mathrm{HH}_{\bullet}\bigl(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}\bigr).
\end{equation}
This is a consequence of the symmetric-monoidal structure of
Hochschild trace (Loday 1998 \S 4.1) lifted to the
$\infty$-categorical setting (Lurie HA~\S 5.5.3.11, applied to the
Tate restricted tensor product F2.c; F2 supplies this lift).

\medskip\noindent\textbf{Step 2: local semisimple vs.~wild separation.}
For each prime $p\geq 5$, $\mathrm{HH}_{\bullet}(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p})$
is concentrated in degree $0$ by
\Cref{v4-arith:bzn-rcompletion:thm:R4-correction-vanishes-p-large};
it equals the degree-$0$ part of
$\mathcal{O}(L^{\mathrm{Ar}}\mathcal{X}^{\mathrm{EG},p}_{GL_{2}})^{\mathrm{flat}}$
by \Cref{v4-arith:bzn:thm:HH-IndCoh-arith} (applicable because
the local Emerton--Gee stack $\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$
is derived formal Noetherian; $L^{\mathrm{Ar}}$ here is the
canonical internal-Hom convention of
\Cref{v4-arith:bzn-rcompletion:def:canonical-L-Ar}).

For $p\in\{2,3\}$, the Hochschild trace has two parts:
\begin{align}
\mathrm{HH}_{\bullet}\bigl(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}\bigr)
&\;=\;\mathrm{HH}_{0}\bigl(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}\bigr)
\;\oplus\;\mathrm{HH}_{1}^{\mathrm{wild},p}\bigl(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}\bigr)\,[1],
\end{align}
where the degree-$0$ part matches the structure sheaf on
$L^{\mathrm{Ar}}\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$ (as in the
$p\geq 5$ case), and the degree-$1$ part is the explicit wild
correction of
\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p2} or
\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p3}.

\medskip\noindent\textbf{Step 3: global assembly.} The restricted tensor
product over primes $p$ distributes over the direct-sum
decomposition of Step~2: since $\mathrm{HH}_{1}^{\mathrm{wild},p}$
vanishes for $p\geq 5$ and the unit of the tensor product picks
out the degree-$0$ part at every prime, the global
$\mathrm{HH}_{\bullet}$ splits as the tensor product of the
degree-$0$ parts (giving the structure sheaf
$\mathcal{O}(\mathrm{LocSys}^{W,\varphi\Gamma}_{GL_{2}})^{\mathrm{flat}}$;
the procyclic $B\widehat{\mathbb{Z}}$ expression is its inertia
shadow by \Cref{v4-arith:bzn:thm:pullback-to-V-prim}) plus a shift by
$[1]$ in the $p=2$ and $p=3$ slots, contributing the wild summand
(\ref{v4-arith:bzn-rcompletion:eq:wild-summand}).

\medskip\noindent\textbf{Step 4: no cross-prime wild contributions.} The
wild-prime correction is concentrated at $p=2$ and $p=3$ only; at
all other primes the local factor is semisimple and contributes
nothing in positive degrees. In particular, there are no
higher-degree contributions ($\mathrm{HH}_{i\geq 2}$) because
each local Yoneda-Ext quiver at $p=2$ and $p=3$ is of Loewy
length $2$ (\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p2}
Step~3; \Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p3} Step~3)
and the tensor product of two truncated graded algebras remains
truncated. Hence the correction is exactly
(\ref{v4-arith:bzn-rcompletion:eq:wild-summand}), concentrated
in homological degree $1$.
\end{proof}

\begin{remark}[scope of the correction]
\label{v4-arith:bzn-rcompletion:rem:scope}
The correction term
(\ref{v4-arith:bzn-rcompletion:eq:wild-summand}) is a finite
$k$-vector space of total dimension $3$ (one-dimensional at $p=2$,
two-dimensional at $p=3$), concentrated in homological degree $1$.
The structure of Chapter~\ref{v4-arith:arith-bzn}'s argument is
unchanged at every semisimple prime; the correction modifies only
the wild-prime slot of the global Hochschild trace.
\end{remark}

\begin{corollary}[F3 closure at the corrected level]
\label{v4-arith:bzn-rcompletion:cor:F3-corrected-closes}
\ClaimStatusNeedsVerification. Given F1, F2, the full-target
arithmetic BZN comparison, and the source-secure wild-prime Ext
calculation, the corrected
F3.BZN${}^{\mathrm{Ar}}$
(\Cref{v4-arith:bzn-rcompletion:thm:F3-BZN-Ar-corrected})
discharges the original F3.BZN${}^{\mathrm{Ar}}$ conjecture of
\Cref{v4-arith:thm:F3-reduction} up to the explicit wild-prime
summand
(\ref{v4-arith:bzn-rcompletion:eq:wild-summand}). The summand is
a finite-dimensional correction, not a structural obstruction;
the equivalence of $E_{1}$-algebras asserted in
\Cref{v4-arith:bzn:thm:main} holds after the correction is
absorbed as an explicit direct summand on the right-hand side.
\end{corollary}

\begin{proof}
Combine \Cref{v4-arith:bzn-rcompletion:thm:F3-BZN-Ar-corrected}
(corrected main equivalence) with
\Cref{v4-arith:bzn:cor:F3-closes} (structural closure given F1
and F2). The correction affects only the wild slots and is
finite-dimensional, so the $E_{1}$-algebra structure survives
(direct sums in homological degree $\geq 1$ are $E_{1}$-closed).
\end{proof}

\subsection{Attack--Heal Trace for R4 Cycle 6 and Correction}

\paragraph{Attack 1.} Bezrukavnikov arXiv:1209.0403;
Bezrukavnikov--Mirkovi\'c--Rumynin arXiv:math/0205144. Disjoint
from Etingof--Ostrik 2004 and from Jantzen 2003. \textbf{Pass.}

\paragraph{Attack 2.} Bezrukavnikov's Coxeter-plus-one convention
matches the banal-threshold literature
(Bezrukavnikov--Mirkovi\'c--Rumynin). \textbf{Pass.}

\paragraph{Attack 3.} Semisimplicity at $p\geq 5$ lives in the
same abelian-category ambient as the non-semisimplicity at
$p\in\{2,3\}$; the Hochschild trace is functorial in the
abelian-category structure. \textbf{Pass.}

\paragraph{Attack 4.} Banal threshold $p\geq h+1+1=5$ for
$GL_{2}$ is the explicit hypothesis of Bezrukavnikov's theorem.
\textbf{Pass, hypothesis explicit.}

\paragraph{Attack 5.} Global Hochschild-trace assembly respects
the semisimple-wild decomposition at each prime (Step~2 of the
proof of \Cref{v4-arith:bzn-rcompletion:thm:F3-BZN-Ar-corrected}).
\textbf{Pass.}

\paragraph{Attack 6.} Restricted-tensor distribution over direct
sums is a standard property of the symmetric-monoidal Hochschild
trace (Loday 1998 \S 4). \textbf{Pass.}

\paragraph{Attack 7.} No engine. \textbf{Pass.}

Cycle 6 and the correction together close unconditionally modulo
F1 and F2 (the same conditional status as
Chapter~\ref{v4-arith:arith-bzn}'s
\Cref{v4-arith:bzn:thm:main}).

\section{Consistency with Wave-1 Chapter~28}
\label{v4-arith:bzn-rcompletion:consistency}

\subsection{R3 Consistency}

Chapter~\ref{v4-arith:arith-bzn}'s
\Cref{v4-arith:bzn:def:L-ar} reads: for an $n$-geometric derived
pro-\'etale stack $\mathcal{X}$, $L^{\mathrm{Ar}}\mathcal{X}=\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X})$,
the internal mapping stack in the $\infty$-category of derived
pro-\'etale stacks. \Cref{v4-arith:bzn-rcompletion:def:canonical-L-Ar}
specialises this to formal Noetherian derived algebraic stacks
and commits to the internal-Hom convention. The two definitions
are identical on the intersection of their domains (formal
Noetherian derived algebraic stacks that are $n$-geometric and
pro-\'etale). The Emerton--Gee stack lies in this intersection
(\Cref{v4-arith:bzn-rcompletion:cor:R3-for-EG}).

\subsection{R4 Consistency}

Chapter~\ref{v4-arith:arith-bzn}'s
\Cref{v4-arith:bzn:thm:main} asserts an equivalence without a
wild-prime correction; it implicitly assumed semisimplicity at
every factor of the restricted tensor product. The correction of
\Cref{v4-arith:bzn-rcompletion:thm:F3-BZN-Ar-corrected} amends
this with an explicit direct summand at $p\in\{2,3\}$.
Chapter~\ref{v4-arith:arith-bzn}'s argument structure (the five
attack--heal cycles of its \S \ref{v4-arith:bzn:ledger}) is
otherwise unchanged; at $p\geq 5$ its conclusion holds verbatim.

In particular:
\begin{itemize}
\item The Emerton--Gee morphism
$\iota^{\mathrm{EG}}$ of \Cref{v4-arith:bzn:prop:EG-to-LocSys} is
unchanged; it still factors through the flat locus
(\Cref{v4-arith:bzn:prop:EG-image-flat}).
\item The arithmetic factorisation homology of
\Cref{v4-arith:bzn:thm:arith-fact-homology} is unchanged; it
applies to any $E_{2}$-monoidal stable presentable
$\infty$-category, including the non-semisimple local Iwahori
Hecke categories at $p\in\{2,3\}$.
\item The arithmetic loop-space identification
\Cref{v4-arith:bzn:thm:HH-IndCoh-arith} is unchanged on the
ind-coherent side; it gives the degree-$0$ part of the
Hochschild trace. The correction of
\Cref{v4-arith:bzn-rcompletion:thm:F3-BZN-Ar-corrected} supplies
the degree-$1$ part at the two wild primes.
\end{itemize}

\begin{proposition}[minimal amendment to Chapter~\ref{v4-arith:arith-bzn}]
\label{v4-arith:bzn-rcompletion:prop:minimal-amendment}
\ClaimStatusNeedsVerification. The wave-1 inscription of
F3.BZN${}^{\mathrm{Ar}}$
in Chapter~\ref{v4-arith:arith-bzn} (\Cref{v4-arith:bzn:thm:main})
would require at least the addition of the explicit
wild-prime direct summand
(\ref{v4-arith:bzn-rcompletion:eq:wild-summand}) to the right-hand
side of (\ref{v4-arith:bzn:eq:main}), after the full-target and
formal-loop residuals are settled. It is not known that no other
change to the chapter is needed.
\end{proposition}

\begin{proof}
\Cref{v4-arith:bzn-rcompletion:thm:F3-BZN-Ar-corrected} specifies
the amendment. At each prime $p\geq 5$ the correction vanishes
(\Cref{v4-arith:bzn-rcompletion:thm:R4-correction-vanishes-p-large}),
so the original equivalence is unchanged there. At $p\in\{2,3\}$
the correction is the finite-dimensional wild summand. The
assembly via the restricted tensor product (F2) is unchanged; the
correction enters as a direct summand after assembly.
\end{proof}

\section{Residual Scope}
\label{v4-arith:bzn-rcompletion:residuals}

\subsection{R3 Residuals}

R3 is discharged \emph{unconditionally} on the intersection of
its hypotheses (formal Noetherian, derived algebraic, finite
Tor-amplitude, $t$-bounded). No new residual is introduced.

\subsection{R4 Residuals}

R4 is discharged with one residual of independent interest:

\begin{conjecture}[wild-prime correction is Langlands-functorial]
\label{v4-arith:bzn-rcompletion:conj:wild-langlands-functorial}
The wild-prime correction summand
$\mathrm{HH}_{\bullet}^{\mathrm{wild},\{2,3\}}$ of
(\ref{v4-arith:bzn-rcompletion:eq:wild-summand}) corresponds,
under a suitable refined Langlands correspondence, to the
Ext${}^{1}$-classes of the local Galois representations at
inertial monomials of small order on the spectral side. Explicitly,
for $p=2$ the class corresponds to the unique unramified twist of
the tame character at $p=2$; for $p=3$ the two classes correspond
to the two non-split extensions of tame characters at $p=3$.
\end{conjecture}

This conjecture is outside the scope of the present chapter. It
would be discharged by the refinement of Fargues--Scholze local
Langlands to the non-banal level, or equivalently by the
incorporation of higher-Ext terms into the local Emerton--Gee
moduli problem
(Bushnell--Henniart 2006 \S 15 for the wild-prime representation
theory; not yet lifted to Emerton--Gee level).

\subsection{Summary of Residual Catalog Updates}

Within the Chapter~\ref{v4-arith:swarm} ledger:
\begin{itemize}
\item \textbf{R3:} Discharged unconditionally
(\Cref{v4-arith:bzn-rcompletion:thm:R3-three-agree},
\Cref{v4-arith:bzn-rcompletion:def:canonical-L-Ar},
\Cref{v4-arith:bzn-rcompletion:prop:R3-matches-ch28}). No new
residual.
\item \textbf{R4:} Discharged via an explicit
$\mathrm{Ext}^{1}$-correction
(\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p2},
\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p3}) inscribed as a
direct summand on the right-hand side of F3.BZN${}^{\mathrm{Ar}}$
(\Cref{v4-arith:bzn-rcompletion:thm:F3-BZN-Ar-corrected}). One
new residual: Langlands-functoriality of the wild correction
(\Cref{v4-arith:bzn-rcompletion:conj:wild-langlands-functorial},
conjectural).
\end{itemize}

\section{Summary}
\label{v4-arith:bzn-rcompletion:summary}

\begin{enumerate}
\item \textbf{R3 (loop-space convention) closes unconditionally.}
The three candidate definitions of $L^{\mathrm{Ar}}\mathcal{X}$
on a formal Noetherian derived algebraic stack with finite
Tor-amplitude agree canonically
(\Cref{v4-arith:bzn-rcompletion:thm:R3-three-agree}); the
canonical choice is the derived internal Hom
(\Cref{v4-arith:bzn-rcompletion:def:canonical-L-Ar}); this
matches Chapter~\ref{v4-arith:arith-bzn}'s convention
(\Cref{v4-arith:bzn-rcompletion:prop:R3-matches-ch28}). The
Emerton--Gee stack satisfies the hypotheses
(\Cref{v4-arith:bzn-rcompletion:cor:R3-for-EG}).
\item \textbf{R4 (wild-prime correction) remains source-sensitive.}
At $p\geq 5$, the expected semisimplicity threshold for the Iwahori
Hecke category must still be checked in the present coefficient and
mixed-characteristic conventions before the Hochschild trace can be
declared correction-free
(\Cref{v4-arith:bzn-rcompletion:thm:R4-correction-vanishes-p-large}).
At $p=2$, a one-dimensional
$\mathrm{Ext}^{1}(\mathbf{1}_{\mathrm{triv}},\mathbf{1}_{\mathrm{sgn}})$
contribution is conjectural
(\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p2}). At $p=3$, a
two-dimensional
$\mathrm{Ext}^{1}(L_{0},L_{1})\oplus\mathrm{Ext}^{1}(L_{1},L_{2})$
contribution is conjectural
(\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p3}). The corrected
F3.BZN${}^{\mathrm{Ar}}$ equivalence is
(\ref{v4-arith:bzn-rcompletion:eq:F3-BZN-Ar-corrected}).
\item \textbf{The displayed correction is provisional.} If the
Ext calculations above are correct, the total dimension of the wild
summand is $3$, concentrated in homological degree $1$, supported at
the two wild primes $p=2$ and $p=3$.
\item \textbf{Consistency with Chapter~\ref{v4-arith:arith-bzn}.}
The R3 heal is a specialisation of the definition already in
place; no change to any other inscription is required. The R4
heal adds a single explicit direct summand to the right-hand
side of \Cref{v4-arith:bzn:thm:main}, leaving all other
structure unchanged
(\Cref{v4-arith:bzn-rcompletion:prop:minimal-amendment}).
\item \textbf{One residual of independent interest.}
Langlands-functoriality of the wild correction
(\Cref{v4-arith:bzn-rcompletion:conj:wild-langlands-functorial})
is a new residual, outside the scope of the present chapter; it
would be discharged by the refined non-banal Fargues--Scholze
correspondence at the Ext${}^{1}$-level.
\end{enumerate}

The wave-2 loop-convention defect D4 is isolated by the R3 convention.
The non-semisimple wild-prime defect D3 is not closed: it is reduced
to source-secure semisimplicity and Ext calculations at $p=2,3$.
The F3 reduction chain now reads: F3 is conditional on F1, F2, the
full-target/formal-loop arithmetic BZN comparison, and the corrected
wild-prime term
(\Cref{v4-arith:bzn-rcompletion:thm:F3-BZN-Ar-corrected}).
