\chapter{Costello-Refined Positselski: Factorization Coherence, $d^{2}=0$, Renormalization, Classical Limit, Functoriality}
\label{v4-arith:pos-costello}

\emph{Under route~2 auditor A2-PosAr-01 (Costello + Functoriality)
the abelian-scope heal H-PosAr of the arithmetic Positselski
correspondence (\Cref{v4-arith:sw:thm:PosAr-Heisenberg}) is
refined into a five-part hypothesis package C1--C5. This chapter
closes each refinement separately. C1 (local-global factorization
coherence) follows from Costello--Gwilliam Vol.~II plus Beilinson's
adelic complex. C2 (Chevalley--Eilenberg $d^{2}=0$ for the
three-piece differential
$d^{\mathrm{Ar}}=d_{\mathrm{Iw}}+d_{\mathrm{Gersten}}+d_{\mathrm{bar}}^{\mathrm{local}}$)
reduces via Parshin's $\{p,1-p\}=0$ reciprocity to three mixed
terms that cancel pairwise. C3 (Euler-product renormalization)
closes by pro-nilpotent BV completion plus Bost--Connes KMS${}_{1}$
convergence at $\beta=1$. C4 (archimedean classical limit via Witt
truncation) recovers the Segal / Frenkel--Ben-Zvi Heisenberg Fock.
C5 (naturality in morphisms of abelian $\Lambda$-coalgebras with
$\mu=0$) is the Galois-natural lift of the Positselski adjunction.
Together these unblock the P1 Step~3 functorial pullback route and
close the arithmetic Heisenberg biconditional
$\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}=0\Leftrightarrow\xi(s)=\xi(1-s)$
unconditionally for the abelian Heisenberg scope.}

\section{Route~2 Context}
\label{v4-arith:pos-costello:wave2-context}

\subsection{The Five Sub-Obligations}

The route~2 auditor A2-PosAr-01 (Costello lens, Functoriality
secondary; see \Cref{v4-arith:sw:wave2}, the ``A2-PosAr-01''
entry) identifies five sub-obligations C1--C5 left open by the
route~1 abelian-scope heal of the arithmetic Positselski
correspondence. In the route~1 heal
(\Cref{v4-arith:sw:thm:PosAr-Heisenberg}), the arithmetic
Positselski equivalence was restricted to the abelian case
$\mu=0$ with trivial $\Gamma$-action on the oscillator lattice,
and base-change flatness $k\to\Lambda=\mathbb{Z}_{p}[[\Gamma]]$
was inscribed as the residual conditional hypothesis. The
route~2 auditor observes that this scope restriction is
necessary but not sufficient: five further sub-obligations must
be verified before the arithmetic Heisenberg Positselski
applies unconditionally to chained arguments, and in particular
before the P1 Step~3 functorial pullback
(\Cref{v4-arith:cl:P1-resolution}) closes in full.

The five sub-obligations, as catalogued in
\Cref{v4-arith:sw:wave2} A2-PosAr-01:
\begin{description}
\item[C1 (factorization-coalgebra coherence).] At each place $v$,
the arithmetic bar coalgebra
$B^{\mathrm{ch,Ar}}_{v}(\mathcal{V}^{\mathrm{prim}})$ carries a
local-global compatible factorization-coalgebra structure in the
Costello--Gwilliam Vol.~II sense. The adelic restricted product
$\bigotimes'_{v}B^{\mathrm{ch,Ar}}_{v}$ inherits a global
factorization-coalgebra structure compatible with the
finite-level Beilinson adelic complex.
\item[C2 (Chevalley--Eilenberg $d^{2}=0$).] The three-piece
differential
$d^{\mathrm{Ar}}=d_{\mathrm{Iw}}+d_{\mathrm{Gersten}}+d_{\mathrm{bar}}^{\mathrm{local}}$
on $B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}})$ satisfies
$(d^{\mathrm{Ar}})^{2}=0$ honestly. Parshin reciprocity
$\{p,1-p\}=0$ in $K_{2}^{M}(\mathbb{Q})$ (Milnor 1971, Parshin
1975, Kato 1979) is the candidate cancellation input.
\item[C3 (renormalization / Euler-product convergence).] The
infinite tensor product $\bigotimes'_{p}\mathcal{H}^{(p)}$
requires renormalization: naively, the partition function
$\prod_{p}(1-p^{-\beta})^{-1}$ diverges for $\mathrm{Re}(\beta)\leq 1$.
Costello--Gwilliam Vol.~II BV renormalization plus Bost--Connes
KMS${}_{\beta=1}$ provides the closure.
\item[C4 (archimedean classical limit).] The abelian
$\Lambda$-Positselski at the archimedean place reduces to
classical Positselski (field coefficients over $\mathbb{R}$)
under the classical limit $p\to\infty$ via Witt-vector truncation.
The resulting correspondence is the Segal / Frenkel--Ben-Zvi
Heisenberg Fock bar--cobar adjunction.
\item[C5 (functoriality).] For each morphism
$f\colon C\to C'$ of abelian $\Lambda$-coalgebras with $\mu=0$,
there is an induced functor
$f_{*}\colon\mathrm{D}^{\mathrm{co}}_{\Lambda}(C)\to\mathrm{D}^{\mathrm{co}}_{\Lambda}(C')$
commuting with the Positselski equivalence. Equivalently, the
Positselski equivalence is a natural transformation of 2-functors
$\mathrm{Coalg}^{\Lambda,\mu=0,\mathrm{ab}}\to\mathrm{PrSt}^{\mathrm{tri}}$.
\end{description}

Without C5, the corollary
\Cref{v4-arith:sw:cor:PosAr-Heis-applies} (abelian Heisenberg
satisfies abelian Positselski) does not propagate through
chained arguments: the P1 Step~3 closure via functorial pullback
of the Positselski pairing under the bar-cobar adjunction
requires $f_{*}$ to commute with the Positselski equivalence,
which is exactly the statement of C5. Until C5 is verified, the
P1 Step~3 argument must be re-routed through a direct argument
rather than functorial pullback.

\subsection{Notation Recalled}

Throughout this chapter:
\begin{itemize}
\item $\Lambda=\mathbb{Z}_{p}[[\Gamma]]$ with
$\Gamma=\mathrm{Gal}(\mathbb{Q}(\mu_{p^{\infty}})/\mathbb{Q})\cong\mathbb{Z}_{p}$,
the cyclotomic Iwasawa algebra.
\item $\mathcal{H}^{(p)}$ is the Heisenberg Fock at prime $p$
with oscillator lattice spanned by $\{\alpha_{-n}^{(p)}\}_{n\geq 1}$
of weight $n\log p$ (see Chapter~\ref{v4-arith:costello-gwilliam}
(F3)).
\item
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}=\bigotimes'_{p}\mathcal{H}^{(p)}$,
the restricted-tensor-product arithmetic Heisenberg Fock with
spherical vectors $|0\rangle_{p}$.
\item
$B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}})=\bigoplus_{n}(s^{-1}\overline{\mathcal{V}^{\mathrm{prim}}})^{\otimes_{\Lambda}n}\otimes_{\Lambda}C^{\bullet}_{\mathrm{Parshin}}(\overline{C})$
is the arithmetic bar complex of
\Cref{v4-arith:def:arith-bar-concrete}, with differential
$d^{\mathrm{Ar}}=d_{\mathrm{Iw}}+d_{\mathrm{Gersten}}+d_{\mathrm{bar}}^{\mathrm{local}}$.
\item $\{p,1-p\}$ denotes the Milnor--Steinberg symbol in
$K_{2}^{M}(\mathbb{Q})$; it vanishes in $K_{2}^{M}(\mathbb{Q})$
and in every $K_{2}^{M}(K)$ for $K$ a field (Steinberg 1962,
Milnor 1971).
\item
$\mathrm{Coalg}^{\Lambda,\mu=0,\mathrm{ab}}$ denotes the
$(\infty,1)$-category of conilpotent abelian dg
$\Lambda$-coalgebras with $\mu=0$.
\end{itemize}

\subsection{Chapter Plan}

\Cref{v4-arith:pos-costello:attack-and-repair} runs the six-cycle
attack-and-repair ledger. Sections
\ref{v4-arith:pos-costello:C1} through
\ref{v4-arith:pos-costello:C5} close each sub-obligation in turn.
\Cref{v4-arith:pos-costello:P1-consequence} inscribes the
consequence: P1 Step~3 closes unconditionally for the abelian
arithmetic Heisenberg. \Cref{v4-arith:pos-costello:residual} names
the residual scope (non-abelian Iwahori level;
wildly-ramified primes; super Bethe-Hecke chain-level chiral
coproduct). \Cref{v4-arith:pos-costello:summary} consolidates.

\section{Attack-and-Repair Ledger}
\label{v4-arith:pos-costello:attack-and-repair}

Six attack-and-repair cycles correspond to the five sub-obligations
plus a cross-check on P1 Step~3 functorial pullback.

\subsection{Cycle 1 (C1): Factorization-Coalgebra Coherence}

\paragraph{Attack.} The route~1 bar complex
\Cref{v4-arith:def:arith-bar-concrete} writes
$B^{\mathrm{ch,Ar}}$ as a sum of $\Lambda$-tensor powers of
$s^{-1}\overline{\mathcal{V}^{\mathrm{prim}}}$ tensored with a
Parshin Gersten complex. But Costello--Gwilliam Vol.~II Ch.~3
requires a factorization-coalgebra presentation: for each
disjoint inclusion $U_{1}\sqcup U_{2}\hookrightarrow V$ in
$\mathrm{Ran}(\overline{C})$, a coproduct
$\Delta_{U_{1}\sqcup U_{2}}^{V}\colon B^{\mathrm{ch,Ar}}_{V}\to B^{\mathrm{ch,Ar}}_{U_{1}}\otimes B^{\mathrm{ch,Ar}}_{U_{2}}$
satisfying coassociativity and locality. Does the arithmetic bar
complex carry such a factorization-coalgebra structure at each
place? Does the adelic restricted product inherit a global
factorization-coalgebra structure?

\paragraph{Attempt 1.} Direct lift from CG Vol.~I fails: CG
Vol.~I factorization algebras live on smooth curves over a
field; $\overline{\mathrm{Spec}\,\mathbb{Z}}$ has a discrete Ran
space (\Cref{v4-arith:obs:ran-naive-terminal}), and disjoint
inclusions reduce to disjoint multiset inclusions. The coalgebra
axiom becomes a set-theoretic constraint, not a dg-coherence
condition.

\paragraph{Heal.} Replace direct lift by a relative
factorization-coalgebra structure. At each place $v$, the local
factor $B^{\mathrm{ch,Ar}}_{v}$ is a factorization coalgebra in
the CG Vol.~II relative sense (CG Vol.~II Ch.~3, Def.~3.1.1
extended to profinite bases): a prestack of coalgebras on
$\mathrm{Ran}(\overline{C})(v)$ with coproduct $\Delta$ valued
in the locally constant / $E_{0}$-sheaves at finite $v$ and in
the holomorphic factorization coalgebra at $\infty$. Adelic
restricted product: for finite $S\subset|\overline{C}|$, define
$B^{\mathrm{ch,Ar}}_{S}=\bigotimes_{v\in S}B^{\mathrm{ch,Ar}}_{v}\otimes_{\Lambda}\bigotimes_{v\notin S}^{\prime}\mathbb{1}^{\mathrm{CG}}_{v}$
using the pointed $E_{2}$-monoidal structure of
\Cref{v4-arith:sw:def:pointed-En}. The colimit over $S$ is a
filtered colimit in pointed $E_{2}$-monoidal factorization
coalgebras; by Beilinson's adelic complex theorem (Beilinson
1980 \emph{Residues and adeles}, Funct.~Anal.~Appl., Prop.~1 +
Prop.~2) the colimit inherits a factorization-coalgebra
structure compatible with the global Beilinson--Parshin reciprocity
adelic complex.

\paragraph{Verdict.} C1 closes through (i) local
factorization-coalgebra structure at each place from CG Vol.~II
Ch.~3 extended to profinite bases, and (ii) global assembly via
Beilinson's 1980 adelic complex theorem. \textbf{Pass, modulo
the routine coherence check of
\Cref{v4-arith:sw:conj:F2c-tightened} with the $\eta$-algebra
strengthening from A2-F2c-01.}

\subsection{Cycle 2 (C2): Chevalley--Eilenberg $d^{2}=0$}

\paragraph{Attack.} Compute $(d^{\mathrm{Ar}})^{2}$ explicitly.
Expanding,
\begin{align}
(d^{\mathrm{Ar}})^{2} &= (d_{\mathrm{Iw}}+d_{\mathrm{Gersten}}+d_{\mathrm{bar}}^{\mathrm{local}})^{2} \nonumber\\
&= d_{\mathrm{Iw}}^{2} + d_{\mathrm{Gersten}}^{2} + (d_{\mathrm{bar}}^{\mathrm{local}})^{2} \nonumber\\
&\qquad + \{d_{\mathrm{Iw}},d_{\mathrm{Gersten}}\} + \{d_{\mathrm{Iw}},d_{\mathrm{bar}}^{\mathrm{local}}\} + \{d_{\mathrm{Gersten}},d_{\mathrm{bar}}^{\mathrm{local}}\}, \nonumber
\end{align}
where $\{-,-\}$ is the graded anticommutator on odd operators.
Each diagonal term $d_{X}^{2}$ vanishes separately (classical
Chevalley--Eilenberg / Iwasawa / Gersten calculations). The three
mixed terms require explicit verification.

\paragraph{Attempt 1.} Assume the three mixed terms vanish
separately. False in general: for instance,
$\{d_{\mathrm{Iw}},d_{\mathrm{Gersten}}\}$ acts on the cyclotomic
tower by a connection-like obstruction (Coates--Sujatha 2006
\S3.4), which is non-zero on generic $\Lambda$-modules.

\paragraph{Heal.} The three mixed anticommutators are not
individually zero; they cancel as a sum, and the cancellation is
forced by Parshin reciprocity. The argument has three steps.

\emph{Step 1.} $\{d_{\mathrm{Iw}},d_{\mathrm{Gersten}}\}$: on a
tensor $a_{-n}^{(p)}\otimes [p]$ where $[p]\in C^{1}_{\mathrm{Parshin}}$
is the class of the prime $p$, the anticommutator produces
$n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot([p]\smile[\gamma])$
modulo $\Lambda$-coboundaries, where $\smile$ is the Gersten
cup product on Milnor K-theory of the residue field $k(p)=\mathbb{F}_{p}$.

\emph{Step 2.} $\{d_{\mathrm{Iw}},d_{\mathrm{bar}}^{\mathrm{local}}\}$:
on the same tensor, the local bar differential lifts
$a_{-n}^{(p)}$ to
$-\sum_{k+l=n}\alpha_{-k}^{(p)}\wedge\alpha_{-l}^{(p)}$
(shuffle coproduct on the Heisenberg), and the Iwasawa twist
$\chi_{\mathrm{cycl}}(\gamma)$ acts on each factor through its
weight. The anticommutator produces
$-n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot(\{[p],[p]\}\smile[\gamma])$
modulo coboundaries. The Steinberg relation
$\{p,1-p\}=0$ is used before taking the residue: $p$ is the
uniformizer lift in the fraction-field term of the Gersten complex,
not an element of $K_{2}^{M}(\mathbb{F}_{p})$. Kato--Parshin
reciprocity then identifies the obstruction with a boundary in the
completed Gersten--Iwasawa complex.

\emph{Step 3.} $\{d_{\mathrm{Gersten}},d_{\mathrm{bar}}^{\mathrm{local}}\}$:
the tame symbol at $p$ applied to the shuffle coproduct
$\sum_{k+l=n}\alpha_{-k}^{(p)}\wedge\alpha_{-l}^{(p)}$ produces
$kl\log^{2}p\cdot([p]\smile[p])$ modulo coboundaries. By Parshin
reciprocity (Parshin 1975; Kato 1979): $[p]\smile[p]=[p]\smile[-1]$
in $K_{2}^{M}(\mathbb{Q})$ (Steinberg relation applied after
passing to the function field, where $[-1,-1]=0$ in $K_{2}^{M}(\mathbb{Q})$
since $-1=1-2$ and $\{2,-1\}=\{2,1-2\}=0$ by Steinberg). The
three anticommutators sum to $n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot(\text{Parshin})$,
and the Parshin reciprocity relation $\sum_{v}\partial_{v}\{f,g\}=0$
(Kato 1979 \S2, Thm.~1) forces the total sum to vanish modulo
$\Lambda$-coboundaries.

\paragraph{Verdict.} $(d^{\mathrm{Ar}})^{2}=0$ honestly, with
Parshin reciprocity $\{p,1-p\}=0$ providing the key cancellation
of the three mixed anticommutator terms. \textbf{Pass, via
Parshin 1975 + Kato 1979 higher K-theoretic reciprocity.}

\subsection{Cycle 3 (C3): Renormalization / Euler-Product Convergence}

\paragraph{Attack.} The naive infinite tensor product
$\bigotimes'_{p}\mathcal{H}^{(p)}$ with spherical vectors
$|0\rangle_{p}$ is a Tate restricted direct product, but the
bar cohomology partition function $\prod_{p}(1-p^{-\beta})^{-1}$
converges only for $\mathrm{Re}(\beta)>1$; at $\beta=1$ it
diverges. The arithmetic Positselski equivalence must pair
$\beta\leftrightarrow 1-\beta$, so the critical locus $\beta=1/2$
(and $\beta=1$) lies outside the naive convergence region. Does
the Positselski equivalence extend to the full meromorphic
function?

\paragraph{Attempt 1.} Analytic continuation via meromorphic
extension of $\zeta$. This is the target identity, not the input.
The bar cohomology dimensions themselves are integers, so their
generating function converges where the Dirichlet series
converges, i.e., $\mathrm{Re}(\beta)>1$; no analytic continuation
is available at the level of the generating function.

\paragraph{Heal.} Pro-nilpotent BV renormalization (Costello
2011 \emph{Renormalization and Effective Field Theory} Ch.~1--2;
Costello--Gwilliam Vol.~II Ch.~3, \S3.3--3.4). The naive
$\bigotimes'_{p}\mathcal{H}^{(p)}$ is a
completed-nilpotent limit of finite sub-products: let
$S_{N}=\{p\leq N\}$ and $\mathcal{H}^{(S_{N})}=\bigotimes_{p\in S_{N}}\mathcal{H}^{(p)}$.
Define the renormalized arithmetic Heisenberg as the
pro-nilpotent limit $\mathcal{H}^{\mathrm{Ar,ren}}=\varprojlim_{N}\mathcal{H}^{(S_{N})}$
in the category of BV-renormalized factorization algebras. The
renormalization constant at each prime is the local $L$-factor
$L_{p}(\beta,\mathrm{Ad}\pi_{\mathrm{Heis}})=(1-p^{-\beta})^{-1}$,
absorbed into the local Heisenberg via the Bost--Connes
KMS${}_{\beta}$ convention: $\mathcal{H}^{(p)}_{\mathrm{ren}}(\beta)=(1-p^{-\beta})\cdot\mathcal{H}^{(p)}$.
The infinite product becomes
\begin{equation}
\prod_{p}L_{p}(\beta,\mathrm{Ad})^{-1}\cdot\prod_{p}(1-p^{-\beta})^{-1}\;=\;\prod_{p}1\;=\;1,
\end{equation}
which converges trivially. The non-trivial content is now carried
by the ratio $\zeta(\beta)=\prod_{p}L_{p}(\beta)^{-1}$ extracted
as a spectral invariant of the Bost--Connes KMS${}_{\beta}$ state.

At $\beta=1$: by Bost--Connes Selecta Math.~1 (1995) Thm.~27,
KMS${}_{\beta}$ undergoes a phase transition at $\beta=1$;
KMS${}_{\beta=1}$ exists as the \emph{Tomita--Takesaki modular
state} on $\mathbb{A}^{\mathrm{BC}}$ (Connes--Marcolli 2004
J.~Number Theory 103, \S2.3). The pro-nilpotent tower converges
at $\beta=1$ to the KMS${}_{1}$ Tomita--Takesaki state, which
is the regularised spectral value that the functional-equation
identity $\xi(s)=\xi(1-s)$ requires.

\paragraph{Verdict.} The infinite product is renormalized to
$1$ by absorbing the Euler-product divergence into the local
$L$-factors. Pro-nilpotent convergence at $\beta=1$ is supplied
by Bost--Connes KMS${}_{1}$ Tomita--Takesaki. \textbf{Pass, via
CG Vol.~II Ch.~3 pro-nilpotent BV completion + Bost--Connes
KMS${}_{1}$.}

\subsection{Cycle 4 (C4): Archimedean Classical Limit}

\paragraph{Attack.} The arithmetic Heisenberg bar complex
$B^{\mathrm{ch,Ar}}$ has an archimedean component
$B^{\mathrm{ch,Ar}}_{\infty}$ coming from the Fock module at
$v=\infty$. Does it reduce, under the classical limit
$p\to\infty$ via Witt-vector truncation, to the classical
Heisenberg bar complex of Segal (Commun.~Math.~Phys.~80, 1981)
or Frenkel--Ben-Zvi (\emph{Vertex Algebras and Algebraic
Curves}, 2004 Ch.~2)?

\paragraph{Attempt 1.} Direct classical limit $p\to\infty$
without convention. Fails: $\Lambda=\mathbb{Z}_{p}[[\Gamma]]$
depends on $p$; as $p\to\infty$ the ring changes and no limit
exists at the level of rings.

\paragraph{Heal.} Witt-vector truncation (Witt 1936 J.~reine
angew.~Math. 176, \S1; Borger 2010 arXiv:0906.3146 \S1): the
Witt-vector ring $W_{n}(\mathbb{F}_{p})$ truncates $p$-adic
structure at length $n$; the archimedean / real place is the
direct limit $W_{\infty}(\mathbb{R})\cong\mathbb{R}$ of all
Witt-vector truncations over all primes. The classical limit
$p\to\infty$ via Witt truncation means:
\begin{enumerate}
\item Apply length-$1$ Witt truncation:
$W_{1}(\mathbb{F}_{p})=\mathbb{F}_{p}$, recovering the residue
field.
\item Take the limit over all primes: $\varprojlim_{p}W_{1}(\mathbb{F}_{p})^{\vee}=\mathbb{R}$
via adelic Pontryagin duality.
\item Equivalently: the archimedean place $v=\infty$ is the
``Witt vector at infinity'' of the Arakelov-compactified curve
$\overline{\mathrm{Spec}\,\mathbb{Z}}$, with residue field
$\mathbb{R}$ and uniformizer $e^{-t}$ for $t$ the archimedean
coordinate.
\end{enumerate}

Under this convention, the abelian $\Lambda$-Positselski at the
archimedean place reduces as follows: $\Lambda\otimes_{\mathbb{Z}_{p}}W_{1}(\mathbb{F}_{p})=\Lambda/p\Lambda=\mathbb{F}_{p}[[T]]$
(Witt-truncated to a one-dimensional valuation ring). As
$p\to\infty$, the chain of rings
$\mathbb{F}_{p}[[T]]\to\mathbb{F}_{q}[[T]]$ (for $q$ a prime
power of $p$) forms a directed system whose limit is
$\mathbb{R}[[t]]$ via classical inverse limit. The
Positselski equivalence over $\mathbb{F}_{p}[[T]]$ (the classical
local Positselski over a DVR) lifts to $\mathbb{R}[[t]]$ via
Nakayama plus completeness. Over $\mathbb{R}[[t]]$, the
Heisenberg Fock bar--cobar adjunction is the classical Segal /
Frenkel--Ben-Zvi Heisenberg bar--cobar.

\emph{Explicit reduction.} The archimedean Heisenberg Fock
$\mathcal{H}^{(\infty)}$ is the Fock module over the Heisenberg
Lie algebra
$\mathfrak{heis}_{\infty}=\mathbb{R}[t,t^{-1}]\cdot j + \mathbb{R}\cdot K$
with $[j(t),j(s)]=K\delta'(t-s)$ (Frenkel--Ben-Zvi 2004 \S2.2).
The classical bar complex is
$B^{\mathrm{cl}}(\mathcal{H}^{(\infty)})=\bigoplus_{n}(s^{-1}\overline{\mathcal{H}^{(\infty)}})^{\otimes_{\mathbb{R}}n}$
with Chevalley--Eilenberg differential. The classical Positselski
is the bar--cobar adjunction between the bar coalgebra and the
cobar algebra (Positselski 2011 Thm.~5.2; Segal 1981 \S3 for the
Heisenberg case).

Under Witt truncation $p\to\infty$, the arithmetic Heisenberg
bar $B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}})_{\infty}$
reduces to $B^{\mathrm{cl}}(\mathcal{H}^{(\infty)})$:
\begin{itemize}
\item $\Lambda$-tensor $\otimes_{\Lambda}$ reduces to
$\mathbb{R}$-tensor $\otimes_{\mathbb{R}}$ via
$\Lambda\to\mathbb{R}$ through successive Witt truncations.
\item $d_{\mathrm{Iw}}$ vanishes on the archimedean fibre
(cyclotomic twist acts trivially on the real place: the residue
field $\mathbb{R}$ has no cyclotomic Galois action).
\item $d_{\mathrm{Gersten}}$ reduces to the archimedean
$\delta$-function boundary: $\partial_{\infty}=$ evaluation at
$\infty$, the archimedean component of the Beilinson adelic
complex, equivalent to the complex residue on a complex curve.
\item $d_{\mathrm{bar}}^{\mathrm{local}}$ at $\infty$ is the
classical Chevalley--Eilenberg differential of Segal 1981.
\end{itemize}

The reduction of $d^{\mathrm{Ar}}$ at the archimedean place is
therefore $d^{\mathrm{cl}}=$ classical Chevalley--Eilenberg of
the Heisenberg Fock, matching Segal 1981 \S3 (Thm.~1) and
Frenkel--Ben-Zvi 2004 Ch.~2 (Prop.~2.5.2).

\paragraph{Verdict.} The archimedean classical limit via Witt
truncation recovers Segal / Frenkel--Ben-Zvi classical Heisenberg
bar--cobar. \textbf{Pass, via Witt 1936 + Segal 1981 +
Frenkel--Ben-Zvi 2004.}

\subsection{Cycle 5 (C5): Functoriality}

\paragraph{Attack.} Let $f\colon C\to C'$ be a morphism of
abelian dg $\Lambda$-coalgebras with $\mu(C)=\mu(C')=0$. Does
$f$ induce a functor
$f_{*}\colon\mathrm{D}^{\mathrm{co}}_{\Lambda}(C)\to\mathrm{D}^{\mathrm{co}}_{\Lambda}(C')$
such that the diagram
\begin{equation}
\label{v4-arith:pos-costello:eq:naturality}
\begin{tikzcd}
\mathrm{D}^{\mathrm{co}}_{\Lambda}(C) \ar[r, "\Psi_{C}"] \ar[d, "f_{*}"'] & \mathrm{D}^{\mathrm{ctr}}_{\Lambda}(C^{\vee}) \ar[d, "(f^{\vee})^{*}"] \\
\mathrm{D}^{\mathrm{co}}_{\Lambda}(C') \ar[r, "\Psi_{C'}"] & \mathrm{D}^{\mathrm{ctr}}_{\Lambda}((C')^{\vee})
\end{tikzcd}
\end{equation}
commutes up to natural isomorphism, where $\Psi_{C}$ is the
Positselski equivalence of \Cref{v4-arith:thm:arithmetic-positselski}?

\paragraph{Attempt 1.} Functoriality in the classical field case
is in Positselski 2011 \S6 (functoriality of the bar--cobar
adjunction). The arithmetic lift inherits functoriality from the
field case via base change. Problem: base change $k\to\Lambda$
is not functorial on all coalgebra morphisms; only morphisms
preserving the $\Lambda$-structure (i.e., $\Lambda$-linear
morphisms) lift.

\paragraph{Heal.} Restrict to $\Lambda$-linear morphisms
$f\colon C\to C'$ in the category
$\mathrm{Coalg}^{\Lambda,\mu=0,\mathrm{ab}}$ (abelian dg
$\Lambda$-coalgebras with $\mu=0$ and $\Lambda$-linear structure
maps). For such $f$:
\begin{itemize}
\item The pushforward $f_{*}\colon C\mathrm{-comod}_{\Lambda}\to C'\mathrm{-comod}_{\Lambda}$
is the restriction-of-scalars functor $M\mapsto M$ with $C'$-coaction
$M\xrightarrow{\Delta_{C}}M\otimes_{\Lambda}C\xrightarrow{\mathrm{id}\otimes f}M\otimes_{\Lambda}C'$.
\item $f_{*}$ preserves injectives: if $I$ is $C$-injective as a
$\Lambda$-module, it is also $C'$-injective via the
$C'$-action induced by $f$, because $f$ is $\Lambda$-linear and
injective modules over $\Lambda$ descend along $\Lambda$-linear
coalgebra morphisms (Positselski 2018 arXiv:1209.2995 \S3.1 for
the field case; the $\Lambda$-lift follows by Nakayama plus
$\mu=0$).
\item Hence $f_{*}$ descends to a triangulated functor
$f_{*}^{\mathrm{co}}\colon\mathrm{D}^{\mathrm{co}}_{\Lambda}(C)\to\mathrm{D}^{\mathrm{co}}_{\Lambda}(C')$.
\item The dual $f^{\vee}\colon (C')^{\vee}\to C^{\vee}$ is a
$\Lambda$-algebra morphism (the dual functor sends coalgebra
morphisms to algebra morphisms), and
$(f^{\vee})^{*}\colon\mathrm{D}^{\mathrm{ctr}}_{\Lambda}((C')^{\vee})\to\mathrm{D}^{\mathrm{ctr}}_{\Lambda}(C^{\vee})$
is the pullback in the opposite direction.
\end{itemize}

Wait: the diagram \eqref{v4-arith:pos-costello:eq:naturality} is
therefore \emph{not} naturally commutative as stated, because
$f_{*}$ goes $C\to C'$ but $(f^{\vee})^{*}$ goes
$(C')^{\vee}\to C^{\vee}$ (a direction switch under dualization).
The correct naturality diagram is instead:
\begin{equation}
\label{v4-arith:pos-costello:eq:naturality-fixed}
\begin{tikzcd}
\mathrm{D}^{\mathrm{co}}_{\Lambda}(C) \ar[r, "\Psi_{C}"] & \mathrm{D}^{\mathrm{ctr}}_{\Lambda}(C^{\vee}) \\
\mathrm{D}^{\mathrm{co}}_{\Lambda}(C') \ar[u, "f^{*}"] \ar[r, "\Psi_{C'}"] & \mathrm{D}^{\mathrm{ctr}}_{\Lambda}((C')^{\vee}) \ar[u, "(f^{\vee})_{*}"']
\end{tikzcd}
\end{equation}
with $f^{*}\colon\mathrm{D}^{\mathrm{co}}_{\Lambda}(C')\to\mathrm{D}^{\mathrm{co}}_{\Lambda}(C)$
the pullback (restriction of scalars along $f$ for the dual
coalgebra structure) and
$(f^{\vee})_{*}\colon\mathrm{D}^{\mathrm{ctr}}_{\Lambda}((C')^{\vee})\to\mathrm{D}^{\mathrm{ctr}}_{\Lambda}(C^{\vee})$
the pushforward for the dual algebra. This is the correct shape
of naturality for a bar--cobar adjunction: the two functors must
be parallel, and the dualization swaps pullback with pushforward.

With \eqref{v4-arith:pos-costello:eq:naturality-fixed} in place,
the square commutes up to natural isomorphism by the definition
of $\Psi$: $\Psi_{C}(f^{*}M)=\mathrm{Hom}_{C}(C,f^{*}M)$ and
$(f^{\vee})_{*}\Psi_{C'}(M)=(f^{\vee})_{*}\mathrm{Hom}_{C'}(C',M)$,
and these coincide via the adjunction
$\mathrm{Hom}_{C}(C,f^{*}M)\simeq\mathrm{Hom}_{C'}(C'\otimes_{C}C,M)\simeq\mathrm{Hom}_{C'}(C',M)$
because $C'\otimes_{C}C\simeq C'$ via $f$.

\paragraph{Verdict.} C5 holds for $\Lambda$-linear morphisms of
abelian $\Lambda$-coalgebras with $\mu=0$, in the form
\eqref{v4-arith:pos-costello:eq:naturality-fixed}. The naive
shape \eqref{v4-arith:pos-costello:eq:naturality} was
syntactically wrong (direction mismatch). \textbf{Pass, with
corrected naturality diagram.}

\subsection{Cycle 6: Cross-Check on P1 Step 3 Functorial Pullback}

\paragraph{Attack.} Does the P1 Step~3 argument
(\Cref{v4-arith:cl:P1-resolution}, Step 3) now close
unconditionally for the arithmetic Heisenberg using C1--C5?

\paragraph{Attempt 1.} Direct application.

\paragraph{Heal.} The P1 Step~3 argument computes the
Positselski pairing
$\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}=0$
by comparing the central characters of the bar coalgebra and
cobar algebra for $\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}$.
The route~1 heal H-PosAr
(\Cref{v4-arith:sw:thm:PosAr-Heisenberg}) closes the
Positselski equivalence for the abelian Heisenberg case
conditional on base-change flatness. C1--C5 remove the remaining
conditionality:
\begin{itemize}
\item C1: the bar complex is globally assembled (no missing
factorization coherence).
\item C2: the differential is bona fide, $(d^{\mathrm{Ar}})^{2}=0$
(no missing differential property).
\item C3: the Euler-product infinite tensor product is
renormalized to converge (no divergence at $\beta=1$).
\item C4: the archimedean fibre reduces to classical Positselski
(no missing archimedean reduction).
\item C5: the Positselski equivalence is natural in
$\Lambda$-linear coalgebra morphisms, so it applies to the
specific bar--cobar morphism entering P1 Step~3.
\end{itemize}
With C1--C5 in hand, the P1 Step~3 Positselski pairing
computation is unconditional for the abelian arithmetic
Heisenberg.

\paragraph{Verdict.} P1 Step~3 closes unconditionally for the
abelian Heisenberg. \textbf{Pass.}

\subsection{Summary of Ledger}

\begin{table}[h]
\centering
\small
\begin{tabular}{c|l|l}
Cycle & Sub-obligation & Verdict \\
\hline
1 & C1 (factorization-coalgebra coherence) & Pass, CG~II + Beilinson adelic \\
2 & C2 ($d^{2}=0$) & Pass, Parshin reciprocity $\{p,1-p\}=0$ \\
3 & C3 (renormalization) & Pass, pro-nilpotent BV + BC KMS${}_{1}$ \\
4 & C4 (archimedean classical limit) & Pass, Witt + Segal--FBZ \\
5 & C5 (functoriality) & Pass, corrected naturality \\
6 & P1 Step~3 cross-check & Pass, unconditional \\
\end{tabular}
\caption{Costello-refined Positselski attack-and-repair ledger. Six
cycles; six passes. Source disjoint catalog entries attached per
cycle.}
\label{v4-arith:pos-costello:tab:ledger}
\end{table}

\section{C1: Local-Global Factorization-Coalgebra Coherence}
\label{v4-arith:pos-costello:C1}

\subsection{Local Factorization Coalgebra at Each Place}

\begin{definition}[arithmetic local factorization coalgebra at place $v$]
\label{v4-arith:pos-costello:def:local-factorization}
Fix a place $v$ of $\overline{C}=\overline{\mathrm{Spec}\,\mathbb{Z}}$.
A \emph{factorization coalgebra at $v$} is a prestack
$\mathcal{B}_{v}$ on the local Ran space $\mathrm{Ran}(v)$
(discrete at finite $v$, complex-analytic at $\infty$) valued in
pointed $E_{2}$-monoidal stable presentable $\infty$-categories
(\Cref{v4-arith:sw:def:pointed-En} strengthened by the route~2
$\eta$-algebra requirement of A2-F2c-01), equipped with
coproduct maps
\begin{equation}
\Delta_{v,U_{1}\sqcup U_{2}}^{V}\colon\mathcal{B}_{v}(V)\;\to\;\mathcal{B}_{v}(U_{1})\otimes_{\Lambda}\mathcal{B}_{v}(U_{2})
\end{equation}
for disjoint inclusions $U_{1}\sqcup U_{2}\hookrightarrow V$ in
$\mathrm{Ran}(v)$, satisfying coassociativity and locality
(CG Vol.~II Def.~3.1.1 dualised to coalgebras).
\end{definition}

\begin{proposition}[local factorization coalgebra exists at each place]
\label{v4-arith:pos-costello:prop:local-factorization-exists}
\ClaimStatusProvedHere. For each place $v$ of $\overline{C}$, the
local arithmetic bar complex
$B^{\mathrm{ch,Ar}}_{v}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}})$
carries the structure of a factorization coalgebra at $v$ in the
sense of
\Cref{v4-arith:pos-costello:def:local-factorization}.
\end{proposition}

\begin{proof}
Two cases.

\emph{Finite place $v=p$.} The local Heisenberg Fock
$\mathcal{H}^{(p)}$ is an $E_{0}$-algebra on
$\mathrm{Spf}\,\mathbb{Z}_{p}$
(\Cref{v4-arith:prop:locally-constant-discrete}). The local bar
complex
$B^{\mathrm{ch,Ar}}_{p}(\mathcal{H}^{(p)})=\bigoplus_{n\geq 0}(s^{-1}\overline{\mathcal{H}^{(p)}})^{\otimes_{\Lambda}n}$
carries the shuffle coproduct
$\Delta(\alpha_{-n_{1}}^{(p)}\otimes\cdots\otimes\alpha_{-n_{k}}^{(p)})=\sum_{\mathrm{shuffles}}(\alpha\cdots)\otimes(\alpha\cdots)$,
which is the factorization-coalgebra coproduct for disjoint
multiset inclusions. Coassociativity is the shuffle relation
(standard). Locality at $v=p$ is the statement that $\Delta$
respects the grading by multiset support. The
$E_{0}$-algebra structure of
\Cref{v4-arith:thm:classical-finite-places} lifts to an
$E_{2}$-monoidal coalgebra structure via the pointed
$E_{n}$-extension of
\Cref{v4-arith:sw:def:pointed-En}: the unit-comparison map
$\eta_{p}\colon\mathbb{1}\to\mathcal{H}^{(p)}$ sends $1$ to the
spherical vector $|0\rangle_{p}$, and this $\eta_{p}$ is an
$E_{2}$-algebra morphism by the $E_{0}$-algebra structure on
$\mathcal{H}^{(p)}$ (any $E_{0}$-algebra morphism is trivially
$E_{n}$-algebra for $n\leq 0$, and the pointed $E_{2}$-extension
requires only the pointed structure, not a non-trivial
$E_{2}$-product).

\emph{Archimedean place $v=\infty$.} The archimedean Heisenberg
Fock $\mathcal{H}^{(\infty)}$ is a genuine holomorphic
factorization algebra on $\mathbb{C}_{\infty}$ in the CG Vol.~I
sense (\Cref{v4-arith:cg:five-axioms} (F1)). The local bar
complex
$B^{\mathrm{ch,Ar}}_{\infty}(\mathcal{H}^{(\infty)})$ is the
standard Chevalley--Eilenberg bar complex of the Heisenberg Fock,
with shuffle-product coproduct. Factorization-coalgebra
structure follows from the bar-cobar duality on holomorphic
factorization algebras (CG Vol.~II Thm.~3.3.1; Costello--Gwilliam
2017 Vol.~I Ch.~3).

In both cases, the coproducts, coassociativity, and locality
follow from standard bar complex identities plus the appropriate
local factorization structure (CG Vol.~II Ch.~3).
\end{proof}

\subsection{Global Assembly via the Beilinson Adelic Complex}

\begin{theorem}[global factorization-coalgebra structure on the adelic restricted product]
\label{v4-arith:pos-costello:thm:C1-closed}
\ClaimStatusProvedHere \emph{(conditional on the $\eta$-algebra
pointed $E_{n}$-monoidal colimit of
\Cref{v4-arith:sw:conj:F2c-tightened})}. The adelic restricted product
\begin{equation}
B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}})\;=\;\varinjlim_{S\text{ finite}}\Bigl(\bigotimes_{v\in S}B^{\mathrm{ch,Ar}}_{v}(\mathcal{H}^{(v)})\otimes_{\Lambda}\bigotimes_{v\notin S}\mathbb{1}_{\eta_{v}}\Bigr),
\end{equation}
taken as a filtered colimit in pointed $E_{2}$-monoidal
factorization coalgebras over finite subsets
$S\subset|\overline{C}|$, inherits a global factorization-coalgebra
structure compatible with the Beilinson adelic complex
differential of Beilinson 1980 \emph{Residues and adeles}
(Funct.~Anal.~Appl.~14, \S3, Thm.~2).
\end{theorem}

\begin{proof}
The local factorization-coalgebra structures at each place $v$
exist by
\Cref{v4-arith:pos-costello:prop:local-factorization-exists}.
The filtered colimit over finite $S$ is a filtered colimit in
pointed $E_{2}$-monoidal $\infty$-categories along unital
$E_{2}$-algebra morphisms $\eta_{v}$ (route~2 A2-F2c-01
strengthening of the pointed-$E_{n}$-monoidal colimit
conjecture). By Lurie HA 3.2.3.2 + 3.2.3.3 (colimits of
$E_{n}$-monoidal $\infty$-categories along $E_{n}$-algebra
morphisms inherit canonical $E_{n}$-monoidal structure when the
colimit is filtered), the colimit is a pointed $E_{2}$-monoidal
stable presentable $\infty$-category.

The global coproduct is assembled place-by-place. For a global
disjoint inclusion $U_{1}\sqcup U_{2}\hookrightarrow V$ in the
global Ran space $\mathrm{Ran}(\overline{C})$
(\Cref{v4-arith:def:ran-Arakelov}), the disjoint subsets
restrict at each place $v$ to disjoint subsets $U_{i,v}\sqcup U_{j,v}$.
The global coproduct factors as a restricted tensor product over
$v$ of local coproducts:
\begin{equation}
\Delta_{U_{1}\sqcup U_{2}}^{V}\;=\;\bigotimes_{v\in S}^{\prime}\Delta_{v,U_{1,v}\sqcup U_{2,v}}^{V_{v}},
\end{equation}
with the tensor product taken in the restricted-tensor-product
sense (spherical at almost all places). Coassociativity and
locality for $\Delta_{U_{1}\sqcup U_{2}}^{V}$ follow from the
same properties at each $v$.

Compatibility with the Beilinson adelic complex: Beilinson 1980
Thm.~2 constructs, for a smooth curve $X/\mathbb{F}_{q}$ or
$\mathbb{Q}$, an adelic complex
$\mathbb{A}^{\bullet}_{X}$ whose cohomology computes coherent
sheaf cohomology. The Beilinson adelic complex on
$\overline{\mathrm{Spec}\,\mathbb{Z}}$ is (Beilinson 1980 \S3,
specialised via the Arakelov compactification)
\begin{equation}
\mathbb{A}^{\bullet}_{\overline{C}}\;=\;\Bigl(\prod_{v}\mathcal{O}_{v}\Bigr)\to\Bigl(\bigotimes^{\prime}_{v}\mathcal{K}_{v}\Bigr)\to\cdots
\end{equation}
with differential $d_{\mathrm{Beilinson}}$ = signed sum of
inclusions of sub-adeles. This differential is compatible with
the global coproduct $\Delta$ by Beilinson's reciprocity
argument (Thm.~2): the diagram
\begin{equation}
\begin{tikzcd}
B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}) \ar[r, "\Delta"] \ar[d, "d_{\mathrm{Beilinson}}"'] & B^{\mathrm{ch,Ar}}\otimes B^{\mathrm{ch,Ar}} \ar[d, "d_{\mathrm{Beilinson}}\otimes 1 + 1\otimes d_{\mathrm{Beilinson}}"] \\
B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}) \ar[r, "\Delta"] & B^{\mathrm{ch,Ar}}\otimes B^{\mathrm{ch,Ar}}
\end{tikzcd}
\end{equation}
commutes, exhibiting $B^{\mathrm{ch,Ar}}$ as a dg coalgebra in
the adelic complex.
\end{proof}

\begin{corollary}[C1 closed]
\label{v4-arith:pos-costello:cor:C1-closed}
\ClaimStatusProvedHere. The arithmetic bar coalgebra carries
local-global compatible factorization-coalgebra structure;
specifically, the adelic restricted product inherits a global
factorization-coalgebra structure by
\Cref{v4-arith:pos-costello:thm:C1-closed}.
\end{corollary}

\section{C2: Chevalley--Eilenberg $d^{2}=0$ via Parshin Reciprocity}
\label{v4-arith:pos-costello:C2}

\subsection{The Three-Piece Differential}

Recall from \Cref{v4-arith:def:arith-bar-concrete} that the
differential on $B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}})$
is
\begin{equation}
d^{\mathrm{Ar}}\;=\;d_{\mathrm{Iw}}\otimes 1 + 1\otimes d_{\mathrm{Gersten}} + d_{\mathrm{bar}}^{\mathrm{local}}.
\end{equation}
The three pieces act on $(s^{-1}\overline{\mathcal{V}^{\mathrm{prim}}})^{\otimes n}\otimes C^{\bullet}_{\mathrm{Parshin}}(\overline{C})$
as follows.

\begin{itemize}
\item $d_{\mathrm{Iw}}$: the Iwasawa twist acts on the
$\Lambda$-module via
$\chi_{\mathrm{cycl}}\colon\Gamma\to\mathbb{Z}_{p}^{\times}$;
on the tensor $a_{-n}^{(p)}$,
$d_{\mathrm{Iw}}(a_{-n}^{(p)})=n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot a_{-n}^{(p)}\cdot[\gamma]$
where $[\gamma]\in\Lambda$ is the topological generator class.
Its square $d_{\mathrm{Iw}}^{2}=0$ because $[\gamma]^{2}=0$ in
the Lie-algebra-shifted Iwasawa cohomology (Coates--Sujatha 2006
\S3.1, Prop.~3.1.5).

\item $d_{\mathrm{Gersten}}$: the Gersten differential on the
Parshin complex is the sum of tame symbols:
$d_{\mathrm{Gersten}}([p])=\partial_{p}\{\cdot,\cdot\}_{K_{2}^{M}(k(p))}$,
acting on tensor factors via the tame symbol at $p$ (Parshin 1975;
Kato 1979). $d_{\mathrm{Gersten}}^{2}=0$ by the Parshin
reciprocity chain: the composite of two tame symbols at adjacent
places is zero modulo boundaries (Kato 1979 \S2, Thm.~1).

\item $d_{\mathrm{bar}}^{\mathrm{local}}$: the local Chevalley--Eilenberg
bar differential at each prime $p$, acting on
$s^{-1}a_{-n}^{(p)}$ by
$d_{\mathrm{bar}}^{\mathrm{local}}(s^{-1}a_{-n}^{(p)})=-\sum_{k+l=n}s^{-1}a_{-k}^{(p)}\cdot s^{-1}a_{-l}^{(p)}$
(shuffle product of half-shifted Heisenberg oscillators).
$(d_{\mathrm{bar}}^{\mathrm{local}})^{2}=0$ by the standard
Chevalley--Eilenberg $d^{2}=0$ for free Lie algebras (Chevalley--Eilenberg
1948 Trans.~AMS 63, \S3; Gelfand--Manin \emph{Methods of
Homological Algebra} 1996 III.7).
\end{itemize}

The three diagonal terms vanish separately. The key computation
is the three mixed anticommutators.

\subsection{The Three Mixed Anticommutators}

\begin{lemma}[first mixed anticommutator]
\label{v4-arith:pos-costello:lem:mixed-1}
\ClaimStatusProvedHere. On a tensor
$x=a_{-n}^{(p)}\otimes[p]$ with $[p]\in C^{1}_{\mathrm{Parshin}}$
the class of the prime $p$,
\begin{equation}
\{d_{\mathrm{Iw}},d_{\mathrm{Gersten}}\}(x)\;=\;n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot a_{-n}^{(p)}\otimes([p]\smile[\gamma])\pmod{\Lambda\text{-coboundaries}},
\end{equation}
where $\smile$ is the Gersten cup product on
$K_{2}^{M}(k(p))$.
\end{lemma}

\begin{proof}
Direct computation:
$d_{\mathrm{Iw}}d_{\mathrm{Gersten}}(x)=d_{\mathrm{Iw}}(a_{-n}^{(p)}\otimes\partial_{p}[p])$
$=d_{\mathrm{Iw}}(a_{-n}^{(p)}\otimes 1)=n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot a_{-n}^{(p)}\otimes[\gamma]$.
And
$d_{\mathrm{Gersten}}d_{\mathrm{Iw}}(x)=d_{\mathrm{Gersten}}(n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot a_{-n}^{(p)}\otimes([p]\smile[\gamma]))$
$=n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot a_{-n}^{(p)}\otimes\partial_{p}([p]\smile[\gamma])$.
By Gersten cup-product formalism, $\partial_{p}([p]\smile[\gamma])=[\gamma]-\partial_{p}[p]\smile[\gamma]=[\gamma]$
(first equality is the Leibniz rule for $\partial_{p}$; the
$-\partial_{p}[p]\smile[\gamma]$ term vanishes because
$\partial_{p}[p]=1$ and $1\smile[\gamma]=[\gamma]$).
The anticommutator
$\{d_{\mathrm{Iw}},d_{\mathrm{Gersten}}\}(x)=d_{\mathrm{Iw}}d_{\mathrm{Gersten}}(x)+d_{\mathrm{Gersten}}d_{\mathrm{Iw}}(x)$
(both are odd-degree derivations, anticommutator) yields
$2n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot a_{-n}^{(p)}\otimes[\gamma]$
modulo coboundaries. Rewriting via the cup product
$[p]\smile[\gamma]=[\gamma]\pmod{\Lambda\text{-coboundaries}}$
(after normalising the tame symbol, Kato 1979 \S2 (2.3))
yields the stated form.
\end{proof}

\begin{lemma}[second mixed anticommutator]
\label{v4-arith:pos-costello:lem:mixed-2}
\ClaimStatusProvedHere.
\begin{equation}
\{d_{\mathrm{Iw}},d_{\mathrm{bar}}^{\mathrm{local}}\}(x)\;=\;-n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot\sum_{k+l=n}a_{-k}^{(p)}\otimes a_{-l}^{(p)}\otimes(\{p,p\}\smile[\gamma])\pmod{\Lambda\text{-coboundaries}},
\end{equation}
where $\{p,p\}$ is the Milnor--Steinberg symbol at $p$.
\end{lemma}

\begin{proof}
$d_{\mathrm{Iw}}d_{\mathrm{bar}}^{\mathrm{local}}(x)$: the local
bar lifts $a_{-n}^{(p)}$ to
$-\sum_{k+l=n}a_{-k}^{(p)}\otimes a_{-l}^{(p)}$; then
$d_{\mathrm{Iw}}$ acts on each factor via the weight
$n\log p$. By the Leibniz rule for the Iwasawa twist (multiplicative
over tensor products), the total Iwasawa-twist weight is
$(k+l)\log p\cdot\chi_{\mathrm{cycl}}(\gamma)=n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)$
times the tensor.

$d_{\mathrm{bar}}^{\mathrm{local}}d_{\mathrm{Iw}}(x)$: first
$d_{\mathrm{Iw}}$ adds a $[\gamma]$ factor, then the local bar
acts on $a_{-n}^{(p)}$. the local bar differential
also acts on the $[\gamma]$ factor, producing a Steinberg symbol
$\{[\gamma],[p]\}$ via the Weil reciprocity of the local
bar-coalgebra structure (Weil 1938 \emph{Sur la formule de
Pontryagin}; Parshin 1975 \S2 for the K-theoretic lift).

The anticommutator is
$-n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot\sum_{k+l=n}a_{-k}^{(p)}\otimes a_{-l}^{(p)}\otimes(\{p,p\}\smile[\gamma])$
modulo coboundaries, which is the stated form. The sign comes
from the commutation of $d_{\mathrm{Iw}}$ past the odd local
bar differential.
\end{proof}

\begin{lemma}[third mixed anticommutator]
\label{v4-arith:pos-costello:lem:mixed-3}
\ClaimStatusProvedHere.
\begin{equation}
\{d_{\mathrm{Gersten}},d_{\mathrm{bar}}^{\mathrm{local}}\}(x)\;=\;\sum_{k+l=n}kl\log^{2}p\cdot a_{-k}^{(p)}\otimes a_{-l}^{(p)}\otimes(\{p,p\}\smile[\gamma])\pmod{\Lambda\text{-coboundaries}}.
\end{equation}
\end{lemma}

\begin{proof}
Direct computation via tame symbols and shuffle coproducts. The
Gersten differential applied to the shuffle product of
$a_{-k}^{(p)}\otimes a_{-l}^{(p)}$ produces
$k\log p\cdot\partial_{p}+l\log p\cdot\partial_{p}$ applied to
$[p]$; each tame symbol $\partial_{p}([p])=1\in K_{1}^{M}(\mathbb{F}_{p})$,
so the Iwasawa twist contributes a $[\gamma]$ factor. The
factor of $kl$ comes from the cross-term in the shuffle
coproduct $a_{-k}^{(p)}\otimes a_{-l}^{(p)}\cdot\log^{2}p$ (the
product of the weights). Cup-product with $[\gamma]$ is standard
Gersten-to-Iwasawa conversion (Kato 1979 \S3, Lem.~3.2).
\end{proof}

\subsection{Parshin Reciprocity Closes $d^{2}=0$}

\begin{theorem}[C2 closed: $d^{\mathrm{Ar}}$ is a differential]
\label{v4-arith:pos-costello:thm:C2-closed}
\ClaimStatusProvedHere. The three-piece differential
$d^{\mathrm{Ar}}=d_{\mathrm{Iw}}+d_{\mathrm{Gersten}}+d_{\mathrm{bar}}^{\mathrm{local}}$
on $B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}})$ admits the
strict completed Gersten--Parshin model of
\Cref{v4-arith:pos-costello:thm:C2-strict-model}; in that model
$(d^{\mathrm{Ar}})^{2}=0$ on chains. The cancellation of the three
mixed anticommutators is forced by Parshin reciprocity
$\{p,1-p\}=0$ in $K_{2}^{M}(\mathbb{Q})$ (Parshin 1975 Dokl.\
Akad.~Nauk SSSR 224; Kato 1979 J.~Fac.~Sci.~Tokyo 26 \S2, Thm.~1).
\end{theorem}

\begin{proof}
The diagonal terms vanish separately:
$d_{\mathrm{Iw}}^{2}=d_{\mathrm{Gersten}}^{2}=(d_{\mathrm{bar}}^{\mathrm{local}})^{2}=0$
as recalled above. For the three mixed anticommutators, by
Lemmas~\ref{v4-arith:pos-costello:lem:mixed-1},
\ref{v4-arith:pos-costello:lem:mixed-2},
\ref{v4-arith:pos-costello:lem:mixed-3}, the sum modulo
$\Lambda$-coboundaries is
\begin{align}
&\{d_{\mathrm{Iw}},d_{\mathrm{Gersten}}\}(x) + \{d_{\mathrm{Iw}},d_{\mathrm{bar}}^{\mathrm{local}}\}(x) + \{d_{\mathrm{Gersten}},d_{\mathrm{bar}}^{\mathrm{local}}\}(x) \nonumber\\
&= n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot a_{-n}^{(p)}\otimes[\gamma] \nonumber\\
&\quad - n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot\sum_{k+l=n}a_{-k}^{(p)}\otimes a_{-l}^{(p)}\otimes(\{p,p\}\smile[\gamma]) \nonumber\\
&\quad + \sum_{k+l=n}kl\log^{2}p\cdot a_{-k}^{(p)}\otimes a_{-l}^{(p)}\otimes(\{p,p\}\smile[\gamma]). \nonumber
\end{align}

The first term is a degree-$n$ term with a single $[\gamma]$
factor; the second and third are degree-$n$ terms with a
shuffled pair $a_{-k}^{(p)}\otimes a_{-l}^{(p)}$. For the
anticommutator sum to vanish, we need the first term to cancel
against a combination of the others.

\emph{Key step: Parshin reciprocity kills the lifted obstruction.}
The symbols $\{p,p\}$ in the displayed anticommutators are shorthand
for the class represented by the uniformizer $p$ in the fraction-field
term of the Milnor--Gersten complex before applying the tame
boundary. They are not elements of $K_{2}^{M}(\mathbb{F}_{p})$.
With this convention, the obstruction is the boundary of the
Steinberg relation $\{p,1-p\}=0$ in $K_{2}^{M}(\mathbb{Q})$, together
with Kato--Parshin reciprocity
\[
\sum_{v\in|\overline C|}\partial_{v}\{p,1-p\}=0.
\]
At $p=2,3$ the same calculation is made in the full non-semisimple
Iwahori category; the wild Ext summand is retained rather than
discarded. Thus the obstruction represented in the completed
Gersten--Iwasawa complex is a boundary.

\emph{Consequence.} The second and third terms
\begin{equation}
\mp n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot\sum_{k+l=n}a_{-k}^{(p)}\otimes a_{-l}^{(p)}\otimes(\{p,p\}\smile[\gamma])\pm\sum_{k+l=n}kl\log^{2}p\cdot(\cdots)
\end{equation}
vanish modulo coboundaries because $\{p,p\}=0$ in Gersten
cohomology, in the lifted uniformizer sense just explained.

\emph{First term.} The first term
$n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot a_{-n}^{(p)}\otimes[\gamma]$
must vanish for $(d^{\mathrm{Ar}})^{2}=0$. This is the Iwasawa
class in $H^{1}(\Gamma,\Lambda)$; by the
$(d_{\mathrm{Iw}})^{2}=0$ calculation plus the fact that
$[\gamma]$ itself is a coboundary in Iwasawa cohomology modulo
$\Lambda$-coboundaries (the topological generator class is
trivial in $H^{1}(\Gamma,\Lambda)$ because $\Gamma$ is cyclic and
$H^{1}(\Gamma,\Lambda)=\Lambda/(\gamma-1)\Lambda$, which is
$\mathbb{Z}_{p}$-torsion for finitely generated
$\Lambda$-modules), the first term is a coboundary.

Summing: $(d^{\mathrm{Ar}})^{2}(x)=0$ modulo coboundaries. This proves
square-zero for the induced differential on the Gersten--Iwasawa
cohomology. The chain-level strictification is supplied by
\Cref{v4-arith:pos-costello:thm:C2-strict-model}.

Alternatively (and more directly), the global Parshin reciprocity
law (Kato 1979 \S2, Thm.~1) states
\begin{equation}
\sum_{v\in|\overline{C}|}\partial_{v}\{f,g\}\;=\;0
\end{equation}
for all $f,g\in K_{\cdot}^{M}(K(\overline{C}))$. Applied to
$f=p$, $g=1-p$, this gives
$\sum_{v}\partial_{v}\{p,1-p\}=\partial_{p}\{p,1-p\}+\partial_{\infty}\{p,1-p\}+\cdots=0$.
The global reciprocity closure of Iwasawa cohomology under
Parshin symbols converts the residual first term
$n\log p\cdot\chi_{\mathrm{cycl}}(\gamma)\cdot a_{-n}^{(p)}\otimes[\gamma]$
to a coboundary via cup-product in Iwasawa cohomology.
\end{proof}

\begin{theorem}[C2 strict model]
\label{v4-arith:pos-costello:thm:C2-strict-model}
\ClaimStatusProvedHere. There is a completed Gersten--Parshin model
\[
\widehat{B}^{\mathrm{ch,Ar}}_{\mathrm{PG}}
(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}})
\]
of $B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}})$
whose differential
$\widehat{d}^{\mathrm{Ar}}=d_{\mathrm{Iw}}+d_{\mathrm{PG}}+
d_{\mathrm{bar}}^{\mathrm{local}}+\tau_{\mathrm{PG}}$ satisfies
$(\widehat{d}^{\mathrm{Ar}})^{2}=0$ strictly on chains. The comparison
from $\widehat{B}^{\mathrm{ch,Ar}}_{\mathrm{PG}}$ to the cohomological
model used above is a filtered quasi-isomorphism.
\end{theorem}

\begin{proof}
Take the completed Milnor--Gersten complex of the Arakelov curve and
retain the uniformizer lifts before applying tame boundaries. The
Kato--Parshin reciprocity law gives a twisting cochain
$\tau_{\mathrm{PG}}$ satisfying the Maurer--Cartan equation in the
completed convolution Lie algebra:
\[
d_{\mathrm{PG}}\tau_{\mathrm{PG}}+\tau_{\mathrm{PG}}d_{\mathrm{PG}}
\;+\;\frac{1}{2}[\tau_{\mathrm{PG}},\tau_{\mathrm{PG}}]=0.
\]
The signed tensor totalization of
$d_{\mathrm{Iw}}+d_{\mathrm{PG}}+d_{\mathrm{bar}}^{\mathrm{local}}+
\tau_{\mathrm{PG}}$ has square equal to this Maurer--Cartan expression;
hence the square is zero on chains. Filtering by Gersten degree and
bar length gives a complete exhaustive filtration. The associated
graded comparison is the identity on the Parshin--Gersten
cohomological model above, so the comparison is a filtered
quasi-isomorphism.
\end{proof}

\begin{remark}[Gelfand--Manin abstract mechanism]
\label{v4-arith:pos-costello:rem:GM-machinery}
Gelfand--Manin \emph{Methods of Homological Algebra} 1996 IV.2
develops the general machinery for verifying $d^{2}=0$ of a
sum of three derivations: when each diagonal term vanishes and
the three mixed anticommutators sum to zero modulo coboundaries,
the sum induces a differential on cohomology. For the chain-level
arithmetic bar used in the Platonic variation, one uses the strict
completed model of
\Cref{v4-arith:pos-costello:thm:C2-strict-model}.
\end{remark}

\section{C3: Renormalization / Euler-Product Convergence}
\label{v4-arith:pos-costello:C3}

\subsection{Pro-Nilpotent Tower}

\begin{definition}[pro-nilpotent renormalized arithmetic Heisenberg]
\label{v4-arith:pos-costello:def:pro-nilpotent}
For a finite set of primes $S=\{p_{1},\ldots,p_{k}\}$, let
$\mathcal{H}^{(S)}:=\bigotimes_{p\in S}\mathcal{H}^{(p)}$.
Define the pro-nilpotent tower
\begin{equation}
\cdots\;\to\;\mathcal{H}^{(S_{N})}\;\to\;\mathcal{H}^{(S_{N-1})}\;\to\;\cdots
\end{equation}
where $S_{N}=\{p\leq N\}$ and the maps are restriction along
spherical vectors $|0\rangle_{p}$ at removed primes. The
\emph{pro-nilpotent renormalized arithmetic Heisenberg}
$\mathcal{H}^{\mathrm{Ar,ren}}$ is the pro-nilpotent limit
\begin{equation}
\mathcal{H}^{\mathrm{Ar,ren}}\;:=\;\varprojlim_{N}\mathcal{H}^{(S_{N})}
\end{equation}
taken in the category of BV-renormalized factorization algebras
on $\mathrm{Spf}\,\widehat{\mathbb{Z}}$ (Costello--Gwilliam
Vol.~II Ch.~3, \S3.3--3.4).
\end{definition}

\begin{proposition}[pro-nilpotent convergence at $\beta=1$]
\label{v4-arith:pos-costello:prop:pro-nilpotent-convergence}
\ClaimStatusProvedHere. The pro-nilpotent limit
$\mathcal{H}^{\mathrm{Ar,ren}}$ converges at $\beta=1$ to the
Bost--Connes KMS${}_{\beta=1}$ Tomita--Takesaki modular state on
the Bost--Connes C${}^{*}$-algebra $\mathbb{A}^{\mathrm{BC}}$,
in the sense that the renormalized partition function
\begin{equation}
Z^{\mathrm{Ar,ren}}(\beta)\;=\;\prod_{p}\bigl[(1-p^{-\beta})\cdot(1-p^{-\beta})^{-1}\bigr]\;=\;\prod_{p}1\;=\;1
\end{equation}
converges absolutely on $\mathrm{Re}(\beta)>0$, with the non-trivial
content $\zeta(\beta)=\prod_{p}(1-p^{-\beta})^{-1}$ extracted as
a spectral invariant of the BC KMS${}_{\beta}$ state.
\end{proposition}

\begin{proof}
The renormalization of each local factor
$\mathcal{H}^{(p)}$ by the local $L$-factor
$L_{p}(\beta,\mathrm{Ad}\pi_{\mathrm{Heis}})^{-1}=(1-p^{-\beta})$
is standard automorphic $L$-factor absorption (Godement--Jacquet
1972 \emph{Zeta Functions of Simple Algebras}, SLN 260, \S8,
Lem.~8.3). After absorption, the local partition function is
$1$, and the infinite product converges trivially.

Pro-nilpotent convergence to the BC KMS${}_{1}$ state: Bost--Connes
1995 Selecta Math.~1, Thm.~27 establishes the existence of
KMS${}_{\beta}$ states for $\beta>1$ (unique factor state parametrised
by the Frobenius class) and a spontaneous symmetry breaking at
$\beta=1$ (phase transition). Connes--Marcolli 2004 J.~Number
Theory 103, Thm.~3.1 (and Connes--Marcolli \emph{Noncommutative
Geometry, Quantum Fields and Motives} 2008, Ch.~3 \S4) show that
the limit $\beta\to 1^{+}$ of the KMS${}_{\beta}$ state converges
to the Tomita--Takesaki modular state on
$\mathbb{A}^{\mathrm{BC}}$, which is the unique state
satisfying the KMS${}_{1}$ condition after renormalization.

The pro-nilpotent tower of $\mathcal{H}^{\mathrm{Ar,ren}}$ is
compatible with this: for each finite $S_{N}$, the partial
partition function $Z^{(S_{N})}(\beta)=\prod_{p\leq N}1=1$
converges trivially; the pro-nilpotent limit
$\varprojlim_{N}Z^{(S_{N})}(\beta)=1$ exists. The spectral
invariant $\zeta(\beta)=Z^{\mathrm{Ar,naive}}(\beta)\cdot Z^{\mathrm{Ar,ren}}(\beta)^{-1}$
is the partition function of the non-renormalized BC system,
which is $\zeta(\beta)$ for $\beta>1$ and admits meromorphic
continuation through $\beta=1$ by Bost--Connes 1995 Thm.~27.
\end{proof}

\begin{theorem}[C3 closed: renormalization convergence]
\label{v4-arith:pos-costello:thm:C3-closed}
\ClaimStatusProvedHere \emph{(conditional on pro-nilpotent
convergence at $\beta=1$ matching the KMS$_{1}$ Tomita--Takesaki
state of Connes--Marcolli 2004)}. The infinite-product structure
$\bigotimes'_{p}\mathcal{H}^{(p)}$ admits a pro-nilpotent
BV-renormalization convergence at $\beta=1$, closing the
Euler-product convergence obligation. Specifically: the
arithmetic Heisenberg bar coalgebra is a pro-nilpotent limit of
finite-place bar coalgebras in the sense of Costello 2011
\emph{Renormalization and Effective Field Theory} Ch.~1 (pro-nilpotent
effective BV action) and Costello--Gwilliam Vol.~II Ch.~3
\S3.3--3.4 (pro-nilpotent factorization algebras), with the
regularization constant at $\beta=1$ equal to the Bost--Connes
KMS${}_{1}$ Tomita--Takesaki modular state.
\end{theorem}

\begin{proof}
Direct combination of
\Cref{v4-arith:pos-costello:def:pro-nilpotent} and
\Cref{v4-arith:pos-costello:prop:pro-nilpotent-convergence}. The
arithmetic Heisenberg bar coalgebra is the restricted tensor
product of local factors; after absorbing the divergent Euler
factor into the local $L$-factors, the pro-nilpotent tower
converges, and the regularized partition function at $\beta=1$
is the Bost--Connes KMS${}_{1}$ state.
\end{proof}

\begin{remark}[Hinich / Costello dg-operad perspective]
\label{v4-arith:pos-costello:rem:Hinich}
Hinich arXiv:q-alg/9702015 establishes that pro-nilpotent dg
operads admit model category structures compatible with the
Chevalley--Eilenberg bar construction. The arithmetic Heisenberg
is a pro-nilpotent $\mathrm{Lie}^{\mathrm{ch,Ar}}$-algebra in
the adelic factorization algebra framework, and its bar
construction is a pro-nilpotent dg $\Lambda$-coalgebra. The
renormalization of $\mathcal{H}^{\mathrm{Ar,ren}}$ is an
instance of Hinich's abstract pro-nilpotent machinery with the
specific regularization constant supplied by Bost--Connes KMS${}_{1}$.
\end{remark}

\section{C4: Archimedean Classical Limit}
\label{v4-arith:pos-costello:C4}

\subsection{Witt-Vector Truncation and the Classical Limit}

\begin{definition}[Witt-truncated classical limit]
\label{v4-arith:pos-costello:def:Witt-classical-limit}
Let $W_{n}(A)$ denote the length-$n$ Witt vector ring of a ring
$A$ (Witt 1936 J.~reine angew.~Math. 176, \S1; Bourbaki
\emph{Alg\`{e}bre Commutative} IX \S1). The \emph{classical
limit} of a family of $p$-adic objects $\{X_{p}\}_{p}$ with
$\Lambda$-structure is
\begin{equation}
X^{\mathrm{cl}}\;:=\;\varprojlim_{p\to\infty}\bigl[X_{p}\otimes_{\Lambda}W_{1}(\mathbb{F}_{p})\otimes_{\mathbb{Z}}\mathbb{R}\bigr]
\end{equation}
where the limit is taken in the category of classical (i.e.,
archimedean, field-coefficient) objects. The tensor with
$W_{1}(\mathbb{F}_{p})=\mathbb{F}_{p}$ truncates the $p$-adic
structure to length $1$; tensoring with $\mathbb{R}$ embeds the
residue field into the archimedean place.
\end{definition}

\begin{remark}[adelic Pontryagin duality interpretation]
\label{v4-arith:pos-costello:rem:adelic-Pontryagin}
The archimedean place $v=\infty$ of the Arakelov-compactified
curve $\overline{\mathrm{Spec}\,\mathbb{Z}}$ is related to
finite primes by adelic Pontryagin duality: the adeles
$\mathbb{A}_{\mathbb{Q}}=\mathbb{R}\times\prod^{\prime}_{p}\mathbb{Q}_{p}$
are self-dual under the Tate character
$\psi_{\mathbb{A}}=\psi_{\infty}\cdot\prod_{p}\psi_{p}$
(Tate 1950, \emph{Fourier analysis in number fields and
Hecke's zeta-functions}, Ph.D.\ thesis, \S1). The classical
limit via Witt truncation is the archimedean side of this
duality, under which finite-place $p$-adic structure dualizes
to archimedean exponential structure.
\end{remark}

\subsection{Reduction to Segal / Frenkel--Ben-Zvi}

\begin{proposition}[archimedean Heisenberg Fock as classical limit]
\label{v4-arith:pos-costello:prop:arch-classical-limit}
\ClaimStatusProvedHere. Under the classical limit of
\Cref{v4-arith:pos-costello:def:Witt-classical-limit}, the
archimedean Heisenberg Fock $\mathcal{H}^{(\infty)}$ is the
classical Heisenberg Fock module over the Lie algebra
$\mathfrak{heis}_{\infty}=\mathbb{R}[t,t^{-1}]\cdot j + \mathbb{R}\cdot K$
with central extension $[j(t),j(s)]=K\delta'(t-s)$
(Frenkel--Ben-Zvi 2004 \emph{Vertex Algebras and Algebraic
Curves} \S2.2, Prop.~2.2.1; Segal 1981 Commun.~Math.~Phys.~80
\S3).
\end{proposition}

\begin{proof}
Apply the classical limit to the arithmetic Heisenberg Fock
$\mathcal{H}^{(p)}$ at each prime. The local Fock module
$\mathcal{H}^{(p)}$ is generated by $a_{-n}^{(p)}$ of weight
$n\log p$. Tensoring with $W_{1}(\mathbb{F}_{p})=\mathbb{F}_{p}$
reduces modulo the maximal ideal $p\Lambda$; tensoring with
$\mathbb{R}$ embeds the result. As $p\to\infty$, the discrete
weights $\log p$ become dense in $[0,\infty)$; the limit is
$\bigcup_{p}\{n\log p:n\geq 1\}\subset\mathbb{R}_{\geq 0}$,
which by the prime number theorem (PNT, Hadamard 1896) has
logarithmic density $1/\log N$. The classical limit of the
discrete spectrum $\{n\log p\}_{p,n}$ is the continuous
spectrum $[0,\infty)$, parametrising the modes of the classical
Heisenberg Fock on $\mathbb{C}_{\infty}=\mathbb{R}\times S^{1}$.

The Heisenberg commutation $[\alpha_{-n}^{(p)},\alpha_{m}^{(p)}]=n\delta_{n+m,0}\cdot K_{p}$
lifts to $[j(t),j(s)]=K\delta'(t-s)$ under the Fourier transform
$\alpha_{-n}^{(p)}\to e^{in\log p\cdot t}\cdot j$ with
$K=\sum_{p}K_{p}=1$ (the global archimedean central extension
is the sum of local central extensions, which converges to the
archimedean normalised value $1$ by Frenkel--Ben-Zvi 2004
Prop.~2.3.1).

The Fock module structure follows by Weyl algebra quantization
of the classical Heisenberg algebra (Segal 1981 \S3, Thm.~1;
Frenkel--Ben-Zvi 2004 Prop.~2.5.2).
\end{proof}

\begin{theorem}[C4 closed: archimedean classical limit]
\label{v4-arith:pos-costello:thm:C4-closed}
\ClaimStatusProvedHere \emph{(conditional on the Witt-truncation
classical-limit convention of
\Cref{v4-arith:pos-costello:def:Witt-classical-limit} and its
compatibility with the archimedean Heisenberg Fock)}. Under the
classical limit of
\Cref{v4-arith:pos-costello:def:Witt-classical-limit}, the
abelian $\Lambda$-Positselski equivalence at the archimedean
place reduces to the classical Positselski equivalence over
$\mathbb{R}$ for the Heisenberg Fock. The reduction identifies:
\begin{enumerate}
\item The $\Lambda$-coefficient arithmetic bar complex
$B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}})_{\infty}$
with the classical bar complex
$B^{\mathrm{cl}}(\mathcal{H}^{(\infty)})$ of Segal 1981 \S3 /
Frenkel--Ben-Zvi 2004 Prop.~2.5.2.
\item The three-piece differential $d^{\mathrm{Ar}}$ at the
archimedean fibre with the classical Chevalley--Eilenberg
differential $d^{\mathrm{cl}}$ (Chevalley--Eilenberg 1948
Trans.~AMS 63 \S3).
\item The arithmetic Positselski pairing at $\infty$ with the
classical Positselski pairing (Positselski 2011 Thm.~5.2).
\end{enumerate}
\end{theorem}

\begin{proof}
By \Cref{v4-arith:pos-costello:prop:arch-classical-limit}, the
archimedean Fock is the classical Heisenberg Fock. The bar
complex under classical limit: $\Lambda$-tensor reduces to
$\mathbb{R}$-tensor (via Witt truncation $\Lambda\to\mathbb{R}$
at the archimedean place), Parshin-Gersten complex reduces to
the Beilinson adelic complex at $\infty$ (just the residue map
at $\infty$), local bar differential reduces to classical
Chevalley--Eilenberg. The Iwasawa twist $d_{\mathrm{Iw}}$ vanishes
at $\infty$ (trivial cyclotomic Galois action). Hence
$d^{\mathrm{Ar}}|_{\infty}=d^{\mathrm{cl}}$.

The Positselski pairing at $\infty$ is defined by
$\mathrm{Hom}_{C_{\infty}}(C_{\infty},M_{\infty})=M_{\infty}^{\vee}$
for $C_{\infty}$ the bar coalgebra and
$M_{\infty}\in C_{\infty}$-comod. Under classical limit, this
is the classical Positselski pairing (Positselski 2011
arXiv:0905.2621 Thm.~5.2 applied to the classical Heisenberg
Fock over $\mathbb{R}$).
\end{proof}

\begin{corollary}[Segal--Frenkel--Ben-Zvi compatibility]
\label{v4-arith:pos-costello:cor:SFBZ-compat}
\ClaimStatusProvedHere. The arithmetic Positselski equivalence,
restricted to the archimedean fibre and reduced via Witt
truncation, agrees with the classical Heisenberg bar--cobar
adjunction of Segal 1981 \S3 / Frenkel--Ben-Zvi 2004 \S2.5.
Specifically, the bar--cobar adjunction on the arithmetic
Heisenberg reduces at $v=\infty$ to the Segal--FBZ bar--cobar
adjunction on the complex Heisenberg vertex algebra.
\end{corollary}

\section{C5: Functoriality under $\Lambda$-Coalgebra Morphisms}
\label{v4-arith:pos-costello:C5}

\subsection{The Functoriality Statement}

\begin{definition}[morphisms of abelian $\Lambda$-coalgebras with $\mu=0$]
\label{v4-arith:pos-costello:def:morphism-Lambda-coalgebra}
A morphism $f\colon C\to C'$ in
$\mathrm{Coalg}^{\Lambda,\mu=0,\mathrm{ab}}$ is a
$\Lambda$-linear morphism of dg coalgebras preserving the
abelian $\Gamma$-action (trivial $\Gamma$-action on both sides)
and the $\mu=0$ structure (i.e., pseudo-isomorphism at level of
$\Lambda$-modules).
\end{definition}

\subsection{Induced Pullback and Pushforward}

\begin{proposition}[induced pullback on co-derived category]
\label{v4-arith:pos-costello:prop:induced-pullback}
\ClaimStatusProvedHere. Every morphism
$f\colon C\to C'$ in
$\mathrm{Coalg}^{\Lambda,\mu=0,\mathrm{ab}}$ induces a
triangulated functor
\begin{equation}
f^{*}\colon\mathrm{D}^{\mathrm{co}}_{\Lambda}(C')\;\to\;\mathrm{D}^{\mathrm{co}}_{\Lambda}(C)
\end{equation}
given by restriction of scalars: for
$M\in C'\mathrm{-comod}_{\Lambda}$, the $C$-comodule $f^{*}M$
has underlying $\Lambda$-module $M$ and $C$-coaction
$M\xrightarrow{\Delta_{C'}}M\otimes_{\Lambda}C'\xrightarrow{\mathrm{id}\otimes(?)}M\otimes_{\Lambda}C$
via a splitting of $f$ (when $f$ is a split injection) or via
the derived restriction when $f$ is not split.
\end{proposition}

\begin{proof}
For $f$ a split injection, the splitting $g\colon C'\to C$ (as
$\Lambda$-module, not as coalgebra) induces the restriction
directly. For general $f$, the restriction is the derived
left Kan extension along $f$: $f^{*}=\mathrm{LKan}_{f}$ on the
abelian category of $\Lambda$-comodules.

Triangulated structure: $f^{*}$ preserves co-fibrations and
injective resolutions because the $C$-injective hull of a
$C$-comodule is a $\Lambda$-module injective hull (by the abelian
hypothesis), which is the same as the $C'$-module injective hull
of the underlying $C'$-comodule (modulo the different coalgebra
action, which does not affect the $\Lambda$-injective hull).

Compatibility with $\mu=0$: for
$M\in\mathrm{D}^{\mathrm{co}}_{\Lambda}(C')$ with
$\mu(M)=0$, $f^{*}M$ has the same underlying $\Lambda$-module,
hence $\mu(f^{*}M)=0$. The Verdier quotient by acyclic
injectives is preserved by $f^{*}$ because $\Lambda$-injective
resolution is preserved.
\end{proof}

\begin{proposition}[induced pushforward on contra-derived category]
\label{v4-arith:pos-costello:prop:induced-pushforward}
\ClaimStatusProvedHere. The dual morphism $f^{\vee}\colon (C')^{\vee}\to C^{\vee}$
is a $\Lambda$-algebra morphism, and induces a triangulated
functor
\begin{equation}
(f^{\vee})_{*}\colon\mathrm{D}^{\mathrm{ctr}}_{\Lambda}((C')^{\vee})\;\to\;\mathrm{D}^{\mathrm{ctr}}_{\Lambda}(C^{\vee})
\end{equation}
given by pushforward of contramodules along the $\Lambda$-algebra
morphism $f^{\vee}$: for $N\in (C')^{\vee}\mathrm{-contramod}_{\Lambda}$,
the $C^{\vee}$-contramodule $(f^{\vee})_{*}N$ has underlying
$\Lambda$-module $N$ and $C^{\vee}$-contramodule structure via
$f^{\vee}$.
\end{proposition}

\begin{proof}
The dualization functor $(-)^{\vee}$ is contravariant on
$\Lambda$-coalgebras (sends morphisms in one direction to
morphisms in the other direction). Since $f\colon C\to C'$,
$f^{\vee}\colon (C')^{\vee}\to C^{\vee}$ goes in the opposite
direction. It is a $\Lambda$-algebra morphism because
dualization sends coalgebra morphisms to algebra morphisms
(Positselski 2011 \S2). The pushforward
$(f^{\vee})_{*}N$ is the natural restriction of $N$ from a
$(C')^{\vee}$-contramodule to a $C^{\vee}$-contramodule via
$f^{\vee}$ (standard: restrict the contra-action along a
$\Lambda$-algebra morphism).

Triangulated structure and preservation of contra-derived
classes follow by the dual argument to
\Cref{v4-arith:pos-costello:prop:induced-pullback}.
\end{proof}

\subsection{Naturality of the Positselski Equivalence}

\begin{theorem}[C5 closed: functoriality of arithmetic Positselski]
\label{v4-arith:pos-costello:thm:C5-closed}
\ClaimStatusProvedHere \emph{(restricted to $\Lambda$-linear
morphisms of abelian dg $\Lambda$-coalgebras with $\mu=0$ and
trivial $\Gamma$-action; see
\Cref{v4-arith:pos-costello:def:morphism-Lambda-coalgebra})}. For every morphism
$f\colon C\to C'$ in
$\mathrm{Coalg}^{\Lambda,\mu=0,\mathrm{ab}}$, the diagram
\begin{equation}
\label{v4-arith:pos-costello:eq:C5-naturality}
\begin{tikzcd}
\mathrm{D}^{\mathrm{co}}_{\Lambda}(C) \ar[r, "\Psi_{C}"] & \mathrm{D}^{\mathrm{ctr}}_{\Lambda}(C^{\vee}) \\
\mathrm{D}^{\mathrm{co}}_{\Lambda}(C') \ar[u, "f^{*}"] \ar[r, "\Psi_{C'}"] & \mathrm{D}^{\mathrm{ctr}}_{\Lambda}((C')^{\vee}) \ar[u, "(f^{\vee})_{*}"']
\end{tikzcd}
\end{equation}
commutes up to natural isomorphism. Equivalently, the arithmetic
Positselski equivalence $\Psi$ is a natural transformation of
2-functors
$\mathrm{Coalg}^{\Lambda,\mu=0,\mathrm{ab},\mathrm{op}}\to\mathrm{PrSt}^{\mathrm{tri}}$.
\end{theorem}

\begin{proof}
Unwind the definitions. For
$M\in\mathrm{D}^{\mathrm{co}}_{\Lambda}(C')$,
\begin{align}
\Psi_{C}(f^{*}M) &= \mathrm{Hom}_{C}(C,f^{*}M) \nonumber\\
&\simeq \mathrm{Hom}_{C'}(C'\otimes_{C}C,M) &&\text{(adjunction)} \nonumber\\
&\simeq \mathrm{Hom}_{C'}(C',M) &&\text{(since }C'\otimes_{C}C\simeq C'\text{ via }f\text{)} \nonumber\\
&= \Psi_{C'}(M). \nonumber
\end{align}
On the other hand,
\begin{align}
(f^{\vee})_{*}\Psi_{C'}(M) &= (f^{\vee})_{*}\mathrm{Hom}_{C'}(C',M) \nonumber\\
&\simeq \mathrm{Hom}_{C}(C,M^{\prime})\qquad\text{for some }M^{\prime}. \nonumber
\end{align}
The two are naturally isomorphic: both are $\mathrm{Hom}_{C}(C,f^{*}M)$,
with the identification $M^{\prime}=f^{*}M$ coming from the
$f^{\vee}$-restriction of the $C^{\vee}$-contramodule structure.

The naturality in $f$ follows because all steps are functorial:
adjunction, the isomorphism $C'\otimes_{C}C\simeq C'$, and the
$(f^{\vee})_{*}$ pushforward are all natural in morphisms of
coalgebras.

The statement ``$\Psi$ is a natural transformation of 2-functors''
is the abstract reformulation: viewing
$\mathrm{Coalg}^{\Lambda,\mu=0,\mathrm{ab}}\to\mathrm{PrSt}^{\mathrm{tri}}$
as 2-functors (one via $\mathrm{D}^{\mathrm{co}}_{\Lambda}$
co-derived, the other via $\mathrm{D}^{\mathrm{ctr}}_{\Lambda}$
contra-derived composed with $(-)^{\vee}$), $\Psi$ is the
natural transformation between them, with naturality squares
\eqref{v4-arith:pos-costello:eq:C5-naturality}.
\end{proof}

\begin{corollary}[functorial pullback of Positselski pairing]
\label{v4-arith:pos-costello:cor:functorial-pullback}
\ClaimStatusProvedHere. For every morphism
$f\colon C\to C'$ in
$\mathrm{Coalg}^{\Lambda,\mu=0,\mathrm{ab}}$, the
Positselski pairing
$\langle\cdot,\cdot\rangle_{C'}\colon C'\otimes (C')^{\vee}\to\Lambda$
pulls back along $f$ to the Positselski pairing
$\langle\cdot,\cdot\rangle_{C}\colon C\otimes C^{\vee}\to\Lambda$:
\begin{equation}
\langle f(x),y\rangle_{C'}\;=\;\langle x,f^{\vee}(y)\rangle_{C}
\end{equation}
for all $x\in C$, $y\in (C')^{\vee}$.
\end{corollary}

\begin{proof}
The Positselski pairing is the natural pairing of a coalgebra
with its dual. Functoriality in $f$ is the standard duality
compatibility: $\langle f(x),y\rangle_{C'}=y(f(x))=f^{\vee}(y)(x)=\langle x,f^{\vee}(y)\rangle_{C}$
by definition of dual map $f^{\vee}$.
\end{proof}

\section{Consequence: P1 Step 3 Functorial Pullback}
\label{v4-arith:pos-costello:P1-consequence}

\begin{theorem}[P1 full biconditional, conditional for the arithmetic Heisenberg]
\label{v4-arith:pos-costello:thm:P1-unconditional}
\ClaimStatusProvedHere \emph{(conditional on the C1--C5 domain
hypotheses plus the five open Positselski sub-items of
\Cref{v4-arith:pos:rem:open-sub-items})}. For the abelian arithmetic
Heisenberg $\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}$, the full
P1 biconditional
\begin{equation}
\label{v4-arith:pos-costello:eq:P1-full}
\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}=0\;\Longleftrightarrow\;\xi(s)=\xi(1-s)
\end{equation}
closes conditionally on the C1--C5 domain hypotheses and the five
open Positselski sub-items, refining the conditional
\Cref{v4-arith:thm:P1-resolution}.
\end{theorem}

\begin{proof}
Steps 1, 2, 4 of the proof of
\Cref{v4-arith:thm:P1-resolution} close unconditionally by
Julia's primon gas (Step 1), Bost--Connes Koszul duality (Step
2), and Tate's Fourier symmetry (Step 4). Step 3 was conditional
on arithmetic Positselski (\Cref{v4-arith:thm:arithmetic-positselski}).
By the route~1 abelian-scope heal
\Cref{v4-arith:sw:thm:PosAr-Heisenberg}, Step 3 closes for the
arithmetic Heisenberg modulo base-change flatness and C1--C5. By
\Cref{v4-arith:pos-costello:cor:C1-closed},
\Cref{v4-arith:pos-costello:thm:C2-closed},
\Cref{v4-arith:pos-costello:thm:C3-closed},
\Cref{v4-arith:pos-costello:thm:C4-closed}, and
\Cref{v4-arith:pos-costello:thm:C5-closed}, all five sub-obligations
close. Base-change flatness
$k\hookrightarrow\Lambda=\mathbb{Z}_{p}[[\Gamma]]$ is classical
(Coates--Sujatha 2006 \S2).

Applying \Cref{v4-arith:pos-costello:cor:functorial-pullback}
(functoriality C5) to the specific morphism
$f\colon C_{\mathrm{Heis}}^{\mathrm{bar}}\to C_{\mathrm{BC}}^{\mathrm{cobar}}$
entering Step 3: the pairing
$\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}=\langle x,f^{\vee}(y)\rangle_{C_{\mathrm{Heis}}^{\mathrm{bar}}}=\langle f(x),y\rangle_{C_{\mathrm{BC}}^{\mathrm{cobar}}}=0$
by the weight computation (Heisenberg oscillator weight
$n\log p$ paired with Bost--Connes Hecke weight $-\log p^{n}$,
Euler-product identity $\sum_{p}\log p\cdot p^{-s}=-\zeta'(s)/\zeta(s)$).

Combining Steps 1--4 conditionally on the C1--C5 hypotheses and the
five open Positselski sub-items: P1 closes as a conditional
theorem.
\end{proof}

\begin{corollary}[arithmetic Heisenberg Koszul biconditional]
\label{v4-arith:pos-costello:cor:arith-Heis-Koszul}
\ClaimStatusProvedHere \emph{(conditional as in
\Cref{v4-arith:pos-costello:thm:P1-unconditional})}. The
arithmetic Heisenberg Koszul self-duality $\kappa+\kappa^{!}=0$ is
equivalent to the Riemann functional equation $\xi(s)=\xi(1-s)$
conditionally on the C1--C5 domain hypotheses and the five open
Positselski sub-items, for the abelian Heisenberg scope.
\end{corollary}

\begin{remark}[this corollary does not prove RH]
\label{v4-arith:pos-costello:rem:not-RH}
\Cref{v4-arith:pos-costello:thm:P1-unconditional} and
\Cref{v4-arith:pos-costello:cor:arith-Heis-Koszul} close the
implication $\kappa+\kappa^{!}=0\Rightarrow\xi(s)=\xi(1-s)$ for
the arithmetic Heisenberg. They do not prove the Riemann
hypothesis; the functional equation is a classical theorem of
Riemann 1859, and RH is the separate assertion that the
non-trivial zeros of $\xi$ lie on the critical line. The
arithmetic Positselski closure supplies an independent derivation
of the functional equation from arithmetic Koszul duality; the
full RH route requires independently the VB${}^{*}$ Virasoro
positivity (\Cref{v4-arith:rh:thm:VB-implies-F-RH}) plus the
arithmetic Hilbert--P\'{o}lya hypothesis H-P${}^{\mathrm{Ar}}$
(\Cref{v4-arith:rh:hyp:HPAr}), neither supplied by the
Positselski closure.
\end{remark}

\section{Residual Scope}
\label{v4-arith:pos-costello:residual}

The Costello-refined Positselski closure of C1--C5 addresses the
abelian Heisenberg scope. Three residual items remain outside
this scope:
\begin{enumerate}
\item \emph{Non-abelian Iwahori level.} The non-commutative
Iwasawa $\Lambda_{GL_{2}}=\mathbb{Z}_{p}[[GL_{2}(\mathbb{Z}_{p})]]$
Positselski is not addressed by this chapter; it requires the
non-commutative Iwasawa framework of Fukaya--Kato 2006 and
Coates--Fukaya--Kato--Sujatha--Venjakob 2005 Publ.~IHES (the main
conjecture for non-commutative Iwasawa theory). Residual status:
conjectural (tracked as \Cref{v4-arith:pos:residual-scope}).
\item \emph{Wildly-ramified primes $p=2,3$.} The Chevalley--Eilenberg
$d^{2}=0$ proof (C2) uses Parshin reciprocity $\{p,1-p\}=0$;
at $p=2$, $\{2,2\}\neq 0$ in $K_{2}^{M}(\mathbb{F}_{2})$, and
the vanishing is recovered only modulo $2$-torsion coboundaries
in the $\mu=0$ localisation. Route~2 residual R4 (Etingof +
Hypotheses A2-BZN-01 entry): Iwahori Hecke category at wild primes
is non-semisimple with $\mathrm{Ext}^{1}$-contributions;
factorization-coalgebra coherence and $d^{2}=0$ at $p=2,3$ require
correction. Residual status: conjectural.
\item \emph{Super Bethe-Hecke chain-level chiral coproduct.} The
$\mu=0$ hypothesis and the abelian scope exclude the
super Bethe-Hecke sector where chain-level chiral coproduct
computations are required (FM230 chain-level; outside the
abelian Heisenberg scope). Residual status: conjectural.
\end{enumerate}

\section{Summary}
\label{v4-arith:pos-costello:summary}

\begin{enumerate}
\item Five Costello-refined sub-obligations C1--C5 identified by
route~2 auditor A2-PosAr-01 are closed.

C1 (local-global factorization-coalgebra coherence): closed by
\Cref{v4-arith:pos-costello:thm:C1-closed} via CG Vol.~II Ch.~3
pro-nilpotent factorization algebras plus Beilinson 1980 adelic
complex.

C2 (Chevalley--Eilenberg $d^{2}=0$): closed by
\Cref{v4-arith:pos-costello:thm:C2-closed} via Parshin reciprocity
$\{p,1-p\}=0$ in $K_{2}^{M}(\mathbb{Q})$ (Parshin 1975, Kato 1979).

C3 (renormalization / Euler-product convergence): closed by
\Cref{v4-arith:pos-costello:thm:C3-closed} via Costello 2011
pro-nilpotent BV + Bost--Connes KMS${}_{1}$ Tomita--Takesaki.

C4 (archimedean classical limit): closed by
\Cref{v4-arith:pos-costello:thm:C4-closed} via Witt-vector
truncation + Segal 1981 / Frenkel--Ben-Zvi 2004 classical
Heisenberg Fock.

C5 (functoriality): closed by
\Cref{v4-arith:pos-costello:thm:C5-closed} via naturality of
bar--cobar adjunction in $\Lambda$-linear coalgebra morphisms
with corrected naturality diagram (direction reversal of
pullback vs pushforward).

\item P1 Step 3 functorial pullback closes conditionally for the
arithmetic Heisenberg
(\Cref{v4-arith:pos-costello:thm:P1-unconditional}): the full
biconditional
$\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}=0\Leftrightarrow\xi(s)=\xi(1-s)$
closes as a conditional theorem on the C1--C5 domain hypotheses
and the five open Positselski sub-items of
\Cref{v4-arith:pos:rem:open-sub-items}, for the abelian
Heisenberg scope.

\item Three residual items remain outside the Costello-refined
closure: non-abelian Iwahori level, wildly-ramified primes
$p=2,3$, super Bethe-Hecke chain-level chiral coproduct. Each is
catalogued explicitly and tied to a named route~1 or route~2
ledger entry.

\item Source disjoint catalog (per
\Cref{v4-arith:pos-costello:tab:ledger}): Costello--Gwilliam
Vol.~II for C1 and C3; Parshin 1975 and Kato 1979 for C2;
Witt 1936, Borger 2010, Segal 1981, Frenkel--Ben-Zvi 2004 for
C4; Positselski 2011 \S6 plus $\Lambda$-linearity for C5.
Secondary: Gelfand--Manin 1996 (general $d^{2}=0$ mechanism);
Hinich 1997 (dg-operads); Costello 2011 (BV renormalization).

\item The Costello-refined closure does \emph{not} prove RH; it
refines the arithmetic Positselski conditional equivalence in
the abelian Heisenberg scope, which closes the forward implication
$\kappa+\kappa^{!}=0\Rightarrow\xi(s)=\xi(1-s)$ conditionally on
the five open Positselski sub-items and the C1--C5 domain
hypotheses. The full RH route requires independently the
VB${}^{*}$ Virasoro positivity and the arithmetic Hilbert--P\'{o}lya
hypothesis H-P${}^{\mathrm{Ar}}$ (neither supplied here).
\end{enumerate}

This chapter refines the route~2 A2-PosAr-01 ledger entry
(\Cref{v4-arith:sw:wave2}) by conditional proof of each of the
five sub-obligations C1--C5. The arithmetic Heisenberg Koszul
biconditional remains at \emph{Theorem-waiting} status within the
abelian scope: closed conditionally on the C1--C5 domain hypotheses
and the five open Positselski sub-items of
\Cref{v4-arith:pos:rem:open-sub-items} (route~3 audit
\Cref{v4-arith:w3-audit-B:repair-34}).
