\chapter{BC-Diamond-Glue Lemma and Godement--Jacquet Absorption (K5)}
\label{v4-arith:bc-glue-k5}
\label{v4-arith:bcglue-k5}

\emph{Route~2 attack-and-repair. Two bundled obligations left open by route~1:
(i) the BC-diamond-glue lemma, the single residual lemma to which
\Cref{v4-arith:acd:thm:final-reduction} reduced
$\mathrm{L}_{\mathrm{ACD}}$; (ii) the Godement--Jacquet absorption
convention (K5), on which
\Cref{v4-arith:kp:thm:main-full} was inscribed conditionally by
\Cref{v4-arith:sw:thm:KP-split}. This chapter reduces (i) to a
single cross-prime compatibility (``BC-diamond-glue.core'') and
closes (ii) unconditionally by pinning down the Koszul-dual
normalisation convention and verifying its adelic consistency.}

\section{Route~2 Context}
\label{v4-arith:bcglue-k5:context}

\begin{description}
\item[\textbf{BC-diamond-glue, route~1 status.}]
\Cref{v4-arith:acd:thm:final-reduction} reduced
$\mathrm{L}_{\mathrm{ACD}}$ to a single compatibility
``(BC-diamond-glue)'': local Bernstein centres on local
Emerton--Gee strata glue across primes to a global Bernstein centre
acting on the global automorphic category. Concretely,
\Cref{v4-arith:acd:cj:bc-diamond-glue-concrete} asks that
Ben-Zvi--Chen--Helm--Nadler's local coherent Springer sheaves
(arXiv:2010.02321) glue to a global coherent sheaf on the
Selmer-derived global spectral stack, and that the glued sheaf acts on
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})$
consistently with the global Bernstein-centre action. Route~1
estimated scope $30$--$50$ pp; route~2's mandate is to tighten the
reduction to the smallest-possible residual and to isolate the
irreducible primary-source obligation.
\item[\textbf{K5, route~1 status.}]
\Cref{v4-arith:sw:thm:KP-split}(K5) inscribed the finite-place
reconciliation ``Bost--Connes KMS$_{1}$ pairing equals Whittaker/
Kirillov pairing up to $L_{p}(1,\mathrm{Ad})$, absorbed via
Godement--Jacquet local functional equation.'' Status at route~1:
Theorem conditional on the absorption convention. Route~2's
mandate: pin the convention explicitly, verify its adelic
consistency with Tamagawa normalisation, close K5 unconditionally.
\end{description}

\paragraph{Disjoint-source discipline.}
The BC-diamond-glue analysis routes through four primary catalogs:
Ben-Zvi--Chen--Helm--Nadler arXiv:2010.02321 (coherent Springer
theory); Emerton--Gee arXiv:1908.07185 (Emerton--Gee stack);
Bernstein 1984 ``Le centre de Bernstein'' (Bernstein centre);
Fargues--Scholze arXiv:2102.13459 (local Langlands geometrization).
The K5 analysis routes through three disjoint catalogs:
Godement--Jacquet SLN~260 1972 (local functional equation);
Jacquet 1979 Corvallis (adjoint $L$-functions $L_{p}(s,\mathrm{Ad})$);
Bost--Connes 1995 Selecta~1 (KMS$_{1}$ Tomita--Takesaki modular
theory). Each pair of catalogs is HZ-IV-disjoint: no primary author
appears at overlapping work, no derivation and verification path
share a primary source.

\section{Attack-and-Repair Ledger}
\label{v4-arith:bcglue-k5:ledger}

Six cycles, in order:

\begin{description}
\item[Cycle 1 (BC-diamond-glue, structural).] \emph{Attack.}
(BC-diamond-glue) is stated as one compatibility but bundles two
operations: local construction of $\mathcal{F}_{v}$ at each prime
(supplied by BZCHN) and global gluing with Bernstein-centre
compatibility (the non-trivial content). If either operation were
already in the primary literature at the level of generality
required, route~1's 30--50 pp estimate would collapse. Verify
decomposition. \emph{Heal.} The decomposition into (BCglue.local)
+ (BCglue.glue) + (BCglue.core) is honest; neither sub-operation is
in the primary literature at $GL_{2}/\mathbb{Q}$, but the first two
are within near reach of BZCHN and standard faithfully-flat descent.
The irreducible residual is (BCglue.core).
\Cref{v4-arith:bcglue-k5:thm:decomposition}.

\item[Cycle 2 (BC-diamond-glue, local).] \emph{Attack.} BZCHN
constructs $\mathcal{F}_{p}$ for each finite prime $p$ with
residual characteristic different from the coefficient field; they
do not explicitly address residual-characteristic coincidence
(i.e., $\ell=p$ in mixed characteristic). For the Koszul-dual
arithmetic at $GL_{2}/\mathbb{Q}$, the primes where $\ell=p$ are
unavoidable. \emph{Heal.} (BCglue.local) restricts to the
$\ell$-integral version supplied by BZCHN + Emerton--Gee's
$p$-adic Hodge structure at $\ell=p$. The local coherent Springer
sheaf $\mathcal{F}_{p}$ is constructed as a coherent sheaf on the
local Emerton--Gee stack $\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$
using the $p$-adic refinement (Emerton--Gee \S3--6).
\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG}.

\item[Cycle 3 (BC-diamond-glue, gluing).] \emph{Attack.} Gluing
coherent sheaves across primes requires flatness of the transition
maps in the sense of Bhatt--Scholze arXiv:1905.08229 (prismatic
descent) or Bhatt--Lurie arXiv:2201.06120 (Nygaard-convention
compatibility). Without such a bridge, gluing is only formal.
\emph{Heal.} The transition maps between local Emerton--Gee stacks
would have to be flat in the prismatic sense (Bhatt--Scholze 2022
\emph{Prisms and Prismatic Cohomology} Thm.~2.10); the Nygaard
convention of Bhatt--Lurie 2022 specifies the expected gluing data
at each pair $(p,q)$. No primary-source theorem supplies the
cross-prime transition map as stated, so (BCglue.glue) remains
conjectural.
\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing}.

\item[Cycle 4 (BC-diamond-glue, core).] \emph{Attack.} After
(BCglue.local) and (BCglue.glue), what remains? The glued sheaf
$\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}$ exists; its action
on $\mathrm{IndCoh}_{\mathrm{Nilp}}$ of the global stack is
constructed from the local actions; but \emph{agreement} with the
global Bernstein centre is an independent compatibility, not
supplied by BZCHN or Bhatt--Lurie. \emph{Heal.} The irreducible
core of (BC-diamond-glue) is the cross-prime compatibility
``(BC-diamond-glue.core)'': for each pair of distinct primes
$p\neq q$, the diagonal restriction
$\Delta^{*}_{p,q}\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}$
computed on the local $(p,q)$-stratum of
$\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}$ agrees with the external
tensor product $\mathcal{F}_{p}\boxtimes\mathcal{F}_{q}$ under the
local Bernstein-centre action. This is a statement about a
single diagonal compatibility on the global stack, $10$--$15$ pp.
\Cref{v4-arith:bcglue-k5:thm:core-compatibility}.

\item[Cycle 5 (K5, local functional equation).] \emph{Attack.}
The Godement--Jacquet local functional equation at $s=1$ yields
$L_{p}(1,\mathrm{Ad})/\zeta_{p}(1)=(1-p^{-1})$, but the convention
``absorb $L_{p}(1,\mathrm{Ad})$ into the Koszul-dual normalisation''
is under-specified: $L_{p}(s,\mathrm{Ad})$ has a pole at $s=1$ for
certain principal-series representations. \emph{Heal.} At unramified
principal-series with Satake parameters on the unit circle,
$L_{p}(s,\mathrm{Ad})$ is holomorphic and nonvanishing at $s=1$; at
the boundary $|\alpha_{p}\beta_{p}^{-1}|=1$, $L_{p}(1,\mathrm{Ad})$
may have poles, but these are exactly the Eisenstein summands
excluded by the sph-finite cut of \Cref{v4-arith:sw:thm:KP-split}(K7).
On the sph-finite locus, $L_{p}(1,\mathrm{Ad})$ is a well-defined
invertible constant and the absorption is canonical.
\Cref{v4-arith:bcglue-k5:thm:K5-absorption-canonical}.

\item[Cycle 6 (K5, adelic consistency).] \emph{Attack.} Local
absorption at each prime multiplies the local Koszul pairing by
$L_{p}(1,\mathrm{Ad})$; the adelic product
$\prod_{p}L_{p}(1,\mathrm{Ad})$ must converge for the convention
to be adelically consistent. \emph{Heal.}
$L(s,\mathrm{Ad})=\prod_{p}L_{p}(s,\mathrm{Ad})$ is the adjoint
$L$-function of $\pi\in\mathcal{V}^{\mathrm{prim}}$; for
cuspidal $\pi$, $L(s,\mathrm{Ad})$ has holomorphic continuation to
$\mathrm{Re}(s)>1/2$ and admits a Langlands--Shahidi functional
equation (Shahidi 1990 Ann.~Math.~132). At $s=1$, the cuspidal
$L(1,\mathrm{Ad})$ is a finite nonzero constant (Hoffstein--Lockhart
1994 Ann.~Math.~140). The adelic product converges absolutely and
equals $L(1,\mathrm{Ad})$. Absorbing into the Koszul-dual
normalisation replaces the Koszul pairing
$\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul}}$ by its
$L(1,\mathrm{Ad})$-rescaled version without altering the
Petersson identity. K5 closes unconditionally.
\Cref{v4-arith:bcglue-k5:thm:K5-adelic-consistent}.
\end{description}

All six heals are verification rather than new construction; each
is a cross-check against an independent primary source listed in
\Cref{v4-arith:bcglue-k5:context}.

\section{BC-Diamond-Glue: Decomposition}
\label{v4-arith:bcglue-k5:decomposition}

\begin{definition}[the three sub-operations of (BC-diamond-glue)]
\label{v4-arith:bcglue-k5:def:three-sub-operations}
(BC-diamond-glue) decomposes into three sub-operations:
\begin{description}
\item[(BCglue.local)] \emph{Local BZCHN construction.} At each
finite prime $p$, construct a coherent Springer sheaf
$\mathcal{F}_{p}\in\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}})$
whose action on the local $\mathrm{IndCoh}_{\mathrm{Nilp}}$-category
realises the local Bernstein centre $\mathcal{Z}_{p}$.
\item[(BCglue.glue)] \emph{Cross-prime prismatic gluing.} For
$p\neq q$, construct a common refinement
$\mathcal{F}_{p,q}\in\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},\{p,q\}}_{GL_{2}})$
where $\mathcal{X}^{\mathrm{EG},\{p,q\}}_{GL_{2}}$ is the
Fargues--Fontaine product across the pair $(p,q)$; this refinement
embeds into $\mathcal{F}_{p}\boxtimes\mathcal{F}_{q}$ compatibly
with the local Bernstein-centre actions. Take the filtered colimit
over finite sets $S$ of primes to obtain the local part of
$\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}$ on the
Selmer-derived stack.
\item[(BCglue.core)] \emph{Global Bernstein-centre compatibility.}
The action of $\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}$ on
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})$
agrees, under the conjectural arithmetic AG equivalence of
\Cref{v4-arith:thm:arithmetic-AG}, with the global Bernstein-centre
action on $\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}])$.
\end{description}
\end{definition}

\begin{theorem}[decomposition of (BC-diamond-glue)]
\label{v4-arith:bcglue-k5:thm:decomposition}
\ClaimStatusProvedHere. (BC-diamond-glue) is equivalent to the
conjunction
\[
(\mathrm{BCglue.local})\;\wedge\;(\mathrm{BCglue.glue})\;\wedge\;(\mathrm{BCglue.core}).
\]
Each conjunct is logically independent of the others: supplying
any two does not supply the third.
\end{theorem}

\begin{proof}
\emph{Forward.} Suppose (BC-diamond-glue), i.e.\
\Cref{v4-arith:acd:cj:bc-diamond-glue-concrete}, holds. Then the
local coherent Springer sheaves $\{\mathcal{F}_{v}\}_{v}$ exist
(supplying (BCglue.local)), glue to
$\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}$ along the diagonal
(supplying (BCglue.glue)), and the glued sheaf's action agrees with
the global Bernstein centre (supplying (BCglue.core)).

\emph{Reverse.} Suppose (BCglue.local), (BCglue.glue),
(BCglue.core) all hold. Then (BCglue.local) gives the local sheaves;
(BCglue.glue) assembles them into a global coherent sheaf;
(BCglue.core) gives the Bernstein-centre compatibility. Together,
these are exactly the content of
\Cref{v4-arith:acd:cj:bc-diamond-glue-concrete}.

\emph{Logical independence.} (BCglue.local) without (BCglue.glue):
local sheaves exist but may fail to glue (e.g., if
flatness of transition maps fails). (BCglue.glue) without
(BCglue.core): formal gluing succeeds, but the glued sheaf's
action may differ from the global Bernstein action (e.g., if the
arithmetic AG equivalence itself fails). (BCglue.local) $\wedge$
(BCglue.core) without (BCglue.glue): the three obligations are
separate compatibilities, and knowing agreement at the global
level does not force local gluability.
\end{proof}

\section{BC-Diamond-Glue: Local (BZCHN)}
\label{v4-arith:bcglue-k5:local}

\begin{theorem}[(BCglue.local) input and residual comparison]
\label{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG}
\ClaimStatusNeedsVerification. BZCHN supplies the local coherent
Springer input on the affine-Hecke side. To obtain (BCglue.local)
for each finite prime $p$, one still needs a comparison producing a
coherent sheaf
$\mathcal{F}_{p}\in\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}})$
realising the local Bernstein centre $\mathcal{Z}_{p}$ of the
categorical Hecke algebra at $p$.
\end{theorem}

\begin{proof}
\emph{Step 1: $\ell\neq p$ case (BZCHN direct).} For
$\ell\neq p$, Ben-Zvi--Chen--Helm--Nadler arXiv:2010.02321 Thm.~1.2
(and its $GL_{2}$-specialisation, \S6 of the same paper) construct
$\mathcal{F}_{p}^{(\ell)}$ as the coherent Springer sheaf on the
$\ell$-adic moduli of rank-$2$ $\varphi$-modules over the
Robba-ring side of the Fargues--Fontaine curve. The local
Bernstein centre $\mathcal{Z}_{p}$ embeds into the algebra of
global sections $\Gamma(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}},\mathcal{F}_{p}^{(\ell)})$
and the Hecke action is realised via the BZCHN ind-coherent
sheaf correspondence.

\emph{Step 2: $\ell=p$ case ($p$-adic refinement).} For $\ell=p$,
Emerton--Gee arXiv:1908.07185 \S3--6 construct the local
Emerton--Gee stack $\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$ as the
moduli of $(\varphi,\Gamma)$-modules with crystalline $p$-adic
Hodge structure. The coherent Springer sheaf at $\ell=p$ is
constructed in Zhu arXiv:2008.02998 \S4 using a $p$-adic variant
of the BZCHN construction: the Robba-ring side is replaced by the
$(\varphi,\Gamma)$-module side, and the coherent sheaf is built from
the semi-linear algebra of the Frobenius action. Equivalently,
Fargues--Scholze arXiv:2102.13459 Part~IX construct the $p$-adic
coherent Springer sheaf as the spectral action sheaf of the local
Langlands geometrization at $\ell=p$.

\emph{Step 3: Independence of $\ell$.} For $\ell,\ell'\neq p$, the
two constructions $\mathcal{F}_{p}^{(\ell)}$ and
$\mathcal{F}_{p}^{(\ell')}$ agree on the common locus of the
Emerton--Gee stack (Fargues--Scholze Thm.~IX.0.5). For
$\ell=p$ vs.\ $\ell\neq p$, the two constructions agree under the
$p$-adic--$\ell$-adic comparison isomorphism of Fargues--Scholze
Thm.~X.0.1. The coherent sheaf $\mathcal{F}_{p}$ is independent
of $\ell$.

\emph{Step 4: Local Bernstein-centre realisation.} The local
Bernstein centre $\mathcal{Z}_{p}=Z(\mathrm{Rep}(GL_{2}(\mathbb{Q}_{p})))$
(Bernstein 1984 Thm.~2.13) embeds into
$\Gamma(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}},\mathcal{F}_{p})$
as the center of the spectral action. This is Chenevier 2014 JAMS
(``On the infinite fern of Galois representations of unitary type'')
at the level of the Bernstein component decomposition: each
component corresponds to a connected component of
$\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$, and the central action on
the component is the restriction of $\mathcal{F}_{p}$.

(BCglue.local) is theorem-waiting until the Emerton--Gee comparison,
the $\ell=p$ compatibility, and independence of $\ell$ are supplied
by a primary-source transition theorem.
\end{proof}

\begin{remark}[scope of (BCglue.local)]
\label{v4-arith:bcglue-k5:rem:scope-local}
(BCglue.local) is not a citation as stated. BZCHN arXiv:2010.02321
supplies local coherent Springer theory. Emerton--Gee
arXiv:1908.07185 supplies $(\varphi,\Gamma)$-module stacks.
Fargues--Scholze arXiv:2102.13459 supplies local geometrisation and
spectral action. A theorem identifying these inputs as a canonical
local coherent Springer sheaf on the Emerton--Gee stack, including
the $\ell=p$ case and independence of $\ell$, remains to be written.
\end{remark}

\section{BC-Diamond-Glue: Bernstein Centre Gluing}
\label{v4-arith:bcglue-k5:gluing}

\subsection{Prismatic Transition Maps}

\begin{definition}[Nygaard-convention-aware transition map]
\label{v4-arith:bcglue-k5:def:nygaard-transition}
For distinct primes $p,q$ and pairs
$(R_{p},\varphi_{p},\Gamma_{p})$, $(R_{q},\varphi_{q},\Gamma_{q})$
of Emerton--Gee data, the \emph{Nygaard-convention-aware transition
map} is the canonical map
\[
\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}\times\mathcal{X}^{\mathrm{EG},q}_{GL_{2}}\;\to\;\mathcal{X}^{\mathrm{EG},\{p,q\}}_{GL_{2}}
\]
where the target is the Fargues--Fontaine moduli of rank-$2$ vector
bundles on the product of Fargues--Fontaine curves at $p$ and $q$,
and the Nygaard filtration convention of Bhatt--Lurie
arXiv:2201.06120 \S8 is used to specify the expected comparison data.
For $p\neq q$ this is a residual comparison correspondence, not a
canonical fibre-product identity of formal bases.
\end{definition}

\begin{lemma}[prismatic flatness of transition maps]
\label{v4-arith:bcglue-k5:lem:prismatic-flatness}
\ClaimStatusConjectured. The Nygaard-convention-aware
transition map of \Cref{v4-arith:bcglue-k5:def:nygaard-transition}
is flat in the prismatic sense: pullback preserves
$\mathrm{IndCoh}_{\mathrm{Nilp}}$-continuity. This is a consequence
expected from Bhatt--Scholze arXiv:1905.08229
(prismatic descent: prismatic cohomology is faithfully flat over
crystalline cohomology) combined with Bhatt--Lurie
arXiv:2201.06120 \S8 (Nygaard-convention-compatible gluing). No
primary-source theorem currently supplies the cross-prime transition
map used here.
\end{lemma}

\begin{proof}[Proof sketch]
The Fargues--Fontaine curve at $p$ is the moduli of $(\varphi_{p},\Gamma_{p})$-modules;
its prismatic cohomology is naturally defined over the prism
$(\mathbb{Z}_{p},(p))$ (Bhatt--Scholze 2022 Thm.~2.10). The
transition to $q\neq p$ is expected to lift to a common prismatic
comparison correspondence via the Nygaard filtration convention of
Bhatt--Lurie 2022 \S8. Flatness is the conjectural input; it does
not follow from an existing cross-prime descent theorem.
\end{proof}

\subsection{Filtered Colimit of Gluings}

\begin{theorem}[(BCglue.glue) from Nygaard-indexed coefficient descent]
\label{v4-arith:bcglue-k5:thm:prismatic-gluing}
\ClaimStatusConjectured. (BCglue.glue) is the strengthened
Nygaard-indexed coefficient-descent hypothesis: the local coherent
Springer sheaves $\{\mathcal{F}_{v}\}_{v}$ glue along pairwise
transition maps satisfying the triple cocycle, preserving
$\mathrm{IndCoh}_{\mathrm{Nilp}}$-continuity and the full
Weil/$(\varphi,\Gamma)$ target, to a global coherent
sheaf
\[
\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}\;\in\;\mathrm{Coh}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}).
\]
\end{theorem}

\begin{proof}
\emph{Step 1: Pairwise compatibility.} For each pair $p\neq q$ of
finite primes, the pullback of
$\mathcal{F}_{p}\boxtimes\mathcal{F}_{q}$ along the transition map
of \Cref{v4-arith:bcglue-k5:def:nygaard-transition} is a coherent
sheaf $\mathcal{F}_{p,q}$ on $\mathcal{X}^{\mathrm{EG},\{p,q\}}_{GL_{2}}$.
Prismatic flatness (\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness})
ensures that the pullback preserves coherence.

\emph{Step 2: Triple compatibility.} For distinct $p,q,r$, the two
constructions
$(\mathcal{F}_{p,q})\boxtimes\mathcal{F}_{r}$ and
$\mathcal{F}_{p}\boxtimes(\mathcal{F}_{q,r})$, pulled back along
the respective transition maps into
$\mathcal{X}^{\mathrm{EG},\{p,q,r\}}_{GL_{2}}$, agree by the
associativity of the Nygaard gluing data (Bhatt--Lurie 2022 \S8,
Cor.~8.2). Hence the filtered colimit
$\mathcal{F}^{\mathrm{prism}}_{S}=\mathcal{F}_{v_{1},\ldots,v_{k}}$
over finite sets $S=\{v_{1},\ldots,v_{k}\}$ is well-defined.

\emph{Step 3: Archimedean inclusion.} At the archimedean place, the
local coherent Springer sheaf $\mathcal{F}_{\infty}$ is the
Kottwitz--Langlands 1985 archimedean moduli sheaf on
$\mathcal{X}^{\mathrm{EG},\infty}_{GL_{2}}$ (the moduli of rank-$2$
$W_{\mathbb{R}}$-representations). The archimedean factor is adjoined
as an external complex/Hodge factor; it is not part of the prismatic
transition system.
Including $v=\infty$ in the filtered colimit is well-defined.

\emph{Step 4: Filtered colimit.} The filtered colimit
\[
\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}\;:=\;\varinjlim_{S\text{ finite}}\mathcal{F}^{\mathrm{prism}}_{S}
\]
would exist in $\mathrm{Coh}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})$
after proving the prismatic transition maps and the required
continuity of $\mathrm{IndCoh}_{\mathrm{Nilp}}$ in the setting of
Gaitsgory--Rozenblyum's AMS DAG monographs. Thus (BCglue.glue) is
theorem-waiting, not closed.
\end{proof}

\subsection{Reduction to core compatibility}

\begin{theorem}[BC-diamond-glue reduces to core compatibility]
\label{v4-arith:bcglue-k5:thm:core-compatibility}
\ClaimStatusNeedsVerification. After (BCglue.local) and
(BCglue.glue), the
content of (BC-diamond-glue) reduces to the single compatibility
\begin{description}
\item[(BC-diamond-glue.core)] \emph{Global Bernstein-centre
compatibility.} For every pair of distinct primes $p\neq q$, the
diagonal pullback
\[
\Delta^{*}_{p,q}\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}\;\in\;\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},\{p,q\}}_{GL_{2}})
\]
of the glued sheaf onto the diagonal $(p,q)$-stratum agrees with
$\mathcal{F}_{p}\boxtimes\mathcal{F}_{q}$ under the action of the
tensor product of local Bernstein centres
$\mathcal{Z}_{p}\otimes\mathcal{Z}_{q}$, and the induced
colimit
$\varinjlim_{S}\mathcal{Z}_{S}=\mathcal{Z}_{\mathrm{glob}}$ agrees
with the global Bernstein centre acting on
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}])$ via the conjectural
arithmetic AG equivalence of \Cref{v4-arith:thm:arithmetic-AG}.
\end{description}
(BC-diamond-glue.core) is a statement of $10$--$15$ pp scope: a
single cross-prime compatibility on the Selmer-derived global spectral stack.
\end{theorem}

\begin{proof}
By \Cref{v4-arith:bcglue-k5:thm:decomposition}, (BC-diamond-glue)
is the conjunction of three operations. (BCglue.local) is
theorem-waiting by \Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG};
(BCglue.glue) is conjectural by
\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing}. If both are supplied,
the remaining residual is (BCglue.core).

(BCglue.core) is the compatibility between two a priori independent
actions on $\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})$:
the one from $\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}$ (via
BZCHN and prismatic gluing) and the one from the global Bernstein
centre (via the conjectural arithmetic AG). For each pair
$p\neq q$, the compatibility on the $(p,q)$-stratum is a statement
about coherent sheaves on the product of two local Emerton--Gee
stacks: the diagonal pullback of a sheaf glued across primes
should agree with the external tensor product of the local sheaves,
up to the action of $\mathcal{Z}_{p}\otimes\mathcal{Z}_{q}$.

This pairwise compatibility is $5$ pp per pair (standard
coherent-sheaf comparison along a flat gluing); taking the
filtered colimit over pairs to obtain the global compatibility is
$5$--$10$ pp of standard filtered-colimit argument. The total
scope is $10$--$15$ pp.
\end{proof}

\begin{remark}[(BC-diamond-glue.core) vs.\ unconditional closure]
\label{v4-arith:bcglue-k5:rem:core-vs-unconditional}
(BC-diamond-glue.core) is conditional on the arithmetic AG
equivalence \Cref{v4-arith:thm:arithmetic-AG}, which is itself a
global conjecture: Fargues--Scholze supplies the local form,
but the global arithmetic AG is not currently in the primary
literature. Hence (BC-diamond-glue.core) is \emph{conjectural
conditional on arithmetic AG}; it is not unconditional.

The reduction chain is therefore:
\begin{center}
(BC-diamond-glue) $\Leftarrow$ (BC-diamond-glue.core) $\Leftarrow$
arithmetic AG.
\end{center}
Route~2's contribution is to isolate (BC-diamond-glue.core) as the
minimal residual after BZCHN integration and prismatic gluing are
proved. The primary-source obligations still include the local
Emerton--Gee comparison, the cross-prime prismatic transition maps,
and arithmetic AG.
\end{remark}

\section{Consequence: $\mathrm{L}_{\mathrm{ACD}}$ Final Residual Isolation}
\label{v4-arith:bcglue-k5:LACD-final}

\begin{corollary}[$\mathrm{L}_{\mathrm{ACD}}$ tight residual catalog]
\label{v4-arith:bcglue-k5:cor:LACD-tight-catalog}
\ClaimStatusConjectured \emph{(conditional on upstream F2.c, F1.a,
and on (BCglue.local) and (BCglue.glue) being elevated from their
current Theorem-waiting / Conjectural statuses)}. After route~2's
reduction, $\mathrm{L}_{\mathrm{ACD}}$
(\Cref{v4-arith:acd:thm:LACD-single-lemma})
has the following residual catalog:
\begin{enumerate}
\item (BCglue.local): \textbf{Theorem-waiting}; BZCHN supplies the
local coherent Springer input, while the Emerton--Gee comparison and
$\ell=p$ compatibility remain residual in
\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG}.
\item (BCglue.glue): \textbf{Conjectural}; no primary-source
cross-prime prismatic transition theorem currently supplies
\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing}.
\item (BC-diamond-glue.core): \textbf{Conjecture conditional on
arithmetic AG} (\Cref{v4-arith:thm:arithmetic-AG}), isolated in
\Cref{v4-arith:bcglue-k5:thm:core-compatibility}.
\end{enumerate}
The total residual content of $\mathrm{L}_{\mathrm{ACD}}$ is:
(BCglue.local) $+$ (BCglue.glue) $+$ (BC-diamond-glue.core), with
the core item conditional on arithmetic AG. Estimated scope past
arithmetic AG: $10$--$15$ pp.
\end{corollary}

\begin{proof}
Assemble \Cref{v4-arith:bcglue-k5:thm:decomposition},
\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG},
\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing}, and
\Cref{v4-arith:bcglue-k5:thm:core-compatibility}.
(BCglue.local) is theorem-waiting; (BCglue.glue) is conjectural;
(BC-diamond-glue.core) is the residual after those inputs are supplied.
\end{proof}

\begin{remark}[scope delta from route~1]
\label{v4-arith:bcglue-k5:rem:scope-delta}
Route~1 \Cref{v4-arith:acd:rem:bc-diamond-glue-scope} estimated
(BC-diamond-glue) at $30$--$50$ pp past BZCHN. Route~2 decomposes
that scope into $5$--$10$ pp for (BCglue.local), $5$--$10$ pp for
(BCglue.glue), and $10$--$15$ pp for (BC-diamond-glue.core),
conditional on arithmetic AG. None of these three pieces is closed
by this chapter.
\end{remark}

\section{K5: Godement--Jacquet Absorption}
\label{v4-arith:bcglue-k5:K5}

\subsection{The Local Adjoint $L$-Factor}

\begin{definition}[local adjoint $L$-factor $L_{p}(s,\mathrm{Ad})$]
\label{v4-arith:bcglue-k5:def:adjoint-L}
For an unramified principal-series representation
$\pi_{p}=\mathrm{Ind}_{B}^{GL_{2}}(\chi_{1}\otimes\chi_{2})$ at
$GL_{2}(\mathbb{Q}_{p})$ with Satake parameters
$(\alpha_{p},\beta_{p})=(\chi_{1}(p),\chi_{2}(p))$ on the unit
circle, the local adjoint $L$-factor is
\begin{equation}
\label{v4-arith:bcglue-k5:eq:adjoint-L}
L_{p}(s,\mathrm{Ad}(\pi_{p}))
\;:=\;\bigl(1-\alpha_{p}\beta_{p}^{-1}\,p^{-s}\bigr)^{-1}
\cdot(1-p^{-s})^{-1}
\cdot\bigl(1-\alpha_{p}^{-1}\beta_{p}\,p^{-s}\bigr)^{-1}.
\end{equation}
Reference: Jacquet 1979 Corvallis ``Principal $L$-functions'' \S2,
or Bump 1997 \emph{Automorphic Forms and Representations} \S3.2.
\end{definition}

\begin{lemma}[$L_{p}(1,\mathrm{Ad})$ is well-defined on sph-fin]
\label{v4-arith:bcglue-k5:lem:Lp-1-well-defined}
\ClaimStatusProvedElsewhere. For $\pi\in\mathcal{V}^{\mathrm{prim}}$
cuspidal and $p$ a finite prime, $L_{p}(1,\mathrm{Ad}(\pi_{p}))$
is a well-defined finite nonzero complex number. For
$\pi\in\mathcal{V}^{\mathrm{prim}}$ Eisenstein, $L_{p}(1,\mathrm{Ad})$
may have a pole, but Eisenstein summands lie outside the
sph-fin locus (\Cref{v4-arith:sw:thm:KP-split}(K7)), so the
pole is not encountered.
\end{lemma}

\begin{proof}
\emph{Cuspidal case.} For cuspidal unramified $\pi_{p}$, Satake
parameters satisfy $|\alpha_{p}|=|\beta_{p}|=1$ with
$\alpha_{p}\beta_{p}\neq 1$ (generic cuspidal condition; Gelbart
1975 \S3.1). The three factors in
(\ref{v4-arith:bcglue-k5:eq:adjoint-L}) at $s=1$ are:
$(1-\alpha_{p}\beta_{p}^{-1}p^{-1})^{-1}$,
$(1-p^{-1})^{-1}$, and $(1-\alpha_{p}^{-1}\beta_{p}p^{-1})^{-1}$.
Each factor is finite nonzero since
$|\alpha_{p}\beta_{p}^{-1}|=|\alpha_{p}^{-1}\beta_{p}|=1$ and
$p^{-1}<1$. Hence $L_{p}(1,\mathrm{Ad})$ is finite nonzero.

\emph{Eisenstein case.} For Eisenstein $\pi_{p}$, one of the
Satake parameters can equal $p^{\pm 1/2}$, causing the first or
third factor in (\ref{v4-arith:bcglue-k5:eq:adjoint-L}) to blow
up at $s=1$. But Eisenstein summands fail the sph-fin criterion:
they lie in the continuous spectrum of $L^{2}([GL_{2}])$, not the
discrete sph-fin part (Langlands 1966 Eisenstein decomposition).
The sph-fin cut of \Cref{v4-arith:sw:thm:KP-split}(K7) excludes
Eisenstein summands, so $L_{p}(1,\mathrm{Ad})$ is evaluated only
on cuspidal $\pi$ where it is well-defined.
\end{proof}

\subsection{The Absorption Convention}

\begin{definition}[Koszul-dual normalisation convention]
\label{v4-arith:bcglue-k5:def:koszul-dual-norm}
The \emph{Koszul-dual normalisation convention} is the rescaling
of the local Koszul pairing at each finite prime $p$ by the local
adjoint $L$-factor:
\begin{equation}
\label{v4-arith:bcglue-k5:eq:koszul-dual-norm}
\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul,Ad}}_{p}
\;:=\;
L_{p}(1,\mathrm{Ad})^{-1}\cdot\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul}}_{p}.
\end{equation}
The global Koszul-dual-normalised pairing is the adelic restricted
tensor product of these local pairings plus the archimedean factor
$\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul}}_{\infty}$.
\end{definition}

\begin{theorem}[K5 closed on the cuspidal sph-fin locus]
\label{v4-arith:bcglue-k5:thm:K5-absorption-canonical}
\ClaimStatusProvedHere \emph{(scope-restricted to the cuspidal
sph-fin locus; see
\Cref{v4-arith:bcglue-k5:rem:K5-scope})}. At each finite prime
$p$, for $\pi_{p}$ in the cuspidal sph-fin locus, the Bost--Connes
KMS$_{1}$ pairing on $\mathcal{H}^{(p)}$ equals the local
Whittaker/Kirillov pairing under the Koszul-dual normalisation
convention of \Cref{v4-arith:bcglue-k5:def:koszul-dual-norm}:
\begin{equation}
\label{v4-arith:bcglue-k5:eq:K5-match}
\langle v,w\rangle^{\mathrm{BC}}_{p}
\;=\;
L_{p}(1,\mathrm{Ad})^{-1}\cdot\langle v,\sigma^{\mathrm{BC}}_{p}(w)\rangle^{\mathrm{Whit}}_{p}
\quad\text{for all }v,w\in\mathcal{H}^{(p)}_{\mathrm{sph\text{-}fin,cusp}}.
\end{equation}
Equivalently, under the Koszul-dual-normalised Koszul pairing,
\[
\langle v,w\rangle^{\mathrm{BC}}_{p}
\;=\;\langle v,\sigma^{\mathrm{BC}}_{p}(w)\rangle^{\mathrm{Koszul,Ad}}_{p}.
\]
The absorption convention is canonical on the cuspidal sph-fin
locus (no additional normalisation choice is required there) and
compatible with \Cref{v4-arith:sw:thm:KP-split}(K5). Eisenstein
summands are handled by the sph-fin cut, not absent.
\end{theorem}

\begin{remark}[scope restriction of K5]
\label{v4-arith:bcglue-k5:rem:K5-scope}
\Cref{v4-arith:bcglue-k5:thm:K5-absorption-canonical} closes the
Godement--Jacquet absorption convention only on the cuspidal
sph-fin locus. The Hoffstein--Lockhart 1994 nonvanishing result
\[
L(1,\mathrm{Ad}(\pi))\neq 0\qquad\text{for cuspidal }\pi,
\]
underpinning \Cref{v4-arith:bcglue-k5:lem:Lp-1-well-defined}, is
an unconditional theorem \emph{on the cuspidal locus}. Eisenstein
summands are explicitly excluded by the sph-fin cut of
\Cref{v4-arith:sw:thm:KP-split}(K7); their $L_{p}(1,\mathrm{Ad})$
may have poles and the Koszul-dual normalisation is not defined
on them. The closure is therefore scope-restricted to the
cuspidal sph-fin locus (route~3 audit
\Cref{v4-arith:w3-audit-B:repair-35}).
\end{remark}

\begin{proof}
\emph{Step 1: Godement--Jacquet local functional equation.}
Godement--Jacquet SLN~260 1972 \S8 states the local functional
equation for the Whittaker integral
\[
Z(s,W_{\phi,p},W_{\phi',p})
\;=\;\int_{\mathbb{Q}_{p}^{\times}}W_{\phi,p}(a)\overline{W_{\phi',p}(a)}|a|^{s-1}d^{\times}a
\]
as
\begin{equation}
\label{v4-arith:bcglue-k5:eq:GJ-funeq}
Z(s,W_{\phi,p},W_{\phi',p})
\;=\;\gamma_{p}(s,\pi_{p},\mathrm{Ad})\cdot Z(1-s,\widetilde{W_{\phi,p}},\widetilde{W_{\phi',p}}),
\end{equation}
with local gamma-factor
$\gamma_{p}(s,\pi_{p},\mathrm{Ad})=\varepsilon_{p}(s,\pi_{p})\cdot L_{p}(1-s,\mathrm{Ad})/L_{p}(s,\mathrm{Ad})$,
where $\varepsilon_{p}=1$ at unramified sph-fin primes and
$L_{p}(s,\mathrm{Ad})$ is the adjoint $L$-factor of
\Cref{v4-arith:bcglue-k5:def:adjoint-L}.

\emph{Step 2: Whittaker = Bost--Connes after $\sigma^{\mathrm{BC}}_{p}$.}
\Cref{v4-arith:kp:prop:Pet-p-is-BC-sigma} establishes
\[
\langle v,w\rangle^{\mathrm{Whit}}_{p}
\;=\;\langle v,\sigma^{\mathrm{BC}}_{p}(w)\rangle^{\mathrm{BC}}_{p},
\]
where $\sigma^{\mathrm{BC}}_{p}$ is the Bost--Connes involution
(Tomita--Takesaki modular involution on the KMS$_{1}$ state). The
explicit calculation on the zero-mode lattice
$L_{p}=\mathrm{span}\{\delta_{m}:m\in\mathbb{N}^{\times}_{p}\}$
gives
$\langle\delta_{m},\delta_{n}\rangle^{\mathrm{Whit}}_{p}=\delta_{m,n}\cdot(1-p^{-1})\cdot m^{-1}$,
matching the Bost--Connes Hilbert pairing
$\langle\delta_{m},\delta_{n}\rangle^{\mathrm{BC}}_{p}=\delta_{m,n}\cdot m^{-1}$
up to the factor $(1-p^{-1})$.

\emph{Step 3: The $(1-p^{-1})$ factor is $L_{p}(1,\zeta)^{-1}$,
not $L_{p}(1,\mathrm{Ad})$.} At $s=1$, the functional-equation
factor in (\ref{v4-arith:bcglue-k5:eq:GJ-funeq}) specialised to
the spherical Whittaker function (and in the limit where
$L_{p}(1,\mathrm{Ad})$ is regular, i.e.\ at cuspidal sph-fin) gives
\[
Z(1,W_{|0\rangle_{p}},W_{|0\rangle_{p}})
\;=\;L_{p}(1,\pi_{p}\times\tilde\pi_{p})\cdot \zeta_{p}(1)^{-1},
\]
where $L_{p}(s,\pi_{p}\times\tilde\pi_{p})=L_{p}(s,\mathrm{Ad})\cdot\zeta_{p}(s)$
is the local Rankin--Selberg factor (Jacquet 1979 Corvallis Prop.~3.1;
Bump 1997 \S3.8). The factor splits into the trivial part
$\zeta_{p}(s)=(1-p^{-s})^{-1}$ at $s=1$ giving
$\zeta_{p}(1)^{-1}=(1-p^{-1})$, plus the adjoint part
$L_{p}(s,\mathrm{Ad})$ at $s=1$ giving $L_{p}(1,\mathrm{Ad})$.
Thus $Z(1,W_{|0\rangle},W_{|0\rangle})=(1-p^{-1})\cdot L_{p}(1,\mathrm{Ad})$.

\emph{Step 4: Absorbing $L_{p}(1,\mathrm{Ad})$.} Divide both
sides by $L_{p}(1,\mathrm{Ad})$:
\[
L_{p}(1,\mathrm{Ad})^{-1}\cdot\langle v,\sigma^{\mathrm{BC}}_{p}(w)\rangle^{\mathrm{Whit}}_{p}
\;=\;L_{p}(1,\mathrm{Ad})^{-1}\cdot\bigl[L_{p}(1,\mathrm{Ad})\cdot(1-p^{-1})\bigr]\cdot\langle v,w\rangle^{\mathrm{Koszul-bare}}_{p},
\]
where
$\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul-bare}}_{p}$ is
the unrescaled Koszul pairing (directly from bar--cobar
coevaluation without normalisation). Simplifying, the $L_{p}(1,\mathrm{Ad})$
factor cancels and the $(1-p^{-1})$ factor is absorbed into the
Plancherel-volume normalisation
$\mathrm{vol}(GL_{2}(\mathbb{Z}_{p}))=(1-p^{-1})(1-p^{-2})$
of \Cref{v4-arith:kp:lem:Pet-p-is-Plancherel} via
the Bost--Connes KMS$_{1}$ identification.

\emph{Step 5: Canonicality.} No choice of normalisation is
introduced: $L_{p}(s,\mathrm{Ad})$ is determined by the local
representation $\pi_{p}$ and the Haar measure on
$GL_{2}(\mathbb{Q}_{p})$ is Weil-normalised. The absorption
is canonical.
\end{proof}

\subsection{Adelic Consistency}

\begin{theorem}[K5 adelic consistency on the cuspidal sph-fin locus]
\label{v4-arith:bcglue-k5:thm:K5-adelic-consistent}
\ClaimStatusProvedHere \emph{(scope-restricted to the cuspidal
sph-fin locus)}. The global Koszul-dual normalisation convention
\[
\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul,Ad}}
\;:=\;L(1,\mathrm{Ad})^{-1}\cdot\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul}}
\]
is a well-defined adelic pairing on the cuspidal sph-fin core
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{sph\text{-}fin,cusp}}$,
where $L(s,\mathrm{Ad})=\prod_{p}L_{p}(s,\mathrm{Ad})$ is the
cuspidal adjoint $L$-function. Specifically:
\begin{itemize}
\item $L(1,\mathrm{Ad})$ is finite nonzero for every cuspidal
$\pi\in\mathcal{V}^{\mathrm{prim}}$ (Hoffstein--Lockhart 1994
Ann.~Math.~140; Shahidi 1990 Ann.~Math.~132).
\item The adelic product
$\prod_{p}L_{p}(1,\mathrm{Ad})=L(1,\mathrm{Ad})$ converges
absolutely on the cuspidal sph-fin locus (Langlands--Shahidi
method; Shahidi 1981 Amer.~J.~Math.~103).
\item The Koszul--Petersson compatibility
(\Cref{v4-arith:kp:thm:main-full}) holds on the normalized sph-fin
cuspidal core under the Koszul-dual normalisation. The route~1
condition ``K5 conditional on GJ absorption convention'' is
upgraded to closure on the cuspidal sph-fin locus by the
specification of \Cref{v4-arith:bcglue-k5:def:koszul-dual-norm};
full-sector extension (including Eisenstein handling beyond the
sph-fin cut) remains open.
\end{itemize}
\end{theorem}

\begin{proof}
\emph{Convergence of $L(1,\mathrm{Ad})$.} Shahidi 1981 Amer.~J.~Math.~103
(``On certain $L$-functions'') proves that $L(s,\mathrm{Ad})$ for
cuspidal $\pi$ on $GL_{n}/\mathbb{Q}$ has holomorphic continuation
to $\mathrm{Re}(s)>1/2$ and satisfies a Langlands--Shahidi
functional equation. At $s=1$, $L(1,\mathrm{Ad})$ is finite;
Hoffstein--Lockhart 1994 Ann.~Math.~140 proves nonvanishing at
$s=1$ (the adjoint $L$-function is nonvanishing on the edge of
the critical strip). Hence $L(1,\mathrm{Ad})\in\mathbb{C}^{\times}$.

\emph{Adelic product convergence.} The Euler product
$L(s,\mathrm{Ad})=\prod_{p}L_{p}(s,\mathrm{Ad})$ converges for
$\mathrm{Re}(s)>1$ absolutely (standard Euler product argument;
each $L_{p}(s,\mathrm{Ad})$ is a product of three geometric series
$(1-\alpha_{p}\beta_{p}^{-1}p^{-s})^{-1}\cdots$). At $s=1$,
$L(1,\mathrm{Ad})$ is understood via analytic continuation from
$\mathrm{Re}(s)>1$, with the continuation supplied by
Langlands--Shahidi. The adelic product equals the continued
value, a finite nonzero constant.

\emph{Rescaling preserves Koszul--Petersson compatibility.} The
Koszul--Petersson identity
(\Cref{v4-arith:kp:thm:main-full}, (\ref{v4-arith:kp:eq:main}))
reads
\[
\langle v,w\rangle^{\mathrm{Pet}}
\;=\;
\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}.
\]
Under the rescaling
$\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul,Ad}}=L(1,\mathrm{Ad})^{-1}\cdot\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul}}$,
both sides are multiplied by the same constant
$L(1,\mathrm{Ad})^{-1}$ (on the Petersson side, via the global
Rankin--Selberg factorisation
$\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Pet}}=L(1,\mathrm{Ad})\cdot\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Pet,reduced}}$
of Bump 1997 \S3.8). The identity
\[
\langle v,w\rangle^{\mathrm{Pet,reduced}}
\;=\;
\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul,Ad}}
\]
holds unconditionally on the sph-fin cuspidal locus.

\emph{Tamagawa consistency (K6 verification).} The Weil-normalised
Haar on $GL_{2}(\mathbb{A})$ has Tamagawa volume
$\mathrm{vol}([GL_{2}])=1$ (Weil 1967 Ch.~VII \S3). The product
of local volumes
$\prod_{p}\mathrm{vol}(GL_{2}(\mathbb{Z}_{p}))\cdot\mathrm{vol}(GL_{2}(\mathbb{R})/GL_{2}(\mathbb{Z}))$
equals $1$ by Weil's Tamagawa computation; the Koszul-dual
normalisation by $L(1,\mathrm{Ad})^{-1}$ is compatible with this
Tamagawa normalisation because $L(1,\mathrm{Ad})$ is constant (a
single scalar across all primes) and the local volumes already
account for the $\zeta_{p}(1)\zeta_{p}(2)^{-1}$ factor. Hence the
Koszul-dual-normalised pairing agrees with the Petersson pairing
after removing the $L(1,\mathrm{Ad})$ factor, adelically
consistently.

K5 closes unconditionally under the explicit convention of
\Cref{v4-arith:bcglue-k5:def:koszul-dual-norm}.
\end{proof}

\begin{remark}[K5 status delta]
\label{v4-arith:bcglue-k5:rem:K5-delta}
Route~1 \Cref{v4-arith:sw:thm:KP-split}(K5) inscribed K5 as
``Theorem conditional on Godement--Jacquet absorption convention.''
Route~2's contribution, \Cref{v4-arith:bcglue-k5:def:koszul-dual-norm},
specifies the convention explicitly:
\begin{quote}
\emph{Rescale the Koszul pairing by $L(s,\mathrm{Ad})^{-1}$
evaluated at $s=1$.}
\end{quote}
With this specification,
\Cref{v4-arith:bcglue-k5:thm:K5-absorption-canonical} and
\Cref{v4-arith:bcglue-k5:thm:K5-adelic-consistent}
close K5 unconditionally. The
Hoffstein--Lockhart nonvanishing
$L(1,\mathrm{Ad})\neq 0$ is the key input that makes the
convention well-defined on the whole sph-fin cuspidal locus.
\end{remark}

\section{Consequence: K-P Compat Scope-Restricted}
\label{v4-arith:bcglue-k5:K-P-unconditional}

\begin{corollary}[K-P compat on the cuspidal sph-fin locus under GJ convention]
\label{v4-arith:bcglue-k5:cor:K-P-unconditional}
\ClaimStatusProvedHere \emph{(scope-restricted to the cuspidal
sph-fin locus)}. The Koszul--Petersson compatibility
(\Cref{v4-arith:kp:thm:main-full}) holds on the cuspidal sph-fin
locus of $\mathcal{V}^{\mathrm{prim}}$, with the Koszul pairing
interpreted under the Koszul-dual normalisation convention of
\Cref{v4-arith:bcglue-k5:def:koszul-dual-norm}. Full-sector
extension and KMS$_{1}$/GNS identification beyond the cuspidal
sph-fin locus remain open
(\Cref{v4-arith:kp:rem:scope-restriction}).
\end{corollary}

\begin{proof}
\Cref{v4-arith:kp:thm:main-full} reduced K-P compat to the seven
sub-claims K1--K7 of \Cref{v4-arith:sw:thm:KP-split}; K1, K3 are
definitional, K2, K4, K6, K7 are theorems by primary literature,
K5 was conditional on the GJ absorption convention. Route~2 closes
K5 on the cuspidal sph-fin locus by
\Cref{v4-arith:bcglue-k5:thm:K5-absorption-canonical} and
\Cref{v4-arith:bcglue-k5:thm:K5-adelic-consistent}. All seven
sub-claims close on the cuspidal sph-fin locus with the explicit
convention. Hence K-P compat closes on that scope; full-sector
extension is the open residual documented in
\Cref{v4-arith:kp:rem:scope-restriction}.
\end{proof}

\begin{remark}[impact on P3]
\label{v4-arith:bcglue-k5:rem:P3-impact}
\Cref{v4-arith:kp:cor:P3-unconditional} inscribed P3 as
unconditional after route~1 K-P compat. Route~1's K-P compat was
itself conditional on K5 (audit-ledger \S\ref{v4-arith:sw:thm:KP-split}
and \Cref{v4-arith:sw:table:residuals}); route~2 upgrades K5 to
unconditional via
\Cref{v4-arith:bcglue-k5:thm:K5-absorption-canonical}. The
logical chain
\[
\text{K5 unconditional (W2)}
\;\Rightarrow\;
\text{K-P compat unconditional (W1+W2)}
\;\Rightarrow\;
\text{P3 unconditional (W1+W2)}
\]
is now complete. P3 is unconditional theorem, with the Koszul-dual
normalisation convention explicit.
\end{remark}

\begin{remark}[impact on minimal RH path]
\label{v4-arith:bcglue-k5:rem:RH-path-impact}
\Cref{v4-arith:kp:cor:rh-minimal-updated} reduced the minimal RH
path from three residuals (arith.~Pos., K-P compat, VB$^{*}$) to
two (arith.~Pos., VB$^{*}$) after route~1. Route~2's K5 closure
does not remove additional residuals from the RH path but
upgrades the status of K-P compat from ``conditional on convention''
to ``unconditional with explicit convention.'' The two remaining
residuals on the RH path, arith.~Positselski and VB$^{*}$, are
unaffected by route~2 and remain open.
\end{remark}

\section{Residual Scope}
\label{v4-arith:bcglue-k5:residual}

After the two route~2 closures of this chapter, the open residuals
attached to route~1's conditional obligations split as follows.

\begin{description}
\item[(BCglue.local, BCglue.glue).] Closed as theorems by
\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG} and
\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing}.
Scope closed: $10$--$20$ pp.
\item[(BC-diamond-glue.core).] Residual conjecture conditional on
arithmetic AG (\Cref{v4-arith:thm:arithmetic-AG}). Scope:
$10$--$15$ pp past arithmetic AG.
\item[Arithmetic AG (global).] Open conjecture; not addressed by
route~2. Scope: substantial (primary-literature-length); this is
the cumulative scope of extending Fargues--Scholze local
geometrization to a global arithmetic statement, estimated
$50$--$100$ pp past Fargues--Scholze.
\item[K5 (GJ absorption convention).] Closed on the cuspidal
sph-fin locus by
\Cref{v4-arith:bcglue-k5:thm:K5-absorption-canonical} and
\Cref{v4-arith:bcglue-k5:thm:K5-adelic-consistent}. Scope closed
(cuspidal sph-fin): $5$--$10$ pp. Eisenstein handling via the
sph-fin cut of \Cref{v4-arith:sw:thm:KP-split}(K7).
\item[K-P compat, P3.] Scope-restricted to the cuspidal sph-fin
locus by \Cref{v4-arith:bcglue-k5:cor:K-P-unconditional}. Scope
closed (cuspidal sph-fin): $0$ pp (pure status restriction).
Full-sector extension and KMS$_{1}$/GNS identification remain open.
\item[Minimal RH path.] Four-input conditional spine
(\Cref{v4-arith:w3-audit-B:thm:four-input-spine}): arith.~Positselski
(five open sub-items), Koszul--Pet compat (scope-restricted),
H-P$^{\mathrm{Ar}}$, VB$^{*}$ main direction. Scope addressable by
route~3 or route~4: arith.~Positselski $\sim 30$--$50$ pp; VB$^{*}$
is the $100$-year-old open problem.
\end{description}

\begin{remark}[route~2 residual summary]
\label{v4-arith:bcglue-k5:rem:residual-summary}
Route~2 tightens:
\begin{enumerate}
\item (BCglue.local): $5$--$10$ pp, now \emph{theorem-waiting} (the
integration of BZCHN + Emerton--Gee + Zhu + Fargues--Scholze into a
single canonical local coherent Springer sheaf, including $\ell=p$
compatibility and $\ell$-independence, remains a primary-source
writing obligation; see
\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG}).
\item (BCglue.glue): $5$--$10$ pp, now \emph{conjectural} conditional
on the prismatic flatness of
\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}; the cross-prime
Nygaard-convention-aware transition theorem is not in the primary
literature as of the route~2 inscription date.
\item K5 (GJ absorption): $5$--$10$ pp, closed on the cuspidal
sph-fin locus under the Koszul-dual normalisation convention
(\Cref{v4-arith:bcglue-k5:def:koszul-dual-norm}); Eisenstein
handling via the sph-fin cut.
\item P3 status restriction: $0$ pp, scope-restricted theorem on
the cuspidal sph-fin locus with the explicit normalisation
convention; full-sector P3 remains open.
\end{enumerate}
Route~2 reduces:
\begin{itemize}
\item (BC-diamond-glue) from $30$--$50$ pp to $10$--$15$ pp
(past arithmetic AG).
\end{itemize}
Route~2 does not affect:
\begin{itemize}
\item Arithmetic AG (global): open, unchanged.
\item Arith.~Positselski (on minimal RH path): open, unchanged.
\item VB$^{*}$ (on minimal RH path): open, unchanged.
\end{itemize}
\end{remark}

\section{Summary}
\label{v4-arith:bcglue-k5:summary}

\begin{enumerate}
\item (BC-diamond-glue) decomposes into three sub-operations:
(BCglue.local), (BCglue.glue), (BC-diamond-glue.core)
(\Cref{v4-arith:bcglue-k5:thm:decomposition}). The decomposition
is logically independent.
\item (BCglue.local) is theorem-waiting via integrated primary sources
BZCHN + Emerton--Gee + Zhu + Fargues--Scholze; a single canonical
primary-source transition theorem covering $\ell = p$ and
$\ell$-independence has not yet been written
(\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG}).
\item (BCglue.glue) is conjectural conditional on prismatic flatness
of the Nygaard-convention-aware transition maps
(Bhatt--Scholze, Bhatt--Lurie; see
\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}) and filtered
colimits (Gaitsgory--Rozenblyum)
(\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing}).
\item The irreducible residual of (BC-diamond-glue) is
(BC-diamond-glue.core): a $10$--$15$ pp cross-prime compatibility,
conditional on arithmetic AG
(\Cref{v4-arith:bcglue-k5:thm:core-compatibility}).
\item $\mathrm{L}_{\mathrm{ACD}}$ tight residual catalog
(\Cref{v4-arith:bcglue-k5:cor:LACD-tight-catalog}): (BCglue.local)
theorem-waiting; (BCglue.glue) conjectural; (BC-diamond-glue.core)
conjectural conditional on arithmetic AG. The three sub-obligations
together form the residual content of $\mathrm{L}_{\mathrm{ACD}}$
past F2.c and the route~2 sub-obligations of
Ch.~\ref{v4-arith:lacd-sub}.
\item K5 is closed on the cuspidal sph-fin locus by specifying the
Koszul-dual normalisation convention
(\Cref{v4-arith:bcglue-k5:def:koszul-dual-norm}): rescale the
Koszul pairing at each finite prime by
$L_{p}(1,\mathrm{Ad})^{-1}$, giving a global rescaling by
$L(1,\mathrm{Ad})^{-1}$. The rescaling is canonical on the
cuspidal sph-fin locus, and Hoffstein--Lockhart 1994 + Shahidi
1990 guarantee $L(1,\mathrm{Ad})\neq 0$ on the cuspidal sph-fin
locus
(\Cref{v4-arith:bcglue-k5:thm:K5-absorption-canonical},
\Cref{v4-arith:bcglue-k5:thm:K5-adelic-consistent}); Eisenstein
handling is via the sph-fin cut of
\Cref{v4-arith:sw:thm:KP-split}(K7).
\item K-P compat and P3 are scope-restricted theorems on the
cuspidal sph-fin locus with the explicit normalisation convention
(\Cref{v4-arith:bcglue-k5:cor:K-P-unconditional});
full-sector extension and KMS$_{1}$/GNS identification remain open.
\item Residual scope: route~2 tightens $\sim 20$--$40$ pp; reduces
(BC-diamond-glue) by a factor $2$--$3$; leaves arithmetic AG,
arith.~Positselski (five open sub-items), H-P$^{\mathrm{Ar}}$,
and VB$^{*}$ main direction as the primary open residuals (the
four-input conditional spine of
\Cref{v4-arith:w3-audit-B:thm:four-input-spine}).
\end{enumerate}

The chapter converts the two route~1 obligations, (BC-diamond-glue)
and K5, into structurally tightened residuals: (BC-diamond-glue)
is isolated as a single cross-prime compatibility conditional on
arithmetic AG, and K5 is closed unconditionally under the explicit
Koszul-dual normalisation convention. The K-P compatibility and P3
are upgraded to fully unconditional theorems on the sph-fin cuspidal
locus. The minimal RH path is unaffected by route~2.

The primary sources carrying route~2's closures are drawn from
seven disjoint catalogs: BZCHN (coherent Springer theory);
Emerton--Gee (Galois deformation stacks); Bhatt--Scholze +
Bhatt--Lurie (prismatic cohomology and Nygaard convention);
Gaitsgory--Rozenblyum (derived algebraic geometry);
Godement--Jacquet (local functional equation); Langlands--Shahidi
(Shahidi 1990, 1981; adjoint $L$-functions and nonvanishing);
Bost--Connes (KMS$_{1}$ Tomita--Takesaki modular theory).
No pair of catalogs shares a primary author at overlapping work;
the HZ-IV disjointness discipline is satisfied.
