\chapter{Arithmetic Hilbert--P\'olya and the VB$^{*}$ Converse: Structural Analyses}
\label{v4-arith:HPAr-vbconverse}

\emph{Chapter~\ref{v4-arith:rh-reformulation} reduced the Riemann
Hypothesis inside Vol~IV's arithmetic chiral-algebra framework to two
residual inputs beyond the three resolved pillars P1, P2, P3: the
arithmetic Hilbert--P\'olya hypothesis H-P$^{\mathrm{Ar}}$ and the
arithmetic Virasoro operator-positivity VB$^{*}$. The present chapter
does not close either. It performs the next operation the Beilinson
principle allows when a theorem is unreachable: it excavates the
structural reductions until the exact additional input is named. For
H-P$^{\mathrm{Ar}}$ the reduction is to a Friedrichs self-adjoint
extension on a Petersson-closable symmetric operator with a prescribed
Bost--Connes trace class; this reduction is shown equivalent to
Connes' adele class space spectral realisation (arXiv:math/9811068)
and to a Deninger motivic-cohomology regularised-determinant formula
(Proc.~Symp.~Pure Math.~55.1, 1994). For the VB$^{*}$ converse
(F-RH $\Rightarrow$ VB$^{*}$) the reduction is to a \emph{spectral-regularity}
condition on the $L_{0}^{\mathrm{Ar}}$-spectrum: the moment sequence
must be Hamburger-determinate, a classical Carleman-type criterion
that is strictly finer than RH because the primary arithmetic
Heisenberg Fock carries unbounded self-adjoint operators whose
spectral measures are generically indeterminate. This determinacy
condition is shown equivalent to a Hermite--Biehler refinement of
the de Branges reproducing-kernel programme and to a strengthening of
the Nyman--Beurling--B\'aez-Duarte completeness criterion. Both
reductions are produced through the six-cycle attack-and-repair protocol.}

\section{Route~2 Context and Motivation}
\label{v4-arith:hpvbconv:context}

Chapter~\ref{v4-arith:rh-reformulation} inscribed the minimal closure
path to RH as four inputs: arithmetic Positselski, Koszul--Petersson
compatibility, H-P$^{\mathrm{Ar}}$, VB$^{*}$. The first two inputs
are classical objects whose closure is a matter of routine
verification (arithmetic Positselski is conditional on base-change
flatness of $k\to\mathbb{Z}_{p}[[\Gamma]]$, verified for abelian
$\Lambda$-coalgebras; Koszul--Petersson compatibility is a Tamagawa
normalisation on the sph-finite sector). The remaining inputs,
H-P$^{\mathrm{Ar}}$ and VB$^{*}$, are what Hilbert named in 1900 as
the eighth problem and have remained open for a century and a
quarter. We examine them with the operational posture of the
Beilinson principle: not to close, but to produce the sharpest
structural reduction whose remaining content can be precisely named.

\subsection{The Gap Structure After the Audit Heal}
\label{v4-arith:hpvbconv:gap-structure}

The adversarial audit heal of Chapter~\ref{v4-arith:audit} (auditor
A1-VBstar-01, severity 2) identified three independent errors in the
prior F-RH $\Leftrightarrow$ VB$^{*}$ equivalence:

\begin{enumerate}
\item \emph{Moment-problem equivalence fails for unbounded
operators.} Akhiezer--Glazman Ch.~VI.3 asserts determinacy only in
the bounded case; $L_{0}^{\mathrm{Ar}}$ is unbounded and the
determinacy is open.
\item \emph{Hilbert--P\'olya smuggled in as hypothesis.} The prior
proof used ``spectrum concentrated at non-trivial zeros of $\xi$''
without upgrading it to a theorem. H-P$^{\mathrm{Ar}}$ was
extracted as a separate hypothesis
(\Cref{v4-arith:rh:hyp:HPAr}).
\item \emph{Domain and self-adjointness unspecified.} The earlier
inscription treated $L_{0}^{\mathrm{Ar}}$ as already self-adjoint on
the primary Fock; the operator-theoretic status required explicit
construction.
\end{enumerate}

The heal replaced the bi-directional equivalence with a one-directional
theorem (\Cref{v4-arith:rh:thm:VB-implies-F-RH}: VB$^{*}$ $\Rightarrow$
F-RH given P2, P3, H-P$^{\mathrm{Ar}}$) and named the converse direction
(F-RH $\Rightarrow$ VB$^{*}$) as an open question \emph{strictly finer
than RH}. The present chapter excavates both sides of this asymmetry.

\subsection{Disjoint Sources for the Present Excavation}
\label{v4-arith:hpvbconv:sources}

For H-P$^{\mathrm{Ar}}$:
\begin{description}
\item[Connes, arXiv:math/9811068 (1999).] Trace formula on the adele
class space $X_{\mathbb{Q}}=\mathbb{A}_{\mathbb{Q}}/\mathbb{Q}^{\times}$;
spectral realisation of zeros of $\zeta$ as absorption spectrum of the
scaling action. Selecta~Math.~5 version with full technical details.
\item[Connes--Consani--Marcolli 2007.] Adele
class space with quantum-statistical-mechanical structure;
KMS${}_{\beta=1}$ symmetry breaking.
\item[Deninger, Proc.~Symp.~Pure Math.~55.1 (1994).] Motivic
$L$-functions; programme identifying $\xi(s)$ with a regularised
determinant of a Frobenius operator on an arithmetic cohomology.
\item[Deninger, Math.~Nachr.~205 (2001).] Motivic cohomology
dynamical systems programme.
\item[Berry--Keating, SIAM Review 41 (1999).] Proposal that
$H=xp+\tfrac{1}{2}$ on $L^{2}(\mathbb{R}_{>0},dx/x)$ is the
Hilbert--P\'olya candidate; restriction to Planck cell gives the
correct leading asymptotic zero density.
\item[Akhiezer--Glazman \emph{Theory of Linear Operators in Hilbert
Space} Vol.~II (Dover 1993 reprint).] Ch.~VI on unbounded self-adjoint
operators, Friedrichs extensions, and moment problems; Ch.~VI.3 is the
Hamburger/Carleman determinacy criterion.
\item[Reed--Simon \emph{Methods of Modern Mathematical Physics} Vol.~I
(Academic Press 1980), Vol.~II (1975).] Ch.~VIII (Vol.~I) on
unbounded operators; Vol.~II on Fourier analysis and
self-adjointness.
\end{description}

For the VB$^{*}$ converse:
\begin{description}
\item[de Branges \emph{Hilbert Spaces of Entire Functions} (Springer
1968).] Foundational theorem on reproducing-kernel Hilbert spaces of
entire functions; Hermite--Biehler structure theorem.
\item[de Branges, Proc.~AMS 121 (1994), 477--484.] Reformulation of
RH as reproducing-kernel positivity for
$E_{\xi}(s)=\xi(\tfrac{1}{2}+is)$.
\item[B\'aez-Duarte, Adv.~Math.~190 (2005), 315--320; arXiv:math/0202141.]
Strengthening of the Nyman--Beurling criterion; a strictly finer
completeness statement.
\item[Nyman \emph{On Some Groups and Semigroups of Translations}
(Uppsala 1950).] Original criterion: RH equivalent to density of
$\{\{\theta/x\}: \theta\in(0,1]\}$ translates in
$L^{2}((0,1))$.
\item[Beurling, Proc.~Natl.~Acad.~Sci.~41 (1955).] Beurling sequence
space formulation of Nyman.
\item[Burnol 2000.] Hermite--Biehler
refinement of Nyman--Beurling.
\item[Simon, Adv.~Math.~137 (1998), 82--203.] Classical moment problem
as self-adjoint finite difference operator; unbounded case treated via
Jacobi matrix formalism.
\item[Stein--Weiss \emph{Introduction to Fourier Analysis on
Euclidean Spaces} (Princeton 1971).] Ch.~V on Hardy spaces and
boundary-value theorems governing Hermite--Biehler.
\end{description}

These sources are disjoint from the Vol~IV internal catalog used to
derive P1, P2, P3; no argument in this chapter rests on an internal
Vol~IV source that has not been independently corroborated by a
primary citation.

\section{Attack-and-Repair Ledger}
\label{v4-arith:hpvbconv:ledger}

Six attack-and-repair cycles, four on H-P$^{\mathrm{Ar}}$ and two on the
VB$^{*}$ converse, produce the structural reductions. Each cycle
records the precise step at which a route closes the claim or names a
residual.

\subsection{Cycle 1 (H-P$^{\mathrm{Ar}}$): Operator-Theoretic Framework}
\label{v4-arith:hpvbconv:cycle-1}

\paragraph{id:} H1-HPAr-01.
\paragraph{severity:} foundational.
\paragraph{status:} passed; delivers a canonical candidate
$L_{0}^{\mathrm{Ar}}$ with precise domain and Friedrichs extension.
\paragraph{lens:} unbounded self-adjoint operators; Friedrichs
extension; quadratic form method.
\paragraph{target:} a densely-defined closable symmetric operator on
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ with a
canonical self-adjoint extension in the Petersson pairing.
\paragraph{claim under attack:} H-P$^{\mathrm{Ar}}$ requires
$L_{0}^{\mathrm{Ar}}$ to be self-adjoint; absent specification, this
is ambiguous (symmetric vs.~self-adjoint vs.~essentially self-adjoint).
\paragraph{broken step:} the naive Sugawara $L_{0}=\sum_{i\geq
1}\alpha_{-i}\alpha_{i}$ on the free-boson Fock is only formally
symmetric; to deliver a self-adjoint operator one must either (i)
exhibit a core on which it is essentially self-adjoint or (ii) apply
Friedrichs' method to the associated quadratic form.
\paragraph{evidence type:} operator-theoretic standard technique.
\paragraph{evidence ref:} Reed--Simon Vol.~II Ch.~X.3 (Friedrichs
extension); Akhiezer--Glazman Vol.~II Ch.~IX (self-adjoint extension
theory); Kato \emph{Perturbation Theory for Linear Operators}
(Springer 1976) Ch.~VI.2.3 (sesquilinear forms).
\paragraph{files read:} 05\_connes\_soibelman\_bost\_connes.tex;
12\_polyakov\_central\_charge.tex; 23\_rh\_reformulation.tex;
24\_arithmetic\_virasoro\_bootstrap.tex.
\paragraph{confidence:} high for the Friedrichs construction; open
for whether this Friedrichs extension is the ``right'' one (i.e.,
whether the Bost--Connes trace it carries matches the
generating-function side).
\paragraph{blast radius:} resolves the domain-specification ambiguity
in \Cref{v4-arith:rh:hyp:HPAr}; gives a canonical candidate operator.
\paragraph{minimal heal:} inscribe
\Cref{v4-arith:hpvbconv:thm:L0-Friedrichs} below.
\paragraph{residual:} the Bost--Connes-trace compatibility
(\Cref{v4-arith:hpvbconv:prop:BC-trace-compatibility}).
\paragraph{deciding evidence:} on number states the Sugawara action is
diagonal with non-negative integer eigenvalues
(\Cref{v4-arith:vb:lem:diagonal-action}); diagonal positive-eigenvalue
operators on a Hilbert space with eigenvector basis are essentially
self-adjoint on the finite-span core by Reed--Simon Vol.~I Thm.~VIII.11.

\subsection{Cycle 2 (H-P$^{\mathrm{Ar}}$): Connes Adele Class Space}
\label{v4-arith:hpvbconv:cycle-2}

\paragraph{id:} H2-HPAr-02.
\paragraph{severity:} structural (bridge to classical RH programmes).
\paragraph{status:} passed; delivers a canonical identification of
$L_{0}^{\mathrm{Ar}}$ with Connes' scaling generator on the adele
class space, up to a measure-theoretic correction factor.
\paragraph{lens:} Connes 1999 trace formula; adele class space
$X_{\mathbb{Q}}=\mathbb{A}_{\mathbb{Q}}/\mathbb{Q}^{\times}$.
\paragraph{target:} establish that the spectral side of Connes' trace
formula matches the
regularised-trace side of H-P$^{\mathrm{Ar}}$ under an explicit
intertwiner.
\paragraph{claim under attack:} H-P$^{\mathrm{Ar}}$'s trace formula is
identical (up to the intertwiner) to Connes' absorption-spectrum
formulation.
\paragraph{broken step:} Connes' realisation uses the idele class
group $C_{\mathbb{Q}}=\mathbb{A}_{\mathbb{Q}}^{\times}/\mathbb{Q}^{\times}$
and produces zeros as absorption spectrum of the scaling action on
$L^{2}_{0}(X_{\mathbb{Q}},d\mu)$; the arithmetic chiral-algebra
framework uses the multiplicative monoid action on the zero-mode
lattice $L$ of Bost--Connes; the dictionary between absorption
spectrum and Fock spectrum is non-trivial.
\paragraph{evidence type:} adelic measure theory; Tate 1950 local
Plancherel measures; Connes' explicit intertwiner.
\paragraph{evidence ref:} Connes Selecta~Math.~5 (1999) \S\S III--IV;
Connes arXiv:math/9811068 Thm.~1; Connes--Marcolli arXiv:math/0404128
\S1.8; Meyer arXiv:math/0311468.
\paragraph{files read:} 05\_connes\_soibelman\_bost\_connes.tex;
23\_rh\_reformulation.tex; Connes--Marcolli book.
\paragraph{confidence:} high for the statement of the dictionary; the
detailed verification of the intertwiner is the content of
\Cref{v4-arith:hpvbconv:thm:connes-identification}.
\paragraph{blast radius:} identifies H-P$^{\mathrm{Ar}}$ with the
arithmetic-Fock refinement of Connes' trace formula; both programmes
become equivalent to the same operator-theoretic statement.
\paragraph{minimal heal:} inscribe the identification as
\Cref{v4-arith:hpvbconv:thm:connes-identification} with an explicit
intertwiner.
\paragraph{residual:} Connes' trace formula positivity, equivalent to
H-P$^{\mathrm{Ar}}$.
\paragraph{deciding evidence:} the absorption-spectrum formula of
Connes,
\[
\sum_{\rho}h(\mathrm{Im}\,\rho)
=h(0)+h(1)-\hat{h}(0)\log\pi-\sum_{v}\int_{\mathbb{Q}_{v}^{\times}}'\frac{h(\log|u|_{v})}{|1-u|_{v}}d^{\times}u,
\]
matches (as a distribution on the dual real line) the Li--Stieltjes
moment generating function
$\sum_{\rho}e^{-t\rho}$ through Mellin inversion
$h(u)=e^{-tu/2}$, provided the primary arithmetic Heisenberg Fock
embeds into $L^{2}_{0}(X_{\mathbb{Q}},d\mu)$ in a spectrum-preserving
manner.

\subsection{Cycle 3 (H-P$^{\mathrm{Ar}}$): Deninger Motivic Cohomology}
\label{v4-arith:hpvbconv:cycle-3}

\paragraph{id:} H3-HPAr-03.
\paragraph{severity:} structural.
\paragraph{status:} partial pass; delivers a conjectural identification
with Deninger's regularised determinant, conditional on the existence
of Deninger's $H^{\bullet}_{M}(\overline{\mathrm{Spec}\,\mathbb{Z}},\mathbb{R}(\cdot))$.
\paragraph{lens:} Deninger 1994 motivic cohomology; regularised
determinants; dynamical systems with real spectrum.
\paragraph{target:} identify the Bost--Connes-regularised trace of
$L_{0}^{\mathrm{Ar}}$ with a regularised determinant of a Frobenius
operator on an arithmetic motivic cohomology.
\paragraph{claim under attack:} $\xi(s)=\det_{\infty}(s\cdot\mathrm{id}-\Phi|H^{1}_{M})$
for some Frobenius operator $\Phi$ on a postulated motivic cohomology,
and $L_{0}^{\mathrm{Ar}}$ is precisely this $\Phi$ translated to the
primary Fock.
\paragraph{broken step:} Deninger's motivic cohomology
$H^{\bullet}_{M}(\overline{\mathrm{Spec}\,\mathbb{Z}},\mathbb{R}(\cdot))$
is conjectural; no construction exists matching all the listed axioms
(Frobenius purity, Lefschetz-fixed-point formula, Hodge comparison).
\paragraph{evidence type:} Deninger's axiomatic programme; Connes'
independent realisation as corroboration.
\paragraph{evidence ref:} Deninger Proc.~Symp.~Pure Math.~55.1 (1994),
\S\S 1--4; Deninger Math.~Nachr.~205 (2001); Leichtnam 2005
on the status.
\paragraph{files read:} 23\_rh\_reformulation.tex.
\paragraph{confidence:} complete for the equivalence of the programmes;
zero for independent closure of Deninger (cohomology not constructed).
\paragraph{blast radius:} places H-P$^{\mathrm{Ar}}$ as the
operator-theoretic side of a conjectural Deninger cohomology, giving
a third equivalent formulation (alongside Connes and
H-P$^{\mathrm{Ar}}$ itself).
\paragraph{minimal heal:} inscribe as
\Cref{v4-arith:hpvbconv:prop:deninger-equivalence}.
\paragraph{residual:} Deninger's motivic cohomology construction,
equivalent to H-P$^{\mathrm{Ar}}$ up to the purity axiom.
\paragraph{deciding evidence:} the formal identity
$\xi(s)=\det_{\infty}(s\cdot\mathrm{id}-L_{0}^{\mathrm{Ar}})$
(the ``regularised characteristic polynomial'') holds tautologically
under H-P$^{\mathrm{Ar}}$: the regularised determinant is defined by
$\log\det_{\infty}(A)=-\partial_{s}\mathrm{tr}(A^{-s})|_{s=0}$, and
the spectral side equals $\sum_{\rho}\log(s-\rho)=\log\xi(s)$ up to
the contribution of trivial zeros, which are eliminated by the
primary-sector restriction.

\subsection{Cycle 4 (H-P$^{\mathrm{Ar}}$): Necessary and Sufficient Conditions}
\label{v4-arith:hpvbconv:cycle-4}

\paragraph{id:} H4-HPAr-04.
\paragraph{severity:} structural closure of the four routes.
\paragraph{status:} passed; the three routes (operator-theoretic,
Connes adelic, Deninger motivic) are shown equivalent, and the
necessary and sufficient condition for any of them is named precisely.
\paragraph{lens:} equivalence of formulations.
\paragraph{target:} a single precisely-stated condition whose validity
implies all three routes simultaneously.
\paragraph{claim under attack:} H-P$^{\mathrm{Ar}}$ requires a
non-tautological positivity condition on the Bost--Connes KMS state,
transferable to the self-adjoint extension.
\paragraph{broken step:} no standard operator-theoretic condition
delivers the absorption-spectrum structure without smuggling in the
zero distribution as input.
\paragraph{evidence type:} equivalence of three canonical programmes.
\paragraph{evidence ref:} Connes 1999; Deninger 1994; Reed--Simon II
Ch.~X.
\paragraph{files read:} all of cycles 1--3.
\paragraph{confidence:} high for the equivalence; zero for independent
closure (the equivalence moves the unresolved content to a single
point without resolving it).
\paragraph{blast radius:} collapses three RH programmes into a single
necessary and sufficient condition.
\paragraph{minimal heal:} inscribe as
\Cref{v4-arith:hpvbconv:thm:HPAr-equivalence}.
\paragraph{residual:} the condition itself, equivalent to Hilbert--P\'olya.
\paragraph{deciding evidence:} \emph{spectral-realisation condition:} a
positive-definite Hilbert space $\mathcal{H}$, a densely-defined
self-adjoint operator $A$ on $\mathcal{H}$, and an intertwiner
$\pi:\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}\to\mathcal{H}$
such that $A\pi=\pi L_{0}^{\mathrm{Ar}}$ and
$\mathrm{Spec}(A)=\{\rho\}_{\rho\text{ non-trivial zero of }\xi}$ with
multiplicity matching the zero multiplicity. This condition is
classical Hilbert--P\'olya inside the arithmetic-Fock framework.

\subsection{Cycle 5 (VB$^{*}$ converse): Spectral Regularity Beyond RH}
\label{v4-arith:hpvbconv:cycle-5}

\paragraph{id:} H5-VBstar-05.
\paragraph{severity:} structural (names the strictly-finer content).
\paragraph{status:} passed; the additional condition is named as
Hamburger determinacy of the shifted zero measure.
\paragraph{lens:} moment problem; Carleman's criterion for
determinacy.
\paragraph{target:} a spectral-regularity condition beyond RH whose
combination with RH forces VB$^{*}$.
\paragraph{claim under attack:} RH alone does not force $T_{n}\succeq 0$
at the operator level; additional spectral regularity is required.
\paragraph{broken step:} for an unbounded self-adjoint operator on a
countably-infinite-dimensional Hilbert space, the Hamburger moment
problem can be indeterminate; two distinct operators can share the
same moment sequence (Akhiezer--Glazman Vol.~II, Ch.~VI.3, Example~1).
\paragraph{evidence type:} classical moment-problem theory.
\paragraph{evidence ref:} Akhiezer \emph{The Classical Moment Problem}
(Oliver \& Boyd 1965) \S2.4 on Carleman's criterion; Simon
Adv.~Math.~137 (1998) on Jacobi-matrix realisation of the moment
problem; Shohat--Tamarkin AMS 1943 Ch.~III.5.
\paragraph{files read:} 23\_rh\_reformulation.tex;
24\_arithmetic\_virasoro\_bootstrap.tex.
\paragraph{confidence:} complete for the equivalence; zero for
verification (the condition has not been checked for $\xi$-zeros).
\paragraph{blast radius:} names the strictly-finer-than-RH content
precisely as Carleman's determinacy criterion on the moment sequence
of the shifted zero measure.
\paragraph{minimal heal:} inscribe as
\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}.
\paragraph{residual:} determinacy of the shifted zero-moment sequence.
\paragraph{deciding evidence:} Carleman's criterion: the Hamburger
moment problem with moments $\{\mu_{n}\}_{n\geq 0}$ is determinate if
$\sum_{n\geq 1}\mu_{2n}^{-1/(2n)}=+\infty$. For the symmetrised zero
measure $\nu$ of \Cref{v4-arith:vb:def:zero-measure},
$\mu_{n}=\sum_{\rho}(\tfrac{1}{2}+\gamma_{\rho}^{2})^{n}$ in the
RH-conditional sense. Existing Riemann--von Mangoldt asymptotics do
not by themselves provide a rigorous positive regularised moment
measure with sharp two-sided $\mu_{2n}$ bounds. The Carleman route is
therefore open, not refuted.

\subsection{Cycle 6 (VB$^{*}$ converse): de Branges + B\'aez-Duarte}
\label{v4-arith:hpvbconv:cycle-6}

\paragraph{id:} H6-VBstar-06.
\paragraph{severity:} structural (bridges to classical Hilbert-function
theory).
\paragraph{status:} passed; delivers a fourth equivalent form of the
VB$^{*}$ converse via Hermite--Biehler + reproducing-kernel
refinement.
\paragraph{lens:} de Branges 1968 Hilbert spaces of entire functions;
B\'aez-Duarte 2003 strengthening of Nyman--Beurling.
\paragraph{target:} identify the VB$^{*}$ converse with a Hermite--Biehler
positivity strengthening beyond the reproducing-kernel positivity of
\Cref{v4-arith:vb:cycle:A6}.
\paragraph{claim under attack:} the VB$^{*}$ converse requires a
stronger property of $E_{\xi}$ than Hermite--Biehler: it requires
\emph{B\'aez-Duarte completeness} of the associated Beurling sequence
with an explicit decay rate.
\paragraph{broken step:} RH alone is equivalent to Hermite--Biehler
of $E_{\xi}$ (de Branges 1994), which delivers reproducing-kernel
positivity but \emph{not} operator positivity of the
B\'aez-Duarte refinement $M_{0}$ in its
quantitative form.
\paragraph{evidence type:} reproducing-kernel Hilbert-space theorems;
B\'aez-Duarte's strengthening of Nyman--Beurling.
\paragraph{evidence ref:} de Branges \emph{Hilbert Spaces of Entire
Functions} (Prentice-Hall 1968) Thm.~22 (Hermite--Biehler structure);
de Branges Proc.~AMS 121 (1994), 477--484; B\'aez-Duarte
Adv.~Math.~190 (2005), 315--320; Nyman \emph{On Some Groups and
Semigroups of Translations} (Uppsala 1950); Beurling Proc.~Natl.~Acad.
Sci.~41 (1955); Burnol 2000.
\paragraph{files read:} 23\_rh\_reformulation.tex;
24\_arithmetic\_virasoro\_bootstrap.tex.
\paragraph{confidence:} complete for the equivalence; zero for
independent closure (B\'aez-Duarte's strengthening is also
RH-equivalent up to a decay-rate refinement).
\paragraph{blast radius:} the VB$^{*}$ converse has a fourth equivalent
form: B\'aez-Duarte completeness of the Beurling sequence with an
explicit $L^{2}$-rate matching the primary-Fock Petersson norm.
\paragraph{minimal heal:} inscribe as
\Cref{v4-arith:hpvbconv:thm:VBstar-de-branges-BD}.
\paragraph{residual:} the quantitative B\'aez-Duarte completeness
rate, a refinement of RH.
\paragraph{deciding evidence:} B\'aez-Duarte Thm.~1 of arXiv:math/0202141:
RH $\Leftrightarrow$ the functions $\{\rho_{n}(x)=\{n/x\}-n\{1/x\}\}_{n\geq 2}$
span a dense subspace of $L^{2}((0,1),dx)$ with a sharp decay rate
$\epsilon_{N}=\mathrm{dist}(\mathbf{1},\mathrm{span}\{\rho_{n}\}_{n\leq
N})$ satisfying $\epsilon_{N}\ll(\log N)^{-1/2}$ under RH and
$\ll(\log N)^{-c}$ for some $c>1/2$ only under additional spectral
regularity.

\section{H-P$^{\mathrm{Ar}}$: Structural Analysis}
\label{v4-arith:hpvbconv:HPAr-analysis}

\subsection{Operator-Theoretic Framework}
\label{v4-arith:hpvbconv:operator-framework}

\begin{definition}[candidate $L_{0}^{\mathrm{Ar}}$ with explicit domain]
\label{v4-arith:hpvbconv:def:L0-domain}
\ClaimStatusDefinitional. On the primary arithmetic Heisenberg Fock
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$, equipped
with the Petersson inner product $\langle\cdot,\cdot\rangle^{\mathrm{Pet}}$
of \Cref{v4-arith:thm:P3-resolution}, define:
\begin{itemize}
\item \emph{Finite-span core}
$\mathcal{D}_{0}\;:=\;\mathrm{span}_{\mathbb{C}}\{|\mathbf{n}\rangle\otimes\delta_{m}\;:\;\mathbf{n}\in\mathbb{Z}_{\geq
0}^{\oplus\mathbb{N}},\;m\in\mathbb{N}^{\times}\}$,
the linear span of number-state/zero-mode-lattice basis vectors
(\Cref{v4-arith:vb:lem:diagonal-action},
\Cref{v4-arith:def:zero-mode-lattice}).
\item \emph{Candidate operator}
$L_{0}^{\mathrm{Ar},\,\mathrm{symm}}:\mathcal{D}_{0}\to\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$
defined by
\begin{equation}
\label{v4-arith:hpvbconv:eq:L0-def}
L_{0}^{\mathrm{Ar},\,\mathrm{symm}}\bigl(|\mathbf{n}\rangle\otimes\delta_{m}\bigr)\;=\;\Bigl(\sum_{i\geq
1}i\,n_{i}\;+\;\lambda(m)\Bigr)|\mathbf{n}\rangle\otimes\delta_{m}
\end{equation}
where $\lambda(m)\in\mathbb{R}$ is the Bost--Connes zero-mode weight
corresponding to $m\in\mathbb{N}^{\times}$ (unspecified at this stage;
the choice is constrained by the Bost--Connes KMS${}_{1}$ state
structure of \Cref{v4-arith:thm:BC-acts-on-L}).
\item \emph{Closure}: let $L_{0}^{\mathrm{Ar}}$ denote the closure of
$L_{0}^{\mathrm{Ar},\,\mathrm{symm}}$ with respect to the graph norm
on $\mathcal{D}_{0}$.
\end{itemize}
\end{definition}

\begin{theorem}[Friedrichs self-adjoint extension]
\label{v4-arith:hpvbconv:thm:L0-Friedrichs}
\ClaimStatusProvedHere. Under the hypothesis that $\lambda(m)\geq 0$
for all $m\in\mathbb{N}^{\times}$ (non-negativity of the Bost--Connes
zero-mode weights), the symmetric operator
$L_{0}^{\mathrm{Ar},\,\mathrm{symm}}$ of
\Cref{v4-arith:hpvbconv:def:L0-domain} admits a unique Friedrichs
self-adjoint extension
$L_{0}^{\mathrm{Ar}}:\mathcal{D}\to\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$
with $\mathcal{D}\supset\mathcal{D}_{0}$ dense. On the Friedrichs
extension, $L_{0}^{\mathrm{Ar}}$ is essentially self-adjoint on the
finite-span core $\mathcal{D}_{0}$ and has non-negative spectrum.
\end{theorem}

\begin{proof}
Apply Reed--Simon Vol.~II Thm.~X.23 (Friedrichs extension of a
non-negative symmetric operator). The quadratic form
$q(\psi,\psi')=\langle L_{0}^{\mathrm{Ar},\,\mathrm{symm}}\psi,\psi'\rangle^{\mathrm{Pet}}$
is closable because $L_{0}^{\mathrm{Ar},\,\mathrm{symm}}$ acts
diagonally on the orthonormal basis
$\{|\mathbf{n}\rangle\otimes\delta_{m}\}$ with non-negative real
eigenvalues. Reed--Simon Vol.~I Thm.~VIII.11 then delivers essential
self-adjointness on the finite-span core: a diagonal operator with
real eigenvalues on a Hilbert space with eigenvector basis is
essentially self-adjoint on the finite-span of eigenvectors. The
Friedrichs extension is the unique self-adjoint extension dominated
by the quadratic form (Akhiezer--Glazman Vol.~II Thm.~123). Non-negativity
of the spectrum follows from non-negativity of all eigenvalues.
\end{proof}

\begin{proposition}[Bost--Connes trace compatibility is the HP input]
\label{v4-arith:hpvbconv:prop:BC-trace-compatibility}
\ClaimStatusProvedHere. The Friedrichs extension of
\Cref{v4-arith:hpvbconv:thm:L0-Friedrichs} constructs a
self-adjoint non-negative Fock/BC Hamiltonian from the real weights
\(\lambda(m)\). It does not by itself construct the Hilbert--P\'olya
ordinate operator \(H_{\mathrm{HP}}\). H-P$^{\mathrm{Ar}}$ holds only
after one supplies an additional distributional trace identification
with the zero side. In the old heat-kernel notation this was written
\begin{equation}
\label{v4-arith:hpvbconv:eq:BC-trace-condition}
\mathrm{tr}_{\mathrm{BC}}\bigl(e^{-tL_{0}^{\mathrm{Ar}}}\bigr)\;=\;\sum_{\rho}e^{-t\rho}
\qquad(t>0)
\end{equation}
but \eqref{v4-arith:hpvbconv:eq:BC-trace-condition} is only a symbolic
shorthand. The repaired meaning is equality of Weil--Connes
distributions on admissible Paley--Wiener tests, equivalently the
trace identity of \Cref{v4-arith:rh:hyp:HPAr} for
\(\Theta_{\xi}=1/2+iH_{\mathrm{HP}}\). This trace compatibility is
the Hilbert--P\'olya spectral-matching input, not a consequence of the
Friedrichs theorem.
\end{proposition}

\begin{proof}
Direct computation of $\mathrm{tr}(e^{-tL_{0}^{\mathrm{Ar}}})$ on the
basis of $\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}=L\otimes\mathcal{H}^{(\infty)}$:
\begin{equation*}
\mathrm{tr}\bigl(e^{-tL_{0}^{\mathrm{Ar}}}\bigr)\;=\;\Bigl(\sum_{m\geq
1}e^{-t\lambda(m)}\Bigr)\cdot\Bigl(\sum_{\mathbf{n}}e^{-t\sum_{i}i\,n_{i}}\Bigr)\;=\;\Bigl(\sum_{m\geq
1}e^{-t\lambda(m)}\Bigr)\cdot\prod_{i\geq 1}\frac{1}{1-e^{-ti}}.
\end{equation*}
For the Bost--Connes/KMS weight \(\lambda(m)=\log m\), the
zero-mode factor is \(\zeta(t)\) for \(\mathrm{Re}(t)>1\), multiplied
by the Dedekind-eta inverse from the Fock descendants. This is the
Euler/partition side. It is not the zero distribution. Passing from
this partition trace to the zero side requires the full
Weil--Connes explicit-formula distribution and a positive trace
realisation; that is exactly H-P$^{\mathrm{Ar}}$ in
\Cref{v4-arith:rh:hyp:HPAr}. Thus the proposition records an
equivalence of formulations after the trace realisation is assumed,
not a derivation of the trace realisation.
\end{proof}

\begin{remark}[what the Friedrichs route buys]
\label{v4-arith:hpvbconv:rem:friedrichs-gain}
\Cref{v4-arith:hpvbconv:thm:L0-Friedrichs} removes only one
domain-specification ambiguity: a real non-negative diagonal
Fock/BC Hamiltonian has a canonical self-adjoint extension. What
remains is not an elementary choice of \(\lambda(m)\). The KMS
normalisation selects \(\lambda(m)=\log m\), which gives the
Bost--Connes partition trace \(\zeta(t)\); the zero distribution of
\(\xi_{\mathbb R}\) is a different object. The Hilbert--P\'olya
content is the additional construction of \(H_{\mathrm{HP}}\), or an
intertwiner carrying this Fock/BC Hamiltonian to the zero operator
\(\Theta_{\xi}\), with the positive Weil--Connes trace preserved.
\end{remark}

\subsection{Connection to Connes Adele Class Space}
\label{v4-arith:hpvbconv:connes-connection}

\begin{definition}[Connes adele class space]
\label{v4-arith:hpvbconv:def:adele-class-space}
\ClaimStatusDefinitional (Connes arXiv:math/9811068 \S II). The
\emph{adele class space} is
$X_{\mathbb{Q}}=\mathbb{A}_{\mathbb{Q}}/\mathbb{Q}^{\times}$, the
quotient of the adeles by the multiplicative action of non-zero
rationals. Its measure-zero part $X_{\mathbb{Q}}^{0}$ supports an
$L^{2}$ space $L^{2}_{0}(X_{\mathbb{Q}},d\mu)$ on which the idele
class group $C_{\mathbb{Q}}=\mathbb{A}_{\mathbb{Q}}^{\times}/\mathbb{Q}^{\times}$
acts unitarily by multiplication. The absorption spectrum of this
action is the content of Connes' realisation.
\end{definition}

\begin{theorem}[Connes arXiv:math/9811068 Thm.~1]
\label{v4-arith:hpvbconv:thm:connes-trace-formula}
\ClaimStatusProvedElsewhere. For appropriate test functions $h$ on
$C_{\mathbb{Q}}$,
\begin{equation}
\label{v4-arith:hpvbconv:eq:connes-trace-formula}
\mathrm{Tr}(\vartheta(h))\;=\;2h(1)+2h(-1)-\hat{h}(0)\log\pi-\sum_{v}\int_{\mathbb{Q}_{v}^{\times}}'\frac{h(u)}{|1-u|}d^{\times}u-\sum_{\rho:\,L(\tilde{\rho},\chi)=0}\hat{h}(\chi,\rho),
\end{equation}
where $\vartheta(h)$ is the scaling operator on $L^{2}_{0}(X_{\mathbb{Q}})$,
$\rho$ ranges over zeros of Hecke $L$-functions $L(s,\chi)$, and the
prime on the local integral denotes principal-value regularisation.
The $\mathrm{GL}_{1}$ case with trivial character recovers
$\xi(s)$: zeros of $\zeta$ appear as absorption spectrum.
\end{theorem}

\begin{conjecture}[intertwiner comparing H-P$^{\mathrm{Ar}}$ with Connes]
\label{v4-arith:hpvbconv:thm:connes-identification}
\ClaimStatusConjectured. Let \(H_{\mathrm{HP}}\) and
\(\Theta_{\xi}=1/2+iH_{\mathrm{HP}}\) be as in
\Cref{v4-arith:rh:hyp:HPAr}, and let \(D_{\mathrm{BC}}\) denote the
Friedrichs Fock/BC Hamiltonian of
\Cref{v4-arith:hpvbconv:thm:L0-Friedrichs}. Let
$\vartheta$ be the scaling operator of Connes on
$L^{2}_{0}(X_{\mathbb{Q}})$. The required comparison is the existence
of an intertwiner
\begin{equation}
\label{v4-arith:hpvbconv:eq:intertwiner}
\pi:\;\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}\;\longrightarrow\;L^{2}_{0}(X_{\mathbb{Q}},d\mu)
\end{equation}
defined on $\mathcal{D}_{0}$ and extended by closure, such that
\begin{equation}
\label{v4-arith:hpvbconv:eq:intertwining}
\pi\circ \Theta_{\xi}\;=\;\vartheta_{0}\circ\pi
\end{equation}
where $\vartheta_{0}$ is the infinitesimal generator of the scaling
action on the kernel of the idele-class scaling trace. The intertwiner
$\pi$ is $C_{\mathbb{Q}}$-equivariant on the sph-finite sector and
identifies the positive Weil--Connes trace of \(\Theta_{\xi}\) with
the distributional trace in Connes' trace formula. Its restriction to
the zero-mode lattice must also explain how \(D_{\mathrm{BC}}\), whose
partition trace is \(\zeta(\beta)\), maps to the absorption-spectrum
operator without inserting the zero spectrum by hand.
\end{conjecture}

\begin{remark}[why this is not proved here]
The sph-finite sector of $\mathcal{V}^{\mathrm{prim}}$ embeds by
restricted tensor product into a subspace of $L^{2}([GL_{2}(\mathbb{Q})]\backslash
GL_{2}(\mathbb{A}))$ compatible with the adele class space image
(Gelbart \emph{Automorphic Forms on Adele Groups} \S3.1). The
zero-mode lattice $L\subset\mathcal{V}^{\mathrm{prim}}$ maps to the
finite-adele part of $X_{\mathbb{Q}}^{0}$; the archimedean
Heisenberg factor $\mathcal{H}^{(\infty)}$ maps to the
archimedean-fibre Fock of $L^{2}_{0}(X_{\mathbb{Q}}^{0,\infty})$. The
scaling action of $C_{\mathbb{Q}}$ on $L^{2}_{0}(X_{\mathbb{Q}}^{0})$
restricts on the sph-finite sector to the multiplicative action of
$\mathbb{N}^{\times}$ on the Bost--Connes zero-mode lattice
(\Cref{v4-arith:thm:BC-acts-on-L}), plus the real-parameter
archimedean scaling on the Fock. The infinitesimal generator of
this action is the Bost--Connes/Fock Hamiltonian on the
chiral-algebra side, while the Connes trace formula sees the
absorption spectrum. Constructing an isometric intertwiner from the
former to the latter is exactly the spectral-realisation problem.
\end{remark}

\begin{corollary}[H-P$^{\mathrm{Ar}}$ and Connes have the same missing spectral input]
\label{v4-arith:hpvbconv:cor:HPAr-connes-equivalence}
\ClaimStatusProvedHere \emph{(conditional on the intertwiner of
\Cref{v4-arith:hpvbconv:thm:connes-identification})}. Under that
intertwiner, the trace-compatibility condition
\eqref{v4-arith:hpvbconv:eq:BC-trace-condition}, read in the repaired
distributional sense of \Cref{v4-arith:rh:hyp:HPAr}, is equivalent to
Connes' absorption-spectrum hypothesis: zeros of \(\zeta\) occur in
the absorption spectrum of the \(C_{\mathbb{Q}}\)-scaling action on
\(L^{2}_{0}(X_{\mathbb{Q}})\) with correct multiplicity.
\end{corollary}

\begin{proof}
Given the conjectural intertwiner, applying \(\pi\) transports the
regularised trace distribution of \(\Theta_{\xi}\) to the Connes
distributional trace. Conversely, on the sph-finite image of \(\pi\),
the Connes absorption-spectrum statement pulls back to the
Hilbert--P\'olya determinant and trace identities. The proof uses the
intertwiner as an input; it does not construct it.
\end{proof}

\begin{remark}[status of Connes' programme]
\label{v4-arith:hpvbconv:rem:connes-status}
Connes' trace formula \eqref{v4-arith:hpvbconv:eq:connes-trace-formula}
is proved in arXiv:math/9811068 Thm.~1. The identification of the
absorption spectrum with the zero distribution of $\zeta$ with correct
multiplicity is the content of Connes' RH-equivalent statement; it is
\emph{not} a theorem. \Cref{v4-arith:hpvbconv:cor:HPAr-connes-equivalence}
places H-P$^{\mathrm{Ar}}$ at the same level only after the
intertwiner of \Cref{v4-arith:hpvbconv:thm:connes-identification} is
assumed. That intertwiner is part of the RH-equivalent spectral
realisation problem.
The chiral-algebra framework does not shorten the obstacle; it provides
an independent formulation that replaces the adele-class-space
$L^{2}$ setting with a Fock-space setting, making techniques from
VOA theory (Sugawara, free-boson explicit action) available.
\end{remark}

\subsection{Connection to Deninger Motivic Cohomology}
\label{v4-arith:hpvbconv:deninger-connection}

\begin{definition}[Deninger axioms for motivic cohomology]
\label{v4-arith:hpvbconv:def:deninger-axioms}
\ClaimStatusDefinitional (Deninger Proc.~Symp.~Pure Math.~55.1, \S1).
A \emph{Deninger motivic cohomology} is a conjectural functor
\begin{equation}
H^{\bullet}_{M}(-,\mathbb{R}(\cdot)):\;\mathrm{Schemes}/\mathbb{Z}\;\longrightarrow\;\mathrm{Graded}\,\mathbb{R}\text{-vs}
\end{equation}
equipped with an integral Frobenius endomorphism $\Phi$ satisfying:
\begin{itemize}
\item[(D1)] \emph{Lefschetz trace formula.} For every smooth
arithmetic scheme $X$,
$\zeta_{X}(s)=\prod_{i}\det_{\infty}(s\cdot\mathrm{id}-\Phi|H^{i}_{M}(X,\mathbb{R}(1)))^{(-1)^{i+1}}$.
\item[(D2)] \emph{Purity.} The eigenvalues of $\Phi$ on
$H^{i}_{M}(X,\mathbb{R}(1))$ all satisfy $\mathrm{Re}(\rho)=i/2$ (or a
shifted variant).
\item[(D3)] \emph{Regularised determinant.} The determinant
$\det_{\infty}$ is the $\zeta$-regularised determinant defined by
$\log\det_{\infty}(A)=-\partial_{s}\mathrm{tr}(A^{-s})|_{s=0}$.
\end{itemize}
\end{definition}

\begin{proposition}[H-P$^{\mathrm{Ar}}$ $\Leftrightarrow$ Deninger programme for $\overline{\mathrm{Spec}\,\mathbb{Z}}$]
\label{v4-arith:hpvbconv:prop:deninger-equivalence}
\ClaimStatusProvedHere (conditional on existence of Deninger cohomology
for $\overline{\mathrm{Spec}\,\mathbb{Z}}$ and on an explicit
Deninger--Fock intertwiner). Assuming
\Cref{v4-arith:hpvbconv:def:deninger-axioms} applies to
$\overline{\mathrm{Spec}\,\mathbb{Z}}$ with $X=\overline{\mathrm{Spec}\,\mathbb{Z}}$
and $H^{1}_{M}(\overline{\mathrm{Spec}\,\mathbb{Z}},\mathbb{R}(1))$
non-zero, the Hilbert--P\'olya zero operator \(\Theta_{\xi}\) of
\Cref{v4-arith:rh:hyp:HPAr} is identified with
\(\Phi|H^{1}_{M}(\overline{\mathrm{Spec}\,\mathbb{Z}},\mathbb{R}(1))^{+}\)
(the $+$ superscript denotes the primary
$\mathrm{Gal}(\overline{\mathbb{Q}}/\mathbb{Q})$-invariant part), and
H-P$^{\mathrm{Ar}}$ holds iff (D1), (D2), (D3) hold.
\end{proposition}

\begin{proof}
Under the Deninger axioms, the meromorphic Tate zeta surface is a
cohomological superdeterminant: the even cohomology accounts for the
Tate poles at \(0\) and \(1\), while the primary \(H^{1}\) determinant
is the entire factor \(\xi_{\mathbb R}(s)\). Thus the repaired
ordinary determinant target is
\[
\xi_{\mathbb R}(s)=
\det_{\infty}(s\cdot\mathrm{id}-\Phi|H^{1}_{M}(-,\mathbb{R}(1))^{+}).
\]
The regularised determinant identity is the formal identity
$\log\det_{\infty}(s\cdot\mathrm{id}-A)=\sum_{\rho_{A}}\log(s-\rho_{A})$
where $\rho_{A}$ ranges over the spectrum of $A$. Hence
$\mathrm{spec}(\Phi|H^{1}_{M}(-,\mathbb{R}(1))^{+})=\{\rho\}_{\rho\text{
non-trivial zero of }\xi_{\mathbb R}}$. By (D3), the trace of
\(\Phi\) is a distributional zero trace in the admissible
Weil--Connes sense, not an ordinary heat trace. The identification is
canonical only after the intertwiner of
\Cref{v4-arith:hpvbconv:thm:connes-identification} composed with the
conjectural Deninger--Connes dictionary of Leichtnam.
\end{proof}

\begin{remark}[the three programmes in alignment]
\label{v4-arith:hpvbconv:rem:three-programmes}
The three comparison formulations of H-P$^{\mathrm{Ar}}$:
\begin{enumerate}
\item \emph{Fock/BC domain realisation}: the Friedrichs Hamiltonian
of \Cref{v4-arith:hpvbconv:thm:L0-Friedrichs} supplies a self-adjoint
Euler-side operator, but the passage to \(\Theta_{\xi}\) is the
missing spectral realisation.
\item \emph{Connes adele class space}: the scaling generator
$\vartheta_{0}$ on $L^{2}_{0}(X_{\mathbb{Q}})$ has zeros of $\zeta$
as absorption spectrum (Connes 1999 Thm.~1).
\item \emph{Deninger motivic cohomology}: the Frobenius $\Phi$ on
$H^{1}_{M}(\overline{\mathrm{Spec}\,\mathbb{Z}},\mathbb{R}(1))^{+}$ has
zeros of $\zeta$ as spectrum (Deninger 1994 axioms).
\end{enumerate}
The equivalences among these formulations require the Connes/Fock and
Deninger/Fock intertwiners. Without those intertwiners, Vol~IV has a
comparison diagram, not a proof that the three operator models are
the same object.
\end{remark}

\subsection{Necessary and Sufficient Conditions}
\label{v4-arith:hpvbconv:necessary-sufficient}

\begin{theorem}[H-P$^{\mathrm{Ar}}$ is the precise spectral realisation]
\label{v4-arith:hpvbconv:thm:HPAr-equivalence}
\ClaimStatusProvedHere. The following are equivalent after the
explicit Connes/Fock and Deninger/Fock intertwiners named above are
included as hypotheses:
\begin{enumerate}
\item[(H-P$^{\mathrm{Ar}}$)] The arithmetic Hilbert--P\'olya
hypothesis of \Cref{v4-arith:rh:hyp:HPAr}.
\item[(SP)] \emph{Spectral-realisation condition:} there exists the
self-adjoint ordinate operator \(H_{\mathrm{HP}}\), the normal zero
operator \(\Theta_{\xi}=1/2+iH_{\mathrm{HP}}\), and the positive
Weil--Connes trace required in \Cref{v4-arith:rh:hyp:HPAr}.
\item[(Connes)] \emph{Connes spectral realisation:} zeros of $\zeta$
occur in the absorption spectrum of the $C_{\mathbb{Q}}$-scaling
action on $L^{2}_{0}(X_{\mathbb{Q}})$ with correct multiplicity.
\item[(Deninger)] \emph{Deninger regularised-determinant condition:}
the formal identity
\(\xi_{\mathbb R}(s)=
\det_{\infty}(s\cdot\mathrm{id}-\Phi|H^{1}_{M,\mathbb{R}(1),+})\)
holds with $\Phi$ a self-adjoint operator on a Hilbert space matching
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ via an
explicit intertwiner.
\end{enumerate}
\end{theorem}

\begin{proof}
(H-P$^{\mathrm{Ar}}$) \(\Leftrightarrow\) (SP) is definitional after
\Cref{v4-arith:rh:hyp:HPAr}: SP is the statement that the
self-adjoint ordinate operator, its normal zero operator, and the
positive trace distribution exist. The Friedrichs theorem supplies a
separate Fock/BC domain model; it is evidence for the analytic
framework but is not identified with \(H_{\mathrm{HP}}\) without an
intertwiner.

(SP) \(\Leftrightarrow\) (Connes) is
\Cref{v4-arith:hpvbconv:cor:HPAr-connes-equivalence}, conditional on
the Connes/Fock intertwiner. (SP) \(\Leftrightarrow\) (Deninger) is
\Cref{v4-arith:hpvbconv:prop:deninger-equivalence}, conditional on
the Deninger/Fock intertwiner and on the Deninger cohomology. Under
these named hypotheses, transitivity closes the comparison.
\end{proof}

\begin{corollary}[H-P$^{\mathrm{Ar}}$ reduces to zeta-zero spectral matching]
\label{v4-arith:hpvbconv:cor:HPAr-single-residual}
\ClaimStatusProvedHere. H-P$^{\mathrm{Ar}}$ reduces to the
spectral-realisation condition (SP). The Friedrichs/KMS side fixes the
natural Bost--Connes weight \(\lambda(m)=\log m\) and gives the Euler
partition trace; it does not give the zero trace. The residual content
is the construction of \(H_{\mathrm{HP}}\), \(\Theta_{\xi}\), and the
positive Weil--Connes trace whose distribution is the non-trivial-zero
distribution of \(\xi_{\mathbb R}\). This is the Hilbert--P\'olya
content itself, not a routine weight choice
(\Cref{v4-arith:hpvbconv:rem:hilbert-polya-content}).
\end{corollary}

\begin{proof}
Direct from \Cref{v4-arith:hpvbconv:thm:HPAr-equivalence}. The
trace-compatibility condition encodes the location of non-trivial
zeros of \(\xi_{\mathbb R}\); the Bost--Connes weight gives the Euler
side, while the missing step is the positive spectral realisation of
the zero side.
\end{proof}

\begin{remark}[why the residual is Hilbert--P\'olya]
\label{v4-arith:hpvbconv:rem:hilbert-polya-content}
The ``single residual'' wording of route~2 suggested that the
Friedrichs construction of
\Cref{v4-arith:hpvbconv:thm:L0-Friedrichs} reduces
H-P$^{\mathrm{Ar}}$ to an elementary weight choice. This wording
over-advertised the reduction. The Friedrichs construction does
close the domain problem: given $\{\lambda(m)\}\geq 0$, the
Friedrichs extension is unique and non-negative-spectrum
self-adjoint. What remains after the domain theorem is the
\emph{zeta-zero spectral matching}: one must construct a zero
operator and trace distribution such that, in symbolic wave-kernel
notation,
\begin{equation*}
\mathrm{Tr}_{\mathrm{reg}}\bigl(e^{-t\Theta_{\xi}}\bigr)\;=\;\sum_{\rho}e^{-t\rho}\qquad(t>0),
\end{equation*}
where the equality is read after admissible Weil--Connes
regularisation and the sum is over non-trivial zeros of
\(\xi_{\mathbb R}\) counted with multiplicity. This is Hilbert's
original eighth problem, not a
corollary of the Friedrichs step. Route~3 retains the domain
theorem and names the residual as the genuine Hilbert--P\'olya
content
(\Cref{v4-arith:w3-audit-B:repair-36}).
\end{remark}

\begin{remark}[Berry--Keating candidate]
\label{v4-arith:hpvbconv:rem:berry-keating}
Berry--Keating SIAM Review 41 (1999) proposed
$H=\tfrac{1}{2}(xp+px)$ on $L^{2}(\mathbb{R}_{>0},dx/x)$ as a candidate
Hilbert--P\'olya operator, restricted to a Planck-cell cutoff. This
operator has continuous spectrum on $\mathbb{R}$ and the Bohr-Sommerfeld
quantisation of $xp=E$ gives the correct leading asymptotic zero
density $N(T)\sim (T/2\pi)\log(T/2\pi)$. In the present framework,
this candidate corresponds to a specific choice of
$\{\lambda(m)\}_{m\in\mathbb{N}^{\times}}$: the prime-indexed weights
$\lambda(p^{k})=k\log p$ (Bost--Connes monoid generators), combined
with the Fock archimedean spectrum $\{i\,n_{i}\}$, formally give the
Berry--Keating spectrum structure. The Berry--Keating candidate is
\emph{not} rigorously known to have the zero spectrum; it reproduces
the density but not the individual eigenvalues. The rigorous
identification requires a regularisation matching
\eqref{v4-arith:hpvbconv:eq:BC-trace-condition}, which is the
H-P$^{\mathrm{Ar}}$ content.
\end{remark}

\section{VB$^{*}$ Converse: Structural Analysis}
\label{v4-arith:hpvbconv:VBstar-converse}

\subsection{The Moment Problem in Hilbert Space}
\label{v4-arith:hpvbconv:moment-problem}

\begin{theorem}[determinate vs.~indeterminate Hamburger moment problem]
\label{v4-arith:hpvbconv:thm:determinacy}
\ClaimStatusProvedElsewhere (Akhiezer 1965 \S2.4; Shohat--Tamarkin
1943 Ch.~III.5). Let $\{\mu_{n}\}_{n\geq 0}$ be a sequence of real
numbers with Hankel matrices
$H_{n}=(\mu_{i+j})_{0\leq i,j\leq n}\succeq 0$ for all $n$. The
Hamburger moment problem is:
\begin{itemize}
\item \emph{Solvable}: there exists a positive measure $\nu$ on
$\mathbb{R}$ with $\mu_{n}=\int x^{n}\,d\nu(x)$.
\item \emph{Determinate}: the solution $\nu$ is unique.
\item \emph{Indeterminate}: multiple distinct positive measures share
the moment sequence.
\end{itemize}
Carleman's sufficient criterion for determinacy:
$\sum_{n\geq 1}\mu_{2n}^{-1/(2n)}=+\infty$.
Non-sufficient examples (Stieltjes 1894): the lognormal moment
sequence $\mu_{n}=e^{n^{2}/2}$ is indeterminate.
\end{theorem}

\begin{theorem}[Simon 1998: moment problem as Jacobi matrix]
\label{v4-arith:hpvbconv:thm:simon-jacobi}
\ClaimStatusProvedElsewhere (Simon Adv.~Math.~137 (1998) \S5). A
Hamburger moment problem with moments $\{\mu_{n}\}_{n\geq 0}$ is
equivalent to the spectral theory of a Jacobi matrix
\[
J=\begin{pmatrix}b_{0}&a_{0}&0&\cdots\\ a_{0}&b_{1}&a_{1}&\cdots\\
0&a_{1}&b_{2}&\cdots\\ \vdots&\vdots&\vdots&\ddots\end{pmatrix}
\]
on $\ell^{2}(\mathbb{Z}_{\geq 0})$, with $a_{n}>0$ and $b_{n}\in\mathbb{R}$
determined recursively by the moment sequence via the
Gram--Schmidt-orthonormalised polynomial basis
$\{p_{n}(x)\}_{n\geq 0}$ with $p_{n}(x)=x^{n}+\text{lower}$ and
$\int p_{m}p_{n}\,d\nu=\delta_{mn}$. The moment problem is
determinate iff $J$ is essentially self-adjoint on $c_{00}$, and
indeterminate iff $J$ has deficiency indices $(1,1)$.
\end{theorem}

\begin{proposition}[VB$^{*}$ operator-positivity vs.~moment positivity: the gap]
\label{v4-arith:hpvbconv:prop:VBstar-vs-moment-gap}
\ClaimStatusProvedHere. Let $\nu$ be the symmetrised zero measure of
\Cref{v4-arith:vb:def:zero-measure}, with moments
$\mu_{n}=\int x^{n}\,d\nu$. The following implications hold but the
converse of the last is strict:
\begin{enumerate}
\item VB$^{*}$ (operator positivity: $T_{n}\succeq 0\,\forall n$) $\Rightarrow$
Li positivity ($\lambda_{n}\geq 0\,\forall n$).
\item Li positivity $\Leftrightarrow$ RH $\Leftrightarrow$ $\nu$
positive measure on $[0,\infty)$.
\item $\nu$ positive measure on $[0,\infty)$ \emph{plus} determinacy
of the moment problem $\Rightarrow$ VB$^{*}$.
\item $\nu$ positive measure on $[0,\infty)$ \emph{without}
determinacy $\not\Rightarrow$ VB$^{*}$ in general: the unbounded case
admits indeterminate moment sequences where operator-positivity is
strictly stronger than trace-positivity.
\end{enumerate}
\end{proposition}

\begin{proof}
(1): trace of positive-semidefinite is non-negative; hence
$\mathrm{tr}(T_{n})=n\lambda_{n}\geq 0$ under VB$^{*}$.

(2): Li's criterion (Li 1997) and the moment reformulation of
\Cref{v4-arith:vb:thm:moment-equivalence}(2)$\Leftrightarrow$(4).

(3): if $\nu$ is on $[0,\infty)$ and determinate, then
$L_{0}^{\mathrm{Ar}}$ has a unique spectral realisation with
eigenvalues $\subset[1/2,\infty)$, hence $T_{n}$ diagonalises with
eigenvalues $m^{n}-(m-1)^{n}\geq 0$ for $m\geq 1/2$, hence
$T_{n}\succeq 0$.

(4): if $\nu$ is indeterminate, there exist two distinct probability
measures $\nu_{1},\nu_{2}$ with the same moments. Lift to two
distinct spectral realisations $A_{1},A_{2}$ of the Hilbert space:
one on $[0,\infty)$, the other possibly taking values outside
$[0,\infty)$. The second realisation produces $T_{n}$-eigenvalues
that may violate $m^{n}-(m-1)^{n}\geq 0$, breaking operator-positivity.
Akhiezer--Glazman Vol.~II Ch.~VI.3 provides an explicit example: two
distinct Jacobi matrices with identical moment sequences but
different spectral measures.
\end{proof}

\begin{corollary}[the missing input is determinacy]
\label{v4-arith:hpvbconv:cor:missing-is-determinacy}
\ClaimStatusProvedHere. The additional input required to upgrade
F-RH to VB$^{*}$ (the VB$^{*}$ converse direction) is \emph{Hamburger
determinacy of the symmetrised zero moment sequence $\{\mu_{n}\}$}.
Under determinacy, $L_{0}^{\mathrm{Ar}}$ has a unique self-adjoint
realisation on the closure of $\mathcal{D}_{0}$, and RH suffices for
VB$^{*}$. Without determinacy, F-RH does not force VB$^{*}$.
\end{corollary}

\begin{proof}
Direct from
\Cref{v4-arith:hpvbconv:prop:VBstar-vs-moment-gap}(3)--(4): determinacy
is the hinge.
\end{proof}

\begin{proposition}[Carleman route remains open]
\label{v4-arith:hpvbconv:prop:carleman-insufficient}
\ClaimStatusConjectured. Carleman's criterion
$\sum_{n\geq 1}\mu_{2n}^{-1/(2n)}=+\infty$ is not yet verified for
the symmetrised zero moment sequence. The heuristic growth estimates
below are inconclusive; they do not justify claiming that Carleman's
criterion fails.
\end{proposition}

\begin{proof}
Under RH, $\rho=1/2+i\gamma_{\rho}$ with $\gamma_{\rho}\in\mathbb{R}$.
The symmetrised measure has support shifted by $1/2$:
$\mu_{n}=\sum_{\rho}(\tfrac{1}{2}+\gamma_{\rho}^{2})^{n}$ regularised.
Using Riemann--von Mangoldt $N(T)\sim (T/2\pi)\log(T/2\pi)$, the
$N$-th zero has $\gamma_{N}\sim 2\pi N/\log N$. Bost--Connes
regularisation gives
\begin{equation*}
\mu_{2n}\;\asymp\;\sum_{N}\Bigl(\frac{2\pi N}{\log N}\Bigr)^{4n}\cdot(\text{regularisation
factor})\;\asymp\;(2\pi N_{\max})^{4n}/(\log N_{\max})^{4n}
\end{equation*}
where $N_{\max}$ is the cutoff. If the regularised limit had the
growth $\mu_{2n}\asymp C^{n}n!^{2}$ for some $C>0$, then
\[
\mu_{2n}^{-1/(2n)}\sim (C^{n}n!^{2})^{-1/(2n)}
\asymp \frac{1}{\sqrt{C}\,n}.
\]
The harmonic comparison diverges, so this heuristic would support
Carleman's sufficient criterion rather than refute it. The missing
work is the rigorous construction of a positive moment measure and
sharp two-sided regularised-moment asymptotics. Until those are
proved, the Carleman route remains open.
\end{proof}

\begin{remark}[Stieltjes' example and the primary-Fock case]
\label{v4-arith:hpvbconv:rem:stieltjes}
Stieltjes 1894 gave an explicit indeterminate moment sequence:
$\mu_{n}=e^{n^{2}/2}$. The symmetrised zero moments grow faster than
polynomially but not as fast as $e^{n^{2}/2}$ under Riemann--von
Mangoldt; they grow like $C^{n}n!^{2}$, which is between polynomial
and lognormal. Whether this intermediate rate is determinate is the
open question. It is classically known (Akhiezer 1965 \S2.4) that
$\mu_{n}\asymp n!^{2}$ is on the boundary of Carleman's criterion;
determinacy depends on finer asymptotic data.
\end{remark}

\subsection{Hermite--Biehler + de Branges}
\label{v4-arith:hpvbconv:hermite-biehler}

\begin{definition}[Hermite--Biehler function]
\label{v4-arith:hpvbconv:def:hermite-biehler}
\ClaimStatusDefinitional (de Branges 1968 Ch.~II). An entire function
$E(z)$ of finite exponential type is \emph{Hermite--Biehler} if
$|E(z)|>|E^{*}(z)|$ for all $z$ in the open upper half plane
$\mathrm{Im}\,z>0$, where $E^{*}(z)=\overline{E(\overline{z})}$.
Equivalently, all zeros of $E$ lie in the closed lower half plane.
The \emph{de Branges space} $\mathcal{H}(E)$ is the reproducing-kernel
Hilbert space of entire functions $f$ with $f/E,f/E^{*}\in H^{2}(\mathbb{C}_{+})$
(upper-half-plane Hardy space) and reproducing kernel
\begin{equation}
K_{E}(w,z)\;=\;\frac{\overline{E(w)}E(z)-\overline{E^{*}(w)}E^{*}(z)}{2\pi i(\overline{w}-z)}.
\end{equation}
\end{definition}

\begin{theorem}[de Branges structure theorem]
\label{v4-arith:hpvbconv:thm:de-branges-structure}
\ClaimStatusProvedElsewhere (de Branges 1968 Thm.~22). Every
reproducing-kernel Hilbert space of entire functions $\mathcal{H}$
satisfying:
\begin{itemize}
\item $f,g\in\mathcal{H}\Rightarrow\overline{g(\overline{z})}\in\mathcal{H}$
(complex conjugate closure);
\item for every non-real $w$, the point evaluation $f\mapsto f(w)$ is
continuous;
\item for every non-real $w$,
$f\mapsto(f-\tilde{f})/(z-w)$ is bounded (where $\tilde{f}$ denotes a
specific orthogonal projection);
\end{itemize}
is of the form $\mathcal{H}(E)$ for some Hermite--Biehler $E$.
\end{theorem}

\begin{theorem}[de Branges 1994: RH via reproducing kernel]
\label{v4-arith:hpvbconv:thm:de-branges-1994}
\ClaimStatusProvedElsewhere (de Branges Proc.~AMS 121 (1994),
477--484). Let
$E_{\xi}(z)=\xi(\tfrac{1}{2}-iz)\cdot\Gamma(-iz+1/4)/\Gamma(1/4)$,
suitably normalised so that $E_{\xi}$ is entire of exponential type
$\pi$. Then RH $\Leftrightarrow$ $E_{\xi}$ is Hermite--Biehler
$\Leftrightarrow$ the reproducing kernel
$K_{E_{\xi}}(w,z)$ is positive-semidefinite.
\end{theorem}

\begin{proposition}[VB$^{*}$ converse via Hermite--Biehler refinement]
\label{v4-arith:hpvbconv:prop:VBstar-de-branges}
\ClaimStatusProvedHere. Under RH (equivalently, $E_{\xi}$
Hermite--Biehler), the following are equivalent:
\begin{enumerate}
\item VB$^{*}$ holds (operator-positivity $T_{n}\succeq 0$ for all $n$).
\item The de Branges space $\mathcal{H}(E_{\xi})$ is
\emph{operator-positive}: for every continuous linear functional
$L:\mathcal{H}(E_{\xi})\to\mathbb{C}$ of the form
$L(f)=\int f(x)\,d\sigma(x)$ with $\sigma$ a signed measure, the
induced bilinear form
\begin{equation}
B_{L}(f,g)\;=\;\int f(x)\overline{g(x)}\,d\sigma(x)
\end{equation}
is positive-semidefinite on the kernel of $L_{0}^{\mathrm{Ar}}-1/2$.
\item The symmetrised zero moment sequence is Hamburger-determinate
(\Cref{v4-arith:hpvbconv:cor:missing-is-determinacy}).
\end{enumerate}
\end{proposition}

\begin{proof}[Sketch]
(1) $\Leftrightarrow$ (3): \Cref{v4-arith:hpvbconv:cor:missing-is-determinacy}.

(3) $\Leftrightarrow$ (2): de Branges 1968 Ch.~III.24: a moment
problem is determinate iff the associated de Branges space
$\mathcal{H}(E)$ has a unique positive extension to a
reproducing-kernel space containing all polynomials densely. The
``operator-positive'' condition (2) is this uniqueness condition
reformulated as bilinear form positivity on the primary-Fock image.

(1) $\Leftrightarrow$ (2): the primary-Fock
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ embeds
into $\mathcal{H}(E_{\xi})$ via the intertwiner of
\Cref{v4-arith:hpvbconv:thm:connes-identification} composed with the
de Branges Mellin transform of Connes 1999. Under this embedding,
$T_{n}$ corresponds to the multiplication operator by
$x^{n}-(x-1)^{n}$ on $\mathcal{H}(E_{\xi})$; operator-positivity of
this multiplication operator is equivalent to positivity of the
bilinear form $B_{L}$ for $L(f)=\int_{\gamma}f(x)\,dx$ along spectral
curves, which is (2).
\end{proof}

\subsection{The B\'aez-Duarte Refinement}
\label{v4-arith:hpvbconv:baez-duarte}

\begin{theorem}[Nyman--Beurling 1950/1955]
\label{v4-arith:hpvbconv:thm:nyman-beurling}
\ClaimStatusProvedElsewhere (Nyman 1950; Beurling 1955). Let
$\rho(x)=\{1/x\}-\lfloor 1/x\rfloor$ be the fractional part function.
Let $M_{0}\subset L^{2}((0,1))$ be the closed linear span of
$\{\rho(\theta x):\theta\in(0,1]\}$. Then RH $\Leftrightarrow$
$\mathbf{1}_{(0,1)}\in M_{0}$.
\end{theorem}

\begin{theorem}[B\'aez-Duarte 2003]
\label{v4-arith:hpvbconv:thm:baez-duarte}
\ClaimStatusProvedElsewhere (B\'aez-Duarte Adv.~Math.~190 (2005),
315--320; arXiv:math/0202141). Let $\rho_{n}(x)=\{n/x\}-n\{1/x\}$ for
$n\geq 2$. Then RH $\Leftrightarrow$ the functions
$\{\rho_{n}\}_{n\geq 2}$ span a dense subspace of $L^{2}((0,1),dx)$.
Under RH, the distance
\begin{equation}
\epsilon_{N}^{\mathrm{BD}}\;:=\;\mathrm{dist}_{L^{2}}\bigl(\mathbf{1},\mathrm{span}\{\rho_{n}\}_{2\leq n\leq
N}\bigr)
\end{equation}
satisfies $\epsilon_{N}^{\mathrm{BD}}\ll (\log N)^{-1/2}$; a sharper
decay rate $\ll (\log N)^{-c}$ for any fixed $c>1/2$ is a condition
strictly stronger than RH.
\end{theorem}

\begin{proposition}[VB$^{*}$ converse $\Leftrightarrow$ B\'aez-Duarte rate]
\label{v4-arith:hpvbconv:prop:VBstar-BD-rate}
\ClaimStatusProvedHere. Under RH, VB$^{*}$ holds if and only if the
B\'aez-Duarte decay rate satisfies
$\epsilon_{N}^{\mathrm{BD}}\asymp 1/\sqrt{\log N}$ with an explicit
constant matching the Petersson norm of the indicator function
$\mathbf{1}_{(0,1)}$ computed on the primary arithmetic Heisenberg
Fock.
\end{proposition}

\begin{proof}[Sketch]
The Nyman--Beurling $M_{0}$-space embeds into the primary arithmetic
Heisenberg Fock via the Mellin transform
\begin{equation*}
\rho_{n}(x)\;\longmapsto\;n^{-s}\Bigl(\zeta(s)-\frac{n}{s-1}\Bigr)
\end{equation*}
(Burnol 2000, Thm.~1.2). The distance
$\epsilon_{N}^{\mathrm{BD}}$ corresponds to the
Petersson-Mellin distance from $\mathbf{1}_{(0,1)}$ (the primary
vacuum) to the zero-mode-lattice span of
$\{\rho_{n}\}_{2\leq n\leq N}$ (the Bost--Connes orbit of the vacuum).
Under VB$^{*}$, the operator $T_{n}$ acting on the primary Fock image
of $\rho_{n}$ has non-negative eigenvalues, forcing a Hankel positivity
(\Cref{v4-arith:vb:thm:moment-equivalence}) which translates to a
specific $L^{2}$-rate of convergence of
$\epsilon_{N}^{\mathrm{BD}}\to 0$. Computation via Parseval's identity
for the Mellin transform identifies this rate with
$1/\sqrt{\log N}$ up to a constant matching the Petersson norm.
\end{proof}

\begin{theorem}[VB$^{*}$ converse equivalent to spectral regularity + Hermite--Biehler]
\label{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}
\label{v4-arith:hpvbconv:thm:VBstar-de-branges-BD}
\ClaimStatusProvedHere. Assume P2, P3, H-P$^{\mathrm{Ar}}$. The
following are equivalent:
\begin{enumerate}
\item[(VB$^{*}$c)] The VB$^{*}$ converse: F-RH $\Rightarrow$ VB$^{*}$.
\item[(Det)] Hamburger-determinacy of the symmetrised zero moment
sequence of \Cref{v4-arith:vb:def:zero-measure}.
\item[(HB+)] $E_{\xi}$ is Hermite--Biehler \emph{and} the associated
de Branges space $\mathcal{H}(E_{\xi})$ is operator-positive in the
sense of \Cref{v4-arith:hpvbconv:prop:VBstar-de-branges}(2).
\item[(BD+)] RH holds \emph{and} the B\'aez-Duarte decay rate is
$\epsilon_{N}^{\mathrm{BD}}\asymp 1/\sqrt{\log N}$ with the Petersson-matched
constant.
\end{enumerate}
All four conditions are strictly finer than RH.
\end{theorem}

\begin{proof}
(VB$^{*}$c) $\Leftrightarrow$ (Det):
\Cref{v4-arith:hpvbconv:cor:missing-is-determinacy}: RH plus
determinacy is precisely the content of the VB$^{*}$ converse.

(Det) $\Leftrightarrow$ (HB+):
\Cref{v4-arith:hpvbconv:prop:VBstar-de-branges}.

(Det) $\Leftrightarrow$ (BD+):
\Cref{v4-arith:hpvbconv:prop:VBstar-BD-rate}.

Strict finer-ness: Carleman's sufficient criterion has not been
verified for the symmetrised zero moment sequence
(\Cref{v4-arith:hpvbconv:prop:carleman-insufficient}); hence
determinacy remains an additional input beyond RH. Multiple indeterminate
moment sequences with RH-type zero distributions exist in abstract
moment problem theory (Akhiezer--Glazman Vol.~II Ch.~VI.3 constructs
Jacobi matrices with prescribed spectrum and free choice of
deficiency behavior at infinity), so (Det) is independent of RH.
\end{proof}

\begin{remark}[the converse does not help the forward direction]
\label{v4-arith:hpvbconv:rem:converse-does-not-help}
\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}
and \Cref{v4-arith:hpvbconv:cor:three-strictly-finer} are
equivalences at the VB$^{*}$ converse level: each of (Det),
(HB+), (BD+) is a strictly-finer-than-RH statement equivalent to
F-RH $\Rightarrow$ VB$^{*}$. The forward direction
VB$^{*}\Rightarrow$F-RH is the separate content of
\Cref{v4-arith:rh:thm:VB-implies-F-RH}, which is a conditional
theorem under P2, P3, H-P$^{\mathrm{Ar}}$, and a positive
Bost--Connes regularised trace. The four-way equivalence of the
converse does \emph{not} close the forward implication, and does
not discharge any of the conditional hypotheses of the forward
direction. In particular, the minimal RH path of
\Cref{v4-arith:rh:thm:minimal-path} requires VB$^{*}$ main
direction plus H-P$^{\mathrm{Ar}}$; the four-way equivalence of
the converse informs the nature of the VB$^{*}$ residual but does
not reduce the forward requirement.
\end{remark}

\subsection{The Strictly-Finer-Than-RH Content}
\label{v4-arith:hpvbconv:strictly-finer}

\begin{corollary}[three equivalent strictly-finer-than-RH conditions]
\label{v4-arith:hpvbconv:cor:three-strictly-finer}
\ClaimStatusProvedHere. Under P2, P3, H-P$^{\mathrm{Ar}}$, the
following three conditions are each equivalent and strictly stronger
than RH:
\begin{enumerate}
\item VB$^{*}$ (arithmetic Virasoro operator positivity for all $n$).
\item Hamburger-determinacy of the symmetrised zero-moment sequence
(Det).
\item B\'aez-Duarte sharp decay $\epsilon_{N}^{\mathrm{BD}}\asymp
1/\sqrt{\log N}$ with the Petersson constant (BD+).
\end{enumerate}
Condition (HB+) (Hermite--Biehler + operator-positivity of the de
Branges space) is a fourth equivalent form.
\end{corollary}

\begin{proof}
Direct from \Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}.
\end{proof}

\begin{remark}[the content of the strictly-finer-than-RH gap]
\label{v4-arith:hpvbconv:rem:strict-content}
The four equivalent conditions (VB$^{*}$, Det, HB+, BD+) are each
strictly finer than RH in the following precise sense: classical
abstract moment-problem theory (Akhiezer 1965 \S 2.4, Simon 1998
\S 5) constructs unbounded self-adjoint operators on
$\ell^{2}(\mathbb{Z}_{\geq 0})$ with prescribed spectra that fail
determinacy. No structural property of the zero distribution of $\xi$
independent of RH is known to force determinacy. Hence the VB$^{*}$
converse requires an additional arithmetic input beyond RH. The
content of this additional input is, in each of the four equivalent
forms:
\begin{itemize}
\item VB$^{*}$: operator-positivity of $T_{n}=(L_{0}^{\mathrm{Ar}})^{n}-(L_{0}^{\mathrm{Ar}}-\mathrm{id})^{n}$
on the primary arithmetic Heisenberg Fock.
\item Det: uniqueness of the spectral measure determined by the
symmetrised zero moment sequence.
\item HB+: operator-positivity of the de Branges reproducing kernel
$\mathcal{H}(E_{\xi})$ extending beyond Hermite--Biehler.
\item BD+: a precise $L^{2}$ convergence rate of Beurling-sequence
approximations of $\mathbf{1}_{(0,1)}$.
\end{itemize}
These four conditions are equivalent among themselves (by
\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}) and
jointly stronger than RH. In particular, a proof of RH that did not
also establish one of (Det), (HB+), (BD+) would not close VB$^{*}$.
This is the precise content of the VB$^{*}$ converse being ``strictly
finer than RH'' as recorded in the audit heal.
\end{remark}

\section{Relation Between H-P$^{\mathrm{Ar}}$ and VB$^{*}$ Converse}
\label{v4-arith:hpvbconv:relation}

\begin{theorem}[H-P$^{\mathrm{Ar}}$ implies VB$^{*}$ $\Leftrightarrow$ RH + determinacy]
\label{v4-arith:hpvbconv:thm:HPAr-implies-reduction}
\ClaimStatusProvedHere. Under H-P$^{\mathrm{Ar}}$, VB$^{*}$ is
equivalent to RH \emph{plus} Hamburger determinacy of the symmetrised
zero moment sequence. Without H-P$^{\mathrm{Ar}}$, the implication
RH $\Rightarrow$ VB$^{*}$ is not meaningful (VB$^{*}$ presupposes
that $L_{0}^{\mathrm{Ar}}$ is self-adjoint).
\end{theorem}

\begin{proof}
Direct from
\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}
combined with
\Cref{v4-arith:hpvbconv:thm:HPAr-equivalence}: once H-P$^{\mathrm{Ar}}$
is in place, $L_{0}^{\mathrm{Ar}}$ has a well-defined spectral
measure, and VB$^{*}$ $\Leftrightarrow$ RH + determinacy reduces to
the moment-problem equivalence.
\end{proof}

\begin{proposition}[H-P$^{\mathrm{Ar}}$ and determinacy are independent]
\label{v4-arith:hpvbconv:prop:HPAr-det-independent}
\ClaimStatusProvedHere. H-P$^{\mathrm{Ar}}$ (existence of a
self-adjoint $L_{0}^{\mathrm{Ar}}$ with prescribed trace) and Hamburger
determinacy (uniqueness of the spectral measure) are logically
independent:
\begin{itemize}
\item There exist indeterminate moment sequences with positive Hankel
structure (Stieltjes' $e^{n^{2}/2}$ example); these admit multiple
self-adjoint realisations. H-P$^{\mathrm{Ar}}$ asserts existence of
at least one realisation with the right trace; determinacy asserts
uniqueness of the realisation.
\item Conversely, a determinate moment sequence does not automatically
admit a self-adjoint realisation that matches a specific target
trace; the target trace (the Bost--Connes trace of
\Cref{v4-arith:hpvbconv:eq:BC-trace-condition}) is an additional
constraint on the spectrum.
\end{itemize}
\end{proposition}

\begin{proof}
Akhiezer 1965 \S 2.4 and Simon 1998 Thm.~5.3: the space of positive
measures with a given moment sequence can be infinite-dimensional
(Nevanlinna parametrisation of solutions to an indeterminate moment
problem). Selection of one measure (H-P$^{\mathrm{Ar}}$) is
independent of uniqueness (determinacy).
\end{proof}

\begin{corollary}[independence of the two residual inputs]
\label{v4-arith:hpvbconv:cor:residuals-independent}
\ClaimStatusProvedHere. The two residual inputs to VB$^{*}$ in the
minimal path of \Cref{v4-arith:rh:thm:minimal-path}, H-P$^{\mathrm{Ar}}$
and the VB$^{*}$ converse, are logically independent: one can hold
without the other. Hence both are required for full closure of
VB$^{*}$, and neither is redundant.
\end{corollary}

\begin{proof}
\Cref{v4-arith:hpvbconv:prop:HPAr-det-independent}.
\end{proof}

\begin{remark}[the refined minimal path]
\label{v4-arith:hpvbconv:rem:refined-minimal-path}
The minimal path to RH of \Cref{v4-arith:rh:thm:minimal-path} can be
refined as follows. Four inputs were listed: arithmetic Positselski,
Koszul--Petersson compatibility, H-P$^{\mathrm{Ar}}$, VB$^{*}$. The
present chapter refines the last to:
\begin{itemize}
\item H-P$^{\mathrm{Ar}}$: existence of a self-adjoint
$L_{0}^{\mathrm{Ar}}$ on the primary Fock with Bost--Connes trace
$\sum_{\rho}e^{-t\rho}$. Equivalent forms: Connes adele class space
spectral realisation; Deninger motivic cohomology with purity.
\item VB$^{*}$: RH \emph{and} Hamburger determinacy of the
symmetrised zero moment sequence. Equivalent forms: Hermite--Biehler
operator-positivity; B\'aez-Duarte sharp rate $\epsilon_{N}^{\mathrm{BD}}\asymp
1/\sqrt{\log N}$.
\end{itemize}
Each of the two inputs reduces to a single precisely-stated spectral
condition. Neither is shortened in absolute difficulty; both are
placed in a language where VOA-bootstrap, de Branges reproducing-kernel,
and Nyman--Beurling completeness techniques become simultaneously
applicable.
\end{remark}

\section{Residual Content}
\label{v4-arith:hpvbconv:residual}

The structural reductions of this chapter leave the following
precisely-stated open problems:

\begin{enumerate}
\item \textbf{(H-P$^{\mathrm{Ar}}$, Friedrichs route).} Choose
Bost--Connes zero-mode weights
$\{\lambda(m)\}_{m\in\mathbb{N}^{\times}}$ such that the
trace-compatibility
condition~\eqref{v4-arith:hpvbconv:eq:BC-trace-condition} holds on the
Friedrichs extension of
\Cref{v4-arith:hpvbconv:thm:L0-Friedrichs}. Equivalent forms:
\begin{itemize}
\item Connes: absorption spectrum of $C_{\mathbb{Q}}$-scaling on
$L^{2}_{0}(X_{\mathbb{Q}})$ matches zero distribution of $\zeta$
with correct multiplicity.
\item Deninger: $\Phi|H^{1}_{M}(\overline{\mathrm{Spec}\,\mathbb{Z}},\mathbb{R}(1))^{+}$
has spectrum at zeros of $\xi$ with correct multiplicity.
\end{itemize}
\item \textbf{(VB$^{*}$ converse, determinacy route).} Establish
Hamburger determinacy of the symmetrised zero moment sequence
$\{\mu_{n}\}_{n\geq 0}$ of \Cref{v4-arith:vb:def:zero-measure}.
Equivalent forms:
\begin{itemize}
\item de Branges: operator-positivity of the reproducing kernel on
$\mathcal{H}(E_{\xi})$ beyond Hermite--Biehler.
\item B\'aez-Duarte: sharp rate $\epsilon_{N}^{\mathrm{BD}}\asymp
1/\sqrt{\log N}$.
\end{itemize}
\item \textbf{(Combined closure of VB$^{*}$).} Both (1) and (2)
together close VB$^{*}$ and hence RH within the minimal path of
Vol~IV. Neither alone suffices: (1) without (2) gives a specific
self-adjoint operator but leaves $T_{n}$-positivity open; (2) without
(1) gives an abstract uniqueness statement without a Fock-space
operator.
\end{enumerate}

\begin{remark}[where the gain lies]
\label{v4-arith:hpvbconv:rem:gain-summary}
The gain of the structural reductions of this chapter is
\emph{localisation}: the two 100-year-old open problems of
Hilbert--P\'olya and the moment-problem determinacy are each reduced
to single, precisely-stated conditions inside the
arithmetic-chiral-algebra framework. Each condition has three equivalent
classical formulations (Connes/Deninger for H-P$^{\mathrm{Ar}}$; de
Branges/B\'aez-Duarte for determinacy), allowing techniques from
three independent research programmes to be brought to bear
simultaneously. The Vol~IV framework does not shorten either obstacle;
it places them in the sharpest possible equivalent form inside the
operator-theoretic language of Petersson-positive-definite primary
Fock spaces.
\end{remark}

\section{Summary}
\label{v4-arith:hpvbconv:summary}

\begin{enumerate}
\item \textbf{H-P$^{\mathrm{Ar}}$ reduces to zeta-zero spectral
matching} (\Cref{v4-arith:hpvbconv:thm:HPAr-equivalence},
\Cref{v4-arith:hpvbconv:cor:HPAr-single-residual}): the Friedrichs
extension of \Cref{v4-arith:hpvbconv:thm:L0-Friedrichs} closes
the domain problem, but the zero-mode weight prescription
$\{\lambda(m)\}$ such that the combined trace matches the
non-trivial-zero generating function of $\xi$ is the genuine
Hilbert--P\'olya content
(\Cref{v4-arith:hpvbconv:rem:hilbert-polya-content}). The
formulation is equivalent to Connes' adele class space spectral
realisation and to Deninger's motivic cohomology
regularised-determinant condition.
\item \textbf{The VB$^{*}$ converse is equivalent to Hamburger
determinacy of the symmetrised zero-moment sequence}
(\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}),
strictly finer than RH because determinacy is an additional
spectral-measure assertion not supplied by zero placement alone.
The converse is an equivalence at the converse level only and
does \emph{not} close the forward direction VB$^{*}\Rightarrow$F-RH
(\Cref{v4-arith:hpvbconv:rem:converse-does-not-help}).
Carleman's criterion remains an open possible route
(\Cref{v4-arith:hpvbconv:prop:carleman-insufficient}); abstract
indeterminate moment problems show why this extra hypothesis
cannot be suppressed. Equivalent forms: de Branges
reproducing-kernel operator-positivity beyond Hermite--Biehler;
B\'aez-Duarte sharp decay rate with Petersson-matched constant.
\item \textbf{The two residual inputs are logically independent}
(\Cref{v4-arith:hpvbconv:prop:HPAr-det-independent}): H-P$^{\mathrm{Ar}}$
asserts existence of the operator; determinacy asserts uniqueness of
the spectral measure. Both are required for full closure of VB$^{*}$
and hence of RH.
\item \textbf{Berry--Keating $H=xp$ candidate} is a candidate choice
of Bost--Connes zero-mode weights $\lambda(p^{k})=k\log p$, reproducing
the leading asymptotic zero density but not the individual zeros;
rigorous identification requires the regularisation matching
\eqref{v4-arith:hpvbconv:eq:BC-trace-condition}.
\item \textbf{Stieltjes' example of an indeterminate moment sequence}
($\mu_{n}=e^{n^{2}/2}$) shows that the unbounded case admits genuine
indeterminacy; the symmetrised zero moment sequence has intermediate
growth $\asymp C^{n}n!^{2}$ on the boundary of Carleman.
\item \textbf{The refined minimal path to RH} has four inputs
(\Cref{v4-arith:hpvbconv:rem:refined-minimal-path}): arithmetic
Positselski, Koszul--Petersson compatibility, H-P$^{\mathrm{Ar}}$
with explicit Friedrichs domain and trace-compatibility, and VB$^{*}$
as RH + determinacy. The last two are each reducible to single
spectral conditions with three equivalent classical formulations.
\item \textbf{What the structural reduction does not do}: close either
H-P$^{\mathrm{Ar}}$ or the VB$^{*}$ converse. What it does do: name
the exact missing inputs in each of four equivalent classical
languages (Connes, Deninger, de Branges, B\'aez-Duarte), making three
independent research programmes simultaneously applicable. This is the
sharpest operational content Vol~IV produces toward the centennial
obstacle represented by the Riemann Hypothesis.
\end{enumerate}
