\chapter{Wave-3 Audit Ledger: Spine A Corrections}
\label{v4-arith:w3-audit-A}

\emph{Wave-3 of the adversarial protocol audits Spine-A chapters of
the arithmetic branch for residual overclaims inherited from waves 1
and 2. The audit uses as its authoritative reference the corrected
post-wave-2 residual catalog
(\Cref{v4-arith:app:C:residual-table-w2}), the Platonic variation
capstone (\Cref{v4-arith:platonic-rh-completion}), and the corrected
F-RH reformulation (\Cref{v4-arith:rh-reformulation}). The principal
overclaim pattern is that several structural reductions, while
logically correct as equivalences, described their component
sub-obligations as ``theorems'' when they are in fact conditional on
still-open inputs (notably the Fargues--Scholze-to-Emerton--Gee
categorical equivalence, the arithmetic Arinkin--Gaitsgory
conjecture, and the formal-Noetherian extension of
Gaitsgory--Rozenblyum). This chapter catalogues the overclaims and
records the in-place repairs.}

\section{Overclaim Catalog}
\label{v4-arith:w3-audit-A:catalog}

The enumerated overclaims, with file:line references, original text,
corrected text, and authority for the correction. ``Authority'' points
to the corrected statement in the post-wave-2 catalog or the
Platonic variation capstone.

\subsection{Ch.~\texorpdfstring{\ref{v4-arith:closure}}{22}: Closure of F1--F3}
\label{v4-arith:w3-audit-A:ch22}

\paragraph{Overclaim 22-01: F1.a attributed to Fargues--Scholze.}
Prior drafts of this branch (before the wave-2 platonic repair)
described F1.a (the local categorical equivalence
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{p})])\simeq
\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}})$)
as ``a theorem of Fargues--Scholze''. The current version of
Ch.~\ref{v4-arith:closure} \S\ref{v4-arith:cl:F1-closure} (F1.a
status: ``Theorem-waiting'') correctly reflects that Fargues--Scholze
arXiv:2102.13459 supplies only the local geometrisation, spectral
action, and Langlands-parameter package, not the displayed
categorical equivalence. Dotto--Emerton--Gee arXiv:2603.26887 gives
a fully-faithful-only, fixed-central-character functor for
$GL_{2}(\mathbb{Q}_{p})$ at $p\geq 5$. \textbf{Authority.} Corrected
residual catalog (\Cref{v4-arith:app:C:residual-table-w2}, row
``F3.BZN$^{\mathrm{Ar}}$ R1.fin-type'' and adjacent rows) and the
explicit ``Theorem-waiting'' tag in
\Cref{v4-arith:thm:F1-reduction}.
\textbf{Repair status:} in place at installation of wave-3.

\paragraph{Overclaim 22-02: Emerton--Gee arXiv ID.}
Earlier drafts cited Emerton--Gee by the Breuil--M\'ezard identifier.
The correct
preprint identifier is arXiv:1908.07185 (\emph{Moduli stacks of
\'etale $(\varphi,\Gamma)$-modules and the existence of crystalline
lifts}, Ann.~Math.~Studies). \textbf{Authority:} App.~A
\S\ref{v4-arith:app:A:langlands}. \textbf{Repair status:} in place
throughout the branch (verified by grep at wave-3 audit time).

\paragraph{Overclaim 22-03: BZCHN arXiv ID.}
Earlier drafts cited Ben-Zvi--Chen--Helm--Nadler by an unrelated
identifier.
The correct identifier is arXiv:2010.02321 (\emph{Coherent Springer
theory and the categorical Deligne--Langlands correspondence},
Invent.~Math.~235 (2024)). \textbf{Authority:} App.~A
\S\ref{v4-arith:app:A:BZN-coherent-Springer}. \textbf{Repair
status:} in place throughout the branch (verified by grep at wave-3
audit time).

\subsection{Ch.~\texorpdfstring{\ref{v4-arith:adelic-descent}}{27}: Adelic Categorical Descent}
\label{v4-arith:w3-audit-A:ch27}

\paragraph{Overclaim 27-01: Function-field transport status.}
The function-field transport theorem
(\Cref{v4-arith:acd:thm:function-field-transport}) was previously
inscribed as closing $(L_{1})$ and $(L_{2})$ unconditionally. The
current inscription, \ClaimStatusNeedsVerification, correctly
records that $(L_{1})$ closes via Raskin's $\infty$-categorical
construction independently of function-field Langlands, but
$(L_{2})$ closure requires the local categorical comparison (F1.a,
Theorem-waiting via DEG) and Bernstein-centre diamond gluing.
\textbf{Repair status:} in place.

\paragraph{Overclaim 27-02: $(L_{2})$ reduction claimed as theorem.}
\Cref{v4-arith:acd:thm:L2-reduction} previously stated that
Fargues--Scholze supplies the comparison functors $\Phi^{\mathrm{loc}}_{v}$
identifying $\mathcal{C}_{v}$ with
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},v}_{GL_{2}})$.
The current text is correctly weakened to
\ClaimStatusNeedsVerification with wording ``the local categorical
comparison is residual'' and ``Fargues--Scholze supplies the local
geometrisation and spectral action, not the displayed categorical
equivalence''. \textbf{Repair status:} in place.

\paragraph{Overclaim 27-03: F1 single-lemma conclusion.}
\Cref{v4-arith:acd:thm:F1-closure} claims ``F1 reduces to F1.a plus
(BC-diamond-glue)'' at \ClaimStatusNeedsVerification; the proof body
correctly notes that F1.a is itself Theorem-waiting, so the
reduction chain leaves F1 conditional on two open inputs (F1.a
\emph{and} (BC-diamond-glue)). \textbf{Repair status:} in place; no
action needed.

\subsection{Ch.~\texorpdfstring{\ref{v4-arith:arith-bzn}}{28}: Arithmetic Ben-Zvi--Nadler}
\label{v4-arith:w3-audit-A:ch28}

\paragraph{Overclaim 28-01: F3.BZN$^{\mathrm{Ar}}$ closure over inertia-only target.}
The wave-1 inscription of F3.BZN$^{\mathrm{Ar}}$
(\Cref{v4-arith:bzn:thm:main}) used the procyclic shadow
$\mathrm{Map}(B\widehat{\mathbb{Z}},\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})$
as the comparison target. This shadow forgets Frobenius and
unramified data; the correct target is the full
Weil/$(\varphi,\Gamma)$ parameter stack
$\mathrm{LocSys}^{W,\varphi\Gamma}_{GL_{2}}$. The current inscription
is correctly downgraded to \ClaimStatusConjectured with explicit
statement ``theorem-waiting beyond F1 and F2'', and
\Cref{v4-arith:bzn:prop:EG-to-LocSys} and
\Cref{v4-arith:bzn:prop:EG-image-flat}
are flagged as \ClaimStatusNeedsVerification and
\ClaimStatusConjectured respectively, with the closed-immersion
property noted as unavailable on the inertia-only shadow.
\textbf{Repair status:} in place.

\subsection{Ch.~\texorpdfstring{\ref{v4-arith:swarm}}{30}: Adversarial Swarm Ledger}
\label{v4-arith:w3-audit-A:ch30}

\paragraph{Overclaim 30-01: $\mathrm{L}_{\mathrm{ACD}}$ split as theorem.}
\Cref{v4-arith:sw:thm:LACD-split} writes ``
\ClaimStatusProvedHere. $\mathrm{L}_{\mathrm{ACD}}$ is equivalent to
the conjunction of ($\mathrm{L}_{\mathrm{ACD}}.1$)\dots($\mathrm{L}_{\mathrm{ACD}}.4$)''.
This is a valid logical equivalence at ProvedHere (the equivalence
itself is a tautological unfolding of $\mathrm{L}_{\mathrm{ACD}}$
against its four separate structural content items). The
sub-obligations $\mathrm{L}_{\mathrm{ACD}}.1$--$.3$ carry
\textbf{Conjectural} sub-statuses; $.4$ is theorem (Kneser 1966).
\textbf{Repair status:} no repair needed; the equivalence statement
is correct. The residual content is honestly recorded in the
sub-obligation statuses.

\paragraph{Overclaim 30-02: F3.BZN$^{\mathrm{Ar}}$ split as theorem.}
\Cref{v4-arith:sw:thm:BZN-Ar-split} similarly writes
``\ClaimStatusProvedHere. F3.BZN$^{\mathrm{Ar}}$, routed through
Gaitsgory--Rozenblyum DAG Vol.~II \dots\ is equivalent to the
conjunction of R1 + R2 + R3.'' Same structural pattern: the
equivalence is valid; R1 carries status ``Theorem for smooth
finite-type; conjectural for Emerton--Gee'' (hence R1.fin-type
theorem, R1.formal conjectural after wave-2 split); R2 is
\emph{Plausibly Theorem}; R3 is definitional.
\textbf{Repair status:} the equivalence statement is correct; the
R1 split is enriched in Ch.~\ref{v4-arith:bzn-sub} and the honest
residual content is in \Cref{v4-arith:bzn-sub:cor:F3-BZN-closure-path}.

\paragraph{Overclaim 30-03: P1 closure in wave-1/2 summary.}
The wave-1 status table asserted ``P1 forward $\Rightarrow$; full
cond.~arith.~Pos.'' with wave-2 claiming ``Full equiv.~\emph{unconditional}
for arith.~Heisenberg'' via the abelian-scope arithmetic Positselski.
The current reading (consistent with the Ch.~\ref{v4-arith:rh-reformulation}
minimal RH path) treats arith.~Positselski C1--C5 as five
sub-obligations that are \emph{not} all closed unconditionally
(C1--C4 are conditional on explicit hypotheses; C5 functoriality is
the named residual). \textbf{Repair status:} no structural repair;
the wave-2 summary's ``unconditional'' wording is scoped by the
C5 footnote inside the same chapter.

\subsection{Ch.~\texorpdfstring{\ref{v4-arith:lacd-sub}}{31}: $\mathrm{L}_{\mathrm{ACD}}$ Sub-Obligations}
\label{v4-arith:w3-audit-A:ch31}

\paragraph{Overclaim 31-01: $\mathrm{L}_{\mathrm{ACD}}.0$ status.}
\Cref{v4-arith:lacd:thm:L0-closed} states ``$\mathrm{L}_{\mathrm{ACD}}.0$
closed'' at \ClaimStatusProvedHere, recording construction of the
archimedean local category $\mathcal{C}_{\infty}$, distinguished
unit, and Langlands--Vogan classification. These four construction
items are indeed theorems (Harish-Chandra 1966, Vogan 1981, Wallach
1988). Hence the archimedean stratum construction closes
unconditionally. \textbf{Repair status:} no action; the closure is
of a construction, not of the global $\mathrm{L}_{\mathrm{ACD}}$.

\paragraph{Overclaim 31-02: $\mathrm{L}_{\mathrm{ACD}}.1$ status.}
\Cref{v4-arith:lacd:thm:L1-closed} states ``$\mathrm{L}_{\mathrm{ACD}}.1$
closed given F2.c'' at \ClaimStatusProvedHere. The proof relies on
F2.c tightened (\Cref{v4-arith:tate:thm:F2c-main}), which the
wave-2 audit records as \textbf{Theorem-waiting}
(\Cref{v4-arith:lacd:tbl:status} row ``F2.c tightened''). Hence
\Cref{v4-arith:lacd:thm:L1-closed} is a conditional theorem on F2.c.
This is honestly stated in the theorem's hypothesis clause
``assume F2.c tightened'', but the \ClaimStatusProvedHere tag may
read as unconditional. \textbf{Repair:} update the claim-status tag
to \ClaimStatusProvedHere\,\emph{(conditional on F2.c tightened)}
at \Cref{v4-arith:lacd:thm:L1-closed}, matching the wording style
used for P3 in \Cref{v4-arith:thm:P3-resolution}.

\paragraph{Overclaim 31-03: $\mathrm{L}_{\mathrm{ACD}}.2$ status.}
\Cref{v4-arith:lacd:thm:L2-closed} proves formal tensor-factor
commutativity of Hecke operators at ProvedHere. The theorem's scope
remark, \Cref{v4-arith:lacd:rem:L2-formal-scope}, correctly notes
that this is commutativity of local endofunctors once the restricted
tensor product is constructed, and does \emph{not} prove global
Hecke functoriality. Hence the ``$\mathrm{L}_{\mathrm{ACD}}.2$''
label on this theorem is narrower than the full sub-obligation
content used in the wave-1 reduction. \textbf{Repair:} no action
needed; the scope remark is already in place.

\paragraph{Overclaim 31-04: $\mathrm{L}_{\mathrm{ACD}}$ reduces to (BC-diamond-glue) alone.}
\Cref{v4-arith:lacd:cor:LACD-residual} states that
$\mathrm{L}_{\mathrm{ACD}}$ is equivalent to (BC-diamond-glue)
alone, under F2.c tightened. In fact the reduction is against
(BCglue.local) $\wedge$ (BCglue.glue) $\wedge$ (BC-diamond-glue.core)
(per \Cref{v4-arith:bcglue-k5:thm:decomposition}), each with
distinct status; and it is additionally conditional on F1.a (the
local categorical comparison), which is Theorem-waiting via DEG.
\textbf{Repair:} add explicit note to
\Cref{v4-arith:lacd:cor:LACD-residual} that the residual
(BC-diamond-glue) further decomposes per
\Cref{v4-arith:bcglue-k5:thm:decomposition}, and that closure of
$\mathrm{L}_{\mathrm{ACD}}$ requires F1.a (Theorem-waiting via DEG).

\subsection{Ch.~\texorpdfstring{\ref{v4-arith:bzn-sub}}{32}: BZN Formal Noetherian and EG Derived}
\label{v4-arith:w3-audit-A:ch32}

\paragraph{Overclaim 32-01: R2 ``closed as theorem''.}
\Cref{v4-arith:bzn-sub:thm:R2-main} states at \ClaimStatusProvedHere
that the Emerton--Gee stack is a \emph{derived} formal algebraic
stack in the Gaitsgory--Rozenblyum DAG sense. The proof correctly
assembles local derived enhancement (Mazur--Kisin--Lurie DAG~X) +
finite-product cotangent complex + ind-colimit cotangent complex +
quasi-smoothness. The construction is standard in Lurie DAG but not
written in Emerton--Gee. \textbf{Repair:} retain \ClaimStatusProvedHere
with an emphasised note that the derived enhancement packaging of
Emerton--Gee is translation, not primary reconstruction; the
\emph{external finite-type input} (R1.fin-type from GR) used
downstream is a theorem only for smooth finite-type stacks, and its
arithmetic application (to formal Noetherian
$\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}$)
is conditional on R1.formal. This is already handled via the
R1.fin-type vs.~R1.formal split in
\Cref{v4-arith:bzn-sub:thm:R1-formal-reduction}. \textbf{Status:}
no further repair needed.

\paragraph{Overclaim 32-02: R1.fin-type application.}
Inside \Cref{v4-arith:bzn-sub:thm:R1-formal-reduction} and the
wave-1 chapter~\ref{v4-arith:arith-bzn} the GR theorem for smooth
finite-type stacks is used as an input to the global equivalence.
The theorem applies only to smooth finite-type stacks; the global
Emerton--Gee stack is formal Noetherian. The wave-2 wording ``R1
further splits into R1.fin-type $+$ R1.formal'' makes this precise;
the arithmetic application of R1.fin-type to the Emerton--Gee
setting is through R1.formal, which is \textbf{Conjectural}.
\textbf{Repair:} no in-place repair needed; ensure
Ch.~\ref{v4-arith:bzn-sub} summary clearly records that downstream
closure of F3.BZN$^{\mathrm{Ar}}$ is conditional.

\subsection{Ch.~\texorpdfstring{\ref{v4-arith:bzn-rcompletion}}{33}: BZN Loop Convention and Wild Primes}
\label{v4-arith:w3-audit-A:ch33}

\paragraph{Overclaim 33-01: R3 ``unconditional'' convention equivalence.}
\Cref{v4-arith:bzn-rcompletion:thm:R3-three-agree} proves that the
three candidate definitions (a), (b), (c) of
$L^{\mathrm{Ar}}\mathcal{X}$ agree on a formal Noetherian derived
algebraic stack with finite Tor-amplitude and $t$-bounded Postnikov
tower. The ProvedHere status is correct as a conditional-on-hypotheses
theorem (the hypotheses are precisely named in the statement).
\textbf{Repair:} no repair needed; the hypotheses are explicit.

\paragraph{Overclaim 33-02: R4 correction ``vanishes at $p\geq 5$''.}
\Cref{v4-arith:bzn-rcompletion:thm:R4-correction-vanishes-p-large}
cites Bezrukavnikov semisimplicity. The current
\ClaimStatusNeedsVerification tag on
\Cref{v4-arith:bzn-rcompletion:thm:bez-ss-large-p} correctly
records that the Bezrukavnikov $p\geq 5$ semisimplicity theorem is
imported from arXiv:1209.0403; the corollary downstream is
conservative. \textbf{Repair:} no repair needed.

\subsection{Ch.~\texorpdfstring{\ref{v4-arith:bcglue-k5}}{35}: BC-Diamond-Glue Decomposition and K5}
\label{v4-arith:w3-audit-A:ch35}

\paragraph{Overclaim 35-01: (BC-diamond-glue) decomposes into two closed theorems + one residual.}
\Cref{v4-arith:bcglue-k5:thm:decomposition} states
(BC-diamond-glue) $\Leftrightarrow$ (BCglue.local) $\wedge$ (BCglue.glue)
$\wedge$ (BC-diamond-glue.core) at ProvedHere. The equivalence
itself is a valid logical factorisation. The downstream theorems
\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG} and
\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing} are correctly
flagged at \ClaimStatusNeedsVerification and
\ClaimStatusConjectured respectively: (BCglue.local) requires a
not-yet-written primary-source transition theorem unifying BZCHN
$\ell\neq p$, Zhu/Emerton--Gee $\ell = p$, and Fargues--Scholze
$\ell$-independence; (BCglue.glue) requires prismatic
faithfully-flat descent in the form of
\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}, itself
\ClaimStatusConjectured. \textbf{Repair:} ensure that the chapter
summary (\Cref{v4-arith:bcglue-k5:rem:residual-summary}) does not
overstate (BCglue.local) or (BCglue.glue) as closed theorems; the
current wording describes them as ``theorems'' but their proof
theorems carry NeedsVerification / Conjectured tags. Update the
summary wording to ``theorem-waiting'' and ``conjectural'' to match
the actual proof tags.

\paragraph{Overclaim 35-02: $\mathrm{L}_{\mathrm{ACD}}$ reduced to (BC-diamond-glue.core) alone.}
\Cref{v4-arith:bcglue-k5:cor:LACD-tight-catalog} asserts that after
wave-2, $\mathrm{L}_{\mathrm{ACD}}$ reduces to (BC-diamond-glue.core)
conditional on arithmetic AG, with scope 10--15 pp. This is conditional
on: (i) (BCglue.local) being a theorem (it is NeedsVerification);
(ii) (BCglue.glue) being a theorem (it is Conjectural); (iii)
F2.c tightened, F1.a, and the $\mathrm{L}_{\mathrm{ACD}}.k$
sub-obligations upstream. \textbf{Repair:} downgrade the corollary's
status from \ClaimStatusNeedsVerification to
\ClaimStatusConjectured, noting it is conditional on (BCglue.local)
and (BCglue.glue) being elevated from their current status.

\subsection{Appendix A: Primary Source Catalog}
\label{v4-arith:w3-audit-A:appA}

\paragraph{Overclaim A-01: arXiv IDs.}
Verified by grep at wave-3 audit time: Emerton--Gee is
arXiv:1908.07185 (correct); BZCHN is arXiv:2010.02321 (correct);
Fargues--Scholze is arXiv:2102.13459 (correct). No incorrect IDs
remain in the catalog. Dotto--Emerton--Gee arXiv:2603.26887 is
cited in Ch.~\ref{v4-arith:closure} \S\ref{v4-arith:cl:F1-closure}
F1.a status line and in Ch.~\ref{v4-arith:open-frontiers}
\S\ref{v4-arith:of:F1}; this citation could optionally be
absorbed into App.~A for completeness. \textbf{Repair:} add the
Dotto--Emerton--Gee entry to App.~A
\S\ref{v4-arith:app:A:langlands} for consolidated bookkeeping.

\section{Repair Summary}
\label{v4-arith:w3-audit-A:summary}

\paragraph{Ch.~\texorpdfstring{\ref{v4-arith:closure}}{22} (Closure of F1--F3 and Pillars).}
No edits required in wave 3. The post-wave-2 content of this
chapter already reflects the corrected F1.a status ``Theorem-waiting
via Dotto--Emerton--Gee arXiv:2603.26887'', and the F1.c status
``Theorem (Emerton--Gee arXiv:1908.07185)''. Arithmetic ID audit
passes (no remaining deprecated EG/BZCHN identifiers).

\paragraph{Ch.~\texorpdfstring{\ref{v4-arith:adelic-descent}}{27} (Adelic Categorical Descent).}
No edits required in wave 3. The function-field transport claim
\Cref{v4-arith:acd:thm:function-field-transport},
the $(L_{2})$ reduction
\Cref{v4-arith:acd:thm:L2-reduction}, and the F1 closure chain
\Cref{v4-arith:acd:thm:F1-closure} carry NeedsVerification tags
that correctly record the conditional nature on F1.a and
(BC-diamond-glue). The source-disjointness remark is intact.

\paragraph{Ch.~\texorpdfstring{\ref{v4-arith:arith-bzn}}{28} (Arithmetic Ben-Zvi--Nadler).}
No edits required in wave 3. The main theorem
\Cref{v4-arith:bzn:thm:main} is already \ClaimStatusConjectured with
explicit statement of four residuals (F1, F2, formal-loop continuity,
full Weil/$(\varphi,\Gamma)$ target). The Emerton--Gee morphism
\Cref{v4-arith:bzn:prop:EG-to-LocSys} is
\ClaimStatusNeedsVerification; the image property
\Cref{v4-arith:bzn:prop:EG-image-flat} is
\ClaimStatusConjectured. The procyclic-shadow limitation is
inscribed explicitly.

\paragraph{Ch.~\texorpdfstring{\ref{v4-arith:swarm}}{30} (Adversarial Swarm Ledger).}
No edits required in wave 3. The wave-1/wave-2 structural splits
\Cref{v4-arith:sw:thm:LACD-split} and
\Cref{v4-arith:sw:thm:BZN-Ar-split} are
valid logical equivalences at ProvedHere; their sub-obligation
statuses correctly record ``Conjectural'' (and Kneser-theorem for
$\mathrm{L}_{\mathrm{ACD}}.4$). Wave-2's summary of P1 closure
``unconditional for arith.~Heisenberg'' is scoped by the
C5 functoriality residual inscribed within the same chapter.

\paragraph{Ch.~\texorpdfstring{\ref{v4-arith:lacd-sub}}{31} ($\mathrm{L}_{\mathrm{ACD}}$ Sub-Obligations).}
One edit: update \Cref{v4-arith:lacd:thm:L1-closed} claim-status
from ``\ClaimStatusProvedHere'' to
``\ClaimStatusProvedHere\,\emph{(conditional on F2.c tightened)}''
to match the hypothesis clause. Also update
\Cref{v4-arith:lacd:cor:LACD-residual} to note the additional
conditionality on F1.a and on (BCglue.local)+(BCglue.glue).

\paragraph{Ch.~\texorpdfstring{\ref{v4-arith:bzn-sub}}{32} (BZN Formal Noetherian and EG Derived).}
No edits required in wave 3. R2 closure is a valid Lurie-DAG
packaging of Emerton--Gee, honestly inscribed as ProvedHere. R1
split into R1.fin-type (theorem, inapplicable to arithmetic setting)
plus R1.formal (conjectural) is already in place. Downstream F3
closure is marked \ClaimStatusProvedHere for the \emph{reduction} to
three sub-obligations; F3 itself remains conditional on R1.formal.b,
R1.formal.c, and R4.

\paragraph{Ch.~\texorpdfstring{\ref{v4-arith:bzn-rcompletion}}{33} (BZN Loop Convention and Wild Primes).}
No edits required in wave 3. R3 (loop convention equivalence) is
proved under explicit hypotheses (formal Noetherian derived
algebraic + finite Tor-amplitude + $t$-bounded); R4
(wild-prime Ext$^{1}$ correction) uses primary-literature inputs
(Bezrukavnikov, Etingof--Ostrik, Jantzen, Carter, Bushnell--Henniart)
correctly tagged.

\paragraph{Ch.~\texorpdfstring{\ref{v4-arith:bcglue-k5}}{35} (BC-Diamond-Glue Decomposition and K5).}
Two edits: update
\Cref{v4-arith:bcglue-k5:rem:residual-summary} to match the actual
proof tags: (BCglue.local) is theorem-waiting (not theorem);
(BCglue.glue) is conjectural (not theorem). Also downgrade
\Cref{v4-arith:bcglue-k5:cor:LACD-tight-catalog} from
\ClaimStatusNeedsVerification to \ClaimStatusConjectured to reflect
its conditional dependence on (BCglue.local), (BCglue.glue), and
upstream $\mathrm{L}_{\mathrm{ACD}}.k$ obligations.

\paragraph{App.~\texorpdfstring{A}{A} (Primary Source Catalog).}
One optional edit: add Dotto--Emerton--Gee arXiv:2603.26887 to
\S\ref{v4-arith:app:A:langlands} for completeness, since it is
cited in Ch.~\ref{v4-arith:closure} F1.a status line and
Ch.~\ref{v4-arith:open-frontiers} F1 residual catalog.

\section{Overall Assessment}
\label{v4-arith:w3-audit-A:overall}

The Spine-A chapters as inscribed post-wave-2 largely reflect
honest conditional-theorem wording. The principal remaining
overclaims are bookkeeping / cross-reference issues: (i) a
ProvedHere tag without an explicit ``conditional on F2.c'' suffix in
\Cref{v4-arith:lacd:thm:L1-closed}; (ii) summary-wording
mismatches in \Cref{v4-arith:bcglue-k5:rem:residual-summary} and
\Cref{v4-arith:bcglue-k5:cor:LACD-tight-catalog}; and (iii) a
missing App.~A entry for Dotto--Emerton--Gee. All three are
addressed by targeted Edit-tool repairs inscribed in
\S\ref{v4-arith:w3-audit-A:summary}. No structural theorems are
deleted; no claim is weakened beyond matching the corrected
residual catalog (\Cref{v4-arith:app:C:residual-table-w2}) and the
Platonic capstone (\Cref{v4-arith:platonic-rh-completion}).

\paragraph{Post-audit residual list (Spine A).}
Unchanged from the post-wave-2 catalog
(\Cref{v4-arith:app:C:residual-table-w2}) with the following
emphases surfaced by this audit:
\begin{itemize}
\item F1.a (local categorical comparison) is \textbf{Theorem-waiting}
via Dotto--Emerton--Gee arXiv:2603.26887 (fully-faithful-only,
$p\geq 5$, fixed central character). Fargues--Scholze supply local
geometrisation, spectral action, and Langlands-parameter package;
not the displayed categorical equivalence.
\item F1 closure requires F1.a $+$ $\mathrm{L}_{\mathrm{ACD}}$;
$\mathrm{L}_{\mathrm{ACD}}$ closure requires F2.c tightened $+$
(BCglue.local) $+$ (BCglue.glue) $+$ (BC-diamond-glue.core).
\item F3.BZN$^{\mathrm{Ar}}$ requires F1 $+$ F2 $+$ R1.formal.b
(profinite formal-loop continuity, $30$--$50$ pp) $+$ R1.formal.c
(flat-locus pullback, $20$--$40$ pp) $+$ R4 (wild-prime correction,
scope TBD beyond the explicit Ext$^{1}$ computation already
inscribed) $+$ full-target Weil/$(\varphi,\Gamma)$ comparison.
\item The Platonic RH completion package
(\Cref{v4-arith:platonic:def:RH-package}) remains the minimal
sufficient set for RH, with VB$^{*}$ operator positivity as the
single RH-equivalent operator residual, H-P$^{\mathrm{Ar}}$ as a
separate hypothesis, and the arithmetic Positselski C1--C5 plus
Koszul--Petersson compatibility on Spine B.
\end{itemize}

Wave-3's audit confirms that the honest residual list in
\Cref{v4-arith:app:C:residual-table-w2} is the correct running
catalog. No Spine-A claim rises above its documented conditional
status after this audit.
