\chapter{Wave-3 Audit Ledger: Spine B Corrections}
\label{v4-arith:w3-audit-B}

\emph{Wave-1 and wave-2 chapters on the RH-path (Spine B) overclaimed
the unconditionality of five load-bearing results: the P1 biconditional
for the abelian arithmetic Heisenberg, the full-sector P3 closure and
KMS$_1$/GNS identification, the K5 Godement--Jacquet normalisation on
the whole primary space, the C1--C5 Costello-refined Positselski, the
H-P$^{\mathrm{Ar}}$ reduction to ``essentially-closed-modulo-weight-choice'',
and the VB$^{*}\Rightarrow$F-RH implication. The authoritative corrected
view is the post-wave-2 residual catalog
(\Cref{v4-arith:app:C:residual-catalog-w2}) and the Platonic capstone
(\Cref{v4-arith:platonic:thm:RH-completion}). This chapter audits each
overclaim, downgrades or restricts the misplaced statuses, and records
the in-place repairs to Chapters~\ref{v4-arith:rh-reformulation},
\ref{v4-arith:virasoro-bootstrap}, \ref{v4-arith:arith-positselski},
\ref{v4-arith:kp-compat}, \ref{v4-arith:pos-costello},
\ref{v4-arith:bc-glue-k5}, \ref{v4-arith:HPAr-vbconverse}. The four-input
conditional spine (arith.~Positselski, Koszul--Pet compat,
H-P$^{\mathrm{Ar}}$, VB$^{*}$) is re-stated explicitly.}

\section{Overclaim Catalog}
\label{v4-arith:w3-audit-B:overclaim-catalog}

The six principal overclaims left by waves~1 and~2 on Spine~B are
catalogued in \Cref{v4-arith:w3-audit-B:tab:overclaims}. Each entry
names the offending statement, locates it at the chapter/theorem level,
identifies the open sub-item that falsifies the unconditional claim,
and points to the repaired statement in the target chapter.

\begin{table}[h]
\centering
\small
\begin{tabular}{l|p{5cm}|p{4.5cm}|l}
OC\# & Offending claim & Open sub-item & Repair target \\
\hline
OC1 & P1 biconditional unconditional for the abelian arithmetic
Heisenberg (\Cref{v4-arith:pos:thm:P1-full-unconditional},
\Cref{v4-arith:pos-costello:thm:P1-unconditional}). & Completed
continuous duals; derived completion; faithful lifting; primitive
zeta-character theorem; Koszul-dual Bost--Connes. & \S\ref{v4-arith:w3-audit-B:repair-25} \\
OC2 & P3 fully unconditional
(\Cref{v4-arith:kp:cor:P3-unconditional},
\Cref{v4-arith:kp:thm:main-full}). & Stable only on normalized
sph-fin cuspidal core; full $\mathcal{V}^{\mathrm{prim}}$
compatibility and KMS$_{1}$/GNS identification remain open. &
\S\ref{v4-arith:w3-audit-B:repair-26} \\
OC3 & K5 closed unconditionally via Hoffstein--Lockhart
(\Cref{v4-arith:bcglue-k5:thm:K5-absorption-canonical},
\Cref{v4-arith:bcglue-k5:thm:K5-adelic-consistent}). &
Conditional on sph-fin cuspidal cut; Eisenstein-pole handling via
sph-fin cut, not absent. & \S\ref{v4-arith:w3-audit-B:repair-35} \\
OC4 & C1--C5 closed as unconditional theorems
(\Cref{v4-arith:pos-costello:thm:C1-closed},
\Cref{v4-arith:pos-costello:thm:C2-closed},
\Cref{v4-arith:pos-costello:thm:C3-closed},
\Cref{v4-arith:pos-costello:thm:C4-closed},
\Cref{v4-arith:pos-costello:thm:C5-closed}). & Continuous duals,
derived completion, base-change faithfulness, pro-nilpotent
convergence, classical-limit check; each refinement restricts
domain but does not close the Positselski equivalence. &
\S\ref{v4-arith:w3-audit-B:repair-34} \\
OC5 & H-P$^{\mathrm{Ar}}$ equivalent to Connes / Deninger
``essentially closed modulo weight choice''
(\Cref{v4-arith:hpvbconv:thm:HPAr-equivalence}). & Domain theorem
closes; zeta-zero spectral matching open; Bost--Connes
trace-compatibility is the zeta-zero placement problem, not a
routine weight choice. & \S\ref{v4-arith:w3-audit-B:repair-36} \\
OC6 & VB$^{*}\Rightarrow$F-RH is unconditional under an
H-P$^{\mathrm{Ar}}$ hypothesis assumed trivial
(\Cref{v4-arith:rh:thm:VB-implies-F-RH}); VB$^{*}$ converse
``four-way equivalence'' closes VB$^{*}$ one direction
(\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}).
& The implication depends on P2, P3, H-P$^{\mathrm{Ar}}$, and a
positive Bost--Connes regularised trace; the converse is strictly
finer than RH and does not help the forward direction. &
\S\ref{v4-arith:w3-audit-B:repair-23},
\S\ref{v4-arith:w3-audit-B:repair-36} \\
\end{tabular}
\caption{Principal wave-1/wave-2 overclaims on Spine~B and their
repair targets.}
\label{v4-arith:w3-audit-B:tab:overclaims}
\end{table}

\paragraph{Authoritative references.} The corrected catalogue is
\Cref{v4-arith:app:C:residual-catalog-w2} (Post-wave-2 residual
catalog); the corrected RH-closure package is
\Cref{v4-arith:platonic:def:RH-package} and the Platonic RH-completion
theorem \Cref{v4-arith:platonic:thm:RH-completion}. The four-input
conditional spine is the minimal path of
\S\ref{v4-arith:app:C:minimal-path}: arith.~Positselski, Koszul--Pet
compat, H-P$^{\mathrm{Ar}}$, and VB$^{*}$ main direction.

\section{Repair Summary}
\label{v4-arith:w3-audit-B:repair-summary}

The repairs proceed chapter by chapter. Each repair downgrades the
offending claim to \texttt{ProvedHere} conditional on explicitly named
open items, or to \texttt{Conjectured}, or to
\texttt{ScopeRestricted} on the sph-fin cuspidal core. No theorems are
deleted; the H-VB$^{*}$ swarm heal in
Chapter~\ref{v4-arith:rh-reformulation} is preserved.

\subsection{Ch.~\ref{v4-arith:rh-reformulation} Repair (RH Reformulation)}
\label{v4-arith:w3-audit-B:repair-23}

\paragraph{Target.} Remark
\Cref{v4-arith:rh:rem:one-directional} already records the
\emph{one-directional} nature of VB$^{*}\Rightarrow$F-RH. The chapter
is otherwise honest in marking \Cref{v4-arith:rh:thm:VB-implies-F-RH}
as conditional on P2, P3, and H-P$^{\mathrm{Ar}}$, and in naming
VB$^{*}$ converse as strictly finer than RH.

\paragraph{Repair.} Add an explicit note at the summary table
(\Cref{v4-arith:rh:summary}) naming the four-input conditional spine
and reiterating that the H-VB$^{*}$ swarm heal has preserved only the
forward implication. The H-VB$^{*}$ heal remains inscribed.

\paragraph{Scope.} No \texttt{ClaimStatusProvedHere} tag is removed.
One clarifying remark is added to make the four-input spine explicit.

\subsection{Ch.~\ref{v4-arith:arith-positselski} Repair (Arithmetic Positselski)}
\label{v4-arith:w3-audit-B:repair-25}

\paragraph{Target.} The chapter's main theorem
\Cref{v4-arith:thm:arithmetic-positselski}, the corollary
\Cref{v4-arith:pos:cor:mu-zero-heisenberg}, and the P1-propagation
theorem \Cref{v4-arith:pos:thm:P1-full-unconditional} claim the
$\Lambda$-coefficient Positselski equivalence unconditionally (under
$\mu=0$) and propagate ``unconditional P1'' downstream. The
underlying arguments in Steps~1--6
(\S\ref{v4-arith:pos:step-1}--\S\ref{v4-arith:pos:step-6}) depend
on open sub-items: completed continuous duals and their compatibility
with co-derived and contra-derived categories
(\S\ref{v4-arith:pos:step-2}), derived completion of projective
and injective resolutions (\S\ref{v4-arith:pos:step-3}), faithful
lifting along Nakayama (\S\ref{v4-arith:pos:step-3}), the primitive
zeta-character theorem underpinning the $\kappa$-pairing weight
computation (\S\ref{v4-arith:pos:step-4}), and Koszul-dual
Bost--Connes interpretation of the $C^{\vee}$ side.

\paragraph{Repair.} Downgrade the status of
\Cref{v4-arith:thm:arithmetic-positselski},
\Cref{v4-arith:pos:cor:step-3-unconditional}, and
\Cref{v4-arith:pos:thm:P1-full-unconditional} from
\texttt{ClaimStatusProvedHere} to
\texttt{ClaimStatusProvedHere conditional on the five open sub-items
(continuous duals, derived completion, faithful lifting, primitive
zeta-character theorem, Koszul-dual Bost--Connes)}.
Add a \texttt{ScopeRestricted} tag to
\Cref{v4-arith:thm:arithmetic-positselski} locating its intended
scope on the abelian primary Heisenberg datum with these five
assumptions. Update summary (\S\ref{v4-arith:pos:summary}).

\paragraph{Scope.} Five \texttt{ClaimStatusProvedHere} upgrades are
downgraded to \texttt{ClaimStatusProvedHere} conditional, not
deleted; the theorems remain, carrying their conditional hypotheses
explicitly.

\subsection{Ch.~\ref{v4-arith:kp-compat} Repair (Koszul--Pet Compatibility and P3)}
\label{v4-arith:w3-audit-B:repair-26}

\paragraph{Target.} The main theorem
\Cref{v4-arith:kp:thm:main-full} and the corollary
\Cref{v4-arith:kp:cor:P3-unconditional} assert Koszul--Petersson
compatibility and P3 unitarity as unconditional. The archimedean
proposition (\Cref{v4-arith:kp:prop:Pet-is-Segal-infty}) is honest;
the finite-place proposition
(\Cref{v4-arith:kp:prop:Pet-p-is-BC-sigma}) depends on an unstated
KMS$_{1}$/GNS identification, and the adelic assembly
(\Cref{v4-arith:kp:thm:tate-assembly}) is only proved on the sph-fin
cuspidal core.

\paragraph{Repair.} Scope-restrict
\Cref{v4-arith:kp:thm:main-full} and
\Cref{v4-arith:kp:cor:P3-unconditional} to the
\emph{normalised sph-fin cuspidal core} of
$\mathcal{V}^{\mathrm{prim}}$, and downgrade them to
\texttt{ScopeRestricted}. Explicitly name the open sub-items: (i)
KMS$_{1}$/GNS identification beyond the normalised sph-fin cuspidal
core; (ii) full-sector Rankin--Selberg extension of the local
Petersson computation; (iii) Eisenstein-sector treatment
(currently excluded by the sph-fin cut). Update summary
(\S\ref{v4-arith:kp:summary}) and the corollary updating the
minimal RH path (\Cref{v4-arith:kp:cor:rh-minimal-updated}).

\paragraph{Scope.} Two \texttt{ProvedHere} tags are replaced by
\texttt{ScopeRestricted}; the theorems survive with their restricted
scope made explicit.

\subsection{Ch.~\ref{v4-arith:pos-costello} Repair (C1--C5)}
\label{v4-arith:w3-audit-B:repair-34}

\paragraph{Target.} The five closure theorems
\Cref{v4-arith:pos-costello:thm:C1-closed},
\Cref{v4-arith:pos-costello:thm:C2-closed},
\Cref{v4-arith:pos-costello:thm:C3-closed},
\Cref{v4-arith:pos-costello:thm:C4-closed},
\Cref{v4-arith:pos-costello:thm:C5-closed} each claim unconditional
closure of a named refinement, and the consequence
\Cref{v4-arith:pos-costello:thm:P1-unconditional} propagates the
unconditional P1 biconditional.

Each C$i$ proof reduces its refinement to a narrower domain (abelian
primary Heisenberg scope, $\mu=0$, unit-compatible pointed $E_{2}$
structure, etc.) but does not close the full Positselski equivalence:
C1 is conditional on the $\eta$-algebra pointed colimit of
\Cref{v4-arith:sw:conj:F2c-tightened}; C2 on Parshin reciprocity
modulo $\Lambda$-coboundaries and the $p=2$ torsion handling; C3
on pro-nilpotent convergence at $\beta=1$ matching the KMS$_{1}$
Tomita--Takesaki state; C4 on the Witt-truncation classical limit
and its compatibility with the archimedean Heisenberg Fock; C5 on
the restricted $\Lambda$-linear morphism class with trivial
$\Gamma$-action.

\paragraph{Repair.} Downgrade
\Cref{v4-arith:pos-costello:thm:C1-closed},
\Cref{v4-arith:pos-costello:thm:C2-closed},
\Cref{v4-arith:pos-costello:thm:C3-closed},
\Cref{v4-arith:pos-costello:thm:C4-closed},
\Cref{v4-arith:pos-costello:thm:C5-closed} from
\texttt{ClaimStatusProvedHere} to
\texttt{ClaimStatusProvedHere conditional} on the named
domain-restricting hypotheses. Downgrade
\Cref{v4-arith:pos-costello:thm:P1-unconditional} and
\Cref{v4-arith:pos-costello:cor:arith-Heis-Koszul} to
\texttt{ClaimStatusProvedHere} conditional on the five C$i$
conditionals plus the five open Positselski sub-items from
\S\ref{v4-arith:w3-audit-B:repair-25}. Update summary
(\S\ref{v4-arith:pos-costello:summary}).

\paragraph{Scope.} Seven \texttt{ProvedHere} tags are each
conditionalised; no theorem is deleted.

\subsection{Ch.~\ref{v4-arith:bc-glue-k5} Repair (K5)}
\label{v4-arith:w3-audit-B:repair-35}

\paragraph{Target.} The two K5 theorems
\Cref{v4-arith:bcglue-k5:thm:K5-absorption-canonical} and
\Cref{v4-arith:bcglue-k5:thm:K5-adelic-consistent} claim
unconditional closure of the Godement--Jacquet absorption
convention via Hoffstein--Lockhart nonvanishing. The corollary
\Cref{v4-arith:bcglue-k5:cor:K-P-unconditional} propagates this
unconditional closure to Koszul--Pet compat and P3.

The Hoffstein--Lockhart 1994 nonvanishing is an unconditional theorem
on the cuspidal sph-fin locus. The K5 absorption is therefore
conditional only on the cuspidal sph-fin scope; Eisenstein summands
are explicitly excluded by the sph-fin cut of
\Cref{v4-arith:sw:thm:KP-split}(K7), not absent.

\paragraph{Repair.} Scope-restrict
\Cref{v4-arith:bcglue-k5:thm:K5-absorption-canonical} and
\Cref{v4-arith:bcglue-k5:thm:K5-adelic-consistent} to the
\emph{cuspidal sph-fin locus}, and retain them as
\texttt{ClaimStatusProvedHere} with
\texttt{ScopeRestricted(cuspidal sph-fin)}. Downgrade the
Koszul--Pet propagation corollary
\Cref{v4-arith:bcglue-k5:cor:K-P-unconditional} to match
Ch.~\ref{v4-arith:kp-compat} scope restriction
(\S\ref{v4-arith:w3-audit-B:repair-26}). Remove the misleading
``unconditional'' phrasing in the summary
(\S\ref{v4-arith:bcglue-k5:summary}).

\paragraph{Scope.} Two \texttt{ProvedHere} tags remain in place with
explicit \texttt{ScopeRestricted(cuspidal sph-fin)} annotation.

\subsection{Ch.~\ref{v4-arith:HPAr-vbconverse} Repair (H-P$^{\mathrm{Ar}}$ and VB$^{*}$ Converse)}
\label{v4-arith:w3-audit-B:repair-36}

\paragraph{Target.} \Cref{v4-arith:hpvbconv:thm:HPAr-equivalence}
names four equivalent formulations of H-P$^{\mathrm{Ar}}$
(Friedrichs Fock, Connes adele class space, Deninger motivic
cohomology, spectral realisation condition) and its corollary
\Cref{v4-arith:hpvbconv:cor:HPAr-single-residual} asserts the
``single residual is the choice of Bost--Connes zero-mode weights.''
The domain theorem \Cref{v4-arith:hpvbconv:thm:L0-Friedrichs}
closes the Friedrichs construction; the trace-compatibility
proposition \Cref{v4-arith:hpvbconv:prop:BC-trace-compatibility}
and the Connes identification
\Cref{v4-arith:hpvbconv:thm:connes-identification} reduce the
trace-compatibility to the zeta-zero spectrum of the Bost--Connes
scaling action---which is Hilbert--P\'olya.

\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}
and its corollary
\Cref{v4-arith:hpvbconv:cor:three-strictly-finer} name four
equivalent forms of the VB$^{*}$ converse, all strictly finer than
RH. This equivalence is honest at the converse level but has been
over-advertised in wave-2 summaries as closing VB$^{*}$ ``one
direction''; the converse is strictly finer than RH and does not
help the forward direction VB$^{*}\Rightarrow$F-RH.

\paragraph{Repair.} Retain
\Cref{v4-arith:hpvbconv:thm:L0-Friedrichs} as \texttt{ProvedHere}
(domain theorem; genuinely closed). Retain
\Cref{v4-arith:hpvbconv:thm:HPAr-equivalence} as
\texttt{ProvedHere} for the equivalence of the four formulations,
but add an explicit remark that the zeta-zero spectral matching is
the open Hilbert--P\'olya content, not a routine ``weight choice.''
Retain
\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}
and its strictly-finer-than-RH status, and add an explicit remark
that the converse does not help VB$^{*}\Rightarrow$F-RH.
Update \Cref{v4-arith:hpvbconv:cor:HPAr-single-residual} to remove
the ``single residual'' wording; the residual is Hilbert--P\'olya
itself. Update summary
(\S\ref{v4-arith:hpvbconv:summary}).

\paragraph{Scope.} No \texttt{ProvedHere} tag is removed; two
corollaries are re-worded to stop advertising ``essentially closed
modulo weight choice.''

\subsection{App.~\ref{v4-arith:app:primary-sources} Repair (Primary-Source Catalog)}
\label{v4-arith:w3-audit-B:repair-A}

\paragraph{Target.} The Li/Weil/Deninger citations in
\S\ref{v4-arith:app:A:li-weil} and
\S\ref{v4-arith:app:A:operator-theory} currently describe the
status of H-P$^{\mathrm{Ar}}$/VB$^{*}$ reductions without pointing
to the wave-3 corrections.

\paragraph{Repair.} Add a short closing remark to
\S\ref{v4-arith:app:A:li-weil} naming the strictly-finer-than-RH
content (Hamburger determinacy of the symmetrised zero measure) as
the VB$^{*}$ converse. Add a short closing remark to
\S\ref{v4-arith:app:A:operator-theory} noting that the Connes and
Deninger programme references anchor equivalent formulations of
H-P$^{\mathrm{Ar}}$ but that the zeta-zero spectral matching
itself remains the open Hilbert--P\'olya content.

\paragraph{Scope.} Purely annotative; no theorem statuses are
affected.

\section{The Four-Input Conditional Spine, Made Explicit}
\label{v4-arith:w3-audit-B:four-input-spine}

After the wave-3 audit, the minimal closure path to RH within Vol~IV's
arithmetic branch is the conjunction of four open inputs. This
matches verbatim the post-wave-2 minimal path of
\S\ref{v4-arith:app:C:minimal-path} and the Platonic RH-completion
hypothesis package of
\Cref{v4-arith:platonic:def:RH-package}.

\begin{theorem}[four-input conditional spine, post-wave-3]
\label{v4-arith:w3-audit-B:thm:four-input-spine}
\ClaimStatusProvedHere. Within the Vol~IV arithmetic branch, the
following four open items form a sufficient conditional package for
the Riemann Hypothesis:
\begin{enumerate}
\item \textbf{arith.~Positselski}: the $\Lambda$-coefficient
Positselski equivalence of
\Cref{v4-arith:thm:arithmetic-positselski} on the abelian primary
Heisenberg scope, conditional on the five open sub-items
(continuous duals; derived completion; faithful lifting; primitive
zeta-character theorem; Koszul-dual Bost--Connes).
\item \textbf{Koszul--Pet compat}: the identification
\Cref{v4-arith:kp:thm:main-full} scope-restricted to the normalized
sph-fin cuspidal core, plus the open KMS$_{1}$/GNS identification
and full-sector Rankin--Selberg extension.
\item \textbf{H-P$^{\mathrm{Ar}}$}: the arithmetic Hilbert--P\'olya
hypothesis in the spectral-realisation form of
\Cref{v4-arith:hpvbconv:thm:HPAr-equivalence}, whose open content is
the zeta-zero spectral matching (Hilbert--P\'olya itself).
\item \textbf{VB$^{*}$ main direction}: the RH-equivalent
operator-positivity statement of
\Cref{v4-arith:rh:thm:VB-implies-F-RH} read as a standalone residual.
\end{enumerate}
The first two are scope-restricted reductions of Spine-B Positselski
and adelic compatibility; the third is a Friedrichs extension plus
the Hilbert--P\'olya content; the fourth is the operator-positivity
residual. Their conjunction is sufficient for F-RH via
\Cref{v4-arith:platonic:thm:RH-completion}. No converse necessity is
claimed for the internal scaffold inputs.
\end{theorem}

\begin{proof}
The sufficiency is exactly the Platonic RH-completion theorem's
assembly of P1, P2, P3, H-P$^{\mathrm{Ar}}$, VB$^{*}$, and
Hamburger determinacy into the RH-closure package; after wave-3 audit
these inputs reduce to the four named above. Logical separation of
the H-P$^{\mathrm{Ar}}$/VB$^{*}$ residuals is
\Cref{v4-arith:hpvbconv:prop:HPAr-det-independent} at the
H-P$^{\mathrm{Ar}}$/VB$^{*}$ boundary and
\Cref{v4-arith:pos:residual-scope},
\Cref{v4-arith:kp:rem:paper-length-reestimate} elsewhere.
\end{proof}

\begin{remark}[what wave-3 preserves]
\label{v4-arith:w3-audit-B:rem:preserved}
The wave-3 audit preserves:
\begin{itemize}
\item All theorem labels, all statements, and the attack--heal
ledgers of wave-1 and wave-2.
\item The H-VB$^{*}$ swarm heal of
Ch.~\ref{v4-arith:rh-reformulation} (one-directional VB$^{*}
\Rightarrow$F-RH).
\item The Platonic RH-completion theorem
\Cref{v4-arith:platonic:thm:RH-completion} and its capstone role
in Ch.~\ref{v4-arith:platonic-rh-completion}.
\item The distinction between the RH-independent Spine~A (F1/F2/F3
residuals) and the RH-dependent Spine~B (four-input conditional).
\end{itemize}
\end{remark}

\begin{remark}[what wave-3 changes]
\label{v4-arith:w3-audit-B:rem:changed}
The wave-3 audit changes only the status tags and the propagation
wording:
\begin{enumerate}
\item Ch.~\ref{v4-arith:arith-positselski}: five theorems
downgraded from \texttt{ProvedHere} to \texttt{ProvedHere
conditional on the five open Positselski sub-items}.
\item Ch.~\ref{v4-arith:kp-compat}: main theorem and P3 corollary
scope-restricted to the normalized sph-fin cuspidal core with
KMS$_{1}$/GNS identification listed as open.
\item Ch.~\ref{v4-arith:pos-costello}: seven closure theorems (C1,
C2, C3, C4, C5, P1 consequence, arith.~Heis Koszul corollary)
conditionalised on their named domain-restricting hypotheses.
\item Ch.~\ref{v4-arith:bc-glue-k5}: two K5 theorems
scope-restricted to the cuspidal sph-fin locus.
\item Ch.~\ref{v4-arith:HPAr-vbconverse}: H-P$^{\mathrm{Ar}}$
single-residual corollary re-worded; VB$^{*}$ converse remark added
clarifying that the converse does not help VB$^{*}\Rightarrow$F-RH.
\item App.~\ref{v4-arith:app:primary-sources}:
Li/Weil/Deninger/operator-theory annotations corrected to match the
post-wave-3 residual catalog.
\end{enumerate}
\end{remark}

\section{Honesty Audit of the Load-Bearing Theorem}
\label{v4-arith:w3-audit-B:load-bearing}

The arithmetic branch's load-bearing theorem
\begin{equation*}
\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}
\;=\;0\;\Longleftrightarrow\;\xi(s)=\xi(1-s)
\end{equation*}
(\Cref{v4-arith:thm:G-row-Riemann-functional-equation},
\Cref{v4-arith:thm:P1-resolution}) is the statement that arithmetic
Koszul self-duality for the abelian Heisenberg archetype is
equivalent to the Riemann functional equation. Its forward direction
$(\Rightarrow)$ is closed in
\Cref{v4-arith:cl:cor:P1-unconditional-forward}
(by Tate 1950 adelic Poisson). The full biconditional requires
arithmetic Positselski, and hence inherits the five open sub-items
named in OC1.

Wave-3 preserves the load-bearing theorem's status as
\emph{Theorem-waiting}: forward direction unconditional, biconditional
conditional on arithmetic Positselski (in the post-wave-3 sense of
OC1). This status is consistent with the Platonic capstone's
reading of the load-bearing theorem as the P1 component of the four-input
conditional spine (\Cref{v4-arith:platonic:thm:RH-completion}).

\section{Summary}
\label{v4-arith:w3-audit-B:summary}

\begin{enumerate}
\item Six principal overclaims OC1--OC6 of waves~1 and~2 on Spine~B
are catalogued in
\Cref{v4-arith:w3-audit-B:tab:overclaims}.
\item Each overclaim is repaired in-place by status downgrade or
scope restriction, not by deletion. The theorems survive; the
advertised unconditionality is corrected.
\item The four-input conditional spine of
\Cref{v4-arith:w3-audit-B:thm:four-input-spine} is the honest
minimal path to RH within Vol~IV's framework, matching the
post-wave-2 catalog
\Cref{v4-arith:app:C:residual-catalog-w2} verbatim.
\item The load-bearing theorem retains its \emph{Theorem-waiting}
status: forward direction unconditional, full biconditional
conditional on arith.~Positselski.
\item The H-VB$^{*}$ swarm heal in
Ch.~\ref{v4-arith:rh-reformulation} is preserved; the Platonic
RH-completion theorem in
Ch.~\ref{v4-arith:platonic-rh-completion} is preserved.
\item Honesty is preferred to closure. The residuals are named
precisely; none is swept under a ``routine'' tag.
\end{enumerate}

This chapter is the wave-3 audit ledger. It contains no new
mathematics; it records the status corrections to Chapters~\ref{v4-arith:rh-reformulation},
\ref{v4-arith:virasoro-bootstrap},
\ref{v4-arith:arith-positselski},
\ref{v4-arith:kp-compat},
\ref{v4-arith:pos-costello},
\ref{v4-arith:bc-glue-k5},
\ref{v4-arith:HPAr-vbconverse}, and to
App.~\ref{v4-arith:app:primary-sources}, and names the four-input
conditional spine explicitly.
