\chapter{The Dotto--Emerton--Gee Extension: F1.a at All Primes}
\label{v4-arith:deg-f1a}

\emph{Wave-2 overclaimed F1.a as closed via Fargues--Scholze.
Fargues--Scholze arXiv:2102.13459 supplies local geometrisation,
spectral action, and the Langlands parameter package; it does not
supply the displayed equivalence
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{p})])\simeq\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}})$.
The state of the art is Dotto--Emerton--Gee arXiv:2603.26887:
\emph{a fully faithful functor}
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{p})])_{\chi}\to\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}})$
for $p\geq 5$ at fixed central character $\chi$. Essential
surjectivity, extension to $p\in\{2,3\}$, and variation over
$\chi$ are all open. This chapter isolates each obstruction,
attacks it via a disjoint source catalog, and inscribes the
strongest reduction available. No unconditional closure of F1.a
is claimed. Each residual is named exactly; each partial closure
is scoped.}

\section{Wave-3 Context}
\label{v4-arith:deg-f1a:context}

\subsection{What Wave-2 Closed, What Wave-2 Overclaimed}

Chapter~\ref{v4-arith:closure} recorded F1.a as a
\emph{local categorical comparison at every prime} and labelled it
\emph{theorem-waiting}, with Fargues--Scholze arXiv:2102.13459
identified as the input supply. The wave-2 ledger entry was accurate
in substance but loose in scope: Fargues--Scholze supply three
components of F1.a and do not supply the fourth. Explicitly:
\begin{itemize}
\item[(FS1)] \emph{Local geometrisation.} The moduli of local Langlands
parameters is realised as a diamond
$\mathrm{LocSys}^{\mathrm{FS}}_{GL_{2},p}$ with a spectral action of
$\mathrm{Perf}(\mathrm{LocSys}^{\mathrm{FS}}_{GL_{2},p})$ on the
$\ell$-adic sheaves category of
$\mathrm{Bun}_{GL_{2}}^{\mathrm{FF}}$ (the moduli of $GL_{2}$-bundles
on the Fargues--Fontaine curve).
\item[(FS2)] \emph{Spectral action.} For each $L$-parameter
$\phi\colon W_{\mathbb{Q}_{p}}\to{}^{L}GL_{2}$, one obtains a functor
$T_{\phi}\colon\mathrm{D}(\mathrm{Bun}_{GL_{2}}^{\mathrm{FF}})\to\mathrm{D}(\mathrm{Bun}_{GL_{2}}^{\mathrm{FF}})$.
\item[(FS3)] \emph{Hecke-functoriality} at each place, compatible with
convolution.
\item[(FS4)] \emph{Displayed equivalence} of the form
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{p})])\simeq\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}})$.
\textbf{Not supplied by FS.}
\end{itemize}

The displayed equivalence (FS4) is a separate local input. The most
recent progress toward it is Dotto--Emerton--Gee arXiv:2603.26887,
which replaces (FS4) by a \emph{fully faithful functor at fixed
central character} for $p\geq 5$. Three obstructions separate DEG
from (FS4):

\begin{description}
\item[\textbf{(a)} Essential surjectivity.] The DEG functor is
fully faithful; its image is a proper full sub-$\infty$-category of
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}})$.
Identifying the image or showing it exhausts the target is open.
\item[\textbf{(b)} Wild primes $p\in\{2,3\}$.] The DEG functor is
proved only at $p\geq 5$. At $p=2,3$ the Iwahori Hecke category is
non-semisimple (Ch.~\ref{v4-arith:bzn-rcompletion}); the standard
Colmez--Paskunas block methods used by DEG change character at the
wild level.
\item[\textbf{(c)} Central character variation.] The DEG functor is
proved for fixed $\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},\mathbb{C}^{\times})$.
The full $\mathrm{D}^{\mathrm{sph\text{-}fin}}$ of F1.a varies over
all central characters and requires a family version over the
character torus.
\end{description}

\subsection{Scope of This Chapter}

We attack each of (a), (b), (c) separately. The target is the
strongest available reduction: prove if possible, otherwise name
the precise obstruction. We do not claim to close F1.a
unconditionally. We record the following partial closures:
\begin{itemize}
\item[(a)] \emph{Essential surjectivity for $p\geq 5$ at fixed
$\chi$} reduces, via the Colmez--Paskunas block decomposition and a
Koszul-type computation of the generating compact objects, to a
single \emph{block-exhaustion} conjecture
(\Cref{v4-arith:deg-f1a:conj:block-exhaustion}). This conjecture is
strictly narrower than (a) itself and is plausibly tractable.
\item[(b)] \emph{Extension to $p=2,3$} reduces to a two-step
programme: (i) a twisted DEG functor on the wild block, constructed
from the Bushnell--Henniart tame/wild correspondence, plus (ii) a
non-semisimple enhancement of the Emerton--Gee stack accounting for
the wild inertia component. We inscribe (i) as
\Cref{v4-arith:deg-f1a:thm:wild-functor-existence} (conditional on
the Bushnell--Henniart packaging) and (ii) as
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}.
\item[(c)] \emph{Central character variation} closes
unconditionally once (a) closes, via a pushforward argument along
the central-character fibration
(\Cref{v4-arith:deg-f1a:thm:central-character-variation}). This is
the cleanest obstruction of the three.
\end{itemize}

The composite closes F1.a modulo two conjectural inputs: block
exhaustion (for (a) at $p\geq 5$) and the wild-EG enhancement (for
(b) at $p=2,3$). The cleanest partial closure is obtained at $p\geq 5$
with fixed central character removed: this closes F1.a
\emph{conditionally on block exhaustion and unconditionally on
central-character variation}.

\subsection{Label and Prose Discipline}

All theorem-like environments in this chapter use the prefix
\texttt{v4-arith:deg-f1a:} to disambiguate from the rest of Vol~IV.
Prose follows the active-voice Russian-school register of the
volume; the CLAUDE.md banned-token list is applied throughout.

\section{Attack--Heal Ledger}
\label{v4-arith:deg-f1a:ledger}

Six attack--heal cycles structure this chapter. Each cycle includes
the seven-attack protocol of \Cref{v4-arith:cl:protocol}
(source collision, sign/convention, ambient category, missing
hypothesis, false functoriality, unproved equivalence,
engine-test sync). The ledger is recorded here in outline and in
detail within each section.

\begin{description}
\item[\textbf{Cycle 1 (essential surjectivity at $p\geq 5$, fixed
$\chi$).}] \emph{Attack.} Take an object
$\mathcal{F}\in\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}})$
not in the image of the DEG functor; show it restricts to
a Colmez--Paskunas block whose generating compact is not hit.
\emph{Heal.} Combine Colmez 2010 $(\varphi,\Gamma)$-module classification
with Paskunas 2013 block decomposition of $\mathrm{Mod}_{GL_{2}(\mathbb{Q}_{p})}^{\mathrm{sm}}$
to reduce essential surjectivity to a finite-block check
(\S\ref{v4-arith:deg-f1a:ess-surj}).
\emph{Residual: block-exhaustion conjecture.}

\item[\textbf{Cycle 2 (extension to $p=2$).}] \emph{Attack.} The
Bushnell--Henniart tame/wild parametrisation of smooth $GL_{2}(\mathbb{Q}_{2})$
representations produces a non-semisimple block structure outside
the regime of DEG. \emph{Heal.} Construct a twisted DEG functor on
each wild block by pairing the Bushnell--Henniart classification
with the Emerton--Gee stack enhanced by the wild inertia data; at
$p=2$ this amounts to incorporating a single Ext${}^{1}$-classified
extension (aligned with Ch.~\ref{v4-arith:bzn-rcompletion}, R4)
(\S\ref{v4-arith:deg-f1a:wild}).
\emph{Residual: wild-EG enhancement.}

\item[\textbf{Cycle 3 (extension to $p=3$).}] \emph{Attack.} At
$p=3$ the wild block structure is the three-simple $A_{2}$-quiver
non-semisimple block of the Iwahori Hecke algebra
(\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p3}). \emph{Heal.}
Construct the twisted DEG functor analogously to Cycle~2, absorbing
the two Ext${}^{1}$-classes of the principal block into a refined
spectral-side moduli problem
(\S\ref{v4-arith:deg-f1a:wild}).
\emph{Residual: same wild-EG enhancement conjecture, instantiated
at $p=3$.}

\item[\textbf{Cycle 4 (central character variation).}] \emph{Attack.}
The DEG functor depends on a choice of
$\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},\mathbb{C}^{\times})$.
The full $\mathrm{D}^{\mathrm{sph\text{-}fin}}$ is a family over
this character torus. \emph{Heal.} Apply the standard decomposition
$\mathrm{D}([GL_{2}(\mathbb{Q}_{p})])\simeq\bigoplus_{\chi}\mathrm{D}([GL_{2}(\mathbb{Q}_{p})])_{\chi}$
over central characters and pushforward DEG block-by-block
(\S\ref{v4-arith:deg-f1a:central-char}).
\emph{Residual: none at this step;
assembly is straightforward once (a) closes.}

\item[\textbf{Cycle 5 (full F1.a closure).}] \emph{Attack.} Assemble
(a), (b), (c) into a single statement for $p$-ranging F1.a.
\emph{Heal.} The assembly is a direct sum over primes of the
per-prime DEG functors, extended by the wild
correction and varied over the central character torus
(\S\ref{v4-arith:deg-f1a:reduction}).
\emph{Residual: conditional closure; two conjectural inputs.}

\item[\textbf{Cycle 6 (global assembly check).}] \emph{Attack.}
Does F1.a closed locally at every prime suffice for the adelic
F1 together with $\mathrm{L}_{\mathrm{ACD}}$? \emph{Heal.} Cross-check
with \Cref{v4-arith:cl:cor:F1-single-lemma}: local F1.a plus
$\mathrm{L}_{\mathrm{ACD}}$ closes F1
(\S\ref{v4-arith:deg-f1a:global-check}).
\emph{Pass.}
\end{description}

Cycle-level seven-attack protocols are recorded inline within each
section. All cycles close either unconditionally or with named
residuals.

\section{Dotto--Emerton--Gee Recalled}
\label{v4-arith:deg-f1a:deg-recalled}

We state the DEG result precisely. This is the theorem on which
everything in this chapter builds.

\subsection{Setup}

Fix a prime $p\geq 5$, an algebraically closed field
$k=\overline{\mathbb{Q}}_{\ell}$ with $\ell\neq p$, and a smooth
character $\chi\colon\mathbb{Z}_{p}^{\times}\to k^{\times}$
realised as the central character of smooth representations of
$GL_{2}(\mathbb{Q}_{p})$. Let
\[
\mathrm{Mod}_{GL_{2}(\mathbb{Q}_{p})}^{\mathrm{sm},\chi}
\]
denote the abelian category of smooth $GL_{2}(\mathbb{Q}_{p})$-representations
over $k$ with central character $\chi$; let
\[
\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{p})]\bigr)_{\chi}
\]
denote the stable presentable $\infty$-category of sph-finite
objects in the derived category of
$\mathrm{Mod}_{GL_{2}(\mathbb{Q}_{p})}^{\mathrm{sm},\chi}$ (sph-finite:
compactly generated by finitely generated modules under the
spherical-Hecke action).

On the spectral side, let
$\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}$ denote the fibre of the
Emerton--Gee stack $\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$ at the
central character $\chi$ (equivalently, the moduli of $(\varphi,\Gamma)$-modules
with determinant $\chi\cdot\chi_{\mathrm{cyc}}$ where $\chi_{\mathrm{cyc}}$
is the cyclotomic character).

\subsection{DEG Theorem}

\begin{theorem}[Dotto--Emerton--Gee arXiv:2603.26887]
\label{v4-arith:deg-f1a:thm:deg-fixed-chi}
\ClaimStatusProvedElsewhere. Let $p\geq 5$ and
$\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},k^{\times})$. There
exists a fully faithful functor
\begin{equation}
\label{v4-arith:deg-f1a:eq:deg-functor}
\Phi^{\mathrm{DEG}}_{p,\chi}\colon
\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{p})]\bigr)_{\chi}
\;\longrightarrow\;
\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}\bigr)
\end{equation}
of stable presentable $\infty$-categories, compatible with the
spectral action of $\mathrm{Perf}(\mathrm{LocSys}^{\mathrm{FS}}_{GL_{2},p,\chi})$
and the Hecke-convolution structure at the place $p$.
\end{theorem}

\begin{proof}[Source]
Dotto--Emerton--Gee arXiv:2603.26887 Theorem~1.1, proved by
combining the Colmez--Paskunas block decomposition of
$\mathrm{Mod}_{GL_{2}(\mathbb{Q}_{p})}^{\mathrm{sm},\chi}$
(Colmez 2010; Paskunas 2013) with the Emerton--Gee stack of
$(\varphi,\Gamma)$-modules (Emerton--Gee arXiv:1908.07185) plus a
gluing argument along the Breuil--Mezard conjectural cycle
(Emerton--Gee arXiv:1908.07185 for the crystalline case;
Breuil--Mezard 2002 for the semistable extension).
\end{proof}

\begin{remark}[what DEG does not assert]
\label{v4-arith:deg-f1a:rem:deg-not-assert}
The theorem asserts fully faithfulness. It does not assert:
\begin{enumerate}
\item Essential surjectivity (there exist objects in the target
not in the image);
\item A statement at $p\in\{2,3\}$ (the proof uses $p\geq 5$ in
multiple places: the Colmez block decomposition of $\mathrm{Mod}^{\mathrm{sm}}_{GL_{2}(\mathbb{Q}_{p})}$
requires semisimple Iwahori Hecke action, failing at $p=2,3$);
\item A statement varying $\chi$ (each central character gives a
separate equivalence).
\end{enumerate}
These three gaps are obstructions (a), (b), (c) attacked in the
rest of this chapter.
\end{remark}

\begin{proposition}[the image of $\Phi^{\mathrm{DEG}}_{p,\chi}$]
\label{v4-arith:deg-f1a:prop:deg-image}
\ClaimStatusProvedElsewhere. The image of $\Phi^{\mathrm{DEG}}_{p,\chi}$
lies in the sub-$\infty$-category
\[
\mathrm{IndCoh}_{\mathrm{Nilp}}^{\mathrm{BM\text{-}image}}\bigl(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}\bigr)
\subseteq\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}\bigr)
\]
generated under colimits and shifts by the structure sheaves of the
Breuil--Mezard cycles
$\{[\mathcal{X}^{\mathrm{BM},\sigma}_{p,\chi}]\}_{\sigma}$
indexed by Serre weights $\sigma$ of the local Galois deformation
problem.
\end{proposition}

\begin{proof}[Source]
Dotto--Emerton--Gee arXiv:2603.26887 \S5 (image computation). The
Breuil--Mezard cycles are the closed substacks of
$\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}$ cut out by imposing a
Serre-weight condition at $p$; their union covers
$\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}$ set-theoretically but
need not generate $\mathrm{IndCoh}_{\mathrm{Nilp}}$ under colimits.
\end{proof}

\subsection{Why Essential Surjectivity is Subtle}

\begin{remark}[intuition for obstruction (a)]
\label{v4-arith:deg-f1a:rem:deg-fails-surj-intuition}
The sub-$\infty$-category $\mathrm{IndCoh}_{\mathrm{Nilp}}^{\mathrm{BM\text{-}image}}$
is the colimit closure of structure sheaves of Breuil--Mezard
cycles. A candidate object not in the image is the structure sheaf
of an \emph{intersection} of two Breuil--Mezard cycles that is not
itself a Breuil--Mezard cycle; such intersections exist at the
boundary of the crystalline locus and at the non-semistable locus
(Emerton--Gee arXiv:1908.07185 \S 6). Whether these intersections
can be resolved into iterated colimits of Breuil--Mezard cycles is
the block-exhaustion question.
\end{remark}

\section{Obstruction (a): Essential Surjectivity at $p\geq 5$}
\label{v4-arith:deg-f1a:ess-surj}

\subsection{The Colmez--Paskunas Block Decomposition}

\begin{theorem}[Colmez 2010; Paskunas 2013]
\label{v4-arith:deg-f1a:thm:colmez-paskunas-blocks}
\ClaimStatusProvedElsewhere. For $p\geq 5$ and a fixed central
character $\chi$, the category
$\mathrm{Mod}_{GL_{2}(\mathbb{Q}_{p})}^{\mathrm{sm},\chi}$
decomposes as a block diagonal sum
\[
\mathrm{Mod}_{GL_{2}(\mathbb{Q}_{p})}^{\mathrm{sm},\chi}
\;=\;\prod_{\rho}\mathrm{Block}_{\rho},
\]
indexed by isomorphism classes
$\rho\colon G_{\mathbb{Q}_{p}}\to GL_{2}(\overline{\mathbb{F}}_{p})$
of residual Galois representations with determinant $\chi|_{G_{\mathbb{Q}_{p}}}$.
Each $\mathrm{Block}_{\rho}$ is a Krull--Schmidt abelian category
with finitely many projective indecomposable generators whose
endomorphism algebra is a local Cohen--Macaulay complete local
Noetherian ring.
\end{theorem}

\begin{proof}[Source]
Colmez 2010 \emph{Repr\'esentations de $GL_{2}(\mathbb{Q}_{p})$ et
$(\varphi,\Gamma)$-modules}, Ast\'erisque~330, pp.~281--509, \S 7
(the $(\varphi,\Gamma)$-module-GL$_{2}$ bijection); Paskunas 2013
\emph{The image of Colmez's Montreal functor}, Publ.~IHES~118:1--191,
\S 6 (block structure of $\mathrm{Mod}^{\mathrm{sm},\chi}$). Both
are proved under $p\geq 5$ with the standard assumptions on
$\rho$ (generic residual, non-scalar semisimplification).
\end{proof}

\subsection{The Corresponding Spectral-Side Decomposition}

\begin{proposition}[spectral-side block decomposition]
\label{v4-arith:deg-f1a:prop:spectral-blocks}
\ClaimStatusProvedHere. For $p\geq 5$ and $\chi$ as above,
the stack $\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}$ admits a
decomposition into formal neighbourhoods
\begin{equation}
\label{v4-arith:deg-f1a:eq:EG-block-decomp}
\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}
\;=\;\coprod_{\rho}\mathcal{X}^{\mathrm{EG},p,\chi,\rho}_{GL_{2}}
\end{equation}
indexed by the same set of residual Galois representations
$\rho$, where
$\mathcal{X}^{\mathrm{EG},p,\chi,\rho}_{GL_{2}}=\mathrm{Spf}\,R_{\rho,\chi}$
is the versal deformation space of $\rho$ with determinant $\chi\cdot\chi_{\mathrm{cyc}}$.
The equivalence is compatible with the decomposition of
\Cref{v4-arith:deg-f1a:thm:colmez-paskunas-blocks} under
$\Phi^{\mathrm{DEG}}_{p,\chi}$ in the sense that
$\Phi^{\mathrm{DEG}}_{p,\chi}(\mathrm{Block}_{\rho})\subseteq\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi,\rho}_{GL_{2}})$.
\end{proposition}

\begin{proof}
\textbf{Step 1: spectral blocks are connected components.} The
Emerton--Gee stack $\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}$ is a
formal algebraic stack over $\mathrm{Spf}\,\mathbb{Z}_{p}$
(Emerton--Gee arXiv:1908.07185 Thm~3.2.1). Its connected components
are indexed by pairs $(\rho,\chi)$: the residual representation
$\rho$ and the central character $\chi$. Fixing $\chi$ leaves
connected components indexed by $\rho$. Each component is the formal
completion of the deformation functor of the pair
$(\rho,\chi\cdot\chi_{\mathrm{cyc}})$, representable by
$\mathrm{Spf}\,R_{\rho,\chi}$ with $R_{\rho,\chi}$ a complete
Noetherian local ring.

\textbf{Step 2: block compatibility.} The DEG functor sends the
generating projective indecomposables of $\mathrm{Block}_{\rho}$ to
the structure sheaves of (or resolutions along) the Breuil--Mezard
cycles attached to $\rho$ (Dotto--Emerton--Gee \S4). These cycles
are supported in $\mathcal{X}^{\mathrm{EG},p,\chi,\rho}_{GL_{2}}$ by
construction (the Breuil--Mezard cycles are defined inside each
component). Hence $\Phi^{\mathrm{DEG}}_{p,\chi}(\mathrm{Block}_{\rho})\subseteq\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi,\rho}_{GL_{2}})$.
\end{proof}

\begin{corollary}[reduction of essential surjectivity to individual blocks]
\label{v4-arith:deg-f1a:cor:ess-surj-block-by-block}
\ClaimStatusProvedHere. Essential surjectivity of
$\Phi^{\mathrm{DEG}}_{p,\chi}$ is equivalent to essential
surjectivity of the individual block functors
\begin{equation}
\Phi^{\mathrm{DEG}}_{p,\chi,\rho}\colon\mathrm{Block}_{\rho}\to\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG},p,\chi,\rho}_{GL_{2}}\bigr)
\end{equation}
for every $\rho$.
\end{corollary}

\begin{proof}
$\Phi^{\mathrm{DEG}}_{p,\chi}$ respects the decomposition of
\Cref{v4-arith:deg-f1a:prop:spectral-blocks}; essential surjectivity
of a direct sum of functors is the direct sum of essential
surjectivities.
\end{proof}

\subsection{The Block-Exhaustion Question}

\begin{definition}[block exhaustion]
\label{v4-arith:deg-f1a:def:block-exhaustion}
\ClaimStatusDefinitional. A block
$(\mathrm{Block}_{\rho},\mathcal{X}^{\mathrm{EG},p,\chi,\rho}_{GL_{2}})$
is \emph{DEG-exhausted} if the functor $\Phi^{\mathrm{DEG}}_{p,\chi,\rho}$
is essentially surjective; equivalently, the Breuil--Mezard cycles
on $\mathcal{X}^{\mathrm{EG},p,\chi,\rho}_{GL_{2}}$ generate
$\mathrm{IndCoh}_{\mathrm{Nilp}}$ under colimits and shifts.
\end{definition}

\begin{conjecture}[block-exhaustion]
\label{v4-arith:deg-f1a:conj:block-exhaustion}
\ClaimStatusConjectured. For every prime $p\geq 5$, every
central character $\chi$, and every residual Galois representation
$\rho$ in the support of $\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}$,
the pair
$(\mathrm{Block}_{\rho},\mathcal{X}^{\mathrm{EG},p,\chi,\rho}_{GL_{2}})$
is DEG-exhausted.
\end{conjecture}

\begin{remark}[what would prove block exhaustion]
\label{v4-arith:deg-f1a:rem:how-to-prove-block-exhaustion}
Sufficient inputs for
\Cref{v4-arith:deg-f1a:conj:block-exhaustion}:
\begin{enumerate}
\item A \emph{Koszul duality} between the projective generators of
$\mathrm{Block}_{\rho}$ and the structure sheaves of the
Breuil--Mezard cycles of $\rho$, in the sense of Beilinson--Ginzburg
1996 (Koszul duality for category O). If Koszul duality holds
at the block level, the generators on each side match under
$\Phi^{\mathrm{DEG}}_{p,\chi,\rho}$, forcing essential surjectivity.
\item A \emph{Breuil--Mezard completeness} statement:
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi,\rho}_{GL_{2}})$
is compactly generated by structure sheaves of Breuil--Mezard cycles
(not merely supported on them).
\item A \emph{generation by types} statement: the projective
indecomposables of $\mathrm{Block}_{\rho}$ are the compact images
of a finite list of Bushnell--Kutzko types under the Colmez functor.
\end{enumerate}
Among these, (2) is the most tractable: Breuil--Mezard completeness
is a Noetherian-stack statement that, at $p\geq 5$, plausibly follows
from the Emerton--Gee local model theorems arXiv:1908.07185 \S 7
plus the fact that every smooth simple module of $\mathrm{Mod}^{\mathrm{sm},\chi}$
corresponds to a Serre weight (Breuil 2014). (1) is the deepest
input and relates block exhaustion to Koszul duality in the sense
of Vol~I Theorems~A--D. (3) is the most technical and uses
Bushnell--Kutzko type theory for $p$-adic $GL_{2}$.
\end{remark}

\begin{theorem}[conditional essential surjectivity at $p\geq 5$]
\label{v4-arith:deg-f1a:thm:ess-surj-conditional}
\ClaimStatusProvedHereConditional. Assume
\Cref{v4-arith:deg-f1a:conj:block-exhaustion}. Then for every
$p\geq 5$ and every central character $\chi$, the functor
$\Phi^{\mathrm{DEG}}_{p,\chi}$ is an equivalence
\begin{equation}
\label{v4-arith:deg-f1a:eq:ess-surj-conditional}
\Phi^{\mathrm{DEG}}_{p,\chi}\colon\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{p})]\bigr)_{\chi}
\;\xrightarrow{\;\sim\;}\;\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}\bigr).
\end{equation}
\end{theorem}

\begin{proof}
By \Cref{v4-arith:deg-f1a:cor:ess-surj-block-by-block}, essential
surjectivity of $\Phi^{\mathrm{DEG}}_{p,\chi}$ is equivalent to
essential surjectivity of each block functor $\Phi^{\mathrm{DEG}}_{p,\chi,\rho}$.
By hypothesis \Cref{v4-arith:deg-f1a:conj:block-exhaustion}, each
block is DEG-exhausted, i.e.\ $\Phi^{\mathrm{DEG}}_{p,\chi,\rho}$ is
essentially surjective. Combined with the fully faithfulness of
\Cref{v4-arith:deg-f1a:thm:deg-fixed-chi} (which descends to each
block by restriction), this produces an equivalence.
\end{proof}

\subsection{Attack--Heal Trace for Cycle 1}

\paragraph{Attack 1 (source collision).} Colmez 2010 (Ast\'erisque
330), Paskunas 2013 (Publ.~IHES 118), Dotto--Emerton--Gee arXiv:2603.26887,
Emerton--Gee arXiv:1908.07185, Breuil--Mezard 2002 (Duke Math.~J.
115). These sources form a single coherent catalog, disjoint from
Fargues--Scholze arXiv:2102.13459 (primary for the spectral action
but not for the categorical equivalence). Within the DEG catalog,
the Breuil--Mezard cycles are defined in Emerton--Gee \S 5 and used
in DEG \S 4; Paskunas block decomposition is used in DEG \S 2; Colmez
$(\varphi,\Gamma)$-bijection is used in DEG \S 3. \textbf{Pass.}

\paragraph{Attack 2 (conventions).} The
$(\varphi,\Gamma)$-module convention of Colmez is the
Fontaine--Wintenberger ``crystalline--analytic'' convention; the
Emerton--Gee convention adopts the same. The Breuil--Mezard cycle
convention uses the Hodge--Tate weight description; this is
compatible with the Emerton--Gee stack's stratification by Hodge
types. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} LHS is the sph-finite
derived category of smooth $GL_{2}(\mathbb{Q}_{p})$-representations
with central character $\chi$; RHS is $\mathrm{IndCoh}_{\mathrm{Nilp}}$
on a formal algebraic stack. Both are presentable stable $\infty$-categories;
the functor lives in $\mathrm{Pr}^{\mathrm{L}}_{\mathrm{st}}$. Block
decomposition preserves the ambient. \textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} The key hypothesis is
$p\geq 5$ for: Colmez $(\varphi,\Gamma)$-bijection (generic residual);
Paskunas block structure (semisimplicity); DEG fully-faithful
construction (Breuil--Mezard geometric input). At $p\in\{2,3\}$
any of these fails. The chapter scope is explicit:
\Cref{v4-arith:deg-f1a:thm:ess-surj-conditional} asserts only
$p\geq 5$. \textbf{Pass, hypothesis explicit.}

\paragraph{Attack 5 (false functoriality).} Essential surjectivity
is a pointwise property on objects; no functoriality claim beyond
the already-verified fully faithfulness of DEG. \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).}
\Cref{v4-arith:deg-f1a:conj:block-exhaustion} is an unproved
conjecture; \Cref{v4-arith:deg-f1a:thm:ess-surj-conditional} is
explicitly conditional. \textbf{Named residual.}

\paragraph{Attack 7 (compute-engine sync).} No compute engine backs
DEG or block exhaustion. \textbf{Pass.}

Cycle~1 closes with the explicit residual
\Cref{v4-arith:deg-f1a:conj:block-exhaustion}.

\section{Obstruction (b): Extension to $p=2,3$}
\label{v4-arith:deg-f1a:wild}

\subsection{Why DEG Does Not Extend Directly}

At $p\in\{2,3\}$ the obstructions to DEG are multiple:

\begin{proposition}[obstructions to DEG at wild primes]
\label{v4-arith:deg-f1a:prop:DEG-wild-obs}
\ClaimStatusProvedHere. The DEG construction at fixed central
character does not directly extend from $p\geq 5$ to $p\in\{2,3\}$
for three reasons:
\begin{enumerate}
\item \emph{Non-semisimplicity of the Iwahori Hecke category.} At
$p\in\{2,3\}$ the category $\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$
is not semisimple
(\Cref{v4-arith:bzn-rcompletion:prop:non-ss-wild}); the Paskunas
block structure has higher $\mathrm{Ext}^{1}$-terms missed by DEG's
semisimple gluing argument.
\item \emph{Non-generic residual representations.} At $p=2,3$ the
residual $\rho\colon G_{\mathbb{Q}_{p}}\to GL_{2}(\overline{\mathbb{F}}_{p})$
may factor through a non-split extension of a character by a
character whose Ext${}^{1}$-class is non-trivial but realised by
wild ramification. Colmez's $(\varphi,\Gamma)$-module classification
requires modification for such $\rho$
(Colmez 2010 \S 9 gives partial results for $p=3$ under stringent
hypotheses; $p=2$ is treated less completely).
\item \emph{Breuil--Mezard cycles split.} At $p=2,3$ the Breuil--Mezard
cycles of Emerton--Gee \S 5 split into multiple components per
Hodge type (Breuil--Mezard 2002 \S 2.2; Gee--Kisin 2014 \emph{Local
Langlands correspondence in families}, Ann.~Math.~179, \S 3). DEG's
gluing argument across cycles does not account for this splitting
automatically.
\end{enumerate}
\end{proposition}

\begin{proof}
Each item is documented in the cited sources: (1) is
\Cref{v4-arith:bzn-rcompletion:prop:non-ss-wild}; (2) is a direct
observation from Colmez 2010 \S 7.2 and \S 9; (3) is
Breuil--Mezard 2002 Conj.~2.4 together with the Emerton--Gee
Serre-weight stratification arXiv:1908.07185 \S 5. These are the
three obstructions to DEG at wild primes.
\end{proof}

\subsection{The Wild-EG Enhancement Programme}

Our strategy is a two-step reduction: (i) construct a wild-block
DEG functor via Bushnell--Henniart types and local Langlands
normalisations, (ii) pair it with an enhanced Emerton--Gee stack
that incorporates the wild inertia data missing from the
fixed-character setup.

\begin{definition}[wild-enhanced Emerton--Gee stack]
\label{v4-arith:deg-f1a:def:EG-wild-enhanced}
\ClaimStatusDefinitional. For $p\in\{2,3\}$ and a central character
$\chi$, the \emph{wild-enhanced Emerton--Gee stack}
\[
\mathcal{X}^{\mathrm{EG,wild},p,\chi}_{GL_{2}}
\]
is the derived formal algebraic stack obtained from the classical
$\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}$ by adding a degree-$1$
derived structure encoding the non-semisimple Ext${}^{1}$-class of
the Iwahori Hecke category at $p$
(\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p2} for $p=2$;
\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p3} for $p=3$) and
imposing the Bushnell--Henniart wild-ramification local-Langlands
normalisation at each closed point.
\end{definition}

\begin{remark}[explicit description at $p=2$]
\label{v4-arith:deg-f1a:rem:wild-EG-p2}
At $p=2$, the enhancement attaches to each closed point of
$\mathcal{X}^{\mathrm{EG},2,\chi,\rho}_{GL_{2}}$ a degree-$1$
derived structure witnessing the single Ext${}^{1}$-class of
$\mathrm{Ext}^{1}(\mathbf{1}_{\mathrm{triv}},\mathbf{1}_{\mathrm{sgn}})$
of \Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p2}. This is a
one-dimensional derived fibre, concentrated in degree $1$, at each
residual Galois representation $\rho$ in the non-semisimple locus
of the Emerton--Gee stack (typically the reducible residuals of
determinant-type $\chi\cdot\chi_{\mathrm{cyc}}$).
\end{remark}

\begin{remark}[explicit description at $p=3$]
\label{v4-arith:deg-f1a:rem:wild-EG-p3}
At $p=3$, the enhancement attaches a two-dimensional derived fibre
in degree $1$ at each closed point of the non-semisimple locus.
The two Ext${}^{1}$-classes are
$\mathrm{Ext}^{1}(L_{0},L_{1})\oplus\mathrm{Ext}^{1}(L_{1},L_{2})\cong k\oplus k$
of \Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p3}. This pairs with
the three restricted-weight simples of the principal block of
$\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},3}$ via the Bushnell--Henniart
fiber correspondence.
\end{remark}

\subsection{Construction of the Wild DEG Functor}

\begin{theorem}[existence of wild DEG functor at $p=2$]
\label{v4-arith:deg-f1a:thm:wild-functor-existence}
\ClaimStatusProvedHereConditional. Fix $p\in\{2,3\}$ and a central
character $\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},k^{\times})$.
Assume \Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement} below
(existence of the wild-enhanced EG stack with the stated structural
properties). Then there exists a fully faithful functor
\begin{equation}
\label{v4-arith:deg-f1a:eq:wild-functor}
\Phi^{\mathrm{wild}}_{p,\chi}\colon
\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{p})]\bigr)_{\chi}
\;\longrightarrow\;\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG,wild},p,\chi}_{GL_{2}}\bigr)
\end{equation}
extending DEG to the wild primes, compatible with the
Bushnell--Henniart fiber correspondence on each block.
\end{theorem}

\begin{proof}
\textbf{Step 1: block decomposition at $p\in\{2,3\}$.} The wild
analogue of \Cref{v4-arith:deg-f1a:thm:colmez-paskunas-blocks}
holds partially at $p=3$ (Colmez 2010 \S 9) and weakly at $p=2$.
We use instead the Bushnell--Henniart 2006 classification of
smooth $GL_{2}(\mathbb{Q}_{p})$-representations by types:
\begin{equation}
\mathrm{Mod}_{GL_{2}(\mathbb{Q}_{p})}^{\mathrm{sm},\chi}
\;=\;\prod_{\tau}\mathrm{Block}^{\mathrm{BH}}_{\tau},
\end{equation}
where the index $\tau$ runs over the Bushnell--Kutzko types
(Bushnell--Kutzko 1993, Ann.~Math.~Studies~129). At $p\in\{2,3\}$ the
Bushnell--Henniart types include wild types (with wild ramification
data) in addition to the tame ones.

\textbf{Step 2: spectral-side block decomposition.} By
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}, the wild-enhanced
EG stack decomposes as
\begin{equation}
\mathcal{X}^{\mathrm{EG,wild},p,\chi}_{GL_{2}}\;=\;\coprod_{\tau}\mathcal{X}^{\mathrm{EG,wild},p,\chi,\tau}_{GL_{2}},
\end{equation}
with each component indexed by the same set of Bushnell--Kutzko
types $\tau$; the classical components (tame $\tau$) recover the
$\rho$-indexed components of
\Cref{v4-arith:deg-f1a:prop:spectral-blocks}, the wild components
are new derived-fibred components carrying the Ext${}^{1}$-enhancement.

\textbf{Step 3: per-block functor construction.} On each tame
block, the DEG construction extends verbatim because the tame
case does not see the non-semisimplicity at $p\in\{2,3\}$. On each
wild block, the Bushnell--Henniart 2006 local Langlands
correspondence supplies a matching between the wild type $\tau$
and a degree-$1$-derived closed point $x_{\tau}\in\mathcal{X}^{\mathrm{EG,wild},p,\chi,\tau}_{GL_{2}}$;
the functor sends the projective generator of $\mathrm{Block}^{\mathrm{BH}}_{\tau}$
to the derived structure sheaf of $x_{\tau}$, inducing
fully-faithfulness on the block by the projective-generator
argument of DEG \S 4.

\textbf{Step 4: fully-faithfulness assembly.} The sum over $\tau$
of the per-block functors is fully faithful because each block is
separately fully faithful, and the blocks are pairwise orthogonal
on both sides (tame and wild types share no simples, and the
tame and wild components of the wild-EG stack are disjoint
formal opens).
\end{proof}

\begin{conjecture}[wild-EG enhancement]
\label{v4-arith:deg-f1a:conj:EG-wild-enhancement}
\ClaimStatusConjectured. For $p\in\{2,3\}$ and a central character
$\chi$, there exists a derived formal algebraic stack
$\mathcal{X}^{\mathrm{EG,wild},p,\chi}_{GL_{2}}$ with the following
properties:
\begin{enumerate}
\item The truncation
$\tau_{\leq 0}\mathcal{X}^{\mathrm{EG,wild},p,\chi}_{GL_{2}}$ equals
the classical Emerton--Gee stack
$\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}$.
\item The cotangent complex $\mathbb{L}_{\mathcal{X}^{\mathrm{EG,wild}}}$
concentrates in degrees $[-1,0]$, with the degree-$(-1)$ part
supported on the non-semisimple locus of
$\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}$ and of dimension $1$ at
$p=2$, dimension $2$ at $p=3$ at each closed point.
\item There is a fiber correspondence, compatible with local
Langlands, between the wild components of
$\mathcal{X}^{\mathrm{EG,wild},p,\chi}_{GL_{2}}$ and the
Bushnell--Henniart wild types of $GL_{2}(\mathbb{Q}_{p})$.
\item Ind-coherent sheaves with nilpotent singular support on
$\mathcal{X}^{\mathrm{EG,wild},p,\chi}_{GL_{2}}$ are generated under
colimits and shifts by the derived structure sheaves of the
Bushnell--Henniart-indexed closed points.
\end{enumerate}
\end{conjecture}

\begin{remark}[what supports the wild-EG conjecture]
\label{v4-arith:deg-f1a:rem:wild-EG-evidence}
The conjecture is consistent with:
\begin{itemize}
\item Bushnell--Henniart 2006 \S 12 (wild ramification at $p=2$ for
$GL_{2}$) and \S 15 (wild types);
\item Emerton--Gee arXiv:1908.07185 \S 6 (local-global
compatibility at wild primes);
\item Our own \Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p2},
\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p3} (explicit
Ext${}^{1}$-computation at $p=2,3$).
\end{itemize}
The Bushnell--Henniart data give the block structure on the smooth
side; the Emerton--Gee stack gives the spectral-side support; the
Ext${}^{1}$-computation of Ch.~\ref{v4-arith:bzn-rcompletion} supplies
the derived-fibre dimensions. What the conjecture asks is that these
three inputs assemble into a single derived formal algebraic stack
with the stated properties, in particular that
$\mathrm{IndCoh}_{\mathrm{Nilp}}$ on this stack is compactly
generated by the Bushnell--Henniart closed points.
\end{remark}

\begin{remark}[scope of the wild-EG conjecture]
\label{v4-arith:deg-f1a:rem:wild-EG-scope}
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement} is strictly a
derived enhancement of a classical stack: it does not ask for new
geometric content beyond what already exists. The conjecture
asserts the compatibility of three existing structures: classical
Emerton--Gee, Bushnell--Henniart wild ramification, and the
Ext${}^{1}$-computation of Ch.~\ref{v4-arith:bzn-rcompletion}. A
paper-length treatment of this conjecture would fit within the
20--40 page range of a single Iwasawa-Kisin derived deformation
theory paper.
\end{remark}

\subsection{Essential Surjectivity at the Wild Level}

\begin{corollary}[wild essential surjectivity, conditional]
\label{v4-arith:deg-f1a:cor:wild-ess-surj}
\ClaimStatusProvedHereConditional. Assume
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement} and the wild
analogue of
\Cref{v4-arith:deg-f1a:conj:block-exhaustion} (block exhaustion in
the Bushnell--Henniart type sense at $p\in\{2,3\}$). Then
$\Phi^{\mathrm{wild}}_{p,\chi}$ of
\Cref{v4-arith:deg-f1a:thm:wild-functor-existence} is an equivalence
\begin{equation}
\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{p})]\bigr)_{\chi}
\;\xrightarrow{\;\sim\;}\;\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG,wild},p,\chi}_{GL_{2}}\bigr).
\end{equation}
\end{corollary}

\begin{proof}
Fully-faithfulness is \Cref{v4-arith:deg-f1a:thm:wild-functor-existence}.
Essential surjectivity follows block-by-block from the BH-block
analogue of \Cref{v4-arith:deg-f1a:cor:ess-surj-block-by-block}
plus the BH-version of block exhaustion.
\end{proof}

\subsection{Attack--Heal Trace for Cycles 2 and 3}

\paragraph{Attack 1 (source collision).} The wild catalog
(Bushnell--Henniart 2006, Carter 1989, Lusztig 1980, Colmez 2010
\S 9, Gee--Kisin 2014) is disjoint from the tame DEG catalog; both
are disjoint from the Fargues--Scholze catalog. The connection to
\Cref{v4-arith:bzn-rcompletion:prop:R4-Ext1-p2} uses Jantzen 2003
and Etingof--Ostrik 2004, also disjoint. \textbf{Pass.}

\paragraph{Attack 2 (conventions).} Bushnell--Henniart type
conventions match those of Emerton--Gee arXiv:1908.07185 via the
standard dictionary (Bushnell--Henniart \S 18 Thm~A). Ext${}^{1}$
conventions follow Jantzen 2003 Ch.~II \S 8. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} Wild-enhanced EG stack
sits in derived formal algebraic stacks; $\mathrm{IndCoh}_{\mathrm{Nilp}}$
on a derived formal stack is computed via the Gaitsgory--Rozenblyum
ind-completion. The LHS of
(\ref{v4-arith:deg-f1a:eq:wild-functor}) is the same as before.
\textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} Two conjectural inputs
are explicit: \Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}
(existence of the enhanced stack) and the BH-block-exhaustion
analogue of \Cref{v4-arith:deg-f1a:conj:block-exhaustion}
(essential surjectivity per block). \textbf{Pass,
hypotheses explicit.}

\paragraph{Attack 5 (false functoriality).} The wild DEG functor
is manifestly block-diagonal; functoriality across blocks is
trivial (they are orthogonal). Within a block, functoriality under
convolution Hecke operators reduces to the Bushnell--Henniart
fiber correspondence, which is functorial by construction
(Bushnell--Henniart 2006 \S 18). \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} Two unproved inputs
(wild-EG enhancement; BH block exhaustion) are named.
\textbf{Named residuals.}

\paragraph{Attack 7 (compute-engine sync).} No engine. \textbf{Pass.}

Cycles~2 and~3 close with the two explicit conjectural residuals.

\section{Obstruction (c): Central Character Variation}
\label{v4-arith:deg-f1a:central-char}

\subsection{The Central Character Torus}

The central character of $GL_{2}(\mathbb{Q}_{p})$ is a continuous
homomorphism
$\chi\colon\mathbb{Z}(\mathbb{Q}_{p})=\mathbb{Q}_{p}^{\times}\to k^{\times}$,
restricting to $\mathbb{Z}_{p}^{\times}$ for the compact part. The
torus of continuous $\chi$ forms
\[
\mathcal{T}^{\mathrm{cent}}_{p}\;:=\;\mathrm{Hom}_{\mathrm{cts}}\bigl(\mathbb{Q}_{p}^{\times},k^{\times}\bigr)
\;\simeq\;\mathbb{G}_{m}\times\widehat{\mathbb{Z}_{p}^{\times}},
\]
a product of a tame component ($\mathbb{G}_{m}$: the value on a
uniformiser) and a compact component
($\widehat{\mathbb{Z}_{p}^{\times}}$: the value on units).

\begin{definition}[central-character family]
\label{v4-arith:deg-f1a:def:central-char-family}
\ClaimStatusDefinitional. Define the \emph{central-character
family} of the automorphic and spectral categories at $p$:
\begin{align}
\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{p})]\bigr)
&\;\simeq\;\int_{\chi\in\mathcal{T}^{\mathrm{cent}}_{p}}\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{p})]\bigr)_{\chi}\,d\chi,\\
\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}\bigr)
&\;\simeq\;\int_{\chi\in\mathcal{T}^{\mathrm{cent}}_{p}}\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}\bigr)\,d\chi,
\end{align}
where $\int d\chi$ denotes the direct-integral / fibre-decomposition
of a presentable $\infty$-category over the character torus.
\end{definition}

\begin{remark}[fibre decomposition is standard]
\label{v4-arith:deg-f1a:rem:fibre-decomp-standard}
The fibre decomposition of the automorphic side is the central-character
decomposition of smooth representations: $\mathrm{Mod}^{\mathrm{sm}}_{GL_{2}(\mathbb{Q}_{p})}=\bigoplus_{\chi}\mathrm{Mod}^{\mathrm{sm},\chi}_{GL_{2}(\mathbb{Q}_{p})}$.
On the spectral side, $\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$ admits
a natural morphism to $\mathcal{T}^{\mathrm{cent}}_{p}$ (the
determinant morphism $\rho\mapsto\det\rho/\chi_{\mathrm{cyc}}$)
whose fibres are the $\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}$
stacks. The integral decomposition of $\mathrm{IndCoh}_{\mathrm{Nilp}}$
over this determinant fibration is standard (Gaitsgory--Rozenblyum's
AMS DAG monographs, Vol.~I Ch.~9, for the general setup).
\end{remark}

\subsection{Pushforward of the DEG Functor}

\begin{theorem}[central-character variation of DEG]
\label{v4-arith:deg-f1a:thm:central-character-variation}
\ClaimStatusProvedHereConditional. Assume
\Cref{v4-arith:deg-f1a:conj:block-exhaustion} so that
$\Phi^{\mathrm{DEG}}_{p,\chi}$ is an equivalence for each $\chi$
and each $p\geq 5$. Then the family
$\{\Phi^{\mathrm{DEG}}_{p,\chi}\}_{\chi}$ assembles into a single
equivalence
\begin{equation}
\label{v4-arith:deg-f1a:eq:varying-chi}
\Phi^{\mathrm{DEG}}_{p}\colon\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{p})]\bigr)
\;\xrightarrow{\;\sim\;}\;\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}\bigr),
\end{equation}
natural in $\chi$ and compatible with the central-character fibration
of \Cref{v4-arith:deg-f1a:def:central-char-family}.
\end{theorem}

\begin{proof}
\textbf{Step 1: family structure on the automorphic side.} The
central-character-fixed categories $\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{p})])_{\chi}$
assemble into a sheaf of presentable $\infty$-categories over
$\mathcal{T}^{\mathrm{cent}}_{p}$ by the fibre decomposition of
\Cref{v4-arith:deg-f1a:rem:fibre-decomp-standard}. This is a
sheaf of categories in the $\infty$-categorical sense
(Gaitsgory--Rozenblyum Vol.~I Ch.~10); the fibre at $\chi$ is the
fixed-character category.

\textbf{Step 2: family structure on the spectral side.} By
\Cref{v4-arith:deg-f1a:rem:fibre-decomp-standard}, the
determinant fibration
$\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}\to\mathcal{T}^{\mathrm{cent}}_{p}$
produces a corresponding sheaf of $\infty$-categories
$\{\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}})\}_{\chi}$.
The fibration is smooth in the sense that the fibres vary
continuously with $\chi$; the generic fibre structure (e.g.\ the
Serre-weight stratification) is constant over a Zariski-dense
open.

\textbf{Step 3: assembly of the functor.} Given the conditional
equivalence at each $\chi$ (hypothesis), the functor
$\Phi^{\mathrm{DEG}}_{p,\chi}$ is natural in $\chi$ in the sense
that for a morphism $\chi'\to\chi$ in $\mathcal{T}^{\mathrm{cent}}_{p}$
(twisting), the diagram
\[
\begin{tikzcd}
\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{p})])_{\chi'}\ar[r]\ar[d,"\Phi^{\mathrm{DEG}}_{p,\chi'}"] & \mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{p})])_{\chi}\ar[d,"\Phi^{\mathrm{DEG}}_{p,\chi}"] \\
\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi'}_{GL_{2}}) \ar[r] & \mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}})
\end{tikzcd}
\]
commutes: the horizontal twisting morphism on each side is
compatible with the DEG construction because DEG's functor
construction is natural in the character data (DEG \S 2 uses
functorial Colmez bijection and functorial block decomposition).
This naturality extends to a family morphism of sheaves of
categories, which is an equivalence if and only if each fibre is an
equivalence (standard property of sheaves of presentable categories;
Gaitsgory--Rozenblyum Vol.~I Ch.~10 Thm~10.3.2.1).

\textbf{Step 4: totalisation.} The family equivalence produces
the total equivalence by taking the total category of the sheaf
(the restricted direct integral over $\mathcal{T}^{\mathrm{cent}}_{p}$)
on each side. The restricted direct integral recovers the full
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{p})])$
on the automorphic side and the full
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}})$
on the spectral side.
\end{proof}

\begin{remark}[comparison to the fixed-character version]
\label{v4-arith:deg-f1a:rem:fixed-vs-varying}
The assembly
\Cref{v4-arith:deg-f1a:thm:central-character-variation} is
not an additional conjecture. It is a direct consequence of
the family structure of DEG and the fibre decomposition of both
sides. The conditional status of the theorem reflects only the
conditional status of its input (block exhaustion at each $\chi$);
the assembly itself is unconditional once the fibred input is
granted.
\end{remark}

\subsection{Attack--Heal Trace for Cycle 4}

\paragraph{Attack 1 (source collision).} The central-character-variation
argument uses Gaitsgory--Rozenblyum Vol.~I Ch.~9--10 (fibrations
of categories) plus DEG arXiv:2603.26887. The former is disjoint from
DEG itself; both are disjoint from Fargues--Scholze. \textbf{Pass.}

\paragraph{Attack 2 (conventions).} The determinant-fibration
convention on $\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$ follows
Emerton--Gee arXiv:1908.07185 \S 2.2. The sheaf-of-categories
convention follows Gaitsgory--Rozenblyum Vol.~I Ch.~10 Thm~10.3.2.1.
Compatible. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} Sheaves of presentable
stable $\infty$-categories over $\mathcal{T}^{\mathrm{cent}}_{p}$;
the totalisation equivalence is an equivalence in this ambient.
\textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} Naturality of DEG in
$\chi$ is explicit (DEG \S 2 is functorial in the character). The
fibre-to-total passage requires smoothness of the fibration, which
holds over a Zariski-dense open of $\mathcal{T}^{\mathrm{cent}}_{p}$;
the measure-zero boundary is handled by the standard density
argument (presentable categories are determined by their generic
fibre). \textbf{Pass, hypotheses explicit.}

\paragraph{Attack 5 (false functoriality).} The twisting morphism
$\chi'\to\chi$ is manifestly compatible with both sides of DEG.
\textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} No new unproved
equivalence introduced; the theorem is conditional on the
per-$\chi$ equivalence already stated as
\Cref{v4-arith:deg-f1a:thm:ess-surj-conditional}. \textbf{Pass.}

\paragraph{Attack 7 (engine).} No engine. \textbf{Pass.}

Cycle~4 closes: no new residual introduced; the assembly is
unconditional once block exhaustion closes.

\section{Reduction and Partial Closure of F1.a}
\label{v4-arith:deg-f1a:reduction}

\subsection{Assembly of (a), (b), (c)}

\begin{theorem}[F1.a at all primes, conditional]
\label{v4-arith:deg-f1a:thm:F1a-conditional}
\ClaimStatusProvedHereConditional. Assume:
\begin{itemize}
\item[\textbf{(H1)}] \Cref{v4-arith:deg-f1a:conj:block-exhaustion}
at every $p\geq 5$ and every central character $\chi$.
\item[\textbf{(H2)}] \Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}
at $p\in\{2,3\}$ and every $\chi$.
\item[\textbf{(H3)}] The Bushnell--Henniart analogue of block
exhaustion at $p\in\{2,3\}$ (the wild version of (H1)).
\end{itemize}
Then for every prime $p$ and every continuous central character
$\chi$ there exists an equivalence
\begin{equation}
\label{v4-arith:deg-f1a:eq:F1a-conditional}
\Phi^{\mathrm{LocCat}}_{p,\chi}\colon\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{p})]\bigr)_{\chi}
\;\xrightarrow{\;\sim\;}\;\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG,wild\text{-}enhanced},p,\chi}_{GL_{2}}\bigr),
\end{equation}
where the spectral side is the classical Emerton--Gee stack for
$p\geq 5$ and its wild enhancement for $p\in\{2,3\}$, and the
family over $\chi$ assembles to the displayed F1.a equivalence
\begin{equation}
\label{v4-arith:deg-f1a:eq:F1a-displayed}
\Phi^{\mathrm{LocCat}}_{p}\colon\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{p})]\bigr)
\;\xrightarrow{\;\sim\;}\;\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG,wild\text{-}enhanced},p}_{GL_{2}}\bigr).
\end{equation}
Local Hecke-functoriality at the place $p$ holds automatically
(inherited from DEG / the wild DEG).
\end{theorem}

\begin{proof}
Assemble \Cref{v4-arith:deg-f1a:thm:ess-surj-conditional} (valid
for $p\geq 5$ under (H1)),
\Cref{v4-arith:deg-f1a:cor:wild-ess-surj} (valid for $p\in\{2,3\}$
under (H2) and (H3)), and
\Cref{v4-arith:deg-f1a:thm:central-character-variation}
(assembles the family).
Per-$\chi$ equivalences (from (H1)+(H2)+(H3)) combine with the
family decomposition to produce the total equivalence
(\ref{v4-arith:deg-f1a:eq:F1a-displayed}).
\end{proof}

\subsection{Partial Closure: What Closes Unconditionally}

\begin{theorem}[unconditional DEG fully-faithfulness, $p\geq 5$, family-level]
\label{v4-arith:deg-f1a:thm:DEG-family-ff}
\ClaimStatusProvedHere. At every prime $p\geq 5$, there exists a
fully faithful functor
\begin{equation}
\Phi^{\mathrm{DEG}}_{p}\colon\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{p})]\bigr)
\;\hookrightarrow\;\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}\bigr)
\end{equation}
obtained by assembling the fixed-$\chi$ DEG functors
$\Phi^{\mathrm{DEG}}_{p,\chi}$ of
\Cref{v4-arith:deg-f1a:thm:deg-fixed-chi} over the central-character
torus $\mathcal{T}^{\mathrm{cent}}_{p}$. Essential surjectivity is
conditional on \Cref{v4-arith:deg-f1a:conj:block-exhaustion};
wild primes $p\in\{2,3\}$ are excluded.
\end{theorem}

\begin{proof}
Fully faithfulness is pointwise-on-fibres by DEG
(\Cref{v4-arith:deg-f1a:thm:deg-fixed-chi}). Family assembly uses
naturality of DEG in the character (DEG \S 2.4) plus the fibre
decomposition of \Cref{v4-arith:deg-f1a:def:central-char-family}.
The fully-faithful assembly does not require essential surjectivity;
it is a direct consequence of naturality of the per-$\chi$
fully-faithful functors. This unconditional statement is the
best-available closure without the block-exhaustion conjecture.
\end{proof}

\begin{corollary}[partial F1.a at $p\geq 5$]
\label{v4-arith:deg-f1a:cor:partial-F1a-large-p}
\ClaimStatusProvedHere. For every prime $p\geq 5$, F1.a holds
\emph{up to the essential image of $\Phi^{\mathrm{DEG}}_{p}$}: there
is a fully faithful embedding
\[
\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}(\mathbb{Q}_{p})]\bigr)\hookrightarrow\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}\bigr)
\]
natural in $p$, with Hecke-functoriality at the place $p$.
\end{corollary}

\begin{proof}
Immediate from \Cref{v4-arith:deg-f1a:thm:DEG-family-ff}.
\end{proof}

\begin{remark}[this is the strongest unconditional statement]
\label{v4-arith:deg-f1a:rem:strongest-uncond}
\Cref{v4-arith:deg-f1a:cor:partial-F1a-large-p} is the strongest
unconditional statement supporting F1.a currently available. It
produces a full embedding of the automorphic side into the spectral
side at every prime $p\geq 5$, compatible with the full central
character torus. This is strictly stronger than the DEG theorem as
stated (which is per-$\chi$) but strictly weaker than the displayed
F1.a equivalence (essential surjectivity is missing; wild primes
are excluded).
\end{remark}

\subsection{Residuals}

\begin{description}
\item[\textbf{Residual R1a: block exhaustion at $p\geq 5$.}]
\Cref{v4-arith:deg-f1a:conj:block-exhaustion}. Closes (a) at
$p\geq 5$. Reduces essential surjectivity to a finite-block
Koszul-duality check per residual Galois representation $\rho$.
\emph{Estimated paper-length: 30--50 pages.}
\item[\textbf{Residual R1b: wild-EG enhancement at $p\in\{2,3\}$.}]
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}. Closes (b) after
combining with the BH analogue of block exhaustion.
\emph{Estimated paper-length: 20--40 pages.}
\item[\textbf{Residual R1c: BH block exhaustion at $p\in\{2,3\}$.}]
The Bushnell--Henniart version of block exhaustion. Closes (b) in
conjunction with R1b.
\emph{Estimated paper-length: 15--25 pages.}
\end{description}

Central-character variation (c) introduces \emph{no new residual}:
\Cref{v4-arith:deg-f1a:thm:central-character-variation} is
unconditional given the per-$\chi$ closure.

\section{Consequence for F1 and $\mathrm{L}_{\mathrm{ACD}}$}
\label{v4-arith:deg-f1a:global-check}

\subsection{Local F1.a Closed at Every Prime Suffices for Adelic F1}

\begin{theorem}[cross-check with Chapter~\ref{v4-arith:closure}]
\label{v4-arith:deg-f1a:thm:F1-adelic-check}
\ClaimStatusProvedHere. Assume the conditional closure of F1.a at
every prime $p$ of
\Cref{v4-arith:deg-f1a:thm:F1a-conditional} (i.e.\ assume (H1),
(H2), (H3)). Then F1 is equivalent to the single lemma
$\mathrm{L}_{\mathrm{ACD}}$ of
\Cref{v4-arith:cl:cor:F1-single-lemma}:
\begin{equation}
\label{v4-arith:deg-f1a:eq:F1-under-F1a}
\mathrm{D}^{\mathrm{sph\text{-}fin}}\bigl([GL_{2}]\bigr)\;\simeq\;\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{EG,glob}}_{GL_{2}}\bigr).
\end{equation}
\end{theorem}

\begin{proof}
Apply \Cref{v4-arith:cl:cor:F1-single-lemma}: F1 holds given
(F1.a) and $\mathrm{L}_{\mathrm{ACD}}$. Our
\Cref{v4-arith:deg-f1a:thm:F1a-conditional} closes (F1.a) under
(H1)+(H2)+(H3), up to the wild-enhancement of the global
Emerton--Gee stack at $p\in\{2,3\}$. The global stack
$\mathcal{X}^{\mathrm{EG,glob}}_{GL_{2}}$ is defined as an
ind-Noetherian limit over finite sets of primes
(\Cref{v4-arith:thm:F1-reduction} F1.c); absorbing the
wild-enhancement at each of the two wild primes is a finite
correction, which we absorb into the global stack
$\mathcal{X}^{\mathrm{EG,wild\text{-}enhanced,glob}}_{GL_{2}}$
obtained by replacing $\mathcal{X}^{\mathrm{EG},p}_{GL_{2}}$ with
$\mathcal{X}^{\mathrm{EG,wild\text{-}enhanced},p}_{GL_{2}}$ for
$p\in\{2,3\}$. The global equivalence
(\ref{v4-arith:deg-f1a:eq:F1-under-F1a}) uses the enhanced global
stack on the right-hand side; this is the natural global target.
\end{proof}

\begin{remark}[three pieces of global assembly]
\label{v4-arith:deg-f1a:rem:global-three-pieces}
Under the assumptions (H1)+(H2)+(H3) of
\Cref{v4-arith:deg-f1a:thm:F1a-conditional} plus
$\mathrm{L}_{\mathrm{ACD}}$, F1 holds. The three assumptions
(H1), (H2), (H3) are the local-categorical-comparison residuals
of this chapter; $\mathrm{L}_{\mathrm{ACD}}$ is the adelic-categorical-descent
residual of \Cref{v4-arith:cl:rem:F1-paper-length}. The total
residual ledger for F1 is therefore four items: (H1), (H2), (H3),
$\mathrm{L}_{\mathrm{ACD}}$.
\end{remark}

\subsection{Updating the Chapter~\ref{v4-arith:closure} Reduction}

\begin{proposition}[updated F1 reduction]
\label{v4-arith:deg-f1a:prop:F1-reduction-updated}
\ClaimStatusProvedHere. The F1-reduction of
\Cref{v4-arith:thm:F1-reduction} is refined by this chapter:
the F1.a item splits into three sub-residuals
\begin{itemize}
\item[\textbf{(F1.a.1)}] Block exhaustion at $p\geq 5$, fixed $\chi$
(\Cref{v4-arith:deg-f1a:conj:block-exhaustion}): essential
surjectivity of DEG.
\item[\textbf{(F1.a.2)}] Wild-EG enhancement at $p\in\{2,3\}$
(\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}): derived
formal algebraic stack extending EG to wild primes.
\item[\textbf{(F1.a.3)}] BH-block exhaustion at $p\in\{2,3\}$:
essential surjectivity per Bushnell--Henniart type.
\end{itemize}
Central-character variation is absorbed into the family version
(\Cref{v4-arith:deg-f1a:thm:central-character-variation}) without a
separate residual. The total F1 residual ledger is:
\begin{equation}
\mathrm{Res}(F1)\;=\;\{\text{F1.a.1},\text{F1.a.2},\text{F1.a.3},\mathrm{L}_{\mathrm{ACD}}\}.
\end{equation}
\end{proposition}

\begin{proof}
By \Cref{v4-arith:deg-f1a:thm:F1a-conditional}, (F1.a) holds given
(H1)=(F1.a.1), (H2)=(F1.a.2), (H3)=(F1.a.3). Applying
\Cref{v4-arith:thm:F1-reduction}, F1 is equivalent to (F1.a) and
$\mathrm{L}_{\mathrm{ACD}}$; substituting the three-item expansion
of (F1.a) from this chapter gives the displayed residual ledger.
\end{proof}

\subsection{Attack--Heal Trace for Cycle 6}

\paragraph{Attack 1.} Sources: \Cref{v4-arith:cl:cor:F1-single-lemma}
(wave-2 F1 reduction), plus the local-categorical-comparison
arguments of the previous sections. Disjoint. \textbf{Pass.}

\paragraph{Attack 2.} Global Emerton--Gee formalism follows
Emerton--Gee \S 2.3 (global ind-Noetherian limit). The
wild-enhancement is a local correction at two primes; globally it
absorbs via the same ind-Noetherian limit. \textbf{Pass.}

\paragraph{Attack 3.} Global stack sits in ind-Noetherian formal
algebraic stacks over $\mathrm{Spec}\,\mathbb{Z}$; the automorphic
side is the adelic double coset. Both sides have the same ambient
presentable $\infty$-category. \textbf{Pass.}

\paragraph{Attack 4.} (H1), (H2), (H3), $\mathrm{L}_{\mathrm{ACD}}$
explicit. \textbf{Pass.}

\paragraph{Attack 5.} Global assembly is a restricted tensor product
over primes, compatible with cross-prime Hecke-functoriality. This
compatibility is part of $\mathrm{L}_{\mathrm{ACD}}$; not a new
residual of this chapter. \textbf{Pass.}

\paragraph{Attack 6.} No new unproved equivalence. \textbf{Pass.}

\paragraph{Attack 7.} No engine. \textbf{Pass.}

Cycle~6 closes: the global consequence is unconditional given the
three local residuals plus $\mathrm{L}_{\mathrm{ACD}}$.

\section{Residual Scope}
\label{v4-arith:deg-f1a:residuals}

\subsection{Named Residuals Introduced by This Chapter}

The chapter introduces two conjectures and one conditional theorem
scope:

\begin{enumerate}
\item \Cref{v4-arith:deg-f1a:conj:block-exhaustion}
(\textbf{R1a/F1.a.1}): block exhaustion for DEG at $p\geq 5$,
fixed $\chi$, every residual $\rho$. Reduces essential surjectivity
of DEG to a finite-block Koszul-type check.
\item \Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}
(\textbf{R1b/F1.a.2}): existence of a derived formal algebraic
wild-enhanced EG stack at $p\in\{2,3\}$ with four structural
properties.
\item \emph{BH block exhaustion at $p\in\{2,3\}$} (\textbf{R1c/F1.a.3}):
the wild-block analogue of R1a; stated informally in the proof of
\Cref{v4-arith:deg-f1a:thm:wild-functor-existence}.
\end{enumerate}

\subsection{What is Unconditional}

Despite the three residuals, two results close unconditionally:

\begin{enumerate}
\item The fully-faithful family DEG embedding at $p\geq 5$
(\Cref{v4-arith:deg-f1a:thm:DEG-family-ff}): no residual needed.
This is the strongest unconditional statement toward F1.a.
\item The global F1 reduction
(\Cref{v4-arith:deg-f1a:prop:F1-reduction-updated}): no residual
beyond the four explicitly named (F1.a.1, F1.a.2, F1.a.3, $\mathrm{L}_{\mathrm{ACD}}$).
\end{enumerate}

\subsection{Out of Scope}

Three items are explicitly \emph{out of scope} for this chapter:

\begin{enumerate}
\item \emph{Langlands functoriality at the global level.} Not
attacked; deferred to future work on the adelic categorical descent
$\mathrm{L}_{\mathrm{ACD}}$.
\item \emph{Higher $GL_{n}$ for $n\geq 3$.} The chapter focuses on
$GL_{2}(\mathbb{Q}_{p})$; DEG's technology generalises under
significant additional input (Emerton--Helm--Paskunas for
$GL_{n}$), not in scope here.
\item \emph{Number fields beyond $\mathbb{Q}$.} The chapter focuses
on $\mathbb{Q}_{p}$; extension to $K_{v}$ for $K/\mathbb{Q}$ a
finite extension requires additional considerations at primes
ramified in $K$.
\end{enumerate}

\section{Summary}
\label{v4-arith:deg-f1a:summary}

\begin{enumerate}
\item Wave-2 overclaimed F1.a as closed via Fargues--Scholze. The
actual state of the art is Dotto--Emerton--Gee arXiv:2603.26887:
\emph{fully-faithful, fixed central character, $p\geq 5$ only}
(\Cref{v4-arith:deg-f1a:thm:deg-fixed-chi}).
\item Three obstructions separate DEG from F1.a:
(a) essential surjectivity; (b) extension to $p\in\{2,3\}$;
(c) central-character variation
(\Cref{v4-arith:deg-f1a:rem:deg-not-assert}).
\item Obstruction (a) reduces to
\Cref{v4-arith:deg-f1a:conj:block-exhaustion} (F1.a.1): block
exhaustion per residual Galois representation.
\Cref{v4-arith:deg-f1a:thm:ess-surj-conditional} closes (a) under
this conjecture.
\item Obstruction (b) reduces to
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement} (F1.a.2: existence
of wild-enhanced EG stack) plus the BH analogue of block exhaustion
(F1.a.3).
\Cref{v4-arith:deg-f1a:thm:wild-functor-existence} and
\Cref{v4-arith:deg-f1a:cor:wild-ess-surj} close (b) under these
conjectures.
\item Obstruction (c) closes unconditionally once (a) closes, via
\Cref{v4-arith:deg-f1a:thm:central-character-variation}: the
central-character variation is automatic from the fibred structure.
\item Full conditional closure of F1.a at all primes:
\Cref{v4-arith:deg-f1a:thm:F1a-conditional}, conditional on (H1),
(H2), (H3) = (F1.a.1), (F1.a.2), (F1.a.3).
\item Unconditional partial closure: a fully-faithful family DEG
embedding at every $p\geq 5$
(\Cref{v4-arith:deg-f1a:thm:DEG-family-ff},
\Cref{v4-arith:deg-f1a:cor:partial-F1a-large-p}). No residual.
\item Global assembly check: F1 follows from F1.a (at every prime,
including wild) plus $\mathrm{L}_{\mathrm{ACD}}$
(\Cref{v4-arith:deg-f1a:thm:F1-adelic-check}); total F1 residual
ledger is four items
(\Cref{v4-arith:deg-f1a:prop:F1-reduction-updated}).
\end{enumerate}

The chapter produces no unconditional closure of F1.a. The
strongest honest statement is the fully-faithful family DEG
embedding at $p\geq 5$
(\Cref{v4-arith:deg-f1a:cor:partial-F1a-large-p}); all other closure
claims are explicitly conditional. The three residuals (F1.a.1,
F1.a.2, F1.a.3) are strictly narrower than the original F1.a
conjecture and each is individually attackable with the
source catalog laid out here.
