\chapter{H-P$^{\mathrm{Ar}}$ Spectral Matching and Hamburger Determinacy}
\label{v4-arith:hpar-det}

\emph{Chapter~\ref{v4-arith:HPAr-vbconverse} reduced the arithmetic
Hilbert--P\'olya hypothesis H-P$^{\mathrm{Ar}}$ to a spectral
realisation (SP) equivalent to the Connes adele-class-space
absorption-spectrum conjecture and to the Deninger regularised-determinant
axioms, and reduced the VB$^{*}$ converse to a four-way equivalence
with Hamburger determinacy of the symmetrised shifted-zero measure.
Chapter~\ref{v4-arith:platonic-rh-completion} assembled the conditional
RH completion package and isolated the positivity/determinacy input
which would close that package. This chapter pushes on that frontier
without claiming closure. On the H-P$^{\mathrm{Ar}}$ side, it separates
the Bost--Connes zero-mode \emph{weight-selection} problem from the
trace-matching problem: the logarithmic Berry--Keating weight is the
only survivor among a small canonical test family, and is unique under
an explicit KMS/zeta-partition normalisation, but existence of the
required trace identity remains the H-P$^{\mathrm{Ar}}$ obstruction.
On the VB$^{*}$ side, it repairs the Carleman route: the
Bombieri--Lagarias Li-coefficient bounds do not by themselves control
the shifted-zero moments. What survives is a precise sufficient
analytic residual, namely a linear upper-growth bound for
$\mu_{2n}^{1/(2n)}$, or equivalently an admissible positive
regularised moment measure with Carleman divergence. Nothing closes;
the contribution is the tightest honest reduction presently available.}

\section{Route~3 Context}
\label{v4-arith:hpar-det:context}

\subsection{What Route~2 Settled}
\label{v4-arith:hpar-det:wave2-recap}

The route~2 structural analysis of
Chapter~\ref{v4-arith:HPAr-vbconverse} established the following
four-point ledger against which route~3 operates:

\begin{enumerate}
\item \emph{Domain theorem for $L_{0}^{\mathrm{Ar}}$.}
\Cref{v4-arith:hpvbconv:thm:L0-Friedrichs}: on the primary arithmetic
Heisenberg Fock, under non-negativity of the Bost--Connes zero-mode
weights $\lambda(m)\geq 0$, the symmetric operator
$L_{0}^{\mathrm{Ar},\,\mathrm{symm}}$ admits a unique Friedrichs
self-adjoint extension $L_{0}^{\mathrm{Ar}}$, essentially self-adjoint
on the finite-span core $\mathcal{D}_{0}$, with non-negative spectrum.
\textbf{Closed}.
\item \emph{Three-way equivalence for H-P$^{\mathrm{Ar}}$.}
\Cref{v4-arith:hpvbconv:thm:HPAr-equivalence}: H-P$^{\mathrm{Ar}}$
(in the spectral-realisation form SP) is equivalent to the Connes
absorption-spectrum conjecture and to the Deninger regularised
determinant condition. \textbf{Structurally closed; inner content
open}.
\item \emph{Four-way equivalence for VB$^{*}$ converse.}
\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}:
the VB$^{*}$ converse is equivalent to Hamburger determinacy (Det) of
the symmetrised shifted-zero measure, to Hermite--Biehler operator
positivity on the de Branges space $\mathcal{H}(E_{\xi})$ (HB+), and
to a sharp B\'aez-Duarte decay rate
$\epsilon_{N}^{\mathrm{BD}}\asymp 1/\sqrt{\log N}$ with the
Petersson-matched constant (BD+). \textbf{Structurally closed; inner
content open}.
\item \emph{Logical independence of the two residuals.}
\Cref{v4-arith:hpvbconv:prop:HPAr-det-independent}: H-P$^{\mathrm{Ar}}$
(existence of a self-adjoint $L_{0}^{\mathrm{Ar}}$ with prescribed
trace) and Hamburger determinacy (uniqueness of the spectral
measure) are logically independent. \textbf{Proved}.
\end{enumerate}

Route~3 does not repair the route~2 ledger; the ledger is correct. Route~3
performs two genuinely new operations inside that ledger.

\subsection{Two Open Items Attacked Here}
\label{v4-arith:hpar-det:wave3-attack}

(A) \emph{Zero-mode weight selection for H-P$^{\mathrm{Ar}}$.}
Route~2's \Cref{v4-arith:hpvbconv:cor:HPAr-single-residual} names the
single residual as ``the choice of Bost--Connes zero-mode weights
$\{\lambda(m)\}_{m\in\mathbb{N}^{\times}}$ such that the combined
trace matches the zero generating function''. Route~3 tests four
canonical weight systems against the arithmetic Koszul
self-duality (P1), the arithmetic Zhu modularity (P2), and
Bost--Connes rigidity at $\beta=1$. This is a finite stress test,
not a classification of all additive functions on
\(\mathbb{N}^{\times}\). A genuine uniqueness theorem requires the
extra KMS/zeta-partition normalisation stated below.

(B) \emph{Hamburger determinacy attack on the symmetrised shifted-zero
measure.} Route~2's
\Cref{v4-arith:hpvbconv:prop:carleman-insufficient} names the Carleman
sum as ``open, not refuted'' under a heuristic $\mu_{2n}\asymp
C^{n}n!^{2}$. Route~3 tests the tempting Bombieri--Lagarias route and
finds the obstruction: Li-coefficient bounds do not transfer to
two-sided estimates for the positive regularised shifted-zero moments.
The usable conclusion is the classical one: Carleman's criterion would
follow from an upper bound \(\mu_{2n}^{1/(2n)}\le Cn\) for all large
\(n\), but Vol~IV does not prove that bound.

The rubric throughout: \emph{Honesty greater than closure.} The
Platonic single positivity theorem of
\Cref{v4-arith:platonic:cor:single-positivity} is sufficient for RH
after the conditional Ch~37 package is supplied. Route~3 produces the
sharpest reduction the framework allows without that closure.

\subsection{Disjoint Source Catalog for Route~3}
\label{v4-arith:hpar-det:sources}

Route~2 used: Connes arXiv:math/9811068, Deninger 1994, Berry--Keating
1999, Reed--Simon, Akhiezer--Glazman, de Branges 1968/1994,
B\'aez-Duarte 2003, Burnol 2000. Route~3 draws on a complementary
catalog to preserve source disjointness:

\begin{description}
\item[Akhiezer, \emph{The Classical Moment Problem} (Oliver \& Boyd
1965).] Definitive monograph on the Hamburger, Stieltjes, Hausdorff
moment problems; \S2.4 Carleman's criterion; \S2.5 Nevanlinna
parametrisation of indeterminate solutions; \S3.1 Jacobi-matrix
formalism; \S5.6 exponential-moment estimates.
\item[Shohat--Tamarkin \emph{The Problem of Moments} (AMS 1943).] The
American companion to Akhiezer; Ch.~III.5 classical determinacy,
Ch.~III.2 Hankel determinants as sufficient tests, Ch.~VI bounded-case
theorems.
\item[Stieltjes, Ann.~Fac.~Sci.~Toulouse (1894).] The original
indeterminate moment problem; the lognormal $\mu_{n}=e^{n^{2}/2}$
example; baseline indeterminacy standard.
\item[Nevanlinna, Ann.~Acad.~Sci.~Fenn.~5 (1922).] Parametrisation of
the convex set of solutions to an indeterminate Hamburger moment
problem by four entire functions $A,B,C,D$ of exponential type zero;
each indeterminate solution corresponds to a Nevanlinna function
$\varphi$ via $(A\varphi-C)/(B\varphi-D)$.
\item[Krein, Dokl.~Akad.~Nauk SSSR 77 (1951) 93--96.] Krein's
Pontryagin-space theorem: self-adjoint operators on indefinite-metric
spaces; prototype for the indeterminate moment problem as a problem
with non-unique positive lift.
\item[Simon, Adv.~Math.~137 (1998), 82--203.] Modern treatment of
classical moment problems via Jacobi matrices: the Hamburger moment
problem with moments $\{\mu_{n}\}$ is determinate iff the associated
Jacobi operator is essentially self-adjoint on $c_{00}$; indeterminate
iff deficiency indices $(1,1)$.
\item[Berg--Christiansen, Math.~Ann.~322 (2002) 451--473.] Exponential
moment condition: $\sum_{n}\mu_{2n}^{-1/(2n)}=+\infty$ implies
determinacy (Carleman); refinements via sharper generating-function
analysis.
\item[Lin, Probab.~Surv.~14 (2017) 129--190.] Modern survey of
determinacy: Carleman vs.~Krein vs.~Lin conditions; exponential-moment
comparison.
\item[Bost--Connes, Selecta Math.~1 (1995) 411--457.] Original
Bost--Connes system; \S2.2 construction of the Hecke algebra
$C^{*}_{\mathbb{Q}}$; \S3.1 KMS states for $\beta>1$; \S4 phase
transition at $\beta=1$.
\item[Laca, J.~Funct.~Anal.~152 (1998) 330--378.] Laca's categorical
approach to the Bost--Connes system: characters of the
$C^{*}(\mathbb{Q}/\mathbb{Z})\rtimes\mathbb{N}^{\times}$ crossed
product; KMS classification via induced representations.
\item[Connes--Marcolli, AMS Colloq.~Publ.~55 (2008).] Comprehensive
reference on Bost--Connes and number theory; Ch.~3 KMS states,
Ch.~4 rigidity at $\beta=1$, Ch.~5 adele class space structure.
\item[Connes--Marcolli--Ramachandran, arXiv:math/0501424.] Explicit
description of the KMS${}_{\beta=1}$ state as the unique symmetric
trace on the Bost--Connes system; rigidity of the zero-mode spectrum
under the Hecke action.
\item[Conrey, J.~Reine Angew.~Math.~399 (1989) 1--26.] Zero-density
theorem: at least 40\% of the non-trivial zeros of $\zeta$ lie on the
critical line. Unconditional.
\item[Selberg, Arch.~Math.~Naturvid.~48 (1946) 89--155.] Positive
proportion of zeros on the critical line, first unconditional
zero-density result.
\item[Levinson, Adv.~Math.~13 (1974) 383--436.] 1/3 of zeros on the
line via Levinson's method.
\item[Odlyzko, 2001 (unpublished note).] Numerical verification of
$10^{13}$ non-trivial zeros on the critical line.
\item[Bombieri--Lagarias, J.~Number Theory 77 (1999) 274--287.]
Unconditional upper bound
$\lambda_{n}\leq n(c_{0}+\log n)/2$, $c_{0}=2-\log(4\pi)+\gamma$, and
a matching lower bound $\lambda_{n}\geq -(n/2)\log n-O(n)$.
\end{description}

These sources are disjoint from the route~2 catalog in the Vol~IV
sense: none of the route~2 primary derivations are cited route~3, and
none of the route~3 verifications are cited route~2.

\section{Attack-and-Repair Ledger}
\label{v4-arith:hpar-det:ledger}

Route~3 executes six attack-and-repair cycles, four on weight selection
(A) and two on Hamburger determinacy (B).

\subsection{Cycle 1 (A, weight enumeration)}
\label{v4-arith:hpar-det:cycle-1}

\paragraph{id:} W3-HPAr-weight-01.
\paragraph{severity:} foundational.
\paragraph{status:} passed as a finite canonical stress test; none of
the four tested systems closes simultaneously against P1, P2, and the
H-P$^{\mathrm{Ar}}$ trace-compatibility condition.
\paragraph{lens:} Bost--Connes rigidity of zero-mode weights.
\paragraph{target:} enumerate four canonical candidate weight systems
$\{\lambda(m)\}_{m\in\mathbb{N}^{\times}}$ and test each against the
three compatibility constraints.
\paragraph{claim under attack:} the Berry--Keating ansatz
$\lambda(p^{k})=k\log p$
(\Cref{v4-arith:hpvbconv:rem:berry-keating}) is the unique natural
candidate.
\paragraph{broken step:} the Berry--Keating ansatz reproduces the
leading asymptotic zero density $N(T)\sim(T/2\pi)\log(T/2\pi)$
(Bohr--Sommerfeld quantisation of $xp=E$) but does not reproduce the
individual spectrum; three independent competitors exist.
\paragraph{evidence type:} finite comparison of canonical
Bost--Connes modular automorphism tests.
\paragraph{evidence ref:} Bost--Connes 1995 \S2.2 (Hecke algebra
structure); Connes--Marcolli 2008 Ch.~3 (KMS${}_{\beta}$
classification); Laca 1998 (categorification).
\paragraph{files read:} 05\_connes\_soibelman\_bost\_connes.tex;
36\_HPAr\_and\_VBstar\_converse.tex;
37\_platonic\_variation\_and\_RH\_completion.tex.
\paragraph{confidence:} high for the four explicit tests; no claim of
classification completeness among all additive prime-weight systems.
\paragraph{blast radius:} reveals the uniqueness obstruction as a
compatibility selection, not a rigidity theorem.
\paragraph{minimal heal:} inscribe four candidate systems as
\Cref{v4-arith:hpar-det:def:candidate-weights}; prove pairwise
compatibility with P1+P2 as
\Cref{v4-arith:hpar-det:thm:two-cancellations}; name the undetermined
trace-compatibility residual.
\paragraph{residual:} trace-compatibility
\eqref{v4-arith:hpvbconv:eq:BC-trace-condition} for each candidate
is equivalent to H-P$^{\mathrm{Ar}}$ for that candidate; no
combination closes unconditionally.
\paragraph{deciding evidence:} the KMS${}_{\beta=1}$ state of the
Bost--Connes system is unique in the symmetric normalisation, but that
rigidity alone does not classify arbitrary additive prime-weight
systems. The finite test therefore supplies evidence and a selection
rule, not an unrestricted uniqueness theorem.

\subsection{Cycle 2 (A, uniqueness under KMS rigidity)}
\label{v4-arith:hpar-det:cycle-2}

\paragraph{id:} W3-HPAr-weight-02.
\paragraph{severity:} structural.
\paragraph{status:} passed as a conditional statement;
Connes--Marcolli rigidity at $\beta=1$ selects a unique weight system
\emph{provided} it is admissible.
\paragraph{lens:} KMS-state rigidity; Connes--Marcolli phase
transition.
\paragraph{target:} show that at most one weight system satisfies
simultaneous compatibility with P1, P2, and the
H-P$^{\mathrm{Ar}}$ trace condition.
\paragraph{claim under attack:} existence \emph{and} uniqueness of a
weight system.
\paragraph{broken step:} existence is open (it is H-P$^{\mathrm{Ar}}$
itself); uniqueness holds conditionally on existence, via
Connes--Marcolli rigidity.
\paragraph{evidence type:} Connes--Marcolli 2008 Ch.~4 rigidity
theorem.
\paragraph{evidence ref:} Connes--Marcolli, AMS Colloq.~Publ.~55
(2008), Thm~4.15 (uniqueness of symmetric KMS${}_{\beta=1}$ state);
Connes--Marcolli--Ramachandran arXiv:math/0501424 (explicit form).
\paragraph{files read:} same as cycle 1 plus
34\_positselski\_costello\_refinements.tex (for KMS phase-transition
discussion).
\paragraph{confidence:} high for rigidity (classical theorem); zero
for existence (it is H-P$^{\mathrm{Ar}}$).
\paragraph{blast radius:} converts uniqueness-under-existence into a
conditional KMS/zeta-normalised statement, while leaving existence as
the H-P$^{\mathrm{Ar}}$ obstruction.
\paragraph{minimal heal:} inscribe
\Cref{v4-arith:hpar-det:thm:uniqueness-given-existence}.
\paragraph{residual:} existence of the weight system, equivalent to
H-P$^{\mathrm{Ar}}$.
\paragraph{deciding evidence:} the KMS${}_{\beta=1}$ state on
$C^{*}_{\mathbb{Q}}$ is unique among \emph{symmetric} states
(invariant under $\mathrm{Gal}(\mathbb{Q}^{\mathrm{ab}}/\mathbb{Q})$)
by Connes--Marcolli 2008 Thm~4.15. To use this for weights one must
add the compatibility theorem identifying the partition function and
prime-generator expectations with the canonical zeta normalisation.
Under that added hypothesis, the logarithmic weight is forced.

\subsection{Cycle 3 (A, consistency with H-P$^{\mathrm{Ar}}$)}
\label{v4-arith:hpar-det:cycle-3}

\paragraph{id:} W3-HPAr-weight-03.
\paragraph{severity:} technical.
\paragraph{status:} passed as a necessary condition; the Hadamard
product expansion forces the weight system to satisfy an
infinite-hierarchy equation.
\paragraph{lens:} Hadamard factorisation of $\xi(s)$; Mellin
inversion; Bost--Connes KMS partition function.
\paragraph{target:} check whether any candidate weight $\lambda(m)$
can turn the Friedrichs Fock/BC Hamiltonian into the zero
distribution required by H-P$^{\mathrm{Ar}}$.
\paragraph{claim under attack:} the Berry--Keating
$\lambda(p^{k})=k\log p$ reproduces the trace identity.
\paragraph{broken step:} the Berry--Keating partition function
$\sum_{n\geq 1}e^{-t\log n}=\sum_{n\geq 1}n^{-t}=\zeta(t)$, multiplied
by the Dedekind-eta inverse, does \emph{not} equal the zero
wave-kernel distribution;
the two sides match only after the archimedean Euler factor is
subtracted and the logarithmic-derivative expansion is inverted.
\paragraph{evidence type:} direct Mellin-transform computation.
\paragraph{evidence ref:} Edwards, \emph{Riemann's Zeta Function}
(Academic Press 1974) \S\S1.13 and 3.3, Mellin inversion of $\xi$
via the logarithmic derivative.
\paragraph{files read:} 05\_connes\_soibelman\_bost\_connes.tex;
22\_closure\_F1\_F2\_F3\_and\_pillars.tex; 23\_rh\_reformulation.tex.
\paragraph{confidence:} complete for the computation; zero for
existence (no weight system is known to close).
\paragraph{blast radius:} reveals that the trace-compatibility
condition is an infinite hierarchy of constraints, not a single
scalar equation; identifies the hierarchy with a regularised
Weil/Connes explicit-formula extension after the admissibility of the
test family is supplied.
\paragraph{minimal heal:} inscribe
\Cref{v4-arith:hpar-det:thm:hierarchy-condition}.
\paragraph{residual:} the infinite hierarchy is the regularised
Weil/Connes trace formula for the nonstandard heat-test family; it is
equivalent to the Connes absorption-spectrum condition only after this
admissibility and regularisation bridge is proved.
\paragraph{deciding evidence:} by Mellin inversion, the repaired
trace identity is an equality of distributions for the normal zero
operator \(\Theta_{\xi}\), equivalently
\(\det_{\infty}(s\mathrm{id}-\Theta_{\xi})=\xi_{\mathbb R}(s)\). The
Friedrichs Fock/BC Hamiltonian supplies the Euler partition side, not
this determinant identity.

\subsection{Cycle 4 (B, Hamburger determinacy reductions)}
\label{v4-arith:hpar-det:cycle-4}

\paragraph{id:} W3-Det-04.
\paragraph{severity:} foundational.
\paragraph{status:} passed as a structural reduction; Carleman's
criterion $\sum_{n\geq 1}\mu_{2n}^{-1/(2n)}=+\infty$ is not refuted
by the known moment estimates; whether it holds is open.
\paragraph{lens:} Carleman's determinacy criterion; Nevanlinna
parametrisation of indeterminate moment problems.
\paragraph{target:} apply Carleman's criterion to the symmetrised
shifted-zero moment sequence $\{\mu_{2n}\}$.
\paragraph{claim under attack:} Carleman's criterion holds for the
symmetrised shifted-zero moment sequence.
\paragraph{broken step:} the moment sequence grows like
$\mu_{2n}\asymp C^{n}n!^{2}$ under Riemann--von Mangoldt heuristics
(Chapter~\ref{v4-arith:HPAr-vbconverse}); this is exactly on the
Carleman boundary, not strictly inside.
\paragraph{evidence type:} classical moment-problem analysis.
\paragraph{evidence ref:} Akhiezer 1965 \S2.4 (Carleman's criterion);
Nevanlinna 1922 (parametrisation of indeterminate solutions);
Shohat--Tamarkin 1943 Ch.~III.5; Berg--Christiansen 2002
(exponential-moment refinements); Lin 2017 (modern survey).
\paragraph{files read:} 36\_HPAr\_and\_VBstar\_converse.tex;
24\_arithmetic\_virasoro\_bootstrap.tex.
\paragraph{confidence:} complete for the classical reduction; zero
for unconditional closure (the moment asymptotics are exactly on
Carleman's boundary).
\paragraph{blast radius:} places the Hamburger determinacy problem
at the finest classical resolution; identifies the remaining gap as
positivity plus a Carleman-scale upper-growth estimate on $\mu_{2n}$.
\paragraph{minimal heal:} inscribe
\Cref{v4-arith:hpar-det:thm:carleman-reformulation}.
\paragraph{residual:} a positive regularised moment measure and an
upper-growth estimate $\mu_{2n}^{1/(2n)}\le Cn$ for all large \(n\);
absent this, the Carleman sum cannot be evaluated.
\paragraph{deciding evidence:} the Riemann--von Mangoldt formula
controls zero counting, not the positivity of the regularised
moment functional. A saddle-point heuristic suggests the
Carleman-scale growth \(C^{n}n!^{2}\), but turning that heuristic into
the upper bound \(\mu_{2n}^{1/(2n)}=O(n)\) is an additional analytic
theorem.

\subsection{Cycle 5 (B, attack via Li--Bombieri--Lagarias)}
\label{v4-arith:hpar-det:cycle-5}

\paragraph{id:} W3-Det-05.
\paragraph{severity:} structural (attempts unconditional path).
\paragraph{status:} failed as an unconditional closure route; the
Bombieri--Lagarias Li-coefficient bounds are unconditional, but they
do not yield the moment upper-growth estimate needed for Carleman's
sum.
\paragraph{lens:} Li--Bombieri--Lagarias unconditional asymptotics
for $\lambda_{n}$.
\paragraph{target:} test whether the unconditional bound
$\lambda_{n}\leq n(c_{0}+\log n)/2$ can be converted into an
unconditional estimate on $\mu_{2n}$.
\paragraph{claim under attack:} Carleman's criterion can be verified
unconditionally from known analytic bounds.
\paragraph{broken step:} the Li coefficients are oscillatory sums over
zeros, whereas \(\mu_{2n}\) is a positive regularised moment. The
unconditional bound \(\lambda_{n}\leq n(c_{0}+\log n)/2\) does not
transfer to \(\mu_{2n}\) without a separate positivity/domination
theorem.
\paragraph{evidence type:} Bombieri--Lagarias explicit formula analysis.
\paragraph{evidence ref:} Bombieri--Lagarias J.~Number Theory 77
(1999) 274--287, Theorem 2; Voros arXiv:math/0308172 (refinements);
Coffey arXiv:math-ph/0507008 (numerical verification to $n\leq 10^{5}$).
\paragraph{files read:}
24\_arithmetic\_virasoro\_bootstrap.tex;
36\_HPAr\_and\_VBstar\_converse.tex.
\paragraph{confidence:} complete for the obstruction; no
unconditional Carleman estimate follows from this route.
\paragraph{blast radius:} blocks the tempting shortcut from
Li-coefficient estimates to Hamburger determinacy; no Carleman bound
is obtained from Bombieri--Lagarias alone.
\paragraph{minimal heal:} inscribe
\Cref{v4-arith:hpar-det:prop:BL-carleman-partial}.
\paragraph{residual:} an independent construction of a positive
regularised shifted-zero moment measure and an upper-growth estimate
$\mu_{2n}^{1/(2n)}\le Cn$; Li-coefficient bounds alone do not supply it.
\paragraph{deciding evidence:} Bombieri--Lagarias Thm~2 bounds the
Li sum
$\lambda_{n}=\sum_{\rho}(1-(1-1/\rho)^{n})$ (Li 1997). This is a
highly oscillatory zero sum. It is not a bound on the absolute moments
$\mu_{2n}$, and cancellations in the Li sum cannot be reversed into
Carleman control without an additional positivity/regularisation
theorem.

\subsection{Cycle 6 (cross-check; residual obstruction naming)}
\label{v4-arith:hpar-det:cycle-6}

\paragraph{id:} W3-Residual-06.
\paragraph{severity:} capstone.
\paragraph{status:} passed as a naming theorem; the residual
obstruction is exactly the positive regularised moment problem with
linear upper growth.
\paragraph{lens:} comparison of the three classical reformulations
(Carleman, Nevanlinna, Akhiezer-Krein) on the symmetrised shifted-zero
measure.
\paragraph{target:} a single precisely-named residual whose closure
would close the Ch~37 Corollary.
\paragraph{claim under attack:} the Ch~37 Corollary's single
positivity theorem reduces to an analytic statement of classical form.
\paragraph{broken step:} this is the route~3 closure target; it
succeeds.
\paragraph{evidence type:} synthesis.
\paragraph{evidence ref:} accumulated route~2 and route~3 sources.
\paragraph{files read:} all of above.
\paragraph{confidence:} complete for the naming; zero for independent
closure.
\paragraph{blast radius:} consolidates all of route~3's reductions
into a single residual statement.
\paragraph{minimal heal:} inscribe
\Cref{v4-arith:hpar-det:thm:single-analytic-residual}.
\paragraph{residual:} a positive regularised interpretation of
$\mu_{2n}=\sum_{\rho}(1/4+|\gamma_{\rho}|^{2})^{n}$ with
$\mu_{2n}^{1/(2n)}=O(n)$; this is the arithmetic content that Vol~IV
does not supply.
\paragraph{deciding evidence:} the arithmetic content required is
an analytic estimate strong enough for Carleman's criterion, together
with positivity of the regularised measure; all other ingredients
remain conditional inputs from route~2 and Ch~37.

\section{H-P$^{\mathrm{Ar}}$ Spectral Matching: Bost--Connes Zero-Mode Weight}
\label{v4-arith:hpar-det:weight-selection}

\subsection{Candidate Weights}
\label{v4-arith:hpar-det:candidate-weights}

The route~2 candidate weight system inscribed was the Berry--Keating
ansatz $\lambda(p^{k})=k\log p$ extended multiplicatively to
$\lambda(m)=\log m$ (\Cref{v4-arith:hpvbconv:rem:berry-keating}). We
test it against three nearby diagnostics. This is deliberately not an
exhaustive classification of all maps
\(\mathbb{N}^{\times}\to\mathbb{R}\): additive weights are determined
by arbitrary prime values \(\{\lambda(p)\}_{p}\). The point is to
separate the canonical BC/zeta generator from common false
substitutes.

\begin{definition}[four canonical zero-mode weight tests]
\label{v4-arith:hpar-det:def:candidate-weights}
\ClaimStatusDefinitional. Let $C^{*}_{\mathbb{Q}}$ be the
Bost--Connes algebra of
\Cref{v4-arith:def:bost-connes-algebra}. Four canonical weight tests
$\{\lambda_{\star}(m)\}_{m\in\mathbb{N}^{\times}}$ are available,
each arising from a distinct structural interpretation of the
Hecke action on the zero-mode lattice:
\begin{description}
\item[(BK)] \emph{Berry--Keating / logarithmic}:
$\lambda_{\mathrm{BK}}(m):=\log m$. Extended multiplicatively:
$\lambda_{\mathrm{BK}}(p^{k})=k\log p$. This is the Euler-product
generator; yields the BC KMS${}_{\beta}$ partition function
$\zeta(\beta)$ at $\beta=1$.
\item[(Li-shift)] \emph{Li spectral translation}:
$\lambda_{\mathrm{Li}}(m):=\log m$ as a semigroup weight, with the
critical-line translation \(s\mapsto s-\frac12\) applied to the
spectral parameter rather than inserted as a constant shift in the
semigroup homomorphism. A literal formula
\(\log m-\frac12\) is not additive on
\(\mathbb{N}^{\times}\) and is therefore not a BC weight.
\item[(vM)] \emph{von Mangoldt / Weil}:
$\lambda_{\mathrm{vM}}(m):=\Lambda(m)\log m$ where
$\Lambda(m)$ is the von Mangoldt function
($\Lambda(p^{k})=\log p$, zero otherwise). This is a logarithmic
derivative diagnostic, not a multiplicative semigroup weight.
\item[(FS-quad)] \emph{quadratic finite-place diagnostic}:
$\lambda_{\mathrm{FS}}(p^{k}):=k^{2}\log p$ and
$\lambda_{\mathrm{FS}}(m):=\sum_{p^{k_{p}}\Vert m}k_{p}^{2}\log p$.
This records the quadratic-exponent alternative suggested by
finite-place Hecke powers on perfectoid Iwahori charts
(\Cref{v4-arith:platonic:def:S2} finite-place orientation). It agrees
with (BK) on squarefree integers and differs on higher prime powers.
\end{description}
\end{definition}

\begin{remark}[scope of the four tests]
\label{v4-arith:hpar-det:rem:four-exhaust}
Under the $\mathbb{Q}$-positive-semigroup action of
$\mathbb{N}^{\times}$ on the zero-mode lattice, a weight system
$\lambda:\mathbb{N}^{\times}\to\mathbb{R}$ is compatible with the
Bost--Connes Hecke action
$\mu_{n}\mu_{m}=\mu_{nm}$ only when
$\lambda(nm)=\lambda(n)+\lambda(m)$. The additive case reduces to
specifying $\lambda(p)$ for each prime $p$, hence contains infinitely
many choices. The zeta partition normalisation
\[
 \sum_{m\ge 1} e^{-\beta\lambda(m)}=\zeta(\beta)
\]
for all \(\mathrm{Re}(\beta)>1\) forces \(e^{-\lambda(p)}=p^{-1}\)
prime-by-prime, and therefore forces (BK). Without that normalisation
there is no uniqueness theorem. The four tests above only record the
canonical logarithmic, translated, logarithmic-derivative, and
quadratic finite-place possibilities used in the attack-and-repair audit.
\end{remark}

\subsection{Pairwise Compatibility with P1 and P2}
\label{v4-arith:hpar-det:compat-P1-P2}

\begin{lemma}[P1 compatibility within the four tests]
\label{v4-arith:hpar-det:lem:P1-compat}
\ClaimStatusProvedHere. Within
\Cref{v4-arith:hpar-det:def:candidate-weights}, the additive
Berry--Keating weight is compatible with the formal
\(m\leftrightarrow m^{-1}\) functional-equation involution. The
Li-shift test is the same additive weight together with an external
critical-line translation. The von Mangoldt and quadratic finite-place
diagnostics are not multiplicative semigroup weights and therefore do
not define BC zero-mode weights satisfying P1.
\end{lemma}

\begin{proof}
For (BK),
\(\lambda_{\mathrm{BK}}(m)+\lambda_{\mathrm{BK}}(m^{-1})=0\) after
Mellin continuation. The Li shift is not the map
\(\log m-\frac12\) on \(\mathbb{N}^{\times}\), since such a map fails
\(\lambda(nm)=\lambda(n)+\lambda(m)\). It is the same additive weight
with the spectral parameter translated by \(1/2\). The von Mangoldt
test is supported on prime powers and the FS-quad test satisfies
\(\lambda_{\mathrm{FS}}(p^{a+b})\ne
\lambda_{\mathrm{FS}}(p^{a})+\lambda_{\mathrm{FS}}(p^{b})\) for
general \(a,b\). Hence neither is a BC semigroup weight.
\end{proof}

\begin{lemma}[P2 compatibility within the four tests]
\label{v4-arith:hpar-det:lem:P2-compat}
\ClaimStatusProvedHere. Within
\Cref{v4-arith:hpar-det:def:candidate-weights}, the Berry--Keating
weight is the only additive weight whose partition function is the
classical zeta partition function. The Li shift changes only the
external critical-line normalisation. The von Mangoldt and FS-quad
tests do not give the \(\zeta\)-partition function and hence do not
satisfy P2 in the arithmetic Zhu sense.
\end{lemma}

\begin{proof}
(BK) gives
\[
 \sum_{m\geq 1}e^{-t\log m}=\sum_{m\geq 1}m^{-t}=\zeta(t).
\]
The Li-shift convention leaves this semigroup partition function
unchanged and moves the \(1/2\) into the spectral variable. For (vM)
one obtains a logarithmic-derivative diagnostic supported on prime
powers, not a Dirichlet series with the \(\xi\)-functional equation.
For (FS-quad) one obtains
\[
 \prod_{p}\sum_{k\geq0}p^{-tk^{2}},
\]
not the Euler product for \(\zeta(t)\). These two diagnostics therefore
fail the P2 partition-function test.
\end{proof}

\begin{theorem}[four-test filter under P1+P2]
\label{v4-arith:hpar-det:thm:two-cancellations}
\ClaimStatusProvedHere. Among the four tests of
\Cref{v4-arith:hpar-det:def:candidate-weights}, simultaneous P1+P2
compatibility leaves only the Berry--Keating semigroup weight
\(\lambda(m)=\log m\), with the Li convention understood as the same
weight after external critical-line translation. This is a finite
filter, not a classification of all possible prime-weight systems.
\end{theorem}

\begin{proof}
\Cref{v4-arith:hpar-det:lem:P1-compat} and
\Cref{v4-arith:hpar-det:lem:P2-compat} eliminate the von Mangoldt and
FS-quad diagnostics as BC semigroup weights. The Li convention does not
produce a new additive weight; it is the Berry--Keating weight with the
spectral parameter centred at \(1/2\). Thus the only surviving
semigroup weight in the four-test family is (BK).
\end{proof}

\begin{remark}[what the filter proves]
\label{v4-arith:hpar-det:rem:BK-survivor}
\Cref{v4-arith:hpar-det:thm:two-cancellations} proves only the
finite-filter statement just stated. Full uniqueness requires the
zeta partition normalisation or an equivalent KMS compatibility
condition; without such a condition, arbitrary prime weights
\(\{\lambda(p)\}_{p}\) remain possible.
\end{remark}

\subsection{Uniqueness under KMS/Zeta Normalisation}
\label{v4-arith:hpar-det:uniqueness-given-existence}

The surviving canonical test is (BK). Existence with the
trace-compatibility condition remains open. What can be proved
honestly is uniqueness after the partition function is fixed.

\begin{theorem}[uniqueness under zeta partition normalisation]
\label{v4-arith:hpar-det:thm:uniqueness-given-existence}
\ClaimStatusProvedHere. Suppose
\(\lambda:\mathbb{N}^{\times}\to\mathbb{R}_{\geq0}\) is additive and
has zeta partition function
\[
 \sum_{m\geq1}e^{-\beta\lambda(m)}=\zeta(\beta)
\]
for all \(\mathrm{Re}(\beta)>1\), with Euler factors matched
prime-by-prime to the Bost--Connes Hecke generators. Then
\(\lambda(m)=\log m\). Consequently any H-P$^{\mathrm{Ar}}$
realisation satisfying this KMS/zeta normalisation uses the
Berry--Keating weight.
\end{theorem}

\begin{proof}
Additivity gives \(\lambda(p^{k})=k\lambda(p)\), so the partition
function factors as
\[
 \prod_{p}(1-e^{-\beta\lambda(p)})^{-1}.
\]
Prime-by-prime equality with
\(\zeta(\beta)=\prod_{p}(1-p^{-\beta})^{-1}\) gives
\(e^{-\lambda(p)}=p^{-1}\), hence \(\lambda(p)=\log p\) for every
prime. Additivity then gives \(\lambda(m)=\log m\).
\end{proof}

\begin{remark}[relation to Connes--Marcolli rigidity]
\label{v4-arith:hpar-det:rem:conditional-uniqueness}
Connes--Marcolli rigidity at \(\beta=1\) is the conceptual source of
this normalisation, but the manuscript must not identify an arbitrary
weight with the unique symmetric KMS state without proving the
prime-generator and partition-function bridge. The theorem above
therefore records the exact conditional uniqueness available to the
Vol~IV path. It does not prove H-P$^{\mathrm{Ar}}$: the
Bost--Connes/Dedekind-eta trace identity is still the unresolved
spectral matching problem.
\end{remark}

\subsection{The Hierarchy Condition}
\label{v4-arith:hpar-det:hierarchy}

\begin{lemma}[admissible Weil--Connes wave-kernel regularisation]
\label{v4-arith:hpar-det:lem:PW-wave-regularisation}
\ClaimStatusProvedHere. Let \(\xi=\xi_{\mathbb R}\) and write each
non-trivial zero as \(\rho=1/2+i\gamma_{\rho}\). Use the Fourier
convention
\[
h(r)=\int_{\mathbb R}\widehat h(u)e^{-iru}\,du .
\]
Let
\[
\mathsf{PW}:=\{h=\mathcal F^{-1}\psi:\psi\in C_c^\infty(\mathbb R)\}
\]
with the LF topology transported from \(C_c^\infty(\mathbb R)\). For
\(h\in\mathsf{PW}\), the Weil--Connes explicit formula gives
\begin{equation}
\label{v4-arith:hpar-det:eq:PW-weil}
\sum_{\rho}h(\gamma_{\rho})
=\int_{\mathbb R}h(r)\,dW_{\infty}(r)
-2\sum_{n\geq1}\frac{\Lambda(n)}{\sqrt n}\widehat h(\log n),
\end{equation}
in the normalisation of \eqref{v4-arith:hpar-det:eq:weil-explicit};
the prime sum is finite because \(\widehat h\) has compact support.

For \(\phi\in C_c^\infty((0,\infty))\), set
\[
h_{\phi}(r):=\int_0^\infty e^{-u/2}\phi(u)e^{-iru}\,du .
\]
Then \(h_{\phi}\in\mathsf{PW}\), and
\[
\langle\mathcal W_{\xi},\phi\rangle
:=\sum_{\rho}h_{\phi}(\gamma_{\rho})
\]
defines a distribution \(\mathcal W_{\xi}\in\mathcal D'((0,\infty))\).
Consequently the symbolic kernel \(\sum_{\rho}e^{-t\rho}\) is a
distributional wave kernel, not an ordinary heat trace.
\end{lemma}

\begin{proof}
This is the standard Paley--Wiener form of the Weil explicit formula:
compact support of \(\widehat h\) makes the prime sum finite and the
archimedean term is the distribution \(W_{\infty}\). The second
statement is obtained by substituting the compactly supported function
\(u\mapsto e^{-u/2}\phi(u)\) into the same formula. Approximation of
the point kernel uses mollifiers
\(\widehat h_{t,\epsilon}(u)=e^{-u/2}\epsilon^{-1}\eta((u-t)/\epsilon)\);
the convergence is in \(\mathcal D'((0,\infty))\), not pointwise heat
trace convergence.
\end{proof}

\begin{theorem}[trace-compatibility as regularised Weil/Connes hierarchy]
\label{v4-arith:hpar-det:thm:hierarchy-condition}
\ClaimStatusProvedHere \emph{(conditional on the H-P$^{\mathrm{Ar}}$
trace realisation)}. Let \(\lambda=\lambda_{\mathrm{BK}}\) be the
Berry--Keating weight of
\Cref{v4-arith:hpar-det:def:candidate-weights}. The
trace-compatibility condition
\eqref{v4-arith:hpvbconv:eq:BC-trace-condition} is the regularised
Weil/Connes trace hierarchy
\begin{equation}
\label{v4-arith:hpar-det:eq:weil-explicit}
\sum_{\rho}^{\mathrm{reg}}h_{t}(\gamma_{\rho})\;=\;
\int_{-\infty}^{\infty}h_{t}(r)\,dW(r)
\,-\,2\sum_{n\geq 1}\frac{\Lambda(n)}{\sqrt{n}}
\widehat{h}_{t}(\log n)
\end{equation}
for the wave-kernel test family associated to
\(e^{-t\Theta_{\xi}}\), after the admissible regularisation of
\Cref{v4-arith:hpar-det:lem:PW-wave-regularisation} is supplied. This
is not an unconditional application of the classical Weil formula to
an inadmissible heat kernel; it is precisely the trace-realisation
bridge needed for H-P$^{\mathrm{Ar}}$.
\end{theorem}

\begin{proof}
Under the BK weight system, the Friedrichs operator acts on
$\delta_{m}$ by eigenvalue $\log m$. The regularised trace of
$e^{-tL_{0}^{\mathrm{Ar}}}$ on the zero-mode lattice is
$\sum_{m\geq 1}e^{-t\log m}=\sum_{m\geq 1}m^{-t}=\zeta(t)$, convergent
for $t>1$ and meromorphically continued.

Combining with the archimedean Dedekind-eta inverse product
$\prod_{i\geq 1}(1-e^{-ti})^{-1}$ and subtracting the archimedean
descendant contribution (Tate-pole and archimedean terms) via the
Bost--Connes regularisation
(\Cref{v4-arith:hpvbconv:prop:BC-trace-compatibility}), one obtains
\begin{equation*}
\mathrm{tr}_{\mathrm{BC}}(e^{-tL_{0}^{\mathrm{Ar}}})
=\zeta(t)\cdot\eta(it)^{-1}\cdot(\text{regularisation}),
\end{equation*}
with the archimedean terms removed by the Bost--Connes/Dedekind-eta
prescription. The Hadamard product for \(\xi_{\mathbb R}\) rewrites
the zero side as a regularised zero trace. The classical Weil explicit
formula supplies this identity for the admissible Paley--Wiener test
spaces of \Cref{v4-arith:hpar-det:lem:PW-wave-regularisation}. The
Vol~IV condition is the additional assertion that the
Bost--Connes/Fock trace is carried to that distributional extension.
Therefore the theorem is a reformulation of the trace-compatibility
hierarchy under H-P$^{\mathrm{Ar}}$, not a proof of
H-P$^{\mathrm{Ar}}$.
\end{proof}

\begin{corollary}[the hierarchy is the Connes absorption-spectrum bridge]
\label{v4-arith:hpar-det:cor:hierarchy-is-weil}
\ClaimStatusProvedHere \emph{(conditional on the H-P$^{\mathrm{Ar}}$
trace realisation)}. Under the BK weight selection, the
H-P$^{\mathrm{Ar}}$ trace-compatibility condition is the
Connes--Meyer--Weil absorption-spectrum bridge for the
Bost--Connes/Weil wave-distribution family. It is not discharged by
citing the classical Weil explicit formula alone.
\end{corollary}

\begin{proof}
The previous theorem identifies the needed equality with the
regularised explicit-formula extension for the BC/Weil wave family.
By \Cref{v4-arith:hpvbconv:cor:HPAr-connes-equivalence}, this is the
same structural condition as the Connes absorption-spectrum
realisation. Since the admissibility and trace-identification step is
exactly what H-P$^{\mathrm{Ar}}$ asks for, it cannot be removed as a
classical-formula citation.
\end{proof}

\begin{remark}[weight selection does not close H-P$^{\mathrm{Ar}}$]
\label{v4-arith:hpar-det:rem:weight-does-not-close}
\Cref{v4-arith:hpar-det:thm:uniqueness-given-existence} and
\Cref{v4-arith:hpar-det:cor:hierarchy-is-weil} together state: if
H-P$^{\mathrm{Ar}}$ holds, the weight is uniquely Berry--Keating
under the zeta/KMS normalisation. Whether the Berry--Keating
weight satisfies the trace compatibility is the
regularised Connes absorption-spectrum problem. The reduction is
tight: route~3 determines the canonical weight under explicit
normalisation, but existence itself remains a classical open problem.
\end{remark}

\section{Hamburger Determinacy Attack}
\label{v4-arith:hpar-det:determinacy}

\subsection{The Symmetrised Shifted-Zero Measure}
\label{v4-arith:hpar-det:symmetrised-measure}

We recall the object of study and its precise moment sequence.

\begin{definition}[symmetrised shifted-zero moment sequence]
\label{v4-arith:hpar-det:def:shifted-moments}
\ClaimStatusDefinitional. Let $\rho=1/2+i\gamma_{\rho}$ denote a
non-trivial zero of $\xi$, written with $\gamma_{\rho}\in\mathbb{C}$
(real for every zero iff RH). The \emph{symmetrised shifted-zero moment
sequence} is
\begin{equation}
\label{v4-arith:hpar-det:eq:mu-2n}
\mu_{2n}\;:=\;\sum_{\rho}\Bigl(\tfrac{1}{4}+\gamma_{\rho}^{2}\Bigr)^{n}
\end{equation}
Bost--Connes regularised. Under RH, $\gamma_{\rho}\in\mathbb{R}$ and
the unregularised terms are real and non-negative. Outside RH the
expression is not automatically a positive moment sequence; positivity
of the regularised functional is part of
\((\mathrm{R}_{\mathrm{analytic}})\).
\end{definition}

\begin{remark}[relation to the symmetrised zero measure of route~2]
\label{v4-arith:hpar-det:rem:measure-relation}
The symmetrised zero measure $\nu$ of
\Cref{v4-arith:vb:def:zero-measure} is the pushforward of the zero
set under the symmetrisation map
$\rho\mapsto 1/4+\gamma_{\rho}^{2}=|\rho|^{2}-1/2\mathrm{Re}(\rho)=\rho(1-\overline{\rho})+1/4-\mathrm{Re}(\rho)+\mathrm{Re}(\rho)^{2}$.
Under RH, $\mathrm{Re}(\rho)=1/2$, and the map simplifies to
$\rho\mapsto\gamma^{2}+1/4$. The shifted moment $\mu_{2n}$ of
\Cref{v4-arith:hpar-det:def:shifted-moments} is the $n$-th moment of
this measure; odd moments vanish by symmetry. Determinacy of
$\nu$ is equivalent to determinacy of $\{\mu_{2n}\}_{n\geq 0}$
under the standard Stieltjes--Hamburger dictionary.
\end{remark}

\subsection{Bombieri--Lagarias Does Not Decide Carleman}
\label{v4-arith:hpar-det:carleman-BL}

\begin{proposition}[Bombieri--Lagarias does not control Carleman moments]
\label{v4-arith:hpar-det:prop:BL-carleman-partial}
\ClaimStatusProvedHere. The Bombieri--Lagarias bounds for Li
coefficients do not imply an unconditional Carleman estimate for the
regularised moments \(\mu_{2n}\). In particular, the implication
\[
 |\lambda_{n}|=O(n\log n)
 \quad\Longrightarrow\quad
 \mu_{2n}^{1/(2n)}=O(n)
\]
is not available from the Li identity alone.
\end{proposition}

\begin{proof}
The Li coefficient is the oscillatory zero sum
\[
 \lambda_{n}=\sum_{\rho}\left(1-\left(1-\frac1{\rho}\right)^{n}\right).
\]
The shifted-zero moment relevant to Carleman is instead the positive
regularised quantity
\[
 \mu_{2n}=\sum_{\rho}^{\mathrm{reg}}\left(\frac14+\gamma_{\rho}^{2}\right)^{n}.
\]
An estimate for the oscillatory Li sum gives no bound on the absolute
or positive regularised \(2n\)-th moment without a separate positivity
and domination theorem. Reversing the cancellations in the Li sum
would itself be a new spectral-positivity input. Hence the
Bombieri--Lagarias theorem is evidence for the Li/RH reformulation but
not a Carleman proof.
\end{proof}

\begin{remark}[the failed shortcut]
\label{v4-arith:hpar-det:rem:carleman-not-decided}
This is the central repair of the route~3 attack. A lower bound on
\(\mu_{2n}\) would give an upper bound on
\(\mu_{2n}^{-1/(2n)}\), not the lower bound needed for Carleman's
divergence. Carleman's criterion is driven by upper growth of the
moments, together with positivity of the representing measure.
\end{remark}

\subsection{Tightest Conditional Reduction}
\label{v4-arith:hpar-det:tightest-reduction}

\begin{theorem}[Hamburger determinacy from linear upper growth]
\label{v4-arith:hpar-det:thm:carleman-reformulation}
\ClaimStatusProvedHere. Suppose the symmetrised shifted-zero moments
come from a positive regularised Hamburger moment functional and
there is a constant \(C>0\) such that
\begin{equation}
\label{v4-arith:hpar-det:eq:sharp-asymptotic}
 \mu_{2n}^{1/(2n)}\le Cn
\end{equation}
for all sufficiently large \(n\). Then Carleman's criterion holds:
\[
 \sum_{n\ge1}\mu_{2n}^{-1/(2n)}=+\infty.
\]
Consequently the associated Hamburger moment problem is determinate.
\end{theorem}

\begin{proof}
The upper-growth hypothesis gives
\[
 \mu_{2n}^{-1/(2n)}\ge \frac{1}{Cn}
\]
for all large \(n\). The harmonic series diverges, so Carleman's
criterion applies. By the classical Carleman theorem for Hamburger
moments, the positive moment functional is determinate.
\end{proof}

\begin{corollary}[current unconditional inputs do not close Carleman]
\label{v4-arith:hpar-det:cor:unconditional-gap}
\ClaimStatusProvedHere. The manuscript's current unconditional inputs
do not prove the hypotheses of
\Cref{v4-arith:hpar-det:thm:carleman-reformulation}. They leave open
both the required positive regularised moment functional and the
linear upper-growth estimate \(\mu_{2n}^{1/(2n)}=O(n)\).
\end{corollary}

\begin{proof}
\Cref{v4-arith:hpar-det:prop:BL-carleman-partial} blocks the only
candidate unconditional shortcut in the present chapter. The
Riemann--von Mangoldt counting formula controls the distribution of
zeros by height, but by itself it does not define the required
positive regularised moment functional nor bound the regularised
moments after off-line and archimedean terms are included. These are
exactly the missing inputs.
\end{proof}

\begin{theorem}[the single analytic residual]
\label{v4-arith:hpar-det:thm:single-analytic-residual}
\ClaimStatusProvedHere. Under the route~2 structural reductions and
the route~3 analytic reductions, the Hamburger-determinacy component
of the Vol~IV RH path reduces to the following sufficient analytic
residual:
\begin{equation}
\label{v4-arith:hpar-det:eq:single-residual}
(\mathrm{R}_{\mathrm{analytic}})\quad
\text{\(\{\mu_{2n}\}\) is a positive regularised Hamburger moment
sequence and }\limsup_{n\to\infty}\frac{\mu_{2n}^{1/(2n)}}{n}<\infty.
\end{equation}
This statement implies Carleman's criterion, hence Hamburger
determinacy, hence the VB$^{*}$ converse in the structural framework
of Chapter~\ref{v4-arith:HPAr-vbconverse}.
\end{theorem}

\begin{proof}
The implication
\((\mathrm{R}_{\mathrm{analytic}})\Rightarrow\) Carleman is
\Cref{v4-arith:hpar-det:thm:carleman-reformulation}. The
Carleman-to-determinacy implication is the classical theorem of
Akhiezer/Shohat--Tamarkin. The structural equivalence between
determinacy and the VB$^{*}$ converse is
\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}.
\end{proof}

\begin{remark}[what \(\mathrm{R}_{\mathrm{analytic}}\) asserts]
\label{v4-arith:hpar-det:rem:residual-content}
\((\mathrm{R}_{\mathrm{analytic}})\) is not a two-sided asymptotic
and is not asserted to be weaker than RH. It asks for the exact
positivity/regularisation and upper-growth information that Carleman's
criterion needs. Standard zero-density theorems do not supply this
data: they count zeros in regions, while the residual controls a
regularised moment functional.
\end{remark}

\begin{remark}[no RH closure]
\label{v4-arith:hpar-det:rem:residual-vs-RH}
The residual above is a sufficient condition for the Vol~IV
determinacy step. The chapter does not prove it, does not prove it
from Bombieri--Lagarias, and does not claim that it is strictly weaker
than RH. Its value is that it identifies the exact analytic shape of
the missing positivity theorem.
\end{remark}

\section{Consequence for Ch~37 RH Completion}
\label{v4-arith:hpar-det:ch37-consequence}

\begin{theorem}[route~3 consequence for the Ch~37 single positivity
corollary]
\label{v4-arith:hpar-det:thm:ch37-consequence}
\ClaimStatusProvedHere. The Ch~37 single positivity corollary
\Cref{v4-arith:platonic:cor:single-positivity} reduces, under
route~3 analysis, to the conjunction:
\begin{enumerate}
\item the Berry--Keating weight is forced by the additive
KMS/zeta-partition normalisation
(\Cref{v4-arith:hpar-det:thm:uniqueness-given-existence}).
\item H-P$^{\mathrm{Ar}}$ holds with the Berry--Keating weight,
meaning that the Bost--Connes trace is identified with the
regularised Weil/Connes trace hierarchy
(\Cref{v4-arith:hpar-det:thm:hierarchy-condition}).
\item $(\mathrm{R}_{\mathrm{analytic}})$: the shifted-zero moments
form a positive regularised Hamburger moment sequence with
$\mu_{2n}^{1/(2n)}=O(n)$
(\Cref{v4-arith:hpar-det:thm:single-analytic-residual}).
\end{enumerate}
Under the conjunction of these three, plus the conditional P1/P3
inputs named in Chapter~\ref{v4-arith:platonic-rh-completion}, the
Ch~37 corollary closes.
\end{theorem}

\begin{proof}
(1) provides the uniquely-determined candidate operator
$L_{0}^{\mathrm{Ar}}=L_{0}^{\mathrm{Ar}}(\lambda_{\mathrm{BK}})$.
(2) is precisely the trace-compatibility condition which, via
\Cref{v4-arith:hpvbconv:thm:HPAr-equivalence}, asserts
H-P$^{\mathrm{Ar}}$. (3), by
\Cref{v4-arith:hpar-det:thm:single-analytic-residual} asserts
Hamburger determinacy of the symmetrised shifted-zero measure;
by
\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity},
this supplies the VB$^{*}$ converse. Combined with the domain theorem,
P2, and the conditional P1/P3 inputs recorded in Ch~37,
the Ch~37 single positivity corollary and its consequence RH hold.
\end{proof}

\begin{corollary}[structure of the route~3 reduction]
\label{v4-arith:hpar-det:cor:wave3-structure}
\ClaimStatusProvedHere. Route~3 reduces the Ch~37 single positivity
theorem to three named residuals:
\begin{description}
\item[($\mathrm{W}$)] \emph{Weight normalisation}: an additive
Bost--Connes weight with zeta partition function and prime-by-prime
KMS compatibility. Under (W), $\lambda=\lambda_{\mathrm{BK}}$.
\item[($\mathrm{H}$)] \emph{H-P trace bridge}: the
Bost--Connes/Dedekind-eta heat trace is the admissible regularised
Weil/Connes zero trace. Under (H), H-P$^{\mathrm{Ar}}$ holds for the
BK operator.
\item[($\mathrm{R}_{\mathrm{analytic}}$)] \emph{Carleman positivity}:
the shifted-zero moments form a positive regularised Hamburger moment
sequence and satisfy $\mu_{2n}^{1/(2n)}=O(n)$. Under
$(\mathrm{R}_{\mathrm{analytic}})$, Hamburger determinacy holds.
\end{description}
All three together close the residual H-P/VB part of the Ch~37 path;
they still sit on top of the conditional P1/P3 inputs stated there.
\end{corollary}

\begin{proof}
Direct from \Cref{v4-arith:hpar-det:thm:ch37-consequence}. (W) fixes
the candidate operator; (H) supplies spectral matching; and
$(\mathrm{R}_{\mathrm{analytic}})$ supplies determinacy. Omitting any
one leaves either no fixed operator, no zero trace, or no VB$^{*}$
converse.
\end{proof}

\section{Residual Obstructions}
\label{v4-arith:hpar-det:residuals}

After the route~3 reductions, the precise remaining gaps in the
Ch~37 RH completion path are:

\begin{enumerate}
\item \textbf{(W) Weight normalisation}. The BK weight is forced once
the additive zeta partition function is fixed prime-by-prime. The
remaining task is to prove that the Vol~IV Friedrichs construction
really lands in this KMS/zeta normalisation.
\item \textbf{(H) H-P trace bridge}. The classical Weil explicit
formula is not the missing theorem. The missing theorem is the
admissible regularised extension identifying the BC/Dedekind-eta heat
trace with the Connes zero trace.
\item \textbf{$(\mathrm{R}_{\mathrm{analytic}})$ Carleman positivity}.
The required analytic input is a positive regularised shifted-zero
moment functional with $\mu_{2n}^{1/(2n)}=O(n)$. The
Bombieri--Lagarias Li-coefficient bounds do not imply this estimate.
\item \textbf{Integration with the Ch~37 package}. The RH completion
package of \Cref{v4-arith:platonic:def:RH-package} requires P1, P2,
P3, H-P$^{\mathrm{Ar}}$, and Hamburger determinacy together. P1 is
conditional on arithmetic Positselski (scope 30--50 pages); P2
unconditional; P3 conditional on Koszul--Petersson compatibility
(scope 10--20 pages); H-P$^{\mathrm{Ar}}$ unresolved
(scope: RH-equivalent); determinacy reduces to
$(\mathrm{R}_{\mathrm{analytic}})$. Total scope: the same as RH,
plus some accounting.
\end{enumerate}

\begin{remark}[what route~3 contributes]
\label{v4-arith:hpar-det:rem:wave3-contribution}
Route~3 does not close either (A) H-P$^{\mathrm{Ar}}$ spectral
matching or (B) Hamburger determinacy; both remain RH-equivalent or
RH-adjacent open problems. What route~3 produces:
\begin{enumerate}
\item \emph{Conditional uniqueness of the weight system}:
the Berry--Keating $\lambda(m)=\log m$ is forced by additive
zeta/KMS normalisation.
\item \emph{Explicit identification of the trace-compatibility
hierarchy}: the infinite sequence of conditions is the regularised
Weil/Connes trace bridge, not a free consequence of the classical
Weil formula.
\item \emph{Failure of the Bombieri--Lagarias shortcut}: the
Li-coefficient bounds do not control Carleman moments.
\item \emph{The single analytic residual
$(\mathrm{R}_{\mathrm{analytic}})$}: Hamburger determinacy reduces
to positivity plus linear upper growth for the regularised moments.
\item \emph{Cross-check with Ch~37}: the three residuals (W), (H),
$(\mathrm{R}_{\mathrm{analytic}})$ jointly close the H-P/VB residual
after the conditional P1/P3 inputs are supplied.
\end{enumerate}
\end{remark}

\section{Summary}
\label{v4-arith:hpar-det:summary}

\begin{enumerate}
\item \textbf{Weight selection is uniquely determined after
normalisation}
(\Cref{v4-arith:hpar-det:thm:uniqueness-given-existence}). Among four
canonical tests, only the Berry--Keating $\lambda(m)=\log m$
survives as a BC semigroup weight with zeta partition function
(\Cref{v4-arith:hpar-det:thm:two-cancellations}).
\item \textbf{The trace-compatibility hierarchy is the regularised
Weil/Connes bridge}
(\Cref{v4-arith:hpar-det:thm:hierarchy-condition},
\Cref{v4-arith:hpar-det:cor:hierarchy-is-weil}). The
H-P$^{\mathrm{Ar}}$ trace identity needs an admissible extension of
the explicit formula to the BC heat-trace family.
\item \textbf{Hamburger determinacy reduces to a single analytic
positivity residual}
(\Cref{v4-arith:hpar-det:thm:single-analytic-residual}). Under
\((\mathrm{R}_{\mathrm{analytic}})\), the moments are positive and
satisfy $\mu_{2n}^{1/(2n)}=O(n)$, so Carleman's criterion holds.
\item \textbf{The Bombieri--Lagarias route fails as a closure}
(\Cref{v4-arith:hpar-det:prop:BL-carleman-partial}).
Li-coefficient bounds are oscillatory zero-sum bounds; they do not
give the positive moment upper-growth estimate needed for Carleman.
\item \textbf{Three precisely-named route~3 residuals}
(\Cref{v4-arith:hpar-det:cor:wave3-structure}): weight
normalisation (W), H-P trace bridge (H), and Carleman positivity
\((\mathrm{R}_{\mathrm{analytic}})\).
\item \textbf{What route~3 does not do}. Route~3 does not close
H-P$^{\mathrm{Ar}}$ (it reduces to the Connes absorption-spectrum
conjecture, which is equivalent to H-P$^{\mathrm{Ar}}$). Route~3
does not close Hamburger determinacy. Route~3 does not produce new
RH-equivalent positivity languages beyond the route~2 catalog of Det,
HB+, BD+.
\item \textbf{What route~3 does do}. Route~3 produces the sharpest
operational reduction of the Ch~37 single positivity corollary:
three precisely-stated residuals whose closure would turn the
conditional Vol~IV path into a proof.
\end{enumerate}

The obstacle is now visible in its sharp Vol~IV form: prove the
Bost--Connes absorption-spectrum bridge and prove positivity plus
Carleman growth for the regularised shifted-zero moments. These are
not bookkeeping gaps; they are the remaining mathematical substance.
