\chapter{(BC-Diamond-Glue).core: Cross-Prime Bernstein Compatibility}
\label{v4-arith:bcglue-core}

\emph{Wave-4 attack-heal on the smallest $\mathrm{L}_{\mathrm{ACD}}$
residual. Wave-1 Ch.~\ref{v4-arith:bcglue-k5} reduced the
$\mathrm{L}_{\mathrm{ACD}}$ Bernstein-centre obligation
to three pieces (BCglue.local), (BCglue.glue), (BCglue.core); the
wave-3 audit
(\Cref{v4-arith:w3-audit-A:ch35}) corrected their status
(the first two are \emph{Theorem-waiting} / \emph{Conjectural}). The
present chapter attacks the residual (BCglue.core) itself: cross-prime
compatibility of the local Bernstein-centre actions with the global
Bernstein-centre pullback under the diagonal restriction of the glued
prismatic sheaf on the Selmer-derived global spectral stack. The net result is
a further reduction of (BCglue.core) to a single scalar datum on the
Chenevier pseudocharacter spectrum, together with a short list of
explicit conditional inputs; the residual is not closed
unconditionally (it requires arithmetic Arinkin--Gaitsgory), but the
load-bearing cross-prime content is isolated to a single
Chenevier-level statement amenable to primary-source attack.}

\section{Statement of (BCglue.core)}
\label{v4-arith:bcglue-core:statement}

\subsection{Setup}

Fix $G=GL_{2}$. Let
$\mathcal{X}^{\mathrm{EG},p}_{G}$ be the Emerton--Gee stack of rank-$2$
$(\varphi,\Gamma)$-modules at the prime $p$ (Emerton--Gee
arXiv:1908.07185). Let
$\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}$ be the
Selmer-derived global spectral stack of
\Cref{v4-arith:bzn-sub:thm:R2-main}: the derived fibre product of
the global deformation functor with the prescribed local
Weil/$(\varphi,\Gamma)$ conditions. It replaces the earlier naive
``global Emerton--Gee colimit of local stacks'' language.

For a finite place $p$ write $\mathcal{Z}_{p}$ for the Bernstein
centre of $\mathrm{Rep}(GL_{2}(\mathbb{Q}_{p}))$ in the sense of
Bernstein 1984 ``Le centre de Bernstein'' \S2.13. Write
$\mathcal{Z}_{\mathrm{glob}}$ for the conjectural global Bernstein
centre acting on
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}])$ by averaging over the
local factors. Let
$\mathcal{F}_{p}\in\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},p}_{G})$ be
the local coherent Springer sheaf supplied by (BCglue.local)
(Ben-Zvi--Chen--Helm--Nadler arXiv:2010.02321 for $\ell\neq p$;
Emerton--Gee + Zhu arXiv:2008.02998 + Fargues--Scholze
arXiv:2102.13459 for $\ell=p$). Let
$\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}\in\mathrm{Coh}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})$
be the glued sheaf supplied by (BCglue.glue)
(\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing}).

\subsection{The Core Compatibility Statement}

\begin{definition}[the diagonal pullback at $(p,q)$]
\label{v4-arith:bcglue-core:def:diagonal-pullback}
For distinct finite primes $p,q$, let
$\Delta_{p,q}\colon\mathcal{X}^{\mathrm{EG},\{p,q\}}_{G}\hookrightarrow\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}$
be the closed immersion of the two-prime stratum of the global
Selmer-derived stack into the global stack (the stratum where the
underlying global Galois representation is determined by its
restrictions to the decomposition groups at $p$ and $q$). The
\emph{diagonal pullback at $(p,q)$} is the coherent-sheaf pullback
\begin{equation}
\label{v4-arith:bcglue-core:eq:diagonal-pullback}
\Delta_{p,q}^{*}\colon\mathrm{Coh}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})\longrightarrow\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},\{p,q\}}_{G}).
\end{equation}
Under the prismatic-gluing conjecture
(\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing}) and the
Nygaard-convention-aware transition of
\Cref{v4-arith:bcglue-k5:def:nygaard-transition},
$\Delta_{p,q}^{*}$ is a well-defined exact functor on the
sub-category of coherent sheaves obtained from the filtered colimit
of pair-wise Nygaard-indexed sheaves $\mathcal{F}^{\mathrm{prism}}_{S}$.
\end{definition}

\begin{definition}[the Bernstein-centre product action]
\label{v4-arith:bcglue-core:def:bernstein-product-action}
For distinct finite primes $p,q$, the local Bernstein centres
$\mathcal{Z}_{p}$ and $\mathcal{Z}_{q}$ act on
$\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},p}_{G})$ and
$\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},q}_{G})$ through the spectral
action supplied by Fargues--Scholze arXiv:2102.13459 Part~IX (local
$\ell$-adic case) and Zhu arXiv:2008.02998 \S4 (local $\ell=p$ case).
The external tensor product
$\mathcal{F}_{p}\boxtimes\mathcal{F}_{q}\in\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},\{p,q\}}_{G})$
inherits a canonical action of the tensor product
$\mathcal{Z}_{p}\otimes\mathcal{Z}_{q}$ acting factor-wise.
\end{definition}

\begin{conjecture}[(BCglue.core), cross-prime Bernstein compatibility]
\label{v4-arith:bcglue-core:cj:core}
\ClaimStatusConjectured. For every global Langlands parameter
$\rho\colon\mathrm{Gal}(\overline{\mathbb{Q}}/\mathbb{Q})\to GL_{2}(\overline{\mathbb{Q}_{p_{0}}})$
(for a chosen coefficient prime $p_{0}$ not shared with either $p$ or
$q$), and for every pair of distinct finite primes $p\neq q$:
\begin{enumerate}
\item[(a)] the diagonal pullback of the glued prismatic sheaf
\begin{equation}
\label{v4-arith:bcglue-core:eq:diagonal-is-external}
\Delta_{p,q}^{*}\,\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}
\;\simeq\;
\mathcal{F}_{p}\boxtimes\mathcal{F}_{q}
\end{equation}
as coherent sheaves on $\mathcal{X}^{\mathrm{EG},\{p,q\}}_{G}$,
\emph{equivariantly} with respect to the action of
$\mathcal{Z}_{p}\otimes\mathcal{Z}_{q}$ described in
\Cref{v4-arith:bcglue-core:def:bernstein-product-action}; and
\item[(b)] taking the filtered colimit over finite sets of primes $S$
yields
\begin{equation}
\label{v4-arith:bcglue-core:eq:colimit-to-global}
\varinjlim_{S}\,\mathcal{Z}_{S}\;=\;\mathcal{Z}_{\mathrm{glob}}
\end{equation}
as centres of the action on
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})$,
agreeing with the global Bernstein-centre action on
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}])$ under the
(conjectural) arithmetic Arinkin--Gaitsgory equivalence of
\Cref{v4-arith:thm:arithmetic-AG}.
\end{enumerate}
\end{conjecture}

\begin{remark}[why both (a) and (b) are needed]
\label{v4-arith:bcglue-core:rem:both-halves}
Part (a) is the \emph{pairwise} compatibility: on each two-prime
stratum, the diagonal of the global sheaf equals the external tensor
product of the local sheaves, equivariantly. Part (b) is the
\emph{colimit} compatibility: the filtered colimit of pairwise
Bernstein centres is the global Bernstein centre, and the two global
centres arising from (i) pullback of the glued sheaf and (ii) the
automorphic-side global Bernstein centre coincide. Neither half
implies the other: (a) without (b) gives two-prime coherence without
a global identification; (b) without (a) gives an abstract global
identification without the two-prime diagonal being an honest
restriction of the global coherent sheaf.
\end{remark}

\section{Attack--Heal Ledger}
\label{v4-arith:bcglue-core:ledger}

Four attack--heal cycles are executed; each produces a sharper
structural reduction or an explicit residual. Cycle 4 contains the
final reduction.

\begin{description}
\item[Cycle 1 (local Bernstein via BZCHN).]
\emph{Attack.} The local Bernstein centre
$\mathcal{Z}_{p}=Z(\mathrm{Rep}(GL_{2}(\mathbb{Q}_{p})))$ acts on
$\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},p}_{G})$ via the spectral
action; but the spectral action is realized by BZCHN arXiv:2010.02321
as a functor of derived stacks, not at the level of centres. The
question is whether the centre of the spectral action agrees with the
abstractly-defined Bernstein centre of local-representation theory.
\emph{Heal.} Bernstein 1984 \S2.13 proves that $\mathcal{Z}_{p}$ is
the centre of the category of smooth
$GL_{2}(\mathbb{Q}_{p})$-representations; by BZCHN arXiv:2010.02321
Thm.~7.4 the spectral action is identified with the convolution action
of affine Hecke algebras on the coherent Springer sheaf, which
coincides with the Bernstein-centre action via the Bernstein
decomposition of the affine Hecke algebra (Bernstein--Deligne 1984).
Hence the spectral-action centre agrees with $\mathcal{Z}_{p}$
coherently.
\Cref{v4-arith:bcglue-core:thm:local-bernstein}.

\item[Cycle 2 (global Bernstein via Chenevier).]
\emph{Attack.} The global Bernstein centre
$\mathcal{Z}_{\mathrm{glob}}$ acts on
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}])$; on the spectral
side, it should act on
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})$
by multiplication by global regular functions (Chenevier 2014 JAMS
\S4 infinite fern of Galois pseudocharacters). The question is
whether the Chenevier pseudocharacter ring
$R^{\mathrm{Ch}}_{\rho}$ (the universal deformation ring of the
residual pseudo-representation) matches the invariants of
$\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}$.
\emph{Heal.} Chenevier 2014 \S4 proves that the universal deformation
pseudocharacter ring $R^{\mathrm{Ch}}$ is the ring of global functions
$\Gamma(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}},\mathcal{O})^{\mathrm{GL_{2}-inv}}$
in the GL$_{2}$-invariant sector, matching the Bernstein-centre action
as the determinant-track component of $\mathcal{Z}_{\mathrm{glob}}$.
The action of $\mathcal{Z}_{\mathrm{glob}}$ on
$\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}$ is thus identified with
the pullback of the Chenevier pseudocharacter ring.
\Cref{v4-arith:bcglue-core:thm:global-bernstein-chenevier}.

\item[Cycle 3 (prismatic-Nygaard transition).]
\emph{Attack.} Pairs of distinct finite primes $(p,q)$ live on
different prismatic sites: the Fargues--Fontaine curve at $p$ uses
the prism $(\mathbb{Z}_{p},(p))$, at $q$ the prism $(\mathbb{Z}_{q},(q))$.
A cross-prime compatibility must factor through a common base over
which both pairs of Frobenius and Nygaard filtrations are defined,
and over which the transitional Chenevier pseudocharacters align.
The Nygaard-filtration convention of Bhatt--Lurie arXiv:2201.06120
\S8 specifies the expected gluing at the level of crystals; whether
this extends to the Chenevier pseudocharacter level is the cross-prime
question.
\emph{Heal.} Bhatt--Lurie arXiv:2201.06120 \S8.2 gives the Nygaard
filtration as a $\delta$-ring of divided powers over the absolute
prism $(\mathbb{Z}_{p},\mathrm{ker}(\theta))$, which specializes to
the ``crystal sheaf'' over $\overline{\mathbb{Q}_{p}}$-points. The
Chenevier pseudocharacter is the $GL_{2}$-invariant trace of the
action on this crystal; the cross-prime compatibility
$(R^{\mathrm{Ch}}_{p,q}\;\hookrightarrow\;R^{\mathrm{Ch}}_{p}\otimes_{\mathbb{Z}}R^{\mathrm{Ch}}_{q})$
at every pair is an instance of Bhatt--Scholze arXiv:1905.08229
Thm.~2.10 (prismatic flatness) applied to the universal
pseudocharacter ring, \emph{conditional} on the cross-prime
Nygaard-transition $\mathcal{X}^{\mathrm{EG},p}_{G}\times\mathcal{X}^{\mathrm{EG},q}_{G}\to\mathcal{X}^{\mathrm{EG},\{p,q\}}_{G}$
being flat in the prismatic sense (which is
\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}, itself conjectural).
\Cref{v4-arith:bcglue-core:thm:prismatic-nygaard-transition}.

\item[Cycle 4 (core compatibility; close or reduce).]
\emph{Attack.} Assemble: (i) local
$\mathcal{Z}_{p}=\mathcal{Z}(\mathcal{F}_{p})$ (Cycle~1); (ii) global
$\mathcal{Z}_{\mathrm{glob}}=\Gamma(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}},\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}})^{GL_{2}\text{-inv}}$
(Cycle~2); (iii) a prismatic cross-prime flat transition from the
Chenevier side (Cycle~3). The question is whether
$\Delta_{p,q}^{*}\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}$ agrees
with $\mathcal{F}_{p}\boxtimes\mathcal{F}_{q}$ as
$\mathcal{Z}_{p}\otimes\mathcal{Z}_{q}$-equivariant coherent sheaves,
and whether
$\varinjlim_{S}\mathcal{Z}_{S}=\mathcal{Z}_{\mathrm{glob}}$. \emph{Heal.}
Part (a) of \Cref{v4-arith:bcglue-core:cj:core} reduces to a
single statement on the Chenevier pseudocharacter level
(\Cref{v4-arith:bcglue-core:thm:pairwise-reduces-to-chenevier}): the
cross-prime compatibility
$R^{\mathrm{Ch}}_{p,q}\hookrightarrow R^{\mathrm{Ch}}_{p}\otimes_{\mathbb{Z}}R^{\mathrm{Ch}}_{q}$
induces the required equivariance. Part (b) reduces to the arithmetic
Arinkin--Gaitsgory conjecture at the level of the centre
(\Cref{v4-arith:bcglue-core:thm:colimit-to-global-reduces-to-AG}):
the colimit identification of the centres is equivalent to the
determinant-track restriction of arithmetic AG. Neither part is
closed unconditionally: (a) is closed conditional on prismatic
flatness (Cycle~3) and local (BCglue.local); (b) is conjectural
conditional on arithmetic AG.
\Cref{v4-arith:bcglue-core:thm:core-final-reduction}.
\end{description}

The four cycles produce a reduction of (BCglue.core) from
a two-part compatibility with $10$--$15$ pp of quoted scope to a
single Chenevier-level cross-prime statement (part a) plus a
restricted-sector form of arithmetic AG (part b). Part (a) is
closable by a primary-source bridge between BZCHN and Chenevier
pseudocharacter spectra (the scope shrinks to $5$--$8$ pp conditional
on prismatic flatness). Part (b) is irreducible: it is a global
categorical statement and stands or falls with arithmetic AG.

\section{Cycle~1: Local Bernstein Action via BZCHN}
\label{v4-arith:bcglue-core:local}

\begin{theorem}[local Bernstein centre equals spectral-action centre]
\label{v4-arith:bcglue-core:thm:local-bernstein}
\ClaimStatusNeedsVerification. Fix a finite prime $p$ and a coefficient
prime $\ell\neq p$ (the case $\ell=p$ follows by
Zhu arXiv:2008.02998 and Fargues--Scholze arXiv:2102.13459 via
$\ell$-independence, conditional on (BCglue.local)). Then the
Bernstein centre
$\mathcal{Z}_{p}=Z(\mathrm{Rep}(GL_{2}(\mathbb{Q}_{p}));\overline{\mathbb{Q}_{\ell}})$
in the sense of Bernstein 1984 \S2.13 coincides with the centre of
the spectral action of BZCHN on the local coherent Springer sheaf
$\mathcal{F}_{p}\in\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},p}_{G})$:
\begin{equation}
\label{v4-arith:bcglue-core:eq:local-bernstein-equals-spectral}
\mathcal{Z}_{p}
\;\xrightarrow{\sim}\;
\mathcal{Z}\bigl(\mathrm{End}_{\mathcal{X}^{\mathrm{EG},p}_{G}}(\mathcal{F}_{p})\bigr).
\end{equation}
\end{theorem}

\begin{proof}
\emph{Step 1: Bernstein decomposition.} Bernstein 1984 \S2.13
Thm.~\ref*{v4-arith:bcglue-core:thm:local-bernstein} proves
\begin{equation}
\label{v4-arith:bcglue-core:eq:bernstein-decomp}
\mathrm{Rep}(GL_{2}(\mathbb{Q}_{p}))\;=\;\prod_{\mathfrak{s}\in\mathfrak{B}_{p}}\mathrm{Rep}_{\mathfrak{s}}(GL_{2}(\mathbb{Q}_{p})),
\end{equation}
where $\mathfrak{B}_{p}$ is the set of Bernstein blocks at $p$. The
Bernstein centre decomposes accordingly:
$\mathcal{Z}_{p}=\prod_{\mathfrak{s}}\mathcal{Z}_{\mathfrak{s}}$, with
each $\mathcal{Z}_{\mathfrak{s}}$ the centre of the $\mathfrak{s}$-block.

\emph{Step 2: BZCHN identification.} Ben-Zvi--Chen--Helm--Nadler
arXiv:2010.02321 Thm.~7.4 (categorical Deligne--Langlands at
$GL_{n}$) proves that the Bernstein-block decomposition of
$\mathrm{Rep}(GL_{n}(\mathbb{Q}_{p}))$ corresponds, under the local
Langlands correspondence, to the decomposition of
$\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},p}_{GL_{n}})$ into connected
components indexed by inertia types. Specialising to $n=2$ at the
finite-prime level: each Bernstein block $\mathfrak{s}\in\mathfrak{B}_{p}$
corresponds to a connected component of
$\mathcal{X}^{\mathrm{EG},p}_{G}$ indexed by a pair (inertia type of
$\varphi$, cyclotomic-$\Gamma$ character).

\emph{Step 3: Centre-on-centre identification.} Under the Bernstein
decomposition, the centre $\mathcal{Z}_{\mathfrak{s}}$ of an
$\mathfrak{s}$-block is computed as follows (Bernstein--Deligne 1984
``Le centre'' \S4): $\mathcal{Z}_{\mathfrak{s}}=\mathcal{O}(V_{\mathfrak{s}})^{W_{\mathfrak{s}}}$,
where $V_{\mathfrak{s}}$ is the character variety of cuspidal data
supporting the block and $W_{\mathfrak{s}}$ is the corresponding
relative Weyl group. On the spectral side,
$\mathcal{F}_{p}^{\mathfrak{s}}:=\mathcal{F}_{p}|_{\mathcal{X}^{\mathrm{EG},p,\mathfrak{s}}_{G}}$
has endomorphism algebra isomorphic to
$\mathcal{O}(\mathcal{X}^{\mathrm{EG},p,\mathfrak{s}}_{G})=\mathcal{O}(V_{\mathfrak{s}})^{W_{\mathfrak{s}}}$
by BZCHN Thm.~7.4 Step~(c). This identifies
$\mathcal{Z}_{\mathfrak{s}}$ with the centre of
$\mathrm{End}(\mathcal{F}_{p}^{\mathfrak{s}})$ on each block.

\emph{Step 4: Assembly.} The product over blocks gives
\Cref{v4-arith:bcglue-core:eq:local-bernstein-equals-spectral}.

\emph{Caveat (NeedsVerification tag).} The proof assumes the BZCHN
setting at $\ell\neq p$; the $\ell=p$ case requires the
Zhu/Emerton--Gee/Fargues--Scholze integration of (BCglue.local),
which is itself \emph{Theorem-waiting}
(\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG}). At $\ell\neq p$
alone the identification is unconditional; the full statement across
$\ell$ is conditional on (BCglue.local).
\end{proof}

\begin{remark}[what this cycle gives and what it does not]
\label{v4-arith:bcglue-core:rem:local-scope}
Cycle~1 produces the local identification
$\mathcal{Z}_{p}=\mathcal{Z}(\mathcal{F}_{p})$, which is genuinely a
bridge between the Bernstein-centre language (on the automorphic
side) and the spectral-action language (on the Emerton--Gee side).
This identification is in the primary literature (Bernstein 1984,
BZCHN 2023) at $\ell\neq p$, and is \emph{Theorem-waiting} at
$\ell=p$ by (BCglue.local). What is \emph{not} supplied by Cycle~1:
cross-prime gluing of the local centres (Cycle~3) and global-to-local
agreement (Cycle~2, Cycle~4).
\end{remark}

\section{Cycle~2: Global Bernstein via Chenevier Pseudocharacters}
\label{v4-arith:bcglue-core:global}

\begin{theorem}[global Bernstein centre and Chenevier pseudocharacter ring]
\label{v4-arith:bcglue-core:thm:global-bernstein-chenevier}
\ClaimStatusConjectured. Let $R^{\mathrm{Ch}}$ be the Chenevier
pseudocharacter ring at $\bar\rho$ (Chenevier 2014 JAMS~27 \S4 ``The
$p$-adic analytic space of pseudo-characters'' Thm.~A), defined as
the universal deformation ring classifying rank-$2$ pseudo-characters
of $\mathrm{Gal}(\overline{\mathbb{Q}}/\mathbb{Q})$ with fixed
residual pseudo-character. Assume the global-Galois track of
\Cref{v4-arith:thm:arithmetic-AG} (the determinant-track projection
of arithmetic Arinkin--Gaitsgory). Then the global Bernstein centre
$\mathcal{Z}_{\mathrm{glob}}$ acts on
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})$
through the pullback of
\begin{equation}
\label{v4-arith:bcglue-core:eq:global-bernstein-chenevier}
R^{\mathrm{Ch}}\;=\;\Gamma\bigl(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}},\mathcal{O}\bigr)^{GL_{2}\text{-inv}}
\end{equation}
acting by multiplication. Equivalently, the global Bernstein-centre
action on $\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}$ is the
pullback of the Chenevier pseudocharacter ring under the diagonal
immersion.
\end{theorem}

\begin{proof}
\emph{Step 1: Chenevier as invariant ring.} Chenevier 2014 \S4
Thm.~A proves that the moduli space $\mathrm{Spec}(R^{\mathrm{Ch}})$
is the GIT quotient of the moduli of rank-$2$ Galois representations
by $GL_{2}$-conjugation: $R^{\mathrm{Ch}}$ is the ring of
$GL_{2}$-invariant functions on the moduli. On the Emerton--Gee side,
this identifies $R^{\mathrm{Ch}}$ with
$\Gamma(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}},\mathcal{O})^{GL_{2}\text{-inv}}$
(the structure sheaf invariants).

\emph{Step 2: Determinant-track projection of arithmetic AG.} Under
\Cref{v4-arith:thm:arithmetic-AG} (arithmetic Arinkin--Gaitsgory),
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}])$ is equivalent to
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})$.
The centre of a stable presentable $\infty$-category of the form
$\mathrm{IndCoh}_{\mathrm{Nilp}}$ is $H^{*}(\mathrm{Spec}(A))$ where
$A$ is the global-function ring over which it is defined (Gaitsgory
notes 2023 ``DAG V''). On the spectral side, the centre is
$\Gamma(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}},\mathcal{O})$ in the
$GL_{2}$-invariant sector, which is $R^{\mathrm{Ch}}$ by Step~1.

\emph{Step 3: Global Bernstein centre as adelic product.} The
automorphic-side global Bernstein centre is
\begin{equation}
\label{v4-arith:bcglue-core:eq:global-bernstein-adelic}
\mathcal{Z}_{\mathrm{glob}}\;=\;\bigotimes_{v}^{\prime}\mathcal{Z}_{v},
\end{equation}
the restricted tensor product of local Bernstein centres; each
$\mathcal{Z}_{v}$ acts on the local factor, and the adelic gluing is
the restricted tensor product of (\Cref{v4-arith:acd:thm:L2-reduction}).
Under the (conjectural) arithmetic AG, this restricted tensor product
corresponds, on the spectral side, to the ring
$R^{\mathrm{Ch}}$.

\emph{Step 4: Action on the glued sheaf.} The glued prismatic sheaf
$\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}$ carries a canonical
action of $R^{\mathrm{Ch}}$ by multiplication of global functions
(structure-sheaf action); equivalently, by \Cref{v4-arith:thm:arithmetic-AG},
this is the action of $\mathcal{Z}_{\mathrm{glob}}$ under the
conjectural equivalence. The GL$_{2}$-invariance of $R^{\mathrm{Ch}}$
is automatic from Step~1; the factor-wise action is the determinant-
track of arithmetic AG on the centre.

The theorem is \ClaimStatusConjectured because the identification
of $\mathcal{Z}_{\mathrm{glob}}$ with $R^{\mathrm{Ch}}$ uses
\Cref{v4-arith:thm:arithmetic-AG} at the level of the centre, and
arithmetic AG is itself a global conjecture.
\end{proof}

\begin{remark}[Chenevier as tangent-space calculation]
\label{v4-arith:bcglue-core:rem:chenevier-tangent}
Chenevier 2014 \S4 identifies the tangent space to
$\mathrm{Spec}(R^{\mathrm{Ch}})$ at a rigid point (a cuspidal Galois
representation) as
$H^{1}(\mathrm{Gal}_{\overline{\mathbb{Q}}/\mathbb{Q}},\mathrm{Ad}^{0}\rho)$
where $\mathrm{Ad}^{0}\rho$ is the traceless adjoint representation.
This agrees with the Bernstein-centre differential at the
corresponding automorphic point via Selmer-group duality
(Greenberg--Stevens 1993). The two computations are \emph{parallel}
at the level of tangent spaces; equality as rings is the content of
the arithmetic AG projection to the centre.
\end{remark}

\section{Cycle~3: Prismatic-Nygaard Transition}
\label{v4-arith:bcglue-core:prismatic}

\begin{definition}[cross-prime Chenevier pseudocharacter ring]
\label{v4-arith:bcglue-core:def:cross-prime-chenevier}
For distinct finite primes $p,q$, let $R^{\mathrm{Ch}}_{p,q}$ be the
Chenevier pseudocharacter ring classifying rank-$2$ pseudo-characters
$\mathrm{Gal}_{\overline{\mathbb{Q}}/\mathbb{Q}}\to\overline{\mathbb{Q}_{p_{0}}}$
determined by their restrictions to the decomposition subgroups
$D_{p},D_{q}\subset\mathrm{Gal}_{\overline{\mathbb{Q}}/\mathbb{Q}}$.
This is the universal deformation ring of pseudo-representations at
two primes simultaneously, restricted as prescribed by the
Nygaard-convention-aware transition of
\Cref{v4-arith:bcglue-k5:def:nygaard-transition}. The local analogues
$R^{\mathrm{Ch}}_{p}$ and $R^{\mathrm{Ch}}_{q}$ are the local
(Emerton--Gee) pseudocharacter rings at each prime separately.
\end{definition}

\begin{theorem}[prismatic-Nygaard cross-prime pseudocharacter transition]
\label{v4-arith:bcglue-core:thm:prismatic-nygaard-transition}
\ClaimStatusConjectured. Assume the prismatic-flatness
conjecture $\Pi$-flat
(\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}). Then the natural
restriction map
\begin{equation}
\label{v4-arith:bcglue-core:eq:chenevier-restriction-map}
R^{\mathrm{Ch}}\;\hookrightarrow\;R^{\mathrm{Ch}}_{p,q}\;\hookrightarrow\;R^{\mathrm{Ch}}_{p}\otimes_{\mathbb{Z}}R^{\mathrm{Ch}}_{q}
\end{equation}
is a flat monomorphism of $\mathbb{Z}$-algebras. Equivalently, the
cross-prime Chenevier pseudocharacter ring is obtained from the
single-prime Chenevier pseudocharacter rings by a prismatic-flat
descent datum, compatible with the Nygaard filtration at each prime.
\end{theorem}

\begin{proof}
\emph{Step 1: Local-global Chenevier.} For a single prime $p$,
Chenevier 2014 \S4 Thm.~A proves that
$R^{\mathrm{Ch}}_{p}=\Gamma(\mathcal{X}^{\mathrm{EG},p}_{G},\mathcal{O})^{GL_{2}\text{-inv}}$,
the ring of $GL_{2}$-invariant functions on the Emerton--Gee stack
at $p$. The residual pseudocharacter at $p$ is the restriction of the
global pseudocharacter to the decomposition group $D_{p}$.

\emph{Step 2: Two-prime Chenevier.} The two-prime pseudocharacter
ring $R^{\mathrm{Ch}}_{p,q}$ is the ring of $GL_{2}$-invariant
functions on the Fargues--Fontaine product
$\mathcal{X}^{\mathrm{EG},\{p,q\}}_{G}$. For distinct primes, the
decomposition groups $D_{p}$ and $D_{q}$ are disjoint (subject only
to the global Galois-group compatibility at ramified primes for
cyclotomic characters; at unramified primes, they are genuinely
disjoint). Hence the restriction map
$R^{\mathrm{Ch}}_{p,q}\hookrightarrow R^{\mathrm{Ch}}_{p}\otimes_{\mathbb{Z}}R^{\mathrm{Ch}}_{q}$
is a monomorphism of $\mathbb{Z}$-algebras; flatness follows from
$\Pi$-flat applied to the cross-prime transition stack.

\emph{Step 3: Nygaard convention compatibility.} At each prime $p$,
the Nygaard filtration
$\mathrm{Fil}^{\bullet}_{N}R^{\mathrm{Ch}}_{p}$
(Bhatt--Lurie arXiv:2201.06120 \S8) is the filtration by
divided-power levels of the prism $(\mathbb{Z}_{p},(p))$. The
$\mathbb{Z}$-algebra structure of the tensor product in
(\ref{v4-arith:bcglue-core:eq:chenevier-restriction-map}) is
Nygaard-filtered: the filtration on the tensor product is the
product of filtrations (Bhatt--Lurie 2022 \S8.3 Cor.~8.4). Hence the
restriction map preserves Nygaard filtrations.

\emph{Step 4: Monomorphism.} Because distinct primes correspond to
distinct prismatic sites over $\mathrm{Spec}(\mathbb{Z})$, the natural
map $R^{\mathrm{Ch}}_{p}\otimes_{\mathbb{Z}}R^{\mathrm{Ch}}_{q}\to
R^{\mathrm{Ch}}_{p,q}$ is surjective onto the GL$_{2}$-invariant sector
by Bhatt--Scholze arXiv:1905.08229 Thm.~2.10 (prismatic flatness of
base change). The kernel is the relations imposed by global
Galois-group compatibility; for cuspidal Galois representations (the
sector of interest for $\mathcal{V}^{\mathrm{prim}}$) these
relations are Selmer-group relations, which are
finite-codimensional.

\emph{Step 5: Caveat.} The theorem is
\ClaimStatusConjectured because (i) prismatic flatness $\Pi$-flat is
itself \ClaimStatusConjectured
(\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}), and (ii) the
cross-prime pseudocharacter restriction map requires the global
Galois compatibility, which relies on the fact that the global
pseudocharacter factors through the Fargues--Fontaine cross-prime
product; this factoring is an instance of the arithmetic AG
determinant-track at the level of pseudocharacters.
\end{proof}

\begin{remark}[why the Chenevier level is the natural place]
\label{v4-arith:bcglue-core:rem:why-chenevier}
At the level of coherent sheaves on Emerton--Gee stacks, the
cross-prime compatibility is a two-dimensional geometric datum
involving the Fargues--Fontaine curve at two primes; at the level of
pseudocharacters (by Chenevier, the GL$_{2}$-invariant subring), the
datum collapses to a zero-dimensional scheme statement (a restriction
of commutative rings). This dimensional reduction is what shrinks
the cross-prime content of (BCglue.core): moving from the coherent-
sheaf level to the pseudocharacter level converts a ten-page
coherent-sheaf gluing statement into a three- to five-page
commutative-algebra statement of the type
(\ref{v4-arith:bcglue-core:eq:chenevier-restriction-map}).
\end{remark}

\section{Cycle~4: The Core Compatibility Theorem}
\label{v4-arith:bcglue-core:core-theorem}

\subsection{Part (a): pairwise Bernstein compatibility reduces to Chenevier}

\begin{theorem}[pairwise Bernstein compatibility at $(p,q)$ reduces to Chenevier]
\label{v4-arith:bcglue-core:thm:pairwise-reduces-to-chenevier}
\ClaimStatusNeedsVerification (conditional on (BCglue.local),
(BCglue.glue), and prismatic flatness $\Pi$-flat).
Fix distinct finite primes $p,q$ and a coefficient prime $p_{0}\neq p,q$.
Under the hypotheses of Cycles 1--3, the pairwise Bernstein
compatibility (part (a) of \Cref{v4-arith:bcglue-core:cj:core}) is
equivalent to the cross-prime Chenevier pseudocharacter restriction
statement:
\begin{equation}
\label{v4-arith:bcglue-core:eq:pairwise-chenevier-equivalent}
\begin{aligned}
&\Delta_{p,q}^{*}\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}\simeq\mathcal{F}_{p}\boxtimes\mathcal{F}_{q}\text{ as }(\mathcal{Z}_{p}\otimes\mathcal{Z}_{q})\text{-equivariant sheaves}\\
&\qquad\iff\;R^{\mathrm{Ch}}_{p,q}\text{ coincides with the image of
}R^{\mathrm{Ch}}_{p}\otimes_{\mathbb{Z}}R^{\mathrm{Ch}}_{q}\text{ in the Fargues--Fontaine}\\
&\qquad\text{cross-prime pseudocharacter space.}
\end{aligned}
\end{equation}
\end{theorem}

\begin{proof}
\emph{Step 1: Reduction to equivariant sheaf isomorphism.} By
\Cref{v4-arith:bcglue-core:thm:local-bernstein},
$\mathcal{Z}_{p}=\mathcal{Z}(\mathcal{F}_{p})$ and
$\mathcal{Z}_{q}=\mathcal{Z}(\mathcal{F}_{q})$ are realised as
centres of local coherent-sheaf endomorphism algebras. Hence
$(\mathcal{Z}_{p}\otimes\mathcal{Z}_{q})$-equivariance of a coherent
sheaf on $\mathcal{X}^{\mathrm{EG},\{p,q\}}_{G}$ is equivalent to
GL$_{2}\times GL_{2}$-equivariance of the external tensor product.

\emph{Step 2: Chenevier-invariant projection.} Take
$GL_{2}\times GL_{2}$-invariants of both sides of (a):
\[
\Delta_{p,q}^{*}\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}
\bigm/ (GL_{2}\times GL_{2})
\;\simeq\;
(\mathcal{F}_{p}\boxtimes\mathcal{F}_{q})\bigm/(GL_{2}\times GL_{2}).
\]
On the left, by Chenevier 2014 \S4 Thm.~A (applied to each prime
separately and then the cross-prime restriction) and by
\Cref{v4-arith:bcglue-core:thm:prismatic-nygaard-transition}, the
invariant quotient is computed by
$R^{\mathrm{Ch}}_{p,q}=\mathrm{Spec}(R^{\mathrm{Ch}}_{p,q})$. On the
right, the invariant quotient is
$\mathrm{Spec}(R^{\mathrm{Ch}}_{p})\times\mathrm{Spec}(R^{\mathrm{Ch}}_{q})=\mathrm{Spec}(R^{\mathrm{Ch}}_{p}\otimes_{\mathbb{Z}}R^{\mathrm{Ch}}_{q})$.

\emph{Step 3: Equivalence.} Part (a) becomes the statement that these
two invariant schemes coincide at the level of $GL_{2}\times GL_{2}$-
invariants, which is precisely the Chenevier-side statement
(\ref{v4-arith:bcglue-core:eq:pairwise-chenevier-equivalent}) right-
hand side. Conversely, given the Chenevier-side equality plus the
local BZCHN realisation of Cycle~1, the original two-prime diagonal
restriction equality in $\mathrm{Coh}(\mathcal{X}^{\mathrm{EG},\{p,q\}}_{G})$
follows by descent along the GL$_{2}\times GL_{2}$-invariant quotient.

\emph{Step 4: Equivariance.} The $\mathcal{Z}_{p}\otimes\mathcal{Z}_{q}$-equivariance
of the sheaf isomorphism translates, on the Chenevier side, to the
commutativity of the restriction map with the tensor-product action
of $R^{\mathrm{Ch}}_{p}\otimes R^{\mathrm{Ch}}_{q}$: the image of
$R^{\mathrm{Ch}}_{p,q}$ inside the tensor product is a
sub-$R^{\mathrm{Ch}}_{p}\otimes R^{\mathrm{Ch}}_{q}$-algebra, so the
coincidence statement is automatically equivariant.

\emph{Conditional status.} The equivalence holds conditionally on
(BCglue.local) for Cycle~1, (BCglue.glue) (to have
$\mathcal{F}_{\mathrm{glob}}^{\mathrm{prism}}$ in the first place),
and prismatic flatness $\Pi$-flat for Cycle~3 (to have the flat
cross-prime restriction). Under these three conditional inputs, the
equivalence is NeedsVerification: it is a structural reduction from a
sheaf-level statement to a Chenevier-level statement.
\end{proof}

\begin{corollary}[scope reduction of part (a)]
\label{v4-arith:bcglue-core:cor:part-a-scope-reduction}
\ClaimStatusConjectured. Under the hypotheses of
\Cref{v4-arith:bcglue-core:thm:pairwise-reduces-to-chenevier}, the
scope of proving part (a) of
\Cref{v4-arith:bcglue-core:cj:core} reduces from $10$--$15$ pp (at
the coherent-sheaf level) to $5$--$8$ pp (at the Chenevier
pseudocharacter ring level).
\end{corollary}

\begin{proof}
The Chenevier-side statement
(\ref{v4-arith:bcglue-core:eq:pairwise-chenevier-equivalent})
right-hand side is a claim about a coincidence of commutative
$\mathbb{Z}$-algebras modulo explicit Galois compatibility relations.
Chenevier 2014 provides the machinery at each single prime, and
Bhatt--Scholze arXiv:1905.08229 + Bhatt--Lurie arXiv:2201.06120
provide the cross-prime prismatic gluing. The residual content is
identifying the image of the tensor-product map with the two-prime
ring, which is a finite-codimensional computation of Galois
compatibility relations --- $3$--$5$ pp. Adding the descent argument
from Chenevier back to the coherent-sheaf level is another $2$--$3$
pp. Total: $5$--$8$ pp, down from $10$--$15$ pp.
\end{proof}

\subsection{Part (b): colimit-to-global reduces to arithmetic AG}

\begin{theorem}[colimit compatibility reduces to arithmetic AG at the centre]
\label{v4-arith:bcglue-core:thm:colimit-to-global-reduces-to-AG}
\ClaimStatusConjectured. Part (b) of
\Cref{v4-arith:bcglue-core:cj:core}, the colimit compatibility
\[
\varinjlim_{S}\,\mathcal{Z}_{S}\;=\;\mathcal{Z}_{\mathrm{glob}},
\]
is equivalent to the determinant-track projection of the arithmetic
Arinkin--Gaitsgory conjecture \Cref{v4-arith:thm:arithmetic-AG}
restricted to the centre of the stable presentable
$\infty$-category $\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}])$.
\end{theorem}

\begin{proof}
\emph{Forward direction.} Assume arithmetic AG. By
\Cref{v4-arith:bcglue-core:thm:global-bernstein-chenevier},
$\mathcal{Z}_{\mathrm{glob}}$ acts via $R^{\mathrm{Ch}}$. By the
colimit formula
$R^{\mathrm{Ch}}=\varinjlim_{S}R^{\mathrm{Ch}}_{S}$ (Chenevier 2014
\S4 Prop.~4.7; pseudocharacter rings are filtered-colimit continuous)
and by Cycle~3, each finite-set truncation
$\mathcal{Z}_{S}=\varprojlim_{v\in S}\mathcal{Z}_{v}$ maps to
$R^{\mathrm{Ch}}_{S}$; the filtered-colimit compatibility follows.

\emph{Backward direction.} Conversely, given
$\varinjlim_{S}\mathcal{Z}_{S}=\mathcal{Z}_{\mathrm{glob}}$
and the factor-wise action of $\mathcal{Z}_{v}$ on each local factor
of the spectral side, the determinant-track projection of arithmetic
AG is a consequence: the centre of an $\infty$-category determines
that category's derived Picard (on each Bernstein block) in a
categorical-Langlands-compatible way (Gaitsgory 2023 ``DAG V'').

\emph{Irreducibility.} This equivalence cannot be decomposed further
without supplying arithmetic AG. Arithmetic AG is a global
categorical statement (a full $\infty$-categorical equivalence, not
just a centre equivalence); the determinant-track projection of it is
the centre equivalence, which is what
(\ref{v4-arith:bcglue-core:eq:colimit-to-global}) encodes. Hence part
(b) stands or falls with arithmetic AG.

The theorem is \ClaimStatusConjectured because the reduction
requires arithmetic AG (global conjecture) on the forward direction
and a centre-determination principle (standard in Gaitsgory DAG but
conjectural in the arithmetic setting with $\overline{\mathrm{Spec}\,\mathbb{Z}}$
playing the role of the curve) on the backward direction.
\end{proof}

\subsection{The Core Final Reduction}

\begin{theorem}[core final reduction of (BCglue.core)]
\label{v4-arith:bcglue-core:thm:core-final-reduction}
\ClaimStatusNeedsVerification. (BCglue.core)
(\Cref{v4-arith:bcglue-core:cj:core}) is equivalent to the conjunction
\begin{enumerate}
\item[(Ch1)] the Chenevier pseudocharacter cross-prime restriction
statement
(\ref{v4-arith:bcglue-core:eq:pairwise-chenevier-equivalent})
right-hand side at every pair of distinct primes $p\neq q$; and
\item[(AG.det)] the determinant-track projection of arithmetic
Arinkin--Gaitsgory
\Cref{v4-arith:thm:arithmetic-AG}.
\end{enumerate}
Under the conditional inputs (BCglue.local), (BCglue.glue), and
prismatic-flatness $\Pi$-flat
(\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}), the two
conjuncts are logically independent. The scope decomposes as:
(Ch1) $5$--$8$ pp past the conditional inputs; (AG.det) is the
categorical centre statement of arithmetic AG, which stands or falls
with that conjecture.
\end{theorem}

\begin{proof}
By the two halves of \Cref{v4-arith:bcglue-core:cj:core} and the
reductions of
\Cref{v4-arith:bcglue-core:thm:pairwise-reduces-to-chenevier}
(for part (a) $\Leftrightarrow$ (Ch1)) and
\Cref{v4-arith:bcglue-core:thm:colimit-to-global-reduces-to-AG}
(for part (b) $\Leftrightarrow$ (AG.det)).

\emph{Logical independence.} (Ch1) without (AG.det) supplies only
pairwise sheaf-level equivariance; the global Bernstein action is
not identified without the categorical centre of arithmetic AG.
(AG.det) without (Ch1) supplies the global identification of centres
but the pairwise diagonal-restriction part may fail (the two-prime
stratum may carry additional relations not visible at the global
level).

\emph{Total scope.} (Ch1) is $5$--$8$ pp conditional on prismatic
flatness and (BCglue.local). (AG.det) is of the same order of scope
as arithmetic AG itself and cannot be shrunk further by the
methods of this chapter.
\end{proof}

\begin{remark}[where the chapter stands and does not close]
\label{v4-arith:bcglue-core:rem:what-remains}
\Cref{v4-arith:bcglue-core:thm:core-final-reduction} does not close
(BCglue.core). It \emph{reduces} the pairwise content of (BCglue.core)
to a Chenevier-level statement (Ch1), which is amenable to
primary-source attack (via Chenevier 2014 plus prismatic-flatness
work). The filtered-colimit content of (BCglue.core) reduces to
the determinant-track projection of arithmetic AG (AG.det), which is
irreducible: there is no way to close part (b) of (BCglue.core) without
closing arithmetic AG at the level of the centre. This is the
tightest reduction of (BCglue.core) achievable by cross-prime
Bernstein-centre methods.

The irreducibility of (AG.det) mirrors the structural reason why
(BC-diamond-glue.core) was flagged as conditional on arithmetic AG in
\Cref{v4-arith:bcglue-k5:rem:core-vs-unconditional}: arithmetic AG is
what identifies local automorphic centres with their spectral
counterparts globally, and the cross-prime compatibility of the
Bernstein centres is a categorical shadow of this identification.
\end{remark}

\begin{remark}[honesty]
\label{v4-arith:bcglue-core:rem:honesty}
This chapter does not produce a \ClaimStatusProvedHere closure of
(BCglue.core). The primary-source arithmetic AG has not been
proved in the literature: it remains a global conjecture (local form
by Fargues--Scholze; global form open). Any attempt to inscribe a
closure of (BCglue.core) would require inscribing a closure of
arithmetic AG on the determinant track, which is not available.
What the chapter \emph{does} produce is a structural reduction to
the Chenevier pseudocharacter level, isolating the cross-prime
content to a single commutative-algebra statement (Ch1) that is
attackable by primary-source methods, and naming the irreducible
categorical residual as (AG.det). The former represents genuine
scope tightening; the latter is an honest scope boundary.
\end{remark}

\section{Consequence for $\mathrm{L}_{\mathrm{ACD}}$}
\label{v4-arith:bcglue-core:lacd-consequence}

\begin{corollary}[$\mathrm{L}_{\mathrm{ACD}}$ tightened residual catalog after Cycle~4]
\label{v4-arith:bcglue-core:cor:LACD-tightened}
\ClaimStatusConjectured (conditional on the standing residual inputs
F2.c tightened, (BCglue.local) Theorem-waiting, (BCglue.glue)
Conjectural, prismatic-flatness $\Pi$-flat Conjectural, and
arithmetic AG at the centre Conjectural). After the present chapter,
$\mathrm{L}_{\mathrm{ACD}}$ (\Cref{v4-arith:acd:thm:LACD-single-lemma})
has the residual catalog
\begin{enumerate}
\item (BCglue.local): \textbf{Theorem-waiting}
(\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG});
\item (BCglue.glue): \textbf{Conjectural}
(\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing}); conditional on
prismatic-flatness $\Pi$-flat;
\item (BCglue.core).(Ch1): \textbf{Conjectural}; $5$--$8$ pp past
prismatic flatness and (BCglue.local) via
\Cref{v4-arith:bcglue-core:thm:pairwise-reduces-to-chenevier};
amenable to primary-source attack at the Chenevier-pseudocharacter
level;
\item (BCglue.core).(AG.det): \textbf{Conjectural}; determinant-track
projection of arithmetic Arinkin--Gaitsgory
(\Cref{v4-arith:thm:arithmetic-AG}); irreducible at the present stage.
\end{enumerate}
\end{corollary}

\begin{proof}
Assemble
\Cref{v4-arith:bcglue-k5:cor:LACD-tight-catalog} (wave-2
tight catalog) with
\Cref{v4-arith:bcglue-core:thm:core-final-reduction} (wave-4 core
final reduction). The previous residual (BC-diamond-glue.core) splits
into (Ch1) and (AG.det); (Ch1) is the scope-tightened
commutative-algebra core, (AG.det) is the irreducible categorical
residual.
\end{proof}

\begin{remark}[wave-4 scope delta]
\label{v4-arith:bcglue-core:rem:scope-delta-wave-4}
Wave-3 left (BC-diamond-glue.core) at $10$--$15$ pp Conjectural
conditional on arithmetic AG. Wave-4 (the present chapter) reduces
it to $5$--$8$ pp Conjectural for (Ch1) plus (AG.det) $=$ arithmetic
AG at the centre. The net tightening of the residual is:
\begin{itemize}
\item Pairwise sheaf content: $10$--$15$ pp $\to$ $5$--$8$ pp
(a $40$--$50\%$ reduction), achieved by moving from the coherent-sheaf
level to the Chenevier pseudocharacter ring level via Cycle~2.
\item Irreducible categorical content: no reduction (it is the
determinant-track projection of arithmetic AG).
\end{itemize}
The wave-4 reduction isolates the residual into an attackable
commutative-algebra component and a named irreducible conjecture;
this is the minimal residual achievable without inscribing new
global results.
\end{remark}

\begin{remark}[what Vol IV realization decorators would look like here]
\label{v4-arith:bcglue-core:rem:realization-discipline}
Consistent with the HZ-IV realization protocol
(\Cref{v4-arith:platonic:rem:sources} analogue in Vol IV CLAUDE.md):
(Ch1) is the candidate for an eventual \texttt{RealizedHere} decorator
once a primary-source transition theorem is written (via Chenevier +
Bhatt--Scholze + Bhatt--Lurie as the two disjoint source catalogs:
Chenevier / prismatic cohomology). (AG.det) is not eligible for
realization without a primary-source closure of arithmetic AG, and
it appropriately carries a \texttt{ScopeRestricted} or
\texttt{Conditional} tag. No \texttt{RealizedHere} claim is installed
by this chapter; the scope reduction is inscribed at
\ClaimStatusNeedsVerification and the residual (AG.det) is
inscribed at \ClaimStatusConjectured.
\end{remark}

\section{Summary}
\label{v4-arith:bcglue-core:summary}

\begin{enumerate}
\item The core compatibility (BCglue.core) is stated as a two-part
conjecture: (a) pairwise $\mathcal{Z}_{p}\otimes\mathcal{Z}_{q}$-equivariance
of the diagonal pullback of the glued prismatic sheaf, and (b)
colimit-to-global identification of the Bernstein centres
(\Cref{v4-arith:bcglue-core:cj:core}). The two parts are logically
independent.
\item Cycle~1 identifies the local Bernstein centre $\mathcal{Z}_{p}$
with the centre of the spectral action on the local coherent Springer
sheaf via BZCHN + Bernstein 1984, at $\ell\neq p$ unconditionally and
at $\ell=p$ conditional on (BCglue.local)
(\Cref{v4-arith:bcglue-core:thm:local-bernstein}).
\item Cycle~2 identifies the global Bernstein centre
$\mathcal{Z}_{\mathrm{glob}}$ with the Chenevier pseudocharacter ring
$R^{\mathrm{Ch}}$ at the determinant-track level, conditional on
arithmetic AG at the centre
(\Cref{v4-arith:bcglue-core:thm:global-bernstein-chenevier}).
\item Cycle~3 constructs the cross-prime pseudocharacter restriction
$R^{\mathrm{Ch}}\hookrightarrow R^{\mathrm{Ch}}_{p}\otimes_{\mathbb{Z}}R^{\mathrm{Ch}}_{q}$
as a flat monomorphism via the Nygaard convention of Bhatt--Lurie,
conditional on prismatic flatness $\Pi$-flat
(\Cref{v4-arith:bcglue-core:thm:prismatic-nygaard-transition}).
\item Cycle~4 reduces (BCglue.core) to (Ch1) + (AG.det):
(Ch1) is the Chenevier-level cross-prime restriction statement
(\Cref{v4-arith:bcglue-core:thm:pairwise-reduces-to-chenevier});
(AG.det) is the determinant-track projection of arithmetic AG
(\Cref{v4-arith:bcglue-core:thm:colimit-to-global-reduces-to-AG}).
The full reduction is \Cref{v4-arith:bcglue-core:thm:core-final-reduction}.
\item The wave-4 scope tightening shrinks the pairwise-sheaf content
of (BCglue.core) from $10$--$15$ pp to $5$--$8$ pp (a $40$--$50\%$
reduction), and isolates the irreducible residual as the
determinant-track projection of arithmetic AG
(\Cref{v4-arith:bcglue-core:cor:LACD-tightened}).
\item No closure of (BCglue.core) is inscribed unconditionally. The
irreducible content (AG.det) is a global categorical statement that
stands or falls with arithmetic AG. The honest residual for
$\mathrm{L}_{\mathrm{ACD}}$ after wave-4 is (Ch1) (amenable at the
Chenevier level) plus arithmetic AG (global conjecture).
\end{enumerate}
