\chapter{Arithmetic Positselski: Primitive Zeta-Character Theorem}
\label{v4-arith:prim-zeta-char}

\emph{Of the five open Positselski sub-items named in the wave-3 audit
(\Cref{v4-arith:pos:rem:open-sub-items}, OC1 of
\Cref{v4-arith:w3-audit-B:tab:overclaims}), four concern categorical
machinery (continuous duals, derived completion, faithful lifting,
Koszul-dual Bost--Connes) and one concerns character arithmetic. This
chapter closes the character-arithmetic sub-item: the
\emph{primitive zeta-character theorem}, which asserts that the
character of the primary subspace
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ is the
completed Riemann zeta function
$\xi(s)=\Gamma_{\mathbb{R}}(s)\zeta(s)$ under the HY-zeta grading,
and that this character is Koszul-self-dual in the Positselski
pairing sense. The proof uses Tate's 1950 Mellin--theta symmetry on
the archimedean sector, the Bost--Connes 1995 KMS$_{\beta}$ partition
function on the Hecke cobar side, and Julia's 1990 primon-gas
identification of the Heisenberg Fock character as $\zeta$; these
three inputs are disjoint sources in the wave-1/wave-2 ledger sense.
The primary subspace is defined as the kernel of the archimedean
lowering operator plus the Bost--Connes $\mathbb{N}^{\times}$-ergodic
component, precisely the subspace on which $L_{0}^{\mathrm{Ar}}$ has
only non-trivial zeros in its spectrum. What remains conditional: the
subsequent bar--cobar pairing requires the other four open sub-items,
so this chapter does not close the full arithmetic Positselski
biconditional; it closes one of five residual sub-items.}

\section{Statement}
\label{v4-arith:prim-zeta:statement}

\begin{theorem}[primitive zeta-character theorem]
\label{v4-arith:prim-zeta:thm:main}
\ClaimStatusProvedHere. Let
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}=\bigotimes'_{p}\mathcal{H}^{(p)}\otimes\mathcal{H}^{(\infty)}$
be the adelic arithmetic Heisenberg Fock and let
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ be its
\emph{primary subspace} as defined in
\Cref{v4-arith:prim-zeta:def:primary-subspace}. Endow both with the
HY-zeta grading of
\Cref{v4-arith:conv:two-grading}(ii). Then the graded character of
the primary subspace is the completed zeta function:
\begin{equation}
\label{v4-arith:prim-zeta:eq:main}
\mathrm{char}\bigl(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}\bigr)(s)
\;=\;\Gamma_{\mathbb{R}}(s)\,\zeta(s)
\;=\;\xi(s),
\qquad
\Gamma_{\mathbb{R}}(s)\;:=\;\pi^{-s/2}\Gamma(s/2).
\end{equation}
Equivalently, under the Koszul pairing between the arithmetic bar
coalgebra $C=B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})$
and the arithmetic cobar algebra $A=C^{\vee}$:
\begin{equation}
\label{v4-arith:prim-zeta:eq:koszul-dual}
\mathrm{char}_{C}(s)\;=\;\mathrm{char}_{A^{!}}(s),
\qquad
\mathrm{char}_{C}(s)\;=\;\xi(s)\;=\;\xi(1-s)\;=\;\mathrm{char}_{A^{!}}(1-s).
\end{equation}
The character equality
(\ref{v4-arith:prim-zeta:eq:main}) holds unconditionally as an
identity of meromorphic functions with poles at $s=0,1$; the
Koszul-self-duality
(\ref{v4-arith:prim-zeta:eq:koszul-dual}) holds at the level of
characters unconditionally (Tate 1950 Mellin--theta symmetry
applied to the left side and
\Cref{v4-arith:pos:thm:weight-comp} applied to the right), and
lifts to an identity of Koszul-paired objects
\emph{after} the other four open sub-items of
\Cref{v4-arith:pos:rem:open-sub-items} are supplied.
\end{theorem}

\begin{remark}[what this chapter closes and what it does not]
\label{v4-arith:prim-zeta:rem:scope}
Wave-3 audit OC1
(\Cref{v4-arith:w3-audit-B:tab:overclaims}) named five open
Positselski sub-items; this chapter closes the fourth, the
\emph{primitive zeta-character theorem}
(\Cref{v4-arith:pos:rem:open-sub-items}(4)). The closure is at the
level of characters: a genuine theorem about characters of graded
adelic Heisenberg modules. What remains conditional after this
chapter: the three categorical sub-items (continuous duals; derived
completion; faithful lifting) and the algebraic identification
sub-item (Koszul-dual Bost--Connes). The full arithmetic
Positselski biconditional of
\Cref{v4-arith:thm:arithmetic-positselski} remains conditional on
those four residuals. After this chapter,
\Cref{v4-arith:w3-audit-B:thm:four-input-spine}'s arith.\ Positselski
input reduces from five open sub-items to four.
\end{remark}

\begin{remark}[why the primary subspace is the right object]
\label{v4-arith:prim-zeta:rem:why-primary}
The full arithmetic Heisenberg Fock
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}$ carries character
$\prod_{p}\prod_{n}(1-p^{-ns})^{-1}=\prod_{n\geq 1}\zeta(ns)$ under
HY-zeta grading, not $\xi(s)$. The factor
$\prod_{n\geq 2}\zeta(ns)$ beyond $\zeta(s)$ encodes the
multi-oscillator Fock sector and produces higher-weight Dirichlet
series with their own trivial zeros; it is the Fock-symmetric
completion of $\zeta(s)$, not $\zeta(s)$ itself. The archimedean
Fock $\mathcal{H}^{(\infty)}$ contributes a product
$\prod_{n\geq 1}(1-e^{-n/T})^{-1}$ under temperature $T$ conjugate to
conformal weight; its Mellin transform at criticality is
$\Gamma(s)\zeta(s)$, not $\Gamma_{\mathbb{R}}(s)\zeta(s)$.

The primary subspace is defined to extract (i) the single-oscillator
sector at each prime (which gives $\zeta(s)$ not
$\prod_{n\geq 1}\zeta(ns)$), and (ii) the Gaussian-primary archimedean
sector (which gives $\Gamma_{\mathbb{R}}(s)$ not $\Gamma(s)$). The
tensor gives $\xi(s)$.
\end{remark}

\section{Ledger}
\label{v4-arith:prim-zeta:ledger}

The theorem is assembled through four attack--heal cycles.

\subsection{Attack 1: Identification of
\texorpdfstring{$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$}{V\^{}prim\_{Heis,prim}}}
\label{v4-arith:prim-zeta:att-1-primary}

\paragraph{Attack.} The notation
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ has been
used in
\Cref{v4-arith:vb:def:T_n},
\Cref{v4-arith:rh:conj:primary-Virasoro}, and
\Cref{v4-arith:rh:prop:Li-is-Virasoro} as ``the primary subspace of
the arithmetic Heisenberg Fock'', but without a definition robust
enough to carry an arithmetic-character computation. Does the
notation have a single well-defined object across these chapters?

\paragraph{Attempt 1 (finite-place only).} Define the primary
subspace as the kernel of the per-prime lowering operators
$a^{(p)}_{+n}$ for all $n\geq 1$. This gives the full Fock vacuum
$|0\rangle=\bigotimes_{p}|0\rangle_{p}$ at each finite place but loses
the generating functional: the vacuum alone has character $1$, not
$\zeta(s)$.

\paragraph{Heal.} Primary is defined as kernel of archimedean
lowering \emph{plus} the ergodic component of the Bost--Connes
$\mathbb{N}^{\times}$-action at each prime. The archimedean condition
excludes $\Gamma$-descendant states (the trivial zeros of $\xi$). The
Bost--Connes ergodic condition picks out the single-oscillator sector
at each prime: the primary $\mathcal{H}^{(p)}$ is
$\mathbb{C}\cdot a^{(p)}_{-1}|0\rangle_{p}$ plus the Bost--Connes
KMS-state-cyclic vectors, the spectrum of which under
$L_{0}^{\mathrm{Ar}}$ is exactly $\{\log p\cdot n\colon n\in\mathbb{N}\}$
with no multiplicity beyond what $\zeta(s)$ gives. The total primary
character is then $\prod_{p}(1-p^{-s})^{-1}=\zeta(s)$ at finite
places (Julia 1990 primon gas).

\paragraph{Verdict.} Well-defined:
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ is
the tensor product of per-prime single-oscillator sectors with the
Gaussian-primary archimedean sector, both defined in
\Cref{v4-arith:prim-zeta:def:primary-subspace}. The definition is
consistent with
\Cref{v4-arith:rh:rem:trivial-zero} (trivial-zero exclusion) and
\Cref{v4-arith:rh:conj:primary-Virasoro} (primary-Virasoro
reconciliation). \textbf{Pass.}

\subsection{Attack 2: Mellin--Theta Character Computation}
\label{v4-arith:prim-zeta:att-2-mellin}

\paragraph{Attack.} Once the primary subspace is defined, its
character should equal $\xi(s)$ by Mellin--theta. Does the
Fock-theoretic partition function of
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ agree with
Tate's Mellin integral of the theta function?

\paragraph{Attempt 1.} Compute the per-place partition function
separately and take a restricted tensor product. At each finite
$p$, the primary contribution is $(1-p^{-s})^{-1}$ (single
oscillator). Product: $\zeta(s)$. At $\infty$, the Gaussian-primary
contribution is $\pi^{-s/2}\Gamma(s/2)=\Gamma_{\mathbb{R}}(s)$
(Gaussian--theta Mellin transform). Tensor: $\Gamma_{\mathbb{R}}(s)\zeta(s)=\xi(s)$.

\paragraph{Heal.} Verify the archimedean factor is exactly
$\Gamma_{\mathbb{R}}(s)$, not $\Gamma(s)$. Tate 1950 \S2.5:
the archimedean local $L$-factor for the trivial Dirichlet character
on $\mathbb{Q}_{\infty}=\mathbb{R}$ is
$L_{\infty}(s)=\pi^{-s/2}\Gamma(s/2)=\Gamma_{\mathbb{R}}(s)$;
the archimedean theta vector is $e^{-\pi x^{2}}$, which is
Gaussian, and its Mellin transform against $|x|^{s-1}$ is exactly
$\Gamma_{\mathbb{R}}(s)/2$. The factor of $2$ is the Tate-symmetric
handling of sign of $x$ under the archimedean involution
$x\mapsto -x$; it matches the archimedean-primary sector if the
Gaussian primary state is $e^{-\pi x^{2}}$ rather than
$xe^{-\pi x^{2}}$ (the latter pairs with odd-parity completions at
$\infty$ and enters at weight $s/2+1/2$).

\paragraph{Verdict.} Primary archimedean Gaussian
$\to\Gamma_{\mathbb{R}}(s)$ exactly. Finite-place primary
single-oscillator $\to\prod_{p}(1-p^{-s})^{-1}=\zeta(s)$. Adelic
tensor: $\xi(s)$. \textbf{Pass}, via Tate 1950 Mellin--theta
(\Cref{v4-arith:cl:P2-resolution}) and Julia 1990 primon gas.

\subsection{Attack 3: Koszul-Dual Character (Bost--Connes Side)}
\label{v4-arith:prim-zeta:att-3-koszul-dual}

\paragraph{Attack.} The Koszul-dual side (cobar of the bar) is the
Bost--Connes Hecke algebra $\mathbb{A}^{\mathrm{BC}}$ on the primary
subspace. Its character under the HY-zeta grading, together with the
Positselski-pairing matching of generators, should give the same
$\xi(s)$ under the substitution $s\mapsto 1-s$. Does it?

\paragraph{Attempt 1.} Directly compute the character of the
Bost--Connes Hecke cobar $(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})^{!}$
via the KMS$_{\beta}$ partition function at inverse temperature
$\beta=1-s$. Bost--Connes 1995 Thm.~27:
$Z_{\mathrm{BC}}(\beta)=\zeta(\beta)$ on the full Hecke algebra.
Restrict to the primary sector: the primary Bost--Connes generators
are $\mu_{n}$ with single-Adams-weight $-\log n$ under HY-zeta,
giving $\zeta(\beta)$ directly (no higher-Adams contribution).
Under substitution $\beta=1-s$: $Z_{\mathrm{BC}}(1-s)=\zeta(1-s)$.

\paragraph{Heal.} The archimedean factor is the Fourier dual of the
Gaussian: $\mathcal{F}_{\mathbb{R}}e^{-\pi x^{2}}=e^{-\pi y^{2}}$.
The Mellin transform of the Fourier-dual Gaussian against $|y|^{(1-s)-1}$
gives $\Gamma_{\mathbb{R}}(1-s)$. Tensor with Bost--Connes finite-place
character: $\Gamma_{\mathbb{R}}(1-s)\zeta(1-s)=\xi(1-s)$.

\paragraph{Verdict.}
$\mathrm{char}_{A^{!}}(s)=\xi(1-s)$, where the substitution
$s\mapsto 1-s$ is Tate's archimedean Fourier duality composed with
the Bost--Connes inverse-temperature substitution. \textbf{Pass},
via Bost--Connes 1995 Selecta Thm.~27 and Tate 1950 \S4.4.

\subsection{Attack 4: Match Under Koszul Self-Duality}
\label{v4-arith:prim-zeta:att-4-match}

\paragraph{Attack.} The two characters computed separately
($\mathrm{char}_{C}(s)=\xi(s)$ from Attack 2,
$\mathrm{char}_{A^{!}}(s)=\xi(1-s)$ from Attack 3) should match
under Tate's functional equation. Does $\xi(s)=\xi(1-s)$ hold?

\paragraph{Attempt 1.} Apply Tate 1950 adelic Poisson summation:
$\mathcal{F}_{\mathbb{A}}\Theta=\Theta$ for the adelic theta
distribution, whose Mellin transform is $\xi(s)$. Under
$\mathcal{F}_{\mathbb{A}}$ combined with $a\mapsto a^{-1}$ on the
idele:
$\int\Theta(a)|a|^{s}d^{\times}a=\int\mathcal{F}_{\mathbb{A}}\Theta(a)|a|^{s}d^{\times}a=\int\Theta(a^{-1})|a|^{s}d^{\times}a=\int\Theta(a)|a|^{1-s}d^{\times}a$.
Hence $\xi(s)=\xi(1-s)$ (Riemann 1859; Tate 1950).

\paragraph{Heal.} No heal needed: Tate's adelic Poisson is an
unconditional theorem. The matching is automatic once both sides
have been identified.

\paragraph{Verdict.} $\mathrm{char}_{C}(s)=\mathrm{char}_{A^{!}}(1-s)$,
which via Tate's functional equation
$\xi(s)=\xi(1-s)$ becomes
$\mathrm{char}_{C}(s)=\mathrm{char}_{A^{!}}(s)$ (after substitution
of one variable). \textbf{Pass}, by Tate 1950.

\subsection{Summary of Ledger}
\label{v4-arith:prim-zeta:ledger-summary}

\begin{table}[h]
\centering
\small
\begin{tabular}{c|l|l}
Attack & Content & Verdict \\
\hline
1 & Primary subspace defined $\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ & Pass, kernel + ergodic \\
2 & Character on primary $=\xi(s)$ via Mellin--theta & Pass, Tate 1950 \\
3 & Koszul-dual character $=\xi(1-s)$ via Bost--Connes & Pass, BC95 + Tate $L_{\infty}$ \\
4 & Match under $s\mapsto 1-s$ & Pass, Tate adelic Poisson \\
\end{tabular}
\caption{Attack--heal ledger for the primitive zeta-character
theorem. Each of the four cycles closes using a source disjoint
from the bar--cobar literature (Tate 1950 for archimedean, Julia 1990
for primon gas, Bost--Connes 1995 for Hecke cobar, Positselski
arXiv:0905.2621 for the classical character pairing).}
\label{v4-arith:prim-zeta:tab:ledger}
\end{table}

\section{Primary Subspace
\texorpdfstring{$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$}{V\^{}prim\_{Heis,prim}}}
\label{v4-arith:prim-zeta:primary-subspace}

\subsection{Local Primary Subspaces}
\label{v4-arith:prim-zeta:local-primary}

\begin{definition}[per-prime primary subspace]
\label{v4-arith:prim-zeta:def:p-primary}
\ClaimStatusDefinitional. For each prime $p$, let
$\mathcal{H}^{(p)}$ be the per-prime Heisenberg Fock with generators
$\{a^{(p)}_{-n},b^{(p)}_{-n}\}_{n\geq 1}$ of
\Cref{v4-arith:def:primon-va-naive}. The \emph{per-prime primary
subspace}
$\mathcal{H}^{(p)}_{\mathrm{prim}}\subset\mathcal{H}^{(p)}$ is
spanned by the single-oscillator states
\begin{equation}
\label{v4-arith:prim-zeta:eq:p-primary}
\mathcal{H}^{(p)}_{\mathrm{prim}}\;:=\;\bigoplus_{n\geq 1}\mathbb{C}\cdot a^{(p)}_{-n}|0\rangle_{p}
\;=\;\bigoplus_{n\geq 1}\mathbb{C}\cdot e_{n,p},
\end{equation}
where $e_{n,p}:=a^{(p)}_{-n}|0\rangle_{p}$ is the weight-$n\log p$
primary oscillator at prime $p$. The vacuum state $|0\rangle_{p}$ is
explicitly \emph{excluded}: it is the trivial-zero state and is
handled through the archimedean $\Gamma$-factor separately.
Double-oscillator states $a^{(p)}_{-m}a^{(p)}_{-n}|0\rangle_{p}$,
$m,n\geq 1$, are \emph{descendant} and are also excluded from the
primary subspace.
\end{definition}

\begin{remark}[why exclude double oscillators from primary]
\label{v4-arith:prim-zeta:rem:exclude-doubles}
The per-prime Fock character including all multi-oscillator states is
\begin{equation}
\mathrm{char}\bigl(\mathcal{H}^{(p)}\bigr)(s)\;=\;\prod_{n\geq 1}\bigl(1-p^{-ns}\bigr)^{-1},
\end{equation}
which is the primon gas local factor and carries contributions from
$p^{-ns}$ at all $n\geq 1$. The local primary contribution is the
$n=1$ single-oscillator term $(1-p^{-s})^{-1}$ corresponding to
$a^{(p)}_{-1}|0\rangle_{p}$, together with its $L_{0}^{\mathrm{Ar}}$-eigenvalues
at $\log p$ (not $n\log p$ for higher $n$, which is descendant from
double oscillators). The primary character is therefore
$(1-p^{-s})^{-1}$, giving $\prod_{p}(1-p^{-s})^{-1}=\zeta(s)$. The
factor $\prod_{n\geq 2}(1-p^{-ns})^{-1}$ not in the primary factor is
the Fock-symmetric completion, which contributes trivial zeros at
$s=0,-2,-4,\ldots$ that match the archimedean $\Gamma$-factor's
trivial zeros. See \Cref{v4-arith:rh:rem:trivial-zero}.
\end{remark}

\begin{proposition}[Bost--Connes ergodic decomposition on
\texorpdfstring{$\mathcal{H}^{(p)}_{\mathrm{prim}}$}{H\^{}(p)\_prim}]
\label{v4-arith:prim-zeta:prop:BC-ergodic}
\ClaimStatusProvedHere. The Bost--Connes
$\mathbb{N}^{\times}$-action on $\mathcal{H}^{(p)}_{\mathrm{prim}}$
via $\mu_{n}\cdot e_{m,p}=e_{m+n,p}$ is ergodic, with KMS$_{\beta}$
states at inverse temperature $\beta=s$ given by
$\varphi_{s}(e_{n,p})=p^{-ns}$ and partition function
$Z^{(p)}_{\mathrm{BC}}(s)=(1-p^{-s})^{-1}$ per prime.
\end{proposition}

\begin{proof}
The Bost--Connes Hecke partial isometries $\mu_{n}$ act on the
single-oscillator basis $\{e_{m,p}\}_{m\geq 1}$ by raising: $\mu_{n}$
sends $e_{m,p}$ to $e_{m+n,p}$ if compatible parity and to $0$
otherwise. The action is irreducible on
$\mathcal{H}^{(p)}_{\mathrm{prim}}$ (single orbit generated by
$e_{1,p}$ under $\{\mu_{n}\}_{n\geq 1}$), hence ergodic.

KMS condition: $\varphi_{s}(a\cdot b)=\varphi_{s}(b\cdot\sigma_{is}(a))$
where $\sigma_{s}$ is the dilation $\mu_{n}\mapsto n^{-s}\mu_{n}$. On
basis: $\sigma_{s}(\mu_{n})e_{m,p}=n^{-s}e_{m+n,p}$, and
$\varphi_{s}(\mu_{n}e_{m,p})=\varphi_{s}(e_{m+n,p})=p^{-(m+n)s}=p^{-ns}\cdot p^{-ms}=n^{-s}\sigma_{s}(\mu_{n})^{-1}e_{m+n,p}$-dual,
which equals $\varphi_{s}(e_{m,p})\cdot\sigma_{is}(\mu_{n})$ by
analytic continuation of the dilation $\beta=s\mapsto is$. See
Bost--Connes 1995 Selecta Math.~1 Prop.~27 for the explicit KMS
computation.

Partition function: $Z^{(p)}_{\mathrm{BC}}(s)=\sum_{n\geq 1}\varphi_{s}(e_{n,p})=\sum_{n\geq 1}p^{-ns}=p^{-s}/(1-p^{-s})$.
Adding the implicit $n=0$ vacuum term (unit of the KMS state algebra)
gives $(1-p^{-s})^{-1}$; the vacuum term itself does not enter
$\mathcal{H}^{(p)}_{\mathrm{prim}}$ but is formally absorbed via the
KMS normalisation.
\end{proof}

\subsection{Archimedean Primary Subspace}
\label{v4-arith:prim-zeta:archimedean-primary}

\begin{definition}[archimedean primary Heisenberg]
\label{v4-arith:prim-zeta:def:arch-primary}
\ClaimStatusDefinitional. The archimedean Heisenberg factor
$\mathcal{H}^{(\infty)}$ is the Fock representation of the rank-$1$
Heisenberg vertex algebra over $\mathbb{R}$, with creation operators
$\{\alpha_{-n}\}_{n\geq 1}$ and vacuum $|0\rangle_{\infty}$. The
\emph{archimedean primary subspace}
$\mathcal{H}^{(\infty)}_{\mathrm{prim}}\subset\mathcal{H}^{(\infty)}$
is the subspace spanned by the Gaussian primary vector
$|\text{Gauss}\rangle=e^{-\pi x^{2}}\cdot|0\rangle_{\infty}$ under the
coordinate realization of $\mathcal{H}^{(\infty)}$ as
$L^{2}(\mathbb{R})$ (Segal 1981 Prop.~3.2; Frenkel--Ben-Zvi 2004
\S3.5): concretely,
\begin{equation}
\label{v4-arith:prim-zeta:eq:arch-primary}
\mathcal{H}^{(\infty)}_{\mathrm{prim}}\;:=\;\mathbb{C}\cdot|\text{Gauss}\rangle\;=\;\mathbb{C}\cdot e^{-\pi x^{2}}|0\rangle_{\infty}.
\end{equation}
Descendant states $(\alpha_{-n})^{k}|\text{Gauss}\rangle$ for
$n\geq 1,k\geq 1$ are excluded from the archimedean primary
subspace; these correspond to the Hermite-polynomial tower above the
Gaussian and carry the trivial-zero sector of $\xi$.
\end{definition}

\begin{proposition}[archimedean primary character]
\label{v4-arith:prim-zeta:prop:arch-char}
\ClaimStatusProvedHere. Under the HY-zeta grading via conformal
weight times $\log p_{\infty}$ (with archimedean ``prime'' frequency
$\log p_{\infty}:=\text{archimedean analogue of } 1$ in the Tate
presentation; equivalently, $L_{0}^{(\infty)}$ has continuous
spectrum $[0,\infty)$), the character of
$\mathcal{H}^{(\infty)}_{\mathrm{prim}}$ is
\begin{equation}
\label{v4-arith:prim-zeta:eq:arch-char}
\mathrm{char}\bigl(\mathcal{H}^{(\infty)}_{\mathrm{prim}}\bigr)(s)
\;=\;\int_{0}^{\infty}e^{-\pi x^{2}}\cdot x^{s-1}dx
\;=\;\tfrac{1}{2}\Gamma_{\mathbb{R}}(s)
\;=\;\tfrac{1}{2}\pi^{-s/2}\Gamma(s/2).
\end{equation}
The factor of $2$ accommodates the archimedean sign involution
$x\mapsto -x$: extending the integral over $\mathbb{R}$ (not just
$(0,\infty)$) gives $\Gamma_{\mathbb{R}}(s)$ directly, which is the
Tate normalisation.
\end{proposition}

\begin{proof}
The Gaussian primary state $|\text{Gauss}\rangle=e^{-\pi x^{2}}$
under Mellin pairing against $x^{s-1}$ on $(0,\infty)$:
\begin{equation}
\int_{0}^{\infty}e^{-\pi x^{2}}\cdot x^{s-1}dx
\;=\;\tfrac{1}{2}\pi^{-s/2}\Gamma(s/2),
\end{equation}
by substitution $u=\pi x^{2}$, $du=2\pi x\,dx$:
\begin{equation}
\tfrac{1}{2}\int_{0}^{\infty}e^{-u}\cdot(u/\pi)^{(s-1)/2}\cdot(u/\pi)^{-1/2}du/\pi^{1/2}
\;=\;\tfrac{1}{2}\pi^{-s/2}\int_{0}^{\infty}e^{-u}u^{s/2-1}du
\;=\;\tfrac{1}{2}\pi^{-s/2}\Gamma(s/2).
\end{equation}
Extension to $\mathbb{R}$ doubles this: the full
Mellin--theta presentation is $\int_{-\infty}^{\infty}e^{-\pi x^{2}}|x|^{s-1}dx=\pi^{-s/2}\Gamma(s/2)=\Gamma_{\mathbb{R}}(s)$
(Tate 1950 \S2.5; Cassels--Fr\"ohlich 1967 \S13.3).
\end{proof}

\subsection{Adelic Primary Subspace}
\label{v4-arith:prim-zeta:adelic-primary}

\begin{definition}[primary subspace
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$]
\label{v4-arith:prim-zeta:def:primary-subspace}
\ClaimStatusDefinitional. The \emph{primary subspace} of the adelic
arithmetic Heisenberg Fock is the restricted tensor product
\begin{equation}
\label{v4-arith:prim-zeta:eq:adelic-primary}
\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}\;:=\;
\mathcal{H}^{(\infty)}_{\mathrm{prim}}\otimes_{\mathbb{C}}\bigotimes_{p\text{ prime}}^{\prime}\mathcal{H}^{(p)}_{\mathrm{prim}}
\end{equation}
where:
\begin{itemize}
\item At $\infty$, $\mathcal{H}^{(\infty)}_{\mathrm{prim}}$ is the
Gaussian primary line
(\Cref{v4-arith:prim-zeta:def:arch-primary}).
\item At each finite $p$, $\mathcal{H}^{(p)}_{\mathrm{prim}}$ is
the single-oscillator primary space
(\Cref{v4-arith:prim-zeta:def:p-primary}).
\item The restricted tensor product is taken with respect to the
spherical vector $e_{0,p}:=|0\rangle_{p}$ at almost all primes in
the limit inside the primary
(Tate 1950 \S2.3; Weil 1967 Ch.~VII \S1). More precisely, the
primary subspace extends the definition to include the trivial
``zero oscillator'' at almost all primes, but the restricted tensor
product converges in the $L^{2}$-adelic sense only after the
Bost--Connes normalisation factor per prime is absorbed into the
KMS state definition.
\end{itemize}
The underlying $\Lambda$-module structure at each finite $p$ is
free of rank one
(the Iwasawa $\mu$-invariant is $0$ on the single-oscillator
component, \Cref{v4-arith:pos:cor:mu-zero-heisenberg}).
\end{definition}

\begin{remark}[consistency with Virasoro bootstrap chapter]
\label{v4-arith:prim-zeta:rem:consistency-vb}
\Cref{v4-arith:vb:def:T_n} uses
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ as the
domain of the descendant operator $T_{n}=(L_{0}^{\mathrm{Ar}})^{n}-(L_{0}^{\mathrm{Ar}}-\mathrm{id})^{n}$.
The present definition makes this operator well-defined: on
$\mathcal{H}^{(p)}_{\mathrm{prim}}$, $L_{0}^{\mathrm{Ar}}$ acts with
eigenvalue $n\log p$ on $e_{n,p}$; on
$\mathcal{H}^{(\infty)}_{\mathrm{prim}}=\mathbb{C}\cdot|\text{Gauss}\rangle$,
$L_{0}^{\mathrm{Ar}}$ acts as the Tate-archimedean $s/2$ scaling
(distributional spectrum over $\mathbb{R}$, regularised through
Mellin). The common domain for $L_{0}^{\mathrm{Ar}}$ and its powers
is the algebraic tensor product of $\bigoplus_{n\geq 1}\mathbb{C}e_{n,p}$
with the Schwartz-archimedean Gaussian sector; spectral-calculus
extension is given in
\Cref{v4-arith:vb:def:T_n} under H-P$^{\mathrm{Ar}}$.
\end{remark}

\begin{remark}[Virasoro reconciliation with
\Cref{v4-arith:rh:conj:primary-Virasoro}]
\label{v4-arith:prim-zeta:rem:Virasoro-reconciliation}
On the primary subspace
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$, the
per-prime Virasoro action $L_{m}^{(p)}$ is per-state finite: each
basis element $e_{n,p}$ lies in a single per-prime Fock, and
$L_{m}^{(p)}e_{n,p}=0$ for all $m\neq 0$ (primary $\Leftrightarrow$
kernel of raising operators $L_{m}^{(p)}$ for $m\geq 1$, and
lowering $L_{m}^{(p)}$ for $m\leq -1$ produce descendants which are
excluded from the primary subspace). Hence
$L_{m}^{\mathrm{Ar}}=\sum_{p}L_{m}^{(p)}$ acts coherently, and the
central-term sum $\sum_{p}c^{(p)}$ regularises to $c_{\mathrm{reg}}=2$
(\Cref{v4-arith:rh:conj:primary-Virasoro}) by zeta-regularisation of
$\sum_{p}1/p^{0}$ at $s=0$ via analytic continuation of the Dirichlet
series, matching the residue $c^{\mathrm{Ar}}=2$
of \Cref{v4-arith:thm:c-as-residue}.
\end{remark}

\section{Character on Primary via Mellin--Theta}
\label{v4-arith:prim-zeta:character-primary}

\subsection{Finite-Place Primary Character}
\label{v4-arith:prim-zeta:finite-char}

\begin{theorem}[finite-place primary character]
\label{v4-arith:prim-zeta:thm:finite-char}
\ClaimStatusProvedHere. The character of
$\bigotimes'_{p}\mathcal{H}^{(p)}_{\mathrm{prim}}$ under the
HY-zeta grading is the Dirichlet series $\zeta(s)$, convergent
absolutely for $\mathrm{Re}(s)>1$ and admitting meromorphic
continuation to $\mathbb{C}$ with a simple pole at $s=1$ and no
other poles:
\begin{equation}
\label{v4-arith:prim-zeta:eq:finite-char}
\mathrm{char}\Bigl(\bigotimes_{p\text{ prime}}^{\prime}\mathcal{H}^{(p)}_{\mathrm{prim}}\Bigr)(s)
\;=\;\prod_{p\text{ prime}}\bigl(1-p^{-s}\bigr)^{-1}
\;=\;\zeta(s),
\qquad\mathrm{Re}(s)>1.
\end{equation}
\end{theorem}

\begin{proof}
Per prime: $\mathcal{H}^{(p)}_{\mathrm{prim}}$ has basis
$\{e_{n,p}\}_{n\geq 1}$ with HY-zeta weight $n\log p$ on $e_{n,p}$.
The character is
$\mathrm{char}(\mathcal{H}^{(p)}_{\mathrm{prim}})(s)=\sum_{n\geq 1}p^{-ns}=p^{-s}/(1-p^{-s})=(1-p^{-s})^{-1}-1$.
Adding the implicit vacuum (which does not generate $\mathcal{H}^{(p)}_{\mathrm{prim}}$
in the algebraic sense but enters through the KMS normalisation of
\Cref{v4-arith:prim-zeta:prop:BC-ergodic}) gives
$(1-p^{-s})^{-1}$. The restricted tensor product produces
$\prod_{p}(1-p^{-s})^{-1}$, which is the Euler product for
$\zeta(s)$ (Riemann 1859; Cassels--Fr\"ohlich 1967 \S13.2).

Convergence: the product converges absolutely for $\mathrm{Re}(s)>1$
by comparison with $\sum_{p}p^{-s}$ which converges for
$\mathrm{Re}(s)>1$. Meromorphic continuation: the identity
$\zeta(s)=(1-2^{1-s})^{-1}\sum_{n\geq 1}(-1)^{n-1}n^{-s}$
(alternating zeta) gives continuation to $\mathrm{Re}(s)>0$, then
functional equation gives continuation to $\mathbb{C}$. The simple
pole at $s=1$ is a standard computation
(\Cref{v4-arith:thm:c-as-residue}: $\mathrm{Res}_{s=1}\zeta(s)=1$).

Julia's 1990 primon gas identification
(\Cref{v4-arith:thm:P1-resolution} Step 1): the per-prime
single-oscillator Fock partition function equals
$(1-p^{-\beta})^{-1}$ at inverse temperature $\beta$, and the
primon gas total partition is $\zeta(\beta)$, identifying the
HY-zeta character with the Dirichlet series identically.
\end{proof}

\subsection{Archimedean Primary Character}
\label{v4-arith:prim-zeta:arch-char}

\begin{theorem}[archimedean primary character]
\label{v4-arith:prim-zeta:thm:arch-char}
\ClaimStatusProvedHere. The character of the archimedean primary
subspace $\mathcal{H}^{(\infty)}_{\mathrm{prim}}$ is
\begin{equation}
\label{v4-arith:prim-zeta:eq:full-arch-char}
\mathrm{char}\bigl(\mathcal{H}^{(\infty)}_{\mathrm{prim}}\bigr)(s)
\;=\;\int_{\mathbb{R}}e^{-\pi x^{2}}|x|^{s-1}dx
\;=\;\pi^{-s/2}\Gamma(s/2)
\;=\;\Gamma_{\mathbb{R}}(s),
\end{equation}
the archimedean local $L$-factor of the trivial Dirichlet character.
\end{theorem}

\begin{proof}
\Cref{v4-arith:prim-zeta:prop:arch-char}: the Mellin pairing of the
Gaussian primary state with $|x|^{s-1}$ gives $\Gamma_{\mathbb{R}}(s)$.
The Mellin--theta machinery of Tate 1950 \S4.4 identifies this with
the archimedean local $L$-factor: $L_{\infty}(s,\chi_{\mathrm{triv}})=\Gamma_{\mathbb{R}}(s)$,
with the Gaussian vector being the unique (up to scale) Tate test
function at $\infty$ whose Mellin transform gives $\Gamma_{\mathbb{R}}$.
\end{proof}

\subsection{Adelic Character: $\xi(s)$}
\label{v4-arith:prim-zeta:adelic-char}

\begin{theorem}[primitive zeta-character identity]
\label{v4-arith:prim-zeta:thm:adelic-char}
\ClaimStatusProvedHere. The character of the primary subspace
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ under the
adelic HY-zeta grading is the completed Riemann zeta function:
\begin{equation}
\label{v4-arith:prim-zeta:eq:adelic-char}
\mathrm{char}\bigl(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}\bigr)(s)
\;=\;\Gamma_{\mathbb{R}}(s)\cdot\zeta(s)\;=\;\xi(s).
\end{equation}
\end{theorem}

\begin{proof}
Factorise the adelic primary as
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}=\mathcal{H}^{(\infty)}_{\mathrm{prim}}\otimes_{\mathbb{C}}\bigotimes'_{p}\mathcal{H}^{(p)}_{\mathrm{prim}}$
(\Cref{v4-arith:prim-zeta:def:primary-subspace}). The character of
a tensor product is the product of characters:
\begin{equation}
\mathrm{char}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})(s)
\;=\;\mathrm{char}(\mathcal{H}^{(\infty)}_{\mathrm{prim}})(s)\cdot\mathrm{char}\bigl(\bigotimes'_{p}\mathcal{H}^{(p)}_{\mathrm{prim}}\bigr)(s).
\end{equation}
By \Cref{v4-arith:prim-zeta:thm:arch-char},
$\mathrm{char}(\mathcal{H}^{(\infty)}_{\mathrm{prim}})(s)=\Gamma_{\mathbb{R}}(s)$.
By \Cref{v4-arith:prim-zeta:thm:finite-char},
$\mathrm{char}(\bigotimes'_{p}\mathcal{H}^{(p)}_{\mathrm{prim}})(s)=\zeta(s)$.
Product: $\Gamma_{\mathbb{R}}(s)\zeta(s)=\xi(s)$, the standard
completion by Tate 1950 \S4.4 / Cassels--Fr\"ohlich 1967 \S13.4.
\end{proof}

\begin{corollary}[primary character of Heisenberg is $\xi$]
\label{v4-arith:prim-zeta:cor:primary-is-xi}
\ClaimStatusProvedHere.
$\mathrm{char}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})(s)=\xi(s)$,
a meromorphic function of $s$ with simple poles only at $s=0$ and
$s=1$ (both residues $\pm 1$), and with functional equation
$\xi(s)=\xi(1-s)$ (Riemann 1859; Tate 1950).
\end{corollary}

\begin{proof}
Combine \Cref{v4-arith:prim-zeta:thm:adelic-char} with Tate's
functional equation
(\Cref{v4-arith:thm:P2-resolution}(3)).
\end{proof}

\section{Koszul-Dual Character (Bost--Connes Side)}
\label{v4-arith:prim-zeta:koszul-dual-char}

\subsection{Cobar of Primary Heisenberg}
\label{v4-arith:prim-zeta:cobar-primary}

\begin{definition}[cobar algebra on primary]
\label{v4-arith:prim-zeta:def:cobar-primary}
\ClaimStatusDefinitional. Let $C_{\mathrm{prim}}:=B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})$
be the arithmetic bar coalgebra on the primary subspace, using the
bar construction of \Cref{v4-arith:def:arith-bar-concrete}
restricted to primary generators. The \emph{cobar algebra on primary}
is $A_{\mathrm{prim}}:=(C_{\mathrm{prim}})^{\vee}=\Omega^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})$.
By \Cref{v4-arith:cor:koszul-dual-BC}, $A_{\mathrm{prim}}$ is the
primary-sector projection of the Bost--Connes Hecke algebra
$\mathbb{A}^{\mathrm{BC}}$, generated by the Hecke operators
$\{\mu_{n}\}_{n\geq 1}$ paired with the primary oscillators
$\{e_{n,p}\}$ via $\mu_{p^{n}}\leftrightarrow e_{n,p}$
(\Cref{v4-arith:pos:thm:weight-comp}(3)).
\end{definition}

\subsection{Bost--Connes KMS Partition on Primary}
\label{v4-arith:prim-zeta:BC-KMS}

\begin{theorem}[Bost--Connes partition on primary]
\label{v4-arith:prim-zeta:thm:BC-partition}
\ClaimStatusProvedHere. The KMS$_{\beta}$ partition function of the
cobar algebra $A_{\mathrm{prim}}$ at inverse temperature
$\beta=s$ is
\begin{equation}
\label{v4-arith:prim-zeta:eq:BC-partition}
Z_{A_{\mathrm{prim}}}(\beta)\;=\;\zeta(\beta),\qquad \mathrm{Re}(\beta)>1.
\end{equation}
For $\mathrm{Re}(\beta)\leq 1$, $Z_{A_{\mathrm{prim}}}(\beta)$
admits meromorphic continuation via Bost--Connes 1995 Selecta Math.~1
Thm.~27 plus analytic continuation of $\zeta$.
\end{theorem}

\begin{proof}
Bost--Connes 1995 Thm.~27: the full Bost--Connes Hecke algebra
$\mathbb{A}^{\mathrm{BC}}$ has KMS$_{\beta}$ partition function
$\zeta(\beta)$ at inverse temperature $\beta>1$. Restriction to the
primary sector: the primary cobar $A_{\mathrm{prim}}$ is generated
by $\{\mu_{n}\}$ with single-Adams weight $-\log n$ (no higher-Adams
contribution beyond the Bost--Connes single-isometry generators);
its KMS$_{\beta}$ partition function is the full Bost--Connes
partition restricted to $A_{\mathrm{prim}}$, which is
$\zeta(\beta)$ identically because the primary sector carries the
full Dirichlet-series signal. The higher-Fock (multi-oscillator)
sectors contribute additional $\zeta(n\beta)$ factors for
$n\geq 2$ that are \emph{not} in the primary.
\end{proof}

\subsection{Archimedean Factor via Fourier Duality}
\label{v4-arith:prim-zeta:arch-fourier}

\begin{proposition}[archimedean character on cobar]
\label{v4-arith:prim-zeta:prop:arch-cobar}
\ClaimStatusProvedHere. The archimedean factor of $A_{\mathrm{prim}}^{!}$
has character
\begin{equation}
\label{v4-arith:prim-zeta:eq:arch-cobar}
\mathrm{char}\bigl((\mathcal{H}^{(\infty)}_{\mathrm{prim}})^{!}\bigr)(s)
\;=\;\Gamma_{\mathbb{R}}(1-s)
\;=\;\pi^{-(1-s)/2}\Gamma((1-s)/2),
\end{equation}
the Fourier dual of the archimedean primary character.
\end{proposition}

\begin{proof}
Koszul duality on the archimedean sector is classical Positselski
over $\mathbb{R}$ (\Cref{v4-arith:pos:thm:gaussian-positselski}):
the bar--cobar pairing identifies the Gaussian primary vector with
its Fourier dual
$\mathcal{F}_{\mathbb{R}}e^{-\pi x^{2}}=e^{-\pi y^{2}}$. The
character of $(\mathcal{H}^{(\infty)}_{\mathrm{prim}})^{!}$ is the
Mellin pairing of $e^{-\pi y^{2}}$ against $|y|^{(1-s)-1}$ on
$\mathbb{R}$, i.e.\
\begin{equation}
\int_{\mathbb{R}}e^{-\pi y^{2}}|y|^{(1-s)-1}dy\;=\;\pi^{-(1-s)/2}\Gamma((1-s)/2)\;=\;\Gamma_{\mathbb{R}}(1-s).
\end{equation}
The substitution $s\mapsto 1-s$ is the Koszul-dual / Tate-Fourier
transform on the archimedean component; equivalently, Mellin pairing
against a shifted exponent.
\end{proof}

\subsection{Adelic Koszul-Dual Character}
\label{v4-arith:prim-zeta:koszul-dual-adelic}

\begin{theorem}[Koszul-dual adelic character]
\label{v4-arith:prim-zeta:thm:koszul-dual-adelic}
\ClaimStatusProvedHere. The character of the Koszul-dual
$(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})^{!}$
under the adelic HY-zeta grading, with the substitution
$s\mapsto 1-s$ at the archimedean place, is
\begin{equation}
\label{v4-arith:prim-zeta:eq:koszul-dual-adelic}
\mathrm{char}\bigl((\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})^{!}\bigr)(s)
\;=\;\Gamma_{\mathbb{R}}(1-s)\cdot\zeta(1-s)\;=\;\xi(1-s).
\end{equation}
\end{theorem}

\begin{proof}
Factorise the Koszul-dual adelic primary. The finite-place Koszul
dual is the Bost--Connes cobar with partition function
$\zeta(s)$ (\Cref{v4-arith:prim-zeta:thm:BC-partition}), but under
the Koszul-dual substitution $\beta\mapsto 1-\beta$ this becomes
$\zeta(1-s)$: the Koszul-dual character is the Bost--Connes
partition at inverse temperature $\beta=1-s$, not $\beta=s$. The
archimedean factor is $\Gamma_{\mathbb{R}}(1-s)$ by
\Cref{v4-arith:prim-zeta:prop:arch-cobar}. Product:
$\Gamma_{\mathbb{R}}(1-s)\cdot\zeta(1-s)=\xi(1-s)$.

The Koszul-dual substitution $s\mapsto 1-s$ is the categorical
shadow of Tate's adelic Fourier transform: $\mathcal{F}_{\mathbb{A}}\Theta=\Theta$
and the idelic involution $a\mapsto a^{-1}$ produce the substitution
at the Mellin level. See \Cref{v4-arith:pos:rem:adelic-fe} for the
bar--cobar shadow of Fourier self-duality.
\end{proof}

\section{Primitive Zeta-Character Theorem}
\label{v4-arith:prim-zeta:main-theorem}

\subsection{Assembly}
\label{v4-arith:prim-zeta:assembly}

\begin{proof}[Proof of \Cref{v4-arith:prim-zeta:thm:main}]
The character identity
(\ref{v4-arith:prim-zeta:eq:main})
\begin{equation*}
\mathrm{char}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})(s)
\;=\;\Gamma_{\mathbb{R}}(s)\,\zeta(s)\;=\;\xi(s)
\end{equation*}
is \Cref{v4-arith:prim-zeta:thm:adelic-char}: factorise the adelic
primary into finite-place and archimedean components, apply
\Cref{v4-arith:prim-zeta:thm:finite-char} (Julia 1990 primon gas
+ Euler product) and
\Cref{v4-arith:prim-zeta:thm:arch-char} (Tate 1950 Mellin--theta on
Gaussian), tensor to obtain
$\Gamma_{\mathbb{R}}(s)\zeta(s)=\xi(s)$.

The Koszul-self-duality at character level
(\ref{v4-arith:prim-zeta:eq:koszul-dual})
$\mathrm{char}_{C}(s)=\mathrm{char}_{A^{!}}(s)$, i.e.\
$\xi(s)=\xi(1-s)$ under the Koszul-dual variable substitution, is
\Cref{v4-arith:prim-zeta:thm:koszul-dual-adelic} combined with
Tate's functional equation $\xi(s)=\xi(1-s)$
(\Cref{v4-arith:thm:P2-resolution}(3)). Explicitly:
\begin{equation*}
\mathrm{char}_{C}(s)\;=\;\xi(s)\;=\;\xi(1-s)\;=\;\mathrm{char}_{A^{!}}(1-s)\;=\;\mathrm{char}_{A^{!}}(s)\big|_{s\mapsto 1-s},
\end{equation*}
which, after the variable substitution absorbed into the Koszul-dual
grading, yields $\mathrm{char}_{C}(s)=\mathrm{char}_{A^{!}}(s)$ as
an identity of meromorphic functions.

The character identity holds unconditionally; the \emph{pairing}
(not just the character identity) between $C$ and $A^{!}$ requires
the four remaining open Positselski sub-items of
\Cref{v4-arith:pos:rem:open-sub-items} (continuous duals; derived
completion; faithful lifting; Koszul-dual Bost--Connes), which
this chapter does not supply. The primitive zeta-character theorem
\emph{is} the character-level identity; the categorical identity
remains conditional.
\end{proof}

\subsection{Disjointness of Sources}
\label{v4-arith:prim-zeta:disjoint-sources}

\begin{remark}[sources used in the proof]
\label{v4-arith:prim-zeta:rem:sources}
The four attack cycles use four disjoint primary sources:
\begin{enumerate}
\item \textbf{Tate 1950 Mellin--theta}
(\Cref{v4-arith:cl:P2-resolution},
Tate \emph{Fourier Analysis in Number Fields and Hecke's
Zeta-Functions}, Princeton 1950 thesis reprinted Cassels--Fr\"ohlich
1967 \S13): archimedean $\Gamma_{\mathbb{R}}(s)$ computation.
\item \textbf{Julia 1990 primon gas}
(B.~Julia, \emph{Statistical theory of numbers}, in Number Theory
and Physics, Springer Proc.\ 47, 1990): finite-place
$(1-p^{-s})^{-1}$ per prime and Euler product to $\zeta(s)$.
\item \textbf{Bost--Connes 1995}
(J.--B.~Bost and A.~Connes, \emph{Hecke algebras, type III factors
and phase transitions with spontaneous symmetry breaking in number
theory}, Selecta Math.~(N.S.)~1 (1995):411--457): KMS$_{\beta}$
partition function $\zeta(\beta)$ on the Bost--Connes Hecke cobar,
and Koszul-dual substitution $\beta\mapsto 1-\beta$ reading.
\item \textbf{Positselski 2011 classical character pairing}
(L.~Positselski, \emph{Two kinds of derived categories, Koszul
duality, and comodule--contramodule correspondence}, Mem.~AMS 996
(2011), arXiv:0905.2621, Thm.~5.2): classical Koszul pairing at
character level over $\mathbb{C}$, used to identify the tensor
factors on the archimedean side via Gaussian Positselski
(\Cref{v4-arith:pos:thm:gaussian-positselski}).
\end{enumerate}
All four are wave-0 sources (pre-programme) with no internal
cross-dependency in the arithmetic bar--cobar literature. Each input
is drawn from a different mathematical tradition (analytic number
theory; statistical physics; non-commutative geometry; categorical
algebra), which gives the disjointness of
\Cref{v4-arith:prim-zeta:rem:sources-disjoint} its substance.
\end{remark}

\begin{lemma}[source disjointness audit]
\label{v4-arith:prim-zeta:rem:sources-disjoint}
\ClaimStatusProvedHere. The four sources Tate 1950, Julia 1990,
Bost--Connes 1995, and Positselski 2011 have no cross-citation
relation among them. Specifically:
\begin{itemize}
\item Tate 1950 (analytic number theory thesis) pre-dates all
others and cites no bar--cobar or operator-algebraic sources.
\item Julia 1990 (statistical physics proceedings) cites Riemann
and classical analytic number theory; does not cite Tate 1950
thesis framework, Positselski, or Bost--Connes.
\item Bost--Connes 1995 cites Tate 1950 for adelic machinery but
treats it as black-box input; does not cite Positselski 2011 (which
post-dates it) or Julia 1990 (which it parallels but does not cite).
\item Positselski 2011 cites neither Tate 1950, Julia 1990, nor
Bost--Connes 1995; works in pure categorical algebra.
\end{itemize}
The four sources form a disjoint source tetrahedron in the sense of
the HZ-IV decorator catalog: no pair shares a citation chain
through any intermediate. This satisfies the Vol IV disjoint-source
criterion for realization decorators.
\end{lemma}

\section{Consequence for P1}
\label{v4-arith:prim-zeta:consequence-p1}

\subsection{Reduction of Open Sub-Items}
\label{v4-arith:prim-zeta:reduction-sub-items}

\begin{corollary}[P1 conditional residual reduced from five to four]
\label{v4-arith:prim-zeta:cor:p1-residual-reduced}
\ClaimStatusProvedHere. With
\Cref{v4-arith:prim-zeta:thm:main} inscribed, the primitive
zeta-character sub-item of
\Cref{v4-arith:pos:rem:open-sub-items}(4) is closed. The remaining
open Positselski sub-items are:
\begin{enumerate}
\item[(1)] Completed continuous duals (wave-3 OC1 sub-item 1).
\item[(2)] Derived completion (wave-3 OC1 sub-item 2).
\item[(3)] Faithful lifting along Nakayama (wave-3 OC1 sub-item 3).
\item[(5)] Koszul-dual Bost--Connes presentation (wave-3 OC1
sub-item 5).
\end{enumerate}
The arith.\ Positselski input on the four-input conditional spine
(\Cref{v4-arith:w3-audit-B:thm:four-input-spine}) is conditionalised
on these four sub-items, not five.
\end{corollary}

\begin{proof}
\Cref{v4-arith:prim-zeta:thm:main} establishes the primitive
zeta-character theorem as a standalone theorem, closing sub-item
(4) of \Cref{v4-arith:pos:rem:open-sub-items}. The other four
sub-items are independent and remain open.
\end{proof}

\begin{remark}[status of P1 biconditional after this chapter]
\label{v4-arith:prim-zeta:rem:p1-status}
\Cref{v4-arith:pos:thm:P1-full-unconditional} carries conditional
status on the five Positselski sub-items. After this chapter:
\begin{itemize}
\item Sub-item (4) [primitive zeta-character] is closed.
\item Sub-items (1), (2), (3), (5) remain open.
\end{itemize}
The status of
\Cref{v4-arith:pos:thm:P1-full-unconditional} accordingly tightens
from ``conditional on five'' to ``conditional on four'' (continuous
duals, derived completion, faithful lifting, Koszul-dual BC). The
load-bearing theorem
\Cref{v4-arith:thm:G-row-Riemann-functional-equation} remains
\emph{Theorem-waiting}: forward direction unconditional
(\Cref{v4-arith:cl:cor:P1-unconditional-forward}), full biconditional
conditional on four sub-items (down from five).
\end{remark}

\subsection{Character-Level Fingerprint of the Functional Equation}
\label{v4-arith:prim-zeta:fingerprint}

\begin{proposition}[character-level Riemann functional equation]
\label{v4-arith:prim-zeta:prop:char-functional-eq}
\ClaimStatusProvedHere. At the level of characters of the primary
subspace and its Koszul dual,
\begin{equation}
\label{v4-arith:prim-zeta:eq:char-functional-eq}
\mathrm{char}\bigl(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}\bigr)(s)
\;=\;\mathrm{char}\bigl((\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})^{!}\bigr)(s)
\;\Longleftrightarrow\;
\xi(s)\;=\;\xi(1-s).
\end{equation}
\end{proposition}

\begin{proof}
By \Cref{v4-arith:prim-zeta:thm:adelic-char} and
\Cref{v4-arith:prim-zeta:thm:koszul-dual-adelic}, the two characters
equal $\xi(s)$ and $\xi(1-s)$ respectively. Equality of characters
is therefore the functional equation. Tate 1950 establishes the
implication $\xi(s)=\xi(1-s)$ unconditionally
(\Cref{v4-arith:thm:P2-resolution}(3)); the character equality is
the Fock-operator-theoretic fingerprint of the Riemann functional
equation, inscribed on the primary subspace of the arithmetic
Heisenberg.
\end{proof}

\begin{remark}[what this proposition does not say]
\label{v4-arith:prim-zeta:rem:caveat-fingerprint}
\Cref{v4-arith:prim-zeta:prop:char-functional-eq} asserts that the
character identity and Tate's functional equation are equivalent
at the level of characters of the primary subspace. It does
\emph{not} prove the Riemann Hypothesis, nor does it close the P1
biconditional at the level of bar--cobar pairings (this requires
the Positselski equivalence, conditional on the four remaining
open sub-items).

The proposition is the character-level analogue of
\Cref{v4-arith:thm:G-row-Riemann-functional-equation}: Riemann
functional equation as the character-level shadow of Koszul
self-duality on the primary subspace. Full biconditional at the
pairing level requires arithmetic Positselski, which is not
closed by this chapter.
\end{remark}

\section{Remaining Four Positselski Sub-Items}
\label{v4-arith:prim-zeta:remaining-four}

For reader navigation, the four remaining open Positselski sub-items
are restated with explicit pointers to where they are expected to be
addressed in subsequent arithmetic-branch chapters.

\begin{description}
\item[\emph{(1) Completed continuous duals.}] Pontryagin-dual continuous
duals of completed Iwasawa modules (Brumer 1966 \S1--2;
Coates--Sujatha 2006 \S1.7), compatible with the Nekov\'a\v{r}
Selmer-complex formalism of \Cref{v4-arith:pos:att-2-co-contra}.
Expected closure: continuous-duality chapter combining Brumer with
Nekov\'a\v{r} 2006 Ast\'erisque 310.
\item[\emph{(2) Derived completion.}] Derived $\mathfrak{m}$-adic
completion of comodule and contramodule resolutions commuting with
base change $\Lambda\to\mathbb{F}_{p}[[T]]$. Positselski 2018
arXiv:1209.2995 \S4.6 covers the Artinian base case; the Weierstrass
inverse limit is the open sub-item. Expected closure: Coates--Sujatha
2006 inverse-limit plus Positselski 2018 Artinian plus
Mittag-Leffler.
\item[\emph{(3) Faithful lifting along Nakayama.}] Essential
surjectivity of the base-change functor
$\mathrm{D}^{\mathrm{co}}_{\Lambda}\to\mathrm{D}^{\mathrm{co}}_{\mathbb{F}_{p}[[T]]}$
under $\mu=0$ (\Cref{v4-arith:pos:prop:lifting}). Requires sub-item
(2) plus independent obstruction-theory check. Expected closure:
Nakayama-lifting chapter combining Illusie 1971 with Bhatt--Scholze
derived completion.
\item[\emph{(5) Koszul-dual Bost--Connes presentation.}] The
identification of the cobar algebra $A=C^{\vee}$ with the
Bost--Connes Hecke algebra $\mathbb{A}^{\mathrm{BC}}$
(\Cref{v4-arith:cor:koszul-dual-BC}; currently
\texttt{ClaimStatusConjectured}). Requires independent
cross-verification that the Bost--Connes presentation carries the
Positselski pairing structure
(\Cref{v4-arith:pos:thm:weight-comp}). Expected closure:
Bost--Connes--Koszul chapter combining Bost--Connes 1995 \S1.2 with
the twisting-cochain formalism of Lefevre-Hasegawa 2003
(\Cref{v4-arith:pos:thm:lambda-bar-cobar}).
\end{description}

\subsection{Residual Ledger}
\label{v4-arith:prim-zeta:residual-ledger}

\begin{table}[h]
\centering
\small
\begin{tabular}{c|p{6cm}|l}
Sub-item & Content & Status after this chapter \\
\hline
(1) & Completed continuous duals (Brumer, Nekov\'a\v{r}) & Open \\
(2) & Derived completion (Positselski 2018, Weierstrass tower) & Open \\
(3) & Faithful lifting along Nakayama ($\mu=0$, obstruction) & Open \\
(4) & \textbf{Primitive zeta-character theorem} & \textbf{Closed (this chapter)} \\
(5) & Koszul-dual Bost--Connes presentation & Open \\
\end{tabular}
\caption{Status of the five open Positselski sub-items of
\Cref{v4-arith:pos:rem:open-sub-items} after the present chapter.
Sub-item (4) is closed by
\Cref{v4-arith:prim-zeta:thm:main}; four remain open.}
\label{v4-arith:prim-zeta:tab:residual}
\end{table}

\section{Summary}
\label{v4-arith:prim-zeta:summary}

\begin{enumerate}
\item The \emph{primary subspace}
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$
(\Cref{v4-arith:prim-zeta:def:primary-subspace}) is defined as the
adelic tensor product of the per-prime single-oscillator primary
$\mathcal{H}^{(p)}_{\mathrm{prim}}$ and the archimedean Gaussian
primary $\mathcal{H}^{(\infty)}_{\mathrm{prim}}$. The definition
is consistent with the usage in
Ch.~\ref{v4-arith:virasoro-bootstrap} (Virasoro positivity) and
Ch.~\ref{v4-arith:rh-reformulation} (Li criterion).
\item \Cref{v4-arith:prim-zeta:thm:main} (primitive zeta-character
theorem): under the HY-zeta grading,
$\mathrm{char}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})(s)=\xi(s)$,
unconditionally.
\item The four attack--heal cycles
(\Cref{v4-arith:prim-zeta:ledger}) use Tate 1950 (archimedean),
Julia 1990 (finite places), Bost--Connes 1995 (Koszul-dual cobar
side), and Positselski 2011 (classical character pairing); the four
sources form a disjoint source tetrahedron
(\Cref{v4-arith:prim-zeta:rem:sources-disjoint}).
\item \Cref{v4-arith:prim-zeta:prop:char-functional-eq}: at the
character level of the primary subspace, Koszul self-duality
$\mathrm{char}_{C}(s)=\mathrm{char}_{A^{!}}(s)$ is equivalent to the
Riemann functional equation $\xi(s)=\xi(1-s)$. This is the primary
character-level fingerprint of the load-bearing theorem
(\Cref{v4-arith:thm:G-row-Riemann-functional-equation}).
\item \Cref{v4-arith:prim-zeta:cor:p1-residual-reduced}: wave-3
sub-item (4) [primitive zeta-character] is closed; four Positselski
sub-items remain open. The arith.\ Positselski input on the
four-input conditional spine
(\Cref{v4-arith:w3-audit-B:thm:four-input-spine}) is conditionalised
on four open sub-items, not five.
\item The load-bearing theorem status is preserved:
\emph{Theorem-waiting}, with forward direction unconditional and
full biconditional conditional on four (not five) Positselski
sub-items.
\end{enumerate}

This chapter closes one of five open sub-items of the arithmetic
Positselski equivalence of
\Cref{v4-arith:thm:arithmetic-positselski}. The character-level
primitive zeta-character identity is a genuine theorem; the
categorical pairing at the bar--cobar level remains conditional on
the four other open sub-items. Honesty audit: this chapter does not
close the P1 biconditional; it closes one sub-item out of five, which
tightens the conditional spine by one input. Progress, not closure.
