\chapter{Koszul--Petersson: KMS\texorpdfstring{${}_{1}$}{1}/GNS Identification and Full-Sector Extension}
\label{v4-arith:kms-gns-full}

\emph{Wave-4. Chapter~\ref{v4-arith:kp-compat} scope-restricted
Koszul--Petersson compatibility to the normalised sph-fin cuspidal
core of $\mathcal{V}^{\mathrm{prim}}$; wave-3
(\Cref{v4-arith:w3-audit-B:repair-26}) isolated three residual
sub-items: (i) the KMS${}_{1}$/GNS identification of the Bost--Connes
involution with the Tomita--Takesaki modular involution; (ii)
extension of local Rankin--Selberg compatibility from the spherical
unramified locus to the full finite-place principal series; (iii)
treatment of the Eisenstein continuous spectrum that was
excluded by the sph-fin cut. This chapter attacks the three items in
priority order. Item (i) closes unconditionally as a classical
operator-algebra identification using Bost--Connes 1995 Selecta~1,
Takesaki 1970 Lecture Notes, and Takesaki 1979 \emph{Theory of
Operator Algebras~I}. Item (ii) extends the tempered cuspidal sector
to all finite-place ramifications via the local functional equation
of Godement--Jacquet at ramified principal series and
Jacquet--Piatetski-Shapiro--Shalika local factors at supercuspidals;
the non-tempered cuspidal locus remains conditional on the Ramanujan
bound. Item (iii) gives a Langlands-decomposition framework and
computes the pointwise discrepancy between the Koszul and Petersson
pairings on the Eisenstein continuum: the Koszul-side density
$\xi(2s)/\xi(2s-1)$ does \emph{not} match the Petersson-side
Maass--Selberg density $1+|M(s)|^{2}=2$ on the critical line; the
Eisenstein sector is therefore \emph{not} automatically closed, and
requires either a convention absorption or a scope exclusion. The
Eisenstein residual is named explicitly; no unconditional closure
of the full-sector compatibility is claimed.}

\section{Statement and Ledger}
\label{v4-arith:kms-gns:statement-ledger}

\subsection{The Three Residuals from Wave-3}
\label{v4-arith:kms-gns:residuals}

Recall from \Cref{v4-arith:kp:rem:scope-restriction} and
\Cref{v4-arith:w3-audit-B:repair-26} the three sub-items left open
by the sph-fin cuspidal scope restriction of
\Cref{v4-arith:kp:thm:main-full}:
\begin{enumerate}
\item[(I)] \textbf{KMS${}_{1}$/GNS identification.} The assertion
\Cref{v4-arith:kp:prop:Pet-p-is-BC-sigma} that the local Petersson
pairing equals the Bost--Connes Hilbert pairing after the
$\sigma^{\mathrm{BC}}_{p}$ involution was established via the
GNS-realised KMS${}_{1}$ state at each prime. The precise
identification ``$\sigma^{\mathrm{BC}}_{p}$ is the Tomita--Takesaki
modular involution of the KMS${}_{1}$ state'' was named but not
verified; wave-3 flagged this as an open sub-item.
\item[(II)] \textbf{Full-sector finite-place Rankin--Selberg.} The
finite-place computations of \Cref{v4-arith:kp:finite} were performed
only on the unramified spherical sector; the ramified principal
series, supercuspidal, and non-tempered sectors were not addressed.
\item[(III)] \textbf{Eisenstein continuous spectrum.} The sph-fin
cut of \Cref{v4-arith:sw:thm:KP-split}(K7) excluded the Eisenstein
continuous spectrum from the Koszul--Pet identity. Whether the
identity extends (in any form) to the continuous spectrum was not
addressed.
\end{enumerate}

\subsection{Deliverables of This Chapter}
\label{v4-arith:kms-gns:deliverables}

\begin{enumerate}
\item[(I)] \emph{Closed unconditionally}
(\Cref{v4-arith:kms-gns:thm:KMS1-GNS-BC-identification}) by classical
Tomita--Takesaki modular theory applied to the Bost--Connes KMS${}_{1}$
state.
\item[(II)] \emph{Closed on the cuspidal tempered full finite-place
sector} (\Cref{v4-arith:kms-gns:thm:ramified-cuspidal-tempered-extension})
via the local functional equation of Godement--Jacquet at ramified
principal series plus Jacquet--Piatetski-Shapiro--Shalika local
factors. \emph{Conditional} on the Ramanujan bound for non-tempered
cuspidal representations of $GL_{2}/\mathbb{Q}$; the current
state of the art is $7/64$ (Kim--Sarnak 2003) which suffices for
$GL_{2}/\mathbb{Q}$ by Deligne's theorem on holomorphic cuspidal
representations, but does not close non-tempered Maass forms
unconditionally.
\item[(III)] \emph{Framework-level placement only.} The Eisenstein
continuous spectrum is placed outside the Koszul--Pet identity and
the discrepancy is computed explicitly
(\Cref{v4-arith:kms-gns:thm:eisenstein-discrepancy}). The Koszul pairing
has a pole at $s=1$ matching the Eisenstein constant term's pole;
the Petersson pairing on the continuum has a distributional pole
matched by Maass--Selberg; but the two distributions differ by an
exactly-computable residue in $\mathrm{Re}(s)>1/2$ involving the
Eisenstein intertwining operator. No unconditional match is claimed
on the continuum.
\end{enumerate}

\subsection{Consequence for P3}
\label{v4-arith:kms-gns:P3-consequence}

After this chapter the P3 scope-restriction of
\Cref{v4-arith:kp:cor:P3-unconditional} tightens in two stages
(\Cref{v4-arith:kms-gns:thm:P3-tempered-cuspidal}): P3 holds
unconditionally on the tempered cuspidal finite-place sector
(not just sph-fin cuspidal), conditional on the Ramanujan bound for
non-tempered. The Eisenstein continuum remains outside P3: the
discrepancy theorem \Cref{v4-arith:kms-gns:thm:eisenstein-discrepancy}
exhibits an explicit density mismatch between Koszul and
Maass--Selberg on the critical line. The Eisenstein residual is
internal to the Koszul--Pet programme and admits two structural
resolutions (convention absorption or scope exclusion); neither is
closed here.

\subsection{Attack--Heal Ledger}
\label{v4-arith:kms-gns:ledger}

Four cycles structure the chapter. Each cycle runs the seven-attack
protocol of \Cref{v4-arith:cl:protocol}.

\begin{description}
\item[\textbf{Cycle 1 (KMS${}_{1}$/GNS identification of the
BC involution).}] \emph{Attack.} The Bost--Connes involution
$\sigma^{\mathrm{BC}}_{p}\colon\mu_{m}\mapsto\mu_{m}^{*}$ was
inscribed in \Cref{v4-arith:kp:eq:BC-involution-local} as a
$*$-antilinear $\mathbb{C}$-algebra automorphism; its identification
with the Tomita--Takesaki modular involution $J_{\mathrm{KMS}_{1}}$
was asserted but not verified. \emph{Heal.} Take the KMS${}_{1}$ state
$\varphi_{1}$ on the Bost--Connes $C^{*}$-algebra
$C^{*}_{\mathbb{Q},p}$ (Bost--Connes Selecta~1 (1995) \S2.2 Thm~25);
build its GNS representation $(\mathcal{H}_{\varphi_{1}},\pi_{\varphi_{1}},\Omega_{\varphi_{1}})$
(Takesaki 1979 \emph{Theory of Operator Algebras~I} Ch.~IV \S5);
form the closed conjugate-linear operator
$S\Omega_{\varphi_{1}}:\,x\Omega_{\varphi_{1}}\mapsto x^{*}\Omega_{\varphi_{1}}$;
polar-decompose $S=J\Delta^{1/2}$; verify $J(\mu_{m}\Omega_{\varphi_{1}})=\mu_{m}^{*}\Omega_{\varphi_{1}}$.
The verification is a direct computation from the GNS inner product
on the cyclic vector. Closes unconditionally.
\emph{Residual: none.}

\item[\textbf{Cycle 2 (full-sector finite-place).}] \emph{Attack.}
The Rankin--Selberg local integral of
\Cref{v4-arith:kp:eq:Pet-p-RS} was computed only at unramified
spherical vectors. Ramified principal series and supercuspidals
contribute to the local $L$-factor with local root numbers
$\varepsilon_{p}(\pi,\psi)$ that must be accounted for.
\emph{Heal.} Use Jacquet 1972 SLN~260 \S3 (local functional equation
for ramified $GL_{2}$), Jacquet--Piatetski-Shapiro--Shalika 1983
Amer.~J.~Math.~105 (local factors via Whittaker uniqueness), and
Godement--Jacquet 1972 SLN~260 \S2 (zeta integrals). The local
Koszul pairing absorbs $\varepsilon_{p}(\pi,\psi)\cdot L_{p}(1,\pi,\mathrm{Ad})$
under the Koszul-dual normalisation (K5 of
\Cref{v4-arith:bcglue-k5:thm:K5-absorption-canonical}) and the
local Petersson absorbs the same constant by the local
functional equation. The match holds for all \emph{tempered cuspidal}
local principal series.
\emph{Residual: non-tempered cuspidal extension is conditional on
the Ramanujan bound (currently $7/64$ after Kim--Sarnak).}

\item[\textbf{Cycle 3 (spectral decomposition of $L^{2}([GL_{2}])$).}]
\emph{Attack.} The full $\mathcal{V}^{\mathrm{prim}}$ is defined
(\Cref{v4-arith:sw:thm:KP-split}) as a restricted tensor product;
it does not automatically sit inside $L^{2}([GL_{2}])$ in the
discrete-spectrum or sph-fin cuspidal component. What is the
relationship between $\mathcal{V}^{\mathrm{prim}}$ as an abstract
arithmetic Heisenberg Fock module and $L^{2}([GL_{2}])$ as a
unitary representation?
\emph{Heal.} The Langlands decomposition
\[
L^{2}([GL_{2}])\;=\;L^{2}_{\mathrm{cusp}}([GL_{2}])\;\oplus\;L^{2}_{\mathrm{disc,res}}([GL_{2}])\;\oplus\;L^{2}_{\mathrm{cont}}([GL_{2}]),
\]
with $L^{2}_{\mathrm{cont}}$ the Eisenstein continuous spectrum
(Langlands 1966 \emph{On the Functional Equations Satisfied by
Eisenstein Series}; Moeglin--Waldspurger 1995 \emph{Spectral
Decomposition and Eisenstein Series}), places
$\mathcal{V}^{\mathrm{prim}}$ inside $L^{2}_{\mathrm{cusp}}\oplus L^{2}_{\mathrm{disc,res}}$
after completion; the Eisenstein continuum is a separate summand on
which the restricted tensor product of Whittaker models does not
give an honest embedding into the discrete spectrum.
\emph{Residual: the discrete-spectrum cuspidal + residual component
is the full-sector closure target; the Eisenstein continuum is
placed outside.}

\item[\textbf{Cycle 4 (Eisenstein handling via Langlands).}]
\emph{Attack.} Can the Eisenstein continuum be handled by a parallel
Koszul identity, perhaps by opening up the scope of
$\mathcal{V}^{\mathrm{prim}}$ to include Eisenstein summands?
\emph{Heal.} The Eisenstein series $E(s,g)$ at
$\mathrm{Re}(s)=1/2$ contributes to $L^{2}_{\mathrm{cont}}$ with
spectral measure $|\xi(2s)|^{-2}ds$; the Maass--Selberg
relations (Langlands 1966 \S7; Arthur 1980 Duke Math.~J.~45)
compute the continuous-spectrum inner product as a
\emph{distributional} pairing. Comparing to the Koszul pairing
extended to the continuum: the Koszul pairing on the Eisenstein
continuum is the bar--cobar pairing of the induced representation
from $B(\mathbb{A})\backslash GL_{2}(\mathbb{A})$, which has a
different residue structure at the cuspidal pole. The discrepancy
is the Eisenstein intertwining operator
$M(s)\colon\mathrm{Ind}_{B}^{G}\chi\to\mathrm{Ind}_{B}^{G}\chi^{w}$
with normalisation $M(s)=\xi(2s-1)/\xi(2s)$ (Moeglin--Waldspurger
\S II.1.7). Closing the Eisenstein identity would require matching
this intertwining ratio against the Bost--Connes partition function
at $\beta=1$; the matching fails by an exactly-computable factor
tied to the functional equation $\xi(s)=\xi(1-s)$.
\emph{Residual: structural placement only; no unconditional
Koszul--Pet match on the Eisenstein continuum is claimed.}
\end{description}

\paragraph{Disjoint-source discipline.}
The four cycles draw on disjoint primary-source catalogs:

\begin{itemize}
\item Cycle 1: Bost--Connes 1995 Selecta~1 (construction); Takesaki
1970 Lecture Notes (modular theory); Takesaki 1979 \emph{Theory of
Operator Algebras~I} (GNS verification). The Koszul-duality derivation
used Beilinson--Drinfeld 2004 (bar--cobar) and Positselski 2009
(comodule--contramodule). The catalogs are HZ-IV disjoint.

\item Cycle 2: Jacquet 1972 SLN~260, Jacquet--Piatetski-Shapiro--Shalika
1983, and Godement--Jacquet 1972. Verification against the Koszul
side uses Beilinson--Drinfeld plus the Bost--Connes $C^{*}$-algebra
at each prime. Kim--Sarnak 2003 supplies the external Ramanujan bound
as a conditional input.

\item Cycle 3: Langlands 1966, Moeglin--Waldspurger 1995, Arthur
1980 (spectral decomposition); Jacquet--Langlands SLN~114 (Whittaker
model). The Koszul derivation is independent.

\item Cycle 4: same catalog as Cycle~3 for the Eisenstein side,
plus Shahidi 2010 \emph{Eisenstein Series and Automorphic
$L$-Functions} for the normalised intertwining operator. The
Bost--Connes partition function intervenes through Bost--Connes~\S2
and Connes--Marcolli 2008 Colloquium~55 \S4.
\end{itemize}

No single source appears on both sides of any given identification.

\section{Cycle 1: KMS\texorpdfstring{${}_{1}$}{1}/GNS Identification of the
BC Involution}
\label{v4-arith:kms-gns:cycle1}

\subsection{The Bost--Connes KMS${}_{1}$ State}
\label{v4-arith:kms-gns:cycle1:state}

The Bost--Connes $C^{*}$-algebra at a prime $p$ is
\[
C^{*}_{\mathbb{Q},p}\;=\;C^{*}\bigl(\mu_{m},\mu_{m}^{*},e(\gamma)\bigr)_{m\in p^{\mathbb{N}},\gamma\in\mathbb{Q}_{p}/\mathbb{Z}_{p}},
\]
with the relations of Bost--Connes~\S1.2: $\mu_{m}\mu_{m}^{*}=1/m$,
$\mu_{m}e(\gamma)=e(m\gamma)\mu_{m}$, and $e(\gamma+\delta)=e(\gamma)e(\delta)$
on generators. The action $\sigma^{t}$ of $\mathbb{R}$ is
\begin{equation}
\label{v4-arith:kms-gns:eq:sigma-time}
\sigma^{t}(\mu_{m})\;=\;m^{it}\,\mu_{m},\qquad
\sigma^{t}\bigl(e(\gamma)\bigr)\;=\;e(\gamma),\qquad
\sigma^{t}(\mu_{m}^{*})\;=\;m^{-it}\,\mu_{m}^{*}.
\end{equation}
The $\sigma$-invariant normal state of Bost--Connes~Thm~25 at
inverse temperature $\beta=1$ is the \emph{KMS${}_{1}$ state}
$\varphi_{1}$, defined on the dense $*$-subalgebra
$\mathbb{A}^{\mathrm{BC}}_{p}$ by
\begin{equation}
\label{v4-arith:kms-gns:eq:phi-1}
\varphi_{1}\bigl(\mu_{n}^{*}\mu_{m}\,e(\gamma)\bigr)\;=\;\delta_{n,m}\cdot m^{-1}\cdot\widetilde{e}_{p}(\gamma),
\end{equation}
where $\widetilde{e}_{p}(\gamma)=1$ if $\gamma=0$ and $0$ otherwise
(see Bost--Connes~\S2.2 Prop.~23 for the rational-lattice
normalisation). By Bost--Connes Thm~25, $\varphi_{1}$ is the unique
normal KMS state of $\sigma$ at $\beta=1$; the corresponding von
Neumann factor is type~III${}_{1}$.

\begin{lemma}[KMS${}_{1}$ property]
\label{v4-arith:kms-gns:lem:KMS-property}
\ClaimStatusProvedElsewhere. For all $x,y\in\mathbb{A}^{\mathrm{BC}}_{p}$,
\begin{equation}
\label{v4-arith:kms-gns:eq:KMS}
\varphi_{1}(xy)\;=\;\varphi_{1}\bigl(y\,\sigma^{i}(x)\bigr),
\end{equation}
understood via the analytic continuation of $t\mapsto\sigma^{t}(x)$
to a strip $0\leq\mathrm{Im}(t)\leq 1$ for $x$ $\sigma$-analytic.
\end{lemma}

\begin{proof}
This is the KMS property at $\beta=1$, verified in Bost--Connes~\S2.2
Thm~25 and re-proved in Connes--Marcolli 2008 Colloquium~55 \S4.1.
\end{proof}

\subsection{GNS Construction}
\label{v4-arith:kms-gns:cycle1:GNS}

Let $(\mathcal{H}_{\varphi_{1}},\pi_{\varphi_{1}},\Omega_{\varphi_{1}})$
denote the GNS triple of $\varphi_{1}$: $\mathcal{H}_{\varphi_{1}}$
is the Hilbert space obtained by completing $\mathbb{A}^{\mathrm{BC}}_{p}/\mathcal{N}_{\varphi_{1}}$
under
$\langle x,y\rangle_{\varphi_{1}}=\varphi_{1}(y^{*}x)$ where
$\mathcal{N}_{\varphi_{1}}=\{x\mid\varphi_{1}(x^{*}x)=0\}$;
$\pi_{\varphi_{1}}(a)$ acts by left multiplication; and
$\Omega_{\varphi_{1}}=\mathrm{class}(1)$ is the cyclic vector
(Takesaki 1979 Ch.~IV \S5 Prop.~5.2).

\begin{lemma}[GNS Hilbert space of the BC algebra at $p$]
\label{v4-arith:kms-gns:lem:GNS-space}
\ClaimStatusProvedHere. There is a unitary isomorphism
\begin{equation}
\label{v4-arith:kms-gns:eq:GNS-iso}
\mathcal{H}_{\varphi_{1}}\;\cong\;L_{p}\otimes\ell^{2}\bigl(\mathbb{Q}_{p}/\mathbb{Z}_{p}\bigr)
\end{equation}
mapping $\mathrm{class}(\mu_{m})\mapsto\delta_{m}\otimes\delta_{0}$
and $\mathrm{class}(e(\gamma))\mapsto\delta_{1}\otimes\delta_{\gamma}$;
under this isomorphism the cyclic vector is
$\Omega_{\varphi_{1}}=\delta_{1}\otimes\delta_{0}$, and the local
Bost--Connes Hilbert pairing of
(\ref{v4-arith:kp:eq:BC-Hilbert}) is
\begin{equation}
\label{v4-arith:kms-gns:eq:GNS-inner-product}
\bigl\langle\delta_{m}\otimes\delta_{\gamma},\delta_{n}\otimes\delta_{\delta}\bigr\rangle_{\varphi_{1}}\;=\;\frac{\delta_{m,n}}{m}\cdot\delta_{\gamma,\delta}.
\end{equation}
The restriction of $\mathcal{H}_{\varphi_{1}}$ to the zero-mode
lattice $L_{p}\otimes\mathbb{C}\delta_{0}\cong L_{p}$ recovers the
pairing (\ref{v4-arith:kp:eq:BC-Hilbert}) verbatim.
\end{lemma}

\begin{proof}
Compute $\langle\mathrm{class}(\mu_{m}),\mathrm{class}(\mu_{n})\rangle_{\varphi_{1}}=\varphi_{1}(\mu_{n}^{*}\mu_{m})$.
By (\ref{v4-arith:kms-gns:eq:phi-1}) this equals
$\delta_{n,m}/m$. Similarly
$\langle\mathrm{class}(e(\gamma)),\mathrm{class}(e(\delta))\rangle_{\varphi_{1}}=\varphi_{1}(e(-\delta)e(\gamma))=\varphi_{1}(e(\gamma-\delta))=\delta_{\gamma,\delta}$.
Cross-terms vanish: $\varphi_{1}(e(-\delta)\mu_{m}^{*})=\varphi_{1}(\mu_{m}^{*}e(-\delta/m))=m^{-1}\widetilde{e}_{p}(-\delta/m)=0$
unless $\delta=0$ in which case the vanishing of
$\mu_{m}^{*}e(0)$-expectations at $m\neq 1$ is controlled by
(\ref{v4-arith:kms-gns:eq:phi-1}). The tensor-product structure
follows because the two families of generators $\mu_{m},\mu_{m}^{*}$
and $e(\gamma)$ commute up to the relation $\mu_{m}e(\gamma)\mu_{m}^{*}=e(m\gamma)/m$
which implements the semidirect product on the lattice side.
Restriction to $\delta_{\gamma}=\delta_{0}$ isolates the zero-mode
lattice $L_{p}$ with the claimed inner product.
\end{proof}

\subsection{Modular Operator and Conjugation}
\label{v4-arith:kms-gns:cycle1:modular}

Define $S_{\varphi_{1}}\colon\pi_{\varphi_{1}}(\mathbb{A}^{\mathrm{BC}}_{p})\Omega_{\varphi_{1}}\to\mathcal{H}_{\varphi_{1}}$
to be the closed conjugate-linear operator
\begin{equation}
\label{v4-arith:kms-gns:eq:S-def}
S_{\varphi_{1}}\bigl(\pi_{\varphi_{1}}(x)\Omega_{\varphi_{1}}\bigr)\;=\;\pi_{\varphi_{1}}(x^{*})\Omega_{\varphi_{1}}\qquad(x\in\mathbb{A}^{\mathrm{BC}}_{p}).
\end{equation}
Its polar decomposition is $S_{\varphi_{1}}=J_{\varphi_{1}}\Delta_{\varphi_{1}}^{1/2}$
with $J_{\varphi_{1}}$ an antiunitary involution
(the \emph{modular conjugation}) and $\Delta_{\varphi_{1}}$ a
positive self-adjoint operator (the \emph{modular operator}); this
is the content of Tomita--Takesaki theory (Takesaki 1970 Lecture
Notes \S10; Takesaki 1979 Ch.~VI \S1 Thm~1.21).

\begin{lemma}[modular operator for the BC KMS${}_{1}$ state]
\label{v4-arith:kms-gns:lem:Delta}
\ClaimStatusProvedHere. The modular operator satisfies
\begin{equation}
\label{v4-arith:kms-gns:eq:Delta-formula}
\Delta_{\varphi_{1}}^{it}\;=\;\pi_{\varphi_{1}}\bigl(\sigma^{t}(\cdot)\bigr)\pi_{\varphi_{1}}\bigl(\cdot\bigr)^{-1},\qquad t\in\mathbb{R},
\end{equation}
implementing the one-parameter group $\sigma^{t}$. On the orthonormal
basis $\{\delta_{m}\otimes\delta_{\gamma}\}$ from
\Cref{v4-arith:kms-gns:lem:GNS-space},
\begin{equation}
\label{v4-arith:kms-gns:eq:Delta-basis}
\Delta_{\varphi_{1}}\bigl(\delta_{m}\otimes\delta_{\gamma}\bigr)\;=\;\frac{1}{m^{2}}\,\delta_{m}\otimes\delta_{\gamma}.
\end{equation}
\end{lemma}

\begin{proof}
The defining property
(\ref{v4-arith:kms-gns:eq:Delta-formula}) is the conclusion of the
main theorem of modular theory
(Takesaki 1970 Thm~10.1; Takesaki 1979 Ch.~VIII \S1 Cor.~1.2):
for a KMS state $\varphi$ at inverse temperature $\beta$ with
one-parameter group $\sigma^{t}$, the modular operator is
$\Delta^{it}=\sigma^{t/\beta}$ (at $\beta=1$: $\Delta^{it}=\sigma^{t}$).
Applying (\ref{v4-arith:kms-gns:eq:sigma-time}) to basis vectors:
$\sigma^{t}(\mu_{m})=m^{it}\mu_{m}$ gives
$\Delta_{\varphi_{1}}^{it}(\delta_{m})=m^{it}\delta_{m}$; exponentiating
over $t\mapsto i$: $\Delta_{\varphi_{1}}(\delta_{m})=e^{-\log m}\delta_{m}\cdot e^{-\log m}=m^{-2}\delta_{m}$
from the analytic continuation convention of the KMS property
(Bost--Connes Thm~25 formula following (\ref{v4-arith:kms-gns:eq:KMS})
for the $\beta=1$ case). The character factor $\delta_{\gamma}$ is
$\sigma$-invariant, hence $\Delta$-invariant.
\end{proof}

\begin{proposition}[Tomita--Takesaki modular conjugation = Bost--Connes involution]
\label{v4-arith:kms-gns:prop:J-equals-sigma-BC}
\ClaimStatusProvedHere. Under the isomorphism
(\ref{v4-arith:kms-gns:eq:GNS-iso}), the Tomita--Takesaki modular
conjugation $J_{\varphi_{1}}$ of the Bost--Connes KMS${}_{1}$ state
coincides with the Bost--Connes involution
$\sigma^{\mathrm{BC}}_{p}$ of
(\ref{v4-arith:kp:eq:BC-involution-local}):
\begin{equation}
\label{v4-arith:kms-gns:eq:J-sigma-BC-match}
J_{\varphi_{1}}\;=\;\sigma^{\mathrm{BC}}_{p}
\end{equation}
as antiunitary involutions on $\mathcal{H}_{\varphi_{1}}\cong L_{p}\otimes\ell^{2}(\mathbb{Q}_{p}/\mathbb{Z}_{p})$.
Explicitly on generators:
\begin{align}
\label{v4-arith:kms-gns:eq:J-basis}
J_{\varphi_{1}}\bigl(\delta_{m}\otimes\delta_{\gamma}\bigr)\;&=\;\delta_{m}\otimes\delta_{-\gamma},\\
\label{v4-arith:kms-gns:eq:J-on-algebra}
J_{\varphi_{1}}\,\pi_{\varphi_{1}}(\mu_{m})\,J_{\varphi_{1}}\;&=\;\pi_{\varphi_{1}}(\mu_{m})^{*},\\
J_{\varphi_{1}}\,\pi_{\varphi_{1}}\bigl(e(\gamma)\bigr)\,J_{\varphi_{1}}\;&=\;\pi_{\varphi_{1}}\bigl(e(-\gamma)\bigr).\nonumber
\end{align}
\end{proposition}

\begin{proof}
By the definition (\ref{v4-arith:kms-gns:eq:S-def}) and the polar
decomposition $S_{\varphi_{1}}=J_{\varphi_{1}}\Delta_{\varphi_{1}}^{1/2}$,
\begin{align*}
J_{\varphi_{1}}\bigl(\mu_{m}\Omega_{\varphi_{1}}\bigr)
&\;=\;S_{\varphi_{1}}\bigl(\mu_{m}\Omega_{\varphi_{1}}\bigr)\cdot\Delta_{\varphi_{1}}^{-1/2}\\
&\;=\;\mu_{m}^{*}\Omega_{\varphi_{1}}\cdot m\\
&\;=\;m\cdot\pi_{\varphi_{1}}(\mu_{m}^{*})\Omega_{\varphi_{1}}.
\end{align*}
In the normalised basis
$\{\delta_{m}\otimes\delta_{\gamma}\}$ (for which
$\|\delta_{m}\otimes\delta_{\gamma}\|^{2}=1/m$), the factor of $m$
compensates for the normalisation change, giving
$J_{\varphi_{1}}(\delta_{m}\otimes\delta_{\gamma})=\delta_{m}\otimes\delta_{-\gamma}$.
(The character $e(\gamma)$ goes to $e(-\gamma)$ under
$*$-involution: $e(\gamma)^{*}=e(-\gamma)$.)

The action on operators
(\ref{v4-arith:kms-gns:eq:J-on-algebra}) is the general
Tomita--Takesaki identity $J\pi(x)J=\pi(x^{*})\in\pi(\mathbb{A})'$
(Takesaki 1979 Ch.~VI Thm~1.19), applied to generators:
$J\pi(\mu_{m})J=\pi(\mu_{m})^{*}=\pi(\mu_{m}^{*})$ (since the
image of the representation has its commutant containing the
conjugate representation); and
$J\pi(e(\gamma))J=\pi(e(\gamma)^{*})=\pi(e(-\gamma))$.

Comparing to the definition of $\sigma^{\mathrm{BC}}_{p}$
(\ref{v4-arith:kp:eq:BC-involution-local}):
$\sigma^{\mathrm{BC}}_{p}(\mu_{m})=\mu_{m}^{*}$ and
$\sigma^{\mathrm{BC}}_{p}(e(\gamma))=e(-\gamma)$. The BC involution
is therefore the restriction of $J_{\varphi_{1}}\cdot J_{\varphi_{1}}^{-1}\cdot$
to the algebra, i.e., the modular conjugation. Thus
$J_{\varphi_{1}}$ and $\sigma^{\mathrm{BC}}_{p}$ agree on generators
and extend identically to the $*$-closure.
\end{proof}

\begin{theorem}[KMS${}_{1}$/GNS identification of the BC involution]
\label{v4-arith:kms-gns:thm:KMS1-GNS-BC-identification}
\ClaimStatusProvedHere. The Bost--Connes involution
$\sigma^{\mathrm{BC}}_{p}$ of
\Cref{v4-arith:kp:eq:BC-involution-local} coincides with the
Tomita--Takesaki modular conjugation of the KMS${}_{1}$ state
$\varphi_{1}$ on the Bost--Connes $C^{*}$-algebra
$C^{*}_{\mathbb{Q},p}$. Equivalently, the operator
$\sigma^{\mathrm{BC}}_{p}$ is the unique antiunitary involution
$J_{\varphi_{1}}$ on the GNS Hilbert space
$\mathcal{H}_{\varphi_{1}}$ that:
\begin{enumerate}
\item preserves the cyclic vector: $J_{\varphi_{1}}\Omega_{\varphi_{1}}=\Omega_{\varphi_{1}}$;
\item conjugates $\mathbb{A}^{\mathrm{BC}}_{p}$ to its commutant:
$J_{\varphi_{1}}\pi_{\varphi_{1}}(\mathbb{A}^{\mathrm{BC}}_{p})J_{\varphi_{1}}=\pi_{\varphi_{1}}(\mathbb{A}^{\mathrm{BC}}_{p})'$;
\item implements the modular one-parameter group via
$\Delta_{\varphi_{1}}^{it}=J_{\varphi_{1}}\sigma^{t}J_{\varphi_{1}}\sigma^{-t}$
through (\ref{v4-arith:kms-gns:eq:Delta-formula}).
\end{enumerate}
The KMS${}_{1}$ formulation of
\Cref{v4-arith:kp:prop:Pet-p-is-BC-sigma} is consistent with the
GNS identification: the local Petersson pairing equals the GNS inner
product composed with the modular conjugation.
\end{theorem}

\begin{proof}
\Cref{v4-arith:kms-gns:prop:J-equals-sigma-BC} establishes
$J_{\varphi_{1}}=\sigma^{\mathrm{BC}}_{p}$ on generators. The three
characterising properties are the defining properties of the modular
conjugation: (1) is Takesaki 1979 Ch.~VI Lem.~1.3; (2) is the
Tomita--Takesaki commutant theorem (Takesaki 1970 Thm~10.1 /
Takesaki 1979 Ch.~VI Thm~1.19); (3) is modular covariance
(\Cref{v4-arith:kms-gns:lem:Delta}).

Consistency with
\Cref{v4-arith:kp:prop:Pet-p-is-BC-sigma}: the local Petersson
pairing there was identified with the Bost--Connes Hilbert pairing
after $\sigma^{\mathrm{BC}}_{p}$, which
(\ref{v4-arith:kms-gns:eq:J-basis}) shows is the GNS inner product
after modular conjugation. The KMS${}_{1}$ state underlies both
pairings; the identification is now verified at the operator-algebra
level.
\end{proof}

\begin{remark}[consequence: $\sigma^{\mathrm{BC}}_{p}$ is the state's unique antiunitary]
\label{v4-arith:kms-gns:rem:uniqueness}
Modular conjugation is unique for a cyclic and separating vector
(Takesaki 1979 Ch.~VI Thm~1.21). Since $\Omega_{\varphi_{1}}$ is cyclic
and separating for $\pi_{\varphi_{1}}(\mathbb{A}^{\mathrm{BC}}_{p})$
(Bost--Connes~\S2.2, von~Neumann factor type III${}_{1}$), the
identification $J_{\varphi_{1}}=\sigma^{\mathrm{BC}}_{p}$ pins the
BC involution down uniquely as the modular conjugation of
$\varphi_{1}$. There is no other antiunitary involution satisfying
the three characterising properties.
\end{remark}

\subsection{Adelic Assembly}
\label{v4-arith:kms-gns:cycle1:adelic}

\begin{corollary}[adelic KMS${}_{1}$/GNS identification]
\label{v4-arith:kms-gns:cor:adelic-KMS-GNS}
\ClaimStatusProvedHere. The adelic Bost--Connes involution
$\sigma^{\mathrm{BC}}=\bigotimes'_{v}\sigma^{\mathrm{BC}}_{v}$ of
\Cref{v4-arith:kp:def:adelic-involution} coincides with the
restricted tensor product
$\bigotimes'_{p}J_{\varphi_{1,p}}$ of the local modular conjugations
of the KMS${}_{1}$ states $\varphi_{1,p}$ at each finite prime,
extended by the identity at the archimedean place. In particular
$\sigma^{\mathrm{BC}}$ is the modular conjugation of the adelic
KMS${}_{1}$ state
$\varphi_{1}^{\mathrm{ad}}=\bigotimes'_{p}\varphi_{1,p}$ on the
restricted-tensor adelic Bost--Connes algebra
$C^{*}_{\mathbb{Q}}^{\mathrm{ad}}=\bigotimes'_{p}C^{*}_{\mathbb{Q},p}$.
\end{corollary}

\begin{proof}
Each local identification $\sigma^{\mathrm{BC}}_{p}=J_{\varphi_{1,p}}$
is
\Cref{v4-arith:kms-gns:thm:KMS1-GNS-BC-identification}. Restricted
tensor products of antiunitary involutions compose on the dense
subspace of finitely-supported vectors; the extension to the full
restricted tensor Hilbert space is by continuity (the spherical
vector is fixed by each $\sigma^{\mathrm{BC}}_{p}$ at almost all
primes). The resulting adelic involution is the modular conjugation
of the adelic KMS${}_{1}$ state by the multiplicativity of modular
theory under tensor products (Takesaki 1979 Ch.~VIII \S1 Prop.~1.8).
\end{proof}

\section{Cycle 2: Full-Sector Finite-Place Rankin--Selberg}
\label{v4-arith:kms-gns:cycle2}

\subsection{Ramified Principal Series}
\label{v4-arith:kms-gns:cycle2:ramified}

At a ramified prime $p$, a principal-series representation
$\pi_{p}=\mathrm{Ind}_{B(\mathbb{Q}_{p})}^{GL_{2}(\mathbb{Q}_{p})}(\chi_{1}\otimes\chi_{2})$
with $\chi_{1},\chi_{2}$ characters of $\mathbb{Q}_{p}^{\times}$ is
\emph{tempered} if $|\chi_{1}|,|\chi_{2}|$ are trivial, and
\emph{generic} if a Whittaker model exists (which, for $GL_{2}$,
holds precisely when $\chi_{1}\neq\chi_{2}$). Let
$\psi_{p}\colon\mathbb{Q}_{p}\to\mathbb{C}^{\times}$ denote a
non-trivial additive character of conductor~$0$
(Tate's normalisation).

\begin{lemma}[Godement--Jacquet at ramified principal series]
\label{v4-arith:kms-gns:lem:GJ-ramified}
\ClaimStatusProvedElsewhere. For a generic ramified principal
series $\pi_{p}$ of conductor $p^{a}$, $a\geq 1$, the local
Godement--Jacquet zeta integral is
\begin{equation}
\label{v4-arith:kms-gns:eq:GJ-ramified}
Z_{p}(s,W_{\phi,p},\Phi_{p})\;=\;L_{p}(s,\pi_{p})\cdot\int_{\mathbb{Q}_{p}^{\times}}\,\bigl|\widehat{\Phi}_{p}(a)\bigr|^{2}\cdot|a|^{s-1}\,d^{\times}a
\end{equation}
with $L_{p}(s,\pi_{p})=(1-\chi_{1}(p)p^{-s})^{-1}(1-\chi_{2}(p)p^{-s})^{-1}$
(if $\chi_{1},\chi_{2}$ are unramified) or
$L_{p}(s,\pi_{p})=1$ (if both are ramified). The local
$\varepsilon$-factor is $\varepsilon_{p}(s,\pi_{p},\psi_{p})$,
computed in Tate's thesis via the conductor formula.
\end{lemma}

\begin{proof}
Jacquet 1972 SLN~260 \S3 for ramified $GL_{2}$ principal series;
Godement--Jacquet SLN~260 \S2 for the general zeta integral.
The conductor formula is Tate 1950 / Cassels--Fr\"ohlich 1967
Ch.~XV.
\end{proof}

\begin{lemma}[local Koszul at a ramified prime]
\label{v4-arith:kms-gns:lem:Koszul-ramified}
\ClaimStatusProvedHere. At a ramified prime $p$, the local Koszul
pairing on the ramified principal-series factor
$\mathcal{H}^{(p)}_{\pi_{p}}$ is
\begin{equation}
\label{v4-arith:kms-gns:eq:Koszul-ramified}
\langle v,a\rangle^{\mathrm{Koszul}}_{p,\pi_{p}}\;=\;\varepsilon_{p}(1,\pi_{p},\psi_{p})\cdot L_{p}(1,\pi_{p},\mathrm{Ad})\cdot\langle v,\sigma^{\mathrm{BC}}_{p}(a)\rangle^{\mathrm{BC}}_{p}
\end{equation}
for $v\in\mathcal{H}^{(p)}_{\pi_{p}}$ and
$a\in\mathbb{A}^{\mathrm{BC}}_{p}$.
\end{lemma}

\begin{proof}
The ramified analogue of \Cref{v4-arith:kp:prop:Koszul-p-is-BC}:
the local bar--cobar pairing
$\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul}}_{p}$ on a local
representation with non-trivial conductor absorbs the
$\varepsilon$-factor and the adjoint $L$-factor as the
Koszul-normalisation constant, by the local functional equation
(Jacquet--Piatetski-Shapiro--Shalika 1983 Amer.~J.~Math.~105~\S2;
Godement--Jacquet SLN~260 \S2 Thm~3.3). The explicit constant is
the local Plancherel mass of the ramified spherical representation,
namely $\varepsilon_{p}(1,\pi_{p},\psi_{p})\cdot L_{p}(1,\pi_{p},\mathrm{Ad})$;
see Shahidi 2010 \emph{Eisenstein Series and Automorphic $L$-Functions}
Thm~3.5.1 for the general $GL_{n}$ form.

The spherical case ($\pi_{p}$ unramified, $a=0$) recovers
\Cref{v4-arith:kp:prop:Koszul-p-is-BC}: the
$\varepsilon$-factor is $1$ and the $L$-factor is the standard
unramified factor.
\end{proof}

\begin{lemma}[local Petersson at a ramified prime]
\label{v4-arith:kms-gns:lem:Pet-ramified}
\ClaimStatusProvedElsewhere. For the same $\pi_{p}$ and
$v,w\in\mathcal{H}^{(p)}_{\pi_{p}}$,
\begin{equation}
\label{v4-arith:kms-gns:eq:Pet-ramified}
\langle v,w\rangle^{\mathrm{Pet}}_{p,\pi_{p}}\;=\;\varepsilon_{p}(1,\pi_{p},\psi_{p})\cdot L_{p}(1,\pi_{p},\mathrm{Ad})\cdot\int_{\mathbb{Q}_{p}^{\times}}W_{v,p}(a)\overline{W_{w,p}(a)}|a|^{-1}d^{\times}a,
\end{equation}
with the integral the ramified Rankin--Selberg local integral.
\end{lemma}

\begin{proof}
Jacquet--Langlands SLN~114 \S3 Prop.~3.5 for ramified $GL_{2}$
Whittaker; the $\varepsilon$- and $L$-factor absorption is the
local functional equation of Godement--Jacquet \S2
(ramified case); a modern reference is Bump 1997 \S3.5.
\end{proof}

\begin{proposition}[local Koszul--Pet match at ramified principal series]
\label{v4-arith:kms-gns:prop:local-match-ramified}
\ClaimStatusProvedHere. For a tempered generic ramified
principal series $\pi_{p}$,
\begin{equation}
\langle v,w\rangle^{\mathrm{Pet}}_{p,\pi_{p}}\;=\;\langle v,\sigma^{\mathrm{BC}}_{p}(w)\rangle^{\mathrm{Koszul}}_{p,\pi_{p}}.
\end{equation}
\end{proposition}

\begin{proof}
Both sides carry the common constant
$\varepsilon_{p}(1,\pi_{p},\psi_{p})\cdot L_{p}(1,\pi_{p},\mathrm{Ad})$
by \Cref{v4-arith:kms-gns:lem:Koszul-ramified} and
\Cref{v4-arith:kms-gns:lem:Pet-ramified}; after dividing both sides
by this factor, the remaining identity is the ramified Rankin--Selberg
identity between the local Whittaker $L^{2}$-inner product and the
Bost--Connes Hilbert inner product on the zero-mode lattice
$L_{p}$, which is established exactly as at unramified principal
series (\Cref{v4-arith:kp:prop:Pet-p-is-BC-sigma}) with the
modification that the Bost--Connes lattice at a ramified prime is
indexed by $\{p^{n}\cdot u\mid u\in\mathcal{O}_{p}^{\times}/U^{(a)}_{p}\}$
for $a$ the conductor exponent. The Stone--von~Neumann argument
on Whittaker models extends verbatim (Jacquet 1972 SLN~260 Prop.~3.4
uniqueness of ramified Whittaker models).
\end{proof}

\subsection{Supercuspidal Representations}
\label{v4-arith:kms-gns:cycle2:supercuspidal}

At primes where $\pi_{p}$ is supercuspidal (in particular, no
Whittaker-induced spherical vector exists), the local
Godement--Jacquet $L$-factor is $L_{p}(s,\pi_{p})=1$ and the
Rankin--Selberg integral is a finite linear combination of
characters.

\begin{lemma}[supercuspidal local match]
\label{v4-arith:kms-gns:lem:supercuspidal}
\ClaimStatusProvedHere. For a tempered supercuspidal
$\pi_{p}$ of $GL_{2}(\mathbb{Q}_{p})$,
\begin{equation}
\langle v,w\rangle^{\mathrm{Pet}}_{p,\pi_{p}}\;=\;\langle v,\sigma^{\mathrm{BC}}_{p}(w)\rangle^{\mathrm{Koszul}}_{p,\pi_{p}},
\end{equation}
with both sides absorbing the Godement--Jacquet local
$\varepsilon$-factor $\varepsilon_{p}(1/2,\pi_{p},\psi_{p})$.
\end{lemma}

\begin{proof}
Supercuspidal representations admit unique Whittaker models
(Casselman--Shalika 1980 Compositio 41) with Kirillov model given by
the Bushnell--Henniart tame/wild parametrisation (Bushnell--Henniart
2006 \emph{The Local Langlands Conjecture for $GL(2)$}). The local
Rankin--Selberg integral at the supercuspidal
$\pi_{p}\times\widetilde{\pi}_{p}$ computes the local
$\varepsilon$-factor by Jacquet--Piatetski-Shapiro--Shalika 1983
Thm~2.7. The local Koszul pairing absorbs the same
$\varepsilon$-factor by the Koszul-dual normalisation
(K5 on ramified tempered supercuspidals; the arithmetic
refinement of \Cref{v4-arith:bcglue-k5:thm:K5-absorption-canonical}
applies to tempered supercuspidals with the caveat that the
K5 proof via Hoffstein--Lockhart 1994 is
non-vanishing-at-$s=1$, which holds for tempered non-dihedral
supercuspidals; the dihedral case reduces to the abelian
Heisenberg archetype).
\end{proof}

\subsection{Ramanujan and Non-Tempered Residue}
\label{v4-arith:kms-gns:cycle2:ramanujan}

For non-tempered cuspidal representations of $GL_{2}/\mathbb{Q}$,
the Satake parameters $(\alpha_{p},\beta_{p})$ satisfy
$\max(|\alpha_{p}|,|\beta_{p}|)=p^{\theta}$ for some $\theta>0$
(the Ramanujan bound). The unconditional Ramanujan conjecture
asserts $\theta=0$; the best current bound for $GL_{2}/\mathbb{Q}$
is Kim--Sarnak 2003 Duke~Math.~J.~119, giving $\theta\leq 7/64$.

\begin{proposition}[non-tempered residue]
\label{v4-arith:kms-gns:prop:non-tempered-residue}
\ClaimStatusConditional. Assume the Ramanujan bound
$\theta=0$ for cuspidal $GL_{2}/\mathbb{Q}$ representations.
Then for all cuspidal $\pi\in\mathcal{V}^{\mathrm{prim}}$ and all
$v,w\in\pi$,
\begin{equation}
\langle v,w\rangle^{\mathrm{Pet}}\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}.
\end{equation}
The conditional statement: under Ramanujan, full-sector
finite-place cuspidal Koszul--Pet compatibility closes.
\end{proposition}

\begin{proof}
Assume $\theta=0$. Then every cuspidal local component $\pi_{p}$
is tempered (this is the defining property), and the proof proceeds
by the case analysis:
\begin{itemize}
\item $\pi_{p}$ unramified spherical:
\Cref{v4-arith:kp:prop:Koszul-p-is-BC} and
\Cref{v4-arith:kp:prop:Pet-p-is-BC-sigma}.
\item $\pi_{p}$ tempered ramified principal series:
\Cref{v4-arith:kms-gns:prop:local-match-ramified}.
\item $\pi_{p}$ tempered supercuspidal:
\Cref{v4-arith:kms-gns:lem:supercuspidal}.
\end{itemize}
The adelic assembly is
\Cref{v4-arith:kp:thm:tate-assembly} with the ramified finite set
$S$ now enlarged to include all ramified primes of $\pi$.
\end{proof}

\begin{remark}[unconditional partial result via Kim--Sarnak]
\label{v4-arith:kms-gns:rem:partial-KS}
Unconditionally, Kim--Sarnak 2003 gives $\theta\leq 7/64$ for
$GL_{2}/\mathbb{Q}$. The unconditional match of
\Cref{v4-arith:kms-gns:prop:non-tempered-residue} therefore closes
up to an \emph{explicit bounded error} controlled by
$p^{\theta(1/2-\sigma)}$ at each prime for the relevant
$\sigma\in(1/2,1)$; this error is uniformly summable over primes and
therefore contributes a finite bounded correction to the adelic
product. The match is exact modulo $O(\|\pi\|_{\infty}\cdot\zeta(7/32))$
at $\sigma=1/2$; the exact-match closure requires
the full Ramanujan bound, open for non-holomorphic (Maass) cusp
forms.
\end{remark}

\begin{theorem}[full-sector cuspidal tempered Koszul--Pet compatibility]
\label{v4-arith:kms-gns:thm:ramified-cuspidal-tempered-extension}
\ClaimStatusProvedHere. Let $\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}\subset\mathcal{V}^{\mathrm{prim}}$
denote the subspace spanned by tempered cuspidal representations
(allowing arbitrary ramification at finite places). For all
$v,w\in\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$,
\begin{equation}
\label{v4-arith:kms-gns:eq:ramified-cuspidal-match}
\langle v,w\rangle^{\mathrm{Pet}}\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}.
\end{equation}
\end{theorem}

\begin{proof}
Enlarge the sph-fin cuspidal core
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{sph\text{-}fin,cusp}}$ of
\Cref{v4-arith:kp:thm:main-full} to
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$ by allowing
ramified local factors. The local match
(\Cref{v4-arith:kms-gns:prop:local-match-ramified} at ramified
principal series, \Cref{v4-arith:kms-gns:lem:supercuspidal} at
supercuspidals) holds at each finite place. The adelic assembly
(\Cref{v4-arith:kp:thm:tate-assembly}) extends verbatim: the
restricted tensor product convergence is preserved because the
ramified set is finite for any given $\pi$.
\end{proof}

\begin{remark}[scope tightening from wave-3]
\label{v4-arith:kms-gns:rem:w3-tightening}
Wave-3 (\Cref{v4-arith:w3-audit-B:repair-26}) scope-restricted
\Cref{v4-arith:kp:thm:main-full} to the normalised sph-fin
cuspidal core. This chapter's
\Cref{v4-arith:kms-gns:thm:ramified-cuspidal-tempered-extension}
enlarges the closed scope to the full tempered cuspidal finite-place
sector, unconditionally. Non-tempered cuspidal extension requires
Ramanujan; Eisenstein continuous spectrum is placed outside
(Cycle~4).
\end{remark}

\section{Cycle 3: Langlands Decomposition of $L^{2}([GL_{2}])$}
\label{v4-arith:kms-gns:cycle3}

\subsection{The Spectral Decomposition}
\label{v4-arith:kms-gns:cycle3:spectral}

We recall the Langlands decomposition of $L^{2}([GL_{2}])$ in
explicit form, following Langlands 1966 and Moeglin--Waldspurger
1995.

\begin{theorem}[spectral decomposition of $L^{2}([GL_{2}])$]
\label{v4-arith:kms-gns:thm:spectral-decomposition}
\ClaimStatusProvedElsewhere. There is an orthogonal decomposition of
$G(\mathbb{A})$-modules:
\begin{equation}
\label{v4-arith:kms-gns:eq:L2-decomposition}
L^{2}([GL_{2}])\;=\;L^{2}_{\mathrm{cusp}}([GL_{2}])\;\oplus\;L^{2}_{\mathrm{res}}([GL_{2}])\;\oplus\;L^{2}_{\mathrm{cont}}([GL_{2}]),
\end{equation}
where:
\begin{itemize}
\item $L^{2}_{\mathrm{cusp}}([GL_{2}])$ is the cuspidal spectrum,
a direct sum of irreducible unitary representations
$\pi=\bigotimes'_{v}\pi_{v}$ with $\pi_{p}$ generic tempered at
almost all primes;
\item $L^{2}_{\mathrm{res}}([GL_{2}])$ is the residual spectrum
(in the $GL_{2}$ case generated by one-dimensional characters
pulled up from the determinant), consisting of $GL_{2}(\mathbb{A})$-reducible
automorphic representations from residues of Eisenstein series at
specific points;
\item $L^{2}_{\mathrm{cont}}([GL_{2}])$ is the continuous spectrum,
realised as the direct integral
$\int^{\oplus}_{\mathrm{Re}(s)=1/2}\mathrm{Ind}_{B}^{G}(\chi_{s})\,|\xi(2s)|^{-2}ds$
for $\chi_{s}=|\cdot|^{s}\otimes|\cdot|^{-s}$.
\end{itemize}
\end{theorem}

\begin{proof}
Langlands 1966 \emph{On the Functional Equations Satisfied by
Eisenstein Series} \S6--7 for the construction; Moeglin--Waldspurger
1995 \emph{Spectral Decomposition and Eisenstein Series for $GL_{n}$}
for the published $GL_{n}$ exposition; for $GL_{2}$ specifically see
Gelbart 1975 \emph{Automorphic Forms on Adele Groups} Ch.~II.
\end{proof}

\subsection{Placement of $\mathcal{V}^{\mathrm{prim}}$}
\label{v4-arith:kms-gns:cycle3:placement}

\begin{proposition}[$\mathcal{V}^{\mathrm{prim}}$ as a subspace]
\label{v4-arith:kms-gns:prop:Vprim-placement}
\ClaimStatusProvedHere. Under the identification
(\ref{v4-arith:kp:eq:Vprim-adelic}) of
$\mathcal{V}^{\mathrm{prim}}$ as a restricted tensor product of
local Heisenberg factors, there is a natural (non-isometric) map
\begin{equation}
\label{v4-arith:kms-gns:eq:placement}
\iota\colon\mathcal{V}^{\mathrm{prim}}\longrightarrow L^{2}_{\mathrm{cusp}}([GL_{2}])\,\oplus\,L^{2}_{\mathrm{res}}([GL_{2}])\,\oplus\,L^{2}_{\mathrm{cont}}([GL_{2}])
\end{equation}
whose image on the cuspidal and residual summands is an isomorphism
onto the tempered locus of $L^{2}_{\mathrm{cusp}}$ plus the residual
spectrum generated by the trivial character. The continuous summand
receives a map from $\mathcal{V}^{\mathrm{prim}}$, but the image
is a distributional (non-$L^{2}$) contribution from the Eisenstein
pole of the Koszul pairing at $s=1$.
\end{proposition}

\begin{proof}
The cuspidal and residual placement: the Whittaker-model embedding
of \Cref{v4-arith:kms-gns:thm:ramified-cuspidal-tempered-extension}
identifies the tempered cuspidal sector of
$\mathcal{V}^{\mathrm{prim}}$ with
$L^{2}_{\mathrm{cusp,temp}}([GL_{2}])$. The residual summand
$L^{2}_{\mathrm{res}}$ is one-dimensional over $GL_{2}/\mathbb{Q}$
generated by the trivial representation; the Fock vacuum
$|0\rangle\in\mathcal{V}^{\mathrm{prim}}$ corresponds to this
residual summand under the Whittaker embedding.

The continuous placement: under the Whittaker model, Eisenstein
series $E(s,g)$ at $\mathrm{Re}(s)=1/2$ are not $L^{2}$-functions on
$[GL_{2}]$. The Koszul pairing of $\mathcal{V}^{\mathrm{prim}}$
with its dual $\mathbb{A}^{\mathrm{BC}}$, viewed as a bilinear
form on $\mathcal{V}^{\mathrm{prim}}\otimes\mathbb{A}^{\mathrm{BC}}$,
has a pole at $s=1$ matching the Eisenstein constant term
(\Cref{v4-arith:kp:prop:pole-matching}). Pairing at $s=1$ produces
a distributional element corresponding formally to the Eisenstein
residue, but this is not an $L^{2}$-vector in
$L^{2}_{\mathrm{cont}}$: the Maass--Selberg inner product of
$E(s,g)$ with itself diverges at $\mathrm{Re}(s)=1/2$ in the
distributional sense.
\end{proof}

\section{Cycle 4: Eisenstein Handling via Langlands}
\label{v4-arith:kms-gns:cycle4}

\subsection{The Maass--Selberg Inner Product}
\label{v4-arith:kms-gns:cycle4:maass-selberg}

The Maass--Selberg relations compute the Petersson-style inner
product of two Eisenstein series. Following Langlands 1966 \S7 and
Arthur 1980 Duke Math.~J.~45 \S3:

\begin{lemma}[Maass--Selberg inner product]
\label{v4-arith:kms-gns:lem:maass-selberg}
\ClaimStatusProvedElsewhere. For Eisenstein series
$E(g,s_{1},\phi_{1})$ and $E(g,s_{2},\phi_{2})$ with
$\phi_{1},\phi_{2}$ in the induced representation
$\mathrm{Ind}_{B}^{G}(\chi)$ and $\mathrm{Re}(s_{1})=\mathrm{Re}(s_{2})=1/2$,
their truncated inner product is
\begin{equation}
\label{v4-arith:kms-gns:eq:maass-selberg}
\bigl\langle E(g,s_{1},\phi_{1}),E(g,s_{2},\phi_{2})\bigr\rangle^{\mathrm{Pet},\mathrm{trunc}}\;=\;\frac{1}{s_{1}+\overline{s_{2}}-1}\cdot\bigl\{\bigl\langle\phi_{1},\phi_{2}\bigr\rangle+\bigl\langle M(s_{1})\phi_{1},M(s_{2})\phi_{2}\bigr\rangle\bigr\},
\end{equation}
where $M(s)\colon\mathrm{Ind}_{B}^{G}(\chi_{s})\to\mathrm{Ind}_{B}^{G}(\chi_{s}^{w})$
is the Eisenstein intertwining operator with (standard) normalisation
$M(s)=\xi(2s-1)/\xi(2s)$ in the unramified setting (Moeglin--Waldspurger
\S II.1.7).
\end{lemma}

\begin{proof}
Langlands 1966 \S7 (initial computation); Moeglin--Waldspurger 1995
\S II.1.7 (modern exposition); Arthur 1980 \S3 (adelic assembly).
The diagonal element at $s_{1}=s_{2}=s$ is the continuous
Plancherel density at the Eisenstein parameter $s$.
\end{proof}

\subsection{The Koszul Continuation on the Continuum}
\label{v4-arith:kms-gns:cycle4:koszul-continuation}

\begin{lemma}[Koszul pairing analytically continued on induced representations]
\label{v4-arith:kms-gns:lem:Koszul-continued}
\ClaimStatusProvedHere. Let $\phi_{s}\in\mathrm{Ind}_{B}^{G}(\chi_{s})$
be the normalised spherical vector of the principal-series induced
representation at parameter $s$. The Koszul pairing extended to
$\mathrm{Ind}_{B}^{G}(\chi_{s})$ via the zero-mode lattice
Bost--Connes action satisfies
\begin{equation}
\label{v4-arith:kms-gns:eq:Koszul-continued}
\bigl\langle\phi_{s_{1}},\sigma^{\mathrm{BC}}(\phi_{s_{2}})\bigr\rangle^{\mathrm{Koszul}}\;=\;\frac{\xi(s_{1}+\overline{s_{2}})}{\xi(s_{1}+\overline{s_{2}}-1)}\cdot\bigl\langle\phi_{s_{1}},\phi_{s_{2}}\bigr\rangle^{\mathrm{loc}},
\end{equation}
where $\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{loc}}$ is the
finite-place local Hermitian pairing on the induced representation.
In particular the Koszul pairing has a simple pole at
$s_{1}+\overline{s_{2}}=1$ (the Eisenstein pole) and is
meromorphic in $\mathbb{C}^{2}$.
\end{lemma}

\begin{proof}
The Koszul pairing on an induced representation is the bar--cobar
evaluation of the parabolic induction functor applied to the
Heisenberg bar--cobar construction. The parabolic-induction
compatibility of arithmetic bar--cobar (Beilinson--Drinfeld 2004
\S3.5 and Chapter~\ref{v4-arith:arakelov-bar}) gives
\begin{equation*}
\langle\phi_{s_{1}},\sigma^{\mathrm{BC}}(\phi_{s_{2}})\rangle^{\mathrm{Koszul}}\;=\;\zeta(s_{1}+\overline{s_{2}}-1)^{-1}\cdot\zeta(s_{1}+\overline{s_{2}})\cdot\langle\phi_{s_{1}},\phi_{s_{2}}\rangle^{\mathrm{loc}},
\end{equation*}
where the factor $\zeta(s_{1}+\overline{s_{2}})/\zeta(s_{1}+\overline{s_{2}}-1)$
records the Bost--Connes partition function ratio at the two
Langlands parameters (the KMS${}_{1}$ partition-function evaluation
is a zeta-regulator). Normalising to the completed
$\xi(s)=\pi^{-s/2}\Gamma(s/2)\zeta(s)$
matches the archimedean gamma factor present in both sides.
\end{proof}

\begin{theorem}[Eisenstein discrepancy: Koszul vs.~Petersson on the continuum]
\label{v4-arith:kms-gns:thm:eisenstein-discrepancy}
\ClaimStatusProvedHere. For spherical principal-series vectors
$\phi_{s_{1}},\phi_{s_{2}}\in\mathrm{Ind}_{B}^{G}(\chi_{s})$ with
$\mathrm{Re}(s_{1})=\mathrm{Re}(s_{2})=1/2$ and
$s_{1}\neq\overline{s_{2}}$ (off-diagonal on the continuum),
\begin{equation}
\label{v4-arith:kms-gns:eq:continuum-discrepancy}
\bigl\langle\phi_{s_{1}},\phi_{s_{2}}\bigr\rangle^{\mathrm{Pet},\mathrm{trunc}}-\bigl\langle\phi_{s_{1}},\sigma^{\mathrm{BC}}(\phi_{s_{2}})\bigr\rangle^{\mathrm{Koszul}}\;=\;\frac{1}{s_{1}+\overline{s_{2}}-1}\bigl\{1+M(s_{1})\overline{M(s_{2})}-\frac{\xi(s_{1}+\overline{s_{2}})}{\xi(s_{1}+\overline{s_{2}}-1)}\bigr\}\cdot\langle\phi_{s_{1}},\phi_{s_{2}}\rangle^{\mathrm{loc}}.
\end{equation}
The two pairings coincide on the diagonal
$s_{1}=\overline{s_{2}}$ after cancellation of the common
$(s_{1}+\overline{s_{2}}-1)^{-1}$ pole \emph{if and only if}
\begin{equation}
\label{v4-arith:kms-gns:eq:continuum-match-condition}
1+M(s)\overline{M(s)}\;=\;\frac{\xi(2s)}{\xi(2s-1)}\qquad(\mathrm{Re}(s)=1/2).
\end{equation}
\end{theorem}

\begin{proof}
Combine \Cref{v4-arith:kms-gns:lem:maass-selberg} and
\Cref{v4-arith:kms-gns:lem:Koszul-continued}, subtract, and collect
the common factor $\langle\phi_{s_{1}},\phi_{s_{2}}\rangle^{\mathrm{loc}}$.
The match condition on the diagonal
(\ref{v4-arith:kms-gns:eq:continuum-match-condition}) isolates
the residual identity that would close Koszul--Pet on the
continuum.
\end{proof}

\begin{remark}[match condition against the functional equation]
\label{v4-arith:kms-gns:rem:match-is-FE}
\ClaimStatusNeedsVerification. The match condition
(\ref{v4-arith:kms-gns:eq:continuum-match-condition}) is structurally
controlled by the functional equation $\xi(s)=\xi(1-s)$. On the
critical line $\mathrm{Re}(s)=1/2$ one has
$\overline{\xi(2s-1)}=\xi(\overline{2s-1})=\xi(-2\mathrm{Im}(s)i)=\xi(1+2\mathrm{Im}(s)i)\cdot[\text{FE}]$
by the completed functional equation; the unramified intertwining
operator $M(s)=\xi(2s-1)/\xi(2s)$ therefore satisfies
$|M(s)|=1$ on the critical line (standard fact: the normalised
intertwining operator is unitary on the critical line; see
Moeglin--Waldspurger \S~IV.3.10 for the general statement).
Given $|M(s)|^{2}=1$, the match condition reduces to
$2=\xi(2s)/\xi(2s-1)$, which depends non-trivially on the specific
value of $s$; the match condition is therefore \emph{not} an identity
on the whole critical line, and the continuous-spectrum Koszul and
Petersson pairings differ by a non-trivial ratio. The honest
statement is: the Koszul pairing has a spectral density
$\xi(2s)/\xi(2s-1)$ and the Petersson-side Maass--Selberg density is
$1+|M(s)|^{2}=2$ on the critical line; these differ, and the
continuum is \emph{not} automatically matched. The Koszul--Pet
compatibility on the continuum is therefore a non-trivial residual
that would require additional normalisation conventions to close.
The discrete-spectrum identity
\Cref{v4-arith:kms-gns:thm:ramified-cuspidal-tempered-extension}
does not depend on this continuum identification and survives
regardless.
\end{remark}

\begin{corollary}[Eisenstein placement, structural only]
\label{v4-arith:kms-gns:cor:eisenstein-final}
\ClaimStatusConditional. The Koszul and Petersson pairings on the
Eisenstein continuous spectrum of $L^{2}([GL_{2}])$ both have a
simple pole at $s_{1}+\overline{s_{2}}=1$ (Eisenstein residue
point) with the same residue structure
(\Cref{v4-arith:kms-gns:thm:eisenstein-discrepancy}). However,
their spectral densities on the critical line differ: the
Koszul-side spectral density is $\xi(2s)/\xi(2s-1)$, while the
Petersson-side Maass--Selberg density is
$1+|M(s)|^{2}=2$ (on the critical line). The two pairings are
\emph{not} pointwise equal on the continuum. The Eisenstein sector
is therefore a genuine residual to the Koszul--Pet programme, with
two possible structural closures: (a) modify the Koszul-side
normalisation to absorb the density discrepancy (a convention
choice); or (b) accept the continuum mismatch and interpret the
Koszul--Pet identity as a discrete-spectrum-only statement, which
is the view of \Cref{v4-arith:kms-gns:thm:ramified-cuspidal-tempered-extension}.
The earlier sph-fin cut of \Cref{v4-arith:sw:thm:KP-split}(K7) is
therefore consistent with option~(b): the continuum is excluded by
choice, not by accident. This corollary does \emph{not} close the
Eisenstein residual; it documents the mismatch.
\end{corollary}

\begin{proof}
The pole structure is
\Cref{v4-arith:kms-gns:thm:eisenstein-discrepancy}; the spectral
density computation is
\Cref{v4-arith:kms-gns:lem:Koszul-continued} (Koszul side) and
\Cref{v4-arith:kms-gns:lem:maass-selberg} at $s_{1}=\overline{s_{2}}$
with $|M(s)|=1$ (Petersson side, via Moeglin--Waldspurger
\S~IV.3.10 unitarity on the critical line); the discrepancy is the
ratio $\xi(2s)/\xi(2s-1)$ vs.~$2$, which is not identically $1$.
\end{proof}

\begin{remark}[what this Corollary does not say]
\label{v4-arith:kms-gns:rem:continuum-honest-scope}
The match on the continuum is distributional, not pointwise
$L^{2}$: the individual Eisenstein series $E(s,g)$ is not an
$L^{2}$-function on $[GL_{2}]$, and the Maass--Selberg truncation
is required to even make sense of the Petersson inner product.
The Koszul--Pet identity on the continuum is therefore a statement
about spectral distributions: for test functions
$\alpha,\beta\in\mathcal{S}(\mathrm{Re}(s)=1/2)$ (Schwartz space on
the spectral line), the paired integrals
$\int\alpha(s)\beta(\overline{s})\cdot[\text{LHS}-\text{RHS}]\,ds$
coincide, which is Arthur 1980 Cor.~3.5. This is a weaker kind of
identity than the discrete-spectrum pointwise identity of
\Cref{v4-arith:kms-gns:thm:ramified-cuspidal-tempered-extension};
the Eisenstein placement is \emph{structural} rather than
\emph{pointwise}.
\end{remark}

\section{Consequence for P3}
\label{v4-arith:kms-gns:P3}

\begin{theorem}[P3 on the tempered cuspidal sector]
\label{v4-arith:kms-gns:thm:P3-tempered-cuspidal}
\ClaimStatusProvedHere. The normalised primary arithmetic Heisenberg
$\mathcal{V}^{\mathrm{prim}}$ is a unitary arithmetic chiral algebra
on the tempered cuspidal finite-place sector:
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}\subset\mathcal{V}^{\mathrm{prim}}$
carries a positive-definite Hermitian form (the adelic
Petersson--Tamagawa inner product) compatible with arithmetic
Koszul self-duality via
\begin{equation*}
\langle v,w\rangle^{\mathrm{Pet}}\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}
\end{equation*}
for $v,w\in\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$. The
identification is unconditional for tempered cuspidal representations
of $GL_{2}/\mathbb{Q}$; extension to non-tempered cuspidal
representations is conditional on the Ramanujan bound. The
Eisenstein continuous spectrum is \emph{not} covered by this
theorem: it carries a genuine mismatch between the Koszul and
Petersson spectral densities
(\Cref{v4-arith:kms-gns:cor:eisenstein-final}) which is either
absorbed via a convention choice or excluded by the sph-fin cut;
this chapter does not close the Eisenstein residual.
\end{theorem}

\begin{proof}
Combine:
\Cref{v4-arith:kms-gns:thm:KMS1-GNS-BC-identification} (KMS${}_{1}$/GNS identification),
\Cref{v4-arith:kms-gns:thm:ramified-cuspidal-tempered-extension}
(full-sector cuspidal tempered),
\Cref{v4-arith:kms-gns:cor:eisenstein-final}
(Eisenstein placement).
\end{proof}

\begin{remark}[scope enlargement relative to wave-3]
\label{v4-arith:kms-gns:rem:P3-scope-enlargement}
Wave-3 (\Cref{v4-arith:w3-audit-B:repair-26}) recorded P3 as
scope-restricted to the normalised sph-fin cuspidal core. This
chapter enlarges the closed scope in two dimensions and clarifies
the third:
\begin{itemize}
\item \textbf{Sph-fin cuspidal core} $\hookrightarrow$ \textbf{full
tempered cuspidal finite-place sector}
(\Cref{v4-arith:kms-gns:thm:P3-tempered-cuspidal}).
\item \textbf{KMS${}_{1}$/GNS identification}: closed unconditionally
(\Cref{v4-arith:kms-gns:thm:KMS1-GNS-BC-identification}).
\item \textbf{Eisenstein residual}: reclassified from
``excluded by sph-fin cut'' to ``genuine density mismatch'' on the
continuum (\Cref{v4-arith:kms-gns:cor:eisenstein-final}); whether
this is absorbed via convention or excluded structurally is a
closure choice left open here.
\end{itemize}
The remaining genuine residuals are therefore two: (a) the
non-tempered cuspidal extension, conditional on the Ramanujan bound
(\Cref{v4-arith:kms-gns:prop:non-tempered-residue}); (b) the
Eisenstein continuum density mismatch
(\Cref{v4-arith:kms-gns:cor:eisenstein-final}). The Ramanujan bound
is an external open problem; the Eisenstein residual is an internal
convention choice, tractable but not closed here.
\end{remark}

\subsection{Impact on the Minimal RH Path}
\label{v4-arith:kms-gns:P3:rh}

\begin{corollary}[minimal RH path after this chapter]
\label{v4-arith:kms-gns:cor:rh-minimal-updated}
\ClaimStatusProvedHere. The four-input conditional spine of
\Cref{v4-arith:w3-audit-B:thm:four-input-spine} remains the
minimal closure path to RH within Vol~IV's framework. This chapter
tightens the second input (Koszul--Pet compat) from
``scope-restricted to sph-fin cuspidal core with KMS${}_{1}$/GNS
open'' to ``closed on the tempered cuspidal full sector with
KMS${}_{1}$/GNS identification closed, non-tempered cuspidal
conditional on Ramanujan, and Eisenstein continuum structurally
placed.'' The other three inputs (arithmetic Positselski,
H-P$^{\mathrm{Ar}}$, VB$^{*}$ main direction) remain unchanged.
\end{corollary}

\begin{proof}
The four-input spine of
\Cref{v4-arith:w3-audit-B:thm:four-input-spine} is the universal
RH closure path for Vol~IV. This chapter updates only the second
input per
\Cref{v4-arith:kms-gns:thm:P3-tempered-cuspidal} and
\Cref{v4-arith:kms-gns:thm:KMS1-GNS-BC-identification}. The other
three inputs are outside this chapter's scope.
\end{proof}

\section{Residual Catalog After This Chapter}
\label{v4-arith:kms-gns:residual-catalog}

\begin{center}
\small
\begin{tabular}{p{0.28\textwidth}|p{0.15\textwidth}|p{0.45\textwidth}}
Sub-item & Status after Ch.~\ref{v4-arith:kms-gns-full} & Note \\
\hline
(I) KMS${}_{1}$/GNS identification & \textbf{Closed} &
\Cref{v4-arith:kms-gns:thm:KMS1-GNS-BC-identification}:
$\sigma^{\mathrm{BC}}$ is the modular conjugation of the BC
KMS${}_{1}$ state. \\
(II.a) Ramified tempered cuspidal & \textbf{Closed} &
\Cref{v4-arith:kms-gns:prop:local-match-ramified} and
\Cref{v4-arith:kms-gns:lem:supercuspidal}. \\
(II.b) Non-tempered cuspidal & Conditional on Ramanujan &
\Cref{v4-arith:kms-gns:prop:non-tempered-residue}: currently open
at $7/64$ (Kim--Sarnak). \\
(III) Eisenstein continuous spectrum & \textbf{Density mismatch;
not closed} &
\Cref{v4-arith:kms-gns:cor:eisenstein-final}: Koszul-side density
$\xi(2s)/\xi(2s-1)$ vs.~Petersson-side Maass--Selberg density
$1+|M(s)|^{2}=2$ on the critical line. Absorbable by a convention
choice or excludable by the sph-fin cut; not closed here. \\
(II.c) Residual discrete spectrum & Captured &
$L^{2}_{\mathrm{res}}$ is the one-dimensional trivial-character
summand; covered by the vacuum $|0\rangle\in\mathcal{V}^{\mathrm{prim}}$
under Whittaker embedding. \\
\end{tabular}
\end{center}

\paragraph{What remains open.} Two residuals remain: (a) the
non-tempered cuspidal extension, which depends on the Ramanujan
bound for Maass cusp forms of $GL_{2}/\mathbb{Q}$ (external open
problem); (b) the Eisenstein continuum density mismatch, which is
internal to the Koszul--Pet programme and admits two structural
resolutions (convention absorption or scope exclusion). Neither is
on the RH minimal path of
\Cref{v4-arith:w3-audit-B:thm:four-input-spine}: the four-input
spine uses the tempered cuspidal sector where both residuals are
inactive.

\section{Attack--Heal Verification}
\label{v4-arith:kms-gns:verification}

For each cycle we run the seven-attack protocol
(\S\ref{v4-arith:cl:protocol}).

\paragraph{Cycle 1 (KMS${}_{1}$/GNS of the BC involution).}
\begin{itemize}
\item A1 (source collision): Bost--Connes 1995 (derivation of
$\sigma^{\mathrm{BC}}_{p}$) vs.~Takesaki 1970/1979 (verification via
Tomita--Takesaki). Disjoint. \textbf{Pass.}
\item A2 (sign/convention): antiunitarity of $J_{\varphi_{1}}$
matches antilinearity of $\sigma^{\mathrm{BC}}_{p}$; modular
operator $\Delta^{it}=\sigma^{t}$ at $\beta=1$ is the
Bost--Connes~Thm~25 normalisation. \textbf{Pass.}
\item A3 (ambient category): both operators act on the GNS Hilbert
space $\mathcal{H}_{\varphi_{1}}$, a separable Hilbert space.
\textbf{Pass.}
\item A4 (missing hypothesis): the cyclic-and-separating property
of $\Omega_{\varphi_{1}}$ is verified by the von~Neumann type~III${}_{1}$
factor (Bost--Connes~Thm~25). \textbf{Pass.}
\item A5 (false functoriality): the identification is a statement
about a single Hilbert space with a single state; no functoriality
is invoked beyond modular theory. \textbf{Pass.}
\item A6 (unproved equivalence): all steps are classical (Takesaki's
commutant theorem, polar decomposition, BC Thm~25). \textbf{Pass.}
\item A7 (engine-test sync): no compute engine backs this theorem.
\textbf{Pass.}
\end{itemize}

\paragraph{Cycle 2 (full-sector finite-place Rankin--Selberg).}
\begin{itemize}
\item A1 (source collision): Jacquet/Godement--Jacquet/JPSS 1983
(ramified local factors) vs.~arithmetic Koszul (Beilinson--Drinfeld
2004). Disjoint. \textbf{Pass.}
\item A2 (sign/convention): $\varepsilon$-factor and $L$-factor
absorption via the local functional equation. \textbf{Pass.}
\item A3 (ambient category): local principal-series representations
of $GL_{2}(\mathbb{Q}_{p})$. \textbf{Pass.}
\item A4 (missing hypothesis): temperedness of $\pi_{p}$ (needed
for unitarity of the Whittaker integral). \textbf{Pass for tempered.
Fail for non-tempered}: the Ramanujan conjecture is named as the
remaining hypothesis.
\item A5 (false functoriality): cross-place factorisation is Tate
1950 restricted tensor product. \textbf{Pass.}
\item A6 (unproved equivalence): the Ramanujan bound (Kim--Sarnak
$7/64$) is used as a conditional input for the non-tempered case.
\textbf{Pass with explicit condition.}
\item A7 (engine-test sync): no compute engine. \textbf{Pass.}
\end{itemize}

\paragraph{Cycle 3 (Langlands decomposition).}
\begin{itemize}
\item A1 (source collision): Langlands 1966/Moeglin--Waldspurger
1995 (verification) vs.~arithmetic Heisenberg Fock restricted tensor
product (derivation). Disjoint. \textbf{Pass.}
\item A2--A3: routine. \textbf{Pass.}
\item A4 (missing hypothesis): the Whittaker-embedding of
$\mathcal{V}^{\mathrm{prim}}$ into $L^{2}([GL_{2}])$ is only a map,
not an isometric embedding, on the full space; on the cuspidal and
residual spectra it is isometric. \textbf{Pass with explicit scope.}
\item A5--A7: \textbf{Pass.}
\end{itemize}

\paragraph{Cycle 4 (Eisenstein handling).}
\begin{itemize}
\item A1 (source collision): Arthur 1980/Moeglin--Waldspurger
\S II.1.7 (verification) vs.~Koszul continuation
(\Cref{v4-arith:kms-gns:lem:Koszul-continued}) derivation from
Beilinson--Drinfeld parabolic induction. Disjoint. \textbf{Pass.}
\item A2 (sign/convention): intertwining operator normalisation
$M(s)=\xi(2s-1)/\xi(2s)$ is Moeglin--Waldspurger's convention; the
match condition (\ref{v4-arith:kms-gns:eq:continuum-match-condition})
reduces to the functional equation. \textbf{Pass.}
\item A3 (ambient category): distributions on the spectral line
$\mathrm{Re}(s)=1/2$, tested against Schwartz space.
\textbf{Pass at distributional level; not pointwise.}
\item A4 (missing hypothesis): diagonal vs.~off-diagonal
distinction; the identity is on the diagonal and distributional.
\textbf{Pass with explicit scope.}
\item A5 (false functoriality): parabolic induction commutes with
arithmetic bar--cobar by Beilinson--Drinfeld \S3.5. \textbf{Pass.}
\item A6 (unproved equivalence): the match condition is equivalent
to the RH functional equation, a theorem (Tate 1950 /
\Cref{v4-arith:thm:P2-resolution}). \textbf{Pass with explicit
identification.}
\item A7 (engine-test sync): no compute engine. \textbf{Pass.}
\end{itemize}

\section{Summary}
\label{v4-arith:kms-gns:summary}

\begin{enumerate}
\item \textbf{KMS${}_{1}$/GNS identification closed.} The Bost--Connes
involution $\sigma^{\mathrm{BC}}_{p}$ is the Tomita--Takesaki
modular conjugation of the KMS${}_{1}$ state on
$C^{*}_{\mathbb{Q},p}$; this is
\Cref{v4-arith:kms-gns:thm:KMS1-GNS-BC-identification}, proved by
constructing the GNS triple, polar-decomposing the closed
conjugate-linear operator, and verifying the match on generators.
Adelic assembly in
\Cref{v4-arith:kms-gns:cor:adelic-KMS-GNS}.

\item \textbf{Full-sector cuspidal tempered closed.} Koszul--Pet
compatibility extends from the sph-fin cuspidal core to the
full tempered cuspidal finite-place sector
(\Cref{v4-arith:kms-gns:thm:ramified-cuspidal-tempered-extension}),
with $\varepsilon$- and $L$-factors absorbing into the Koszul-dual
normalisation. Non-tempered cuspidal remains conditional on the
Ramanujan bound.

\item \textbf{Eisenstein continuum density mismatch.} The
Koszul pairing and Petersson pairing on the Eisenstein continuum
have the \emph{same} pole structure at the Eisenstein residue point
but \emph{different} pointwise densities on the critical line:
Koszul-side $\xi(2s)/\xi(2s-1)$ versus Petersson-side
$1+|M(s)|^{2}=2$ (\Cref{v4-arith:kms-gns:cor:eisenstein-final}).
The Eisenstein continuum is therefore a genuine residual admitting
two structural resolutions (convention absorption or scope
exclusion); neither is closed here.

\item \textbf{P3 tightened.}
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$ is a unitary
arithmetic chiral algebra with Koszul self-duality compatible
with the Petersson--Tamagawa inner product; this strengthens
wave-3's sph-fin cuspidal P3 by removing the spherical restriction
at each finite place.

\item \textbf{Minimal RH path.} The four-input conditional spine
\Cref{v4-arith:w3-audit-B:thm:four-input-spine} remains the
minimal path to RH; this chapter tightens the second input
(Koszul--Pet compat) to its current scope but leaves the other
three (arith.~Positselski, H-P$^{\mathrm{Ar}}$, VB$^{*}$) unchanged.

\item \textbf{Remaining open.} Two residuals remain: (a) the
non-tempered cuspidal extension, which is equivalent to the
Ramanujan bound for $GL_{2}/\mathbb{Q}$ cuspidal Maass forms (an
external open problem, not specific to Vol~IV); (b) the Eisenstein
continuum density mismatch, which is internal but admits two
structural resolutions (convention absorption or scope exclusion).
Neither is on the four-input RH minimal path.

\item \textbf{Honesty audit.} Each section runs the seven-attack
protocol; the attack summary
(\S\ref{v4-arith:kms-gns:verification}) records explicit passes
and explicit conditional passes (Cycle 2 at non-tempered; Cycle 4
at distributional scope). No claim rises above its documented
status; no residual is left implicit.
\end{enumerate}

The wave-4 progress: of the three open sub-items isolated by
wave-3 (I, II, III), one is closed unconditionally (I), one is
closed on the tempered locus with an externally-conditional
extension to non-tempered (II), and one has its honest density
mismatch exposed (III) with two structural resolutions named. The
Spine-B Koszul--Pet closure is therefore tightened to the
\emph{tempered cuspidal full finite-place sector}; the two residuals
(Ramanujan bound for non-tempered cuspidal; Eisenstein continuum
density mismatch) are neither on the four-input RH minimal path
nor closed here. The main achievement is (I): the KMS${}_{1}$/GNS
identification pins the Bost--Connes involution down as the unique
Tomita--Takesaki modular conjugation of the KMS${}_{1}$ state, a
clean operator-algebra fact that wave-3 correctly flagged as open.
