\chapter{Arithmetic Positselski: Four Residual Sub-Items}
\label{v4-arith:w5-d:chapter}

\emph{Of the five open Positselski sub-items named in route~3 audit OC1
(\Cref{v4-arith:pos:rem:open-sub-items}), sub-item (4) (primitive
zeta-character theorem) is closed unconditionally in
Chapter~\ref{v4-arith:prim-zeta-char} via Tate 1950 Mellin--theta and
Julia 1990 primon gas. Four remain: (1) completed continuous duals for
the Iwasawa algebra $\Lambda_{p}=\mathbb{Z}_{p}[[G_{p}]]$, (2) derived
$p$-adic completion of chain complexes of $\Lambda_{p}$-modules,
(3) faithful lifting of mod-$p$ representations along
$\Lambda_{p}\to\mathbb{F}_{p}$, and (5) Koszul-dual description of the
Bost--Connes system as the enveloping sheaf of the adele class space.
This chapter closes all four using first-principles tools: Pontryagin
duality on locally compact abelian groups (classical since Weil 1940),
Greenlees--May derived completion (Trans.~AMS 340, 1992), Matlis
duality on the compact heart (Matlis 1958), and Bost--Connes 1995
Selecta Math.~1 (1995), 411--457, combined with Consani--Marcolli adele-class
duality. None of the four arguments uses Iwasawa theory proper; each
reduces to a classical compactness or completion argument applied to
the correct Pontryagin-dual lattice. The combined four-sub-item
theorem delivers the full arithmetic Positselski closure: combined
with sub-item (4) of Ch.~\ref{v4-arith:prim-zeta-char},
\Cref{v4-arith:thm:arithmetic-positselski} lifts from conditional to
unconditional. Status upgrade: \emph{Theorem-waiting} $\to$
\emph{Theorem}, conditional only on the non-abelian Iwasawa extension
(Attack 6 of Ch.~\ref{v4-arith:arith-positselski} residual scope).}

\section{Continuous Duals}
\label{v4-arith:w5-d:sec:continuous-duals}

\subsection{Iwasawa Algebra and Pontryagin Dual}
\label{v4-arith:w5-d:cts-dual:iwasawa}

Fix a prime $p$. Let $G_{p}=\mathrm{Gal}(\mathbb{Q}_{p}^{\mathrm{ab}}/\mathbb{Q}_{p})$
and
\begin{equation}
\label{v4-arith:w5-d:eq:iwasawa-def}
\Lambda_{p}\;:=\;\mathbb{Z}_{p}[[G_{p}]]\;=\;\varprojlim_{U}\mathbb{Z}_{p}[G_{p}/U],
\end{equation}
the inverse limit over open normal subgroups $U\trianglelefteq G_{p}$
of finite index. By local class field theory (Serre 1962,
\emph{Corps locaux}, Ch.~XIV \S5), $G_{p}$ is a profinite group and
$\Lambda_{p}$ is a compact topological ring in the inverse-limit
topology (each $\mathbb{Z}_{p}[G_{p}/U]$ is a finite $\mathbb{Z}_{p}$-module
in the $p$-adic topology). The underlying additive group is a compact
topological abelian group; in the notation of Weil 1940 \emph{L'int\'egration}
Ch.~II, $\Lambda_{p}\in\mathrm{LCA}$, the category of locally compact
abelian groups.

\begin{definition}[continuous Pontryagin dual]
\label{v4-arith:w5-d:cts-dual:def:pontryagin}
\ClaimStatusDefinitional. For $A\in\mathrm{LCA}$, the
\emph{continuous Pontryagin dual} is
\begin{equation}
\label{v4-arith:w5-d:eq:pontryagin-def}
A^{\ast}\;:=\;\mathrm{Hom}_{\mathrm{cts}}(A,\mathbb{R}/\mathbb{Z}),
\end{equation}
the group of continuous homomorphisms into the circle, topologised by
compact-open convergence. For $A$ compact, $A^{\ast}$ is discrete;
for $A$ discrete, $A^{\ast}$ is compact (Pontryagin 1934, Weil 1940
Ch.~II \S2). For $A$ a $p$-primary torsion group (a $\mathbb{Z}_{p}$-module
in the sense that $p^{n}A\to 0$), $A^{\ast}$ takes values in
$\mathbb{Q}_{p}/\mathbb{Z}_{p}\subset\mathbb{R}/\mathbb{Z}$ and one
writes
\begin{equation}
\label{v4-arith:w5-d:eq:p-pontryagin}
A^{\vee}\;:=\;\mathrm{Hom}_{\mathrm{cts}}(A,\mathbb{Q}_{p}/\mathbb{Z}_{p}),
\end{equation}
the \emph{$p$-adic Pontryagin dual}.
\end{definition}

\begin{theorem}[Pontryagin double duality, LCA version]
\label{v4-arith:w5-d:cts-dual:thm:pontryagin}
\ClaimStatusProvedElsewhere. The contravariant functor $A\mapsto A^{\ast}$
from $\mathrm{LCA}$ to $\mathrm{LCA}$ is an anti-equivalence of
categories: the double-dual natural transformation
$A\to A^{\ast\ast}$, $a\mapsto\mathrm{ev}_{a}$, is an isomorphism of
topological groups for every $A\in\mathrm{LCA}$. Restriction to compact
abelian groups: the anti-equivalence exchanges compact and discrete.
Restriction to $p$-primary: the anti-equivalence exchanges compact
pro-$p$ and discrete $p$-primary torsion.
\end{theorem}

The proof is Pontryagin 1934 (originally for separable compact abelian
groups); the general LCA formulation is Weil 1940 Ch.~II \S5 and
Folland 1995 \emph{A Course in Abstract Harmonic Analysis} Ch.~4,
Thm.~4.31 (the latter has the cleanest topological-group-valued
statement).

\subsection{The Continuous Dual of $\Lambda_{p}$}
\label{v4-arith:w5-d:cts-dual:dual-of-Lambda}

\begin{proposition}[continuous dual of Iwasawa algebra]
\label{v4-arith:w5-d:cts-dual:prop:main}
\ClaimStatusProvedHere. The continuous Pontryagin dual of
$\Lambda_{p}$ is naturally isomorphic to the discrete $p$-primary
torsion module of continuous $\mathbb{Q}_{p}/\mathbb{Z}_{p}$-valued
functions on $G_{p}$:
\begin{equation}
\label{v4-arith:w5-d:eq:dual-of-lambda}
(\Lambda_{p})^{\ast}\;=\;\Lambda_{p}^{\vee}\;=\;C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p}),
\end{equation}
equipped with the discrete topology and the $G_{p}$-module structure
induced by translation: $(g\cdot f)(h)=f(g^{-1}h)$.
\end{proposition}

\begin{proof}
The first equality $(\Lambda_{p})^{\ast}=\Lambda_{p}^{\vee}$ is
immediate: $\Lambda_{p}$ is pro-$p$ (compact pro-$p$ group), so every
continuous homomorphism $\Lambda_{p}\to\mathbb{R}/\mathbb{Z}$ factors
through the pro-$p$ part $\mathbb{Q}_{p}/\mathbb{Z}_{p}$ of the circle
(\Cref{v4-arith:w5-d:cts-dual:def:pontryagin} ad finem).

The second equality $\Lambda_{p}^{\vee}=C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p})$
is the content. Write $\Lambda_{p}=\varprojlim_{U}\mathbb{Z}_{p}[G_{p}/U]$
as an inverse limit of finite $\mathbb{Z}_{p}$-modules. The dual of a
cofiltered inverse limit of compact groups is the filtered direct
limit of duals (Weil 1940 Ch.~II \S5 Prop.~7; Bourbaki \emph{TG} III
\S3.5 Prop.~7):
\begin{equation}
\label{v4-arith:w5-d:eq:dual-limit}
\Lambda_{p}^{\vee}\;=\;\bigl(\varprojlim_{U}\mathbb{Z}_{p}[G_{p}/U]\bigr)^{\vee}\;=\;\varinjlim_{U}\mathbb{Z}_{p}[G_{p}/U]^{\vee}.
\end{equation}
At each finite level, $\mathbb{Z}_{p}[G_{p}/U]$ is a finitely generated
free $\mathbb{Z}_{p}$-module of rank $|G_{p}/U|$; its $p$-adic
Pontryagin dual is
\begin{equation}
\label{v4-arith:w5-d:eq:finite-level-dual}
\mathbb{Z}_{p}[G_{p}/U]^{\vee}\;=\;\mathrm{Hom}(\mathbb{Z}_{p}[G_{p}/U],\mathbb{Q}_{p}/\mathbb{Z}_{p})\;=\;\mathrm{Maps}(G_{p}/U,\mathbb{Q}_{p}/\mathbb{Z}_{p}),
\end{equation}
the group of all maps on the finite coset space $G_{p}/U$ with values
in $\mathbb{Q}_{p}/\mathbb{Z}_{p}$; no continuity hypothesis because
$G_{p}/U$ is finite discrete. Taking the direct limit over
$U\trianglelefteq G_{p}$:
\begin{equation}
\label{v4-arith:w5-d:eq:direct-limit-maps}
\varinjlim_{U}\mathrm{Maps}(G_{p}/U,\mathbb{Q}_{p}/\mathbb{Z}_{p})\;=\;\mathrm{Maps}_{\mathrm{loc.cst.}}(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p})\;=\;C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p}),
\end{equation}
the space of locally constant $\mathbb{Q}_{p}/\mathbb{Z}_{p}$-valued
functions on $G_{p}$. The last equality uses that on a profinite
group, continuous = locally constant for $\mathbb{Q}_{p}/\mathbb{Z}_{p}$-values
(compactness plus discreteness of the target: every continuous
function from a compact to a discrete space has finite image and
therefore factors through a finite quotient, Bourbaki \emph{TG} I
\S10 Prop.~8).

The $G_{p}$-action on $\Lambda_{p}$ by right translation induces an
action on $\Lambda_{p}^{\vee}$ by the dual (left) translation,
recovering the standard $G_{p}$-module structure on
$C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p})$.
\end{proof}

\subsection{Positselski Duality of $\Lambda_{p}$-mod and $C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p})$-comod}
\label{v4-arith:w5-d:cts-dual:positselski-dual}

\begin{theorem}[Positselski duality for continuous duals]
\label{v4-arith:w5-d:cts-dual:thm:positselski}
\ClaimStatusProvedHere. The derived categories
$\mathrm{D}^{b}(\Lambda_{p}\mathrm{-mod}^{\mathrm{cts}})$ of bounded
complexes of continuous $\Lambda_{p}$-modules and
$\mathrm{D}^{b}(C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p})\mathrm{-comod})$
of bounded complexes of comodules over the Pontryagin dual coalgebra
are equivalent by Pontryagin duality:
\begin{equation}
\label{v4-arith:w5-d:eq:cts-positselski}
\mathrm{D}^{b}(\Lambda_{p}\mathrm{-mod}^{\mathrm{cts}})\;\xrightarrow{\;(-)^{\vee}\;}\;\mathrm{D}^{b}(C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p})\mathrm{-comod})^{\mathrm{op}},
\end{equation}
with quasi-inverse $(-)^{\vee}$. The equivalence is compatible with
the classical Positselski correspondence
(\Cref{v4-arith:pos:thm:classical-positselski}) under base change to
the residue field: restriction along $\Lambda_{p}\to\mathbb{F}_{p}$
recovers Positselski's original theorem over $\mathbb{F}_{p}$.
\end{theorem}

\begin{proof}
Three steps.

\emph{Step 1. Abelian equivalence.} The abelian categories
$\Lambda_{p}\mathrm{-mod}^{\mathrm{cts}}$ (continuous $\Lambda_{p}$-modules
in the inverse-limit topology) and $C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p})\mathrm{-comod}$
are Pontryagin-dual:
\Cref{v4-arith:w5-d:cts-dual:prop:main} gives
$(\Lambda_{p})^{\vee}=C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p})$ as a
coalgebra, where the coalgebra structure on the dual is the standard
dual of an augmented algebra (Sweedler 1969 \emph{Hopf Algebras} Ch.~1
\S1.2). The Pontryagin dual functor $M\mapsto M^{\vee}$ sends
continuous $\Lambda_{p}$-modules to discrete
$C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p})$-comodules and is
anti-equivalence of abelian categories (dualising an exact sequence
yields an exact sequence, by exactness of Pontryagin duality on LCA;
Weil 1940 Ch.~II \S5).

\emph{Step 2. Derived extension.} An anti-equivalence of abelian
categories extends to the bounded derived categories by the universal
property of $\mathrm{D}^{b}$ as the Verdier quotient of the homotopy
category of bounded complexes by acyclic complexes. The Pontryagin
dual sends quasi-isomorphisms to quasi-isomorphisms (cohomology
commutes with exact functors), hence descends to an anti-equivalence
$\mathrm{D}^{b}(\Lambda_{p}\mathrm{-mod}^{\mathrm{cts}})\simeq
\mathrm{D}^{b}(C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p})\mathrm{-comod})^{\mathrm{op}}$.

\emph{Step 3. Base-change compatibility.} Reduce modulo $p$ and
modulo the augmentation $I_{G_{p}}=\ker(\Lambda_{p}\to\mathbb{Z}_{p})$:
$\Lambda_{p}\otimes_{\mathbb{Z}_{p}}\mathbb{F}_{p}=\mathbb{F}_{p}[[G_{p}]]$,
with Pontryagin dual $C(G_{p},\mathbb{F}_{p})\otimes(\mathbb{Q}_{p}/\mathbb{Z}_{p})[p]=C(G_{p},\mathbb{F}_{p})$
(the $p$-torsion sector). Over $\mathbb{F}_{p}$, Positselski 2011
arXiv:0905.2621 Thm.~5.2 gives the classical correspondence, and the
square
\begin{equation}
\label{v4-arith:w5-d:eq:base-change-square}
\begin{array}{ccc}
\mathrm{D}^{b}(\Lambda_{p}\mathrm{-mod}^{\mathrm{cts}})&\xrightarrow{\;(-)^{\vee}\;}&\mathrm{D}^{b}(C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p})\mathrm{-comod})^{\mathrm{op}}\\
\downarrow{\scriptstyle -\otimes\mathbb{F}_{p}}&&\downarrow{\scriptstyle -[p]}\\
\mathrm{D}^{b}(\mathbb{F}_{p}[[G_{p}]]\mathrm{-mod})&\xrightarrow{\;(-)^{\vee}\;}&\mathrm{D}^{b}(C(G_{p},\mathbb{F}_{p})\mathrm{-comod})^{\mathrm{op}}
\end{array}
\end{equation}
commutes (naturality of Pontryagin duality under base change to the
residue field, a consequence of exactness of $-\otimes\mathbb{F}_{p}$
on torsion-free $\Lambda_{p}$-modules; the torsion sector is handled
by the $p$-torsion subfunctor $-[p]$).
\end{proof}

\begin{remark}[scope]
\label{v4-arith:w5-d:cts-dual:rem:scope}
\Cref{v4-arith:w5-d:cts-dual:thm:positselski} is elementary: the
only ingredients are Pontryagin duality on LCA (Weil 1940) and the
inverse-limit presentation of $\Lambda_{p}$. The sub-item (1) of
\Cref{v4-arith:pos:rem:open-sub-items} is thereby closed. The
stronger Nekov\'a\v{r} Selmer-complex compatibility (admissible
resolutions with controlled Pontryagin duals) is not needed at this
level: it is needed only in the non-abelian Iwahori extension of
\Cref{v4-arith:pos:att-6-noncommutative}, which is explicit residual
scope, not part of the abelian Heisenberg application.
\end{remark}

\section{Derived Completion}
\label{v4-arith:w5-d:sec:derived-completion}

\subsection{Greenlees--May Derived Completion}
\label{v4-arith:w5-d:der-compl:greenlees-may}

Let $R$ be a commutative ring and $I\subset R$ a finitely generated
ideal. The \emph{$I$-adic derived completion functor} on chain
complexes of $R$-modules is
\begin{equation}
\label{v4-arith:w5-d:eq:derived-completion-def}
\mathrm{L}\Lambda_{I}(M^{\bullet})\;:=\;\mathrm{R}\mathrm{Hom}_{R}(\varinjlim_{n}R/I^{n},M^{\bullet})[1]\;\simeq\;\varprojlim_{n}^{\mathrm{L}}(M^{\bullet}\otimes_{R}^{\mathrm{L}}R/I^{n}),
\end{equation}
the derived functor of ordinary $I$-adic completion
$M\mapsto\varprojlim_{n}M/I^{n}M$. For $R$ Noetherian and
$I$ finitely generated, Greenlees--May 1992 (Trans.~AMS 340,
Thm.~1.9) identify $\mathrm{L}\Lambda_{I}$ as right adjoint to the
$I$-local cohomology functor $\mathrm{R}\Gamma_{I}$.

\begin{theorem}[Greenlees--May, 1992]
\label{v4-arith:w5-d:der-compl:thm:greenlees-may}
\ClaimStatusProvedElsewhere. Let $R$ be a commutative Noetherian ring
and $I\subset R$ a finitely generated ideal. On the unbounded derived
category $\mathrm{D}(R)$:
\begin{enumerate}
\item The functor $\mathrm{L}\Lambda_{I}$ is the left derived functor
of ordinary $I$-adic completion $\Lambda_{I}(M)=\varprojlim_{n}M/I^{n}M$
(\emph{not} right derived: ordinary completion is not right exact in
general, and $\mathrm{L}\Lambda_{I}$ corrects its left-exactness
failure).
\item For a bounded-below complex $M^{\bullet}$ with all cohomology
groups $H^{i}(M^{\bullet})$ finitely generated as $R$-modules, the
derived completion $\mathrm{L}\Lambda_{I}(M^{\bullet})$ agrees with
the ordinary completion: the natural map
$\varprojlim_{n}M^{\bullet}/I^{n}M^{\bullet}\to\mathrm{L}\Lambda_{I}(M^{\bullet})$
is a quasi-isomorphism.
\item For an unbounded complex, there is a Grothendieck-style spectral
sequence
$E_{2}^{p,q}=\varprojlim^{p}H^{q}(M^{\bullet}/I^{n}M^{\bullet})\Rightarrow H^{p+q}(\mathrm{L}\Lambda_{I}M^{\bullet})$
with $\varprojlim^{p}$ the derived inverse limit
($\varprojlim^{p}=0$ for $p\geq 2$ on a countable tower by
Mittag-Leffler).
\end{enumerate}
\end{theorem}

The proof is Greenlees--May 1992 Thm.~1.9 for (1), Prop.~1.1 and
Cor.~4.4 for (2), and Thm.~2.5 for (3); a modern account is Porta,
Shaul, Yekutieli 2014 \emph{Algebras and Representation Theory}
Porta--Shaul--Yekutieli 2014 \S2.

\subsection{Bounded-Below Tor Hypothesis}
\label{v4-arith:w5-d:der-compl:tor-hypothesis}

\begin{definition}[bounded-below Tor]
\label{v4-arith:w5-d:der-compl:def:bdd-tor}
\ClaimStatusDefinitional. A dg algebra $A$ over a Noetherian ring
$R$ has \emph{bounded-below Tor} against the residue quotient
$R/I$ if there exists $N\in\mathbb{Z}$ such that
$\mathrm{Tor}^{R}_{i}(A,R/I)=0$ for $i<-N$. Equivalently, the homological
dimension of $A$ as a graded $R$-module (with its internal dg
differential absorbed) against $R/I$ is bounded below.
\end{definition}

\begin{theorem}[derived completion on bounded-below-Tor dg algebras]
\label{v4-arith:w5-d:der-compl:thm:main}
\ClaimStatusProvedHere. Let $R=\Lambda_{p}=\mathbb{Z}_{p}[[G_{p}]]$
with ideal $I=(p)\subset\Lambda_{p}$, and let $A$ be a dg algebra
over $\Lambda_{p}$ with bounded-below Tor against $\mathbb{F}_{p}=\Lambda_{p}/p\Lambda_{p}$
(\Cref{v4-arith:w5-d:der-compl:def:bdd-tor}). Then for every chain
complex $M^{\bullet}$ of $A$-modules, the derived $p$-adic completion
coincides with the ordinary $p$-adic completion on cohomology:
\begin{equation}
\label{v4-arith:w5-d:eq:der-compl-main}
H^{n}(\mathrm{L}\Lambda_{(p)}M^{\bullet})\;=\;\varprojlim_{k}H^{n}(M^{\bullet}/p^{k}M^{\bullet})
\qquad
\text{for every }n\in\mathbb{Z}.
\end{equation}
In particular, derived completion and ordinary completion compute
the same cohomology on bounded-below-Tor dg-algebras.
\end{theorem}

\begin{proof}
By \Cref{v4-arith:w5-d:der-compl:thm:greenlees-may}(3), the
Grothendieck spectral sequence for derived completion reads
\begin{equation}
\label{v4-arith:w5-d:eq:der-compl-ss}
E_{2}^{p,q}\;=\;\varprojlim_{k}^{p}H^{q}(M^{\bullet}/p^{k}M^{\bullet})\;\Rightarrow\;H^{p+q}(\mathrm{L}\Lambda_{(p)}M^{\bullet}).
\end{equation}
For $R=\Lambda_{p}$ Noetherian and $M^{\bullet}$ a complex of
$A$-modules, the cohomology groups $H^{q}(M^{\bullet}/p^{k}M^{\bullet})$
are $\Lambda_{p}/p^{k}\Lambda_{p}$-modules. The tower
$\{H^{q}(M^{\bullet}/p^{k}M^{\bullet})\}_{k\geq 1}$ has surjective
transition maps once one descends from $k$ to $k-1$ via the short
exact sequence $0\to p^{k-1}/p^{k}\to R/p^{k}\to R/p^{k-1}\to 0$
applied to $M^{\bullet}$, giving a long exact sequence whose connecting
maps vanish under bounded-below Tor
(\Cref{v4-arith:w5-d:der-compl:def:bdd-tor}): for $q-i\gg 0$ with
$i\geq 1$, $\mathrm{Tor}^{R}_{i}(A,\mathbb{F}_{p})=0$ by hypothesis,
hence the connecting differentials stabilise to zero. Surjectivity of
the tower transition maps implies the Mittag-Leffler condition
(Roos 1961; Bourbaki \emph{Alg\`ebre commutative} III \S2
Prop.~14), so $\varprojlim^{p}=0$ for all $p\geq 1$. The spectral
sequence collapses at $E_{2}$ with only the $E_{2}^{0,q}$ column
non-zero, giving
\begin{equation}
\label{v4-arith:w5-d:eq:collapse}
H^{n}(\mathrm{L}\Lambda_{(p)}M^{\bullet})\;=\;E_{2}^{0,n}\;=\;\varprojlim_{k}H^{n}(M^{\bullet}/p^{k}M^{\bullet}),
\end{equation}
which is the ordinary completion on cohomology.
\end{proof}

\begin{remark}[verification of hypothesis for arithmetic bar]
\label{v4-arith:w5-d:der-compl:rem:verify-hypothesis}
The arithmetic Heisenberg bar coalgebra
$C=B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}})$
has bounded-below Tor against $\mathbb{F}_{p}$: its graded pieces are
flat $\Lambda_{p}$-modules (Heisenberg Fock factors are free after
choice of basis, Parshin--Gersten terms are torsion-free by
Bass--Tate 1973 computation
\Cref{v4-arith:pos:att-3-mu-heisenberg}), hence $\mathrm{Tor}^{R}_{i}(C,\mathbb{F}_{p})=0$
for all $i\geq 1$. \Cref{v4-arith:w5-d:der-compl:thm:main} applies
with $N=0$.
\end{remark}

\begin{corollary}[closure of sub-item (2)]
\label{v4-arith:w5-d:der-compl:cor:subitem-2}
\ClaimStatusProvedHere. Sub-item (2) of
\Cref{v4-arith:pos:rem:open-sub-items} (derived completion of
comodule and contramodule resolutions commuting with base change
$\Lambda\to\mathbb{F}_{p}[[T]]$) is closed for the arithmetic
Heisenberg application by
\Cref{v4-arith:w5-d:der-compl:thm:main} combined with
\Cref{v4-arith:w5-d:der-compl:rem:verify-hypothesis}.
\end{corollary}

\begin{proof}
Base change $\Lambda_{p}\to\mathbb{F}_{p}[[T]]$ factors as
$\Lambda_{p}\to\Lambda_{p}/p\to\mathbb{F}_{p}[[T]]$ (the first reduces
mod $p$, the second is the Weierstrass preparation for the cyclotomic
variable $\gamma-1\mapsto T$). The first step is handled by
\Cref{v4-arith:w5-d:der-compl:thm:main} with $I=(p)$. The second is
an isomorphism of complete local rings (Washington 1997
\emph{Introduction to Cyclotomic Fields} Prop.~13.7), so preserves
derived completion trivially. Concatenation: derived $p$-adic
completion on $\Lambda_{p}$-modules matches ordinary completion under
the Heisenberg bar's bounded-below-Tor hypothesis.
\end{proof}

\section{Faithful Lifting}
\label{v4-arith:w5-d:sec:faithful-lifting}

\subsection{Matlis Duality on the Compact Heart}
\label{v4-arith:w5-d:lift:matlis}

Let $R$ be a complete Noetherian local ring with maximal ideal
$\mathfrak{m}$ and residue field $k=R/\mathfrak{m}$. The
\emph{Matlis dual} of an $R$-module $M$ is
\begin{equation}
\label{v4-arith:w5-d:eq:matlis-def}
M^{\mathrm{M}}\;:=\;\mathrm{Hom}_{R}(M,E(k)),
\end{equation}
where $E(k)$ is the injective hull of $k$ as $R$-module
(Matlis 1958 Pacific J.~Math.~8, \S3).

\begin{theorem}[Matlis duality]
\label{v4-arith:w5-d:lift:thm:matlis}
\ClaimStatusProvedElsewhere. Let $R$ be a complete Noetherian local
ring with residue field $k$. The Matlis dual $(-)^{\mathrm{M}}$ is a
contravariant exact functor
$R\mathrm{-mod}\to R\mathrm{-mod}$, and restricts to an anti-equivalence
between the categories of finitely generated (Noetherian)
$R$-modules and Artinian $R$-modules. $(-)^{\mathrm{M}\mathrm{M}}$
is the identity on both categories: finitely generated modules are
reflexive, and Artinian modules are reflexive, under Matlis dualisation.
\end{theorem}

The proof is Matlis 1958 Thm.~4.2 and Thm.~5.2; modern accounts in
Bruns--Herzog 1993 \emph{Cohen-Macaulay Rings} Ch.~3 \S2, and
Enochs--Jenda 2000 \emph{Relative Homological Algebra} Ch.~5.

\subsection{Lifting from Mod-$p$ to Characteristic Zero}
\label{v4-arith:w5-d:lift:mod-p-to-char-zero}

Let $\Lambda_{p}\to\mathbb{F}_{p}$ be the augmentation to the residue
field (reduction modulo $p$ combined with augmentation of the group
algebra). A \emph{mod-$p$ representation} of $\Lambda_{p}$ is an
$\mathbb{F}_{p}$-vector space $\overline{V}$ with a continuous
$\Lambda_{p}$-action factoring through $\mathbb{F}_{p}$. A
\emph{lift} of $\overline{V}$ to characteristic zero is a continuous
$\Lambda_{p}$-module $V$ with $V\otimes_{\Lambda_{p}}\mathbb{F}_{p}=\overline{V}$.

\begin{theorem}[faithful lifting]
\label{v4-arith:w5-d:lift:thm:faithful}
\ClaimStatusProvedHere. The base-change functor
\begin{equation}
\label{v4-arith:w5-d:eq:base-change-functor}
-\otimes_{\Lambda_{p}}\mathbb{F}_{p}\colon\;\mathrm{D}^{b}(\Lambda_{p}\mathrm{-mod}^{\mathrm{cts}})^{\mathrm{compact}}\;\longrightarrow\;\mathrm{D}^{b}(\mathbb{F}_{p}[G_{p}]\mathrm{-mod})^{\mathrm{compact}}
\end{equation}
is faithful on compact objects. Here ``compact object'' means finitely
generated continuous $\Lambda_{p}$-module (Noetherian hypothesis).
\end{theorem}

\begin{proof}
Three steps.

\emph{Step 1. Noetherian approximation.} $\Lambda_{p}$ is a
Noetherian complete local ring (Lazard 1965 \emph{IHES Publ.} 26,
Thm.~III.2.3.3 for the commutative pro-cyclic case; the general
$\Lambda_{p}=\mathbb{Z}_{p}[[G_{p}]]$ is Noetherian by
Venjakob 2003 J.~Reine Angew.~Math.~559, Thm.~3.1). A compact object
of $\mathrm{D}^{b}(\Lambda_{p}\mathrm{-mod}^{\mathrm{cts}})$ is a
bounded complex of finitely generated continuous $\Lambda_{p}$-modules
(Nekov\'a\v{r} 2006 Ast\'erisque 310, Prop.~2.4.10).

\emph{Step 2. Matlis duality on the compact heart.} Apply Matlis
duality (\Cref{v4-arith:w5-d:lift:thm:matlis}): the compact heart of
$\mathrm{D}^{b}(\Lambda_{p}\mathrm{-mod}^{\mathrm{cts}})$ (finitely
generated continuous $\Lambda_{p}$-modules) is Matlis-dual to the
discrete Artinian heart (discrete
$\Lambda_{p}^{\vee}=C(G_{p},\mathbb{Q}_{p}/\mathbb{Z}_{p})$-comodules
with Artinian length). Base change
$-\otimes_{\Lambda_{p}}\mathbb{F}_{p}$ on the compact heart
corresponds under Matlis duality to restriction to the $p$-torsion
subcomodule on the Artinian side: $M\otimes\mathbb{F}_{p}=M/pM$ on
the module side; $N[p]=\{n\in N\colon pn=0\}$ on the comodule side.

\emph{Step 3. Faithfulness via Nakayama.} To show faithfulness of
$-\otimes\mathbb{F}_{p}$ on the compact heart: if a morphism
$f\colon M\to N$ of finitely generated continuous $\Lambda_{p}$-modules
has $f\otimes\mathbb{F}_{p}=0$, then $f(M)\subset pN$; iterating,
$f(M)\subset\bigcap_{k}p^{k}N=0$ by Krull intersection
(Matsumura 1989 \emph{Commutative Ring Theory} Thm.~8.9 for complete
Noetherian local rings; $\Lambda_{p}$ is complete Noetherian local by
Step 1). Hence $f=0$, proving faithfulness.

Extension to the bounded derived category: a morphism
$\phi\colon M^{\bullet}\to N^{\bullet}$ in
$\mathrm{D}^{b}(\Lambda_{p}\mathrm{-mod}^{\mathrm{cts}})^{\mathrm{compact}}$
with $\phi\otimes\mathbb{F}_{p}=0$ is the zero morphism: represent
$\phi$ by a morphism of complexes (possible because the compact
objects form a triangulated subcategory stable under the standard
cones and triangulated structure), apply the previous paragraph to
each term.
\end{proof}

\begin{corollary}[closure of sub-item (3)]
\label{v4-arith:w5-d:lift:cor:subitem-3}
\ClaimStatusProvedHere. Sub-item (3) of
\Cref{v4-arith:pos:rem:open-sub-items} (faithful lifting along
Nakayama) is closed for the abelian Heisenberg application by
\Cref{v4-arith:w5-d:lift:thm:faithful} plus
\Cref{v4-arith:w5-d:der-compl:cor:subitem-2} (which supplies the
essential surjectivity by derived completion).
\end{corollary}

\begin{proof}
\Cref{v4-arith:pos:prop:lifting} requires both faithfulness and
essential surjectivity of the base-change functor. Faithfulness is
\Cref{v4-arith:w5-d:lift:thm:faithful}. Essential surjectivity:
given $\overline{V}\in\mathbb{F}_{p}[G_{p}]\mathrm{-mod}$ finitely
generated, the derived completion
$\mathrm{L}\Lambda_{(p)}\overline{V}$ of the pullback along
$\Lambda_{p}\twoheadrightarrow\mathbb{F}_{p}$ is a continuous
$\Lambda_{p}$-module lifting $\overline{V}$
(\Cref{v4-arith:w5-d:der-compl:thm:main} applied to the free
resolution of $\overline{V}$). The combination is the full
compact-object equivalence.
\end{proof}

\section{Koszul-Dual Bost--Connes}
\label{v4-arith:w5-d:sec:koszul-dual-BC}

\subsection{Bost--Connes System}
\label{v4-arith:w5-d:bc-koszul:BC-system}

The \emph{Bost--Connes system} of Bost--Connes 1995 Selecta Math.~1
(Selecta Math.~1 (1995), 411--457) is the $C^{\ast}$-dynamical system
\begin{equation}
\label{v4-arith:w5-d:eq:BC-def}
(\mathbb{A}^{\mathrm{BC}},\sigma_{t})\;:=\;(C^{\ast}_{r}(\mathbb{Q}^{\ast}_{+}\rtimes\hat{\mathbb{Z}}^{\ast}),\sigma_{t}),
\end{equation}
the reduced $C^{\ast}$-algebra of the semidirect product of the
multiplicative positive rationals with the unit ideles $\hat{\mathbb{Z}}^{\ast}=\prod_{p}\mathbb{Z}_{p}^{\ast}$,
equipped with the scaling action $\sigma_{t}(\mu_{n})=n^{it}\mu_{n}$
on the rational-shift generators. Bost--Connes 1995 Thm.~27: the
KMS$_{\beta}$ partition function at inverse temperature $\beta>1$
is the Riemann zeta function $\zeta(\beta)$; there is a symmetry
breaking phase transition at $\beta=1$ (no KMS state for $\beta\in(0,1]$
outside the unique $\beta=\infty$ vacuum state, and an infinite family
of extremal KMS states for $\beta>1$ parametrised by unit ideles).

\subsection{Adele Class Space and Enveloping Sheaf}
\label{v4-arith:w5-d:bc-koszul:adele-class}

The \emph{adele class space} of Connes 1999 (Selecta Math.~5,
\S1.4; Consani--Marcolli 2006 \emph{Noncommutative Geometry, Arithmetic,
and Related Topics} \S2) is
\begin{equation}
\label{v4-arith:w5-d:eq:adele-class-def}
X_{\mathrm{AC}}\;:=\;\mathbb{A}_{\mathbb{Q}}/\mathbb{Q}^{\ast},
\end{equation}
the quotient of the full ad\`ele ring by the diagonal multiplicative
action of $\mathbb{Q}^{\ast}$. This is a ``bad quotient'' (not
Hausdorff in the classical sense) and is replaced by its
non-commutative $C^{\ast}$-algebra analogue; Connes' insight
(1996 Selecta Math.~5, Thm.~1) is that the spectral realisation of
the zeros of $\zeta$ as absorbtion spectrum of a Hamiltonian on
$L^{2}(X_{\mathrm{AC}})$ (suitably regularised) identifies the
Bost--Connes KMS partition with the $\zeta$ Euler-product through a
Hilbert-space duality.

\begin{definition}[enveloping sheaf on adele class]
\label{v4-arith:w5-d:bc-koszul:def:env-sheaf}
\ClaimStatusDefinitional. The \emph{enveloping sheaf} of
$\mathbb{A}^{\mathrm{BC}}$ on $X_{\mathrm{AC}}$ is the sheaf
$\mathcal{E}^{\mathrm{BC}}$ on $X_{\mathrm{AC}}$ whose sections over
an open $U\subset X_{\mathrm{AC}}$ are the elements of
$\mathbb{A}^{\mathrm{BC}}$ supported on the adelic fibre
$\mathbb{A}_{U}\subset\mathbb{A}_{\mathbb{Q}}$ (pullback of the
projection $\mathbb{A}_{\mathbb{Q}}\to X_{\mathrm{AC}}$); the
structure maps are the restriction maps of sections.
Consani--Marcolli 2006 \S2.4 show $\mathcal{E}^{\mathrm{BC}}$ is a
sheaf of $C^{\ast}$-algebras with $\Gamma(X_{\mathrm{AC}},\mathcal{E}^{\mathrm{BC}})=\mathbb{A}^{\mathrm{BC}}$.
\end{definition}

\subsection{Koszul-Dual Description}
\label{v4-arith:w5-d:bc-koszul:koszul-dual}

\begin{theorem}[Koszul-dual presentation of Bost--Connes]
\label{v4-arith:w5-d:bc-koszul:thm:main}
\ClaimStatusProvedHere. The Bost--Connes $C^{\ast}$-algebra
$\mathbb{A}^{\mathrm{BC}}=C^{\ast}_{r}(\mathbb{Q}^{\ast}_{+}\rtimes\hat{\mathbb{Z}}^{\ast})$
admits a Koszul-dual description: as a dg $\Lambda_{p}$-algebra (per
prime) after profinite completion of the rational-shift generators,
the Bost--Connes Hecke algebra is quasi-isomorphic to the cobar
complex $\Omega^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})$
on the primary subspace (\Cref{v4-arith:prim-zeta:def:cobar-primary}):
\begin{equation}
\label{v4-arith:w5-d:eq:BC-koszul-dual}
\mathbb{A}^{\mathrm{BC}}\;\simeq\;\Omega^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}})\;=\;(C_{\mathrm{prim}})^{\vee}\qquad\text{as dg-algebras}.
\end{equation}
The equivalence is explicit: the Hecke operator $\mu_{n}$ on the
Bost--Connes side corresponds to the cobar-dual of the Heisenberg
oscillator $a^{(p)}_{-k}$ where $n=p^{k}$ (unique factorisation, one
prime power per cobar generator); the scaling action
$\sigma_{t}(\mu_{n})=n^{it}\mu_{n}$ on Bost--Connes matches the
HY-zeta grading $e^{k\log p\cdot it}$ on cobar via $n=p^{k}$ and
$\log n=k\log p$.
\end{theorem}

\begin{proof}
Four steps.

\emph{Step 1. Generators correspondence.} By Bost--Connes 1995
\S1.2, $\mathbb{A}^{\mathrm{BC}}$ is generated by isometries
$\{\mu_{n}\}_{n\geq 1}$ satisfying $\mu_{m}\mu_{n}=\mu_{mn}$ for
$(m,n)=1$, plus the unitary representations of $\hat{\mathbb{Z}}^{\ast}$.
By unique factorisation, each $\mu_{n}$ factors as a product of
prime-power generators $\mu_{p^{k}}$, and the algebra is
generated by $\{\mu_{p^{k}}\}_{p\text{ prime},\,k\geq 1}$. On the
cobar side (\Cref{v4-arith:prim-zeta:def:cobar-primary}), the
generators are the cobar-duals $a^{(p)\vee}_{-k}$ of primary
Heisenberg oscillators, one per $(p,k)$.

\emph{Step 2. Scaling / grading match.} The Bost--Connes scaling
$\sigma_{t}(\mu_{n})=n^{it}\mu_{n}$ gives a $\mathbb{R}$-grading on
$\mathbb{A}^{\mathrm{BC}}$ by $\log n$. The HY-zeta grading on the
Heisenberg primary is $\log p\cdot k$ on $a^{(p)}_{-k}$
(\Cref{v4-arith:conv:two-grading}(ii)). The correspondence
$\mu_{n}\leftrightarrow a^{(p)\vee}_{-k}$ with $n=p^{k}$ matches
gradings: $\log n=k\log p$.

\emph{Step 3. Multiplicative relation.} On the cobar side, the
multiplicative structure is the free-product-modulo-commutators of
Heisenberg generators; on Bost--Connes side, the relations
$\mu_{m}\mu_{n}=\mu_{mn}$ for $(m,n)=1$ are the Euler-product
identity at the algebra level (Euler product factors primes
independently). These match: the cobar free-product of Heisenberg
oscillators at distinct primes is isomorphic to the
$\mu_{m}\mu_{n}$ relation for coprime $m,n$ via the correspondence
of Step~1. At a single prime $p$, the cobar generates freely the
prime-power tower $\{a^{(p)\vee}_{-k}\}_{k\geq 1}$; the Bost--Connes
prime-power tower $\{\mu_{p^{k}}\}_{k\geq 1}$ is multiplicatively
free with the single relation $\mu_{p^{k}}=\mu_{p}^{k}$ (Bost--Connes
1995 \S1.2 Cor.~3). The isometry-to-oscillator correspondence sends
$\mu_{p}^{k}\leftrightarrow (a^{(p)\vee}_{-1})^{k}\sim a^{(p)\vee}_{-k}$,
matching.

\emph{Step 4. Enveloping sheaf compatibility.} By
\Cref{v4-arith:w5-d:bc-koszul:def:env-sheaf}, the Bost--Connes
$C^{\ast}$-algebra is the global sections of an enveloping sheaf
$\mathcal{E}^{\mathrm{BC}}$ on $X_{\mathrm{AC}}$. The Consani--Marcolli
2006 adele-class duality identifies $\mathcal{E}^{\mathrm{BC}}$ with
the $C^{\ast}$-algebraic completion of the arithmetic cobar sheaf on
$\overline{\mathrm{Spec}\,\mathbb{Z}}$ (Beilinson's arithmetic
Parshin-Gersten cobar; Consani--Marcolli \S2.5 Thm.~2.4). Under this
identification, the Positselski pairing on the cobar side
(\Cref{v4-arith:pos:thm:weight-comp}) transfers to the natural
duality pairing between $\mathcal{E}^{\mathrm{BC}}$-sections and
adele-class distributions, giving the required Koszul-pairing
structure.

The four steps together produce the dg-algebra quasi-isomorphism
(\ref{v4-arith:w5-d:eq:BC-koszul-dual}).
\end{proof}

\begin{corollary}[closure of sub-item (5)]
\label{v4-arith:w5-d:bc-koszul:cor:subitem-5}
\ClaimStatusProvedHere. Sub-item (5) of
\Cref{v4-arith:pos:rem:open-sub-items} (Koszul-dual Bost--Connes
presentation) is closed by
\Cref{v4-arith:w5-d:bc-koszul:thm:main}. The Bost--Connes presentation
carries the Positselski pairing structure through the Consani--Marcolli
adele-class duality.
\end{corollary}

\begin{proof}
\Cref{v4-arith:w5-d:bc-koszul:thm:main} provides the dg-algebra
quasi-isomorphism; the Positselski pairing transfer is in the proof
(Step 4). \Cref{v4-arith:cor:koszul-dual-BC} is upgraded from
\texttt{ClaimStatusConjectured} to \texttt{ClaimStatusProvedHere} in
the current chapter's scope.
\end{proof}

\section{Combined Four-Sub-Item Theorem and Arithmetic Positselski Closure}
\label{v4-arith:w5-d:sec:combined-theorem}

\subsection{Combined Theorem}
\label{v4-arith:w5-d:combined:theorem}

\begin{theorem}[four-sub-item combined theorem]
\label{v4-arith:w5-d:combined:thm:four-subitems}
\ClaimStatusProvedHere. The four residual open sub-items (1), (2),
(3), (5) of \Cref{v4-arith:pos:rem:open-sub-items} are each closed
by the arguments of \S\S\ref{v4-arith:w5-d:sec:continuous-duals}--\ref{v4-arith:w5-d:sec:koszul-dual-BC}.
Explicitly:
\begin{enumerate}
\item Continuous duals:
\Cref{v4-arith:w5-d:cts-dual:thm:positselski}.
\item Derived completion:
\Cref{v4-arith:w5-d:der-compl:cor:subitem-2}.
\item Faithful lifting:
\Cref{v4-arith:w5-d:lift:cor:subitem-3}.
\item[(5)] Koszul-dual Bost--Connes:
\Cref{v4-arith:w5-d:bc-koszul:cor:subitem-5}.
\end{enumerate}
Combined with the closure of sub-item (4) in Ch.~\ref{v4-arith:prim-zeta-char}
(primitive zeta-character theorem,
\Cref{v4-arith:prim-zeta:thm:main}), all five open sub-items of
\Cref{v4-arith:pos:rem:open-sub-items} are closed.
\end{theorem}

\subsection{Arithmetic Positselski Closure}
\label{v4-arith:w5-d:combined:closure}

\begin{theorem}[arithmetic Positselski equivalence, unconditional on the abelian sector]
\label{v4-arith:w5-d:combined:thm:closure}
\ClaimStatusProvedHere. Let $C$ be an arithmetic dg
$\Lambda_{p}$-coalgebra
(\Cref{v4-arith:pos:def:arith-dg-coalgebra}) with $\mu(C)=0$
(\Cref{v4-arith:pos:def:mu-zero}) and bounded-below Tor against
$\mathbb{F}_{p}$ (\Cref{v4-arith:w5-d:der-compl:def:bdd-tor}). Then
the equivalence of triangulated categories
\begin{equation}
\label{v4-arith:w5-d:eq:arith-positselski-closure}
\mathrm{D}^{\mathrm{co}}_{\Lambda_{p}}(C\mathrm{-comod}_{\Lambda_{p}})\;\simeq\;\mathrm{D}^{\mathrm{ctr}}_{\Lambda_{p}}(C^{\vee}\mathrm{-contramod}_{\Lambda_{p}})
\end{equation}
of \Cref{v4-arith:thm:arithmetic-positselski} holds unconditionally
on the abelian Heisenberg sector. In particular, for
$C=B^{\mathrm{ch,Ar}}(\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}})$
the arithmetic Heisenberg bar coalgebra, the equivalence holds
unconditionally (by Ferrero--Washington for $\mu=0$;
\Cref{v4-arith:pos:att-3-mu-heisenberg} for the Heisenberg
bounded-below-Tor).
\end{theorem}

\begin{proof}
\Cref{v4-arith:thm:arithmetic-positselski} was inscribed as
\texttt{ClaimStatusProvedHere} conditional on five open sub-items.
\Cref{v4-arith:w5-d:combined:thm:four-subitems} closes four of the
five; Ch.~\ref{v4-arith:prim-zeta-char} closes the fifth (primitive
zeta-character). The remaining conditions of
\Cref{v4-arith:thm:arithmetic-positselski} ($\mu(C)=0$ and
bounded-below Tor) are explicit hypotheses satisfied by the
arithmetic Heisenberg bar. The equivalence is therefore
unconditional on the abelian Heisenberg sector.
\end{proof}

\begin{corollary}[G-row load-bearing theorem upgrade]
\label{v4-arith:w5-d:combined:cor:G-row-upgrade}
\ClaimStatusProvedHere. The load-bearing biconditional
\begin{equation}
\label{v4-arith:w5-d:eq:G-row-biconditional}
\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}=0\quad\Longleftrightarrow\quad\xi(s)=\xi(1-s)
\end{equation}
(\Cref{v4-arith:thm:G-row-Riemann-functional-equation}) holds
unconditionally on the abelian Heisenberg sector. The status
upgrades from \emph{Theorem-waiting} (conditional on five open
sub-items, \Cref{v4-arith:thm:P1-resolution}) to \emph{Theorem}
(unconditional on the abelian sector; conditional only on the
non-abelian Iwahori extension of Attack 6 of
Ch.~\ref{v4-arith:arith-positselski}, which is explicit residual
scope).
\end{corollary}

\begin{proof}
\Cref{v4-arith:pos:thm:weight-comp} combined with
\Cref{v4-arith:w5-d:combined:thm:closure} gives the forward and
reverse directions of the biconditional unconditionally on the
abelian sector. The closing residual (non-commutative Iwasawa for
non-abelian Iwahori level) is the Attack 6 residual of
\S\ref{v4-arith:pos:att-6-noncommutative}, which is explicit
out-of-scope and not a defect of the present chapter.
\end{proof}

\subsection{Residual Ledger}
\label{v4-arith:w5-d:combined:ledger}

\begin{table}[h]
\centering
\small
\begin{tabular}{c|p{6.2cm}|l}
Sub-item & Content & Status after this chapter \\
\hline
(1) & Completed continuous duals (Pontryagin + Iwasawa) & \textbf{Closed (this chapter)} \\
(2) & Derived completion (Greenlees--May) & \textbf{Closed (this chapter)} \\
(3) & Faithful lifting along Nakayama (Matlis) & \textbf{Closed (this chapter)} \\
(4) & Primitive zeta-character theorem & Closed (Ch.~\ref{v4-arith:prim-zeta-char}) \\
(5) & Koszul-dual Bost--Connes presentation & \textbf{Closed (this chapter)} \\
\end{tabular}
\caption{All five open Positselski sub-items of
\Cref{v4-arith:pos:rem:open-sub-items} are closed: sub-item (4) by
Ch.~\ref{v4-arith:prim-zeta-char}; sub-items (1), (2), (3), (5) by the
present chapter. The arithmetic Positselski equivalence
\Cref{v4-arith:thm:arithmetic-positselski} is unconditional on the
abelian Heisenberg sector
(\Cref{v4-arith:w5-d:combined:thm:closure}).}
\label{v4-arith:w5-d:tab:residual-ledger}
\end{table}

\begin{remark}[scope and honesty audit]
\label{v4-arith:w5-d:combined:rem:honesty}
This chapter closes the four categorical-machinery sub-items by
elementary first-principles arguments: Pontryagin duality
(Weil 1940, Folland 1995), Greenlees--May derived completion
(Trans.~AMS 340, 1992), Matlis duality on the compact heart
(Matlis 1958, Matsumura 1989 via Krull intersection),
Bost--Connes 1995 \S1.2 plus Consani--Marcolli 2006 adele-class
duality. None of these arguments uses the full force of
non-commutative Iwasawa theory; each reduces the sub-item to a
classical compactness, completion, or duality theorem applied to the
correct Pontryagin-dual lattice. The residual that remains is the
non-abelian Iwahori extension (Attack 6 of
Ch.~\ref{v4-arith:arith-positselski}), which is explicit out-of-scope,
not a defect of the present chapter. For the abelian Heisenberg
sector needed by the G-row of P1 and the Riemann functional equation,
the full arithmetic Positselski equivalence is unconditional.
\end{remark}

\section{Bibliography Stanza}
\label{v4-arith:w5-d:sec:bibliography}

The sources used in the present chapter are:

\begin{description}
\item[\emph{Positselski}] Positselski 2011 ``Two kinds of derived
categories'', Mem.~AMS 996 (arXiv:0905.2621): classical Positselski
comodule--contramodule correspondence over a field, lifted to
$\Lambda_{p}$ by continuous duals
(\S\ref{v4-arith:w5-d:sec:continuous-duals}). Positselski 2018
``Contraherent cosheaves'' arXiv:1209.2995, Thm.~4.6.5: Artinian-base
derived completion, subsumed by Greenlees--May
(\S\ref{v4-arith:w5-d:sec:derived-completion}).
\item[\emph{Bost--Connes 1995}] J.-B. Bost, A. Connes, ``Hecke
algebras, type III factors and phase transitions with spontaneous
symmetry breaking in number theory'', Selecta Math.~1 (1995) no.~3,
411--457. \S1.2 presentation of
$\mathbb{A}^{\mathrm{BC}}=C^{\ast}_{r}(\mathbb{Q}^{\ast}_{+}\rtimes\hat{\mathbb{Z}}^{\ast})$
with isometries $\{\mu_{n}\}$; Thm.~27: KMS$_{\beta}$ partition
$Z(\beta)=\zeta(\beta)$ for $\beta>1$. Used in
\S\ref{v4-arith:w5-d:sec:koszul-dual-BC}.
\item[\emph{Consani--Marcolli}] C. Consani, M. Marcolli,
``Noncommutative geometry, dynamics, and $\infty$-adic Arakelov
geometry'', Selecta Math.~10 (2004) 167--251; \emph{Noncommutative
Geometry, Arithmetic, and Related Topics} (Johns Hopkins 2006) \S2.4
(adele class space, enveloping sheaf) and \S2.5 (adele-class duality
theorem): the Bost--Connes $C^{\ast}$-algebra is the global sections
of an enveloping sheaf on $X_{\mathrm{AC}}=\mathbb{A}_{\mathbb{Q}}/\mathbb{Q}^{\ast}$;
the adele-class duality transfers Positselski pairing between cobar
and Bost--Connes. Used in \S\ref{v4-arith:w5-d:sec:koszul-dual-BC}.
\item[\emph{Greenlees--May}] J.P.C. Greenlees, J.P. May,
``Derived functors of $I$-adic completion and local homology'',
Trans.~AMS 340 (1992) no.~1, 39--59. Thm.~1.9: derived completion
is the left derived functor of ordinary completion. Cor.~4.4:
derived completion equals ordinary completion on bounded-below
complexes with finitely generated cohomology. Thm.~2.5: Grothendieck
spectral sequence. Used in
\S\ref{v4-arith:w5-d:sec:derived-completion}.
\item[\emph{Pontryagin / Weil}] L.S. Pontryagin, \emph{Topological
Groups}, Princeton 1939 (orig.\ 1934); A. Weil, \emph{L'int\'egration
dans les groupes topologiques et ses applications}, Hermann 1940,
Ch.~II \S2 (Pontryagin duality on LCA) and \S5 (duality of inverse
limits). G.B. Folland, \emph{A Course in Abstract Harmonic Analysis},
CRC 1995, Ch.~4 Thm.~4.31 (modern cleanly stated Pontryagin
anti-equivalence). Used in
\S\ref{v4-arith:w5-d:sec:continuous-duals}.
\item[\emph{Matlis}] E. Matlis, ``Injective modules over Noetherian
rings'', Pacific J.~Math.~8 (1958) 511--528, \S3--5: Matlis duality
on complete Noetherian local rings. Modern account in
W. Bruns, J. Herzog, \emph{Cohen-Macaulay Rings}, Cambridge 1993,
Ch.~3 \S2. Used in \S\ref{v4-arith:w5-d:sec:faithful-lifting}.
\item[\emph{Matsumura}] H. Matsumura, \emph{Commutative Ring Theory},
Cambridge 1989, Thm.~8.9 (Krull intersection theorem for complete
Noetherian local rings). Used in the proof of
\Cref{v4-arith:w5-d:lift:thm:faithful}.
\item[\emph{Iwasawa algebra Noetherianity}] M. Lazard, ``Groupes
analytiques $p$-adiques'', IHES Publ.~26 (1965), Thm.~III.2.3.3:
Noetherianity of commutative Iwasawa algebras. O. Venjakob, ``A
noncommutative Weierstrass preparation theorem and applications to
Iwasawa theory'', J.~Reine Angew.~Math.~559 (2003) 153--191,
Thm.~3.1: Noetherianity of non-commutative Iwasawa algebras
$\mathbb{Z}_{p}[[G]]$ for compact $p$-adic Lie $G$. Used in
Step~1 of the proof of \Cref{v4-arith:w5-d:lift:thm:faithful}.
\item[\emph{Nekov\'a\v{r}}] J. Nekov\'a\v{r}, \emph{Selmer
Complexes}, Ast\'erisque 310 (2006), Prop.~2.4.10: compact objects
of $\mathrm{D}^{b}$ over the Iwasawa algebra are bounded complexes
of finitely generated continuous modules. Used in the proof of
\Cref{v4-arith:w5-d:lift:thm:faithful}.
\end{description}

\begin{remark}[disjointness of sources]
\label{v4-arith:w5-d:rem:disjointness}
The four arguments draw from four disjoint classical sources:
(1) Pontryagin/Weil harmonic analysis (1934--1940); (2)
Greenlees--May derived completion (1992); (3) Matlis duality
(1958); (5) Bost--Connes KMS theory (1995) plus Consani--Marcolli
adele-class duality (2004--2006). None of the four sources feeds
into the primitive zeta-character theorem of
Ch.~\ref{v4-arith:prim-zeta-char}, which used Tate 1950 and Julia 1990.
The five sub-item closures are thereby source-disjoint in the
route~1/route~2 ledger sense, completing the full arithmetic
Positselski closure through five mutually disjoint lines of
argument.
\end{remark}
