\chapter{Full $\mathcal{V}^{\mathrm{prim}}$ P3 and the Koszul--Petersson Compatibility on the Discrete Core}
\label{v4-arith:w5-c:full-vprim-P3}

\emph{Wave-5, agent~C. The residual of the Koszul--Petersson
programme after wave-4 (Chapter~\ref{v4-arith:kms-gns-full}) is
threefold: the tempered cuspidal core was closed unconditionally
through the Tomita--Takesaki polar decomposition of the
Bost--Connes KMS${}_{1}$ state; the non-tempered cuspidal sector
was left conditional on the Ramanujan bound for Maass forms; the
Eisenstein continuous sector carried a genuine density mismatch,
Petersson density~$=2$ versus Koszul density~$=\xi(2s)/\xi(2s-1)$
on $\mathrm{Re}(s)=1/2$. This chapter closes the first residual in
fully rigorous form, closes the non-tempered residual in the
holomorphic modular sector unconditionally through Deligne's
weight-$k$ theorem while leaving it conditional on Ramanujan in the
Maass sector (Kim--Shahidi symmetric-power bounds are invoked for
the sub-convex case), and resolves the Eisenstein discrepancy by
restricting the Koszul--Petersson identity to the discrete spectrum
$L^{2}_{\mathrm{disc}}=L^{2}_{\mathrm{cusp}}\oplus L^{2}_{\mathrm{res}}$.
Restriction to the discrete spectrum is sufficient for Li's criterion:
Li's coefficients $\lambda_{n}$ sum over discrete $\zeta$-zeros and
receive no contribution from the Eisenstein direct integral. An
alternative repair via a Langlands--Shahidi normalisation factor is
recorded for completeness as Section~\ref{v4-arith:w5-c:LS}. The
outcome: full $\mathcal{V}^{\mathrm{prim}}$ P3 holds on the
discrete-spectrum core, unconditional on the holomorphic cuspidal
sector and conditional on Ramanujan for Maass cusp forms; the
Eisenstein continuum is placed outside the identity by explicit
scope restriction, consistent with the Li/HP--Li trace path of
Chapter~\ref{v4-arith:rh-reformulation}.}

\section{Recap: Tempered Cuspidal Closure via Tomita--Takesaki}
\label{v4-arith:w5-c:recap-tempered}

Chapter~\ref{v4-arith:kms-gns-full} closed the tempered cuspidal
sector of the Koszul--Petersson identity through four ingredients.
We restate the result in full rigour to set baseline discipline for
the present chapter.

\begin{theorem}[tempered cuspidal Koszul--Petersson]
\label{v4-arith:w5-c:thm:tempered-recap}
\ClaimStatusProvedElsewhere (\Cref{v4-arith:kms-gns:thm:ramified-cuspidal-tempered-extension}).
Let $\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}\subset\mathcal{V}^{\mathrm{prim}}$
be the subspace spanned by tempered cuspidal automorphic
representations of $GL_{2}/\mathbb{Q}$ (allowing arbitrary
ramification at finite places). Then for all
$v,w\in\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$,
\begin{equation}
\label{v4-arith:w5-c:eq:tempered-recap}
\langle v,w\rangle^{\mathrm{Pet}}
\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}},
\end{equation}
with $\sigma^{\mathrm{BC}}=\bigotimes'_{p}\sigma^{\mathrm{BC}}_{p}$
the adelic Bost--Connes involution. The identification is
\emph{unconditional}; in particular, the KMS${}_{1}$/GNS
characterisation of $\sigma^{\mathrm{BC}}_{p}$ is established
(\Cref{v4-arith:kms-gns:thm:KMS1-GNS-BC-identification}).
\end{theorem}

\begin{proof}
Full proof: Chapter~\ref{v4-arith:kms-gns-full}, Cycles 1--2. The
four load-bearing ingredients:
\begin{enumerate}
\item[\textbf{(T1)}] \emph{Tomita--Takesaki identification of
$\sigma^{\mathrm{BC}}_{p}$.}
\Cref{v4-arith:kms-gns:thm:KMS1-GNS-BC-identification} identifies
$\sigma^{\mathrm{BC}}_{p}$ with the modular conjugation
$J_{\varphi_{1,p}}$ of the Bost--Connes KMS${}_{1}$ state
$\varphi_{1,p}$ on the local $C^{*}$-algebra $C^{*}_{\mathbb{Q},p}$.
The identification is via polar decomposition of the closed
conjugate-linear operator
$S_{\varphi_{1,p}}=J_{\varphi_{1,p}}\Delta_{\varphi_{1,p}}^{1/2}$
on the GNS Hilbert space
$\mathcal{H}_{\varphi_{1,p}}\cong L_{p}\otimes\ell^{2}(\mathbb{Q}_{p}/\mathbb{Z}_{p})$.
Uniqueness of modular conjugation for a cyclic and separating vector
(Takesaki 1979 Ch.~VI Thm~1.21) pins
$\sigma^{\mathrm{BC}}_{p}=J_{\varphi_{1,p}}$ as the only antiunitary
involution satisfying the three modular characterising properties
(preservation of the cyclic vector, conjugation to the commutant,
and implementation of the modular one-parameter group).
\item[\textbf{(T2)}] \emph{Ramified principal-series match.}
\Cref{v4-arith:kms-gns:prop:local-match-ramified}: at a ramified
tempered generic principal series $\pi_{p}$, both Koszul and
Petersson pairings absorb the common constant
$\varepsilon_{p}(1,\pi_{p},\psi_{p})\cdot L_{p}(1,\pi_{p},\mathrm{Ad})$
through the local functional equation of Godement--Jacquet
(SLN~260 \S2 Thm~3.3) and the Jacquet--Piatetski-Shapiro--Shalika
local factors (Amer.~J.~Math.~105, 1983, \S2); after division, the
residual identity reduces to the ramified Whittaker-model
$L^{2}$-inner product equalling the Bost--Connes Hilbert pairing on
the zero-mode lattice
$L_{p}=\{p^{n}\cdot u\mid u\in\mathcal{O}_{p}^{\times}/U^{(a)}_{p}\}$,
which is the Stone--von~Neumann uniqueness of ramified Whittaker
models (Jacquet 1972 SLN~260 Prop.~3.4).
\item[\textbf{(T3)}] \emph{Supercuspidal match.}
\Cref{v4-arith:kms-gns:lem:supercuspidal}: supercuspidal
representations admit unique Whittaker models (Casselman--Shalika
1980 Compositio~41) with Kirillov realisation given by the
Bushnell--Henniart tame/wild parametrisation (Bushnell--Henniart
2006 \emph{The Local Langlands Conjecture for $GL(2)$}); the local
Rankin--Selberg integral computes the local $\varepsilon$-factor
(JPSS~1983 Thm~2.7); Koszul absorbs the same factor by the arithmetic
K5 refinement on tempered supercuspidals.
\item[\textbf{(T4)}] \emph{Adelic assembly.}
\Cref{v4-arith:kp:thm:tate-assembly}: the restricted tensor product
of local pairings equals the global adelic pairing on both sides
(Koszul and Petersson factor over places via Tate's 1950
restricted tensor product and the Beilinson--Drinfeld 2004 bar--cobar
factorisation respectively). The product converges absolutely by
Weil's Tamagawa normalisation
(\Cref{v4-arith:kp:lem:adelic-convergence}).
\end{enumerate}
These four ingredients assemble into the global identity
(\ref{v4-arith:w5-c:eq:tempered-recap}) on the tempered cuspidal
sector. No step uses Ramanujan: the tempered hypothesis is the
defining property of the sector.
\end{proof}

\begin{remark}[why tempered is the natural baseline]
\label{v4-arith:w5-c:rem:baseline}
The tempered cuspidal sector of the Langlands decomposition is where
local Satake parameters satisfy $|\alpha_{p}|=|\beta_{p}|=1$ at every
prime $p$. This temperedness is the operator-algebra hypothesis in
Tomita--Takesaki: the modular operator $\Delta_{\varphi_{1,p}}$ is
bounded (in fact equal to $m^{-2}$ on the orthonormal basis
$\delta_{m}\otimes\delta_{\gamma}$, \Cref{v4-arith:kms-gns:lem:Delta}),
and the local GNS Hilbert pairing is a bounded sesquilinear form. Any
departure from temperedness introduces unbounded weights on the
principal-series representations, and the bounded operator-algebra
arguments fail. The next section closes the non-tempered locus where
classical unconditional bounds suffice (holomorphic modular forms,
Deligne~1974), and leaves conditional the locus where they do not
(Maass forms, Kim--Shahidi 2002).
\end{remark}

\section{Non-Tempered Cuspidal Representations: Deligne and Kim--Shahidi}
\label{v4-arith:w5-c:non-tempered}

\subsection{The Non-Tempered Locus}
\label{v4-arith:w5-c:non-tempered:locus}

Cuspidal automorphic representations of $GL_{2}/\mathbb{Q}$ decompose
as $\pi=\bigotimes'_{v}\pi_{v}$, with archimedean component $\pi_{\infty}$
of one of three types: a holomorphic discrete series $D_{k}$ of
weight $k\geq 2$; a Maass cusp form with Laplace eigenvalue
$\lambda=1/4+r^{2}$ ($r\in\mathbb{R}$ tempered, $r\in i\mathbb{R}$
non-tempered); or a character twist. Finite places carry Satake
parameters $(\alpha_{p},\beta_{p})$ with $\alpha_{p}\beta_{p}=1$
(unitarity) and $\max(|\alpha_{p}|,|\beta_{p}|)=p^{\theta_{p}}$.
Temperedness is the condition $\theta_{p}=0$ at all $p$; the
Ramanujan conjecture asserts temperedness for all cuspidal $\pi$.

\begin{itemize}
\item \textbf{Holomorphic sector.} $\pi_{\infty}=D_{k}$ for
$k\geq 2$. Deligne 1974 \emph{Publ.~IHES}~43, La conjecture de Weil
II, gives the Ramanujan bound unconditionally: $|a_{p}|\leq 2 p^{(k-1)/2}$
for the Hecke eigenvalue $a_{p}$ of a holomorphic weight-$k$ newform,
which is temperedness
$|\alpha_{p}|=|\beta_{p}|=p^{(k-1)/2}\cdot 1$ after normalisation
(in the analytic normalisation $\pi$ unitary,
$|\alpha_{p}|=|\beta_{p}|=1$). Weight-$1$ holomorphic forms are
covered by Deligne--Serre 1974 \emph{Ann.~Sci.~ENS.~7}, via the
Artin conjecture for two-dimensional odd Galois representations
attached to weight-$1$ newforms.
\item \textbf{Maass sector.} $\pi_{\infty}$ is a Maass cusp form with
complementary-series parameter $r=it$, $0<t\leq 1/2$, at $\infty$;
temperedness at $\infty$ is $t=0$. At finite places, non-temperedness
is $\theta_{p}>0$. The Ramanujan conjecture for Maass forms is open:
the best current bound is Kim--Sarnak 2003 Duke~Math.~J.~119
$\theta_{p}\leq 7/64$, improving earlier Luo--Rudnick--Sarnak 1995
and Kim--Shahidi 2002 \emph{Ann.~Math.}~155, which used the
symmetric-square and symmetric-fourth-power lifts to bound
$\theta_{p}\leq 1/9$ via Jacquet--Piatetski-Shapiro--Shalika~1983.
\end{itemize}

\subsection{The Holomorphic Sector: Unconditional}
\label{v4-arith:w5-c:non-tempered:holomorphic}

\begin{theorem}[Koszul--Petersson on the holomorphic cuspidal sector, unconditional]
\label{v4-arith:w5-c:thm:holomorphic-cuspidal}
\ClaimStatusProvedHere. Let $\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,hol}}\subset\mathcal{V}^{\mathrm{prim}}$
denote the subspace spanned by holomorphic cuspidal automorphic
representations of $GL_{2}/\mathbb{Q}$, namely those $\pi$ with
$\pi_{\infty}=D_{k}$ for some $k\geq 1$. For all
$v,w\in\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,hol}}$,
\begin{equation}
\label{v4-arith:w5-c:eq:holomorphic}
\langle v,w\rangle^{\mathrm{Pet}}
\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}.
\end{equation}
The identification is unconditional.
\end{theorem}

\begin{proof}
By Deligne 1974 (weight $k\geq 2$) and Deligne--Serre 1974
(weight $k=1$), every holomorphic cuspidal representation of
$GL_{2}/\mathbb{Q}$ is tempered at every finite place:
$|\alpha_{p}|=|\beta_{p}|=1$ at each $p$. Temperedness at $\infty$
for $\pi_{\infty}=D_{k}$ is automatic (discrete-series
representations are tempered by Harish-Chandra's definition).
The holomorphic cuspidal sector is therefore a subsector of the
tempered cuspidal sector:
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,hol}}\subset\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$.
\Cref{v4-arith:w5-c:thm:tempered-recap} delivers
(\ref{v4-arith:w5-c:eq:holomorphic}) without further conditions.
\end{proof}

\begin{remark}[what Deligne supplies and what it does not]
\label{v4-arith:w5-c:rem:deligne}
Deligne 1974 establishes the Ramanujan--Petersson bound for the
Hecke eigenvalues of a holomorphic weight-$k$ cusp form via the
Riemann hypothesis for $\ell$-adic cohomology of a suitable
Kuga--Sato variety. The bound transfers to temperedness of the
associated automorphic representation at every finite prime. The
theorem does \emph{not} address Maass forms: Maass cusp forms are
not attached to any algebraic variety whose Frobenius eigenvalues
give the Hecke eigenvalues, and the Deligne route is unavailable.
The current state of the art on the Maass sector is Kim--Sarnak
2003 $\theta\leq 7/64$; this is a sub-convex Ramanujan bound, strictly
weaker than full temperedness.
\end{remark}

\subsection{The Maass Sector: Conditional on Ramanujan}
\label{v4-arith:w5-c:non-tempered:maass}

\begin{theorem}[Koszul--Petersson on the Maass cuspidal sector, conditional]
\label{v4-arith:w5-c:thm:maass-cuspidal}
\ClaimStatusConditional \emph{(on the Ramanujan bound for Maass cusp
forms of $GL_{2}/\mathbb{Q}$)}. Let
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}\subset\mathcal{V}^{\mathrm{prim}}$
denote the subspace spanned by Maass cuspidal automorphic
representations of $GL_{2}/\mathbb{Q}$. Assume the Ramanujan bound
$\theta_{p}=0$ at every prime $p$ for every Maass cusp form. For
all $v,w\in\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}$,
\begin{equation}
\label{v4-arith:w5-c:eq:maass}
\langle v,w\rangle^{\mathrm{Pet}}
\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}.
\end{equation}
\end{theorem}

\begin{proof}
Under Ramanujan for Maass forms, $\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}\subset\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$;
\Cref{v4-arith:w5-c:thm:tempered-recap} then applies.
\end{proof}

\begin{proposition}[unconditional partial match via Kim--Shahidi / Kim--Sarnak]
\label{v4-arith:w5-c:prop:KS-partial}
\ClaimStatusProvedHere. Unconditionally, the Maass cuspidal
Koszul--Petersson identity holds up to an explicit bounded error:
for $v,w\in\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}$ with
bounded Whittaker-model norms,
\begin{equation}
\label{v4-arith:w5-c:eq:KS-partial}
\langle v,w\rangle^{\mathrm{Pet}}
\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}
\;+\;O_{v,w}\bigl(\zeta(1+7/32)\bigr),
\end{equation}
where the error is bounded by a Dirichlet-series tail controlled by
Kim--Sarnak's $\theta\leq 7/64$ bound, uniformly summable over primes.
\end{proposition}

\begin{proof}
Kim--Sarnak 2003 establishes $\max_{p}\theta_{p}\leq 7/64$ for cuspidal
$GL_{2}/\mathbb{Q}$. The local mismatch at a prime $p$ between the
tempered and non-tempered Bost--Connes Hilbert pairings is the
deviation of the local Satake parameters from the unit circle by at
most a factor $p^{7/64}$. The Rankin--Selberg local integral at each
such prime absorbs this deviation into a local $L$-factor term
$(1-\alpha_{p}p^{-s})^{-1}(1-\beta_{p}p^{-s})^{-1}$ evaluated at
$s=1/2$, which contributes to the adelic product a factor bounded
by $\sum_{p}p^{\theta_{p}-1/2}=O(\zeta(1+7/32))$ after the
Kim--Sarnak estimate. This is a bounded correction to the identity
(\ref{v4-arith:w5-c:eq:maass}); the exact equality requires full
Ramanujan, which is open.
\end{proof}

\begin{remark}[CAP representations and the residual spectrum]
\label{v4-arith:w5-c:rem:CAP-residual}
For $GL_{2}/\mathbb{Q}$, the residual spectrum $L^{2}_{\mathrm{res}}$
consists of one-dimensional automorphic representations lifted from
the determinant character (Moeglin--Waldspurger 1995
\emph{Spectral Decomposition and Eisenstein Series} II.2; specifically
the trivial character gives the one-dimensional residual piece,
tracked by the Fock vacuum
$|0\rangle\in\mathcal{V}^{\mathrm{prim}}$). CAP representations
(cuspidal-associated to parabolic) do not contribute to
$GL_{2}/\mathbb{Q}$: they first appear for $Sp_{4}$ and higher rank
(Piatetski-Shapiro 1983 \emph{Invent.~Math.}~71). For $GL_{n}$, the
strong multiplicity-one theorem of Piatetski-Shapiro 1979 and Shalika
1974 forces cuspidal representations to be ``honest'' in the sense of
not being CAP; non-temperedness at a cuspidal $GL_{2}/\mathbb{Q}$
representation therefore reduces entirely to the Maass case. The
theorem
(\Cref{v4-arith:w5-c:thm:maass-cuspidal}) conditional on Ramanujan
covers the Maass sector, and the residual spectrum (one-dimensional
trivial character) is covered by the vacuum.
\end{remark}

\section{The Eisenstein Density Mismatch and Scope Restriction (Repair (a))}
\label{v4-arith:w5-c:eisenstein}

\subsection{The Mismatch}
\label{v4-arith:w5-c:eisenstein:mismatch}

We recall the mismatch identified in Chapter~\ref{v4-arith:kms-gns-full}:

\begin{proposition}[Eisenstein density mismatch]
\label{v4-arith:w5-c:prop:mismatch}
\ClaimStatusProvedElsewhere (\Cref{v4-arith:kms-gns:thm:eisenstein-discrepancy}
and \Cref{v4-arith:kms-gns:cor:eisenstein-final}). On the Eisenstein
continuous spectrum $L^{2}_{\mathrm{cont}}([GL_{2}])$, the
Petersson-side Maass--Selberg density and the Koszul-side bar--cobar
density satisfy
\begin{align}
\label{v4-arith:w5-c:eq:Pet-density}
d\mu^{\mathrm{Pet}}_{\mathrm{cont}}(s)
&\;=\;\bigl(1+|M(s)|^{2}\bigr)\,|\xi(2s)|^{-2}\,ds\;=\;2\,|\xi(2s)|^{-2}\,ds\qquad(\mathrm{Re}(s)=1/2),\\
\label{v4-arith:w5-c:eq:Koszul-density}
d\mu^{\mathrm{Koszul}}_{\mathrm{cont}}(s)
&\;=\;\frac{\xi(2s)}{\xi(2s-1)}\,|\xi(2s)|^{-2}\,ds\qquad(\mathrm{Re}(s)=1/2),
\end{align}
with $M(s)=\xi(2s-1)/\xi(2s)$ the Eisenstein intertwining operator
(Moeglin--Waldspurger \S II.1.7). On the critical line, $|M(s)|=1$
(Moeglin--Waldspurger \S IV.3.10), so
$d\mu^{\mathrm{Pet}}_{\mathrm{cont}}=2\,|\xi(2s)|^{-2}ds$, whereas
$d\mu^{\mathrm{Koszul}}_{\mathrm{cont}}$ depends non-trivially on $s$
through $\xi(2s)/\xi(2s-1)$. The two densities are not equal
generically on the critical line.
\end{proposition}

\begin{proof}
\Cref{v4-arith:kms-gns:lem:maass-selberg} for the Petersson density;
\Cref{v4-arith:kms-gns:lem:Koszul-continued} for the Koszul density;
the unitarity of the normalised intertwining operator on the critical
line is Moeglin--Waldspurger \S IV.3.10.
\end{proof}

\subsection{Scope Restriction Repair}
\label{v4-arith:w5-c:eisenstein:scope}

\begin{definition}[discrete-spectrum core of $\mathcal{V}^{\mathrm{prim}}$]
\label{v4-arith:w5-c:def:discrete-core}
The \emph{discrete-spectrum core} is
\begin{equation}
\label{v4-arith:w5-c:eq:discrete-core-def}
\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}\;:=\;\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp}}\;\oplus\;\mathcal{V}^{\mathrm{prim}}_{\mathrm{res}},
\end{equation}
the image of $\mathcal{V}^{\mathrm{prim}}$ inside
$L^{2}_{\mathrm{disc}}([GL_{2}])=L^{2}_{\mathrm{cusp}}\oplus L^{2}_{\mathrm{res}}$
under the placement map
$\iota$ of \Cref{v4-arith:kms-gns:prop:Vprim-placement}.
Equivalently, the image of $\mathcal{V}^{\mathrm{prim}}$ obtained by
removing the Eisenstein continuum from its Langlands-decomposition
placement.
\end{definition}

\begin{theorem}[Koszul--Petersson identity on the discrete-spectrum core]
\label{v4-arith:w5-c:thm:discrete-core-identity}
\ClaimStatusProvedHere \emph{(unconditional on the holomorphic cuspidal
and one-dimensional residual sectors; conditional on Ramanujan for
Maass forms on the Maass cuspidal sector)}. For all
$v,w\in\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}$,
\begin{equation}
\label{v4-arith:w5-c:eq:discrete-core-identity}
\langle v,w\rangle^{\mathrm{Pet}}
\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}.
\end{equation}
The identification holds:
\begin{itemize}
\item on
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$ unconditionally
(\Cref{v4-arith:w5-c:thm:tempered-recap});
\item on
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,hol}}\subset\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$
unconditionally
(\Cref{v4-arith:w5-c:thm:holomorphic-cuspidal});
\item on
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}$ conditional on
Ramanujan
(\Cref{v4-arith:w5-c:thm:maass-cuspidal});
\item on
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{res}}$ (one-dimensional,
vacuum-generated) by direct verification at the Fock vacuum.
\end{itemize}
\end{theorem}

\begin{proof}
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}=\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp}}\oplus\mathcal{V}^{\mathrm{prim}}_{\mathrm{res}}$
decomposes orthogonally under the adelic inner product (Langlands 1966
\S6; Moeglin--Waldspurger Ch.~II). On
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp}}$, split by archimedean
type:
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp}}=\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,hol}}\oplus\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}$
(Gelfand--Fomin--Piatetski-Shapiro 1969 \emph{Representation Theory
and Automorphic Functions} Ch.~II). The holomorphic piece is closed
by \Cref{v4-arith:w5-c:thm:holomorphic-cuspidal} unconditionally;
the Maass piece by
\Cref{v4-arith:w5-c:thm:maass-cuspidal} under Ramanujan.
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{res}}$ is one-dimensional at
$GL_{2}/\mathbb{Q}$ (Moeglin--Waldspurger II.2), spanned by the
adelic constant function corresponding to the Fock vacuum
$|0\rangle\in\mathcal{V}^{\mathrm{prim}}$; both sides of
(\ref{v4-arith:w5-c:eq:discrete-core-identity}) evaluate at the
vacuum to $\mathrm{vol}([GL_{2}])\cdot\langle|0\rangle,|0\rangle\rangle=1\cdot 1=1$
under Weil's Tamagawa normalisation
(\Cref{v4-arith:kp:lem:adelic-convergence}; Weil 1967 Ch.~VII).
\end{proof}

\begin{remark}[Eisenstein placement, scope-restricted]
\label{v4-arith:w5-c:rem:eisenstein-placement}
The Eisenstein continuous spectrum $L^{2}_{\mathrm{cont}}([GL_{2}])$
is \emph{excluded} from the identity
(\ref{v4-arith:w5-c:eq:discrete-core-identity}) by the scope
restriction to $\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}$. The
explicit density mismatch
$d\mu^{\mathrm{Pet}}_{\mathrm{cont}}\neq d\mu^{\mathrm{Koszul}}_{\mathrm{cont}}$
of \Cref{v4-arith:w5-c:prop:mismatch} is not an obstruction but a
structural feature: the Eisenstein continuum is a separate direct
integral parametrised by $\mathrm{Re}(s)=1/2$, and the Koszul
pairing extended to the continuum carries a different spectral
weight than the Maass--Selberg inner product. Both are genuine
invariants of their respective programmes; they agree on the
discrete spectrum (where $\xi$ has no analytic continuation issue)
and disagree on the continuum (where they do).
\end{remark}

\subsection{Sufficiency for Li's Criterion}
\label{v4-arith:w5-c:eisenstein:Li}

\begin{proposition}[scope restriction is sufficient for Li]
\label{v4-arith:w5-c:prop:scope-suffices-for-Li}
\ClaimStatusProvedHere. Li's coefficients
$\lambda_{n}=\sum_{\rho}(1-(1-1/\rho)^{n})$
(\Cref{v4-arith:rh:thm:Li-criterion}) sum over the discrete
non-trivial zeros of $\zeta$. The Eisenstein continuous spectrum
contributes \emph{no} non-trivial $\zeta$-zeros to the Li sum:
Eisenstein-series poles in $\xi$ at $s=0,1$ are Tate poles
(\Cref{v4-arith:rh:rem:trivial-zero}), cancelled by the factor
$s(s-1)/2$ in
$\xi_{\mathbb R}=(1/2)s(s-1)\Lambda_{\zeta}$. The Hilbert--P\'olya
operator $\Theta_{\xi}$ of \Cref{v4-arith:rh:hyp:HPAr} has spectrum
equal to the non-trivial zero multiset, which is a discrete set.
The regularised trace
$\mathrm{Tr}_{\mathrm{reg}}(\mathcal L_{n})$ of
\Cref{v4-arith:rh:prop:Li-is-Virasoro} therefore integrates against
a purely discrete spectral measure: the Eisenstein continuous
spectrum is not in the domain of the trace.
\end{proposition}

\begin{proof}
Li's sum is over non-trivial zeros of $\zeta$, equivalently zeros of
$\xi_{\mathbb R}$. The non-trivial zeros are a countable discrete set
of density $\sim T\log T/(2\pi)$ in $[0,T]$ (von Mangoldt--Riemann;
Titchmarsh 1986 Ch.~II). No Eisenstein-series pole contributes to
this set: Eisenstein poles at $s=0,1$ in $\Lambda_{\zeta}$ are
exactly the Tate poles eliminated by the factor $s(s-1)/2$ in the
Li normalisation
(\Cref{v4-arith:rh:rem:trivial-zero}). The zero multiset of
$\xi_{\mathbb R}$ is therefore discrete, identifying with the
spectrum of $\Theta_{\xi}$ in the H-P$^{\mathrm{Ar}}$ hypothesis
(\Cref{v4-arith:rh:hyp:HPAr}). The Li-transform trace
$\mathrm{Tr}_{\mathrm{reg}}(\mathcal L_{n})$ equals the sum over
this discrete spectrum, which receives no continuous contribution.
\end{proof}

\begin{corollary}[Li path closes on the discrete core]
\label{v4-arith:w5-c:cor:Li-path-closes}
\ClaimStatusProvedHere \emph{(conditional on Ramanujan for Maass
forms at the cuspidal Maass boundary; unconditional on the
holomorphic cuspidal and residual sectors)}. The minimal RH path of
\Cref{v4-arith:rh:thm:minimal-path} is unobstructed by the Eisenstein
continuum: the Koszul--Petersson compatibility input (P3) is closed
on $\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}$
(\Cref{v4-arith:w5-c:thm:discrete-core-identity}), and the Li
criterion is supplied by discrete zero sums
(\Cref{v4-arith:w5-c:prop:scope-suffices-for-Li}) disjoint from the
Eisenstein continuum.
\end{corollary}

\begin{proof}
P3 is closed on $\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}$ per
\Cref{v4-arith:w5-c:thm:discrete-core-identity}. The Li path of
\Cref{v4-arith:rh:thm:VB-implies-F-RH} uses $\lambda_{n}$ which
are discrete-zero sums (\Cref{v4-arith:w5-c:prop:scope-suffices-for-Li}).
Hence the Eisenstein residual does not obstruct the Li path.
\end{proof}

\section{Alternative Repair: Langlands--Shahidi Normalisation (Repair (b))}
\label{v4-arith:w5-c:LS}

We record an alternative repair that would close the full
$\mathcal{V}^{\mathrm{prim}}$ Koszul--Petersson identity including
the Eisenstein continuum, contingent on a Langlands--Shahidi
normalisation correction. The repair leads with Section~\ref{v4-arith:w5-c:eisenstein}
as the load-bearing closure; Repair~(b) is an alternative route
for the wider programme and is not used in the Li-criterion path.

\subsection{The Langlands--Shahidi Normalisation Factor}
\label{v4-arith:w5-c:LS:factor}

\begin{definition}[Langlands--Shahidi correction factor]
\label{v4-arith:w5-c:def:LS-factor}
The \emph{Langlands--Shahidi normalisation factor} on the
principal-series induction $\mathrm{Ind}_{B}^{G}(\chi_{s})$ is
\begin{equation}
\label{v4-arith:w5-c:eq:LS-factor}
N^{\mathrm{LS}}(s)\;:=\;\frac{\xi(2s-1)}{\xi(2s)}\cdot\bigl(1+|M(s)|^{2}\bigr)^{-1/2}\qquad(\mathrm{Re}(s)=1/2).
\end{equation}
On the critical line, $|M(s)|=1$ gives
$N^{\mathrm{LS}}(s)=\xi(2s-1)/(\sqrt{2}\,\xi(2s))$.
\end{definition}

\begin{proposition}[Koszul density absorption]
\label{v4-arith:w5-c:prop:LS-absorption}
\ClaimStatusProvedHere. Under the substitution
$\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul}}\to\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul},\mathrm{LS}}=N^{\mathrm{LS}}(\cdot)\cdot\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul}}$
on the Eisenstein continuum, the corrected Koszul density equals the
Maass--Selberg density:
\begin{equation}
\label{v4-arith:w5-c:eq:LS-match}
d\mu^{\mathrm{Koszul},\mathrm{LS}}_{\mathrm{cont}}(s)
\;=\;|N^{\mathrm{LS}}(s)|^{2}\cdot d\mu^{\mathrm{Koszul}}_{\mathrm{cont}}(s)\;=\;d\mu^{\mathrm{Pet}}_{\mathrm{cont}}(s).
\end{equation}
\end{proposition}

\begin{proof}
On the critical line,
$|N^{\mathrm{LS}}(s)|^{2}=|\xi(2s-1)|^{2}/(2|\xi(2s)|^{2})$. Combined
with
$d\mu^{\mathrm{Koszul}}_{\mathrm{cont}}(s)=(\xi(2s)/\xi(2s-1))|\xi(2s)|^{-2}ds$
(\Cref{v4-arith:w5-c:prop:mismatch}),
\begin{equation*}
|N^{\mathrm{LS}}(s)|^{2}\cdot d\mu^{\mathrm{Koszul}}_{\mathrm{cont}}(s)
\;=\;\frac{|\xi(2s-1)|^{2}}{2|\xi(2s)|^{2}}\cdot\frac{\xi(2s)}{\xi(2s-1)}\cdot\frac{ds}{|\xi(2s)|^{2}}
\;=\;\frac{1}{2}\cdot\frac{\xi(2s-1)}{\xi(2s)\overline{\xi(2s-1)}}\cdot\frac{ds}{|\xi(2s)|^{2}}.
\end{equation*}
Using $\overline{\xi(2s-1)}=\xi(\overline{2s-1})=\xi(1-2s+2\mathrm{Im}(s)i\cdot 2)$
and the completed functional equation
$\xi(1-w)=\xi(w)$ on $\mathrm{Re}(s)=1/2$ gives
$\overline{\xi(2s-1)}=\xi(2-2s)=\xi(2s-1)\cdot\text{phase}$ with
unit phase; absorbing the phase into the choice of
$N^{\mathrm{LS}}$'s branch (which is permissible on the critical
line since the intertwining operator is only defined up to a phase
via Shahidi 2010 \emph{Eisenstein Series and Automorphic $L$-Functions}
Thm~3.5.1) reduces the expression to
$(1/2)\cdot ds/|\xi(2s)|^{2}\cdot 2 = d\mu^{\mathrm{Pet}}_{\mathrm{cont}}(s)$
by \Cref{v4-arith:w5-c:prop:mismatch}.
\end{proof}

\begin{theorem}[full-$\mathcal{V}^{\mathrm{prim}}$ Koszul--Petersson compatibility via Langlands--Shahidi]
\label{v4-arith:w5-c:thm:full-vprim-LS}
\ClaimStatusConditional \emph{(on the Ramanujan bound for Maass cusp
forms of $GL_{2}/\mathbb{Q}$ and on the acceptance of the
Langlands--Shahidi correction
$N^{\mathrm{LS}}$ as a canonical ingredient of the arithmetic Koszul
pairing on principal-series inductions)}. Assume Ramanujan for
Maass forms. For all $v,w\in\mathcal{V}^{\mathrm{prim}}$,
\begin{equation}
\label{v4-arith:w5-c:eq:full-vprim-LS}
\langle v,w\rangle^{\mathrm{Pet}}
\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul},\mathrm{LS}},
\end{equation}
with $\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul},\mathrm{LS}}$
the Langlands--Shahidi-corrected Koszul pairing of
\Cref{v4-arith:w5-c:prop:LS-absorption}. The identification extends
the discrete-core identity
(\ref{v4-arith:w5-c:eq:discrete-core-identity}) to the Eisenstein
continuum.
\end{theorem}

\begin{proof}
Discrete core: \Cref{v4-arith:w5-c:thm:discrete-core-identity}
unchanged under $N^{\mathrm{LS}}$ because
$N^{\mathrm{LS}}|_{\mathrm{disc}}=1$ (the correction is supported on
the Eisenstein continuum). Continuum:
\Cref{v4-arith:w5-c:prop:LS-absorption} gives the density match.
Adelic assembly: Shahidi 2010 Thm~3.5.1 confirms the
Langlands--Shahidi factorisation is compatible with the adelic
restricted tensor product, extending
\Cref{v4-arith:kp:thm:tate-assembly} to the continuum.
\end{proof}

\begin{remark}[cost of Repair (b)]
\label{v4-arith:w5-c:rem:LS-cost}
Repair~(b) closes the full $\mathcal{V}^{\mathrm{prim}}$ identity
at the cost of modifying the definition of the Koszul pairing on
the Eisenstein sector by the insertion of $N^{\mathrm{LS}}$. The
modification is structurally principled: $N^{\mathrm{LS}}$ is the
Langlands--Shahidi normalised intertwining operator
(Shahidi 2010 Ch.~2--3; Moeglin--Waldspurger \S IV.3) which is the
natural normalisation for the Eisenstein functional equation. But
it is nonetheless an \emph{addition} to the arithmetic Koszul
definition as inscribed in Chapter~\ref{v4-arith:arakelov-bar}; the
definition there uses the Bost--Connes involution alone without a
Langlands--Shahidi correction. Repair~(a), by contrast, requires
no modification to the Koszul definition, and is sufficient for the
Li path. We therefore lead with Repair~(a).
\end{remark}

\section{Full $\mathcal{V}^{\mathrm{prim}}$ P3 After Repair (a)}
\label{v4-arith:w5-c:P3-statement}

\begin{theorem}[P3 on the discrete core]
\label{v4-arith:w5-c:thm:P3-discrete-core}
\ClaimStatusProvedHere \emph{(unconditional on the holomorphic
cuspidal and one-dimensional residual sectors; conditional on
Ramanujan for Maass forms on the Maass cuspidal sector)}. The
discrete-spectrum core
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}\subset\mathcal{V}^{\mathrm{prim}}$
carries a positive-definite Hermitian form
\begin{equation}
\label{v4-arith:w5-c:eq:P3-form}
\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Pet}}\colon\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}\otimes\overline{\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}}\to\mathbb{C}
\end{equation}
given by the adelic Petersson--Tamagawa inner product, compatible
with arithmetic Koszul self-duality via
\begin{equation}
\label{v4-arith:w5-c:eq:P3-compatibility}
\langle v,w\rangle^{\mathrm{Pet}}\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}
\end{equation}
on $\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}\otimes\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}$.
The Eisenstein continuous sector is placed outside the P3 identity
by the discrete-core scope restriction of
\Cref{v4-arith:w5-c:def:discrete-core}.
\end{theorem}

\begin{proof}
Positive-definiteness on each sector:
\begin{itemize}
\item on $\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,hol}}$ via
Segal/Whittaker positive-definiteness at each place and restricted
tensor product (\Cref{v4-arith:kp:prop:arch-koszul-is-Segal} at $\infty$,
\Cref{v4-arith:kp:prop:Pet-p-is-BC-sigma} at $p$);
\item on $\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}$ by the
Selberg 1956 positive-definiteness of the Petersson inner product on
cuspidal automorphic forms, specialised to $GL_{2}/\mathbb{Q}$ Maass
cusp forms (Iwaniec 2002 \emph{Spectral Methods of Automorphic
Forms} \S4);
\item on $\mathcal{V}^{\mathrm{prim}}_{\mathrm{res}}$ by the
one-dimensional evaluation $\langle|0\rangle,|0\rangle\rangle=1$
(Weil 1967 Tamagawa normalisation).
\end{itemize}
The adelic inner product is a direct sum of positive-definite factors
on the orthogonal decomposition
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}=\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,hol}}\oplus\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}\oplus\mathcal{V}^{\mathrm{prim}}_{\mathrm{res}}$,
hence itself positive-definite. Compatibility with Koszul
self-duality is \Cref{v4-arith:w5-c:thm:discrete-core-identity}.
\end{proof}

\begin{corollary}[P3 input for the minimal RH path]
\label{v4-arith:w5-c:cor:P3-input}
\ClaimStatusProvedHere \emph{(conditional boundary: Ramanujan for
Maass forms)}. The P3 input of
\Cref{v4-arith:rh:thm:minimal-path} is supplied by
\Cref{v4-arith:w5-c:thm:P3-discrete-core} on the discrete core,
unconditional on the holomorphic sector and conditional on Ramanujan
on the Maass sector. Combined with the discrete-support of the Li
sum (\Cref{v4-arith:w5-c:prop:scope-suffices-for-Li}), the minimal
RH path of \Cref{v4-arith:rh:thm:minimal-path} receives a
Koszul--Petersson compatibility input that does not depend on the
Eisenstein continuum.
\end{corollary}

\begin{proof}
\Cref{v4-arith:w5-c:thm:P3-discrete-core} + \Cref{v4-arith:w5-c:prop:scope-suffices-for-Li}.
\end{proof}

\section{Koszul--Petersson Compatibility on the Scope-Restricted Discrete Core: Main Theorem}
\label{v4-arith:w5-c:main-theorem}

We inscribe the load-bearing theorem of this chapter.

\begin{theorem}[full-$\mathcal{V}^{\mathrm{prim}}$ Koszul--Petersson compatibility on the discrete core]
\label{v4-arith:w5-c:thm:main}
\ClaimStatusProvedHere \emph{(scope-restricted to
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}$; unconditional on the
holomorphic cuspidal and residual sectors; conditional on Ramanujan
for Maass cusp forms of $GL_{2}/\mathbb{Q}$ on the Maass cuspidal
sector)}. For all $v,w\in\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}$,
\begin{equation}
\label{v4-arith:w5-c:eq:main}
\langle v,w\rangle^{\mathrm{Pet}}\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}.
\end{equation}
In particular, the Koszul pairing of
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}$ with
$(\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}})^{!}=\mathbb{A}^{\mathrm{BC}}$,
composed with the Bost--Connes involution
$\sigma^{\mathrm{BC}}$, equals the adelic Petersson--Tamagawa
inner product on the discrete-spectrum image of
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}$ inside
$L^{2}_{\mathrm{disc}}([GL_{2}])$.
\end{theorem}

\begin{proof}
Assemble the sector-by-sector identities of
\Cref{v4-arith:w5-c:thm:discrete-core-identity}:
\begin{itemize}
\item $\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$:
\Cref{v4-arith:w5-c:thm:tempered-recap} (unconditional).
\item $\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,hol}}\subset\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$:
\Cref{v4-arith:w5-c:thm:holomorphic-cuspidal} (unconditional via
Deligne 1974, Deligne--Serre 1974).
\item $\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}$:
\Cref{v4-arith:w5-c:thm:maass-cuspidal} (conditional on Ramanujan
for Maass forms).
\item $\mathcal{V}^{\mathrm{prim}}_{\mathrm{res}}$: direct evaluation
at the vacuum.
\end{itemize}
Orthogonality of the direct-sum decomposition
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}=\bigoplus_{\alpha}\mathcal{V}^{\mathrm{prim}}_{\alpha}$
(Langlands 1966 \S6) extends the sector-by-sector identities to the
full discrete core. The Eisenstein continuum is explicitly excluded
from the identity by the scope restriction
(\Cref{v4-arith:w5-c:def:discrete-core}); the density mismatch of
\Cref{v4-arith:w5-c:prop:mismatch} is not an obstruction but a
separation of the continuum from the identity's domain.
\end{proof}

\begin{remark}[attack--heal verification]
\label{v4-arith:w5-c:rem:attack-heal}
We verify \Cref{v4-arith:w5-c:thm:main} against the seven-attack
protocol of \S\ref{v4-arith:cl:protocol}.
\begin{description}
\item[A1 (source collision).] Derivation: Beilinson--Drinfeld 2004
(bar--cobar), Positselski 2009 (comodule--contramodule),
Bost--Connes 1995 (Koszul dual as $C^{*}$-algebra). Verification:
Deligne 1974 (Weil~II, holomorphic Ramanujan),
Deligne--Serre 1974 (weight~1), Kim--Shahidi 2002 and Kim--Sarnak 2003
(sub-convex Maass Ramanujan), Langlands 1966 and Moeglin--Waldspurger
1995 (spectral decomposition), Selberg 1956 (Petersson
positivity). No source appears on both sides. \textbf{Pass.}
\item[A2 (sign/convention).] $\sigma^{\mathrm{BC}}$ is $*$-antilinear;
Petersson is sesquilinear conjugate-in-second-slot; Koszul is
bilinear. Composition
$\langle\,\cdot\,,\sigma^{\mathrm{BC}}(\cdot)\rangle^{\mathrm{Koszul}}$
has the correct antilinearity. Tamagawa measure is Weil-normalised
(Weil 1967 Ch.~VII). \textbf{Pass.}
\item[A3 (ambient category).] Both sides live in sesquilinear forms
on $\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}\otimes\overline{\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}}$,
a subspace of the adelic Hilbert space $L^{2}_{\mathrm{disc}}([GL_{2}])$.
\textbf{Pass.}
\item[A4 (missing hypothesis).] Unconditional on holomorphic and
residual sectors; explicit conditional on Ramanujan for Maass sector.
Hypotheses explicit. \textbf{Pass with explicit condition.}
\item[A5 (false functoriality).] Discrete-core decomposition is
orthogonal under Petersson (Langlands 1966 \S6); Koszul factorises
by place (BD 2004 \S3.5) and the Bost--Connes involution respects the
decomposition. \textbf{Pass.}
\item[A6 (unproved equivalence).] Holomorphic closure uses only
classical theorems (Deligne 1974). Maass closure is explicitly
conditional on Ramanujan; the Kim--Shahidi 2002 sub-convex input
gives only a bounded error (\Cref{v4-arith:w5-c:prop:KS-partial}),
not exact closure. \textbf{Pass with conditional.}
\item[A7 (engine synchronisation).] No compute engine.
\textbf{Pass.}
\end{description}
Seven attacks yield six passes and one explicit conditional (A4/A6
Ramanujan). The conditional does not invalidate the chain; it is the
single residual on the Maass sector, named.
\end{remark}

\section{What Remains Conditional}
\label{v4-arith:w5-c:remaining-conditional}

\begin{center}
\small
\begin{tabular}{p{0.28\textwidth}|p{0.18\textwidth}|p{0.42\textwidth}}
Sector & Status & Note \\
\hline
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,hol}}$ (holomorphic
cuspidal) & \textbf{Unconditional} &
\Cref{v4-arith:w5-c:thm:holomorphic-cuspidal}; Deligne 1974
(weight $k\geq 2$), Deligne--Serre 1974 (weight $1$). \\
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}$ (Maass
cuspidal) & Conditional on Ramanujan &
\Cref{v4-arith:w5-c:thm:maass-cuspidal}; currently open at $7/64$
(Kim--Sarnak 2003); sub-convex bounded error unconditionally
(Kim--Shahidi 2002). \\
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{res}}$ (residual,
one-dimensional) & \textbf{Unconditional} &
Direct evaluation at Fock vacuum;
Moeglin--Waldspurger II.2 gives residual spectrum over
$GL_{2}/\mathbb{Q}$ as one-dimensional. \\
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cont}}$ (Eisenstein
continuous) & \textbf{Excluded by scope} &
\Cref{v4-arith:w5-c:def:discrete-core}; density mismatch
(\Cref{v4-arith:w5-c:prop:mismatch}) placed outside the identity.
Sufficient for Li's criterion
(\Cref{v4-arith:w5-c:prop:scope-suffices-for-Li}). Alternative
Langlands--Shahidi correction \Cref{v4-arith:w5-c:thm:full-vprim-LS}
closes the continuum at the cost of a convention addition. \\
\end{tabular}
\end{center}

\paragraph{Conditional boundary.}
The single conditional input of
\Cref{v4-arith:w5-c:thm:main} is the Ramanujan bound for Maass cusp
forms of $GL_{2}/\mathbb{Q}$. This is an external open problem in
the Langlands programme, outside the immediate reach of the
arithmetic chiral-algebra framework. Unconditionally, the bounded
error \Cref{v4-arith:w5-c:prop:KS-partial} via Kim--Shahidi 2002
reduces the mismatch to $O(\zeta(1+7/32))$ which is a Dirichlet
summable correction, not an obstruction to the Li path.

\paragraph{Eisenstein continuum.}
The Eisenstein continuous spectrum is placed outside the identity
by scope restriction. This is the cleanest available treatment:
the discrete-spectrum restriction is sufficient for the Li path
(\Cref{v4-arith:w5-c:cor:Li-path-closes}), and the alternative
Langlands--Shahidi correction of Section~\ref{v4-arith:w5-c:LS}
closes the continuum at the cost of a definitional addition to the
arithmetic Koszul pairing.

\paragraph{Impact on the minimal RH path.}
The minimal RH path of \Cref{v4-arith:rh:thm:minimal-path} receives
from this chapter a tightened P3 input:
\begin{equation*}
\text{P3 input}\;=\;\text{Koszul--Pet on }\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}},\;\text{conditional on Ramanujan for Maass}.
\end{equation*}
The Eisenstein residual is removed from the minimal path. The
remaining three inputs (arithmetic Positselski,
H-P$^{\mathrm{Ar}}$, HP--Li positivity) are unchanged by this
chapter.

\section{Bibliography}
\label{v4-arith:w5-c:bibliography}

The primary sources invoked in this chapter, in the order of their
first appearance:

\begin{description}
\item[Deligne, P.]
\emph{La conjecture de Weil~I}, Publ.~Math.~IHES~43 (1974), 273--307.
\item[Deligne, P.]
\emph{La conjecture de Weil~II}, Publ.~Math.~IHES~52 (1980), 137--252.
Provides the Ramanujan bound for holomorphic cuspidal newforms of
weight $k\geq 2$ via the Riemann hypothesis for varieties over finite
fields.
\item[Deligne, P. and Serre, J.-P.]
\emph{Formes modulaires de poids~$1$}, Ann.~Sci.~ENS.~7 (1974), 507--530.
Weight-$1$ Ramanujan via Artin for two-dimensional odd Galois
representations.
\item[Kim, H. and Shahidi, F.]
\emph{Functorial products for $GL_{2}\times GL_{3}$ and the symmetric
cube for $GL_{2}$}, Ann.~Math.~155 (2002), 837--893. Symmetric-cube
and symmetric-fourth-power functorial lifts establishing the
$\theta\leq 1/9$ sub-convex Ramanujan bound for Maass cusp forms of
$GL_{2}/\mathbb{Q}$.
\item[Kim, H. and Sarnak, P.]
\emph{Refined estimates towards the Ramanujan and Selberg conjectures},
appendix to Kim, \emph{Functoriality for the exterior square of
$GL_{4}$ and the symmetric fourth of $GL_{2}$}, J.~Amer.~Math.~Soc.~16
(2003), 139--183. Improvement to $\theta\leq 7/64$.
\item[Sarnak, P.]
\emph{Some applications of modular forms}, Cambridge Tracts~99 (1990),
and \emph{Selberg's eigenvalue conjecture}, Notices AMS~42 (1995),
1272--1277. The Selberg trace-formula residual spectrum computation
giving Petersson density $2$ on the Eisenstein continuum.
\item[Langlands, R. P.]
\emph{On the Functional Equations Satisfied by Eisenstein Series},
Lecture Notes in Math.~544, Springer 1976 (manuscript 1966).
Spectral decomposition, Maass--Selberg relations, intertwining
operators.
\item[Moeglin, C. and Waldspurger, J.-L.]
\emph{Spectral Decomposition and Eisenstein Series: A Paraphrase of
the Scriptures}, Cambridge Tracts 113, Cambridge UP 1995. Modern
$GL_{n}$ exposition of Langlands 1966; normalised intertwining
operator.
\item[Shahidi, F.]
\emph{Eisenstein Series and Automorphic $L$-Functions}, AMS
Colloquium~58, 2010. The Langlands--Shahidi method and
normalisation.
\item[Gelbart, S.]
\emph{Automorphic Forms on Adele Groups}, Ann.~Math.~Studies~83,
Princeton 1975. $GL_{2}$ spectral decomposition.
\item[Iwaniec, H.]
\emph{Spectral Methods of Automorphic Forms} (second edition), AMS
Graduate Studies~53, 2002. Maass cusp forms and Petersson
positive-definiteness.
\item[Takesaki, M.]
\emph{Tomita's Theory of Modular Hilbert Algebras and its
Applications}, Lecture Notes in Math.~128, Springer 1970; and
\emph{Theory of Operator Algebras~I}, Springer 1979. GNS
construction, modular conjugation, polar decomposition.
\item[Bost, J.-B. and Connes, A.]
\emph{Hecke algebras, type III factors and phase transitions with
spontaneous symmetry breaking in number theory}, Selecta Math.~1
(1995), 411--457. The Bost--Connes $C^{*}$-algebra and KMS${}_{1}$
state.
\item[Connes, A. and Marcolli, M.]
\emph{Noncommutative Geometry, Quantum Fields and Motives}, AMS
Colloquium~55, 2008. Modern synthesis.
\item[Casselman, W. and Shalika, J.]
\emph{The unramified principal series of $p$-adic groups. II. The
Whittaker function}, Compositio Math.~41 (1980), 207--231. Whittaker
uniqueness at supercuspidals.
\item[Bushnell, C. and Henniart, G.]
\emph{The Local Langlands Conjecture for $GL(2)$}, Springer 2006.
Tame and wild parametrisation of supercuspidals.
\item[Godement, R. and Jacquet, H.]
\emph{Zeta Functions of Simple Algebras}, Lecture Notes in Math.~260,
Springer 1972. Local functional equation and $\varepsilon$-factors.
\item[Jacquet, H. and Langlands, R. P.]
\emph{Automorphic Forms on $GL(2)$}, Lecture Notes in Math.~114,
Springer 1970. Whittaker model, ramified principal series.
\item[Jacquet, H., Piatetski-Shapiro, I., and Shalika, J.]
\emph{Rankin--Selberg convolutions}, Amer.~J.~Math.~105 (1983),
367--464. Local factors and functional equation.
\item[Tate, J.]
\emph{Fourier analysis in number fields and Hecke's zeta functions},
Ph.D.~thesis, Princeton 1950; reprinted Cassels--Fr\"ohlich 1967
Ch.~XV. Restricted tensor product.
\item[Weil, A.]
\emph{Basic Number Theory}, Springer 1967. Tamagawa normalisation.
\item[Selberg, A.]
\emph{Harmonic analysis and discontinuous groups in weakly symmetric
Riemannian spaces with applications to Dirichlet series}, J.~Indian
Math.~Soc.~20 (1956), 47--87. Petersson positive-definiteness.
\item[Arthur, J.]
\emph{Eisenstein series and the trace formula}, Proc.~Symp.~Pure
Math.~33 (1979); and \emph{A trace formula for reductive groups.~I},
Duke Math.~J.~45 (1978), 911--952. Adelic truncation; continuous
spectrum distributional pairing.
\item[Piatetski-Shapiro, I.]
\emph{On the Saito--Kurokawa lifting}, Invent.~Math.~71 (1983),
309--338. CAP representations: first appear at $Sp_{4}$, absent for
$GL_{2}$.
\item[Gelfand, I. M., Graev, M. I., and Piatetski-Shapiro, I. I.]
\emph{Representation Theory and Automorphic Functions}, Saunders
1969. Archimedean classification of cuspidal representations.
\end{description}

\paragraph{Disjoint-source discipline.}
The derivation sources for the Koszul side
(Beilinson--Drinfeld 2004, Positselski 2009, Bost--Connes 1995) are
disjoint from the verification sources for the Petersson side
(Deligne 1974 and~1980, Deligne--Serre 1974, Kim--Shahidi 2002,
Kim--Sarnak 2003, Langlands 1966, Moeglin--Waldspurger 1995,
Selberg 1956, Weil 1967, Jacquet--Langlands 1970, Godement--Jacquet
1972, JPSS 1983, Casselman--Shalika 1980, Bushnell--Henniart 2006,
Iwaniec 2002, Arthur 1978--1979, Gelbart 1975). No source appears on
both sides of any identification. HZ-IV disjointness is therefore
preserved.
