\chapter{Constructing $H_{\mathrm{HP}}$: Bost--Connes GNS, Modular Spectrum, and the Primary-Heisenberg Twist}
\label{v4-arith:w5-b:hp-operator}

\emph{The obligation (W) left open by
Chapters~\ref{v4-arith:hpar-det},
\ref{v4-arith:R-analytic-audit},
\ref{v4-arith:kms-gns-full} is weight existence: construct a
self-adjoint ordinate operator $H_{\mathrm{HP}}$ such that
$\Theta_{\xi}:=\frac12\mathrm{id}+iH_{\mathrm{HP}}$ has regularised
determinant $\xi_{\mathbb R}$ and Weil--Connes trace distribution
equal to the non-trivial-zero distribution of $\zeta$. This chapter
builds the operator in elementary steps. Sections~1--2 construct the
unconditional skeleton: the Bost--Connes $C^{*}$-algebra, its
KMS${}_{1}$ state, the GNS representation, and the modular operator
whose logarithm is a self-adjoint diagonal operator on the GNS
Hilbert space with a spectrum indexed by $\{\log m\mid m\in
\mathbb{N}^{\times}\}$. Section~3 sets up the arithmetic Fock and the
primary Heisenberg core. Section~4 names the \emph{primary-Heisenberg
twist} that is required to carry the modular log-operator to a
candidate zeta-zero operator; the twist is a Maass/Mellin transform
pre-composed with the identification of spectral variables, and its
\emph{existence with the correct spectrum} is the Hilbert--P\'olya
obstruction itself. Sections~5--6 state the target determinant and
trace-distribution identities and record which implications are
tautological consequences of a spectrum-realising twist and which are
additional positivity inputs. Section~7 separates the three layers
precisely: what is unconditional (the GNS skeleton and the modular
operator), what is conditional-tautological (determinant and trace
identities given the twist), and what is the 100-year
Hilbert--P\'olya obstruction (existence of the twist).}

\section{Bost--Connes $C^{*}$-Dynamical Setup}
\label{v4-arith:w5-b:bc-setup}

We recall the Bost--Connes $C^{*}$-algebra and its $\mathbb{R}$-action
in the form fixed in Chapter~\ref{v4-arith:kms-gns-full}, in a
normalisation convenient for the primary-Heisenberg operator
construction.

\begin{definition}[local and adelic Bost--Connes algebras]
\label{v4-arith:w5-b:def:bc-algebra}
\ClaimStatusDefinitional. For each rational prime $p$, the local
Bost--Connes algebra is the $C^{*}$-algebra
\[
C^{*}_{\mathbb{Q},p}\;:=\;C^{*}\bigl(\mu_{m},\mu_{m}^{*},e(\gamma)\bigr)_{m\in p^{\mathbb{N}},\,\gamma\in\mathbb{Q}_{p}/\mathbb{Z}_{p}},
\]
with Bost--Connes 1995 Selecta~1 \S2.2 relations $\mu_{m}\mu_{m}^{*}=1/m$,
$\mu_{m}e(\gamma)\mu_{m}^{*}=e(m\gamma)/m$, $e(\gamma+\delta)=e(\gamma)e(\delta)$.
The adelic algebra is the restricted tensor product
\[
C^{*}_{\mathbb{Q}}\;:=\;\bigotimes{}'_{p}\,C^{*}_{\mathbb{Q},p},
\]
restricted with respect to the local units $1_{p}\in C^{*}_{\mathbb{Q},p}$.
The $\mathbb{R}$-action $\sigma^{t}\colon C^{*}_{\mathbb{Q}}\to
C^{*}_{\mathbb{Q}}$ is the tensor product of
\begin{equation}
\label{v4-arith:w5-b:eq:bc-time}
\sigma^{t}_{p}(\mu_{m})=m^{it}\mu_{m},\qquad
\sigma^{t}_{p}(e(\gamma))=e(\gamma),\qquad
\sigma^{t}_{p}(\mu_{m}^{*})=m^{-it}\mu_{m}^{*}.
\end{equation}
\end{definition}

\begin{remark}[reference to route~4 construction]
\label{v4-arith:w5-b:rem:wave4-ref}
The local construction is \Cref{v4-arith:def:bost-connes-algebra};
the adelic assembly is
\Cref{v4-arith:kms-gns:cor:adelic-KMS-GNS}. The relations
\eqref{v4-arith:w5-b:eq:bc-time} are the modular automorphism
generators; we use them below to fix normalisations.
\end{remark}

\begin{lemma}[KMS${}_{1}$ state]
\label{v4-arith:w5-b:lem:kms-1}
\ClaimStatusProvedElsewhere. There is a unique normal
$\sigma$-KMS state $\varphi_{1}$ on $C^{*}_{\mathbb{Q}}$ at inverse
temperature $\beta=1$, factoring locally as
$\varphi_{1}=\bigotimes'_{p}\varphi_{1,p}$, with
\[
\varphi_{1,p}(\mu_{n}^{*}\mu_{m}e(\gamma))\;=\;\delta_{n,m}\,m^{-1}\,\widetilde{e}_{p}(\gamma),\qquad
\widetilde{e}_{p}(\gamma)=[\gamma=0],
\]
and normalised partition function $Z_{1}(\beta)=\zeta(\beta)$ on the
zero-mode sector for $\mathrm{Re}(\beta)>1$. The associated von~Neumann
factor is type~III${}_{1}$.
\end{lemma}

\begin{proof}
This is Bost--Connes 1995 Selecta~1 Theorem~25, with the adelic
assembly of Connes--Marcolli 2008 AMS Colloquium~55 \S4.1. The
normalisation choice and the factor type are Bost--Connes Thm~25
(ii)-(iii). We cite only; no new content is added here.
\end{proof}

\begin{remark}[partition at $\beta=1$]
\label{v4-arith:w5-b:rem:partition-at-one}
The nominal partition $Z_{1}(1)=\zeta(1)$ diverges. The Bost--Connes
convention regularises $Z_{1}(\beta)$ at $\beta\to 1^{+}$ as
Euler--Mascheroni $\gamma$ (via
$\zeta(\beta)=1/(\beta-1)+\gamma+O(\beta-1)$); we do not use this
regularisation as an operator input, only to match the route~3 ledger
of \Cref{v4-arith:hpar-det:thm:uniqueness-given-existence}.
\end{remark}

\section{GNS Representation and the Modular Operator}
\label{v4-arith:w5-b:gns-modular}

We record the GNS data and pin down the spectrum of the modular
operator. This section is entirely classical and unconditional.

\begin{definition}[GNS triple of $\varphi_{1}$]
\label{v4-arith:w5-b:def:gns}
\ClaimStatusDefinitional. Let $(\mathcal{H}_{1},\pi_{1},\Omega_{1})$
denote the GNS triple of $\varphi_{1}$ on $C^{*}_{\mathbb{Q}}$:
$\mathcal{H}_{1}$ is the Hilbert space obtained by completing
$C^{*}_{\mathbb{Q}}/\mathcal{N}_{1}$ with
$\mathcal{N}_{1}=\{x\mid\varphi_{1}(x^{*}x)=0\}$ under
$\langle x,y\rangle=\varphi_{1}(y^{*}x)$; $\pi_{1}$ is left
multiplication; $\Omega_{1}$ is the class of the identity.
\end{definition}

\begin{lemma}[GNS Hilbert space as a restricted tensor]
\label{v4-arith:w5-b:lem:gns-restricted-tensor}
\ClaimStatusProvedElsewhere. There is a unitary isomorphism
\[
\mathcal{H}_{1}\;\cong\;\bigotimes{}'_{p}\Bigl(L_{p}\otimes\ell^{2}(\mathbb{Q}_{p}/\mathbb{Z}_{p})\Bigr),
\]
with $L_{p}=\ell^{2}(p^{\mathbb{N}},m^{-1}dm)$ (Bost--Connes zero-mode
lattice at $p$), restricted with respect to the local vacuum
$\delta_{1}\otimes\delta_{0}$ at each $p$, and
$\Omega_{1}=\bigotimes'_{p}(\delta_{1}\otimes\delta_{0})$.
\end{lemma}

\begin{proof}
Local statement is
\Cref{v4-arith:kms-gns:lem:GNS-space}; adelic assembly is restricted
tensor product by modularity of tensors under KMS states (Takesaki
1979 Ch.~VIII \S1 Prop.~1.8).
\end{proof}

\begin{lemma}[modular operator on the GNS space]
\label{v4-arith:w5-b:lem:modular}
\ClaimStatusProvedElsewhere. The modular operator
$\Delta_{1}$ of $\varphi_{1}$ satisfies, on the basis
$\{\delta_{m}\otimes\delta_{\gamma}\}_{m\in\mathbb{N}^{\times},\gamma\in\mathbb{Q}/\mathbb{Z}}$
of the zero-mode lattice times character sector,
\begin{equation}
\label{v4-arith:w5-b:eq:Delta-basis}
\Delta_{1}\bigl(\delta_{m}\otimes\delta_{\gamma}\bigr)\;=\;m^{-2}\,\delta_{m}\otimes\delta_{\gamma},
\qquad
\Delta_{1}^{it}\;=\;\pi_{1}\circ\sigma^{t}\circ\pi_{1}^{-1}\quad(t\in\mathbb{R}).
\end{equation}
In particular $\log\Delta_{1}$ is self-adjoint on the dense
$\sigma$-analytic core and has pure point spectrum
$\{-2\log m\mid m\in\mathbb{N}^{\times}\}$ on the zero-mode lattice,
with multiplicity equal to the number of character sectors.
\end{lemma}

\begin{proof}
Tomita--Takesaki theory: for a KMS state at $\beta=1$,
$\Delta_{1}^{it}=\sigma^{t}$ on the GNS image of analytic elements
(Takesaki 1970 Lecture Notes Thm~10.1; Takesaki 1979 Ch.~VIII \S1
Cor.~1.2). Applying $\sigma^{t}(\mu_{m})=m^{it}\mu_{m}$ twice, one to
each of $\mu_{m}\Omega_{1}$ and $\mu_{m}^{*}\Omega_{1}$, produces the
$m^{-2}$ eigenvalue. This is the content of
\Cref{v4-arith:kms-gns:lem:Delta}; we use it as recorded there.
\end{proof}

\begin{definition}[BC log-modular operator]
\label{v4-arith:w5-b:def:N-BC}
\ClaimStatusDefinitional. The \emph{Bost--Connes log-modular
operator} is
\[
N_{\mathrm{BC}}\;:=\;-\tfrac12\log\Delta_{1}
\]
on the $\sigma$-analytic core. On the basis of
\Cref{v4-arith:w5-b:lem:gns-restricted-tensor}, it acts diagonally by
\begin{equation}
\label{v4-arith:w5-b:eq:N-BC}
N_{\mathrm{BC}}\bigl(\delta_{m}\otimes\delta_{\gamma}\bigr)\;=\;(\log m)\,\delta_{m}\otimes\delta_{\gamma}.
\end{equation}
\end{definition}

\begin{theorem}[unconditional self-adjointness and spectrum of $N_{\mathrm{BC}}$]
\label{v4-arith:w5-b:thm:N-BC-self-adjoint}
\ClaimStatusProvedHere. $N_{\mathrm{BC}}$ is essentially self-adjoint
on the finite-span core
$\mathcal{D}_{\mathrm{BC}}:=\mathrm{span}_{\mathbb{C}}\{\delta_{m}\otimes\delta_{\gamma}\}$
of $\mathcal{H}_{1}$. Its closure is self-adjoint, non-negative, and
has pure point spectrum
\[
\mathrm{Spec}(N_{\mathrm{BC}})\;=\;\{\log m\mid m\in\mathbb{N}^{\times}\}\;=\;\{0\}\cup\{\log p_{1}^{a_{1}}\cdots p_{k}^{a_{k}}\mid\text{prime powers}\},
\]
with multiplicity at $\log m$ equal to $\sharp(\mathbb{Q}/\mathbb{Z})$
(countable) unless one restricts to the spherical character sector
$\gamma=0$, where the multiplicity is~$1$.
\end{theorem}

\begin{proof}
Diagonal operator on a basis of the Hilbert space with real
eigenvalues: Reed--Simon Vol.~I Thm.~VIII.11 gives essential
self-adjointness on the finite-span core; the closure is the
standard $L^{2}$-diagonal self-adjoint operator with spectrum equal
to the eigenvalue set. The multiplicities are read off from the
basis.
\end{proof}

\begin{remark}[what $N_{\mathrm{BC}}$ is \emph{not}]
\label{v4-arith:w5-b:rem:N-BC-not}
$N_{\mathrm{BC}}$ is the canonical self-adjoint operator extracted
from the KMS${}_{1}$ modular data: it is the Bost--Connes Hamiltonian
of Chapter~\ref{v4-arith:def:bost-connes-algebra} times a normalisation,
and its spectrum is \emph{log-primes} and their additive
semigroup, not zeros of $\zeta$. This is the honest content of the
unconditional Bost--Connes/Tomita--Takesaki construction. The
Berry--Keating weight $\lambda(p^{k})=k\log p$ of
\Cref{v4-arith:hpar-det:def:candidate-weights}(BK) is the eigenvalue
of $N_{\mathrm{BC}}$ at the monomial $m=p^{k}$, consistent with
route~3 weight selection
(\Cref{v4-arith:hpar-det:thm:uniqueness-given-existence}).
Confusing $N_{\mathrm{BC}}$ with the zeta-zero operator is the
Hilbert--P\'olya mistake that
\Cref{v4-arith:rh:rem:spectral-convention} warns against.
\end{remark}

\section{Primary Heisenberg Fock and Arithmetic Virasoro}
\label{v4-arith:w5-b:primary-heisenberg}

We recall the arithmetic Heisenberg Fock on which the candidate
Hilbert--P\'olya operator will be defined; the primary core is the
relevant subspace.

\begin{definition}[arithmetic Fock and primary subspace]
\label{v4-arith:w5-b:def:fock}
\ClaimStatusDefinitional. The \emph{arithmetic Heisenberg Fock} is
\[
\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}\;:=\;\bigotimes{}'_{p}\,\mathrm{Fock}^{(p)}\,\otimes\,\mathcal{H}^{(\infty)},
\]
where $\mathrm{Fock}^{(p)}$ is the per-prime chiral Heisenberg Fock
(Chapter~\ref{v4-arith:drinfeld-kapranov}) and
$\mathcal{H}^{(\infty)}$ is the archimedean complex Heisenberg Fock
(Chapter~\ref{v4-arith:polyakov}). The \emph{primary core} is the
dense subspace
\[
\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}\;:=\;\mathrm{span}_{\mathbb{C}}\Bigl\{|\mathbf{n}\rangle\otimes\delta_{m}\;:\;\mathbf{n}\in\mathbb{Z}_{\geq0}^{\oplus\mathbb{N}},\;m\in\mathbb{N}^{\times}\Bigr\}
\]
of finite-support number-state/zero-mode tensors
(\Cref{v4-arith:hpvbconv:def:L0-domain}).
\end{definition}

\begin{lemma}[primary Fock embeds into GNS]
\label{v4-arith:w5-b:lem:fock-embeds-gns}
\ClaimStatusProvedHere. There is a canonical isometric embedding
\[
\iota:\;\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}\;\hookrightarrow\;\mathcal{H}_{1}
\]
sending the finite-support number-state $|\mathbf{n}\rangle\otimes\delta_{m}$
to $\mathrm{Asc}(\mathbf{n})\cdot(\delta_{m}\otimes\delta_{0})$ where
$\mathrm{Asc}(\mathbf{n})$ is the Heisenberg ascending operator at
number-occupation $\mathbf{n}$. The image is dense in the spherical
character sector of $\mathcal{H}_{1}$ on the zero-mode lattice.
\end{lemma}

\begin{proof}
The primary Fock is generated from the vacuum by finite products of
Heisenberg creation operators acting on spherical zero-mode lattice
vectors. Each creation operator lifts to a multiplication operator
on the GNS space commuting with $\pi_{1}(e(\gamma))$ for $\gamma=0$,
and the spherical zero-mode lattice is the $\gamma=0$ image of the
Bost--Connes lattice. Isometry is the Heisenberg/GNS inner-product
match on number states. See \Cref{v4-arith:thm:BC-acts-on-L} for
the commuting of Heisenberg creation with BC multiplication in the
spherical sector.
\end{proof}

\begin{remark}[density and scope of the embedding]
\label{v4-arith:w5-b:rem:embedding-scope}
The embedding $\iota$ lands in the spherical-character zero-mode
sector; the non-spherical $\gamma\neq 0$ sectors of the GNS space
carry the Eisenstein/ramified content not needed for the primary
construction (the Eisenstein residual of
Chapter~\ref{v4-arith:kms-gns-full} Cycle~4). All subsequent
spectral matching is performed inside $\iota$'s image; the operator
$N_{\mathrm{BC}}$ restricts there without loss.
\end{remark}

\section{The Primary-Heisenberg Twist and the Candidate $H_{\mathrm{HP}}$}
\label{v4-arith:w5-b:twist}

The goal of this section is to state precisely what a \emph{primary-Heisenberg
twist} is; we will see that its existence with the correct
spectral property is the content of H-P$^{\mathrm{Ar}}$ and is not
delivered by the Bost--Connes construction alone.

\subsection{Statement of the Twist}
\label{v4-arith:w5-b:twist:statement}

\begin{definition}[twist data]
\label{v4-arith:w5-b:def:twist}
\ClaimStatusDefinitional. A \emph{primary-Heisenberg twist} is a
triple $(\mathcal{H}_{\xi},U,A)$ consisting of:
\begin{enumerate}
\item a Hilbert space $\mathcal{H}_{\xi}$ equipped with the Petersson
inner product of \Cref{v4-arith:thm:P3-resolution} (on the
sph-finite cuspidal core, conditional on
\Cref{v4-arith:cl:cj:koszul-Petersson-compat});
\item a dense invariant core
$\mathcal{D}_{\xi}\subset\mathcal{H}_{\xi}$;
\item an isometric map
$U:\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}\to\mathcal{H}_{\xi}$
with dense range in $\mathcal{D}_{\xi}$;
\item a self-adjoint unbounded operator
$A:\mathcal{D}_{\xi}\to\mathcal{H}_{\xi}$ satisfying
\begin{equation}
\label{v4-arith:w5-b:eq:twist-intertwine}
A\,U\,|\mathbf{n}\rangle\otimes\delta_{m}\;=\;U\,\bigl(L_{0}^{\mathrm{Ar},\mathrm{Heis}}+\log m\bigr)\,|\mathbf{n}\rangle\otimes\delta_{m}\quad\text{on}\quad
\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}},
\end{equation}
in a chain-level sense, where $L_{0}^{\mathrm{Ar},\mathrm{Heis}}$ is
the Sugawara $L_{0}$ on the primary Heisenberg Fock.
\end{enumerate}
Given such data, the \emph{candidate Hilbert--P\'olya operator} is
\begin{equation}
\label{v4-arith:w5-b:eq:H-HP-def}
H_{\mathrm{HP}}\;:=\;A,
\end{equation}
and the \emph{arithmetic zero operator} is
\begin{equation}
\label{v4-arith:w5-b:eq:Theta-xi-def}
\Theta_{\xi}\;:=\;\tfrac12\mathrm{id}\;+\;iH_{\mathrm{HP}}.
\end{equation}
\end{definition}

\begin{remark}[what (iv) says]
\label{v4-arith:w5-b:rem:what-iv-says}
Condition~(iv) names the intertwining of $A$ with the log-prime
semigroup shift. At $\mathbf{n}=0$, the right-hand side of
\eqref{v4-arith:w5-b:eq:twist-intertwine} is $\log m\cdot
U(\delta_{m})$, i.e.\ an eigenvector at eigenvalue $\log m$; this is
exactly the BC log-spectrum of
\Cref{v4-arith:w5-b:thm:N-BC-self-adjoint}. The twist is therefore
required to be \emph{consistent with} the Bost--Connes modular
data, not replace it. The new content is the Sugawara-cross-term
$L_{0}^{\mathrm{Ar},\mathrm{Heis}}$ on the descendants.
\end{remark}

\subsection{The Twist Must Invert Hadamard, Not Euler}
\label{v4-arith:w5-b:twist:hadamard-inversion}

The spectrum requirement on $A$ is the critical-line zero-placement
of $\xi_{\mathbb R}$: the spectral multiset of $A$ must match
$\{\gamma_{\rho}\mid\xi(1/2+i\gamma_{\rho})=0\}$. This is
\emph{not} the spectrum of $N_{\mathrm{BC}}$, which is
$\{\log m\}_{m\in\mathbb{N}^{\times}}$. The two multisets are
related by the Mellin transform of $\xi$ through its Hadamard
factorisation:
\begin{equation}
\label{v4-arith:w5-b:eq:hadamard}
\xi_{\mathbb R}(s)\;=\;\frac{1}{2}\,e^{B s}\,\prod_{\rho}\Bigl(1-\frac{s}{\rho}\Bigr)e^{s/\rho}
\end{equation}
(Riemann 1859; Hadamard 1893), where the product is over non-trivial
zeros and $B$ is the Hadamard constant. The primes appear on the
side of the \emph{logarithmic derivative}
\begin{equation}
\label{v4-arith:w5-b:eq:log-deriv-xi}
-\frac{\xi_{\mathbb R}'(s)}{\xi_{\mathbb R}(s)}\;=\;-B-\frac{1}{s}-\frac{1}{s-1}+\frac{1}{2}\log\pi-\frac{1}{2}\Gamma'/\Gamma(s/2)+\sum_{n\geq1}\frac{\Lambda(n)}{n^{s}}
\end{equation}
(von Mangoldt 1895), and the zero-prime duality is the Weil explicit
formula. The twist $A$ is the operator-level analogue of
\emph{inverting this duality}: from the log-prime spectrum of
$N_{\mathrm{BC}}$, read off the zero-spectrum of $A$ via the
Hadamard expansion. This is not an operation that produces a
self-adjoint operator by construction; the Hadamard expansion is a
statement about an entire function, not about a self-adjoint operator
on a Hilbert space.

\subsection{What a Closed Twist Would Deliver}
\label{v4-arith:w5-b:twist:consequences}

\begin{hypothesis}[H-P$^{\mathrm{Ar}}$-twist]
\label{v4-arith:w5-b:hyp:twist-existence}
There exists a primary-Heisenberg twist $(\mathcal{H}_{\xi},U,A)$ in
the sense of \Cref{v4-arith:w5-b:def:twist} with the additional
spectral property
\begin{equation}
\label{v4-arith:w5-b:eq:spec-A}
\mathrm{Spec}(A)\;=\;\{\gamma_{\rho}\mid\rho=\tfrac12+i\gamma_{\rho}\text{ is a non-trivial zero of }\xi_{\mathbb R}\},
\end{equation}
with multiplicities matching zero multiplicities and the
$\mathbb{Z}/2$-symmetry $\gamma_{\rho}\mapsto-\gamma_{\rho}$ acting on
the spectrum as the arithmetic $S$-modular involution.
\end{hypothesis}

\begin{remark}[relation to H-P$^{\mathrm{Ar}}$]
\label{v4-arith:w5-b:rem:equals-HPAr}
\Cref{v4-arith:w5-b:hyp:twist-existence} is the functional-analytic
content of \Cref{v4-arith:rh:hyp:HPAr}: an operator $A$ with the
specified spectrum is exactly $H_{\mathrm{HP}}$ of the reformulation
chapter, and $\Theta_{\xi}=1/2+iA$ is the arithmetic zero operator.
The classical Hilbert--P\'olya programme requests this object; the
Vol~IV chiral-algebra framework requests it together with the
intertwining with $N_{\mathrm{BC}}$ via the log-prime spectrum. The
latter is an additional constraint which, if imposed,
\emph{disambiguates} which operator $A$ is the correct one among
many candidates with the same zero spectrum; it does not provide
existence.
\end{remark}

\section{Determinant Identity: Hadamard Factorisation}
\label{v4-arith:w5-b:determinant}

We state the determinant identity and identify precisely what
portion is tautological (given
\Cref{v4-arith:w5-b:hyp:twist-existence}) and what portion is an
additional regularisation input.

\begin{proposition}[regularised determinant from Hadamard]
\label{v4-arith:w5-b:prop:det-formal}
\ClaimStatusProvedHere\emph{, conditional on
\Cref{v4-arith:w5-b:hyp:twist-existence}}. Assume the twist
$(\mathcal{H}_{\xi},U,A)$ has the spectral property
\eqref{v4-arith:w5-b:eq:spec-A}. Define the regularised determinant
of the shifted operator by the $\zeta$-regularised prescription
\[
\log\det_{\infty}(s\mathrm{id}-\Theta_{\xi})\;:=\;-\partial_{u}\mathrm{Tr}_{\mathrm{reg}}\bigl((s\mathrm{id}-\Theta_{\xi})^{-u}\bigr)\Big|_{u=0},
\]
interpreted as a distribution on $s$ in the admissible Weil--Connes
Paley--Wiener class. Then
\begin{equation}
\label{v4-arith:w5-b:eq:det-identity}
\det_{\infty}\bigl(s\mathrm{id}-\Theta_{\xi}\bigr)\;=\;\xi_{\mathbb R}(s).
\end{equation}
\end{proposition}

\begin{proof}
Under
\Cref{v4-arith:w5-b:hyp:twist-existence}, the spectral multiset of
$\Theta_{\xi}=1/2+iA$ is $\{1/2+i\gamma_{\rho}\}_{\rho}=\{\rho\}$
with multiplicities matching. The Hadamard product
\eqref{v4-arith:w5-b:eq:hadamard} expresses $\xi_{\mathbb R}$ as a
product over the same zeros, with the convergence factor
$e^{s/\rho}$ and the Hadamard constant $B$ absorbing the sum over
$1/\rho$. The $\zeta$-regularised definition of $\det_{\infty}$
(Ray--Singer 1971; Voros 1987) for an operator with positive
Hadamard genus produces
$\prod_{\rho}(1-s/\rho)e^{s/\rho}$ after subtraction of the
Hadamard terms. The remaining prefactor $e^{Bs}/2$ is the
regularisation ambiguity and is fixed by the Weil--Connes
normalisation compatibility with the primary sector (the Tate-pole
removal of \Cref{v4-arith:rh:rem:trivial-zero}). Combining these:
\eqref{v4-arith:w5-b:eq:det-identity} holds as an equality of
regularised determinants in the distributional Paley--Wiener sense,
modulo explicit normalisation constants.
\end{proof}

\begin{remark}[what this does and does not buy]
\label{v4-arith:w5-b:rem:det-does-not-buy}
\Cref{v4-arith:w5-b:prop:det-formal} is \emph{conditional} on the
spectrum condition \eqref{v4-arith:w5-b:eq:spec-A}. Given that
spectrum, the Hadamard identity is essentially tautological: the
regularised determinant of an operator whose spectrum equals the
zeros of an entire function of order~$1$ with genus~$1$ is the
function itself (up to a convergence-factor normalisation). The
content of H-P$^{\mathrm{Ar}}$ is therefore \emph{not} the
determinant identity, but the existence of a self-adjoint operator
with the prescribed spectrum. The determinant identity is the
statement that Hadamard factorisation is compatible with
$\zeta$-regularisation; the spectral identity is the statement that
there is a self-adjoint operator realising the zeros.
\end{remark}

\begin{remark}[why this is not the Berry--Keating step]
\label{v4-arith:w5-b:rem:berry-keating-contrast}
Berry--Keating (SIAM Review 41, 1999) propose $H=xp+1/2$ on
$L^{2}(\mathbb{R}_{>0},dx/x)$ as the candidate $H_{\mathrm{HP}}$.
Their proposal reproduces the leading-order Riemann--von Mangoldt
zero density via Bohr--Sommerfeld quantisation but does not
deliver the individual zero spectrum: the Planck-cell regularisation
is not self-adjoint as stated. The Vol~IV twist construction
inherits the same obstruction in a different form: the BC log-prime
spectrum is classical and self-adjoint, but its lift to the zero
spectrum via the Hadamard-dual twist is the missing content. See
\Cref{v4-arith:hpvbconv:rem:berry-keating} for the route~2 discussion.
\end{remark}

\section{Trace Distribution: Weil--Connes Explicit Formula}
\label{v4-arith:w5-b:trace}

\begin{proposition}[distributional trace identity]
\label{v4-arith:w5-b:prop:weil-trace}
\ClaimStatusProvedHere\emph{, conditional on
\Cref{v4-arith:w5-b:hyp:twist-existence}}. Assume the twist with
spectral property \eqref{v4-arith:w5-b:eq:spec-A}. For every
admissible Weil--Connes Paley--Wiener test function $h$
(in the class $\mathsf{PW}$ of
\Cref{v4-arith:hpar-det:lem:PW-wave-regularisation}),
\begin{equation}
\label{v4-arith:w5-b:eq:trace-identity}
\mathrm{Tr}_{\mathrm{reg}}\bigl(h(H_{\mathrm{HP}})\bigr)\;=\;\sum_{\rho}h(\gamma_{\rho})\;=\;\int_{\mathbb R}h(r)\,dW_{\infty}(r)\;-\;2\sum_{n\geq1}\frac{\Lambda(n)}{\sqrt n}\widehat h(\log n),
\end{equation}
where the second equality is the Weil--Connes explicit formula
(\Cref{v4-arith:hpar-det:eq:PW-weil}).
\end{proposition}

\begin{proof}
Given
\Cref{v4-arith:w5-b:hyp:twist-existence}, the regularised trace of
$h(H_{\mathrm{HP}})=h(A)$ computed in the spectral representation of
$A$ is $\sum_{\rho}h(\gamma_{\rho})$, which is the classical Weil
explicit formula for $\mathsf{PW}$ test functions
(\Cref{v4-arith:hpar-det:lem:PW-wave-regularisation}; Weil 1952;
Connes 1999 arXiv:math/9811068 Thm.~1). The admissibility of the
regularisation for $\mathrm{Tr}_{\mathrm{reg}}$ is preserved by
$\iota$ (\Cref{v4-arith:w5-b:lem:fock-embeds-gns}) because the
embedding is isometric on the spherical primary-Fock image.
\end{proof}

\begin{corollary}[Weil-positive cone compatibility]
\label{v4-arith:w5-b:cor:weil-positive}
\ClaimStatusProvedHere\emph{, conditional on
\Cref{v4-arith:w5-b:hyp:twist-existence}}. The regularised trace
$\mathrm{Tr}_{\mathrm{reg}}(h(H_{\mathrm{HP}}))$ is non-negative for
every $h\in\mathsf{PW}$ of the form $h=|\phi|^{2}$ with $\phi$ in the
Petersson-positive cone on the primary Fock, \emph{if and only if}
Weil positivity holds for $\zeta$. In particular, Li positivity
(\Cref{v4-arith:rh:thm:Li-criterion}) is implied.
\end{corollary}

\begin{proof}
By \Cref{v4-arith:w5-b:prop:weil-trace}, the regularised trace
equals the Weil/Connes zero-side distribution on $\mathsf{PW}$ tests.
Non-negativity on $|\phi|^{2}$-tests is Weil's positivity statement
(Weil 1952 \S5; Barner 1981; Bombieri 2000 RH notes). Li positivity
follows by
\Cref{v4-arith:rh:prop:Li-is-Virasoro}.
\end{proof}

\section{Status: Unconditional Core, Conditional Tautologies, and the Obstruction}
\label{v4-arith:w5-b:status}

We separate three layers and state precisely what each contributes.

\subsection{Layer 1 (Unconditional Skeleton)}
\label{v4-arith:w5-b:status:layer-1}

\begin{itemize}
\item The Bost--Connes $C^{*}$-algebra, its KMS${}_{1}$ state,
its GNS representation, and the modular operator $\Delta_{1}$ with
spectrum $\{m^{-2}\}_{m\in\mathbb{N}^{\times}}$ on the zero-mode
lattice: Sections~1--2, unconditional
(\Cref{v4-arith:w5-b:lem:modular},
\Cref{v4-arith:w5-b:thm:N-BC-self-adjoint}).
\item The BC log-modular operator $N_{\mathrm{BC}}$ is self-adjoint
on the finite-span core, non-negative, with pure point spectrum
$\{\log m\}_{m\in\mathbb{N}^{\times}}$: unconditional theorem
(\Cref{v4-arith:w5-b:thm:N-BC-self-adjoint}).
\item The primary Heisenberg Fock embeds isometrically into the GNS
space on the spherical character sector
(\Cref{v4-arith:w5-b:lem:fock-embeds-gns}).
\end{itemize}

\subsection{Layer 2 (Conditional Tautologies given the Twist)}
\label{v4-arith:w5-b:status:layer-2}

\begin{itemize}
\item Given a twist $(\mathcal{H}_{\xi},U,A)$ with spectral property
\eqref{v4-arith:w5-b:eq:spec-A}, the regularised determinant identity
$\det_{\infty}(s\mathrm{id}-\Theta_{\xi})=\xi_{\mathbb R}(s)$ holds
(\Cref{v4-arith:w5-b:prop:det-formal}).
\item Given the same twist, the distributional trace identity
$\mathrm{Tr}_{\mathrm{reg}}(h(H_{\mathrm{HP}}))=\sum_{\rho}h(\gamma_{\rho})$
holds for $h\in\mathsf{PW}$ (\Cref{v4-arith:w5-b:prop:weil-trace}).
\item Given the same twist, Li positivity holds if and only if Weil
positivity for $\zeta$ holds (\Cref{v4-arith:w5-b:cor:weil-positive}).
\end{itemize}

These are not vacuous: they verify that the Vol~IV primary-Fock
setting is compatible with the classical Hadamard/Weil calculus.

\subsection{Layer 3 (the 100-Year Hilbert--P\'olya Obstruction)}
\label{v4-arith:w5-b:status:layer-3}

\begin{itemize}
\item The existence of a self-adjoint operator $A$ on a Hilbert space
$\mathcal{H}_{\xi}$, densely defined on a core
$\mathcal{D}_{\xi}\subset\mathcal{H}_{\xi}$, intertwining the BC
log-modular operator $N_{\mathrm{BC}}$ on the primary Fock and with
spectrum equal to the imaginary parts of non-trivial zeros of
$\zeta$ with correct multiplicities, is
\Cref{v4-arith:w5-b:hyp:twist-existence}. It is not delivered by
any part of the Bost--Connes/Tomita--Takesaki construction.
\item The route~2 structural analysis
(Chapter~\ref{v4-arith:HPAr-vbconverse}) shows this is equivalent
to Connes' adele class space absorption spectrum conjecture
(Connes arXiv:math/9811068 \S IV) and to Deninger's motivic
cohomology Frobenius purity conjecture (Deninger 1994). No
independent construction exists.
\end{itemize}

\begin{theorem}[precise obstruction]
\label{v4-arith:w5-b:thm:precise-obstruction}
\ClaimStatusProvedHere. The Hilbert--P\'olya obligation
(\Cref{v4-arith:rh:hyp:HPAr}) in the Vol~IV framework reduces to
the existence, in the sense of
\Cref{v4-arith:w5-b:def:twist}-\Cref{v4-arith:w5-b:hyp:twist-existence},
of a self-adjoint operator $A$ intertwining $N_{\mathrm{BC}}$ via
the primary-Heisenberg-to-zeta-zero twist and having spectrum
\eqref{v4-arith:w5-b:eq:spec-A}. The BC log-modular operator
$N_{\mathrm{BC}}$ supplies the zero-mode eigenvalues at $\log m$
unconditionally. The twist exists iff the Connes
absorption-spectrum condition is realised in the chiral-Fock
framework. Neither half of this equivalence is closed by this
chapter or by any earlier one.
\end{theorem}

\begin{proof}
By \Cref{v4-arith:w5-b:thm:N-BC-self-adjoint}, the operator
$N_{\mathrm{BC}}$ is unconditionally present with the log-prime
spectrum. By \Cref{v4-arith:w5-b:prop:det-formal} and
\Cref{v4-arith:w5-b:prop:weil-trace}, \emph{conditional on} a twist
with the spectral property \eqref{v4-arith:w5-b:eq:spec-A}, both
the determinant identity \eqref{v4-arith:w5-b:eq:det-identity} and
the trace identity \eqref{v4-arith:w5-b:eq:trace-identity} hold.
The spectral property is equivalent to
\Cref{v4-arith:hpvbconv:cor:HPAr-connes-equivalence}, the Connes
absorption-spectrum condition. The equivalence is the route~2
three-way equivalence theorem
(\Cref{v4-arith:hpvbconv:thm:HPAr-equivalence}) in its repaired
form after the Friedrichs construction of
\Cref{v4-arith:hpvbconv:thm:L0-Friedrichs}.
\end{proof}

\begin{remark}[honest status of the (W) obligation]
\label{v4-arith:w5-b:rem:W-honest}
The (W) weight-existence obligation of
\Cref{v4-arith:hpar-det:cor:wave3-structure} asks for an additive
Bost--Connes weight system satisfying the zeta partition
normalisation. This chapter supplies the weight $\lambda=\lambda_{\mathrm{BK}}$
unconditionally as the eigenvalues of $N_{\mathrm{BC}}$ on the
primary Fock image
(\Cref{v4-arith:w5-b:thm:N-BC-self-adjoint}); the weight is the
unique one consistent with KMS${}_{1}$ and the symmetric
normalisation. What the chapter does \emph{not} supply is the
Hilbert--P\'olya operator $H_{\mathrm{HP}}$ with zeta-zero
spectrum. In the route~3 ledger vocabulary, (W) is closed
unconditionally as far as the weight is concerned, and the
remaining residual is (H) (the H-P trace bridge). The (W) step is
unblocked by this construction; the full H-P$^{\mathrm{Ar}}$
closure requires the Layer~3 obstruction of
\Cref{v4-arith:w5-b:thm:precise-obstruction}.
\end{remark}

\begin{remark}[what an honest conditional theorem looks like]
\label{v4-arith:w5-b:rem:honest-conditional}
A faithful Vol~IV statement about $H_{\mathrm{HP}}$ reads: ``There
is a canonical self-adjoint operator $N_{\mathrm{BC}}$ on the GNS
space of the Bost--Connes KMS${}_{1}$ state with pure point
spectrum $\{\log m\}_{m\in\mathbb{N}^{\times}}$; this operator is
not $H_{\mathrm{HP}}$. There is an intertwining primary-Heisenberg
twist whose existence with the zeta-zero spectrum is
\Cref{v4-arith:w5-b:hyp:twist-existence}, equivalent to the Connes
and Deninger spectral-realisation conjectures. Under that
hypothesis, the determinant and trace identities
\eqref{v4-arith:w5-b:eq:det-identity},
\eqref{v4-arith:w5-b:eq:trace-identity} hold and agree with
Hadamard factorisation and the Weil explicit formula.'' This
statement closes (W) in the form it can honestly be closed; it
does not close H-P$^{\mathrm{Ar}}$ (the twist-existence statement
is what H-P$^{\mathrm{Ar}}$ asks for).
\end{remark}

\subsection{Summary Table}
\label{v4-arith:w5-b:status:summary}

\begin{center}
\small
\begin{tabular}{l|l|l}
Component & Status in Vol~IV & Reference \\
\hline
BC $C^{*}$-algebra and KMS${}_{1}$ state & Unconditional & Bost--Connes 1995 \\
GNS triple $(\mathcal{H}_{1},\pi_{1},\Omega_{1})$ & Unconditional & \Cref{v4-arith:w5-b:def:gns} \\
Modular operator $\Delta_{1}$ and spectrum & Unconditional & \Cref{v4-arith:w5-b:lem:modular} \\
BC log-modular $N_{\mathrm{BC}}$, self-adjoint & Unconditional & \Cref{v4-arith:w5-b:thm:N-BC-self-adjoint} \\
Primary Fock $\hookrightarrow$ GNS (spherical) & Unconditional & \Cref{v4-arith:w5-b:lem:fock-embeds-gns} \\
Twist data $(\mathcal{H}_{\xi},U,A)$ with zero spectrum & Conjectural (=H-P$^{\mathrm{Ar}}$) & \Cref{v4-arith:w5-b:hyp:twist-existence} \\
$\det_{\infty}(s\mathrm{id}-\Theta_{\xi})=\xi_{\mathbb R}(s)$ & Conditional on twist & \Cref{v4-arith:w5-b:prop:det-formal} \\
$\mathrm{Tr}_{\mathrm{reg}}(h(H_{\mathrm{HP}}))=\sum_{\rho}h(\gamma_{\rho})$ & Conditional on twist & \Cref{v4-arith:w5-b:prop:weil-trace} \\
Li positivity from Petersson positivity & Conditional on twist + Weil positivity & \Cref{v4-arith:w5-b:cor:weil-positive} \\
(W) weight existence in the route~3 ledger & Closed (with $\lambda_{\mathrm{BK}}$) & \Cref{v4-arith:w5-b:rem:W-honest} \\
(H) H-P trace bridge in the route~3 ledger & Open; equivalent to twist existence & \Cref{v4-arith:w5-b:thm:precise-obstruction}
\end{tabular}
\end{center}

\section{Bibliography and Source Catalog}
\label{v4-arith:w5-b:biblio}

The construction draws on four disjoint source catalogs, recorded
here with publisher/arXiv identifiers for reproducibility.

\paragraph{Operator-algebra and KMS theory.}
\begin{description}
\item[Bost--Connes.] J.-B.~Bost and A.~Connes, \emph{Hecke algebras,
type~III factors and phase transitions with spontaneous symmetry
breaking in number theory}, Selecta Math.~1 (1995), 411--457.
\item[Connes.] A.~Connes, \emph{Trace formula in noncommutative
geometry and the zeros of the Riemann zeta function}, Selecta
Math.~5 (1999), 29--106; arXiv:math/9811068.
\item[Connes--Marcolli.] A.~Connes and M.~Marcolli, \emph{Noncommutative
geometry, quantum fields, and motives}, AMS Colloquium Publications
55 (2008). Ch.~3--4 for KMS states and rigidity; Ch.~5 for the
adele class space.
\item[Takesaki.] M.~Takesaki, \emph{Tomita's theory of modular
Hilbert algebras and its applications}, Lecture Notes in Mathematics
128 (Springer 1970); \emph{Theory of Operator Algebras~I}, (Springer
1979), Ch.~IV \S5 (GNS), Ch.~VI \S1 (Tomita--Takesaki); \emph{Theory
of Operator Algebras~II} (Springer 2003), Ch.~VIII \S1 (modular
automorphism).
\item[Meyer.] R.~Meyer, \emph{On a representation of the idele class
group related to primes and zeros of $L$-functions}, Duke Math.~J.
127 (2005), 519--595; arXiv:math/0311468.
\end{description}

\paragraph{Hilbert--P\'olya candidates and spectral realisations.}
\begin{description}
\item[Berry--Keating.] M.~V.~Berry and J.~P.~Keating, \emph{The
Riemann zeros and eigenvalue asymptotics}, SIAM Review 41 (1999),
236--266.
\item[Reed--Simon.] M.~Reed and B.~Simon, \emph{Methods of Modern
Mathematical Physics}, Vol.~I (Academic Press 1980),
Thm.~VIII.11 (diagonal operators); Vol.~II (Academic Press 1975),
Thm.~X.23 (Friedrichs extension).
\item[Deninger.] C.~Deninger, \emph{Motivic $L$-functions and
regularised determinants}, Proc.~Symp.~Pure Math.~55.1 (1994),
707--743; \emph{A note on arithmetic topology and dynamical systems},
Math.~Nachr.~205 (2001), 107--135.
\item[Ray--Singer.] D.~B.~Ray and I.~M.~Singer, \emph{$R$-torsion
and the Laplacian on Riemannian manifolds}, Advances in
Mathematics 7 (1971), 145--210 (source of $\zeta$-regularised
determinants).
\item[Voros.] A.~Voros, \emph{Spectral functions, special functions
and the Selberg zeta function}, Comm.~Math.~Phys.~110 (1987),
439--465.
\end{description}

\paragraph{Hadamard factorisation and explicit formula.}
\begin{description}
\item[Riemann.] B.~Riemann, \emph{\"Uber die Anzahl der Primzahlen
unter einer gegebenen Gr\"osse}, Monatsberichte der Berliner
Akademie, 1859.
\item[Hadamard.] J.~Hadamard, \emph{\'Etude sur les propri\'et\'es
des fonctions enti\`eres et en particulier d'une fonction consid\'er\'ee
par Riemann}, J.~Math.~Pures Appl.~9 (1893), 171--215.
\item[von Mangoldt.] H.~von Mangoldt, \emph{Zu Riemann's Abhandlung
``\"Uber die Anzahl der Primzahlen unter einer gegebenen Gr\"osse''},
J.~Reine Angew.~Math.~114 (1895), 255--305.
\item[Weil.] A.~Weil, \emph{Sur les ``formules explicites'' de la
th\'eorie des nombres premiers}, Comm.~S\'em.~Math.~Univ.~Lund (1952),
252--265.
\item[Edwards.] H.~M.~Edwards, \emph{Riemann's Zeta Function},
Academic Press 1974.
\end{description}

\paragraph{Chiral algebra and arithmetic Fock background.}
\begin{description}
\item[Beilinson--Drinfeld.] A.~Beilinson and V.~Drinfeld,
\emph{Chiral Algebras}, AMS Colloquium Publications 51 (2004).
\item[Bost--Connes~(cited above).]
\item[Vol~IV chapters.] \Cref{v4-arith:kms-gns-full},
\Cref{v4-arith:HPAr-vbconverse}, \Cref{v4-arith:hpar-det},
\Cref{v4-arith:R-analytic-audit}, \Cref{v4-arith:rh-reformulation}.
\end{description}

No source in this catalog appears on both sides of the
Koszul--Pet/KMS derivation and the Hilbert--P\'olya spectral-realisation
verification. The route~3 catalogue of
\Cref{v4-arith:hpar-det:sources} is disjoint from the route~2
catalogue (\Cref{v4-arith:hpvbconv:sources}); the present chapter
draws on the intersection of the two with the Takesaki modular
theory and the Hadamard/von~Mangoldt classical analysis, both
outside the Vol~IV internal derivations.
