\chapter{VB$^{*}$ Main Direction via Stieltjes--Hamburger Positivity, Determinacy, and HB$^{+}$/BD$^{+}$}
\label{v4-arith:w5-j:VBstar-spectral-positivity}

\emph{Chapter~\ref{v4-arith:HPAr-vbconverse} isolated the VB$^{*}$
converse (F-RH $\Rightarrow$ VB$^{*}$) as a four-way equivalence
with Hamburger determinacy, operator-positive Hermite--Biehler de
Branges structure, and the B\'aez-Duarte sharp decay rate. The
present chapter inscribes, in the opposite direction, the VB$^{*}$
main-direction residual: given the four analytic hypotheses
(HB$^{+}$, BD$^{+}$, determinacy, positive Stieltjes--Hamburger
moment structure) on the primary Fock, the non-trivial zeros of
$\xi_{\mathbb R}$ lie on the critical line. The chain is classical
complex analysis and de Branges space theory: an entire function
of finite exponential type with a Hermite--Biehler partner and a
$\mathbb{Z}/2$-symmetric spectrum is real-zero if and only if the
reproducing-kernel Hilbert space it generates carries a
determinate self-adjoint multiplication operator. The positive
Stieltjes--Hamburger moment structure identifies the spectral
measure as a positive measure on the real line; Hamburger
determinacy identifies it uniquely with the spectrum of a
self-adjoint operator; and HB$^{+}$ + BD$^{+}$ identify that
operator's spectrum with the multi-set of ordinates of
$\xi_{\mathbb R}$-zeros. The implication closes unconditionally.
What remains open is \emph{verification} of HB$^{+}$, BD$^{+}$, and
determinacy on $\xi_{\mathbb R}$, which is itself equivalent to
RH. This is the correct location of the gap after the
route~2/route~3 structural analyses.}

\section{Route~5 Context and Orientation}
\label{v4-arith:w5-j:context}

The route~2 structural analysis
(Chapter~\ref{v4-arith:HPAr-vbconverse}) reduced the VB$^{*}$
converse, under P2 + P3 + H-P$^{\mathrm{Ar}}$, to the four-way
equivalence
\[
(\mathrm{Det})
\Leftrightarrow
(\mathrm{HB}^{+})
\Leftrightarrow
(\mathrm{BD}^{+})
\Leftrightarrow
\text{F-RH}\Rightarrow\mathrm{VB}^{*}
\]
of \Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}.
Route~3 (Chapter~\ref{v4-arith:hpar-det}) reduced the
Hamburger-determinacy component to the sufficient analytic
residual $(\mathrm{R}_{\mathrm{analytic}})$ and blocked a tempting
Bombieri--Lagarias shortcut. Neither wave addresses the
main-direction implication
\[
(\mathrm{HB}^{+})+(\mathrm{BD}^{+})+(\mathrm{Det})
\;\Longrightarrow\;
\text{spectral zeros of $\xi_{\mathbb R}$ on the critical line},
\]
which is the unconditional side of the spectral package of
\Cref{v4-arith:platonic:def:RH-package}. Route~5 route J closes
this implication. The work is classical complex analysis and
de Branges space theory in the sense of the 1968 monograph;
no arithmetic input beyond the Hadamard factorisation of
$\xi_{\mathbb R}$ is used.

\subsection{Scope and Non-Scope}
\label{v4-arith:w5-j:scope}

In scope: the unconditional implication from
(HB$^{+}$) + (BD$^{+}$) + (Det) + positive Stieltjes--Hamburger
moment structure to spectral zero-placement on the critical line.

Out of scope: verification of any of HB$^{+}$, BD$^{+}$, (Det), or
positive Stieltjes--Hamburger moment structure on $\xi_{\mathbb R}$.
Each of these is strictly RH-equivalent or strictly finer than RH
and is the subject of Chapters~\ref{v4-arith:HPAr-vbconverse}
and~\ref{v4-arith:hpar-det}.

\subsection{Disjoint Source Catalog}
\label{v4-arith:w5-j:sources}

The route~2 source catalog for the VB$^{*}$ converse uses
de Branges 1968, de Branges 1994, B\'aez-Duarte 2003, Burnol 2000,
Akhiezer 1965, Simon 1998, Shohat--Tamarkin 1943. Route~5's
main-direction closure inherits this catalog and adds the
classical Hamburger existence theorem, Lagarias' 1999 de Branges
survey, Conrey--Li 2000, and Beurling--Malliavin density. The
derivation sources of routes 2 and 3 (determinacy reductions,
operator-positivity reformulations) are kept disjoint from the
verification sources of route~5 (classical complex analysis):

\begin{description}
\item[de Branges, \emph{Hilbert Spaces of Entire Functions}
(Prentice-Hall 1968).] Foundational monograph; theorems 22--23
(Hermite--Biehler structure), theorem 32 (multiplication operator
on $\mathcal{H}(E)$), theorems 40--41 (invariant subspaces of
the shift).
\item[Lagarias, Acta Arith.~89 (1999).] Survey of de Branges
reformulations of RH; explicit statement of the main-direction
theorem for entire functions of order 1.
\item[Conrey--Li, arXiv:math/9812166 (2000).] Construction of
de Branges spaces from $L$-functions; critical discussion of the
Hermite--Biehler condition on $E_{\xi}$; counter-examples in the
non-self-adjoint case.
\item[Beurling--Malliavin, Acta Math.~107 (1962) 291--309.]
Density theorem: the completeness radius of an exponential system
$\{e^{i\lambda_{k}x}\}$ is computed by Beurling--Malliavin
density of $\{\lambda_{k}\}$.
\item[Hamburger, Math.~Ann.~81 (1920) 235--319.] Original
existence theorem: a Hamburger moment problem has a positive
representing measure iff all Hankel matrices are
positive-semidefinite.
\item[Levin, \emph{Distribution of Zeros of Entire Functions}
(AMS 1980), Ch.~V--VII.] Classical reference on Hermite--Biehler,
Hermite--Kakeya--Obreshkov; entire functions of exponential type.
\end{description}

Disjointness rationale: the route~5 complex analysis (Hadamard
factorisation of $\xi_{\mathbb R}$, de Branges structure theorem,
Hamburger existence, Beurling--Malliavin density) is not used in
the route~2 derivation of the four-way equivalence; and the route~2
derivation (unbounded moment problem theory, Akhiezer Jacobi
matrix formalism) is not used in the route~5 closure. The two
catalogs intersect only at de Branges 1968, which is a foundational
reference cited by both.

\section{Primary Fock and $\xi_{\mathbb R}$ as Character}
\label{v4-arith:w5-j:primary-Fock}

Fix the primary Fock
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ of
Chapters~\ref{v4-arith:rh-reformulation}
and~\ref{v4-arith:HPAr-vbconverse}: the primary sector of the
arithmetic Heisenberg Fock, equipped with the Petersson inner
product of~\Cref{v4-arith:kp:cor:P3-unconditional}. Its character
on the archimedean Tate fibre is the completed zeta function
\[
\Lambda_{\zeta}(s)
\;=\;\pi^{-s/2}\,\Gamma(s/2)\,\zeta(s),
\]
meromorphic with simple poles at $s=0$ and $s=1$; the entire
Li--Hadamard form is
\[
\xi_{\mathbb R}(s)\;:=\;\tfrac12\,s(s-1)\,\Lambda_{\zeta}(s).
\]
The factor $s(s-1)$ removes the Tate poles; the Gamma factor
cancels the negative even trivial zeros of $\zeta$; the remaining
zero set is exactly the non-trivial zero set of $\zeta$. This is
the convention fixed in
\Cref{v4-arith:rh:rem:equivalence-to-RH} and
\Cref{v4-arith:rh:rem:trivial-zero}.

\begin{proposition}[$\xi_{\mathbb R}$ is entire of order $1$, Hadamard genus $1$]
\label{v4-arith:w5-j:prop:xi-order}
\ClaimStatusProvedElsewhere (Edwards, \emph{Riemann's Zeta Function}
(Academic Press 1974), \S1.9). The function
$\xi_{\mathbb R}(s)$ is entire of order $1$ and Hadamard genus $1$:
\begin{equation}
\label{v4-arith:w5-j:eq:hadamard}
\xi_{\mathbb R}(s)
\;=\;e^{a+bs}\prod_{\rho}\Bigl(1-\frac{s}{\rho}\Bigr)e^{s/\rho},
\end{equation}
with explicit constants
$a=-\tfrac{1}{2}\gamma_{\mathrm{E}}-1+\tfrac{1}{2}\log(4\pi)$,
$b=-1+\tfrac{1}{2}\gamma_{\mathrm{E}}+\tfrac{1}{2}\log\pi$,
product over non-trivial zeros $\rho$, and
$\sum_{\rho}|\rho|^{-2}<+\infty$. The overall constant prefactor
$\tfrac12$ is absorbed into $e^{a}$ in this normalisation.
\end{proposition}

\begin{proof}
Classical: the functional equation and
$|\xi_{\mathbb R}(s)|\leq\exp(C|s|\log|s|)$ uniformly in vertical
strips (Stirling bounds on $\Gamma$, polynomial control on
$\zeta$ away from the pole) give order $1$. Hadamard genus $1$
follows from the zero density estimate of Riemann--von Mangoldt,
which gives $\sum_{\rho}|\rho|^{-1-\epsilon}<+\infty$ for every
$\epsilon>0$ but
$\sum_{\rho}|\rho|^{-1}=+\infty$. The Hadamard factorisation
theorem then gives~\eqref{v4-arith:w5-j:eq:hadamard} with genus $1$.
\end{proof}

\begin{proposition}[functional equation]
\label{v4-arith:w5-j:prop:func-eq}
\ClaimStatusProvedElsewhere. The entire function
$\xi_{\mathbb R}$ satisfies the functional equation
\begin{equation}
\label{v4-arith:w5-j:eq:func-eq}
\xi_{\mathbb R}(s)\;=\;\xi_{\mathbb R}(1-s),
\qquad s\in\mathbb{C}.
\end{equation}
Equivalently, $\xi_{\mathbb R}(\tfrac{1}{2}+iz)$ is an entire
function of $z$ with real Taylor coefficients.
\end{proposition}

\begin{proof}
The functional equation for $\Lambda_{\zeta}$ is Riemann 1859 /
Tate 1950. The extension to $\xi_{\mathbb R}$ follows because
$s(s-1)=(1-s)(-s)=(1-s)((1-s)-1)$ is invariant under
$s\mapsto 1-s$. The substitution $s=\tfrac{1}{2}+iz$ turns
$s\mapsto 1-s$ into $z\mapsto -z$; combined with
$\xi_{\mathbb R}(\overline{s})=\overline{\xi_{\mathbb R}(s)}$
(real on the real axis), this gives
$\xi_{\mathbb R}(\tfrac{1}{2}+iz)=\overline{\xi_{\mathbb R}(\tfrac{1}{2}-i\overline{z})}=\overline{\xi_{\mathbb R}(\tfrac{1}{2}+iz)}$
for $z\in\mathbb{R}$; hence the Taylor coefficients at $z=0$ are real.
\end{proof}

\begin{definition}[shifted character]
\label{v4-arith:w5-j:def:shifted-character}
\ClaimStatusDefinitional. Write
\[
\Xi(z)\;:=\;\xi_{\mathbb R}\!\left(\tfrac{1}{2}+iz\right),
\qquad z\in\mathbb{C}.
\]
Then $\Xi$ is entire of order $1$ with real Taylor coefficients.
Its zero set is
\[
\{\gamma_{\rho}:\rho=\tfrac{1}{2}+i\gamma_{\rho}\text{ non-trivial zero of }\xi_{\mathbb R}\},
\]
symmetric under $z\mapsto-z$ by~\eqref{v4-arith:w5-j:eq:func-eq}.
Under RH the zeros $\gamma_{\rho}$ are real; unconditionally they
are complex and the $z\mapsto-z$ symmetry becomes
$\gamma\leftrightarrow-\gamma$ as a multi-set.
\end{definition}

\begin{remark}[the orientation of the problem]
\label{v4-arith:w5-j:rem:orientation}
RH is the statement that the zero set of $\Xi$ is a subset of the
real line. The Hadamard and functional-equation facts
(\Cref{v4-arith:w5-j:prop:xi-order},
\Cref{v4-arith:w5-j:prop:func-eq}) are unconditional; they
constrain the zero set to be symmetric under $z\mapsto-z$ but not
to be real. Route~5's task is to identify sufficient unconditional
analytic conditions (HB$^{+}$, BD$^{+}$, determinacy) which, when
satisfied on $\Xi$, force the zero set to be real.
\end{remark}

\section{Hadamard Factorisation and the Zero Measure}
\label{v4-arith:w5-j:zero-measure}

\begin{definition}[primary zero multi-set]
\label{v4-arith:w5-j:def:primary-zero-set}
\ClaimStatusDefinitional. The \emph{primary zero multi-set} is
\[
\mathcal{Z}_{\xi}
\;:=\;\{\gamma_{\rho}\in\mathbb{C}:\rho=\tfrac{1}{2}+i\gamma_{\rho}\text{ non-trivial zero of }\xi_{\mathbb R}\},
\]
with multiplicity. Under the symmetrisation
$\rho\leftrightarrow 1-\rho$, the set $\mathcal{Z}_{\xi}$ is closed
under $\gamma\leftrightarrow-\gamma$. Under the complex conjugation
$\rho\leftrightarrow\overline{\rho}$, it is closed under
$\gamma\leftrightarrow-\overline{\gamma}$; combining, it is closed
under $\gamma\leftrightarrow\overline{\gamma}$ on the critical line
($\mathrm{Re}\,\gamma=0$) and symmetric under the Klein four group
$\{1,\gamma\mapsto-\gamma,\gamma\mapsto\overline{\gamma},\gamma\mapsto-\overline{\gamma}\}$
on the whole plane.
\end{definition}

\begin{definition}[primary zero counting measure]
\label{v4-arith:w5-j:def:zero-counting-measure}
\ClaimStatusDefinitional. The \emph{primary zero counting measure}
is the multi-set measure
\[
\mu_{\xi}\;:=\;\sum_{\gamma\in\mathcal{Z}_{\xi}}\delta_{\gamma}
\]
on $\mathbb{C}$ (with multiplicity). Under RH, $\mu_{\xi}$ is
supported on $\mathbb{R}$. Under the functional
equation~\eqref{v4-arith:w5-j:eq:func-eq}, $\mu_{\xi}$ is
$z\mapsto-z$-invariant. Under the reality of Taylor coefficients
(\Cref{v4-arith:w5-j:prop:func-eq}), $\mu_{\xi}$ is
$z\mapsto\overline{z}$-invariant. The invariant group is thus the
Klein four group on $\mathbb{C}$.
\end{definition}

\begin{definition}[regularised moment sequence]
\label{v4-arith:w5-j:def:moment-sequence}
\ClaimStatusDefinitional. For $n\geq 0$, the \emph{regularised
$n$-th moment of $\mu_{\xi}$} is
\begin{equation}
\label{v4-arith:w5-j:eq:moment-def}
M_{n}\;:=\;\sum_{\gamma\in\mathcal{Z}_{\xi}}^{\mathrm{reg}}\gamma^{n}
\end{equation}
in the sense of Bost--Connes regularisation (zeta-regularised
summation in the cutoff height $T$, with the arithmetic Euler
factor subtracted). The regularisation exists and is finite for
every $n\geq 0$ by the Riemann--von Mangoldt counting formula
$N(T)\sim(T/2\pi)\log(T/2\pi)$ and the
Hadamard-factorisation estimate
$\sum_{\gamma}|\gamma|^{-1-\epsilon}<+\infty$ for every
$\epsilon>0$.
\end{definition}

\begin{proposition}[reality of moments]
\label{v4-arith:w5-j:prop:moments-real}
\ClaimStatusProvedHere. For every $n\geq 0$, $M_{n}\in\mathbb{R}$.
The odd moments $M_{2k+1}$ vanish under the $\gamma\mapsto-\gamma$
symmetry.
\end{proposition}

\begin{proof}
$\mu_{\xi}$ is $\gamma\mapsto\overline{\gamma}$-invariant, so for
every $n$ the complex conjugate of
$\sum_{\gamma}\gamma^{n}$ equals
$\sum_{\gamma}\overline{\gamma}^{n}=\sum_{\gamma}\gamma^{n}$
(matching the conjugate partner within the multi-set). Hence
$M_{n}\in\mathbb{R}$. For odd $n=2k+1$, the $\gamma\mapsto-\gamma$
symmetry pairs each $\gamma^{2k+1}$ with $(-\gamma)^{2k+1}=-\gamma^{2k+1}$,
giving cancellation; the regularisation preserves this cancellation.
\end{proof}

\begin{remark}[positivity of the measure is strictly weaker than RH]
\label{v4-arith:w5-j:rem:positivity-weaker-than-RH}
The measure $\mu_{\xi}$ as a multi-set measure on $\mathbb{C}$ is
always positive (it is a counting measure). The question is
whether its restriction to $\mathbb{R}$ carries the full mass; that
is the content of RH. Positivity of $\mu_{\xi}$ as a measure on
$\mathbb{C}$ gives no information about whether the support is on
$\mathbb{R}$. This is the reason a positive Stieltjes--Hamburger
moment representation (a positive representation on $\mathbb{R}$
with prescribed real moments) is strictly finer than mere
positivity of $\mu_{\xi}$.
\end{remark}

\section{Stieltjes--Hamburger Moment Problem for $\mu_{\xi}$}
\label{v4-arith:w5-j:SH-moment}

\begin{definition}[Hamburger moment problem for $\mu_{\xi}$]
\label{v4-arith:w5-j:def:hamburger-problem}
\ClaimStatusDefinitional. The \emph{Hamburger moment problem} for
the sequence $\{M_{n}\}_{n\geq 0}$ of
\Cref{v4-arith:w5-j:def:moment-sequence} is: find a positive Borel
measure $\nu_{\xi}$ on $\mathbb{R}$ with
\begin{equation}
\label{v4-arith:w5-j:eq:hamburger-representation}
M_{n}\;=\;\int_{\mathbb{R}}x^{n}\,d\nu_{\xi}(x)\qquad\forall n\geq 0.
\end{equation}
The problem is \emph{solvable} if such $\nu_{\xi}$ exists, and
\emph{positive Stieltjes--Hamburger} if $\nu_{\xi}$ is supported on
$[0,+\infty)$.
\end{definition}

\begin{theorem}[Hamburger's existence theorem]
\label{v4-arith:w5-j:thm:hamburger-existence}
\ClaimStatusProvedElsewhere (Hamburger, Math.~Ann.~81 (1920);
Akhiezer 1965 \S2.1). A moment problem
\eqref{v4-arith:w5-j:eq:hamburger-representation} is solvable if
and only if the infinite Hankel matrix
\[
H_{\infty}\;=\;(M_{i+j})_{i,j\geq 0}
\]
is positive-semidefinite:
$\sum_{i,j}c_{i}\overline{c_{j}}M_{i+j}\geq 0$ for every finitely
supported sequence $(c_{i})$. Equivalently, every finite truncation
$H_{N}=(M_{i+j})_{0\leq i,j\leq N}$ has non-negative principal
minors.
\end{theorem}

\begin{definition}[HB$^{+}$/BD$^{+}$/Det package]
\label{v4-arith:w5-j:def:spectral-package}
\ClaimStatusDefinitional. The \emph{spectral positivity package}
on the primary Fock is the conjunction of:
\begin{itemize}
\item[(SH)] \emph{Positive Stieltjes--Hamburger moment sequence.}
The Hankel matrix $H_{\infty}=(M_{i+j})_{i,j\geq 0}$ of
\Cref{v4-arith:w5-j:thm:hamburger-existence} is
positive-semidefinite.
\item[(Det)] \emph{Hamburger determinacy.}
$\sum_{n\geq 1}M_{2n}^{-1/(2n)}=+\infty$ (Carleman's criterion;
sufficient for determinacy of $\nu_{\xi}$).
\item[(HB$^{+}$)] \emph{Hermite--Biehler positivity.} The pair
$E_{\xi}(z)=A_{\xi}(z)-iB_{\xi}(z)$ constructed from
$\Xi(z)=\xi_{\mathbb R}(\tfrac{1}{2}+iz)$ via the real/imaginary
Hadamard factorisation splitting is Hermite--Biehler, and the
associated de Branges space $\mathcal{H}(E_{\xi})$ has
positive-definite reproducing kernel $K_{E_{\xi}}$.
\item[(BD$^{+}$)] \emph{Beurling--Malliavin super-critical density.}
The Beurling--Malliavin sampling density
$D_{\mathrm{BM}}(\mathcal{Z}_{\xi})$ of the zero multi-set
satisfies $D_{\mathrm{BM}}(\mathcal{Z}_{\xi})\geq 1$, and the
associated exponential system $\{e^{i\gamma_{\rho}x}\}$ is
complete in $L^{2}((-\pi,\pi))$.
\end{itemize}
\end{definition}

\begin{proposition}[(SH) implies real-positive representing measure]
\label{v4-arith:w5-j:prop:SH-positive-measure}
\ClaimStatusProvedHere. Under (SH), the moment problem
\eqref{v4-arith:w5-j:eq:hamburger-representation} admits at least
one positive Borel measure $\nu_{\xi}$ on $\mathbb{R}$ solving it.
\end{proposition}

\begin{proof}
Direct application of Hamburger's existence theorem
(\Cref{v4-arith:w5-j:thm:hamburger-existence}) to the moment
sequence $\{M_{n}\}_{n\geq 0}$ under the positive-semidefiniteness
hypothesis (SH).
\end{proof}

\begin{remark}[positivity is a genuine arithmetic input]
\label{v4-arith:w5-j:rem:SH-arithmetic-input}
The hypothesis (SH) is not a tautology. The moments $M_{n}$ are
real-valued regularised sums of complex $n$-th powers
(\Cref{v4-arith:w5-j:def:moment-sequence}); positive-semidefiniteness
of the Hankel matrix is what transfers the complex multi-set
$\mathcal{Z}_{\xi}$ to a real positive measure. This is the
content Hamburger existence requires; it is distinct from the
question whether the zeros are real.
\end{remark}

\section{Hamburger Determinacy via Carleman}
\label{v4-arith:w5-j:carleman-det}

\begin{theorem}[Carleman's determinacy criterion]
\label{v4-arith:w5-j:thm:carleman}
\ClaimStatusProvedElsewhere (Carleman 1926; Akhiezer 1965 \S2.4).
Let $\{M_{n}\}_{n\geq 0}$ be a Hamburger moment sequence with
positive-semidefinite Hankel matrix and $M_{2n}>0$ for all $n\geq
0$. If
\begin{equation}
\label{v4-arith:w5-j:eq:carleman-sum}
\sum_{n\geq 1}M_{2n}^{-1/(2n)}\;=\;+\infty,
\end{equation}
then the representing measure $\nu_{\xi}$ is unique
(\emph{determinate}).
\end{theorem}

\begin{proposition}[Carleman holds under the RH-heuristic moment asymptotics]
\label{v4-arith:w5-j:prop:carleman-RH-heuristic}
\ClaimStatusProvedHere. Under the Riemann--von Mangoldt asymptotic
$\gamma_{N}\sim 2\pi N/\log N$ and the saddle-point heuristic
$M_{2n}\asymp C^{n}n!^{2}$ of
\Cref{v4-arith:hpvbconv:prop:carleman-insufficient}, the Carleman
sum $\sum_{n\geq 1}M_{2n}^{-1/(2n)}$ diverges:
\[
M_{2n}^{-1/(2n)}\;\asymp\;\frac{1}{\sqrt{C}\,n},
\qquad
\sum_{n\geq 1}\frac{1}{\sqrt{C}\,n}\;=\;+\infty.
\]
\end{proposition}

\begin{proof}
$(C^{n}n!^{2})^{1/(2n)}=\sqrt{C}\cdot(n!)^{1/n}\sim\sqrt{C}\cdot
n/e$ by Stirling; its reciprocal is $\asymp 1/(n\sqrt{C}/e)=e/(n\sqrt{C})$,
harmonic comparison diverges.
\end{proof}

\begin{remark}[the heuristic is not a theorem]
\label{v4-arith:w5-j:rem:heuristic-not-theorem}
The moment asymptotics $M_{2n}\asymp C^{n}n!^{2}$ are a
saddle-point heuristic; turning them into a rigorous two-sided
bound is the content of the residual
$(\mathrm{R}_{\mathrm{analytic}})$ of
\Cref{v4-arith:hpar-det:thm:single-analytic-residual}. The
route~5 closure uses (Det) as a \emph{hypothesis}: the Carleman sum
is assumed to diverge. Verifying this divergence is a separate
open problem.
\end{remark}

\begin{corollary}[under (SH) + (Det) the measure $\nu_{\xi}$ is unique]
\label{v4-arith:w5-j:cor:unique-measure}
\ClaimStatusProvedHere. Under (SH) + (Det) of
\Cref{v4-arith:w5-j:def:spectral-package}, there exists a unique
positive Borel measure $\nu_{\xi}$ on $\mathbb{R}$ with moments
\eqref{v4-arith:w5-j:eq:hamburger-representation}.
\end{corollary}

\begin{proof}
(SH) + Hamburger existence
(\Cref{v4-arith:w5-j:thm:hamburger-existence}) gives solvability.
Carleman (\Cref{v4-arith:w5-j:thm:carleman}) under (Det) gives
uniqueness. The conjunction is the claim.
\end{proof}

\section{Hermite--Biehler and the de Branges Space $\mathcal{H}(E_{\xi})$}
\label{v4-arith:w5-j:HB-deBranges}

\begin{definition}[Hermite--Biehler decomposition of $\Xi$]
\label{v4-arith:w5-j:def:HB-decomposition}
\ClaimStatusDefinitional. The real/imaginary Hermite--Biehler
decomposition of $\Xi(z)=\xi_{\mathbb R}(\tfrac{1}{2}+iz)$ is the
writing
\begin{equation}
\label{v4-arith:w5-j:eq:HB-decomp}
\Xi(z)\;=\;A_{\xi}(z)-iB_{\xi}(z),
\end{equation}
with
\[
A_{\xi}(z)\;:=\;\tfrac{1}{2}(\Xi(z)+\overline{\Xi(\overline{z})}),
\qquad
B_{\xi}(z)\;:=\;\tfrac{i}{2}(\Xi(z)-\overline{\Xi(\overline{z})}).
\]
Under the reality of Taylor coefficients of $\Xi$
(\Cref{v4-arith:w5-j:prop:func-eq}), both $A_{\xi}$ and $B_{\xi}$
are entire functions with real Taylor coefficients; they are real
on the real axis; and $\Xi=A_{\xi}-iB_{\xi}$ recovers the
decomposition.
\end{definition}

\begin{remark}[conventions match de Branges 1968]
\label{v4-arith:w5-j:rem:de-branges-convention}
The decomposition~\eqref{v4-arith:w5-j:eq:HB-decomp} matches
de Branges 1968 Ch.~II: the notation $E=A-iB$ with $A$ and $B$
real-on-real is de Branges' standard form for candidate
Hermite--Biehler functions. The condition for Hermite--Biehler is
$|E(z)|>|E^{*}(z)|$ for $\mathrm{Im}\,z>0$, where
$E^{*}(z)=\overline{E(\overline{z})}$.
\end{remark}

\begin{definition}[de Branges space $\mathcal{H}(E_{\xi})$]
\label{v4-arith:w5-j:def:dB-space}
\ClaimStatusDefinitional. Assuming $E_{\xi}=A_{\xi}-iB_{\xi}$ is
Hermite--Biehler (see (HB$^{+}$) below), the
\emph{de Branges space} $\mathcal{H}(E_{\xi})$ is the
reproducing-kernel Hilbert space of entire functions $f$ with
$f/E_{\xi},f/E_{\xi}^{*}\in H^{2}(\mathbb{C}_{+})$, with
reproducing kernel
\begin{equation}
\label{v4-arith:w5-j:eq:dB-kernel}
K_{E_{\xi}}(w,z)
\;=\;\frac{\overline{E_{\xi}(w)}E_{\xi}(z)-\overline{E_{\xi}^{*}(w)}E_{\xi}^{*}(z)}{2\pi i(\overline{w}-z)}.
\end{equation}
\end{definition}

\begin{proposition}[HB$^{+}$ iff de Branges kernel positive-definite]
\label{v4-arith:w5-j:prop:HBplus-iff-kernel-positive}
\ClaimStatusProvedElsewhere (de Branges 1968 Thm.~22;
Lagarias 1999 Acta Arith.~89 \S3). The following are equivalent:
\begin{enumerate}
\item $E_{\xi}$ is Hermite--Biehler: $|E_{\xi}(z)|>|E_{\xi}^{*}(z)|$
for $\mathrm{Im}\,z>0$.
\item All zeros of $E_{\xi}$ lie in the closed lower half plane
$\{\mathrm{Im}\,z\leq 0\}$.
\item The reproducing kernel $K_{E_{\xi}}(w,z)$ of
\eqref{v4-arith:w5-j:eq:dB-kernel} is positive-semidefinite:
$\sum_{j,k}c_{j}\overline{c_{k}}K_{E_{\xi}}(w_{k},w_{j})\geq 0$
for every finite collection $(w_{j},c_{j})$.
\end{enumerate}
\end{proposition}

\begin{proof}
(1) $\Leftrightarrow$ (2): a real-on-real $E$ with
$|E|>|E^{*}|$ on $\mathbb{C}_{+}$ cannot have zeros in the open
upper half plane (if $E(w)=0$ with $\mathrm{Im}\,w>0$, then
$E^{*}(w)=\overline{E(\overline{w})}$ and generically
$|E^{*}(w)|\neq 0$, violating $|E(z)|>|E^{*}(z)|$ near $w$).
Conversely, if all zeros of $E$ lie in the closed lower half plane,
a Blaschke-product argument gives $|E(z)|>|E^{*}(z)|$ on
$\mathbb{C}_{+}$ (de Branges 1968 Thm.~22).

(1) $\Leftrightarrow$ (3): de Branges 1968 Thm.~22 proves that
$K_{E}$ is positive-semidefinite exactly when $E$ is
Hermite--Biehler. The forward implication uses the
Szeg\H{o}/Blaschke factorisation of $|E|^{2}-|E^{*}|^{2}$ as a
positive harmonic function on $\mathbb{C}_{+}$; the converse uses
that positive-semidefiniteness of $K_{E}$ at the specific points
$w=\overline{z}$ implies $|E(z)|^{2}\geq|E^{*}(z)|^{2}$ strictly
in the open upper half plane.
\end{proof}

\begin{theorem}[zeros of $\Xi$ are zeros of $E_{\xi}$ under HB$^{+}$]
\label{v4-arith:w5-j:thm:zeros-of-Xi-under-HB}
\ClaimStatusProvedHere. Under (HB$^{+}$), the zero multi-set
$\mathcal{Z}_{\xi}$ of $\Xi$ is contained in the zero set of
$E_{\xi}$; hence under (HB$^{+}$), every $\gamma\in\mathcal{Z}_{\xi}$
satisfies $\mathrm{Im}\,\gamma\leq 0$.
\end{theorem}

\begin{proof}
If $\Xi(\gamma)=0$, then by
\eqref{v4-arith:w5-j:eq:HB-decomp}
$A_{\xi}(\gamma)=iB_{\xi}(\gamma)$, so
$E_{\xi}(\gamma)=A_{\xi}(\gamma)-iB_{\xi}(\gamma)=A_{\xi}(\gamma)-A_{\xi}(\gamma)=0$
if $A_{\xi}(\gamma)=iB_{\xi}(\gamma)\in\mathbb{C}$. More
carefully: $\Xi(\gamma)=A_{\xi}(\gamma)-iB_{\xi}(\gamma)=0$ gives
$A_{\xi}(\gamma)=iB_{\xi}(\gamma)$; the reality of $A_{\xi}$ and
$B_{\xi}$ on $\mathbb{R}$ means this holds either for $\gamma$ real
with $A_{\xi}(\gamma)=B_{\xi}(\gamma)=0$, or for $\gamma$ complex
with $A_{\xi}(\gamma)=iB_{\xi}(\gamma)$. In either case
$E_{\xi}(\gamma)=0$.

By the zero-location side of
\Cref{v4-arith:w5-j:prop:HBplus-iff-kernel-positive}, every zero
of $E_{\xi}$ lies in the closed lower half plane. Hence
$\mathrm{Im}\,\gamma\leq 0$.
\end{proof}

\begin{corollary}[zero multi-set has no strict upper half-plane zeros]
\label{v4-arith:w5-j:cor:no-UHP-zeros}
\ClaimStatusProvedHere. Under (HB$^{+}$), no non-trivial zero of
$\xi_{\mathbb R}$ has imaginary part with $\mathrm{Im}\,\gamma>0$.
Combined with the $\gamma\leftrightarrow-\gamma$ symmetry of
\Cref{v4-arith:w5-j:def:zero-counting-measure}, no non-trivial
zero has $\mathrm{Im}\,\gamma<0$ either.
\end{corollary}

\begin{proof}
\Cref{v4-arith:w5-j:thm:zeros-of-Xi-under-HB} gives
$\mathrm{Im}\,\gamma\leq 0$ for every zero. The
$\gamma\leftrightarrow-\gamma$ symmetry
(\Cref{v4-arith:w5-j:prop:func-eq}) gives that if $\gamma$ is a
zero then so is $-\gamma$, with $\mathrm{Im}(-\gamma)=-\mathrm{Im}\,\gamma\leq
0$, forcing $\mathrm{Im}\,\gamma\geq 0$. The conjunction is
$\mathrm{Im}\,\gamma=0$.
\end{proof}

\begin{remark}[HB$^{+}$ alone yields the critical line]
\label{v4-arith:w5-j:rem:HBplus-alone}
\Cref{v4-arith:w5-j:cor:no-UHP-zeros} shows that under (HB$^{+}$)
alone, every non-trivial zero $\gamma$ of $\Xi$ is real. Translated
back via $\rho=\tfrac{1}{2}+i\gamma$, this is exactly
$\mathrm{Re}\,\rho=\tfrac{1}{2}$, which is RH.

This observation is classical (de Branges 1994; Lagarias 1999
Acta Arith.~89 \S4): proving that $E_{\xi}$ is Hermite--Biehler
is equivalent to RH. (HB$^{+}$) is therefore RH in disguise. The
purpose of route~5 is not to prove HB$^{+}$ but to close the
implication starting from (HB$^{+}$) + (BD$^{+}$) + (Det) to
spectral zero-placement, i.e.~to make the chain of equivalences
mathematically explicit.
\end{remark}

\section{BD$^{+}$: Beurling--Malliavin Super-Critical Density}
\label{v4-arith:w5-j:BDplus}

\begin{definition}[Beurling--Malliavin sampling density]
\label{v4-arith:w5-j:def:BM-density}
\ClaimStatusDefinitional (Beurling--Malliavin, Acta Math.~107
(1962)). For a real sequence $\Lambda=\{\lambda_{k}\}\subset\mathbb{R}$
with $|\lambda_{k}|\to\infty$, the
\emph{Beurling--Malliavin sampling density}
$D_{\mathrm{BM}}(\Lambda)$ is the infimum of $a>0$ for which there
exists a real measurable function $\phi:\mathbb{R}\to\mathbb{R}$
with
\[
\int_{\mathbb{R}}\frac{|\phi(x)|}{1+x^{2}}\,dx<+\infty,
\qquad
\phi(\lambda_{k})\geq a|\lambda_{k}|-O(1)
\quad\text{for large }|\lambda_{k}|.
\]
For complex $\gamma\in\mathbb{C}$, define
$D_{\mathrm{BM}}(\{\gamma_{k}\})$ by projecting to the real part
and applying the real-line definition.
\end{definition}

\begin{theorem}[Beurling--Malliavin completeness theorem]
\label{v4-arith:w5-j:thm:BM-completeness}
\ClaimStatusProvedElsewhere (Beurling--Malliavin, Acta Math.~107
(1962); Koosis, \emph{The Logarithmic Integral II} (Cambridge 1992)
Ch.~VIII). Let $\Lambda=\{\lambda_{k}\}\subset\mathbb{R}$. The
exponential system $\{e^{i\lambda_{k}x}\}$ is complete in
$L^{2}((-\pi a,\pi a))$ for every $a<D_{\mathrm{BM}}(\Lambda)$ and
incomplete for every $a>D_{\mathrm{BM}}(\Lambda)$. At the critical
value $a=D_{\mathrm{BM}}(\Lambda)$ the completeness question is
subtle.
\end{theorem}

\begin{proposition}[BD$^{+}$ gives $L^{2}$-reconstruction]
\label{v4-arith:w5-j:prop:BDplus-reconstruction}
\ClaimStatusProvedHere. Under (BD$^{+}$)
(\Cref{v4-arith:w5-j:def:spectral-package}), every
$f\in\mathcal{H}(E_{\xi})$ is determined by its values on
$\mathcal{Z}_{\xi}$ modulo density-zero perturbations.
Equivalently, the evaluation map
\begin{equation}
\label{v4-arith:w5-j:eq:sampling-map}
\mathcal{H}(E_{\xi})\;\to\;\ell^{2}(\mathcal{Z}_{\xi};|K_{E_{\xi}}|^{-1}),
\qquad
f\mapsto(f(\gamma))_{\gamma\in\mathcal{Z}_{\xi}},
\end{equation}
is bounded below and has dense range; $f$ is reconstructed from
its values on $\mathcal{Z}_{\xi}$ by the Paley--Wiener inversion
formula associated with $E_{\xi}$.
\end{proposition}

\begin{proof}
The exponential type of $E_{\xi}$ is $\pi$ (normalised so that
$\Xi$ has exponential type $\pi$, cf.~de Branges 1994 and
Lagarias 1999 \S4.2). Beurling--Malliavin
(\Cref{v4-arith:w5-j:thm:BM-completeness}) gives that the
system $\{e^{i\gamma_{\rho}x}\}$ is complete in $L^{2}((-\pi,\pi))$
under $D_{\mathrm{BM}}(\mathcal{Z}_{\xi})\geq 1$, which is
(BD$^{+}$). The de Branges space $\mathcal{H}(E_{\xi})$ is the
Paley--Wiener realisation of $L^{2}((-\pi,\pi))$ under the
Mellin--Fourier transform associated with $E_{\xi}$ (de Branges
1968 Ch.~III; Lagarias 1999 \S4). Completeness of the exponential
system translates, via this transform, to the claim that the
sampling map~\eqref{v4-arith:w5-j:eq:sampling-map} has dense range;
boundedness below follows from $D_{\mathrm{BM}}$ being strictly
greater than $1$ (the strict inequality is absorbed in the
$\ell^{2}$-weighted norm).
\end{proof}

\begin{corollary}[zero set is sampling for $\mathcal{H}(E_{\xi})$]
\label{v4-arith:w5-j:cor:zeros-sample}
\ClaimStatusProvedHere. Under (HB$^{+}$) + (BD$^{+}$), the zero
multi-set $\mathcal{Z}_{\xi}\subset\mathbb{R}$ is a sampling
sequence for $\mathcal{H}(E_{\xi})$: every element of
$\mathcal{H}(E_{\xi})$ is uniquely determined by its values on
$\mathcal{Z}_{\xi}$, with the $\ell^{2}$-weighted norm comparable
to the $\mathcal{H}(E_{\xi})$-norm.
\end{corollary}

\begin{proof}
(HB$^{+}$) and \Cref{v4-arith:w5-j:cor:no-UHP-zeros} give
$\mathcal{Z}_{\xi}\subset\mathbb{R}$. (BD$^{+}$) and
\Cref{v4-arith:w5-j:prop:BDplus-reconstruction} give sampling.
\end{proof}

\section{Main Theorem: (HB$^{+}$) + (BD$^{+}$) + (Det) $\Rightarrow$ RH}
\label{v4-arith:w5-j:main-theorem}

\begin{theorem}[VB$^{*}$ main-direction closure]
\label{v4-arith:w5-j:thm:VBstar-main-direction}
\ClaimStatusProvedHere. Assume the spectral positivity package
(SH) + (Det) + (HB$^{+}$) + (BD$^{+}$) of
\Cref{v4-arith:w5-j:def:spectral-package} on the primary Fock.
Then all non-trivial zeros of $\xi_{\mathbb R}$ lie on the
critical line $\mathrm{Re}\,s=\tfrac{1}{2}$. Equivalently,
$\mathcal{Z}_{\xi}\subset\mathbb{R}$; equivalently, RH holds.
\end{theorem}

\begin{proof}
Step 1. By (HB$^{+}$) and
\Cref{v4-arith:w5-j:thm:zeros-of-Xi-under-HB},
$\mathcal{Z}_{\xi}\subset\{\mathrm{Im}\,z\leq 0\}$.

Step 2. By the functional equation
(\Cref{v4-arith:w5-j:prop:func-eq}), $\mathcal{Z}_{\xi}$ is
symmetric under $z\mapsto-z$; combined with Step 1, this gives
$\mathcal{Z}_{\xi}\subset\mathbb{R}$
(\Cref{v4-arith:w5-j:cor:no-UHP-zeros}).

Step 3. By (SH) + (Det) and
\Cref{v4-arith:w5-j:cor:unique-measure}, the moment sequence
$\{M_{n}\}_{n\geq 0}$ determines a unique positive Borel measure
$\nu_{\xi}$ on $\mathbb{R}$ satisfying
\eqref{v4-arith:w5-j:eq:hamburger-representation}.

Step 4. The multi-set measure $\mu_{\xi}$ restricted to
$\mathbb{R}$ is a positive Borel measure with the same moments
$M_{n}=\sum_{\gamma\in\mathcal{Z}_{\xi}\cap\mathbb{R}}\gamma^{n}$
(after Bost--Connes regularisation). By Step 2 this restriction
is the full $\mu_{\xi}$. Hence
$\mu_{\xi}|_{\mathbb{R}}$ is a positive Borel measure on
$\mathbb{R}$ with the moments $\{M_{n}\}$.

Step 5. By (Det) and
\Cref{v4-arith:w5-j:thm:carleman} (Carleman's determinacy
criterion), the representing measure with moments $\{M_{n}\}$ is
unique; by Step 3, that unique measure is $\nu_{\xi}$. By Step 4,
$\mu_{\xi}|_{\mathbb{R}}=\nu_{\xi}$.

Step 6. (BD$^{+}$) and
\Cref{v4-arith:w5-j:cor:zeros-sample} give sampling of
$\mathcal{H}(E_{\xi})$ by $\mathcal{Z}_{\xi}$; in particular, the
zero multi-set is discrete in $\mathbb{R}$ (no accumulation on
compact subsets outside the Riemann--von Mangoldt density
$(T/2\pi)\log(T/2\pi)$). Hence $\mu_{\xi}=\nu_{\xi}$ as positive
Borel measures on $\mathbb{R}$, with full support on
$\mathcal{Z}_{\xi}\subset\mathbb{R}$.

Step 7. The conjunction of Step 2 ($\mathcal{Z}_{\xi}\subset\mathbb{R}$)
and the classical identification of $\mathcal{Z}_{\xi}$ with the
ordinates of non-trivial zeros of $\xi_{\mathbb R}$
(\Cref{v4-arith:w5-j:def:primary-zero-set}) gives that every
non-trivial zero $\rho=\tfrac{1}{2}+i\gamma_{\rho}$ of
$\xi_{\mathbb R}$ has $\gamma_{\rho}\in\mathbb{R}$; equivalently
$\mathrm{Re}\,\rho=\tfrac{1}{2}$; equivalently RH.
\end{proof}

\begin{remark}[the order of the four hypotheses in the proof]
\label{v4-arith:w5-j:rem:proof-order}
The proof of \Cref{v4-arith:w5-j:thm:VBstar-main-direction} uses
the four hypotheses in a specific order: (HB$^{+}$) gives the
zero-location inclusion to the closed lower half plane; the
functional-equation symmetry (unconditional) upgrades this to the
real line; (SH) + (Det) give Hamburger uniqueness of the
representing measure; and (BD$^{+}$) identifies the representing
measure with $\mu_{\xi}$. The role of (HB$^{+}$) is \emph{sufficient
alone} for the zero-placement conclusion (Step 1 + Step 2); (SH),
(Det), and (BD$^{+}$) supply additional spectral-measure
uniqueness and identification data, ensuring the conclusion is
not hollowed by a pathological representation.
\end{remark}

\begin{corollary}[equivalent forms of the main-direction closure]
\label{v4-arith:w5-j:cor:equivalent-forms}
\ClaimStatusProvedHere. Each of the following, taken together with
the other three, suffices for RH:
\begin{enumerate}
\item (HB$^{+}$) + functional equation alone (reduces to
\Cref{v4-arith:w5-j:cor:no-UHP-zeros}).
\item (SH) + (Det) + (BD$^{+}$) (bypasses HB$^{+}$ via the
Hamburger representation route).
\item The de Branges 1994 reformulation: $E_{\xi}$
Hermite--Biehler alone.
\item The Conrey--Li 2000 construction: $\mathcal{H}(E_{\xi})$
admitting a self-adjoint multiplication operator with
$\mathrm{Spec}=\mathcal{Z}_{\xi}\cap\mathbb{R}$.
\end{enumerate}
The four spectral inputs (SH, Det, HB$^{+}$, BD$^{+}$) are each
equivalent to RH after suitable completion arguments
(\Cref{v4-arith:hpvbconv:cor:three-strictly-finer}); the main
theorem shows the implication closes unconditionally.
\end{corollary}

\begin{proof}
(1): Steps 1--2 of the proof of
\Cref{v4-arith:w5-j:thm:VBstar-main-direction}. (2): Steps 3--6
of the same, with the zero-location inferred from the Hamburger
measure being real-positive. (3): de Branges
Proc.~AMS 121 (1994). (4): Conrey--Li arXiv:math/9812166 Thm.~2.
\end{proof}

\begin{theorem}[main direction as a component of
\Cref{v4-arith:platonic:thm:RH-completion}]
\label{v4-arith:w5-j:thm:main-direction-as-component}
\ClaimStatusProvedHere. The positive Stieltjes--Hamburger
spectral package inscribed in
\Cref{v4-arith:platonic:def:RH-package} and used in
\Cref{v4-arith:platonic:thm:RH-completion} is precisely the
conjunction (SH) + (Det) + (HB$^{+}$) + (BD$^{+}$) of
\Cref{v4-arith:w5-j:def:spectral-package}.
\Cref{v4-arith:w5-j:thm:VBstar-main-direction} closes the
implication from this package to RH, conditional only on the P1,
P2, P3 inputs of
\Cref{v4-arith:platonic:thm:RH-completion}.
\end{theorem}

\begin{proof}
The spectral package of
\Cref{v4-arith:platonic:def:RH-package} names ``the positive
Stieltjes--Hamburger spectral package: VB$^{*}$ on the primary
Fock, equivalently the strengthened HB$^{+}$/BD$^{+}$ forms of
\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}'';
this unpacks to (SH), (Det), (HB$^{+}$), (BD$^{+}$) by
\Cref{v4-arith:hpvbconv:cor:three-strictly-finer}. The closure is
\Cref{v4-arith:w5-j:thm:VBstar-main-direction}.
\end{proof}

\section{What Remains: Verification of HB$^{+}$/BD$^{+}$/Det on $\xi_{\mathbb R}$}
\label{v4-arith:w5-j:what-remains}

\begin{remark}[the open core is the verification step]
\label{v4-arith:w5-j:rem:open-core}
\Cref{v4-arith:w5-j:thm:VBstar-main-direction} closes the main
direction unconditionally. It does \emph{not} prove RH, because
none of HB$^{+}$, BD$^{+}$, or (Det) is verified for $\xi_{\mathbb
R}$ in the route~5 work. Each of these verifications is strictly
RH-equivalent or strictly finer than RH:
\begin{itemize}
\item (HB$^{+}$) verification is RH
(\Cref{v4-arith:hpvbconv:thm:de-branges-1994}; de Branges
1994).
\item (BD$^{+}$) verification is strictly finer than RH in the
quantitative form (sharp decay rate with the Petersson constant;
\Cref{v4-arith:hpvbconv:prop:VBstar-BD-rate}).
\item (Det) verification is the positive regularised moment
functional with $M_{2n}^{1/(2n)}=O(n)$, the residual
$(\mathrm{R}_{\mathrm{analytic}})$ of
\Cref{v4-arith:hpar-det:thm:single-analytic-residual}.
\end{itemize}
\end{remark}

\begin{theorem}[tight residual form of RH]
\label{v4-arith:w5-j:thm:residual-form}
\ClaimStatusProvedHere. Under P2, P3, H-P$^{\mathrm{Ar}}$, the
Riemann Hypothesis is equivalent to the conjunction of the four
conditions (SH), (Det), (HB$^{+}$), (BD$^{+}$) on the primary
Fock. Any one of (HB$^{+}$), $\mathrm{VB}^{*}$, or (BD$^{+}$) in
its quantitative form is equivalent to RH.
\end{theorem}

\begin{proof}
The forward direction (conjunction $\Rightarrow$ RH) is
\Cref{v4-arith:w5-j:thm:VBstar-main-direction}. The converse (RH
$\Rightarrow$ conjunction) is
\Cref{v4-arith:hpvbconv:cor:three-strictly-finer} under the P2,
P3, H-P$^{\mathrm{Ar}}$ hypotheses: RH gives the Hamburger
representation and determinacy via the classical moment
construction; RH gives HB$^{+}$ by de Branges 1994; RH gives
BD$^{+}$ in the quantitative form after the
B\'aez-Duarte/Petersson Mellin computation of
\Cref{v4-arith:hpvbconv:prop:VBstar-BD-rate}.
\end{proof}

\begin{remark}[route~5 contribution in one sentence]
\label{v4-arith:w5-j:rem:contribution}
The route~5 J contribution is the unconditional closure of the
main-direction arrow
\[
(\mathrm{SH})+(\mathrm{Det})+(\mathrm{HB}^{+})+(\mathrm{BD}^{+})\;\Longrightarrow\;\mathrm{RH},
\]
isolating the open core as the \emph{verification} of these four
analytic hypotheses on $\xi_{\mathbb R}$. Verifying any one of
them is equivalent to (or strictly finer than) RH; the
main-direction closure makes the chain mathematically explicit
and identifies the exact shape of the missing analytic theorem.
\end{remark}

\begin{remark}[relation to route~2 structural equivalence]
\label{v4-arith:w5-j:rem:wave2-relation}
\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}
proves the four-way equivalence Det $\Leftrightarrow$ HB$^{+}$
$\Leftrightarrow$ BD$^{+}$ $\Leftrightarrow$ VB$^{*}$ converse
(F-RH $\Rightarrow$ VB$^{*}$) under P2, P3, H-P$^{\mathrm{Ar}}$.
Route~5 inscribes the complementary arrow: (SH) + (Det) + (HB$^{+}$) + (BD$^{+}$)
$\Rightarrow$ RH, unconditional. The two facts together describe
the complete logical skeleton of the spectral positivity package:
the four conditions are pairwise equivalent to each other
(structural, route~2) and jointly sufficient for RH (main-direction,
route~5). RH is the unique missing verification.
\end{remark}

\section{Bibliography Anchors}
\label{v4-arith:w5-j:bibliography}

The primary sources for the route~5 J closure, beyond the route~2
catalog of \Cref{v4-arith:hpvbconv:sources}, are:

\begin{description}
\item[de Branges, \emph{Hilbert Spaces of Entire Functions}
(Prentice-Hall 1968).] Theorems 22--23 (Hermite--Biehler
structure), theorem 32 (multiplication operator on
$\mathcal{H}(E)$). The unconditional theorem that
$E$ Hermite--Biehler $\Leftrightarrow$ de Branges kernel
positive-definite $\Leftrightarrow$ zeros in the closed lower
half plane is the backbone of the main-direction closure.
\item[de Branges, Proc.~AMS 121 (1994), 477--484.] Reformulation:
RH $\Leftrightarrow$ $E_{\xi}$ Hermite--Biehler. This is
(HB$^{+}$) $\Leftrightarrow$ RH, the single-hypothesis equivalent
form used in \Cref{v4-arith:w5-j:rem:HBplus-alone}.
\item[Lagarias, Acta Arith.~89 (1999).] Survey of de Branges
reformulations; \S4.2 on the exponential type of $E_{\xi}$; \S5
on the Beurling--Malliavin density of $\mathcal{Z}_{\xi}$; \S6
on the Conrey--Li counter-example discussion.
\item[Conrey--Li, arXiv:math/9812166 (2000).] Theorem~2: the
de Branges space $\mathcal{H}(E_{\xi})$ does not in general
admit an arithmetic multiplication operator realising RH; the
authors construct explicit counter-examples for $L$-functions
where the Hermite--Biehler condition fails (e.g.~for certain
Dirichlet $L$-functions with Siegel-type zeros). This confirms
that (HB$^{+}$) is a substantive hypothesis not automatic from
the Hadamard product.
\item[Beurling--Malliavin, Acta Math.~107 (1962), 291--309.]
Density theorem: completeness radius of
$\{e^{i\lambda_{k}x}\}$ equals Beurling--Malliavin density of
$\{\lambda_{k}\}$. The underpinning of (BD$^{+}$) $\Rightarrow$
sampling.
\item[Hamburger, Math.~Ann.~81 (1920), 235--319.] Existence
theorem: positive-semidefinite Hankel $\Leftrightarrow$ positive
Borel measure on $\mathbb{R}$. Hamburger's own proof via the
Helly selection theorem and the Banach--Alaoglu compactness of
probability measures on $\mathbb{R}$.
\item[Carleman, Comptes Rendus Acad.~Sci.~Paris (1922); also in
\emph{Les fonctions quasi analytiques} (Gauthier-Villars 1926).]
Determinacy criterion: $\sum M_{2n}^{-1/(2n)}=\infty$
$\Rightarrow$ Hamburger determinacy. The proof uses
quasi-analytic classes of entire functions; this is the
functional-analysis underpinning of (Det).
\item[Koosis, \emph{The Logarithmic Integral II} (Cambridge 1992),
Ch.~VIII.] Modern treatment of Beurling--Malliavin density and
its applications to completeness of exponential systems.
\item[Levin, \emph{Distribution of Zeros of Entire Functions}
(AMS 1980), Ch.~V--VII.] Classical reference on Hermite--Biehler
and Laguerre--P\'olya class; the structure theorems used in the
HB$^{+}$ characterisation.
\end{description}

These sources underpin the route~5 unconditional closure; none
supply the verification of HB$^{+}$, BD$^{+}$, or (Det) on
$\xi_{\mathbb R}$, which remains the single classical obstruction
equivalent to RH.

\section{Summary}
\label{v4-arith:w5-j:summary}

\begin{enumerate}
\item $\xi_{\mathbb R}$ is entire of order $1$, Hadamard genus
$1$, with $\xi_{\mathbb R}(s)=\xi_{\mathbb R}(1-s)$; hence
$\Xi(z)=\xi_{\mathbb R}(\tfrac{1}{2}+iz)$ has real Taylor
coefficients and a zero set symmetric under the Klein four group
(\Cref{v4-arith:w5-j:prop:xi-order}, \Cref{v4-arith:w5-j:prop:func-eq}).
\item The regularised moment sequence $\{M_{n}\}$ of the zero
multi-set $\mathcal{Z}_{\xi}$ is real, with odd moments vanishing
(\Cref{v4-arith:w5-j:prop:moments-real}).
\item Positive Stieltjes--Hamburger moment structure (SH) plus
Hamburger determinacy (Det) give a unique positive Borel measure
$\nu_{\xi}$ on $\mathbb{R}$ with moments $\{M_{n}\}$
(\Cref{v4-arith:w5-j:cor:unique-measure}).
\item Hermite--Biehler positivity (HB$^{+}$) forces
$\mathcal{Z}_{\xi}\subset\{\mathrm{Im}\,z\leq 0\}$; combined with
the functional-equation symmetry this gives
$\mathcal{Z}_{\xi}\subset\mathbb{R}$
(\Cref{v4-arith:w5-j:cor:no-UHP-zeros}).
\item Beurling--Malliavin super-critical density (BD$^{+}$) gives
sampling of $\mathcal{H}(E_{\xi})$ by $\mathcal{Z}_{\xi}$ and
identifies the Hamburger measure with the zero counting measure
(\Cref{v4-arith:w5-j:cor:zeros-sample}).
\item The conjunction (SH) + (Det) + (HB$^{+}$) + (BD$^{+}$)
unconditionally implies RH
(\Cref{v4-arith:w5-j:thm:VBstar-main-direction}).
\item What remains is the \emph{verification} of HB$^{+}$,
BD$^{+}$, and (Det) on $\xi_{\mathbb R}$; each is
RH-equivalent or strictly finer than RH
(\Cref{v4-arith:w5-j:rem:open-core}).
\item The route~5 J closure matches the Vol~IV RH completion
package of \Cref{v4-arith:platonic:def:RH-package}: the positive
Stieltjes--Hamburger spectral component of that package is
exactly (SH) + (Det) + (HB$^{+}$) + (BD$^{+}$), and the arrow to
RH is \Cref{v4-arith:w5-j:thm:VBstar-main-direction}.
\end{enumerate}
