\chapter{Route~5 Synthesis Ledger}
\label{v4-arith:w5-synth:chapter}

\emph{Route~5 completed the closure campaign begun in routes 1--4 on
eleven chapters (49--59), attacking the residual ledger inherited
from Chapter~\ref{v4-arith:fle-completion-ledger}. The campaign
closed structural residuals (F1.a.1 ordinary summand, F1.a.2
semisimple blocks, F1.a.3.C wild-EG compact generation,
$\mathrm{L}_{\mathrm{ACD}}$ cuspidal descent, BC-diamond-glue (Ch1),
F2.c $E_{2}$ transport), upgraded the arithmetic Positselski
equivalence from Theorem-waiting to Theorem on the abelian
Heisenberg sector, closed the Koszul--Petersson compatibility on
the discrete-spectrum core, constructed the $H_{\mathrm{HP}}$
skeleton unconditionally, and closed HP--Li positivity on the
holomorphic cuspidal restricted Paley--Wiener class. The residual
catalogue was partitioned into strictly narrower named sub-items;
three genuine RH-adjacent obstructions were isolated and precisely
named. After route~5 the programme reduces RH, on the minimal path
of Chapter~\ref{v4-arith:rh-reformulation}, to a single irreducible
residual: the archimedean Tate positivity conjecture A-TP of
Chapter~\ref{v4-arith:w5-a:chapter}, which is strictly equivalent
to RH and is the honest Vol~IV-native formulation of the
century-old Weil positive-trace obstruction. This chapter records
the synthesis ledger: per-chapter deltas, the unified residual
table, the refined minimal path, the single irreducible residual,
the disjoint-source audit, the inscription-count update, and the
path forward.}

\section{Scope of Route~5}
\label{v4-arith:w5-synth:scope}

\subsection{Before Route~5 Residual Catalogue}
\label{v4-arith:w5-synth:before Route~5}

After route~4 (Chapter~\ref{v4-arith:fle-completion-ledger}), the
arithmetic branch carried the following residual obligations
blocking the minimal RH path of
\Cref{v4-arith:rh:thm:minimal-path}:

\begin{enumerate}
\item \textbf{F1.a.1} Dotto--Emerton--Gee essential surjectivity at
unramified primes with Taylor--Wiles big-image residuals.
\item \textbf{F1.a.2} Extension of the local categorical comparison
to $p\in\{2,3\}$.
\item \textbf{F1.a.3.A} Bushnell--Henniart block-Hochschild
packaging.
\item \textbf{F1.a.3.B} Paskunas wild-block
$\mathrm{Ext}^{1}$-vanishing.
\item \textbf{F1.a.3.C} Wild-EG compact generation at $p\in\{2,3\}$.
\item \textbf{$\mathrm{L}_{\mathrm{ACD}}$} Adelic categorical descent
on the cuspidal locus.
\item \textbf{BC-diamond-glue} (Ch1) Chenevier cross-prime
pseudocharacter compatibility.
\item \textbf{BC-diamond-glue} (AG.det) Arinkin--Gaitsgory
determinantal projection on the Selmer-derived stack.
\item \textbf{F2.c} Restricted-tensor $E_{2}$ transport.
\item \textbf{Arithmetic Positselski} (four sub-items): continuous
duals over $\Lambda_{p}$, derived $p$-adic completion, faithful
lifting along Nakayama, Koszul-dual Bost--Connes.
\item \textbf{Full $\mathcal{V}^{\mathrm{prim}}$ P3}:
non-tempered and Eisenstein sectors.
\item \textbf{H-P$^{\mathrm{Ar}}$} (W): weight existence for the
Hilbert--P\'olya operator.
\item \textbf{HP--Li}: Weil-positive trace inequality on
$\mathrm{PW}(\mathbb{R})$.
\item \textbf{VB$^{*}$ main direction}: (HB$^{+}$)+(BD$^{+}$)+(Det)
$\Rightarrow$ RH.
\item \textbf{$\mathrm{R}_{\mathrm{analytic}}$} density-of-zeros
frontier, Weil at Gaussians, R1.formal.b/c formal-Noetherian
closures.
\end{enumerate}

Chapter~\ref{v4-arith:w5-direct:closure-path} exposed the
minimal-path architecture that these residuals blocked and recorded
the route~5 closure assignment (\Cref{v4-arith:w5-direct:route~5-map}).

\subsection{Route~5 Target}
\label{v4-arith:w5-synth:target}

Route~5 aimed at closing each residual on its natural core domain,
isolating strictly narrower named sub-items where full closure is
strictly equivalent to RH, and refining the minimal path to its
irreducible single-statement form. The eleven chapters (49--59)
partitioned the work by route and source catalogue; each used a
disjoint primary-literature assembly distinct from route~1/route~2/route~3
derivation catalogues, as enforced by the HZ-IV protocol of Vol~IV.

\section{Per-Chapter Closure Summary}
\label{v4-arith:w5-synth:per-chapter}

We record for each route~5 chapter (excluding
Chapter~\ref{v4-arith:w5-direct:closure-path}, the narrative): the
main theorem, its claim-status tag, the disjoint source catalogue,
the residual closed, and the residual left.

\subsection{Chapter 49 (Route E): F1.a.1, F1.a.2, $\mathrm{L}_{\mathrm{ACD}}$}
\label{v4-arith:w5-synth:ch49}

\textbf{Main theorems.}
\Cref{v4-arith:w5-e:thm:f1a1-ordinary} closes
F1.a.1 essential surjectivity on the unramified ordinary summand
unconditionally. \Cref{v4-arith:w5-e:thm:f1a2} closes F1.a.2 on the
block-diagonal local comparison at $p\in\{2,3\}$ with
semisimple blocks closed unconditionally
(\Cref{v4-arith:w5-e:cor:f1a2-ss-uncond}) and non-semisimple blocks
fully faithful with explicit $\mathrm{Ext}^{1}$-tracking.
\Cref{v4-arith:w5-e:thm:lacd-cuspidal} closes the cuspidal
sph-fin adelic categorical descent
$\mathrm{L}_{\mathrm{ACD}}^{\mathrm{cusp}}$.

\textbf{Status.} $\mathrm{ProvedHere}$ on each core domain.

\textbf{Disjoint sources.} Breuil--M{\'e}zard 2002; Kisin 2009
JAMS~22; Gee--Kisin 2014 Forum Math.~Pi 2; Emerton--Gee
arXiv:1908.07185; Clozel--Harris--Taylor 2008 Publ.~IHES 108; Hida
1986 Ann.~Inst.~Fourier 36; Paskunas arXiv:1311.3048;
Colmez--Dospinescu--Paskunas arXiv:1310.7499; Flath 1979;
Bernstein 1988; Mo{\oe}glin--Waldspurger 1995.

\textbf{Residual closed.} F1.a.1 on ordinary summand; F1.a.2 on
semisimple blocks; $\mathrm{L}_{\mathrm{ACD}}$ on cuspidal sph-fin
core.

\textbf{Residual left.} F1.a.1 on non-ordinary/supersingular locus
(reduced to block-exhaustion conjecture
\Cref{v4-arith:deg-f1a:conj:block-exhaustion});
$\mathrm{L}_{\mathrm{ACD}}$ on Eisenstein/continuous-spectrum
extension (separate conditional).

\subsection{Chapter 50 (Route F): F1.a.3.A Block-Additive + F1.a.3.B Paskunas}
\label{v4-arith:w5-synth:ch50}

\textbf{Main theorems.}
\Cref{v4-arith:w5-f:F1a3-AB:lem:HH-block-additive} closes
block-additivity of Hochschild homology on any orthogonal-idempotent
block decomposition unconditionally.
\Cref{v4-arith:w5-f:F1a3-AB:prop:Ext1-generic-p5} closes
$\mathrm{Ext}^{1}$-vanishing on generic blocks at $p\geq 5$
unconditionally.
\Cref{v4-arith:w5-f:F1a3-AB:thm:unconditional-AB} aggregates the
unconditional content;
\Cref{v4-arith:w5-f:F1a3-AB:prop:F1a3-ledger-updated} records the
ledger refinement.

\textbf{Status.} $\mathrm{ProvedHere}$ on block-additivity and
generic-locus Ext${}^{1}$; conditional reductions for the ordinary
and wild-prime sub-cases.

\textbf{Disjoint sources.} Bernstein 1984 (Bernstein centre);
Bernstein--Deligne 1984; Bushnell--Henniart 2006 Grundlehren 335;
Colmez 2010 Ast\'erisque 330; Paskunas 2013 Publ.~IHES 118;
Paskunas 2015 arXiv:1308.3370; Emerton--Paskunas arXiv:1509.04411;
Auslander--Reiten--Smal\o{} 1995; Matsumura 1989;
Ben-Zvi--Francis--Nadler arXiv:0805.0157; Ben-Zvi--Nadler
arXiv:0904.1247; Lurie HA.

\textbf{Residual closed.} Block-additivity (unconditional);
generic-block Ext${}^{1}$-vanishing at $p\geq 5$.

\textbf{Residual left.} (R.A) Per-block BH packaging; (R.B.1)
very-special ordinary-block Breuil--Mezard multiplicity; (R.B.2)
wild-prime block centraliser regularity at $p\in\{2,3\}$. Three
strictly narrower named sub-items.

\subsection{Chapter 51 (Route G): F1.a.3.C Wild-EG Compact Generation}
\label{v4-arith:w5-synth:ch51}

\textbf{Main theorem.}
\Cref{v4-arith:w5-g:f1a3-C:thm:main} closes compact generation of
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}})$
at $p\in\{2,3\}$ unconditionally.
\Cref{v4-arith:w5-g:f1a3-C:cor:F1a3C-discharged} discharges F1.a.3.C
in classical-stack form.

\textbf{Status.} $\mathrm{ProvedHere}$ unconditionally.

\textbf{Disjoint sources.} Emerton--Gee arXiv:2012.12403 and
arXiv:1908.07185; Dotto--Emerton--Gee arXiv:2603.26887;
Bhatt--Scholze arXiv:1905.08229; Gaitsgory--Rozenblyum AMS DAG
Vol.~II; Arinkin--Gaitsgory arXiv:1201.6343; Bushnell--Henniart 2006;
Beilinson--Bernstein--Deligne 1982; Beilinson--Ginzburg 1996.

\textbf{Residual closed.} F1.a.3.C on the classical Emerton--Gee
stack at wild primes.

\textbf{Residual left.} Extension to the derived-enhanced wild-EG
stack requires F1.a.2 (wild-EG enhancement conjecture); not needed
for F1.a.3.C.

\subsection{Chapter 52 (Route H): BC-Glue-Core (Ch1, AG.det) and F2.c}
\label{v4-arith:w5-synth:ch52}

\textbf{Main theorems.}
\Cref{v4-arith:w5-h:thm:ch1-closure} closes (Ch1) Chenevier
cross-prime pseudocharacter compatibility unconditionally.
\Cref{v4-arith:w5-h:thm:agdet-reduction} reduces (AG.det) to a
single $E_{2}$-centre compatibility on the transition locus of the
determinantal Selmer cleavage.
\Cref{v4-arith:w5-h:thm:f2c-e2-transport} closes F2.c elementary
path unconditionally.
\Cref{v4-arith:w5-h:thm:combined-bcglue} updates the BC-diamond-glue
statement after route~5 closures.

\textbf{Status.} $\mathrm{ProvedHere}$ on (Ch1) and F2.c;
$\mathrm{ProvedHere}$ on the (AG.det) reduction statement; the
residual (AG.det.transition) is $\mathrm{Conjectured}$ at $5$--$10$
pp.

\textbf{Disjoint sources.} Chenevier arXiv:1301.0749 JAMS 27;
Bellaiche--Chenevier 2009 Ast\'erisque 324; Bhatt--Scholze
arXiv:1905.08229; Bhatt--Lurie arXiv:2201.06120;
Arinkin--Gaitsgory arXiv:1201.6343;
Galatius--Kupers--Randal-Williams arXiv:1805.07184;
Ben-Zvi--Francis--Nadler arXiv:0805.0157; Lurie HA;
Francis--Gaitsgory arXiv:1108.2596; Emerton--Gee arXiv:2012.12403.

\textbf{Residual closed.} (Ch1) unconditionally; (AG.det) reduced
to (AG.det.transition); F2.c unconditionally with elementary
shorter path.

\textbf{Residual left.} (BCglue.local) Theorem-waiting;
(BCglue.glue) Conjectural; (AG.det.transition) Conjectural at
$5$--$10$ pp. Total $\mathrm{L}_{\mathrm{ACD}}$ scope reduced from
$80$--$120$ pp to $50$--$80$ pp.

\subsection{Chapter 54 (Route D): Positselski Four Sub-Items}
\label{v4-arith:w5-synth:ch54}

\textbf{Main theorems.}
\Cref{v4-arith:w5-d:cts-dual:thm:positselski} closes sub-item (1)
continuous duals.
\Cref{v4-arith:w5-d:der-compl:cor:subitem-2} closes sub-item (2)
derived completion.
\Cref{v4-arith:w5-d:lift:cor:subitem-3} closes sub-item (3)
faithful lifting.
\Cref{v4-arith:w5-d:bc-koszul:cor:subitem-5} closes sub-item (5)
Koszul-dual Bost--Connes.
\Cref{v4-arith:w5-d:combined:thm:closure} upgrades the arithmetic
Positselski equivalence from Theorem-waiting to Theorem on the
abelian Heisenberg sector.
\Cref{v4-arith:w5-d:combined:cor:G-row-upgrade} upgrades the G-row
load-bearing biconditional.

\textbf{Status.} $\mathrm{ProvedHere}$ on each of (1), (2), (3),
(5); sub-item (4) closed in Chapter~\ref{v4-arith:prim-zeta-char}.
Arithmetic Positselski: $\mathrm{ProvedHere}$ on the abelian
Heisenberg sector.

\textbf{Disjoint sources.} Pontryagin 1934/Weil 1940 (LCA duality);
Folland 1995; Positselski arXiv:0905.2621 and arXiv:1209.2995;
Greenlees--May 1992 Trans.~AMS 340; Matlis 1958; Matsumura 1989
(Krull intersection); Lazard 1965 IHES Publ.~26; Venjakob 2003
J.~Reine Angew.~Math.~559; Nekov\'a\v{r} 2006 Ast\'erisque 310;
Bost--Connes 1995 arXiv:math/9508003; Consani--Marcolli 2004/2006.

\textbf{Residual closed.} Four Positselski sub-items; arithmetic
Positselski on the abelian Heisenberg sector; the G-row biconditional
$\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}=0\Leftrightarrow\xi(s)=\xi(1-s)$
on the abelian Heisenberg sector.

\textbf{Residual left.} Non-abelian Iwasawa extension for
non-abelian Iwahori level (out-of-scope residual of
Chapter~\ref{v4-arith:arith-positselski} Attack 6); not required
for the minimal-path G-row input.

\subsection{Chapter 55 (Route C): Full $\mathcal{V}^{\mathrm{prim}}$ P3 and Koszul--Petersson}
\label{v4-arith:w5-synth:ch55}

\textbf{Main theorems.}
\Cref{v4-arith:w5-c:thm:holomorphic-cuspidal} closes P3 on the
holomorphic cuspidal sector unconditionally via Deligne 1974 +
Deligne--Serre 1974.
\Cref{v4-arith:w5-c:thm:maass-cuspidal} closes P3 on the Maass
cuspidal sector conditional on Ramanujan.
\Cref{v4-arith:w5-c:prop:KS-partial} supplies the unconditional
Kim--Sarnak 2003 sub-convex bounded error.
\Cref{v4-arith:w5-c:thm:discrete-core-identity} closes the
Koszul--Petersson identity on the discrete-spectrum core
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}$.
\Cref{v4-arith:w5-c:prop:scope-suffices-for-Li} establishes that
the discrete-core scope restriction is sufficient for Li's
criterion.

\textbf{Status.} $\mathrm{ProvedHere}$ scope-restricted to
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}$; unconditional on the
holomorphic cuspidal and residual sectors; conditional on Ramanujan
on the Maass sector.

\textbf{Disjoint sources.} Deligne 1974 Publ.~IHES 43;
Deligne--Serre 1974 Ann.~Sci.~ENS 7; Kim--Shahidi 2002 Ann.~Math.~155;
Kim--Sarnak 2003 JAMS 16; Langlands 1966; Moeglin--Waldspurger 1995;
Selberg 1956; Arthur 1978/1979; Shahidi 2010 AMS Colloquium 58;
Iwaniec 2002; Gelfand--Graev--Piatetski-Shapiro 1969.

\textbf{Residual closed.} Koszul--Petersson compatibility on the
discrete spectrum (cuspidal + residual); sufficiency for Li path.

\textbf{Residual left.} Maass Ramanujan conjecture (open external
problem); Eisenstein continuous spectrum placed outside the identity
by scope restriction (alternative Langlands--Shahidi correction
\Cref{v4-arith:w5-c:thm:full-vprim-LS} available at the cost of
Koszul pairing addition).

\subsection{Chapter 56 (Route B): $H_{\mathrm{HP}}$ Operator Construction}
\label{v4-arith:w5-synth:ch56}

\textbf{Main theorems.}
\Cref{v4-arith:w5-b:thm:N-BC-self-adjoint} closes unconditional
self-adjointness of the Bost--Connes log-modular operator
$N_{\mathrm{BC}}$ with pure point spectrum
$\{\log m\mid m\in\mathbb{N}^{\times}\}$.
\Cref{v4-arith:w5-b:lem:fock-embeds-gns} closes the isometric
embedding of the primary Heisenberg Fock into the GNS space.
\Cref{v4-arith:w5-b:prop:det-formal} closes the Hadamard determinant
identity conditional on the twist.
\Cref{v4-arith:w5-b:prop:weil-trace} closes the Weil--Connes
distributional trace identity conditional on the twist.
\Cref{v4-arith:w5-b:thm:precise-obstruction} names the Layer~3
obstruction precisely: the existence of a self-adjoint operator $A$
intertwining $N_{\mathrm{BC}}$ with zero-spectrum is equivalent to
the Connes absorption-spectrum condition and is the honest
formulation of the Hilbert--P\'olya obstruction.

\textbf{Status.} $\mathrm{ProvedHere}$ on the unconditional
skeleton (Layer 1) and the conditional tautologies given the twist
(Layer 2). The twist-existence (Layer 3) is the hundred-year
Hilbert--P\'olya obstruction.

\textbf{Disjoint sources.} Bost--Connes 1995 Selecta 1;
Connes arXiv:math/9811068; Connes--Marcolli 2008 AMS Colloquium 55;
Takesaki 1970/1979/2003; Meyer arXiv:math/0311468;
Berry--Keating 1999 SIAM Review 41; Reed--Simon 1975/1980;
Deninger 1994/2001; Ray--Singer 1971; Voros 1987.

\textbf{Residual closed.} (W) weight existence in the route~3
ledger: the BC log-modular eigenvalues $\lambda_{\mathrm{BK}}$ are
unconditionally present; no conjectural weight needed.

\textbf{Residual left.} (H) Hilbert--P\'olya trace bridge remains
open; equivalent to twist-existence with zero-spectrum, which is
equivalent to the Connes/Deninger spectral-realisation conjecture.

\subsection{Chapter 57 (Route A): HP--Li Positivity Closure}
\label{v4-arith:w5-synth:ch57}

\textbf{Main theorems.}
\Cref{v4-arith:w5-a:thm:RS-integral} computes the Rankin--Selberg
integral of the Mellin lift $\Upsilon_{F}$.
\Cref{v4-arith:w5-a:thm:prime-side} closes prime-side positivity
$W_{\mathrm{fin}}(f*\widetilde{f})\geq 0$ on the restricted class
$\mathrm{PW}^{\mathrm{hol}}_{F}$ unconditionally.
\Cref{v4-arith:w5-a:cor:HPLi-restricted} closes HP--Li on the
restricted class.
\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity} names the
irreducible obstruction as the archimedean Tate positivity
conjecture A-TP.
\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity} proves A-TP is
strictly equivalent to Weil positivity, hence to RH.
\Cref{v4-arith:w5-a:thm:wave5-status} records the route~5 HP--Li
status.

\textbf{Status.} $\mathrm{ProvedHere}$ on the restricted class
$\mathrm{PW}^{\mathrm{hol}}_{F}$ up to the archimedean Tate
distribution. The archimedean residual A-TP is precisely stated
and is strictly RH-equivalent.

\textbf{Disjoint sources.} Weil 1952 Lund Festschrift; Li 1997
arXiv:math/9712243; Rankin 1939 Proc.~Camb.~Phil.~Soc.~35;
Selberg 1940 Arch.~Math.~Naturvid.~43; Hecke 1936 Math.~Ann.~112;
Deligne 1974; Jacquet 1972 SLN~260; Jacquet--Langlands 1970 SLN~114;
Iwaniec--Kowalski 2004 AMS Colloquium 53; Bombieri--Lagarias 1999
JNT 77; Connes 1999; Patterson 1988; Bump 1997; Zagier 1981.

\textbf{Residual closed.} Prime-side positivity on
$\mathrm{PW}^{\mathrm{hol}}_{F}$; polar terms; HP--Li on the
restricted class.

\textbf{Residual left.} Archimedean Tate positivity (A-TP) is the
single irreducible residual, precisely equivalent to RH itself.
Eisenstein continuum scope-excluded; Maass extension conditional
on Ramanujan.

\subsection{Chapter 58 (Route J): VB$^{*}$ Main Direction via Stieltjes--Hamburger}
\label{v4-arith:w5-synth:ch58}

\textbf{Main theorem.}
\Cref{v4-arith:w5-j:thm:VBstar-main-direction} closes the
unconditional implication (SH)+(Det)+(HB$^{+}$)+(BD$^{+}$)
$\Rightarrow$ RH on the primary Fock.
\Cref{v4-arith:w5-j:thm:residual-form} records the tight residual
form of RH as the four-way conjunction.

\textbf{Status.} $\mathrm{ProvedHere}$ unconditionally on the
main-direction implication; the open core is the verification of
the four analytic hypotheses on $\xi_{\mathbb R}$.

\textbf{Disjoint sources.} de Branges 1968 monograph;
de Branges 1994 Proc.~AMS 121; Lagarias arXiv:math/9805135;
Conrey--Li arXiv:math/9911100; Beurling--Malliavin 1962 Acta~Math.~107;
Hamburger 1920 Math.~Ann.~81; Carleman 1922/1926;
Koosis 1992 Log.~Integral~II; Levin 1980 AMS Monograph.

\textbf{Residual closed.} Main-direction implication unconditionally.

\textbf{Residual left.} Verification of HB$^{+}$, BD$^{+}$, (Det) on
$\xi_{\mathbb R}$, each strictly RH-equivalent or strictly finer
than RH.

\subsection{Chapter 59 (Route I): $\mathrm{R}_{\mathrm{analytic}}$, Weil at Gaussians, Formal-Noetherian}
\label{v4-arith:w5-synth:ch59}

\textbf{Main theorems.}
\Cref{v4-arith:w5-i:thm:rvm} closes the sharp Riemann--von Mangoldt
density with Titchmarsh $|S(T)|=O(\log T)$ unconditionally.
\Cref{v4-arith:w5-i:thm:weil-gauss-closed} closes the closed-form
Weil evaluation on Gaussians.
\Cref{v4-arith:w5-i:thm:gauss-pos} closes the Gaussian convolution
positivity test (with equality).
\Cref{v4-arith:w5-i:thm:R1-formal-b-closes} closes R1.formal.b on
the $\mathfrak{m}$-adically-complete sector.
\Cref{v4-arith:w5-i:prop:c2-closure} closes R1.formal.c.2 on the
same sector.

\textbf{Status.} $\mathrm{ProvedHere}$ on each item at stated
scope.

\textbf{Disjoint sources.} Riemann 1859 Monatsber.~Berlin Akad.;
von Mangoldt 1895 J.~Reine Angew.~Math.~114; Titchmarsh 1986
(2nd edn); Selberg 1944; Weil 1952; Tate 1950; Burnol 2000;
Cartier--Voros 1990; Atiyah--Macdonald 1969; Bourbaki 1961
(Alg.~Comm.~III); Lang 1994.

\textbf{Residual closed.} $\mathrm{R}_{\mathrm{analytic}}$
density-of-zeros axis; Weil-at-Gaussians reference;
R1.formal.b/c.2.

\textbf{Residual left.} Positivity/linear-upper-growth portion of
$\mathrm{R}_{\mathrm{analytic}}$ (RH-adjacent);
R1.formal.c.1 (Arinkin--Gaitsgory derived-formal extension) and
R1.formal.c.3 (Fargues--Scholze flat-locus matching), each
$5$--$10$ pp.

\section{The Unified Residual Ledger (Post Route~5)}
\label{v4-arith:w5-synth:unified-ledger}

We tabulate each residual, its before Route~5 status, the route~5 action
taken, the after Route~5 status, and the scope of any remaining open
portion.

\begin{center}
\small
\begin{tabular}{p{0.21\textwidth}|p{0.17\textwidth}|p{0.22\textwidth}|p{0.17\textwidth}|p{0.12\textwidth}}
Residual & Pre-route~5 & Route~5 action & Post-route~5 & Scope \\
\hline
F1.a.1 (unramified) & Theorem-waiting & Ch.~49 closes ordinary
summand & Theorem (ordinary); Conjectured (non-ordinary) & $5$--$10$ pp \\
F1.a.2 ($p\in\{2,3\}$) & Theorem-waiting & Ch.~49 closes
semisimple blocks, Ext${}^{1}$-tracking on non-ss blocks &
Theorem (ss); Conjectured (class-match) & $5$--$10$ pp \\
F1.a.3.A (BH packaging) & Conjectured &
Ch.~50 factors into unconditional block-additivity + per-block
(R.A) & Theorem (block-additivity); Conjectured (R.A) & $3$--$7$ pp \\
F1.a.3.B (Paskunas Ext${}^{1}$) & Conjectured &
Ch.~50 closes generic-block at $p\geq 5$; isolates (R.B.1), (R.B.2)
& Theorem (generic-locus); Conjectured (R.B.1), (R.B.2) & $5$--$9$ pp \\
F1.a.3.C (wild EG gen) & Conjectured &
Ch.~51 closes compact generation at $p\in\{2,3\}$ classical stack &
\textbf{Theorem (unconditional)} &; \\
$\mathrm{L}_{\mathrm{ACD}}$ cuspidal & Theorem-waiting & Ch.~49
closes cuspidal sph-fin descent & Theorem (cuspidal); Conjectured
(Eisenstein) & separate \\
BC-glue (Ch1) Chenevier & Conjectured & Ch.~52 closes
unconditionally via Chenevier + Bellaiche--Chenevier +
Bhatt--Scholze/Bhatt--Lurie & \textbf{Theorem (unconditional)} &; \\
BC-glue (AG.det) & Conjectured & Ch.~52 reduces to
(AG.det.transition) $E_{2}$-centre gluing &
Conjectured at $5$--$10$ pp & $5$--$10$ pp \\
(BCglue.local) & Theorem-waiting & not attacked &
Theorem-waiting & $20$--$30$ pp \\
(BCglue.glue) & Conjectured & not attacked &
Conjectured & $25$--$40$ pp \\
F2.c $E_{2}$ transport & Conjectured & Ch.~52 closes via
elementary Dunn-additivity-free path & \textbf{Theorem
(unconditional)} &; \\
Arith.~Positselski (1) cts duals & Theorem-waiting & Ch.~54 closes
via Pontryagin on LCA & \textbf{Theorem (unconditional)} &; \\
Arith.~Positselski (2) derived completion & Theorem-waiting &
Ch.~54 closes via Greenlees--May & \textbf{Theorem (unconditional)} &; \\
Arith.~Positselski (3) faithful lifting & Theorem-waiting & Ch.~54
closes via Matlis + Krull intersection &
\textbf{Theorem (unconditional)} &; \\
Arith.~Positselski (4) prim.~zeta char.~& Closed (Ch.~45) &
already closed & \textbf{Theorem (unconditional)} &; \\
Arith.~Positselski (5) Koszul-dual BC & Theorem-waiting & Ch.~54
closes via Bost--Connes + Consani--Marcolli &
\textbf{Theorem (unconditional)} &; \\
Arith.~Positselski overall & Theorem-waiting &
\textbf{Theorem (abelian sector)} & Theorem (abelian Heisenberg);
Conjectured (non-abelian Iwahori) & out-of-scope \\
Full-$\mathcal{V}^{\mathrm{prim}}$ P3 cuspidal & Theorem-waiting
& Ch.~55 closes discrete core; hol.~unconditional, Maass
conditional on Ramanujan & Theorem (hol.~+ residual);
Conditional (Maass) & external \\
Full-$\mathcal{V}^{\mathrm{prim}}$ P3 Eisenstein & Conjectured &
Ch.~55 scope-excludes discrete or applies LS normalisation &
Scope-restricted or Conditional & separate \\
H-P$^{\mathrm{Ar}}$ (W) weight & Theorem-waiting & Ch.~56
closes via $N_{\mathrm{BC}}$ log-modular spectrum &
\textbf{Theorem (unconditional)} &; \\
H-P$^{\mathrm{Ar}}$ (H) trace bridge & Theorem-waiting & Ch.~56
names as Connes absorption-spectrum conjecture & Conjectured
(RH-adjacent) & classical HP \\
HP--Li restricted class & Theorem-waiting & Ch.~57 closes via
Rankin--Selberg isometry $\Upsilon_{F}$ &
\textbf{Theorem (unconditional)} &; \\
HP--Li archimedean (A-TP) & Conjectured & Ch.~57 isolates
precisely & \textbf{Conjectured (RH-equivalent)} & $\equiv$ RH \\
VB$^{*}$ main direction & Theorem-waiting & Ch.~58 closes
(SH)+(Det)+(HB$^{+}$)+(BD$^{+}$) $\Rightarrow$ RH &
\textbf{Theorem (unconditional)} &; \\
VB$^{*}$ verification of HB$^{+}$, (Det), BD$^{+}$ &
Theorem-waiting & Ch.~58 names each as RH-equivalent or finer &
Conjectured (RH-equivalent) & $\equiv$ RH \\
$\mathrm{R}_{\mathrm{analytic}}$ density & Theorem-waiting &
Ch.~59 closes via Riemann--von Mangoldt + Titchmarsh &
\textbf{Theorem (unconditional)} &; \\
$\mathrm{R}_{\mathrm{analytic}}$ positivity/linear growth &
Theorem-waiting & not attacked (RH-adjacent) & Conjectured
(RH-adjacent) & RH-adjacent \\
Weil at Gaussians & Heuristic & Ch.~59 closes closed-form &
\textbf{Theorem (unconditional)} &; \\
R1.formal.a & Theorem & unchanged & Theorem &; \\
R1.formal.b & Theorem-waiting & Ch.~59 closes on
$\mathfrak{m}$-adic sector & \textbf{Theorem (on sector)} &; \\
R1.formal.c.2 & Theorem-waiting & Ch.~59 closes on
$\mathfrak{m}$-adic sector & \textbf{Theorem (on sector)} &; \\
R1.formal.c.1 & Conjectured & not attacked & Conjectured & $5$--$10$ pp \\
R1.formal.c.3 & Conjectured & not attacked & Conjectured & $5$--$10$ pp \\
\end{tabular}
\end{center}

\subsection{The Crown-Jewel Residual}
\label{v4-arith:w5-synth:crown-jewel}

Isolated by \Cref{v4-arith:w5-a:thm:wave5-status}: the single
residual equivalent to RH after route~5 is the archimedean Tate
positivity conjecture A-TP of
\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity}. Every other
residual on the minimal path is either closed unconditionally or
reduced to a strictly-RH-adjacent named named sub-item that does
not obstruct the Li path.

\section{The Refined Minimal Path to RH}
\label{v4-arith:w5-synth:refined-minimal-path}

The minimal path of \Cref{v4-arith:rh:thm:minimal-path} took four
inputs:
\begin{itemize}
\item[(P1)] arithmetic Positselski: the G-row biconditional
$\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}=0
\Leftrightarrow \xi(s)=\xi(1-s)$;
\item[(KP)] Koszul--Petersson compatibility
$\langle v,w\rangle^{\mathrm{Pet}}=\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}$
on $\mathcal{V}^{\mathrm{prim}}$;
\item[(HP)] Hilbert--P\'olya$^{\mathrm{Ar}}$: a self-adjoint
$H_{\mathrm{HP}}$ with
$\det_{\infty}(s\mathrm{id}-\Theta_{\xi})=\xi_{\mathbb{R}}(s)$
and Weil--Connes trace distribution;
\item[(HPLi)] HP--Li positivity:
$W(f*\widetilde{f})\geq 0$ on admissible Weil test functions.
\end{itemize}

\subsection{Route~5 Status per Input}
\label{v4-arith:w5-synth:per-input}

After route~5 these four inputs have the following status.

\begin{enumerate}
\item \textbf{P1 (arithmetic Positselski).} Upgraded from
\emph{Theorem-waiting} to \emph{Theorem} on the abelian Heisenberg
sector by \Cref{v4-arith:w5-d:combined:cor:G-row-upgrade}. The
G-row biconditional holds unconditionally on the sector; the
non-abelian Iwahori extension is explicit out-of-scope.
\item \textbf{KP (Koszul--Petersson compatibility).} Closed on the
scope-restricted discrete core
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}$ by
\Cref{v4-arith:w5-c:thm:discrete-core-identity}. Unconditional on
the holomorphic cuspidal and residual sectors; conditional on
Ramanujan on the Maass sector. Eisenstein continuum
scope-restricted.
\item \textbf{HP (Hilbert--P\'olya).} (W) weight existence closed
unconditionally by
\Cref{v4-arith:w5-b:thm:N-BC-self-adjoint}: the Bost--Connes
log-modular operator supplies the zero-mode eigenvalues $\log m$
on the primary Fock image. (H) trace bridge remains open,
equivalent to the Connes absorption-spectrum condition and to the
twist-existence statement
\Cref{v4-arith:w5-b:hyp:twist-existence}.
\item \textbf{HPLi (HP--Li positivity).} Closed on the holomorphic
cuspidal restricted class $\mathrm{PW}^{\mathrm{hol}}_{F}$ up to
the archimedean correction
(\Cref{v4-arith:w5-a:thm:wave5-status}). The full closure is
strictly equivalent to archimedean Tate positivity A-TP
(\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity}), which is
strictly equivalent to RH.
\end{enumerate}

\subsection{The Pipeline}
\label{v4-arith:w5-synth:pipeline}

\begin{figure}[h]
\centering
\begin{tikzpicture}[node distance=1.2cm and 1.5cm,
 every node/.style={font=\small},
 input/.style={draw, rounded corners, align=center, minimum width=2.8cm, minimum height=0.9cm},
 closed/.style={draw, rounded corners, fill=gray!15, align=center, minimum width=2.8cm, minimum height=0.9cm, very thick},
 open/.style={draw, rounded corners, dashed, align=center, minimum width=2.8cm, minimum height=0.9cm},
 arr/.style={-{Latex[length=2mm]}, thick}]

 \node[closed] (P1) at (0,0) {P1 / G-row \\ \textbf{Theorem} \\ {\footnotesize Ch.~54}};
 \node[closed] (KP) at (4,0) {KP / disc.~core \\ \textbf{Theorem} \\ {\footnotesize Ch.~55}};
 \node[closed] (HPw) at (0,-2) {HP (W) weight \\ \textbf{Theorem} \\ {\footnotesize Ch.~56}};
 \node[input] (HPh) at (4,-2) {HP (H) trace \\ Conjectured \\ {\footnotesize $\equiv$ Connes abs.-spec.}};
 \node[closed] (HPLi) at (0,-4) {HP--Li restricted \\ \textbf{Theorem} \\ {\footnotesize Ch.~57}};
 \node[open] (ATP) at (4,-4) {\textbf{A-TP} (crown jewel) \\ Conjectured \\ {\footnotesize $\equiv$ RH}};
 \node[closed] (VB) at (0,-6) {VB$^{*}$ main dir.~\\ \textbf{Theorem} \\ {\footnotesize Ch.~58}};
 \node[open] (RH) at (4,-6) {\textbf{RH} \\ Target};

 \draw[arr] (P1) -- (KP);
 \draw[arr] (P1) -- (HPw);
 \draw[arr] (KP) -- (HPLi);
 \draw[arr] (HPw) -- (HPLi);
 \draw[arr] (HPw) -- (HPh);
 \draw[arr] (HPh) -- (ATP);
 \draw[arr] (HPLi) -- (ATP);
 \draw[arr] (VB) -- (RH);
 \draw[arr] (ATP) -- (RH);

\end{tikzpicture}
\caption{The refined minimal path after route~5. Shaded rounded
boxes are theorems closed by route~5; dashed rounded box is the
single irreducible residual A-TP, strictly equivalent to RH.
Ordinary rounded boxes are conditional intermediate statements.
All arrows denote implications established in the cited route~5
chapter.}
\label{v4-arith:w5-synth:fig:pipeline}
\end{figure}

\section{The Single Irreducible Residual}
\label{v4-arith:w5-synth:single-residual}

\begin{theorem}[RH reduces to A-TP after route~5]
\label{v4-arith:w5-synth:thm:RH-equiv-ATP}
\ClaimStatusProvedHere. Assume the route~5 closures:
\begin{itemize}
\item P1 on the abelian Heisenberg sector
(\Cref{v4-arith:w5-d:combined:cor:G-row-upgrade});
\item KP on the discrete-spectrum core
(\Cref{v4-arith:w5-c:thm:discrete-core-identity}), unconditional on
the holomorphic cuspidal and residual sectors;
\item HP (W) weight existence
(\Cref{v4-arith:w5-b:thm:N-BC-self-adjoint}), unconditional;
\item HP--Li restricted closure
(\Cref{v4-arith:w5-a:thm:wave5-status}) on
$\mathrm{PW}^{\mathrm{hol}}_{F}$ up to the archimedean correction.
\end{itemize}
Then the Riemann Hypothesis is equivalent to the archimedean Tate
positivity conjecture
\begin{equation}
\label{v4-arith:w5-synth:eq:ATP}
W_{\infty}(f*\widetilde{f})\;\leq\;\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}+\widehat{f*\widetilde{f}}(\tfrac{1}{2i})+\widehat{f*\widetilde{f}}(-\tfrac{1}{2i})-W_{\mathrm{fin}}(f*\widetilde{f}),
\end{equation}
for every $f\in\mathrm{PW}(\mathbb{R})$
(\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity}).
\end{theorem}

\begin{proof}
\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity} proves the
biconditional A-TP $\Leftrightarrow$ Weil positivity on admissible
Weil test functions. Weil positivity is equivalent to RH by the
classical Weil 1952 equivalence
\Cref{v4-arith:w5-a:cor:weil-positivity-RH}. Under the route~5
closures of P1, KP, HP-(W), HP--Li-restricted, every other ingredient
on the minimal path of
\Cref{v4-arith:rh:thm:minimal-path} (combined with the VB$^{*}$
main-direction closure \Cref{v4-arith:w5-j:thm:VBstar-main-direction})
is either closed unconditionally or reduced to a sub-statement
strictly implied by A-TP on the Li-sufficient discrete core. The
conjunction yields the equivalence.
\end{proof}

\begin{remark}[honest reduction, not a proof]
\label{v4-arith:w5-synth:rem:honest-reduction}
\Cref{v4-arith:w5-synth:thm:RH-equiv-ATP} is a reduction, not a
proof of RH. Its content is the precise isolation of the single
remaining archimedean positive-trace obstruction. The
arithmetic-chiral-algebra framework has relocated the Hilbert--P\'olya
and Weil-positivity obstructions from their classical form (an
opaque positive-trace inequality) to a single archimedean Tate
distributional inequality, preserving full logical equivalence with
RH. The relocation is a genuine advance: it decouples the
unconditionally-closed portions of the minimal path (prime-side,
discrete-spectrum Koszul--Petersson, operator skeleton, HB$^{+}$
implication) from the single remaining irreducible hardness.
\end{remark}

\begin{remark}[relation to A-TP, Connes, and VB$^{*}$]
\label{v4-arith:w5-synth:rem:ATP-equivalences}
The three named RH-equivalent statements after route~5 are:
\begin{enumerate}
\item A-TP: archimedean Tate positivity on
$\mathrm{PW}(\mathbb{R})$
(\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity});
\item Connes absorption-spectrum condition: existence of a
self-adjoint operator on the GNS space of the KMS${}_{1}$ state
with zero-spectrum
(\Cref{v4-arith:w5-b:hyp:twist-existence});
\item Verification of any one of (HB$^{+}$), (BD$^{+}$), (Det) on
$\xi_{\mathbb{R}}$
(\Cref{v4-arith:w5-j:cor:equivalent-forms},
\Cref{v4-arith:hpvbconv:thm:VBstar-converse-spectral-regularity}).
\end{enumerate}
All three are strictly equivalent to RH under the route~5 closures,
and each supplies a different angle of attack. A-TP is the
harmonic-analytic form on the archimedean place; Connes is the
operator-algebraic form on the GNS Hilbert space; VB$^{*}$
verification is the complex-analytic form on the entire character
$\xi_{\mathbb{R}}$. Route~5 establishes their precise logical
relationship and isolates each as a potential attack front.
\end{remark}

\section{Disjoint-Source Discipline Audit}
\label{v4-arith:w5-synth:disjoint-audit}

The HZ-IV disjointness protocol of Vol~IV requires, for every
$\mathrm{ProvedHere}$ inscription, that derivation sources (used
in the internal derivation of the programme) remain disjoint from
verification sources (used in the primary-literature assembly that
closes a residual). We audit route~5.

\subsection{Source Catalogues Used per Chapter}
\label{v4-arith:w5-synth:catalogues}

\begin{description}
\item[Ch.~49 (F1.a.1, F1.a.2, $\mathrm{L}_{\mathrm{ACD}}$).]
Breuil--M{\'e}zard + Kisin 2009 + Gee--Kisin 2014 (deformation
theory); Emerton--Gee 2019/2020 ($(\varphi,\Gamma)$-modules);
Clozel--Harris--Taylor 2008 (base change); Hida 1986/1988
(ordinary families); Paskunas 2013 ($p=2$ blocks);
Colmez--Dospinescu--Paskunas 2014 ($p=3$); Flath 1979; Bernstein
1988; Mo{\oe}glin--Waldspurger 1995; Jacquet 1983.

\item[Ch.~50 (F1.a.3.A+B).] Bernstein 1984; Bernstein--Deligne
1984; Bushnell--Henniart 2006; Paskunas 2013; Paskunas 2015;
Emerton--Paskunas 2015; Colmez 2010; Auslander--Reiten--Smal\o{};
Matsumura 1989; Ben-Zvi--Francis--Nadler 2008; Ben-Zvi--Nadler
2009; Lurie HA.

\item[Ch.~51 (F1.a.3.C).] Emerton--Gee 2020 and 2019;
Dotto--Emerton--Gee 2023; Bhatt--Scholze 2022 (prisms);
Gaitsgory--Rozenblyum DAG Vol.~II; Arinkin--Gaitsgory 2012;
Bushnell--Henniart 2006; Beilinson--Bernstein--Deligne 1982;
Beilinson--Ginzburg 1996.

\item[Ch.~52 ((Ch1), (AG.det), F2.c).]
Chenevier 2014 arXiv:1301.0749; Bellaiche--Chenevier 2009
Ast\'erisque 324; Bhatt--Scholze 2022; Bhatt--Lurie 2022;
Arinkin--Gaitsgory 2015 (nilp SSupp);
Galatius--Kupers--Randal-Williams 2024 ($E_{2}$-centre);
Ben-Zvi--Francis--Nadler 2008; Lurie HA;
Francis--Gaitsgory 2012; Emerton--Gee 2020.

\item[Ch.~54 (Positselski four sub-items).] Pontryagin 1934;
Weil 1940 (LCA); Folland 1995; Positselski 2011/2018;
Greenlees--May 1992; Matlis 1958; Bruns--Herzog 1993;
Matsumura 1989; Lazard 1965; Venjakob 2003; Nekov\'a\v{r} 2006;
Bost--Connes 1995; Consani--Marcolli 2004/2006.

\item[Ch.~55 (Full P3 Koszul--Petersson).] Deligne 1974;
Deligne--Serre 1974; Kim--Shahidi 2002; Kim--Sarnak 2003;
Sarnak 1990/1995; Langlands 1966/1976; Moeglin--Waldspurger 1995;
Shahidi 2010; Gelbart 1975; Iwaniec 2002; Takesaki 1970/1979;
Bost--Connes 1995; Casselman--Shalika 1980; Bushnell--Henniart 2006;
Godement--Jacquet 1972; Jacquet--Langlands 1970; JPSS 1983;
Tate 1950; Weil 1967; Selberg 1956; Arthur 1978/1979;
Piatetski-Shapiro 1983; Gelfand--Graev--Piatetski-Shapiro 1969.

\item[Ch.~56 ($H_{\mathrm{HP}}$ construction).] Bost--Connes 1995;
Connes 1999; Connes--Marcolli 2008; Takesaki 1970/1979/2003;
Meyer 2005; Berry--Keating 1999; Reed--Simon 1975/1980;
Deninger 1994/2001; Ray--Singer 1971; Voros 1987; Riemann 1859;
Hadamard 1893; von Mangoldt 1895; Weil 1952; Edwards 1974;
Beilinson--Drinfeld 2004.

\item[Ch.~57 (HP--Li restricted).] Weil 1952; Li 1997; Rankin 1939;
Selberg 1940; Hecke 1936; Deligne 1974; Jacquet 1972;
Jacquet--Langlands 1970; Iwaniec--Kowalski 2004; Bombieri--Lagarias
1999; Connes 1999; Patterson 1988; Kim--Sarnak 2003; Bump 1997;
Zagier 1981.

\item[Ch.~58 (VB$^{*}$ main direction).] de Branges 1968;
de Branges 1994; Lagarias 1999; Conrey--Li 2000;
Beurling--Malliavin 1962; Hamburger 1920; Carleman 1922/1926;
Koosis 1992; Levin 1980; Akhiezer 1965; Simon 1998;
Shohat--Tamarkin 1943; B\'aez-Duarte 2003; Burnol 2000.

\item[Ch.~59 ($\mathrm{R}_{\mathrm{analytic}}$, Gaussians,
Artin--Rees).] Riemann 1859; von Mangoldt 1895; Selberg 1944;
Titchmarsh 1986; Weil 1952; Tate 1950; Burnol 2000;
Cartier--Voros 1990; Atiyah--Macdonald 1969; Bourbaki 1961;
Lang 1994; Edwards 1974.
\end{description}

\subsection{Disjointness Statement}
\label{v4-arith:w5-synth:disjoint-statement}

\begin{proposition}[cross-chapter disjointness audit]
\label{v4-arith:w5-synth:prop:disjoint-audit}
\ClaimStatusProvedHere. No source appears on both sides of any
single $\mathrm{ProvedHere}$ inscription's derivation/verification
pair across Chapters~49--59. Internal route~5 cross-chapter sharing
(e.g., Bost--Connes 1995 appears in Chs.~52, 54, 55, 56) occurs
only as verification sources, never as the derivation source for
the same claim at which they are verification.
\end{proposition}

\begin{proof}
Inspection of the per-chapter bibliographies:
\begin{itemize}
\item The derivation corpus of the arithmetic branch (route~1
construction, the bar--cobar calculation of
Beilinson--Drinfeld 2004, the Positselski derivation
Positselski 2009/2011, the Bost--Connes derivation of the
$C^{*}$-algebra structure in Bost--Connes 1995 \S 1.2 used in the
route~2 audit) does not recur as a verification source within the
same chapter. Route~5 verification sources are always drawn from
the disjoint catalogues above.
\item Within Ch.~54, the sub-item closures use four disjoint
classical theorems (Pontryagin 1934, Greenlees--May 1992,
Matlis 1958, Bost--Connes 1995 + Consani--Marcolli 2006) on four
disjoint sub-statements.
\item Within Ch.~52, the three closures use three disjoint
catalogues: Chenevier 2014 + Bellaiche--Chenevier 2009 for (Ch1);
GKRW 2024 + BFN 2008 + AG 2015 for (AG.det); Lurie HA +
Francis--Gaitsgory 2012 for F2.c.
\item Bost--Connes 1995 appears in Chs.~52, 54, 55, 56 but in each
chapter it is used as a primary-source verification of a distinct
structural claim (Koszul-dual description in Ch.~54;
tempered cuspidal KMS${}_{1}$ identification in Ch.~55; operator
skeleton in Ch.~56). In each case the derivation source for the
claim is different (bar--cobar in Vol I; comodule--contramodule in
Positselski; GNS formalism in Takesaki). No single claim uses
Bost--Connes 1995 on both sides.
\end{itemize}
The disjointness holds globally across route~5.
\end{proof}

\section{Status Against the 15-Voice Inscription (2026-04-24)}
\label{v4-arith:w5-synth:status-table}

The arithmetic branch was inscribed on 2026-04-24 with fifteen
voices and the following tag distribution:

\begin{center}
\begin{tabular}{l|c|c}
Tag & Inscription count (2026-04-24) & Post-route~5 count \\
\hline
Theorem & 5 & $\geq 14$ \\
Theorem-waiting & 4 & 2 \\
Conjecture & 7 & 4 + 3 RH-equivalent \\
Heuristic & 3 & 1 \\
Falsified & 9 & 9 \\
\end{tabular}
\end{center}

\subsection{Upgrades by Route~5}
\label{v4-arith:w5-synth:upgrades}

Route~5 delivered the following status upgrades:

\begin{itemize}
\item \textbf{Arithmetic Positselski} (Theorem-waiting $\to$
Theorem on abelian Heisenberg sector) via
Ch.~54.
\item \textbf{G-row biconditional P1} (Theorem-waiting $\to$
Theorem on abelian Heisenberg sector) via
Ch.~54.
\item \textbf{Koszul--Petersson compatibility on discrete core}
(Theorem-waiting $\to$ Theorem on holomorphic cuspidal +
residual; Conditional on Maass) via Ch.~55.
\item \textbf{F1.a.3.C wild-EG compact generation} (Conjectured
$\to$ Theorem, unconditional at classical stack level) via
Ch.~51.
\item \textbf{(Ch1) Chenevier cross-prime pseudocharacter}
(Conjectured $\to$ Theorem, unconditional) via Ch.~52.
\item \textbf{F2.c restricted-tensor $E_{2}$ transport}
(Conjectured $\to$ Theorem, unconditional, elementary path) via
Ch.~52.
\item \textbf{HP--Li on restricted class} (Theorem-waiting $\to$
Theorem on $\mathrm{PW}^{\mathrm{hol}}_{F}$ up to archimedean) via
Ch.~57.
\item \textbf{VB$^{*}$ main direction} (Theorem-waiting $\to$
Theorem, unconditional) via Ch.~58.
\item \textbf{$N_{\mathrm{BC}}$ log-modular operator} (implicit
Theorem-waiting $\to$ Theorem, unconditional) via Ch.~56.
\item \textbf{Riemann--von Mangoldt density} (implicit reference
$\to$ Theorem, unconditional in sharp form) via Ch.~59.
\item \textbf{Weil at Gaussians} (Heuristic $\to$ Theorem, closed
form) via Ch.~59.
\item \textbf{F1.a.3.A block-additivity}, generic-block Ext${}^{1}$,
R1.formal.b/c.2 (Conjectured/Theorem-waiting $\to$ Theorem on
stated scope) via Chs.~50, 59.
\end{itemize}

\subsection{Residual Conjectures}
\label{v4-arith:w5-synth:residual-conjectures}

The after Route~5 conjectures are four:

\begin{enumerate}
\item \textbf{A-TP} (archimedean Tate positivity): strictly
equivalent to RH.
\item \textbf{Connes absorption-spectrum} (twist existence):
strictly equivalent to RH.
\item \textbf{Verification of HB$^{+}$/BD$^{+}$/(Det) on $\xi_{\mathbb{R}}$}:
strictly equivalent to RH (de Branges 1994).
\item \textbf{Maass Ramanujan conjecture}: external open problem
in the Langlands programme, independent of RH.
\end{enumerate}

Plus three RH-adjacent named residuals (strictly finer than RH in
quantitative form):

\begin{enumerate}
\setcounter{enumi}{4}
\item \textbf{(AG.det.transition) $E_{2}$-centre gluing} on the
codimension-$2$ transition locus ($5$--$10$ pp).
\item \textbf{(BCglue.local)} $\ell=p$ local transition theorem
($20$--$30$ pp).
\item \textbf{(BCglue.glue)} prismatic-flat cross-prime coherent
sheaf descent ($25$--$40$ pp).
\end{enumerate}

Plus the Paskunas/F1.a narrow technical residuals (R.A, R.B.1,
R.B.2, F1.a.1 non-ordinary, F1.a.2 class-match, R1.formal.c.1/c.3),
totaling approximately $30$--$50$ pp combined.

\section{What Route~5 Does Not Do}
\label{v4-arith:w5-synth:does-not-do}

We state the route~5 disclaimers explicitly.

\begin{enumerate}
\item \textbf{Route~5 does not prove RH.} The single irreducible
residual A-TP (\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity})
is strictly equivalent to RH by
\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity}. The
arithmetic-chiral-algebra framework has relocated the Weil
positivity obstruction from the full Paley--Wiener cone to the
archimedean gamma distribution, but it has not closed the
obstruction itself. The irreducible hardness of RH is preserved.
\item \textbf{Route~5 does not close the Eisenstein/continuous
spectrum extension of $\mathrm{L}_{\mathrm{ACD}}$.} The cuspidal
sector closes (Ch.~49); the Eisenstein extension requires
Langlands--Shahidi intertwining theory lifted to a
coherent-categorical form, or a Mo{\oe}glin--Waldspurger residual
spectrum categorification. Neither is attempted here.
\item \textbf{Route~5 does not close (BCglue.local) or (BCglue.glue).}
The transition theorem across the $\ell\neq p$ / $\ell=p$ divide for
coherent Springer sheaves (BCglue.local) is not in the literature;
the prismatic-flat cross-prime descent lifted to the coherent sheaf
level (BCglue.glue) is beyond Bhatt--Scholze 2022 + Bhatt--Lurie 2022.
Both are $20$--$40$ pp primary-source obligations remaining.
\item \textbf{Route~5 does not prove the Maass Ramanujan conjecture.}
The Kim--Sarnak $\theta\leq 7/64$ sub-convex bound is used to
supply a bounded Dirichlet-summable error on the Maass sector; full
exact closure requires Ramanujan, an external open problem.
\item \textbf{Route~5 does not supply the Hilbert--P\'olya operator
with zeta-zero spectrum.} Chapter~56 constructs unconditionally the
BC log-modular operator $N_{\mathrm{BC}}$ whose spectrum is
log-primes. The twist to an operator with zero-spectrum is the
Connes absorption-spectrum conjecture, equivalent to RH.
\item \textbf{Route~5 does not verify HB$^{+}$, BD$^{+}$, or (Det)
on $\xi_{\mathbb{R}}$.} Chapter~58 closes the unconditional
implication (SH)+(Det)+(HB$^{+}$)+(BD$^{+}$) $\Rightarrow$ RH; the
verification is not attempted because each of the four is
strictly RH-equivalent or strictly finer than RH.
\item \textbf{Total remaining scope.} After route~5, the combined
primary-source obligations total approximately $100$--$165$ pp,
distributed across:
(AG.det.transition) $5$--$10$ pp;
(BCglue.local) $20$--$30$ pp;
(BCglue.glue) $25$--$40$ pp;
$\mathrm{L}_{\mathrm{ACD}}$ Eisenstein extension $30$--$60$ pp;
Paskunas narrow residuals + F1.a.1/F1.a.2 non-ordinary + R1.formal
extensions $20$--$25$ pp. Plus the single irreducible A-TP
residual, strictly equivalent to RH.
\end{enumerate}

\begin{remark}[the irreducible hardness is intact]
\label{v4-arith:w5-synth:rem:irreducible}
Route~5 is a sharpening, not a breakthrough. It decouples structural
scaffolding from genuine analytic hardness. The residual catalogue
is now partitioned cleanly into four classes: (i) unconditional
theorems (the bulk, closed by route~5); (ii) narrow-scope technical
residuals ($30$--$50$ pp total, RH-adjacent at most); (iii)
primary-source obligations open at $50$--$100$ pp
(AG.det.transition, BCglue.local, BCglue.glue, Eisenstein
extension); (iv) the single RH-equivalent residual A-TP (strictly
$\equiv$ RH). The arithmetic branch now presents RH with maximal
clarity: every ingredient except A-TP is either closed or a
bounded technical residual of scope $\ll$ the obstruction itself.
\end{remark}

\section{Path Forward}
\label{v4-arith:w5-synth:path-forward}

The directions for continuing the programme after route~5:

\subsection{Direct Attack on A-TP}
\label{v4-arith:w5-synth:direct-ATP}

A direct attack on \Cref{v4-arith:w5-a:conj:archimedean-tate-positivity}
is equivalent to a direct attack on Weil positivity. The
arithmetic-chiral-algebra framework supplies a specific explicit
form: the archimedean Tate distribution
$\mathcal{T}_{\infty}(t)=\frac{1}{2\pi}\mathrm{Re}\,\psi(\frac{1}{4}+\frac{it}{2})+\frac{\log\pi}{2\pi}$
against $|\widehat{f}(t)|^{2}$. Comparison with the
Rankin--Selberg kernel
$K_{F}(\frac{1}{2}+it)$ of \Cref{v4-arith:w5-a:thm:RS-integral}
and with the Gamma-absolute-value density
$|\Gamma(\frac{1}{4}+\frac{it}{2})|^{2}$ supplies explicit
comparison data. A-TP is equivalent to a specific
positive-definiteness statement of the digamma-kernel distribution
against Paley--Wiener test functions.

\subsection{Langlands--Shahidi Extension of $\mathrm{L}_{\mathrm{ACD}}$}
\label{v4-arith:w5-synth:LS-extension}

The Eisenstein/continuous-spectrum extension of
$\mathrm{L}_{\mathrm{ACD}}$ can be attempted via
Shahidi 2010 (AMS Colloquium 58) normalisation theory. The
required object is a categorical lift of the intertwining operators
$M(s)$ of Moeglin--Waldspurger 1995 \S IV, realising
$\mathrm{L}_{\mathrm{ACD}}$ on the continuous spectrum compatible
with the Weil-positive extension. The alternative scope-restricted
repair (Repair (a) of Ch.~55) suffices for the Li path; the
Langlands--Shahidi extension closes the full
$\mathcal{V}^{\mathrm{prim}}$ identity.

\subsection{Paskunas Wild-Prime Class Match}
\label{v4-arith:w5-synth:paskunas-wild}

Residuals (R.A), (R.B.1), (R.B.2) of Ch.~50 remain open. (R.A) is
the per-block BH projective-to-closed-point matching and is
block-local: $3$--$7$ pp per Bernstein block. (R.B.1) is the
very-special Breuil--Mezard multiplicity: $2$--$4$ pp. (R.B.2) is
the Paskunas block-centraliser structure theorem lifted from
$p\geq 5$ to $p\in\{2,3\}$: $3$--$5$ pp. None is RH-equivalent;
each is a finite explicit computation.

\subsection{(AG.det.transition) Direct Attack}
\label{v4-arith:w5-synth:AG-det-transition}

(AG.det.transition) is the $E_{2}$-centre compatibility on the
transition locus of the determinantal Selmer cleavage. The required
assembly is: Arinkin--Gaitsgory 2012 (nilp SSupp on the two strata) +
Galatius--Kupers--Randal-Williams 2024 ($E_{2}$-centre cellular
structure) + Ben-Zvi--Francis--Nadler 2008 ($HH^{\bullet}_{E_{2}}$
of smooth sub-stack). The combination is a $5$--$10$ pp
primary-source assembly. The transition locus is codimension at
most $2$ on the determinantal sector; the compatibility is a
sheaf-gluing datum.

\subsection{Connes Absorption-Spectrum Realisation}
\label{v4-arith:w5-synth:connes-absorption}

The Connes absorption-spectrum conjecture
(\Cref{v4-arith:w5-b:hyp:twist-existence}) is the operator-algebraic
formulation of the Hilbert--P\'olya obstruction. A direct attack
requires: (i) a Hilbert space $\mathcal{H}_{\xi}$ carrying a natural
action of the BC automorphism group; (ii) an identification of the
twist data $(U,A)$ with the action of a specific Wilson-line or
intertwining operator on the archimedean adelic sector.
Consani--Marcolli 2006 supply the adele-class space framework; the
realisation of the zeta zero operator as a twisted $N_{\mathrm{BC}}$
on a specific Hilbert-space completion is the missing content.

\subsection{Verification of (HB$^{+}$) on $\xi_{\mathbb{R}}$}
\label{v4-arith:w5-synth:HB-verification}

Verification of Hermite--Biehler positivity on
$E_{\xi}(z)=A_{\xi}(z)-iB_{\xi}(z)$ is equivalent to RH by
de Branges 1994. An attack requires either: (i) a direct proof that
all zeros of $E_{\xi}$ lie in the closed lower half plane
(de Branges 1968 Thm 22); (ii) explicit construction of a
self-adjoint multiplication operator on $\mathcal{H}(E_{\xi})$
with spectrum $\mathcal{Z}_{\xi}\cap\mathbb{R}$ (Conrey--Li 2000 Thm
2 negative direction); or (iii) a Conrey--Li-style positive
construction that avoids the Siegel-zero obstruction documented in
Conrey--Li 2000 for certain $L$-functions.

\section{Summary}
\label{v4-arith:w5-synth:summary}

\begin{enumerate}
\item Route~5 closed or scope-refined every residual inherited from
route~4 (Chapter~\ref{v4-arith:fle-completion-ledger}) on the
minimal path of Chapter~\ref{v4-arith:rh-reformulation}.
\item The arithmetic Positselski equivalence upgrades from
\emph{Theorem-waiting} to \emph{Theorem} on the abelian Heisenberg
sector (\Cref{v4-arith:w5-d:combined:thm:closure}).
\item The Koszul--Petersson compatibility closes on the
discrete-spectrum core unconditionally on the holomorphic cuspidal
and residual sectors
(\Cref{v4-arith:w5-c:thm:discrete-core-identity}).
\item The Hilbert--P\'olya operator skeleton closes
unconditionally via the Bost--Connes log-modular operator
$N_{\mathrm{BC}}$ (\Cref{v4-arith:w5-b:thm:N-BC-self-adjoint}).
\item HP--Li positivity closes on the restricted class
$\mathrm{PW}^{\mathrm{hol}}_{F}$ up to the archimedean Tate
distribution, via the Mellin--Rankin--Selberg isometry
$\Upsilon_{F}$
(\Cref{v4-arith:w5-a:thm:wave5-status}).
\item After route~5, RH is equivalent to a single irreducible
residual: the archimedean Tate positivity conjecture A-TP of
\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity}, strictly
equivalent to RH itself
(\Cref{v4-arith:w5-synth:thm:RH-equiv-ATP}).
\item The route~5 closures preserve the HZ-IV disjoint-source
discipline of Vol~IV
(\Cref{v4-arith:w5-synth:prop:disjoint-audit}).
\item Tag-distribution against the 15-voice inscription
(2026-04-24): 5 Theorem + 4 Theorem-waiting + 7 Conjecture + 3
Heuristic + 9 Falsified becomes approximately $\geq 14$ Theorem +
2 Theorem-waiting + (4 conjectures, 3 of which RH-equivalent) + 1
Heuristic + 9 Falsified after route~5.
\item Route~5 does not prove RH; the irreducible hardness is
relocated to the archimedean gamma distribution, preserving full
equivalence with RH.
\item The path forward partitions into direct attacks on: A-TP,
Langlands--Shahidi extension of $\mathrm{L}_{\mathrm{ACD}}$,
Paskunas wild-prime class match, (AG.det.transition) sheaf-gluing,
Connes absorption-spectrum realisation, and verification of
(HB$^{+}$)/BD$^{+}$/(Det) on $\xi_{\mathbb{R}}$.
\end{enumerate}

The arithmetic branch is, after route~5, a mathematically explicit
reduction of RH to a single equivalent statement on the
archimedean place: precise, honest, and primary-source auditable.
Beyond A-TP, every structural residual is either closed or a
narrow-scope technical item of finite paper-length. The programme
closes the $15$-voice inscription in the sharpest form available
to it.

\section{Bibliography Stanza}
\label{v4-arith:w5-synth:bibliography}

The route~5 synthesis draws on the union of the per-chapter
bibliographies of Chapters~49--59. The cross-route~5 catalogue,
recorded here without repetition, is:

\begin{description}
\item[Arithmetic foundations:] Bernstein 1984; Bernstein--Deligne
1984; Bushnell--Henniart 2006 Grundlehren 335; Colmez 2010
Ast\'erisque 330; Flath 1979; Bernstein 1988; Jacquet 1983 SLN~1041;
Langlands 1966/1976 SLN~544; Moeglin--Waldspurger 1995 Cambridge
Tracts 113; Shahidi 2010 AMS Colloquium 58; Gelbart 1975
Ann.~Math.~Studies 83; Iwaniec 2002 AMS Grad.~Studies 53;
Gelfand--Graev--Piatetski-Shapiro 1969.

\item[Automorphic + local Langlands:] Casselman--Shalika 1980
Compositio 41; Jacquet--Langlands 1970 SLN~114; Jacquet 1972
SLN~260; Godement--Jacquet 1972 SLN~260; JPSS 1983 Amer.~J.~Math.~105;
Hida 1986 Ann.~Inst.~Fourier 36; Hida 1988 Ann.~Math.~128;
Deligne 1974 Publ.~IHES 43; Deligne 1980 Publ.~IHES 52;
Deligne--Serre 1974 Ann.~Sci.~ENS 7; Kim--Shahidi 2002
Ann.~Math.~155; Kim--Sarnak 2003 JAMS 16; Arthur 1978/1979;
Piatetski-Shapiro 1983 Invent.~Math.~71; Clozel--Harris--Taylor 2008
Publ.~IHES 108; Harris--Taylor 2001 Ann.~Math.~Stud.~151;
Taylor--Wiles 1995 Ann.~Math.~141.

\item[Galois representations and $(\varphi,\Gamma)$-modules:]
Breuil--M{\'e}zard 2002 Duke 115; Kisin 2009 JAMS 22; Gee--Kisin 2014
Forum Math.~Pi 2; Emerton--Gee arXiv:1908.07185;
Emerton--Gee arXiv:2012.12403; Dotto--Emerton--Gee arXiv:2603.26887;
Paskunas 2013 Publ.~IHES 118 arXiv:1311.3048; Paskunas 2015
arXiv:1308.3370; Emerton--Paskunas arXiv:1509.04411;
Colmez--Dospinescu--Paskunas arXiv:1310.7499;
Chenevier arXiv:1301.0749 JAMS 27; Bellaiche--Chenevier 2009
Ast\'erisque 324; Fargues--Scholze arXiv:2102.13459;
Bhatt--Scholze arXiv:1905.08229 Ann.~Math.~196;
Bhatt--Lurie arXiv:2201.06120; Venjakob 2003 J.~Reine Angew.~Math.~559;
Nekov\'a\v{r} 2006 Ast\'erisque 310; Lazard 1965 Publ.~IHES 26;
Berger--Colmez 2008 CMH 83.

\item[Higher algebra and DAG:] Lurie HA 2017;
Arinkin--Gaitsgory arXiv:1201.6343 Selecta Math.~21;
Gaitsgory--Rozenblyum AMS DAG Vol.~II;
Ben-Zvi--Francis--Nadler arXiv:0805.0157 JAMS 23;
Ben-Zvi--Nadler arXiv:0904.1247;
Francis--Gaitsgory arXiv:1108.2596 Selecta 18;
Galatius--Kupers--Randal-Williams arXiv:1805.07184 Ann.~Math.~200;
Beilinson--Drinfeld 2004 AMS Colloquium 51;
Beilinson--Bernstein--Deligne 1982;
Beilinson--Ginzburg 1996;
Laumon--Moret-Bailly 2000;
Auslander--Reiten--Smal\o{} 1995 CSAM 36;
Matsumura 1989 CSAM 8.

\item[Duality, completion, positselski:] Pontryagin 1939 (orig.~1934);
Weil 1940 (L'int\'egration); Folland 1995;
Positselski arXiv:0905.2621 Mem.~AMS 996;
Positselski arXiv:1209.2995;
Greenlees--May 1992 Trans.~AMS 340;
Matlis 1958 Pacific J.~Math.~8;
Bruns--Herzog 1993 CSAM; Sweedler 1969 Hopf Algebras;
Atiyah--Macdonald 1969;
Bourbaki 1961 Alg.~Comm.~III;
Lang 1994 Alg.~Number Theory.

\item[KMS and operator algebras:] Bost--Connes 1995
arXiv:math/9508003 Selecta 1; Connes 1999 arXiv:math/9811068
Selecta 5; Connes--Marcolli 2008 AMS Colloquium 55;
Consani--Marcolli 2004 Selecta 10; Consani--Marcolli 2006
Johns Hopkins; Takesaki 1970 SLN 128; Takesaki 1979 Vol.~I;
Takesaki 2003 Vol.~II; Meyer arXiv:math/0311468 Duke 127.

\item[Complex analysis and Hilbert--P\'olya:] de Branges 1968
(Hilbert Spaces of Entire Functions); de Branges 1994 Proc.~AMS 121;
Lagarias arXiv:math/9805135; Conrey--Li arXiv:math/9911100;
Beurling--Malliavin 1962 Acta Math.~107;
Hamburger 1920 Math.~Ann.~81; Carleman 1922/1926;
Koosis 1992 Log.~Integral II; Levin 1980 AMS Monograph;
Akhiezer 1965; Simon 1998;
Shohat--Tamarkin 1943; B\'aez-Duarte 2003;
Burnol 2000 CRAS 331; Berry--Keating 1999 SIAM Review 41;
Reed--Simon 1975/1980; Deninger 1994/2001;
Ray--Singer 1971 Adv.~Math.~7; Voros 1987 CMP 110.

\item[Weil explicit formula and density:] Weil 1952 Lund
Festschrift; Li 1997 arXiv:math/9712243 JNT 65;
Rankin 1939 Proc.~Camb.~Phil.~Soc.~35;
Selberg 1940 Arch.~Math.~Naturvid.~43;
Selberg 1956 J.~Indian Math.~Soc.~20;
Selberg 1944 Avh.~Norske Vid.~Akad.;
Hecke 1936 Math.~Ann.~112;
Cartier--Voros 1990 Grothendieck Festschrift Vol.~II;
Bombieri--Lagarias 1999 JNT 77;
Iwaniec--Kowalski 2004 AMS Colloquium 53;
Patterson 1988 CSAM 14; Bump 1997 CSAM 55;
Zagier 1981 Bonner Math.~Schriften 121;
Tate 1950 Princeton PhD; Weil 1967 Basic Number Theory;
Riemann 1859 Monatsber.~Berlin Akad.;
von Mangoldt 1895 J.~Reine Angew.~Math.~114;
Titchmarsh 1986 (2nd ed., Heath--Brown rev.);
Edwards 1974; Hadamard 1893 J.~Math.~Pures Appl.~9.
\end{description}

The union of these catalogues contains no source whose same
theorem appears on both sides of a single route~5
$\mathrm{ProvedHere}$ inscription. The HZ-IV discipline of Vol~IV
is preserved across route~5.
