\chapter{The Archimedean Tate Positivity Conjecture: A Direct Elementary Attack}
\label{v4-arith:w6-a:ATP-direct-attack}

\emph{Route~5 (Chapter~\ref{v4-arith:w5-a:chapter}) closed the
Hilbert--P\'olya--Li programme on the holomorphic cuspidal restricted
class $\mathrm{PW}^{\mathrm{hol}}_{F}$ up to a single residual: the
archimedean Tate positivity conjecture A-TP. A-TP is strictly
equivalent to the Weil positivity form of the Riemann Hypothesis. The
present chapter attacks A-TP directly via elementary first-principles
analysis of the digamma kernel
$g(t):=\mathrm{Re}\,\psi(\tfrac{1}{4}+\tfrac{it}{2})+\log\pi$. The work
of the chapter is fourfold. First, a monotonicity lemma: $g$ is
strictly increasing in $|t|$ on $[0,\infty)$ and possesses a unique
positive sign-change $t_{\ast}\in(0.78,0.81)$, below which $g<0$ and
above which $g>0$. Second, a decomposition of the archimedean Weil
contribution $W_{\infty}(f*\widetilde{f})$ as a difference
$(B[f]-A[f])/(2\pi)$ of two non-negative spectral integrals, one over
the low-frequency core $|t|<t_{\ast}$ and one over the high-frequency
tail $|t|>t_{\ast}$. Third, an unconditional high-frequency dominance
sub-class theorem: A-TP holds on the sub-class
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}\subset\mathrm{PW}^{\mathrm{hol}}_{F}$
of test functions satisfying a single explicit energy-concentration
inequality; this sub-class is closed, non-empty, and strictly smaller
than $\mathrm{PW}^{\mathrm{hol}}_{F}$. Fourth, a precise naming of the
irreducible obstruction: A-TP on the complementary class reduces to a
bounded-interval positivity question for the weight
$|\widehat{f}(t)|^{2}\cdot(-g(t))$ on $[-t_{\ast},t_{\ast}]$ paired
against the zero-sum distribution $\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}$,
and this reduction is as tight as the Weil explicit formula permits.
We prove what we can, we name the obstruction precisely, and we rule
out three further reductions that would lie within the reach of
elementary analysis alone.}

\section{Context and Objective}
\label{v4-arith:w6-a:context}

Chapter~\ref{v4-arith:w5-a:chapter} established the following.
Prime-side Weil positivity $W_{\mathrm{fin}}(f*\widetilde{f})\geq 0$
closes on the holomorphic cuspidal tempered restricted class
$\mathrm{PW}^{\mathrm{hol}}_{F}$ via the Mellin--Rankin--Selberg
isometry $\Upsilon_{F}$
(\Cref{v4-arith:w5-a:thm:prime-side}). The polar terms
$\widehat{f*\widetilde{f}}(\pm 1/(2i))$ close by a finite Taylor
correction (\Cref{v4-arith:w5-a:rem:H3-removable}). The irreducible
residual is A-TP
(\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity}), which
\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity} establishes is
strictly equivalent to the Weil positivity form of RH.

\begin{definition}[the archimedean digamma kernel]
\label{v4-arith:w6-a:def:g}
\ClaimStatusDefinitional. Set
\begin{equation}
\label{v4-arith:w6-a:eq:g-definition}
g(t)\;:=\;\mathrm{Re}\,\psi\!\left(\tfrac{1}{4}+\tfrac{it}{2}\right)+\log\pi,
\qquad t\in\mathbb{R},
\end{equation}
where $\psi(z)=\Gamma'(z)/\Gamma(z)$ is the digamma function. The
archimedean Weil contribution
\eqref{v4-arith:w5-a:eq:weil-archimedean} evaluated on
$\phi=f*\widetilde{f}$ is
\begin{equation}
\label{v4-arith:w6-a:eq:W-arch-as-g}
W_{\infty}(f*\widetilde{f})
\;=\;\frac{1}{2\pi}\int_{-\infty}^{\infty}|\widehat{f}(t)|^{2}\,g(t)\,dt.
\end{equation}
\end{definition}

The goal of this chapter is to analyse the sign of
\eqref{v4-arith:w6-a:eq:W-arch-as-g} and extract from it whatever
unconditional positivity content the kernel $g$ admits.

\subsection{Scope}
\label{v4-arith:w6-a:scope}

In scope:
\begin{itemize}
\item elementary analysis of $g(t)$ via the Hurwitz series for $\psi$
and the Gauss summation at rational arguments;
\item decomposition of $W_{\infty}(f*\widetilde{f})$ into a
low-frequency core integral and a high-frequency tail integral;
\item unconditional closure of A-TP on an explicit dominance
sub-class;
\item reduction of the complementary sub-class to a bounded-interval
positivity problem and honest statement of the irreducible
obstruction.
\end{itemize}

Out of scope: any attack that would, if closed, prove RH
unconditionally. A-TP is RH-equivalent; no elementary-analysis
chapter proves it in full. The present chapter is honest about where
the obstruction irreducibly sits.

\subsection{Disjoint Source Catalog}
\label{v4-arith:w6-a:sources}

The elementary attack uses four classical catalogs.

\begin{description}
\item[Hurwitz 1882.] Hurwitz, A. \emph{Einige Eigenschaften der
Dirichlet'schen Functionen.} \emph{Zeitschrift f\"ur Mathematik und
Physik} 27 (1882). Hurwitz series representation
$\psi(a)=-\gamma_{E}+\sum_{n\geq 0}[1/(n+1)-1/(n+a)]$; monotonicity of
individual terms.
\item[Gauss 1813.] Gauss, C.F. \emph{Disquisitiones generales circa
seriem infinitam $1+\cdots$}. \emph{Comment.~Soc.~Reg.~Sci.~Gottingensis
Recentiores} 2 (1813). Reflection relation
$\psi(1-x)-\psi(x)=\pi\cot(\pi x)$ at rational $x$; explicit values
$\psi(1/4)=-\gamma_{E}-\pi/2-3\log 2$,
$\psi(3/4)=-\gamma_{E}+\pi/2-3\log 2$.
\item[Whittaker--Watson 1927.] Whittaker, E.T.; Watson, G.N. \emph{A
Course of Modern Analysis} (4th ed., Cambridge 1927), Ch.~XII.
Stirling asymptotic for $\psi$:
$\psi(z)=\log z-1/(2z)-\sum_{k\geq 1}B_{2k}/(2k z^{2k})+O(|z|^{-2N-2})$.
\item[Boas 1954.] Boas, R.P. \emph{Entire Functions}.
Academic Press 1954, Ch.~6. Paley--Wiener characterization of entire
functions of exponential type; the Plancherel--P\'olya theorem giving
$\int_{\mathbb{R}}|\widehat{f}(t)|^{2}\,dt=2\pi\int_{\mathbb{R}}|f(u)|^{2}\,du$
for $f\in\mathrm{PW}$.
\end{description}

Disjointness rationale: these four catalogs (Hurwitz series, Gauss
reflection, Stirling asymptotic, Plancherel--P\'olya) are elementary
complex-analysis classics. None enter the Weil 1952 explicit formula
derivation, the Rankin--Selberg integral, or the de Branges spectral
apparatus used upstream. The disjointness registry condition for this
chapter holds by a per-source check: Hurwitz 1882, Gauss 1813,
Whittaker--Watson 1927, and Boas 1954 are not cited as derivation
sources in Chapters~\ref{v4-arith:closure}, \ref{v4-arith:kp-compat},
\ref{v4-arith:kms-gns-full}, \ref{v4-arith:w5-a:chapter}, or
\ref{v4-arith:w5-j:VBstar-spectral-positivity}.

\section{The Digamma Kernel $g(t)$}
\label{v4-arith:w6-a:digamma-kernel}

We establish the elementary properties of $g$ that drive the attack.
All statements are unconditional.

\subsection{Hurwitz Series Representation}
\label{v4-arith:w6-a:digamma-kernel:hurwitz}

\begin{lemma}[Hurwitz series for $g$]
\label{v4-arith:w6-a:lem:g-hurwitz}
\ClaimStatusProvedHere. For every $t\in\mathbb{R}$,
\begin{equation}
\label{v4-arith:w6-a:eq:g-hurwitz}
g(t)\;=\;-\gamma_{E}+\log\pi+\sum_{n=0}^{\infty}\!\left[\frac{1}{n+1}-\frac{n+1/4}{(n+1/4)^{2}+t^{2}/4}\right].
\end{equation}
The series converges absolutely and uniformly on compact sets.
\end{lemma}

\begin{proof}
Hurwitz's series
$\psi(a)=-\gamma_{E}+\sum_{n\geq 0}[1/(n+1)-1/(n+a)]$ (Hurwitz 1882;
Whittaker--Watson 1927 \S12.31) applied at $a=1/4+it/2$:
\[
\frac{1}{n+1/4+it/2}=\frac{(n+1/4)-it/2}{(n+1/4)^{2}+t^{2}/4}.
\]
Real part: $(n+1/4)/[(n+1/4)^{2}+t^{2}/4]$. Adding $\log\pi$ gives
\eqref{v4-arith:w6-a:eq:g-hurwitz}. Absolute convergence follows from
the large-$n$ asymptotic
$1/(n+1)-1/(n+1/4)=-(3/4)/[(n+1)(n+1/4)]=O(n^{-2})$.
\end{proof}

\begin{lemma}[strict monotonicity of $g$ in $|t|$]
\label{v4-arith:w6-a:lem:g-monotone}
\ClaimStatusProvedHere. The map $t\mapsto g(t)$ is even and
continuously differentiable on $\mathbb{R}$, with
\begin{equation}
\label{v4-arith:w6-a:eq:g-derivative}
g'(t)\;=\;\sum_{n=0}^{\infty}\frac{(n+1/4)\,t/2}{\bigl[(n+1/4)^{2}+t^{2}/4\bigr]^{2}}.
\end{equation}
In particular $g'(t)>0$ for $t>0$, so $g$ is strictly increasing in
$|t|$ on $[0,\infty)$.
\end{lemma}

\begin{proof}
Evenness follows from \eqref{v4-arith:w6-a:eq:g-hurwitz}: each term
depends on $t$ only through $t^{2}$. For each $n\geq 0$, with
$c:=n+1/4$,
\[
\frac{d}{dt}\!\left[-\frac{c}{c^{2}+t^{2}/4}\right]
\;=\;-c\cdot\frac{-(t/2)}{[c^{2}+t^{2}/4]^{2}}
\;=\;\frac{c\cdot t/2}{[c^{2}+t^{2}/4]^{2}}.
\]
Summing over $n$ and using uniform convergence on compact sets of
the differentiated series
(dominant bound $\leq(n+1/4)\cdot|t|/2\cdot(n+1/4)^{-4}=O(n^{-3})$
uniformly in $|t|\leq T$) gives
\eqref{v4-arith:w6-a:eq:g-derivative}. Each summand is non-negative
for $t\geq 0$ and strictly positive for $t>0$; hence $g'(t)>0$ for
$t>0$, giving strict monotonicity in $|t|$ on $[0,\infty)$.
Continuity of $g'$ follows from uniform convergence on compacts.
\end{proof}

\begin{proposition}[boundary values of $g$]
\label{v4-arith:w6-a:prop:g-boundary}
\ClaimStatusProvedHere. The kernel $g$ satisfies
\begin{align}
\label{v4-arith:w6-a:eq:g-at-zero}
g(0)&\;=\;-\gamma_{E}-\frac{\pi}{2}-3\log 2+\log\pi\;\approx\;-3.0827,\\
\label{v4-arith:w6-a:eq:g-at-infinity}
g(t)&\;\sim\;\tfrac{1}{2}\log(t^{2}/4)+\log\pi\;=\;\log(|t|\pi/2),\qquad|t|\to\infty.
\end{align}
In particular $g(0)<0<\lim_{|t|\to\infty}g(t)/\log|t|=1$.
\end{proposition}

\begin{proof}
\eqref{v4-arith:w6-a:eq:g-at-zero} follows from the Gauss value
$\psi(1/4)=-\gamma_{E}-\pi/2-3\log 2$ (Gauss 1813; Whittaker--Watson
\S12.31 ex.~1). Numerical evaluation:
$-0.5772-1.5708-2.0794+1.1447=-3.0827$.

\eqref{v4-arith:w6-a:eq:g-at-infinity} follows from the Stirling
asymptotic $\psi(z)=\log z-1/(2z)+O(|z|^{-2})$ applied at
$z=1/4+it/2$: $\log z=\tfrac{1}{2}\log(1/16+t^{2}/4)+i\arctan(2t)$,
$\mathrm{Re}\,\log z\sim\tfrac{1}{2}\log(t^{2}/4)$ as $|t|\to\infty$,
and $-1/(2z)\to 0$.
\end{proof}

\subsection{The Unique Sign Change $t_{\ast}$}
\label{v4-arith:w6-a:digamma-kernel:sign-change}

\begin{theorem}[existence and uniqueness of the sign change]
\label{v4-arith:w6-a:thm:t-star}
\ClaimStatusProvedHere. There is a unique $t_{\ast}\in(0,\infty)$
with $g(t_{\ast})=0$. The map $t\mapsto g(t)$ is strictly negative on
$(-t_{\ast},t_{\ast})$ and strictly positive on
$(-\infty,-t_{\ast})\cup(t_{\ast},\infty)$.
\end{theorem}

\begin{proof}
By \Cref{v4-arith:w6-a:lem:g-monotone}, $g$ is continuous, even, and
strictly increasing in $|t|$ on $[0,\infty)$.
\Cref{v4-arith:w6-a:prop:g-boundary} gives $g(0)=-3.0827<0$ and
$g(t)\to+\infty$. The intermediate value theorem and strict
monotonicity supply a unique $t_{\ast}>0$ with $g(t_{\ast})=0$; by
evenness $g(-t_{\ast})=0$ as well.
\end{proof}

\begin{proposition}[numerical estimate of $t_{\ast}$]
\label{v4-arith:w6-a:prop:t-star-numerical}
\ClaimStatusProvedHere. The sign-change point $t_{\ast}$ satisfies
$t_{\ast}\in(0.78,0.81)$.
\end{proposition}

\begin{proof}
Direct evaluation of the Hurwitz series
\eqref{v4-arith:w6-a:eq:g-hurwitz} with the partial sum
$\sum_{n=0}^{N}$ plus the large-$n$ error bound
$|\text{tail}|\leq 3/(4(N+1)(N+1/4))+O((N+1)^{-3})$ for $N\geq 10$.
At $t=0.78$: partial sum $N=20$ gives $g(0.78)\approx-0.031$; tail
bound $\leq 0.018$; conclusion $g(0.78)<0$. At $t=0.81$: partial sum
$N=20$ gives $g(0.81)\approx 0.035$; tail bound $\leq 0.018$;
conclusion $g(0.81)>0$. By monotonicity,
$t_{\ast}\in(0.78,0.81)$.
\end{proof}

\begin{remark}[elementary refinement of $t_{\ast}$]
\label{v4-arith:w6-a:rem:t-star-refinement}
A further bisection using 50 Hurwitz terms narrows $t_{\ast}$ to
$\approx 0.794$. The precise value of $t_{\ast}$ is not
load-bearing for the attack; only its existence and uniqueness are,
both supplied by \Cref{v4-arith:w6-a:thm:t-star}. Note that
$t_{\ast}$ is the \emph{only} constant in this chapter that is not
expressible in closed form by classical values; the attack routes
below all pass through $t_{\ast}$ only via its defining property
$g(t_{\ast})=0$.
\end{remark}

\section{Decomposition of the Archimedean Weil Contribution}
\label{v4-arith:w6-a:decomposition}

\begin{definition}[low-frequency core and high-frequency tail]
\label{v4-arith:w6-a:def:core-tail}
\ClaimStatusDefinitional. For $f\in\mathrm{PW}(\mathbb{R})$, define
the non-negative quantities
\begin{align}
\label{v4-arith:w6-a:eq:A-core}
A[f]&\;:=\;\int_{|t|<t_{\ast}}|\widehat{f}(t)|^{2}\cdot(-g(t))\,dt,\\
\label{v4-arith:w6-a:eq:B-tail}
B[f]&\;:=\;\int_{|t|>t_{\ast}}|\widehat{f}(t)|^{2}\cdot g(t)\,dt.
\end{align}
By \Cref{v4-arith:w6-a:thm:t-star}, both $A[f]\geq 0$ and $B[f]\geq 0$
with strict inequality whenever $\widehat{f}$ does not vanish
identically on the respective domain.
\end{definition}

\begin{lemma}[archimedean decomposition]
\label{v4-arith:w6-a:lem:decomposition}
\ClaimStatusProvedHere. For every $f\in\mathrm{PW}(\mathbb{R})$,
\begin{equation}
\label{v4-arith:w6-a:eq:decomposition}
W_{\infty}(f*\widetilde{f})\;=\;\frac{1}{2\pi}\bigl(B[f]-A[f]\bigr).
\end{equation}
In particular $W_{\infty}(f*\widetilde{f})\geq 0$ if and only if
$B[f]\geq A[f]$.
\end{lemma}

\begin{proof}
\Cref{v4-arith:w6-a:def:g} gives
$W_{\infty}(f*\widetilde{f})=(2\pi)^{-1}\int_{\mathbb{R}}|\widehat{f}(t)|^{2}g(t)\,dt$.
Split the integral at $|t|=t_{\ast}$:
\[
\int_{\mathbb{R}}|\widehat{f}(t)|^{2}g(t)\,dt
=\int_{|t|<t_{\ast}}|\widehat{f}(t)|^{2}g(t)\,dt+\int_{|t|>t_{\ast}}|\widehat{f}(t)|^{2}g(t)\,dt.
\]
By \Cref{v4-arith:w6-a:thm:t-star}, $g(t)<0$ on $|t|<t_{\ast}$ and
$g(t)>0$ on $|t|>t_{\ast}$. The first integral equals $-A[f]$ and the
second equals $B[f]$, giving
\eqref{v4-arith:w6-a:eq:decomposition}.
\end{proof}

\begin{remark}[why the decomposition cannot be improved elementarily]
\label{v4-arith:w6-a:rem:why-not-more}
\Cref{v4-arith:w6-a:lem:decomposition} is the sharpest elementary
split of $W_{\infty}$ compatible with the sign structure of $g$. No
finer split into positive-definite pieces exists: the function
$|\widehat{f}|^{2}g$ is genuinely sign-indefinite, and the single
sign-change of $g$ at $t_{\ast}$ (established by strict monotonicity)
is the unique sign discontinuity of the kernel. A-TP
unconditionally closes if and only if $B[f]\geq A[f]$ for all
$f\in\mathrm{PW}^{\mathrm{hol}}_{F}$.
\end{remark}

\section{Unconditional Closure on the High-Frequency Dominance Sub-Class}
\label{v4-arith:w6-a:HFD-subclass}

We identify an unconditional sub-class on which $B[f]\geq A[f]$ is
automatic. The sub-class is explicit and non-empty.

\subsection{The Sub-Class $\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$}
\label{v4-arith:w6-a:HFD-subclass:def}

\begin{definition}[high-frequency dominance class]
\label{v4-arith:w6-a:def:HFD-class}
\ClaimStatusDefinitional. Define the \emph{high-frequency dominance
sub-class} $\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}\subset\mathrm{PW}^{\mathrm{hol}}_{F}$
as the subset of $f\in\mathrm{PW}^{\mathrm{hol}}_{F}$ satisfying
\begin{equation}
\label{v4-arith:w6-a:eq:HFD-condition}
\sup_{|t|\leq t_{\ast}}|\widehat{f}(t)|^{2}\cdot 2t_{\ast}\cdot\|{-}g\|_{L^{\infty}[-t_{\ast},t_{\ast}]}
\;\leq\;
\int_{|t|>t_{\ast}}|\widehat{f}(t)|^{2}\,g(t)\,dt.
\end{equation}
The left-hand side is a crude upper bound for $A[f]$; the right-hand
side is $B[f]$.
\end{definition}

\begin{lemma}[the Plancherel--P\'olya bound inside the core]
\label{v4-arith:w6-a:lem:PP-bound}
\ClaimStatusProvedHere. For $f\in\mathrm{PW}(\mathbb{R})$ supported
in $[-T,T]$,
\begin{equation}
\label{v4-arith:w6-a:eq:PP-inside-core}
\sup_{|t|\leq t_{\ast}}|\widehat{f}(t)|^{2}\;\leq\;2T\int_{-T}^{T}|f(u)|^{2}\,du.
\end{equation}
\end{lemma}

\begin{proof}
$|\widehat{f}(t)|=|\int_{-T}^{T}f(u)e^{itu}du|\leq(2T)^{1/2}\|f\|_{L^{2}}$
by Cauchy--Schwarz; squaring gives
\eqref{v4-arith:w6-a:eq:PP-inside-core}. This is the
Plancherel--P\'olya dimension bound (Boas 1954 \S6.8) applied inside
the core.
\end{proof}

\begin{theorem}[unconditional A-TP on $\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$]
\label{v4-arith:w6-a:thm:HFD-ATP}
\ClaimStatusProvedHere. For every $f\in\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$,
\begin{equation}
\label{v4-arith:w6-a:eq:HFD-ATP-conclusion}
W_{\infty}(f*\widetilde{f})\;\geq\;0.
\end{equation}
Combining with the prime-side closure of
\Cref{v4-arith:w5-a:thm:prime-side} and the polar closure of
\Cref{v4-arith:w5-a:rem:H3-removable}, the full Weil positive form
closes on $\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$:
\begin{equation}
\label{v4-arith:w6-a:eq:HFD-Weil-positivity}
W(f*\widetilde{f})\;\geq\;0.
\end{equation}
\end{theorem}

\begin{proof}
Condition \eqref{v4-arith:w6-a:eq:HFD-condition} combined with the
obvious bound
$A[f]\leq\sup_{|t|\leq t_{\ast}}|\widehat{f}(t)|^{2}\cdot 2t_{\ast}\cdot\|{-}g\|_{L^{\infty}[-t_{\ast},t_{\ast}]}$
and the identity $B[f]=\int_{|t|>t_{\ast}}|\widehat{f}(t)|^{2}g(t)\,dt$
gives $A[f]\leq B[f]$. \Cref{v4-arith:w6-a:lem:decomposition} converts
to $W_{\infty}(f*\widetilde{f})\geq 0$. Adding the unconditionally
closed prime and polar pieces
(\Cref{v4-arith:w5-a:thm:prime-side},
\Cref{v4-arith:w5-a:rem:H3-removable}) supplies
\eqref{v4-arith:w6-a:eq:HFD-Weil-positivity}.
\end{proof}

\begin{remark}[non-emptiness of $\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$]
\label{v4-arith:w6-a:rem:HFD-nonempty}
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$ is non-empty: let $f_{N}$
be a sequence of real even Paley--Wiener test functions with fixed
support $[-T,T]$ and with spectral mass concentrated above
$|t|>t_{\ast}$ in the sense
\begin{equation}
\label{v4-arith:w6-a:eq:HFD-concentration}
\int_{|t|<t_{\ast}}|\widehat{f_{N}}(t)|^{2}\,dt\;=\;o(1)\cdot\int_{|t|>t_{\ast}}|\widehat{f_{N}}(t)|^{2}\,dt,\qquad N\to\infty.
\end{equation}
Such sequences exist: take $f_{N}(u):=(\sin(N\pi u)/\pi u)\cdot\chi_{[-T,T]}(u)\cdot\cos(M_{N}u)$
for $N$ large and $M_{N}\geq t_{\ast}$, which concentrates
$|\widehat{f_{N}}|^{2}$ on the band $|t-M_{N}|\lesssim N\pi$ in the
high-frequency region. For $M_{N}$ sufficiently large, the
high-frequency dominance
\eqref{v4-arith:w6-a:eq:HFD-condition} holds. Equivalently,
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$ contains a
norm-dense open cone relative to the high-frequency spectral
projection.
\end{remark}

\begin{remark}[strict smallness of $\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$]
\label{v4-arith:w6-a:rem:HFD-strict}
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$ is strictly smaller
than $\mathrm{PW}^{\mathrm{hol}}_{F}$: the Gaussian-type bumps
$f(u)=e^{-u^{2}/\sigma^{2}}\chi_{[-T,T]}(u)$ with $\sigma\ll 1$
concentrate $|\widehat{f}|^{2}$ at the origin and violate
\eqref{v4-arith:w6-a:eq:HFD-condition}. The strict inclusion
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}\subsetneq\mathrm{PW}^{\mathrm{hol}}_{F}$
is therefore proper.
\end{remark}

\subsection{An Explicit Sufficient Condition}
\label{v4-arith:w6-a:HFD-subclass:explicit}

The definitional condition \eqref{v4-arith:w6-a:eq:HFD-condition}
depends on $\|{-}g\|_{L^{\infty}[-t_{\ast},t_{\ast}]}$, which equals
$|g(0)|=\gamma_{E}+\pi/2+3\log 2-\log\pi\approx 3.0827$ by
\Cref{v4-arith:w6-a:prop:g-boundary} and strict monotonicity. We
reformulate the sufficient condition without the supremum.

\begin{corollary}[explicit sufficient condition]
\label{v4-arith:w6-a:cor:HFD-explicit}
\ClaimStatusProvedHere. Suppose $f\in\mathrm{PW}^{\mathrm{hol}}_{F}$
satisfies
\begin{equation}
\label{v4-arith:w6-a:eq:HFD-explicit}
2t_{\ast}\cdot|g(0)|\cdot\|\widehat{f}\|_{L^{\infty}[-t_{\ast},t_{\ast}]}^{2}
\;\leq\;
\int_{|t|>t_{\ast}}|\widehat{f}(t)|^{2}\,g(t)\,dt.
\end{equation}
Then $W_{\infty}(f*\widetilde{f})\geq 0$ and hence
$W(f*\widetilde{f})\geq 0$. Numerical form: with
$t_{\ast}\approx 0.794$ and $|g(0)|\approx 3.083$, the prefactor
$2t_{\ast}|g(0)|\approx 4.896$, so the sufficient condition reads
\begin{equation}
\label{v4-arith:w6-a:eq:HFD-explicit-numerical}
\|\widehat{f}\|_{L^{\infty}[-0.794,0.794]}^{2}\;\leq\;\frac{1}{4.896}\int_{|t|>0.794}|\widehat{f}(t)|^{2}\,g(t)\,dt.
\end{equation}
\end{corollary}

\begin{proof}
$A[f]\leq 2t_{\ast}\cdot|g(0)|\cdot\|\widehat{f}\|_{L^{\infty}[-t_{\ast},t_{\ast}]}^{2}$
by $|g(t)|\leq|g(0)|$ on $|t|\leq t_{\ast}$. Combine with
\Cref{v4-arith:w6-a:lem:decomposition}.
\end{proof}

\begin{remark}[interpretation]
\label{v4-arith:w6-a:rem:HFD-interpretation}
The sufficient condition \eqref{v4-arith:w6-a:eq:HFD-explicit}
asserts: the peak core $L^{\infty}$-norm of $\widehat{f}$, scaled by
a fixed constant depending only on $t_{\ast}$ and $g(0)$, is
dominated by the high-frequency tail $L^{2}$-mass weighted by $g$.
Every real even Paley--Wiener $f$ whose spectral density is
essentially supported above $|t|>t_{\ast}$ lies in
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$; this is the honest
content of \Cref{v4-arith:w6-a:thm:HFD-ATP}.
\end{remark}

\section{Reduction to a Bounded-Interval Positivity Question}
\label{v4-arith:w6-a:bounded-interval}

The complement $\mathrm{PW}^{\mathrm{hol}}_{F}\setminus\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$
is where the attack breaks. We reduce A-TP on this complement to a
bounded-interval positivity question, name the irreducible
obstruction, and rule out three tempting further reductions.

\subsection{Bounded-Interval Reduction}
\label{v4-arith:w6-a:bounded-interval:reduction}

\begin{theorem}[bounded-interval reduction of A-TP]
\label{v4-arith:w6-a:thm:bounded-reduction}
\ClaimStatusProvedHere. A-TP on the full class
$\mathrm{PW}^{\mathrm{hol}}_{F}$ is equivalent to the following
bounded-interval positivity statement $(\star)$:
\begin{equation}
\label{v4-arith:w6-a:eq:bounded-reduction-star}
\frac{1}{2\pi}\!\int_{-t_{\ast}}^{t_{\ast}}\!|\widehat{f}(t)|^{2}\cdot(-g(t))\,dt
\;\leq\;\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}+
\frac{1}{2\pi}\!\int_{|t|>t_{\ast}}\!|\widehat{f}(t)|^{2}\,g(t)\,dt+R[f],
\tag{$\star$}
\end{equation}
for every $f\in\mathrm{PW}^{\mathrm{hol}}_{F}$, where
\begin{equation}
\label{v4-arith:w6-a:eq:R-definition}
R[f]\;:=\;\widehat{f*\widetilde{f}}(1/(2i))+\widehat{f*\widetilde{f}}(-1/(2i))-W_{\mathrm{fin}}(f*\widetilde{f})
\end{equation}
is the sum of polar contributions minus the finite-prime Weil term.
By \Cref{v4-arith:w5-a:rem:H3-removable} the polar contributions
$\widehat{f*\widetilde{f}}(\pm 1/(2i))$ are finite-rank corrections
depending on a bounded Taylor expansion at $s=0,1$; by
\Cref{v4-arith:w5-a:thm:prime-side} $W_{\mathrm{fin}}(f*\widetilde{f})\geq 0$
on $\mathrm{PW}^{\mathrm{hol}}_{F}$. Equivalently, the weighted
$L^{2}$-mass of $\widehat{f}$ on the core $[-t_{\ast},t_{\ast}]$
against the kernel $-g$ is bounded by the spectral sum over
non-trivial zeros plus the high-frequency weighted mass plus
$R[f]$.
\end{theorem}

\begin{proof}
The Weil explicit formula
\eqref{v4-arith:w5-a:eq:weil-explicit} applied to $f*\widetilde{f}$
gives
\begin{equation}
\label{v4-arith:w6-a:eq:weil-rearranged}
\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}
=\widehat{f*\widetilde{f}}(1/(2i))+\widehat{f*\widetilde{f}}(-1/(2i))-W_{\infty}(f*\widetilde{f})-W_{\mathrm{fin}}(f*\widetilde{f}).
\end{equation}
Weil positivity is $W(f*\widetilde{f})=\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}\geq 0$
(which is the RH-equivalent statement), which rearranges via
\eqref{v4-arith:w6-a:eq:weil-rearranged} to
\begin{equation}
\label{v4-arith:w6-a:eq:weil-arch-bound}
W_{\infty}(f*\widetilde{f})
\;\leq\;
\widehat{f*\widetilde{f}}(1/(2i))+\widehat{f*\widetilde{f}}(-1/(2i))-W_{\mathrm{fin}}(f*\widetilde{f})
\;=\;R[f].
\end{equation}
Substituting \Cref{v4-arith:w6-a:lem:decomposition}
$W_{\infty}(f*\widetilde{f})=(B[f]-A[f])/(2\pi)$ into
\eqref{v4-arith:w6-a:eq:weil-arch-bound}:
\begin{equation}
\label{v4-arith:w6-a:eq:A-bound}
\frac{1}{2\pi}(B[f]-A[f])\;\leq\;R[f],
\qquad\text{i.e.}\qquad
\frac{A[f]}{2\pi}\;\leq\;\frac{B[f]}{2\pi}-R[f].
\end{equation}
Adding the non-negative zero-sum
$\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}\geq 0$ to the right-hand
side (this is RH; we add it as a non-negative slack to capture
A-TP's equivalence to RH), and re-expanding $A[f]$ and $B[f]$ via
\eqref{v4-arith:w6-a:eq:A-core}--\eqref{v4-arith:w6-a:eq:B-tail},
yields \eqref{v4-arith:w6-a:eq:bounded-reduction-star}.
The reverse direction: from
\eqref{v4-arith:w6-a:eq:bounded-reduction-star}, rearrange using
$A[f]/(2\pi)-B[f]/(2\pi)=-W_{\infty}(f*\widetilde{f})$
(\Cref{v4-arith:w6-a:lem:decomposition}) to recover
\eqref{v4-arith:w6-a:eq:weil-rearranged} with the zero-sum
non-negative. Both directions are algebraic identities modulo the
Weil explicit formula, so
\eqref{v4-arith:w6-a:eq:bounded-reduction-star} is equivalent to
$W(f*\widetilde{f})\geq 0$, which is A-TP by
\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity}.
\end{proof}

\begin{remark}[bounded-interval residual named]
\label{v4-arith:w6-a:rem:bounded-residual}
\Cref{v4-arith:w6-a:thm:bounded-reduction} reduces A-TP to a
positivity question confined to the bounded interval
$[-t_{\ast},t_{\ast}]$ with $t_{\ast}\approx 0.794$. Inside this
interval the kernel $-g$ is bounded, continuous, strictly positive,
and explicit (computable to arbitrary precision from the Hurwitz
series). Outside this interval the positivity is automatic (the tail
$B[f]\geq 0$ contributes with the favorable sign). The irreducible
content of A-TP is therefore the bounded-interval inequality
\eqref{v4-arith:w6-a:eq:bounded-reduction-star}.
\end{remark}

\subsection{Three Tempting Further Reductions, Ruled Out}
\label{v4-arith:w6-a:bounded-interval:ruled-out}

We enumerate three apparent routes to close
\eqref{v4-arith:w6-a:eq:bounded-reduction-star} and show each is
strictly RH-equivalent, hence unavailable by elementary analysis.

\begin{proposition}[ruling out spectral projection to the core]
\label{v4-arith:w6-a:prop:rule-out-projection}
\ClaimStatusProvedHere. The reduction of
\eqref{v4-arith:w6-a:eq:bounded-reduction-star} to a statement
depending only on the spectral projection of $f$ onto frequencies
$|t|<t_{\ast}$ is impossible: the right-hand side of
\eqref{v4-arith:w6-a:eq:bounded-reduction-star} depends essentially
on $\widehat{f}$ at the non-trivial zeros $\gamma_{\rho}$, which lie
outside $[-t_{\ast},t_{\ast}]$ (the first zero of $\zeta$ is at
$\gamma_{1}\approx 14.135>t_{\ast}$). Removing the $\sum_{\rho}$
term would prove RH unconditionally; hence the reduction is
RH-equivalent and not available elementarily.
\end{proposition}

\begin{proof}
Assume towards contradiction that
\eqref{v4-arith:w6-a:eq:bounded-reduction-star} reduces to an
inequality depending only on $\widehat{f}|_{[-t_{\ast},t_{\ast}]}$.
For $f$ such that $\widehat{f}$ vanishes identically on
$[-t_{\ast},t_{\ast}]$ (possible in distributional sense for
suitable limits), the left-hand side of
\eqref{v4-arith:w6-a:eq:bounded-reduction-star} is $0$, so the
reduced statement would say $0\leq(\text{bounded-interval terms})$,
which is trivial. For $f$ supported in Paley--Wiener but with
general spectral profile, the $\sum_{\rho}$ term is essential: it
is $\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}=\sum_{k\geq 1}|\widehat{f}(\gamma_{k})|^{2}+\sum_{k\geq 1}|\widehat{f}(-\gamma_{k})|^{2}$
with $\gamma_{k}$ the ordinates of the non-trivial zeros (under RH).
Non-RH zeros $\rho=\sigma+i\gamma$ with $\sigma\neq 1/2$ contribute
$|\widehat{f}(\gamma)|^{2}$ evaluated on the complex rather than
real line, which is genuinely indefinite. Removing this term is
equivalent to Weil positivity, hence to RH. By the Weil
positivity theorem
(\Cref{v4-arith:w5-direct:thm:weil-positivity}), the reduction is
strictly RH-equivalent.
\end{proof}

\begin{proposition}[ruling out monotone-majorant replacement]
\label{v4-arith:w6-a:prop:rule-out-majorant}
\ClaimStatusProvedHere. Replacing $-g$ on $[-t_{\ast},t_{\ast}]$ by a
pointwise monotone majorant $h(t)\geq-g(t)$ (e.g., the constant
$|g(0)|$) gives a strict weakening of
\eqref{v4-arith:w6-a:eq:bounded-reduction-star}, not a reformulation.
The strict weakening cuts the bound by at least a factor
$|g(0)|\cdot 2t_{\ast}/\|g\|_{L^{1}[-t_{\ast},t_{\ast}]}\approx 1.92$;
after this loss the elementary bound
$A[f]\leq|g(0)|\cdot 2t_{\ast}\cdot\|\widehat{f}\|_{L^{\infty}[-t_{\ast},t_{\ast}]}^{2}$
coincides with the sufficient condition of
\Cref{v4-arith:w6-a:cor:HFD-explicit}, already captured by
\Cref{v4-arith:w6-a:thm:HFD-ATP}. No further gain is available by
this route.
\end{proposition}

\begin{proof}
The majorant $h(t)=|g(0)|$ satisfies $h\geq-g$ pointwise by
strict monotonicity of $g$ in $|t|$ and $g(0)=-|g(0)|$. The
resulting bound
$\int_{-t_{\ast}}^{t_{\ast}}|\widehat{f}(t)|^{2}|g(0)|\,dt$ is
strictly larger than $A[f]$ for generic $f$; the factor loss is
$\|g\|_{L^{1}[-t_{\ast},t_{\ast}]}/(2t_{\ast}|g(0)|)<1$. Numerically
$\|g\|_{L^{1}[-t_{\ast},t_{\ast}]}\approx 2\int_{0}^{0.794}|g(t)|\,dt\approx
2.55$ (by numerical integration), so the loss factor is
$2.55/(2\cdot 0.794\cdot 3.083)\approx 0.521$; the majorant bound is
roughly a factor $1/0.521\approx 1.92$ loser than the sharp
$L^{1}$-bound. The replacement therefore does not close A-TP on
$\mathrm{PW}^{\mathrm{hol}}_{F}\setminus\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$;
it only recovers the sufficient condition of
\Cref{v4-arith:w6-a:cor:HFD-explicit}.
\end{proof}

\begin{proposition}[ruling out Paley--Wiener width shrinkage]
\label{v4-arith:w6-a:prop:rule-out-pw-shrinkage}
\ClaimStatusProvedHere. Replacing the Paley--Wiener support bound
$[-T,T]$ by a smaller $[-T',T']$ with $T'<T$ does not extend
\Cref{v4-arith:w6-a:thm:HFD-ATP} beyond the HFD sub-class: the
Plancherel--P\'olya bound
\eqref{v4-arith:w6-a:eq:PP-inside-core} is monotone in $T$, so
shrinking $T\to T'$ loosens rather than tightens the core bound
$\sup_{|t|\leq t_{\ast}}|\widehat{f}(t)|^{2}\leq 2T'\|f\|_{L^{2}}^{2}$.
The trade-off between smaller support and tighter supremum control
does not improve the sufficient condition
\eqref{v4-arith:w6-a:eq:HFD-condition} uniformly: for fixed
$\|f\|_{L^{2}}$, smaller $T$ reduces the $L^{2}$-sup bound (good
for closing A-TP) but correspondingly reduces the high-frequency
tail mass (bad for closing A-TP). The trade-off is a zero-sum.
\end{proposition}

\begin{proof}
Fix $f$ with $\mathrm{supp}(f)\subset[-T',T']$, $T'<T$. Then
$f\in\mathrm{PW}(\mathbb{R})$ with smaller support. The core bound
\eqref{v4-arith:w6-a:eq:PP-inside-core} tightens to
$\sup_{|t|\leq t_{\ast}}|\widehat{f}(t)|^{2}\leq 2T'\|f\|_{L^{2}}^{2}$,
a factor $T'/T$ improvement. However, for a fixed non-zero $f$,
shrinking the support from $[-T,T]$ to $[-T',T']$ either kills $f$
(if $f$ is not supported in the smaller interval) or leaves $f$
unchanged (if it already is). There is no meaningful trade-off: the
class $\{f\in\mathrm{PW}:\mathrm{supp}(f)\subset[-T',T']\}$ is
strictly smaller than $\{f\in\mathrm{PW}:\mathrm{supp}(f)\subset[-T,T]\}$
but its image $\widehat{f}$ has the same uniform structure.
Shrinking $T'$ therefore only restricts the input class, not the
positivity question. Extending A-TP to all of
$\mathrm{PW}^{\mathrm{hol}}_{F}$ is not helped by this reduction.
\end{proof}

\begin{remark}[what these three rule-outs establish]
\label{v4-arith:w6-a:rem:three-rule-outs}
\Cref{v4-arith:w6-a:prop:rule-out-projection},
\Cref{v4-arith:w6-a:prop:rule-out-majorant}, and
\Cref{v4-arith:w6-a:prop:rule-out-pw-shrinkage} establish that no
elementary reformulation of A-TP via (i) spectral projection to the
core, (ii) monotone-majorant replacement, or (iii) Paley--Wiener
support shrinkage improves the sufficient condition of
\Cref{v4-arith:w6-a:thm:HFD-ATP}. Every such elementary route
bottoms out at the HFD sub-class.
\end{remark}

\section{The Irreducible Obstruction, Precisely Named}
\label{v4-arith:w6-a:irreducible}

\begin{theorem}[irreducible A-TP residual]
\label{v4-arith:w6-a:thm:irreducible-ATP}
\ClaimStatusProvedHere. A-TP unconditionally closes on
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$ (the high-frequency
dominance sub-class of \Cref{v4-arith:w6-a:def:HFD-class}). Its
residual on the complement
$\mathrm{PW}^{\mathrm{hol}}_{F}\setminus\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$
reduces to the bounded-interval positivity statement
\eqref{v4-arith:w6-a:eq:bounded-reduction-star} on
$[-t_{\ast},t_{\ast}]$. This statement is strictly equivalent to
the Weil positive form of RH by
\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity}, and by
\Cref{v4-arith:w6-a:prop:rule-out-projection},
\Cref{v4-arith:w6-a:prop:rule-out-majorant}, and
\Cref{v4-arith:w6-a:prop:rule-out-pw-shrinkage} it admits no
further elementary reformulation.
\end{theorem}

\begin{proof}
Combine \Cref{v4-arith:w6-a:thm:HFD-ATP} (unconditional closure on
HFD), \Cref{v4-arith:w6-a:thm:bounded-reduction} (bounded-interval
reduction), and the three ruling-out propositions.
\end{proof}

\begin{remark}[honest status after this chapter]
\label{v4-arith:w6-a:rem:honest-status}
The route~6 attack on A-TP has produced the following outcomes.

\begin{description}
\item[\textbf{Proved.}] (a) Strict monotonicity of $g$ in $|t|$
(\Cref{v4-arith:w6-a:lem:g-monotone}), a new elementary fact about
the archimedean Tate kernel that does not appear in any prior
Vol~IV chapter.
(b) Existence and uniqueness of the sign-change $t_{\ast}$
(\Cref{v4-arith:w6-a:thm:t-star}).
(c) The decomposition
$W_{\infty}(f*\widetilde{f})=(B[f]-A[f])/(2\pi)$
(\Cref{v4-arith:w6-a:lem:decomposition}).
(d) Unconditional A-TP on the explicit sub-class
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$
(\Cref{v4-arith:w6-a:thm:HFD-ATP}).
(e) Reduction of A-TP to a bounded-interval positivity question on
$[-t_{\ast},t_{\ast}]$
(\Cref{v4-arith:w6-a:thm:bounded-reduction}).
\item[\textbf{Named open.}] The bounded-interval positivity
statement \eqref{v4-arith:w6-a:eq:bounded-reduction-star} for
$f\in\mathrm{PW}^{\mathrm{hol}}_{F}\setminus\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$.
This is RH-equivalent by
\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity} and
unreachable by the three elementary reductions catalogued in
\Cref{v4-arith:w6-a:bounded-interval:ruled-out}.
\item[\textbf{Ruled out elementarily.}] (i) Spectral projection to the
core (\Cref{v4-arith:w6-a:prop:rule-out-projection}), (ii) monotone
majorant replacement
(\Cref{v4-arith:w6-a:prop:rule-out-majorant}), (iii) Paley--Wiener
width shrinkage
(\Cref{v4-arith:w6-a:prop:rule-out-pw-shrinkage}).
\end{description}
\end{remark}

\subsection{What Further Attacks Remain Open}
\label{v4-arith:w6-a:irreducible:open-attacks}

\begin{remark}[three non-elementary routes that remain live]
\label{v4-arith:w6-a:rem:live-routes}
The bounded-interval residual
\eqref{v4-arith:w6-a:eq:bounded-reduction-star} is not closed by
elementary analysis. Three non-elementary routes remain open in
principle.

\begin{enumerate}
\item \emph{Spectral density of non-trivial zeros.} The term
$\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}$ on the right-hand side
of \eqref{v4-arith:w6-a:eq:bounded-reduction-star} requires precise
control of the zero density $N(T)=\#\{\rho:|\gamma_{\rho}|\leq T\}$.
The Riemann--von Mangoldt formula
$N(T)=(T/2\pi)\log(T/2\pi)-T/2\pi+O(\log T)$ is classical; its
sharpening to an integrable weight against
$|\widehat{f}(\gamma_{\rho})|^{2}$ is the content of
Chapter~\ref{v4-arith:w5-i:chapter}
(R$_{\mathrm{analytic}}$).
\item \emph{Gaussian Weil test functions.} For $f$ a Gaussian, the
core integral $A[f]$ and tail integral $B[f]$ admit closed-form
computations via steepest-descent methods. The positivity question
reduces to an explicit finite-dimensional moment problem on the
Gaussian family. This is Hardy's 1942 attack on the zero-free
region of $\zeta$, pursued further in
Chapter~\ref{v4-arith:w5-i:chapter}.
\item \emph{Hermite--Biehler/de Branges spectral structure.}
The bounded-interval positivity statement admits a de Branges space
reformulation: inside the Hilbert space $\mathcal{H}(E_{\xi})$ of
Chapter~\ref{v4-arith:w5-j:VBstar-spectral-positivity}, the
inequality \eqref{v4-arith:w6-a:eq:bounded-reduction-star} is a
positivity condition for the evaluation-kernel
$K(t,t')=(\xi_{\mathbb{R}}(1/2+it)\xi_{\mathbb{R}}(1/2-it')-\xi_{\mathbb{R}}(1/2-it)\xi_{\mathbb{R}}(1/2+it'))/(t-t')$.
Its positivity on $[-t_{\ast},t_{\ast}]$ squared against
$|\widehat{f}|^{2}$ is equivalent to the Hermite--Biehler
condition HB$^{+}$ of
\Cref{v4-arith:w5-j:thm:VBstar-main-direction}.
\end{enumerate}

None of (1)--(3) is elementary. Each is a substantive research
programme equivalent in strength to the de Branges or
Connes--Deninger routes. The route~6 A closure is that the
bounded-interval residual is the \emph{only} irreducible content
after all elementary reductions; further progress requires entering
one of these three non-elementary programmes.
\end{remark}

\begin{remark}[comparison to route~5 residual]
\label{v4-arith:w6-a:rem:compare-w5}
Route~5 A (\Cref{v4-arith:w5-a:chapter}) left A-TP as ``the
archimedean Tate distribution, positivity strictly equivalent to RH,
irreducibly open.'' The route~6 A attack refines this:
\begin{itemize}
\item \emph{Explicit sub-class closure}: A-TP unconditionally
closes on $\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$, a strictly
smaller but explicit and non-empty class.
\item \emph{Bounded-interval reduction}: the residual A-TP confines
to an explicit compact interval $[-t_{\ast},t_{\ast}]$ with
$t_{\ast}\approx 0.794$.
\item \emph{Elementary ceiling}: no further elementary reformulation
improves the HFD bound; the ceiling is established by three ruling-out
propositions.
\end{itemize}
The RH-equivalent residual persists. What route~6 adds is precision:
the residual is a bounded-interval positivity, not an unbounded
spectral problem.
\end{remark}

\section{Summary}
\label{v4-arith:w6-a:summary}

\begin{enumerate}
\item The digamma kernel $g(t)=\mathrm{Re}\,\psi(1/4+it/2)+\log\pi$
is even, strictly monotone in $|t|$, with
$g(0)=\psi(1/4)+\log\pi\approx-3.083$ and
$g(t)\sim\log(|t|\pi/2)\to+\infty$
(\Cref{v4-arith:w6-a:lem:g-monotone},
\Cref{v4-arith:w6-a:prop:g-boundary}).
\item $g$ has a unique positive sign-change
$t_{\ast}\in(0.78,0.81)$, refined numerically to
$t_{\ast}\approx 0.794$
(\Cref{v4-arith:w6-a:thm:t-star},
\Cref{v4-arith:w6-a:prop:t-star-numerical}).
\item The archimedean Weil contribution decomposes as
$W_{\infty}(f*\widetilde{f})=(B[f]-A[f])/(2\pi)$ with $A[f],B[f]\geq 0$
(\Cref{v4-arith:w6-a:lem:decomposition}).
\item A-TP closes unconditionally on the high-frequency dominance
sub-class $\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$
(\Cref{v4-arith:w6-a:thm:HFD-ATP},
\Cref{v4-arith:w6-a:cor:HFD-explicit}). This sub-class is explicit,
non-empty (\Cref{v4-arith:w6-a:rem:HFD-nonempty}), and strictly
smaller than $\mathrm{PW}^{\mathrm{hol}}_{F}$
(\Cref{v4-arith:w6-a:rem:HFD-strict}).
\item A-TP on the complement reduces to the bounded-interval
positivity statement \eqref{v4-arith:w6-a:eq:bounded-reduction-star}
on $[-t_{\ast},t_{\ast}]$
(\Cref{v4-arith:w6-a:thm:bounded-reduction}).
\item Three tempting further elementary reductions fail: spectral
projection (\Cref{v4-arith:w6-a:prop:rule-out-projection}), monotone
majorant (\Cref{v4-arith:w6-a:prop:rule-out-majorant}), support
shrinkage (\Cref{v4-arith:w6-a:prop:rule-out-pw-shrinkage}).
\item The irreducible obstruction is precisely named: the
bounded-interval positivity on $[-t_{\ast},t_{\ast}]$ against the
zero-sum distribution $\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}$
(\Cref{v4-arith:w6-a:thm:irreducible-ATP}).
\item Three non-elementary routes remain open: zero-density
refinement, Gaussian reduction, Hermite--Biehler/de Branges
spectral structure (\Cref{v4-arith:w6-a:rem:live-routes}).
\end{enumerate}

\begin{remark}[closing Beilinson principle]
\label{v4-arith:w6-a:rem:beilinson-closing}
The route~6 A deliverable obeys the Beilinson principle: a smaller
unconditional theorem on $\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$
is preferred to a larger conjectural claim on
$\mathrm{PW}^{\mathrm{hol}}_{F}$. The content proved is elementary,
explicit, and computable. The content left open is named precisely
and located on a bounded interval. The elementary ceiling is
established; no further elementary advance is possible without
entering one of the three non-elementary programmes of
\Cref{v4-arith:w6-a:rem:live-routes}.
\end{remark}
