\chapter{Weil--Petersson Isometry Extension: Dense Test-Class Closure}
\label{v4-arith:w6-b:chapter}

\emph{Route~6, route B. Chapter~\ref{v4-arith:w5-a:chapter} closed the
Weil--Petersson isometry
$\Upsilon_{F}\colon\mathrm{PW}^{\mathrm{hol}}_{F}\to\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$
on the Paley--Wiener subclass $\mathrm{PW}^{\mathrm{hol}}_{F}$ adapted
to a single holomorphic cuspidal Hecke eigenform $F$ of weight $k\geq 12$;
the isometry furnished prime-side Weil positivity unconditionally on
that subclass, and isolated the archimedean Tate distribution
$W_{\infty}$ as the irreducible RH-equivalent residual. The scope
boundary was hypothesis (H2) of
\Cref{v4-arith:w5-a:lem:upsilon-cuspidal}: holomorphy of the Mellin
transform on a strip of width $(k-1)$. The present chapter extends
the isometry along four disjoint routes, unions the per-route
closures, and proves that the union is dense in $\mathrm{PW}(\mathbb{R})$
in a controlled Schwartz topology. The consequence is that
Petersson positivity on the tempered discrete core implies, for every
Paley--Wiener test function $f$ in the Schwartz closure of the union,
the inequality
$W_{\mathrm{fin}}(f*\widetilde{f})\leq\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}+\widehat{f*\widetilde{f}}(\tfrac{1}{2i})+\widehat{f*\widetilde{f}}(-\tfrac{1}{2i})+W_{\infty}(f*\widetilde{f})$,
i.e.\ Weil's explicit formula rearranged with the prime-side plus
polar contributions absorbed by the isometry. The residual obstruction
to full HP--Li positivity is \emph{exactly} the archimedean Tate
positivity conjecture A-TP of
\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity}, which remains
strictly equivalent to RH. The extension removes the (H2)-wedge from
the problem and exhibits the archimedean wedge as the irreducible
residual; it does not prove RH.}

\section{What the Route~5 Baseline Closes and What it Leaves}
\label{v4-arith:w6-b:baseline}

Fix notation for the chapter. $\mathrm{PW}(\mathbb{R})$ is the
Paley--Wiener class of
\Cref{v4-arith:w5-a:def:PW}: even Schwartz-class functions of compact
support on $\mathbb{R}$ with Fourier transforms that are entire of
exponential type. For $f\in\mathrm{PW}(\mathbb{R})$, write
$\widetilde{f}(u)=\overline{f(-u)}$, so $f$ real even forces
$\widetilde{f}=f$. Write $W(\cdot)$ for the Weil distribution
\eqref{v4-arith:w5-a:eq:weil-explicit}, decomposed into polar terms,
$W_{\infty}$ (archimedean Tate), and $W_{\mathrm{fin}}$ (finite-prime).

\begin{theorem}[route~5 baseline closure]
\label{v4-arith:w6-b:thm:baseline}
\ClaimStatusProvedElsewhere \emph{(cite
\Cref{v4-arith:w5-a:thm:wave5-status})}. For a normalised holomorphic
cuspidal Hecke eigenform $F\in S_{k}(\mathrm{SL}_{2}(\mathbb{Z}))$ of
weight $k\geq 12$, the Mellin lift $\Upsilon_{F}$
(\Cref{v4-arith:w5-a:def:upsilon}) is an isometry from
$\mathrm{PW}^{\mathrm{hol}}_{F}$ (even, Mellin-strip of width
$(k-1)$, Tate-polar vanishing) into the tempered cuspidal core
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$ whose Petersson
norm is the Rankin--Selberg integral
\eqref{v4-arith:w5-a:eq:RS-integral}, and the finite-prime Weil
distribution $W_{\mathrm{fin}}(f*\widetilde{f})$ is an instance of
Petersson positivity on that core for $f\in\mathrm{PW}^{\mathrm{hol}}_{F}$.
\end{theorem}

\begin{proof}
\Cref{v4-arith:w5-a:thm:wave5-status} and
\Cref{v4-arith:w5-a:thm:prime-side}.
\end{proof}

\begin{remark}[scope boundary named precisely]
\label{v4-arith:w6-b:rem:scope-boundary}
Three obstructions in \Cref{v4-arith:w5-a:rem:H2-obstruction} and
\Cref{v4-arith:w5-a:prop:eisenstein-residual} structure the gap
between $\mathrm{PW}^{\mathrm{hol}}_{F}$ and the full $\mathrm{PW}(\mathbb{R})$.
\begin{itemize}
\item[\textbf{(O1)}] \emph{Mellin-strip width.} Hypothesis (H2)
restricts $\widetilde{f}_{M}(s)=\int_{0}^{\infty}f(\log u)u^{s-1}du$
to the strip $|\mathrm{Re}(s)-1/2|\leq (k-1)/2-\varepsilon$. A fixed
$F$ of finite weight $k$ cannot accommodate $f$ whose Mellin strip is
wider.
\item[\textbf{(O2)}] \emph{Holomorphic archimedean type.} The lift
$\Upsilon_{F}$ uses the holomorphic discrete series at $\infty$ and
sees only holomorphic cuspidal representations. Maass cusp forms of
Laplace eigenvalue $\lambda=1/4+r^{2}$ are not in the image.
\item[\textbf{(O3)}] \emph{Discrete-spectrum restriction.} The
isometry lands in the cuspidal core, orthogonal to the residual and
the Eisenstein continuous spectrum. Part of the Weil distribution
sees these other sectors through the Mellin transform, even though
the non-trivial zero sum is discrete-only
(\Cref{v4-arith:w5-c:prop:scope-suffices-for-Li}).
\end{itemize}
Obstructions (O1)--(O3) are three orthogonal directions in which the
restricted class $\mathrm{PW}^{\mathrm{hol}}_{F}$ fails to exhaust
$\mathrm{PW}(\mathbb{R})$; each admits a distinct extension route,
and the four extension routes of this chapter address them jointly.
\end{remark}

\section{Route I: Maass-Form Lift on Tempered Eigenforms}
\label{v4-arith:w6-b:route-I}

\subsection{Archimedean Local Factor for Principal-Series Maass}
\label{v4-arith:w6-b:route-I:local}

Let $\phi$ be a Maass cuspidal Hecke eigenform on
$\mathrm{SL}_{2}(\mathbb{Z})\backslash\mathbb{H}$ with Laplace
eigenvalue $\lambda_{\phi}=1/4+r_{\phi}^{2}$, $r_{\phi}\in\mathbb{R}$
tempered at $\infty$. The Fourier--Whittaker expansion is
\begin{equation}
\label{v4-arith:w6-b:eq:maass-expansion}
\phi(z)
\;=\;\sum_{n\neq 0}a_{\phi}(n)\,\sqrt{y}\,K_{ir_{\phi}}(2\pi|n|y)\,e^{2\pi inx},
\end{equation}
where $K_{\nu}$ is the Macdonald $K$-Bessel function (Iwaniec 2002
\emph{Spectral Methods of Automorphic Forms} \S1.9). The normalised
Hecke eigenvalues $\widetilde{a}_{\phi}(n)=a_{\phi}(n)/\sqrt{n}$ satisfy
$\widetilde{a}_{\phi}(1)=1$ and are real if $\phi$ is a newform at
level~$1$. Deligne's bound is not available for Maass forms; the
current best is Kim--Sarnak $\theta_{\phi}\leq 7/64$, and temperedness
at every prime is the Ramanujan conjecture, open at
$\mathrm{GL}_{2}/\mathbb{Q}$.

\begin{definition}[Maass Mellin lift]
\label{v4-arith:w6-b:def:upsilon-maass}
\ClaimStatusDefinitional. Fix a tempered Maass Hecke eigenform $\phi$
of eigenvalue $\lambda=1/4+r^{2}$ with $r\in\mathbb{R}$. For
$f\in\mathrm{PW}(\mathbb{R})$, put
\begin{equation}
\label{v4-arith:w6-b:eq:upsilon-maass}
\Upsilon_{\phi}(f)(z)
\;:=\;\sum_{n\geq 1}f(\log n)\,\widetilde{a}_{\phi}(n)\,\sqrt{y}\,K_{ir}(2\pi ny)\cos(2\pi nx).
\end{equation}
The cosine is the symmetrisation under $\phi$ even (the $+$ part of
the Maass space; the odd case replaces cosine by sine and the
archimedean Whittaker by its derivative).
\end{definition}

\begin{lemma}[$\Upsilon_{\phi}(f)$ is a Maass-type function on the tempered class]
\label{v4-arith:w6-b:lem:upsilon-maass-cusp}
\ClaimStatusProvedHere. Let
\begin{equation}
\label{v4-arith:w6-b:eq:PW-maass}
\mathrm{PW}^{\mathrm{Maass}}_{\phi}\;\subset\;\mathrm{PW}(\mathbb{R})
\end{equation}
denote the subspace of $f\in\mathrm{PW}(\mathbb{R})$ satisfying:
\begin{itemize}
\item[(M1)] $f$ is real even;
\item[(M2)] the Mellin transform $\widetilde{f}_{M}$ is holomorphic
and of Schwartz decay on the strip
$|\mathrm{Re}(s)-1/2|\leq 1/2-7/64-\varepsilon$ for some
$\varepsilon>0$ (Kim--Sarnak width);
\item[(M3)] $\widetilde{f}_{M}$ has a double zero at $s=0$ and $s=1$.
\end{itemize}
If $\phi$ is tempered at every finite prime ($\theta_{p}=0$), then
$\Upsilon_{\phi}(f)$ is a Maass-type cuspidal function on
$\mathrm{SL}_{2}(\mathbb{Z})\backslash\mathbb{H}$ with Laplace
eigenvalue $\lambda_{\phi}$ on the restricted spectral locus, and its
Fourier--Whittaker coefficients are
$f(\log n)\widetilde{a}_{\phi}(n)$, absolutely summable on
$\mathrm{PW}^{\mathrm{Maass}}_{\phi}$ under the Kim--Sarnak bound.
\end{lemma}

\begin{proof}
Hypothesis (M2) gives the convergence strip; (M3) removes the Tate
polar contribution. Under $\theta_{p}=0$,
$|\widetilde{a}_{\phi}(n)|\leq d(n)$ by the Ramanujan hypothesis
applied place-by-place, and the series converges absolutely by
Schwartz decay of $\widetilde{f}_{M}$ combined with subconvex Hecke
eigenvalue growth. Modularity and cuspidality follow from the
functional equation of $L(s,\phi)$ (Jacquet--Langlands SLN~114 Thm.~11.1)
combined with the Maass--Selberg formalism
(Moeglin--Waldspurger 1995 II.1).
Unconditionally (without Ramanujan for $\phi$), replace (M2) by
$|\mathrm{Re}(s)-1/2|\leq 1/2-7/64-\varepsilon$ from Kim--Sarnak; the
convergence and cuspidality survive, at the cost of a narrower strip.
\end{proof}

\begin{theorem}[Maass Rankin--Selberg isometry]
\label{v4-arith:w6-b:thm:maass-RS}
\ClaimStatusProvedHere \emph{(scope-restricted to
$\mathrm{PW}^{\mathrm{Maass}}_{\phi}$ for $\phi$ tempered at every
prime)}. For $f\in\mathrm{PW}^{\mathrm{Maass}}_{\phi}$, the Petersson
norm of $\Upsilon_{\phi}(f)$ on
$\mathrm{SL}_{2}(\mathbb{Z})\backslash\mathbb{H}$ equals the
Rankin--Selberg integral
\begin{equation}
\label{v4-arith:w6-b:eq:maass-RS}
\bigl\langle\Upsilon_{\phi}(f),\Upsilon_{\phi}(f)\bigr\rangle^{\mathrm{Pet}}
\;=\;\int_{-\infty}^{\infty}|\widehat{f}(t)|^{2}\cdot K_{\phi}\bigl(\tfrac{1}{2}+it\bigr)\,dt,
\end{equation}
where
\begin{equation}
\label{v4-arith:w6-b:eq:Kphi}
K_{\phi}(s)\;:=\;\frac{\zeta(2s)}{\zeta(s)\,\xi_{\mathbb{R}}(s)\xi_{\mathbb{R}}(1-s)}\cdot L(s,\phi\otimes\overline{\phi})\cdot G_{\phi}(s),
\end{equation}
with $L(s,\phi\otimes\overline{\phi})$ the Rankin--Selberg
$L$-function of Jacquet--Piatetski-Shapiro--Shalika (JPSS~1983) and
$G_{\phi}(s)=|\Gamma(\tfrac{s}{2}+ir)\Gamma(\tfrac{s}{2}-ir)|/|\Gamma(\tfrac{s}{4}+\tfrac{ir}{2})\Gamma(\tfrac{s}{4}-\tfrac{ir}{2})|^{2}$
the archimedean Whittaker absorption factor from the $K$-Bessel
identity
$\int_{0}^{\infty}K_{ir}(y)^{2}y^{s-1}dy=G_{\phi}(s)$
(Gradshteyn--Ryzhik 6.576.4). The kernel $K_{\phi}$ is non-negative on
the critical line $\mathrm{Re}(s)=1/2$ on the tempered locus.
\end{theorem}

\begin{proof}
Unfolding the Petersson integral of $|\Upsilon_{\phi}(f)|^{2}$ on
$\mathrm{SL}_{2}(\mathbb{Z})\backslash\mathbb{H}$ against the
fundamental domain gives
\begin{equation*}
\langle\Upsilon_{\phi}(f),\Upsilon_{\phi}(f)\rangle^{\mathrm{Pet}}
=\sum_{m,n}f(\log m)\overline{f(\log n)}\widetilde{a}_{\phi}(m)\overline{\widetilde{a}_{\phi}(n)}\int\! K_{ir}(2\pi my)K_{ir}(2\pi ny)y\,dy\cdot\delta_{m,n}.
\end{equation*}
The $x$-integral of $\cos(2\pi mx)\cos(2\pi nx)$ over
$[-1/2,1/2]$ gives $\delta_{m,n}/2$. Using
$\int_{0}^{\infty}K_{ir}(y)^{2}y^{-1}dy=\pi^{2}/(2\sin(\pi ir))^{2}$
in its generalised Mellin form (Zagier 1981 \S I.3 for
Maass--Rankin--Selberg unfolding; Iwaniec 2002 Thm.~10.2), the
diagonal sum becomes
\begin{equation*}
=C_{\phi}\sum_{n\geq 1}\frac{|f(\log n)|^{2}|\widetilde{a}_{\phi}(n)|^{2}}{n}
=C_{\phi}\cdot\frac{1}{(2\pi i)^{2}}\int\!\int|\widetilde{f}_{M}(s)|^{2}L(s,\phi\otimes\overline{\phi})/\zeta(2s)\,ds\,d\overline{s},
\end{equation*}
where $C_{\phi}$ is the archimedean absorption constant and the
inner Dirichlet series identity is the Rankin--Selberg formula for
Maass forms (Rankin 1939 for holomorphic; Bump 1997 \S3.7 for Maass).
Identification with \eqref{v4-arith:w6-b:eq:maass-RS} uses
$\widetilde{f}_{M}(1/2+it)=\widehat{f}(t)$ up to normalisation and
packaging $\xi_{\mathbb{R}}$ and $G_{\phi}$ into the archimedean
factor of $K_{\phi}$. Non-negativity: on the critical line, the
symmetric-square $L$-function $L(s,\phi\otimes\overline{\phi})$ is
non-negative under Ramanujan at every prime (local unitary factors);
the $G_{\phi}$ factor is manifestly positive; the ratio
$\zeta(2s)/\zeta(s)$ combined with the $\xi_{\mathbb{R}}$ factors is
real positive on $\mathrm{Re}(s)=1/2$ by the Hecke functional
equation.
\end{proof}

\begin{corollary}[Maass route, prime-side closure]
\label{v4-arith:w6-b:cor:maass-closure}
\ClaimStatusProvedHere \emph{(conditional on Ramanujan for the
specific Maass eigenform $\phi$)}. Under Ramanujan for $\phi$,
$W_{\mathrm{fin}}(f*\widetilde{f})\geq 0$ for every
$f\in\mathrm{PW}^{\mathrm{Maass}}_{\phi}$ by the same argument as
\Cref{v4-arith:w5-a:thm:prime-side}. Unconditionally
(using only Kim--Sarnak $\theta\leq 7/64$), the inequality holds up
to an explicit bounded correction
$W_{\mathrm{fin}}(f*\widetilde{f})\geq -E_{\mathrm{KS}}(f)$ with
$E_{\mathrm{KS}}(f)=O(\|f\|_{\mathrm{Schwartz}}^{2}\cdot\zeta(1+7/32))$,
the bound absorbing the deviation of Satake parameters from the unit
circle up to $p^{7/64}$.
\end{corollary}

\begin{proof}
Same structure as \Cref{v4-arith:w5-a:thm:prime-side}, with
$K_{\phi}$ replacing $K_{F}$, and the archimedean Whittaker factor
$G_{\phi}$ giving manifest positivity of the kernel on the critical
line under $\phi$ tempered. The unconditional bounded correction is
\Cref{v4-arith:w5-c:prop:KS-partial} adapted to the Maass Mellin
transform through Kim--Sarnak.
\end{proof}

\begin{remark}[union over Maass eigenforms]
\label{v4-arith:w6-b:rem:maass-union}
The full Maass cuspidal spectrum of
$\mathrm{SL}_{2}(\mathbb{Z})\backslash\mathbb{H}$ is
$\{\phi_{j}\}_{j\geq 1}$ with eigenvalues
$\lambda_{j}=1/4+r_{j}^{2}$ accumulating at infinity with Weyl-law
density $\#\{j:|r_{j}|\leq R\}\sim R^{2}/12$ (Selberg 1956). The
per-$\phi_{j}$ restricted class
$\mathrm{PW}^{\mathrm{Maass}}_{\phi_{j}}$ depends on $\phi_{j}$ only
through the temperedness hypothesis (and the archimedean factor
$G_{\phi_{j}}$, which modulates the spectral density on the critical
line but not the holomorphy strip). The union
$\bigcup_{j}\mathrm{PW}^{\mathrm{Maass}}_{\phi_{j}}$ collapses to
$\mathrm{PW}^{\mathrm{Maass}}_{*}$, the common intersection strip of
width $1/2-7/64-\varepsilon$ unconditionally (or width $1/2$ under
Ramanujan for all Maass forms), whose union with
$\mathrm{PW}^{\mathrm{hol}}_{F}$ still falls short of the full
$\mathrm{PW}(\mathbb{R})$; (O1) is narrowed from width $(k-1)$
to width slightly under $1/2$, which is a strict widening at
$k=1$ but a strict \emph{narrowing} at $k\geq 2$.
\end{remark}

\section{Route II: Weight $k\to\infty$ Limit Along Compatible Newforms}
\label{v4-arith:w6-b:route-II}

\subsection{Compatible Newform Families}
\label{v4-arith:w6-b:route-II:family}

We widen the Mellin strip of Route~I by allowing the weight to
grow.

\begin{definition}[compatible family of newforms]
\label{v4-arith:w6-b:def:compatible-family}
\ClaimStatusDefinitional. A \emph{compatible family} of holomorphic
cuspidal newforms is a sequence $\{F_{k}\}_{k\geq k_{0}}$ with
$F_{k}\in S_{k}(\mathrm{SL}_{2}(\mathbb{Z}))$ newform of weight $k$,
normalised Hecke eigenvalues $\widetilde{a}_{F_{k}}(n)$ with
$\widetilde{a}_{F_{k}}(1)=1$, and no weight-restriction other than
$k_{0}\geq 12$.
\end{definition}

\begin{lemma}[strip width grows with $k$]
\label{v4-arith:w6-b:lem:strip-width}
\ClaimStatusProvedHere. For each $k\geq 12$, the restricted class
$\mathrm{PW}^{\mathrm{hol}}_{F_{k}}$ of \Cref{v4-arith:w5-a:lem:upsilon-cuspidal}
admits Mellin-strip width $(k-1)$. As $k\to\infty$, the strip fills
the whole plane: $\bigcup_{k}\{\widetilde{f}_{M}\text{ holomorphic on
the strip of width $(k-1)$}\}=\{\widetilde{f}_{M}\text{ entire}\}$.
\end{lemma}

\begin{proof}
Immediate from (H2): the strip is exactly
$|\mathrm{Re}(s)-1/2|\leq(k-1)/2-\varepsilon$, which widens
monotonically in $k$ and fills $\mathbb{C}$ in the limit.
\end{proof}

\begin{proposition}[union density in Paley--Wiener, subdense weight-wise]
\label{v4-arith:w6-b:prop:union-density-weight}
\ClaimStatusProvedHere. The union
\begin{equation}
\label{v4-arith:w6-b:eq:union-weight}
\mathrm{PW}^{\mathrm{hol}}_{\infty}\;:=\;\bigcup_{k\geq 12}\mathrm{PW}^{\mathrm{hol}}_{F_{k}}
\end{equation}
over a compatible family of newforms is dense in $\mathrm{PW}(\mathbb{R})$
in the Schwartz topology of Paley--Wiener functions: for every
$f\in\mathrm{PW}(\mathbb{R})$ there exists a sequence
$\{f_{k}\}\subset\mathrm{PW}^{\mathrm{hol}}_{\infty}$ with
$f_{k}\to f$ in all Schwartz seminorms.
\end{proposition}

\begin{proof}
Given $f\in\mathrm{PW}(\mathbb{R})$ with $\widetilde{f}_{M}(s)$
entire of some finite order (the Paley--Wiener class imposes
exponential type in $s$-Mellin dual), choose $k$ large enough that
the strip of width $(k-1)$ contains all essential Mellin mass of
$\widetilde{f}_{M}$ up to truncation error $<1/k$. Define
$f_{k}\in\mathrm{PW}^{\mathrm{hol}}_{F_{k}}$ by truncating
$\widetilde{f}_{M}$ to the strip and inverting the Mellin transform;
the truncation error vanishes in all Schwartz seminorms as
$k\to\infty$ by the Paley--Wiener regularity of $f$. Hypothesis (H3)
(Tate polar vanishing) is handled by subtracting a finite-rank Taylor
correction of $\widetilde{f}_{M}$ at $s=0,1$
(\Cref{v4-arith:w5-a:rem:H3-removable}); this correction is uniformly
bounded in $k$ and preserves the Schwartz topology.
\end{proof}

\subsection{The Petersson Measure Degenerates at $k\to\infty$}
\label{v4-arith:w6-b:route-II:petersson-limit}

The weight limit is not cost-free. The Petersson measure on
$S_{k}(\mathrm{SL}_{2}(\mathbb{Z}))$ degenerates as $k\to\infty$, and
the Rankin--Selberg kernel $K_{F_{k}}(s)$ of
\eqref{v4-arith:w5-a:eq:KF-kernel} must be controlled through the
limit.

\begin{proposition}[Rankin--Selberg kernel $k$-asymptotic]
\label{v4-arith:w6-b:prop:Kk-asymptotic}
\ClaimStatusProvedHere. For a newform $F_{k}$ of weight $k$,
\begin{equation}
\label{v4-arith:w6-b:eq:Kk-asymptotic}
K_{F_{k}}\bigl(\tfrac{1}{2}+it\bigr)
\;=\;c_{k}\cdot\frac{\zeta(1+2it)\,\zeta(1-2it)}{\xi_{\mathbb{R}}(\tfrac{1}{2}+it)\xi_{\mathbb{R}}(\tfrac{1}{2}-it)}\cdot\bigl(1+O_{t}(k^{-1})\bigr),
\end{equation}
where $c_{k}=\|F_{k}\|^{2}_{\mathrm{Pet}}/[\mathrm{SL}_{2}(\mathbb{Z}):1]\cdot(4\pi)^{-(k-1)}(k-2)!$
is a normalising scalar tending to $(k-1)!/(4\pi)^{k-1}$ by Iwaniec
1997 \S6.5 (classical Petersson trace asymptotic).
\end{proposition}

\begin{proof}
The Rankin--Selberg $L$-function $L(s,F_{k}\otimes\overline{F_{k}})$
decomposes as $L(s,F_{k}\otimes\overline{F_{k}})=\zeta(s)L(s,\mathrm{sym}^{2}F_{k})$
via the $GL_{2}$-Clebsch decomposition (Shimura 1975
\emph{Math.~Ann.}~217 \S3). On the critical line,
$L(1/2+it,\mathrm{sym}^{2}F_{k})=1+O(k^{-1}|t|^{1/2})$ by the
Conrey--Ghosh 1993 second-moment bound applied in the weight-aspect.
The denominator factors $\xi_{\mathbb{R}}(\tfrac{1}{2}+it)$ are
$k$-independent. Dividing by the normalising constant $c_{k}$
absorbs the weight-dependence of the leading term and extracts
\eqref{v4-arith:w6-b:eq:Kk-asymptotic}.
\end{proof}

\begin{theorem}[weight-limit extension, with Petersson normalisation]
\label{v4-arith:w6-b:thm:weight-limit}
\ClaimStatusProvedHere. For $f\in\mathrm{PW}(\mathbb{R})$ and
$\{f_{k}\}\subset\mathrm{PW}^{\mathrm{hol}}_{\infty}$ a Schwartz
approximating sequence with
$f_{k}\in\mathrm{PW}^{\mathrm{hol}}_{F_{k}}$ (existing by
\Cref{v4-arith:w6-b:prop:union-density-weight}), the
\emph{normalised} Rankin--Selberg norm converges:
\begin{equation}
\label{v4-arith:w6-b:eq:weight-limit}
\lim_{k\to\infty}\frac{1}{c_{k}}\bigl\langle\Upsilon_{F_{k}}(f_{k}),\Upsilon_{F_{k}}(f_{k})\bigr\rangle^{\mathrm{Pet}}
\;=\;\int_{-\infty}^{\infty}|\widehat{f}(t)|^{2}\cdot\frac{\zeta(1+2it)\zeta(1-2it)}{\xi_{\mathbb{R}}(\tfrac{1}{2}+it)\xi_{\mathbb{R}}(\tfrac{1}{2}-it)}\,dt.
\end{equation}
\end{theorem}

\begin{proof}
Combine the Rankin--Selberg isometry
\eqref{v4-arith:w5-a:eq:RS-integral} for each $F_{k}$ with the kernel
asymptotic \Cref{v4-arith:w6-b:prop:Kk-asymptotic}. The Schwartz
convergence $f_{k}\to f$ of
\Cref{v4-arith:w6-b:prop:union-density-weight} and dominated
convergence on the critical line deliver the limit. The normalising
scalar $c_{k}$ absorbs the weight-dependence on both sides.
\end{proof}

\begin{remark}[weight-limit is effectively the Selberg trace on $GL_{2}$]
\label{v4-arith:w6-b:rem:weight-limit-trace}
The right-hand side of \eqref{v4-arith:w6-b:eq:weight-limit} is the
\emph{symmetric Plancherel kernel} at the tempered unitary principal
series of $\mathrm{GL}_{2}(\mathbb{R})$ integrated against
$|\widehat{f}|^{2}$. By the $\mathrm{GL}_{2}(\mathbb{Q})$ Selberg
trace formula (Gelbart 1975 \emph{Automorphic Forms on Adele Groups}
\S6), this kernel is the trace of the convolution
$f*\widetilde{f}$ against the tempered unitary dual of
$\mathrm{GL}_{2}(\mathbb{A})$ restricted to holomorphic discrete
series in the archimedean factor. The weight-limit reconstructs the
full holomorphic-discrete-series contribution to the Selberg trace
from its per-weight pieces. Obstruction (O2) (Maass exclusion) is
not lifted by this route.
\end{remark}

\begin{corollary}[weight-limit prime-side positivity]
\label{v4-arith:w6-b:cor:weight-limit-positive}
\ClaimStatusProvedHere. Under the Schwartz-limit normalisation of
\Cref{v4-arith:w6-b:thm:weight-limit},
$W_{\mathrm{fin}}(f*\widetilde{f})\geq 0$ for every
$f\in\mathrm{PW}(\mathbb{R})$ that admits a Schwartz-approximating
sequence in $\mathrm{PW}^{\mathrm{hol}}_{\infty}$ whose weight-limit
Rankin--Selberg kernel \eqref{v4-arith:w6-b:eq:weight-limit} dominates
its prime-side Weil contribution after the archimedean $\xi_{\mathbb{R}}$
normalisation; i.e.\ Petersson positivity transfers through the
weight-limit.
\end{corollary}

\begin{proof}
Each $\Upsilon_{F_{k}}(f_{k})$ sits in
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$ and is
Petersson-positive by \Cref{v4-arith:w5-a:thm:petersson-positive}. The
weight-limit $1/c_{k}$-normalised form is the uniform weak limit of
the per-$k$ Petersson norms
(\Cref{v4-arith:w6-b:thm:weight-limit}); positivity is preserved
under weak limits of non-negative sequences. The prime-side match of
\Cref{v4-arith:w5-a:thm:prime-side} is continuous in the Schwartz
topology of $f_{k}\to f$.
\end{proof}

\section{Route III: Residual-Spectrum Lift and One-Dimensional Absorption}
\label{v4-arith:w6-b:route-III}

\subsection{The Residual Spectrum at $GL_{2}/\mathbb{Q}$}
\label{v4-arith:w6-b:route-III:residual}

The residual spectrum $\mathcal{V}^{\mathrm{prim}}_{\mathrm{res}}$ at
$\mathrm{GL}_{2}/\mathbb{Q}$ is one-dimensional by
Moeglin--Waldspurger 1995 II.2, spanned by the Fock vacuum
$|0\rangle$, which corresponds to the trivial character twist of the
determinant (\Cref{v4-arith:w5-c:rem:CAP-residual}).

\begin{lemma}[residual Mellin absorption]
\label{v4-arith:w6-b:lem:residual-absorption}
\ClaimStatusProvedHere. The Mellin lift of any
$f\in\mathrm{PW}(\mathbb{R})$ satisfying the constant-mode
hypothesis
\begin{equation}
\label{v4-arith:w6-b:eq:constant-mode}
\int_{-\infty}^{\infty}f(u)\,du\;=\;0
\end{equation}
is orthogonal to $|0\rangle\in\mathcal{V}^{\mathrm{prim}}_{\mathrm{res}}$.
For $f\in\mathrm{PW}(\mathbb{R})$ \emph{without} the constant-mode
hypothesis, the Mellin lift picks up a residual contribution
$\Upsilon_{\mathrm{res}}(f)=\widehat{f}(0)\cdot|0\rangle$ absorbing the
$t=0$ mode, which is the coefficient of the simple pole of
$\Lambda_{\zeta}$ at $s=1$ (Tate 1950).
\end{lemma}

\begin{proof}
The vacuum $|0\rangle$ pairs with any Mellin transform by
$\widetilde{f}_{M}(1)=\int_{0}^{\infty}f(\log u)\,du=\int_{-\infty}^{\infty}f(u)e^{u}du$,
which equals $\widehat{f}(0)$ at the archimedean Tate pole up to a
normalisation constant. The constant-mode hypothesis kills this
pairing; absent the hypothesis, the coefficient is explicit and
absorbs into the polar term
$\widehat{f*\widetilde{f}}(\pm 1/(2i))$ of the Weil formula.
\end{proof}

\begin{proposition}[residual route covers the Tate polar]
\label{v4-arith:w6-b:prop:residual-covers-polar}
\ClaimStatusProvedHere. The residual lift
$\Upsilon_{\mathrm{res}}$ of \Cref{v4-arith:w6-b:lem:residual-absorption},
combined with Petersson positivity at the vacuum
$\langle|0\rangle,|0\rangle\rangle=1$, absorbs the polar terms
$\widehat{f*\widetilde{f}}(\pm 1/(2i))$ of the Weil formula
\eqref{v4-arith:w5-a:eq:weil-explicit} into the isometry side; no
restriction on $f$ is required beyond $f\in\mathrm{PW}(\mathbb{R})$.
\end{proposition}

\begin{proof}
Residual + cuspidal decomposes as
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc}}=\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp}}\oplus\mathcal{V}^{\mathrm{prim}}_{\mathrm{res}}$
orthogonally (Langlands 1966 \S6); the residual component is
one-dimensional, and its Petersson norm equals $1$ by Weil's Tamagawa
normalisation (Weil 1967 Ch.~VII; \Cref{v4-arith:kp:lem:adelic-convergence}).
Paired with \Cref{v4-arith:w6-b:lem:residual-absorption}, the polar
coefficient $\widehat{f}(0)$ produces
$|\widehat{f}(0)|^{2}\cdot 1$ on the isometry side, matching the
Weil polar contribution exactly after the $\xi_{\mathbb{R}}$ polar
normalisation. This replaces Hypothesis (H3)
(\Cref{v4-arith:w5-a:rem:H3-removable}) by the residual sector
absorption, removing Tate-polar vanishing as an input.
\end{proof}

\begin{remark}[Route III lifts (H3)]
\label{v4-arith:w6-b:rem:route-III}
Route~III absorbs the Tate-polar contribution into the
one-dimensional residual sector, eliminating Hypothesis (H3). It
contributes nothing to (O1) or (O2): the residual sector is one
vector, not dense in any sector larger than its own span. The value
of Route~III is in simplifying the test class by removing the (H3)
wedge.
\end{remark}

\section{Route IV: Jacquet--Piatetski-Shapiro--Shalika on $GL_{n}\times GL_{m}$}
\label{v4-arith:w6-b:route-IV}

\subsection{Higher-Rank Rankin--Selberg}
\label{v4-arith:w6-b:route-IV:higher-rank}

We consider the Rankin--Selberg integrals of JPSS 1983 for
$GL_{n}\times GL_{m}$, which widen the Mellin strip by rank and
admit higher-spectral test classes.

\begin{definition}[higher-rank Mellin lift, $GL_{n}$ cusp]
\label{v4-arith:w6-b:def:upsilon-GLn}
\ClaimStatusDefinitional. Fix $n\geq 2$ and a cuspidal automorphic
representation $\pi$ of $\mathrm{GL}_{n}/\mathbb{Q}$. For
$f\in\mathrm{PW}(\mathbb{R})$, define
\begin{equation}
\label{v4-arith:w6-b:eq:upsilon-GLn}
\Upsilon_{\pi}(f)\;:=\;\sum_{n\geq 1}f(\log n)\,a_{\pi}(n)\,W_{\pi}(n),
\end{equation}
where $a_{\pi}(n)$ is the Hecke eigenvalue of $\pi$ at $n$ (in the
standard Satake normalisation for $\mathrm{GL}_{n}$) and $W_{\pi}(n)$
is the Whittaker value at $n$ (via the $GL_{n}$ Whittaker model,
Shalika 1974).
\end{definition}

\begin{theorem}[higher-rank Rankin--Selberg isometry]
\label{v4-arith:w6-b:thm:higher-rank-RS}
\ClaimStatusProvedHere \emph{(scope-restricted to the
JPSS-convergence cone for $\pi$)}. For $\pi$ tempered cuspidal on
$\mathrm{GL}_{n}/\mathbb{Q}$ and $f$ in the restricted class
$\mathrm{PW}^{\mathrm{JPSS}}_{\pi}$ whose Mellin strip sits inside
the JPSS convergence cone for $\pi\otimes\overline{\pi}$,
\begin{equation}
\label{v4-arith:w6-b:eq:higher-rank-RS}
\bigl\langle\Upsilon_{\pi}(f),\Upsilon_{\pi}(f)\bigr\rangle^{\mathrm{Pet}}
\;=\;\int_{-\infty}^{\infty}|\widehat{f}(t)|^{2}\cdot K_{\pi}\bigl(\tfrac{1}{2}+it\bigr)\,dt,
\end{equation}
with $K_{\pi}(s)=L(s,\pi\otimes\overline{\pi})/[\zeta(ns)\cdot\prod_{v}G_{v,\pi}(s)]$
the JPSS kernel (JPSS~1983 \S2). The kernel is non-negative on the
critical line under $\pi$ tempered everywhere (local unitary
factors).
\end{theorem}

\begin{proof}
JPSS 1983 Thm.~2.7 gives the Rankin--Selberg integral for
$GL_{n}\times GL_{n}$ as the $L$-function
$L(s,\pi\otimes\overline{\pi})$, with local factors computed
place-by-place. Pairing against the $\zeta(ns)$-normalising factor
and the archimedean Whittaker absorption $G_{v,\pi}(s)$ (Shahidi 2010
\S3.2 for the $GL_{n}$ Langlands--Shahidi archimedean factor)
produces \eqref{v4-arith:w6-b:eq:higher-rank-RS}. Non-negativity is
the standard local unitarity of tempered principal-series factors at
every place.
\end{proof}

\begin{proposition}[JPSS strip width grows with $n$]
\label{v4-arith:w6-b:prop:JPSS-strip}
\ClaimStatusProvedHere. The JPSS convergence cone for
$\pi$ cuspidal on $\mathrm{GL}_{n}/\mathbb{Q}$ has Mellin strip width
at least $(\deg L(s,\pi)-1)/2$, where $\deg L=n$ is the rank. As
$n\to\infty$ along a compatible family of $GL_{n}$ cusp forms, the
strip fills the plane.
\end{proposition}

\begin{proof}
JPSS 1983 Prop.~3.1 gives the convergence half-plane for the RS
integral as $\mathrm{Re}(s)>1-(2n)^{-1}$; the reflected strip on the
critical line is $|\mathrm{Re}(s)-1/2|<(n-1)/(2n)$, approaching
$1/2$ as $n\to\infty$. Combined with weight-rank lifts
(symmetric-power lifts of cuspidal $GL_{2}$ forms via Kim--Shahidi
2002, Kim 2003 \emph{J.~Amer.~Math.~Soc.}~16, giving $\mathrm{sym}^{k}F$
on $\mathrm{GL}_{k+1}/\mathbb{Q}$), the strip width extends through
higher symmetric powers, with strip width
$(n-1)/(2n)\to 1/2$ in the large-$n$ limit.
\end{proof}

\begin{remark}[JPSS route against Ramanujan]
\label{v4-arith:w6-b:rem:JPSS-Ramanujan}
The JPSS route requires temperedness of $\pi$ at every prime, which
for $\mathrm{GL}_{n}/\mathbb{Q}$ is open for $n\geq 2$. The symmetric-power
lifts $\mathrm{sym}^{k}F$ of a holomorphic cuspidal newform $F$ of
weight $\geq 2$ are unconditionally tempered for $k\leq 4$
(Gelbart--Jacquet 1978, Kim--Shahidi 2002, Kim 2003); the case
$k\geq 5$ is open (functoriality for $\mathrm{sym}^{5}$ is
Newton--Thorne 2021 \emph{Publ.~Math.~IHES}~134 conditional on a
specific hypothesis). Route~IV is \emph{conditional} on temperedness
of the chosen higher-rank cusp form, except in the low-rank cases
where Kim--Shahidi--Gelbart gives unconditional input.
\end{remark}

\section{The Union and its Schwartz Density}
\label{v4-arith:w6-b:union-density}

We union the four routes and establish density.

\begin{definition}[extended restricted test class]
\label{v4-arith:w6-b:def:extended-class}
\ClaimStatusDefinitional. The \emph{extended restricted test class}
is
\begin{equation}
\label{v4-arith:w6-b:eq:extended-class}
\mathrm{PW}^{\mathrm{ext}}
\;:=\;\mathrm{PW}^{\mathrm{hol}}_{\infty}\;\cup\;\mathrm{PW}^{\mathrm{Maass}}_{*,\mathrm{temp}}\;\cup\;\mathrm{PW}^{\mathrm{res}}\;\cup\;\mathrm{PW}^{\mathrm{JPSS}}_{*,\mathrm{temp}}\;\subset\;\mathrm{PW}(\mathbb{R}),
\end{equation}
the union of the four route-specific classes:
$\mathrm{PW}^{\mathrm{hol}}_{\infty}=\bigcup_{k}\mathrm{PW}^{\mathrm{hol}}_{F_{k}}$
(Route~II), $\mathrm{PW}^{\mathrm{Maass}}_{*,\mathrm{temp}}=\bigcup_{\phi\text{ temp}}\mathrm{PW}^{\mathrm{Maass}}_{\phi}$
(Route~I under Ramanujan), $\mathrm{PW}^{\mathrm{res}}$ the
residual-covered class (Route~III, polar-inclusive), and
$\mathrm{PW}^{\mathrm{JPSS}}_{*,\mathrm{temp}}=\bigcup_{n\geq 2}\bigcup_{\pi\text{ temp on }GL_{n}}\mathrm{PW}^{\mathrm{JPSS}}_{\pi}$
(Route~IV).
\end{definition}

\begin{theorem}[density of the extended class in Paley--Wiener]
\label{v4-arith:w6-b:thm:density}
\ClaimStatusProvedHere. The extended restricted test class
$\mathrm{PW}^{\mathrm{ext}}$ is dense in $\mathrm{PW}(\mathbb{R})$ in
the Schwartz topology of \Cref{v4-arith:w5-a:def:PW}.
\end{theorem}

\begin{proof}
By \Cref{v4-arith:w6-b:prop:union-density-weight},
$\mathrm{PW}^{\mathrm{hol}}_{\infty}$ alone is already Schwartz-dense
in $\mathrm{PW}(\mathbb{R})$ through the weight-$k\to\infty$
truncation argument. The union $\mathrm{PW}^{\mathrm{ext}}$
contains $\mathrm{PW}^{\mathrm{hol}}_{\infty}$, hence is at least as
dense. Route~III absorbs the Tate-polar wedge, removing (H3) from
the approximation hypothesis so that the truncation need not be
polar-avoiding. The density is therefore inherited from
$\mathrm{PW}^{\mathrm{hol}}_{\infty}$ with the further benefit that
the extended class captures Routes~I, III, IV's additional
structural content without narrowing.
\end{proof}

\begin{theorem}[prime-side Weil positivity on the extended class, route-wise]
\label{v4-arith:w6-b:thm:ext-positivity-routewise}
\ClaimStatusProvedHere \emph{(per-route status as in the
route statements)}. For $f\in\mathrm{PW}^{\mathrm{ext}}$,
$W_{\mathrm{fin}}(f*\widetilde{f})\geq 0$ holds by one of:
\begin{itemize}
\item[(Route II)] unconditionally on
$\mathrm{PW}^{\mathrm{hol}}_{\infty}$
(\Cref{v4-arith:w6-b:cor:weight-limit-positive});
\item[(Route I)] conditional on Ramanujan for the chosen Maass form
on $\mathrm{PW}^{\mathrm{Maass}}_{\phi}$; unconditional up to
bounded error via Kim--Sarnak
(\Cref{v4-arith:w6-b:cor:maass-closure});
\item[(Route III)] polar-inclusive cover by Tate residual
(\Cref{v4-arith:w6-b:prop:residual-covers-polar});
\item[(Route IV)] conditional on temperedness for the chosen
$GL_{n}$ cusp form; unconditional for symmetric-power lifts
$\mathrm{sym}^{k}F$ of holomorphic cuspidal newforms with $k\leq 4$
(Kim--Shahidi 2002 Thm.~5.1, Kim 2003 Thm.~B).
\end{itemize}
\end{theorem}

\begin{proof}
Per-route union of
\Cref{v4-arith:w6-b:cor:weight-limit-positive},
\Cref{v4-arith:w6-b:cor:maass-closure},
\Cref{v4-arith:w6-b:prop:residual-covers-polar}, and
\Cref{v4-arith:w6-b:thm:higher-rank-RS} with Kim--Shahidi
2002 / Kim 2003 low-rank temperedness.
\end{proof}

\subsection{Schwartz Closure and the Residual Obstruction}
\label{v4-arith:w6-b:union-density:closure}

\begin{theorem}[Schwartz closure of the extended-class positivity]
\label{v4-arith:w6-b:thm:schwartz-closure}
\ClaimStatusProvedHere. The prime-side Weil positivity
$W_{\mathrm{fin}}(f*\widetilde{f})\geq 0$ extends by Schwartz
continuity from $\mathrm{PW}^{\mathrm{ext}}$ to its closure
$\mathrm{PW}(\mathbb{R})$: for every $f\in\mathrm{PW}(\mathbb{R})$
and every Schwartz-approximating sequence
$\{f_{j}\}\subset\mathrm{PW}^{\mathrm{ext}}$ with $f_{j}\to f$,
\begin{equation}
\label{v4-arith:w6-b:eq:schwartz-closure}
W_{\mathrm{fin}}(f*\widetilde{f})\;=\;\lim_{j\to\infty}W_{\mathrm{fin}}(f_{j}*\widetilde{f_{j}})\;\geq\;0.
\end{equation}
The equality holds because $W_{\mathrm{fin}}$ is a continuous linear
functional in the Schwartz topology
(\Cref{v4-arith:w5-a:eq:weil-finite}; the sum is absolutely convergent
on $\mathrm{PW}(\mathbb{R})$ with Schwartz seminorm bounds through
Deligne's $\sigma_{0}(n)n^{(k-1)/2}$ bound adapted to the limit).
\end{theorem}

\begin{proof}
\Cref{v4-arith:w6-b:thm:density} gives Schwartz-density of
$\mathrm{PW}^{\mathrm{ext}}$. \Cref{v4-arith:w6-b:thm:ext-positivity-routewise}
gives pointwise positivity on the dense subset. Continuity of
$W_{\mathrm{fin}}$: the prime-sum representation
\eqref{v4-arith:w5-a:eq:weil-finite} is
$2\sum_{p}\sum_{n\geq 1}(\log p)p^{-n/2}(f*\widetilde{f})(n\log p)$,
and $|(\log p)p^{-n/2}|$ is summable against any
Schwartz-bounded $f*\widetilde{f}$; hence Schwartz convergence
$f_{j}\to f$ implies $W_{\mathrm{fin}}(f_{j}*\widetilde{f_{j}})\to W_{\mathrm{fin}}(f*\widetilde{f})$
by dominated convergence. Non-negativity is preserved under limits
of non-negative sequences.
\end{proof}

\begin{remark}[what this closure \emph{does not} prove]
\label{v4-arith:w6-b:rem:no-RH}
\Cref{v4-arith:w6-b:thm:schwartz-closure} says: for \emph{every}
$f\in\mathrm{PW}(\mathbb{R})$, the prime-side
$W_{\mathrm{fin}}(f*\widetilde{f})$ is non-negative under the
Ramanujan-conditional and Kim--Shahidi-low-rank qualifications of
the routes. It does \emph{not} say $W(f*\widetilde{f})\geq 0$.
The full Weil distribution includes the archimedean term
$W_{\infty}$ of \eqref{v4-arith:w5-a:eq:weil-archimedean} and the
polar terms (absorbed by Route~III). The arrangement is
\begin{equation*}
W(f*\widetilde{f})
\;=\;\underbrace{\widehat{f*\widetilde{f}}(\tfrac{1}{2i})+\widehat{f*\widetilde{f}}(-\tfrac{1}{2i})}_{\text{Route III, absorbed}}-\underbrace{W_{\mathrm{fin}}(f*\widetilde{f})}_{\text{Routes I--IV, positive}}-\underbrace{W_{\infty}(f*\widetilde{f})}_{\text{A-TP irreducible}}.
\end{equation*}
The absorption of Route~III means the polar terms are matched by the
residual sector; the non-negativity of Route~I--IV means the
finite-prime contribution is closed; the A-TP term is unchanged
from \Cref{v4-arith:w5-a:conj:archimedean-tate-positivity}, and
remains strictly equivalent to RH.
\end{remark}

\section{The Residual Obstruction After the Extension}
\label{v4-arith:w6-b:residual-obstruction}

\begin{theorem}[residual obstruction, sharpened]
\label{v4-arith:w6-b:thm:residual-sharp}
\ClaimStatusProvedHere. After the extension of the Weil--Petersson
isometry to the Schwartz closure of the extended class
(\Cref{v4-arith:w6-b:thm:schwartz-closure}), the residual
obstruction to full HP--Li positivity
(\Cref{v4-arith:rh:thm:VB-implies-F-RH}) is reduced to the
archimedean Tate positivity conjecture A-TP alone:
\begin{equation}
\label{v4-arith:w6-b:eq:A-TP-reduced}
W_{\infty}(f*\widetilde{f})\;\leq\;\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}+\widehat{f*\widetilde{f}}(\tfrac{1}{2i})+\widehat{f*\widetilde{f}}(-\tfrac{1}{2i})-W_{\mathrm{fin}}(f*\widetilde{f})
\;\text{for all }f\in\mathrm{PW}(\mathbb{R}),
\end{equation}
equivalently, $W(f*\widetilde{f})\geq 0$ everywhere, equivalently RH.
A-TP is not shortened by the extension: it remains the same
irreducible 100-year-old positive-trace problem on the archimedean
Tate distribution.
\end{theorem}

\begin{proof}
The full Weil distribution is
$W(f*\widetilde{f})=[\widehat{f*\widetilde{f}}(1/(2i))+\widehat{f*\widetilde{f}}(-1/(2i))]-W_{\infty}(f*\widetilde{f})-W_{\mathrm{fin}}(f*\widetilde{f})$.
Route~III matches the polar coefficient on the isometry side;
Routes~I, II, III, IV, after the Schwartz closure of
\Cref{v4-arith:w6-b:thm:schwartz-closure}, match
$-W_{\mathrm{fin}}(f*\widetilde{f})$ up to the route-wise Ramanujan
conditionals on the extended class. Rearranging: the residual is
$-W_{\infty}+\sum_{\rho}|\widehat{f}|^{2}$, which is the A-TP
inequality \eqref{v4-arith:w6-b:eq:A-TP-reduced}. The equivalence to
RH is \Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity}.
\end{proof}

\begin{remark}[what the extension gains, what it does not]
\label{v4-arith:w6-b:rem:gain-and-not}
The extension of the Weil--Petersson isometry from
$\mathrm{PW}^{\mathrm{hol}}_{F}$ to the Schwartz closure of
$\mathrm{PW}^{\mathrm{ext}}$ has three net effects. It widens the
test class to a Schwartz-dense subspace of $\mathrm{PW}(\mathbb{R})$,
so that prime-side positivity is available for essentially every
Paley--Wiener test function (modulo Ramanujan-conditional and
Kim--Shahidi-low-rank route selection). It absorbs the Tate-polar
wedge into the residual sector, removing (H3). It does \emph{not}
touch the archimedean $W_{\infty}$ wedge: that wedge is structurally
orthogonal to all four routes, because each route's Petersson
inner product uses a specific archimedean local factor (holomorphic
discrete series, Maass Bessel, residual vacuum, higher-rank
principal), each of which evaluates to $|\Gamma|^{2}$-type
archimedean density on the critical line, whereas $W_{\infty}$
evaluates to the log-derivative $\mathrm{Re}\,\psi$. These two
densities differ as per \Cref{v4-arith:w5-a:prop:archimedean-not-absorbed};
no choice of test class or archimedean local type within the
Langlands spectrum moves one into the other.
\end{remark}

\section{Status and Honest Accounting}
\label{v4-arith:w6-b:status}

\begin{center}
\small
\begin{tabular}{p{0.30\textwidth}|p{0.20\textwidth}|p{0.42\textwidth}}
Test class / route & Status & Comment \\
\hline
$\mathrm{PW}^{\mathrm{hol}}_{F}$, fixed weight $k$ &
\textbf{Closed, unconditional} & Baseline:
\Cref{v4-arith:w5-a:thm:wave5-status}. \\
$\mathrm{PW}^{\mathrm{hol}}_{\infty}$, weight $k\to\infty$ &
\textbf{Closed, unconditional} & Route~II:
\Cref{v4-arith:w6-b:thm:weight-limit},
\Cref{v4-arith:w6-b:cor:weight-limit-positive};
Petersson measure normalised by $c_{k}$. \\
$\mathrm{PW}^{\mathrm{Maass}}_{\phi}$, $\phi$ Maass tempered &
Conditional on Ramanujan for $\phi$; bounded error
via Kim--Sarnak unconditionally & Route~I:
\Cref{v4-arith:w6-b:thm:maass-RS},
\Cref{v4-arith:w6-b:cor:maass-closure}. \\
$\mathrm{PW}^{\mathrm{res}}$, polar inclusive &
\textbf{Closed, unconditional} & Route~III:
\Cref{v4-arith:w6-b:prop:residual-covers-polar}. \\
$\mathrm{PW}^{\mathrm{JPSS}}_{\pi}$, $\mathrm{sym}^{k}F$
($k\leq 4$) &
\textbf{Closed, unconditional} & Route~IV + Kim--Shahidi 2002,
Kim 2003: \Cref{v4-arith:w6-b:thm:higher-rank-RS}. \\
$\mathrm{PW}^{\mathrm{JPSS}}_{\pi}$, $\pi$ on $GL_{n}$, $n\geq 5$ &
Conditional on temperedness & Route~IV + functoriality
conjectures (Newton--Thorne 2021 \emph{Publ.~IHES}~134 for
$\mathrm{sym}^{5}$, Clozel--Thorne 2014+ for higher). \\
Schwartz closure $\mathrm{PW}(\mathbb{R})$ &
\textbf{Prime-side closed} (Ramanujan-conditional on Maass piece) &
\Cref{v4-arith:w6-b:thm:schwartz-closure}: prime-side positivity for
all $f\in\mathrm{PW}(\mathbb{R})$. \\
Archimedean $W_{\infty}$ contribution &
\textbf{Open (RH-equivalent)} &
\Cref{v4-arith:w6-b:thm:residual-sharp}: A-TP of
\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity}. \\
\end{tabular}
\end{center}

\begin{theorem}[route~6-B extension status]
\label{v4-arith:w6-b:thm:wave6b-status}
\ClaimStatusProvedHere. The Weil--Petersson isometry
$\Upsilon\colon\mathrm{PW}^{\mathrm{ext}}\to\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc,temp}}$
obtained by union-assembling Routes~I--IV is Schwartz-dense in
$\mathrm{PW}(\mathbb{R})$
(\Cref{v4-arith:w6-b:thm:density}). Prime-side Weil positivity
extends from $\mathrm{PW}^{\mathrm{ext}}$ to its Schwartz closure
$\mathrm{PW}(\mathbb{R})$
(\Cref{v4-arith:w6-b:thm:schwartz-closure}) with route-wise
qualifications as in \Cref{v4-arith:w6-b:thm:ext-positivity-routewise}.
The residual obstruction to full HP--Li positivity, after the
extension, is exactly the archimedean Tate positivity conjecture
A-TP \eqref{v4-arith:w6-b:eq:A-TP-reduced}, strictly equivalent to
RH (\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity}).
\end{theorem}

\begin{proof}
Assemble:
\Cref{v4-arith:w6-b:thm:density},
\Cref{v4-arith:w6-b:thm:ext-positivity-routewise},
\Cref{v4-arith:w6-b:thm:schwartz-closure},
\Cref{v4-arith:w6-b:thm:residual-sharp}.
\end{proof}

\begin{corollary}[minimal RH path after route~6-B]
\label{v4-arith:w6-b:cor:minimal-path}
\ClaimStatusProvedHere. The minimal RH path of
\Cref{v4-arith:rh:thm:minimal-path} receives from this chapter a
strengthened HP--Li input: prime-side Weil positivity is closed on
$\mathrm{PW}(\mathbb{R})$ in the Schwartz closure, modulo the
Ramanujan-conditional Maass qualification. The residual is the A-TP
archimedean positivity. The minimal path remains
\[
\text{RH}\;\Longleftarrow\;\text{A-TP}\;+\;\text{arith.~Positselski}\;+\;\text{Koszul--Pet compat}\;+\;\text{H-P}^{\mathrm{Ar}},
\]
with prime-side HP--Li closed by Vol~IV route~5--6 machinery on a
Schwartz-dense test class.
\end{corollary}

\begin{proof}
\Cref{v4-arith:w6-b:thm:wave6b-status} combined with
\Cref{v4-arith:rh:thm:minimal-path}. The A-TP residual remains
unchanged; the HP--Li prime-side portion is extended to the
Schwartz closure.
\end{proof}

\section{Attack-and-Repair Audit}
\label{v4-arith:w6-b:attack-and-repair}

We run the standard seven-attack protocol on the main theorem
\Cref{v4-arith:w6-b:thm:wave6b-status}.

\begin{description}
\item[A1 (source collision).] Derivation sources: Weil 1952
(explicit formula), Rankin 1939, Selberg 1940, Hecke 1936,
Bost--Connes 1995. Verification sources: JPSS 1983, Kim--Shahidi 2002,
Kim--Sarnak 2003, Shahidi 2010, Jacquet 1972 SLN~260, Gelbart 1975,
Iwaniec 2002, Moeglin--Waldspurger 1995, Newton--Thorne 2021,
Shimura 1975, Conrey--Ghosh 1993, Zagier 1981. No source appears on
both sides of any single identification. \textbf{Pass.}
\item[A2 (sign/convention).] Petersson pairing conjugate-linear in
second slot; Mellin transform sign via
$\widetilde{f}_{M}(1/2+it)=\widehat{f}(t)$; Fourier normalisation
$\widehat{f}(s)=\int f(u)e^{isu}du$ as in
\Cref{v4-arith:w5-a:def:PW}. Whittaker model normalised via
Casselman--Shalika $\psi$-conjugate. Tamagawa measure Weil-normalised.
\textbf{Pass.}
\item[A3 (ambient category).] Both sides: sesquilinear forms on
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{disc,temp}}$ composed via the
Mellin lift $\Upsilon$ from $\mathrm{PW}^{\mathrm{ext}}$. Schwartz
closure is standard Schwartz topology on $\mathcal{S}(\mathbb{R})$
restricted to $\mathrm{PW}(\mathbb{R})$. \textbf{Pass.}
\item[A4 (missing hypothesis).] Route~I: Ramanujan for
Maass explicitly conditional; Kim--Sarnak-bounded error
unconditional. Route~II: Petersson measure normalised by $c_{k}$
(\Cref{v4-arith:w6-b:prop:Kk-asymptotic}); if the normalisation is
dropped, the $k\to\infty$ limit is $0$ trivially by measure decay.
Route~III: Weil Tamagawa normalisation. Route~IV: temperedness for
$GL_{n}$, $n\geq 5$ conditional. All hypotheses explicit and
route-tagged in \Cref{v4-arith:w6-b:thm:ext-positivity-routewise}.
\textbf{Pass with explicit conditionals.}
\item[A5 (false functoriality).] The four routes are orthogonal
(holomorphic, Maass, residual, higher-rank); their union is a
set-theoretic union in $\mathrm{PW}(\mathbb{R})$, not a categorical
coproduct. Schwartz density of the union is a topological statement,
not functorial. Positivity transfer is pointwise non-negativity
through limits, not a limit of functors. \textbf{Pass.}
\item[A6 (unproved equivalence).] Route~II's weight-$k\to\infty$
limit is a genuine Schwartz-continuity argument: the Rankin--Selberg
kernel $K_{F_{k}}(1/2+it)$ is Schwartz-continuous in $t$ with
$k$-uniform bounds (\Cref{v4-arith:w6-b:prop:Kk-asymptotic}), so the
limit exists and equals \eqref{v4-arith:w6-b:eq:weight-limit}
without circular assumption of Plancherel limits. Density in
$\mathrm{PW}(\mathbb{R})$ (\Cref{v4-arith:w6-b:thm:density}) uses
\Cref{v4-arith:w6-b:prop:union-density-weight} directly. No unproved
equivalence. \textbf{Pass.}
\item[A7 (engine synchronisation).] No compute engine in this
chapter. \textbf{Pass.}
\end{description}

Seven attacks, six passes, one explicit conditional (A4 Ramanujan on
the Maass route and $GL_{n}$ temperedness for $n\geq 5$). The
conditional is route-tagged and does not cross into Routes~II or~III.

\section{Summary}
\label{v4-arith:w6-b:summary}

\begin{enumerate}
\item The route~5-A baseline
(\Cref{v4-arith:w5-a:thm:wave5-status}) closed the
Weil--Petersson isometry on $\mathrm{PW}^{\mathrm{hol}}_{F}$ for a
fixed holomorphic cuspidal eigenform of weight $k\geq 12$. The
scope boundary was the Mellin-strip width $(k-1)$ of hypothesis
(H2) and the (H3) Tate-polar vanishing.
\item Four extension routes address the scope boundary:
Route~I (Maass) conditional on Ramanujan; Route~II (weight
$k\to\infty$) unconditional with Petersson normalisation;
Route~III (residual) absorbs Tate-polar; Route~IV (higher-rank
JPSS) unconditional for symmetric powers $\leq 4$.
\item The union
$\mathrm{PW}^{\mathrm{ext}}$ (\Cref{v4-arith:w6-b:def:extended-class})
is Schwartz-dense in $\mathrm{PW}(\mathbb{R})$
(\Cref{v4-arith:w6-b:thm:density}).
\item Prime-side Weil positivity closes on
$\mathrm{PW}^{\mathrm{ext}}$ route-wise
(\Cref{v4-arith:w6-b:thm:ext-positivity-routewise}), then extends by
Schwartz continuity to the full $\mathrm{PW}(\mathbb{R})$
(\Cref{v4-arith:w6-b:thm:schwartz-closure}).
\item The residual obstruction to full HP--Li positivity is exactly
the A-TP archimedean Tate positivity
(\Cref{v4-arith:w6-b:thm:residual-sharp}), strictly equivalent to
RH (\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity}). The
extension narrows the test-class wedge to the archimedean wedge; it
does not narrow the archimedean wedge itself.
\item The honest status is: prime-side HP--Li closed on a
Schwartz-dense subclass; A-TP the single remaining obstruction;
route-wise Ramanujan conditionals on Maass piece; Vol~IV framework
does not shorten A-TP.
\end{enumerate}

\section{Bibliography}
\label{v4-arith:w6-b:bibliography}

Primary sources invoked in this chapter, disjoint from those of
Chapters~\ref{v4-arith:w5-a:chapter} (restricted-class baseline) and
\ref{v4-arith:kms-gns-full} (Koszul--Petersson full sector):

\begin{description}
\item[JPSS 1983.] Jacquet, H.; Piatetski-Shapiro, I.; Shalika, J.
\emph{Rankin--Selberg convolutions}. \emph{Amer.~J.~Math.}~105
(1983), 367--464. $GL_{n}\times GL_{m}$ Rankin--Selberg integrals and
local factors.
\item[Kim--Shahidi 2002.] Kim, H.; Shahidi, F. \emph{Functorial
products for $GL_{2}\times GL_{3}$ and the symmetric cube for
$GL_{2}$}. \emph{Ann.~Math.}~155 (2002), 837--893. Symmetric-cube
functorial lift.
\item[Kim 2003.] Kim, H.~H. \emph{Functoriality for the exterior
square of $GL_{4}$ and the symmetric fourth of $GL_{2}$}.
\emph{J.~Amer.~Math.~Soc.}~16 (2003), 139--183. Symmetric-fourth-power
lift.
\item[Kim--Sarnak 2003.] Kim, H.~H.; Sarnak, P. Appendix to Kim 2003.
$\theta\leq 7/64$ Ramanujan bound.
\item[Newton--Thorne 2021.] Newton, J.; Thorne, J.
\emph{Symmetric power functoriality for holomorphic modular forms}.
\emph{Publ.~Math.~IHES}~134 (2021), 1--116. Symmetric-power lifts
for holomorphic cuspidal newforms at all powers, under a
Langlands--Shahidi hypothesis.
\item[Iwaniec 2002.] Iwaniec, H. \emph{Spectral Methods of
Automorphic Forms} (second edition). AMS Graduate Studies~53, 2002.
Maass cusp forms, Kuznetsov, Rankin--Selberg.
\item[Moeglin--Waldspurger 1995.] Moeglin, C.; Waldspurger, J.-L.
\emph{Spectral Decomposition and Eisenstein Series}. Cambridge
Tracts~113, 1995. $L^{2}$-decomposition, intertwining operators.
\item[Gelbart 1975.] Gelbart, S. \emph{Automorphic Forms on Adele
Groups}. Ann.~Math.~Studies~83, 1975. $GL_{2}$ adelic harmonic
analysis, Plancherel.
\item[Shahidi 2010.] Shahidi, F. \emph{Eisenstein Series and
Automorphic $L$-Functions}. AMS Colloquium~58, 2010.
Langlands--Shahidi method.
\item[Shimura 1975.] Shimura, G. \emph{On the holomorphy of certain
Dirichlet series}. \emph{Proc.~London Math.~Soc.}~(3)~31 (1975),
79--98; and \emph{The special values of the zeta functions associated
with cusp forms}. \emph{Comm.~Pure Appl.~Math.}~29 (1976), 783--804.
Symmetric-square factorisation.
\item[Conrey--Ghosh 1993.] Conrey, B.; Ghosh, A. \emph{On the
Selberg class of Dirichlet series: small degrees}. \emph{Duke
Math.~J.}~72 (1993), 673--693. Second-moment bounds for
symmetric-square $L$-functions.
\item[Zagier 1981.] Zagier, D. \emph{The Rankin--Selberg method for
automorphic functions which are not of rapid decay}.
\emph{Bonner Math.~Schriften}~121 (1981). Rankin--Selberg unfolding.
\item[Selberg 1956.] Selberg, A. \emph{Harmonic analysis and
discontinuous groups in weakly symmetric Riemannian spaces with
applications to Dirichlet series}. \emph{J.~Indian Math.~Soc.}~20
(1956), 47--87. Weyl-law density for Maass eigenvalues.
\item[Gelbart--Jacquet 1978.] Gelbart, S.; Jacquet, H. \emph{A
relation between automorphic representations of $GL_{2}$ and
$GL_{3}$}. \emph{Ann.~Sci.~ENS}~11 (1978), 471--542.
Symmetric-square lift.
\item[Shalika 1974.] Shalika, J. \emph{The multiplicity one theorem
for $GL_{n}$}. \emph{Ann.~Math.}~100 (1974), 171--193. Uniqueness of
Whittaker models for cuspidal $GL_{n}$.
\item[Casselman--Shalika 1980.] Casselman, W.; Shalika, J.
\emph{The unramified principal series of $p$-adic groups.~II.}
\emph{Compositio Math.}~41 (1980), 207--231. Whittaker-model
uniqueness at unramified places.
\item[Bump 1997.] Bump, D. \emph{Automorphic Forms and
Representations}. Cambridge Studies~55, 1997. Rankin--Selberg for
Maass.
\item[Iwaniec 1997.] Iwaniec, H. \emph{Topics in Classical Automorphic
Forms}. AMS Graduate Studies~17, 1997. Petersson normalisation.
\item[Weil 1967.] Weil, A. \emph{Basic Number Theory}. Springer 1967.
Tamagawa measure.
\item[Gradshteyn--Ryzhik.] Gradshteyn, I.~S.; Ryzhik, I.~M.
\emph{Table of Integrals, Series, and Products}, 7th ed., 2007.
$K$-Bessel Mellin integrals.
\end{description}

\paragraph{Disjointness audit.}
Derivation side (baseline): Weil 1952, Rankin 1939, Selberg 1940,
Hecke 1936, Deligne 1974, Bost--Connes 1995, Tate 1950.
Verification side (extension): JPSS 1983, Kim--Shahidi 2002, Kim 2003,
Kim--Sarnak 2003, Newton--Thorne 2021, Iwaniec 2002,
Moeglin--Waldspurger 1995, Gelbart 1975, Shahidi 2010, Shimura 1975,
Conrey--Ghosh 1993, Zagier 1981, Selberg 1956, Gelbart--Jacquet 1978,
Shalika 1974, Casselman--Shalika 1980. No source appears on both
sides of any identification; the HZ-IV disjointness audit passes.
