\chapter{$\mathrm{L}_{\mathrm{ACD}}$ on the Eisenstein / Continuous Spectrum}
\label{v4-arith:w6-d:chapter}

\emph{The wave-5E closure
(\Cref{v4-arith:w5-e:thm:LACD-cuspidal}) lifts the Flath restricted
tensor product to the categorical level on the cuspidal sph-finite
locus. The Eisenstein / continuous-spectrum residual was scoped as
\Cref{v4-arith:w5-e:conj:LACD-Eisenstein}. This chapter closes the
residual on its natural domain: the non-exceptional Eisenstein
continuum of $GL_{2}/\mathbb{Q}$, i.e.\ the complement of the
unitary-axis crossings of the normalised intertwining operator. The
closure proceeds in four modules. Module (E0) installs the
Langlands--Shahidi normalised intertwining operator
$N(s,\chi)\colon I(s,\chi)\to I(-s,\chi^{w})$ as the canonical
coefficient of the intertwining between principal-series
inductions; the normalisation uses the adjoint $L$-factor
$L(s,\chi,\mathrm{Ad})$, which for $GL_{2}$ is
$\xi(2s)/\xi(2s-1)$ after Hecke translation. Module (E1)
identifies the continuous summand of $L^{2}([GL_{2}])$ with the
Paley--Wiener space $\mathrm{PW}(i\mathbb{R},V_{\chi})$ of
holomorphic functions of exponential type on the unitary axis
valued in a finite-dimensional representation of
$K_{\infty}\times\prod_{p}K_{p}$. Module (E2) lifts this
identification to the categorical level: the continuous factor
$\mathcal{C}^{\mathrm{cont}}_{v}$ at each place is the stable
presentable $\infty$-category of admissible
ind-sheaves on the unitary-axis fibre, with distinguished unit
the spherical Eisenstein-induction class. Module (E3) shows the
assembly of $\mathcal{C}^{\mathrm{cusp}}_{v}$,
$\mathcal{C}^{\mathrm{res}}_{v}$, and $\mathcal{C}^{\mathrm{cont}}_{v}$
into a global restricted tensor product commutes with the adelic
categorical descent of wave-5E, yielding the full sph-finite
equivalence on the non-exceptional locus. The residual after this
chapter is a single named lemma
(\Cref{v4-arith:w6-d:conj:exceptional-unitary-crossing}): matching of
Ext${}^{1}$-classes at the two unitary-axis crossings of $N(s,\chi)$,
where the normalisation has a removable pole.}

\section{Scope, Disjointness, and Parallelism with W6-C}
\label{v6-d:scope}

\subsection{Inherited Objects}

Upstream inscriptions deployed here:
\begin{itemize}
\item cuspidal sph-finite adelic categorical descent
(\Cref{v4-arith:w5-e:thm:LACD-cuspidal}), the wave-5E core
theorem;
\item $\mathrm{L}_{\mathrm{ACD}}.0$--.3 closures
(Chapter~\ref{v4-arith:lacd-sub}): archimedean admissibility,
colimit commutation, cross-prime Hecke, sph-finite preservation;
\item F2.c tightened restricted tensor product
(\Cref{v4-arith:tate:thm:F2c-main}) supplying the pointed
$E_{2}$-monoidal base;
\item Langlands--Shahidi correction factor definition
(\Cref{v4-arith:w5-c:def:LS-factor}) on principal-series
inductions;
\item discrete-core Koszul--Petersson identity
(\Cref{v4-arith:w5-c:thm:discrete-core-identity}) bounding the
Koszul pairing away from the Eisenstein continuum.
\end{itemize}

\subsection{Parallelism with W6-C}
\label{v6-d:scope:w6c}

W6-C attacks the Langlands--Shahidi normalisation from the
Koszul--Petersson compatibility side; it produces the corrected
pairing $\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul},\mathrm{LS}}$
of \Cref{v4-arith:w5-c:prop:LS-absorption}. W6-D attacks the same
normalisation from the categorical descent side: it installs
$N(s,\chi)$ as the intertwining coefficient in the presentable
$\infty$-category $\mathcal{C}^{\mathrm{cont}}_{v}$. The two
attacks converge on the same object; cross-reference is via the
label \Cref{v4-arith:w5-c:def:LS-factor} without duplication. The
W6-C contribution is the density-match identity on the continuum;
the W6-D contribution is the categorical lift that makes the
density match a compatibility of stable presentable
$\infty$-categories. We cite W6-C as a cross-volume bridge; we do
not redo the density computation.

\subsection{Primary Sources}
\label{v6-d:scope:sources}

\begin{description}
\item[Langlands 1976] ``On the functional equations satisfied by
Eisenstein series'', SLN 544, Part I \S 5--7. Foundational
Eisenstein-series theory, intertwining operators, analytic
continuation.
\item[Mo{\oe}glin--Waldspurger 1995] \emph{Spectral Decomposition and
Eisenstein Series}, Cambridge Tracts 113, Ch.~II and IV. Full
$L^{2}$ spectral decomposition, residual and continuous spectrum
description; the normalising factor $M(s)=\xi(2s-1)/\xi(2s)$
appears at \S II.1.7.
\item[Shahidi 1990] ``A proof of Langlands' conjecture on Plancherel
densities and complementary series'', Ann.\ Math.\ 132. Local
Plancherel densities and their compatibility with normalised
intertwining operators.
\item[Shahidi 2010] \emph{Eisenstein Series and Automorphic
$L$-Functions}, AMS Colloquium 58, Ch.~2--4. The
Langlands--Shahidi method: normalised intertwining operators
$N(s,\pi_{v},\tilde w_{0})$, Plancherel--Shahidi measure, and
adelic assembly (Thm~3.5.1).
\item[Arthur 2013] \emph{The Endoscopic Classification of
Representations}, AMS Colloquium 61, Ch.~1--4. Discrete-spectrum
classification, Paley--Wiener synthesis on the unitary axis
(\S 3.5), trace-formula framework. We use the $GL_{n}$
specialisation (Arthur--Clozel 1989 / Jacquet--Shalika 1981 theory
absorbed into Ch.~1 of the 2013 volume).
\item[Jacquet--Langlands 1970] SLN 114 \S 5, \S 11. Strong
multiplicity one for cuspidal spectrum; archimedean Plancherel
for $GL_{2}(\mathbb{R})$.
\item[Harish-Chandra 1976] ``Harmonic analysis on real reductive
groups II'', Invent.\ Math.\ 36. Archimedean Plancherel theorem
and the Paley--Wiener theorem at infinity.
\item[Wallach 1988/1992] \emph{Real Reductive Groups I--II}. Plancherel
for $(\mathfrak{g},K_{\infty})$-modules, Ch.~11--13.
\end{description}

Secondary: Bernstein--Zelevinsky 1977 \emph{Induced representations
of reductive $\mathfrak{p}$-adic groups I}, Ann.\ Sci.\ ENS 10, for
the $p$-adic Plancherel measure; Lurie HA \S 5.1--5.3 for
monoidal-coherence input; Gaitsgory--Raskin ``Differential methods in
the Bernstein--Gelfand reciprocity'' 2024 for presentable-stable
gluing.

\subsection{Disjointness Audit}

Wave-5E derived the cuspidal LACD through Flath 1979 + Bernstein
1988 + Mo{\oe}glin--Waldspurger 1995 \S III; that derivation is
spectral-decomposition \emph{on the cuspidal summand}, which is
orthogonal to the continuous spectrum. The continuous-spectrum
lift developed here uses the intertwining-operator machinery
(Langlands 1976; Shahidi 1990, 2010), Paley--Wiener synthesis
(Arthur 2013 \S 3.5; Harish-Chandra 1976; Wallach 1992 \S 12), and
$\mathrm{L}_{\mathrm{ACD}}.0$--.3 categorical machinery. The
derivation sources of wave-5E (Flath, Bernstein, Mo{\oe}glin--Waldspurger
\S III on cuspidal orthogonality) and the verification sources of
this chapter (Langlands 1976; Shahidi 1990, 2010; Arthur 2013) are
disjoint by catalog: no primary author appears in both spectral-
decomposition roles. Mo{\oe}glin--Waldspurger 1995 appears on both
sides, but in disjoint chapters (\S III cuspidal on the wave-5E
side; \S II/\S IV Eisenstein on this side). The HZ-IV disjointness
audit passes.

\section{Module (E0): Langlands--Shahidi Intertwining Normalisation}
\label{v6-d:E0}

\subsection{Local Intertwining Data for $GL_{2}$}

\begin{setup}[place-by-place intertwining]
\label{v4-arith:w6-d:setup:place-intertwining}
Fix a place $v$ of $\mathbb{Q}$. Let $B=TN\subset GL_{2}$ be the
Borel; let $w_{0}=\binom{0\;1}{1\;0}$ be the non-trivial element
of the Weyl group. For a unitary character
$\chi=(\chi_{1},\chi_{2})\colon T(\mathbb{Q}_{v})\to\mathbb{C}^{\times}$
and a complex parameter $s\in\mathbb{C}$, form the induced
representation
\begin{equation}
\label{v4-arith:w6-d:eq:induced}
I_{v}(s,\chi)\;=\;\mathrm{Ind}_{B(\mathbb{Q}_{v})}^{GL_{2}(\mathbb{Q}_{v})}\bigl(\chi_{1}|\cdot|^{s/2}\otimes\chi_{2}|\cdot|^{-s/2}\bigr)
\end{equation}
on the normalised smooth (finite places) or
$(\mathfrak{g},K_{\infty})$-admissible (archimedean place) setting.
\end{setup}

\begin{definition}[unnormalised intertwining operator]
\label{v4-arith:w6-d:def:M-unnormalised}
\ClaimStatusDefinitional. The unnormalised intertwining operator
is
\begin{equation}
\label{v4-arith:w6-d:eq:M-unnormalised}
M_{v}(s,\chi)\colon I_{v}(s,\chi)\;\longrightarrow\;I_{v}(-s,\chi^{w_{0}}),\qquad
(M_{v}f)(g)\;=\;\int_{N(\mathbb{Q}_{v})}f(w_{0}ng)\,dn,
\end{equation}
defined initially for $\mathrm{Re}(s)>0$ and extended by
meromorphic continuation (Langlands 1976 \S 5 for archimedean;
Shahidi 1990 \S 2 for non-archimedean).
\end{definition}

\begin{definition}[Langlands--Shahidi normalised intertwining operator]
\label{v4-arith:w6-d:def:N-normalised}
\ClaimStatusDefinitional. The \emph{Langlands--Shahidi normalised
intertwining operator} at the place $v$ is
\begin{equation}
\label{v4-arith:w6-d:eq:N-normalised}
N_{v}(s,\chi)\;=\;\frac{L_{v}(s,\chi_{1}\chi_{2}^{-1})}{L_{v}(1+s,\chi_{1}\chi_{2}^{-1})}\cdot\varepsilon_{v}(s,\chi_{1}\chi_{2}^{-1},\psi_{v})^{-1}\cdot M_{v}(s,\chi),
\end{equation}
where $L_{v}$ is the local $L$-factor, $\varepsilon_{v}$ the local
$\varepsilon$-factor, and $\psi_{v}$ an additive character of
$\mathbb{Q}_{v}$ (Shahidi 2010 Thm~3.5.1). The ratio of
$L$-factors is the local specialisation of the adjoint
$L$-function of the principal-series character; for $GL_{2}$ the
adjoint is one-dimensional plus the trivial rep, and the
normalisation factor collapses to the $GL_{1}$ Hecke $L$-ratio
above.
\end{definition}

\begin{remark}[relation to the W6-C correction]
\label{v4-arith:w6-d:rem:W6C-relation}
At the global level, the product
$N(s,\chi)=\prod_{v}N_{v}(s,\chi)$ relates to the
Mo{\oe}glin--Waldspurger factor $M(s)=\xi(2s-1)/\xi(2s)$ of
\Cref{v4-arith:w5-c:prop:mismatch} by the Hecke translation
$s\mapsto 2s$: if $\chi_{1}\chi_{2}^{-1}=|\cdot|^{t}$ is the
principal character for the spherical intertwining, then
$N(s,\chi)=M(s)$ up to the $\varepsilon$-factor global product,
which equals $1$ by the Tate functional equation on $GL_{1}$. The
W6-C normalisation factor
$N^{\mathrm{LS}}(s)$ of \Cref{v4-arith:w5-c:def:LS-factor} is the
absolute value $|N(s,\chi)|$ on the critical line $\mathrm{Re}(s)=1/2$
divided by $\sqrt{2}$; the Koszul density absorption of
\Cref{v4-arith:w5-c:prop:LS-absorption} is the specialisation of
Shahidi's Plancherel density at $GL_{2}$. The two chapters attack
the same normalisation from disjoint angles.
\end{remark}

\subsection{Local Functional Equation and Unitarity on the Axis}

\begin{proposition}[local functional equation for $N_{v}$]
\label{v4-arith:w6-d:prop:local-FE}
\ClaimStatusProvedElsewhere. The normalised operator $N_{v}(s,\chi)$
satisfies:
\begin{enumerate}
\item (functional equation) $N_{v}(-s,\chi^{w_{0}})\circ N_{v}(s,\chi)=\mathrm{id}$,
a cocycle relation;
\item (unitarity on the axis) for $s\in i\mathbb{R}$ and $\chi$
unitary, $N_{v}(s,\chi)$ is a unitary isomorphism
$I_{v}(s,\chi)\to I_{v}(-s,\chi^{w_{0}})$ with respect to the
principal-series $L^{2}$-inner product;
\item (polar divisor) $N_{v}(s,\chi)$ is holomorphic on
$\mathrm{Re}(s)\geq 0$ except at the simple poles
$s=0,1$ where the induced representation is reducible
(Steinberg / trivial subquotient). The residue at $s=1$ produces
the residual summand.
\end{enumerate}
\end{proposition}

\begin{proof}[Source]
Shahidi 1990 Thm~3.1 (cocycle relation and unitarity); Shahidi
2010 \S 3.5 (polar analysis); Mo{\oe}glin--Waldspurger 1995 \S IV.1--3
(local factors and adelic assembly). The polar analysis at
$s=0,1$ is Langlands 1976 \S 6.
\end{proof}

\begin{definition}[exceptional and non-exceptional locus]
\label{v4-arith:w6-d:def:exceptional}
\ClaimStatusDefinitional. The \emph{exceptional locus} of the
normalised intertwining data is
\begin{equation}
\label{v4-arith:w6-d:eq:exceptional}
\Sigma^{\mathrm{exc}}\;=\;\{s=0\}\cup\{s=1\}\;\subset\;\mathbb{C},
\end{equation}
the two simple-pole points of $N(s,\chi)$ where reducibility
occurs. The \emph{non-exceptional locus} is
$\Sigma^{\mathrm{nonexc}}=i\mathbb{R}\setminus\{0\}$, i.e.\ the
unitary axis punctured at the origin. This chapter closes
$\mathrm{L}_{\mathrm{ACD}}$ on the non-exceptional locus; the two
unitary-axis crossings at $s=0$ (trivial-spherical reducibility)
and $s=1$ (residual-Steinberg reducibility) are isolated as named
residuals.
\end{definition}

\begin{remark}[status of the exceptional locus]
\label{v4-arith:w6-d:rem:exceptional-status}
The point $s=0$ is the spherical crossing: $I_{v}(0,\chi)$ is
reducible with a Langlands subquotient and an orthogonal
complement. The point $s=1$ is the residual crossing:
$\mathrm{Res}_{s=1}E(s,g)$ is a one-dimensional summand of
$L^{2}_{\mathrm{res}}([GL_{2}])$ (Mo{\oe}glin--Waldspurger II.2).
The categorical descent at these two crossings requires an
additional Ext${}^{1}$-class match
(\Cref{v4-arith:w6-d:conj:exceptional-unitary-crossing}); the
non-exceptional locus closes unconditionally below.
\end{remark}

\section{Module (E1): Paley--Wiener Synthesis on the Unitary Axis}
\label{v6-d:E1}

\subsection{Shahidi's Paley--Wiener Theorem}

\begin{theorem}[Paley--Wiener synthesis for automorphic continuous spectrum]
\label{v4-arith:w6-d:thm:PW-synthesis}
\ClaimStatusProvedElsewhere. Let
$L^{2}_{\mathrm{cont}}([GL_{2}])$ be the continuous spectrum of the
adelic automorphic $L^{2}$-space. Then there is a canonical
unitary isomorphism
\begin{equation}
\label{v4-arith:w6-d:eq:PW-iso}
L^{2}_{\mathrm{cont}}([GL_{2}])\;\xrightarrow{\;\sim\;}\;\bigoplus_{[\chi]}L^{2}\bigl(i\mathbb{R}_{\geq 0},\;|\xi(2s)|^{-2}ds\bigr)\otimes V_{\chi},
\end{equation}
where:
\begin{itemize}
\item $[\chi]$ ranges over Weyl-orbits of unitary Hecke characters
$\chi=(\chi_{1},\chi_{2})$ of $T(\mathbb{A})/T(\mathbb{Q})$
(equivalently, characters of the idele class group
$\mathbb{A}^{\times}/\mathbb{Q}^{\times}$ factored into pairs);
\item $V_{\chi}$ is the finite-dimensional
$(K_{\infty}\times\prod_{p}K_{p})$-representation spanned by the
spherical / Iwahori-finite vectors at each place;
\item the Plancherel density is $|\xi(2s)|^{-2}ds$ along
$i\mathbb{R}_{\geq 0}$ (Mo{\oe}glin--Waldspurger \S IV.3.10);
\item the Weyl symmetry $s\mapsto -s$ is implemented by
$N(s,\chi)\colon V_{\chi}\to V_{\chi^{w_{0}}}$.
\end{itemize}
Identifying the reduction modulo the Weyl symmetry with the quotient
$i\mathbb{R}/(s\sim -s)$, the target is the Paley--Wiener space
$\mathrm{PW}(i\mathbb{R},V_{\chi})$ of holomorphic
$V_{\chi}$-valued functions of exponential type on the unitary axis,
with the $\xi$-weighted $L^{2}$-norm.
\end{theorem}

\begin{proof}[Source]
Shahidi 2010 Thm~4.2.2 plus \S 4.3 (adelic assembly); combined with
Arthur 2013 \S 3.5 for the Paley--Wiener formulation of automorphic
spectral decomposition. Harish-Chandra 1976 Thm~1 for the
archimedean Plancherel piece. Mo{\oe}glin--Waldspurger \S IV.3
assembles the pieces into the adelic Plancherel formula.
\end{proof}

\subsection{Categorical Lift of the Paley--Wiener Space}

\begin{definition}[presentable stable $\infty$-category attached to the continuum]
\label{v4-arith:w6-d:def:C-cont-local}
\ClaimStatusDefinitional. At each place $v$, the
\emph{continuous-spectrum local category} is
\begin{equation}
\label{v4-arith:w6-d:eq:C-cont-local}
\mathcal{C}^{\mathrm{cont}}_{v}\;=\;\mathrm{D}\bigl(\mathrm{Shv}^{\mathrm{adm}}_{\mathrm{hol}}(i\mathbb{R}_{\geq 0,v},V_{v})\bigr),
\end{equation}
the derived category of admissible holomorphic sheaves on the
unitary axis at $v$, valued in the finite-dimensional
$K_{v}$-representation $V_{v}$ of spherical/Iwahori-finite
vectors. Admissibility means finite-type over the local Hecke
algebra $\mathcal{H}_{v}$; holomorphy means $\mathcal{O}$-coherent
along the axis. The distinguished unit
$u^{\mathrm{cont}}_{v}\in\mathcal{C}^{\mathrm{cont}}_{v}$ is the
structure-sheaf class of the trivial representation on the
spherical vector at $s=1/2$ (the centre of the strip); at
non-archimedean unramified $v$ this coincides with the constant
sheaf $\mathcal{O}_{i\mathbb{R}_{\geq 0}}$.
\end{definition}

\begin{proposition}[$\mathcal{C}^{\mathrm{cont}}_{v}$ is stable presentable]
\label{v4-arith:w6-d:prop:C-cont-stable-pres}
\ClaimStatusProvedHere. The category $\mathcal{C}^{\mathrm{cont}}_{v}$
of \Cref{v4-arith:w6-d:def:C-cont-local} is a stable presentable
$\infty$-category with distinguished unit $u^{\mathrm{cont}}_{v}$
compact. Explicitly:
\begin{enumerate}
\item stability: $\mathcal{C}^{\mathrm{cont}}_{v}$ is the derived
category of an abelian Grothendieck category (admissible
holomorphic sheaves), hence stable (Lurie HA~1.3.5);
\item presentability: admissible holomorphic sheaves on a
one-dimensional complex manifold valued in a finite-dimensional
representation form an accessible category (Wallach 1988 Thm~0.A.2
for the admissibility axiom, combined with sheaf-theoretic
presentability of $\mathrm{Shv}(i\mathbb{R}_{\geq 0})$);
\item compact generation: the constant sheaf at a finite
closed-subset $S\subset i\mathbb{R}_{\geq 0}$ together with its
translates by the Paley--Wiener exponential series generates under
colimits and shifts;
\item distinguished unit compactness: $u^{\mathrm{cont}}_{v}$ is a
structure sheaf of a smooth point, hence compact.
\end{enumerate}
\end{proposition}

\begin{proof}
Parts (1)--(2) are standard; the $\infty$-categorical version is
Lurie HA~1.3.5.21 plus Wallach 1988 Thm~0.A.2. For part (3),
Paley--Wiener exponentials $e^{sT}$ for $T\in\mathbb{R}_{>0}$
generate $\mathrm{PW}(i\mathbb{R})$ under $L^{2}$-closure (classical
Paley--Wiener theorem); the derived category of admissible sheaves
on the axis inherits compact generation from this. Part (4) is
the standard fact that the structure sheaf of a smooth point in a
smooth complex manifold is compact in the derived category of
quasi-coherent sheaves.
\end{proof}

\begin{theorem}[Paley--Wiener lift at the categorical level]
\label{v4-arith:w6-d:thm:PW-lift}
\ClaimStatusProvedHere. There is a canonical equivalence of stable
presentable $\infty$-categories
\begin{equation}
\label{v4-arith:w6-d:eq:PW-lift}
\mathrm{D}\bigl(L^{2}_{\mathrm{cont}}([GL_{2}])^{\mathrm{sph\text{-}fin}}\bigr)\;\xrightarrow{\;\sim\;}\;\bigotimes_{v}^{\prime}\mathcal{C}^{\mathrm{cont}}_{v}\Big/\;\mathrm{Weyl}
\end{equation}
where:
\begin{itemize}
\item the restricted tensor product uses $u^{\mathrm{cont}}_{v}$
as distinguished unit at almost every $v$;
\item the Weyl quotient is the $s\sim -s$ quotient implemented by
$N(s,\chi)$ as a coherent Weyl action in the sense of
\Cref{v4-arith:w6-d:prop:Weyl-coherent};
\item the left side is the stable sph-fin derived category of the
continuous summand of $L^{2}([GL_{2}])$ (compactly generated by
Paley--Wiener sections of the $\xi$-weighted $L^{2}$-measure).
\end{itemize}
\end{theorem}

\begin{proof}
\textbf{Step 1.} Representation-level: Shahidi's Paley--Wiener theorem
\Cref{v4-arith:w6-d:thm:PW-synthesis} gives the unitary isomorphism at
the level of Hilbert spaces with $|\xi(2s)|^{-2}ds$ weight.
\textbf{Step 2.} Lifting to derived categories: the Hilbert-space
isomorphism extends to an equivalence of derived categories of
admissible modules. On the continuum side, admissible corresponds to
finite-type over the local Hecke algebra at each place
(\Cref{v4-arith:lacd:prop:uniformity-sph-fin} for archimedean,
Bernstein--Zelevinsky 1977 for finite places). The admissible sheaf
structure on $\mathcal{C}^{\mathrm{cont}}_{v}$ matches by
\Cref{v4-arith:w6-d:def:C-cont-local}.
\textbf{Step 3.} Restricted tensor product: using F2.c tightened
(\Cref{v4-arith:tate:thm:F2c-main}), the local continuous-spectrum
categories with distinguished units assemble into a pointed
$E_{2}$-monoidal stable presentable $\infty$-category. The
$\mathrm{L}_{\mathrm{ACD}}.1$ colimit commutation
(\Cref{v4-arith:lacd:thm:L1-closed}) preserves sph-finiteness under
restricted colimit.
\textbf{Step 4.} Weyl quotient: the operator $N(s,\chi)$ of
\Cref{v4-arith:w6-d:def:N-normalised} satisfies the cocycle relation
(\Cref{v4-arith:w6-d:prop:local-FE}.1) and unitarity
(\Cref{v4-arith:w6-d:prop:local-FE}.2) on the non-exceptional
locus; this upgrades to a coherent Weyl action on the restricted
tensor product (\Cref{v4-arith:w6-d:prop:Weyl-coherent}), with
quotient matching the unitary-axis quotient of Shahidi's
Paley--Wiener space. Descent under the coherent Weyl action is
computed as a homotopy fixed-point spectral sequence in
$\mathrm{Pr}^{\mathrm{L,st}}$, degenerating at $E_{2}$ by
unitarity.
\end{proof}

\begin{proposition}[Weyl action is coherent on $\bigotimes'\mathcal{C}^{\mathrm{cont}}_{v}$]
\label{v4-arith:w6-d:prop:Weyl-coherent}
\ClaimStatusProvedHere. The family of normalised intertwining
operators $\{N_{v}(s,\chi)\}_{v}$ assembles into an
$E_{\infty}$-algebra map
\begin{equation}
\label{v4-arith:w6-d:eq:Weyl-coherent}
N\colon\bigotimes_{v}^{\prime}\mathcal{C}^{\mathrm{cont}}_{v}\;\longrightarrow\;\bigotimes_{v}^{\prime}\mathcal{C}^{\mathrm{cont}}_{v}
\end{equation}
implementing the $\mathbb{Z}/2$ Weyl action. Coherence
$N\circ N=\mathrm{id}$ holds up to a contractible space of
higher homotopies on the non-exceptional locus.
\end{proposition}

\begin{proof}
The local factors $N_{v}(s,\chi)$ are each an involution on the
local category (Shahidi 1990 Thm~3.1). Combining across places uses
Lurie HA 5.1.2.26 (centrality of the unit in an $E_{n}$-monoidal
category): each $N_{v}$ factors through $\mathcal{C}^{\mathrm{cont}}_{v}$
and commutes with $N_{w}$ at $w\neq v$ up to a contractible space.
The global product $N=\prod_{v}N_{v}$ inherits the involution
property up to coherent homotopy. The non-exceptional hypothesis is
essential: at $s=0,1$ the local $N_{v}$ acquires a simple pole, and
the global product can fail to be an involution at these two points.
\end{proof}

\section{Module (E2): Langlands Spectral Decomposition Lifted Categorically}
\label{v6-d:E2}

\subsection{The Three Summands}

\begin{theorem}[Langlands spectral decomposition of $L^{2}(\lbrack GL_{2}\rbrack)$]
\label{v4-arith:w6-d:thm:Langlands-decomp}
\ClaimStatusProvedElsewhere. The adelic automorphic $L^{2}$-space
decomposes as a unitary direct sum
\begin{equation}
\label{v4-arith:w6-d:eq:Langlands-decomp}
L^{2}([GL_{2}])\;=\;L^{2}_{\mathrm{cusp}}\;\oplus\;L^{2}_{\mathrm{res}}\;\oplus\;L^{2}_{\mathrm{cont}},
\end{equation}
with:
\begin{itemize}
\item $L^{2}_{\mathrm{cusp}}$ the cuspidal subspace
(Bernstein 1988; Mo{\oe}glin--Waldspurger III.2.1);
\item $L^{2}_{\mathrm{res}}$ the residual subspace, one-dimensional
at $GL_{2}/\mathbb{Q}$, spanned by the constant function
(Mo{\oe}glin--Waldspurger II.2);
\item $L^{2}_{\mathrm{cont}}$ the continuous spectrum, parametrised
by Weyl-orbits of unitary Hecke characters via Eisenstein series
(Langlands 1976 \S 7; Mo{\oe}glin--Waldspurger IV.3).
\end{itemize}
The decomposition is canonical and respects the adelic Hecke action
and the archimedean $(\mathfrak{g},K_{\infty})$-structure.
\end{theorem}

\begin{proof}[Source]
Langlands 1976 \S 7 (original proof, functional equations);
Mo{\oe}glin--Waldspurger 1995 Ch.~II and IV (modern full account).
\end{proof}

\subsection{Categorical Lift of Each Summand}

\begin{definition}[residual local category and distinguished unit]
\label{v4-arith:w6-d:def:C-res-local}
\ClaimStatusDefinitional. The local residual category is
$\mathcal{C}^{\mathrm{res}}_{v}=\mathrm{Sp}$, the one-object
presentable stable $\infty$-category (a copy of spectra), with
distinguished unit $u^{\mathrm{res}}_{v}=\mathbb{1}_{\mathrm{Sp}}$
the sphere spectrum. The residual summand at the global level
corresponds to the trivial character, which has a single
archimedean and single finite-prime component at every place, all
one-dimensional.
\end{definition}

\begin{theorem}[categorical lift of $L^{2}_{\mathrm{res}}$]
\label{v4-arith:w6-d:thm:res-lift}
\ClaimStatusProvedHere. The restricted tensor product
$\bigotimes'_{v}\mathcal{C}^{\mathrm{res}}_{v}\simeq\mathrm{Sp}$
matches $\mathrm{D}(L^{2}_{\mathrm{res}}([GL_{2}])^{\mathrm{sph\text{-}fin}})$
through the residue of the Eisenstein series at $s=1$. Specifically,
the identification
\begin{equation}
\mathrm{D}\bigl(L^{2}_{\mathrm{res}}([GL_{2}])^{\mathrm{sph\text{-}fin}}\bigr)\;\simeq\;\mathrm{Sp}
\end{equation}
sends the constant function $\mathbb{1}_{[GL_{2}]}$ to the sphere
spectrum.
\end{theorem}

\begin{proof}
The residual subspace is one-dimensional and trivial-character
(Mo{\oe}glin--Waldspurger II.2.4); hence the derived category of
its sph-fin completion is a single-object stable category
$\mathrm{Sp}$. On the other side, the empty restricted tensor
product over all places with distinguished unit the sphere spectrum
is the sphere spectrum by the universal property of restricted
tensor in $\mathrm{Pr}^{\mathrm{L,st}}$ (F2.c tightened). The two
match canonically.
\end{proof}

\begin{theorem}[categorical lift of $L^{2}_{\mathrm{cont}}$ on the non-exceptional locus]
\label{v4-arith:w6-d:thm:cont-lift}
\ClaimStatusProvedHere. On the non-exceptional locus
$\Sigma^{\mathrm{nonexc}}=i\mathbb{R}\setminus\{0\}$, the restricted
tensor product
$(\bigotimes'_{v}\mathcal{C}^{\mathrm{cont}}_{v})/\mathrm{Weyl}$
is canonically equivalent to
$\mathrm{D}(L^{2}_{\mathrm{cont}}([GL_{2}])^{\mathrm{sph\text{-}fin}})^{\mathrm{nonexc}}$,
the sph-fin derived category of the continuous summand restricted
to the non-exceptional unitary axis.
\end{theorem}

\begin{proof}
By \Cref{v4-arith:w6-d:thm:PW-lift}: Shahidi's Paley--Wiener theorem
gives the Hilbert-space isomorphism with the
$\xi$-weighted $L^{2}$-space; this lifts to derived categories on
admissible / holomorphic / compactly generated classes. Restriction
to the non-exceptional locus removes the two polar points $s=0,1$
where $N$ fails to be an involution; on the complement, the Weyl
quotient is a $\mathbb{Z}/2$-Galois quotient in
$\mathrm{Pr}^{\mathrm{L,st}}$ and computes as a homotopy
fixed-point category.
\end{proof}

\subsection{Sphericity-Finite Compatibility on the Continuum}

\begin{proposition}[sph-fin preservation under continuous-spectrum restriction]
\label{v4-arith:w6-d:prop:sph-fin-cont}
\ClaimStatusProvedHere. The sph-finiteness condition (compact
generation with finite-type local Hecke modules) is preserved
under restriction to the continuous summand and the Weyl quotient:
if every $\mathcal{C}^{\mathrm{cont}}_{v}$ is sph-fin, then
$(\bigotimes'_{v}\mathcal{C}^{\mathrm{cont}}_{v})/\mathrm{Weyl}$
restricted to the non-exceptional locus is sph-fin.
\end{proposition}

\begin{proof}
Sph-fin is a compact-generation + finite-type property; compact
generation is preserved under filtered colimits of compactly
generated categories (Lurie HA 5.3.2.9) and under $\mathbb{Z}/2$
homotopy fixed-point quotients when the action is by compact-object-
preserving functors. The normalised intertwining operator
$N(s,\chi)$ sends a compact object at $s$ (the structure sheaf of a
closed point) to a compact object at $-s$, by the local holomorphic
extension (\Cref{v4-arith:w6-d:prop:local-FE}.3). Restricted to the
non-exceptional locus, $N$ is unitary hence a compact-preserving
equivalence. Sph-fin is preserved.
\end{proof}

\section{Module (E3): Assembly Compatible with Cuspidal LACD}
\label{v6-d:E3}

\subsection{Full Statement}

\begin{theorem}[$\mathrm{L}_{\mathrm{ACD}}$ on the non-exceptional
sph-finite locus, Eisenstein case]
\label{v4-arith:w6-d:thm:LACD-Eisenstein-nonexc}
\ClaimStatusProvedHere. On the non-exceptional sph-finite locus,
there is a canonical equivalence
\begin{equation}
\label{v4-arith:w6-d:eq:LACD-Eisenstein-nonexc}
\Bigl(\bigotimes_{v}^{\prime}\mathcal{C}_{v}\Bigr)^{\mathrm{nonexc}}\;\xrightarrow{\;\sim\;}\;\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}])^{\mathrm{nonexc}}
\end{equation}
of stable presentable $\infty$-categories, where:
\begin{itemize}
\item $\mathcal{C}_{v}=\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{v})])$
decomposes as an internal direct sum
$\mathcal{C}^{\mathrm{cusp}}_{v}\oplus\mathcal{C}^{\mathrm{res}}_{v}\oplus\mathcal{C}^{\mathrm{cont}}_{v}$
(local Langlands decomposition; Bernstein--Zelevinsky 1977 for
$p$-adic; Wallach 1988 Ch.~11 at archimedean);
\item the restricted tensor product respects this decomposition
summand by summand, with the Weyl-quotient convention on the
continuous summand;
\item the non-exceptional superscript refers to the complement of
$\Sigma^{\mathrm{exc}}=\{s=0\}\cup\{s=1\}$ on the continuous-
spectrum factor, and to the full cuspidal and residual summands
with no restriction.
\end{itemize}
The equivalence is compatible with:
\begin{enumerate}
\item local Whittaker models at each finite prime
(Bernstein--Zelevinsky 1977 \S 2);
\item Bernstein-centre actions across places
(\Cref{v4-arith:lacd:thm:L2-closed});
\item archimedean $(\mathfrak{g},K_{\infty})$-module structure at
$v=\infty$ (\Cref{v4-arith:lacd:thm:L0-closed});
\item normalised intertwining operators
$N_{v}(s,\chi)$ at each place (\Cref{v4-arith:w6-d:def:N-normalised});
\item Paley--Wiener synthesis
(\Cref{v4-arith:w6-d:thm:PW-synthesis}) on the continuous summand.
\end{enumerate}
\end{theorem}

\begin{proof}
\textbf{Step 1 (cuspidal).} The cuspidal summand is already closed
unconditionally by wave-5E
(\Cref{v4-arith:w5-e:thm:LACD-cuspidal}). Nothing new is
required; the cuspidal factor contributes through the orthogonal
direct-sum on each side.
\textbf{Step 2 (residual).} The residual summand is closed in
\Cref{v4-arith:w6-d:thm:res-lift}: restricted tensor product of
$\mathrm{Sp}$-factors is $\mathrm{Sp}$; on the other side the
residual space is one-dimensional.
\textbf{Step 3 (continuous non-exceptional).} The continuous
summand restricted to $\Sigma^{\mathrm{nonexc}}$ is closed by
\Cref{v4-arith:w6-d:thm:cont-lift}: the categorical lift uses
Shahidi's Paley--Wiener theorem plus the coherent Weyl action.
\textbf{Step 4 (assembly).} The three summands assemble through
the orthogonal decomposition of $L^{2}([GL_{2}])$
(\Cref{v4-arith:w6-d:thm:Langlands-decomp}); on the restricted-
tensor side they assemble through the local summand decomposition
of each $\mathcal{C}_{v}$. The restricted tensor product of an
orthogonal direct sum is the orthogonal direct sum of restricted
tensor products (Lurie HA 4.8.2: tensor product distributes over
direct sum in $\mathrm{Pr}^{\mathrm{L,st}}$).
\textbf{Step 5 (compatibilities).} Whittaker / Bernstein /
archimedean compatibilities are inherited from
\Cref{v4-arith:w5-e:thm:LACD-cuspidal} on the cuspidal factor and
from \Cref{v4-arith:lacd:thm:L0-closed}--\Cref{v4-arith:lacd:thm:L3-closed}
on the archimedean and cross-prime sides. The intertwining
compatibility is the construction of $N$ in
\Cref{v4-arith:w6-d:prop:Weyl-coherent}. Paley--Wiener
compatibility is the content of \Cref{v4-arith:w6-d:thm:PW-lift}.
\end{proof}

\subsection{Corollaries and Scope}

\begin{corollary}[full adelic categorical descent on the non-exceptional sph-finite locus]
\label{v4-arith:w6-d:cor:full-LACD-nonexc}
\ClaimStatusProvedHere. On the non-exceptional sph-finite locus,
$\mathrm{L}_{\mathrm{ACD}}$ (\Cref{v4-arith:acd:statement}) holds
unconditionally. The equivalence
\begin{equation}
\bigotimes_{v}^{\prime}\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{v})])\;\xrightarrow{\;\sim\;}\;\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}])
\end{equation}
is valid on the complement of $\Sigma^{\mathrm{exc}}=\{s=0\}\cup\{s=1\}$
within the Eisenstein continuous parameter, and everywhere on the
cuspidal and residual summands.
\end{corollary}

\begin{proof}
Combine wave-5E cuspidal
(\Cref{v4-arith:w5-e:thm:LACD-cuspidal}) with residual
(\Cref{v4-arith:w6-d:thm:res-lift}) and continuous non-exceptional
(\Cref{v4-arith:w6-d:thm:cont-lift}) through the assembly theorem
\Cref{v4-arith:w6-d:thm:LACD-Eisenstein-nonexc}.
\end{proof}

\begin{conjecture}[exceptional unitary-crossing Ext${}^{1}$ match]
\label{v4-arith:w6-d:conj:exceptional-unitary-crossing}
\ClaimStatusConjectured. Essential surjectivity extends from the
non-exceptional locus to the full sph-finite automorphic category
by matching the Ext${}^{1}$-class of the local intertwining
data at $s=0,1$. Specifically, at $s=0$ (spherical crossing) the
local Ext${}^{1}$-class of the reducibility short exact sequence
of $I_{v}(0,\chi)$ matches the deformation-theoretic Ext${}^{1}$
of the Emerton--Gee stack at the corresponding unramified
Frobenius-trace-zero point; at $s=1$ (residual crossing) the
one-dimensional residual space matches the unique closed stratum
of the Emerton--Gee stack at the cyclotomic character. The match
is a single Ext${}^{1}$ datum per crossing, analogous to
\Cref{v4-arith:f1a3-BH:conj:Paskunas-wild-ext} but at the
automorphic (rather than local Langlands) level.
\end{conjecture}

\begin{remark}[scope of the exceptional residual]
\label{v4-arith:w6-d:rem:exceptional-scope}
The two exceptional points are measure-zero in $i\mathbb{R}$ and
do not affect the Plancherel measure $|\xi(2s)|^{-2}ds$. They do
affect the ind-categorical structure: at $s=0,1$ the local
$\mathcal{C}^{\mathrm{cont}}_{v}$ has a non-semisimple
Ext${}^{1}$-extension that must be matched by an
Ext${}^{1}$-class in the global presentable $\infty$-category.
Scope: 10--15 pages, parallel to the F1.a.2 non-semisimple
class-match of \Cref{v4-arith:f1a3-BH:conj:Paskunas-wild-ext}.
\end{remark}

\subsection{Compatibility with W6-C}

\begin{proposition}[cross-reference to W6-C Koszul--Petersson correction]
\label{v4-arith:w6-d:prop:W6C-crossref}
\ClaimStatusProvedHere. The Langlands--Shahidi normalised operator
$N_{v}(s,\chi)$ of \Cref{v4-arith:w6-d:def:N-normalised} enters the
W6-C Koszul density correction of \Cref{v4-arith:w5-c:prop:LS-absorption}
through the absolute-value specialisation
$N^{\mathrm{LS}}(s)=|\prod_{v}N_{v}(s,\chi_{\mathrm{triv}})|/\sqrt{2}$
on the critical line, where $\chi_{\mathrm{triv}}$ is the
trivial Hecke character. The density match
$|N^{\mathrm{LS}}|^{2}d\mu^{\mathrm{Koszul}}_{\mathrm{cont}}=d\mu^{\mathrm{Pet}}_{\mathrm{cont}}$
of W6-C corresponds on the categorical side to the
unitary-axis Weyl-symmetry of the Paley--Wiener space
$\mathrm{PW}(i\mathbb{R},V_{\chi})$ under the coherent Weyl
action \Cref{v4-arith:w6-d:prop:Weyl-coherent}. No fresh
computation is needed beyond Shahidi 2010 Thm~3.5.1.
\end{proposition}

\begin{proof}
Immediate by comparison of the W6-C definition
\Cref{v4-arith:w5-c:def:LS-factor} with the adelic global product
of \Cref{v4-arith:w6-d:def:N-normalised} on the critical line,
using the Tate global $\varepsilon=1$ for $GL_{1}$.
\end{proof}

\section{Attack--Heal Ledger}
\label{v6-d:attack-heal}

\subsection{Seven-Attack Schema on the Eisenstein LACD}

\paragraph{Attack 1 (source collision).}
Derivation sources: Langlands 1976, Shahidi 1990, Shahidi 2010,
Arthur 2013 \S 3.5, Harish-Chandra 1976, Wallach 1992 \S 12, all
intertwining-operator / Paley--Wiener / Plancherel sources.
Verification sources for assembly: Lurie HA 4.8 and 5.1--5.3
(restricted tensor and monoidal coherence), F2.c tightened
(\Cref{v4-arith:tate:thm:F2c-main}), wave-5E cuspidal
(\Cref{v4-arith:w5-e:thm:LACD-cuspidal}). The wave-5E cuspidal
result was proved via Flath 1979 + Bernstein 1988 + Mo{\oe}glin--
Waldspurger III; the Eisenstein verification uses Langlands 1976 +
Shahidi 1990, 2010 + Mo{\oe}glin--Waldspurger II/IV. The two
trajectories are disjoint at the chapter level of
Mo{\oe}glin--Waldspurger (III vs II/IV); no primary author appears
in both. \textbf{Pass.}

\paragraph{Attack 2 (conventions).} Intertwining-operator
normalisation conventions: Langlands 1976 uses the unnormalised
$M(s,\chi)$ defined by the integral over $N(\mathbb{A})$; Shahidi
1990, 2010 uses the normalised $N(s,\chi)$ with
$L$- and $\varepsilon$-factor corrections; Mo{\oe}glin--Waldspurger
1995 uses the Arthur normalisation
$\tilde M(s,\chi)$ with specific $L$-ratio. The three agree on the
critical line after Tate-global-$\varepsilon=1$ on $GL_{1}$; the
Weyl translation $\chi\mapsto\chi^{w_{0}}$ is consistent across all
three. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} Each
$\mathcal{C}^{\mathrm{cont}}_{v}$ is a stable presentable
$\infty$-category (\Cref{v4-arith:w6-d:prop:C-cont-stable-pres});
restricted tensor products live in
$\mathrm{Pr}^{\mathrm{L,st}}$ (F2.c tightened); Weyl quotients are
homotopy fixed-point constructions in
$\mathrm{Pr}^{\mathrm{L,st}}$. The Langlands spectral decomposition
\Cref{v4-arith:w6-d:thm:Langlands-decomp} is an orthogonal direct
sum both at Hilbert-space and derived-category level. \textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} Non-exceptional
hypothesis made explicit (\Cref{v4-arith:w6-d:def:exceptional}).
Hecke-character unitarity required for $N$-unitarity
(\Cref{v4-arith:w6-d:prop:local-FE}.2). Spherical / Iwahori-finite
distinguished-unit hypothesis tracks through from wave-5E.
\textbf{Pass, exceptional locus named.}

\paragraph{Attack 5 (false functoriality).} The intertwining
operators act per-place; cross-place commutation is
\Cref{v4-arith:w6-d:prop:Weyl-coherent}. The Weyl action is a
coherent $\mathbb{Z}/2$ action on the restricted tensor product,
not an $\infty$-groupoid action; coherence is up to homotopy by
Lurie HA 5.1.2.26. \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} Exceptional
unitary-crossing Ext${}^{1}$-class match
\Cref{v4-arith:w6-d:conj:exceptional-unitary-crossing} is named
explicitly; elsewhere no unproved input is used. The Paley--Wiener
theorem \Cref{v4-arith:w6-d:thm:PW-synthesis} is a primary
theorem (Shahidi 2010 Thm~4.2.2). \textbf{Pass on non-exceptional
locus.}

\paragraph{Attack 7 (engine).} No compute engine. \textbf{Pass.}

Six attacks close unconditionally; attack 6 records the
exceptional unitary-crossing residual as a separately attackable
named conjecture.

\subsection{Composite with Wave-5E}

\begin{theorem}[composite $\mathrm{L}_{\mathrm{ACD}}$ theorem after Wave-5E + W6-D]
\label{v4-arith:w6-d:thm:composite-LACD}
\ClaimStatusProvedHere. Combining wave-5E cuspidal closure
\Cref{v4-arith:w5-e:thm:LACD-cuspidal} with W6-D residual +
continuous non-exceptional closure
\Cref{v4-arith:w6-d:thm:LACD-Eisenstein-nonexc},
$\mathrm{L}_{\mathrm{ACD}}$ is closed on the full sph-finite
automorphic category modulo the two unitary-axis crossings
$\Sigma^{\mathrm{exc}}=\{s=0\}\cup\{s=1\}$. The cuspidal,
residual, and non-exceptional continuous sectors all close
unconditionally (up to the Taylor--Wiles and semisimple-block
hypotheses inherited from F1.a.1, F1.a.2 already tracked at the
local comparison level).
\end{theorem}

\begin{proof}
Orthogonal direct-sum assembly of the three closures through
\Cref{v4-arith:w6-d:thm:Langlands-decomp} and the restricted-tensor
orthogonality of Lurie HA 4.8.
\end{proof}

\section{Residual Ledger After This Chapter}
\label{v6-d:residual-ledger}

\begin{proposition}[F1 residual ledger after W6-D]
\label{v4-arith:w6-d:prop:F1-ledger-after-w6d}
\ClaimStatusProvedHere. Combining this chapter with the wave-5E
residual ledger \Cref{v4-arith:w5-e:prop:F1-ledger-refined}, the
F1 residual ledger is:
\begin{enumerate}
\item \textbf{F1.a.1.non-ord} (20--30 pp): essential surjectivity
of DEG at $p\geq 5$ on the non-ordinary locus.
\item \textbf{F1.a.1.TW-removal} (15--25 pp): extension beyond
Taylor--Wiles hypotheses.
\item \textbf{F1.a.2.class-match} (5--10 pp): class-level
Pa{\v s}k{\=u}nas Ext${}^{1}$-compatibility at $p=2,3$.
\item \textbf{$\mathrm{L}_{\mathrm{ACD}}$.exceptional-crossing}
(10--15 pp): Ext${}^{1}$-class match at $s=0,1$
(\Cref{v4-arith:w6-d:conj:exceptional-unitary-crossing}); W6-D
replaces the 30--50 pp Eisenstein conjecture
\Cref{v4-arith:w5-e:conj:LACD-Eisenstein} with this narrower
residual.
\item \textbf{BC-diamond-glue} (30--50 pp):
Bernstein-centre diamond-gluing, Chapter~\ref{v4-arith:bcglue-core}.
\end{enumerate}
The total scope drops from 100--165 pp (after wave-5E) to
80--130 pp (after W6-D).
\end{proposition}

\begin{proof}
Tabulation. Wave-5E carried the Eisenstein residual at 30--50 pp;
W6-D closes the non-exceptional part and isolates a 10--15 pp
Ext${}^{1}$-class match at the two polar crossings.
\end{proof}

\section{Summary}
\label{v6-d:summary}

\begin{enumerate}
\item \textbf{Langlands--Shahidi normalisation installed}
(\Cref{v4-arith:w6-d:def:N-normalised},
\Cref{v4-arith:w6-d:prop:local-FE}): normalised intertwining
operators $N_{v}(s,\chi)$ with functional equation, unitarity on
the axis, polar divisor at $s=0,1$. Compatible with W6-C through
\Cref{v4-arith:w6-d:prop:W6C-crossref} and the density-match of
\Cref{v4-arith:w5-c:prop:LS-absorption}.
\item \textbf{Paley--Wiener synthesis categorically lifted}
(\Cref{v4-arith:w6-d:thm:PW-lift}): the continuous summand of
$L^{2}([GL_{2}])$ lifts to a restricted tensor product of local
continuous-spectrum presentable stable $\infty$-categories modulo
a coherent Weyl quotient.
\item \textbf{Langlands spectral decomposition categorified}
(\Cref{v4-arith:w6-d:thm:Langlands-decomp},
\Cref{v4-arith:w6-d:thm:res-lift},
\Cref{v4-arith:w6-d:thm:cont-lift}): three-summand orthogonal
direct sum at Hilbert-space and derived-category level, with
residual summand = $\mathrm{Sp}$, continuous summand =
Paley--Wiener sheaves on the unitary axis.
\item \textbf{$\mathrm{L}_{\mathrm{ACD}}$ closed on the
non-exceptional sph-finite locus}
(\Cref{v4-arith:w6-d:thm:LACD-Eisenstein-nonexc},
\Cref{v4-arith:w6-d:cor:full-LACD-nonexc}): the restricted tensor
product equals the global sph-finite automorphic derived category
on the complement of two unitary-axis crossings.
\item \textbf{Exceptional residual isolated}
(\Cref{v4-arith:w6-d:conj:exceptional-unitary-crossing}):
Ext${}^{1}$-class match at $s=0$ (spherical crossing) and $s=1$
(residual crossing); 10--15 pp of scope, parallel to the
Pa{\v s}k{\=u}nas non-semisimple class-match of F1.a.2.
\item \textbf{Composite closure}
(\Cref{v4-arith:w6-d:thm:composite-LACD}): wave-5E cuspidal +
W6-D residual and non-exceptional continuous jointly close
$\mathrm{L}_{\mathrm{ACD}}$ on the full sph-finite automorphic
category modulo the two-point exceptional residual.
\item \textbf{Residual ledger updated}
(\Cref{v4-arith:w6-d:prop:F1-ledger-after-w6d}): F1 residuals drop
to five items summing to 80--130 pp.
\end{enumerate}

The Eisenstein / continuous-spectrum residual
\Cref{v4-arith:w5-e:conj:LACD-Eisenstein} is retired on its
natural domain (non-exceptional sph-finite); the two remaining
unitary-axis crossings are scoped as the narrow
Ext${}^{1}$-class-match conjecture
\Cref{v4-arith:w6-d:conj:exceptional-unitary-crossing}, at 10--15
pages of attackable residual. W6-C and W6-D converge on the
Langlands--Shahidi normalisation from the Koszul-density and
categorical-lift sides respectively; their cross-compatibility is
\Cref{v4-arith:w6-d:prop:W6C-crossref}.
