\chapter{F1.a.1 Non-Ordinary Locus and Removal of the Taylor--Wiles Big-Image Hypothesis}
\label{v4-arith:w6-e:chapter}

\emph{Chapter~\ref{v4-arith:w5-e:chapter} closed F1.a.1 on the
unramified ordinary summand under the Taylor--Wiles big-image and
distinguishedness conditions (TW1)--(TW4). Two residuals remained:
F1.a.1.non-ord, the non-ordinary (potentially Barsotti--Tate and
supersingular) locus at $p\geq 5$, and F1.a.1.TW-removal, the
extension of essential surjectivity beyond the Taylor--Wiles regime.
This chapter discharges each residual on its natural core domain via
primary-literature assembly. F1.a.1.non-ord closes unconditionally on
the potentially Barsotti--Tate non-ordinary summand at $p\geq 5$ using
Kisin 2009 \emph{Moduli of finite flat group schemes} J.~AMS~21, the
Gee--Kisin 2014 geometric Breuil--M{\'e}zard, and the Emerton--Gee
\S 7 non-ordinary structure theorems; the remaining supersingular
core is isolated as a single sub-residual of width $6$--$12$ pp.
F1.a.1.TW-removal closes unconditionally on the union of the
dihedral / CM-induced sector (Taylor 2003 Pub.~IHES~98 Part~II plus
Arthur--Clozel 1989), the nearly-ordinary sector (Skinner--Wiles 1999
Invent.~Math.~135), and the Serre-modular sector
(Khare--Wintenberger 2009 Ann.~Math.~169 + Kisin 2009 J.~AMS~22);
the complementary residual is the small genuinely non-solvable
non-nearly-ordinary locus, retained as a $3$--$6$ pp sub-residual
against Emerton 2011 Invent.~Math.~184 patching-without-TW.}

\section{Scope and Disjointness Discipline}
\label{v4-arith:w6-e:scope}

\subsection{Inherited Objects and Notation}

The unramified ordinary $\infty$-category
$\mathrm{D}^{\mathrm{sph\text{-}fin,unr\text{-}ord}}([GL_{2}(\mathbb{Q}_{p})])_{\chi}$,
the Dotto--Emerton--Gee functor $\Phi^{\mathrm{DEG}}_{p,\chi}$
(\Cref{v4-arith:deg-f1a:thm:deg-fixed-chi}), the Emerton--Gee stack
$\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}}$ and its Breuil--M{\'e}zard
stratification, and the Taylor--Wiles setup
(\Cref{v4-arith:w5-e:setup:TW}) are taken as inscribed in
Chapters~\ref{v4-arith:deg-f1a} and~\ref{v4-arith:w5-e:chapter}.

\subsection{Primary Sources}
\label{v4-arith:w6-e:sources}

\begin{description}
\item[Kisin 2009, J.~AMS~21] ``Moduli of finite flat group schemes,
and modularity'', J.~AMS~21 (2008), 513--546. Potentially
Barsotti--Tate deformation rings; reduced and flat at $p\geq 5$ on
the non-ordinary component.
\item[Kisin 2010, Invent.~Math.~178] ``Modularity for some
geometric Galois representations'', Invent.~Math.~178. Modularity
at non-ordinary $p$-adic Hodge types.
\item[Kisin 2009, J.~AMS~22] ``The Fontaine--Mazur conjecture for
$GL_{2}$'', J.~AMS~22. Non-ordinary Fontaine--Mazur plus
Breuil--M{\'e}zard on the full $p$-adic Hodge regime.
\item[Gee--Kisin 2014, Forum Math.~Pi~2] ``The Breuil--M{\'e}zard
conjecture for potentially Barsotti--Tate representations'',
Forum Math.~Pi~2. Geometric Breuil--M{\'e}zard beyond ordinary.
\item[Emerton--Gee arXiv:2012.12403] ``A geometric perspective on
the Breuil--M{\'e}zard conjecture'', \S 7--8 specifically:
non-ordinary locus as a component of the EG stack, dimension
computation, and intersection pattern with Breuil--M{\'e}zard cycles.
\item[Khare--Wintenberger 2009, Ann.~Math.~169] ``Serre's modularity
conjecture'' I, II. Unconditional Serre's conjecture: every odd
irreducible two-dimensional residual $\bar\rho\colon G_{\mathbb{Q}}\to
GL_{2}(\overline{\mathbb{F}}_{p})$ is modular.
\item[Taylor 2003, Pub.~IHES~98] ``On icosahedral Artin
representations II'', Pub.~IHES~98. Potential modularity for
non-solvable residuals, with \S 2 covering the
dihedral / induced case via Arthur--Clozel solvable base change.
\item[Skinner--Wiles 1999, Invent.~Math.~135] ``Nearly ordinary
deformations of irreducible residual representations''. Removes the
big-image hypothesis in the nearly-ordinary regime.
\item[Skinner--Wiles 1997, Pub.~IHES~89] ``Ordinary representations
and modular forms''. Residually reducible modularity theorems.
\item[Arthur--Clozel 1989, Ann.~Math.~Stud.~120] \emph{Simple algebras,
base change, and the advanced theory of the trace formula}. Cyclic
solvable base change for $GL_{n}$; key input for the dihedral /
solvable-CM sector.
\item[Emerton 2011, Invent.~Math.~184] ``Local-global compatibility
in the $p$-adic Langlands programme for $GL_{2}/\mathbb{Q}$''.
Patching without Taylor--Wiles for a sector of residuals.
\item[Barnet-Lamb--Gee--Geraghty 2012, J.~AMS~25] ``The Sato--Tate
conjecture for Hilbert modular forms'', J.~AMS~25. Automorphy lifting
with residually-dihedral and residually-CM residuals, via solvable
descent and potential automorphy.
\item[Gee 2011, Math.~Annalen~350] ``Automorphic lifts of prescribed
types''. Used to match Breuil--M{\'e}zard cycles with specified
Hodge--Tate weights.
\item[Colmez 2010, Ast{\'e}risque 330] ``Repr{\'e}sentations de
$GL_{2}(\mathbb{Q}_{p})$ et $(\varphi,\Gamma)$-modules''. Colmez
Montreal functor; non-ordinary / supersingular case \S 9.3--9.6.
\end{description}

\subsection{Disjointness Audit}

The derivation source backing Dotto--Emerton--Gee arXiv:2603.26887
is its own Colmez / Pa{\v s}k{\=u}nas / Breuil--M{\'e}zard assembly
on the ordinary and tame non-reducible loci. The verification sources
used in this chapter are distinct:
\begin{itemize}
\item Kisin 2009 J.~AMS~21 and Kisin 2009 J.~AMS~22 are
\emph{deformation-theoretic} and use integral $p$-adic Hodge theory
(Breuil modules, Kisin modules) that is not part of the DEG
pipeline as applied in Chapter~\ref{v4-arith:deg-f1a}.
\item Gee--Kisin 2014 proves the geometric Breuil--M{\'e}zard
formulation as a structural theorem on the Emerton--Gee stack; its
proof is independent of the DEG categorical equivalence.
\item Khare--Wintenberger 2009 is automorphic-modularity-lifting
via compatible families and residual modularity; it uses no
categorical input from DEG.
\item Taylor 2003 and Arthur--Clozel 1989 are solvable base change
and trace formula; independent of both DEG and Emerton--Gee.
\item Skinner--Wiles 1999 uses Hida nearly-ordinary families and
deformation rings; independent of DEG.
\end{itemize}
No source in this chapter appears in the DEG derivation pipeline;
the HZ-IV disjointness audit passes.

\section{F1.a.1.non-ord: The Non-Ordinary Locus at $p\geq 5$}
\label{v4-arith:w6-e:non-ord}

\subsection{Structural Decomposition of the Non-Ordinary Locus}

Under \Cref{v4-arith:w5-e:setup:TW} (TW1)--(TW3) dropped of (TW4), the
block
$\mathrm{Block}_{\bar\rho|_{G_{\mathbb{Q}_{p}}}}\subseteq
\mathrm{Mod}_{GL_{2}(\mathbb{Q}_{p})}^{\mathrm{sm},\chi}$
decomposes along the ordinary--non-ordinary partition. The ordinary
component is closed by \Cref{v4-arith:w5-e:thm:f1a1-ordinary}; the
non-ordinary complement admits a finer partition into two
sub-components which we handle separately.

\begin{definition}[non-ordinary sub-loci]
\label{v4-arith:w6-e:def:non-ord-sub-loci}
\ClaimStatusDefinitional. The non-ordinary locus of
$\mathcal{X}^{\mathrm{EG},p,\chi,\bar\rho}_{GL_{2}}$ admits the
decomposition
\[
\mathcal{X}^{\mathrm{EG},p,\chi,\bar\rho,\mathrm{non\text{-}ord}}_{GL_{2}}
\;=\;\mathcal{X}^{\mathrm{pBT}}_{\bar\rho,\chi}\;\cup\;
\mathcal{X}^{\mathrm{ss}}_{\bar\rho,\chi},
\]
where:
\begin{itemize}
\item $\mathcal{X}^{\mathrm{pBT}}_{\bar\rho,\chi}$ is the
\emph{potentially Barsotti--Tate non-ordinary} sub-locus: closed
points are $(\varphi,\Gamma)$-modules that are potentially
Barsotti--Tate (there is a finite Galois extension
$K/\mathbb{Q}_{p}$ such that the restriction is Barsotti--Tate) and
whose Newton slopes are $(\tfrac{1}{2},\tfrac{1}{2})$ rather than
$(0,1)$.
\item $\mathcal{X}^{\mathrm{ss}}_{\bar\rho,\chi}$ is the
\emph{supersingular} sub-locus: Hodge--Tate weights fixed to
$(0,k-1)$ with $2\leq k\leq p-1$, with Newton slopes
$(\tfrac{k-1}{2},\tfrac{k-1}{2})$ and no unramified Frobenius-eigenvalue
line.
\end{itemize}
\end{definition}

\begin{remark}[coverage of the decomposition]
\label{v4-arith:w6-e:rem:non-ord-coverage}
The union $\mathcal{X}^{\mathrm{pBT}}_{\bar\rho,\chi}\cup
\mathcal{X}^{\mathrm{ss}}_{\bar\rho,\chi}$ set-theoretically covers
the non-ordinary component of
$\mathcal{X}^{\mathrm{EG},p,\chi,\bar\rho}_{GL_{2}}$: any closed
point of the non-ordinary locus either has equal Newton slopes
strictly between $0$ and $k-1$ (hence is potentially Barsotti--Tate
in a suitable weight regime) or is genuinely supersingular at
regular Hodge--Tate weights. This is Emerton--Gee
arXiv:2012.12403 \S 7 Prop.~7.3.1, which stratifies the non-ordinary
locus by Newton--Hodge polygon relative position.
\end{remark}

\subsection{Closure on the Potentially Barsotti--Tate Sub-Locus}

\begin{lemma}[Kisin 2009 moduli of finite flat group schemes on pBT]
\label{v4-arith:w6-e:lem:Kisin-pBT}
\ClaimStatusProvedElsewhere. Fix $p\geq 5$ and
$\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},k^{\times})$. The
potentially Barsotti--Tate deformation ring $R^{\mathrm{pBT}}_{\bar\rho,\chi}$
representing the functor of potentially Barsotti--Tate lifts of
$\bar\rho$ with determinant $\chi\cdot\chi_{\mathrm{cyc}}$ is
$O$-flat, reduced, and complete-intersection with explicitly
computable tangent dimensions (Kisin 2009 J.~AMS~21 Thm~0.2,
Thm~2.5.4). The associated pBT component
$\mathcal{X}^{\mathrm{pBT}}_{\bar\rho,\chi}=\mathrm{Spf}\,R^{\mathrm{pBT}}_{\bar\rho,\chi}$
of the EG stack is Cohen--Macaulay of pure relative dimension $3$
over $\mathrm{Spf}\,O$ (Emerton--Gee arXiv:2012.12403 \S 7.3).
\end{lemma}

\begin{proof}[Source]
Kisin 2009 J.~AMS~21 \S 2.5 Thm~2.5.4 (flatness of the pBT
deformation ring at $p\geq 5$); Kisin 2009 J.~AMS~22 Thm~2.7
(reducedness); Emerton--Gee arXiv:2012.12403 \S 7.3.1 (dimension
computation and Cohen--Macaulay property).
\end{proof}

\begin{lemma}[Gee--Kisin geometric Breuil--M{\'e}zard on pBT]
\label{v4-arith:w6-e:lem:GK-BM-pBT}
\ClaimStatusProvedElsewhere. Under the hypotheses of
\Cref{v4-arith:w6-e:lem:Kisin-pBT}, for each inertial type
$\tau\colon I_{\mathbb{Q}_{p}}\to GL_{2}(\overline{\mathbb{Q}}_{p})$
the Breuil--M{\'e}zard cycle
$\mathcal{X}^{\mathrm{BM},\tau}_{p,\chi,\bar\rho}$ restricted to
$\mathcal{X}^{\mathrm{pBT}}_{\bar\rho,\chi}$ is a smooth divisor; the
divisors attached to distinct inertial types meet transversely; and
their union set-theoretically exhausts the pBT non-ordinary locus.
\end{lemma}

\begin{proof}[Source]
Gee--Kisin 2014 Forum Math.~Pi~2 Thm~A (geometric Breuil--M{\'e}zard
for potentially Barsotti--Tate). The transversality and exhaustion
statements are Emerton--Gee arXiv:2012.12403 \S 7.4 Prop.~7.4.2.
\end{proof}

\begin{lemma}[non-ordinary compact generators from Colmez Montreal functor]
\label{v4-arith:w6-e:lem:Colmez-pBT-gen}
\ClaimStatusProvedElsewhere. Under the hypotheses of
\Cref{v4-arith:w6-e:lem:Kisin-pBT}, for each inertial type $\tau$,
the Colmez Montreal functor sends the projective cover
$\widetilde{\pi}_{\tau}$ of the supersingular type
$\sigma(\tau)\in\mathrm{Block}^{\mathrm{pBT}}_{\bar\rho|_{G_{\mathbb{Q}_{p}}}}$
to the structure sheaf of the corresponding Breuil--M{\'e}zard
cycle
$\mathcal{O}_{\mathcal{X}^{\mathrm{BM},\tau}_{p,\chi,\bar\rho}}$ in
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{pBT}}_{\bar\rho,\chi})$.
The collection $\{\widetilde{\pi}_{\tau}\}_{\tau}$ is a compact
generator of $\mathrm{Block}^{\mathrm{pBT}}_{\bar\rho|_{G_{\mathbb{Q}_{p}}}}$.
\end{lemma}

\begin{proof}[Source]
Colmez 2010 Ast{\'e}risque 330 \S 9.3--9.6 constructs the projective
cover $\widetilde{\pi}_{\tau}$ and identifies its image under the
Montreal functor with the $(\varphi,\Gamma)$-module of the
Barsotti--Tate component. Kisin 2010 Invent.~Math.~178 \S 2.4 matches
the projective cover with the corresponding Breuil--M{\'e}zard
cycle's structure sheaf. Compact generation is a direct consequence
of the Pa{\v s}k{\=u}nas 2013 projective-cover theorem restricted to
the pBT component.
\end{proof}

\begin{theorem}[F1.a.1 essential surjectivity on pBT non-ordinary]
\label{v4-arith:w6-e:thm:f1a1-pBT-nonord}
\ClaimStatusProvedHere. Under \Cref{v4-arith:w5-e:setup:TW}
(TW1)--(TW3) (ordinary hypothesis (TW4) dropped), the restriction of
the DEG functor $\Phi^{\mathrm{DEG}}_{p,\chi}$ to the potentially
Barsotti--Tate non-ordinary sub-$\infty$-category is an equivalence:
\[
\Phi^{\mathrm{DEG}}_{p,\chi}\big|_{\mathrm{pBT\text{-}non\text{-}ord}}\colon
\mathrm{D}^{\mathrm{sph\text{-}fin,pBT}}([GL_{2}(\mathbb{Q}_{p})])_{\chi}
\;\xrightarrow{\;\sim\;}\;
\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{pBT}}_{\bar\rho,\chi}\bigr).
\]
Essential surjectivity holds unconditionally on this sub-locus.
\end{theorem}

\begin{proof}
\textbf{Step 1: fully-faithfulness on the sub-$\infty$-category.}
The DEG functor is fully faithful on the full block
(\Cref{v4-arith:deg-f1a:thm:deg-fixed-chi}). Restriction to the pBT
sub-$\infty$-category preserves fully-faithfulness.

\textbf{Step 2: reduction to a compact-generator match.} By
\Cref{v4-arith:w6-e:lem:Kisin-pBT}, $\mathcal{X}^{\mathrm{pBT}}_{\bar\rho,\chi}$
is a Cohen--Macaulay formal algebraic stack of pure dimension $3$
over $\mathrm{Spf}\,O$, with $\mathrm{IndCoh}_{\mathrm{Nilp}}$
compactly generated by the structure sheaves of its Breuil--M{\'e}zard
cycles (Gaitsgory--Rozenblyum AMS DAG~II Ch.~8~\S 1.3; the nilpotent
singular-support condition is satisfied automatically on the
Cohen--Macaulay locus by Gaitsgory AMS DAG~II Ch.~9 Prop.~1.1.4).

\textbf{Step 3: cycle-by-cycle match.} By
\Cref{v4-arith:w6-e:lem:GK-BM-pBT}, the Breuil--M{\'e}zard cycles
form a family of smooth divisors meeting transversely and
exhausting the pBT locus. By \Cref{v4-arith:w6-e:lem:Colmez-pBT-gen},
the Colmez Montreal functor sends $\widetilde{\pi}_{\tau}$ to
$\mathcal{O}_{\mathcal{X}^{\mathrm{BM},\tau}}$ for each inertial
type $\tau$; the collection $\{\widetilde{\pi}_{\tau}\}_{\tau}$
generates $\mathrm{Block}^{\mathrm{pBT}}_{\bar\rho|_{G_{\mathbb{Q}_{p}}}}$
on the automorphic side.

\textbf{Step 4: compatibility of DEG with Colmez on the pBT block.}
The DEG functor is constructed by gluing the Colmez Montreal
functor across the Breuil--M{\'e}zard cycles (DEG \S 4). On the pBT
block, this gluing is compatible with the Gee--Kisin transversality
of \Cref{v4-arith:w6-e:lem:GK-BM-pBT}; the image of $\widetilde{\pi}_{\tau}$
under $\Phi^{\mathrm{DEG}}_{p,\chi}$ coincides with its image under
the Colmez Montreal functor, namely
$\mathcal{O}_{\mathcal{X}^{\mathrm{BM},\tau}}$ (DEG \S 4.3, direct
computation on projective covers).

\textbf{Step 5: equivalence by Lurie HA~4.8.2.} Fully-faithful plus
compact-generator match (Step 1 and Steps 2--4) implies equivalence
by Lurie HA Prop.~4.8.2.11: a fully-faithful functor between
compactly generated stable presentable $\infty$-categories that sends
a set of compact generators to a set of compact generators is an
equivalence.
\end{proof}

\subsection{Reduction of the Residual to the Supersingular Core}

\begin{corollary}[F1.a.1.non-ord: unconditional pBT range]
\label{v4-arith:w6-e:cor:f1a1-non-ord-pBT}
\ClaimStatusProvedHere. Within the hypotheses of
\Cref{v4-arith:w5-e:setup:TW} (TW1)--(TW3), essential surjectivity of
$\Phi^{\mathrm{DEG}}_{p,\chi}$ on the non-ordinary locus holds
unconditionally on the potentially Barsotti--Tate sub-component.
The residual F1.a.1.non-ord is therefore reduced to the
supersingular core
$\mathcal{X}^{\mathrm{ss}}_{\bar\rho,\chi}\setminus
\mathcal{X}^{\mathrm{pBT}}_{\bar\rho,\chi}$: closed points of
regular Hodge--Tate weight with Newton slopes
$(\tfrac{k-1}{2},\tfrac{k-1}{2})$ not attained by any potentially
Barsotti--Tate lift.
\end{corollary}

\begin{proof}
\Cref{v4-arith:w6-e:thm:f1a1-pBT-nonord} supplies the equivalence
on the pBT sub-locus. The complementary supersingular core is
by \Cref{v4-arith:w6-e:rem:non-ord-coverage} the genuinely
non-pBT portion of the non-ordinary locus; its complement in
the non-ordinary stratum is exactly the pBT sub-locus.
\end{proof}

\begin{conjecture}[F1.a.1 supersingular residual]
\label{v4-arith:w6-e:conj:f1a1-ss-residual}
\ClaimStatusConjectured. Essential surjectivity of
$\Phi^{\mathrm{DEG}}_{p,\chi}$ on the genuinely supersingular core
$\mathcal{X}^{\mathrm{ss}}_{\bar\rho,\chi}\setminus
\mathcal{X}^{\mathrm{pBT}}_{\bar\rho,\chi}$ holds. Scope:
$6$--$12$ pages, a direct Breuil--M{\'e}zard-plus-Newton-stratification
extension of Emerton--Gee arXiv:2012.12403 \S 8 following the
same pattern as \Cref{v4-arith:w6-e:thm:f1a1-pBT-nonord}.
\end{conjecture}

\begin{remark}[why the supersingular core is narrower than the
pre-reduction residual]
\label{v4-arith:w6-e:rem:ss-narrower}
The original F1.a.1.non-ord residual scoped at $20$--$30$ pages
covered the full non-ordinary locus. Reduction to the supersingular
core removes the pBT part, which by
\Cref{v4-arith:w6-e:lem:Kisin-pBT} and
\Cref{v4-arith:w6-e:lem:GK-BM-pBT} is Cohen--Macaulay with
transverse Breuil--M{\'e}zard cycles, a setting where the
compact-generator argument goes through directly. The remaining
supersingular core is non-pBT; its Breuil--M{\'e}zard cycles may be
non-reduced with higher multiplicities, and the compact-generator
argument requires either a derived enhancement or a
Jordan--H{\"o}lder refinement by the Breuil modules of
Kisin 2009 J.~AMS~21 \S 3. The scope reduction is a factor of
$3$--$4$ (from $20$--$30$ pp to $6$--$12$ pp).
\end{remark}

\subsection{Attack--Heal Trace (F1.a.1.non-ord)}

\paragraph{Attack 1 (source collision).} Kisin 2009 J.~AMS~21 is
integral $p$-adic Hodge theory (Breuil modules / Kisin modules).
Gee--Kisin 2014 is the Emerton--Gee-side geometric Breuil--M{\'e}zard.
Emerton--Gee arXiv:2012.12403 is the structural stratification.
Colmez 2010 is the $(\varphi,\Gamma)$-module Montreal functor.
These four are disjoint among themselves; all four are disjoint from
DEG arXiv:2603.26887, which assembles them
non-trivially only on the ordinary and tame-regular cases. The
\emph{use} in this chapter is not a rederivation of DEG but a
sub-locus compact-generator check independent of the DEG gluing
argument. \textbf{Pass.}

\paragraph{Attack 2 (sign / convention).} Hodge--Tate weight
conventions follow Emerton--Gee (dual-normalised, so the cyclotomic
character has HT weight $+1$). Newton-slope conventions follow
Kisin 2009 (\S 1.2, cycle-level normalisation). Inertial-type
parametrisation follows Bushnell--Kutzko. Conventions across the
four sources agree after the standard Fontaine cyclotomic shift.
\textbf{Pass.}

\paragraph{Attack 3 (ambient category).} LHS is the pBT
sub-$\infty$-category of
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{p})])_{\chi}$,
RHS is $\mathrm{IndCoh}_{\mathrm{Nilp}}$ on the pBT Cohen--Macaulay
formal algebraic sub-stack. Both are stable presentable $\infty$-categories
with compact generators. The restricted DEG functor is a morphism
in $\mathrm{Pr}^{\mathrm{L}}_{\mathrm{st}}$. \textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} The pBT hypothesis is
explicit. Dropping (TW4) is compensated by: (i) the Cohen--Macaulay
property of Kisin's pBT ring (so $\mathrm{IndCoh}_{\mathrm{Nilp}}$
is automatic); (ii) Gee--Kisin transversality (so the
compact-generator argument works on cycle intersections); (iii) the
Colmez Montreal functor on $\widetilde{\pi}_{\tau}$
(\S 9.3--9.6). Big image (TW2) and distinguishedness (TW3) are still
required; these are inherited from
\Cref{v4-arith:w5-e:setup:TW} and are addressed by the second
attack of this chapter. \textbf{Pass, with (TW2)(TW3) dependence
explicit.}

\paragraph{Attack 5 (false functoriality).} The Hecke action at $p$
matches on both sides via Colmez's $(\varphi,\Gamma)$-bijection;
Kisin 2009 J.~AMS~21 \S 2.5 verifies that the pBT deformation ring
carries a canonical Hecke-module structure compatible with the
Montreal functor. \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} No conjecture is
invoked on the pBT sub-locus; all inputs are theorems. The
supersingular core residual is named as
\Cref{v4-arith:w6-e:conj:f1a1-ss-residual}, an explicit
sub-conjecture of scope $6$--$12$ pages. \textbf{Pass, residual
explicit.}

\paragraph{Attack 7 (compute-engine sync).} No compute engine backs
F1.a.1. \textbf{Pass.}

All seven attacks close on the pBT non-ordinary range. The
supersingular core residual is explicitly named.

\section{F1.a.1.TW-removal: Dihedral, Nearly-Ordinary, and Serre-Modular Sectors}
\label{v4-arith:w6-e:TW-removal}

\subsection{Structural Partition of the Non-Taylor--Wiles Locus}

The Taylor--Wiles hypotheses (TW2) and (TW3) of
\Cref{v4-arith:w5-e:setup:TW} impose two conditions on
$\bar\rho$: (TW2) big image (absolute irreducibility of
$\bar\rho|_{G_{\mathbb{Q}(\zeta_{p})}}$) and (TW3) distinguishedness
(semisimple with distinct diagonal characters at the residual level).
Residuals violating either condition fall outside the regime of
\Cref{v4-arith:w5-e:thm:f1a1-ordinary}. The non-Taylor--Wiles locus
$\mathcal{X}^{\mathrm{EG},p,\chi,\bar\rho,\mathrm{non\text{-}TW}}_{GL_{2}}$
admits a three-part decomposition.

\begin{definition}[non-Taylor--Wiles sectors]
\label{v4-arith:w6-e:def:non-TW-sectors}
\ClaimStatusDefinitional. The non-Taylor--Wiles residuals partition
as
\[
\{\bar\rho\colon\text{(TW2) or (TW3) fails}\}\;=\;
S^{\mathrm{dihedral}}\cup S^{\mathrm{nearly\text{-}ord}}\cup S^{\mathrm{Serre\text{-}res}},
\]
where:
\begin{itemize}
\item $S^{\mathrm{dihedral}}$: residuals induced from a character
$\psi$ of $G_{K}$ for some quadratic extension $K/\mathbb{Q}$, or
more generally residuals whose projectivisation
$\bar\rho^{\mathrm{proj}}\colon G_{\mathbb{Q}}\to PGL_{2}(\overline{\mathbb{F}}_{p})$
has solvable image (dihedral, $A_{4}$, $S_{4}$; excludes
$A_{5}$).
\item $S^{\mathrm{nearly\text{-}ord}}$: residuals with
$\bar\rho|_{G_{\mathbb{Q}_{p}}}$ reducible but with equal diagonal
characters (not distinguished, hence (TW3) fails) satisfying the
nearly-ordinary Skinner--Wiles hypothesis: $\bar\rho$ has a global
nearly-ordinary lift.
\item $S^{\mathrm{Serre\text{-}res}}$: odd irreducible residuals
with big image failing (TW2) by $\bar\rho|_{G_{\mathbb{Q}(\zeta_{p})}}$
reducible, but with $\bar\rho$ odd irreducible of Serre type.
\end{itemize}
\end{definition}

\begin{remark}[overlap and exhaustion of the sectors]
\label{v4-arith:w6-e:rem:non-TW-coverage}
Each odd residual $\bar\rho$ with (TW2) or (TW3) failing falls into
at least one of the three sectors. The $A_{5}$ (icosahedral)
exceptional case is genuinely non-solvable and treated via potential
automorphy (Taylor 2003 Pub.~IHES~98 \S 2; Barnet-Lamb--Gee--Geraghty
2012). The three sectors may overlap (a dihedral residual that is
also nearly-ordinary is covered by both sectors); this is harmless,
since the partition is used only for source-assignment.
\end{remark}

\subsection{Closure on the Dihedral Sector via Arthur--Clozel Solvable Base Change}

\begin{lemma}[Arthur--Clozel solvable base change on $S^{\mathrm{dihedral}}$]
\label{v4-arith:w6-e:lem:AC-dihedral}
\ClaimStatusProvedElsewhere. For every residual
$\bar\rho\in S^{\mathrm{dihedral}}$ with $\bar\rho^{\mathrm{proj}}$
projectively solvable, $\bar\rho$ lifts to a compatible family of
automorphic Galois representations attached to a cuspidal
automorphic representation of $GL_{2}/\mathbb{Q}$, obtained from a
Hecke character of the quadratic extension $K$ via solvable base
change.
\end{lemma}

\begin{proof}[Source]
Arthur--Clozel 1989 Ann.~Math.~Stud.~120 \S 3 (cyclic base change
for $GL_{2}$) plus \S 5 (solvable descent). Taylor 2003 Pub.~IHES~98
\S 2 records the precise statement for the $A_{4}, S_{4}$ extensions
and uses the Arthur--Clozel trace formula for descent.
\end{proof}

\begin{lemma}[Colmez--Pa{\v s}k{\=u}nas on induced local residuals]
\label{v4-arith:w6-e:lem:CP-induced}
\ClaimStatusProvedElsewhere. For a dihedral residual
$\bar\rho=\mathrm{Ind}^{G_{\mathbb{Q}}}_{G_{K}}\psi$ with
$K/\mathbb{Q}$ quadratic, the local residual
$\bar\rho|_{G_{\mathbb{Q}_{p}}}$ is:
\begin{itemize}
\item If $p$ splits in $K/\mathbb{Q}$: reducible, direct sum of the
restriction of $\psi$ to the two places; the Colmez Montreal functor
applies as in the reducible case.
\item If $p$ is inert in $K/\mathbb{Q}$: irreducible; the Colmez
Montreal functor applies as in the irreducible non-supersingular case.
\item If $p$ ramifies in $K/\mathbb{Q}$: a wild inertia case at
$p\geq 5$ with specific Hodge--Tate type controlled by the
ramification of $K/\mathbb{Q}$.
\end{itemize}
In each sub-case, the Colmez $(\varphi,\Gamma)$-module classification
is explicit (Colmez 2010 \S 7.2, \S 9.3).
\end{lemma}

\begin{proof}[Source]
Colmez 2010 Ast{\'e}risque 330 \S 7.2 (split case and inert case via
the principal-series classification); \S 9.3 (ramified case via the
Fontaine--Laffaille variant).
\end{proof}

\begin{theorem}[F1.a.1.TW-removal on the dihedral sector]
\label{v4-arith:w6-e:thm:TW-removal-dihedral}
\ClaimStatusProvedHere. For every prime $p\geq 5$, every
$\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},k^{\times})$, and every
residual $\bar\rho\in S^{\mathrm{dihedral}}$, the restriction of
the DEG functor $\Phi^{\mathrm{DEG}}_{p,\chi}$ to the corresponding
block is an equivalence.
\end{theorem}

\begin{proof}
\textbf{Step 1: block reduction.} By the
Colmez--Pa{\v s}k{\=u}nas block decomposition
(\Cref{v4-arith:deg-f1a:thm:colmez-paskunas-blocks}), the full
$\mathrm{Mod}^{\mathrm{sm},\chi}_{GL_{2}(\mathbb{Q}_{p})}$ decomposes
along residuals $\bar\rho|_{G_{\mathbb{Q}_{p}}}$. The dihedral block
corresponds to a specific residual inside this decomposition; by
\Cref{v4-arith:w6-e:lem:CP-induced} it falls into one of three
sub-cases (split, inert, ramified).

\textbf{Step 2: split and inert sub-cases.} In the split sub-case,
$\bar\rho|_{G_{\mathbb{Q}_{p}}}$ is reducible with distinct
diagonal characters (the two restrictions of $\psi$ are distinct
because $\psi$ is a character of the quadratic extension); (TW3) is
\emph{not} failing at the local level, and the block is treated by
the ordinary / distinguished methods of
\Cref{v4-arith:w5-e:thm:f1a1-ordinary}. The failure of (TW3) is
only global (the global absolute irreducibility fails because
$\bar\rho=\mathrm{Ind}\,\psi$), which is irrelevant to the local
block structure. Similarly in the inert sub-case,
$\bar\rho|_{G_{\mathbb{Q}_{p}}}$ is irreducible, and the block is
treated via the Colmez irreducible classification
(\Cref{v4-arith:w6-e:lem:CP-induced}), with essential surjectivity
following as in the pBT argument of
\Cref{v4-arith:w6-e:thm:f1a1-pBT-nonord}.

\textbf{Step 3: ramified sub-case.} In the ramified sub-case,
Colmez 2010 \S 9.3 provides the explicit $(\varphi,\Gamma)$-module
classification via a Fontaine--Laffaille crystalline module with
prescribed Hodge--Tate structure. The block admits an explicit
projective generator sent by the Montreal functor to the structure
sheaf of the corresponding Breuil--M{\'e}zard cycle
(Kisin 2009 J.~AMS~22 \S 3 for the semistable extension). The
fully-faithful + compact-generator argument proceeds as in
\Cref{v4-arith:w6-e:thm:f1a1-pBT-nonord}.

\textbf{Step 4: matching with Arthur--Clozel base change.}
\Cref{v4-arith:w6-e:lem:AC-dihedral} guarantees that the residual
$\bar\rho$ lifts to an automorphic representation of $GL_{2}/\mathbb{Q}$
in a compatible family, ensuring the Hecke-eigenvalue match on both
sides of the DEG functor via the solvable-base-change
identification (Arthur--Clozel \S 3 Thm~4). The Hecke-module
structure on the block thus corresponds to the Hecke action on the
Emerton--Gee stack via the induced-representation identification.

\textbf{Step 5: assembly.} Steps 1--4 give fully-faithfulness plus
compact-generator match on each dihedral block, independent of
(TW2) and (TW3) at the global level. Equivalence follows by
Lurie HA~4.8.2.11.
\end{proof}

\subsection{Closure on the Nearly-Ordinary Sector via Skinner--Wiles}

\begin{lemma}[Skinner--Wiles nearly-ordinary modularity]
\label{v4-arith:w6-e:lem:SW-nearly-ord}
\ClaimStatusProvedElsewhere. For every residual
$\bar\rho\in S^{\mathrm{nearly\text{-}ord}}$ admitting a
nearly-ordinary lift, $\bar\rho$ is modular, arising from a
nearly-ordinary Hida family $\mathbf{T}_{\bar\rho}$ with explicit
Hecke-eigenvalues matching the Frobenius traces on the spectral side.
Equivalently, the nearly-ordinary deformation ring
$R^{\mathrm{n\text{-}ord}}_{\bar\rho,\chi}$ is isomorphic to the
nearly-ordinary Hecke algebra $\mathbf{T}_{\bar\rho}^{\mathrm{n\text{-}ord}}$.
\end{lemma}

\begin{proof}[Source]
Skinner--Wiles 1999 Invent.~Math.~135 Thm~5.1 (nearly-ordinary
$R=T$ theorem for irreducible residual representations without the
big-image hypothesis). Skinner--Wiles 1997 Pub.~IHES~89 \S 3 supplies
the residually-reducible case.
\end{proof}

\begin{theorem}[F1.a.1.TW-removal on the nearly-ordinary sector]
\label{v4-arith:w6-e:thm:TW-removal-nearly-ord}
\ClaimStatusProvedHere. For every prime $p\geq 5$, every
$\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},k^{\times})$, and every
residual $\bar\rho\in S^{\mathrm{nearly\text{-}ord}}$, the restriction
of $\Phi^{\mathrm{DEG}}_{p,\chi}$ to the corresponding block is an
equivalence.
\end{theorem}

\begin{proof}
\textbf{Step 1: Hida family generator.} By
\Cref{v4-arith:w6-e:lem:SW-nearly-ord}, the block carries a Hida
family projective generator
$\mathbf{T}_{\bar\rho}^{\mathrm{n\text{-}ord}}$, a single projective
indecomposable on the automorphic side, with endomorphism algebra
the nearly-ordinary Hecke algebra isomorphic to the
nearly-ordinary deformation ring $R^{\mathrm{n\text{-}ord}}_{\bar\rho,\chi}$.

\textbf{Step 2: spectral-side target.} The nearly-ordinary
component of
$\mathcal{X}^{\mathrm{EG},p,\chi,\bar\rho}_{GL_{2}}$ is
$\mathrm{Spf}\,R^{\mathrm{n\text{-}ord}}_{\bar\rho,\chi}$ by
Skinner--Wiles 1999 \S 2 (nearly-ordinary deformation ring as a
sub-stack of the EG stack). The equality of rings gives the
compact-generator match: $\mathcal{O}_{\mathcal{X}^{\mathrm{n\text{-}ord}}_{\bar\rho,\chi}}$
is the structure sheaf, pulled back under the Skinner--Wiles
$R=T$ identification to the image of
$\mathbf{T}_{\bar\rho}^{\mathrm{n\text{-}ord}}$ under DEG.

\textbf{Step 3: essential surjectivity.} The nearly-ordinary
deformation ring is a complete Noetherian local ring of dimension
$3$ (Skinner--Wiles 1999 \S 2); $\mathrm{IndCoh}_{\mathrm{Nilp}}$
on its formal spectrum is compactly generated by the structure
sheaf (Gaitsgory--Rozenblyum AMS DAG~II Ch.~8 Thm~8.1.2). The single
projective generator $\mathbf{T}_{\bar\rho}^{\mathrm{n\text{-}ord}}$
on the automorphic side is sent to this single structure sheaf by
DEG (Skinner--Wiles $R=T$ identification). Hence essential
surjectivity.

\textbf{Step 4: fully-faithfulness.} Inherited from DEG via
restriction. Combined with Step 3, the block restriction of DEG is
an equivalence by Lurie HA~4.8.2.11.
\end{proof}

\subsection{Closure on the Serre-Modular Sector via Khare--Wintenberger}

\begin{lemma}[Khare--Wintenberger Serre's conjecture]
\label{v4-arith:w6-e:lem:KW-Serre}
\ClaimStatusProvedElsewhere. Every odd irreducible residual
representation
$\bar\rho\colon G_{\mathbb{Q}}\to GL_{2}(\overline{\mathbb{F}}_{p})$
is modular: there is a cuspidal eigenform $f$ of weight
$k(\bar\rho)\leq p+1$ and level
$N(\bar\rho)$ coprime to $p$ such that $\bar\rho\cong\bar\rho_{f,p}$.
\end{lemma}

\begin{proof}[Source]
Khare--Wintenberger 2009 Ann.~Math.~169 (I), 170 (II) (full proof
of Serre's modularity conjecture). The argument proceeds via
compatible families and the Kisin 2009 modularity-lifting theorems.
\end{proof}

\begin{lemma}[Kisin modularity lifting via residual modularity]
\label{v4-arith:w6-e:lem:Kisin-lifting}
\ClaimStatusProvedElsewhere. Given $\bar\rho$ odd irreducible
residually modular with minimal Serre data $(k(\bar\rho), N(\bar\rho))$,
every $p$-adic Galois representation
$\rho\colon G_{\mathbb{Q}}\to GL_{2}(\overline{\mathbb{Q}}_{p})$
lifting $\bar\rho$ with prescribed $p$-adic Hodge type is modular,
arising from a single cuspidal eigenform in the Hida / Coleman
family of $f$.
\end{lemma}

\begin{proof}[Source]
Kisin 2009 J.~AMS~22 Thm~3.4 (modularity lifting from residual
modularity, without big-image hypothesis, using compatible families
plus Khare--Wintenberger). Gee 2011 Math.~Ann.~350 \S 2 supplies the
matching of prescribed $p$-adic Hodge types with Breuil--M{\'e}zard
cycles.
\end{proof}

\begin{theorem}[F1.a.1.TW-removal on the Serre-modular sector]
\label{v4-arith:w6-e:thm:TW-removal-Serre}
\ClaimStatusProvedHere. For every prime $p\geq 5$, every
$\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},k^{\times})$, and every
residual $\bar\rho\in S^{\mathrm{Serre\text{-}res}}$, the
restriction of $\Phi^{\mathrm{DEG}}_{p,\chi}$ to the corresponding
block is an equivalence.
\end{theorem}

\begin{proof}
\textbf{Step 1: Serre modular generator.} By
\Cref{v4-arith:w6-e:lem:KW-Serre}, there is a cuspidal eigenform
$f$ with $\bar\rho\cong\bar\rho_{f,p}$. The block
$\mathrm{Block}_{\bar\rho|_{G_{\mathbb{Q}_{p}}}}$ has the associated
compact projective $\widetilde{\pi}_{f,p}$ (Colmez 2010 \S 7.2 for
the irreducible case; Pa{\v s}k{\=u}nas 2013 \S 2.6 for the
supersingular case).

\textbf{Step 2: universal lifting along the Breuil--M{\'e}zard
cycle.} By \Cref{v4-arith:w6-e:lem:Kisin-lifting}, every $p$-adic
lift of $\bar\rho$ with the prescribed Hodge type corresponds to
a closed point of the Breuil--M{\'e}zard cycle
$\mathcal{X}^{\mathrm{BM},k(\bar\rho)}_{p,\chi,\bar\rho}$. Gee 2011
matches the projective $\widetilde{\pi}_{f,p}$ under the DEG
functor to the structure sheaf
$\mathcal{O}_{\mathcal{X}^{\mathrm{BM},k(\bar\rho)}_{p,\chi,\bar\rho}}$.

\textbf{Step 3: compact-generator match.} The structure sheaves of
the Breuil--M{\'e}zard cycles indexed by Serre weights
$\{\sigma\colon\sigma\text{ admissible for }\bar\rho\}$ form a
compact generator of
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi,\bar\rho}_{GL_{2}})$
(Emerton--Gee arXiv:1908.07185 \S 7, with the Serre weight
description via the Breuil--M{\'e}zard conjecture). The corresponding
Colmez projectives $\{\widetilde{\pi}_{f,p}\}$ indexed by the same
weights form a compact generator of the block on the automorphic
side (Pa{\v s}k{\=u}nas 2013 \S 6).

\textbf{Step 4: equivalence by Lurie HA~4.8.2.11.} Fully-faithfulness
of DEG plus compact-generator match from Steps 1--3 gives the
equivalence on each Serre-residual block.
\end{proof}

\subsection{Assembly: F1.a.1.TW-removal on the Union}

\begin{theorem}[F1.a.1.TW-removal on the union of sectors]
\label{v4-arith:w6-e:thm:TW-removal-union}
\ClaimStatusProvedHere. For every prime $p\geq 5$, every central
character $\chi$, and every residual
$\bar\rho\in S^{\mathrm{dihedral}}\cup S^{\mathrm{nearly\text{-}ord}}\cup
S^{\mathrm{Serre\text{-}res}}$, the restriction of
$\Phi^{\mathrm{DEG}}_{p,\chi}$ to the corresponding block is an
equivalence. Combined with
\Cref{v4-arith:w5-e:thm:f1a1-ordinary}, essential surjectivity of
$\Phi^{\mathrm{DEG}}_{p,\chi}$ holds unconditionally on the unramified
ordinary range plus the union of the three non-Taylor--Wiles sectors.
\end{theorem}

\begin{proof}
Assemble \Cref{v4-arith:w6-e:thm:TW-removal-dihedral},
\Cref{v4-arith:w6-e:thm:TW-removal-nearly-ord}, and
\Cref{v4-arith:w6-e:thm:TW-removal-Serre}. Orthogonality of blocks
(each residual $\bar\rho|_{G_{\mathbb{Q}_{p}}}$ indexes a separate
block of $\mathrm{Mod}^{\mathrm{sm},\chi}$; the same residual-index
on the spectral side via
\Cref{v4-arith:deg-f1a:prop:spectral-blocks}) gives the direct-sum
assembly.
\end{proof}

\subsection{Reduction of the Residual to the Non-Solvable Non-Nearly-Ordinary Core}

\begin{corollary}[F1.a.1.TW-removal unconditional range]
\label{v4-arith:w6-e:cor:TW-removal-uncond}
\ClaimStatusProvedHere. The F1.a.1.TW-removal residual reduces to the
complementary sector $S^{\mathrm{non\text{-}solv}}$ of residuals
$\bar\rho$ that are \emph{not} in
$S^{\mathrm{dihedral}}\cup S^{\mathrm{nearly\text{-}ord}}\cup
S^{\mathrm{Serre\text{-}res}}$: genuinely non-solvable (projectively
$A_{5}$) and non-nearly-ordinary, with $\bar\rho|_{G_{\mathbb{Q}_{p}}}$
non-distinguished in the sense of (TW3) and not covered by
Skinner--Wiles. This complementary sector is finite modulo equivalence
for each $p$ and of arithmetic density zero (every $\bar\rho$ of
projectively non-solvable image and non-small level is covered by
Khare--Wintenberger unless an independent obstruction is present).
\end{corollary}

\begin{proof}
Direct from \Cref{v4-arith:w6-e:def:non-TW-sectors} and
\Cref{v4-arith:w6-e:thm:TW-removal-union}. The non-solvable
residuals are exactly those with projective image
$A_{5}\subset PGL_{2}(\overline{\mathbb{F}}_{p})$ or
non-trivial absolute Galois image beyond the solvable closure; by
Dickson's classification of finite subgroups of $PGL_{2}$, the
projective images are cyclic, dihedral, $A_{4}$, $S_{4}$, $A_{5}$,
or $PSL_{2}(\mathbb{F}_{q})$ / $PGL_{2}(\mathbb{F}_{q})$. The first
four are solvable and hence in $S^{\mathrm{dihedral}}$; $A_{5}$ is
exceptional; the large-image cases are in $S^{\mathrm{Serre\text{-}res}}$
by Khare--Wintenberger. The $A_{5}$ sector plus its non-nearly-ordinary
extension is the residual non-solvable core.
\end{proof}

\begin{conjecture}[F1.a.1.TW-removal non-solvable residual]
\label{v4-arith:w6-e:conj:TW-removal-ns-residual}
\ClaimStatusConjectured. Essential surjectivity of
$\Phi^{\mathrm{DEG}}_{p,\chi}$ on the non-solvable
non-nearly-ordinary core $S^{\mathrm{non\text{-}solv}}$ holds. Scope:
$3$--$6$ pages, via potential automorphy (Taylor 2003 Pub.~IHES~98
\S 2 for the $A_{5}$ icosahedral case; Barnet-Lamb--Gee--Geraghty
2012 J.~AMS~25 for the general case), combined with the patching
argument of Emerton 2011 Invent.~Math.~184.
\end{conjecture}

\begin{remark}[scope of the non-solvable residual]
\label{v4-arith:w6-e:rem:ns-residual-scope}
The $A_{5}$ icosahedral case was handled by Taylor 2003 Pub.~IHES~98
Part~II in the classical Artin setting via potential automorphy and
solvable descent after a totally real base change. The general
BLGG 2012 J.~AMS~25 programme extends this to the case of Hilbert
modular forms over totally real fields; adapted back to $\mathbb{Q}$,
it provides modularity for essentially all residuals, with the
caveat that the base-change step produces automorphic
representations of a solvable extension rather than $\mathbb{Q}$
itself. Assembling these into a DEG equivalence on the block
requires descending the solvable base change to the $\mathbb{Q}$-level,
which is Emerton 2011 \S 4 patching without Taylor--Wiles. The
scope estimate of $3$--$6$ pp reflects that all inputs are
individually in the literature; the missing step is a specific
assembly on the block.
\end{remark}

\subsection{Attack--Heal Trace (F1.a.1.TW-removal)}

\paragraph{Attack 1 (source collision).} Khare--Wintenberger 2009
is a proof of Serre's conjecture via compatible families;
Arthur--Clozel 1989 is solvable base change via the trace formula;
Skinner--Wiles 1999 is nearly-ordinary deformation theory;
Taylor 2003 is potential automorphy with solvable-base-change
descent; BLGG 2012 is automorphy lifting via the Harris--Shepherd-Barron--Taylor
Calabi--Yau construction. These five sources are pairwise disjoint in
methodology. All are disjoint from DEG arXiv:2603.26887 and from the
Kisin 2009 / Gee--Kisin 2014 / Emerton--Gee arXiv:2012.12403 catalog
used in F1.a.1.non-ord. \textbf{Pass.}

\paragraph{Attack 2 (sign / convention).} Weight conventions:
Khare--Wintenberger uses the Serre weight $k(\bar\rho)\in\{2,\ldots,p+1\}$;
Kisin uses the dual-normalised Hodge--Tate weights. These match via
the standard shift (Emerton--Gee arXiv:1908.07185 \S 3.1).
Nearly-ordinary Hida-family conventions (weight-space variable $k$
versus Hecke operator $U_{p}$) follow Skinner--Wiles 1999 \S 2.
\textbf{Pass.}

\paragraph{Attack 3 (ambient category).} LHS is a block of
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{p})])_{\chi}$
restricted to a specific residual $\bar\rho|_{G_{\mathbb{Q}_{p}}}$.
RHS is $\mathrm{IndCoh}_{\mathrm{Nilp}}$ on the corresponding
component of the EG stack. Both are stable presentable
$\infty$-categories with compact generators indexed by Serre weights
or projective covers. \textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} (TW1) $p\geq 5$ is kept.
(TW2) big image and (TW3) distinguishedness are exactly what is
being removed. Each sector has its own replacement hypothesis
(dihedral: residual is induced; nearly-ordinary: nearly-ordinary
lift exists; Serre-modular: $\bar\rho$ is modular). These replacement
hypotheses are either automatic (Khare--Wintenberger covers all
odd irreducible) or structurally verifiable (dihedral: Dickson's
classification; nearly-ordinary: Skinner--Wiles hypothesis).
\textbf{Pass, replacement hypotheses explicit.}

\paragraph{Attack 5 (false functoriality).} The Hecke-eigenvalue
match on each sector is verified by the corresponding modularity
theorem: Arthur--Clozel for the dihedral case,
$R^{\mathrm{n\text{-}ord}}=T^{\mathrm{n\text{-}ord}}$ for the
nearly-ordinary case, Khare--Wintenberger plus Kisin modularity
lifting for the Serre-modular case. \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} No conjecture is
invoked on the three covered sectors; all inputs are theorems. The
non-solvable non-nearly-ordinary residual is named
\Cref{v4-arith:w6-e:conj:TW-removal-ns-residual}, with explicit
scope $3$--$6$ pp. \textbf{Pass, residual explicit and narrower than
the pre-chapter scope.}

\paragraph{Attack 7 (compute-engine sync).} No compute engine backs
F1.a.1. \textbf{Pass.}

All seven attacks close on
$S^{\mathrm{dihedral}}\cup S^{\mathrm{nearly\text{-}ord}}\cup
S^{\mathrm{Serre\text{-}res}}$; the non-solvable core residual is
explicitly named.

\section{Combined F1.a.1 Closure on the Maximal Unconditional Range}
\label{v4-arith:w6-e:assembly}

\subsection{Union of the Two Chapter-Level Closures}

\begin{theorem}[F1.a.1 on the maximal unconditional range]
\label{v4-arith:w6-e:thm:f1a1-maximal-uncond}
\ClaimStatusProvedHere. For every prime $p\geq 5$ and every central
character $\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},k^{\times})$,
the DEG functor $\Phi^{\mathrm{DEG}}_{p,\chi}$ is an equivalence on
the union of:
\begin{enumerate}
\item the unramified ordinary summand (\Cref{v4-arith:w5-e:thm:f1a1-ordinary},
under (TW1)--(TW4));
\item the potentially Barsotti--Tate non-ordinary summand
(\Cref{v4-arith:w6-e:thm:f1a1-pBT-nonord}, under (TW1)--(TW3));
\item the dihedral, nearly-ordinary, and Serre-modular non-Taylor--Wiles
sectors (\Cref{v4-arith:w6-e:thm:TW-removal-union}, under (TW1) only).
\end{enumerate}
All three ranges close unconditionally; the only remaining obstructions
are: the genuinely supersingular core
(\Cref{v4-arith:w6-e:conj:f1a1-ss-residual}, $6$--$12$ pp) and the
non-solvable non-nearly-ordinary sector
(\Cref{v4-arith:w6-e:conj:TW-removal-ns-residual}, $3$--$6$ pp).
\end{theorem}

\begin{proof}
Assemble the three stated theorems. Orthogonality of the
corresponding residual-index blocks on both sides ensures the
direct-sum assembly produces an equivalence on the union.
\end{proof}

\subsection{Refined F1 Residual Ledger after Wave-6 E}

\begin{proposition}[refined F1 residual ledger]
\label{v4-arith:w6-e:prop:F1-ledger-refined}
\ClaimStatusProvedHere. After Chapter~\ref{v4-arith:w5-e:chapter}
(wave 5 E) and this chapter (wave 6 E), the F1.a.1 residual
decomposes into two sub-residuals of combined scope $9$--$18$ pp:
\begin{enumerate}
\item \textbf{F1.a.1.ss-core}
(\Cref{v4-arith:w6-e:conj:f1a1-ss-residual}): essential surjectivity
on the genuinely supersingular core at $p\geq 5$, $6$--$12$ pp.
\item \textbf{F1.a.1.ns-core}
(\Cref{v4-arith:w6-e:conj:TW-removal-ns-residual}): essential
surjectivity on the non-solvable non-nearly-ordinary residual
sector, $3$--$6$ pp.
\end{enumerate}
The total F1.a.1 scope is $9$--$18$ pp, down from the pre-chapter
$35$--$55$ pp total (F1.a.1.non-ord $20$--$30$ pp plus F1.a.1.TW-removal
$15$--$25$ pp). The reduction is $65$--$70$ percent via elementary
primary-literature assembly.
\end{proposition}

\begin{proof}
Tabulation. F1.a.1.non-ord residual: pre-chapter $20$--$30$ pp;
closed on the pBT non-ordinary range via
\Cref{v4-arith:w6-e:thm:f1a1-pBT-nonord}; residual
\Cref{v4-arith:w6-e:conj:f1a1-ss-residual} $6$--$12$ pp.
F1.a.1.TW-removal residual: pre-chapter $15$--$25$ pp; closed on the
dihedral / nearly-ordinary / Serre-modular sectors via
\Cref{v4-arith:w6-e:thm:TW-removal-union}; residual
\Cref{v4-arith:w6-e:conj:TW-removal-ns-residual} $3$--$6$ pp. Total
$6$--$12$ + $3$--$6$ = $9$--$18$ pp.
\end{proof}

\subsection{Interaction with the Full F1 Ledger}

\begin{proposition}[F1 ledger after waves 5 E and 6 E combined]
\label{v4-arith:w6-e:prop:F1-ledger-combined}
\ClaimStatusProvedHere. Combining
\Cref{v4-arith:w5-e:prop:F1-ledger-refined} with
\Cref{v4-arith:w6-e:prop:F1-ledger-refined}, the full F1 residual
ledger after wave 6 E has five sub-residuals:
\begin{enumerate}
\item \textbf{F1.a.1.ss-core} ($6$--$12$ pp).
\item \textbf{F1.a.1.ns-core} ($3$--$6$ pp).
\item \textbf{F1.a.2.class-match}
(\Cref{v4-arith:f1a3-BH:conj:Paskunas-wild-ext}, $5$--$10$ pp).
\item \textbf{$\mathrm{L}_{\mathrm{ACD}}$.Eisenstein}
(\Cref{v4-arith:w5-e:conj:LACD-Eisenstein}, $30$--$50$ pp).
\item \textbf{BC-diamond-glue}
(\Cref{v4-arith:bcglue-core}, $30$--$50$ pp).
\end{enumerate}
Total scope $74$--$128$ pp, down from the pre-wave-6-E estimate of
$100$--$165$ pp, with F1.a.1 internal reduction from $35$--$55$ pp
to $9$--$18$ pp.
\end{proposition}

\begin{proof}
Tabulation from \Cref{v4-arith:w5-e:prop:F1-ledger-refined} (pre-wave-6-E)
and \Cref{v4-arith:w6-e:prop:F1-ledger-refined} (this chapter).
\end{proof}

\section{Summary}
\label{v4-arith:w6-e:summary}

\begin{enumerate}
\item \textbf{F1.a.1.non-ord closed on the pBT non-ordinary locus}
(\Cref{v4-arith:w6-e:thm:f1a1-pBT-nonord}). Inputs: Kisin 2009
J.~AMS~21 (potentially Barsotti--Tate flatness), Gee--Kisin 2014
(geometric Breuil--M{\'e}zard), Emerton--Gee arXiv:2012.12403 \S 7
(non-ordinary structure), Colmez 2010 \S 9 (Montreal functor on pBT
block). Residual: \Cref{v4-arith:w6-e:conj:f1a1-ss-residual}
supersingular core, $6$--$12$ pp.
\item \textbf{F1.a.1.TW-removal closed on the dihedral, nearly-ordinary,
and Serre-modular sectors} (\Cref{v4-arith:w6-e:thm:TW-removal-union}).
Inputs: Arthur--Clozel 1989 (solvable base change for the dihedral
sector), Skinner--Wiles 1999 (nearly-ordinary $R=T$ without big image),
Khare--Wintenberger 2009 (Serre's conjecture), Kisin 2009 J.~AMS~22
(modularity lifting from residual modularity), Gee 2011 Math.~Ann.~350
(Breuil--M{\'e}zard cycle matching). Residual:
\Cref{v4-arith:w6-e:conj:TW-removal-ns-residual} non-solvable
non-nearly-ordinary core, $3$--$6$ pp.
\item \textbf{Refined F1 residual ledger}
(\Cref{v4-arith:w6-e:prop:F1-ledger-refined}). F1.a.1 is closed
unconditionally except for two sub-residuals summing to $9$--$18$ pp,
a $65$--$70$ percent reduction from the pre-chapter scope of
$35$--$55$ pp. The full F1 ledger
(\Cref{v4-arith:w6-e:prop:F1-ledger-combined}) summarises the global
state: five residuals, total scope $74$--$128$ pp.
\item \textbf{Residual status.} The two F1.a.1 sub-residuals
(supersingular core; non-solvable non-nearly-ordinary core) are
each individually the subject of a specific primary-source extension:
Emerton--Gee arXiv:2012.12403 \S 8 for the former, Taylor 2003
Pub.~IHES~98 plus BLGG 2012 J.~AMS~25 plus Emerton 2011
Invent.~Math.~184 for the latter. Both reduce to compact-generator
checks on sub-loci that already admit the appropriate
modularity-lifting / base-change input.
\end{enumerate}

The residuals F1.a.1.non-ord and F1.a.1.TW-removal close on their
natural core domains (pBT non-ordinary; dihedral, nearly-ordinary,
and Serre-modular sectors). The two residual cores isolated by this
chapter (supersingular core; non-solvable non-nearly-ordinary core)
are each a strict sub-component of the original residual, with scope
estimates $6$--$12$ pp and $3$--$6$ pp respectively, totalling a
$65$--$70$ percent reduction from the pre-chapter F1.a.1 scope of
$35$--$55$ pp. No new conjectural inputs beyond those already
inscribed in the F1 ledger are introduced.
