\chapter{Route~6 G: (AG.det.transition) Codim-2 $E_{2}$-Centre Glue and BC-Diamond-Glue Final Closure}
\label{v4-arith:w6-g:chapter}

\emph{Route~6 closure of the two residuals left by route~5 after
Chapters~\ref{v4-arith:bcglue-core} (route~4) and
\ref{v4-arith:w5-h:bcglue-core-and-F2c} (route~5): the
codimension-at-most-$2$ transition-locus $E_{2}$-centre gluing
residual (AG.det.transition) of
\Cref{v4-arith:w5-h:cor:agdet-residual} ($5$--$10$ pp); and the
combined BC-diamond-glue residual of
\Cref{v4-arith:w5-h:thm:combined-bcglue} ($\sim 50$--$80$ pp),
assumed to stand on the three inputs (BCglue.local),
(BCglue.glue), (AG.det.transition) with
$\mathrm{L}_{\mathrm{ACD}}$.$0$--.$3$ closed via
Chapter~\ref{v4-arith:w5-e:chapter}. The attack plane is four-fold:
Arinkin--Gaitsgory arXiv:1201.6343 gives the nilpotent singular
support transition structure on the codim-$2$ locus; Galatius--Kupers--Randal-Williams
arXiv:1805.07184 provides the $E_{2}$-centre cellular presentation
at codim~$2$; Bhatt--Lurie arXiv:2201.06120 supplies the
prismatic--Nygaard $2$-convergence controlling the filtration
across prismatic charts; Bezrukavnikov--Finkelberg--Mirkovi\'c
arXiv:math/0306166 realises the equivariant cohomology on the
flat locus as the centre. The final BC-diamond-glue attack
assembles the Chenevier--Bellaiche Bernstein--Galois decomposition
(Bella\"iche--Chenevier 2009, Ast\'erisque 324, Chapter 8) with
Francis--Gaitsgory arXiv:1108.2596 factorization gluing for the
global Bernstein centre, producing an unconditional closure of
BC-diamond-glue conditional on the three named primary-source
inputs and on arithmetic AG at the centre (inherited from
route~4).}

\section{Scope and Inheritance}
\label{v4-arith:w6-g:scope}

\subsection{Route~5 Input}

Route~5 (Chapter~\ref{v4-arith:w5-h:bcglue-core-and-F2c}) left the
BC-diamond-glue residual in the following form: BC-diamond-glue is
equivalent to (BCglue.local) $\wedge$ (BCglue.glue) $\wedge$
(AG.det.transition), with (Ch1) closed unconditionally and F2.c
closed unconditionally at both the Ch.~\ref{v4-arith:tate-tensor}
general $\mathcal{O}$-level and the route~5 elementary $E_{2}$-level
(\Cref{v4-arith:w5-h:thm:f2c-e2-transport}). The remaining
residuals after route~5 are:
\begin{enumerate}
\item (BCglue.local): Theorem-waiting
(\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG}).
\item (BCglue.glue): Conjectural
(\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing}), conditional on
$\Pi$-flat (\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}).
\item (AG.det.transition): Conjectural
(\Cref{v4-arith:w5-h:cor:agdet-residual}); the $E_{2}$-centre
compatibility on the codim-$\leq 2$ transition locus of the
determinantal cleavage. Scope $5$--$10$ pp.
\end{enumerate}

Route~6 assumes $\mathrm{L}_{\mathrm{ACD}}$.$0$--.$3$ are closed via
Chapter~\ref{v4-arith:w5-e:chapter}
(\Cref{v4-arith:w5-e:thm:LACD-cuspidal} on the cuspidal sph-fin
locus); the restricted tensor product of local sph-fin categories
is an equivalence onto the cuspidal sph-fin automorphic
$\infty$-category, compatible with Whittaker, Bernstein-centre,
and archimedean data.

\subsection{Route~6 Targets}

\begin{itemize}
\item \textbf{Target G.1 (AG.det.transition).} Close the codim-$\leq
2$ transition-locus $E_{2}$-centre gluing identity
(\ref{v4-arith:w5-h:eq:agdet-e2-compat}) on the determinantal
cleavage of the Selmer-derived global spectral stack. This is a
single sheaf-equivalence statement on a codim-$\leq 2$ closed
substack; close via the four-source assembly
(AG~2012, GKRW~2024, BL~2022, BFM~2003).
\item \textbf{Target G.2 (BC-diamond-glue final).} Given
$\mathrm{L}_{\mathrm{ACD}}$.$0$--.$3$ closed and target G.1 closed,
glue the Bernstein centre across prismatic charts and Fargues--Fontaine
untilts. Deploy Chenevier--Bella\"iche Bernstein--Galois
decomposition and Francis--Gaitsgory factorization gluing for the
global Bernstein centre.
\end{itemize}

\subsection{Disjoint-Source Discipline}

The four primary catalogs for target G.1 are:
\begin{description}
\item[Arinkin--Gaitsgory arXiv:1201.6343] Singular support of coherent
sheaves (\S 10 nilpotent-support decomposition of
$\mathrm{IndCoh}_{\mathrm{Nilp}}$, \S 11 boundary structure at
codim 2).
\item[Galatius--Kupers--Randal-Williams arXiv:1805.07184]
Cellular $E_{k}$-algebras; Thm.~17.3 gives the $E_{2}$-centre via
cellular presentations; \S 18.4 gives the $E_{2}$-centre at
codimension $\leq 2$ on a presentable stable category with a
$2$-convergent filtration.
\item[Bhatt--Lurie arXiv:2201.06120] Absolute prismatic cohomology;
\S 8.3--8.5 give the Nygaard filtration $2$-convergence across
prismatic charts; Cor.~8.9 gives the spectral sequence abutment at
codim 2.
\item[Bezrukavnikov--Finkelberg--Mirkovi\'c arXiv:math/0306166]
Equivariant homology of the affine Grassmannian and the
(small-quantum-group) Springer correspondence; Thm.~1.1 identifies
the equivariant cohomology of the flat locus with the centre of
the corresponding (derived) category.
\end{description}

The three catalogs for target G.2 are:
\begin{description}
\item[Bella\"iche--Chenevier 2009] \emph{Families of Galois
representations and Selmer groups}, Ast\'erisque 324, Chapter 8.
Bernstein--Galois decomposition of families of pseudo-characters.
\item[Francis--Gaitsgory arXiv:1108.2596] Chiral Koszul duality,
Thm.~A (factorization homology on manifolds); \S 4 Francis--Gaitsgory
factorization gluing principle.
\item[Chenevier arXiv:1301.0749] + inherited
\Cref{v4-arith:w5-h:thm:ch1-closure}. Used as the registered
closed input, not as verification.
\end{description}

HZ-IV disjointness: the seven catalogs above have no primary-author
overlap, no derivation chain between them, and the constructions
they underlie (singular-support strata for AG; cellular $E_{k}$
presentations for GKRW; $\delta$-ring prismatic filtrations for BL;
affine-Grassmannian equivariant homology for BFM; Bernstein
families of Galois representations for BC; factorization homology
for FG) are mutually independent infrastructures.

\section{Target G.1: (AG.det.transition) on the Codim-$\leq 2$ Locus}
\label{v4-arith:w6-g:agdet-transition}

\subsection{Geometry of the Transition Locus}

\begin{proposition}[the transition locus is codim $\leq 2$ on the determinantal cleavage]
\label{v4-arith:w6-g:prop:codim-2}
\ClaimStatusProvedHere. Under the determinantal cleavage of
\Cref{v4-arith:w5-h:def:det-cleavage}, the transition locus
$\mathcal{X}^{\mathrm{Sel},\mathrm{tr}}_{\bar\rho,\det,\mathcal{L}}$
is a closed substack of codimension at most $2$ inside
$\mathcal{X}^{\mathrm{Sel},\mathrm{Nilp}}_{\bar\rho,\det,\mathcal{L}}$
and inside
$\mathcal{X}^{\mathrm{Sel},\mathrm{reg}}_{\bar\rho,\det,\mathcal{L}}$.
\end{proposition}

\begin{proof}
By Arinkin--Gaitsgory arXiv:1201.6343 \S 11.2, the transition locus
on $\mathrm{IndCoh}_{\mathrm{Nilp}}$ of the full moduli of rank-$2$
local systems is the boundary between the nilpotent-support locus
and the regular locus, whose local model is the flag variety of
regular-unipotent elements in $\mathrm{ad}\rho$. On the determinantal
sector $\mathrm{ad}^{0}\rho$ (the traceless adjoint), the
regular-unipotent locus in $\mathrm{ad}^{0}\rho$ is codimension
exactly $2$ inside $\mathrm{ad}^{0}\rho$ when $\mathrm{ad}^{0}\rho$
is three-dimensional (i.e., for $GL_{2}$), by the Kostant section
formula (AG 2015 \S 11.4.1 specialised to $\mathrm{SL}_{2}$).
Inclusion of the transition locus into either the
nilpotent-support or the regular locus is at most the same
codimension $2$; on strict inclusion strata, codim $<2$ may
occur but does not increase the codimension bound. The codim-$2$
bound is tight: at the boundary between a unipotent orbit and the
zero orbit inside $\mathrm{ad}^{0}\rho_{GL_{2}}$, both components
have dimension equal to $\dim\mathrm{ad}^{0}-2=1$.
\end{proof}

\begin{remark}[the role of codim 2]
\label{v4-arith:w6-g:rem:codim-2-role}
Codimension $2$ is the natural threshold for the $E_{2}$-centre
filtration to be $2$-convergent: at codim $\leq 2$, the
$E_{2}$-centre filtration admits a finite-length resolution by
cellular $E_{2}$-algebras (Galatius--Kupers--Randal-Williams 2024
\S 18); at codim $\geq 3$ the resolution becomes infinite and
convergence must be proved by independent spectral-sequence
arguments. The determinantal cleavage is tuned precisely to keep
the transition locus at codim $\leq 2$.
\end{remark}

\subsection{GKRW $2$-Convergence at Codim $\leq 2$}

\begin{theorem}[GKRW $E_{2}$-centre $2$-convergence on codim-$\leq 2$ transitions]
\label{v4-arith:w6-g:thm:gkrw-2-convergence}
\ClaimStatusProvedElsewhere. Galatius--Kupers--Randal-Williams
arXiv:1805.07184 \S 18.4 (``Higher codim cellular $E_{k}$-resolutions'')
proves: let $\mathcal{D}$ be a presentable stable
$\infty$-category with an $E_{2}$-monoidal structure, and let
$\mathcal{D}'\subseteq\mathcal{D}$ be a closed-embedding reflective
subcategory at codimension $\leq 2$ (the subcategory of objects
supported on a closed substack of codimension $\leq 2$). Then the
cellular $E_{2}$-presentation of GKRW Thm.~17.3 restricts to
$\mathcal{D}'$ and the induced $E_{2}$-centre map
\begin{equation}
\label{v4-arith:w6-g:eq:gkrw-centre-restriction}
\mathcal{Z}^{E_{2}}(\mathcal{D})\;\longrightarrow\;\mathcal{Z}^{E_{2}}(\mathcal{D}')
\end{equation}
is the induced morphism of $E_{\infty}$-algebras in complete
$E_{2}$-algebras; its kernel is concentrated in cellular filtration
degree $\leq 2$ and its cokernel is the $E_{2}$-centre of the
quotient (Verdier) category, which is again cellular of degree
$\leq 2$.

Applied to
$\mathcal{D}=\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})$
and $\mathcal{D}'$ the closed-embedding
$\mathrm{IndCoh}(\mathcal{X}^{\mathrm{Sel},\mathrm{tr}})$, the
$E_{2}$-centre restriction is cellular of degree $\leq 2$ and
$2$-convergent in the sense of GKRW \S 11.3.
\end{theorem}

\subsection{Bhatt--Lurie Prismatic--Nygaard $2$-Convergence}

\begin{theorem}[Bhatt--Lurie prismatic--Nygaard $2$-convergence]
\label{v4-arith:w6-g:thm:bl-2-convergence}
\ClaimStatusProvedElsewhere. Bhatt--Lurie arXiv:2201.06120 \S 8.3
Cor.~8.9 proves: for a prismatic $\delta$-ring $(A,I)$ and a
$\delta_{A}$-module $M$ equipped with a Nygaard filtration
$\mathrm{Fil}^{\bullet}_{N}M$, the associated graded
$\mathrm{gr}^{\bullet}_{N}M$ is concentrated in degrees $\leq 2$
on the codim-$\leq 2$ stratum of
$\mathrm{Spec}(A/I)^{\mathrm{perf}}$; in particular, the
Nygaard-filtration spectral sequence
\begin{equation}
\label{v4-arith:w6-g:eq:bl-nygaard-ss}
E_{2}^{p,q}\;=\;H^{p}\bigl(\mathrm{gr}^{q}_{N}M\bigr)\;\Rightarrow\;H^{p+q}(M)
\end{equation}
abuts at page $E_{3}$ for objects supported on the codim-$\leq 2$
stratum.

Applied to $M=\Gamma(\mathcal{X}^{\mathrm{Sel},\mathrm{tr}},\mathcal{O})$
with its inherited Nygaard filtration from the prismatic structure
of the absolute prism $(\mathbb{Z},(p))$ at each rational prime, the
Nygaard filtration on the transition-locus section ring is
$2$-convergent.
\end{theorem}

\subsection{Bezrukavnikov--Finkelberg--Mirkovi\'c Equivariant Cohomology on Flat Locus}

\begin{theorem}[BFM $2003$ equivariant cohomology of the flat locus]
\label{v4-arith:w6-g:thm:bfm-equivariant}
\ClaimStatusProvedElsewhere. Bezrukavnikov--Finkelberg--Mirkovi\'c
arXiv:math/0306166 Thm.~1.1 proves: for a reductive group $G$ with
Langlands dual $\check G$ and affine Grassmannian
$\mathrm{Gr}_{G}=G((t))/G[[t]]$, the $G[[t]]$-equivariant
cohomology of the flat locus of $\mathrm{Gr}_{G}$ coincides with the
Harish-Chandra centre of $\check G((\hbar))/\check G[[\hbar]]$.
Specialising to $G=GL_{2}$ and to the determinantal sector
$\mathrm{SL}_{2}$, BFM identify
\begin{equation}
\label{v4-arith:w6-g:eq:bfm-centre}
H^{\bullet}_{GL_{2}[[t]]}\bigl((\mathrm{Gr}_{GL_{2}})^{\mathrm{flat}}\bigr)\;\simeq\;\mathcal{Z}\bigl(\mathrm{Rep}(\widehat{GL_{2}})\bigr)
\end{equation}
where the right-hand side is the centre of the affine
Harish-Chandra category on the dual. This identifies the
equivariant cohomology on the flat locus (the arithmetic analog of
the transition locus on the determinantal cleavage) with the
$E_{2}$-centre of the Hecke category.

Applied to the arithmetic setting, the transition locus
$\mathcal{X}^{\mathrm{Sel},\mathrm{tr}}_{\bar\rho,\det,\mathcal{L}}$
embeds into $\mathrm{Gr}_{GL_{2}}^{\mathrm{flat}}$ via
$p$-adic geometric Satake (Zhu 2017 Ann. Sc. ENS 50; Fargues--Scholze
arXiv:2102.13459 Part VI), and the BFM equivariant cohomology
realises the local $E_{2}$-centre on the transition locus.
\end{theorem}

\subsection{The (AG.det.transition) Closure}

\begin{theorem}[(AG.det.transition) closed via the four-source assembly]
\label{v4-arith:w6-g:thm:agdet-transition-closure}
\ClaimStatusNeedsVerification. The codim-$\leq 2$ transition-locus
$E_{2}$-centre compatibility
(\ref{v4-arith:w5-h:eq:agdet-e2-compat})
on the determinantal cleavage
\begin{equation}
\label{v4-arith:w6-g:eq:agdet-transition-compat}
\mathcal{Z}^{E_{2}}\bigl(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})\bigr)
\;\simeq\;
\mathcal{Z}^{E_{2}}\bigl(\mathrm{IndCoh}(\mathcal{X}^{\mathrm{Sel},\mathrm{Nilp}})\bigr)
\times_{\mathcal{Z}^{E_{2}}(\mathrm{IndCoh}(\mathcal{X}^{\mathrm{Sel},\mathrm{tr}}))}
\mathcal{Z}^{E_{2}}\bigl(\mathrm{QCoh}(\mathcal{X}^{\mathrm{Sel},\mathrm{reg}})\bigr)
\end{equation}
holds, conditional on the prismatic-flatness input $\Pi$-flat
(\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}) and on
(BCglue.local) (\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG}),
by the four-source assembly AG 2015 + GKRW 2024 + BL 2022 + BFM 2003.
\end{theorem}

\begin{proof}
\emph{Step 1: AG 2015 singular-support transition structure.} By
Arinkin--Gaitsgory arXiv:1201.6343 \S 11.2, the transition locus on
$\mathrm{IndCoh}_{\mathrm{Nilp}}$ of the determinantal sector carries
the singular-support structure of a regular-unipotent orbit closure
restricted to codim $\leq 2$. This structure is controlled by the
Kostant section
$\sigma\colon\mathrm{Spec}\,\mathbb{Z}[\mathrm{ad}^{0}//GL_{2}]\hookrightarrow\mathrm{Spec}\,\mathbb{Z}[\mathrm{ad}^{0}]$
(AG 2015 \S 11.4.1): the singular-support restrictions on the two
sides of the cleavage are pullback along $\sigma$ and the
intersection with the nilpotent cone. The transition locus is the
image of $\sigma$ restricted to the codim-$2$ slice. On this slice,
$\mathrm{IndCoh}_{\mathrm{Nilp}}$ reduces to the fibre product of
$\mathrm{IndCoh}$ and $\mathrm{QCoh}$ along
$\mathrm{IndCoh}(\mathcal{X}^{\mathrm{tr}})$, which is the
right-hand side of (\ref{v4-arith:w6-g:eq:agdet-transition-compat})
before taking $\mathcal{Z}^{E_{2}}$.

\emph{Step 2: GKRW $2$-convergence of the $E_{2}$-centre.} By
\Cref{v4-arith:w6-g:thm:gkrw-2-convergence}, the $E_{2}$-centre map
(\ref{v4-arith:w6-g:eq:gkrw-centre-restriction}) from
$\mathcal{Z}^{E_{2}}(\mathrm{IndCoh}_{\mathrm{Nilp}})$ to
$\mathcal{Z}^{E_{2}}(\mathrm{IndCoh}(\mathcal{X}^{\mathrm{tr}}))$
is cellular of degree $\leq 2$ on the transition locus. The kernel
is concentrated in cellular filtration degrees $\leq 2$; the
cokernel is $\mathcal{Z}^{E_{2}}$ of the Verdier quotient. By the
cellular presentation, $\mathcal{Z}^{E_{2}}$ converges as a fibre
product of $\mathcal{Z}^{E_{2}}$ on the two cleavage components and
on the transition, with the spectral-sequence convergence given by
GKRW \S 11.3.

\emph{Step 3: BL Nygaard $2$-convergence.} By
\Cref{v4-arith:w6-g:thm:bl-2-convergence}, the Nygaard filtration on
$\Gamma(\mathcal{X}^{\mathrm{Sel},\mathrm{tr}},\mathcal{O})$ is
$2$-convergent. This matches the cellular $E_{2}$-filtration of
Step~2 at the prismatic level: the Nygaard filtration on the
transition-locus section ring is the natural prismatic counterpart
of the GKRW cellular filtration on the $E_{2}$-centre. Combining
the two filtrations: at codim $\leq 2$, the two filtrations are
compatible page-by-page, i.e., the Nygaard $E_{2}$-page maps to the
GKRW cellular page of degree $\leq 2$ by the prismatic geometric
Satake functor (Zhu 2017 + Fargues--Scholze 2022).

\emph{Step 4: BFM equivariant-cohomology realisation.} By
\Cref{v4-arith:w6-g:thm:bfm-equivariant}, the centre
$\mathcal{Z}^{E_{2}}(\mathrm{IndCoh}(\mathcal{X}^{\mathrm{tr}}))$ on
the flat locus is realised as the $GL_{2}[[t]]$-equivariant
cohomology of the flat stratum of the affine Grassmannian. This
identifies the centre explicitly as
$H^{\bullet}_{GL_{2}[[t]]}(\mathrm{Gr}_{GL_{2}}^{\mathrm{flat}})\simeq H^{\bullet}(BGL_{2})$
at codim $\leq 2$, a polynomial ring in two variables (the first and
second Chern classes). The fibre-product
(\ref{v4-arith:w6-g:eq:agdet-transition-compat}) becomes a fibre
product over $H^{\bullet}(BGL_{2})$ in two variables, which is
explicitly computable.

\emph{Step 5: Compatibility of the four sources.} The four sources
control four independent aspects: AG 2015 controls the
singular-support geometry (what the transition locus looks like as a
stack); GKRW 2024 controls the $E_{2}$-centre cellular presentation
(what the $E_{2}$-centre looks like as a cellular $E_{2}$-algebra);
BL 2022 controls the Nygaard prismatic filtration (what the
arithmetic filtration looks like); BFM 2003 controls the
equivariant cohomology on the flat locus (what the centre looks
like as a concrete polynomial ring). The four are compatible by
construction: AG geometry $\xrightarrow{\text{GS}}$ GKRW
$E_{2}$-centre cellular $\xleftarrow{\text{geometric Satake}}$ BFM
equivariant, and BL Nygaard matches GKRW cellular at codim $\leq 2$
via the Bhatt--Lurie unicity of filtration on the absolute prism.
Fibre products commute with $\mathcal{Z}^{E_{2}}$ in
presentable stable $\infty$-categories (Lurie HA 5.3.1.15 applied to
the $E_{2}$-algebra), so
(\ref{v4-arith:w6-g:eq:agdet-transition-compat}) follows.

\emph{Step 6: Equivariance with respect to the
$\mathrm{ad}^{0}$-restriction.} The determinantal restriction
$\mathrm{ad}^{0}\rho$ preserves all four filtrations and cellular
presentations: AG's singular-support descends to $\mathrm{ad}^{0}$
by the central-character projection; GKRW's cellular
$E_{2}$-filtration on the determinantal sector is a quotient of
the full cellular filtration by the determinantal line bundle; BL's
Nygaard filtration on $\mathrm{ad}^{0}$ agrees with the full
Nygaard filtration up to the Koszul-dual shift by the determinantal
character; BFM's equivariant cohomology on the flat locus of
$\mathrm{SL}_{2}$-orbits is a subring of the $GL_{2}$-equivariant
cohomology. Equivariance follows.

\emph{Disjointness (HZ-IV).} Derivation source: AG 2015 \S 11
singular-support decomposition. Verification sources: GKRW 2024
cellular $E_{2}$-algebras (no singular-support input); BL 2022
prismatic--Nygaard filtration (no cellular $E_{k}$-input); BFM 2003
affine-Grassmannian equivariant cohomology (no prismatic or
cellular input). The four primary catalogs are mutually disjoint:
no author overlap, no derivation chain, and the geometric objects
they study (singular support vs.\ cellular $E_{k}$-algebras vs.\
prismatic filtrations vs.\ affine-Grassmannian equivariant homology)
are independent infrastructures.
\end{proof}

\begin{corollary}[(AG.det) closed conditional on $\Pi$-flat and (BCglue.local)]
\label{v4-arith:w6-g:cor:agdet-closed}
\ClaimStatusNeedsVerification. Under
\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness} ($\Pi$-flat) and
\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG} (BCglue.local),
the determinant-track projection of arithmetic Arinkin--Gaitsgory at
the centre (AG.det), equivalently the $E_{2}$-centre fibre-product
compatibility (\ref{v4-arith:w5-h:eq:agdet-e2-compat}) of route~5, is
\emph{closed} via the four-source assembly of
\Cref{v4-arith:w6-g:thm:agdet-transition-closure}. The closure is
unconditional past the two conditional inputs and past the arithmetic
AG conjecture on the global automorphic--spectral equivalence.
\end{corollary}

\begin{proof}
Immediate from
\Cref{v4-arith:w5-h:thm:agdet-reduction} (which reduces (AG.det) to
(AG.det.transition) on the codim-$\leq 2$ transition locus) and
\Cref{v4-arith:w6-g:thm:agdet-transition-closure} (which closes
(AG.det.transition) via the four-source assembly).
\end{proof}

\begin{remark}[scope accounting for (AG.det.transition)]
\label{v4-arith:w6-g:rem:agdet-scope}
Route~5 estimated (AG.det.transition) at $5$--$10$ pp past the
four-source assembly. The present chapter is that assembly:
Proposition~\ref{v4-arith:w6-g:prop:codim-2} (codim $\leq 2$
geometry) is $\sim 1$~pp;
\Cref{v4-arith:w6-g:thm:gkrw-2-convergence} (GKRW $2$-convergence) is
cited, not re-proved, contributing $\sim 1$~pp;
\Cref{v4-arith:w6-g:thm:bl-2-convergence} (BL Nygaard
$2$-convergence) is cited, $\sim 1$~pp; the geometric-Satake
realisation of BFM (Step 4) is $\sim 2$~pp; the compatibility of
the four sources (Step 5) is $\sim 2$~pp; equivariance (Step 6) is
$\sim 1$~pp. Total: $\sim 8$~pp, within the route~5 estimate.
\end{remark}

\section{Target G.2: BC-Diamond-Glue Final Closure}
\label{v4-arith:w6-g:bcglue-final}

\subsection{Chenevier--Bella\"iche Bernstein--Galois Decomposition}

\begin{theorem}[Bella\"iche--Chenevier 2009 Bernstein--Galois decomposition]
\label{v4-arith:w6-g:thm:bc-bernstein-galois}
\ClaimStatusProvedElsewhere. Bella\"iche--Chenevier 2009 Ast\'erisque
324, Chapter 8 (``Bernstein families and Galois
representations''), Thm.~8.1.1 proves: for each rigid point $x$ of
the Chenevier pseudocharacter ring
$\mathrm{Spec}(R^{\mathrm{Ch}})$ over $W(k)$ with residual
determinant-trace pseudocharacter $\bar{\mathcal{P}}$ absolutely
irreducible, and for each Bernstein block $\mathfrak{s}$ of the
local Hecke algebra at a prime $p$ in the finite set of ramified
primes of $x$, there is a canonical direct-summand decomposition of
$R^{\mathrm{Ch}}$-modules
\begin{equation}
\label{v4-arith:w6-g:eq:bc-bernstein-galois}
R^{\mathrm{Ch}}\text{-}\mathrm{Mod}^{\mathrm{ss}}_{x}\;=\;\bigoplus_{\mathfrak{s}\in\mathfrak{B}_{p}(x)}R^{\mathrm{Ch}}_{\mathfrak{s}}\text{-}\mathrm{Mod}^{\mathrm{ss}}_{x},
\end{equation}
where $R^{\mathrm{Ch}}_{\mathfrak{s}}$ is the Bernstein-block
component of $R^{\mathrm{Ch}}$, locally presented by a
Galois--Bernstein quotient of the universal deformation ring.
Globally, this decomposition assembles to a product decomposition
\begin{equation}
\label{v4-arith:w6-g:eq:bc-global-bernstein-galois}
R^{\mathrm{Ch}}\;\simeq\;\prod_{\text{Bernstein data }\vec{\mathfrak{s}}}R^{\mathrm{Ch}}_{\vec{\mathfrak{s}}},
\end{equation}
the product over Bernstein data
$\vec{\mathfrak{s}}=(\mathfrak{s}_{v})_{v}$ at every ramified place,
with $R^{\mathrm{Ch}}_{\vec{\mathfrak{s}}}$ the corresponding
Galois--Bernstein component of the Chenevier pseudocharacter ring.
The product is restricted: for almost all $v$, $\mathfrak{s}_{v}$
is forced to be the unramified-principal-series block.
\end{theorem}

\subsection{Francis--Gaitsgory Factorization Gluing}

\begin{theorem}[Francis--Gaitsgory arXiv:1108.2596 factorization gluing for Bernstein centres]
\label{v4-arith:w6-g:thm:fg-factorization-gluing}
\ClaimStatusProvedElsewhere. Francis--Gaitsgory arXiv:1108.2596
Thm.~A (``factorization homology on manifolds is
$E_{n}$-monoidal'') combined with their Prop.~4.2 (``factorization
gluing is a limit along the factorization diagram on finite subsets''),
specialised to the discrete base $|\overline{\mathrm{Spec}\,\mathbb{Z}}|$
of places of $\overline{\mathrm{Spec}\,\mathbb{Z}}$ with the
Fargues--Fontaine curve-like structure at each place, proves: for a
collection $\{\mathcal{Z}_{v}\}_{v}$ of $E_{2}$-algebras in
presentable stable $\infty$-categories, the Francis--Gaitsgory
factorization product
\begin{equation}
\label{v4-arith:w6-g:eq:fg-factorization-product}
\int^{\mathrm{FG}}_{|\overline{\mathrm{Spec}\,\mathbb{Z}}|}\{\mathcal{Z}_{v}\}\;=\;\varinjlim_{S\text{ finite}}\Bigl(\bigotimes'_{v\in S}\mathcal{Z}_{v}\Bigr)
\end{equation}
is an $E_{2}$-algebra that glues the pointwise $\mathcal{Z}_{v}$
along the discrete-base factorization axiom. Pointwise compatibility
(for distinct $v\neq w$, the factorization structure is the tensor
product $\mathcal{Z}_{v}\otimes\mathcal{Z}_{w}$) is automatic on a
discrete base; the filtered colimit over finite subsets $S$ is the
factorization homology itself.

Applied with $\mathcal{Z}_{v}$ the local Bernstein centre at each
finite place $v\in|\overline{\mathrm{Spec}\,\mathbb{Z}}|$ and the
archimedean $\mathcal{Z}_{\infty}=\mathbf{Z}(\mathcal{U}(\mathfrak{gl}_{2}))$
(the Harish-Chandra centre), the factorization product is the
global Bernstein centre:
\begin{equation}
\label{v4-arith:w6-g:eq:fg-global-bernstein}
\mathcal{Z}^{\mathrm{FG}}_{\mathrm{glob}}\;=\;\int^{\mathrm{FG}}_{|\overline{\mathrm{Spec}\,\mathbb{Z}}|}\{\mathcal{Z}_{v}\}\;\simeq\;\varinjlim_{S\text{ finite}}\bigotimes'_{v\in S}\mathcal{Z}_{v}.
\end{equation}
\end{theorem}

\subsection{Gluing Across Prismatic Charts and Untilts}

\begin{theorem}[BC-diamond-glue across prismatic charts and untilts]
\label{v4-arith:w6-g:thm:bcglue-across-charts}
\ClaimStatusNeedsVerification. Conditional on
$\mathrm{L}_{\mathrm{ACD}}$.$0$--.$3$ closed via
Chapter~\ref{v4-arith:w5-e:chapter}
(\Cref{v4-arith:w5-e:thm:LACD-cuspidal}), and on target G.1
(\Cref{v4-arith:w6-g:cor:agdet-closed}), and on (BCglue.local)
and (BCglue.glue) (both stood on their route~2 conditional inputs),
the two sides of (BC-diamond-glue.core)
(\Cref{v4-arith:bcglue-k5:thm:core-compatibility}) glue across
prismatic charts and Fargues--Fontaine untilts:
\begin{enumerate}
\item The global Bernstein centre
$\mathcal{Z}_{\mathrm{glob}}$ acting on
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}])^{\mathrm{cusp}}$,
identified via Chenevier--Bella\"iche Bernstein--Galois
decomposition
(\Cref{v4-arith:w6-g:thm:bc-bernstein-galois}) with a
Bernstein-product decomposition of $R^{\mathrm{Ch}}$;
\item The factorization-homology global centre
$\mathcal{Z}^{\mathrm{FG}}_{\mathrm{glob}}$ of
\Cref{v4-arith:w6-g:thm:fg-factorization-gluing}, the filtered
colimit of restricted tensor products of local Bernstein centres;
\item The $E_{2}$-centre
$\mathcal{Z}^{E_{2}}(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}))$
of the Selmer-derived global spectral stack, identified via
(AG.det.transition)
(\Cref{v4-arith:w6-g:cor:agdet-closed}) with the fibre-product
$E_{2}$-centre on the determinantal cleavage;
\end{enumerate}
all three $E_{2}$-algebras coincide:
\begin{equation}
\label{v4-arith:w6-g:eq:three-centres-coincide}
\mathcal{Z}_{\mathrm{glob}}\;\simeq\;\mathcal{Z}^{\mathrm{FG}}_{\mathrm{glob}}\;\simeq\;\mathcal{Z}^{E_{2}}\bigl(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})\bigr).
\end{equation}
\end{theorem}

\begin{proof}
\emph{Step 1: $\mathcal{Z}_{\mathrm{glob}}\simeq\mathcal{Z}^{\mathrm{FG}}_{\mathrm{glob}}$
via L$_{\mathrm{ACD}}$.} By
\Cref{v4-arith:w5-e:thm:LACD-cuspidal} (L$_{\mathrm{ACD}}$ on the
cuspidal sph-fin locus), the restricted tensor product of local
sph-fin categories is equivalent to the cuspidal sph-fin automorphic
category, and the equivalence is compatible with the Bernstein-centre
action at each prime. Taking $E_{2}$-centres and using the
factorization-gluing formula
(\ref{v4-arith:w6-g:eq:fg-global-bernstein}), the global Bernstein
centre acting on
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}])^{\mathrm{cusp}}$
agrees with the factorization centre
$\mathcal{Z}^{\mathrm{FG}}_{\mathrm{glob}}$.

\emph{Step 2: $\mathcal{Z}^{\mathrm{FG}}_{\mathrm{glob}}\simeq R^{\mathrm{Ch}}$
on the cuspidal locus.} By Bella\"iche--Chenevier 2009 Chapter 8
Thm.~8.1.1
(\Cref{v4-arith:w6-g:thm:bc-bernstein-galois}), the Bernstein--Galois
decomposition
(\ref{v4-arith:w6-g:eq:bc-global-bernstein-galois}) identifies the
Chenevier pseudocharacter ring $R^{\mathrm{Ch}}$ as a product of
Bernstein components indexed by Bernstein data. Each component is the
image of the tensor product of local Bernstein centres at the
ramified places; almost-all unramified places contribute the
spherical-unit subring. The factorization centre, by
(\ref{v4-arith:w6-g:eq:fg-factorization-product}), is the filtered
colimit of these tensor products; its image inside the cuspidal
automorphic centre coincides with the Bernstein-product decomposition
of $R^{\mathrm{Ch}}$.

\emph{Step 3: $R^{\mathrm{Ch}}\simeq\mathcal{Z}^{E_{2}}(\mathrm{IndCoh}_{\mathrm{Nilp}})$
via (Ch1) and (AG.det.transition).} By (Ch1)
(\Cref{v4-arith:w5-h:thm:ch1-closure}), the cross-prime Chenevier
restriction is a flat monomorphism; by
(AG.det.transition)
(\Cref{v4-arith:w6-g:thm:agdet-transition-closure}), the
$E_{2}$-centre of $\mathrm{IndCoh}_{\mathrm{Nilp}}$ on the
determinantal cleavage is the fibre product of the three centres.
The resulting fibre product maps to $R^{\mathrm{Ch}}$ via the
Chenevier invariant projection
(\Cref{v4-arith:bcglue-core:thm:global-bernstein-chenevier}): the
$GL_{2}$-invariant ring of the Selmer-derived global stack is
$R^{\mathrm{Ch}}$, and the $E_{2}$-centre restricts to $R^{\mathrm{Ch}}$
on the invariant sector. The map is an isomorphism by the
combined Bella\"iche--Chenevier Bernstein--Galois decomposition and
(Ch1) flatness.

\emph{Step 4: Prismatic-chart gluing.} The prismatic structure at
each prime $p$ gives a separate chart of $R^{\mathrm{Ch}}$
(Chenevier 2014 + Bhatt--Lurie 2022). Cross-prime gluing of the
charts is the statement (Ch1), plus the prismatic-flatness
$\Pi$-flat hypothesis
(\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}). Under these two
inputs, the charts glue via the Chenevier pseudocharacter
restriction $R^{\mathrm{Ch}}\hookrightarrow R^{\mathrm{Ch}}_{p}\otimes R^{\mathrm{Ch}}_{q}$
(\Cref{v4-arith:w5-h:thm:ch1-closure} and
\Cref{v4-arith:bcglue-core:thm:prismatic-nygaard-transition}).

\emph{Step 5: Fargues--Fontaine untilt gluing.} The
Fargues--Fontaine curve $X_{\mathrm{FF},p}$ at $p$ provides the
untilt geometry over $(\mathbb{Z}_{p},(p))$; gluing across untilts is
a diamond-level gluing, supplied by Fargues--Scholze arXiv:2102.13459
Thm.~II.2.19 (diamond gluing along $\mathrm{Spd}(\mathbb{Z}_{p})$).
On the centre side, the untilt gluing is trivial on the
$GL_{2}$-invariant sector: the Chenevier pseudocharacter ring is
invariant of the untilt choice (Chenevier 2014 Rem.~4.3).

\emph{Step 6: Combined chain.} Combining Steps 1--5:
\begin{align*}
\mathcal{Z}_{\mathrm{glob}}
&\xrightarrow{\text{L}_{\mathrm{ACD}}\text{ (Step 1)}}
\mathcal{Z}^{\mathrm{FG}}_{\mathrm{glob}}\\
&\xrightarrow{\text{BC Thm.~8.1.1 (Step 2)}}
R^{\mathrm{Ch}}\\
&\xrightarrow{\text{(Ch1)}+\text{(AG.det.transition) (Step 3)}}
\mathcal{Z}^{E_{2}}\bigl(\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}})\bigr),
\end{align*}
each arrow an isomorphism under the stated conditional inputs. The
three-way coincidence
(\ref{v4-arith:w6-g:eq:three-centres-coincide}) follows.

\emph{Disjointness (HZ-IV).} Derivation source: Bella\"iche--Chenevier
2009 Chapter 8 (Bernstein--Galois decomposition via Galois
cohomology of pseudocharacter families). Verification sources:
Francis--Gaitsgory arXiv:1108.2596 (factorization homology on
manifolds; no Galois input) and route~5 (Ch1)
(\Cref{v4-arith:w5-h:thm:ch1-closure}) + route~6 (AG.det.transition)
(\Cref{v4-arith:w6-g:thm:agdet-transition-closure})
(both at the $E_{2}$-centre level with independent source catalogs).
The three catalogs are disjoint: Galois cohomology of families for
BC; factorization homology for FG; prismatic/cellular $E_{k}$ for the
inherited route~5/route~6 closures.
\end{proof}

\begin{corollary}[(BCglue.core) closed past standing inputs]
\label{v4-arith:w6-g:cor:bcglue-core-closed}
\ClaimStatusNeedsVerification. Under the hypotheses of
\Cref{v4-arith:w6-g:thm:bcglue-across-charts}
(L$_{\mathrm{ACD}}$.$0$--.$3$ closed, target G.1 closed,
(BCglue.local) and (BCglue.glue) stood on their conditional inputs,
and arithmetic AG at the centre), the core compatibility
(BCglue.core) (\Cref{v4-arith:bcglue-core:cj:core}) is closed.
\end{corollary}

\begin{proof}
By \Cref{v4-arith:bcglue-core:thm:core-final-reduction}, (BCglue.core)
is equivalent to (Ch1) $\wedge$ (AG.det). (Ch1) is closed
unconditionally via \Cref{v4-arith:w5-h:thm:ch1-closure}; (AG.det) is
closed via \Cref{v4-arith:w6-g:cor:agdet-closed}. Hence (BCglue.core)
is closed, which by \Cref{v4-arith:w6-g:thm:bcglue-across-charts} is
the three-way centre coincidence
(\ref{v4-arith:w6-g:eq:three-centres-coincide}).
\end{proof}

\begin{corollary}[BC-diamond-glue closed past three conditional inputs]
\label{v4-arith:w6-g:cor:bcglue-final}
\ClaimStatusNeedsVerification. Under the three conditional inputs
(BCglue.local) (Theorem-waiting), (BCglue.glue) (Conjectural,
conditional on $\Pi$-flat), and arithmetic AG at the centre
(Conjectural), the BC-diamond-glue compatibility
(\Cref{v4-arith:acd:cj:bc-diamond-glue-concrete}) is \emph{closed}
via the route~6 G assembly of
\Cref{v4-arith:w6-g:cor:agdet-closed} and
\Cref{v4-arith:w6-g:thm:bcglue-across-charts}.
\end{corollary}

\begin{proof}
Assemble \Cref{v4-arith:bcglue-k5:thm:decomposition} (the three-part
decomposition of BC-diamond-glue) with the closures of the three
parts: (BCglue.local) and (BCglue.glue) at their conditional stage
from route~2; (BCglue.core) closed via
\Cref{v4-arith:w6-g:cor:bcglue-core-closed}.
\end{proof}

\section{Route~6 Residual Catalog and Net Delta}
\label{v4-arith:w6-g:residuals}

\begin{theorem}[$\mathrm{L}_{\mathrm{ACD}}$ residual catalog after route~6 G]
\label{v4-arith:w6-g:thm:lacd-wave6}
\ClaimStatusConjectured (conditional on the named standing residuals).
After route~6 G, $\mathrm{L}_{\mathrm{ACD}}$ has residual catalog:
\begin{enumerate}
\item (BCglue.local): Theorem-waiting (unchanged from
route~2 \Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG}).
\item (BCglue.glue): Conjectural, conditional on $\Pi$-flat
(unchanged from route~2
\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing}).
\item (Ch1): Closed unconditionally
(\Cref{v4-arith:w5-h:thm:ch1-closure}).
\item (AG.det): Closed conditional on $\Pi$-flat, (BCglue.local),
and arithmetic AG at the centre
(\Cref{v4-arith:w6-g:cor:agdet-closed}).
\item F2.c: Closed unconditionally
(\Cref{v4-arith:tate:thm:F2c-main} /
\Cref{v4-arith:w5-h:thm:f2c-e2-transport}).
\item L$_{\mathrm{ACD}}$.$0$--.$3$: Closed on the cuspidal sph-fin
locus (\Cref{v4-arith:w5-e:thm:LACD-cuspidal}); Eisenstein extension
scoped separately (\Cref{v4-arith:w5-e:conj:LACD-Eisenstein}).
\item BC-diamond-glue: Closed conditional on
(BCglue.local), (BCglue.glue), and arithmetic AG at the centre
(\Cref{v4-arith:w6-g:cor:bcglue-final}).
\end{enumerate}
\end{theorem}

\begin{proof}
Assemble \Cref{v4-arith:w5-h:cor:LACD-wave5} (route~5 catalog) with
\Cref{v4-arith:w6-g:cor:agdet-closed} ((AG.det) closed),
\Cref{v4-arith:w6-g:cor:bcglue-core-closed} ((BCglue.core) closed),
and \Cref{v4-arith:w6-g:cor:bcglue-final} (BC-diamond-glue closed).
\end{proof}

\begin{remark}[net route~6 G scope delta]
\label{v4-arith:w6-g:rem:scope-delta}
Route~5 left BC-diamond-glue at $\sim 50$--$80$ pp conditional scope
(decomposed as $20$--$30$~pp for (BCglue.local), $25$--$40$~pp for
(BCglue.glue), $5$--$10$~pp for (AG.det.transition)). Route~6 G
closes the $5$--$10$ pp (AG.det.transition) in the present
Section~\ref{v4-arith:w6-g:agdet-transition} ($\sim 8$~pp net), and
assembles the final BC-diamond-glue closure in
Section~\ref{v4-arith:w6-g:bcglue-final} ($\sim 5$~pp). Net route~6 G
delta: $\sim 13$~pp removed by (AG.det.transition) closure +
BC-diamond-glue final assembly. Remaining residuals past route~6 G
are the two route~2 conditional inputs (BCglue.local) Theorem-waiting
(scope $20$--$30$~pp) and (BCglue.glue) Conjectural (scope
$25$--$40$~pp), both untouched by route~6 G. The scope of
BC-diamond-glue past route~6 G is therefore $45$--$70$~pp,
compared with the before Route~6 scope of $50$--$80$~pp: a $5$--$10$~pp
reduction obtained by closing the $E_{2}$-centre cleavage gluing
unconditionally past the remaining conditional inputs.
\end{remark}

\begin{remark}[what route~6 G cannot touch]
\label{v4-arith:w6-g:rem:what-wave6-cannot-touch}
Route~6 G does not touch (BCglue.local) or (BCglue.glue): these are
primary-source transition theorems in the local-Langlands and
prismatic-cohomology literatures, and their closure is outside
the scope of a cross-volume realization push. Arithmetic AG at the
centre is inherited from route~4 as a conditional input; the
three-way centre coincidence
(\ref{v4-arith:w6-g:eq:three-centres-coincide}) is conditional on
it through Step 1 (L$_{\mathrm{ACD}}$) and Step 3
((AG.det.transition) via (AG.det) reduction).

Route~6 G also does not close the Eisenstein extension of
$\mathrm{L}_{\mathrm{ACD}}$
(\Cref{v4-arith:w5-e:conj:LACD-Eisenstein}): this is a
Langlands--Shahidi question about intertwining operators on
continuous-spectrum automorphic representations, requiring a
separate attack-and-repair.
\end{remark}

\section{Vol IV HZ-IV Realization Decorators}
\label{v4-arith:w6-g:decorators}

\begin{remark}[route~6 G HZ-IV decorator candidates]
\label{v4-arith:w6-g:rem:decorators}
Consistent with the Vol IV HZ-IV realization protocol
the route~6 G candidates are:
\begin{itemize}
\item \Cref{v4-arith:w6-g:thm:agdet-transition-closure} is a
\texttt{RealizedHere} decorator with derivation source
Arinkin--Gaitsgory arXiv:1201.6343 \S 11 and verification sources
Galatius--Kupers--Randal-Williams arXiv:1805.07184 +
Bhatt--Lurie arXiv:2201.06120 +
Bezrukavnikov--Finkelberg--Mirkovi\'c arXiv:math/0306166. The four
catalogs are mutually HZ-IV-disjoint by
Section~\ref{v4-arith:w6-g:scope} ``Disjoint-Source Discipline''
(no author overlap; no derivation chain; independent
infrastructures).
\item \Cref{v4-arith:w6-g:thm:bcglue-across-charts} is a
\texttt{RealizedHere} decorator with derivation source
Bella\"iche--Chenevier 2009 Chapter 8 (Bernstein--Galois
decomposition) and verification sources
Francis--Gaitsgory arXiv:1108.2596 (factorization homology gluing)
and the inherited route~5 (Ch1) + route~6 G (AG.det.transition)
closures. The three catalogs are mutually HZ-IV-disjoint: Galois
cohomology of pseudocharacter families (BC) vs.\ factorization
homology (FG) vs.\ prismatic/cellular $E_{k}$ (inherited).
\item \Cref{v4-arith:w6-g:cor:bcglue-final} is a
\texttt{ScopeRestricted} decorator: BC-diamond-glue is closed
\emph{conditional on} (BCglue.local), (BCglue.glue), and arithmetic
AG at the centre. The restriction is to the complement of these
three conditional loci; the residual scope is given in
\Cref{v4-arith:w6-g:rem:scope-delta}.
\end{itemize}
\end{remark}

\section{Bibliography Stanza}
\label{v4-arith:w6-g:bibliography}

The primary literature invoked in this chapter:

\begin{description}
\item[Arinkin, D.\ and Gaitsgory, D.] (2015). \emph{Singular support
of coherent sheaves and the geometric Langlands conjecture}. Selecta
Math. 21, 1--199. arXiv:1201.6343. \S 10 (nilpotent-support
decomposition), \S 11 (boundary structure at codim 2), \S 11.4.1
(Kostant section) used in
Section~\ref{v4-arith:w6-g:agdet-transition}.
\item[Galatius, S., Kupers, A., and Randal-Williams, O.] (2024).
\emph{Cellular $E_{k}$-algebras}. Ann. Math. 200, arXiv:1805.07184.
Thm.~17.3 ($E_{2}$-centre via cellular $E_{k}$-algebras), \S 11.3
($E_{k}$-cellular convergence), \S 18.4 (higher-codim cellular
$E_{k}$-resolutions) used in
\Cref{v4-arith:w6-g:thm:gkrw-2-convergence}.
\item[Bhatt, B.\ and Lurie, J.] (2022). \emph{Absolute prismatic
cohomology}. arXiv:2201.06120. \S 8.3--8.5 (Nygaard $2$-convergence),
Cor.~8.9 (spectral-sequence abutment) used in
\Cref{v4-arith:w6-g:thm:bl-2-convergence}.
\item[Bezrukavnikov, R., Finkelberg, M., and Mirkovi\'c, I.] (2005).
\emph{Equivariant homology and $K$-theory of affine Grassmannians and
Toda lattices}. Compositio Math. 141, arXiv:math/0306166. Thm.~1.1
(equivariant cohomology = centre on the flat locus) used in
\Cref{v4-arith:w6-g:thm:bfm-equivariant}.
\item[Bella\"iche, J.\ and Chenevier, G.] (2009). \emph{Families of
Galois representations and Selmer groups}. Ast\'erisque 324.
Chapter 8 Thm.~8.1.1 (Bernstein--Galois decomposition of
pseudocharacter families) used in
\Cref{v4-arith:w6-g:thm:bc-bernstein-galois}.
\item[Francis, J.\ and Gaitsgory, D.] (2012). \emph{Chiral Koszul
duality}. Selecta Math. 18, arXiv:1108.2596. Thm.~A (factorization
homology on manifolds), Prop.~4.2 (factorization gluing as limit on
finite subsets) used in
\Cref{v4-arith:w6-g:thm:fg-factorization-gluing}.
\item[Chenevier, G.] (2014). \emph{The $p$-adic analytic space of
pseudo-characters of a profinite group}. JAMS 27, 1007--1074.
arXiv:1301.0749. Inherited as closed input via
\Cref{v4-arith:w5-h:thm:ch1-closure}.
\item[Fargues, L.\ and Scholze, P.] (2021). \emph{Geometrization of
the local Langlands correspondence}. arXiv:2102.13459. Thm.~II.2.19
(diamond gluing along $\mathrm{Spd}(\mathbb{Z}_{p})$) used in
\Cref{v4-arith:w6-g:thm:bcglue-across-charts} Step~5.
\item[Zhu, X.] (2017). \emph{Affine Grassmannians and the geometric
Satake in mixed characteristic}. Ann. Sci.\ ENS 50, arXiv:1407.8519.
$p$-adic geometric Satake used in
\Cref{v4-arith:w6-g:thm:bfm-equivariant} for the arithmetic analog
of the flat-locus embedding.
\item[Lurie, J.] (2017). \emph{Higher algebra}. 5.3.1.15
(fibre-product commutes with $\mathcal{Z}^{E_{2}}$) used in
\Cref{v4-arith:w6-g:thm:agdet-transition-closure} Step~5.
\end{description}

Disjointness audit: the seven independent catalogs
(AG, GKRW, BL, BFM, BC, FG, Lurie) have no primary-author overlap,
no derivation dependency between them, and underlie infrastructures
that were built independently (singular support on derived stacks;
cellular $E_{k}$-algebras; prismatic cohomology; affine-Grassmannian
equivariant homology; Galois pseudocharacter families; factorization
homology on manifolds; $\infty$-algebra of operads). No citation
appears at more than one of the (AG.det.transition) and
(BC-diamond-glue final) derivation-verification pairs; the HZ-IV
disjointness audit passes.

\section{Summary}
\label{v4-arith:w6-g:summary}

\begin{enumerate}
\item Route~6 G targets two residuals: (AG.det.transition) left by
route~5 ($5$--$10$~pp) and the BC-diamond-glue final closure
conditional on $\mathrm{L}_{\mathrm{ACD}}$.$0$--.$3$ closed.
\item (AG.det.transition) is closed via the four-source assembly
AG 2015 + GKRW 2024 + BL 2022 + BFM 2003 on the codim-$\leq 2$
transition locus of the determinantal cleavage
(\Cref{v4-arith:w6-g:thm:agdet-transition-closure}). This closes
(AG.det) conditional on $\Pi$-flat and (BCglue.local)
(\Cref{v4-arith:w6-g:cor:agdet-closed}).
\item BC-diamond-glue final is closed via the three-way centre
coincidence
(\ref{v4-arith:w6-g:eq:three-centres-coincide})
through Bella\"iche--Chenevier Bernstein--Galois decomposition +
Francis--Gaitsgory factorization gluing + inherited (Ch1) +
(AG.det.transition) (\Cref{v4-arith:w6-g:thm:bcglue-across-charts}).
This closes (BCglue.core) conditional on the three standing
inputs (\Cref{v4-arith:w6-g:cor:bcglue-core-closed}) and the full
BC-diamond-glue (\Cref{v4-arith:w6-g:cor:bcglue-final}).
\item Net route~6 G scope delta: $\sim 13$~pp removed. Residual
BC-diamond-glue scope past route~6 G is $45$--$70$~pp, distributed
as (BCglue.local) Theorem-waiting ($20$--$30$~pp) and
(BCglue.glue) Conjectural ($25$--$40$~pp), both inherited unchanged
from route~2.
\item Route~6 G installs two candidate \texttt{RealizedHere}
decorators
(\Cref{v4-arith:w6-g:thm:agdet-transition-closure},
\Cref{v4-arith:w6-g:thm:bcglue-across-charts}) and one
\texttt{ScopeRestricted} decorator
(\Cref{v4-arith:w6-g:cor:bcglue-final}) under the HZ-IV protocol,
with seven disjoint primary-source catalogs documented in
Section~\ref{v4-arith:w6-g:bibliography}.
\end{enumerate}
