\chapter{Route~6J: Source-Disjoint Audit of Route~5 Chapters (49--59)}
\label{v4-arith:w6-j:chapter}

\emph{Route~6J runs the seven-test hostile audit on the
eleven route~5 chapters (49--59) inscribed 2026-04-24. Discipline:
find overclaims, hidden regressions, label collisions, missed
references, and dubious proofs; fix syntactic / cross-reference
errors in place; flag mathematical overclaims to the synthesis
ledger without rewriting. Outcome: eleven chapter audits, each
with a seven-test trace; three cross-chapter tables
(label uniqueness, cross-reference validity, prose-discipline scan);
a bug ledger covering the fixes made in this pass; an overclaim
ledger covering the items flagged but not rewritten; and a
route~5 quality-of-proof summary. The audit is severe:
the route~5 work is substantive, internally consistent across
chapters, and free of prohibited prose; the label and
cross-reference hygiene has a small number of concrete breakages
(all fixed); a handful of strong-sounding claim-status tags
sit above the actual mathematical content and are flagged as
overclaims for downstream reconciliation.}

\section{Per-Chapter Audit Trace}
\label{v4-arith:w6-j:per-chapter}

\subsection{Chapter 49 (Route E): F1.a.1, F1.a.2, and $\mathrm{L}_{\mathrm{ACD}}$}
\label{v4-arith:w6-j:ch49}

\begin{description}
\item[A1 Source collision.] Clozel--Harris--Taylor, Kisin 2009,
Gee--Kisin 2014, Emerton--Gee, Hida are jointly disjoint from
Dotto--Emerton--Gee and Fargues--Scholze as claimed. \textbf{Pass.}
\item[A2 Sign/convention.] Hodge--Tate normalisation via
Berger--Colmez 2008 is consistent. \textbf{Pass.}
\item[A3 Ambient category.] Compactly generated presentable stable
$\infty$-categories on both sides; block-diagonal preserves this.
\textbf{Pass.}
\item[A4 Missing hypothesis.] Setup~\ref{v4-arith:w5-e:setup:TW}
enumerates (TW1)--(TW4) explicitly. The ``unique cusp at level 1''
remark restricts to $\mathrm{SL}_{2}(\mathbb{Z})$ implicitly.
\textbf{Pass.}
\item[A5 False functoriality.] Hecke compatibility via
\Cref{v4-arith:w5-e:lem:CHT-unr-Hecke}. Block-diagonal action.
\textbf{Pass.}
\item[A6 Unproved equivalence.] Non-ordinary extension named as
\Cref{v4-arith:w5-e:conj:f1a1-full}; non-semisimple class match
conditional on \Cref{v4-arith:f1a3-BH:conj:Paskunas-wild-ext};
Eisenstein extension as \Cref{v4-arith:w5-e:conj:LACD-Eisenstein}.
All named. \textbf{Pass.}
\item[A7 Engine.] None. \textbf{Pass.}
\end{description}

\paragraph{Flag.} Citation to ``Dotto--Emerton--Gee arXiv:2603.26887''
uses an arXiv identifier with a leading year code inconsistent with
2026 submission conventions. The paper is quoted repeatedly as
load-bearing; verifying the arXiv identifier against the primary
literature is a downstream obligation. Recorded in the overclaim
ledger, not corrected here.

\paragraph{Verdict.} Chapter 49 is structurally sound. Seven-attack
protocol passes; residual tags are honest; the
\texttt{ClaimStatusProvedHere} on
\Cref{v4-arith:w5-e:thm:f1a1-ordinary} is justified by the primary
literature cascade.

\subsection{Chapter 50 (Route F): F1.a.3 (A+B)}
\label{v4-arith:w6-j:ch50}

\begin{description}
\item[A1 Source collision.] Bernstein 1984, Bushnell--Henniart 2006,
Paskunas 2013, Paskunas 2015, Ben-Zvi--Francis--Nadler, Lurie HA
form a disjoint tensor catalog. \textbf{Pass.}
\item[A2 Sign/convention.] Co-Hochschild convention (HA 5.5.3)
matches BFN and Costello--Gwilliam. \textbf{Pass.}
\item[A3 Ambient category.] Presentable stable $\infty$-category
Pr${}^{L}_{st}$; fibre product with product is ok by HA 4.8.1.17.
\textbf{Pass.}
\item[A4 Missing hypothesis.] Orthogonal idempotent block
decomposition is hypothesis; Lemma~\ref{v4-arith:w5-f:F1a3-AB:lem:HH-block-additive}
states this cleanly. \textbf{Pass.}
\item[A5 False functoriality.] Block-additivity of Hochschild uses
cocontinuity only; matches HA 5.1.2.2 Dunn additivity. \textbf{Pass.}
\item[A6 Unproved equivalence.] Per-block residual (R.A)
conjectural; named. ``Very special'' ordinary block (R.B.1) named.
Wild prime centraliser (R.B.2) named. \textbf{Pass.}
\item[A7 Engine.] None. \textbf{Pass.}
\end{description}

\paragraph{Flag (disjointness).}
The disjointness audit in \S\ref{v4-arith:w5-f:F1a3-AB:bibliography}
lists ``Paskunas 2013'' and ``Paskunas 2015'' as separate sources
yielding ``one citation chain, two disjoint inputs''. Strictly, same
author papers are partially but not fully disjoint in the Vol IV
HZ-IV sense. The block-additivity and generic-fibre arguments do
not rely on this; the ordinary-block controlled-deformation result
\Cref{v4-arith:w5-f:F1a3-AB:prop:Ext1-ordinary-controlled}
(\texttt{ClaimStatusProvedHereConditional}) does, and is tagged
correctly.

\paragraph{Verdict.} Chapter 50 is the strongest route~5 chapter.
The factoring of F1.a.3.A/F1.a.3.B into (unconditional lemma +
narrower conjectures) is a genuine structural reduction; the
block-additivity lemma is a clean \texttt{ProvedHere} on first-principles
$\infty$-category theory.

\subsection{Chapter 51 (Route G): F1.a.3.C Wild-EG Compact Generation}
\label{v4-arith:w6-j:ch51}

\begin{description}
\item[A1 Source collision.] Emerton--Gee, Bhatt--Scholze,
Gaitsgory--Rozenblyum, Arinkin--Gaitsgory, Bushnell--Henniart form
a disjoint catalog. \textbf{Pass.}
\item[A2 Sign/convention.] Arinkin--Gaitsgory nilpotent-singular
support; Gaitsgory--Rozenblyum Serre-twist convention. \textbf{Pass.}
\item[A3 Ambient category.] $\mathrm{IndCoh}_{\mathrm{Nilp}}$ on a
Noetherian formal algebraic stack. \textbf{Pass.}
\item[A4 Missing hypothesis.] Tangent complex of tor-amplitude
$[-1,0]$ on each stratum. Supplied by Emerton--Gee for every prime
$p$. \textbf{Pass.}
\item[A5 False functoriality.] Recollement across strata via
Beilinson--Bernstein--Deligne extended by Gaitsgory--Rozenblyum.
Push-forward preserves compact generators (DAG Vol.~II Prop.~4.4).
\textbf{Pass.}
\item[A6 Unproved equivalence.] None in the classical-stack
statement. The derived enhancement conjecture
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement} is not invoked.
\textbf{Pass.}
\item[A7 Engine.] None. \textbf{Pass.}
\end{description}

\paragraph{Flag (Step 4 claim).}
\Cref{v4-arith:w5-g:f1a3-C:prop:compact-gen-wild-p3} Step 3 asserts
``Matching at dimension two is exact: $2=2$
(\Cref{v4-arith:f1a3-BH:prop:dim-audit-p3} in the reverse direction);
the two classes $\alpha_{01}$ and $\alpha_{12}$ are the two
degree-$(-1)$ cotangent directions.'' The ``reverse direction'' of
the dim-audit is not established; as stated, it is a dimensional
count, not a class-level identification. This is labelled
\texttt{ClaimStatusProvedHere} but is in fact a matching up to
dimension only. Flagged for downstream refinement; not corrected.

\paragraph{Verdict.} Chapter 51 closes F1.a.3.C in its
classical-stack form rigorously. The ``does not invoke the wild-EG
enhancement'' scope declaration is explicit and honest. The
dimension-only flag above is a minor overclaim on the class level;
the proof still goes through on compact generation.

\subsection{Chapter 52 (Route H): BC-Glue-Core Residuals and F2.c}
\label{v4-arith:w6-j:ch52}

\begin{description}
\item[A1 Source collision.] Chenevier 2013, Bellaiche--Chenevier
2009, Bhatt--Scholze, Bhatt--Lurie, Arinkin--Gaitsgory, GKRW,
BFN, Lurie HA, Francis--Gaitsgory. \textbf{Pass.}
\item[A2 Sign/convention.] Nygaard filtration (Bhatt--Lurie
\S 8.3) matches prismatic flatness convention. \textbf{Pass.}
\item[A3 Ambient category.] Coherent $\infty$-operads (E${}_{2}$);
Pr${}^{L}_{st}$. \textbf{Pass.}
\item[A4 Missing hypothesis.] Absolutely irreducible residual
$\bar\rho$ for (Ch1); $\mathfrak{m}$-adic completeness; discrete
indexing for F2.c. All explicit. \textbf{Pass.}
\item[A5 False functoriality.] GKRW E${}_{2}$-centre identified
with $HH^{\bullet}_{E_{2}}$ via BFN; fibre product of centres.
\textbf{Pass.}
\item[A6 Unproved equivalence.] (AG.det.transition) named as
\texttt{ClaimStatusConjectured}; (BCglue.local), (BCglue.glue)
unchanged from route~4. \textbf{Pass.}
\item[A7 Engine.] None. \textbf{Pass.}
\end{description}

\paragraph{Flag (Step 5 chain).}
\Cref{v4-arith:w5-h:thm:ch1-closure} Step 5 invokes the
``pro-\'etale comparison isomorphism of Bhatt--Scholze \emph{Integral
$p$-adic Hodge Theory}'' to bridge prismatic cohomology with the
Emerton--Gee stack; the comparison is stated loosely as ``the
universal determinantal cocharacter is recovered as the
$GL_{2}$-invariant trace of the universal
$(\varphi,\Gamma)$-module''. This is correct direction but
requires spelling out the flatness compatibility at the level of
universal pseudocharacter rings; the reference to BS Ann. Scient.
ENS 52 (2019) is load-bearing and should be checked against a
primary source in the synthesis wave.

\paragraph{Flag (AG.det reduction).}
\Cref{v4-arith:w5-h:thm:agdet-reduction} is labelled
\texttt{ClaimStatusProvedHere} for a scope-reduction statement; the
reduction is of (AG.det) to (AG.det.transition). The reduction
itself is legitimate, but the \texttt{ProvedHere} tag sits on
the reduction, not on the closure. Acceptable; consistent with Vol
IV protocol for scope-reduction theorems.

\paragraph{Verdict.} Chapter 52 is technically sophisticated; the
three-way reduction is a genuine simplification of the
$\mathrm{L}_{\mathrm{ACD}}$ residual. The F2.c elementary path is a
clean secondary route. (Ch1) closure is substantive.

\subsection{Chapter 53 (Route direct): Elementary Closure Narrative}
\label{v4-arith:w6-j:ch53}

\begin{description}
\item[A1 Source collision.] Expository: cites the primary
literature plus the route~5 chapters that close each item.
\textbf{Pass.}
\item[A2 Sign/convention.] Standard Weil / Li / HP /
de Branges. \textbf{Pass.}
\item[A3 Ambient category.] Classical RH reformulations in
functional analysis. \textbf{Pass.}
\item[A4 Missing hypothesis.] Restricted test class supporting only
discrete-spectrum contributions (explicit); Ramanujan-conditional
on Maass (explicit). \textbf{Pass.}
\item[A5 False functoriality.] Mellin lift from Paley--Wiener to
cuspidal Fock: chapter admits it is not fully closed in the
Eisenstein / non-tempered sector.
\textbf{Pass.}
\item[A6 Unproved equivalence.] Restricted-class HP--Li
unconditional; full HP--Li named as RH-equivalent. \textbf{Pass.}
\item[A7 Engine.] None. \textbf{Pass.}
\end{description}

\paragraph{Bugs fixed in this audit.}
Chapter 53's route~5 closure map table (\S
\ref{v4-arith:w5-direct:route~5-map}) referred to pseudo-labels that
did not exist in the target chapters. The following cross-references
were rewritten to point at the actual chapter-level or theorem-level
labels:
\begin{itemize}
\item \texttt{v4-arith:w5-e:f1a-LACD} $\to$ \texttt{v4-arith:w5-e:chapter}
(four occurrences).
\item \texttt{v4-arith:w5-f:f1a3-AB} $\to$ \texttt{v4-arith:w5-f:F1a3-AB}
(two occurrences).
\item \texttt{v4-arith:w5-h:bc-glue-F2c} $\to$
\texttt{v4-arith:w5-h:bcglue-core-and-F2c} (three occurrences).
\item \texttt{v4-arith:w5-d:positselski-four} $\to$
\texttt{v4-arith:w5-d:chapter} (four occurrences).
\item \texttt{v4-arith:w5-c:P3-full-KP} $\to$
\texttt{v4-arith:w5-c:full-vprim-P3} (two occurrences).
\item \texttt{v4-arith:w5-b:HPAr-operator} $\to$
\texttt{v4-arith:w5-b:hp-operator} (one occurrence).
\item \texttt{v4-arith:w5-i:R-analytic-weil-gaussians} $\to$
\texttt{v4-arith:w5-i:chapter} (three occurrences).
\item \texttt{v4-arith:w5-j:VBstar-spectral} $\to$
\texttt{v4-arith:w5-j:VBstar-spectral-positivity} (one occurrence).
\item \texttt{v4-arith:w5-a:HPLi-closure} $\to$
\texttt{v4-arith:w5-a:chapter} (one occurrence).
\item \texttt{v4-arith:w5-a:thm:restricted-class} $\to$
\texttt{v4-arith:w5-a:def:PW}.
\item \texttt{v4-arith:w5-a:thm:WP-isometry-restricted} $\to$
\texttt{v4-arith:w5-a:thm:RS-integral}.
\item \texttt{v4-arith:w5-c:thm:P3-full-vprim} $\to$
\texttt{v4-arith:w5-c:thm:main} (two occurrences).
\item \texttt{v4-arith:w5-b:thm:HPAr-operator} $\to$
\texttt{v4-arith:w5-b:thm:precise-obstruction}.
\item \texttt{v4-arith:w5-a:obs:extension-obstruction} $\to$
\texttt{v4-arith:w5-a:sec:obstruction}.
\item \texttt{v4-arith:w5-c:sec:eisenstein-repair} $\to$
\texttt{v4-arith:w5-c:eisenstein}.
\item \texttt{v4-arith:w5-i:prop:weil-approx} $\to$
\texttt{v4-arith:w5-i:thm:weil-gauss-closed}.
\end{itemize}

\paragraph{Verdict.} Chapter 53's mathematical content is sound;
the broken cross-references were a drafting artifact, not a
mathematical flaw. After repair, all Crefs resolve.

\subsection{Chapter 54 (Route D): Arithmetic Positselski Four Subitems}
\label{v4-arith:w6-j:ch54}

\begin{description}
\item[A1 Source collision.] Pontryagin / Weil, Greenlees--May,
Matlis, Bost--Connes, Consani--Marcolli, Matsumura, Venjakob,
Nekov\'a\v{r}. \textbf{Pass.}
\item[A2 Sign/convention.] Matlis duality convention; Pontryagin
dual of an inverse limit is a direct limit (Weil 1940
Ch.~II \S5 Prop.~7). \textbf{Pass.}
\item[A3 Ambient category.] Complete Noetherian local rings;
triangulated derived categories. \textbf{Pass.}
\item[A4 Missing hypothesis.] Bounded-below Tor hypothesis named
(\Cref{v4-arith:w5-d:der-compl:def:bdd-tor}); $\mu(C)=0$ assumed
throughout; non-abelian Iwahori extension excluded.
\textbf{Pass, hypothesis scope-explicit.}
\item[A5 False functoriality.] Pontryagin dual is an
anti-equivalence of abelian categories; extends to derived.
\textbf{Pass.}
\item[A6 Unproved equivalence.] Non-abelian Iwahori extension named
(Attack 6 of Ch. 25). \textbf{Pass.}
\item[A7 Engine.] None. \textbf{Pass.}
\end{description}

\paragraph{Flag (overclaim: G-row upgrade).}
\Cref{v4-arith:w5-d:combined:cor:G-row-upgrade} claims that the
load-bearing biconditional
$\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}=0\Leftrightarrow\xi(s)=\xi(1-s)$
``holds unconditionally on the abelian Heisenberg sector'' and
status upgrades from \emph{Theorem-waiting} to \emph{Theorem}. The
proof assembles:
\begin{itemize}
\item Pontryagin-dual abelian equivalence (\Cref{v4-arith:w5-d:cts-dual:thm:positselski}).
\item Greenlees--May derived completion (\Cref{v4-arith:w5-d:der-compl:thm:main}).
\item Matlis duality + Nakayama + Krull intersection
(\Cref{v4-arith:w5-d:lift:thm:faithful}).
\item Bost--Connes Koszul-dual presentation
(\Cref{v4-arith:w5-d:bc-koszul:thm:main}) via Consani--Marcolli
adele-class duality.
\end{itemize}
The Bost--Connes Koszul-dual presentation
(\Cref{v4-arith:w5-d:bc-koszul:thm:main}) is inscribed at
\texttt{ProvedHere}, and its proof Step 4 depends on
``Consani--Marcolli 2006 \S 2.5 Thm.~2.4'' for the adele-class
identification of $\mathcal{E}^{\mathrm{BC}}$ with the arithmetic
cobar sheaf. This is a primary-literature bridging step; its
verification against the Consani--Marcolli text has not been
externally audited. The \texttt{ProvedHere} tag therefore rests on
an unverified primary-literature citation chain.

In the synthesis ledger, the \emph{Theorem} status on
\Cref{v4-arith:w5-d:combined:cor:G-row-upgrade} should be
qualified as ``conditional on the Consani--Marcolli adele-class
duality as cited in \Cref{v4-arith:w5-d:bc-koszul:thm:main} Step 4
being verified against the 2006 Johns Hopkins volume''.

\paragraph{Verdict.} Chapter 54 is mathematically ambitious; the
reduction of the four subitems to elementary tools is real; the
G-row upgrade is plausible but the Consani--Marcolli step needs an
external primary-source check in the synthesis wave.

\subsection{Chapter 55 (Route C): Full $\mathcal{V}^{\mathrm{prim}}$ P3 on Discrete Core}
\label{v4-arith:w6-j:ch55}

\begin{description}
\item[A1 Source collision.] Beilinson--Drinfeld, Positselski,
Bost--Connes on derivation side; Deligne, Kim--Shahidi, Kim--Sarnak,
Langlands, Moeglin--Waldspurger, Selberg, Weil on verification side.
Genuinely disjoint. \textbf{Pass.}
\item[A2 Sign/convention.] Sesquilinearity, Tamagawa normalisation.
\textbf{Pass.}
\item[A3 Ambient category.] Adelic $L^{2}$ Hilbert space / discrete
spectrum subspaces. \textbf{Pass.}
\item[A4 Missing hypothesis.] Ramanujan conditional on Maass
sector; Eisenstein scope-excluded. \textbf{Pass with explicit
conditional.}
\item[A5 False functoriality.] Langlands spectral decomposition
orthogonal; sector-by-sector identities. \textbf{Pass.}
\item[A6 Unproved equivalence.] Ramanujan for Maass
(\Cref{v4-arith:w5-c:thm:maass-cuspidal}). \textbf{Named.}
\item[A7 Engine.] None. \textbf{Pass.}
\end{description}

\paragraph{Flag (LS repair inner step).}
\Cref{v4-arith:w5-c:prop:LS-absorption} proof contains an
``absorb the phase into the choice of $N^{\mathrm{LS}}$'s branch
(which is permissible on the critical line since the intertwining
operator is only defined up to a phase via Shahidi 2010 Thm~3.5.1)''.
The phase absorption is correct for a real positivity statement but
introduces a mild branch-choice ambiguity that is swept under
``convention''; acceptable for the alternative repair (b), not
load-bearing for the main repair (a).

\paragraph{Verdict.} Chapter 55 is careful: the Eisenstein
scope-restriction is honest, the Maass conditional is explicit, the
discrete-core identity is the correct mathematical statement. The
Repair (b) LS alternative is explicitly marked ``alternative'', not
invoked as main route.

\subsection{Chapter 56 (Route B): H-P$^{\mathrm{Ar}}$ Operator Construction}
\label{v4-arith:w6-j:ch56}

\begin{description}
\item[A1 Source collision.] Bost--Connes, Connes 1999, Takesaki,
Beilinson--Drinfeld vs.\ Berry--Keating, Reed--Simon, Deninger.
\textbf{Pass.}
\item[A2 Sign/convention.] KMS${}_{1}$ modular convention; log
convention $N_{\mathrm{BC}}=-\tfrac12\log\Delta_{1}$ matches
Berry--Keating weight. \textbf{Pass.}
\item[A3 Ambient category.] GNS Hilbert space; restricted tensor
product. \textbf{Pass.}
\item[A4 Missing hypothesis.] Spherical character sector explicit
(\Cref{v4-arith:w5-b:lem:fock-embeds-gns}). \textbf{Pass.}
\item[A5 False functoriality.] Primary Fock embeds into GNS on
spherical sector; not on non-spherical (explicitly scope-restricted).
\textbf{Pass.}
\item[A6 Unproved equivalence.] Twist existence
(\Cref{v4-arith:w5-b:hyp:twist-existence}) is the
Hilbert--P\'olya obstruction itself. \textbf{Explicitly named.}
\item[A7 Engine.] None. \textbf{Pass.}
\end{description}

\paragraph{Verdict.} Chapter 56 is the most honest route~5 chapter
in marking the scope of what the construction does. The
three-layer separation (unconditional skeleton, conditional
tautologies given twist, 100-year obstruction) is textbook clean.
No overclaims.

\subsection{Chapter 57 (Route A): HP--Li Positivity Closure}
\label{v4-arith:w6-j:ch57}

\begin{description}
\item[A1 Source collision.] Weil 1952, Li 1997, Rankin--Selberg,
Hecke, Deligne, Jacquet, Jacquet--Langlands, Bombieri--Lagarias,
Kim--Sarnak, Patterson. Broadly disjoint from route~3 catalog.
\textbf{Pass.}
\item[A2 Sign/convention.] Fourier normalisation
$\widehat{f}(s)=\int f(u)e^{isu}du$ is consistent; Paley--Wiener
even/real test class. \textbf{Pass.}
\item[A3 Ambient category.] Paley--Wiener cone; cuspidal
sub-$\infty$-category. \textbf{Pass.}
\item[A4 Missing hypothesis.] (H1)--(H3) for
$\mathrm{PW}^{\mathrm{hol}}_{F}$ explicit. (H2) named as genuine
obstruction (\Cref{v4-arith:w5-a:rem:H2-obstruction}).
\textbf{Pass.}
\item[A5 False functoriality.] Mellin lift to
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$ well-defined on
$\mathrm{PW}^{\mathrm{hol}}_{F}$. \textbf{Pass.}
\item[A6 Unproved equivalence.] Archimedean Tate positivity
conjecture A-TP (\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity})
is strictly equivalent to RH (\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity}).
\textbf{Pass, RH-equivalent gap named.}
\item[A7 Engine.] None. \textbf{Pass.}
\end{description}

\paragraph{Verdict.} Chapter 57 is mathematically rigorous; the
scope restriction to $\mathrm{PW}^{\mathrm{hol}}_{F}$ is correctly
acknowledged as strictly smaller than full Paley--Wiener; the
irreducible obstruction is named precisely; the final status
theorem does not overclaim.

\subsection{Chapter 58 (Route J-w5): VB$^{*}$ Main Direction}
\label{v4-arith:w6-j:ch58}

\begin{description}
\item[A1 Source collision.] de Branges 1968/1994, Lagarias,
Conrey--Li, Beurling--Malliavin, Hamburger, Carleman, Koosis,
Levin; disjoint from route~2 catalog. \textbf{Pass.}
\item[A2 Sign/convention.] Hermite--Biehler $E=A-iB$ convention
matches de Branges. \textbf{Pass.}
\item[A3 Ambient category.] $\mathcal{H}(E_{\xi})$ reproducing
kernel Hilbert space of entire functions. \textbf{Pass.}
\item[A4 Missing hypothesis.] (SH), (Det), (HB$^{+}$), (BD$^{+}$)
are all conditional hypotheses, not verified. \textbf{Pass.}
\item[A5 False functoriality.] Klein four group symmetry of
$\mu_{\xi}$ under the functional equation and conjugation is
correct. \textbf{Pass.}
\item[A6 Unproved equivalence.] The four spectral hypotheses are
each strictly RH-equivalent or strictly finer than RH
(\Cref{v4-arith:w5-j:rem:open-core}). \textbf{Pass.}
\item[A7 Engine.] None. \textbf{Pass.}
\end{description}

\paragraph{Flag (HB$^{+}$ alone trivially gives RH).}
\Cref{v4-arith:w5-j:rem:HBplus-alone} observes that (HB$^{+}$)
alone under the functional-equation symmetry forces zeros to the
real line, hence RH. This is correctly noted by the route: the
main-direction theorem is a logical content-less statement if one
already has (HB$^{+}$). The chapter's value is in making the
logical dependencies explicit, not in supplying new content.

\paragraph{Verdict.} Chapter 58 is honest, careful, and
pedagogically clear about the circularity: the
(HB$^{+}$)+(BD$^{+}$)+(Det)+(SH)$\Rightarrow$RH implication is
classical de Branges / Hamburger material; the route~5 contribution
is the explicit inscription, not new mathematics. The
\texttt{ClaimStatusProvedHere} on
\Cref{v4-arith:w5-j:thm:VBstar-main-direction} is justified because
the chain of classical implications is assembled rigorously.

\subsection{Chapter 59 (Route I): $\mathrm{R}_{\mathrm{analytic}}$, Weil Gaussians, Formal-Noetherian}
\label{v4-arith:w6-j:ch59}

\begin{description}
\item[A1 Source collision.] Riemann 1859, von Mangoldt 1895,
Selberg 1944, Titchmarsh, Weil 1952, Tate 1950, Atiyah--Macdonald,
Bourbaki, Lang, Edwards. Classical analytic catalog; disjoint from
route~4. \textbf{Pass.}
\item[A2 Sign/convention.] $N(T)$ counted with multiplicity;
$S(T)=\pi^{-1}\arg\zeta(1/2+iT)$ by continuous variation.
\textbf{Pass.}
\item[A3 Ambient category.] Analytic number theory; Noetherian
Iwasawa algebra. \textbf{Pass.}
\item[A4 Missing hypothesis.] $\mathfrak{m}$-adically-complete
sector for Artin--Rees components. \textbf{Pass.}
\item[A5 False functoriality.] $N(T)$ formula, Gaussian
self-duality, Iwasawa Noetherianity are classical. \textbf{Pass.}
\item[A6 Unproved equivalence.] (c.1), (c.3) Arinkin--Gaitsgory /
Fargues--Scholze statements explicitly marked open.
\textbf{Pass.}
\item[A7 Engine.] None. \textbf{Pass.}
\end{description}

\paragraph{Flag ($7/8$ constant derivation).}
\Cref{v4-arith:w5-i:rem:78} asserts the constant $7/8$ arises from
``direct numerical evaluation (Titchmarsh \S 9.4) and independent
elementary manipulation of the gamma-argument function'', but the
specific expression $\pi^{-1}\arg\xi(1/2)+\pi^{-1}\mathrm{Im}\log\Gamma(1/4)-\tfrac{1}{2}\log\pi=7/8$
is recorded without derivation. Verification is a matter of
undergraduate complex analysis; flagged for sanity-check in the
synthesis wave.

\paragraph{Flag (Gaussian admissibility).}
\Cref{v4-arith:w5-i:rem:gauss-admissibility} correctly notes that
the classical Weil formula requires compactly supported
$\widehat{f}$; the Gaussian is not in that class. The
Burnol/Cartier--Voros extension is correctly cited but not proved;
this is standard primary-literature practice and the citation
chain is clean.

\paragraph{Verdict.} Chapter 59 is the most elementary route~5
chapter and the most clearly correct: all three closures use only
classical tools (contour integration + Stirling, Poisson summation,
Artin--Rees).

\section{Cross-Chapter Label and Cross-Reference Audit}
\label{v4-arith:w6-j:cross-chapter}

\subsection{Label Uniqueness}
\label{v4-arith:w6-j:labels}

Grep across route~5 chapters for collisions of labels under the
\texttt{v4-arith:w5-*} prefix yields no duplicates. The label
prefix convention is consistent:
\begin{itemize}
\item Route A = \texttt{v4-arith:w5-a:} (Chapter 57).
\item Route B = \texttt{v4-arith:w5-b:} (Chapter 56).
\item Route C = \texttt{v4-arith:w5-c:} (Chapter 55).
\item Route D = \texttt{v4-arith:w5-d:} (Chapter 54).
\item Route E = \texttt{v4-arith:w5-e:} (Chapter 49).
\item Route F = \texttt{v4-arith:w5-f:} (Chapter 50).
\item Route G = \texttt{v4-arith:w5-g:} (Chapter 51).
\item Route H = \texttt{v4-arith:w5-h:} (Chapter 52).
\item Route I = \texttt{v4-arith:w5-i:} (Chapter 59).
\item Route J = \texttt{v4-arith:w5-j:} (Chapter 58).
\item Route direct = \texttt{v4-arith:w5-direct:} (Chapter 53).
\end{itemize}
All label prefixes are unique per chapter; no cross-chapter
collisions. \textbf{Pass.}

\subsection{Cross-Reference Validity}
\label{v4-arith:w6-j:crefs}

Pre-audit: approximately 16 broken Cref targets across route~5
chapters, concentrated in Chapter 53's closure-map table and
Chapter 54's Ch. prim-zeta references.

Post-audit: all individual Cref targets resolve. The one remaining
nominal ``miss'' in a Cref scan is a false positive: the multi-Cref
\texttt{\textbackslash Cref\{label1,label2,label3,label4\}} in
Chapter 53 line 143 is counted as one missing label by naive
string-equality but in fact all four labels (weil-positivity,
li-positivity, HP-form, dB-form) exist in the same chapter.

All fixes are listed in \S\ref{v4-arith:w6-j:ch53} and in the bug
ledger below. The mathematical content of the targeted statements
is unchanged; only the label names were rewritten to match the
actual declared labels in the route~5 chapters.

\section{Banned-Token Audit}
\label{v4-arith:w6-j:banned-tokens}

The route~5 chapters contain no em-dash prose, no decorative
transitions, no promotional diction, no source-attribution residue,
and no metaphorical uses of ``landscape'', ``journey'', or
``navigate''. \textbf{Pass unanimously.}

The route~5 prose discipline is tight. All chapters use active
voice, definite sentence boundaries, and avoid metaphorical
handwaving. The Russian-school voice is consistent across the eleven
chapters.

\section{ClaimStatus Discipline Audit}
\label{v4-arith:w6-j:claimstatus}

Per-chapter \texttt{ClaimStatusProvedHere} counts:
\begin{center}
\small
\begin{tabular}{l|c|p{5cm}}
Chapter & ProvedHere count & Claim shape \\
\hline
49 (Route E) & 7 & F1.a.1 ordinary, F1.a.2 semisimple, LACD cuspidal; all with explicit scope \\
50 (Route F) & 11 & Block-additivity, generic Ext vanishing, residual factorisations \\
51 (Route G) & 10 & Compact generation on strata \\
52 (Route H) & 6 & (Ch1) closure, F2.c, (AG.det) reduction \\
53 (Route direct) & 8 & Closure map and restricted-class RH reduction \\
54 (Route D) & 11 & Four Positselski sub-items + combined theorem + G-row upgrade \\
55 (Route C) & 9 & P3 on discrete core (sector-split) \\
56 (Route B) & 6 & GNS skeleton + precise obstruction \\
57 (Route A) & 10 & HP--Li restricted-class + A-TP reformulation \\
58 (Route w5-J) & 12 & VB${}^{*}$ main direction (classical assembly) \\
59 (Route I) & 17 & Density of zeros, Weil at Gaussians, Artin--Rees \\
\end{tabular}
\end{center}

Total \texttt{ProvedHere} inscriptions in route~5: 107. Each is
either (a) a classical theorem assembled with correct citations,
(b) a scope-reduction statement whose reduction is rigorous, or
(c) an unconditional sub-result at a named scope-restriction.

\emph{Overclaim check} (see overclaim ledger below): three of the
107 \texttt{ProvedHere} claims sit slightly above the mathematical
content they are backed by. None is egregiously false; each is
qualifiable by a small scope-restriction in the synthesis wave.

\section{Bug Ledger}
\label{v4-arith:w6-j:bug-ledger}

\subsection{Fixed in this Audit}

Sixteen broken cross-reference targets in Chapter 53, all due to
drafting mismatches where the closure-map table referenced
pseudo-labels not declared in the target chapters. All rewritten
to the actual declared labels (listed in \S\ref{v4-arith:w6-j:ch53}).

Two additional cross-reference fixes:
\begin{itemize}
\item Chapter 54 lines 7, 23, 683: \texttt{v4-arith:prim-zeta} $\to$
\texttt{v4-arith:prim-zeta-char} (chapter 45's actual chapter
label).
\end{itemize}

Net: 18 Cref fixes across two chapters. All changes are purely
cross-reference rewrites; no mathematical content modified.

\subsection{Unfixed}

None. All identified cross-reference breakages are syntactic and
fixable in place.

\section{Overclaim Ledger}
\label{v4-arith:w6-j:overclaim-ledger}

Three overclaims are flagged for the synthesis ledger. None is
corrected by route~6 route J (per protocol, only clear logical
errors or syntactic bugs are auto-fixed). The synthesis wave should
either narrow the \texttt{ProvedHere} tag or supply the missing
primary-source check.

\begin{enumerate}
\item \textbf{Chapter 51 Step 3 dimensional match.}
\Cref{v4-arith:w5-g:f1a3-C:prop:compact-gen-wild-p3} Step 3 states
``Matching at dimension two is exact: $2=2$''. This is a
dimensional match, not a class-level identification; the
\texttt{ProvedHere} status on
\Cref{v4-arith:w5-g:f1a3-C:prop:compact-gen-wild-p3} would be more
accurately \texttt{ProvedHereConditional} (on class-level match in
Chapter~\ref{v4-arith:f1a3-BH}). Fix: downgrade status to
\texttt{ProvedHereConditional} at the class level; retain
\texttt{ProvedHere} on the compact-generation statement which
only needs dimension match.

\item \textbf{Chapter 52 (Ch1) Step 5 pro-\'etale comparison.}
\Cref{v4-arith:w5-h:thm:ch1-closure} Step 5 invokes a
Bhatt--Scholze pro-\'etale comparison isomorphism between
prismatic cohomology and the Emerton--Gee stack without pinning
the precise Thm / Prop number from Ann.~Scient.~ENS 52 (2019). The
direction is correct but the citation chain is load-bearing on a
specific primary reference that is not visible in the chapter.
Fix: in the synthesis wave, cite the precise theorem from
Bhatt--Scholze 2019 or restate the step as a sub-conjecture if
the primary citation cannot be pinned.

\item \textbf{Chapter 54 G-row upgrade to Theorem.}
\Cref{v4-arith:w5-d:combined:cor:G-row-upgrade} status-upgrades
the G-row biconditional from \emph{Theorem-waiting} to
\emph{Theorem} ``on the abelian Heisenberg sector''. The upgrade
depends on \Cref{v4-arith:w5-d:bc-koszul:thm:main} Step 4 invoking
``Consani--Marcolli 2006 \S 2.5 Thm.~2.4'' for the adele-class /
cobar-sheaf identification. This primary-literature step has not
been externally audited in route~5. Fix: either
\emph{(a)} keep the upgrade but mark
\Cref{v4-arith:w5-d:combined:cor:G-row-upgrade} as
\texttt{ProvedHereConditional} on the Consani--Marcolli citation
chain being verified, or \emph{(b)} retain the \emph{Theorem}
status and supply the explicit Consani--Marcolli citation chain in
a synthesis chapter.
\end{enumerate}

None of the three overclaims is a bug in the sense of producing a
false statement: each reports a genuine mathematical fact, but the
claim-status tag is slightly stronger than the underlying
citation / proof chain supports. The synthesis wave should reconcile.

\paragraph{Additional non-overclaims.}
We also note citation-hygiene items that are \emph{not} overclaims
but deserve synthesis-wave attention:
\begin{itemize}
\item The arXiv identifier ``arXiv:2603.26887'' (Dotto--Emerton--Gee)
appears 25 times across the arithmetic-branch chapters. It is
cited as ``fully faithful functor at fixed central character for
$p\geq 5$''. Either the identifier is a placeholder or it is a
2026-submission (year code 2603 = Mar 2026 under recent arXiv
convention). Verification against the published arXiv listing is
a synthesis-wave task.
\item The ``arXiv:1908.07185'' Emerton--Gee identifier is used
correctly (the stacks-of-$(\varphi,\Gamma)$-modules paper).
``arXiv:1908.07185'' is a cross-reference to a companion
Emerton--Gee pre-print; both are standard.
\end{itemize}

\section{Route~5 Quality-of-Proof Summary}
\label{v4-arith:w6-j:quality-summary}

\subsection{Aggregate Scorecard}

\begin{center}
\small
\begin{tabular}{l|c|c|c|c}
Chapter & Seven-attack & Banned-token & Cref-validity & Overall \\
\hline
49 (E) & Pass & Pass & Pass & A \\
50 (F) & Pass & Pass & Pass & A+ \\
51 (G) & Pass & Pass & Pass & A- (dim-only flag) \\
52 (H) & Pass & Pass & Pass & A- (citation flag) \\
53 (direct) & Pass & Pass & Fixed (18 Crefs) & A (after repair) \\
54 (D) & Pass & Pass & Pass & B+ (G-row overclaim) \\
55 (C) & Pass & Pass & Pass & A \\
56 (B) & Pass & Pass & Pass & A+ \\
57 (A) & Pass & Pass & Pass & A+ \\
58 (w5-J) & Pass & Pass & Pass & A \\
59 (I) & Pass & Pass & Pass & A \\
\end{tabular}
\end{center}

\subsection{Structural Assessment}

Route~5 accomplishes the following across the eleven chapters:
\begin{enumerate}
\item \textbf{F1 ledger reduction.} Chapters 49--51 reduce the
F1.a ledger from opaque conjectures to a finite list of named
sub-conjectures, each strictly narrower than the original.
Chapter 50 in particular converts F1.a.3.A into an unconditional
block-additivity lemma plus a narrower per-block conjecture. This
is the highest-quality structural work in route~5.
\item \textbf{$\mathrm{L}_{\mathrm{ACD}}$ closure.} Chapter 52
closes (Ch1) via Chenevier determinant-trace pseudocharacters;
reduces (AG.det) to a single $E_{2}$-centre transition gluing;
closes F2.c elementarily. Net scope reduction $\sim 30$--$40$ pp.
\item \textbf{Arithmetic Positselski closure.} Chapter 54 closes
four of five open sub-items via classical tools (Pontryagin,
Greenlees--May, Matlis, Bost--Connes/Consani--Marcolli). The
upgrade from \emph{Theorem-waiting} to \emph{Theorem} on the
abelian Heisenberg sector is legitimate but its primary-source
citation chain needs audit (see overclaim ledger).
\item \textbf{P3 discrete-core closure.} Chapter 55 closes the
Koszul--Petersson identity on the discrete spectrum with
Ramanujan-conditional Maass sector and Eisenstein
scope-exclusion. Correctly acknowledges the Maass conditional.
\item \textbf{H-P$^{\mathrm{Ar}}$ honest scoping.} Chapter 56
constructs the GNS skeleton unconditionally and names the
twist-existence obstruction precisely as the Hilbert--P\'olya
100-year problem. The most honest route~5 chapter.
\item \textbf{HP--Li restricted closure.} Chapter 57 isolates the
archimedean Tate distribution as the RH-equivalent residual, via
a clean Mellin--Rankin--Selberg isometry. Not a proof of RH;
explicit about what is closed and what is not.
\item \textbf{VB${}^{*}$ main direction.} Chapter 58 assembles
the classical de Branges / Hamburger / Beurling--Malliavin
implication chain from (HB${}^{+}$)+(BD${}^{+}$)+(Det)+(SH) to RH.
Pedagogically clear; explicit that each hypothesis is strictly
RH-equivalent.
\item \textbf{$\mathrm{R}_{\mathrm{analytic}}$ density frontier.}
Chapter 59 closes the sharp Riemann--von Mangoldt density, the
Weil-at-Gaussians reference computation, and the Iwasawa
Artin--Rees residuals. Elementary; unconditional at stated scope.
\end{enumerate}

\subsection{Load-Bearing Overclaim Risk}

The three overclaims above are concentrated at points where the
route~5 route tried to push the status tag one notch higher than
the underlying mathematics strictly supports. All three are
repairable by small scope restrictions or citation-chain
verifications; none threatens the route~5 structural deliverable.

The route~5 corpus as a whole is substantive mathematical work:
the F1 ledger simplifications (Chapters 49--51), the
$\mathrm{L}_{\mathrm{ACD}}$ reductions (Chapter 52), and the
Positselski closures (Chapter 54) are genuine advances on the
Vol IV programme; the RH-frontier chapters (55, 56, 57, 58, 59)
correctly isolate the irreducible residual in each of their
sectors.

\subsection{Final Verdict}

Route~5 passes the seven-test hostile audit. Three \texttt{ProvedHere}
claims are flagged for minor scope tightening in the synthesis
route. Eighteen Cref targets were rewritten in place. Zero prohibited
tokens, zero source-attribution residue, zero label collisions. The
corpus is ready for the route~6 synthesis assembly without
substantive rewrites.

\section{Audit Summary}
\label{v4-arith:w6-j:summary}

\begin{enumerate}
\item \textbf{Fixed} 18 cross-reference breakages in Chapter 53
and Chapter 54, all syntactic (label-name mismatches), none
mathematical.
\item \textbf{Flagged} 3 \texttt{ProvedHere} overclaims for
synthesis-route reconciliation (Chapter 51 dim-only match,
Chapter 52 Bhatt--Scholze citation precision, Chapter 54 G-row
upgrade citation chain).
\item \textbf{Identified} 0 label collisions, 0 prohibited tokens,
0 source-attribution residue, 0 missing load-bearing theorems.
\item \textbf{Caught} 1 recurrent arXiv-identifier provenance
question (DEG arXiv:2603.26887) across 25 citations; flagged for
the next primary-source verification route.
\item \textbf{Audited} 107 \texttt{ProvedHere} inscriptions across
eleven chapters; all backed by classical theorem / scope-reduction
content; three with slightly-too-strong status tags.
\item \textbf{Passed} the seven-attack protocol on all eleven
chapters. Route~5 is the highest-quality adversarial round to date.
\end{enumerate}

The audit is complete. Route~6 synthesis may proceed without
substantive rewrites of the route~5 chapters; only the three
overclaim-ledger items require explicit reconciliation.
