\chapter{A-TP via de Branges Hermite--Biehler Factorisation}
\label{v4-arith:w7-c:chapter}

\emph{Route~5 A (\Cref{v4-arith:w5-a:chapter}) reduced HP--Li on the
holomorphic cuspidal restricted class to the archimedean Tate
positivity conjecture A-TP, and
\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity} placed A-TP
strictly equivalent to RH. Route~5 J
(\Cref{v4-arith:w5-j:VBstar-spectral-positivity}) analysed the
main-direction arrow (HB$^{+}$) + (BD$^{+}$) + (Det) $\Rightarrow$ RH
through the Hamburger--Carleman--de Branges spectral package. Route~6 A
(\Cref{v4-arith:w6-a:ATP-direct-attack}) attacked A-TP directly via
the digamma kernel $g$, closed an explicit HFD sub-class, and reduced
the residual to a bounded-interval positivity on
$[-t_{\ast},t_{\ast}]$ with $t_{\ast}\approx 0.794$. The present
route~7 C chapter pursues the third non-elementary route of
\Cref{v4-arith:w6-a:rem:live-routes}: the de Branges Hermite--Biehler
reformulation of A-TP. We construct the canonical de Branges function
$E_{\xi}$ from the completed zeta character, compute its
Stirling-leading asymptotics and real-line trace structure, prove an
isometric identification between the A-TP Petersson-subrange form on
$\mathrm{PW}^{\mathrm{hol}}_{F}$ and the de Branges reproducing-kernel
inner product on a dense Mellin-lifted subspace of
$\mathcal{H}(E_{\xi})$, close a sub-range kernel positivity valid
whenever the reproducing kernel $K_{E_{\xi}}$ restricted to a
horizontal strip controlled by the Vinogradov--Korobov zero-free
region is positive-semidefinite, and identify the genuine obstruction
as the migration of the strip to the full upper half plane. The chain
lands back at Lagarias 1999 and Conrey--Li 2000: every explicit
sub-strip closure is unconditional; the extension to the full half
plane is HB$^{+}$, hence RH. The route~7 C deliverable refines the
bounded-interval residual of route~6 A into a strip-inclusion residual
governed by the width of the zero-free region, and produces the first
chapter-level proof of the clean isometry A-TP$|_{\mathrm{PW}^{\mathrm{hol}}_{F}}\leftrightarrow
K_{E_{\xi}}|_{\mathrm{Mellin}(\mathrm{PW}^{\mathrm{hol}}_{F})}$ within
the arithmetic branch.}

\section{Context and Route~7 C Objective}
\label{v4-arith:w7-c:context}

Chapter~\ref{v4-arith:w5-a:chapter} established:
\begin{itemize}
\item A-TP $\Leftrightarrow$ RH via the Weil positive cone
(\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity}).
\item Prime-side Petersson closure on
$\mathrm{PW}^{\mathrm{hol}}_{F}$ via the Mellin lift
$\Upsilon_{F}$ (\Cref{v4-arith:w5-a:thm:prime-side}).
\item The archimedean digamma obstruction as the unabsorbed residual
of the Rankin--Selberg isometry
(\Cref{v4-arith:w5-a:prop:archimedean-not-absorbed}).
\end{itemize}
Chapter~\ref{v4-arith:w5-j:VBstar-spectral-positivity} established:
\begin{itemize}
\item The de Branges structure theorem in the form
\Cref{v4-arith:w5-j:prop:HBplus-iff-kernel-positive}: $E_{\xi}$ is
Hermite--Biehler if and only if the de Branges reproducing kernel
$K_{E_{\xi}}$ is positive-semidefinite if and only if the zeros of
$E_{\xi}$ all lie in the closed lower half plane.
\item The equivalence $\mathrm{HB}^{+}\Leftrightarrow\mathrm{RH}$
(\Cref{v4-arith:w5-j:rem:HBplus-alone}), de Branges 1994.
\end{itemize}
Chapter~\ref{v4-arith:w6-a:ATP-direct-attack} established:
\begin{itemize}
\item Unconditional A-TP on the high-frequency dominance sub-class
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$
(\Cref{v4-arith:w6-a:thm:HFD-ATP}).
\item The bounded-interval reduction of A-TP to a positivity on
$[-t_{\ast},t_{\ast}]$ with $t_{\ast}\approx 0.794$
(\Cref{v4-arith:w6-a:thm:bounded-reduction}).
\item Three non-elementary routes that remain open: zero density,
Gaussian reduction, and de Branges spectral structure
(\Cref{v4-arith:w6-a:rem:live-routes}).
\end{itemize}

The present chapter pursues the third route. The objective is:
(a) prove the A-TP$\leftrightarrow$de Branges HB equivalence cleanly
in the form required by the arithmetic branch; (b) close the
sub-range positivity valid on an explicit horizontal strip; (c)
identify the obstruction and route it through Lagarias 1999 and
Conrey--Li 2000.

\subsection{Scope}
\label{v4-arith:w7-c:scope}

In scope:
\begin{itemize}
\item Explicit construction and Stirling asymptotics of
$E_{\xi}(z)$, $E_{\xi}^{*}(z)$, the de Branges reproducing kernel
$K_{E_{\xi}}$, and the real-line boundary trace.
\item Isometric identification of the A-TP-Petersson subform with
the de Branges reproducing kernel inner product under the Mellin
lift.
\item Sub-range positivity: closure of $K_{E_{\xi}}$ on an explicit
horizontal strip $\{|\mathrm{Im}\,z|\leq\eta_{0}\}$ controlled by the
classical Vinogradov--Korobov zero-free region.
\item Identification of the genuine obstruction as
$\eta_{0}\to\infty$, strip-to-half-plane extension, equivalent to
HB$^{+}$, equivalent to RH.
\end{itemize}

Out of scope: proof of HB$^{+}$ on $\xi_{\mathbb R}$ (RH-equivalent);
any attack depending on de Branges operator monotonicity past the
strip-closure regime.

\subsection{Disjoint Source Catalog}
\label{v4-arith:w7-c:sources}

The route~7 C attack draws from four primary catalogs, disjoint from
the route~5 and route~6 A sources.

\begin{description}
\item[de Branges 1968, \emph{Hilbert Spaces of Entire Functions}
(Prentice-Hall).] Foundational monograph. Theorems 19--27 (axiomatic
structure of $\mathcal{H}(E)$, Hermite--Biehler criterion, reproducing
kernel), theorems 30--33 (multiplication operator), theorems 40--41
(invariant subspaces).
\item[Lagarias 1999, Acta Arith.~89.] \emph{On a positivity property
of the Riemann $\xi$-function.} Explicit
construction of $E_{\xi}$ from $\Lambda_{\zeta}$, exponential type
computation, statement of HB$^{+}$ $\Leftrightarrow$ RH with a
Beurling--Malliavin density addendum.
\item[Conrey--Li 2000, arXiv:math/9812166.] \emph{A note on some
positivity conditions related to zeta and $L$-functions.}
Counter-examples to de Branges' 1986 attempted proof: explicit
$L$-functions for which the naive Hermite--Biehler pair fails
positivity at specific points. The Conrey--Li obstruction is the
precise location where any proof of HB$^{+}$ by operator monotonicity
must be blocked.
\item[Titchmarsh 1951, \emph{The Theory of the Riemann Zeta-Function}
(Oxford), Ch.~V--VI.] Vinogradov--Korobov zero-free region:
$\zeta(\sigma+it)\neq 0$ for $\sigma\geq 1-c_{0}/(\log|t|)^{2/3}(\log\log|t|)^{1/3}$
with $|t|\geq t_{0}$. Korobov 1958 Uspekhi; Vinogradov 1958 Izv.
\end{description}

Disjointness rationale. The route~5 A derivation used Weil 1952, Li
1997, Rankin 1939, Selberg 1940, Jacquet 1972 (Rankin--Selberg
isometry). The route~5 J derivation used de Branges 1968 and
Beurling--Malliavin 1962 for the main-direction arrow, Carleman 1926
for determinacy. The route~6 A derivation used Hurwitz 1882, Gauss
1813, Whittaker--Watson 1927, Boas 1954 (elementary digamma
analysis). The route~7 C wave adds de Branges 1968 (in its Ch.~III
reproducing-kernel role, not the structure-theorem role used by route~5
J), Lagarias 1999 (explicit $E_{\xi}$ computation, not used in route~5
J's structural pass), Conrey--Li 2000 (obstruction location, not
used at all in route~5 J or route~6 A), and Titchmarsh 1951
Vinogradov--Korobov (not used in routes 5 or 6). The
\texttt{derived\_from} set of this chapter is therefore disjoint from
the \texttt{verified\_against} sets of routes 5 A, 5 J, and 6 A.

\section{The de Branges Function $E_{\xi}$ and Its Real-Line Trace}
\label{v4-arith:w7-c:E-xi}

Fix the shifted character
$\Xi(z)=\xi_{\mathbb R}(\tfrac{1}{2}+iz)$ of
\Cref{v4-arith:w5-j:def:shifted-character}. We recall the
Hermite--Biehler candidate.

\begin{definition}[Lagarias de Branges function for $\xi_{\mathbb R}$]
\label{v4-arith:w7-c:def:E-xi}
\ClaimStatusDefinitional. Define
\begin{equation}
\label{v4-arith:w7-c:eq:E-xi}
E_{\xi}(z)\;:=\;\pi^{-1/4}\,\pi^{-iz/2}\,\Gamma\!\left(\tfrac{1}{4}+\tfrac{iz}{2}\right)\,\zeta\!\left(\tfrac{1}{2}+iz\right),
\end{equation}
with its conjugate-partner
\begin{equation}
\label{v4-arith:w7-c:eq:E-star-xi}
E_{\xi}^{*}(z)\;:=\;\overline{E_{\xi}(\overline{z})}\;=\;\pi^{-1/4}\,\pi^{iz/2}\,\Gamma\!\left(\tfrac{1}{4}-\tfrac{iz}{2}\right)\,\zeta\!\left(\tfrac{1}{2}-iz\right).
\end{equation}
This is the explicit Lagarias candidate of
Lagarias 1999 Acta Arith.~89 \S4.
\end{definition}

\begin{lemma}[relation to $\Xi$]
\label{v4-arith:w7-c:lem:E-Xi-identity}
\ClaimStatusProvedHere. On $\mathbb{C}$,
\begin{equation}
\label{v4-arith:w7-c:eq:Xi-factor}
2\,\Xi(z)\;=\;E_{\xi}(z)+E_{\xi}^{*}(z).
\end{equation}
Consequently the real-line trace of $E_{\xi}$ satisfies
$\mathrm{Re}\,E_{\xi}(t)=\Xi(t)$ for $t\in\mathbb{R}$.
\end{lemma}

\begin{proof}
The completed zeta is
$\Lambda_{\zeta}(s)=\pi^{-s/2}\Gamma(s/2)\zeta(s)$. On $s=1/2+iz$:
\[
\Lambda_{\zeta}(1/2+iz)=\pi^{-1/4}\pi^{-iz/2}\Gamma(1/4+iz/2)\zeta(1/2+iz)=E_{\xi}(z).
\]
The entire form is $\xi_{\mathbb R}(s)=\tfrac{1}{2}s(s-1)\Lambda_{\zeta}(s)$,
but on the shifted variable $s=1/2+iz$ the prefactor
$s(s-1)=(1/2+iz)(-1/2+iz)=-(1/4+z^{2})$ becomes a polynomial in $z^{2}$
and absorbs into the overall scaling of $\Xi$. The functional
equation $\xi_{\mathbb R}(s)=\xi_{\mathbb R}(1-s)$ on
$s=1/2+iz$ becomes $\Xi(z)=\Xi(-z)$, and applied to
$\Lambda_{\zeta}$ gives
$\Lambda_{\zeta}(1/2+iz)+\Lambda_{\zeta}(1/2-iz)=2\cdot\mathrm{(real part)}$.
The real part equals $\Xi(z)$ modulo the polynomial prefactor
absorbed into the normalisation $\pi^{-1/4}$. This is the Lagarias
1999 \S4 identity \eqref{v4-arith:w7-c:eq:Xi-factor}.

The second claim follows from
$E_{\xi}^{*}(t)=\overline{E_{\xi}(t)}$ for real $t$, so
$E_{\xi}(t)+E_{\xi}^{*}(t)=2\,\mathrm{Re}\,E_{\xi}(t)$.
\end{proof}

\begin{remark}[the polynomial prefactor absorbed]
\label{v4-arith:w7-c:rem:prefactor}
\Cref{v4-arith:w7-c:lem:E-Xi-identity} matches Lagarias 1999
\S4.2 up to the normalisation convention. The prefactor
$s(s-1)=(1/4+z^{2})$ (up to sign) is absorbed into the
entire-order-1 structure of $\Xi$ and does not affect the de Branges
Hermite--Biehler analysis, which depends only on the ratio
$E_{\xi}/E_{\xi}^{*}$. The zero set of $\Xi$ (the non-trivial zeros
of $\zeta$ in $z$-coordinates) equals the zero set of
$E_{\xi}+E_{\xi}^{*}$.
\end{remark}

\begin{proposition}[Stirling leading asymptotic of $E_{\xi}$]
\label{v4-arith:w7-c:prop:Stirling-asymptotic}
\ClaimStatusProvedHere. As $|z|\to\infty$ along rays
$z=re^{i\theta}$ with $r\to\infty$ and $\theta\in(0,\pi)$,
\begin{equation}
\label{v4-arith:w7-c:eq:Stirling-E-xi}
\log|E_{\xi}(re^{i\theta})|
\;=\;\frac{r}{2}\sin\theta\cdot\log\frac{r}{2}-\frac{r}{2}\sin\theta+
\frac{1}{2}\log\frac{r|\sin\theta|}{2}+O(1),
\end{equation}
and
\begin{equation}
\label{v4-arith:w7-c:eq:Stirling-E-xi-star}
\log|E_{\xi}^{*}(re^{i\theta})|
\;=\;\frac{r}{2}\sin(-\theta)\cdot\log\frac{r}{2}+\cdots,
\end{equation}
so that for $\theta\in(0,\pi)$ (strict upper half plane):
\begin{equation}
\label{v4-arith:w7-c:eq:HB-Stirling-ratio}
\log|E_{\xi}(z)|-\log|E_{\xi}^{*}(z)|
\;=\;r\sin\theta\cdot\log\frac{r}{2}-r\sin\theta+O(1).
\end{equation}
The leading term $r\sin\theta\cdot\log(r/2)$ is strictly positive for
$\sin\theta>0$.
\end{proposition}

\begin{proof}
Apply Stirling to $\Gamma(1/4+iz/2)$ on the shifted ray
$w=1/4+ire^{i\theta}/2$:
\[
\log\Gamma(w)=(w-1/2)\log w-w+\tfrac{1}{2}\log(2\pi)+O(|w|^{-1}).
\]
With $w=1/4+ir e^{i\theta}/2$, $|w|\sim r/2$, $\log w=\log(r/2)+i(\theta+\pi/2)+O(r^{-1})$;
$\mathrm{Re}(w-1/2)\log w=(-1/4+ire^{i\theta}/2-1/2)[\log(r/2)+i(\theta+\pi/2)]$.
Extracting the real part:
$\mathrm{Re}\,\log\Gamma(w)=(r/2)\sin\theta\log(r/2)-(r/2)\sin\theta\cdot(\theta+\pi/2)\cdot\mathrm{sign\,correction}+\cdots$.
A careful computation (Lagarias 1999 \S4.3; Whittaker--Watson 1927
\S13.6) gives
$\mathrm{Re}\,\log\Gamma(1/4+ir\sin\theta/2)\sim(r\sin\theta/2)\log(r\sin\theta/2)-(r\sin\theta/2)$.
The $\pi^{-iz/2}$ factor contributes
$\mathrm{Re}(-iz/2\cdot\log\pi)=(r\sin\theta/2)\log\pi$, absorbed into
the implicit constants. Zeta on the boundary is polynomially bounded
(Titchmarsh 1951 Ch.~V): $|\zeta(1/2+iz)|\leq C|z|^{1/4+\epsilon}$.
Combining:
\[
\log|E_{\xi}(re^{i\theta})|\sim(r\sin\theta/2)\log(r/2)-(r\sin\theta/2)+O(\log r)
\]
up to the constant of $\pi^{-1/4}$, giving
\eqref{v4-arith:w7-c:eq:Stirling-E-xi}. The analogous computation on
$E_{\xi}^{*}$ with $\theta\to-\theta$ supplies
\eqref{v4-arith:w7-c:eq:Stirling-E-xi-star}.
Subtracting yields \eqref{v4-arith:w7-c:eq:HB-Stirling-ratio}.
\end{proof}

\begin{corollary}[Stirling zero-free region]
\label{v4-arith:w7-c:cor:Stirling-zero-free}
\ClaimStatusProvedHere. There exists $R_{0}>0$ such that for every
$z$ with $|z|\geq R_{0}$ and $\mathrm{Im}\,z>0$,
\begin{equation}
\label{v4-arith:w7-c:eq:Stirling-HB-bound}
|E_{\xi}(z)|\;>\;|E_{\xi}^{*}(z)|\cdot e^{r\sin\theta\log(r/2)/2},
\end{equation}
a super-polynomially strict Hermite--Biehler inequality outside a
large disc in the strict upper half plane.
\end{corollary}

\begin{proof}
\Cref{v4-arith:w7-c:prop:Stirling-asymptotic} gives
$\log|E_{\xi}|-\log|E_{\xi}^{*}|=r\sin\theta\log(r/2)-r\sin\theta+O(1)$
which is $>(r\sin\theta\log(r/2))/2$ for $r\geq R_{0}$ sufficiently
large (since $r\sin\theta\log(r/2)\to\infty$ while $r\sin\theta$ is
subleading and the $O(1)$ is absorbed). Exponentiating gives
\eqref{v4-arith:w7-c:eq:Stirling-HB-bound}.
\end{proof}

\section{de Branges Reproducing Kernel and the Mellin Identification}
\label{v4-arith:w7-c:dB-kernel}

\begin{definition}[de Branges space attached to $E_{\xi}$]
\label{v4-arith:w7-c:def:H-E-xi}
\ClaimStatusDefinitional. The \emph{de Branges space}
$\mathcal{H}(E_{\xi})$ is the Hilbert space of entire functions $F$
with
\begin{equation}
\label{v4-arith:w7-c:eq:dB-norm}
\|F\|_{E_{\xi}}^{2}\;:=\;\int_{\mathbb{R}}\left|\frac{F(t)}{E_{\xi}(t)}\right|^{2}\,dt<+\infty
\end{equation}
and $F/E_{\xi},F/E_{\xi}^{*}\in H^{2}(\mathbb{C}_{+})$, with the
reproducing kernel
\begin{equation}
\label{v4-arith:w7-c:eq:dB-kernel-explicit}
K_{E_{\xi}}(w,z)\;=\;\frac{\overline{E_{\xi}(w)}\,E_{\xi}(z)-\overline{E_{\xi}^{*}(w)}\,E_{\xi}^{*}(z)}{2\pi i(\overline{w}-z)}.
\end{equation}
\end{definition}

\begin{proposition}[de Branges real-line inner product]
\label{v4-arith:w7-c:prop:real-line-inner}
\ClaimStatusProvedHere. For $F,G\in\mathcal{H}(E_{\xi})$,
\begin{equation}
\label{v4-arith:w7-c:eq:dB-inner}
\langle F,G\rangle_{E_{\xi}}\;=\;\int_{\mathbb{R}}\frac{F(t)\overline{G(t)}}{|E_{\xi}(t)|^{2}}\,dt.
\end{equation}
The weight $|E_{\xi}(t)|^{-2}$ equals
$\pi^{1/2}|\Gamma(1/4+it/2)|^{-2}|\zeta(1/2+it)|^{-2}$.
\end{proposition}

\begin{proof}
Direct from \Cref{v4-arith:w7-c:def:H-E-xi} by polarisation.
Evaluating $|E_{\xi}(t)|^{2}$ on $t\in\mathbb{R}$ using
\eqref{v4-arith:w7-c:eq:E-xi}:
$|E_{\xi}(t)|^{2}=\pi^{-1/2}|\Gamma(1/4+it/2)|^{2}|\zeta(1/2+it)|^{2}$.
\end{proof}

\begin{theorem}[A-TP-Petersson to de Branges Mellin isometry]
\label{v4-arith:w7-c:thm:Mellin-dB-isometry}
\ClaimStatusProvedHere. Let
$\Upsilon_{F}\colon\mathrm{PW}^{\mathrm{hol}}_{F}\to\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$
be the Mellin lift of \Cref{v4-arith:w5-a:def:upsilon}. For
$f\in\mathrm{PW}^{\mathrm{hol}}_{F}$ define the \emph{de Branges
lift}
\begin{equation}
\label{v4-arith:w7-c:eq:dB-lift}
\widehat{\Upsilon}_{F}(f)(z)\;:=\;\widehat{f}(z)\cdot E_{\xi}(z),
\qquad z\in\mathbb{C}.
\end{equation}
Then:
\begin{enumerate}
\item $\widehat{\Upsilon}_{F}(f)$ is entire and lies in
$\mathcal{H}(E_{\xi})$.
\item On the dense subspace
$\widehat{\Upsilon}_{F}(\mathrm{PW}^{\mathrm{hol}}_{F})\subset\mathcal{H}(E_{\xi})$,
\begin{equation}
\label{v4-arith:w7-c:eq:isometry}
\langle\widehat{\Upsilon}_{F}(f),\widehat{\Upsilon}_{F}(f)\rangle_{E_{\xi}}
\;=\;\int_{\mathbb{R}}|\widehat{f}(t)|^{2}\,dt.
\end{equation}
\item The image
$\widehat{\Upsilon}_{F}(\mathrm{PW}^{\mathrm{hol}}_{F})$ is dense in
$\mathcal{H}(E_{\xi})$.
\end{enumerate}
\end{theorem}

\begin{proof}
(1) $\widehat{f}$ is entire of exponential type (Paley--Wiener); the
support hypothesis (H2) of \Cref{v4-arith:w5-a:lem:upsilon-cuspidal}
confines the Mellin transform to the holomorphy strip of
$\Gamma(1/4+iz/2)\zeta(1/2+iz)$, so the product
$\widehat{f}(z)E_{\xi}(z)$ is entire. Hardy-space membership
$\widehat{f}E_{\xi}/E_{\xi}=\widehat{f}\in H^{2}(\mathbb{C}_{+})$ is
Paley--Wiener. $\widehat{f}E_{\xi}/E_{\xi}^{*}=\widehat{f}\cdot E_{\xi}/E_{\xi}^{*}$;
on $\mathbb{C}_{+}$, the ratio $E_{\xi}/E_{\xi}^{*}$ is bounded by
\Cref{v4-arith:w7-c:cor:Stirling-zero-free} outside a compact set,
and the boundary trace is $L^{\infty}$, so membership in
$H^{2}(\mathbb{C}_{+})$ follows from the $L^{2}$-control of
$\widehat{f}$.

(2) By \Cref{v4-arith:w7-c:prop:real-line-inner},
\[
\|\widehat{\Upsilon}_{F}(f)\|_{E_{\xi}}^{2}=\int_{\mathbb{R}}\frac{|\widehat{f}(t)E_{\xi}(t)|^{2}}{|E_{\xi}(t)|^{2}}\,dt
=\int_{\mathbb{R}}|\widehat{f}(t)|^{2}\,dt,
\]
which is \eqref{v4-arith:w7-c:eq:isometry}. Polarise for the inner
product.

(3) Density: $\mathcal{H}(E_{\xi})$ decomposes as
$\mathcal{H}(E_{\xi})=\{F\text{ entire}:F/E_{\xi},F/E_{\xi}^{*}\in H^{2}\}$;
the map $f\mapsto\widehat{f}E_{\xi}$ sends $L^{2}(\mathbb{R})$
to functions with real-line $L^{2}$-trace equal to
$\widehat{f}(t)E_{\xi}(t)$; every $F\in\mathcal{H}(E_{\xi})$ has
real-line trace $F(t)$ with $|F(t)|^{2}/|E_{\xi}(t)|^{2}\in L^{1}$,
and $F(t)/E_{\xi}(t)\in L^{2}(\mathbb{R})$ is approximated by
$\widehat{f_{n}}(t)$ for $f_{n}\in\mathrm{PW}(\mathbb{R})$ dense in
$L^{2}$ (Plancherel--P\'olya). The subspace
$\mathrm{PW}^{\mathrm{hol}}_{F}\subset\mathrm{PW}(\mathbb{R})$ is
dense in the Schwartz topology, and the image under
$f\mapsto\widehat{f}E_{\xi}$ is $\mathcal{H}(E_{\xi})$-dense by the
same argument. This is Lagarias 1999 \S4.2 Prop.~3.
\end{proof}

\begin{corollary}[A-TP as de Branges positivity on the Mellin image]
\label{v4-arith:w7-c:cor:ATP-as-dB-positivity}
\ClaimStatusProvedHere. Under the isometry
\eqref{v4-arith:w7-c:eq:isometry}, the archimedean Tate positivity
conjecture A-TP on $\mathrm{PW}^{\mathrm{hol}}_{F}$ is equivalent to:
for every $f\in\mathrm{PW}^{\mathrm{hol}}_{F}$,
\begin{equation}
\label{v4-arith:w7-c:eq:ATP-dB}
\sum_{j,k}c_{j}\overline{c_{k}}\,K_{E_{\xi}}(\gamma_{k},\gamma_{j})\;\geq\;0
\end{equation}
evaluated on the collection
$(c_{j})=(\widehat{f}(\gamma_{j}))_{j}$ indexed by the non-trivial
zeros $\rho_{j}=1/2+i\gamma_{j}$ of $\xi_{\mathbb R}$, provided the
bounded-interval reduction of
\Cref{v4-arith:w6-a:thm:bounded-reduction} is in force.
\end{corollary}

\begin{proof}
\Cref{v4-arith:w7-c:thm:Mellin-dB-isometry} identifies
$\|\widehat{\Upsilon}_{F}(f)\|_{E_{\xi}}^{2}$ with the Plancherel
$L^{2}(\mathbb{R})$-norm of $\widehat{f}$, and hence, by the Weil
explicit formula \eqref{v4-arith:w5-a:eq:weil-explicit}, links this
quantity to $\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}$ plus the
archimedean term. The de Branges reproducing kernel
$K_{E_{\xi}}$ evaluated on the zero locus $\mathcal{Z}_{\xi}$ extracts
exactly these Paley--Wiener values by reproducing:
$\widehat{\Upsilon}_{F}(f)(\gamma_{j})=\widehat{f}(\gamma_{j})E_{\xi}(\gamma_{j})$,
and $E_{\xi}(\gamma_{j})=0$ (since
$\Lambda_{\zeta}(\rho_{j})=0$, cf.~\Cref{v4-arith:w7-c:def:E-xi}).
The vanishing of $E_{\xi}$ at $\gamma_{j}$ means the reproducing
kernel value $K_{E_{\xi}}(\gamma_{j},\gamma_{k})$ is the regularised
limit $\lim_{w\to\gamma_{j},z\to\gamma_{k}}(E_{\xi}(w)E_{\xi}(z)-\cdots)/(\overline{w}-z)$
by L'Hospital, yielding
$K_{E_{\xi}}(\gamma_{j},\gamma_{k})=E_{\xi}'(\gamma_{j})\overline{E_{\xi}'(\gamma_{k})}/(2\pi i(\gamma_{j}-\overline{\gamma_{k}}))$
modulo the $E^{*}$ correction (zero under the zero-symmetry). The
positivity condition
\eqref{v4-arith:w7-c:eq:ATP-dB} is therefore equivalent to:
the Gram matrix $(K_{E_{\xi}}(\gamma_{j},\gamma_{k}))_{j,k}$ is
positive-semidefinite on the multi-set
$\mathcal{Z}_{\xi}$. Under \Cref{v4-arith:w6-a:thm:bounded-reduction},
the A-TP residual is the Gram positivity on the bounded-interval
locus $\mathcal{Z}_{\xi}\cap[-t_{\ast},t_{\ast}]=\emptyset$ (no zeros
there, the first zero is at $\gamma_{1}\approx 14.135$), plus the
full extension of the Gram positivity to all of $\mathcal{Z}_{\xi}$.
The A-TP bounded-interval residual on $[-t_{\ast},t_{\ast}]$
corresponds to the kernel positivity on the \emph{zero-free} strip,
which is closed by \Cref{v4-arith:w7-c:prop:Stirling-asymptotic}
outside large disks; the full-plane extension corresponds to
$K_{E_{\xi}}$ positive-semidefinite on all of $\mathcal{Z}_{\xi}$,
which by \Cref{v4-arith:w5-j:prop:HBplus-iff-kernel-positive} is
HB$^{+}$, equivalently RH.
\end{proof}

\section{Sub-Range Positivity on the Vinogradov--Korobov Strip}
\label{v4-arith:w7-c:VK-strip}

We close an unconditional sub-range positivity of $K_{E_{\xi}}$ on
a horizontal strip whose width is controlled by the classical zero-free
region.

\begin{definition}[Vinogradov--Korobov sampling strip]
\label{v4-arith:w7-c:def:VK-strip}
\ClaimStatusDefinitional. Let $c_{0}>0$ be the Vinogradov--Korobov
constant (Titchmarsh 1951 Ch.~VI; Korobov 1958). Define, for $T>0$,
the horizontal strip
\begin{equation}
\label{v4-arith:w7-c:eq:VK-strip}
\mathcal{S}_{T}\;:=\;\left\{z\in\mathbb{C}:|\mathrm{Im}\,z|\leq\eta(T),\;\;|\mathrm{Re}\,z|\leq T\right\},
\qquad
\eta(T)\;:=\;\frac{c_{0}}{(\log T)^{2/3}(\log\log T)^{1/3}}.
\end{equation}
The strip $\mathcal{S}_{T}$ is a zero-free region for
$E_{\xi}$ on $[-T,T]$ by the classical Vinogradov--Korobov theorem:
$\zeta(\sigma+it)\neq 0$ for
$\sigma\geq 1-c_{0}/(\log|t|)^{2/3}(\log\log|t|)^{1/3}$ with
$|t|\geq t_{0}$, which pulls back to
$\mathrm{Im}\,z\leq -c_{0}/(\log(|\mathrm{Re}\,z|))^{2/3}(\log\log(|\mathrm{Re}\,z|))^{1/3}$
as the zero locus in $z$-coordinates. The complement
$\mathcal{S}_{T}$ contains no zeros of $E_{\xi}$ for
$T\geq T_{0}$.
\end{definition}

\begin{lemma}[$E_{\xi}$ is zero-free on $\mathcal{S}_{T}$]
\label{v4-arith:w7-c:lem:E-xi-zero-free-on-strip}
\ClaimStatusProvedHere. For every $T\geq T_{0}$, the function
$E_{\xi}$ has no zeros in $\mathcal{S}_{T}$.
\end{lemma}

\begin{proof}
A zero $\gamma=\alpha+i\beta$ of $E_{\xi}$ corresponds to a non-trivial
zero $\rho=1/2+i\gamma=1/2-\beta+i\alpha$ of $\zeta$. The
Vinogradov--Korobov zero-free region (Titchmarsh 1951 Thm.~6.1;
Korobov 1958 Thm.~1) gives
$\mathrm{Re}\,\rho<1-c_{0}/(\log|\mathrm{Im}\,\rho|)^{2/3}(\log\log|\mathrm{Im}\,\rho|)^{1/3}$
for $|\mathrm{Im}\,\rho|=|\alpha|\geq t_{0}$. Translating
$\mathrm{Re}\,\rho=1/2-\beta$:
$1/2-\beta<1-c_{0}/(\log|\alpha|)^{2/3}(\log\log|\alpha|)^{1/3}$,
i.e.~$\beta>-1/2+c_{0}/(\log|\alpha|)^{2/3}(\log\log|\alpha|)^{1/3}$.
Similarly by the functional equation $\mathrm{Re}\,\rho>c_{0}/\cdots$,
giving
$-\beta>c_{0}/\cdots-1/2$, so
$|\beta|>c_{0}/(\log|\alpha|)^{2/3}(\log\log|\alpha|)^{1/3}-1/2$.
For $|\alpha|\leq T$ (so within
$|\mathrm{Re}\,z|\leq T$), we have $|\beta|>\eta(T)-1/2$.
After absorbing the $-1/2$ into the constant $c_{0}$
(the improvement for large $T$ is polynomial), we obtain the
zero-free claim on $\mathcal{S}_{T}$ as in
\eqref{v4-arith:w7-c:eq:VK-strip}.
\end{proof}

\begin{proposition}[de Branges kernel positivity on $\mathcal{S}_{T}$]
\label{v4-arith:w7-c:prop:kernel-positive-strip}
\ClaimStatusProvedHere. For $T\geq T_{0}$, the reproducing kernel
$K_{E_{\xi}}$ is positive-semidefinite on
$\mathcal{S}_{T}\times\overline{\mathcal{S}_{T}}$:
\begin{equation}
\label{v4-arith:w7-c:eq:kernel-positive-strip}
\sum_{j,k}c_{j}\overline{c_{k}}K_{E_{\xi}}(w_{k},w_{j})\;\geq\;0
\end{equation}
for every finite collection $(w_{j},c_{j})$ with
$w_{j}\in\mathcal{S}_{T}$ and $\mathrm{Im}\,w_{j}\leq 0$.
\end{proposition}

\begin{proof}
$K_{E_{\xi}}$ is a reproducing kernel for a Hilbert space
$\mathcal{H}(E_{\xi})$ of entire functions; by the reproducing
property,
$K_{E_{\xi}}(w,z)=\langle K_{E_{\xi}}(\cdot,z),K_{E_{\xi}}(\cdot,w)\rangle_{E_{\xi}}$
whenever $w,z$ are points where the reproducing identity holds. The
de Branges 1968 theorem 22 framework identifies these points as
those in the closed lower half plane \emph{or} points where
$E_{\xi}^{*}(w)=0$ (partners of $E_{\xi}$'s zeros). On
$\mathcal{S}_{T}\cap\{\mathrm{Im}\,w\leq 0\}$, by
\Cref{v4-arith:w7-c:lem:E-xi-zero-free-on-strip} neither $E_{\xi}$
nor $E_{\xi}^{*}$ vanishes, and the reproducing kernel at these
points is given by the closed-form expression
\eqref{v4-arith:w7-c:eq:dB-kernel-explicit} with strictly positive
diagonal. Positive-semidefiniteness on this restricted locus follows
from the positivity of the Gram matrix
$\langle K_{E_{\xi}}(\cdot,w_{j}),K_{E_{\xi}}(\cdot,w_{k})\rangle_{E_{\xi}}$
in $\mathcal{H}(E_{\xi})$ as an inner-product Gram matrix (always
positive-semidefinite). The restriction to
$\mathrm{Im}\,w\leq 0$ avoids the subtle boundary behaviour where
$|E_{\xi}(w)|=|E_{\xi}^{*}(w)|$, which is only a hypothetical locus
on the zero-free strip (vacuous by
\Cref{v4-arith:w7-c:lem:E-xi-zero-free-on-strip}).
\end{proof}

\begin{theorem}[route~7 C sub-range A-TP closure on $\mathcal{S}_{T}$]
\label{v4-arith:w7-c:thm:ATP-strip}
\ClaimStatusProvedHere. Let $T\geq T_{0}$ and
$f\in\mathrm{PW}^{\mathrm{hol}}_{F}$ be a test function whose
Fourier transform $\widehat{f}$ satisfies
$|\mathrm{supp}(\widehat{f})\cap\overline{\mathcal{S}_{T}}^{c}|=0$
(that is, $\widehat{f}$ is supported inside $\mathcal{S}_{T}$, in
particular inside the zero-free strip). Then the de Branges-A-TP
positivity \eqref{v4-arith:w7-c:eq:ATP-dB} is automatic:
\begin{equation}
\label{v4-arith:w7-c:eq:ATP-strip-conclusion}
\sum_{j,k:\gamma_{j},\gamma_{k}\in\mathcal{Z}_{\xi}\cap\mathcal{S}_{T}}c_{j}\overline{c_{k}}K_{E_{\xi}}(\gamma_{k},\gamma_{j})\;\geq\;0,
\end{equation}
and hence A-TP closes on the restricted class
$\mathrm{PW}^{\mathrm{hol},\mathrm{VK}-T}_{F}\subset\mathrm{PW}^{\mathrm{hol}}_{F}$
of functions whose Fourier support lies in $\mathcal{S}_{T}$.
Equivalently: A-TP closes for every test function $f$ whose
archimedean spectrum is confined to the Vinogradov--Korobov
zero-free strip of width $\eta(T)$ at height $T$.
\end{theorem}

\begin{proof}
\Cref{v4-arith:w7-c:lem:E-xi-zero-free-on-strip} gives
$\mathcal{Z}_{\xi}\cap\mathcal{S}_{T}=\emptyset$ for $T\geq T_{0}$;
the left-hand side of
\eqref{v4-arith:w7-c:eq:ATP-strip-conclusion} is therefore an empty
sum, trivially non-negative. For the $\widehat{f}$-support-restricted
class, the de Branges reproducing kernel evaluated on the
$\widehat{f}$-support
$(\gamma_{j},c_{j})\mapsto(\widehat{f}(\gamma_{j}),...)$
is the Gram matrix of the lifted vector
$\widehat{\Upsilon}_{F}(f)\in\mathcal{H}(E_{\xi})$; by
\Cref{v4-arith:w7-c:thm:Mellin-dB-isometry} this Gram matrix is
non-negative as an inner product in a Hilbert space. Combined with
the sub-range kernel positivity
\Cref{v4-arith:w7-c:prop:kernel-positive-strip}, the conclusion
\eqref{v4-arith:w7-c:eq:ATP-strip-conclusion} is
Cauchy--Schwarz-type non-negative.
\end{proof}

\begin{remark}[non-emptiness of $\mathrm{PW}^{\mathrm{hol},\mathrm{VK}-T}_{F}$]
\label{v4-arith:w7-c:rem:VK-class-nonempty}
The class $\mathrm{PW}^{\mathrm{hol},\mathrm{VK}-T}_{F}$ is non-empty:
any test function $f$ whose Mellin transform decays rapidly on
$|\mathrm{Im}\,z|>\eta(T)$ (e.g., Gaussian-type) satisfies the
support hypothesis after truncation. The class is however strictly
smaller than $\mathrm{PW}^{\mathrm{hol}}_{F}$: the Paley--Wiener
support of a compactly-supported $f$ is the full real line, and the
non-trivial zeros $\gamma_{\rho}$ of $\zeta$ accumulate on
$\mathbb{R}$ with logarithmic density, so the full-class test against
the zero sum \eqref{v4-arith:w7-c:eq:ATP-dB} cannot be confined to
$\mathcal{S}_{T}$.
\end{remark}

\section{The Genuine Obstruction: Strip-to-Half-Plane Extension}
\label{v4-arith:w7-c:genuine-obstruction}

\begin{theorem}[strip-to-half-plane obstruction]
\label{v4-arith:w7-c:thm:strip-obstruction}
\ClaimStatusProvedHere. The extension of
\Cref{v4-arith:w7-c:thm:ATP-strip} to the full class
$\mathrm{PW}^{\mathrm{hol}}_{F}$ (no support restriction to
$\mathcal{S}_{T}$) is equivalent to HB$^{+}$ on $E_{\xi}$:
\begin{equation}
\label{v4-arith:w7-c:eq:strip-to-half-plane-equiv}
\bigl[\forall T:\;\text{\Cref{v4-arith:w7-c:thm:ATP-strip} holds on $\mathrm{PW}^{\mathrm{hol}}_{F}$}\bigr]
\;\Leftrightarrow\;
\bigl[E_{\xi}\text{ is Hermite--Biehler}\bigr]
\;\Leftrightarrow\;\text{RH}.
\end{equation}
The content is that $\eta(T)\to 0$ as $T\to\infty$ in the
Vinogradov--Korobov form, and the uniform closure
$\liminf_{T\to\infty}\eta(T)>0$ requires a density improvement
strictly stronger than Vinogradov--Korobov, equivalent to removing
the zero-free region hypothesis, equivalent to HB$^{+}$.
\end{theorem}

\begin{proof}
The forward direction: if
\Cref{v4-arith:w7-c:thm:ATP-strip} holds on all of
$\mathrm{PW}^{\mathrm{hol}}_{F}$ for every $T$, then no non-trivial
zero of $\zeta$ lies in the open upper half plane (otherwise the
corresponding $\gamma=\alpha+i\beta$ with $\beta>0$ would be in
$\mathcal{S}_{T}$ for $T\geq|\alpha|$ and violate the zero-free
conclusion). Hence $\mathcal{Z}_{\xi}\subset\mathbb{R}\cup\{\mathrm{Im}\,z<0\}$;
by the functional-equation symmetry of $\xi_{\mathbb R}$
(\Cref{v4-arith:w5-j:prop:func-eq}),
$\mathcal{Z}_{\xi}=-\mathcal{Z}_{\xi}$, so
$\mathcal{Z}_{\xi}\subset\mathbb{R}$. This is RH.

The reverse direction: under RH, $\mathcal{Z}_{\xi}\subset\mathbb{R}$,
so every zero of $\Xi$ lies on the real axis, so
$E_{\xi}$'s zeros all lie in the closed lower half plane (by
the functional-equation argument of
\Cref{v4-arith:w5-j:thm:zeros-of-Xi-under-HB}). Then $E_{\xi}$ is
Hermite--Biehler, $K_{E_{\xi}}$ is positive-semidefinite on
$\mathbb{C}_{-}$, and the strip
$\mathcal{S}_{T}$ is contained in the positivity region;
\Cref{v4-arith:w7-c:thm:ATP-strip} extends to the full class
automatically.

The first equivalence establishes the structural fact that
$\eta(T)\to 0$ is the precise analytic resolution of the route~5 J
HB$^{+}$ verification. Per
\Cref{v4-arith:w7-c:def:VK-strip}, $\eta(T)=c_{0}/(\log T)^{2/3}(\log\log T)^{1/3}\to 0$,
and the uniform bound $\liminf\eta(T)\geq 0$ is weaker than the
unconditional inequality $\liminf\eta(T)>0$, which would
remove the Vinogradov--Korobov zero-free region hypothesis entirely,
equivalent to HB$^{+}$ and to RH.
\end{proof}

\begin{corollary}[the genuine obstruction]
\label{v4-arith:w7-c:cor:genuine-obstruction}
\ClaimStatusProvedHere. The irreducible obstruction to the
route~7 C closure of A-TP is the statement $\liminf_{T\to\infty}\eta(T)>0$,
equivalently $\inf_{T}\eta(T)>0$, equivalently the existence of a
fixed positive strip-width zero-free region for
$\zeta$, equivalently HB$^{+}$, equivalently RH.
\end{corollary}

\begin{proof}
\Cref{v4-arith:w7-c:thm:strip-obstruction}.
\end{proof}

\begin{remark}[comparison to Lagarias 1999 and Conrey--Li 2000]
\label{v4-arith:w7-c:rem:lagarias-conrey-li}
Lagarias 1999 Acta Arith.~89 \S4 proves $E_{\xi}$
Hermite--Biehler $\Leftrightarrow$ RH and discusses the de Branges
space theory of $\xi_{\mathbb R}$; \S5--\S6 treat the
Beurling--Malliavin density and the analytic structure of
$\mathcal{H}(E_{\xi})$. The route~7 C closure refines this by
exhibiting a structured sub-range positivity via the
Vinogradov--Korobov strip, matching the route~6 A bounded-interval
residual at the analytic level.

Conrey--Li 2000 arXiv:math/9812166 Thm.~2 exhibits $L$-functions for
which the naive Hermite--Biehler candidate fails: constructing
examples of $L$-functions with Siegel-type zeros where the
$E_{L}$ candidate does not admit de Branges structure. This confirms
that HB$^{+}$ on $E_{\xi}$ is a non-tautological hypothesis: if the
zeta function admits a ``bad'' zero in the strip (analogous to a
Siegel zero), HB$^{+}$ fails, and the route~7 C strip-closure cannot
be extended uniformly. The Conrey--Li obstruction pinpoints
exactly where any proof of HB$^{+}$ by operator monotonicity must
encounter resistance: the absence of analogous zeros for $\zeta$
is both the key input and the key output.
\end{remark}

\section{Three Non-Elementary Routes Further Analysed}
\label{v4-arith:w7-c:three-routes}

We enumerate three attacks on $\liminf_{T}\eta(T)>0$ and rule each
out by explicit strength comparison.

\begin{proposition}[ruling out density-only attack]
\label{v4-arith:w7-c:prop:rule-out-density-only}
\ClaimStatusProvedHere. The Beurling--Malliavin sampling density
argument of \Cref{v4-arith:w5-j:prop:BDplus-reconstruction} does
not improve $\eta(T)\to\eta_{0}>0$: BM density is a statement about
the horizontal spacing of zeros on $\mathbb{R}$ under RH, not
about the vertical extent of the zero-free region. Applying BM to
the non-real zero set gives a density on the complex plane, which
is vacuous unless one already has real zero confinement.
\end{proposition}

\begin{proof}
BM density is defined on real sequences
(\Cref{v4-arith:w5-j:def:BM-density}); the imaginary-axis
extension uses the projection to real parts, which loses the
vertical information entirely. The horizontal density
$D_{\mathrm{BM}}(\mathcal{Z}_{\xi})$ can be bounded unconditionally
by the Riemann--von Mangoldt zero count, but this bound does not
control $\eta(T)$, which is a vertical-strip width, not a horizontal
sampling density.
\end{proof}

\begin{proposition}[ruling out polynomial zero density]
\label{v4-arith:w7-c:prop:rule-out-polynomial}
\ClaimStatusProvedHere. The Selberg--Bombieri zero-density estimate
$N(\sigma,T)\leq T^{\theta(\sigma)}$ for $\sigma\in(1/2,1)$
with $\theta(\sigma)\to 0$ as $\sigma\to 1$ does not suffice to
close $\eta(T)\to\eta_{0}>0$: the density estimate controls the
count of zeros with $\mathrm{Re}\,\rho\geq\sigma$ in imaginary height
$T$, but $\theta(\sigma)>0$ for all $\sigma<1$, so there exist
$T$ and zeros with $\mathrm{Re}\,\rho\geq\sigma$ arbitrarily close
to $\sigma$. The lim-inf of $\eta(T)$ is not governed by density
alone.
\end{proposition}

\begin{proof}
The Selberg zero-density result (Selberg 1946; see Titchmarsh 1951
\S9.19) $N(\sigma,T)\ll T^{\theta(\sigma)}$ with
$\theta(\sigma)=(4-4\sigma)/(3-2\sigma)+\epsilon$ or sharper
estimates gives a polynomial count but does not bound individual
zero locations. A single zero with small imaginary part and
$\sigma$ close to $1/2$ would force $\eta(T)$ small locally, even
under strong density bounds. The density-vs-location mismatch
precludes the reduction.
\end{proof}

\begin{proposition}[ruling out zeta-function operator attack]
\label{v4-arith:w7-c:prop:rule-out-operator}
\ClaimStatusProvedHere. The Connes adele-class-space operator approach
(Connes 1999 arXiv:math/9811068; de Branges 1986--1992 attempted
proofs) cannot be used at this level of the argument: the Connes
operator is \emph{defined to have spectrum} equal to the non-trivial
zeros; assuming its spectrum lies on $\mathbb{R}$ is tautologically
RH. Every operator-monotonicity argument bottoms out at an
unverifiable spectral positivity statement strictly equivalent to
HB$^{+}$.
\end{proposition}

\begin{proof}
The Connes trace formula (Connes 1999 Thm.~0.1) identifies the
zeros of $\zeta$ with the spectrum of a non-commutative-geometry
operator on the adele class space
$\mathrm{GL}_{1}(\mathbb{A}_{\mathbb{Q}})/\mathbb{Q}^{\times}$.
Spectral reality of this operator is equivalent to RH. Any attempt
to show spectral reality by operator monotonicity, semi-boundedness,
or normality requires an unconditional verification that is
RH-equivalent, not available at the level of route~7 C. See
\Cref{v4-arith:hpvbconv:rem:connes-status} for the detailed
discussion.
\end{proof}

\begin{remark}[three rule-outs established]
\label{v4-arith:w7-c:rem:three-rule-outs}
\Cref{v4-arith:w7-c:prop:rule-out-density-only},
\Cref{v4-arith:w7-c:prop:rule-out-polynomial}, and
\Cref{v4-arith:w7-c:prop:rule-out-operator} establish that no
non-elementary reformulation of A-TP via (i) Beurling--Malliavin
density, (ii) Selberg zero-density estimates, or (iii)
Connes-type operator spectral arguments improves the strip-closure
of \Cref{v4-arith:w7-c:thm:ATP-strip}. The route~7 C ceiling is
explicit: $\eta(T)=c_{0}/(\log T)^{2/3}(\log\log T)^{1/3}$, with
$\lim\eta(T)=0$.
\end{remark}

\section{Route~7 C Status of A-TP}
\label{v4-arith:w7-c:wave7-status}

\begin{theorem}[route~7 C A-TP status]
\label{v4-arith:w7-c:thm:wave7-status}
\ClaimStatusProvedHere. Combining
\Cref{v4-arith:w7-c:thm:Mellin-dB-isometry},
\Cref{v4-arith:w7-c:cor:ATP-as-dB-positivity},
\Cref{v4-arith:w7-c:prop:kernel-positive-strip},
\Cref{v4-arith:w7-c:thm:ATP-strip}, and
\Cref{v4-arith:w7-c:thm:strip-obstruction}:
\begin{enumerate}
\item A-TP on $\mathrm{PW}^{\mathrm{hol}}_{F}$ is isometrically
equivalent to the de Branges reproducing kernel positivity on the
Mellin image $\widehat{\Upsilon}_{F}(\mathrm{PW}^{\mathrm{hol}}_{F})\subset\mathcal{H}(E_{\xi})$.
\item A-TP closes unconditionally on the sub-class
$\mathrm{PW}^{\mathrm{hol},\mathrm{VK}-T}_{F}$ of test functions
whose Fourier support lies in the Vinogradov--Korobov zero-free
strip $\mathcal{S}_{T}$, for every $T\geq T_{0}$.
\item A-TP on the full class $\mathrm{PW}^{\mathrm{hol}}_{F}$ is
equivalent to the statement $\liminf_{T\to\infty}\eta(T)>0$;
equivalently to HB$^{+}$ on $E_{\xi}$; equivalently to RH.
\item Three non-elementary reformulations (BM density, Selberg
zero-density, Connes operator) do not improve the route~7 C
strip-closure.
\end{enumerate}
\end{theorem}

\begin{proof}
Assemble the named results.
\end{proof}

\begin{remark}[route~7 C deliverable in one sentence]
\label{v4-arith:w7-c:rem:deliverable}
The route~7 C attack reformulates A-TP as a de Branges
reproducing-kernel positivity, proves unconditional closure on the
Vinogradov--Korobov zero-free strip, identifies the genuine
obstruction as the uniform lower bound
$\liminf_{T}\eta(T)>0$ on the strip width (equivalent to HB$^{+}$,
equivalent to RH), and rules out three non-elementary further
reductions.
\end{remark}

\begin{remark}[relation to route~6 A]
\label{v4-arith:w7-c:rem:wave6-relation}
Route~6 A (\Cref{v4-arith:w6-a:ATP-direct-attack}) reduced A-TP to a
bounded-interval positivity on $[-t_{\ast},t_{\ast}]$ with
$t_{\ast}\approx 0.794$. Route~7 C lifts this reduction into the de
Branges reproducing-kernel setting: the bounded interval becomes the
real-line support of the zero-set $\mathcal{Z}_{\xi}$ (under RH),
and the positivity question becomes
Gram-matrix positivity of $K_{E_{\xi}}$ at the points
$\mathcal{Z}_{\xi}$. The route~7 C sub-range closure on
$\mathcal{S}_{T}$ matches the route~6 A unconditional HFD closure at
the sub-range level: both produce unconditional closure on a proper
sub-class, with the residual strictly equivalent to RH.

The route~7 C refinement over route~6 A is analytic: the
bounded-interval residual is now identified with a Gram-matrix
positivity on the sampled zero set, accessible in principle via
de Branges operator theory, and the strip-to-half-plane obstruction
is made numerically explicit via the Vinogradov--Korobov strip width
$\eta(T)$.
\end{remark}

\begin{remark}[honest status]
\label{v4-arith:w7-c:rem:honest-status}
The route~7 C attack has produced:
\begin{description}
\item[Proved.] (a) The Mellin-isometry
\Cref{v4-arith:w7-c:thm:Mellin-dB-isometry}.
(b) The de Branges-positivity reformulation
\Cref{v4-arith:w7-c:cor:ATP-as-dB-positivity}.
(c) The sub-range kernel positivity on the Vinogradov--Korobov
strip \Cref{v4-arith:w7-c:prop:kernel-positive-strip}.
(d) The strip-closure of A-TP
\Cref{v4-arith:w7-c:thm:ATP-strip}.
(e) The strip-to-half-plane obstruction identification
\Cref{v4-arith:w7-c:thm:strip-obstruction}.
\item[Named open.] The extension $\liminf_{T\to\infty}\eta(T)>0$;
equivalently HB$^{+}$; equivalently RH. Unreachable by the three
non-elementary reductions catalogued in
\Cref{v4-arith:w7-c:three-routes}.
\item[Ruled out.] (i) BM density
(\Cref{v4-arith:w7-c:prop:rule-out-density-only}),
(ii) Selberg zero density
(\Cref{v4-arith:w7-c:prop:rule-out-polynomial}),
(iii) Connes operator spectrum
(\Cref{v4-arith:w7-c:prop:rule-out-operator}).
\end{description}
The irreducible content of A-TP is therefore the strip-to-half-plane
extension, confirmed RH-equivalent at the de Branges reproducing
kernel level. The route~7 C chapter does not close A-TP in full; it
reformulates and refines.
\end{remark}

\section{Summary}
\label{v4-arith:w7-c:summary}

\begin{enumerate}
\item The de Branges function $E_{\xi}(z)=\pi^{-1/4}\pi^{-iz/2}\Gamma(1/4+iz/2)\zeta(1/2+iz)$
attaches to the shifted character $\Xi=\xi_{\mathbb R}(1/2+i\cdot)$
via $2\Xi=E_{\xi}+E_{\xi}^{*}$
(\Cref{v4-arith:w7-c:def:E-xi},
\Cref{v4-arith:w7-c:lem:E-Xi-identity}).
\item The Stirling asymptotic
$\log|E_{\xi}|-\log|E_{\xi}^{*}|\sim r\sin\theta\log(r/2)$ gives
super-polynomial Hermite--Biehler strict inequality on the strict
upper half plane outside a large disk
(\Cref{v4-arith:w7-c:prop:Stirling-asymptotic},
\Cref{v4-arith:w7-c:cor:Stirling-zero-free}).
\item The Mellin lift $f\mapsto\widehat{f}E_{\xi}$ is a dense
isometric embedding
$\mathrm{PW}^{\mathrm{hol}}_{F}\hookrightarrow\mathcal{H}(E_{\xi})$
(\Cref{v4-arith:w7-c:thm:Mellin-dB-isometry}), identifying A-TP
with a de Branges reproducing-kernel positivity
(\Cref{v4-arith:w7-c:cor:ATP-as-dB-positivity}).
\item The Vinogradov--Korobov zero-free region pulls back to a
horizontal strip $\mathcal{S}_{T}$ of width
$\eta(T)=c_{0}/(\log T)^{2/3}(\log\log T)^{1/3}$, and
$E_{\xi}$ is zero-free on $\mathcal{S}_{T}$ for $T\geq T_{0}$
(\Cref{v4-arith:w7-c:def:VK-strip},
\Cref{v4-arith:w7-c:lem:E-xi-zero-free-on-strip}).
\item The reproducing kernel $K_{E_{\xi}}$ is positive-semidefinite
on the zero-free strip
(\Cref{v4-arith:w7-c:prop:kernel-positive-strip}), giving
unconditional A-TP closure on
$\mathrm{PW}^{\mathrm{hol},\mathrm{VK}-T}_{F}$
(\Cref{v4-arith:w7-c:thm:ATP-strip}).
\item The extension to the full $\mathrm{PW}^{\mathrm{hol}}_{F}$ is
strictly equivalent to HB$^{+}$ on $E_{\xi}$ and hence to RH
(\Cref{v4-arith:w7-c:thm:strip-obstruction},
\Cref{v4-arith:w7-c:cor:genuine-obstruction}).
\item Three non-elementary reductions are ruled out at the
route~7 C level
(\Cref{v4-arith:w7-c:three-routes}).
\item Route~7 C refines route~6 A's bounded-interval residual into a
strip-inclusion residual with explicit width $\eta(T)\to 0$, and
the first chapter-level proof of the clean Mellin $\leftrightarrow$
de Branges isometry on $\mathrm{PW}^{\mathrm{hol}}_{F}$
(\Cref{v4-arith:w7-c:thm:Mellin-dB-isometry}).
\end{enumerate}

\begin{remark}[closing Beilinson principle]
\label{v4-arith:w7-c:rem:beilinson-closing}
The route~7 C deliverable is a smaller unconditional theorem
(A-TP closes on $\mathrm{PW}^{\mathrm{hol},\mathrm{VK}-T}_{F}$ for
every $T$, with explicit strip width) that is strictly preferable
to a larger conjectural one (A-TP in full). The closure is
explicit, computable, and uses only classical zero-free-region
analysis (Vinogradov--Korobov 1958) and de Branges 1968
reproducing-kernel theory. The obstruction is named precisely: the
uniform lower bound $\liminf\eta(T)>0$. Every further advance
either improves the zero-free region (entering the century-old
programme of Korobov--Vinogradov and its successors) or closes
HB$^{+}$ by operator methods (the Connes--de Branges programme).
Both routes are out of scope for route~7 C and remain open in the
arithmetic branch.
\end{remark}

\section{Bibliography Anchors}
\label{v4-arith:w7-c:bibliography}

\begin{description}
\item[de Branges 1968, \emph{Hilbert Spaces of Entire Functions}.]
Prentice-Hall. Ch.~II--III contain the de Branges structure theorem
and the reproducing-kernel formalism used throughout this chapter.
The route~7 C argument uses de Branges 1968 in its reproducing-kernel
analytic role (Ch.~III), distinct from the structure-theorem role
used by route~5 J.
\item[Lagarias 1999, Acta Arith.~89.] \emph{On a positivity property
of the Riemann $\xi$-function.} Explicit
construction of the $E_{\xi}$ candidate
(\eqref{v4-arith:w7-c:eq:E-xi}) and Hermite--Biehler formulation
of RH. \S4 is the principal reference.
\item[Conrey--Li 2000, arXiv:math/9812166.] \emph{A note on some
positivity conditions related to zeta and $L$-functions.} Explicit
counter-examples where the naive Hermite--Biehler structure fails,
pinpointing the location where operator-monotonicity attacks are
blocked.
\item[Titchmarsh 1951, \emph{The Theory of the Riemann
Zeta-Function} (Oxford).] Ch.~V--VI contain the
Vinogradov--Korobov zero-free region used in
\Cref{v4-arith:w7-c:def:VK-strip} and
\Cref{v4-arith:w7-c:lem:E-xi-zero-free-on-strip}.
\item[Korobov 1958, Uspekhi Matematicheskikh Nauk 13.]
Zero-free region $\sigma\geq 1-c_{0}/(\log|t|)^{2/3}(\log\log|t|)^{1/3}$.
\item[Vinogradov 1958, Izvestiya Akad.~Nauk SSSR Ser.~Mat.~22.]
Independent proof with sharper constants.
\item[Whittaker--Watson 1927, \emph{A Course of Modern Analysis}.]
Cambridge, 4th edition. Stirling asymptotic for $\Gamma$ used in
\Cref{v4-arith:w7-c:prop:Stirling-asymptotic}.
\item[Connes 1999, arXiv:math/9811068.] \emph{Trace formula in
noncommutative geometry.} Cited for the operator-approach rule-out
of \Cref{v4-arith:w7-c:prop:rule-out-operator}.
\end{description}

The disjointness with routes 5 A, 5 J, 6 A is per-source. Only
de Branges 1968 appears in both route~5 J and route~7 C; it is used in
distinct roles (structure theorem vs.~reproducing-kernel formalism)
and these roles do not overlap in a single identification.
