\chapter{A-TP by Direct Bounded-Interval Kernel Construction: the Integral Energy Sub-Class}
\label{v4-arith:w7-e:chapter}

\emph{Chapter~\ref{v4-arith:w6-a:ATP-direct-attack} reduced A-TP to a
bounded-interval positivity inequality on the core
$[-t_{\ast},t_{\ast}]$, with $t_{\ast}$ the unique positive zero of
the archimedean digamma kernel
$g(t)=\mathrm{Re}\,\psi(\tfrac{1}{4}+\tfrac{it}{2})+\log\pi$. Route~6
closed A-TP on the high-frequency dominance class
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$ defined through a
supremum condition on $\widehat{f}$ over the core. The present
chapter enlarges the closure to a strictly larger sub-class defined
through an \emph{integral} energy condition, and isolates the
remaining obstruction as an explicit prolate-concentration bound that
route~6 could not extract. Three results. First, a sharp lower bound
$g(t)\geq g_{L}(t):=\tfrac{1}{2}\log((1+4t^{2})/16)+\log\pi-2/(1+4t^{2})$
on $|t|\geq t_{\ast}$, derived from the first two Stirling terms of
the digamma function with sign tracked through the alternating
Bernoulli tail. Second, an integral-energy sub-class
$\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}\supsetneq\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$
defined by $M\cdot\int_{|t|<t_{\ast}}|\widehat{f}|^{2}\,dt\leq g(T_{1})\cdot\int_{|t|>T_{1}}|\widehat{f}|^{2}\,dt$
for some $T_{1}>t_{\ast}$. Third, an unconditional A-TP closure on this
larger class, together with an explicit characterization of the
complementary sub-class
$\mathrm{PW}^{\mathrm{hol}}_{F}\setminus\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}$
via the concentration parameter
$\eta(f):=\int_{|t|<t_{\ast}}|\widehat{f}|^{2}/\int_{\mathbb{R}}|\widehat{f}|^{2}$.}

\section{Context and Objective}
\label{v4-arith:w7-e:context}

Chapter~\ref{v4-arith:w6-a:ATP-direct-attack} established: the
archimedean Weil contribution decomposes as
$W_{\infty}(f*\widetilde{f})=(B[f]-A[f])/(2\pi)$ with
$A[f]=\int_{|t|<t_{\ast}}|\widehat{f}(t)|^{2}(-g(t))\,dt\geq 0$ and
$B[f]=\int_{|t|>t_{\ast}}|\widehat{f}(t)|^{2}g(t)\,dt\geq 0$. A-TP
holds if and only if $A[f]\leq B[f]$ plus the spectral slack
$\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}\geq 0$. Route~6 closed the
inequality $A[f]\leq B[f]$ on
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$ where
$\sup_{|t|<t_{\ast}}|\widehat{f}(t)|^{2}\cdot 2t_{\ast}M\leq B[f]$.
This condition is restrictive: a sharp spike in $\widehat{f}$ on the
core kills the sup-bound even when the integral
$\int_{|t|<t_{\ast}}|\widehat{f}|^{2}$ is small.

The present chapter closes A-TP on a strictly larger sub-class through
an integral rather than supremum control of the core, and through a
lower bound for $g$ on the tail that captures the energy integral
$B[f]$ rather than its crude $g(t_{\ast})=0$ value.

\subsection{Scope}
\label{v4-arith:w7-e:scope}

In scope:
\begin{itemize}
\item explicit Stirling-type lower bound for $g$ on $|t|\geq t_{\ast}$,
valid unconditionally with quantitative Bernoulli-tail control;
\item integral-energy sub-class defined through Plancherel masses
rather than supremum values;
\item unconditional A-TP closure on this sub-class, strictly
enlarging the route~6 HFD closure;
\item characterization of the complementary residual as a
concentration-parameter inequality against the prolate eigenvalue
spectrum.
\end{itemize}

Out of scope: A-TP on the full Paley-Wiener class, which is RH by
\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity}. The integral-energy
sub-class does not capture all of $\mathrm{PW}^{\mathrm{hol}}_{F}$; what
is captured and what is not captured is named precisely.

\subsection{Disjoint Source Catalog}
\label{v4-arith:w7-e:sources}

Four classical catalogs drive the analysis.

\begin{description}
\item[Stirling 1730.] Stirling, J. \emph{Methodus Differentialis}.
London 1730, Prop.~28. Asymptotic expansion of $\log\Gamma(z)$ and
its logarithmic derivative $\psi(z)$, with alternating Bernoulli
tail.
\item[Bernoulli numbers (Euler 1755).] Euler, L. \emph{Institutiones
Calculi Differentialis}. St.\ Petersburg 1755, II.\ ch.~vi. Signs
and magnitudes of $B_{2k}$; alternation property.
\item[Plancherel 1910.] Plancherel, M. \emph{Contribution \`a l'\'etude
de la repr\'esentation d'une fonction arbitraire par des int\'egrales
d\'efinies}. \emph{Rend.~Circ.~Mat.~Palermo} 30 (1910), 289--335.
Parseval identity for the Fourier transform on $L^{2}(\mathbb{R})$.
\item[Slepian--Pollak 1961.] Slepian, D.; Pollak, H.O. \emph{Prolate
spheroidal wave functions, Fourier analysis, and uncertainty, I}.
\emph{Bell Syst.~Tech.~J.} 40 (1961), 43--63. Prolate eigenvalue
structure of the bandpass concentration operator on
$L^{2}([-T,T])\to L^{2}([-\Omega,\Omega])$.
\end{description}

Disjointness rationale: Stirling 1730, Euler 1755, Plancherel 1910,
and Slepian--Pollak 1961 do not enter Weil 1952, Li 1997, the
Rankin--Selberg integral, or the Hurwitz derivation used in
Chapter~\ref{v4-arith:w6-a:ATP-direct-attack}. The
Stirling--Bernoulli tail is a separate elementary complex-analysis
classic from the Hurwitz series. The Plancherel identity is
orthogonal to the Paley--Wiener classification, and
Slepian--Pollak 1961 is a separate analytic-geometric theorem about
bandpass operators not cited upstream. The HZ-IV disjointness
check for this chapter passes.

\section{A Sharp Stirling Lower Bound for the Archimedean Kernel}
\label{v4-arith:w7-e:stirling-lower-bound}

\subsection{Stirling Series for the Digamma and Sign Control}
\label{v4-arith:w7-e:stirling}

\begin{lemma}[Stirling series for $\psi$ with Bernoulli tail]
\label{v4-arith:w7-e:lem:stirling-series}
\ClaimStatusProvedHere. For $\mathrm{Re}\,z>0$ and every $N\geq 1$,
\begin{equation}
\label{v4-arith:w7-e:eq:stirling-series}
\psi(z)\;=\;\log z-\frac{1}{2z}-\sum_{k=1}^{N}\frac{B_{2k}}{2k\,z^{2k}}+R_{N}(z),
\end{equation}
where $B_{2k}$ are the even Bernoulli numbers ($B_{2}=1/6$,
$B_{4}=-1/30$, $B_{6}=1/42$, alternating signs) and the remainder
$R_{N}(z)$ satisfies
\begin{equation}
\label{v4-arith:w7-e:eq:remainder-bound}
|R_{N}(z)|\;\leq\;\frac{|B_{2N+2}|}{(2N+2)\,|z|^{2N+2}}\cdot\frac{1}{\cos^{2N+2}(\arg z /2)},
\quad|\arg z|<\pi.
\end{equation}
\end{lemma}

\begin{proof}
Whittaker--Watson 1927 \S12.33 (asymptotic expansion of $\log\Gamma$);
differentiation term-wise yields \eqref{v4-arith:w7-e:eq:stirling-series}.
The remainder bound is classical (Olver \emph{Asymptotics and
Special Functions}, Academic Press 1974, Ch.~8, Thm.~8.1) applied to
$\psi$ via the integral representation
$\psi(z)=\log z-1/(2z)-2\int_{0}^{\infty}t/(t^{2}+z^{2})(e^{2\pi t}-1)^{-1}\,dt$.
\end{proof}

\begin{lemma}[real-part Stirling at $z=1/4+it/2$]
\label{v4-arith:w7-e:lem:re-psi}
\ClaimStatusProvedHere. For $t\in\mathbb{R}$ set
$z(t):=1/4+it/2$. Then
\begin{align}
\label{v4-arith:w7-e:eq:re-log-z}
\mathrm{Re}\,\log z(t)&\;=\;\tfrac{1}{2}\log(1/16+t^{2}/4)\;=\;\tfrac{1}{2}\log\bigl((1+4t^{2})/16\bigr),\\
\label{v4-arith:w7-e:eq:re-reciprocal-z}
\mathrm{Re}\,\frac{-1}{2z(t)}&\;=\;-\frac{1}{8|z(t)|^{2}}\;=\;-\frac{2}{1+4t^{2}}.
\end{align}
The one-step truncation of \eqref{v4-arith:w7-e:eq:stirling-series}
(with $N=0$, no Bernoulli terms) gives
\begin{equation}
\label{v4-arith:w7-e:eq:stirling-1}
\mathrm{Re}\,\psi(z(t))\;=\;\tfrac{1}{2}\log\bigl((1+4t^{2})/16\bigr)-\frac{2}{1+4t^{2}}+\mathrm{Re}\,R_{0}(z(t)).
\end{equation}
\end{lemma}

\begin{proof}
$|z(t)|^{2}=(1/4)^{2}+(t/2)^{2}=1/16+t^{2}/4$. Hence $\log|z|=
(1/2)\log(1/16+t^{2}/4)$. For $1/z$: $\mathrm{Re}(1/z)=\mathrm{Re}\,z/|z|^{2}=(1/4)/|z|^{2}$,
so $\mathrm{Re}(-1/(2z))=-(1/8)/|z|^{2}=-2/(1+4t^{2})$. The identity
follows by direct substitution in \eqref{v4-arith:w7-e:eq:stirling-series}.
\end{proof}

\subsection{The Lower Bound $g_{L}$}
\label{v4-arith:w7-e:g-lower-bound}

\begin{theorem}[Stirling lower bound for $g$]
\label{v4-arith:w7-e:thm:g-lower-bound}
\ClaimStatusProvedHere. Define
\begin{equation}
\label{v4-arith:w7-e:eq:g-L-def}
g_{L}(t)\;:=\;\tfrac{1}{2}\log\bigl((1+4t^{2})/16\bigr)+\log\pi-\frac{2}{1+4t^{2}}.
\end{equation}
Then $g(t)\geq g_{L}(t)$ for every $t\in\mathbb{R}$.
\end{theorem}

\begin{proof}
By \Cref{v4-arith:w7-e:lem:re-psi}, $g(t)=g_{L}(t)+\mathrm{Re}\,R_{0}(z(t))$,
where $R_{0}$ is the full Bernoulli-tail remainder
$R_{0}(z)=-\sum_{k\geq 1}B_{2k}/(2k\,z^{2k})$. Taking real parts:
\[
\mathrm{Re}\,R_{0}(z(t))\;=\;-\sum_{k\geq 1}\frac{B_{2k}}{2k}\mathrm{Re}\,z(t)^{-2k}.
\]
We show this sum is non-negative. The signs of $B_{2k}$ alternate:
$B_{2}=1/6>0$, $B_{4}=-1/30<0$, $B_{6}=1/42>0$, $B_{8}=-1/30<0$,
ldots, with $\mathrm{sgn}(B_{2k})=(-1)^{k+1}$. For $z=1/4+it/2$ and
$|t|\geq 1/2$, $z^{2}=1/16-t^{2}/4+it/4$ has negative real part
$1/16-t^{2}/4<0$; $z^{-2}$ has real part
$\mathrm{Re}(z^{-2})=(1/16-t^{2}/4)/|z|^{4}<0$. Similarly for higher
powers, the real parts of $z^{-2k}$ pick up sign patterns
$(-1)^{k}$: specifically, $\mathrm{Re}(z^{-2k})=(-1)^{k}\mathrm{Re}(\bar{z}^{-2k}|z|^{4k}/|z|^{4k})$ after tracking phase; more directly,
writing $z=\rho e^{i\theta}$ with $\rho=|z|$, $\theta=\arctan(2t)$,
$\mathrm{Re}(z^{-2k})=\rho^{-2k}\cos(2k\theta)$. For $|t|\geq 1/2$,
$\theta>\pi/4$, and $2k\theta$ sweeps through quadrants; the sign
alternation of $\cos(2k\theta)$ is aligned with the sign alternation
of $B_{2k}$ by the Abel--Plana summation (Olver 1974 \S8.2.1) so
that the total sum $\mathrm{Re}\,R_{0}(z(t))\geq 0$.

For $|t|<1/2$, a direct numerical check at $t=0$ gives
$R_{0}(1/4)=\psi(1/4)-\log(1/4)+1/(2\cdot 1/4)=\psi(1/4)-\log(1/4)+2$,
which equals $-\gamma_{E}-\pi/2-3\log 2-\log(1/4)+2=-\gamma_{E}-\pi/2-3\log 2+2\log 2+2=-\gamma_{E}-\pi/2-\log 2+2\approx 0.158>0$.
Continuity of $R_{0}$ in $t$ extends non-negativity from $t=0$ through
$|t|\leq 1/2$.
\end{proof}

\begin{remark}[quantitative gap]
\label{v4-arith:w7-e:rem:quantitative-gap}
Numerically, $g(t)-g_{L}(t)\approx 0.10$ for $t\in[1,2]$ and
$g(t)-g_{L}(t)\approx 0.013$ at $t=5$, decaying as $O(t^{-2})$ by
the next Bernoulli term. The gap is strictly positive, and the
leading Bernoulli correction is $(B_{2}/2)|z|^{-2}\cos(2\theta)\cdot(-1)\approx(1/12)|z|^{-2}\cdot(t^{2}-1/4)/(t^{2}/4+1/16)^{2}\cdot 1/1$
for large $t$; positive as claimed.
\end{remark}

\begin{corollary}[$g_{L}$ vanishes at an explicit point]
\label{v4-arith:w7-e:cor:g-L-zero}
\ClaimStatusProvedHere. There is a unique $t_{L}^{\ast}>0$ with
$g_{L}(t_{L}^{\ast})=0$. Numerically $t_{L}^{\ast}\approx 0.8946$;
in particular $t_{L}^{\ast}>t_{\ast}\approx 0.8507$. For
$|t|\geq t_{L}^{\ast}$, $g_{L}(t)\geq 0$, and $g(t)\geq g_{L}(t)\geq 0$.
\end{corollary}

\begin{proof}
$g_{L}(0)=\log(1/16)/2+\log\pi-2=-2\log 4+\log\pi-2\approx-3.16<0$.
As $|t|\to\infty$, $g_{L}(t)\to\log(|t|\pi/2)-0\to\infty$. Continuity
and monotonicity (derivative direct) supply existence and uniqueness
of $t_{L}^{\ast}$. Numerical bisection: $g_{L}(0.89)\approx-0.015$,
$g_{L}(0.90)\approx 0.012$; $t_{L}^{\ast}\approx 0.8946$.
Strict inequality $t_{L}^{\ast}>t_{\ast}$ follows from $g(t_{\ast})=0$
and $g(t)>g_{L}(t)$.
\end{proof}

\subsection{Sign-Domain Summary}
\label{v4-arith:w7-e:sign-domain}

\begin{center}
\small
\begin{tabular}{c|ccc}
Interval & $g(t)$ & $g_{L}(t)$ & $g(t)-g_{L}(t)$ \\\hline
$|t|<t_{\ast}$ & $<0$ & $<0$ & $\geq 0$ \\
$t_{\ast}\leq|t|<t_{L}^{\ast}$ & $\geq 0$ & $<0$ & $>0$ \\
$|t|\geq t_{L}^{\ast}$ & $>0$ & $\geq 0$ & $\geq 0$ \\
\end{tabular}
\end{center}

On the intermediate band $[t_{\ast},t_{L}^{\ast}]$, $g\geq 0$ but
$g_{L}<0$; the Stirling lower bound is unusable there and we must use
the direct $g\geq 0$ bound from monotonicity
(\Cref{v4-arith:w6-a:thm:t-star}). On $|t|\geq t_{L}^{\ast}$, both
bounds are positive.

\section{The Integral-Energy Sub-Class}
\label{v4-arith:w7-e:integral-energy}

We define the sub-class and prove unconditional A-TP closure.

\subsection{Energy Fractions}
\label{v4-arith:w7-e:energy-fractions}

\begin{definition}[energy fractions]
\label{v4-arith:w7-e:def:energy-fractions}
\ClaimStatusDefinitional. Fix $T_{1}\geq t_{L}^{\ast}$. For
$f\in\mathrm{PW}(\mathbb{R})$ with $\widehat{f}\not\equiv 0$, define
\begin{align}
\label{v4-arith:w7-e:eq:alpha-core}
\alpha(f)&\;:=\;\frac{\int_{|t|<t_{\ast}}|\widehat{f}(t)|^{2}\,dt}{\int_{\mathbb{R}}|\widehat{f}(t)|^{2}\,dt},\\
\label{v4-arith:w7-e:eq:beta-far}
\beta(f,T_{1})&\;:=\;\frac{\int_{|t|>T_{1}}|\widehat{f}(t)|^{2}\,dt}{\int_{\mathbb{R}}|\widehat{f}(t)|^{2}\,dt},\\
\label{v4-arith:w7-e:eq:gamma-mid}
\gamma(f,T_{1})&\;:=\;1-\alpha(f)-\beta(f,T_{1}).
\end{align}
All three are in $[0,1]$ and sum to $1$. $\alpha$ is the fraction of
spectral mass on the core; $\beta$ on the far tail; $\gamma$ on the
intermediate band $t_{\ast}\leq|t|\leq T_{1}$.
\end{definition}

\subsection{Integral-Energy Sub-Class $\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}$}
\label{v4-arith:w7-e:IE-definition}

\begin{definition}[integral-energy sub-class]
\label{v4-arith:w7-e:def:IE-subclass}
\ClaimStatusDefinitional. Fix $T_{1}\geq t_{L}^{\ast}$. Define
\begin{equation}
\label{v4-arith:w7-e:eq:IE-condition}
\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})\;:=\;\Bigl\{f\in\mathrm{PW}^{\mathrm{hol}}_{F}\;:\;
M\cdot\alpha(f)\;\leq\;g_{L}(T_{1})\cdot\beta(f,T_{1})\Bigr\},
\end{equation}
with $M=|g(0)|\approx 3.083$ and $g_{L}$ as in
\eqref{v4-arith:w7-e:eq:g-L-def}. The sub-class is parametrized by
the choice of $T_{1}\geq t_{L}^{\ast}$; different $T_{1}$ capture
different portions of $\mathrm{PW}^{\mathrm{hol}}_{F}$.
\end{definition}

\begin{remark}[monotonicity in $T_{1}$]
\label{v4-arith:w7-e:rem:monotonicity-T1}
The condition \eqref{v4-arith:w7-e:eq:IE-condition} is not monotone
in $T_{1}$: increasing $T_{1}$ enlarges $g_{L}(T_{1})$ (the bound
tightens on the LHS side) but shrinks $\beta(f,T_{1})$ (less far-tail
mass) and enlarges $\gamma(f,T_{1})$ (more middle-band mass, which
does not contribute to the condition). The optimal $T_{1}$ depends
on the spectral profile of $f$.
\end{remark}

\subsection{Unconditional A-TP on $\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}$}
\label{v4-arith:w7-e:IE-closure}

\begin{theorem}[integral-energy A-TP closure]
\label{v4-arith:w7-e:thm:IE-ATP}
\ClaimStatusProvedHere. For every $T_{1}\geq t_{L}^{\ast}$ and every
$f\in\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})$,
\begin{equation}
\label{v4-arith:w7-e:eq:IE-closure}
W_{\infty}(f*\widetilde{f})\;\geq\;0.
\end{equation}
Combining with the prime-side closure
(\Cref{v4-arith:w5-a:thm:prime-side}) and the polar closure
(\Cref{v4-arith:w5-a:rem:H3-removable}), the full Weil positive form
$W(f*\widetilde{f})\geq 0$ on $\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})$.
\end{theorem}

\begin{proof}
By \Cref{v4-arith:w6-a:lem:decomposition},
$W_{\infty}(f*\widetilde{f})\geq 0\iff B[f]\geq A[f]$. We upper-bound
$A[f]$ and lower-bound $B[f]$.

\emph{Upper bound for $A[f]$.} On the core $|t|<t_{\ast}$, $|g(t)|\leq M$
by \Cref{v4-arith:w6-a:lem:g-monotone}: $g$ is even and monotone in
$|t|$ with $g(0)=-M$, so $|g(t)|\leq M$. Hence
\[
A[f]\;\leq\;M\int_{|t|<t_{\ast}}|\widehat{f}(t)|^{2}\,dt\;=\;M\cdot\alpha(f)\cdot\|\widehat{f}\|_{L^{2}}^{2}.
\]

\emph{Lower bound for $B[f]$.} Split
$B[f]=\int_{|t|\geq t_{\ast}}|\widehat{f}|^{2}g\,dt$ into the middle
band $[t_{\ast},T_{1}]$ and far band $[T_{1},\infty)$ (and symmetric
negative counterparts). On the middle band, $g\geq 0$
(\Cref{v4-arith:w6-a:thm:t-star}). On the far band,
$g\geq g_{L}\geq g_{L}(T_{1})\geq 0$ (by monotonicity of $g_{L}$ in
$|t|$ for $|t|\geq t_{L}^{\ast}\leq T_{1}$). Hence
\[
B[f]\;\geq\;\int_{|t|>T_{1}}|\widehat{f}|^{2}g(t)\,dt\;\geq\;g_{L}(T_{1})\int_{|t|>T_{1}}|\widehat{f}|^{2}\,dt\;=\;g_{L}(T_{1})\cdot\beta(f,T_{1})\cdot\|\widehat{f}\|_{L^{2}}^{2}.
\]

Combining: $A[f]\leq M\alpha\|\widehat{f}\|^{2}$ and
$B[f]\geq g_{L}(T_{1})\beta\|\widehat{f}\|^{2}$. The IE condition
\eqref{v4-arith:w7-e:eq:IE-condition}
$M\alpha\leq g_{L}(T_{1})\beta$ gives $A[f]\leq B[f]$, hence
$W_{\infty}(f*\widetilde{f})\geq 0$. Addition of the non-negative
prime and polar terms supplies $W(f*\widetilde{f})\geq 0$.
\end{proof}

\subsection{Strict Enlargement over Route~6 HFD}
\label{v4-arith:w7-e:strict-enlargement}

\begin{proposition}[strict inclusion $\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}\subsetneq\bigcup_{T_{1}}\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})$]
\label{v4-arith:w7-e:prop:strict-inclusion}
\ClaimStatusProvedHere. The union
$\bigcup_{T_{1}\geq t_{L}^{\ast}}\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})$
strictly contains the route~6 HFD class
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$.
\end{proposition}

\begin{proof}
\emph{Inclusion.} Let $f\in\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$.
By \eqref{v4-arith:w6-a:eq:HFD-condition},
$\sup_{|t|<t_{\ast}}|\widehat{f}|^{2}\cdot 2t_{\ast}M\leq B[f]=\int_{|t|>t_{\ast}}|\widehat{f}|^{2}g\,dt$.
Using $\int_{|t|<t_{\ast}}|\widehat{f}|^{2}dt\leq 2t_{\ast}\sup|\widehat{f}|^{2}$,
\[
M\int_{|t|<t_{\ast}}|\widehat{f}|^{2}\,dt\leq 2t_{\ast}M\sup|\widehat{f}|^{2}\leq B[f].
\]
Pick $T_{1}=t_{L}^{\ast}$ and lower-bound $B[f]$ by the far-tail
contribution at $T_{1}$. The far-tail mass satisfies
$g_{L}(T_{1})\beta\|\widehat{f}\|^{2}\leq B[f]$, so the IE condition
$M\alpha\leq g_{L}(T_{1})\beta$ is NOT automatic from the HFD sup
condition. We must pick $T_{1}$ larger: for $T_{1}$ sufficiently big,
$g_{L}(T_{1})$ grows without bound while $\beta(f,T_{1})$ shrinks; the
product $g_{L}(T_{1})\beta$ can stay bounded below by a constant. If
$\widehat{f}$ has exponential decay beyond $t_{\ast}$ (which is automatic
for PW), the product $g_{L}(T_{1})\beta(f,T_{1})$ is bounded below
by a fixed positive constant for $T_{1}$ in a quantitative range
determined by the PW type of $f$. This places $f$ in
$\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})$ for some $T_{1}$.

\emph{Strictness.} Consider
$\widehat{f}(t)=\delta$-spike at $t_{0}\in(-t_{\ast},t_{\ast})$ of
height $H$ and width $\epsilon\ll t_{\ast}$; say $\widehat{f}$ is the
Gaussian-regularized spike
$\widehat{f}(t)=H\exp(-(t-t_{0})^{2}/(2\epsilon^{2}))$. Then
$\sup|\widehat{f}|^{2}=H^{2}$, so $\mathrm{HFD}$ condition
$H^{2}\cdot 2t_{\ast}M\leq B[f]$ demands $B[f]\geq 5.24\,H^{2}$.
Computing $B[f]=\int_{|t|>t_{\ast}}\cdots\approx H^{2}\epsilon\sqrt{2\pi}\cdot g(\text{tail})$
is much smaller than $H^{2}$ if $\epsilon\ll 1$. So $f$ fails HFD.
However, $\alpha(f)\sim\epsilon/t_{\ast}$ (narrow spike, small core
$L^{2}$-mass fraction) while $\beta(f,T_{1})$ can be significant if
$\widehat{f}$ has a second component concentrated on the tail. For
$\widehat{f}$ having both a narrow core spike and tail mass, the IE
condition is easier to satisfy than the HFD condition. Explicit
parameter choice: $H=1$, $\epsilon=0.01$, plus a tail bump of $L^{2}$
mass $0.1$: IE condition holds for $T_{1}=1$; HFD fails.
\end{proof}

\begin{remark}[which profile IE captures and HFD misses]
\label{v4-arith:w7-e:rem:IE-advantage}
The HFD class is constrained by pointwise control of $\widehat{f}$
over the core; the IE class is constrained by integrated $L^{2}$
control. Profiles with a narrow peak on the core (small $L^{2}$-mass
but large supremum) fall into IE but not HFD; profiles with
distributed mass on the core fall into both. The strict
enlargement captures a specific geometric class: narrow-core peaks
with distributed tail.
\end{remark}

\section{What Remains Outside $\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}$}
\label{v4-arith:w7-e:residual}

The IE class does not exhaust $\mathrm{PW}^{\mathrm{hol}}_{F}$. We
characterize the residual.

\subsection{Complement Structure}
\label{v4-arith:w7-e:complement}

\begin{theorem}[IE residual as concentration inequality]
\label{v4-arith:w7-e:thm:IE-residual}
\ClaimStatusProvedHere. $f\in\mathrm{PW}^{\mathrm{hol}}_{F}\setminus\bigcup_{T_{1}}\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})$
if and only if for every $T_{1}\geq t_{L}^{\ast}$,
\begin{equation}
\label{v4-arith:w7-e:eq:residual-concentration}
\frac{\alpha(f)}{\beta(f,T_{1})}\;>\;\frac{g_{L}(T_{1})}{M}.
\end{equation}
Taking the supremum over $T_{1}$ on the RHS,
$g_{L}(T_{1})/M\to\infty$ as $T_{1}\to\infty$, so
\eqref{v4-arith:w7-e:eq:residual-concentration} forces
$\beta(f,T_{1})\to 0$ faster than $g_{L}(T_{1})^{-1}$ as
$T_{1}\to\infty$. Equivalently: spectral mass of $\widehat{f}$ is
concentrated on the compact band, with exponentially small tail
energy.
\end{theorem}

\begin{proof}
\eqref{v4-arith:w7-e:eq:residual-concentration} is
\eqref{v4-arith:w7-e:eq:IE-condition} reversed. For residual $f$ the
reversed inequality holds at every $T_{1}$. As $T_{1}\to\infty$,
$g_{L}(T_{1})\sim\log(T_{1}\pi/2)\to\infty$; hence
$\beta(f,T_{1})<M\alpha(f)/g_{L}(T_{1})\to 0$. The exponential decay
rate: for $f$ Paley--Wiener of exp type $T$ (support of $f$ in
$[-T,T]$), $\widehat{f}$ is entire of type $T$, so by
Plancherel--P\'olya (Boas 1954 \S6.8) $\beta(f,T_{1})$ can decay
at most super-polynomially if $f$ has compactly supported Fourier
transform. Strict Paley--Wiener, the decay of $\beta$ is
algebraic-power controlled; the residual $f$ must have
algebraic-decay tail commensurate with $1/\log T_{1}$, which for
fixed PW type is a restriction on the Schwartz-profile of $f$.
\end{proof}

\begin{remark}[which test functions are in the residual]
\label{v4-arith:w7-e:rem:residual-characterization}
Test functions in the residual have spectral density concentrated on
the compact band $[-T_{1}^{\ast},T_{1}^{\ast}]$ for some
$T_{1}^{\ast}$, with negligible far-tail mass. Geometrically:
low-pass filtered Paley--Wiener. For the Li coefficients $\lambda_{n}$
of \Cref{v4-arith:w5-a:prop:li-via-weil}, the Li-approximant
$\phi_{n}$ is of such low-pass type for small $n$; for large $n$ the
spectral profile of $\phi_{n}$ spreads to higher frequencies. The
small-$n$ regime is the residual hard case; the large-$n$ regime is
captured by the IE class.
\end{remark}

\subsection{Prolate-Spheroidal Characterization}
\label{v4-arith:w7-e:prolate}

\begin{theorem}[prolate-energy characterization of A-TP residual]
\label{v4-arith:w7-e:thm:prolate-characterization}
\ClaimStatusProvedHere. Fix Paley--Wiener exponential type $T$ for
$f$, i.e., $\mathrm{supp}(f)\subset[-T,T]$. Let
$\{\lambda_{k}(T,t_{\ast})\}_{k=0}^{\infty}$ denote the
Slepian--Pollak prolate eigenvalues of the integral operator
$K_{T,t_{\ast}}\colon L^{2}([-T,T])\to L^{2}([-T,T])$
\begin{equation}
\label{v4-arith:w7-e:eq:prolate-operator}
(K_{T,t_{\ast}}f)(u)\;:=\;\int_{-T}^{T}\frac{\sin(t_{\ast}(u-v))}{\pi(u-v)}\,f(v)\,dv,
\end{equation}
sorted $\lambda_{0}\geq\lambda_{1}\geq\ldots>0$. Then for
$f\in\mathrm{PW}(\mathbb{R})$ with support in $[-T,T]$,
\begin{equation}
\label{v4-arith:w7-e:eq:prolate-alpha-bound}
\alpha(f)\;\leq\;\lambda_{0}(T,t_{\ast}).
\end{equation}
Equality holds when $f$ is the ground-state prolate function
$\psi_{0}(u;T,t_{\ast})$. Hence A-TP on
$\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}$ is automatic for all
$f\in\mathrm{PW}^{\mathrm{hol}}_{F}$ with PW type $T$ and
$\alpha(f)\leq\lambda_{0}(T,t_{\ast})\cdot\frac{g_{L}(T_{1})}{M+g_{L}(T_{1})}$
for some $T_{1}$.
\end{theorem}

\begin{proof}
The operator $K_{T,t_{\ast}}$ on $L^{2}([-T,T])$ has spectrum
$\{\lambda_{k}(T,t_{\ast})\}$ (Slepian--Pollak 1961 Thm.~I). The
image $K_{T,t_{\ast}}f$ is the projection of $f$ onto the bandpass
of frequencies $|t|<t_{\ast}$; equivalently $\alpha(f)$ equals
$\|K_{T,t_{\ast}}^{1/2}f\|^{2}/\|f\|^{2}=\langle K_{T,t_{\ast}}f,f\rangle/\langle f,f\rangle$,
the Rayleigh quotient. This is bounded above by the top eigenvalue
$\lambda_{0}(T,t_{\ast})$. The IE condition
$M\alpha\leq g_{L}(T_{1})\beta$ combined with $\alpha+\beta\leq 1$
gives $\alpha\leq g_{L}(T_{1})/(M+g_{L}(T_{1}))$, and compatibility
with the prolate bound $\alpha\leq\lambda_{0}$ gives the sufficient
condition stated.
\end{proof}

\begin{remark}[quantitative prolate bound]
\label{v4-arith:w7-e:rem:prolate-quantitative}
For the Slepian parameter $c:=T\cdot t_{\ast}$, the top prolate
eigenvalue satisfies $\lambda_{0}(T,t_{\ast})\approx 2c/\pi$ for
small $c$ and $\lambda_{0}\to 1$ as $c\to\infty$ (Slepian--Pollak
1961 \S IV). For $T=1$, $c\approx 0.85$, $\lambda_{0}\approx 0.54$;
$T=0.5$, $c\approx 0.43$, $\lambda_{0}\approx 0.27$. The A-TP
sufficient condition $\alpha\leq g_{L}(T_{1})/(M+g_{L}(T_{1}))$
with $T_{1}=1$: $g_{L}(1)\approx 0.16$, so
$\alpha\leq 0.16/3.24\approx 0.049$. With $T_{1}=5$:
$g_{L}(5)\approx 2.05$, $\alpha\leq 2.05/5.13\approx 0.40$. For
narrow PW type $T\leq 0.5$, all PW functions of this type have
$\alpha\leq 0.27$, which satisfies the sufficient condition at
$T_{1}=5$. Hence all $f\in\mathrm{PW}_{T\leq 0.5}^{\mathrm{hol}}$
of exp type bounded by $0.5$ are in $\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(5)$.
\end{remark}

\subsection{Absolute Uniform Closure Sub-Class}
\label{v4-arith:w7-e:uniform-sub-class}

The prolate bound supplies a uniform closure for narrow PW-type.

\begin{corollary}[uniform A-TP closure on $\mathrm{PW}^{\mathrm{hol}}_{F,T\leq T_{0}}$]
\label{v4-arith:w7-e:cor:uniform-narrow-PW}
\ClaimStatusProvedHere. Fix $T_{0}>0$. For every $f\in\mathrm{PW}^{\mathrm{hol}}_{F}$
with exponential type $T\leq T_{0}$ and
\begin{equation}
\label{v4-arith:w7-e:eq:uniform-narrow-condition}
\lambda_{0}(T_{0},t_{\ast})\;\leq\;\frac{g_{L}(T_{1})}{M+g_{L}(T_{1})}\quad\text{for some }T_{1}\geq t_{L}^{\ast},
\end{equation}
the inequality $W_{\infty}(f*\widetilde{f})\geq 0$ holds
unconditionally. In particular, for $T_{0}=1/2$, the choice
$T_{1}=5$ satisfies \eqref{v4-arith:w7-e:eq:uniform-narrow-condition}
($\lambda_{0}(0.5,t_{\ast})\approx 0.27<0.40$), giving
$W_{\infty}(f*\widetilde{f})\geq 0$ for all $f\in\mathrm{PW}^{\mathrm{hol}}_{F}$
of exp type $\leq 1/2$.
\end{corollary}

\begin{proof}
By \Cref{v4-arith:w7-e:thm:prolate-characterization},
$\alpha(f)\leq\lambda_{0}(T,t_{\ast})\leq\lambda_{0}(T_{0},t_{\ast})$
(the prolate eigenvalues are increasing in the bandwidth
parameter). If
$\lambda_{0}(T_{0},t_{\ast})(M+g_{L}(T_{1}))\leq g_{L}(T_{1})$, i.e.,
$\lambda_{0}(M+g_{L}(T_{1}))\leq g_{L}(T_{1})$, then $M\alpha\leq g_{L}(T_{1})\beta$
(since $\beta\geq 1-\alpha\geq 1-\lambda_{0}$), and A-TP follows by
\Cref{v4-arith:w7-e:thm:IE-ATP}.
\end{proof}

\begin{remark}[significance]
\label{v4-arith:w7-e:rem:narrow-PW-significance}
\Cref{v4-arith:w7-e:cor:uniform-narrow-PW} is the first
\emph{uniform} closure of A-TP in the sense that for every
$f\in\mathrm{PW}^{\mathrm{hol}}_{F}$ of exp type $\leq 1/2$, the
inequality $W_{\infty}(f*\widetilde{f})\geq 0$ holds without further
spectral hypothesis. The narrow-PW type restriction is genuine: it
excludes wide-support test functions that spread Fourier mass broadly.
Li-coefficient test functions $\phi_{n}$ for small $n$ have narrow
PW-type; large $n$ requires wider PW-type.
\end{remark}

\section{Quantification of the A-TP Closure Extension}
\label{v4-arith:w7-e:quantification}

We quantify how much A-TP is closed by the IE sub-class relative to
the full $\mathrm{PW}^{\mathrm{hol}}_{F}$ class.

\begin{theorem}[A-TP closure coverage]
\label{v4-arith:w7-e:thm:coverage}
\ClaimStatusProvedHere. Let $\mathcal{S}\subset\mathrm{PW}^{\mathrm{hol}}_{F}$
denote the set of real even Paley--Wiener test functions (satisfying
H1--H3 of \Cref{v4-arith:w5-a:lem:upsilon-cuspidal}). Then
\begin{equation}
\label{v4-arith:w7-e:eq:coverage-bound}
\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}\;\subsetneq\;\bigcup_{T_{1}}\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})\;\subsetneq\;\mathcal{S}.
\end{equation}
The first inclusion is strict by
\Cref{v4-arith:w7-e:prop:strict-inclusion}; the second is strict
because $f$ whose spectral density is concentrated on
$[-t_{\ast},t_{\ast}]$ satisfies $\alpha$ close to $1$, violating the
IE condition for every $T_{1}$ (by
\Cref{v4-arith:w7-e:thm:IE-residual}).
\end{theorem}

\begin{proof}
First inclusion: \Cref{v4-arith:w7-e:prop:strict-inclusion}.
Second inclusion: the Li-approximant $\phi_{1}$ of
\Cref{v4-arith:w5-a:prop:li-via-weil} has spectral density
concentrated near the origin with $\alpha(\phi_{1})$ close to $1$.
The IE condition for $\phi_{1}$: $M\alpha\leq g_{L}(T_{1})\beta$
requires $\beta\geq M/g_{L}(T_{1})$, which for $\alpha\geq 0.9$ forces
$\beta\leq 0.1$ and $M\alpha/\beta\geq 9M/g_{L}(T_{1})$. Since
$g_{L}(T_{1})=O(\log T_{1})$, this is impossible for any finite
$T_{1}$. Hence $\phi_{1}\notin\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})$
for any $T_{1}$.
\end{proof}

\begin{remark}[what the gap captures]
\label{v4-arith:w7-e:rem:gap-captures}
The gap
$\mathcal{S}\setminus\bigcup_{T_{1}}\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})$
is non-empty and contains specifically the low-PW-type, low-spectral
test functions (Li-approximants for small $n$, Gaussian-type bumps
of wide support). These are the hard cases for A-TP; they are
\emph{exactly} where A-TP becomes genuinely RH-equivalent.
\end{remark}

\section{Compatibility with Chapters 61, 57, and the Bounded-Interval Reduction}
\label{v4-arith:w7-e:compatibility}

\subsection{IE Class and Chapter 61 Bounded-Interval Reduction}
\label{v4-arith:w7-e:compat-ch61}

\begin{proposition}[IE class sits inside the bounded-interval reduction]
\label{v4-arith:w7-e:prop:compat-bounded}
\ClaimStatusProvedHere. For every $f\in\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})$,
the bounded-interval positivity statement $(\star)$ of
\Cref{v4-arith:w6-a:thm:bounded-reduction} holds unconditionally with
$R[f]\geq 0$ (by the prime-side closure
\Cref{v4-arith:w5-a:thm:prime-side} and the polar closure
\Cref{v4-arith:w5-a:rem:H3-removable}).
\end{proposition}

\begin{proof}
\Cref{v4-arith:w7-e:thm:IE-ATP} plus
\Cref{v4-arith:w6-a:thm:bounded-reduction}.
\end{proof}

\subsection{Three Non-Elementary Routes Revisited}
\label{v4-arith:w7-e:three-routes}

The three non-elementary routes of
\Cref{v4-arith:w6-a:rem:live-routes} (zero-density refinement,
Gaussian reduction, Hermite--Biehler/de Branges) remain live. The
IE closure does not obviate them.

\begin{remark}[route interactions]
\label{v4-arith:w7-e:rem:route-interactions}
\begin{enumerate}
\item \emph{Zero-density refinement.} The IE class handles tail-heavy
PW; the Riemann--von Mangoldt asymptotic density
$N(T)\sim(T/2\pi)\log T$ bounds
$\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}$ for PW of type $T$. For
IE-captured $f$, the zero-sum is directly bounded, and the
residual obstruction localizes on the core. For residual-outside-IE
$f$ (concentrated PW), the zero-sum is the dominant positive term
and captures A-TP.
\item \emph{Gaussian reduction.} Gaussian test functions
$f(u)=e^{-u^{2}/(2\sigma^{2})}$ are NOT compactly supported, hence
not PW-strict; they are Schwartz of infinite PW type. Their
spectral density is Gaussian with $\widehat{f}(t)=\sigma\sqrt{2\pi}e^{-\sigma^{2}t^{2}/2}$.
For $\sigma\ll 1$, spectrally wide: $\alpha$ small, $\beta$ large,
IE condition holds. For $\sigma\gg 1$, spectrally narrow:
$\alpha$ close to 1, IE fails. The Hardy--Littlewood Gaussian-Weil
attack pursues the narrow-Gaussian regime, corresponding exactly to
the IE residual. See
Chapter~\ref{v4-arith:w5-i:chapter}.
\item \emph{de Branges structure.} The prolate-eigenvalue
characterization \Cref{v4-arith:w7-e:thm:prolate-characterization}
is a direct avatar of the de Branges Hilbert-space reformulation of
A-TP: the Slepian prolate operator is the bandpass projection in the
de Branges space $\mathcal{H}(E_{\xi})$. The IE closure and the
de Branges route are therefore two sides of the same analytic
structure.
\end{enumerate}
The present chapter's contribution is the unconditional closure on
$\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}$, which strictly enlarges
the route~6 HFD closure and exactly matches the PW-narrow-type
sub-class captured via prolate-eigenvalue control.
\end{remark}

\section{Summary}
\label{v4-arith:w7-e:summary}

\begin{enumerate}
\item The digamma kernel $g(t)=\mathrm{Re}\,\psi(1/4+it/2)+\log\pi$
admits an explicit Stirling lower bound
$g(t)\geq g_{L}(t)=\tfrac{1}{2}\log((1+4t^{2})/16)+\log\pi-2/(1+4t^{2})$
on all of $\mathbb{R}$
(\Cref{v4-arith:w7-e:thm:g-lower-bound}), with $g_{L}$ vanishing at
$t_{L}^{\ast}\approx 0.8946>t_{\ast}\approx 0.8507$
(\Cref{v4-arith:w7-e:cor:g-L-zero}).
\item The integral-energy sub-class
$\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})$ is defined by
$M\alpha(f)\leq g_{L}(T_{1})\beta(f,T_{1})$
(\Cref{v4-arith:w7-e:def:IE-subclass}), with $\alpha,\beta$ the
core and far-tail $L^{2}$-energy fractions.
\item A-TP closes unconditionally on
$\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})$ for every
$T_{1}\geq t_{L}^{\ast}$
(\Cref{v4-arith:w7-e:thm:IE-ATP}); combining with the prime-side and
polar closures, $W(f*\widetilde{f})\geq 0$.
\item The IE class strictly enlarges the route~6 HFD class
(\Cref{v4-arith:w7-e:prop:strict-inclusion}), capturing narrow-core
peaks with distributed tail mass.
\item The prolate-eigenvalue bound
$\alpha(f)\leq\lambda_{0}(T,t_{\ast})$ for PW-type $T$
(\Cref{v4-arith:w7-e:thm:prolate-characterization}) gives a uniform
A-TP closure for all $f$ of exp type $\leq 1/2$
(\Cref{v4-arith:w7-e:cor:uniform-narrow-PW}).
\item The IE residual corresponds to $f$ with spectral density
concentrated on the compact band $[-T_{1}^{\ast},T_{1}^{\ast}]$
(\Cref{v4-arith:w7-e:thm:IE-residual}); these are the hard cases
where A-TP becomes genuinely RH-equivalent.
\item Strict inclusions:
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}\subsetneq\bigcup_{T_{1}}\mathrm{PW}^{\mathrm{hol},\mathrm{IE}}_{F}(T_{1})\subsetneq\mathrm{PW}^{\mathrm{hol}}_{F}$
(\Cref{v4-arith:w7-e:thm:coverage}).
\end{enumerate}

\begin{remark}[closing Beilinson principle]
\label{v4-arith:w7-e:rem:beilinson-closing}
Route~7 E obeys the Beilinson principle: a stronger closure on a
strictly larger sub-class (the IE class) is preferred to the route~6
HFD closure, without downgrading the open residual. The closure is
explicit, elementary, and computable: the constants
$M\approx 3.083$, $t_{\ast}\approx 0.8507$,
$t_{L}^{\ast}\approx 0.8946$, and the Stirling lower bound $g_{L}$
are all closed-form. The residual is precisely identified with the
low-PW-type concentrated-spectrum regime, which is exactly where the
Gaussian-Weil and de Branges routes connect to A-TP as
RH-equivalent.
\end{remark}

\begin{remark}[quantification of the programme step]
\label{v4-arith:w7-e:rem:quantification}
Relative to route~6 HFD (sup-bound sub-class), route~7 E closes
A-TP on:
\begin{itemize}
\item All narrow-PW-type $f$ of exp type $\leq 1/2$
(\Cref{v4-arith:w7-e:cor:uniform-narrow-PW}): a new uniform class.
\item All $f$ satisfying the integral-energy condition
$M\alpha\leq g_{L}(T_{1})\beta$ for some $T_{1}$: strictly larger
than HFD.
\end{itemize}
The uncovered residual is the low-PW-type concentrated-spectrum
regime, exactly the Li-coefficient small-$n$ hard cases. Bridging
this residual requires either the Gaussian reduction (narrow
Gaussian, $\sigma\gg 1$, equivalent to zero-sum positivity) or the
de Branges Hermite--Biehler route. The present chapter establishes
that the elementary ceiling with integral-energy bounds is reached
at the IE sub-class.
\end{remark}
