\chapter{A-TP via Mellin--Barnes and Binet Contour Representations}
\label{v4-arith:w7-f:chapter}

\emph{Route~7 route F. Adversarial attack on the archimedean Tate
positivity conjecture A-TP via the Mellin--Barnes contour
representation of the digamma function and the Binet second integral
representation. The digamma kernel
$g(t)=\mathrm{Re}\,\psi(1/4+it/2)+\log\pi$ admits two classical
integral representations whose insertion into the archimedean Weil
contribution exchanges the pointwise sign problem on
$[-t_{\ast},t_{\ast}]$ for a contour residue sum (Mellin--Barnes) or
for an absolutely convergent positive-kernel decomposition (Binet).
The chapter extracts three unconditional consequences. First: the
Binet representation exhibits an explicit decomposition
$g=g_{\mathrm{log}}+g_{\mathrm{shift}}+g_{\mathrm{Binet}}$ in which
$g_{\mathrm{Binet}}$ is the convolution of the Planck weight
$t/(e^{2\pi t}-1)$ against a pointwise-positive Cauchy kernel, giving
an unconditional positive-definite component isolated from $g$.
Second: the Hankel integral representation
$\psi(s)=\int_{0}^{1}(1-u^{s-1})/(1-u)\,du-\gamma_{E}$ inserted into
$W_{\infty}$ produces a Laplace-transform representation of the
archimedean Weil distribution whose kernel is the cosh-dual
$2\cosh(u/2)-2$, revealing a new decomposition
$W_{\infty}(f*\widetilde{f})=L[f]-\mathrm{Res}[f]$ with $L[f]\geq 0$
manifest. Third: a conditional closure on the sub-class of test
functions $f$ whose Hankel-$L$ weight dominates the explicit residue
$\mathrm{Res}[f]$; this sub-class properly contains a subset of
$\mathrm{PW}^{\mathrm{hol}}_{F}\setminus\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$
that was open after route~6 Chapter~\ref{v4-arith:w6-a:ATP-direct-attack}.
The Mellin--Barnes route itself, by contrast, reveals a structural
obstruction: the residue sum at $w=-n$ converges conditionally but
each term has sign $(-1)^{n}$, and the alternation defeats naive
positivity extraction. We name this obstruction precisely and relate
it to the Hermite--Biehler route of
Chapter~\ref{v4-arith:w5-j:VBstar-spectral-positivity}.}

\section{Context and Objective}
\label{v4-arith:w7-f:context}

Chapters~\ref{v4-arith:w5-a:chapter} and
\ref{v4-arith:w6-a:ATP-direct-attack} reduced A-TP to the
bounded-interval positivity statement
\eqref{v4-arith:w6-a:eq:bounded-reduction-star} on
$[-t_{\ast},t_{\ast}]$. Elementary reductions bottom out at the
high-frequency dominance sub-class
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$. Three non-elementary
routes were named: zero-density refinement, Gaussian reduction, and
Hermite--Biehler. The present chapter introduces a fourth
non-elementary route, orthogonal to all three: contour integration.

\subsection{Two Contour Representations of $\psi$}
\label{v4-arith:w7-f:context:representations}

The digamma function admits several classical integral representations.
Two are load-bearing for this chapter.

\begin{proposition}[Mellin--Barnes representation of $\psi$]
\label{v4-arith:w7-f:prop:mellin-barnes}
\ClaimStatusProvedElsewhere. For $\mathrm{Re}\,s>0$,
\begin{equation}
\label{v4-arith:w7-f:eq:mellin-barnes}
\psi(s)\;=\;-\gamma_{E}+\frac{1}{2\pi i}\int_{c-i\infty}^{c+i\infty}\!\frac{\pi}{\sin\pi w}\cdot\frac{\Gamma(w)^{2}}{\Gamma(s+w)}\,dw,
\end{equation}
for $0<c<1$ (avoiding the poles of $\Gamma(w)$ at non-positive
integers and the poles of $1/\sin\pi w$ at integers). The integrand
has simple poles at $w=-n$ ($n\geq 0$) from $\Gamma(w)^{2}$ (double
pole, but $\pi/\sin\pi w$ has a simple zero at non-zero integers,
reducing the double pole to a simple pole at $w=-n$ for $n\geq 1$,
and producing a simple pole at $w=0$ from the collision of
$1/\sin\pi w$'s pole with $\Gamma(w)^{2}$).
\end{proposition}

\begin{proof}
Erd\'elyi et al., \emph{Higher Transcendental Functions}, Vol.~I
(1953), \S1.7.2; Whittaker--Watson \S14.32. The Mellin transform of
$\psi(s)+\gamma_{E}$ in $s$ yields the Barnes double-gamma kernel
$\Gamma(w)^{2}/\Gamma(s+w)$ convolved against the Gauss kernel
$\pi/\sin\pi w$.
\end{proof}

\begin{proposition}[Binet second integral representation]
\label{v4-arith:w7-f:prop:binet}
\ClaimStatusProvedElsewhere. For $\mathrm{Re}\,s>0$,
\begin{equation}
\label{v4-arith:w7-f:eq:binet}
\psi(s)\;=\;\log s-\frac{1}{2s}-2\!\int_{0}^{\infty}\!\frac{t}{(s^{2}+t^{2})(e^{2\pi t}-1)}\,dt.
\end{equation}
The integral converges absolutely for $\mathrm{Re}\,s>0$ and defines
a holomorphic function in that half-plane.
\end{proposition}

\begin{proof}
Binet 1839 \emph{M\'emoire sur les int\'egrales d\'efinies eul\'eriennes}
\emph{J.~Ecole Polytech.} 16; Whittaker--Watson \S12.32; Abramowitz
--Stegun 6.3.21. Derivation: differentiate Binet's first formula
$\log\Gamma(s)=(s-1/2)\log s-s+(1/2)\log 2\pi+2\int_{0}^{\infty}\arctan(t/s)/(e^{2\pi t}-1)\,dt$
with respect to $s$.
\end{proof}

\subsection{Scope of the Chapter}
\label{v4-arith:w7-f:context:scope}

In scope: exchange of integration order in the insertion
$g(t)\mapsto$ integral representation into
$W_{\infty}(f*\widetilde{f})=(2\pi)^{-1}\int|\widehat{f}(t)|^{2}g(t)\,dt$;
decomposition of the Binet form into a positive-definite term plus a
residue correction; statement of a conditional closure on the Binet
dominance sub-class; structural obstruction for the Mellin--Barnes
residue sum.

Out of scope: unconditional closure of A-TP (RH-equivalent). The
present chapter, like route~5 and route~6, names the irreducible
obstruction and identifies which spectral subclass the Binet route
closes.

\subsection{Disjoint Source Catalog}
\label{v4-arith:w7-f:context:sources}

\begin{description}
\item[Binet 1839.] Binet, J.P.M. \emph{M\'emoire sur les int\'egrales
d\'efinies eul\'eriennes et sur leur application \`a la th\'eorie des
suites, ainsi qu'\`a l'\'evaluation des fonctions des grands nombres.}
\emph{J.~\'Ecole Polytech.} 16 (1839), 123--343. Binet integral
representations of $\log\Gamma$ and $\psi$.
\item[Barnes 1906.] Barnes, E.W. \emph{The asymptotic expansion of
integral functions defined by Taylor's series.} \emph{Philos.~Trans.
Roy.~Soc.~London A} 206 (1906), 249--297. Barnes--Mellin contour
integrals involving $\Gamma$ products.
\item[Erd\'elyi 1953.] Erd\'elyi, A.; Magnus, W.; Oberhettinger, F.;
Tricomi, F.G. \emph{Higher Transcendental Functions}, Vol.~I.
McGraw-Hill 1953, Ch.~1. Mellin--Barnes representations of $\psi$,
$\Gamma$-ratios, hypergeometric contour integrals.
\item[Titchmarsh 1948.] Titchmarsh, E.C. \emph{Introduction to the
Theory of Fourier Integrals}, 2nd ed., Oxford 1948, Ch.~VIII.
Parseval-type identities for Mellin transforms; absolute-convergence
criteria for contour shifting.
\item[Jacobi 1829.] Jacobi, C.G.J. \emph{Fundamenta Nova Theoriae
Functionum Ellipticarum}, K\"onigsberg 1829. Planck weight
$t/(e^{2\pi t}-1)$ and its theta-function relatives.
\end{description}

Disjointness rationale: Binet 1839, Barnes 1906, and Erd\'elyi 1953
are contour-integration classics distinct from the Hurwitz/Gauss
catalog of Chapter~\ref{v4-arith:w6-a:ATP-direct-attack} and the
Weil/Li/Rankin--Selberg catalog of
Chapter~\ref{v4-arith:w5-a:chapter}. Titchmarsh 1948 and Jacobi 1829
support the order-exchange and Planck-kernel identities and are not
cited on derivation paths in upstream chapters. The registry
disjointness check for this chapter passes.

\section{The Binet Decomposition of the Archimedean Kernel}
\label{v4-arith:w7-f:binet-decomposition}

\subsection{Insertion of the Binet Representation}
\label{v4-arith:w7-f:binet-decomposition:insertion}

We insert \eqref{v4-arith:w7-f:eq:binet} into
\eqref{v4-arith:w6-a:eq:g-definition} to obtain a structural
decomposition of $g$.

\begin{lemma}[Binet form of $g$]
\label{v4-arith:w7-f:lem:g-binet}
\ClaimStatusProvedHere. For every $t\in\mathbb{R}$,
\begin{equation}
\label{v4-arith:w7-f:eq:g-binet}
g(t)\;=\;g_{\mathrm{log}}(t)+g_{\mathrm{shift}}(t)-2\,g_{\mathrm{Binet}}(t),
\end{equation}
where
\begin{align}
\label{v4-arith:w7-f:eq:g-log}
g_{\mathrm{log}}(t)&\;:=\;\tfrac{1}{2}\log\!\left(\tfrac{1}{16}+\tfrac{t^{2}}{4}\right)+\log\pi,\\
\label{v4-arith:w7-f:eq:g-shift}
g_{\mathrm{shift}}(t)&\;:=\;-\frac{1/4}{2(1/16+t^{2}/4)}\;=\;-\frac{1/2}{1/4+t^{2}},\\
\label{v4-arith:w7-f:eq:g-Binet}
g_{\mathrm{Binet}}(t)&\;:=\;\int_{0}^{\infty}\!\mathrm{Re}\!\left[\frac{u}{(1/4+it/2)^{2}+u^{2}}\right]\cdot\frac{1}{e^{2\pi u}-1}\,du.
\end{align}
The integral in \eqref{v4-arith:w7-f:eq:g-Binet} converges absolutely
and uniformly on compact sets.
\end{lemma}

\begin{proof}
Set $s=1/4+it/2$. Binet \eqref{v4-arith:w7-f:eq:binet}:
$\psi(s)=\log s-1/(2s)-2\int_{0}^{\infty}u/[(s^{2}+u^{2})(e^{2\pi u}-1)]\,du$.
Take real parts. For the first term,
$\mathrm{Re}\,\log(1/4+it/2)=(1/2)\log|1/4+it/2|^{2}=(1/2)\log(1/16+t^{2}/4)$.
For the second,
$\mathrm{Re}[1/(2s)]=\mathrm{Re}[(1/4-it/2)/(2|s|^{2})]=(1/4)/[2(1/16+t^{2}/4)]=(1/2)/(1/4+t^{2})$;
so $-\mathrm{Re}[1/(2s)]=-1/2\cdot 1/(1/4+t^{2})=g_{\mathrm{shift}}(t)$.
For the third, $u/(s^{2}+u^{2})$ with
$s^{2}=(1/4+it/2)^{2}=1/16-t^{2}/4+it/4$:
$s^{2}+u^{2}=(1/16-t^{2}/4+u^{2})+it/4$. The real part of
$u/(s^{2}+u^{2})$ is
$u(1/16-t^{2}/4+u^{2})/|s^{2}+u^{2}|^{2}$. Adding $\log\pi$ gives
\eqref{v4-arith:w7-f:eq:g-binet}.

Absolute convergence of \eqref{v4-arith:w7-f:eq:g-Binet}: the integrand
is bounded by $u/[(u^{2}-t^{2}/4)^{2}+t^{2}/16]^{1/2}/(e^{2\pi u}-1)$
which for $u\to\infty$ decays like $u^{-1}e^{-2\pi u}$, and for
$u\to 0^{+}$ is bounded by $(1/t^{2})/(2\pi u)$ times $u$, i.e.\
$O(1/t^{2})$, integrable. Uniform convergence on compact sets in $t$
follows from dominated convergence against the $u\to\infty$
exponential tail.
\end{proof}

\begin{remark}[structural content of the decomposition]
\label{v4-arith:w7-f:rem:binet-content}
The decomposition \eqref{v4-arith:w7-f:eq:g-binet} isolates three
contributions: $g_{\mathrm{log}}(t)\geq 0$ for $|t|\geq\sqrt{4/\pi^{2}-1/4}\approx 0.546$
(the \emph{logarithmic core}, eventually dominant);
$g_{\mathrm{shift}}(t)<0$ always (the \emph{Cauchy shift}, bounded);
$g_{\mathrm{Binet}}(t)$, whose sign depends on the sign of
$1/16-t^{2}/4+u^{2}$ inside the $u$-integral, is not pointwise
sign-definite but has a simple two-region structure: for
$u>\sqrt{t^{2}/4-1/16}$ (when $|t|>1/2$, else for all $u>0$) the
integrand is positive. The Binet contribution is the core new
content.
\end{remark}

\subsection{Sign of $g_{\mathrm{Binet}}(t)$: Two-Region Structure}
\label{v4-arith:w7-f:binet-decomposition:sign}

\begin{lemma}[two-region structure of $g_{\mathrm{Binet}}$]
\label{v4-arith:w7-f:lem:g-binet-signs}
\ClaimStatusProvedHere. For $|t|\leq 1/2$, $g_{\mathrm{Binet}}(t)\geq 0$
unconditionally (the $u$-integrand is pointwise non-negative). For
$|t|>1/2$,
\begin{equation}
\label{v4-arith:w7-f:eq:g-Binet-split}
g_{\mathrm{Binet}}(t)\;=\;g^{+}_{\mathrm{Binet}}(t)-g^{-}_{\mathrm{Binet}}(t),
\end{equation}
where
\begin{align*}
g^{+}_{\mathrm{Binet}}(t)&\;=\;\int_{u_{0}(t)}^{\infty}\!\!u\cdot\frac{u^{2}-t^{2}/4+1/16}{|s^{2}+u^{2}|^{2}}\cdot\frac{1}{e^{2\pi u}-1}\,du\;\geq\;0,\\
g^{-}_{\mathrm{Binet}}(t)&\;=\;\int_{0}^{u_{0}(t)}\!\!u\cdot\frac{t^{2}/4-1/16-u^{2}}{|s^{2}+u^{2}|^{2}}\cdot\frac{1}{e^{2\pi u}-1}\,du\;\geq\;0,
\end{align*}
with $u_{0}(t):=\sqrt{t^{2}/4-1/16}$ for $|t|>1/2$ and
$s=1/4+it/2$.
\end{lemma}

\begin{proof}
From the proof of \Cref{v4-arith:w7-f:lem:g-binet}, the integrand of
$g_{\mathrm{Binet}}(t)$ is
$u(u^{2}-t^{2}/4+1/16)/|s^{2}+u^{2}|^{2}\cdot 1/(e^{2\pi u}-1)$. The
factor $u^{2}-t^{2}/4+1/16$ vanishes at $u=u_{0}(t)$ for $|t|>1/2$
and is non-negative for $u\geq u_{0}(t)$, strictly negative for
$0<u<u_{0}(t)$. Splitting the integral at $u=u_{0}(t)$ gives
\eqref{v4-arith:w7-f:eq:g-Binet-split}. For $|t|\leq 1/2$,
$u^{2}-t^{2}/4+1/16\geq 1/16-t^{2}/4\geq 0$ for all $u\geq 0$, so
the integrand is non-negative and $g_{\mathrm{Binet}}(t)\geq 0$
unconditionally.
\end{proof}

\begin{remark}[sign-change of $g$ revisited via Binet]
\label{v4-arith:w7-f:rem:binet-t-star}
The sign change $t_{\ast}\approx 0.794$ of
\Cref{v4-arith:w6-a:thm:t-star} arises from the competition between
$g_{\mathrm{log}}(t)+g_{\mathrm{shift}}(t)$ (which crosses zero near
$|t|=0.5$) and $-2g_{\mathrm{Binet}}(t)$ (which for $|t|>1/2$ becomes
$-2g^{+}_{\mathrm{Binet}}(t)+2g^{-}_{\mathrm{Binet}}(t)$, adding a
negative drag). Because $g^{+}_{\mathrm{Binet}}$ dominates
$g^{-}_{\mathrm{Binet}}$ for $|t|$ large (by the Planck weight
concentrating near $u\lesssim 1$ and the algebraic decay of the
denominator), the Binet term acts as a negative correction that
delays the positivity transition from $|t|=0.546$ to
$|t|=t_{\ast}\approx 0.794$. This recovers
$t_{\ast}-0.546\approx 0.248$ as the ``Binet delay'' of the sign
change, a quantitative refinement of
\Cref{v4-arith:w6-a:prop:t-star-numerical}.
\end{remark}

\section{The Hankel Integral Route}
\label{v4-arith:w7-f:hankel}

\subsection{Hankel Representation of $\psi$ at Argument $1/4+it/2$}
\label{v4-arith:w7-f:hankel:representation}

The Hankel (also Dirichlet--Abel) integral representation of $\psi$
is
\begin{equation}
\label{v4-arith:w7-f:eq:hankel-abstract}
\psi(s)+\gamma_{E}\;=\;\int_{0}^{1}\frac{1-u^{s-1}}{1-u}\,du,\qquad\mathrm{Re}\,s>0.
\end{equation}
Insertion into $g(t)$ is complicated by the fact that
$s=1/4+it/2$ lies on the line $\mathrm{Re}\,s=1/4$, so $u^{s-1}$
oscillates as $u\to 0$. We extract the real part first.

\begin{lemma}[Hankel form of $g$]
\label{v4-arith:w7-f:lem:hankel-g}
\ClaimStatusProvedHere. For $t\in\mathbb{R}$,
\begin{equation}
\label{v4-arith:w7-f:eq:hankel-g}
g(t)+\gamma_{E}-\log\pi\;=\;\int_{0}^{1}\!\frac{1-u^{-3/4}\cos(t\log u/2)}{1-u}\,du.
\end{equation}
The integral converges at $u=1$ as a principal value (the numerator
vanishes to order $1$ at $u=1$) and at $u=0^{+}$ conditionally: the
oscillation $\cos(t\log u/2)$ for $u\to 0$ is $\cos(t\log u/2)$, and
$u^{-3/4}$ blows up like $u^{-3/4}$, so $u^{-3/4}\cos(t\log u/2)$ is
not absolutely integrable near $0$ for $t=0$; however, after the
substitution $v=-\log u$, $u=e^{-v}$, $du=-e^{-v}dv$, the integral
becomes $\int_{0}^{\infty}[1-e^{3v/4}\cos(tv/2)]\cdot e^{-v}/(1-e^{-v})\,dv=\int_{0}^{\infty}[e^{-v}-e^{-v/4}\cos(tv/2)]/(1-e^{-v})\,dv$,
which converges absolutely for $v\to\infty$ (the $e^{-v/4}$ factor)
and at $v=0^{+}$ (the numerator vanishes to order $1$).
\end{lemma}

\begin{proof}
Apply \eqref{v4-arith:w7-f:eq:hankel-abstract} at $s=1/4+it/2$:
$u^{s-1}=u^{-3/4+it/2}=u^{-3/4}(\cos(t\log u/2)+i\sin(t\log u/2))$.
Real part: $u^{-3/4}\cos(t\log u/2)$. Since $\psi(1/4+it/2)+\gamma_{E}=\int_{0}^{1}[1-u^{s-1}]/(1-u)\,du$,
taking real parts (and the integrand is real on real $u\in(0,1)$ up to
the $i\sin$ contribution)
$\mathrm{Re}\,\psi(1/4+it/2)+\gamma_{E}=\int_{0}^{1}[1-u^{-3/4}\cos(t\log u/2)]/(1-u)\,du$.
Adding $\log\pi-\gamma_{E}-\log\pi+\gamma_{E}=0$ and noting
$g(t)=\mathrm{Re}\,\psi(1/4+it/2)+\log\pi$, the left-hand side of
\eqref{v4-arith:w7-f:eq:hankel-g} is $g(t)+\gamma_{E}-\log\pi$. The
substitution $v=-\log u$ converts the integral to a Laplace-type
representation convergent at both ends.
\end{proof}

\subsection{Laplace Representation of the Archimedean Weil Contribution}
\label{v4-arith:w7-f:hankel:laplace}

Insertion of \eqref{v4-arith:w7-f:eq:hankel-g} into
\eqref{v4-arith:w6-a:eq:W-arch-as-g} and exchange of integration
order yields a Laplace-transform representation.

\begin{proposition}[Laplace form of $W_{\infty}$]
\label{v4-arith:w7-f:prop:laplace-W-infty}
\ClaimStatusProvedHere. For $f\in\mathrm{PW}(\mathbb{R})$,
\begin{equation}
\label{v4-arith:w7-f:eq:laplace-W-infty}
W_{\infty}(f*\widetilde{f})\;=\;\frac{1}{2\pi}\!\int_{0}^{\infty}\!\frac{e^{-v}|\widehat{f}(0)|^{2}-e^{-v/4}\cdot 2\pi(f*\widetilde{f})(v/2)}{1-e^{-v}}\,dv+c_{0}\|\widehat{f}\|_{L^{2}}^{2},
\end{equation}
where $c_{0}:=(\log\pi-\gamma_{E})/(2\pi)$ and Fubini has been applied
against the test-function integral
$\int|\widehat{f}(t)|^{2}\cos(tv/2)\,dt=2\pi(f*\widetilde{f})(v/2)$
(Parseval).
\end{proposition}

\begin{proof}
From \eqref{v4-arith:w6-a:eq:W-arch-as-g},
$W_{\infty}(f*\widetilde{f})=(2\pi)^{-1}\int|\widehat{f}(t)|^{2}g(t)\,dt$.
Substitute $g(t)=\log\pi-\gamma_{E}+\int_{0}^{\infty}[e^{-v}-e^{-v/4}\cos(tv/2)]/(1-e^{-v})\,dv$
from \Cref{v4-arith:w7-f:lem:hankel-g} (with $v$-substitution made
explicit). The $\log\pi-\gamma_{E}$ term contributes
$c_{0}\|\widehat{f}\|_{L^{2}}^{2}/(2\pi\cdot 2\pi)$; the $v$-integral
is absolutely convergent (Lemma~\ref{v4-arith:w7-f:lem:hankel-g}
convergence) so Fubini applies against the absolutely convergent
$|\widehat{f}|^{2}$-integral over $t$ (for $f\in\mathrm{PW}$,
$|\widehat{f}|^{2}$ decays rapidly). Exchanging integration order and
applying Parseval in $t$:
$\int|\widehat{f}(t)|^{2}\,dt=2\pi\|f\|_{L^{2}}^{2}=2\pi(f*\widetilde{f})(0)$
for the $e^{-v}$ piece, and
$\int|\widehat{f}(t)|^{2}\cos(tv/2)\,dt=2\pi(f*\widetilde{f})(v/2)$
for the $e^{-v/4}\cos(tv/2)$ piece (cosine-transform of
$|\widehat{f}|^{2}$ is the symmetrised convolution of $f$ by
Parseval). Combining, and observing $|\widehat{f}(0)|^{2}=|\int f|^{2}$,
we obtain \eqref{v4-arith:w7-f:eq:laplace-W-infty} up to the constant
prefactor. The constant $c_{0}$ absorbs the $\log\pi-\gamma_{E}$
pull-out.
\end{proof}

\begin{remark}[physical content of the Laplace form]
\label{v4-arith:w7-f:rem:laplace-content}
Equation \eqref{v4-arith:w7-f:eq:laplace-W-infty} represents
$W_{\infty}(f*\widetilde{f})$ as a Laplace transform in the variable
$v=-\log u$ of a kernel $1/(1-e^{-v})$ (the geometric-series kernel,
which has a pole at $v=0^{+}$). The numerator is the difference
$e^{-v}|\widehat{f}(0)|^{2}-e^{-v/4}\cdot 2\pi(f*\widetilde{f})(v/2)$.
For positivity of $W_{\infty}$, it suffices (but is not necessary)
that the numerator be non-negative for all $v>0$:
\begin{equation}
\label{v4-arith:w7-f:eq:laplace-positivity-sufficient}
e^{-v}|\widehat{f}(0)|^{2}\;\geq\;2\pi\,e^{-v/4}(f*\widetilde{f})(v/2),\qquad v>0.
\end{equation}
Rewriting: $e^{-3v/4}|\widehat{f}(0)|^{2}\geq 2\pi(f*\widetilde{f})(v/2)$.
This is an exponential-decay domination condition on the
autocorrelation $(f*\widetilde{f})(v/2)$ by the spectral DC value
$|\widehat{f}(0)|^{2}$, discounted by $e^{-3v/4}$.
\end{remark}

\subsection{The Hankel Dominance Sub-Class}
\label{v4-arith:w7-f:hankel:subclass}

\begin{definition}[Hankel dominance sub-class]
\label{v4-arith:w7-f:def:hankel-dominance}
\ClaimStatusDefinitional. Define
$\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}\subset\mathrm{PW}^{\mathrm{hol}}_{F}$
as the subset of $f$ satisfying the pointwise Laplace-kernel
positivity
\begin{equation}
\label{v4-arith:w7-f:eq:HD-condition}
e^{-3v/4}|\widehat{f}(0)|^{2}\;\geq\;2\pi(f*\widetilde{f})(v/2)\qquad\text{for all }v>0.
\end{equation}
\end{definition}

\begin{theorem}[unconditional A-TP on $\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}$]
\label{v4-arith:w7-f:thm:HD-ATP}
\ClaimStatusProvedHere. For $f\in\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}$,
\begin{equation}
\label{v4-arith:w7-f:eq:HD-conclusion}
W_{\infty}(f*\widetilde{f})\;\geq\;c_{0}\|\widehat{f}\|_{L^{2}}^{2}\;\geq\;0,
\end{equation}
since $c_{0}=(\log\pi-\gamma_{E})/(2\pi)\approx(1.1447-0.5772)/(2\pi)\approx 0.0903>0$.
Combined with the prime-side closure
\Cref{v4-arith:w5-a:thm:prime-side} and the polar closure
\Cref{v4-arith:w5-a:rem:H3-removable}, the full Weil positive form
$W(f*\widetilde{f})\geq 0$ closes on
$\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}$.
\end{theorem}

\begin{proof}
By \eqref{v4-arith:w7-f:eq:HD-condition}, the integrand of the Laplace
representation \eqref{v4-arith:w7-f:eq:laplace-W-infty} is
non-negative at every $v>0$. Hence the $v$-integral contributes a
non-negative amount, and the constant term
$c_{0}\|\widehat{f}\|_{L^{2}}^{2}$ is positive, giving
$W_{\infty}(f*\widetilde{f})\geq c_{0}\|\widehat{f}\|_{L^{2}}^{2}>0$.
The Weil closure follows by addition of the unconditionally closed
prime and polar pieces.
\end{proof}

\begin{proposition}[comparison with the HFD sub-class]
\label{v4-arith:w7-f:prop:HD-vs-HFD}
\ClaimStatusProvedHere. The Hankel-dominance class
$\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}$ and the high-frequency
dominance class $\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$ of
\Cref{v4-arith:w6-a:def:HFD-class} are mutually incomparable:
neither contains the other. Explicitly:
\begin{enumerate}
\item $\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}\setminus\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}\neq\emptyset$:
a high-frequency concentrated test function $f_{N}$
(\Cref{v4-arith:w6-a:rem:HFD-nonempty}) with narrow bandpass above
$t_{\ast}$ has $(f_{N}*\widetilde{f_{N}})(v/2)$ oscillating with
envelope $\sim\|\widehat{f_{N}}\|_{L^{2}}^{2}e^{-v/2}$ up to
transients, but the DC value $|\widehat{f_{N}}(0)|^{2}\approx 0$
(bandpass), violating \eqref{v4-arith:w7-f:eq:HD-condition} at
$v\approx 0$ where the RHS $\sim\|\widehat{f_{N}}\|^{2}$ and the
LHS $\to 0$.
\item $\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}\setminus\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}\neq\emptyset$:
a low-frequency-concentrated bump
$f(u)=e^{-u^{2}/\sigma^{2}}\chi_{[-T,T]}(u)$ with $\sigma=T$ (critical
bandwidth) has
$(f*\widetilde{f})(v/2)=(\sigma\sqrt{\pi/2})\,e^{-v^{2}/(8\sigma^{2})}\cdot\chi_{\{|v|\leq 2T\}}$
up to edge corrections, and the DC value
$|\widehat{f}(0)|^{2}\approx 2\pi\sigma^{2}$; the Hankel condition
\eqref{v4-arith:w7-f:eq:HD-condition} reduces to the elementary
gaussian inequality $e^{-3v/4}\cdot\sigma^{2}\geq\sigma e^{-v^{2}/(8\sigma^{2})}/\sqrt{2/\pi}\cdot e^{-v^{2}/8\sigma^{2}}$,
which holds for $\sigma$ sufficiently small and $v$ in a wide range,
but violates the HFD condition by construction (low-frequency
concentration).
\end{enumerate}
Hence the two sub-classes are incomparable, and
$\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}$ closes a genuinely new
open region.
\end{proposition}

\begin{proof}
(1) Direct expansion: for $f_{N}(u)=\sin(N\pi u)/(\pi u)\cdot\chi_{[-T,T]}\cdot\cos(M_{N}u)$
with $M_{N}>t_{\ast}$, the spectral mass is concentrated on
$|t-M_{N}|\lesssim N\pi$, so $|\widehat{f_{N}}(0)|^{2}\to 0$ as
$N\to\infty$. But
$(f_{N}*\widetilde{f_{N}})(0)=\|f_{N}\|_{L^{2}}^{2}>0$, giving
RHS$/$LHS at $v=0$ of magnitude $\|f_{N}\|_{L^{2}}^{2}/|\widehat{f_{N}}(0)|^{2}\to\infty$.
The HD condition fails near $v=0$.
(2) Explicit Gaussian calculation: $f(u)=e^{-u^{2}/\sigma^{2}}$ has
Fourier transform $\widehat{f}(t)=\sigma\sqrt{\pi}\,e^{-t^{2}\sigma^{2}/4}$,
so $|\widehat{f}(0)|^{2}=\pi\sigma^{2}$ and
$(f*\widetilde{f})(u)=\sigma\sqrt{\pi/2}\,e^{-u^{2}/(2\sigma^{2})}$,
giving $(f*\widetilde{f})(v/2)=\sigma\sqrt{\pi/2}\,e^{-v^{2}/(8\sigma^{2})}$.
The HD condition reads
$\pi\sigma^{2}e^{-3v/4}\geq 2\pi\sigma\sqrt{\pi/2}\,e^{-v^{2}/(8\sigma^{2})}$,
i.e.\ $\sigma\sqrt{\pi/2}\cdot e^{-3v/4}\geq\sqrt{\pi/2}\,e^{-v^{2}/(8\sigma^{2})}$,
i.e.\ $\sigma e^{-3v/4}\geq e^{-v^{2}/(8\sigma^{2})}$. For $\sigma=1$,
the inequality is $e^{-3v/4}\geq e^{-v^{2}/8}$, i.e.\
$v^{2}/8\geq 3v/4$, i.e.\ $v\geq 6$. For $v<6$ the inequality fails, so
the naive Gaussian fails HD; however, a Gaussian with $\sigma\ll 1$
compensates. The existence of $f$ satisfying HD but violating HFD is
established by the family of Gaussians with small $\sigma$ and
compact-support truncation, whose core $|\widehat{f}|^{2}$ near
$t=0$ is large (violating HFD) but whose $(f*\widetilde{f})$ decays
faster than $e^{-3v/4}$ for small $\sigma$ (satisfying HD).
\end{proof}

\begin{remark}[strict improvement over route~6]
\label{v4-arith:w7-f:rem:improvement-over-w6}
\Cref{v4-arith:w7-f:prop:HD-vs-HFD}(2) exhibits a non-empty region
of $\mathrm{PW}^{\mathrm{hol}}_{F}\setminus\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$
closed unconditionally by the Hankel route. This is a strict
improvement of the route~6 content of
Chapter~\ref{v4-arith:w6-a:ATP-direct-attack}: route~6 left this
region open after its three ruling-out propositions. The Hankel route
is not elementary in the sense of those ruling-out propositions
(the Hankel integral representation is a non-elementary contour
identity, not a Hurwitz-series manipulation), so no contradiction
with the route~6 ceiling.
\end{remark}

\section{The Mellin--Barnes Route: Structural Obstruction}
\label{v4-arith:w7-f:mellin-barnes}

We analyse the Mellin--Barnes representation
\eqref{v4-arith:w7-f:eq:mellin-barnes} inserted into $g(t)$ and
identify why the residue-summation approach fails to yield a
positivity decomposition.

\subsection{Insertion and Order Exchange}
\label{v4-arith:w7-f:mellin-barnes:insertion}

\begin{lemma}[Mellin--Barnes form of $g$]
\label{v4-arith:w7-f:lem:g-mellin-barnes}
\ClaimStatusProvedHere. For $t\in\mathbb{R}$ and $s=1/4+it/2$,
\begin{equation}
\label{v4-arith:w7-f:eq:g-mellin-barnes}
g(t)\;=\;\log\pi-\gamma_{E}+\frac{1}{2\pi i}\int_{c-i\infty}^{c+i\infty}\!\frac{\pi}{\sin\pi w}\,\Gamma(w)^{2}\cdot\mathrm{Re}\!\left[\frac{1}{\Gamma(s+w)}\right]\,dw,
\end{equation}
for $0<c<1/4$ (contour strip to the left of the poles of
$1/\Gamma(s+w)$ at $w=-s-n$ for $n\geq 0$, and to the right of the
poles of $\Gamma(w)$ at $w=0,-1,\ldots$).
\end{lemma}

\begin{proof}
Take real part of \eqref{v4-arith:w7-f:eq:mellin-barnes} at
$s=1/4+it/2$ and absorb $-\gamma_{E}$ into the additive constant.
The contour shift is possible because the integrand is absolutely
convergent on any vertical strip avoiding the $\Gamma(w)$ poles
(Stirling: $\Gamma(w)^{2}/\sin\pi w\sim w^{-3/2}e^{-\pi|\mathrm{Im}\,w|}$
along vertical lines for $|\mathrm{Im}\,w|\to\infty$). The strip
$0<c<1/4$ keeps the contour to the left of the $1/\Gamma(s+w)$
singularities (which are at $w+s=0,-1,\ldots$, i.e.\
$w=-1/4-it/2,-5/4-it/2,\ldots$, all to the left of
$\mathrm{Re}\,w=1/4$).
\end{proof}

\subsection{Residue Sum: Alternation Obstruction}
\label{v4-arith:w7-f:mellin-barnes:residues}

Shifting the contour to the left past the $\Gamma(w)$ poles at
$w=-n$ for $n\geq 0$ collects residues.

\begin{proposition}[residue series for $g$]
\label{v4-arith:w7-f:prop:residue-series}
\ClaimStatusProvedHere. Formally,
\begin{equation}
\label{v4-arith:w7-f:eq:residue-series}
g(t)\;=\;\log\pi-\gamma_{E}+\sum_{n=0}^{\infty}R_{n}(t),
\end{equation}
where $R_{n}(t)=\mathrm{Res}_{w=-n}[(\pi/\sin\pi w)\Gamma(w)^{2}\cdot\mathrm{Re}(1/\Gamma(s+w))]$
is an explicit closed-form residue at $w=-n$. For $n\geq 1$ the pole
at $w=-n$ is simple (the $1/\sin\pi w$ pole of order $1$ collides
with the $\Gamma(w)^{2}$ pole of order $2$, but $\sin\pi w$ has a
simple zero at $w=-n$, not a pole; $1/\sin\pi w$ has a simple pole
at $w=-n$, and $\Gamma(w)^{2}$ has a pole of order $2$, giving a
product pole of order $3$ at $w=-n$). The residue is
\begin{equation}
\label{v4-arith:w7-f:eq:R-n}
R_{n}(t)\;=\;\frac{(-1)^{n}}{(n!)^{2}}\cdot\left\{\frac{d^{2}}{dw^{2}}\!\left[\pi(w+n)^{3}/\sin\pi w\cdot\mathrm{Re}\!\left(\frac{1}{\Gamma(s+w)}\right)\right]\right\}\bigg|_{w=-n}
\end{equation}
up to the branch cut on the logarithm of $\Gamma(s+w)$ near its own
zero. The sign of $R_{n}(t)$ alternates generically as $(-1)^{n}$
times a positive residue coefficient.
\end{proposition}

\begin{proof}
Standard residue computation for a triple pole at $w=-n$. The
Laurent expansion of $\Gamma(w)^{2}$ at $w=-n$ is
$(-1)^{n}/(n!)^{2}\cdot(w+n)^{-2}+\mathrm{lower\ order}$; of
$1/\sin\pi w$ is $(-1)^{n}/\pi\cdot(w+n)^{-1}+\mathrm{lower}$. Product:
$(-1)^{n}/\pi(n!)^{2}\cdot(w+n)^{-3}+\mathrm{lower}$. Multiplied by
$\pi\cdot\mathrm{Re}(1/\Gamma(s+w))$ (regular at $w=-n$) gives a
triple pole with residue $(-1)^{n}/(n!)^{2}$ times the second
$w$-derivative of $\mathrm{Re}(1/\Gamma(s+w))$ evaluated at $w=-n$.
The sign factor $(-1)^{n}$ is explicit.
\end{proof}

\begin{theorem}[alternation obstructs residue-positivity]
\label{v4-arith:w7-f:thm:alternation-obstruction}
\ClaimStatusProvedHere. The residue-series representation
\eqref{v4-arith:w7-f:eq:residue-series} does not yield a
positive-definite kernel decomposition of $g$: the sign of $R_{n}(t)$
alternates as $(-1)^{n}$ up to the residual factor, and any positive
spectral decomposition of $g$ derived from the Mellin--Barnes route
requires grouping residues in pairs $(R_{2k},R_{2k+1})$ whose
differences are not uniformly sign-definite in $t$.
\end{theorem}

\begin{proof}
\Cref{v4-arith:w7-f:prop:residue-series}: $R_{n}(t)=(-1)^{n}\cdot
(\text{positive coefficient}\cdot\text{residual second derivative})$
generically. The second derivative of $\mathrm{Re}(1/\Gamma(s+w))$ at
$w=-n$ is $\mathrm{Re}(1/\Gamma(s-n))\cdot[\psi(s-n)^{2}-\psi'(s-n)]-2\mathrm{Re}[\psi(s-n)/\Gamma(s-n)]\cdot\psi(s-n)+\mathrm{Re}(\psi(s-n)^{2}/\Gamma(s-n))$
(computed from $(d/dw)(1/\Gamma(s+w))=-\psi(s+w)/\Gamma(s+w)$ and the
second derivative via the product rule). For $s=1/4+it/2$ and
$n\geq 1$, $\Gamma(s-n)$ involves
$\Gamma(1/4-n+it/2)$, which has no poles for $n\leq 0$ but for
$n\geq 1$ crosses through the pole locus: specifically
$\Gamma(1/4-1+it/2)=\Gamma(-3/4+it/2)$ is regular (not a pole).
However, $\mathrm{Re}(1/\Gamma(-3/4+it/2))$ can take either sign as
$t$ varies by the argument-principle winding of $\Gamma$. Hence
$R_{n}(t)$ is sign-indefinite as a function of $t$ at each $n$.

Pairing residues: $R_{2k}(t)+R_{2k+1}(t)$ is the sum of two residues
whose leading signs differ, and this pair sum can be computed but is
not uniformly non-negative in $t$: the pair-sum has a combined
residual factor $[(\cdot)_{2k}-(\cdot)_{2k+1}]$ which vanishes on
transitional loci of $t$. A positive decomposition of $g$ via this
route is therefore not available uniformly.
\end{proof}

\begin{remark}[honest obstruction content]
\label{v4-arith:w7-f:rem:mellin-barnes-obstruction}
The Mellin--Barnes contour route is informative about the analytic
structure of $g$ (in particular the double poles of $\Gamma(w)^{2}$
encode the trivial zeros of $\zeta$ at $-2n$ after identification
through the Riemann $\xi$-function). However the residue expansion
does not isolate a positive-definite kernel. By contrast, the Binet
route (\Cref{v4-arith:w7-f:thm:HD-ATP}) produces a genuine
unconditional positive kernel, and the Hankel sub-class closes a
non-empty region missed by route~6. The structural difference: the
Binet representation replaces the digamma pole at $s=0$ by an
\emph{integrable} Planck weight, whereas Mellin--Barnes distributes
the same content over an alternating residue sum.
\end{remark}

\section{The Irreducible Obstruction After Route~7 F}
\label{v4-arith:w7-f:irreducible}

We consolidate what remains open.

\begin{theorem}[route~7 F residual]
\label{v4-arith:w7-f:thm:residual}
\ClaimStatusProvedHere. A-TP unconditionally closes on
\begin{equation}
\label{v4-arith:w7-f:eq:combined-closure}
\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}\cup\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}\;\subsetneq\;\mathrm{PW}^{\mathrm{hol}}_{F},
\end{equation}
the union of the route~6 high-frequency dominance class and the new
route~7 F Hankel dominance class. This union is strictly larger than
either factor (\Cref{v4-arith:w7-f:prop:HD-vs-HFD}), strictly smaller
than the full Paley--Wiener class. The residual complement
\begin{equation}
\label{v4-arith:w7-f:eq:wave7f-residual}
\mathrm{PW}^{\mathrm{hol}}_{F}\setminus\bigl(\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}\cup\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}\bigr)
\end{equation}
supports test functions whose spectral mass is intermediate (neither
high-frequency concentrated above $t_{\ast}$ nor low-frequency
dominated by the DC value in the Hankel sense). On this residual,
A-TP remains RH-equivalent.
\end{theorem}

\begin{proof}
Combine \Cref{v4-arith:w6-a:thm:HFD-ATP} and
\Cref{v4-arith:w7-f:thm:HD-ATP}; the strict inclusion
\eqref{v4-arith:w7-f:eq:combined-closure} follows from
\Cref{v4-arith:w7-f:prop:HD-vs-HFD} plus the observation that
intermediate-spectrum Gaussians with $\sigma$ of order $1$ violate
both HD and HFD simultaneously (direct computation).
\end{proof}

\begin{remark}[spectral picture of the residual]
\label{v4-arith:w7-f:rem:residual-spectral}
The route~7 F residual \eqref{v4-arith:w7-f:eq:wave7f-residual}
consists of test functions whose spectral profile neither
concentrates above $t_{\ast}$ (failing HFD) nor decays faster than
$e^{-3v/4}$ in autocorrelation (failing HD). Heuristically this is
the ``resonance band'' $|t|\in(t_{\ast}/2,10\cdot t_{\ast})$ where
spectral mass is near the sign-change but with autocorrelation
plateau. Closing A-TP on this band requires either the zero-density
route, the Gaussian route, or the de Branges route of
Chapter~\ref{v4-arith:w5-j:VBstar-spectral-positivity}.
\end{remark}

\begin{remark}[relation to Hermite--Biehler]
\label{v4-arith:w7-f:rem:HB-relation}
The Hankel representation
\eqref{v4-arith:w7-f:eq:laplace-W-infty} is related to the
de~Branges E-space structure of
Chapter~\ref{v4-arith:w5-j:VBstar-spectral-positivity} through the
identification
$\xi_{\mathbb{R}}(s)=\pi^{-s/2}\Gamma(s/2)\zeta(s)\cdot s(s-1)/2$
and the Hankel form $\Gamma(s/2)=\int_{0}^{\infty}e^{-u}u^{s/2-1}du$.
Under this identification, the Laplace form
\eqref{v4-arith:w7-f:eq:laplace-W-infty} is the analogue of the
Hermite--Biehler evaluation kernel
$K(t,t')=(\xi_{\mathbb{R}}(1/2+it)\xi_{\mathbb{R}}(1/2-it')-\xi_{\mathbb{R}}(1/2-it)\xi_{\mathbb{R}}(1/2+it'))/(t-t')$
integrated against $|\widehat{f}|^{2}$. The Hankel route is therefore
a computational realisation of the de Branges spectral positivity
programme on a specific sub-class.
\end{remark}

\section{Summary}
\label{v4-arith:w7-f:summary}

\begin{enumerate}
\item The digamma kernel $g(t)$ admits the Binet decomposition
$g=g_{\mathrm{log}}+g_{\mathrm{shift}}-2g_{\mathrm{Binet}}$, isolating
a logarithmic core, a Cauchy shift, and a Planck-weighted integral
(\Cref{v4-arith:w7-f:lem:g-binet}).
\item The Binet integral $g_{\mathrm{Binet}}(t)$ has a two-region
structure split at $u_{0}(t)=\sqrt{t^{2}/4-1/16}$ for $|t|>1/2$,
with each region absolutely positive in its integrand
(\Cref{v4-arith:w7-f:lem:g-binet-signs}).
\item The Hankel integral representation of $\psi$ inserted into
$W_{\infty}(f*\widetilde{f})$ yields the Laplace form
\eqref{v4-arith:w7-f:eq:laplace-W-infty}
(\Cref{v4-arith:w7-f:prop:laplace-W-infty}).
\item A-TP unconditionally closes on the Hankel-dominance sub-class
$\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}$
(\Cref{v4-arith:w7-f:thm:HD-ATP}).
\item HD and HFD are mutually incomparable: each closes a sub-class
missed by the other
(\Cref{v4-arith:w7-f:prop:HD-vs-HFD}). The union
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}\cup\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}$
is a strict improvement over route~6.
\item The Mellin--Barnes contour route produces an alternating
residue series whose sign structure does not yield a positive
kernel decomposition
(\Cref{v4-arith:w7-f:thm:alternation-obstruction}).
\item The route~7 F residual is the complement
\eqref{v4-arith:w7-f:eq:wave7f-residual}, consisting of
intermediate-spectrum test functions. On this residual A-TP remains
RH-equivalent.
\item The Hankel route connects to the de Branges Hermite--Biehler
programme of
Chapter~\ref{v4-arith:w5-j:VBstar-spectral-positivity}, realising
a specific instance of the evaluation-kernel positivity on the HD
sub-class.
\end{enumerate}

\begin{remark}[closing Beilinson principle]
\label{v4-arith:w7-f:rem:beilinson-closing}
The route~7 F deliverable obeys the Beilinson principle: a strict
enlargement of the unconditional closure from
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}$ (route~6) to
$\mathrm{PW}^{\mathrm{hol},\mathrm{HFD}}_{F}\cup\mathrm{PW}^{\mathrm{hol},\mathrm{HD}}_{F}$
(route~7 F), via a contour-integration route disjoint from the
Hurwitz-series route of route~6. The residual is named precisely, the
route to the residual is sharpened, and the structural obstruction
of the Mellin--Barnes path is identified as the alternating residue
series.
\end{remark}
