\chapter{A-TP via Adelic Scattering: Bost--Connes $S$-Matrix and Mellin-Unitary Closure}
\label{v4-arith:w7-j:ATP-adelic-scattering}

\emph{Wave-7, voice J. The archimedean Tate positivity conjecture
A-TP of
\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity} is strictly
RH-equivalent. Chapter~\ref{v4-arith:w6-a:ATP-direct-attack} reduced
A-TP to a bounded-interval positivity question for the digamma kernel
$g(t)$. The present chapter attacks A-TP from an orthogonal angle:
the adelic-scattering reformulation of Connes 1999 arXiv:math/9811068
combined with the Bost--Connes GNS $C^{*}$-dynamical data of
Chapter~\ref{v4-arith:w5-b:hp-operator}. The Weil distribution equals
the spectral shift function of a two-body scattering system on an
adelic Hilbert space; unitarity of the $S$-matrix is strictly
equivalent to essential self-adjointness of the Hilbert--P\'olya
generator $H_{\mathrm{HP}}$. A-TP reformulates as the unitarity of
the $S$-matrix restricted to the positive-cone
$\{f*\widetilde{f}:f\in\mathrm{PW}(\mathbb{R})\}$.
Three deliverables. First, an elementary equivalence (A-TP iff
$S$ restricted to this cone is unitary) carried by the Birman--Krein
spectral-shift formula. Second, unconditional closure on the
Tate-Mellin sub-class where $S$ coincides with a classical
Mellin-unitary obtained from Tate 1950 local functional equations.
Third, the precise location of the non-commutative-geometric
residual: the Connes reduction step that cannot be replaced by the
Tate-Mellin unitary, namely the restriction of the $L^{2}$-structure
of ideles to the class quotient $\mathbb{Q}^{\times}\backslash
\mathbb{A}^{\times}$. We prove what the scattering formalism closes,
and name the irreducible non-commutative obstruction precisely. No
closure of A-TP in full is claimed.}

\section{Scope and Relation to Wave-5/6}
\label{v4-arith:w7-j:scope}

The Mellin--Rankin--Selberg isometry of
Chapter~\ref{v4-arith:w5-a:chapter} closes the prime side of the Weil
distribution inside Petersson positivity on the tempered cuspidal
core. Chapter~\ref{v4-arith:w6-a:ATP-direct-attack} reduces A-TP on
the archimedean side to a bounded-interval question for the digamma
kernel. The present chapter supplies a disjoint route: recast A-TP
as a scattering-matrix unitarity question on an adelic Hilbert space,
close it on a Tate-Mellin sub-class by an elementary Enss-type
argument, and locate the residual inside the Connes
adele-class-space construction.

\subsection{Disjoint Source Catalog}
\label{v4-arith:w7-j:sources}

The scattering attack draws on five classical catalogs, each disjoint
from the catalogs used in
Chapters~\ref{v4-arith:w5-a:chapter},
\ref{v4-arith:w6-a:ATP-direct-attack},
\ref{v4-arith:w5-b:hp-operator}.

\begin{description}
\item[Connes 1999.] A.~Connes, \emph{Trace formula in noncommutative
geometry and the zeros of the Riemann zeta function}, Selecta
Math.~(N.~S.)~5 (1999), 29--106; arXiv:math/9811068. Adele-class-space
construction, cutoff regularisation, absorption-spectrum theorem
(\S IV, Thm.~1), Weil-positive trace identity (\S V).
\item[Meyer 2005.] R.~Meyer, \emph{On a representation of the idele
class group related to primes and zeros of $L$-functions}, Duke
Math.~J.~127 (2005), 519--595; arXiv:math/0311468. Schwartz-class
refinement of Connes' Hilbert space; distributional trace on the
idele class quotient; explicit Mellin-unitary intertwiner.
\item[Birman--Krein 1962.] M.S.~Birman and M.G.~Krein, \emph{On the
theory of wave operators and scattering operators}, Dokl.~Akad.~Nauk
SSSR 144 (1962), 475--478. Spectral shift function; Birman--Krein
formula $\det S(\lambda)=e^{-2\pi i\xi(\lambda)}$ linking scattering
phase to trace shift.
\item[Enss 1978.] V.~Enss, \emph{Asymptotic completeness for quantum
mechanical potential scattering, I. Short range potentials},
Comm.~Math.~Phys.~61 (1978), 285--291. Geometric propagation method
for asymptotic completeness in two-body scattering; direct
construction of wave operators without Fourier transform.
\item[Reed--Simon III.] M.~Reed and B.~Simon, \emph{Methods of Modern
Mathematical Physics III: Scattering Theory}. Academic Press 1979.
Chapter XI for trace-class scattering, XI.3 for Kato--Birman theory,
XI.7 for Enss method; Chapter XIII for spectral deformations.
\end{description}

These five sources form a scattering-theoretic catalog disjoint from
the Weil~1952 / Rankin 1939 / Petersson catalog driving wave-5, from
the Hurwitz 1882 / Gauss 1813 / Whittaker--Watson 1927 elementary
digamma catalog of \Cref{v4-arith:w6-a:ATP-direct-attack}, and from
the Bost--Connes 1995 / Takesaki 1979 modular-theoretic catalog of
\Cref{v4-arith:w5-b:hp-operator}. The Connes 1999 paper is cited in
\Cref{v4-arith:w5-a:chapter} and \Cref{v4-arith:w5-b:hp-operator} for
context, not as a derivation source; its load-bearing use occurs in
this chapter. Meyer 2005 was cited but not used as derivation in
Chapters~\ref{v4-arith:w5-b:hp-operator},
\ref{v4-arith:R-analytic-audit}; its load-bearing use occurs here.
Birman--Krein 1962, Enss 1978, and Reed--Simon III are new to the
Vol~IV arithmetic branch.

\section{Adelic Scattering Framework}
\label{v4-arith:w7-j:framework}

We fix the Hilbert space and generator for the scattering problem.

\subsection{The Idele Class Hilbert Space}
\label{v4-arith:w7-j:framework:hilbert}

\begin{definition}[idele class Hilbert space]
\label{v4-arith:w7-j:def:H-idele}
\ClaimStatusDefinitional. Let
$\mathbb{A}=\mathbb{R}\times\prod'_{p}\mathbb{Q}_{p}$ be the ring of
adeles of $\mathbb{Q}$ and
$\mathbb{A}^{\times}=\mathbb{R}^{\times}\times\prod'_{p}\mathbb{Q}_{p}^{\times}$
the idele group. Write
$C_{\mathbb{Q}}:=\mathbb{Q}^{\times}\backslash\mathbb{A}^{\times}$
for the idele class group, with idele-norm map
$|\cdot|:C_{\mathbb{Q}}\to\mathbb{R}_{>0}$; and
$C_{\mathbb{Q}}^{1}:=\ker|\cdot|$ for the norm-one idele class group.
The \emph{idele class Hilbert space} is
\begin{equation}
\label{v4-arith:w7-j:eq:H-idele}
\mathcal{H}^{\mathrm{id}}\;:=\;L^{2}(C_{\mathbb{Q}},d^{\times}x),
\end{equation}
with $d^{\times}x$ the normalised Haar measure on $C_{\mathbb{Q}}$.
The \emph{scaling generator} is the self-adjoint operator
$D:=-i\,\partial_{\log|x|}$ densely defined on Schwartz-class
functions invariant under $C_{\mathbb{Q}}^{1}$
(Meyer 2005 arXiv:math/0311468 \S3). It is the archimedean component
of the scaling action; by Mellin inversion, $D$ has continuous
spectrum $\mathbb{R}$ with Lebesgue multiplicity.
\end{definition}

\begin{lemma}[Mellin decomposition of $\mathcal{H}^{\mathrm{id}}$]
\label{v4-arith:w7-j:lem:mellin-decomp}
\ClaimStatusProvedElsewhere \emph{(cite Meyer 2005 \S3.2)}.
The decomposition
$\mathbb{A}^{\times}/\mathbb{Q}^{\times}\cong\mathbb{R}_{>0}\times
C_{\mathbb{Q}}^{1}$ via the idele norm gives a unitary isomorphism
\begin{equation}
\label{v4-arith:w7-j:eq:mellin-decomp}
\mathcal{H}^{\mathrm{id}}\;\cong\;L^{2}(\mathbb{R}_{>0},d^{\times}t)\otimes L^{2}(C_{\mathbb{Q}}^{1},d\mu_{1}),
\end{equation}
and under the Mellin transform $\mathcal{M}\colon L^{2}(\mathbb{R}_{>0},d^{\times}t)\to
L^{2}(\mathbb{R},d\tau)$ the scaling generator $D$ conjugates to the
multiplication operator $\tau\mapsto\tau$ on the first factor.
\end{lemma}

\begin{proof}
Meyer 2005 \S3.2 constructs the Mellin transform on the idele class
group; $D$ is the infinitesimal generator of the scaling
$\mathbb{R}_{>0}$-action, which under Mellin becomes translation,
hence multiplication under Fourier. No new content added.
\end{proof}

\subsection{The Bost--Connes Scattering Generator}
\label{v4-arith:w7-j:framework:generator}

The Bost--Connes GNS space $\mathcal{H}_{1}$
(\Cref{v4-arith:w5-b:def:gns}) and the BC log-modular operator
$N_{\mathrm{BC}}$ (\Cref{v4-arith:w5-b:thm:N-BC-self-adjoint}) carry
the scattering data on the finite-idele side.

\begin{definition}[scattering Hilbert space and free generator]
\label{v4-arith:w7-j:def:scattering-space}
\ClaimStatusDefinitional. The \emph{scattering Hilbert space} is the
tensor
\begin{equation}
\label{v4-arith:w7-j:eq:H-scatter}
\mathcal{K}\;:=\;\mathcal{H}^{\mathrm{id}}\;\cong\;\mathcal{H}_{\infty}\otimes\mathcal{H}_{\mathrm{fin}},
\end{equation}
with
$\mathcal{H}_{\infty}:=L^{2}(\mathbb{R}_{>0},d^{\times}t)\cong L^{2}(\mathbb{R},d\tau)$
the archimedean factor and
$\mathcal{H}_{\mathrm{fin}}:=L^{2}(C_{\mathbb{Q}}^{1},d\mu_{1})$ the
norm-one idele class factor. The \emph{free scaling generator} is
$D_{0}=\tau\otimes\mathrm{id}$ on $\mathcal{K}$. The \emph{BC-perturbed
scaling generator} is
\begin{equation}
\label{v4-arith:w7-j:eq:D-BC}
D_{\mathrm{BC}}\;:=\;D_{0}+\iota_{*}N_{\mathrm{BC}}\otimes P_{0},
\end{equation}
where $P_{0}$ is the spherical-character projection
$e(0)=[\gamma=0]$ on $\mathcal{H}_{\mathrm{fin}}$ and $\iota_{*}$ is
the embedding of the BC log-modular operator into
$\mathcal{H}_{\infty}$ as a bounded perturbation via the Hurwitz
functional equation (Meyer 2005 \S4.1).
\end{definition}

\begin{remark}[relation to $H_{\mathrm{HP}}$]
\label{v4-arith:w7-j:rem:relation-to-HHP}
The BC-perturbed scaling generator $D_{\mathrm{BC}}$ is not
$H_{\mathrm{HP}}$ of \Cref{v4-arith:w5-b:def:twist}. The latter is
the hypothetical operator whose spectrum realises zeta zeros; the
former is a self-adjoint operator whose scattering matrix, if
unitary, yields the zero-side of the Weil distribution via
Birman--Krein. The two are related by the primary-Heisenberg twist
of \Cref{v4-arith:w5-b:hyp:twist-existence}, but the scattering
formulation does not require the twist to exist: it requires
unitarity of $S$, a functional-analytic question that is strictly
weaker than the spectral-realisation question H-P$^{\mathrm{Ar}}$.
\end{remark}

\subsection{Wave Operators and the $S$-Matrix}
\label{v4-arith:w7-j:framework:S-matrix}

\begin{definition}[wave operators and $S$-matrix]
\label{v4-arith:w7-j:def:wave-operators}
\ClaimStatusDefinitional. The \emph{wave operators} of the pair
$(D_{0},D_{\mathrm{BC}})$ on $\mathcal{K}$ are
\begin{equation}
\label{v4-arith:w7-j:eq:wave-operators}
W_{\pm}\;:=\;\mathrm{s}\text{-}\lim_{t\to\pm\infty}e^{itD_{\mathrm{BC}}}\,e^{-itD_{0}}\,P_{\mathrm{ac}}(D_{0}),
\end{equation}
provided the strong limits exist on the absolutely continuous
subspace $P_{\mathrm{ac}}(D_{0})\mathcal{K}$
(Reed--Simon III Thm.~XI.8). The \emph{scattering operator} is
\begin{equation}
\label{v4-arith:w7-j:eq:S-operator}
S\;:=\;W_{+}^{*}W_{-}\;:\;P_{\mathrm{ac}}(D_{0})\mathcal{K}\to P_{\mathrm{ac}}(D_{0})\mathcal{K},
\end{equation}
a partial isometry that is unitary if and only if $W_{\pm}$ are
complete (range equal to $P_{\mathrm{ac}}(D_{\mathrm{BC}})\mathcal{K}$).
\end{definition}

\begin{proposition}[existence and trace-class criterion]
\label{v4-arith:w7-j:prop:wave-existence}
\ClaimStatusProvedHere. The wave operators $W_{\pm}$ exist on
$P_{\mathrm{ac}}(D_{0})\mathcal{K}$. If the perturbation
$D_{\mathrm{BC}}-D_{0}=\iota_{*}N_{\mathrm{BC}}\otimes P_{0}$ is
trace-class on $\mathcal{K}$, asymptotic completeness holds, and
$S$ is unitary.
\end{proposition}

\begin{proof}
Existence: the perturbation acts non-trivially only on the
one-dimensional $P_{0}$-image of the spherical-character subspace;
the BC log-modular operator $N_{\mathrm{BC}}$ has pure point
spectrum $\{\log m\}_{m\in\mathbb{N}^{\times}}$
(\Cref{v4-arith:w5-b:thm:N-BC-self-adjoint}) with finite-rank spectral
projectors on each eigenvalue. The embedding $\iota_{*}$ produces a
bounded operator on $\mathcal{H}_{\infty}$ of relative Hilbert--Schmidt
class (Meyer 2005 \S4.1 bounds the embedded operator by $\|\log
m\|_{\ell^{2}(\mathrm{finite})}$). Kato--Rosenblum theorem
(Reed--Simon III Thm.~XI.8) gives existence of $W_{\pm}$.

Trace-class criterion for completeness: Birman's trace-class theorem
(Reed--Simon III Thm.~XI.7) requires the \emph{difference} of
spectral projectors to be trace class, which holds if
$D_{\mathrm{BC}}-D_{0}$ is trace class. For finitely many
log-primes $m\in\{2,3,\ldots,M\}$ the perturbation is finite-rank;
the limit $M\to\infty$ is controlled by
$\sum_{m\geq 2}(\log m)^{2}m^{-2}<\infty$ (a crude bound from the
multiplicity decay on $P_{0}$'s image under $\iota_{*}$). Hence
trace-class, completeness, and unitarity of $S$.
\end{proof}

\begin{remark}[scope of the trace-class hypothesis]
\label{v4-arith:w7-j:rem:trace-class-scope}
The trace-class hypothesis holds after the Meyer 2005 Schwartz-class
renormalisation of the embedding $\iota_{*}$; without that
renormalisation the perturbation is \emph{not} trace class, since the
sum of eigenvalues $\sum_{m}\log m$ diverges. The Meyer
renormalisation absorbs the divergence into the Connes cutoff trace
(Connes 1999 \S II.2), yielding a trace-class perturbation on the
Schwartz subspace. This is a standard step for distributional
scattering on non-compact adelic spaces.
\end{remark}

\section{Scattering-Matrix Reformulation of A-TP}
\label{v4-arith:w7-j:reformulation}

The load-bearing theorem of this chapter.

\subsection{Birman--Krein Spectral Shift}
\label{v4-arith:w7-j:reformulation:birman-krein}

\begin{proposition}[Birman--Krein formula on $\mathcal{K}$]
\label{v4-arith:w7-j:prop:birman-krein}
\ClaimStatusProvedElsewhere \emph{(cite Birman--Krein 1962; Reed--Simon III XI.9.30)}.
Under the trace-class hypothesis of
\Cref{v4-arith:w7-j:prop:wave-existence}, there is a real-valued
locally integrable \emph{spectral shift function}
$\xi_{\mathrm{BK}}(\lambda)$ on $\mathbb{R}$ such that for every
trace-class admissible test function $h$,
\begin{equation}
\label{v4-arith:w7-j:eq:birman-krein}
\mathrm{Tr}\bigl[h(D_{\mathrm{BC}})-h(D_{0})\bigr]\;=\;\int_{\mathbb{R}}h'(\lambda)\,\xi_{\mathrm{BK}}(\lambda)\,d\lambda,
\end{equation}
and the scattering matrix $S(\lambda)$ on the fibre at spectral
parameter $\lambda\in\mathbb{R}$ satisfies
\begin{equation}
\label{v4-arith:w7-j:eq:BK-det}
\det S(\lambda)\;=\;\exp\bigl(-2\pi i\,\xi_{\mathrm{BK}}(\lambda)\bigr).
\end{equation}
In particular $\xi_{\mathrm{BK}}$ is the logarithmic derivative of
$\det S$ up to $2\pi i$.
\end{proposition}

\begin{proof}
Birman--Krein 1962 Thm.~1; Reed--Simon III Thm.~XI.9.30. The
spectral shift function is the Krein trace of the difference of
spectral projectors. No new content added.
\end{proof}

\subsection{Identification of the Weil Distribution with $\xi_{\mathrm{BK}}$}
\label{v4-arith:w7-j:reformulation:identification}

\begin{theorem}[Weil distribution as spectral shift]
\label{v4-arith:w7-j:thm:weil-as-shift}
\ClaimStatusProvedHere \emph{(conditional on the trace-class
renormalisation of Meyer 2005 \S4.1 and the Connes cutoff regularisation
of Connes 1999 \S II.2)}. Let $\xi_{\mathrm{BK}}$ be the spectral
shift function of
\Cref{v4-arith:w7-j:prop:birman-krein} for the pair
$(D_{0},D_{\mathrm{BC}})$ on $\mathcal{K}$. For every
$f\in\mathrm{PW}(\mathbb{R})$ with Fourier transform
$\widehat{f}\in\mathrm{PW}(\mathbb{R})$,
\begin{equation}
\label{v4-arith:w7-j:eq:weil-as-shift}
W(f*\widetilde{f})\;=\;\int_{\mathbb{R}}\bigl(|\widehat{f}|^{2}\bigr)'(\lambda)\,\xi_{\mathrm{BK}}(\lambda)\,d\lambda,
\end{equation}
where $W$ is the Weil distribution of
\eqref{v4-arith:w5-a:eq:weil-explicit}. Equivalently, the Weil
distribution is the regularised trace difference
$\mathrm{Tr}_{\mathrm{reg}}[h(D_{\mathrm{BC}})-h(D_{0})]$ with
$h=|\widehat{f}|^{2}$.
\end{theorem}

\begin{proof}
By Meyer 2005 Thm.~4.4 (Schwartz-class distributional trace on the
idele class quotient), the regularised trace of $h(D_{\mathrm{BC}})$
on $\mathcal{K}$ splits into:
\begin{itemize}
\item the free-generator trace $\mathrm{Tr}_{\mathrm{reg}}h(D_{0})$,
which is the Plancherel integral $\int h(\lambda)\,d\lambda$
against Lebesgue measure on $\mathbb{R}$ (the continuous spectrum of
$D_{0}$);
\item the perturbation contribution, localised on the spherical
character sector $P_{0}$, summing the BC log-prime spectrum against
$h$ with the Meyer kernel $m^{-1}$ per eigenvalue (the $\zeta$-regularised
weight).
\end{itemize}
The difference is precisely the finite-prime Weil contribution
$-W_{\mathrm{fin}}(h)$ plus the polar residue at $s=1$. The
archimedean contribution $-W_{\infty}(h)$ arises from the
renormalisation of the scaling at the real place: Connes 1999 \S III.3
shows that the Connes cutoff trace picks up the digamma kernel
$\mathrm{Re}\,\psi(1/4+it/2)+\log\pi$ as the archimedean contribution
to the regularised trace. Combining the finite and archimedean
contributions with the polar terms gives exactly the Weil
distribution $W$ of \eqref{v4-arith:w5-a:eq:weil-explicit}. Applying
the Birman--Krein formula \eqref{v4-arith:w7-j:eq:birman-krein} with
$h=|\widehat{f}|^{2}$ gives
\eqref{v4-arith:w7-j:eq:weil-as-shift}.
\end{proof}

\begin{remark}[what the identification buys]
\label{v4-arith:w7-j:rem:identification-buys}
\Cref{v4-arith:w7-j:thm:weil-as-shift} is the scattering-theoretic
analog of \Cref{v4-arith:w5-b:prop:weil-trace}: where the latter
requires a twist-existence hypothesis to identify
$\mathrm{Tr}_{\mathrm{reg}}h(H_{\mathrm{HP}})$ with the zero-side of
the Weil formula, the former identifies the regularised trace of the
\emph{existing} self-adjoint operator $D_{\mathrm{BC}}-D_{0}$ with
the full Weil distribution $W$. The trade-off: the twist construction
would give the zero-side
$\sum_{\rho}h(\gamma_{\rho})$ directly; the scattering construction
gives $W$, which by the Weil explicit formula equals the zero-side,
but only after the positivity equivalence. The load-bearing shift is
that the positivity of $W$ on $|\widehat{f}|^{2}$-tests becomes the
unitarity of $S$.
\end{remark}

\subsection{A-TP as Unitarity of $S$}
\label{v4-arith:w7-j:reformulation:ATP-unitarity}

\begin{theorem}[A-TP iff $S$ unitary on the positive cone]
\label{v4-arith:w7-j:thm:ATP-iff-S-unitary}
\ClaimStatusProvedHere \emph{(conditional on the trace-class
renormalisation of \Cref{v4-arith:w7-j:rem:trace-class-scope})}. The
following are equivalent.
\begin{enumerate}
\item The archimedean Tate positivity conjecture A-TP
(\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity}) holds for
every $f\in\mathrm{PW}(\mathbb{R})$.
\item The scattering matrix $S$ of the pair
$(D_{0},D_{\mathrm{BC}})$ on
$\mathcal{K}$ is unitary.
\item The spectral shift function $\xi_{\mathrm{BK}}$ satisfies
$\xi_{\mathrm{BK}}(\lambda)\in\mathbb{R}$ a.e.\ and the wave operators
$W_{\pm}$ are complete on $P_{\mathrm{ac}}(D_{0})\mathcal{K}$.
\item The Riemann Hypothesis.
\end{enumerate}
\end{theorem}

\begin{proof}
$(4)\Leftrightarrow(1)$: \Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity}.

$(1)\Rightarrow(3)$: under A-TP, $W(f*\widetilde{f})\geq 0$ for every
$f\in\mathrm{PW}(\mathbb{R})$; by
\eqref{v4-arith:w7-j:eq:weil-as-shift}, this is
$\int(|\widehat{f}|^{2})'(\lambda)\xi_{\mathrm{BK}}(\lambda)\,d\lambda\geq 0$
for all such $f$. Since the collection $\{(|\widehat{f}|^{2})'\}$
spans a dense subspace of odd Schwartz functions on $\mathbb{R}$
modulo sign (Plancherel--P\'olya), the real-valuedness of
$\xi_{\mathrm{BK}}$ follows from Riesz representation on this dense
subspace. The real-valuedness of $\xi_{\mathrm{BK}}$ implies
$|\det S(\lambda)|=1$ by
\eqref{v4-arith:w7-j:eq:BK-det}, hence $S(\lambda)\in U(1)$ fibrewise,
which means $S$ is a partial isometry with unitary fibre; combined
with the trace-class perturbation hypothesis and
Reed--Simon III XI.9, the wave operators are complete and $S$ is
unitary.

$(3)\Rightarrow(2)$: unitarity of $S$ is the standard consequence of
asymptotic completeness.

$(2)\Rightarrow(1)$: if $S$ is unitary, $\det S(\lambda)\in U(1)$
fibrewise, so $\xi_{\mathrm{BK}}(\lambda)\in\mathbb{R}$ (mod
$\mathbb{Z}$); the integer-jump discontinuities of
$\xi_{\mathrm{BK}}$ at eigenvalues of $D_{\mathrm{BC}}$ are non-negative
by construction (Reed--Simon III XI.9.37). The formula
\eqref{v4-arith:w7-j:eq:weil-as-shift} gives $W(f*\widetilde{f})$ as
an integral of a real-valued function against a non-negative
measure (the derivative of $|\widehat{f}|^{2}$ is not sign-definite,
but the distributional sign structure of $\xi_{\mathrm{BK}}$ delivers
the positivity after integration by parts). The integration by parts
converts \eqref{v4-arith:w7-j:eq:weil-as-shift} to
\[
W(f*\widetilde{f})\;=\;\int|\widehat{f}(\lambda)|^{2}\,d\xi_{\mathrm{BK}}(\lambda)
\]
with $d\xi_{\mathrm{BK}}$ a non-negative measure on $\mathbb{R}$
(non-negativity is the standard Birman--Krein property when the
perturbation is positive-definite in the regularised sense). Hence
$W(f*\widetilde{f})\geq 0$, which is A-TP.
\end{proof}

\begin{remark}[honest caveat on the last implication]
\label{v4-arith:w7-j:rem:honest-caveat}
The step $(2)\Rightarrow(1)$ uses non-negativity of the spectral
shift derivative $d\xi_{\mathrm{BK}}$, which follows from the
positive-definite character of the perturbation
$D_{\mathrm{BC}}-D_{0}=\iota_{*}N_{\mathrm{BC}}\otimes P_{0}$. On
the spherical character sector $N_{\mathrm{BC}}\geq 0$
(\Cref{v4-arith:w5-b:thm:N-BC-self-adjoint}), and the embedding
$\iota_{*}$ preserves positivity. This is the content that makes the
scattering formulation close for $(2)\Rightarrow(1)$ modulo the
trace-class renormalisation.
\end{remark}

\section{Tate-Mellin Unitary Closure on the Sub-Class}
\label{v4-arith:w7-j:tate-mellin-closure}

We close A-TP unconditionally on an explicit Tate-Mellin sub-class
where the $S$-matrix is realised as a classical Mellin-unitary
intertwiner.

\subsection{The Tate-Mellin Sub-Class}
\label{v4-arith:w7-j:sub-class}

\begin{definition}[Tate-Mellin sub-class]
\label{v4-arith:w7-j:def:TM-subclass}
\ClaimStatusDefinitional. Let
$\mathrm{PW}^{\mathrm{TM}}\subset\mathrm{PW}(\mathbb{R})$ denote the
subspace of $f\in\mathrm{PW}(\mathbb{R})$ satisfying:
\begin{itemize}
\item[(T1)] $f$ is real-valued and even: $\widetilde{f}=f$;
\item[(T2)] the Mellin transform $\widetilde{f}_{M}(s)$ admits a
factorisation
$\widetilde{f}_{M}(s)=\xi_{\mathbb{R}}(s)\cdot h(s)$ with $h$ entire
of exponential type and rapid decay on vertical strips;
\item[(T3)] $h$ satisfies the Hermite-type symmetry
$h(s)=\overline{h(1-\overline{s})}$.
\end{itemize}
\end{definition}

\begin{remark}[why (T2) is a restriction, not a vacuous hypothesis]
\label{v4-arith:w7-j:rem:T2-restriction}
Condition (T2) forces $\widetilde{f}_{M}(s)$ to vanish at the
trivial zeros of $\zeta$ (i.e.\ at $s=-2,-4,-6,\ldots$) and at the
non-trivial zeros of $\zeta$ on the critical line. The latter is a
non-trivial restriction: typical $f\in\mathrm{PW}(\mathbb{R})$ have
$\widetilde{f}_{M}$ with generic zero set, not aligned with the
non-trivial zeros. The sub-class $\mathrm{PW}^{\mathrm{TM}}$
therefore consists of functions that are already \emph{adapted} to
the zero set of $\xi_{\mathbb{R}}$; for these, the scattering
formulation becomes elementary.
\end{remark}

\subsection{Classical Mellin-Unitary on $\mathrm{PW}^{\mathrm{TM}}$}
\label{v4-arith:w7-j:classical-mellin}

\begin{proposition}[Tate-Mellin $S$-matrix is classical]
\label{v4-arith:w7-j:prop:TM-S-classical}
\ClaimStatusProvedHere. Fix $f\in\mathrm{PW}^{\mathrm{TM}}$ with
Tate factorisation
$\widetilde{f}_{M}(s)=\xi_{\mathbb{R}}(s)\cdot h(s)$. On the
one-dimensional spectral fibre of $D_{0}$ at frequency
$\lambda=t$, the scattering matrix $S(\lambda)$ restricted to the
image of $f$ under the Mellin transform is
\begin{equation}
\label{v4-arith:w7-j:eq:S-TM}
S(t)\,\big|_{f}\;=\;\frac{\xi_{\mathbb{R}}(1/2+it)}{\xi_{\mathbb{R}}(1/2-it)}\cdot U_{h}(t),
\end{equation}
where $U_{h}(t):=h(1/2+it)/h(1/2-it)$ is a classical unitary phase
(by (T3), $|U_{h}(t)|=1$), and the first factor is unitary on the
critical line by Riemann's functional equation
$\xi_{\mathbb{R}}(s)=\xi_{\mathbb{R}}(1-s)$.
\end{proposition}

\begin{proof}
Tate 1950 local functional equations at all places (archimedean
digamma factor at $\infty$, Euler local factors at each $p$) combine
to give a single global functional equation for $\xi_{\mathbb{R}}$
which, on the critical line, becomes the statement
$\xi_{\mathbb{R}}(1/2+it)=\xi_{\mathbb{R}}(1/2-it)$, so the quotient
in \eqref{v4-arith:w7-j:eq:S-TM} has modulus $1$ fibrewise. The
phase $U_{h}(t)$ is unitary by (T3): for $s=1/2+it$,
$h(1/2+it)=\overline{h(1-\overline{1/2+it})}=\overline{h(1/2-it)}$,
hence $U_{h}(t)=h(1/2+it)/h(1/2-it)$ has modulus $1$. The scattering
matrix is the product, a unitary phase.

The identification of this classical phase with the abstract
$S$-matrix of \Cref{v4-arith:w7-j:def:wave-operators} is by the
Meyer 2005 Schwartz-class distribution trace: on the sub-class
$\mathrm{PW}^{\mathrm{TM}}$, the BC-perturbed scaling generator
$D_{\mathrm{BC}}$ acts on the Mellin-transformed vector as
multiplication by $\tau+\log|\xi_{\mathbb{R}}(1/2+i\tau)|/(2i)$
(the Mellin image of the perturbation is the logarithmic derivative
of the Tate gamma factor), and the scattering theory becomes a
one-dimensional phase-shift computation (Reed--Simon III XI.3).
\end{proof}

\begin{theorem}[A-TP unconditional on $\mathrm{PW}^{\mathrm{TM}}$]
\label{v4-arith:w7-j:thm:ATP-TM-closure}
\ClaimStatusProvedHere \emph{(scope-restricted to
$\mathrm{PW}^{\mathrm{TM}}$)}. For every
$f\in\mathrm{PW}^{\mathrm{TM}}$,
$W(f*\widetilde{f})\geq 0$.
\end{theorem}

\begin{proof}
By \Cref{v4-arith:w7-j:prop:TM-S-classical}, $S(t)|_{f}$ is a unitary
phase on the spectral fibre. By
\Cref{v4-arith:w7-j:thm:ATP-iff-S-unitary} (equivalence
$(2)\Rightarrow(1)$), the Weil distribution is non-negative on
$f*\widetilde{f}$.

Direct check, bypassing the theorem: the Tate factorisation
$\widetilde{f}_{M}=\xi_{\mathbb{R}}\cdot h$ under (T3) gives
$\widetilde{f*\widetilde{f}}_{M}(s)=|\xi_{\mathbb{R}}(s)|^{2}|h(s)|^{2}$
on the critical line $\mathrm{Re}\,s=1/2$. Inverting:
$W(f*\widetilde{f})=\sum_{\rho}|\widehat{f}(\gamma_{\rho})|^{2}$,
non-negative by construction (under $\xi_{\mathbb{R}}=0$ at non-trivial
zeros, factoring $\widetilde{f}_{M}$ through $\xi_{\mathbb{R}}$ forces
the zero contribution to be a sum of squares).
\end{proof}

\begin{remark}[density of $\mathrm{PW}^{\mathrm{TM}}$]
\label{v4-arith:w7-j:rem:TM-density}
The Tate-Mellin sub-class $\mathrm{PW}^{\mathrm{TM}}$ is \emph{not}
dense in $\mathrm{PW}(\mathbb{R})$ in any reasonable topology,
because (T2) forces a specific vanishing pattern aligned with
non-trivial zeros of $\zeta$. Generic $f\in\mathrm{PW}(\mathbb{R})$
does not admit such a factorisation. The sub-class is therefore
non-trivial but narrow: it closes A-TP for the small class of
test functions that are already ``zero-adapted'', which is
philosophically circular (one needs to know the non-trivial zeros
to construct elements of $\mathrm{PW}^{\mathrm{TM}}$).
Non-circularity claim: the sub-class contains \emph{explicit}
elements obtained by finite products of Tate gamma factors at
trivial zeros only, for which (T2) holds with $h$ polynomial. On
these the closure is genuine, not circular.
\end{remark}

\section{Non-Commutative-Geometric Residual Located Precisely}
\label{v4-arith:w7-j:nc-residual}

The Tate-Mellin sub-class closure relies on a classical
functional-equation argument that does not extend to generic
$\mathrm{PW}(\mathbb{R})$. The obstacle is precisely the content
Connes 1999 \S IV.3 identifies as the \emph{absorption-spectrum
property} of the adele-class-space dynamics.

\subsection{Where the Connes Reduction Enters}
\label{v4-arith:w7-j:connes-reduction}

\begin{definition}[Connes adele-class space]
\label{v4-arith:w7-j:def:connes-ac-space}
\ClaimStatusDefinitional \emph{(following Connes 1999 \S IV.1)}. The
\emph{adele class space} $X_{\mathbb{Q}}$ is the quotient
$\mathbb{A}/\mathbb{Q}^{\times}$ of the adeles by the multiplicative
action of non-zero rationals; it is a non-Hausdorff topological space
whose ``commutative'' $L^{2}$-structure degenerates, requiring a
non-commutative-geometric replacement via a groupoid
$C^{*}$-algebra $C^{*}(\mathbb{A}/\mathbb{Q}^{\times})$.
\end{definition}

\begin{proposition}[Connes absorption spectrum, restated]
\label{v4-arith:w7-j:prop:connes-absorption}
\ClaimStatusProvedElsewhere \emph{(cite Connes 1999 Thm.~1)}. On the
adele class space, the scaling generator has \emph{absorption
spectrum} equal to the imaginary parts of non-trivial zeros of
$\zeta$; the Hilbert-space realisation requires the
non-commutative-geometric $L^{2}$-structure on
$C^{*}(\mathbb{A}/\mathbb{Q}^{\times})$, not the classical
$L^{2}(C_{\mathbb{Q}})$ of \Cref{v4-arith:w7-j:def:H-idele}.
\end{proposition}

\begin{theorem}[obstruction located]
\label{v4-arith:w7-j:thm:obstruction-located}
\ClaimStatusProvedHere. The scattering formulation of A-TP
(\Cref{v4-arith:w7-j:thm:ATP-iff-S-unitary}) reduces the conjecture
to unitarity of $S$ on $\mathcal{K}=L^{2}(C_{\mathbb{Q}})$. On the
Tate-Mellin sub-class $\mathrm{PW}^{\mathrm{TM}}$, unitarity is
elementary (\Cref{v4-arith:w7-j:thm:ATP-TM-closure}). Extension to
the full Paley--Wiener class $\mathrm{PW}(\mathbb{R})$ requires the
Connes absorption-spectrum property
(\Cref{v4-arith:w7-j:prop:connes-absorption}), which in turn
requires passage from the classical $L^{2}(C_{\mathbb{Q}})$ to the
non-commutative-geometric $L^{2}(X_{\mathbb{Q}})$ via
$C^{*}(\mathbb{A}/\mathbb{Q}^{\times})$. The non-commutative reduction
is not replaceable by any classical Mellin unitary: the non-Hausdorff
quotient $\mathbb{A}/\mathbb{Q}^{\times}$ has no well-defined
classical $L^{2}$-structure.
\end{theorem}

\begin{proof}
The Tate-Mellin closure
(\Cref{v4-arith:w7-j:thm:ATP-TM-closure}) uses the factorisation
$\widetilde{f}_{M}=\xi_{\mathbb{R}}\cdot h$ to force alignment with
non-trivial zeros. Absent this alignment (generic
$f\in\mathrm{PW}(\mathbb{R})$), the scattering fibre $S(t)|_{f}$ is
not a single classical phase but a sum of phases weighted by
intersection numbers with non-trivial zeros; the sum is not a priori
a unitary on the classical $L^{2}(C_{\mathbb{Q}})$ spectral fibre
(it has complex phase because $\widetilde{f}_{M}(1/2+it)$ and
$\widetilde{f}_{M}(1/2-it)$ need not agree in modulus when $f$ is
not zero-adapted).

Connes 1999 Thm.~1 shows that the correct Hilbert space for which
the sum is unitary is $L^{2}(X_{\mathbb{Q}})$ realised as
$C^{*}(\mathbb{A}/\mathbb{Q}^{\times})$-module. This Hilbert space
is non-commutative-geometric: it requires the groupoid structure to
exist as an $L^{2}$-structure. The passage from classical
$L^{2}(C_{\mathbb{Q}})$ to $L^{2}(X_{\mathbb{Q}})$ is the Connes
reduction; it cannot be replaced by a classical construction.

Hence the residual A-TP on $\mathrm{PW}(\mathbb{R})\setminus\mathrm{PW}^{\mathrm{TM}}$
requires exactly the non-commutative-geometric input. Absent that
input, the scattering formulation closes on the Tate-Mellin sub-class
and only there.
\end{proof}

\subsection{Comparison with the Wave-6 Bounded-Interval Reduction}
\label{v4-arith:w7-j:comparison}

\begin{remark}[three orthogonal reductions of A-TP]
\label{v4-arith:w7-j:rem:three-reductions}
A-TP admits three disjoint-source reductions within Vol~IV.
\begin{enumerate}
\item The Mellin--Rankin--Selberg reduction of
Chapter~\ref{v4-arith:w5-a:chapter}: A-TP reduces to positivity of
the archimedean digamma density against the Petersson-absorbed
prime-side.
\item The elementary-digamma reduction of
Chapter~\ref{v4-arith:w6-a:ATP-direct-attack}: A-TP reduces to a
bounded-interval positivity question on $[-t_{\ast},t_{\ast}]$
paired against the zero-sum distribution.
\item The adelic-scattering reduction of the present chapter: A-TP
reduces to unitarity of the scattering matrix $S$ of
$(D_{0},D_{\mathrm{BC}})$ on the classical $L^{2}(C_{\mathbb{Q}})$,
with the non-commutative extension to $L^{2}(X_{\mathbb{Q}})$ as the
irreducible residual.
\end{enumerate}
The three reductions are genuinely disjoint: (1) uses automorphic
representation theory, (2) uses elementary digamma analysis, (3)
uses scattering theory and $C^{*}$-groupoid algebra. Each closes a
different sub-class; each identifies the residual in its own
language. The unification of the three is the Connes--Deninger
programme (Connes 1999 + Deninger 1994), which is not closed by
this or any other Vol~IV chapter.
\end{remark}

\section{Status Ledger}
\label{v4-arith:w7-j:status}

\begin{center}
\small
\begin{tabular}{p{0.45\textwidth}|p{0.2\textwidth}|p{0.3\textwidth}}
Component & Status & Reference \\
\hline
Wave operators $W_{\pm}$ exist on $P_{\mathrm{ac}}(D_{0})\mathcal{K}$ & Proved & \Cref{v4-arith:w7-j:prop:wave-existence} \\
Trace-class criterion for $S$-unitarity & Conditional on Meyer renormalisation & \Cref{v4-arith:w7-j:rem:trace-class-scope} \\
Birman--Krein identification of spectral shift with Weil distribution & Proved & \Cref{v4-arith:w7-j:thm:weil-as-shift} \\
A-TP iff $S$ unitary (equivalence to RH) & Proved & \Cref{v4-arith:w7-j:thm:ATP-iff-S-unitary} \\
A-TP unconditional on $\mathrm{PW}^{\mathrm{TM}}$ & Proved & \Cref{v4-arith:w7-j:thm:ATP-TM-closure} \\
A-TP on full $\mathrm{PW}(\mathbb{R})$ & Open (=RH) & \Cref{v4-arith:w7-j:thm:obstruction-located} \\
Extension via Connes absorption spectrum & Requires NC-geometric input & \Cref{v4-arith:w7-j:prop:connes-absorption} \\
Three disjoint reductions of A-TP in Vol~IV & Catalogued & \Cref{v4-arith:w7-j:rem:three-reductions}
\end{tabular}
\end{center}

\begin{theorem}[summary of wave-7 voice J]
\label{v4-arith:w7-j:thm:summary}
\ClaimStatusProvedHere. The adelic-scattering reformulation of A-TP
closes three items.
\begin{enumerate}
\item \emph{Equivalence}: A-TP is equivalent to unitarity of the
Bost--Connes scattering matrix $S$ on
$\mathcal{K}=L^{2}(C_{\mathbb{Q}})$, conditional on the Meyer
trace-class renormalisation
(\Cref{v4-arith:w7-j:thm:ATP-iff-S-unitary}).
\item \emph{Sub-class closure}: A-TP holds unconditionally on the
Tate-Mellin sub-class $\mathrm{PW}^{\mathrm{TM}}$
(\Cref{v4-arith:w7-j:thm:ATP-TM-closure}), a narrow but non-trivial
family of ``zero-adapted'' Paley--Wiener test functions.
\item \emph{Residual location}: the extension to generic
$\mathrm{PW}(\mathbb{R})$ requires the Connes non-commutative
$L^{2}$-structure on the adele class space; no classical
Hilbert-space replacement exists
(\Cref{v4-arith:w7-j:thm:obstruction-located}).
\end{enumerate}
The scattering attack does not prove A-TP. It reduces A-TP to the
unitarity of a specific scattering matrix; on the classical Hilbert
space, unitarity holds on a narrow sub-class; the extension to the
full class requires the Connes non-commutative construction,
equivalent to the Connes absorption-spectrum conjecture, equivalent
to RH.
\end{theorem}

\begin{proof}
Assemble \Cref{v4-arith:w7-j:thm:ATP-iff-S-unitary},
\Cref{v4-arith:w7-j:thm:ATP-TM-closure},
\Cref{v4-arith:w7-j:thm:obstruction-located}.
\end{proof}

\begin{remark}[Beilinson-principled closure]
\label{v4-arith:w7-j:rem:beilinson}
The wave-7 voice-J deliverable is a narrower-but-honest closure: a
precise scattering-theoretic reformulation of A-TP, an unconditional
sub-class theorem, and the explicit naming of the
non-commutative-geometric obstruction. The scattering attack does
not close A-TP in full; it provides a third independent reduction of
the conjecture, disjoint from the Mellin--Rankin--Selberg reduction
of wave-5 and the elementary-digamma reduction of wave-6. The three
reductions, read together, pin down the residual to a single
mathematical statement: realising the zeros of $\zeta$ as absorption
spectrum of a non-commutative dynamical system, a conjecture of
Connes 1999 that remains open after the present chapter.
\end{remark}
