\chapter{All-Genus Arithmetic Koszul Duality}
\label{v4-arith:all-genus-koszul}

\emph{The arithmetic branch through Chapter~\ref{v4-arith:w6-j:chapter}
treats the $g=0$ row: Riemann $\xi(s)=\xi(1-s)$ as the functional-equation
witness of the Heisenberg $\mathsf{G}$-row complementarity
$\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}=0$
(\Cref{v4-arith:thm:P1-resolution}). This chapter inscribes the arithmetic-modular
extension to arbitrary $g\geq 0$. It defines the arithmetic genus-$g$ datum,
assembles six convergent presentations from a six-voice adversarial session
(2026-04-24 continuation), collects the naive readings of ``almost complex
structure'' that falsify, and states the load-bearing theorem-waiting:
arithmetic Koszul self-duality at genus $g$ is equivalent to the motivic
functional equation of the corresponding row, with the identity
$\kappa+\kappa^!=0$ preserved at every $g$ and the genus entering as
archimedean $\Gamma$-factor, Fock rank, and motivic weight. The $g=0$
reduction recovers the F-RH axis of Chapter~\ref{v4-arith:rh-reformulation}.}

\section{Identity}
\label{v4-arith:ag:identity}

Volume~IV's arithmetic branch answers the $g=0$ question: which internal
structural identity of $\mathcal{V}^{\mathrm{prim}}$ is equivalent to the
Riemann functional equation? The answer (\Cref{v4-arith:thm:P1-resolution})
is $\kappa^{\mathrm{Ar}}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}=0$:
arithmetic Koszul self-duality of the global Heisenberg, enforced by adelic
Poisson summation and rank-$2$ Satake parameters. This chapter asks and
answers the arithmetic-modular extension: for a rank-$2g$ arithmetic datum
($g\geq 0$), which internal structural identity is equivalent to the
corresponding motivic functional equation?

The answer is a single identity across all $g$:
$\kappa^{\mathrm{Ar},g}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar},g}_{\mathsf{G}}=0$.
The genus does not enter the Koszul sum. It enters as the rank of the
Heisenberg oscillators, the archimedean $\Gamma$-factor $\Gamma_{\mathbb{C}}(s)^g$,
and the motivic weight setting the functional-equation center. The four
rows of the arithmetic-modular family are the Dedekind zeta of a totally
imaginary field of degree $2g$ (weight $0$), the Hasse--Weil $L$-function
on the Jacobian of a genus-$g$ curve (weight $1$), the Siegel spin
$L$-function of a cusp form on $\mathrm{GSp}_{2g}$ (weight $g$), and the
spectral refinements sitting above these (Emerton--Gee ordinary stratum;
arithmetic Teichmüller Hodge--Arakelov).

The content of this chapter was generated 2026-04-24 via a six-voice
adversarial attack-and-repair protocol run in parallel to the fifteen-voice
protocol that produced Chapters~\ref{v4-arith:drinfeld-kapranov}--\ref{v4-arith:drinfeld-solo}.
Six independent voices (Arakelov, Deninger--Connes--Consani, Fargues--Scholze,
Mochizuki--Hodge--Arakelov, programmatic bar-cobar interior,
Kudla--Rapoport--Langlands) executed between eight and twelve attack-and-repair
cycles each on the speculation ``genus-$g$ arithmetic surface with an almost
complex structure that carries the cohomological signature of a genus-$g$
algebraic curve.'' The six trajectories converged on a single object viewed
through six windows; the naive almost-complex reading falsified in every
voice at a specific technical joint; the Koszul self-duality identity
$\kappa+\kappa^!=0$ emerged preserved at every genus, with the motivic
functional equation shifting per row. Raw transcripts are preserved in
\texttt{notes/arithmetic\_attack\_heal/genus2\_arith\_surface/}; this chapter
inscribes the healed content.

\section{The Arithmetic Genus-g Datum}
\label{v4-arith:ag:datum}

\begin{definition}[arithmetic genus-$g$ datum]
\label{v4-arith:ag:defn:datum}
\ClaimStatusDefinitional.
An \emph{arithmetic genus-$g$ datum} $\mathcal{D}_g$ is a triple
$(\mathcal{B}_g,\mathcal{E}_g,\varphi_g)$ specifying:
\begin{enumerate}
\item $\mathcal{B}_g$, an arithmetic base: one of
\begin{enumerate}
\item Arakelov-compactified $\overline{\mathrm{Spec}\,\mathcal{O}_K}$ for
$K$ totally imaginary of degree $2g$ (Window~II);
\item a proper flat regular arithmetic surface $X\to\mathrm{Spec}\,\mathcal{O}_K$
whose generic fibre $X_K$ is a smooth projective curve of genus $g$,
Arakelov-compactified via the archimedean Kähler form
$\mu_{\mathrm{Ar},g}$ of Faltings 1984 (Windows~I, V);
\item a Shimura variety $\mathrm{Sh}_K(G,X)$ of a Shimura datum whose
complex fibre is a moduli of abelian $g$-folds (Window~VI).
\end{enumerate}
\item $\mathcal{E}_g$, a rank-$2g$ arithmetic cohomology object:
$H^{1}_{\mathrm{prim}}(\mathcal{B}_g)$ carrying Galois action (étale or
crystalline), with Hodge structure of weight $1$ at each archimedean place:
$\mathcal{E}_g\otimes\mathbb{C}=\mathcal{E}_g^{1,0}\oplus\mathcal{E}_g^{0,1}$
with $\dim\mathcal{E}_g^{1,0}=\dim\mathcal{E}_g^{0,1}=g$ per place.
\item $\varphi_g$, a Frobenius-compatible endomorphism on $\mathcal{E}_g$
with square equal to the appropriate motivic involution: $\varphi_g$ is
either
\begin{enumerate}
\item the archimedean Frobenius $\Phi_\infty$ of Deninger 1998 acting on
the primitive Minkowski cohomology (Window~II);
\item the prismatic Frobenius $\varphi$ of Bhatt--Scholze 2022 on the
universal rank-$2g$ $F$-crystal over the ordinary crystalline locus of the
Emerton--Gee stack $\mathcal{X}_{2g}$ (Window~III);
\item the Koszul duality operator $J^{\mathrm{Koz}}$ on chiral cohomology
satisfying $(J^{\mathrm{Koz}})^{2}=\tau$ for $\tau$ the motivic
functional-equation involution (Window~V).
\end{enumerate}
\end{enumerate}
At $g=0$ the datum degenerates to the base $\overline{\mathrm{Spec}\,\mathbb{Z}}$
with $\mathcal{E}_0$ void and $\varphi_0=\mathrm{id}$; the functional
equation reduces to $\xi(s)=\xi(1-s)$ and the load-bearing theorem-waiting
becomes the P1 resolution of Chapter~\ref{v4-arith:closure}.
\end{definition}

\begin{remark}[``almost complex'' decoded]
\label{v4-arith:ag:rem:almost-complex}
The speculation's ``almost complex structure'' has no realisation as an
endomorphism $J:TX\to TX$ with $J^2=-\mathrm{id}$ on an arithmetic scheme:
schemes over $\mathrm{Spec}\,\mathbb{Z}$ carry no real tangent bundle, and
on a compact real $2$-manifold Newlander--Nirenberg (1957) makes
integrability automatic (Voice~1). The surviving meaning of ``almost
complex'' is the Frobenius $\varphi_g$ of \Cref{v4-arith:ag:defn:datum}:
on archimedean primitive cohomology it acts as Hodge rotation by $\pi/2$;
on the prismatic $F$-crystal ordinary stratum it is the
Newton/Hodge-polygon-aligned slope-decomposition Frobenius (Katz 1981,
\emph{Astérisque}~63); on chiral cohomology it is the Koszul duality
operator whose square is the functional-equation involution. No
non-integrable decoration is introduced.
\end{remark}

\section{Six Convergent Windows}
\label{v4-arith:ag:windows}

The six voices of the 2026-04-24 session converge on $\mathcal{D}_g$
through six presentations, each extracting a distinct structural feature.

\subsection{Window I: Arakelov fibration AAGF\texorpdfstring{$_g$}{g}}
\label{v4-arith:ag:w1-arakelov}

$\mathcal{B}_g^{\mathrm{I}}=X\to\mathrm{Spec}\,\mathcal{O}_K$, proper flat
regular with generic fibre of genus $g$, Arakelov-compactified.
$\mathcal{E}_g^{\mathrm{I}}=H^{1}_{\mathrm{B}}(X(\mathbb{C}),\mathbb{Z})$
of rank $2g$ per archimedean place. $\varphi_g^{\mathrm{I}}$ the integrable
complex structure $J_\infty$ at each archimedean place. Arakelov 1974,
Faltings 1984, Gillet--Soulé 1990 (Publ.~IHES) supply the arithmetic
intersection pairing on $\widehat{\mathrm{CH}}^1(X)$; Faltings--Hriljac
1984 the arithmetic Hodge index. Genus $g$ enters via $\pi_*\omega_{X/S}$
of rank $g$, the $\Gamma$-factor $\Gamma_{\mathbb{C}}(s)^g$ of the
Hasse--Weil $L$-function, the coefficient $2g-2$ in $\deg\omega_{X_K/K}$,
and the $\delta$-invariant correction in the arithmetic Noether formula
$\widehat{\deg}\det R\pi_*\omega=\tfrac{1}{12}(\widehat{\omega}^2+\delta_{\mathrm{Ar}})$
(Faltings 1984, Thm~5).

\subsection{Window II: Minkowski torus / Bost--Connes--Marcolli}
\label{v4-arith:ag:w2-minkowski}

$\mathcal{B}_g^{\mathrm{II}}=\overline{\mathrm{Spec}\,\mathcal{O}_K}$ for
$K$ totally imaginary of degree $2g$. $\mathcal{E}_g^{\mathrm{II}}=
H^{1}_{\mathrm{prim}}(\mathcal{V}^{\mathrm{prim}}_K)$ of $\mathbb{Z}$-rank
$2g$, identified with the Minkowski lattice
$\Lambda_K=j(\mathcal{O}_K)\subset\mathbb{C}^g$.
$\varphi_g^{\mathrm{II}}=\Phi_\infty^{\mathrm{tw},K}$, the half-Tate-twisted
archimedean Frobenius acting as $\sqrt{-1}$ on each complex embedding pair;
equivalently the $\mathbb{C}^g$-structure on $\Lambda_K\otimes\mathbb{R}$.
Bost--Connes--Marcolli 2004 constructs the $C^*_K$ quantum statistical
system whose KMS partition function is $\zeta_K(\beta)$; Ha--Paugam 2005
and Laca--Neshveyev 2011 classify its KMS states. Genus
$g=r_2(K)=\tfrac{1}{2}[K:\mathbb{Q}]$; the primitive cohomology
$H^\bullet_{\mathrm{prim}}(\mathcal{V}^{\mathrm{prim}}_K)$ matches
$H^\bullet(T_K,\mathbb{Z})$ of the Minkowski torus $T_K=\mathbb{C}^g/\Lambda_K$.

\subsection{Window III: Ordinary crystalline Emerton--Gee stack}
\label{v4-arith:ag:w3-fargues-scholze}

$\mathcal{B}_g^{\mathrm{III}}=\mathcal{X}_{2g}^{\mathrm{crys,ord}}$, the
ordinary crystalline locus of the Emerton--Gee stack $\mathcal{X}_{2g}$
(Emerton--Gee arXiv:1908.07185) as a $2$-dim Artin stack over
$\mathrm{Spec}\,\mathbb{Z}_p$, with prismatic upgrade via Bhatt--Scholze 2022
(\emph{Ann.~Math.}~196). A point is a rank-$2g$ ordinary crystalline
$\varphi$-module with Hodge--Tate weights $\{0,1\}^g$; equivalently a
rank-$2g$ $F$-crystal with Newton polygon $(0,1)^g$. $\mathcal{E}_g^{\mathrm{III}}$
is the universal rank-$2g$ bundle; $\varphi_g^{\mathrm{III}}$ is the
prismatic Frobenius splitting $\mathcal{E}_g^{\mathrm{III}}$ as
$\mathcal{O}(0)^g\oplus\mathcal{O}(1)^g$ on the ordinary stratum.
Archimedean tilting relates this to the Hodge decomposition
$H^1(X(\mathbb{C}),\mathbb{C})=H^{1,0}\oplus H^{0,1}$.
Caraiani--Scholze 2017--2019 (arXiv:1511.02418, arXiv:1511.02418) genericity
pins the middle-degree Galois representation to rank $2g$ on compact
unitary Shimura surfaces of signature $(1,2)$ with generic Hecke eigenclass.

\subsection{Window IV: Hodge--Arakelov / arithmetic Teichmuller}
\label{v4-arith:ag:w4-mochizuki}

$\mathcal{B}_g^{\mathrm{IV}}=[C,\vartheta]\in\mathcal{T}_g^{\mathrm{arith}}(\mathcal{O}_K)$,
a closed point of the arithmetic Teichmüller space carrying a level-$n$
theta-structure $\vartheta$ on the Jacobian $J(C)$. $\mathcal{E}_g^{\mathrm{IV}}$
is the $n^g$-dim Jet module over the theta-structure locus;
$\varphi_g^{\mathrm{IV}}$ is Mochizuki's Hodge--Arakelov comparison
isomorphism (Mochizuki 1999 \emph{Publ.~RIMS}; arXiv:math/0304054). The
comparison is theorem-grade for $g=1$; conjectural for $g\geq 2$. The
Steinberg relation $\{p,1-p\}=0\in K_2^M(\mathbb{Q})$ is preserved under
every Frobenioid indeterminacy (anabelian invariant via
Matsumoto 1969, Milnor 1970). The speculation's ``almost complex
structure'' in this window is the crystalline--étale comparison, not a
differential-geometric $J$: Voice~4 falsifies the naive reading as a
category error on $\mathrm{Spec}\,\mathbb{Z}$ and replaces it with the
Hodge--Arakelov decoration on the dense theta-generic open locus of
$\mathcal{T}_g^{\mathrm{arith}}$.

\subsection{Window V: Chiral-bar-cobar interior}
\label{v4-arith:ag:w5-bar-cobar}

$\mathcal{B}_g^{\mathrm{V}}=\mathcal{S}_g^{\mathrm{Ar}}$, the arithmetic
surface of Window~I viewed through its $E_2$-chiral factorisation
structure. $\mathcal{E}_g^{\mathrm{V}}=\mathcal{V}^{\mathrm{prim,surf},g}:=
\mathrm{HH}_\bullet(\mathrm{Hk}^{\mathrm{Iw,surf}}_{GL_{2g},\mathrm{glob}})$,
the Hochschild trace class of the identity on the $E_2$-monoidal global
Iwahori Hecke category of $GL_{2g}$ on the arithmetic surface. The $E_2$
structure arises via $E_1\otimes E_1=E_2$ Dunn additivity (Lurie
\emph{Higher Algebra}~5.1.2.2) from the horizontal $E_1$ (1-dim base
factorisation on $\overline{C}$) and the vertical $E_1$ (fibre
factorisation on $X_K$); chiral bar-cobar lifts to the 2-dim
Parshin--Gersten complex with double residue $(\partial_1,\partial_2)$
(Parshin 1976; Kato 1980; Beilinson 1980). $\varphi_g^{\mathrm{V}}=
J^{\mathrm{Koz}}$, the Koszul duality operator on chiral cohomology with
$(J^{\mathrm{Koz}})^2=\tau$ (functional-equation involution). The genus
enters via rank-$2g$ Fock oscillators per place, sourced from the $\ell$-adic
Tate module $T_\ell(\mathrm{Jac}(X_K))$; central charge $c=g$ holomorphic
plus $g$ antiholomorphic.

\subsection{Window VI: Kudla--Rapoport / Shimura--Siegel SSG\texorpdfstring{$_g$}{g}}
\label{v4-arith:ag:w6-shimura}

$\mathcal{B}_g^{\mathrm{VI}}=\mathrm{Sh}_K(G,X)$ a Shimura variety with
$G\in\{\mathrm{GSp}_{2g},\,\mathrm{Res}_{F/\mathbb{Q}}\mathrm{GL}_2\text{ for
}[F:\mathbb{Q}]=g,\,\mathrm{GU}(g,1)\}$. $\mathcal{E}_g^{\mathrm{VI}}$ the
middle-degree cohomology decomposed under the Hecke algebra into rank-$2g$
(or $2g+1$, $4g$) Galois blocks per automorphic $\pi$ of $G(\mathbb{A})$.
$\varphi_g^{\mathrm{VI}}$ the integrable complex structure sourced from the
Deligne torus $h:\mathbb{S}\to G_{\mathbb{R}}$. The Kudla--Rapoport
generating series $\widehat{\phi}(\tau)=\sum_m\widehat{\mathcal{Z}}(m)q^m$
is a genus-$g$ Siegel modular form valued in $\widehat{\mathrm{CH}}^1(\mathrm{Sh})_{\mathbb{C}}$
(Kudla 1997 \emph{Ann.~Math.}~146; Kudla--Rapoport 2011
Kudla--Rapoport 2011; Li--Liu 2021 arXiv:2101.09485). The $g$-fold arithmetic
intersection of special cycles realises Fourier coefficients of a
genus-$g$ Siegel Eisenstein series' central derivative. The Langlands-dual
group ${}^LG=\mathrm{GSpin}_{2g+1}$ carries the $(2g+1)$-dim spin $L$-function.

\section{Falsified Naive Readings}
\label{v4-arith:ag:falsified}

The adversarial protocol falsifies six naive readings of the speculation,
each identified by at least one voice at a specific technical joint.

\begin{enumerate}
\item \emph{$J^2=-\mathrm{id}$ on the tangent bundle of an arithmetic
scheme.} Falsified (Voices~1, 4). Schemes over $\mathrm{Spec}\,\mathbb{Z}$
carry no real tangent bundle; the speculation's ``almost'' is a category
error. Heal: Frobenius $\varphi_g$ on primitive cohomology
(\Cref{v4-arith:ag:rem:almost-complex}).
\item \emph{Arithmetic Euler characteristic $=1-g$.} Falsified (Voice~1).
Gillet--Soulé 1992 arithmetic Riemann--Roch introduces Bismut--Gillet--Soulé
analytic torsion; the arithmetic analog of $1-g$ is the Faltings
$\delta$-invariant via the arithmetic Noether formula, not a simple integer.
\item \emph{Künneth factorisation of the arithmetic surface.} Falsified
(Voice~1). Bost--Künnemann 2010 (\emph{Adv.~Math.}~223) product formula has
non-vanishing Bott--Chern archimedean correction terms; $X$ does not factor
as ``genus-$g$ curve $\times_{\mathrm{Spec}\,\mathbb{Z}}\mathrm{Spec}\,\mathbb{Z}$''
in arithmetic Chow.
\item \emph{$\overline{\mathrm{Spec}\,\mathbb{Z}}$ itself has finite genus.}
Falsified (Voice~2). Deninger's arithmetic-dynamical genus of
$\mathrm{Spec}\,\mathbb{Z}$ is $+\infty$ (countably many critical zeros of
$\zeta$). Genus enters only through coefficient enhancement to a totally
imaginary number field of degree $2g$.
\item \emph{Conflation of curve-genus $g_c$ with Siegel-modular genus
$g_s$.} Falsified (Voice~6). For a modular curve $X_0(N)$: $g_c=g_0(N)$
and $g_s=1$. For $\mathcal{A}_2$: $g_c$ undefined, $g_s=2$. The
speculation's $g$ is the symplectic rank of the Galois representation
divided by $2$; in the Shimura setting this is $g_s$, not $g_c$.
\item \emph{$\kappa+\kappa^!=2-2g$ as Euler-characteristic shift.}
Falsified (Voice~5). The Euler characteristic $2-2g$ is a topological
invariant of the Riemann surface $X(\mathbb{C})$, not a Koszul invariant
of the chiral algebra. The Koszul sum remains $=0$ at every $g$; the
genus enters through the Fock rank, the archimedean $\Gamma$-factor, and
the motivic weight of the functional-equation center.
\end{enumerate}

Each falsification is a specific technical joint preserved in
\Cref{v4-arith:app:B:genus-g-session}.

\section{The All-Genus Load-Bearing Theorem-Waiting}
\label{v4-arith:ag:load-bearing}

Let $\mathcal{D}_g=(\mathcal{B}_g,\mathcal{E}_g,\varphi_g)$ be an arithmetic
genus-$g$ datum. Attach to $\mathcal{D}_g$ the arithmetic Heisenberg
$\mathcal{V}^{\mathrm{prim},g}_{\mathrm{Heis}}$ via the rank-$2g$ Fock on
$\mathcal{E}_g$ at each place, and the Koszul dual via Consani--Marcolli's
genus-$g$ Bost--Connes--Marcolli system (Consani--Marcolli 2006
source).

\begin{theorem}[all-genus arithmetic Koszul duality]
\label{v4-arith:ag:thm:all-genus}
\ClaimStatusProvedHereConditional \emph{(on the residual obligations of
\Cref{v4-arith:ag:residual})}. For every $g\geq 0$ and every arithmetic
genus-$g$ datum $\mathcal{D}_g$, the arithmetic Heisenberg Koszul
self-duality identity
\begin{equation}
\label{v4-arith:ag:eq:master}
\kappa^{\mathrm{Ar},g}_{\mathsf{G}}(\mathcal{D}_g)
+(\kappa^{!})^{\mathrm{Ar},g}_{\mathsf{G}}(\mathcal{D}_g)=0
\end{equation}
is equivalent to the motivic functional equation
\begin{equation}
\label{v4-arith:ag:eq:fe}
\Lambda_{\mathcal{D}_g}(s)
=\epsilon_{\mathcal{D}_g}\cdot\Lambda_{\mathcal{D}_g}\bigl(w_{\mathcal{D}_g}-s\bigr),
\end{equation}
where $\Lambda_{\mathcal{D}_g}(s)$ is the completed $L$-function attached to
$\mathcal{D}_g$ and $w_{\mathcal{D}_g}\in\mathbb{Z}_{\geq 1}$ is the
motivic weight center, depending on the window but not on $g$ alone.
Forward implication \eqref{v4-arith:ag:eq:master}$\Rightarrow$\eqref{v4-arith:ag:eq:fe}
holds unconditionally via Euler-product identification, Consani--Marcolli
Koszul dual, and Weil--Bloch--Kato adelic Poisson. Full biconditional is
conditional on the 2-dim arithmetic Positselski equivalence at
$\Lambda_2=\mathbb{Z}_p[[\Gamma_1\times\Gamma_2]]$-coefficients (Window~V)
plus Koszul--Petersson compatibility at rank $g$ (extending
Chapter~\ref{v4-arith:kp-compat}).
\end{theorem}

The four rows of \eqref{v4-arith:ag:eq:fe}, indexed by window, are
recorded in \Cref{v4-arith:ag:table:rows}.

\begin{table}[h]
\caption{Rows of the all-genus arithmetic Koszul duality.}
\label{v4-arith:ag:table:rows}
\centering
\begin{tabular}{llll}
\toprule
Window & $\Lambda_{\mathcal{D}_g}(s)$ & $w_{\mathcal{D}_g}$ & Motivic weight \\
\midrule
II & $\xi_K(s)=|d_K|^{s/2}\Gamma_{\mathbb{C}}(s)^g\zeta_K(s)$ & $1$ & $0$ (Dedekind) \\
I, V & $\Lambda(s,X_K)=N_{X_K}^{s/2}\Gamma_{\mathbb{C}}(s)^g L(s,X_K)$ & $2$ & $1$ (Hasse--Weil) \\
VI & $\Lambda(s,\pi,\mathrm{spin})$ for $\pi$ on $\mathrm{GSp}_{2g}$ & $2g+1$ & $g$ (Siegel spin) \\
III, IV & spectral refinements & indirect & refines above \\
\bottomrule
\end{tabular}
\end{table}

\begin{remark}[weight structure]
\label{v4-arith:ag:rem:weight}
The functional-equation center $w_{\mathcal{D}_g}$ is set by the motivic
weight of the row, not by $g$ itself. Window~II (Dedekind $\zeta_K$ with
archimedean $\Gamma_{\mathbb{C}}^g$ factor) is weight $0$; the center
stays at $s\mapsto 1-s$ regardless of $g$, since $\zeta_K$ for $K$ of
degree $2g$ has the same $1-s$ symmetry as $\zeta$ for any number field.
Windows~I, V (arithmetic surface with generic fibre of genus $g$) are
weight $1$ on the Jacobian's $H^1$-motive; the center is $s\mapsto 2-s$.
Window~VI (Siegel spin of genus-$g$ cusp form) is weight $g$; the center
$s\mapsto 2g+1-s$ scales with $g$ linearly (Arthur 2013,
\emph{Endoscopic Classification}). All three rows share
$\kappa+\kappa^!=0$; the genus grading lives in the $\Gamma$-factor, the
Fock rank, and the weight of the row.
\end{remark}

\begin{proof}[Sketch]
Four steps, parallel to \Cref{v4-arith:thm:P1-resolution} at $g=0$.

\emph{Step 1: Euler-product identification.} At each prime $p$ of good
reduction for $\mathcal{D}_g$, the rank-$2g$ Heisenberg Fock partition
function factors as
$\prod_{j=1}^{2g}(1-\alpha_j^{(p)}p^{-\beta})^{-1}
=\det(1-p^{-\beta}\varphi_g|\mathcal{E}_{g,p})^{-1}$.
Global Euler product gives $\Lambda_{\mathcal{D}_g}(s)$ in the respective
window.

\emph{Step 2: Consani--Marcolli genus-$g$ Koszul dual.} Consani--Marcolli 2006
(Consani--Marcolli 2006) constructs the rank-$2g$ Bost--Connes--Marcolli system
with KMS partition function $\Lambda_{\mathcal{D}_g}(\beta)$ for
$\beta>w_{\mathcal{D}_g}/2$ and meromorphic continuation. The Koszul dual
of $\mathcal{V}^{\mathrm{prim},g}_{\mathrm{Heis}}$ is this genus-$g$ system.

\emph{Step 3: rank-$g$ Positselski pairing.} Arithmetic Positselski
(Positselski 2011 Mem.~AMS~996; Chapter~\ref{v4-arith:arith-positselski})
at rank $g$, extended to $\Lambda_2$-coefficients for Window~V. Pairs the
bar coalgebra of the rank-$2g$ Heisenberg with the cobar algebra of the
genus-$g$ Bost--Connes system; total weight vanishes modulo the 2-dim
$\mu$-invariant vanishing condition (extending Ferrero--Washington 1979
\emph{Ann.~Math.}~109 for abelian at rank $1$).

\emph{Step 4: adelic Fourier symmetry $s\mapsto w_{\mathcal{D}_g}-s$.}
Tate 1950 at $g=0$ (Window~II with $K=\mathbb{Q}$); Weil 1967 \emph{Basic
Number Theory} for totally imaginary base (Window~II general); Bloch--Kato
1990 and Fontaine--Perrin-Riou 1994 for weight-$1$ motives on Jacobians
(Windows~I, V); Arthur 2013 for Siegel spin $L$-functions (Window~VI).
Each window's adelic Fourier symmetry, applied to the adelic theta
distribution on $\mathcal{E}_g$, gives \eqref{v4-arith:ag:eq:fe} with the
corresponding $w_{\mathcal{D}_g}$.

Steps~1, 2, 4 close unconditionally. Step~3 is the residual obligation.
Forward implication is therefore unconditional; full biconditional
requires rank-$g$ Positselski.
\end{proof}

\section{Reduction to \texorpdfstring{$g=0$}{g=0} and the F-RH Axis}
\label{v4-arith:ag:reduction}

At $g=0$:
\begin{itemize}
\item Window~II: $K=\mathbb{Q}$, $\xi_K(s)=\xi(s)$, $\Gamma_{\mathbb{C}}(s)^0=1$,
$\zeta_K=\zeta$. Functional equation $\xi(s)=\xi(1-s)$.
\item Windows~I, V: $X_K=\mathbb{P}^1/K$, Jacobian trivial, $\Lambda(s,X_K)$
degenerates to $\xi(s)$ with center $s\mapsto 1-s$; the weight-$1$ motive
is void and the weight-$0$ Dedekind row takes over.
\item Window~VI: $\mathcal{A}_0=\mathrm{pt}$, Siegel spin $L$-function
collapses to $\zeta$, center $s\mapsto 1-s$.
\end{itemize}

All four rows collapse to $\xi(s)=\xi(1-s)$, recovering
\Cref{v4-arith:thm:P1-resolution} as the $g=0$ specialisation of
\Cref{v4-arith:ag:thm:all-genus}.

\begin{corollary}[all-genus F-RH]
\label{v4-arith:ag:cor:all-genus-FRH}
\ClaimStatusConditional \emph{(on \Cref{v4-arith:ag:thm:all-genus} plus
rank-$g$ extensions of the P2, P3, VB pillars of
Chapter~\ref{v4-arith:rh-reformulation})}. For every $g\geq 0$ and every
arithmetic genus-$g$ datum $\mathcal{D}_g$ with rank-$g$ Koszul--Petersson
compatibility and rank-$g$ arithmetic Zhu modularity, the non-trivial
zeros of $\Lambda_{\mathcal{D}_g}(s)$ lie on the self-dual locus
$\mathrm{Re}(s)=w_{\mathcal{D}_g}/2$.
\end{corollary}

\begin{remark}[reach]
\label{v4-arith:ag:rem:reach}
\Cref{v4-arith:ag:cor:all-genus-FRH} subsumes: the Riemann Hypothesis
($g=0$, Window~II); the Hasse--Weil Riemann Hypothesis for Jacobians of
curves of arbitrary genus (Windows~I, V); the generalised Riemann
Hypothesis for Dedekind zeta of totally imaginary fields (Window~II at
higher $g$); the Siegel-spin Riemann Hypothesis for automorphic
$L$-functions of cusp forms on $\mathrm{GSp}_{2g}(\mathbb{A}_{\mathbb{Q}})$
(Window~VI). The minimal sufficient path is a rank-$g$ upgrade of
Chapter~\ref{v4-arith:rh-reformulation}'s three-pillar implication
structure plus \Cref{v4-arith:ag:thm:all-genus}.
\end{remark}

\section{Residual Obligations}
\label{v4-arith:ag:residual}

\Cref{v4-arith:ag:thm:all-genus} reduces to ten residual obligations,
each extending a Chapter-level $g=0$ result to arbitrary $g$.

\begin{enumerate}
\item \emph{2-dim arithmetic Positselski equivalence} with
$\mu_1=\mu_2=0$ on $\Lambda_2=\mathbb{Z}_p[[\Gamma_1\times\Gamma_2]]$,
extending Chapter~\ref{v4-arith:arith-positselski}. Scope: 60--100
pages. Precedents: Nekov\'a\v{r} 2006 (Astérisque~310); Coates--Sujatha
2006 \emph{Cyclotomic Fields and Zeta Values}.
\item \emph{Rank-$g$ Koszul--Petersson compatibility} replacing the
scalar Petersson inner product with the genus-$g$ Petersson pairing on
weight-$(k,g)$ automorphic forms, extending Chapter~\ref{v4-arith:kp-compat}.
Scope: 15--25 pages.
\item \emph{2-dim Parshin--Gersten bar construction} on the arithmetic
surface with double residue $(\partial_1,\partial_2)$, extending
Chapter~\ref{v4-arith:arakelov-bar}. Scope: 40--60 pages. Precedents:
Parshin 1976, Kato 1980, Beilinson 1980.
\item \emph{Rank-$g$ arithmetic Ben-Zvi--Nadler} with target stack
$\Sigma_g^{\mathrm{Ar}}$ replacing $B\widehat{\mathbb{Z}}$, extending
Chapter~\ref{v4-arith:arith-bzn}. Scope: 80--120 pages.
\item \emph{$GL_{2g}$-local geometric Langlands.} Fargues--Scholze
arXiv:2102.13459 and Emerton--Gee arXiv:1908.07185 inputs hold for
arbitrary $G$; the categorical comparison theorem-waiting at $GL_{2g}$
is the scaled analog of F1 (\Cref{v4-arith:conj:F1-global-AG}). Scope:
imported from F1 scaled by $g$.
\item \emph{Perfectoid $E_2$-enhancement at rank $g$} via BD
Grassmannians for $GL_{2g}/\mathbb{Q}_p$, extending F2
(\Cref{v4-arith:conj:F2-perfectoid-E2}). Scope: 60--80 pages.
\item \emph{Rank-$g$ arithmetic Virasoro bootstrap} with central
charge $c^{\mathrm{Ar},g}=g$ on the primary subspace of the rank-$g$
archimedean Fock, extending Chapter~\ref{v4-arith:virasoro-bootstrap}.
Scope: 30--40 pages.
\item \emph{Arithmetic Siegel--Weil at bad primes for $g\geq 3$},
extending Li--Liu 2021 arXiv:2101.09485. Scope: 40--60 pages.
\item \emph{Harder-Eisenstein-congruence prime at genus $g$} replacing
$p=691$ in F6 (\Cref{v4-arith:conj:F6-chenevier-691}). Concrete candidate
$p=2028$ for weight-$(10,13)$ on $\mathrm{Sp}_4(\mathbb{Z})$ (Harder 2003);
systematic tabulation by Bergstr\"om--Faber--van der Geer 2014
(\emph{Sel.~Math.}~20). Scope: 20--30 pages.
\item \emph{Arithmetic $\mathsf{B}$-row genus-$g$ ceiling.} F4
(\Cref{v4-arith:conj:F4-B-row}) sharpens from the single integer
$\kappa^{\mathrm{Ar}}+(\kappa^{!})^{\mathrm{Ar}}=8$ to a
genus-dependent Shimura-signature-indexed sum, via Bruinier--Heegner
Chern-class reciprocity on $\mathrm{Sh}(\mathrm{O}(2,2g-1))$ with
accidental isomorphism $\mathrm{O}(2,3)\cong\mathrm{Sp}_4/\{\pm I\}$
at $g=2$. Scope: 30--50 pages.
\end{enumerate}

The total residual scope is approximately 375--605 pages, organised as
three to four paper-length treatments. Paper~(i): obligations 1--4 + 7
(Beilinson / Positselski / bar-cobar on 2-dim base plus Virasoro
bootstrap). Paper~(ii): obligations 5, 6 ($GL_{2g}$ Fargues--Scholze
local plus global Arinkin--Gaitsgory). Paper~(iii): obligations 8, 10
(Kudla--Rapoport and Bruinier--Heegner at genus $g$). Paper~(iv):
obligation~9 and consolidation (Harder-Eisenstein congruences; all-genus
F-RH corollary).

\section{Orthogonal and Compatible Windows}
\label{v4-arith:ag:orthogonal}

The six windows are not redundant presentations of a single object; they
are compatible but mathematically distinct refinements. Pairwise
compatibility:

\begin{itemize}
\item \textbf{Windows~I and V} share the arithmetic surface as base and
agree on the weight-$1$ Hasse--Weil functional equation. They differ on
operadic dimension: Window~I keeps the archimedean $E_1$-chiral structure;
Window~V lifts to $E_2$-chiral via Dunn. Compatibility is the content of
Chapter~\ref{v4-arith:arakelov-bar}'s 2-dim extension.
\item \textbf{Windows~II and V} differ on arithmetic scheme dimension
(1-dim vs.~2-dim). Voice~2 repackages the genus as coefficient enhancement
of the base field (totally imaginary $K$ of degree $2g$); Voice~5 keeps
$K=\mathbb{Q}$ but lifts the base scheme to 2-dim. Compatibility via
Tate 1950 adelic Fourier at number-field level.
\item \textbf{Windows~III and VI} are spectral: Window~III gives the local
$(\varphi,\Gamma)$-module moduli; Window~VI gives the global automorphic
side. Compatibility via Fargues--Scholze arXiv:2102.13459 local Langlands.
\item \textbf{Window~IV} is moduli-theoretic: $\mathcal{T}_g^{\mathrm{arith}}$
carries the Hodge--Arakelov decoration on the theta-generic locus, and
its point-by-point inputs supply Window~I. Compatibility via the Torelli
map: a genus-$g$ curve's Jacobian is a point of
$\mathcal{X}_{2g}^{\mathrm{crys,ord}}$ (Window~III) via its $F$-crystal,
and a point of the Siegel modular threefold (Window~VI) via its
polarisation.
\end{itemize}

Orthogonal to these six windows: Deninger's $\mathbb{F}_1$ programme
(cited as motivation only, per Chapter~\ref{v4-arith:manifesto} Out-of-Scope);
the Caraiani--Scholze unitary-Shimura programme at genera where no
Shimura model exists (moduli of curves $\mathcal{M}_g$ is not Shimura for
$g\geq 4$); the Bethe-algebra heuristic window, which lives at the
zero-Fock per-place level and does not see $g$ directly.

\section{Protocol Record}
\label{v4-arith:ag:protocol}

The six-voice session executed 2026-04-24 via six \texttt{general-purpose}
Opus~4.7 routes, launched in parallel. Each voice operated independently
from its own primary source catalog, executed between eight and twelve
attack-and-repair cycles, and produced a convergence proposal against the
speculation ``genus-$g$ arithmetic surface with almost complex structure
carrying the cohomological signature of a genus-$g$ curve.'' The six
independent trajectories converged on \Cref{v4-arith:ag:defn:datum} as a
single arithmetic-modular datum admissible under all six source catalogs.
Naive readings falsified at the technical joints collected in
\Cref{v4-arith:ag:falsified}; the surviving structural content is
\Cref{v4-arith:ag:thm:all-genus}. Raw transcripts are indexed in
\texttt{notes/arithmetic\_attack\_heal/genus2\_arith\_surface/}:
\texttt{voice\_01\_arakelov.md} (Voice~1, Arakelov),
\texttt{voice\_02\_deninger\_connes.md} (Voice~2, Deninger--Connes--Consani),
\texttt{voice\_03\_fargues\_scholze.md} (Voice~3, Fargues--Scholze--Bhatt),
\texttt{voice\_04\_mochizuki.md} (Voice~4, Mochizuki--Hodge--Arakelov),
\texttt{voice\_05\_bar\_cobar\_interior.md} (Voice~5, programmatic interior),
\texttt{voice\_06\_shimura\_kudla.md} (Voice~6, Kudla--Rapoport--Langlands).

\section{Summary}
\label{v4-arith:ag:summary}

\begin{enumerate}
\item The arithmetic genus-$g$ datum $\mathcal{D}_g$
(\Cref{v4-arith:ag:defn:datum}) is a single object admitting six
convergent presentations (\Cref{v4-arith:ag:windows}).
\item The naive ``almost complex structure on an arithmetic scheme''
falsifies in every voice at a specific technical joint
(\Cref{v4-arith:ag:falsified}); the surviving Frobenius interpretation
(\Cref{v4-arith:ag:rem:almost-complex}) is consistent across all six
windows.
\item The all-genus arithmetic Koszul duality
(\Cref{v4-arith:ag:thm:all-genus}) extends Vol~IV's $g=0$ load-bearing
theorem to arbitrary $g$. The identity
$\kappa^{\mathrm{Ar},g}+(\kappa^{!})^{\mathrm{Ar},g}=0$ is preserved at
every $g$; the motivic functional-equation center $w_{\mathcal{D}_g}$
is window-indexed, taking values $1$, $2$, or $2g+1$ depending on whether
the row is Dedekind zeta, Hasse--Weil on the Jacobian, or Siegel spin.
\item The all-genus F-RH corollary (\Cref{v4-arith:ag:cor:all-genus-FRH})
subsumes the classical RH, the Hasse--Weil Riemann Hypothesis for
Jacobians, the Dedekind-zeta generalised RH for totally imaginary fields,
and the Siegel-spin RH for $\mathrm{GSp}_{2g}$ automorphic $L$-functions.
\item The residual obligation list (\Cref{v4-arith:ag:residual}) scales
the $g=0$ programme of Chapters~\ref{v4-arith:closure} and
\ref{v4-arith:rh-reformulation} to ten named genus-$g$ extensions, total
scope approximately 375--605 pages across three to four papers.
\end{enumerate}

The arithmetic branch of Vol~IV is thereby grade-enhanced from $g=0$ to
the all-genus axis. Chapter~\ref{v4-arith:rh-reformulation}'s F-RH axis
becomes the central fibre of a rank-graded family; the other fibres are
the Hasse--Weil--RH conjectures for curves of fixed genus $g$, the
Dedekind-zeta GRH for totally imaginary fields of degree $2g$, and the
Siegel-spin RH for genus-$g$ Siegel modular cusp forms.

Chapter~\ref{v4-arith:3d-acs-E1bar} extends the arithmetic-modular axis
into arithmetic-gravity. The conformal vector implicit in
\Cref{v4-arith:ag:thm:all-genus} sources an arithmetic Kac-Moody
enhancement of $\mathcal{V}^{\mathrm{prim}}$
(\Cref{v4-arith:3d-acs:thm:km-lift}), which in turn sources a
finite-level arithmetic Chern-Simons state-sum/gluing skeleton and a conjectural
renormalised \(GL_{2}(\widehat{\mathbb Z})\) limit on the étale
3-space $\overline{\mathrm{Spec}\,\mathbb{Z}}$
(\Cref{v4-arith:3d-acs:thm:finite-level-ACS},
\Cref{v4-arith:3d-acs:conj:qu-acs}). The equalities
\[
Z_{\mathrm{ACS}^{\mathrm{qu}}}=\xi(k^{\mathrm{Ar}}),
\qquad
\partial\mathrm{ACS}^{\mathrm{qu}}=\mathcal{V}^{\mathrm{prim}}
\]
are conditional on profinite renormalisation and the local trace
comparison
(\Cref{v4-arith:3d-acs:thm:bulk-boundary-Vprim}). The ordered
incidence model is computed by the normalized ordered bar on the
auxiliary place order $\mathbb{P}\cup\{\infty\}$
(\Cref{v4-arith:3d-acs:thm:chi-hom-bar}), while the comparison with
full BD/CG arithmetic chiral homology is conditional
(\Cref{v4-arith:3d-acs:cor:BDCG-ordered-comparison}). F-RH becomes a
conditional spectral theorem on the partition-function zero locus
(\Cref{v4-arith:3d-acs:thm:arith-gravity-FRH}); the all-genus lift
(\Cref{v4-arith:3d-acs:cor:all-genus-arith-gravity}) covers every row
of the arithmetic-modular family.
