\chapter{Deninger's Arithmetic Cohomology as a Chiral Candidate}
\label{v4-arith:w8-a:deninger-chiral-homology}

\emph{This chapter records the post-attack-and-repair state of the
Deninger construction. The surviving object is not Deninger's missing
cohomology. It is a chiral candidate package: an ordered-incidence
bar skeleton, two formal Tate polar lines, the Bost--Connes Euler
prime-side character, and a named spectral-flow hypothesis. If that
spectral-flow hypothesis is supplied, the package has Deninger's
shape. Without it, the construction does not produce the zero-side
cohomology, the Lefschetz trace formula, or RH.}

\section{Deninger's Wish List}
\label{v4-arith:w8-a:deninger-wishlist}

Deninger's programme asks for a cohomology theory
\[
H^\bullet_\Delta(\overline{\mathrm{Spec}\,\mathbb Z})
\]
with three cohomological degrees, a Frobenius/flow operator, a
regularised determinant equal to the completed zeta function, a
Lefschetz trace formula whose closed-orbit side is the prime side of
the explicit formula, Poincare duality, and purity. For the Riemann
zeta function the middle degree should carry the non-trivial zeros.

\begin{equation}
\label{v4-arith:w8-a:eq:deninger-det}
\zeta(s)
\stackrel{?}{=}
\det\nolimits_\infty
\bigl(s\cdot\mathrm{id}-\Theta\mid
H^\bullet_\Delta\bigr)^{(-1)^\bullet}.
\end{equation}

\begin{equation}
\label{v4-arith:w8-a:eq:deninger-lefschetz}
\sum_\rho h(\rho)
\stackrel{?}{=}
\sum_\bullet(-1)^\bullet
\operatorname{tr}\bigl(h(\Theta)\mid H^\bullet_\Delta\bigr)
\stackrel{?}{=}
\text{polar terms}+\text{archimedean term}
-\sum_{p,k}(\log p)p^{-k/2}\widehat h(k\log p).
\end{equation}

\begin{remark}[absence of a construction]
\label{v4-arith:w8-a:deninger-wishlist:rem:absence}
The axioms above are not a construction. They specify what the missing
arithmetic cohomology must do. The Vol~IV chiral framework supplies
several pieces of this shape, but the operator whose spectrum is the
zero set is not constructed.
\end{remark}

\begin{remark}[Vol IV scoping]
\label{v4-arith:w8-a:deninger-wishlist:rem:vol4}
Chapter~\ref{v4-arith:3d-acs-E1bar} isolates the correct boundary:
the ordered-incidence bar is theorem-grade as an algebraic model, while
the comparison with genuine BD/CG chiral homology, the profinite
quantum ACS theory, and the Deninger spectral flow remain conditional.
This chapter keeps that boundary fixed.
\end{remark}

\section{Surviving Inputs}
\label{v4-arith:w8-a:machinery}
\label{v4-arith:w8-a:machinery:ch23}

The post-audit core has four usable inputs.

\begin{enumerate}
\item The finite-level arithmetic Chern--Simons state sum and gluing
formula of \Cref{v4-arith:3d-acs:thm:finite-level-ACS}. This is a
closed finite groupoid state-sum statement, not a full profinite TQFT.
\item The ordered-incidence bar
\Cref{v4-arith:3d-acs:defn:E1-bar} and its normalized-bar computation
\Cref{v4-arith:3d-acs:thm:chi-hom-bar}. This computes the explicitly
defined incidence model, not automatically BD/CG factorization
homology on \(\overline{\mathrm{Spec}\,\mathbb Z}\).
\item The Bost--Connes Euler skeleton
\Cref{v4-arith:3d-acs:prop:deninger-prime-side}. It gives the KMS
character \(\zeta(s)\) and the prime-power logarithmic derivative in
\(\mathrm{Re}(s)>1\).
\item The Deninger spectral-flow hypothesis
\Cref{v4-arith:3d-acs:conj:spectral-flow}. This is the Hilbert--Polya
/ Connes--Deninger zero-side input. It carries the hard part.
\end{enumerate}

\section{The Chiral Candidate}
\label{v4-arith:w8-a:identification}

Let \(H^\bullet_{\mathrm{ord}}(\mathcal V^{\mathrm{prim}})\) denote the
homology of the ordered-incidence bar of
\Cref{v4-arith:3d-acs:defn:E1-bar}.

\begin{definition}[arithmetic chiral homology candidate]
\label{v4-arith:w8-a:def:chiral-homology}
\ClaimStatusDefinitional. The \emph{arithmetic chiral homology
candidate} is
\begin{equation}
\label{v4-arith:w8-a:eq:chiral-homology-def}
H^\bullet_{\mathrm{ord}}
(\overline{\mathrm{Spec}\,\mathbb Z},\mathsf H^{\mathrm{Ar}})
:=
H^\bullet\bigl(
B^{\mathrm{ord}}_\bullet(\mathcal V^{\mathrm{prim}})
\bigr).
\end{equation}
It is an ordered-incidence model. Calling it genuine arithmetic chiral
homology requires the separate BD/CG comparison of
\Cref{v4-arith:3d-acs:cor:BDCG-ordered-comparison}.
\end{definition}

\begin{definition}[Deninger chiral candidate]
\label{v4-arith:w8-a:def:deninger-cohomology}
\ClaimStatusDefinitional. The \emph{Deninger chiral candidate} is the
candidate complex of \Cref{v4-arith:3d-acs:def:chiral-deninger-complex}:
\begin{equation}
\label{v4-arith:w8-a:eq:deninger-chiral-def}
H^\bullet_{\Delta,\chi}
(\overline{\mathrm{Spec}\,\mathbb Z})
:=
H^\bullet_{\mathrm{Den},\chi}
(\overline{\mathrm{Spec}\,\mathbb Z}).
\end{equation}
It consists of the ordered-incidence core, completed continuous duals,
and formal Tate polar lines in degrees \(0\) and \(2\).
\end{definition}

\begin{remark}[three labels, not one theorem]
\label{v4-arith:w8-a:rem:three-labels}
There are three nearby objects: Deninger's conjectural cohomology,
the ordered-incidence chiral candidate, and the boundary state space of
the conjectural 3D ACS bulk. The manuscript now treats their equality
as a conditional package, not as a proved identification.
\end{remark}

\begin{proposition}[conditional Deninger packaging]
\label{v4-arith:w8-a:thm:deninger-chiral-equals}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:3d-acs:conj:spectral-flow}, the BD/CG comparison
\Cref{v4-arith:3d-acs:cor:BDCG-ordered-comparison}, and the
topological-dual choices in
\Cref{v4-arith:3d-acs:def:chiral-deninger-complex})}. The chiral
candidate \(H^\bullet_{\Delta,\chi}\), together with the two Tate polar
lines and the spectral-flow operator assumed in
\Cref{v4-arith:3d-acs:conj:spectral-flow}, packages Deninger's formal
axioms for \(\overline{\mathrm{Spec}\,\mathbb Z}\).
\end{proposition}

\begin{proof}
The finite-prime Euler terms are exactly the Bost--Connes series of
\Cref{v4-arith:3d-acs:prop:deninger-prime-side}. The polar lines are
inserted by definition in
\Cref{v4-arith:3d-acs:def:chiral-deninger-complex}. The zero-side
operator, determinant identity, trace formula, and purity are precisely
the extra data demanded by
\Cref{v4-arith:3d-acs:conj:spectral-flow}. Thus the statement is a
packaging implication, not an independent construction of the missing
cohomology.
\end{proof}

\section{No Triple Identification Yet}
\label{v4-arith:w8-a:integration}
\label{v4-arith:w8-a:ah:identification}

\begin{theorem}[no unconditional triple identification]
\label{v4-arith:w8-a:thm:triple-id}
\ClaimStatusProvedHere. The present manuscript does not prove an
unconditional equality among Deninger's conjectural cohomology, the
ordered-incidence chiral candidate, and the boundary homology of
\(\mathrm{ACS}^{\mathrm{qu}}\).
\end{theorem}

\begin{proof}
The first object is conjectural. The second is an explicitly defined
ordered-incidence homology object. The third depends on the profinite
quantum ACS conjecture and on a boundary comparison with
\(\mathcal V^{\mathrm{prim}}\). The only theorem-grade equality is the
normalized-bar computation of the ordered-incidence model. The BD/CG
comparison and spectral-flow identifications are listed as residual
obligations in \Cref{v4-arith:3d-acs:residual}.
\end{proof}

\begin{corollary}[conditional triangle]
\label{v4-arith:w8-a:cor:triangle}
\ClaimStatusConditional \emph{(on the profinite ACS conjecture, the
BD/CG ordered-model comparison, a regularised character map, and the
Deninger spectral-flow hypothesis)}. Under these assumptions one may
write
\begin{equation}
\label{v4-arith:w8-a:eq:triangle}
Z_{\mathrm{ACS}^{\mathrm{qu}}}
(\overline{\mathrm{Spec}\,\mathbb Z};k^{\mathrm{Ar}})
=
\xi(k^{\mathrm{Ar}})
=
\operatorname{ch}_{\mathrm{reg}}
\bigl(H^\bullet_{\Delta,\chi}\bigr)(k^{\mathrm{Ar}}).
\end{equation}
Without those assumptions, \eqref{v4-arith:w8-a:eq:triangle} is a
conditional shorthand.
\end{corollary}

\section{Frobenius and Flow}
\label{v4-arith:w8-a:global-F}

\begin{definition}[finite Euler operators]
\label{v4-arith:w8-a:def:F-finite}
\ClaimStatusDefinitional. At a finite prime \(p\), the Bost--Connes
Adams operation \(\psi_p\) records the prime length \(\log p\) and
contributes the Euler factor \((1-p^{-s})^{-1}\). It is denoted here by
\[
F^{\mathrm{Euler}}_p:=\psi_p.
\]
This is an Euler-skeleton operator, not by itself Deninger's global
Frobenius on middle cohomology.
\end{definition}

\begin{proposition}[finite Wilson/Frobenius comparison is conditional]
\label{v4-arith:w8-a:lem:wilson-finite}
\ClaimStatusConditional \emph{(on the Wilson-line axiom in
\Cref{v4-arith:3d-acs:conj:qu-acs})}. A Wilson loop around the
Morishita knot attached to \(p\) should recover the corresponding
Frobenius trace. This is part of the conjectural ACS package, not a
consequence of the ordered bar.
\end{proposition}

\begin{definition}[archimedean scaling candidate]
\label{v4-arith:w8-a:def:F-infinity}
\ClaimStatusDefinitional. The archimedean scaling generator is the
Mellin infinitesimal \( -\partial_t\) on
\(\mathbb R_+\). It becomes a Deninger zero operator only after a
spectral-flow identification with
\(\Theta_\xi=\frac12\mathrm{id}+iH_{\mathrm{HP}}\).
\begin{equation}
\label{v4-arith:w8-a:eq:F-infinity}
\Theta_{\infty,\chi}\stackrel{?}{=}
\Theta_\xi.
\end{equation}
\end{definition}

\begin{proposition}[Virasoro conjugacy is not available]
\label{v4-arith:w8-a:lem:L0-conjugacy}
\ClaimStatusConditional \emph{(on the spectral-flow hypothesis)}.
The manuscript cannot identify the Virasoro \(L_0^{\mathrm{Ar}}\),
the Bost--Connes logarithmic Hamiltonian, and the Hilbert--Polya
operator without the spectral-flow theorem. They remain distinct
operators until that theorem is supplied.
\end{proposition}

\begin{definition}[formal global flow]
\label{v4-arith:w8-a:def:F-global}
\ClaimStatusDefinitional. The formal global flow symbol is
\begin{equation}
\label{v4-arith:w8-a:eq:F-global}
F_\chi:=
\Theta_{\infty,\chi}\oplus\bigoplus_p F^{\mathrm{Euler}}_p.
\end{equation}
The notation records finite-prime lengths and archimedean scaling. It
does not assert a well-defined Deninger Frobenius on a completed
cohomology theory.
\end{definition}

\begin{theorem}[global Frobenius obstruction]
\label{v4-arith:w8-a:thm:F-global-welldef}
\ClaimStatusProvedHere. The ordered-incidence bar and Bost--Connes
Euler skeleton do not construct Deninger's global Frobenius operator.
\end{theorem}

\begin{proof}
The Bost--Connes side gives Euler factors and the prime-power series
in the half-plane of convergence. Deninger's operator must act on the
middle cohomology with spectral data equal to the non-trivial zeros and
must participate in a Lefschetz trace formula. That zero-side operator
is exactly the missing spectral-flow input of
\Cref{v4-arith:3d-acs:conj:spectral-flow}.
\end{proof}

\begin{remark}[archimedean Wilson surface]
\label{v4-arith:w8-a:rem:wilson-infinity}
The phrase ``archimedean Wilson surface'' is useful only as a
conditional dictionary entry inside the profinite ACS conjecture. It
is not an independent construction of \(\Theta_\xi\).
\end{remark}

\section{Character, Degrees, and Purity}
\label{v4-arith:w8-a:character}
\label{v4-arith:w8-a:H-structure}

\begin{theorem}[character identity is conditional]
\label{v4-arith:w8-a:thm:character-identity}
\ClaimStatusConditional \emph{(on
\Cref{v4-arith:3d-acs:cor:partition-bar} and
\Cref{v4-arith:3d-acs:conj:spectral-flow})}. The regularised
character of the Deninger chiral candidate is \(\xi(s)\) only after
the partition-function comparison and the zero-side spectral-flow
operator are assumed.
\begin{equation}
\label{v4-arith:w8-a:eq:character}
\operatorname{ch}_{\mathrm{reg}}
\bigl(H^\bullet_{\Delta,\chi}\bigr)(s)
\stackrel{\mathrm{cond}}{=}
\xi(s).
\end{equation}
\end{theorem}

\begin{remark}[normalisation]
\label{v4-arith:w8-a:rem:normalisation}
The additive determinant form
\(\det_\infty(s\cdot\mathrm{id}-\Theta)\) and the multiplicative
Euler-character form are interchangeable only after the operator
\(\Theta\), the polar signs, and the regularisation convention have
been fixed.
\end{remark}

\begin{proposition}[formal Tate polar lines]
\label{v4-arith:w8-a:prop:H0-H2}
\ClaimStatusProvedHere. The candidate complex contains formal
one-dimensional Tate lines in degrees \(0\) and \(2\). This accounts
for the polar terms in the Deninger skeleton but does not prove that
the total complex has only Deninger's three degrees.
\end{proposition}

\begin{proposition}[middle cohomology is the hard part]
\label{v4-arith:w8-a:prop:H1-structure}
\ClaimStatusConditional \emph{(on
\Cref{v4-arith:3d-acs:conj:spectral-flow})}. Identifying the middle
cohomology with a Hilbert space whose self-adjoint generator has
spectrum \(\{\gamma_\rho\}\) is precisely the Hilbert--Polya part of
the programme.
\end{proposition}

\begin{remark}[critical-line locus]
\label{v4-arith:w8-a:rem:crit-line-weight}
Purity of the middle degree is the assertion that the zero-side
operator has real part \(1/2\). For zeta this is RH in cohomological
language.
\end{remark}

\section{Duality and Positivity}
\label{v4-arith:w8-a:poincare-duality}

\begin{theorem}[duality gives the functional equation, not positivity]
\label{v4-arith:w8-a:thm:triple-duality}
\ClaimStatusConditional \emph{(on the relevant Koszul and ACS
comparison hypotheses)}. The Koszul self-duality framework accounts
for the functional-equation symmetry \(s\leftrightarrow 1-s\). It does
not by itself imply positivity of the Deninger middle pairing or RH.
\end{theorem}

\section{Purity as the RH-Level Input}
\label{v4-arith:w8-a:purity}

\begin{theorem}[purity is RH-level]
\label{v4-arith:w8-a:thm:purity-equivalence}
\ClaimStatusConditional \emph{(on the spectral-flow/Hilbert--Polya
realisation)}. Deninger purity for
\(H^1_{\Delta,\chi}\), Hilbert--Polya self-adjointness for
\(\Theta_\xi\), and the RH zero-placement statement are equivalent
forms of the same missing input.
\end{theorem}

\begin{corollary}[Deninger-chiral RH route]
\label{v4-arith:w8-a:cor:rh-route}
\ClaimStatusConditional. The chiral route can prove RH only by proving
the spectral-flow/positivity input. The ordered-incidence bar and the
Bost--Connes Euler skeleton reduce the shape of the problem; they do
not remove it.
\end{corollary}

\section{All-Genus Extension}
\label{v4-arith:w8-a:all-genus}

\begin{definition}[genus-\(g\) chiral Deninger candidate]
\label{v4-arith:w8-a:def:deninger-g}
\ClaimStatusDefinitional. For a genus-\(g\) arithmetic datum
\(\mathcal D_g\), the genus-\(g\) candidate is
\begin{equation}
\label{v4-arith:w8-a:eq:deninger-g-def}
H^\bullet_{\Delta,\chi,g}
:=
H^\bullet_{\mathrm{ord}}
(\mathcal D_g,\mathcal V^{\mathrm{prim},g}).
\end{equation}
\end{definition}

\begin{theorem}[all-genus packaging]
\label{v4-arith:w8-a:thm:all-genus-deninger}
\ClaimStatusConditional \emph{(on the all-genus ACS, ordered-model
comparison, and spectral-flow hypotheses)}. The genus-\(g\) candidate
packages the expected motivic functional-equation centre and prime-side
Euler data. It does not construct the genus-\(g\) Deninger cohomology
without the same spectral-flow input.
\end{theorem}

\begin{remark}[weight convention]
\label{v4-arith:w8-a:rem:weight-g}
The expected purity line is
\(\mathrm{Re}(s)=w_{\mathcal D_g}/2\). This is a target condition, not
a theorem of the ordered bar.
\end{remark}

\section{Dictionary}
\label{v4-arith:w8-a:dictionary}

\begin{table}[h]
\centering
\small
\begin{tabular}{p{0.26\linewidth}p{0.31\linewidth}p{0.31\linewidth}}
\toprule
Deninger target & Chiral/ACS object & Status \\
\midrule
finite prime orbit lengths & Bost--Connes Euler skeleton & proved in
\(\mathrm{Re}(s)>1\) \\
cohomology object & ordered-incidence candidate plus polar lines &
defined, not identified with Deninger cohomology \\
global Frobenius/flow & spectral-flow operator \(\Theta_\xi\) &
open, Hilbert--Polya strength \\
determinant \(=\xi\) & regularised character & conditional \\
Lefschetz trace formula & prime-power trace distribution & open \\
purity & real part \(1/2\) for middle spectrum & RH-level \\
\bottomrule
\end{tabular}
\caption{Surviving Deninger--chiral dictionary.}
\label{v4-arith:w8-a:table:triple}
\end{table}

\section{What Closes}
\label{v4-arith:w8-a:what-closes}

\subsection*{Closed}
\label{v4-arith:w8-a:what-closes:uncond}

\begin{enumerate}
\item Ordered-incidence homology is computed by the normalized ordered
bar.
\item The finite-prime Bost--Connes side gives the Euler product and
logarithmic derivative in the convergence half-plane.
\item The formal Tate polar lines can be inserted as part of the
candidate complex.
\item Koszul self-duality explains the functional-equation symmetry.
\end{enumerate}

\subsection*{Conditional}
\label{v4-arith:w8-a:what-closes:cond}

\begin{enumerate}
\item Profinite quantum arithmetic Chern--Simons.
\item Boundary comparison with \(\mathcal V^{\mathrm{prim}}\).
\item BD/CG comparison with the ordered-incidence model.
\item Regularised character equality with \(\xi\).
\item Spectral flow/Hilbert--Polya zero operator.
\item Positivity/purity of the middle degree.
\end{enumerate}

\section{Residual Obligations}
\label{v4-arith:w8-a:residual}

The residue is a single mathematical obstruction seen through several
interfaces: construct the middle operator and prove the trace formula
with positivity. Equivalently, prove the spectral-flow hypothesis of
\Cref{v4-arith:3d-acs:conj:spectral-flow}. All other pieces are
preparation, bookkeeping, or conditional packaging.

\section{Summary}
\label{v4-arith:w8-a:summary}

\begin{enumerate}
\item The manuscript now constructs a Deninger \emph{candidate}, not
Deninger's missing cohomology.
\item The ordered bar computes the ordered-incidence model only.
\item The prime side is the Bost--Connes Euler skeleton; the full
Weil--Guinand/Lefschetz trace formula is not obtained from it alone.
\item The global Frobenius and the middle zero spectrum are exactly
the spectral-flow/Hilbert--Polya obstruction.
\item Arithmetic gravity therefore gives a geometric reformulation of
RH-level positivity, not a proof of RH.
\end{enumerate}
