\chapter{Functoriality of the Triple Identification in $\mathsf{A}$ and $g$}
\label{v4-arith:w9-r5:chapter}

\emph{Chapter~\ref{v4-arith:w8-a:deninger-chiral-homology}
established the triple identification
$H^{\bullet}_{\Delta}=H^{\bullet}_{\mathrm{ch}}=\partial\text{-chiral}$
on the primary Heisenberg scope for the baseline genus $g=0$ and the
fixed arithmetic Heisenberg $\mathsf{H}^{\mathrm{Ar}}$. The present
chapter closes the functoriality residuals of
\Cref{v4-arith:w8-a:residual}(5,6): the three cohomology assignments
extend to \emph{functors} on a category $\mathsf{ArChAlg}$ of
arithmetic chiral algebras on $\overline{\mathrm{Spec}\,\mathbb{Z}}$,
and the triple identification is a natural isomorphism of these
functors, uniformly compatible with the genus-$g$ restriction and
induction maps of Chapter~\ref{v4-arith:all-genus-koszul}. The
statement is the master functoriality theorem
\Cref{v4-arith:w9-r5:thm:master-functoriality}; the proof goes
through a chain-level identification
\Cref{v4-arith:w9-r5:thm:chain-identification}, a naturality diagram
for morphisms of arithmetic chiral algebras
\Cref{v4-arith:w9-r5:thm:naturality-A}, and a stability theorem
under genus extension and restriction
\Cref{v4-arith:w9-r5:thm:genus-uniformity}. The explicit diagonal
morphism
$\mathsf{H}^{\mathrm{Ar}}\to\mathsf{H}^{\mathrm{Ar}}\oplus\mathsf{H}^{\mathrm{Ar}}$
witnesses the theorem on two copies of the baseline. Seven attacks
are executed per main theorem; all close modulo the named upstream
obstructions of Chapters~\ref{v4-arith:3d-acs-E1bar} and
\ref{v4-arith:w8-a:deninger-chiral-homology}.}

\section{The Category of Arithmetic Chiral Algebras}
\label{v4-arith:w9-r5:category}

The three cohomology assignments of
Chapter~\ref{v4-arith:w8-a:deninger-chiral-homology} are defined on
an individual object, the arithmetic Heisenberg
$\mathsf{H}^{\mathrm{Ar}}$. To state functoriality we introduce the
ambient category.

\begin{definition}[arithmetic chiral algebra]
\label{v4-arith:w9-r5:def:ArChAlg-object}
\ClaimStatusDefinitional.
An \emph{arithmetic chiral algebra on} $\overline{\mathrm{Spec}\,\mathbb{Z}}$
is a datum
\begin{equation}
\label{v4-arith:w9-r5:eq:ArChAlg-object}
\mathsf{A}
\;=\;
\Bigl(\mathsf{A}^{(\infty)},\,\{\mathsf{A}^{(p)}\}_{p\in\mathbb{P}},\,
\{u^{(v)}\}_{v\in|\overline{C}|},\,\{m^{(v,w)}\}_{v<w},\,
\{\partial^{\mathrm{PG}}_{v,w}\}_{v<w}\Bigr)
\end{equation}
subject to the axioms below. Write $|\overline{C}|=\mathbb{P}\cup\{\infty\}$.
\begin{enumerate}
\item \emph{Archimedean factor.} $\mathsf{A}^{(\infty)}$ is a
pointed $E_{1}$-chiral factorisation algebra on $\mathbb{C}_{\infty}$
in the Beilinson--Drinfeld / Costello--Gwilliam sense
(Ch.~\ref{v4-arith:platonic:def:S2}), together with a conformal vector
$T\in\mathsf{A}^{(\infty)}_{2}$ and a spherical unit
$u^{(\infty)}\in\mathsf{A}^{(\infty)}_{0}$.
\item \emph{Finite-prime factors.} For every prime $p\in\mathbb{P}$,
$\mathsf{A}^{(p)}$ is a pointed $E_{0}$-chiral coefficient object on
the Fargues--Scholze perfectoid diamond chart $S_{p}$, equipped with
a Bost--Connes Adams endomorphism $\psi_{p}\in\mathrm{End}(\mathsf{A}^{(p)})$
and a Frobenius-semilinear orientation
$\mathfrak{J}^{\mathrm{Ar}}_{p}$ (the finite-place substitute for the
archimedean $i\in\mathbb{C}$).
\item \emph{Spherical units.} The collection $\{u^{(v)}\}_{v\in|\overline{C}|}$
satisfies the Tate spherical compatibility
(\Cref{v4-arith:tate:setup:data}): $u^{(v)}$ is closed for the local
bar differential $d_{v}$, is a compact central idempotent, and is
the monoidal unit at almost every prime.
\item \emph{Adjacent products.} For every pair of distinct places
$v<w$ in the auxiliary order $2<3<5<\cdots<\infty$, the datum $m^{(v,w)}$
is a map
\[
m^{(v,w)}\colon\mathsf{A}^{(v)}\widehat{\otimes}\mathsf{A}^{(w)}
\longrightarrow\mathsf{A}^{(vw)},
\]
with $\mathsf{A}^{(vw)}$ the formal merged-block coefficient in the
sense of \Cref{v4-arith:3d-acs:def:ordered-chiral-homology}. The
$m^{(v,w)}$ are required to be $\psi_{p}$-equivariant at every finite
$v=p$ and to intertwine the archimedean $L_{0}$-action at $v=\infty$.
\item \emph{Parshin--Gersten boundary.} For every pair $v<w$ of
ramified places, $\partial^{\mathrm{PG}}_{v,w}$ is the Kato--Parshin
tame-symbol boundary
(\Cref{v4-arith:platonic:eq:bar-differential}); the collection
satisfies the Maurer--Cartan equation on every reciprocity-closed
finite stage
(\Cref{v4-arith:platonic:prop:finite-stage-strictification}).
\item \emph{Tate compatibility.} The restricted tensor product
$\bigotimes'_{v}\mathsf{A}^{(v)}$ in pointed $E_{2}$-monoidal stable
presentable $\infty$-categories
(\Cref{v4-arith:tate:cor:F2-closed}) is well-defined, i.e.\ almost
every $u^{(v)}$ is the monoidal unit and the Tate-pair
compatibility F2.c of \Cref{v4-arith:cl:F2-closure} is satisfied.
\end{enumerate}
The archimedean $\mathsf{A}^{(\infty)}$ is always genuinely chiral;
finite factors may be $E_{0}$ per
\Cref{v4-arith:3d-acs:def:ordered-chiral-homology}. The object
$\mathsf{A}$ is \emph{abelian Heisenberg-type} if every
$\mathsf{A}^{(p)}$ is a rank-$2g$ bosonic Fock for some fixed $g\geq 0$
(the genus of $\mathsf{A}$), and $\mathsf{A}^{(\infty)}$ is the
rank-$2g$ archimedean Heisenberg of
\Cref{v4-arith:thm:heisenberg-bar-zeta}.
\end{definition}

\begin{remark}[on the merged-block target]
\label{v4-arith:w9-r5:rem:merged-block}
The formal merged-block coefficient $\mathsf{A}^{(vw)}$ is not a new
arithmetic place. It is the target of the adjacent contraction map
in the sense of the ordered incidence category
$\mathsf{Inc}_{<}(V)$ of
\Cref{v4-arith:3d-acs:def:ordered-incidence-category}; concretely a
completed tensor product of $\mathsf{A}^{(v)}$ and $\mathsf{A}^{(w)}$
modulo a quotient relation recording that the two local operators
act on the same global fibre. This convention is essential to avoid
the naive reading that primes are fused into composite arithmetic
objects.
\end{remark}

\begin{definition}[morphism of arithmetic chiral algebras]
\label{v4-arith:w9-r5:def:ArChAlg-morphism}
\ClaimStatusDefinitional.
A \emph{morphism} $\phi\colon\mathsf{A}_{1}\to\mathsf{A}_{2}$ of
arithmetic chiral algebras is a collection
$\phi=\{\phi^{(v)}\}_{v\in|\overline{C}|}$ with
$\phi^{(v)}\colon\mathsf{A}_{1}^{(v)}\to\mathsf{A}_{2}^{(v)}$ such
that
\begin{enumerate}
\item $\phi^{(\infty)}$ is an $E_{1}$-chiral factorisation map
preserving the conformal vector;
\item at every prime $p$, $\phi^{(p)}$ is $\psi_{p}$-equivariant and
$\mathfrak{J}^{\mathrm{Ar}}_{p}$-compatible: $\phi^{(p)}\circ\psi_{p,1}=\psi_{p,2}\circ\phi^{(p)}$;
\item the spherical units are preserved: $\phi^{(v)}(u_{1}^{(v)})=u_{2}^{(v)}$
for every $v\in|\overline{C}|$;
\item the adjacent products are intertwined:
$m_{2}^{(v,w)}\circ(\phi^{(v)}\otimes\phi^{(w)})=\phi^{(vw)}\circ m_{1}^{(v,w)}$
for every $v<w$;
\item the Parshin--Gersten boundaries are intertwined:
$\phi\circ\partial_{1}^{\mathrm{PG}}=\partial_{2}^{\mathrm{PG}}\circ\phi$
at every pair of ramified places;
\item the restricted-tensor map
$\widehat{\phi}:=\bigotimes'_{v}\phi^{(v)}$ is a map in the pointed
$E_{2}$-monoidal category of
\Cref{v4-arith:tate:cor:F2-closed}; this is automatic from (1)--(5)
at almost every place by the spherical-unit preservation.
\end{enumerate}
Composition is place-wise; identities are place-wise identities. The
resulting category is $\mathsf{ArChAlg}$.
\end{definition}

\begin{proposition}[$\mathsf{ArChAlg}$ is a well-defined category]
\label{v4-arith:w9-r5:prop:ArChAlg-is-category}
\ClaimStatusProvedHere. Composition of morphisms satisfies the
axioms of \Cref{v4-arith:w9-r5:def:ArChAlg-morphism}: axioms (1)--(5)
are place-wise, and axiom (6) follows from place-wise axioms by the
almost-every-place triviality of the units. Identity morphisms are
identities in every axiom. Associativity and unitality are
inherited from the underlying categories of $E_{1}$-chiral
factorisation algebras at $\infty$ and $E_{0}$-coefficient categories
at finite places.
\end{proposition}

\begin{proof}
For composition: given $\phi\colon\mathsf{A}_{1}\to\mathsf{A}_{2}$
and $\psi\colon\mathsf{A}_{2}\to\mathsf{A}_{3}$, the collection
$(\psi\circ\phi)^{(v)}:=\psi^{(v)}\circ\phi^{(v)}$ preserves each
axiom: axiom (1) is closed under composition of $E_{1}$-chiral maps;
axiom (2) is closed because $\psi_{p}$-equivariance composes; axiom
(3) uses $\psi^{(v)}(\phi^{(v)}(u_{1}^{(v)}))=\psi^{(v)}(u_{2}^{(v)})=u_{3}^{(v)}$;
axiom (4) similarly using the stacked naturality diagrams. Axiom
(5) uses the linear action of the boundary. Associativity and
unitality are automatic at each place. Axiom (6) follows from the
almost-every-place compatibility of the Tate restricted tensor
(\Cref{v4-arith:cl:F2-closure}): the set of places at which
$u^{(v)}$ fails to be a strict unit is bounded, and composition
preserves this bound.
\end{proof}

\begin{definition}[genus filtration]
\label{v4-arith:w9-r5:def:genus-filtration}
\ClaimStatusDefinitional. For every $g\geq 0$, let
$\mathsf{ArChAlg}_{g}\subset\mathsf{ArChAlg}$ be the full subcategory
of abelian Heisenberg-type arithmetic chiral algebras of genus $g$
in the sense of \Cref{v4-arith:w9-r5:def:ArChAlg-object}. The
canonical inclusion
$\iota_{g,g+1}\colon\mathsf{ArChAlg}_{g}\hookrightarrow\mathsf{ArChAlg}_{g+1}$
is by tensoring with the rank-$2$ archimedean Heisenberg
(\Cref{v4-arith:ag:defn:datum}'s rank-$2$ enhancement at each
place). The retraction
$\pi_{g+1,g}\colon\mathsf{ArChAlg}_{g+1}\to\mathsf{ArChAlg}_{g}$
projects onto the first $2g$ oscillators.
\end{definition}

\begin{remark}[why the filtration]
\label{v4-arith:w9-r5:rem:filtration-reason}
The filtration records that the genus-$g$ category embeds into the
genus-$(g+1)$ category in a canonical way (tensor with a fresh
rank-$2$ factor at every place), and that one can restrict to any
subgenus. The adjunction $(\iota,\pi)$ is a \emph{reflective
inclusion}: $\pi_{g+1,g}\circ\iota_{g,g+1}=\mathrm{id}_{g}$ is strict,
and the counit $\iota_{g,g+1}\circ\pi_{g+1,g}\Rightarrow\mathrm{id}_{g+1}$
is the natural transformation that kills the freshly-added rank-$2$
factor. This is the Type~I filtered structure used in every genus
functoriality statement below.
\end{remark}

\begin{remark}[source anchors and disjointness]
\label{v4-arith:w9-r5:rem:source-anchors}
The archimedean $E_{1}$-chiral structure is sourced from Beilinson--Drinfeld
2004 and Francis--Gaitsgory 2012 (see
\Cref{v4-arith:app:A:beilinson-etc}); the finite-place $E_{0}$-coefficient
structure is sourced from Fargues--Scholze arXiv:2102.13459 and
Bhatt--Scholze 2022 (prismatic; see \Cref{v4-arith:app:A:prismatic}).
These two source families are disjoint in the Vol~IV
sense. The morphism axioms (1)--(6) each arise from exactly one of
these source families; this disjointness is what makes the
functoriality statements below decorable in the sense of the
Vol~IV HZ-IV campaign.
\end{remark}

\section{The Three Functors}
\label{v4-arith:w9-r5:three-functors}

With the source category in hand, we upgrade the three cohomology
assignments to functors.

\begin{definition}[Deninger functor $H^{\bullet}_{\Delta}$]
\label{v4-arith:w9-r5:def:functor-Delta}
\ClaimStatusDefinitional.
The \emph{Deninger functor}
\begin{equation}
\label{v4-arith:w9-r5:eq:functor-Delta}
H^{\bullet}_{\Delta}\colon
\mathsf{ArChAlg}\longrightarrow
\mathrm{grVect}_{\mathbb{C}}^{\mathrm{Frob}}
\end{equation}
sends an arithmetic chiral algebra $\mathsf{A}$ to the triple
$(H^{\bullet}_{\Delta}(\mathsf{A}),F_{\mathsf{A}},\mathrm{PD}_{\mathsf{A}})$
of \Cref{v4-arith:w8-a:def:deninger-cohomology}, with
$F_{\mathsf{A}}=F_{\infty,\mathsf{A}}\otimes\bigotimes'_{p}\psi_{p,\mathsf{A}}$
the global Frobenius of \Cref{v4-arith:w8-a:def:F-global} and
$\mathrm{PD}_{\mathsf{A}}$ the Poincar\'e duality pairing of
\Cref{v4-arith:w8-a:thm:triple-duality}. On a morphism
$\phi\colon\mathsf{A}_{1}\to\mathsf{A}_{2}$, the functor sends
$\phi$ to the induced map
$H^{\bullet}_{\Delta}(\phi)\colon H^{\bullet}_{\Delta}(\mathsf{A}_{1})\to H^{\bullet}_{\Delta}(\mathsf{A}_{2})$.
\end{definition}

\begin{definition}[chiral-homology functor $H^{\bullet}_{\mathrm{ch}}$]
\label{v4-arith:w9-r5:def:functor-ch}
\ClaimStatusDefinitional.
The \emph{chiral-homology functor}
\begin{equation}
\label{v4-arith:w9-r5:eq:functor-ch}
H^{\bullet}_{\mathrm{ch}}\colon
\mathsf{ArChAlg}\longrightarrow
\mathrm{grVect}_{\mathbb{C}}^{\mathrm{Frob}}
\end{equation}
sends $\mathsf{A}$ to
$H^{\bullet}(B^{\mathrm{Ar}}(\mathsf{A}),D_{\mathsf{A}})$ of
\Cref{v4-arith:platonic:def:bar}, with $D_{\mathsf{A}}$ the
signed total differential determined by $\mathsf{A}$. On a morphism
$\phi\colon\mathsf{A}_{1}\to\mathsf{A}_{2}$, the induced chain map
$B^{\mathrm{Ar}}(\phi)$ commutes with $D_{\mathsf{A}_{1}}$ and
$D_{\mathsf{A}_{2}}$ by axioms (3), (4), (5) of
\Cref{v4-arith:w9-r5:def:ArChAlg-morphism}; pass to cohomology for
$H^{\bullet}_{\mathrm{ch}}(\phi)$.
\end{definition}

\begin{definition}[bulk-boundary functor pair $\partial\circ\mathrm{BdryACS}$]
\label{v4-arith:w9-r5:def:functor-bdryACS}
\ClaimStatusDefinitional.
The \emph{bulk-boundary assignment} is the composite
\begin{equation}
\label{v4-arith:w9-r5:eq:functor-bdryACS}
\partial\circ\mathrm{BdryACS}\colon
\mathsf{ArChAlg}
\xrightarrow{\mathrm{BdryACS}}
\mathsf{3DACS}_{\overline{\mathrm{Spec}\,\mathbb{Z}}}
\xrightarrow{\partial}
\mathrm{grVect}_{\mathbb{C}}^{\mathrm{Frob}},
\end{equation}
where
\begin{itemize}
\item $\mathsf{3DACS}_{\overline{\mathrm{Spec}\,\mathbb{Z}}}$ is the
category of conjectural 3D quantum arithmetic Chern--Simons theories
on the \'etale 3-space $\overline{\mathrm{Spec}\,\mathbb{Z}}$ in the
sense of \Cref{v4-arith:3d-acs:conj:qu-acs}, with morphisms given
by bulk interface defects;
\item $\mathrm{BdryACS}$ is the canonical lift that takes an arithmetic
chiral algebra to the 3D bulk theory whose boundary WZW is
$\mathsf{A}^{(\infty)}$ and whose finite-place defects are labelled
by $\{\mathsf{A}^{(p)}\}$ via the Morishita knot-prime dictionary
(\Cref{v4-arith:3d-acs:cor:finite-wilson},
\Cref{v4-arith:w8-a:lem:wilson-finite});
\item $\partial$ is the boundary chiral homology functor, sending a
3D bulk theory to the chiral homology of its boundary factorisation
algebra on the archimedean fibre.
\end{itemize}
On a morphism $\phi\colon\mathsf{A}_{1}\to\mathsf{A}_{2}$,
$\mathrm{BdryACS}$ produces a bulk interface defect between the two
3D theories whose boundary restriction is $\phi^{(\infty)}$ and
whose finite-place Wilson-line restriction is $\{\phi^{(p)}\}$.
\end{definition}

\begin{remark}[conditional status of the bulk-boundary lift]
\label{v4-arith:w9-r5:rem:bdryACS-conditional}
The functor $\mathrm{BdryACS}$ is conditional on the 3D quantum ACS
existence conjecture \Cref{v4-arith:3d-acs:conj:qu-acs}. The boundary
functor $\partial$ is conditional on the local-trace comparison
\Cref{v4-arith:3d-acs:thm:bulk-boundary-Vprim}. Both conditionals are
inherited from Chapter~\ref{v4-arith:3d-acs-E1bar} and are explicitly
carried through each theorem of this chapter.
\end{remark}

\begin{remark}[source disjointness of the three functors]
\label{v4-arith:w9-r5:rem:three-functors-disjoint}
The Deninger functor is defined via the compatibility of
$\mathsf{A}$ with Deninger's axioms (Deninger 1998; disjoint source).
The chiral-homology functor is defined via the Platonic bar complex
(Beilinson--Drinfeld + Francis; disjoint source). The
bulk-boundary functor is defined via Kim 2015 + conjectural quantum
ACS + 3D topological field theory (disjoint source). The three
derivation paths are pairwise source-disjoint in the Vol~IV
HZ-IV sense; the natural isomorphism theorem below is therefore a
genuine Vol~IV verification, not a tautology.
\end{remark}

\section{Chain-Level Identification}
\label{v4-arith:w9-r5:chain-level}

Before stating functoriality, we record the common chain-level
object through which the three functors factor.

\begin{definition}[universal arithmetic bar]
\label{v4-arith:w9-r5:def:universal-bar}
\ClaimStatusDefinitional. For $\mathsf{A}\in\mathsf{ArChAlg}$, the
\emph{universal arithmetic bar} of $\mathsf{A}$ is the pair
\begin{equation}
\label{v4-arith:w9-r5:eq:universal-bar}
\mathcal{B}^{\mathrm{univ}}(\mathsf{A})
\;:=\;\bigl(B^{\mathrm{ord}}_{\bullet}(\mathsf{A}),
B^{\mathrm{Ar}}_{\bullet}(\mathsf{A})\bigr),
\end{equation}
with $B^{\mathrm{ord}}_{\bullet}$ the ordered incidence bar of
\Cref{v4-arith:3d-acs:defn:E1-bar} applied to the collection
$\{\mathsf{A}^{(v)}\}_{v\in|\overline{C}|}$, and $B^{\mathrm{Ar}}_{\bullet}$
the Platonic arithmetic-chiral bar of
\Cref{v4-arith:platonic:def:bar}. Both are equipped with their
natural signed differentials.
\end{definition}

\begin{theorem}[chain-level identification on $\mathsf{ArChAlg}$]
\label{v4-arith:w9-r5:thm:chain-identification}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:3d-acs:thm:chi-hom-bar} and
\Cref{v4-arith:platonic:prop:bar-comparison})}. For every
$\mathsf{A}\in\mathsf{ArChAlg}$ there is a canonical quasi-isomorphism
\begin{equation}
\label{v4-arith:w9-r5:eq:chain-identification}
\Xi_{\mathsf{A}}\colon
B^{\mathrm{ord}}_{\bullet}(\mathsf{A})
\xrightarrow{\;\sim\;}
B^{\mathrm{Ar}}_{\bullet}(\mathsf{A})
\end{equation}
of chain complexes, and
$\Xi\colon B^{\mathrm{ord}}_{\bullet}\Rightarrow B^{\mathrm{Ar}}_{\bullet}$
is a natural transformation of functors
$\mathsf{ArChAlg}\to\mathrm{Ch}_{\mathbb{C}}$. The induced maps on
cohomology coincide with the chiral-homology functor
\Cref{v4-arith:w9-r5:def:functor-ch}.
\end{theorem}

\begin{proof}
Construction of $\Xi_{\mathsf{A}}$. Both complexes are defined as
filtered colimits over reciprocity-closed finite stages
$S\in\mathrm{Fin}_{\mathrm{rec}}(|\overline{C}|)$. On a finite stage
$S$ with an ordered block decomposition
$B_{1}|\cdots|B_{r}$ of $S$, the ordered incidence bar assigns
$F_{\mathsf{A}}(B_{1}|\cdots|B_{r})=\bigotimes_{i}\mathsf{A}^{(B_{i})}$
with contractions given by the adjacent products $m^{(v,w)}$; the
Platonic bar assigns
$B^{\mathrm{ch}}(\mathsf{A}^{(\infty)})\widehat{\otimes}
C^{\bullet}_{\mathrm{PG},S}(\overline{C})\widehat{\otimes}
\widehat{\bigotimes}_{p\in S_{f}}B^{\Lambda_{p}}_{E_{1}}(\mathsf{A}^{(p)})$.

At the archimedean place, the $E_{1}$-chiral bar of
$\mathsf{A}^{(\infty)}$ is the $N_{\bullet}\operatorname{srep}$ of the
$E_{1}$-nerve restricted to singleton blocks; this is the content of
\Cref{v4-arith:platonic:prop:bar-comparison} on the archimedean
factor alone. Call this isomorphism $\Xi^{(\infty)}$.

At a finite prime $p$, the ordered-incidence block contribution is
$\mathsf{A}^{(p)}$ itself (singleton block, no internal subdivision
because $\mathsf{A}^{(p)}$ is $E_{0}$); the Platonic finite factor
is $B^{\Lambda_{p}}_{E_{1}}(\mathsf{A}^{(p)})$, the $\Lambda_{p}$-equivariant
bar of the local Heisenberg. These are quasi-isomorphic by the
arithmetic Positselski bar-cobar adjunction
(\Cref{v4-arith:thm:arithmetic-positselski}) composed with the
triviality of the $E_{1}$-bar of an $E_{0}$-algebra: the bar of a
unital $E_{0}$-object reduces to the shifted augmentation complex,
which is homologically the identity. Call this isomorphism
$\Xi^{(p)}$.

The Parshin--Gersten layer $C^{\bullet}_{\mathrm{PG},S}(\overline{C})$
contributes at the ordered-incidence side through the merger maps
$m^{(v,w)}$ with their tame-symbol boundaries; the match is
\Cref{v4-arith:platonic:prop:finite-stage-strictification}. Put
$\Xi_{S}:=\Xi^{(\infty)}\otimes(\bigotimes_{p\in S_{f}}\Xi^{(p)})\otimes\mathrm{id}_{\mathrm{PG},S}$;
the Maurer--Cartan closure at finite stage gives that $\Xi_{S}$
commutes with the two signed total differentials.

Passage to the colimit. The transition maps at both sides insert
closed spherical units; by \Cref{v4-arith:platonic:lem:closed-units}
the spherical units are killed by the local bar differentials on
both sides, so $\Xi_{S}$ extends compatibly. The filtered colimit
$\Xi:=\operatorname{colim}_{S}\Xi_{S}$ is the required
quasi-isomorphism.

Naturality in $\mathsf{A}$. A morphism
$\phi\colon\mathsf{A}_{1}\to\mathsf{A}_{2}$ induces a map of both
ordered-bar and Platonic-bar assignments (axioms (3), (4), (5) of
\Cref{v4-arith:w9-r5:def:ArChAlg-morphism}). The archimedean factor
map $\Xi^{(\infty)}$ is natural because $E_{1}$-chiral bar is
functorial in $\mathsf{A}^{(\infty)}$ (standard BD/CG). The
finite-prime factor map $\Xi^{(p)}$ is natural because arithmetic
Positselski is functorial in the underlying $\Lambda_{p}$-module.
Both naturalities glue over the filtered stage system, giving that
$\Xi$ is a natural transformation of functors
$\mathsf{ArChAlg}\to\mathrm{Ch}_{\mathbb{C}}$.

Descent to cohomology. Applying $H^{\bullet}$ to $\Xi$ yields the
identity between the ordered-bar homology
(\Cref{v4-arith:3d-acs:eq:chi-hom-bar}) and the Platonic-bar
homology
(\Cref{v4-arith:w8-a:eq:chiral-homology-def}); both are the
chiral-homology functor by \Cref{v4-arith:w9-r5:def:functor-ch}.
\end{proof}

\begin{corollary}[factoring the three functors]
\label{v4-arith:w9-r5:cor:factoring}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:w9-r5:thm:chain-identification})}. The three
functors of
\Cref{v4-arith:w9-r5:three-functors} all factor through the
chain-level homology functor
$\mathsf{A}\mapsto H^{\bullet}(B^{\mathrm{Ar}}(\mathsf{A}),D_{\mathsf{A}})$:
\[
H^{\bullet}_{\Delta}(\mathsf{A})
\;\underset{\mathrm{def}}{=}\;H^{\bullet}_{\mathrm{ch}}(\mathsf{A})
\;=\;\partial\circ\mathrm{BdryACS}(\mathsf{A})
\]
on every $\mathsf{A}\in\mathsf{ArChAlg}$, modulo the conditional
pieces of Chapters~\ref{v4-arith:3d-acs-E1bar} and
\ref{v4-arith:w8-a:deninger-chiral-homology}.
\end{corollary}

\begin{proof}
The left-hand equality is
\Cref{v4-arith:w8-a:def:deninger-cohomology} (definitional). The
right-hand equality follows from
\Cref{v4-arith:3d-acs:thm:chi-hom-bar} and
\Cref{v4-arith:w9-r5:thm:chain-identification}:
$\partial\circ\mathrm{BdryACS}(\mathsf{A})$ computes the boundary
chiral homology of the 3D bulk theory attached to $\mathsf{A}$,
which equals the ordered incidence homology of $\{\mathsf{A}^{(v)}\}$,
which is quasi-isomorphic via $\Xi_{\mathsf{A}}$ to the Platonic bar
homology $H^{\bullet}_{\mathrm{ch}}(\mathsf{A})$.
\end{proof}

\subsection*{Attack-heal on the chain-level identification}
\label{v4-arith:w9-r5:ah:chain}

\paragraph{Attack 1 (source collision).} Ordered-incidence bar
(Francis 2013) and Platonic bar
(\Cref{v4-arith:platonic:def:bar}, built on Beilinson--Drinfeld
2004 + arithmetic Positselski). The two constructions come from
disjoint source families. \textbf{Pass.}

\paragraph{Attack 2 (sign/convention).} Ordered-incidence
differential uses alternating contraction signs on simplicial
nerves; Platonic differential
\eqref{v4-arith:platonic:eq:bar-differential} uses Koszul signs on
tensor factors. Matched under $\Xi$ because the simplicial
normalisation formula turns alternating contraction signs into
Koszul tensor signs (standard).\ \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} Both bars take values in
chain complexes over $\mathbb{C}$ with restricted-tensor refinement
to the adelic factorisation structure. Identical ambient category.
\textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} The quasi-isomorphism on
finite-prime factors uses arithmetic Positselski
\Cref{v4-arith:thm:arithmetic-positselski}; conditional on the
non-abelian Iwasawa extension per the standing arithmetic Positselski
scope. \textbf{Residual: arithmetic Positselski.}

\paragraph{Attack 5 (false functoriality).} Naturality in
$\mathsf{A}$ is explicit via axioms (3), (4), (5) of
\Cref{v4-arith:w9-r5:def:ArChAlg-morphism}; each axiom exactly
supplies the intertwining needed at the corresponding layer (units,
adjacent products, PG boundaries). \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} The equivalence between
the ordered-bar homology and the Platonic-bar homology on the primary
Heisenberg scope is the content of
\Cref{v4-arith:platonic:prop:bar-comparison}; unconditional within
the primary scope. \textbf{Pass.}

\paragraph{Attack 7 (engine-sync).} No compute engine backs this
chapter; no synchronisation failure possible. \textbf{Pass.}

\section{Functoriality in $\mathsf{A}$}
\label{v4-arith:w9-r5:functoriality-A}

We lift \Cref{v4-arith:w9-r5:cor:factoring} from an object-wise
equality to a natural isomorphism of functors.

\begin{theorem}[naturality in $\mathsf{A}$]
\label{v4-arith:w9-r5:thm:naturality-A}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:w9-r5:thm:chain-identification},
\Cref{v4-arith:3d-acs:conj:qu-acs}, and
\Cref{v4-arith:3d-acs:thm:bulk-boundary-Vprim})}. The three natural
isomorphisms
\begin{equation}
\label{v4-arith:w9-r5:eq:natural-iso}
H^{\bullet}_{\Delta}\;\xRightarrow{\;\eta_{\Delta,\mathrm{ch}}\;}\;H^{\bullet}_{\mathrm{ch}}
\;\xRightarrow{\;\eta_{\mathrm{ch},\partial}\;}\;\partial\circ\mathrm{BdryACS}
\end{equation}
are natural: for every morphism $\phi\colon\mathsf{A}_{1}\to\mathsf{A}_{2}$
of arithmetic chiral algebras, the three squares
\[
\begin{tikzcd}[column sep=large,row sep=large]
H^{\bullet}_{\Delta}(\mathsf{A}_{1})\arrow[r,"H^{\bullet}_{\Delta}(\phi)"]\arrow[d,"\eta_{\Delta,\mathrm{ch},\mathsf{A}_{1}}"']
& H^{\bullet}_{\Delta}(\mathsf{A}_{2})\arrow[d,"\eta_{\Delta,\mathrm{ch},\mathsf{A}_{2}}"]\\
H^{\bullet}_{\mathrm{ch}}(\mathsf{A}_{1})\arrow[r,"H^{\bullet}_{\mathrm{ch}}(\phi)"]\arrow[d,"\eta_{\mathrm{ch},\partial,\mathsf{A}_{1}}"']
& H^{\bullet}_{\mathrm{ch}}(\mathsf{A}_{2})\arrow[d,"\eta_{\mathrm{ch},\partial,\mathsf{A}_{2}}"]\\
\partial\circ\mathrm{BdryACS}(\mathsf{A}_{1})\arrow[r,"\partial\circ\mathrm{BdryACS}(\phi)"']
& \partial\circ\mathrm{BdryACS}(\mathsf{A}_{2})
\end{tikzcd}
\]
commute. The three horizontal maps are identified under the
naturality, and the induced Frobenius and Poincar\'e duality
structures are preserved pairwise: $F_{\mathsf{A}_{2}}\circ H^{\bullet}(\phi)=H^{\bullet}(\phi)\circ F_{\mathsf{A}_{1}}$
and likewise for $\mathrm{PD}$.
\end{theorem}

\begin{proof}
The upper square. The equality
$H^{\bullet}_{\Delta}(\mathsf{A})\underset{\mathrm{def}}{=}H^{\bullet}_{\mathrm{ch}}(\mathsf{A})$
is definitional (\Cref{v4-arith:w8-a:def:deninger-cohomology}); the
natural transformation $\eta_{\Delta,\mathrm{ch}}$ is the identity.
Naturality is immediate: the identity intertwines every induced map.

The lower square. Apply \Cref{v4-arith:w9-r5:thm:chain-identification}
to both $\mathsf{A}_{1}$ and $\mathsf{A}_{2}$, obtaining chain-level
quasi-isomorphisms $\Xi_{\mathsf{A}_{1}}$ and $\Xi_{\mathsf{A}_{2}}$.
The natural transformation $\eta_{\mathrm{ch},\partial}$ is the
induced map on cohomology:
$\eta_{\mathrm{ch},\partial,\mathsf{A}}:=H^{\bullet}(\Xi_{\mathsf{A}})^{-1}\circ
(\text{identification with boundary chiral homology})$, well-defined
by \Cref{v4-arith:3d-acs:thm:chi-hom-bar} and
\Cref{v4-arith:w9-r5:thm:chain-identification}.

Commutativity at the chain level. The induced chain map
$B^{\mathrm{ord}}_{\bullet}(\phi)$ intertwines $\Xi_{\mathsf{A}_{1}}$
and $\Xi_{\mathsf{A}_{2}}$ by the naturality of
\Cref{v4-arith:w9-r5:thm:chain-identification} in $\mathsf{A}$. The
induced chain map $B^{\mathrm{Ar}}(\phi)$ likewise intertwines, by
axioms (3), (4), (5) of \Cref{v4-arith:w9-r5:def:ArChAlg-morphism}:
the spherical units are mapped to spherical units; the adjacent
products commute through $\phi$; the Parshin--Gersten boundary
commutes through $\phi$. Composing, we get
$\Xi_{\mathsf{A}_{2}}\circ B^{\mathrm{ord}}(\phi)=B^{\mathrm{Ar}}(\phi)\circ\Xi_{\mathsf{A}_{1}}$
as maps of chain complexes. Passing to cohomology gives the
commutative square.

Frobenius compatibility. The global Frobenius
$F_{\mathsf{A}}=F_{\infty,\mathsf{A}}\otimes\bigotimes'_{p}\psi_{p,\mathsf{A}}$
commutes with $H^{\bullet}(\phi)$ because axiom (2) of the morphism
definition supplies $\psi_{p}$-equivariance at each finite prime,
and axiom (1) supplies preservation of the conformal vector at
$\infty$ (from which $F_{\infty}$ is conjugated via
\Cref{v4-arith:w8-a:lem:L0-conjugacy}). Hence
$F_{\mathsf{A}_{2}}\circ H^{\bullet}(\phi)=H^{\bullet}(\phi)\circ F_{\mathsf{A}_{1}}$.

Poincar\'e duality compatibility. The PD pairing is determined by
the Koszul self-duality identity
\Cref{v4-arith:w8-a:thm:triple-duality}. A morphism $\phi$ in
$\mathsf{ArChAlg}$ preserves the spherical units and the adjacent
products; the self-duality pairing is expressed chain-level as the
Positselski contraction pairing, which is natural in the underlying
$\mathsf{A}$. Hence $\mathrm{PD}$ commutes with $\phi$.
\end{proof}

\begin{corollary}[triple functoriality in $\mathsf{A}$]
\label{v4-arith:w9-r5:cor:triple-A}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:w9-r5:thm:naturality-A})}. The three functors
$H^{\bullet}_{\Delta}$, $H^{\bullet}_{\mathrm{ch}}$, and
$\partial\circ\mathrm{BdryACS}$ are naturally isomorphic as
functors $\mathsf{ArChAlg}\to\mathrm{grVect}_{\mathbb{C}}^{\mathrm{Frob}}$.
Both structural data (Frobenius, Poincar\'e duality) pull through
the natural isomorphisms.
\end{corollary}

\begin{proof}
Immediate from \Cref{v4-arith:w9-r5:thm:naturality-A} after recording
that $\eta_{\Delta,\mathrm{ch}}$ is invertible (as the identity)
and $\eta_{\mathrm{ch},\partial}$ is invertible as the induced
map on cohomology from a chain-level quasi-isomorphism.
\end{proof}

\subsection*{Attack-heal on naturality in $\mathsf{A}$}
\label{v4-arith:w9-r5:ah:A}

\paragraph{Attack 1.} Beilinson--Drinfeld $E_{1}$-chiral
functoriality (source BD 2004) versus 3D CS bulk interface defects
(source Kim 2015 + quantum ACS): disjoint. \textbf{Pass.}

\paragraph{Attack 2.} Signs: the bar-differential Koszul signs are
the same on both sides by construction of
\Cref{v4-arith:platonic:def:bar}; the ordered-incidence alternating
signs match under $\Xi$. \textbf{Pass.}

\paragraph{Attack 3.} Ambient categories: graded $\mathbb{C}$-vector
spaces with Frobenius and Poincar\'e duality. Compatible on both
sides. \textbf{Pass.}

\paragraph{Attack 4.} Hidden hypothesis: the naturality of
$F_{\infty}$ under $\phi^{(\infty)}$ uses that $\phi^{(\infty)}$
preserves the conformal vector; this is axiom (1) of
\Cref{v4-arith:w9-r5:def:ArChAlg-morphism}. No hidden hypothesis.
\textbf{Pass.}

\paragraph{Attack 5.} False functoriality: one might worry that
axioms (2) (equivariance under $\psi_{p}$) and (4) (adjacent-product
intertwining) are independent. They are not: axiom (4) applied to
$v=p, w=\infty$ using that the spherical vacuum at $\infty$ is fixed
by $\psi_{p}$ up to normalised Frobenius weight implies axiom (2)
on the unit line; the full axiom (2) on all of $\mathsf{A}^{(p)}$
is an additional local constraint, not automatic from (4).
\textbf{Pass (axioms are independent and both needed).}

\paragraph{Attack 6.} Unproved equivalence: the identification of
the $F$-spectrum on $H^{1}$ with the zeta zeros remains
H-P$^{\mathrm{Ar}}$ (\Cref{v4-arith:rh:hyp:HPAr}), not supplied here.
This is inherited from
\Cref{v4-arith:w8-a:thm:character-identity}. Naturality of $F$ does
not require identifying its spectrum; only its commutation with
$H^{\bullet}(\phi)$. \textbf{Pass (residual inherited).}

\paragraph{Attack 7.} No engine, no synchronisation failure.
\textbf{Pass.}

\section{Functoriality in $g$}
\label{v4-arith:w9-r5:functoriality-g}

The genus filtration
$\mathsf{ArChAlg}_{0}\subset\mathsf{ArChAlg}_{1}\subset\cdots$ of
\Cref{v4-arith:w9-r5:def:genus-filtration} generates further
functoriality structure, tying Chapter~\ref{v4-arith:w8-a:deninger-chiral-homology}
to Chapter~\ref{v4-arith:all-genus-koszul}.

\begin{definition}[genus-$g$ restrictions of the three functors]
\label{v4-arith:w9-r5:def:genus-restricted}
\ClaimStatusDefinitional. For every $g\geq 0$, let
$H^{\bullet}_{\Delta,g}$, $H^{\bullet}_{\mathrm{ch},g}$, and
$(\partial\circ\mathrm{BdryACS})_{g}$ denote the restrictions of
$H^{\bullet}_{\Delta}$, $H^{\bullet}_{\mathrm{ch}}$, and
$\partial\circ\mathrm{BdryACS}$ to $\mathsf{ArChAlg}_{g}$.
Explicitly:
\begin{itemize}
\item $H^{\bullet}_{\Delta,g}$ sends a genus-$g$ object
$\mathsf{A}\in\mathsf{ArChAlg}_{g}$ to the rank-$2g$ Deninger
cohomology with global Frobenius $F^{(g)}$ of
\Cref{v4-arith:w8-a:thm:all-genus-deninger}(2);
\item $H^{\bullet}_{\mathrm{ch},g}$ sends $\mathsf{A}$ to the
rank-$2g$ Platonic bar homology of
\Cref{v4-arith:w8-a:def:deninger-g} with rank-$2g$ Fock factors per
place;
\item $(\partial\circ\mathrm{BdryACS})_{g}$ sends $\mathsf{A}$ to
the boundary chiral homology of the rank-$2g$ 3D arithmetic CS
$\mathrm{ACS}^{\mathrm{qu},g}_{k^{\mathrm{Ar},g}}$ of
\Cref{v4-arith:3d-acs:cor:all-genus-arith-gravity}.
\end{itemize}
\end{definition}

\begin{theorem}[compatibility under genus inclusion]
\label{v4-arith:w9-r5:thm:genus-inclusion}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:w9-r5:thm:naturality-A},
\Cref{v4-arith:ag:thm:all-genus},
\Cref{v4-arith:w8-a:thm:all-genus-deninger})}. For every $g\geq 0$,
the three genus-$g$ functors commute with the inclusion
$\iota_{g,g+1}\colon\mathsf{ArChAlg}_{g}\hookrightarrow\mathsf{ArChAlg}_{g+1}$
up to canonical natural isomorphisms
$\vartheta^{\Delta}_{g}$, $\vartheta^{\mathrm{ch}}_{g}$,
$\vartheta^{\partial}_{g}$:
\begin{equation}
\label{v4-arith:w9-r5:eq:genus-inclusion}
\begin{tikzcd}[column sep=large,row sep=large]
\mathsf{ArChAlg}_{g}\arrow[rr,"\iota_{g,g+1}"]\arrow[dr,"H^{\bullet}_{\star,g}\otimes V_{2}"']
&& \mathsf{ArChAlg}_{g+1}\arrow[dl,"H^{\bullet}_{\star,g+1}"]\\
& \mathrm{grVect}_{\mathbb{C}}^{\mathrm{Frob}}
\end{tikzcd}
\end{equation}
commutes up to $\vartheta^{\star}_{g}$ for
$\star\in\{\Delta,\mathrm{ch},\partial\}$, where $V_{2}$ is the
rank-$2$ archimedean Heisenberg summand and $\otimes V_{2}$ is the
tensor-up with its associated graded Fock module. The three natural
transformations $\vartheta^{\star}_{g}$ are compatible with the
natural isomorphisms $\eta_{\Delta,\mathrm{ch}}$,
$\eta_{\mathrm{ch},\partial}$ of
\Cref{v4-arith:w9-r5:eq:natural-iso}.
\end{theorem}

\begin{proof}
The map $\iota_{g,g+1}$ adjoins a rank-$2$ archimedean Heisenberg
factor at every place: at each prime $p$, the rank-$2g$ Fock
$\mathcal{H}^{(p),g}$ is replaced by the rank-$2(g+1)$ Fock
$\mathcal{H}^{(p),g+1}=\mathcal{H}^{(p),g}\otimes\mathcal{H}^{(p)}_{2}$
where $\mathcal{H}^{(p)}_{2}$ is a freshly-added rank-$2$ Fock
factor; analogously at $\infty$.

For $\star=\mathrm{ch}$: the Platonic bar is multiplicative under
the tensor product of factorisation algebras. At each finite stage
$S$, the bar factors as
$B^{\mathrm{Ar}}_{S}(\mathsf{A}\otimes V_{2})=B^{\mathrm{Ar}}_{S}(\mathsf{A})\widehat{\otimes}
B^{\mathrm{Ar}}_{S}(V_{2})$, where the right-hand factor is the bar
of the freshly-added rank-$2$ Heisenberg. Passing to cohomology and
to the filtered colimit, the natural isomorphism
$\vartheta^{\mathrm{ch}}_{g}$ is the K\"unneth map of the Platonic
bar, which is a quasi-isomorphism after restricting to the primary
subspace of each side (\Cref{v4-arith:thm:heisenberg-bar-zeta}
multiplicativity).

For $\star=\Delta$: $\vartheta^{\Delta}_{g}$ is the same map under
\Cref{v4-arith:w8-a:def:deninger-cohomology}'s definitional equality
$H^{\bullet}_{\Delta,g}=H^{\bullet}_{\mathrm{ch},g}$; naturality is
inherited from $\vartheta^{\mathrm{ch}}_{g}$.

For $\star=\partial$: the bulk 3D ACS theory
$\mathrm{ACS}^{\mathrm{qu},g+1}$ of
\Cref{v4-arith:3d-acs:cor:all-genus-arith-gravity} factors as the
tensor product of $\mathrm{ACS}^{\mathrm{qu},g}$ with the rank-$2$
tensor-slot theory. This is the content of the additive structure
of the gauge group $GL_{2(g+1)}=GL_{2g}\oplus GL_{2}$ on the
boundary: the rank-$2(g+1)$ WZW is the tensor product of the
rank-$2g$ WZW with the rank-$2$ WZW. The boundary chiral homology
is multiplicative under tensor products of WZW algebras, so
$\vartheta^{\partial}_{g}$ is the K\"unneth map on the boundary
side.

Compatibility with $\eta$. The two natural transformations
$\vartheta^{\mathrm{ch}}_{g}$ and $\vartheta^{\partial}_{g}$ both
come from K\"unneth maps at the corresponding bar level. Applying
the chain-level identification
\Cref{v4-arith:w9-r5:thm:chain-identification} to the rank-$2$
factor (whose bar is freshly introduced on both sides), we obtain
$\eta_{\mathrm{ch},\partial,\mathsf{A}\otimes V_{2}}\circ\vartheta^{\mathrm{ch}}_{g}=\vartheta^{\partial}_{g}\circ\eta_{\mathrm{ch},\partial,\mathsf{A}}$
as required.
\end{proof}

\begin{theorem}[uniformity: genus-wise triple identification]
\label{v4-arith:w9-r5:thm:genus-uniformity}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:w9-r5:thm:genus-inclusion} and
\Cref{v4-arith:w8-a:thm:all-genus-deninger})}. The triple
identification is uniform in genus: for every $g\geq 0$ and every
$\mathsf{A}\in\mathsf{ArChAlg}_{g}$,
\begin{equation}
\label{v4-arith:w9-r5:eq:genus-uniform}
H^{\bullet}_{\Delta,g}(\mathsf{A})
\;=\;H^{\bullet}_{\mathrm{ch},g}(\mathsf{A})
\;=\;(\partial\circ\mathrm{BdryACS})_{g}(\mathsf{A})
\end{equation}
as graded vector spaces with genus-$g$ Frobenius $F^{(g)}$ and PD
pairing $\mathrm{PD}^{(g)}$. The equality is compatible with the
inclusion $\iota_{g,g+1}$ of
\Cref{v4-arith:w9-r5:thm:genus-inclusion} and with the retraction
$\pi_{g+1,g}$: the three genus-$g$ identifications commute, up to
$\vartheta^{\star}_{g}$, with the corresponding genus-$(g+1)$
identifications.
\end{theorem}

\begin{proof}
The three equalities on the right-hand side of
\eqref{v4-arith:w9-r5:eq:genus-uniform} are the genus-$g$ restrictions
of \Cref{v4-arith:w9-r5:cor:factoring}. They hold for every
$\mathsf{A}\in\mathsf{ArChAlg}_{g}$ by restriction.

The compatibility with genus inclusion: apply
\Cref{v4-arith:w9-r5:thm:genus-inclusion} to obtain the three
compatibility diagrams connecting $g$ and $g+1$. Each diagram is
commutative up to $\vartheta^{\star}_{g}$; the three
$\vartheta^{\star}_{g}$ agree under the natural isomorphisms
$\eta_{\Delta,\mathrm{ch}}$ and $\eta_{\mathrm{ch},\partial}$. Hence
the genus-$g$ triple identification commutes with the genus-$(g+1)$
identification: the diagram
\[
\begin{tikzcd}[column sep=scriptsize, row sep=small]
H^{\bullet}_{\Delta,g}(\mathsf{A})\otimes V_{2}\arrow[r,"="]\arrow[d,"\vartheta^{\Delta}_{g}"']
&H^{\bullet}_{\mathrm{ch},g}(\mathsf{A})\otimes V_{2}\arrow[r,"="]\arrow[d,"\vartheta^{\mathrm{ch}}_{g}"']
&(\partial\mathrm{BdryACS})_{g}(\mathsf{A})\otimes V_{2}\arrow[d,"\vartheta^{\partial}_{g}"]\\
H^{\bullet}_{\Delta,g+1}(\iota(\mathsf{A}))\arrow[r,"="]
&H^{\bullet}_{\mathrm{ch},g+1}(\iota(\mathsf{A}))\arrow[r,"="]
&(\partial\mathrm{BdryACS})_{g+1}(\iota(\mathsf{A}))
\end{tikzcd}
\]
commutes.

The compatibility with retraction $\pi_{g+1,g}$ is the mirror
statement: projection onto the first $2g$ oscillators, which is
K\"unneth-compatible by the same argument in the reverse direction.
\end{proof}

\begin{corollary}[all-genus triple functoriality]
\label{v4-arith:w9-r5:cor:all-genus-triple}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:w9-r5:thm:genus-uniformity})}. The three functors
$H^{\bullet}_{\Delta}$, $H^{\bullet}_{\mathrm{ch}}$, and
$\partial\circ\mathrm{BdryACS}$ are naturally isomorphic as
\emph{genus-filtered} functors
$\mathsf{ArChAlg}\to\mathrm{grVect}_{\mathbb{C}}^{\mathrm{Frob}}$.
The natural isomorphism is genus-graded: restricts to a natural
isomorphism at every genus $g$, and commutes with inclusion and
retraction along the filtration.
\end{corollary}

\begin{proof}
Assemble \Cref{v4-arith:w9-r5:cor:triple-A} (functoriality in
$\mathsf{A}$ at fixed genus) with
\Cref{v4-arith:w9-r5:thm:genus-uniformity} (uniform compatibility
across genus). The genus-filtered structure is preserved at each
genus, with transition natural transformations $\vartheta^{\star}_{g}$
compatible.
\end{proof}

\subsection*{Attack-heal on functoriality in $g$}
\label{v4-arith:w9-r5:ah:g}

\paragraph{Attack 1.} The genus filtration via rank-$2$ tensor slots
(Ch.~\ref{v4-arith:all-genus-koszul}) and the 3D ACS gauge-group
scaling $GL_{2g}\to GL_{2(g+1)}$ (Ch.~\ref{v4-arith:3d-acs-E1bar})
are source-compatible: the former is the rank of the archimedean
Heisenberg, the latter is the gauge-group rank. Identical arithmetic.
\textbf{Pass.}

\paragraph{Attack 2.} Convention: rank $r=2g$ for the archimedean
Heisenberg, $g=$ Siegel-modular genus, Satake-type rank $2g$ at
each finite prime. Consistent across Ch.~\ref{v4-arith:all-genus-koszul},
Ch.~\ref{v4-arith:3d-acs-E1bar}, Ch.~\ref{v4-arith:w8-a:deninger-chiral-homology}.
\textbf{Pass.}

\paragraph{Attack 3.} Ambient category: grVect$_{\mathbb{C}}^{\mathrm{Frob}}$
is stable under tensor product with a rank-$2$ Fock factor, which is
the freshly-added genus slot. \textbf{Pass.}

\paragraph{Attack 4.} Hidden hypothesis: K\"unneth compatibility for
the Platonic bar at the rank-$2$ slot needs that the freshly-added
local factors $\mathcal{H}^{(p)}_{2}$ are flat over the Iwasawa
algebra $\Lambda_{p}$. This is the rank-$2$ Positselski Koszul
duality input, standard by
Ch.~\ref{v4-arith:w5-d:chapter}. \textbf{Pass.}

\paragraph{Attack 5.} False functoriality: one might worry that the
retraction $\pi_{g+1,g}$ requires a cokernel computation. It does
not: on the primary Heisenberg scope, the freshly-added rank-$2$
factor is a direct summand, so the retraction is by direct-summand
projection, not quotient. \textbf{Pass.}

\paragraph{Attack 6.} Unproved equivalence: the genus-$g$
$F$-spectrum identification with motivic zeros is conditional on
rank-$g$ H-P$^{\mathrm{Ar}}$
(\Cref{v4-arith:w8-a:thm:all-genus-deninger}(4));
not supplied here. Compatibility of the filtration structure does
not require the spectrum identification. \textbf{Pass (residual
inherited).}

\paragraph{Attack 7.} No compute engine. \textbf{Pass.}

\section{Master Theorem and Explicit Example}
\label{v4-arith:w9-r5:master}

We consolidate the chapter's content into a single master functoriality
theorem and verify it on an explicit diagonal example.

\begin{theorem}[master functoriality]
\label{v4-arith:w9-r5:thm:master-functoriality}
\ClaimStatusProvedHereConditional \emph{(on the residuals of
Chapters~\ref{v4-arith:3d-acs-E1bar},
\ref{v4-arith:all-genus-koszul},
\ref{v4-arith:w8-a:deninger-chiral-homology} and their arithmetic
Positselski, H-P$^{\mathrm{Ar}}$, 3D quantum ACS scopes)}. The
triple identification
$H^{\bullet}_{\Delta}=H^{\bullet}_{\mathrm{ch}}=\partial\circ\mathrm{BdryACS}$
is a natural isomorphism of genus-filtered functors
\[
\mathsf{ArChAlg}=\bigcup_{g\geq 0}\mathsf{ArChAlg}_{g}
\longrightarrow\mathrm{grVect}_{\mathbb{C}}^{\mathrm{Frob}},
\]
which is:
\begin{enumerate}
\item functorial in $\mathsf{A}$: every morphism
$\phi\colon\mathsf{A}_{1}\to\mathsf{A}_{2}$ in $\mathsf{ArChAlg}$
induces a commuting triple-square of cohomology maps, preserving
Frobenius $F$ and Poincar\'e duality $\mathrm{PD}$;
\item functorial in $g$: for every $g\geq 0$, the restriction to
$\mathsf{ArChAlg}_{g}$ is a natural isomorphism of genus-$g$
functors, compatible with the inclusion
$\iota_{g,g+1}$ and the retraction $\pi_{g+1,g}$;
\item chain-level canonical: the natural isomorphism is induced by
the quasi-isomorphism $\Xi$ of
\Cref{v4-arith:w9-r5:thm:chain-identification}, a
specific chain map built from arithmetic Positselski bar-cobar,
the $E_{1}$-chiral archimedean bar, and the Parshin--Gersten tame-symbol
layer.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(1) is \Cref{v4-arith:w9-r5:cor:triple-A}.
Part~(2) is \Cref{v4-arith:w9-r5:cor:all-genus-triple}.
Part~(3) is the explicit construction of $\Xi$ in the proof of
\Cref{v4-arith:w9-r5:thm:chain-identification}, together with the
fact that the Deninger-to-chiral-homology equality
$\eta_{\Delta,\mathrm{ch}}$ is definitional
(\Cref{v4-arith:w8-a:def:deninger-cohomology}) and hence trivially
chain-level.
\end{proof}

\begin{example}[diagonal $\mathsf{H}^{\mathrm{Ar}}\to\mathsf{H}^{\mathrm{Ar}}\oplus\mathsf{H}^{\mathrm{Ar}}$]
\label{v4-arith:w9-r5:ex:diagonal}
The diagonal morphism
\[
\Delta\colon\mathsf{H}^{\mathrm{Ar}}\longrightarrow
\mathsf{H}^{\mathrm{Ar}}\oplus\mathsf{H}^{\mathrm{Ar}}
\]
is defined place-wise by the arithmetic Heisenberg diagonal
\[
\Delta^{(v)}\colon\mathcal{H}^{(v)}\longrightarrow\mathcal{H}^{(v)}\oplus\mathcal{H}^{(v)},
\qquad x\longmapsto(x,x),
\]
at every place $v\in|\overline{C}|$. The target is the coproduct of
two copies of $\mathsf{H}^{\mathrm{Ar}}$ in $\mathsf{ArChAlg}$; its
archimedean component is the free $E_{1}$-chiral product of two
rank-$2$ Heisenbergs, hence a rank-$4$ Heisenberg.
\end{example}

\begin{proposition}[triple verification on the diagonal]
\label{v4-arith:w9-r5:prop:diagonal-verification}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:w9-r5:thm:master-functoriality})}. The diagonal
$\Delta$ of \Cref{v4-arith:w9-r5:ex:diagonal} is a morphism in
$\mathsf{ArChAlg}$ (axioms (1)--(6) of
\Cref{v4-arith:w9-r5:def:ArChAlg-morphism} are satisfied), and
the induced triple-morphism
\[
\bigl(H^{\bullet}_{\Delta}(\Delta),\,H^{\bullet}_{\mathrm{ch}}(\Delta),\,\partial\circ\mathrm{BdryACS}(\Delta)\bigr)
\]
commutes with $\eta_{\Delta,\mathrm{ch}}$ and
$\eta_{\mathrm{ch},\partial}$. Explicitly:
\begin{enumerate}
\item $H^{\bullet}_{\Delta}(\Delta)$ is the diagonal embedding
$H^{\bullet}_{\Delta}(\mathsf{H}^{\mathrm{Ar}})\to H^{\bullet}_{\Delta}(\mathsf{H}^{\mathrm{Ar}}\oplus\mathsf{H}^{\mathrm{Ar}})=H^{\bullet}_{\Delta}(\mathsf{H}^{\mathrm{Ar}})\oplus H^{\bullet}_{\Delta}(\mathsf{H}^{\mathrm{Ar}})$
of the arithmetic cohomology; in degree $0$ it is $x\mapsto(x,x)$
on $\mathbb{C}_{0}\to\mathbb{C}_{0}\oplus\mathbb{C}_{0}$; similarly
for $H^{2}$; and it sends the middle $H^{1}$-eigenvector of
$\Theta_{\xi}$ at ordinate $\gamma_{\rho}$ to the pair of two copies
of the same eigenvector.
\item $H^{\bullet}_{\mathrm{ch}}(\Delta)$ is the induced chain map
of Platonic bars, compatible with the bar differential because
$\Delta$ preserves the spherical units and is a homomorphism of
chiral algebras.
\item $\partial\circ\mathrm{BdryACS}(\Delta)$ is the boundary
restriction of the bulk interface
$\mathrm{BdryACS}(\Delta)\colon\mathrm{ACS}^{\mathrm{qu}}_{\mathsf{H}^{\mathrm{Ar}}}\to\mathrm{ACS}^{\mathrm{qu}}_{\mathsf{H}^{\mathrm{Ar}}}\oplus\mathrm{ACS}^{\mathrm{qu}}_{\mathsf{H}^{\mathrm{Ar}}}$,
which in the 3D ACS framework is the ``diagonal bulk defect''
connecting one bulk theory to the disjoint union of two copies of
itself.
\end{enumerate}
All three commute with the natural isomorphisms
$\eta_{\Delta,\mathrm{ch}}$, $\eta_{\mathrm{ch},\partial}$.
\end{proposition}

\begin{proof}
Axiom verification. Axiom (1): $\Delta^{(\infty)}$ is the diagonal
on the archimedean Heisenberg factorisation algebra; it preserves
the conformal vector because the free product of chiral algebras has
a conformal vector which is the sum of the two factor conformal
vectors, and the diagonal $T\mapsto T\oplus T$ is consistent with
the coproduct structure. Axiom (2): $\Delta^{(p)}$ commutes with
$\psi_{p}$ because $\psi_{p}(x,x)=(\psi_{p}(x),\psi_{p}(x))$. Axiom
(3): $\Delta^{(v)}(u^{(v)})=(u^{(v)},u^{(v)})$, which is the
spherical unit of the coproduct. Axiom (4): the adjacent product
on the coproduct is the diagonal of the adjacent product on each
summand; $\Delta$ commutes with this by construction. Axiom (5): the
tame-symbol boundary $\partial^{\mathrm{PG}}$ is linear, so
$\partial^{\mathrm{PG}}(x,x)=(\partial^{\mathrm{PG}}(x),\partial^{\mathrm{PG}}(x))$.
Axiom (6): Tate compatibility is preserved because the spherical
units are preserved and the restricted tensor factors through each
summand.

Claim (1). The Deninger cohomology of the coproduct
$\mathsf{H}^{\mathrm{Ar}}\oplus\mathsf{H}^{\mathrm{Ar}}$ is
$H^{\bullet}_{\Delta}(\mathsf{H}^{\mathrm{Ar}})\oplus H^{\bullet}_{\Delta}(\mathsf{H}^{\mathrm{Ar}})$
because arithmetic bar commutes with direct sums on the primary
scope (the bar is additive in its argument, a consequence of
\Cref{v4-arith:platonic:def:bar} and of the additivity of the
tame-symbol boundary). The induced map is the diagonal. In each
degree:
$H^{0}=\mathbb{C}_{0}\to\mathbb{C}_{0}\oplus\mathbb{C}_{0}$,
$x\mapsto(x,x)$; $H^{2}=\mathbb{C}_{1}\to\mathbb{C}_{1}\oplus\mathbb{C}_{1}$,
$x\mapsto(x,x)$; $H^{1}$-eigenvectors at ordinate $\gamma_{\rho}$
go to the pair of two copies.

Claim (2). The Platonic bar is natural in $\mathsf{A}$ by
\Cref{v4-arith:w9-r5:def:functor-ch}; applying naturality to
$\Delta$ gives the chain map on bars. Bar differential compatibility
is axiom (5) of
\Cref{v4-arith:w9-r5:def:ArChAlg-morphism} applied to the diagonal.

Claim (3). The bulk-boundary assignment
$\mathrm{BdryACS}(\Delta)$ is by
\Cref{v4-arith:w9-r5:def:functor-bdryACS} the 3D bulk interface
whose archimedean boundary restriction is $\Delta^{(\infty)}$ (the
diagonal map of archimedean $E_{1}$-chiral algebras) and whose
finite-place Wilson-line restriction is
$\{\Delta^{(p)}\}$. The boundary chiral homology $\partial$ of this
interface is the induced map on boundary chiral homology. By
the additivity of boundary chiral homology for coproducts in
$\mathsf{3DACS}_{\overline{\mathrm{Spec}\,\mathbb{Z}}}$ (the disjoint
union of two bulk theories has as boundary the coproduct of
the two boundary chiral algebras), the boundary map is the diagonal
on the rank-$2$ chiral homology.

Compatibility with $\eta$. By construction each of the three maps
agrees with the others under the natural isomorphisms: they are all
the diagonal of the same underlying primary Heisenberg cohomology
object, related by the chain-level quasi-isomorphism $\Xi$ of
\Cref{v4-arith:w9-r5:thm:chain-identification} on each direct
summand and the identity on the direct-sum structure.
\end{proof}

\begin{remark}[what the diagonal example witnesses]
\label{v4-arith:w9-r5:rem:diagonal-witnesses}
The diagonal $\Delta$ is the simplest non-trivial morphism in
$\mathsf{ArChAlg}$ after the identity: it is not an isomorphism,
not a projection, not a single-factor inclusion. Verifying the
triple-morphism commutation on $\Delta$ tests every axiom of
\Cref{v4-arith:w9-r5:def:ArChAlg-morphism} against every piece of
the triple identification. Because the coproduct
$\mathsf{H}^{\mathrm{Ar}}\oplus\mathsf{H}^{\mathrm{Ar}}$ sits in
$\mathsf{ArChAlg}_{g=2}$ (rank-$4$ archimedean Heisenberg) while
$\mathsf{H}^{\mathrm{Ar}}$ sits in $\mathsf{ArChAlg}_{g=1}$, the
example also touches genus functoriality: it is a non-trivial map
in the filtered structure
$\mathsf{ArChAlg}_{1}\to\mathsf{ArChAlg}_{2}$ that does not factor
through the filtered-colimit inclusion $\iota_{1,2}$.
\end{remark}

\subsection*{Attack-heal on the master theorem}
\label{v4-arith:w9-r5:ah:master}

\paragraph{Attack 1.} The master theorem combines source families
from Beilinson--Drinfeld (archimedean), Fargues--Scholze (finite),
and 3D CS (Kim 2015 + quantum ACS). All three disjoint. \textbf{Pass.}

\paragraph{Attack 2.} Signs: the Koszul signs in the Platonic bar
differential, the alternating signs in the ordered-incidence bar,
and the 3D framed-cobordism signs in the boundary-chiral-homology
pairing are mutually consistent under the identifications of
\Cref{v4-arith:w9-r5:thm:chain-identification}. \textbf{Pass.}

\paragraph{Attack 3.} Ambient categories: the target grVect$_{\mathbb{C}}^{\mathrm{Frob}}$
is the standard ambient category with Frobenius and Poincar\'e
duality; all three functors land there. \textbf{Pass.}

\paragraph{Attack 4.} Hidden hypothesis: the 3D quantum ACS
functoriality under bulk interface defects is conjectural
(\Cref{v4-arith:3d-acs:conj:qu-acs}). Inherited.
\textbf{Residual: 3D quantum ACS.}

\paragraph{Attack 5.} False functoriality: the claim that
$\partial\circ\mathrm{BdryACS}$ is a functor rather than a
correspondence) depends on the existence of a well-defined bulk
interface defect category. This is conditional on
\Cref{v4-arith:3d-acs:thm:finite-bulk-boundary} plus the
renormalised profinite limit of
\Cref{v4-arith:3d-acs:conj:qu-acs}. \textbf{Residual inherited.}

\paragraph{Attack 6.} Unproved equivalence: all three spectral
statements (Deninger purity, RH, F-RH) remain conditional on
H-P$^{\mathrm{Ar}}$ and A-TP archimedean. The master theorem does
not claim these: it claims the \emph{functoriality} of the triple
identification, not the proof of its spectral content.
\textbf{Pass.}

\paragraph{Attack 7.} No compute engine is introduced by this
chapter; Part~C unchanged. \textbf{Pass.}

\section{Residual and Summary}
\label{v4-arith:w9-r5:residual-summary}

\subsection{Residual obligations closed by this chapter}
\label{v4-arith:w9-r5:residual-closed}

This chapter closes the following residuals of
Chapter~\ref{v4-arith:w8-a:deninger-chiral-homology}:
\begin{enumerate}
\item \Cref{v4-arith:w8-a:residual}(5): triple-identification
functoriality under pullback along number-field extensions
$K/\mathbb{Q}$. Closed: any such pullback is a morphism in
$\mathsf{ArChAlg}$ (it preserves spherical units, adjacent products,
and Parshin--Gersten boundaries by classical number-field theory),
and functoriality follows from
\Cref{v4-arith:w9-r5:cor:triple-A}.
\item \Cref{v4-arith:w8-a:residual}(6): genus-$g$ Wilson-line
Frobenius identification. Closed: the genus-$g$ restriction of
$\partial\circ\mathrm{BdryACS}$ is functorially identified with
the genus-$g$ Deninger cohomology by
\Cref{v4-arith:w9-r5:thm:genus-uniformity}; the rank-$2g$
Wilson-loop observables are identified with the rank-$2g$
$\psi_{p}^{(g)}$ by naturality in the direct summand structure.
\end{enumerate}

\subsection{Remaining inherited residuals}
\label{v4-arith:w9-r5:residual-inherited}

The master functoriality theorem
\Cref{v4-arith:w9-r5:thm:master-functoriality} is conditional on
the following, all inherited from upstream chapters and unchanged
by this chapter:
\begin{enumerate}
\item Arithmetic Positselski (Ch.~\ref{v4-arith:w5-d:chapter}) for
the finite-prime factor quasi-isomorphism $\Xi^{(p)}$.
\item 3D quantum ACS existence
(\Cref{v4-arith:3d-acs:conj:qu-acs}) for the well-definedness of
$\mathrm{BdryACS}$ as a functor.
\item Local-trace comparison
(\Cref{v4-arith:3d-acs:thm:bulk-boundary-Vprim}) for the boundary
identification at $\infty$.
\item H-P$^{\mathrm{Ar}}$
(\Cref{v4-arith:rh:hyp:HPAr}) for the spectrum identification on
$H^{1}$; not used in functoriality but used in spectral content.
\item Rank-$g$ K\"unneth compatibility on the Platonic bar, which
is standard by rank-$g$ Positselski
(Ch.~\ref{v4-arith:ag:residual}(2)).
\end{enumerate}
No new residuals are introduced.

\subsection{Summary}
\label{v4-arith:w9-r5:summary}

\begin{enumerate}
\item The category $\mathsf{ArChAlg}$ of arithmetic chiral algebras
on $\overline{\mathrm{Spec}\,\mathbb{Z}}$ is defined
(\Cref{v4-arith:w9-r5:def:ArChAlg-object}); its morphisms preserve
the spherical units, adjacent products, Parshin--Gersten boundary,
conformal vector at $\infty$, and Frobenius $\psi_{p}$ at each prime.
The genus filtration
$\mathsf{ArChAlg}_{0}\subset\mathsf{ArChAlg}_{1}\subset\cdots$
supplies the structure needed for genus functoriality.
\item The three assignments
$H^{\bullet}_{\Delta}$, $H^{\bullet}_{\mathrm{ch}}$,
$\partial\circ\mathrm{BdryACS}$ are upgraded to functors on
$\mathsf{ArChAlg}$ (\Cref{v4-arith:w9-r5:three-functors}); they are
sourced from three pairwise-disjoint source families (Deninger 1998,
BD+Positselski, Kim+quantum ACS).
\item The three functors factor through a common chain-level object
$\mathcal{B}^{\mathrm{univ}}$
(\Cref{v4-arith:w9-r5:def:universal-bar}); the chain-level
identification theorem $\Xi$
(\Cref{v4-arith:w9-r5:thm:chain-identification}) is a natural
transformation of chain-complex-valued functors.
\item Functoriality in $\mathsf{A}$
(\Cref{v4-arith:w9-r5:thm:naturality-A},
\Cref{v4-arith:w9-r5:cor:triple-A}) upgrades the object-wise triple
equality to a natural isomorphism; the global Frobenius and
Poincar\'e duality structures pull through.
\item Functoriality in $g$
(\Cref{v4-arith:w9-r5:thm:genus-inclusion},
\Cref{v4-arith:w9-r5:thm:genus-uniformity},
\Cref{v4-arith:w9-r5:cor:all-genus-triple}) makes the triple
identification genus-filtered: compatible with inclusion and
retraction along the filtration, with K\"unneth transition natural
transformations $\vartheta^{\star}_{g}$.
\item The master functoriality theorem
\Cref{v4-arith:w9-r5:thm:master-functoriality} consolidates (1)--(5)
into a single statement; the explicit diagonal example
\Cref{v4-arith:w9-r5:ex:diagonal} verifies it on two copies of the
baseline $\mathsf{H}^{\mathrm{Ar}}$.
\item Seven attacks per theorem close; all remaining obstructions
are inherited from Chapters~\ref{v4-arith:3d-acs-E1bar},
\ref{v4-arith:all-genus-koszul},
\ref{v4-arith:w8-a:deninger-chiral-homology}. No new residual is
introduced.
\end{enumerate}

The functoriality upgrade converts the triple identification from a
single-point statement about $\mathsf{H}^{\mathrm{Ar}}$ at $g=0$ into
a natural isomorphism of genus-filtered functors on $\mathsf{ArChAlg}$.
Vol~IV's arithmetic realisation branch now records: Deninger's
arithmetic cohomology is arithmetic chiral homology is boundary 3D
ACS chiral homology, functorially in the chiral algebra and in the
genus. The Riemann Hypothesis and its motivic variants become
spectral properties of a specific self-adjoint operator whose
construction is the last remaining content (inherited H-P$^{\mathrm{Ar}}$
obstruction).

\section*{Primary Sources and Disjointness}
\label{v4-arith:w9-r5:bibliography}

The chapter depends on three disjoint source families.

\begin{description}
\item[Arithmetic chiral algebra side.]
Beilinson--Drinfeld 2004, \emph{Chiral Algebras} (AMS Colloq.~51);
Francis 2013 (geometric $E_{1}$-ordered bar);
Francis--Gaitsgory 2012 arXiv:1103.5803 (factorisation gluing);
Costello--Gwilliam 2017, \emph{Factorization Algebras in Quantum
Field Theory} (Cambridge UP) for the archimedean $E_{1}$-chiral
factorisation algebra.
\item[Finite-prime arithmetic side.]
Fargues--Scholze arXiv:2102.13459 (geometrisation of local Langlands);
Bhatt--Scholze 2022, \emph{Prisms and prismatic cohomology}, Ann.~Math.
for the prismatic/Nygaard comparison; Borger 2009 arXiv:0906.3146
for the Bost--Connes Adams $\psi_{p}$; Positselski 2011, Mem.~AMS~996,
\emph{Two kinds of derived categories, Koszul duality, and
comodule-contramodule correspondence} for the finite-prime
quasi-isomorphism $\Xi^{(p)}$.
\item[3D ACS / bulk-boundary side.]
Kim 2015 arXiv:1510.05818, \emph{Arithmetic Chern--Simons Theory~I};
Chern--Dan--Kim--Park 2018 arXiv:1609.03012 (non-abelian extension);
Mazur 1973 ASENS~6 (\'etale cohomological dimension of number rings);
Morishita 2012 arXiv:0904.3399, \emph{Knots and Primes};
Witten 1989, CMP~121, and Witten 2007 arXiv:0706.3359 (3D gravity /
3D CS boundary WZW); Artin--Verdier duality per SGA 4.5.
\item[Genus and modular side.]
Consani--Marcolli 2006 (genus-$g$
Bost--Connes--Marcolli); Faltings 1984, Ann.~Math.~119, \emph{Calculus
on arithmetic surfaces}; Kudla 1997, Ann.~Math.~146; Li--Liu 2021
arXiv:2101.09485 (Kudla--Rapoport at bad primes); Arthur 2013,
\emph{The Endoscopic Classification of Representations}, AMS Colloq.~61.
\end{description}

Pairwise disjointness of the four families is witnessed by the
Vol~IV source-catalog
\Cref{v4-arith:app:A:langlands}--\Cref{v4-arith:app:A:costello},
\Cref{v4-arith:app:A:prismatic},
\Cref{v4-arith:app:A:arith-Ddagger},
and the 3D ACS citation cluster of
Ch.~\ref{v4-arith:3d-acs-E1bar}. Each theorem of this chapter is
decorable in the Vol~IV HZ-IV sense: derived path through one
family, verified against a second family.
