\chapter{Wilson-Line Frobenius and Archimedean Wilson-Surface at Genus $g$}
\label{v4-arith:w9-r6:chapter}

\emph{Chapter~\ref{v4-arith:all-genus-koszul} establishes the all-genus
arithmetic Koszul duality identity
$\kappa^{\mathrm{Ar},g}_{\mathsf{G}}+(\kappa^{!})^{\mathrm{Ar},g}_{\mathsf{G}}=0$
on an arithmetic genus-$g$ datum
$\mathcal{D}_{g}=(\mathcal{B}_{g},\mathcal{E}_{g},\varphi_{g})$, with
the genus entering through the rank-$2g$ Fock grading, the archimedean
$\Gamma_{\mathbb{C}}(s)^{g}$ factor, and the motivic weight
$w_{\mathcal{D}_{g}}\in\{1,2,2g+1\}$. Chapter~\ref{v4-arith:3d-acs-E1bar}
builds the 3D arithmetic Chern--Simons theory
$\mathrm{ACS}^{\mathrm{qu}}$ on $\overline{\mathrm{Spec}\,\mathbb{Z}}$,
with Wilson-line Frobenius identity
$\langle W_{\rho}(K_{p})\rangle=\mathrm{tr}\,\rho(\mathrm{Frob}_{p})$ at
$g=0$. Chapter~\ref{v4-arith:w8-a:deninger-chiral-homology} identifies
its boundary chiral homology with Deninger's conjectural arithmetic
cohomology and isolates the global Frobenius
$F_{\infty}\otimes\bigotimes_{p}'\psi_{p}$ realised as Wilson loops and
surfaces. This chapter extends the Wilson-line Frobenius identity and
the archimedean Wilson-surface $F_{\infty}$ to arithmetic genus-$g$
data. The genus-$g$ gauge group is the profinite limit of
$GL_{2g}(\mathbb{Z}/N\mathbb{Z})$; the rank-$2g$ local representation
$\rho_{g}:G_{\mathbb{Q}_{p}}\to\mathrm{GSp}_{2g}$ sources a genus-$g$
Wilson loop whose expectation in
$\mathrm{ACS}^{\mathrm{qu},g}$ is
$\mathrm{tr}_{\rho_{g}}(\mathrm{Frob}_{p})$; the archimedean
Wilson-surface $F^{(g)}_{\infty}$ is the rank-$2g$ Arakelov area-scaling
conjugate to the genus-$g$ Virasoro zero-mode
$L^{(g)}_{0}$ with central charge $g$. The all-genus Deninger
identification is the motivic-weight-$w_{\mathcal{D}_{g}}$
specialisation of the character identity of
\Cref{v4-arith:w8-a:thm:all-genus-deninger}. Specialising to $g=0$
recovers the Riemann framework of
Ch.~\ref{v4-arith:w9-r1:wilson-frobenius} (R1, g=0 Wilson-line
Frobenius baseline) and Ch.~\ref{v4-arith:w9-r2:archimedean-wilson-surface}
(R2, g=0 archimedean Wilson-surface baseline), together with
Chs.~\ref{v4-arith:rh-reformulation} and \ref{v4-arith:tfe-gutzwiller}.
This chapter covers the genus-$g$ row; the uniform $g=0$ reduction is
recorded in \Cref{v4-arith:w9-r6:cor:g-zero}.}

\section{Genus-$g$ Arithmetic Data Recap}
\label{v4-arith:w9-r6:datum}

Fix $g\geq 0$ and an arithmetic genus-$g$ datum
$\mathcal{D}_{g}=(\mathcal{B}_{g},\mathcal{E}_{g},\varphi_{g})$ as in
\Cref{v4-arith:ag:defn:datum}. The load-bearing structural features of
$\mathcal{D}_{g}$ used below are four.

\begin{enumerate}
\item \emph{Rank-$2g$ local Galois representation.} At each prime $p$
of good reduction for $\mathcal{D}_{g}$, there is a continuous rank-$2g$
representation
$\rho_{g,p}:G_{\mathbb{Q}_{p}}:=\mathrm{Gal}(\overline{\mathbb{Q}}_{p}/\mathbb{Q}_{p})\to\mathrm{GSp}_{2g}(\overline{\mathbb{Q}}_{\ell})$
with symplectic Weil pairing; in Window~I, $\rho_{g,p}=T_{\ell}\mathrm{Jac}(X_{K})_{\mathbb{Q}_{p}}$
(Tate module of the Jacobian); in Window~III, the prismatic
$F$-crystal; in Window~VI, the spin representation of the
automorphic $\pi$.
\item \emph{Satake parameters $\{\alpha_{j}^{(p)}\}_{j=1}^{2g}$.}
At an unramified prime, $\rho_{g,p}(\mathrm{Frob}_{p})$ has
$2g$ eigenvalues $\alpha_{1}^{(p)},\dots,\alpha_{2g}^{(p)}$ with
symplectic pairing $\alpha_{j}^{(p)}\alpha_{2g+1-j}^{(p)}=p^{w_{\mathcal{D}_{g}}-1}$;
these source the local Euler factor
$L_{p}(\mathcal{D}_{g},s)=\prod_{j=1}^{2g}(1-\alpha_{j}^{(p)}p^{-s})^{-1}$.
\item \emph{Rank-$2g$ Fock oscillators per place.} The local factor
$\mathcal{H}^{(p),g}$ of
$\mathcal{V}^{\mathrm{prim},g}_{\mathrm{Heis}}=\bigotimes_{p}'\mathcal{H}^{(p),g}\otimes\mathcal{H}^{(\infty),g}$
is the rank-$2g$ Fock whose character is the local Euler factor above.
The archimedean factor $\mathcal{H}^{(\infty),g}$ carries the
rank-$2g$ archimedean Heisenberg with $\Gamma$-factor
$\Gamma_{\mathbb{C}}(s)^{g}$ at weight $1$ (Windows~I, V) or the
corresponding $\Gamma$-factor of
\Cref{v4-arith:ag:table:rows} at Dedekind or Siegel-spin weight.
\item \emph{Motivic functional-equation centre
$w_{\mathcal{D}_{g}}\in\{1,2,2g+1\}$.} The completed $L$-function
$\Lambda_{\mathcal{D}_{g}}(s)$ satisfies
$\Lambda_{\mathcal{D}_{g}}(s)=\epsilon_{\mathcal{D}_{g}}\Lambda_{\mathcal{D}_{g}}(w_{\mathcal{D}_{g}}-s)$
by \Cref{v4-arith:ag:thm:all-genus}; purity lies on
$\mathrm{Re}(s)=w_{\mathcal{D}_{g}}/2$.
\end{enumerate}

\begin{remark}[degeneration at $g=0$]
\label{v4-arith:w9-r6:rem:g-zero}
At $g=0$ the representation $\rho_{0,p}$ is the trivial
$0$-dim representation; $\mathcal{E}_{0}$ is void; $\varphi_{0}=\mathrm{id}$;
the Heisenberg degenerates to the rank-$0$ Fock whose local factor is
the trivial Euler line, and the global character $\xi_{\mathbb{R}}(s)$
retains only the Bost--Connes primon-gas contribution
$\zeta(s)$ multiplied by $\pi^{-s/2}\Gamma(s/2)$ and the Tate-pole
factor $\tfrac{1}{2}s(s-1)$. The Wilson-line identity and the
archimedean Wilson-surface degenerate to
\Cref{v4-arith:3d-acs:conj:qu-acs}(3) and
\Cref{v4-arith:w8-a:rem:wilson-infinity} respectively. Specialisation
is recorded in Section~\ref{v4-arith:w9-r6:g-zero-recovery}.
\end{remark}

\section{Genus-$g$ 3D Arithmetic Chern--Simons Theory}
\label{v4-arith:w9-r6:3d-acs-g}

Chapter~\ref{v4-arith:3d-acs-E1bar} builds the 3D arithmetic
Chern--Simons theory on $\overline{\mathrm{Spec}\,\mathbb{Z}}$ with
gauge group $GL_{2}(\widehat{\mathbb{Z}})$ in the profinite limit,
level $k^{\mathrm{Ar}}=\kappa^{\mathrm{Ar}}_{\mathsf{G}}$, boundary WZW
$\mathcal{V}^{\mathrm{prim}}$, and Wilson-loop axiom
\Cref{v4-arith:3d-acs:conj:qu-acs}(3). The genus-$g$ scaling is the
following rank change.

\begin{definition}[genus-$g$ arithmetic Chern--Simons]
\label{v4-arith:w9-r6:def:acs-g}
\ClaimStatusDefinitional. The \emph{genus-$g$ arithmetic Chern--Simons
theory} is a family of 3D topological gauge theories on an arithmetic
$3$-space $\mathcal{B}_{g}^{(3)}$ parameterised by
$\mathcal{D}_{g}$, with
\begin{enumerate}
\item \emph{Arithmetic $3$-space.} For Window~II at totally imaginary
$K$ of degree $2g$:
$\mathcal{B}_{g}^{(3)}=\overline{\mathrm{Spec}\,\mathcal{O}_{K}}$ with
Artin--Verdier fundamental class
$[\mathcal{B}_{g}^{(3)}]\in H^{3}_{\mathrm{\acute{e}t}}(\mathcal{B}_{g}^{(3)},\widehat{\mathbb{Z}})$
(Mazur 1973). For Window~I at $X\to\mathrm{Spec}\,\mathcal{O}_{K}$:
$\mathcal{B}_{g}^{(3)}=\overline{\mathrm{Spec}\,\mathcal{O}_{K}}$ with
extra fibre cohomology in $H^{2}$ of the generic fibre collected into
the archimedean boundary via the Arakelov K\"ahler form
$\mu_{\mathrm{Ar},g}$ of Faltings 1984. For Window~VI, Shimura varieties
of $\mathrm{GSp}_{2g}$ have their own Artin--Verdier-type fundamental
class assembled via \'etale cohomology of the special fibre plus
Deligne 1974 Weil cohomology.
\item \emph{Gauge group.}
$G_{g,N}:=GL_{2g}(\mathbb{Z}/N\mathbb{Z})$, with profinite limit
$G_{g,\infty}:=GL_{2g}(\widehat{\mathbb{Z}})$.
\item \emph{Level.}
$k^{\mathrm{Ar},g}:=\kappa^{\mathrm{Ar},g}_{\mathsf{G}}(\mathcal{D}_{g})$,
the rank-$2g$ arithmetic Koszul level of
\Cref{v4-arith:ag:thm:all-genus}.
\item \emph{Boundary WZW at the archimedean fibre.}
$\partial\,\mathrm{ACS}^{\mathrm{qu},g}_{k^{\mathrm{Ar},g}}=\mathcal{V}^{\mathrm{prim},g}$
in the sense of
\Cref{v4-arith:3d-acs:thm:bulk-boundary-Vprim} scaled to rank $2g$ per
\Cref{v4-arith:3d-acs:genus-g}.
\end{enumerate}
The finite-level state sums
$Z^{\mathrm{Ar}}_{G_{g,N},\alpha_{g,N}}$ extend
\Cref{v4-arith:3d-acs:thm:finite-level-ACS} unchanged at each finite
rank; the profinite renormalisation
$\mathrm{ACS}^{\mathrm{qu},g}_{k^{\mathrm{Ar},g}}$ remains conditional
in the sense of \Cref{v4-arith:3d-acs:conj:qu-acs} extended to rank
$2g$.
\end{definition}

\begin{remark}[rank scaling and residual profinite limit]
\label{v4-arith:w9-r6:rem:rank-scaling}
The rank-change $2\to 2g$ does not alter the closed finite-level
state-sum of \Cref{v4-arith:3d-acs:thm:finite-level-ACS}: the field
groupoid
$\mathcal{F}_{G_{g,N}}(\mathcal{B}_{g}^{(3)})$
is a finite groupoid for each $N$, the action
$S_{\alpha_{g,N}}^{\mathrm{Ar}}$ is the same Artin--Verdier pairing,
and the gluing formula follows from \'etale descent of
rank-$2g$ local systems. The profinite limit
$\mathrm{ACS}^{\mathrm{qu},g}$ shares the profinite-renormalisation
residual of \Cref{v4-arith:3d-acs:conj:qu-acs}.
\end{remark}

\begin{proposition}[partition function at genus $g$]
\label{v4-arith:w9-r6:prop:partition-g}
\ClaimStatusConditional \emph{(on the genus-$g$ extension of
\Cref{v4-arith:3d-acs:conj:qu-acs}(2) and the genus-$g$ BD/CG
comparison of \Cref{v4-arith:3d-acs:cor:BDCG-ordered-comparison})}.
The partition function of
$\mathrm{ACS}^{\mathrm{qu},g}_{k^{\mathrm{Ar},g}}$ on
$\mathcal{B}_{g}^{(3)}$ equals the completed $L$-function
\begin{equation}
\label{v4-arith:w9-r6:eq:partition-g}
Z_{\mathrm{ACS}^{\mathrm{qu},g}}\bigl(\mathcal{B}_{g}^{(3)};k^{\mathrm{Ar},g}\bigr)
\;=\;\Lambda_{\mathcal{D}_{g}}\bigl(k^{\mathrm{Ar},g}\bigr),
\end{equation}
with $\Lambda_{\mathcal{D}_{g}}$ the row-specific completed $L$-function
of \Cref{v4-arith:ag:table:rows} (Dedekind $\xi_{K}$, Hasse--Weil
$\Lambda(s,X_{K})$, or Siegel spin $\Lambda(s,\pi,\mathrm{spin})$).
\end{proposition}

\begin{proof}
The rank-$2g$ ordered incidence bar $B^{\mathrm{ord},g}_{\bullet}$ on
$\mathbb{P}\cup\{\infty\}$ with per-place factor $\mathcal{H}^{(p),g}$
is the rank-$2g$ generalisation of the bar of
\Cref{v4-arith:3d-acs:defn:E1-bar}. The local character at $p$ is
$\chi_{p}^{(g)}(s)=\prod_{j=1}^{2g}(1-\alpha_{j}^{(p)}p^{-s})^{-1}$,
the local Euler factor of $\Lambda_{\mathcal{D}_{g}}$ (item (2) of
\Cref{v4-arith:w9-r6:datum}); the archimedean character is the rank-$g$
$\Gamma$-factor. The genus-$g$ extension of
\Cref{v4-arith:tfe:lem:ord-bar} gives
$H_{\bullet}(B^{\mathrm{ord},g})=\Lambda_{\mathcal{D}_{g}}(s)$. Under
the conditional genus-$g$ BD/CG comparison and the renormalised
profinite limit, the bulk partition function coincides with this
homology evaluated at $s=k^{\mathrm{Ar},g}$.
\end{proof}

\section{Wilson-Line Frobenius Identity at Genus $g$}
\label{v4-arith:w9-r6:wilson-line-g}

The genus-$g$ analog of
\Cref{v4-arith:3d-acs:conj:qu-acs}(3) and
\Cref{v4-arith:w8-a:lem:wilson-finite} is the following identity.

\begin{definition}[genus-$g$ Wilson line]
\label{v4-arith:w9-r6:def:wilson-line-g}
\ClaimStatusDefinitional. Fix a prime $p$ of good reduction for
$\mathcal{D}_{g}$; let $K_{p}\subset\mathcal{B}_{g}^{(3)}$ denote the
prime-knot associated to $p$ under the Morishita dictionary. For a
continuous representation
$\rho_{g}:G_{\mathbb{Q}_{p}}\to\mathrm{GSp}_{2g}(\overline{\mathbb{Q}}_{\ell})$
of rank $2g$, the \emph{genus-$g$ Wilson line} along $K_{p}$ is the
defect operator
\begin{equation}
\label{v4-arith:w9-r6:eq:wilson-line-def}
W^{(g)}_{\rho_{g}}(K_{p})\;:=\;\mathrm{tr}_{\rho_{g}}\bigl(\mathrm{Hol}_{K_{p}}(\mathsf{A})\bigr),
\end{equation}
with $\mathsf{A}\in\mathcal{F}_{G_{g,\infty}}(\mathcal{B}_{g}^{(3)})$
the bulk rank-$2g$ gauge field in the profinite limit and
$\mathrm{Hol}_{K_{p}}$ the path-ordered holonomy around the meridian
$K_{p}$, assembled from the rank-$2g$ Bost--Connes Adams operations
$\psi^{(g)}_{p}$ per finite prime.
\end{definition}

\begin{theorem}[genus-$g$ Wilson-line Frobenius identity]
\label{v4-arith:w9-r6:thm:wilson-frobenius-g}
\ClaimStatusProvedHereConditional \emph{(on the rank-$2g$ extension of
\Cref{v4-arith:3d-acs:conj:qu-acs}(3) and on rank-$2g$ local Langlands
at unramified $p$ of good reduction for $\mathcal{D}_{g}$, per the
genus-$g$ Fargues--Scholze arXiv:2102.13459 input
\Cref{v4-arith:ag:residual}(5))}. For every unramified prime $p$ of
good reduction for $\mathcal{D}_{g}$,
\begin{equation}
\label{v4-arith:w9-r6:eq:wilson-frobenius-g}
\langle W^{(g)}_{\rho_{g}}(K_{p})\rangle_{\mathrm{ACS}^{\mathrm{qu},g}}
\;=\;\mathrm{tr}_{\rho_{g}}\bigl(\mathrm{Frob}_{p}\bigr)
\;=\;\sum_{j=1}^{2g}\alpha_{j}^{(p)}.
\end{equation}
Equivalently, the Wilson-line defect expectation reproduces the linear
Euler character of $\rho_{g}$ at $p$.
\end{theorem}

\begin{proof}
Three steps.

\emph{Step 1: Morishita-dictionary reduction.} The prime-knot
$K_{p}\subset\mathcal{B}_{g}^{(3)}$ corresponds, under the
Mazur--Morishita dictionary (Mazur 1973 ENS~6; Morishita 2012
arXiv:0904.3399), to the inertia-generated meridian around the closed
point $\mathfrak{p}$ above $p$. Restriction of the rank-$2g$ gauge
field $\mathsf{A}$ to a tubular neighbourhood of $K_{p}$ is determined
by the local Galois representation $\rho_{g,p}$ via the rank-$2g$
generalisation of \Cref{v4-arith:3d-acs:cor:finite-wilson}: at finite
level $G_{g,N}$, the defect expectation equals
$\chi_{\rho_{g}\,\mathrm{mod}\,N}(\mathrm{Frob}_{p})$ for the induced
mod-$N$ representation.

\emph{Step 2: Profinite assembly.} The compatible tower
$\{\chi_{\rho_{g}\,\mathrm{mod}\,N}(\mathrm{Frob}_{p})\}_{N}$ assembles
under the renormalised profinite limit of
\Cref{v4-arith:3d-acs:conj:qu-acs} to the continuous Frobenius trace
$\mathrm{tr}_{\rho_{g}}(\mathrm{Frob}_{p})$. This requires the
rank-$2g$ refinement of the Wilson-line axiom of
\Cref{v4-arith:3d-acs:conj:qu-acs}(3), which is the residual
hypothesis; it is the same assumption that supplies
\Cref{v4-arith:w8-a:lem:wilson-finite} at $g=0$.

\emph{Step 3: Bost--Connes Adams identification.} Borger 2009
arXiv:0906.3146 \S8 identifies each $\psi_{p}$ with the classical
Frobenius on the $\lambda$-ring envelope of the Tate motive; the
rank-$2g$ generalisation replaces the scalar action on
$\mathcal{H}_{p}^{\mathrm{BC}}$ by the $2g$-fold generating-series
action with Satake parameters
$\{\alpha_{j}^{(p)}\}_{j=1}^{2g}$. Under the unramified hypothesis,
$\mathrm{tr}\,\rho_{g}(\mathrm{Frob}_{p})=\sum_{j=1}^{2g}\alpha_{j}^{(p)}$
by definition of the Satake parameters. Combining with Step~1--2 gives
\eqref{v4-arith:w9-r6:eq:wilson-frobenius-g}.
\end{proof}

\subsection*{Attack-heal on the Wilson-line Frobenius identity}
\label{v4-arith:w9-r6:ah:wilson-line-g}

\paragraph{Attack 1 (source collision).} The rank-$2g$ Bost--Connes
Adams action of Borger 2009 \S8 and the rank-$2g$ local Langlands of
Fargues--Scholze 2021 arXiv:2102.13459 derive from disjoint sources
(absolute $\lambda$-ring theory; $p$-adic geometric Langlands). The
Morishita knot-prime dictionary derives from Mazur 1973 plus Morishita
2012, also disjoint. \textbf{Pass.}

\paragraph{Attack 2 (sign/convention).} Satake parameter
normalisation: unramified $\rho_{g,p}$ has eigenvalues
$\alpha_{j}^{(p)}$ with symplectic pairing
$\alpha_{j}^{(p)}\alpha_{2g+1-j}^{(p)}=p^{w_{\mathcal{D}_{g}}-1}$; the
Frobenius trace is $\sum_{j=1}^{2g}\alpha_{j}^{(p)}$ rather than the
character-value $\chi_{\rho_{g}}(\mathrm{Frob}_{p})$ on a
higher-exterior-power representation. Fixed: we use $\rho_{g}$ itself,
not $\bigwedge^{k}\rho_{g}$. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} The Wilson-line defect lives
in the category of bulk local operators of
$\mathrm{ACS}^{\mathrm{qu},g}$; at finite level,
\Cref{v4-arith:3d-acs:thm:finite-bulk-boundary} locates it in
$\mathrm{Sh}_{\tau_{\Sigma}(\alpha_{g,N})}(\mathcal{F}_{G_{g,N}}(\Sigma))$
for $\Sigma=\partial(\text{tubular neighbourhood of }K_{p})$. The
rank-$2g$ generalisation is structurally identical. \textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} The identification of the
profinite-renormalised Wilson-line expectation with
$\mathrm{tr}_{\rho_{g}}(\mathrm{Frob}_{p})$ requires:
(a) profinite renormalisation of
$\{Z^{\mathrm{Ar}}_{G_{g,N},\alpha_{g,N}}\}_{N}$; (b) compatible
tower $\{\alpha_{g,N}\}_{N}$; (c) rank-$2g$ local Langlands at
$p$ (Fargues--Scholze for general linear; Genestier--Lafforgue /
Zhu for $\mathrm{GSp}_{2g}$). (a)--(b) are residuals from
\Cref{v4-arith:3d-acs:residual}(2); (c) is
\Cref{v4-arith:ag:residual}(5). \textbf{Residual: (a)--(c) inherited.}

\paragraph{Attack 5 (false functoriality).} The Wilson line is
functorial under tensor operations on representations:
$W^{(g)}_{\rho_{1}\otimes\rho_{2}}=W^{(g)}_{\rho_{1}}\cdot W^{(g)}_{\rho_{2}}$
at the classical defect level. At the quantum level this requires the
factorisation algebra structure of $\mathcal{V}^{\mathrm{prim},g}$
(rank-$2g$ Heisenberg); matches Ch.~\ref{v4-arith:all-genus-koszul}
Window~V. \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} Identification of the
bulk holonomy $\mathrm{Hol}_{K_{p}}(\mathsf{A})$ with the local Galois
class
$\rho_{g,p}:G_{\mathbb{Q}_{p}}\to\mathrm{GSp}_{2g}$ passes through the
Artin--Verdier fundamental-class pairing of
\Cref{v4-arith:3d-acs:def:finite-field-groupoid}, which is unchanged
at genus $g$. Unramified good reduction of $\mathcal{D}_{g}$ at $p$
excludes wild ramification and singular-fibre pathologies.
\textbf{Pass on good reduction; residual at ramified primes.}

\paragraph{Attack 7 (compute-engine sync).} No compute engine currently
backs this chapter; the $g=0$ counterpart
\Cref{v4-arith:w8-a:lem:wilson-finite} is engine-free; Part~C of
Vol~IV is not affected. \textbf{Pass.}

\section{Archimedean Wilson-Surface at Genus $g$}
\label{v4-arith:w9-r6:wilson-surface-g}

The archimedean fibre at $\infty$ of $\mathcal{B}_{g}^{(3)}$ is not a
knot but a closed surface (or a bundle of closed surfaces, in
Window~I). The archimedean Wilson-surface $F^{(g)}_{\infty}$ is the
genus-$g$ analog of \Cref{v4-arith:w8-a:def:F-infinity}.

\begin{definition}[genus-$g$ archimedean Arakelov K\"ahler form]
\label{v4-arith:w9-r6:def:arakelov-kahler-g}
\ClaimStatusDefinitional. The \emph{genus-$g$ Arakelov K\"ahler form}
on the archimedean fibre $\mathcal{B}_{g}^{(3)}\mid_{\infty}$ is
\begin{equation}
\label{v4-arith:w9-r6:eq:arakelov-kahler-g}
\mu_{\mathrm{Ar},g}\;:=\;\frac{i}{2g}\sum_{j=1}^{g}\omega_{j}\wedge\overline{\omega_{j}},
\end{equation}
with $\{\omega_{j}\}_{j=1}^{g}$ a basis of holomorphic differentials on
the archimedean fibre
$X_{\infty}(\mathbb{C})\hookrightarrow\mathcal{B}_{g}^{(3)}\mid_{\infty}$
(for Window~I) or $g$ copies of the archimedean Haar form on the
Minkowski torus $T_{K}$ (for Window~II) or the natural Riemannian
volume form scaled per Siegel-modular signature (for Window~VI). This
is the Faltings 1984 arithmetic K\"ahler form (Faltings 1984
\emph{Ann.~Math.}~119) on the generic fibre; at $g=0$ the sum is
empty and
$\mu_{\mathrm{Ar},0}=0$.
\end{definition}

\begin{definition}[archimedean Wilson-surface at genus $g$]
\label{v4-arith:w9-r6:def:wilson-surface-g}
\ClaimStatusDefinitional. The \emph{genus-$g$ archimedean
Wilson-surface} is the bulk area-scaling defect
\begin{equation}
\label{v4-arith:w9-r6:eq:wilson-surface-g-def}
F^{(g)}_{\infty}\;:=\;\exp\Bigl(-k^{\mathrm{Ar},g}\int_{\Sigma_{\infty}}\mu_{\mathrm{Ar},g}\Bigr),
\end{equation}
where $\Sigma_{\infty}\subset\mathcal{B}_{g}^{(3)}$ is the archimedean
fibre $\mathcal{B}_{g}^{(3)}\mid_{\infty}$ viewed as a closed
$2$-surface with the Faltings K\"ahler form of
\Cref{v4-arith:w9-r6:def:arakelov-kahler-g}. In operator-theoretic
form on
$\mathcal{H}^{(\infty),g}$,
\begin{equation}
\label{v4-arith:w9-r6:eq:wilson-surface-g-op}
F^{(g)}_{\infty}\;=\;\exp\bigl(-k^{\mathrm{Ar},g}\sum_{j=1}^{g}L_{0,j}^{\mathrm{Ar}}\bigr),
\end{equation}
for $L_{0,j}^{\mathrm{Ar}}$ the Fock zero-mode on the $j$-th archimedean
Heisenberg factor $\mathcal{H}^{(\infty),g}_{j}$.
\end{definition}

\begin{theorem}[conjugacy to genus-$g$ Virasoro]
\label{v4-arith:w9-r6:thm:virasoro-conjugacy-g}
\ClaimStatusProvedHereConditional \emph{(on the rank-$g$ extension of
the primary-Virasoro reconciliation
\Cref{v4-arith:rh:conj:primary-Virasoro} per
\Cref{v4-arith:ag:residual}(7), and on the rank-$g$ Arakelov--Mellin
unitarity of \Cref{v4-arith:w9-r6:lem:mellin-unitary-g} below)}. The
genus-$g$ archimedean Wilson-surface $F^{(g)}_{\infty}$ is conjugate
to the genus-$g$ arithmetic Virasoro zero-mode
$L^{(g)}_{0}$ with central charge $c^{\mathrm{Ar},g}=g$:
\begin{equation}
\label{v4-arith:w9-r6:eq:virasoro-conjugacy-g}
F^{(g)}_{\infty}\;=\;U^{(g)}\,\exp\bigl(-L^{(g)}_{0}\bigr)\,(U^{(g)})^{-1},
\end{equation}
with $U^{(g)}$ the rank-$g$ Mellin-transform unitary of
\Cref{v4-arith:w9-r6:lem:mellin-unitary-g}. Equivalently, the Sugawara
construction on the rank-$2g$ archimedean Heisenberg produces
$L^{(g)}_{0}$ as the arithmetic Virasoro zero-mode sourced by the
rank-$2g$ archimedean Fock; the Arakelov area-scaling
$F^{(g)}_{\infty}$ is its Mellin conjugate.
\end{theorem}

\begin{lemma}[rank-$g$ Arakelov--Mellin unitarity]
\label{v4-arith:w9-r6:lem:mellin-unitary-g}
\ClaimStatusProvedHereConditional \emph{(on the rank-$g$ Weil--Petersson
isometry lift of Ch.~\ref{v4-arith:w5-a:chapter} restricted to the
archimedean fibre; genus-$g$ Petersson inner-product of
\Cref{v4-arith:ag:residual}(2))}. There exists a unitary
$U^{(g)}:L^{2}(\mathbb{R}_{+}^{g},\prod_{j=1}^{g}d^{\times}x_{j})\to L^{2}(\mathrm{Re}\,s_{j}=w_{\mathcal{D}_{g}}/2,\,j=1,\dots,g)$
defined by the $g$-fold tensor of Mellin transforms
\begin{equation}
\label{v4-arith:w9-r6:eq:mellin-g}
U^{(g)}f(s_{1},\dots,s_{g})\;=\;\prod_{j=1}^{g}\int_{0}^{\infty}f_{j}(x_{j})x_{j}^{s_{j}}d^{\times}x_{j},
\end{equation}
conjugating the rank-$g$ Arakelov area-scaling flow
$\partial_{t_{j}}=\partial/\partial\log\|\cdot\|_{\infty,j}$ to
multiplication by $s_{j}-w_{\mathcal{D}_{g}}/2$ on the critical
poly-line.
\end{lemma}

\begin{proof}
The Faltings K\"ahler form
\eqref{v4-arith:w9-r6:eq:arakelov-kahler-g} decomposes as a sum of
$g$ orthogonal rank-$1$ pieces under the Hodge decomposition
$\mathcal{E}_{g}\otimes\mathbb{C}=\mathcal{E}_{g}^{1,0}\oplus\mathcal{E}_{g}^{0,1}$;
each piece carries a rank-$1$ Arakelov scaling flow
$t_{j}\mapsto e^{-t_{j}}\|\cdot\|_{\infty,j}$ with Mellin variable
$s_{j}$. The rank-$1$ unitary is
$\mathrm{Mellin}:L^{2}(\mathbb{R}_{+},d^{\times}x)\to L^{2}(\mathrm{Re}\,s=w_{\mathcal{D}_{g}}/2)$,
classical (Tate 1950; Titchmarsh 1986 Chapter~14); the $g$-fold tensor
is unitary by Fubini on the product measure. The scaling flow is
diagonalised by Mellin at the centre
$\mathrm{Re}\,s_{j}=w_{\mathcal{D}_{g}}/2$ to match
\Cref{v4-arith:w9-r6:datum}(4).
\end{proof}

\begin{proof}[Proof of \Cref{v4-arith:w9-r6:thm:virasoro-conjugacy-g}]
Under $U^{(g)}$, the archimedean Wilson-surface
\eqref{v4-arith:w9-r6:eq:wilson-surface-g-op} becomes
$\exp(-k^{\mathrm{Ar},g}\sum_{j=1}^{g}(s_{j}-w_{\mathcal{D}_{g}}/2))$ on
the product Mellin space; this coincides with
$\exp(-L^{(g)}_{0})$ where
$L^{(g)}_{0}=\sum_{j=1}^{g}L_{0,j}^{\mathrm{Ar}}$ is the rank-$g$
arithmetic Virasoro zero-mode on the product archimedean Heisenberg
Fock. The Sugawara construction of
\Cref{v4-arith:3d-acs:thm:km-lift} scales rank-linearly per
Ch.~\ref{v4-arith:all-genus-koszul} (central charge $c^{\mathrm{Ar},g}=g$);
the rank-$g$ primary sector admits a Virasoro zero-mode which is the
natural lift of $L_{0,j}^{\mathrm{Ar}}$ on each archimedean Heisenberg
factor. Summing over factors gives the rank-$g$ zero-mode
$L^{(g)}_{0}$; this is the \Cref{v4-arith:rh:conj:primary-Virasoro}
reconciliation at rank $g$.
\end{proof}

\begin{remark}[Wilson-surface realisation as bulk $\partial_{k}$-derivative]
\label{v4-arith:w9-r6:rem:wilson-surface-realisation}
In the 3D ACS framework, the archimedean Wilson-surface is the bulk
partition-function derivative along the arithmetic-level deformation
restricted to the archimedean fibre:
$F^{(g)}_{\infty}=\partial Z_{\mathrm{ACS}^{\mathrm{qu},g}}/\partial k^{\mathrm{Ar},g}\mid_{\mathrm{archimedean}}$,
by the area-generation scheme of
\Cref{v4-arith:w8-a:rem:wilson-infinity} scaled to rank $2g$. This is
the arithmetic analog of the Witten-Verlinde area operator on complex
Riemann surfaces.
\end{remark}

\subsection*{Attack-heal on the archimedean Wilson-surface}
\label{v4-arith:w9-r6:ah:wilson-surface-g}

\paragraph{Attack 1 (source collision).} Faltings 1984 arithmetic
K\"ahler form (Arakelov geometry) and
\Cref{v4-arith:rh:conj:primary-Virasoro} (primary Virasoro sector) are
source-disjoint. The Mellin-transform unitary derives from Tate 1950;
also disjoint. \textbf{Pass.}

\paragraph{Attack 2 (sign/convention).} The sign in
$F^{(g)}_{\infty}=\exp(-k^{\mathrm{Ar},g}\int\mu_{\mathrm{Ar},g})$
matches the Mellin convention
$\partial_{t}\leftrightarrow-s+w_{\mathcal{D}_{g}}/2$ on the critical
line; the Faltings normalisation
\eqref{v4-arith:w9-r6:eq:arakelov-kahler-g} with prefactor
$(2g)^{-1}$ is adjusted so that the total area integrates to
$g\cdot(\text{area per factor})$. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} The Wilson-surface lives in
the category of bulk codimension-$1$ defects of
$\mathrm{ACS}^{\mathrm{qu},g}$; at finite level this is
$\mathrm{Sh}_{\tau(\alpha_{g,N})}(\mathcal{F}_{G_{g,N}}(\Sigma_{\infty}))$
restricted to the archimedean surface. Standard. \textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} Conjugacy to
$L^{(g)}_{0}$ requires rank-$g$ primary-Virasoro reconciliation
(\Cref{v4-arith:ag:residual}(7)) and rank-$g$ Weil--Petersson
isometry lift (\Cref{v4-arith:ag:residual}(2)). Both listed residuals.
\textbf{Residual: (7), (2).}

\paragraph{Attack 5 (false functoriality).} The Wilson-surface is
not the tensor product of $g$ rank-$1$ Wilson-surfaces unless the
Faltings K\"ahler form splits as a direct sum. For Windows~I, II it
does split by Hodge decomposition; for Window~VI (Shimura) it
requires the Siegel--Maass metric, distinct from the product metric.
\textbf{Pass on Windows~I, II; Window~VI requires further Siegel
data.}

\paragraph{Attack 6 (unproved equivalence).} Conjugacy
$F^{(g)}_{\infty}=U^{(g)}\exp(-L^{(g)}_{0})(U^{(g)})^{-1}$ presumes
Mellin unitarity at rank $g$; this is
\Cref{v4-arith:w9-r6:lem:mellin-unitary-g} conditioned on the
rank-$g$ Weil--Petersson lift. \textbf{Residual: rank-$g$ Mellin
unitarity.}

\paragraph{Attack 7 (compute-engine sync).} No compute engine
currently backs the archimedean Wilson-surface; the $g=0$ counterpart
in Ch.~\ref{v4-arith:w8-a:deninger-chiral-homology} is similarly
engine-free. Part~C of Vol~IV unaffected. \textbf{Pass.}

\section{Global Frobenius at Genus $g$ and the Deninger Identification}
\label{v4-arith:w9-r6:deninger-g}

\begin{definition}[global genus-$g$ Frobenius]
\label{v4-arith:w9-r6:def:global-F-g}
\ClaimStatusDefinitional. The \emph{global genus-$g$ Frobenius} on
$H^{\bullet}_{\Delta,g}(\mathcal{B}_{g})$ is the restricted-tensor
product
\begin{equation}
\label{v4-arith:w9-r6:eq:global-F-g}
F^{(g)}\;:=\;F^{(g)}_{\infty}\otimes\bigotimes_{p}{}^{\prime}\,\psi^{(g)}_{p},
\end{equation}
acting on
$\mathcal{V}^{\mathrm{prim},g}_{\mathrm{Heis}}=\mathcal{H}^{(\infty),g}\otimes\bigotimes_{p}'\mathcal{H}^{(p),g}$
and descending to the genus-$g$ Vol~IV Deninger cohomology
$H^{\bullet}_{\Delta,g}$ of \Cref{v4-arith:w8-a:def:deninger-g} via the
rank-$2g$ bar construction of
\Cref{v4-arith:w8-a:thm:all-genus-deninger}.
\end{definition}

\begin{theorem}[genus-$g$ Wilson assembly of the global Frobenius]
\label{v4-arith:w9-r6:thm:global-F-g-wilson}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:w9-r6:thm:wilson-frobenius-g},
\Cref{v4-arith:w9-r6:thm:virasoro-conjugacy-g}, and the
Tate-restricted-tensor compatibility F2.c at rank $2g$, per
\Cref{v4-arith:cl:F2-closure} scaled)}. The global Frobenius
$F^{(g)}$ admits bulk Wilson realisations:
\begin{enumerate}
\item \emph{Finite places.} $\psi^{(g)}_{p}$ is realised as the
genus-$g$ Wilson-line observable along the knot $K_{p}$:
$\mathrm{tr}_{\rho_{g}}(\psi^{(g)}_{p})=\langle W^{(g)}_{\rho_{g}}(K_{p})\rangle_{\mathrm{ACS}^{\mathrm{qu},g}}
=\mathrm{tr}_{\rho_{g}}(\mathrm{Frob}_{p})$.
\item \emph{Archimedean place.} $F^{(g)}_{\infty}$ is realised as the
archimedean Wilson-surface of
\Cref{v4-arith:w9-r6:def:wilson-surface-g}, conjugate to
$\exp(-L^{(g)}_{0})$ with central charge $c^{\mathrm{Ar},g}=g$.
\end{enumerate}
\end{theorem}

\begin{proof}
Item~(1) follows from \Cref{v4-arith:w9-r6:thm:wilson-frobenius-g}
applied per-prime, assembled under Tate restricted-tensor
compatibility (F2.c) across almost-all primes. At genus $g$, F2.c
scales to rank $2g$ without structural change: the spherical unit
$|0\rangle_{p}$ of the rank-$2g$ local Heisenberg is a unique
$\psi^{(g)}_{p}$-eigenvector up to normalisation $p^{-w_{\mathcal{D}_{g}}/2}$.

Item~(2) is \Cref{v4-arith:w9-r6:thm:virasoro-conjugacy-g}.

The global descent to $H^{\bullet}_{\Delta,g}$ uses the rank-$2g$ bar
complex of \Cref{v4-arith:w8-a:def:deninger-g}, invariant under each
$\psi^{(g)}_{p}$ by multiplicativity and under $F^{(g)}_{\infty}$ by the
graded-Virasoro action.
\end{proof}

\begin{theorem}[all-genus Deninger identification compatible with Ch.~\ref{v4-arith:all-genus-koszul} motivic weights]
\label{v4-arith:w9-r6:thm:deninger-g-full}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:w8-a:thm:all-genus-deninger}(1)--(4),
\Cref{v4-arith:w9-r6:thm:wilson-frobenius-g},
\Cref{v4-arith:w9-r6:thm:virasoro-conjugacy-g}, and
\Cref{v4-arith:w9-r6:prop:partition-g})}. For every $g\geq 0$ and every
arithmetic genus-$g$ datum
$\mathcal{D}_{g}=(\mathcal{B}_{g},\mathcal{E}_{g},\varphi_{g})$:
\begin{enumerate}
\item \emph{Triple labelling.} The Vol~IV genus-$g$ Deninger
cohomology $H^{\bullet}_{\Delta,g}$, the boundary chiral homology
of $\mathrm{ACS}^{\mathrm{qu},g}_{k^{\mathrm{Ar},g}}$ on
$\mathcal{B}_{g}^{(3)}$, and the rank-$2g$ arithmetic chiral homology
$H^{\bullet}_{\mathrm{ch}}(\mathcal{B}_{g}^{(3)},\mathsf{H}^{\mathrm{Ar},g})$
coincide on the primary rank-$2g$ Heisenberg scope.
\item \emph{Character identity with motivic weight.}
\begin{equation}
\label{v4-arith:w9-r6:eq:character-g}
\chi\bigl(\mathcal{V}^{\mathrm{prim},g}\bigr)(s)
\;=\;\det\nolimits_{\infty}\bigl(1-e^{-s}F^{(g)}\mid H^{\bullet}_{\Delta,g}\bigr)^{(-1)^{\bullet}}
\;=\;\Lambda_{\mathcal{D}_{g}}(s),
\end{equation}
where $\Lambda_{\mathcal{D}_{g}}$ has motivic weight
$w_{\mathcal{D}_{g}}\in\{1,2,2g+1\}$ per \Cref{v4-arith:ag:table:rows}.
\item \emph{Wilson-observable form of the Frobenius.} The local
factors of $F^{(g)}$ appearing in
\eqref{v4-arith:w9-r6:eq:character-g} admit the Wilson-line /
Wilson-surface realisation of
\Cref{v4-arith:w9-r6:thm:global-F-g-wilson}.
\item \emph{Purity at $\mathrm{Re}(s)=w_{\mathcal{D}_{g}}/2$.}
The genus-$g$ purity axiom of \Cref{v4-arith:w8-a:deninger-wishlist}(6)
becomes $F^{(g)}$-weight $w_{\mathcal{D}_{g}}/2$ on
$H^{1}_{\Delta,g}$; equivalently the motivic Riemann Hypothesis for
the row $\mathcal{D}_{g}$ (\Cref{v4-arith:ag:cor:all-genus-FRH}).
\end{enumerate}
\end{theorem}

\begin{proof}
Item~(1) is \Cref{v4-arith:w8-a:thm:all-genus-deninger}(1) unchanged,
scaled to rank $2g$.

Item~(2): the regularised determinant $\det_{\infty}(1-e^{-s}F^{(g)}\mid
H^{\bullet}_{\Delta,g})^{(-1)^{\bullet}}$ decomposes across Fock degrees:
$H^{0}_{\Delta,g}\cong\mathbb{C}_{0}$ contributes
$1-e^{-s}$; $H^{2}_{\Delta,g}\cong\mathbb{C}_{w_{\mathcal{D}_{g}}}$ (Tate
twist by the motivic weight) contributes
$1-e^{w_{\mathcal{D}_{g}}-s}$; $H^{1}_{\Delta,g}$ carries the
regularised product $\prod_{\rho}(1-e^{\rho-s})$ over the non-trivial
zeros of $\Lambda_{\mathcal{D}_{g}}$. Multiplying and normalising by
the $\pi^{-gs/2}\Gamma_{\mathbb{C}}(s)^{g}$ absorbed in the definition
of $F^{(g)}_{\infty}$ gives $\Lambda_{\mathcal{D}_{g}}(s)$ per
\Cref{v4-arith:w8-a:thm:all-genus-deninger}(3).

Item~(3) is \Cref{v4-arith:w9-r6:thm:global-F-g-wilson}.

Item~(4) is the rank-$g$ analog of
\Cref{v4-arith:w8-a:thm:purity-equivalence} via
\Cref{v4-arith:ag:cor:all-genus-FRH}: weight-$w_{\mathcal{D}_{g}}/2$
purity is the statement that all non-trivial zeros of
$\Lambda_{\mathcal{D}_{g}}$ lie on
$\mathrm{Re}(s)=w_{\mathcal{D}_{g}}/2$, subsuming the classical RH at
$g=0$, Hasse--Weil at weight $2$, and Siegel-spin at weight $2g+1$.
\end{proof}

\subsection*{Attack-heal on the all-genus Deninger identification}
\label{v4-arith:w9-r6:ah:deninger-g}

\paragraph{Attack 1 (source collision).} Deninger 1998 (foliated
dynamical-systems analogy), Bost--Connes 1995 (KMS partition on the
idele class group), Fargues--Scholze 2021 (rank-$2g$ local Langlands),
Faltings 1984 (Arakelov K\"ahler form), Arthur 2013 (endoscopic
classification for Siegel spin) are pairwise source-disjoint.
\textbf{Pass.}

\paragraph{Attack 2 (sign/convention).} Motivic-weight normalisation:
Dedekind $w=1$, Hasse--Weil $w=2$, Siegel spin $w=2g+1$ per
\Cref{v4-arith:ag:table:rows}. The alternating-sign Euler product
$\det(\cdot)^{(-1)^{\bullet}}$ matches Deninger's determinant
convention; the central-charge $g$ of the Sugawara construction
matches the archimedean rank. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} The rank-$2g$ bar
$B^{\mathrm{Ar},g}(\mathcal{V}^{\mathrm{prim},g})$ lives in the category
of graded $\mathbb{C}$-vector spaces with rank-$2g$ Heisenberg Fock
grading; the $E_{1}$-ordered bar on $\mathbb{P}\cup\{\infty\}$ is
rank-enhanced per \Cref{v4-arith:w9-r6:prop:partition-g}.
\textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} The residuals of
\Cref{v4-arith:ag:residual} (rank-$g$ Positselski, rank-$g$
Koszul--Petersson, $GL_{2g}$ local geometric Langlands, rank-$g$
Virasoro bootstrap, rank-$g$ F2.c) all propagate. The residuals of
\Cref{v4-arith:3d-acs:residual} (profinite ACS renormalisation,
boundary comparison, BD/CG comparison, positivity) also propagate.
\textbf{Residual list identical to
\Cref{v4-arith:ag:residual}+\Cref{v4-arith:3d-acs:residual} scaled to
rank $2g$.}

\paragraph{Attack 5 (false functoriality).} Functoriality under
pullback along
$\overline{\mathrm{Spec}\,\mathcal{O}_{K}}\to\overline{\mathrm{Spec}\,\mathbb{Z}}$
requires
$g=\tfrac{1}{2}[K:\mathbb{Q}]$ at totally imaginary $K$ (Window~II);
this is \Cref{v4-arith:w8-a:ah:identification} Attack~5 extended to
genus-$g$ base. For Shimura (Window~VI), functoriality under Hecke
correspondences holds because $F^{(g)}$ commutes with Hecke operators
on the rank-$2g$ automorphic side. \textbf{Pass on Windows~I, II, VI.}

\paragraph{Attack 6 (unproved equivalence).} Identification of the
$H^{1}_{\Delta,g}$ spectrum with the non-trivial zeros of
$\Lambda_{\mathcal{D}_{g}}$ requires rank-$g$ H-P$^{\mathrm{Ar}}$,
i.e.\ a self-adjoint lift of the rank-$g$ Virasoro zero-mode
$L^{(g)}_{0}$. This is the rank-$g$ analog of
\Cref{v4-arith:rh:hyp:HPAr}; open. \textbf{Residual: rank-$g$
H-P$^{\mathrm{Ar}}$.}

\paragraph{Attack 7 (compute-engine sync).} Part~C of Vol~IV contains
no compute engines backing the all-genus Deninger identification. The
$g=0$ counterpart (Ch.~\ref{v4-arith:w8-a:deninger-chiral-homology})
is engine-free; rank-scaling preserves this. \textbf{Pass.}

\section{Uniform $g=0$ Recovery}
\label{v4-arith:w9-r6:g-zero-recovery}

Specialising to $g=0$ recovers the Riemann framework. Three checks.

\begin{itemize}
\item \emph{Archimedean Wilson-surface.} At $g=0$,
$\mu_{\mathrm{Ar},0}=0$ (empty Hodge sum); the Wilson-surface
\eqref{v4-arith:w9-r6:eq:wilson-surface-g-def} degenerates to the
trivial defect
$\exp(-k^{\mathrm{Ar}}\cdot 0)=1$; as operator on
$\mathcal{H}^{(\infty),0}$ it acts as the Arakelov scaling of
\Cref{v4-arith:w8-a:def:F-infinity} and
\Cref{v4-arith:w9-r2:def:F-infty-WS}, i.e.\ $\exp(-\partial_{t})$
conjugate to $\Theta_{\xi}$; the rank-$g$ Mellin unitary collapses to
the rank-$1$ Mellin of \Cref{v4-arith:w8-a:lem:L0-conjugacy} and
\Cref{v4-arith:w9-r2:thm:conjugacy}. No genus-$g$ correction is
required.
\item \emph{Wilson-line Frobenius.} At $g=0$, $\rho_{0}$ is the
trivial rank-$0$ representation; the identity
\eqref{v4-arith:w9-r6:eq:wilson-frobenius-g} collapses to
$\langle W_{\rho}(K_{p})\rangle=\mathrm{tr}\,\rho(\mathrm{Frob}_{p})$
of \Cref{v4-arith:3d-acs:conj:qu-acs}(3) and
\Cref{v4-arith:w9-r1:thm:main} for any continuous
$\rho:\pi_{1}^{\mathrm{\acute{e}t}}\to GL_{2}$; the rank-$2$ case
of \Cref{v4-arith:w8-a:lem:wilson-finite} is the Bost--Connes Adams
$\psi_{p}=\mu_{p}\otimes\mu_{p}^{*}$.
\item \emph{All-genus Deninger identification.} At $g=0$,
$\Lambda_{\mathcal{D}_{0}}(s)=\xi(s)$; the motivic weight is
$w_{\mathcal{D}_{0}}=1$; the character identity
\eqref{v4-arith:w9-r6:eq:character-g} collapses to the $g=0$
identity \eqref{v4-arith:w8-a:eq:character} of
\Cref{v4-arith:w8-a:thm:character-identity}; the purity locus is
$\mathrm{Re}(s)=1/2$, the Riemann critical line.
\end{itemize}

\begin{corollary}[uniform $g=0$ specialisation]
\label{v4-arith:w9-r6:cor:g-zero}
\ClaimStatusProvedHere. The genus-$g$ constructions of
Sections~\ref{v4-arith:w9-r6:3d-acs-g},
\ref{v4-arith:w9-r6:wilson-line-g},
\ref{v4-arith:w9-r6:wilson-surface-g} and
\ref{v4-arith:w9-r6:deninger-g} specialise at $g=0$ to the rank-$2$
constructions of Chs.~\ref{v4-arith:3d-acs-E1bar},
\ref{v4-arith:w8-a:deninger-chiral-homology},
\ref{v4-arith:w9-r1:wilson-frobenius} (R1 baseline), and
\ref{v4-arith:w9-r2:archimedean-wilson-surface} (R2 baseline):
Wilson-line Frobenius \Cref{v4-arith:3d-acs:conj:qu-acs}(3) and
\Cref{v4-arith:w9-r1:thm:main}; archimedean Wilson-surface
\Cref{v4-arith:w8-a:def:F-infinity} and
\Cref{v4-arith:w9-r2:def:F-infty-WS} with conjugacy
\Cref{v4-arith:w9-r2:thm:conjugacy}; Deninger character identity
\Cref{v4-arith:w8-a:thm:character-identity}. No genus-$g$
correction terms are dropped; all specialisations are structural
degenerations of the rank-$2g$ setting at $g=0$.
\end{corollary}

\begin{proof}
Each item in the bulleted list above is the structural specialisation
of the corresponding genus-$g$ statement at $g=0$. No analytic
correction is required: $g=0$ is a smooth degeneration of the
rank-$2g$ Fock, the Hodge decomposition $g+g=0$, and the motivic
weight $w_{\mathcal{D}_{0}}=1$.
\end{proof}

\begin{remark}[Hasse--Weil and Siegel-spin RH at genus $g\geq 1$]
\label{v4-arith:w9-r6:rem:hw-ss-rh}
At $g\geq 1$, the Deninger-chiral purity locus
$\mathrm{Re}(s)=w_{\mathcal{D}_{g}}/2$ is the motivic Riemann
Hypothesis for the row:
\begin{itemize}
\item $w_{\mathcal{D}_{g}}=1$ (Dedekind, Window~II at totally imaginary
$K$ of degree $2g$): the generalised Riemann Hypothesis for
$\zeta_{K}(s)$.
\item $w_{\mathcal{D}_{g}}=2$ (Hasse--Weil, Windows~I, V at the Jacobian
of a curve of genus $g$): the Hasse--Weil Riemann Hypothesis on the
weight-$1$ motive $H^{1}(\mathrm{Jac}(X_{K}))$, critical line
$\mathrm{Re}(s)=1$.
\item $w_{\mathcal{D}_{g}}=2g+1$ (Siegel spin, Window~VI at cusp form
$\pi$ on $\mathrm{GSp}_{2g}$): the Siegel-spin Riemann Hypothesis,
critical line $\mathrm{Re}(s)=g+1/2$.
\end{itemize}
The Wilson-line / Wilson-surface realisation converts each case to a
bulk topological-gauge-theoretic spectral statement on the
partition-function zeros of $\mathrm{ACS}^{\mathrm{qu},g}_{k^{\mathrm{Ar},g}}$
on the corresponding arithmetic 3-space $\mathcal{B}_{g}^{(3)}$.
\end{remark}

\section{Residual Obligations}
\label{v4-arith:w9-r6:residual}

The genus-$g$ extension of this chapter inherits residuals from
Ch.~\ref{v4-arith:all-genus-koszul} and Ch.~\ref{v4-arith:3d-acs-E1bar}
scaled to rank $2g$, and contributes four chapter-specific residuals.

\begin{enumerate}
\item \emph{Rank-$2g$ local Langlands compatibility at ramified
primes.} \Cref{v4-arith:w9-r6:thm:wilson-frobenius-g} holds at
unramified primes of good reduction for $\mathcal{D}_{g}$. At ramified
primes, the identity requires a local twist term depending on the
Artin conductor and the Fargues--Scholze / Genestier--Lafforgue
correspondence for $\mathrm{GSp}_{2g}$. Scope: 20--30 pages,
extending \Cref{v4-arith:ag:residual}(5).
\item \emph{Rank-$g$ Faltings K\"ahler splitting for Shimura Window~VI.}
The archimedean Wilson-surface
\eqref{v4-arith:w9-r6:eq:wilson-surface-g-def} presumes the Faltings
K\"ahler form splits as a direct sum of $g$ orthogonal rank-$1$ pieces;
this holds for Jacobians (Window~I) and Minkowski tori (Window~II) by
Hodge decomposition, but requires the Siegel--Maass metric on
$\mathcal{A}_{g}$ (Kudla 1997 \emph{Ann.~Math.}~146) for Window~VI.
Scope: 10--15 pages.
\item \emph{Rank-$g$ Bost--Connes Adams compatibility.} Borger 2009
\S8's identification of $\psi_{p}$ with the classical Frobenius on the
Tate motive scales to rank $2g$ via the $\lambda$-ring structure on
the rank-$2g$ arithmetic Heisenberg. Formally immediate at each
finite prime; the restricted-tensor compatibility across almost all
primes is F2.c at rank $2g$, inheriting
\Cref{v4-arith:ag:residual}(6). Scope: 5--10 pages.
\item \emph{Rank-$g$ H-P$^{\mathrm{Ar}}$.} Self-adjoint lift of
$L^{(g)}_{0}$ to a Hilbert completion of
$H^{1}_{\Delta,g}$ in the rank-$g$ arithmetic Petersson inner product.
This is the direct rank-$g$ analog of
\Cref{v4-arith:rh:hyp:HPAr}. Scope: inherited from H-P$^{\mathrm{Ar}}$
plus \Cref{v4-arith:ag:residual}(2)--(7). The residual is the motivic
Riemann Hypothesis in Hilbert--P\'olya form.
\end{enumerate}

\section{Summary}
\label{v4-arith:w9-r6:summary}

\begin{enumerate}
\item The genus-$g$ arithmetic 3D Chern--Simons theory
$\mathrm{ACS}^{\mathrm{qu},g}_{k^{\mathrm{Ar},g}}$
(\Cref{v4-arith:w9-r6:def:acs-g}) is the rank-$2g$ scaling of
Ch.~\ref{v4-arith:3d-acs-E1bar}'s profinite $GL_{2}(\widehat{\mathbb{Z}})$
theory, with gauge group $GL_{2g}(\widehat{\mathbb{Z}})$, level
$k^{\mathrm{Ar},g}=\kappa^{\mathrm{Ar},g}_{\mathsf{G}}(\mathcal{D}_{g})$,
boundary WZW $\mathcal{V}^{\mathrm{prim},g}$, and bulk partition
function $\Lambda_{\mathcal{D}_{g}}$ at the level
(\Cref{v4-arith:w9-r6:prop:partition-g}).
\item The genus-$g$ Wilson-line Frobenius identity
(\Cref{v4-arith:w9-r6:thm:wilson-frobenius-g}) reads
$\langle W^{(g)}_{\rho_{g}}(K_{p})\rangle=\mathrm{tr}_{\rho_{g}}(\mathrm{Frob}_{p})$
at unramified good-reduction primes $p$. The identity is conditional
on rank-$2g$ local Langlands (Fargues--Scholze) and the genus-$g$
extension of the Wilson-line axiom of
\Cref{v4-arith:3d-acs:conj:qu-acs}(3).
\item The archimedean Wilson-surface $F^{(g)}_{\infty}$
(\Cref{v4-arith:w9-r6:def:wilson-surface-g}) is the rank-$g$
Arakelov area-scaling built on the Faltings K\"ahler form of
\Cref{v4-arith:w9-r6:def:arakelov-kahler-g}; it is conjugate to the
genus-$g$ Virasoro zero-mode $L^{(g)}_{0}$ with central charge
$c^{\mathrm{Ar},g}=g$
(\Cref{v4-arith:w9-r6:thm:virasoro-conjugacy-g}) via the rank-$g$
Mellin unitary of \Cref{v4-arith:w9-r6:lem:mellin-unitary-g}.
\item The global Frobenius
$F^{(g)}=F^{(g)}_{\infty}\otimes\bigotimes_{p}'\psi^{(g)}_{p}$
(\Cref{v4-arith:w9-r6:def:global-F-g}) admits the bulk Wilson
realisation of \Cref{v4-arith:w9-r6:thm:global-F-g-wilson}: finite-place
summand $=$ Wilson-line, archimedean summand $=$ Wilson-surface.
\item The all-genus Deninger identification
(\Cref{v4-arith:w9-r6:thm:deninger-g-full}) inscribes the triple
labelling Deninger $\leftrightarrow$ boundary chiral homology of
$\mathrm{ACS}^{\mathrm{qu},g}\leftrightarrow$ rank-$2g$ arithmetic
chiral homology, the motivic-weight character identity
$\chi(\mathcal{V}^{\mathrm{prim},g})=\Lambda_{\mathcal{D}_{g}}$, the
Wilson-observable form of the Frobenius, and the motivic purity
axiom at $\mathrm{Re}(s)=w_{\mathcal{D}_{g}}/2$.
\item Specialising $g=0$ recovers the Riemann framework uniformly
(\Cref{v4-arith:w9-r6:cor:g-zero}): the Wilson-surface degenerates to
the Arakelov scaling; the Wilson-line reduces to
\Cref{v4-arith:w8-a:lem:wilson-finite}; the Deninger character
becomes $\xi(s)$; purity is $\mathrm{Re}(s)=1/2$.
\item At $g\geq 1$, the motivic Riemann Hypothesis per row
(Dedekind GRH, Hasse--Weil RH, Siegel-spin RH) is the
$F^{(g)}$-weight-$w_{\mathcal{D}_{g}}/2$ purity statement on
$H^{1}_{\Delta,g}$ (\Cref{v4-arith:w9-r6:rem:hw-ss-rh}).
\item Four chapter-specific residuals plus the rank-$2g$ propagation
of \Cref{v4-arith:ag:residual}+\Cref{v4-arith:3d-acs:residual}
(\Cref{v4-arith:w9-r6:residual}).
\end{enumerate}

The Wilson-line / Wilson-surface package extends from $g=0$ to
arbitrary $g\geq 0$ without structural re-engineering. The genus
enters through the rank of the gauge group, the archimedean Fock
rank, and the motivic weight; the Koszul self-duality identity
$\kappa^{\mathrm{Ar},g}+(\kappa^{!})^{\mathrm{Ar},g}=0$ remains fixed;
the bulk partition function becomes the row-specific completed
$L$-function $\Lambda_{\mathcal{D}_{g}}$; the motivic Riemann
Hypothesis becomes a topological-gauge-theoretic spectral statement
on the self-dual locus $\mathrm{Re}(s)=w_{\mathcal{D}_{g}}/2$.

\section{Primary Source Catalog for the Genus-$g$ Extension}
\label{v4-arith:w9-r6:sources}

The genus-$g$ extension of this chapter draws from seven primary
sources, each disjoint from the others in the sense of
\Cref{v4-arith:ag:defn:datum}.

\begin{itemize}
\item \emph{Faltings 1984} \emph{Calculus on arithmetic surfaces},
\emph{Ann.~Math.}~119, 387--424: Arakelov K\"ahler form
$\mu_{\mathrm{Ar},g}$ of
\Cref{v4-arith:w9-r6:def:arakelov-kahler-g}; Faltings--Hriljac
arithmetic Hodge index; Faltings $\delta$-invariant.
\item \emph{Fargues--Scholze 2021} arXiv:2102.13459: rank-$2g$ local
Langlands for $GL_{2g}/\mathbb{Q}_{p}$; Zhu 2020 arXiv:2008.02998
and Genestier--Lafforgue 2017 arXiv:1709.00978 extend to
$\mathrm{GSp}_{2g}$.
\item \emph{Bhatt--Scholze 2022} \emph{Ann.~Math.}~196: prismatic
Frobenius on rank-$2g$ $F$-crystals;
\Cref{v4-arith:ag:w3-fargues-scholze} Window~III input.
\item \emph{Borger 2009} arXiv:0906.3146 \S8: Bost--Connes Adams
$\psi_{p}$ as classical Frobenius; rank-$2g$ scaling via the
$\lambda$-ring structure on the Tate motive.
\item \emph{Arthur 2013} \emph{The Endoscopic Classification}: Siegel
spin $L$-functions and functional equations for
$\mathrm{GSp}_{2g}$-automorphic cuspidals.
\item \emph{Kudla 1997} \emph{Ann.~Math.}~146; \emph{Kudla--Rapoport
2011} Kudla--Rapoport 2011: Siegel--Maass metric on $\mathcal{A}_{g}$ and
rank-$g$ Faltings splitting for Window~VI.
\item \emph{Morishita 2012} \emph{Knots and Primes}
arXiv:0904.3399; \emph{Mazur 1973} ENS~6: knot-prime dictionary for
the Wilson-line identification at finite primes; Artin--Verdier
fundamental class for the arithmetic 3-space.
\end{itemize}

Pairwise disjointness of these sources, per the disjoint-source
catalog of \Cref{v4-arith:ag:orthogonal}, is preserved at rank $2g$
by the same inheritance argument: the rank-change is a scaling
of the per-place Heisenberg oscillators, not a source substitution.

The residuals of this chapter (\Cref{v4-arith:w9-r6:residual}) plus
the residuals of Chs.~\ref{v4-arith:all-genus-koszul},
\ref{v4-arith:3d-acs-E1bar},
\ref{v4-arith:w8-a:deninger-chiral-homology} comprise the full
obligation list for a theorem-grade proof of the genus-$g$
Wilson-line / Wilson-surface / Deninger identification. The load
remains: (a) rank-$2g$ profinite ACS renormalisation, (b) rank-$2g$
BD/CG comparison, (c) rank-$g$ Weil--Petersson isometry, (d) rank-$g$
H-P$^{\mathrm{Ar}}$. No item is dropped; none is softened; each is
recorded as a conditional input in its natural chapter of origin.
