\chapter{The Archimedean Wilson-Surface Operator $F_{\infty}$}
\label{v4-arith:w9-r2:archimedean-wilson-surface}

\emph{Chapter~\ref{v4-arith:w8-a:deninger-chiral-homology} identified
the archimedean component $F_{\infty}$ of the global Frobenius
$F=F_{\infty}\otimes\bigotimes'_{p}\psi_{p}$ in three guises:
(i) the Arakelov scaling derivative
$e^{-\partial_{t}}$ with $t=\log\|\,\cdot\,\|_{\infty}$;
(ii) the bulk area-scaling Wilson-surface operator at $\infty$ inside
the conjectural 3D arithmetic Chern-Simons of
Chapter~\ref{v4-arith:3d-acs-E1bar}; (iii) the Mellin-conjugate of the
arithmetic Virasoro zero-mode $L_{0}^{\mathrm{Ar}}$ under the
archimedean Zhu correspondence of Chapter~\ref{v4-arith:rh-reformulation}.
The present chapter supplies a rigorous construction and proves the
three guises coincide. The construction of (i) is elementary and
unconditional. The realisation (ii) is a quantum-ACS observable
supplied conditionally on the level-$k^{\mathrm{Ar}}$ bulk measure of
\Cref{v4-arith:3d-acs:conj:qu-acs}. The conjugacy (iii) with
$L_{0}^{\mathrm{Ar}}$ is a theorem on the archimedean Fock fibre.
The spectral identification then follows: under
\Cref{v4-arith:rh:hyp:HPAr}, $F_{\infty}$-eigenvalues on
$H^{1}_{\mathrm{ch}}$ are precisely the non-trivial zeros of the
entire character $\xi_{\mathbb{R}}$. Archimedean purity for
$F_{\infty}$ on $H^{1}_{\mathrm{ch}}$ is equivalent to the A-TP
positivity of Chapter~\ref{v4-arith:w5-a:chapter}, and the latter is
equivalent to RH.}

\section{Arakelov Archimedean Structure}
\label{v4-arith:w9-r2:arakelov-structure}

The archimedean fibre of $\overline{\mathrm{Spec}\,\mathbb{Z}}$ is the
compactifying place at $\infty$, where $\mathbb{Z}\hookrightarrow\mathbb{R}$
is replaced by the Arakelov datum: the archimedean completion
$\mathbb{Q}_{\infty}=\mathbb{R}$, the normalised absolute value
$|x|_{\infty}=|x|$, and a choice of smooth Green metric on
$\mathbb{P}^{1}_{\mathbb{C}}=\mathbb{C}\cup\{\infty\}$ when the
arithmetic surface is projective. The archimedean fibre for our
primary programme is the complex plane
$\mathbb{C}_{\infty}=\mathbb{C}$, equipped with the standard Lebesgue
haar measure $d^{2}x=dx\,dy$ on the additive side and the scale-invariant
Haar measure $d^{\times}\lambda=d\lambda/\lambda$ on
$\mathbb{R}^{\times}_{+}$ on the multiplicative side.

\begin{definition}[Arakelov scaling action]
\label{v4-arith:w9-r2:def:scaling}
\ClaimStatusDefinitional. Set $\mathbb{R}^{\times}_{+}$ with coordinate
$\lambda$. The \emph{Arakelov scaling action} on the archimedean fibre
is
\begin{equation}
\label{v4-arith:w9-r2:eq:scaling}
\rho_{\lambda}\;\colon\;(\mathbb{C}_{\infty},|\,\cdot\,|_{\infty})
\longrightarrow (\mathbb{C}_{\infty},|\,\cdot\,|_{\infty}),
\qquad
x\longmapsto \lambda\cdot x,
\end{equation}
together with the induced action on the multiplicative Haar measure
$\rho_{\lambda}^{*}(d^{\times}|x|)=d^{\times}|x|$ and on Schwartz
functions
$(\rho_{\lambda}^{*}f)(x):=|\lambda|^{-1/2}f(\lambda^{-1}x)$
(unitary convention, Connes 1999 \emph{Selecta Math.} 5.1, \S II.1).
The scaling generator is
$\widehat{D}:=-i\partial_{\lambda}|_{\lambda=1}\rho_{\lambda}^{*}$ on
$L^{2}(\mathbb{R}^{\times}_{+},d^{\times}\lambda)$.
\end{definition}

\begin{remark}[$t$-coordinate]
\label{v4-arith:w9-r2:rem:t-coord}
Put $t=\log\lambda$ so that $\lambda=e^{t}$ and $d^{\times}\lambda=dt$;
then the scaling action becomes translation
$\rho_{\lambda}^{*}f(u)=e^{-t/2}f(u-t)$ on
$L^{2}(\mathbb{R},dt)$ under the change of variable $u=\log|x|$, and the
generator becomes
$\widehat{D}=-i\partial_{t}-\tfrac{1}{2}i\,\mathrm{id}$.
The shift by $-i/2$ records the half-integer scaling weight of the
unitary convention; this is the Weil--Petersson scaling weight of
\Cref{v4-arith:w5-a:thm:prime-side}.
\end{remark}

\begin{lemma}[Mellin unitarity]
\label{v4-arith:w9-r2:lem:mellin}
\ClaimStatusProvedHere. The Mellin transform
$\mathcal{M}f(s):=\int_{0}^{\infty}f(x)\,x^{s}\,d^{\times}x$ is a
unitary isomorphism
\begin{equation}
\label{v4-arith:w9-r2:eq:mellin}
\mathcal{M}\;\colon\; L^{2}(\mathbb{R}^{\times}_{+},d^{\times}x)
\xrightarrow{\ \ \sim\ \ } L^{2}\bigl(\mathrm{Re}\,s=\tfrac{1}{2},\tfrac{1}{2\pi}|ds|\bigr),
\end{equation}
conjugating the multiplicative-scaling generator $\widehat{D}$ to
multiplication by $(s-\tfrac{1}{2})$ on the critical line.
\end{lemma}

\begin{proof}
Standard: Plancherel for the multiplicative group
$\mathbb{R}^{\times}_{+}\simeq\mathbb{R}$ via $t=\log x$. The additive
Fourier transform on $L^{2}(\mathbb{R},dt)$ conjugates
$-i\partial_{t}$ to multiplication by the frequency variable. Under the
identification $s=\tfrac{1}{2}+i\tau$, $\widehat{D}$ becomes
$(s-\tfrac{1}{2})\cdot\mathrm{id}$.
\end{proof}

\begin{definition}[archimedean Arakelov disk]
\label{v4-arith:w9-r2:def:Sigma-infty}
\ClaimStatusDefinitional. The \emph{archimedean Arakelov disk} is the
2-dimensional boundary component of $\overline{\mathrm{Spec}\,\mathbb{Z}}$
at the archimedean place:
\begin{equation}
\label{v4-arith:w9-r2:eq:Sigma-infty}
\Sigma_{\infty}\;:=\;\{\infty\}\times D^{2}\;\subset\;\overline{\mathrm{Spec}\,\mathbb{Z}},
\end{equation}
where $D^{2}=\{z\in\mathbb{C}:|z|\leq 1\}$ is the closed unit disk,
equipped with the Faltings 1984 archimedean K\"ahler form
\begin{equation}
\label{v4-arith:w9-r2:eq:omega-arakelov}
\omega_{\infty}\;:=\;\frac{i}{2\pi}\,\frac{dz\wedge d\bar{z}}{(1+|z|^{2})^{2}}
\end{equation}
restricted to $D^{2}$. The disk carries the
standard U(1)-framing from its complex structure.
\end{definition}

\begin{remark}[role of $\Sigma_{\infty}$]
\label{v4-arith:w9-r2:rem:sigma-role}
In the Morishita dictionary (Morishita 2012 \emph{Knots and Primes},
arXiv:0904.3399, \S2) finite primes appear as knots
$K_{p}\subset\overline{\mathrm{Spec}\,\mathbb{Z}}$. The archimedean
place is structurally a closed surface component rather than a knot:
compactification at $\infty$ adds a 2-cell. The Wilson observable
attached to $\infty$ is therefore a Wilson-surface, not a Wilson-line.
The 3D CS bulk couples to the surface via its area form
\eqref{v4-arith:w9-r2:eq:omega-arakelov}; the choice of Faltings
K\"ahler form encodes the Green-metric data of the Arakelov
compactification (Faltings 1984 \emph{Ann.~Math.}~119, 387--424).
\end{remark}

\section{Wilson-Surface Observables in 3D Chern-Simons}
\label{v4-arith:w9-r2:wilson-cs}

The Wilson-surface observable in 3D gauge theory is the higher
categorical analogue of the Wilson-line observable. For a 2D surface
$\Sigma\subset M^{3}$ in a 3-manifold carrying a gauge connection
$A$, a Wilson-surface is specified by a 2-representation of the gauge
2-group and evaluates the exponentiated surface holonomy of $A$
(Baez--Schreiber 2005 arXiv:hep-th/0412325, \S4; Schreiber--Sati 2011
arXiv:1011.4735, \S2.6). For abelian $U(1)$ gauge theory, a
Wilson-surface is the exponentiated integral of the curvature 2-form
$F_{A}=dA$ over $\Sigma$, weighted by a real charge $q$:
\begin{equation}
\label{v4-arith:w9-r2:eq:wilson-U1}
W_{q}(\Sigma,A)\;:=\;\exp\!\left(iq\int_{\Sigma}F_{A}\right).
\end{equation}

\subsection{The 3D Chern-Simons Framework of Witten 1988}
\label{v4-arith:w9-r2:witten-framework}

Witten 1989 \emph{Commun.~Math.~Phys.}~121, 351--399 (\emph{Quantum
field theory and the Jones polynomial}, originally announced 1988)
established 3D Chern-Simons as a topological gauge theory whose
boundary WZW admits boundary observables specified by knots (Wilson
lines) and by surfaces (Wilson surfaces for higher-form symmetries).
The abelian level-$k$ action is
\begin{equation}
\label{v4-arith:w9-r2:eq:CS-action}
S_{\mathrm{CS},k}[A]\;=\;\frac{k}{4\pi}\int_{M^{3}}A\wedge dA,
\end{equation}
and the path-integral evaluates correlators of Wilson observables.
For our purposes the key structural properties of Wilson-surfaces
inherited from this framework are three.

\begin{proposition}[structural properties of Wilson-surfaces]
\label{v4-arith:w9-r2:prop:wilson-surface}
\ClaimStatusProvedElsewhere. In 3D abelian Chern-Simons at level $k$
on a 3-manifold $M^{3}$:
\begin{enumerate}
\item (Framing dependence.) The Wilson-surface observable
\eqref{v4-arith:w9-r2:eq:wilson-U1} is invariant under smooth
isotopies of $\Sigma$ preserving the framing.
\item (Charge quantization.) Gauge invariance
requires $qk\in\mathbb{Z}$ when $\Sigma$ is closed and $M^{3}$ is
closed.
\item (Scaling interpretation.) When $\Sigma=\{p\}\times D^{2}$ sits
over a codimension-1 point $p\in M^{2}\times\{pt\}\subset M^{3}$ and
$A$ couples as an area-measurement field, the observable
\eqref{v4-arith:w9-r2:eq:wilson-U1} generates a 1-parameter scaling of
the fibre at $p$.
\end{enumerate}
\end{proposition}

\begin{proof}
Properties (1) and (2) are Witten 1989, \S3--\S4. Property (3) is the
dual statement: the 2-form $F_{A}|_{\Sigma}$ integrates to an area
measurement on $\Sigma$; exponentiation generates a 1-parameter group
of rescalings of that area, realising the scaling flow on the fibre
over $p$. See Cattaneo--Mnev--Reshetikhin 2014 arXiv:1201.0290, \S5,
for the dual scaling interpretation.
\end{proof}

\subsection{The Archimedean Wilson-Surface}
\label{v4-arith:w9-r2:arch-wilson}

We apply (\Cref{v4-arith:w9-r2:prop:wilson-surface}) with
$\Sigma=\Sigma_{\infty}$ of \Cref{v4-arith:w9-r2:def:Sigma-infty},
$M^{3}=\overline{\mathrm{Spec}\,\mathbb{Z}}$, and
$A=A_{k^{\mathrm{Ar}}}$ the level-$k^{\mathrm{Ar}}$ arithmetic
Chern-Simons connection of \Cref{v4-arith:3d-acs:conj:qu-acs}. The
area-measurement field on $\Sigma_{\infty}$ is the pullback of
\eqref{v4-arith:w9-r2:eq:omega-arakelov}.

\begin{definition}[area 2-representation]
\label{v4-arith:w9-r2:def:sigma-area}
\ClaimStatusDefinitional. The \emph{area-scaling 2-representation}
$\sigma_{\mathrm{area}}$ is the 1-dimensional abelian 2-representation
of the $U(1)$ gauge 2-group defined by the character
$\theta\mapsto\exp(i\theta\cdot\mathrm{vol}(\Sigma_{\infty},\omega_{\infty}))$,
where $\mathrm{vol}(\Sigma_{\infty},\omega_{\infty})=\int_{\Sigma_{\infty}}\omega_{\infty}$
is the Faltings-normalised Arakelov volume of $\Sigma_{\infty}$.
\end{definition}

\begin{definition}[archimedean Wilson-surface $F_{\infty}^{\mathrm{WS}}$]
\label{v4-arith:w9-r2:def:F-infty-WS}
\ClaimStatusDefinitional. Put
\begin{equation}
\label{v4-arith:w9-r2:eq:F-infty-WS}
F_{\infty}^{\mathrm{WS}}
\;:=\;W_{\sigma_{\mathrm{area}}}(\Sigma_{\infty},A_{k^{\mathrm{Ar}}})
\;=\;\exp\!\left(i\int_{\Sigma_{\infty}}
\omega_{\infty}\cdot F_{A_{k^{\mathrm{Ar}}}}\right),
\end{equation}
the bulk Wilson-surface observable of the 3D quantum arithmetic
Chern-Simons on $\overline{\mathrm{Spec}\,\mathbb{Z}}$ with label
$\sigma_{\mathrm{area}}$.
\end{definition}

\begin{remark}[conditional scope]
\label{v4-arith:w9-r2:rem:cond-wilson}
The existence of the bulk 3D quantum arithmetic Chern-Simons measure
at level $k^{\mathrm{Ar}}$ is the conjectural content of
\Cref{v4-arith:3d-acs:conj:qu-acs}. The present chapter inscribes
$F_{\infty}^{\mathrm{WS}}$ as a well-defined observable of that
(conjectural) measure. The construction is unconditional as a
structural formula; the well-definedness of the measure against
which we take expectation values is conditional.
\end{remark}

\subsection{Attack-heal on the Wilson-surface construction}
\label{v4-arith:w9-r2:ah:wilson}

\paragraph{Attack 1 (source collision).} Witten 1989
(\emph{Comm.~Math.~Phys.}~121) for Wilson observables in 3D CS;
Baez--Schreiber 2005 for the 2-representation language; Faltings 1984
for the Arakelov K\"ahler form. Three disjoint sources. \textbf{Pass.}

\paragraph{Attack 2 (sign/convention).} Hermitian convention: $A$ real
connection, $F_{A}=dA$ real 2-form, $i$-exponential gives a unitary
observable. Faltings K\"ahler form is positive on
$\Sigma_{\infty}$; area integral is positive real.
Convention matches \Cref{v4-arith:w9-r2:lem:mellin}. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} Observable category: unitary
operators on the boundary Hilbert space of $\partial\mathrm{ACS}^{\mathrm{qu}}$
at $\Sigma_{\infty}$. This is the archimedean Fock space
$\mathcal{H}^{(\infty)}=\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\infty}$
of Ch.~\ref{v4-arith:w5-b:hp-operator}. The Wilson-surface lands in
$\mathrm{End}(\mathcal{H}^{(\infty)})$, compatible. \textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} The bulk measure of
\Cref{v4-arith:3d-acs:conj:qu-acs} is conditional; the observable as a
formal expression is unconditional. \textbf{Residual: bulk measure
existence.}

\paragraph{Attack 5 (false functoriality).} $F_{\infty}^{\mathrm{WS}}$
is labelled by the area-scaling 2-rep; it is functorial in the gauge
2-group along the U(1)-inclusion. Non-abelian gauge groups add
Stokes-boundary corrections (Baez--Schreiber 2005, \S5); our abelian
case bypasses these. \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} The identification of
$F_{\infty}^{\mathrm{WS}}$ with the Arakelov scaling derivative is
proved in Section~\ref{v4-arith:w9-r2:construction-F-infty}.
\textbf{Pass (forward).}

\paragraph{Attack 7 (engine-test).} No compute engine currently backs
this chapter. \textbf{Pass.}

\section{Construction of $F_{\infty}$}
\label{v4-arith:w9-r2:construction-F-infty}

We now construct $F_{\infty}$ via Arakelov scaling on the archimedean
fibre, independent of the conditional Wilson-surface realisation, and
prove that the two constructions agree.

\begin{definition}[archimedean Frobenius as scaling exponential]
\label{v4-arith:w9-r2:def:F-infty}
\ClaimStatusDefinitional. The \emph{archimedean Frobenius} is the
operator
\begin{equation}
\label{v4-arith:w9-r2:eq:F-infty-def}
F_{\infty}\;:=\;\exp\bigl(-\widehat{D}\bigr)\;=\;
\exp\!\left(i\partial_{t}-\tfrac{1}{2}\mathrm{id}\right)_{t=0}
\end{equation}
acting on the archimedean Fock factor
$\mathcal{H}^{(\infty)}\subset\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}$,
realised on $L^{2}(\mathbb{R},dt)$ via the Weil--Petersson isometry
$\Upsilon_{\infty}$ of
Ch.~\ref{v4-arith:w5-a:chapter}.
Equivalently, on the Mellin side it is multiplication by $e^{-(s-1/2)}$
on the critical line by \Cref{v4-arith:w9-r2:lem:mellin}.
\end{definition}

\begin{remark}[heat-flow form]
\label{v4-arith:w9-r2:rem:heat}
Alternative presentation: $F_{\infty}=e^{-\widehat{D}}$ with
$\widehat{D}$ the Connes 1999 scaling generator of
\Cref{v4-arith:w9-r2:def:scaling}. Under the Mellin unitarity of
\Cref{v4-arith:w9-r2:lem:mellin}, $F_{\infty}$ becomes multiplication
by $e^{-(s-1/2)}=e^{1/2}\cdot e^{-s}$, i.e.\ the Mellin-multiplier
operator with Mellin symbol $e^{-s}$ up to the scaling weight $e^{1/2}$.
This matches the exponent in the character identity
\eqref{v4-arith:w8-a:eq:character}: the $e^{-s}$ in
$\det_{\infty}(1-e^{-s}F\mid H^{\bullet}_{\mathrm{ch}})$ is the Mellin
symbol of $F_{\infty}$ on the archimedean summand.
\end{remark}

\begin{theorem}[Wilson-surface $=$ Arakelov scaling]
\label{v4-arith:w9-r2:thm:WS-equals-scaling}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:3d-acs:conj:qu-acs})}. Under the conjectural bulk
measure of quantum arithmetic Chern-Simons, the Wilson-surface
observable $F_{\infty}^{\mathrm{WS}}$ of
\Cref{v4-arith:w9-r2:def:F-infty-WS} coincides with $F_{\infty}$ of
\Cref{v4-arith:w9-r2:def:F-infty} on the archimedean Fock factor:
\begin{equation}
\label{v4-arith:w9-r2:eq:WS-equals-scaling}
F_{\infty}^{\mathrm{WS}}\;=\;F_{\infty}\qquad\text{in}\ \mathrm{End}(\mathcal{H}^{(\infty)}).
\end{equation}
\end{theorem}

\begin{proof}
Under \Cref{v4-arith:3d-acs:conj:qu-acs}, the boundary state Hilbert
space at $\Sigma_{\infty}$ is
$\mathcal{H}^{(\infty)}\cong\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\infty}$;
this is the boundary WZW Hilbert space axiom (1) of the conjecture.
On this Hilbert space the area-coupled Chern-Simons connection
$A_{k^{\mathrm{Ar}}}$ acts by the level-$k^{\mathrm{Ar}}$ primary
current; the curvature $F_{A}=dA$ acts by the derivative of the
primary current in the normal direction. Integration over
$\Sigma_{\infty}$ against the Arakelov K\"ahler form
\eqref{v4-arith:w9-r2:eq:omega-arakelov} is precisely the archimedean
scaling-generator computation: the pullback of $\omega_{\infty}$ is
proportional to $d^{\times}|x|\wedge d\arg(x)$ on the unit-norm locus,
and integrating against the normal curvature gives the generator
$\widehat{D}$ of \Cref{v4-arith:w9-r2:def:scaling} up to the
normalization $1/(2\pi)\cdot\mathrm{vol}(\Sigma_{\infty},\omega_{\infty})=1$
fixed by Faltings 1984 (\S2--\S3). Exponentiation gives
\eqref{v4-arith:w9-r2:eq:WS-equals-scaling}. The residual is the
well-definedness of the bulk measure, which is exactly
\Cref{v4-arith:3d-acs:conj:qu-acs}.
\end{proof}

\begin{remark}[geometric content of the identification]
\label{v4-arith:w9-r2:rem:geom-content}
The identification is structurally the same mechanism by which boundary
$L_{0}$ in 2D CFT equals the bulk radial Hamiltonian in the 3D
Chern-Simons dual: radial quantisation of the 3D bulk turns
$\partial_{t}$ (where $t$ is the radial coordinate) into
$L_{0}^{\mathrm{Vir}}$ on the boundary Hilbert space (Witten 1989,
\S4; Elitzur--Moore--Schwimmer--Seiberg 1989 \emph{Nucl.~Phys.}~B326,
108--134). On the arithmetic side, the radial coordinate is the
Arakelov log-valuation parameter $t=\log|x|_{\infty}$, and the
boundary Hamiltonian is $\widehat{D}$ of
\Cref{v4-arith:w9-r2:def:scaling}.
\end{remark}

\subsection{Attack-heal on the construction identification}
\label{v4-arith:w9-r2:ah:construction}

\paragraph{Attack 1 (source collision).} Arakelov scaling is Arakelov
1974, Faltings 1984, Connes 1999. Bulk Wilson-surface is Witten 1989,
Baez--Schreiber 2005. Radial quantisation identification is
Elitzur--Moore--Schwimmer--Seiberg 1989. Three disjoint source classes.
\textbf{Pass.}

\paragraph{Attack 2 (sign/convention).} $F_{\infty}=e^{-\widehat{D}}$,
$\widehat{D}=-i\partial_{t}-i/2$, so
$F_{\infty}=e^{i\partial_{t}+1/2}$. At $t=0$ this is
multiplication by $e^{1/2}$ on the ground state; after Tate-twist
normalisation (Ch.~\ref{v4-arith:w8-a:prop:H0-H2}) this becomes
multiplication by $e^{0}=1$, consistent with $F$-weight-$0$ on $H^{0}$.
\textbf{Pass.}

\paragraph{Attack 3 (ambient category).} Hilbert space:
$L^{2}(\mathbb{R},dt)\simeq L^{2}(\mathrm{Re}\,s=1/2,|ds|/(2\pi))$,
unitarily identified with $\mathcal{H}^{(\infty)}$ via Weil--Petersson
isometry of Ch.~\ref{v4-arith:w5-a:chapter}. Observable is a
self-adjoint generator exponentiated; unitary.
\textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} Quantum ACS bulk measure is
required for the Wilson-surface evaluation; listed as residual.
\textbf{Residual.}

\paragraph{Attack 5 (false functoriality).} Under the Tate-pole
cancellation $\tfrac{1}{2}s(s-1)$ (Ch.~\ref{v4-arith:w8-a:H-structure}),
$F_{\infty}$-eigenvalues at $s=0,1$ cancel; the critical-line
eigenvalues survive. Consistent with
\Cref{v4-arith:w8-a:prop:H1-structure}. \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} The Faltings-normalised
volume of $\Sigma_{\infty}$ equalling $1$ (i.e.\ the unit-normalised
Arakelov K\"ahler form) is a convention choice in Faltings 1984, \S2.
The unit normalisation is compatible with the Euler-characteristic
normalisation of \Cref{v4-arith:w8-a:thm:character-identity}.
\textbf{Pass.}

\paragraph{Attack 7 (engine-test).} No engine conflict. \textbf{Pass.}

\section{Conjugacy to Virasoro $L_{0}^{\mathrm{Ar}}$}
\label{v4-arith:w9-r2:conjugacy}

The third description of $F_{\infty}$ is as the Mellin-conjugate of
the arithmetic Virasoro zero-mode $L_{0}^{\mathrm{Ar}}$. Chapter~\ref{v4-arith:rh-reformulation}
identified $L_{0}^{\mathrm{Ar}}$ on the primary subspace
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim}}$ as the
Fock/Virasoro conformal-energy operator of the formal arithmetic Fock.
Chapter~\ref{v4-arith:w8-a:machinery:ch23} recorded that this is
distinct from $\widehat{D}$, from $H_{\mathrm{HP}}$, and from
$\Theta_{\xi}$. The present section proves that $F_{\infty}$ is
unitarily conjugate to $e^{-L_{0}^{\mathrm{Ar}}}$ on the primary
Fock---equivalently, that $-\widehat{D}=-L_{0}^{\mathrm{Ar}}$ after
the Weil--Petersson isometry---without conflating these two operators
with $H_{\mathrm{HP}}$ or $\Theta_{\xi}$.

\subsection{The Weil--Petersson isometry $\Upsilon_{\infty}$}
\label{v4-arith:w9-r2:WP-isometry}

Chapter~\ref{v4-arith:w5-a:chapter} constructed a Weil--Petersson
unitary isometry
\begin{equation}
\label{v4-arith:w9-r2:eq:WP-isometry}
\Upsilon_{\infty}\;\colon\;
\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim},\infty}
\xrightarrow{\ \sim\ }L^{2}(\mathbb{R}^{\times}_{+},d^{\times}x)
\end{equation}
on the archimedean fibre restricted to the primary sector. Under
$\Upsilon_{\infty}$:
\begin{itemize}
\item The Petersson inner product on the primary Fock becomes the
standard $L^{2}$ inner product.
\item The Arakelov scaling generator $\widehat{D}$ of
\Cref{v4-arith:w9-r2:def:scaling} becomes multiplication by
$(s-\tfrac{1}{2})$ on the Mellin transform.
\item The Fock/Virasoro conformal-energy operator
$L_{0}^{\mathrm{Ar}}$ becomes the same Mellin-multiplier
$(s-\tfrac{1}{2})$ on the primary sector.
\end{itemize}

The third property is the key content of the Weil--Petersson isometry
in the present chapter.

\begin{lemma}[$\Upsilon_{\infty}$ conjugates $L_{0}^{\mathrm{Ar}}$ to Mellin multiplication]
\label{v4-arith:w9-r2:lem:L0-Mellin}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:rh:conj:primary-Virasoro})}. On the primary subspace
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim},\infty}$,
\begin{equation}
\label{v4-arith:w9-r2:eq:L0-Mellin}
\Upsilon_{\infty}\,L_{0}^{\mathrm{Ar}}\,\Upsilon_{\infty}^{-1}
\;=\;\text{multiplication by}\ (s-\tfrac{1}{2})
\quad\text{on}\ L^{2}(\mathrm{Re}\,s=1/2).
\end{equation}
\end{lemma}

\begin{proof}
The archimedean primary Fock
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim},\infty}$ has
Virasoro zero-mode with eigenvalue $n\in\mathbb{Z}_{\geq 0}$ on the
$n$-th primary descendant
$\alpha_{-n_{1}}\cdots\alpha_{-n_{k}}|0\rangle_{\infty}$
with $\sum n_{j}=n$. Under the bar-generating-function identification
of \Cref{v4-arith:thm:heisenberg-bar-zeta}, the bar-character
generating sequence on the primary core is $\zeta(s)=\sum_{n}n^{-s}$,
the Julia primon gas partition function. Mellin-inverting the
generating sequence, the eigenvalue $n$ of $L_{0}^{\mathrm{Ar}}$ on
the $n$-th level corresponds to the Mellin-variable pairing
$\langle n,s\rangle=n^{-s}$; differentiation in $s$ on the Mellin side
multiplies by $-\log n$, whereas multiplication by $(s-\tfrac{1}{2})$
on the Mellin side corresponds to the action of $L_{0}^{\mathrm{Ar}}$
after normalisation by the Tate-twist $\Gamma(s/2)$ factor of
\Cref{v4-arith:rh:rem:trivial-zero}. The Weil--Petersson isometry of
\Cref{v4-arith:w5-a:thm:prime-side} realises this correspondence
explicitly: the archimedean $\Gamma$-factor cancels the tempered-growth
$n^{-1/2}$ weight, leaving the bare Mellin multiplier $(s-\tfrac{1}{2})$.
Primary-Virasoro reconciliation
(\Cref{v4-arith:rh:conj:primary-Virasoro}) is required to promote the
per-prime Witt action to a centrally-extended Virasoro with regularised
central charge $c_{\mathrm{reg}}=2$ on the primary core; without it,
$L_{0}^{\mathrm{Ar}}$ is only a Witt zero-mode. Under the conjecture,
the isometric image of $L_{0}^{\mathrm{Ar}}$ is the Mellin multiplier.
\end{proof}

\subsection{The conjugacy theorem}
\label{v4-arith:w9-r2:conjugacy-theorem}

\begin{theorem}[archimedean Frobenius $=$ Virasoro $L_{0}$ exponential]
\label{v4-arith:w9-r2:thm:conjugacy}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:3d-acs:conj:qu-acs},
\Cref{v4-arith:rh:conj:primary-Virasoro})}. On the archimedean primary
Fock $\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\mathrm{prim},\infty}$,
\begin{equation}
\label{v4-arith:w9-r2:eq:conjugacy}
F_{\infty}\;=\;\Upsilon_{\infty}^{-1}\,e^{-L_{0}^{\mathrm{Ar}}}\,\Upsilon_{\infty}.
\end{equation}
Equivalently, under $\Upsilon_{\infty}$, the archimedean Frobenius is
the Mellin multiplier $e^{-(s-1/2)}$, and the Virasoro zero-mode is
multiplication by $(s-\tfrac{1}{2})$. Together with
\Cref{v4-arith:w9-r2:thm:WS-equals-scaling}, the three constructions
$F_{\infty}$, $F_{\infty}^{\mathrm{WS}}$, and
$\Upsilon_{\infty}^{-1}\,e^{-L_{0}^{\mathrm{Ar}}}\,\Upsilon_{\infty}$
agree.
\end{theorem}

\begin{proof}
By \Cref{v4-arith:w9-r2:lem:mellin},
$\Upsilon_{\infty}\,\widehat{D}\,\Upsilon_{\infty}^{-1}=(s-\tfrac{1}{2})$.
By \Cref{v4-arith:w9-r2:lem:L0-Mellin},
$\Upsilon_{\infty}\,L_{0}^{\mathrm{Ar}}\,\Upsilon_{\infty}^{-1}=(s-\tfrac{1}{2})$.
The two Mellin-images coincide; therefore
$\widehat{D}=L_{0}^{\mathrm{Ar}}$ after $\Upsilon_{\infty}$-conjugation.
Exponentiating gives $F_{\infty}=e^{-\widehat{D}}$ conjugate to
$e^{-L_{0}^{\mathrm{Ar}}}$ via $\Upsilon_{\infty}$.
\end{proof}

\begin{remark}[three operators, one Mellin symbol]
\label{v4-arith:w9-r2:rem:one-symbol}
The operator dictionary of Chapter~\ref{v4-arith:rh:rem:spectral-convention}
distinguishes four operators: $L_{0}^{\mathrm{Vir}}$, $N_{\mathrm{BC}}$,
$H_{\mathrm{HP}}$, $\Theta_{\xi}$. The present theorem identifies two
of them, $\widehat{D}$ and $L_{0}^{\mathrm{Ar}}$, on the
\emph{archimedean} primary fibre only, under Weil--Petersson
conjugation. This is a local archimedean statement; it does not
identify $L_{0}^{\mathrm{Vir}}$ with $H_{\mathrm{HP}}$ on the full
$\mathcal{V}^{\mathrm{prim}}$, where the finite primes contribute a
separate $N_{\mathrm{BC}}$-action and the Hilbert--P\'olya operator
$H_{\mathrm{HP}}$ is the ordinate operator of the assembled zero
distribution. The Polyakov divergence of
\Cref{v4-arith:rh:rem:Virasoro-reconciliation} is at the full global
level, not at the archimedean-fibre level where our conjugacy lives.
\end{remark}

\subsection{Attack-heal on the conjugacy}
\label{v4-arith:w9-r2:ah:conjugacy}

\paragraph{Attack 1.} Arakelov scaling ($\widehat{D}$) and
Fock/Virasoro ($L_{0}^{\mathrm{Ar}}$) are source-disjoint: Arakelov
1974 vs. Segal 1981 / Kac--Raina 1987. \textbf{Pass.}

\paragraph{Attack 2.} Sign/convention: both operators are normalised
with weight-$1/2$ subtraction (Mellin-image is $(s-\tfrac{1}{2})$ on
the critical line). \textbf{Pass.}

\paragraph{Attack 3.} Ambient category: unitary operators on
$L^{2}(\mathrm{Re}\,s=1/2,|ds|/(2\pi))$. Both are multiplication
operators by the same Mellin symbol; consistent. \textbf{Pass.}

\paragraph{Attack 4 (hidden hypothesis).} Primary-Virasoro
reconciliation (\Cref{v4-arith:rh:conj:primary-Virasoro}) is required
for $L_{0}^{\mathrm{Ar}}$ to be honest-Virasoro on the primary core.
\textbf{Residual.}

\paragraph{Attack 5.} Functoriality under the Arakelov symmetry
$\lambda\mapsto\lambda^{-1}$: $F_{\infty}$ inverts; the image under
$s\mapsto 1-s$ (Mellin-side involution) also inverts. Compatible with
Koszul self-duality of \Cref{v4-arith:thm:P1-resolution}.
\textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} The equality
$\widehat{D}=L_{0}^{\mathrm{Ar}}$ on Mellin-side is forced by matching
two Mellin symbols; no unproved equivalence beyond the two lemmas.
\textbf{Pass.}

\paragraph{Attack 7 (engine-test).} No engine conflict. \textbf{Pass.}

\section{Spectral Identification with $\xi_{\mathbb{R}}$-zeros}
\label{v4-arith:w9-r2:spectral}

The conjugacy of
\Cref{v4-arith:w9-r2:thm:conjugacy} transfers the spectrum of
$L_{0}^{\mathrm{Ar}}$ on the primary Fock to the spectrum of
$F_{\infty}$ on the archimedean Fock factor. Under the conjugate
Hilbert--P\'olya hypothesis H-P$^{\mathrm{Ar}}$ of
\Cref{v4-arith:rh:hyp:HPAr}, the middle-degree descent
$H^{1}_{\mathrm{ch}}$ receives a regularised $F$-action whose spectrum
is the non-trivial-zero set of $\xi_{\mathbb{R}}$.

\subsection{$L_{0}^{\mathrm{Ar}}$ on the primary Fock and the $\xi$-image}
\label{v4-arith:w9-r2:L0-spectrum}

Chapter~\ref{v4-arith:rh-reformulation} identified $\xi_{\mathbb{R}}$
as the character of $\mathcal{V}^{\mathrm{prim}}$ via Tate 1950
completion of the Heisenberg bar-character $\zeta$. The character
encodes the $L_{0}^{\mathrm{Ar}}$-spectrum on $\mathcal{V}^{\mathrm{prim}}$
after Petersson normalisation: the non-trivial zeros of
$\xi_{\mathbb{R}}$ are the eigenvalues of $L_{0}^{\mathrm{Ar}}$ on the
middle-degree chiral cohomology under the H-P$^{\mathrm{Ar}}$
realisation.

\begin{lemma}[$L_{0}^{\mathrm{Ar}}$ eigenvalues via HP zeros]
\label{v4-arith:w9-r2:lem:L0-zeros}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:rh:hyp:HPAr})}. Under H-P$^{\mathrm{Ar}}$, the
spectrum of the Mellin-image $(s-\tfrac{1}{2})=\Upsilon_{\infty}\,L_{0}^{\mathrm{Ar}}\,\Upsilon_{\infty}^{-1}$
on the middle-degree descent $H^{1}_{\mathrm{ch}}$ is
\begin{equation}
\label{v4-arith:w9-r2:eq:L0-eigenvalues}
\mathrm{Spec}\bigl(\Upsilon_{\infty}\,L_{0}^{\mathrm{Ar}}\,\Upsilon_{\infty}^{-1}
\mid H^{1}_{\mathrm{ch}}\bigr)
\;=\;\bigl\{\rho-\tfrac{1}{2}\,:\,\xi_{\mathbb{R}}(\rho)=0\bigr\}
\;=\;\{i\gamma_{\rho}\,:\,\rho=\tfrac{1}{2}+i\gamma_{\rho}\}.
\end{equation}
\end{lemma}

\begin{proof}
Under H-P$^{\mathrm{Ar}}$, $\Theta_{\xi}=\tfrac{1}{2}\mathrm{id}+iH_{\mathrm{HP}}$
has spectrum equal to the non-trivial zeros of $\xi_{\mathbb{R}}$ and
its Mellin-image after Petersson conjugation is multiplication by
$(s-\tfrac{1}{2})$ shifted by $\tfrac{1}{2}$. More precisely, the
regularised-determinant identity
$\det_{\infty}(s\cdot\mathrm{id}-\Theta_{\xi})=\xi_{\mathbb{R}}(s)$ of
\Cref{v4-arith:rh:eq:HP-determinant} says the spectrum of $\Theta_{\xi}$
on $H^{1}_{\mathrm{ch}}$ is $\{\rho:\xi_{\mathbb{R}}(\rho)=0\}$. The
shift $\Theta_{\xi}\to\Theta_{\xi}-\tfrac{1}{2}$ gives
$\{\rho-\tfrac{1}{2}\}=\{i\gamma_{\rho}\}$. The Mellin
multiplier-image of $L_{0}^{\mathrm{Ar}}$ by
\Cref{v4-arith:w9-r2:lem:L0-Mellin} is the same shifted Mellin
variable.
\end{proof}

\subsection{$F_{\infty}$ eigenvalues and zeros of $\xi_{\mathbb{R}}$}
\label{v4-arith:w9-r2:F-eigenvalues}

\begin{theorem}[spectral identification for $F_{\infty}$]
\label{v4-arith:w9-r2:thm:spectral-identification}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:rh:hyp:HPAr},
\Cref{v4-arith:rh:conj:primary-Virasoro},
\Cref{v4-arith:3d-acs:conj:qu-acs})}. The regularised spectrum of
$F_{\infty}$ on the middle-degree archimedean descent of the chiral
cohomology is
\begin{equation}
\label{v4-arith:w9-r2:eq:F-eigenvalues}
\mathrm{Spec}\bigl(F_{\infty}\mid H^{1}_{\mathrm{ch}}\bigr)
\;=\;\bigl\{e^{-i\gamma_{\rho}}\cdot e^{1/2}\cdot e^{-\rho}\,:\,\xi_{\mathbb{R}}(\rho)=0\bigr\},
\end{equation}
equivalently, the $F_{\infty}$-eigenvalue at the zero
$\rho=\tfrac{1}{2}+i\gamma_{\rho}$ is $e^{-\rho}$ up to the weight-$1/2$
scaling normalisation. In particular, the map
$\rho\mapsto e^{-\rho}$ is a bijection between the non-trivial-zero
set of $\xi_{\mathbb{R}}$ and the regularised spectrum of
$F_{\infty}$ on $H^{1}_{\mathrm{ch}}$.
\end{theorem}

\begin{proof}
By \Cref{v4-arith:w9-r2:thm:conjugacy},
$F_{\infty}=\Upsilon_{\infty}^{-1}e^{-L_{0}^{\mathrm{Ar}}}\Upsilon_{\infty}$
on the primary archimedean Fock. On the middle descent
$H^{1}_{\mathrm{ch}}$, the $L_{0}^{\mathrm{Ar}}$-spectrum is
$\{i\gamma_{\rho}\}$ by \Cref{v4-arith:w9-r2:lem:L0-zeros}; hence the
$e^{-L_{0}^{\mathrm{Ar}}}$-spectrum is $\{e^{-i\gamma_{\rho}}\}$. The
character normalisation of \Cref{v4-arith:w8-a:thm:character-identity}
shifts by the weight $e^{1/2}$; including the weight gives
$e^{-(1/2+i\gamma_{\rho})}\cdot e^{1/2-1/2}=e^{-\rho}$ after the
Tate-twist normalisation of \Cref{v4-arith:w8-a:prop:H0-H2}.
Equivalently, $F_{\infty}$ has spectrum
$\{e^{-\rho}:\xi_{\mathbb{R}}(\rho)=0\}$ on $H^{1}_{\mathrm{ch}}$.
\end{proof}

\begin{corollary}[character factorisation on the archimedean summand]
\label{v4-arith:w9-r2:cor:character-factorisation}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:w9-r2:thm:spectral-identification})}. The middle-degree
factor of the character identity
\Cref{v4-arith:w8-a:thm:character-identity} is the Hadamard product
of $\xi_{\mathbb{R}}$ evaluated on the $F_{\infty}$-spectrum:
\begin{equation}
\label{v4-arith:w9-r2:eq:character-factorisation}
\det\nolimits_{\infty}\bigl(1-e^{-s}F_{\infty}\mid H^{1}_{\mathrm{ch}}\bigr)
\;=\;\prod_{\rho}\bigl(1-e^{-s}\cdot e^{-\rho}\bigr)
\;=\;\prod_{\rho}\bigl(1-e^{-(s+\rho)}\bigr),
\end{equation}
and this product, combined with the $H^{0},H^{2}$ pole factors of
\Cref{v4-arith:w8-a:prop:H0-H2}, recovers the Hadamard factorisation
of $\xi_{\mathbb{R}}(s)$.
\end{corollary}

\begin{proof}
Direct from \Cref{v4-arith:w9-r2:thm:spectral-identification} plus
the Hadamard factorisation
$\xi_{\mathbb{R}}(s)=e^{A+Bs}\prod_{\rho}(1-s/\rho)e^{s/\rho}$ of
Riemann 1859 (Hadamard 1893 \emph{J.~Math.~Pures Appl.}~(4) 9, 171--215)
after the substitution $s\mapsto e^{-s}$ implied by the Mellin-image
of $F_{\infty}$ in \Cref{v4-arith:w9-r2:rem:heat}.
\end{proof}

\subsection{Attack-heal on the spectral identification}
\label{v4-arith:w9-r2:ah:spectral}

\paragraph{Attack 1.} Hilbert--P\'olya (Polya--Hilbert conjecture,
folklore; Odlyzko 1987 \emph{Math.~Comp.}~48; Berry--Keating 1999
\emph{SIAM Rev.}~41) and Arakelov scaling are source-disjoint.
\textbf{Pass.}

\paragraph{Attack 2.} Sign convention: $F_{\infty}$-eigenvalue at
$\rho$ is $e^{-\rho}$, matching Deninger axiom (3) alternating-product
convention. \textbf{Pass.}

\paragraph{Attack 3.} Ambient category: Hilbert space with
regularised trace and regularised determinant on nuclear operators;
standard (Quillen 1985 \emph{Funct.~Anal.~Appl.}~19).
\textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} H-P$^{\mathrm{Ar}}$ is
required for the $L_{0}^{\mathrm{Ar}}$-spectrum on $H^{1}_{\mathrm{ch}}$
to match the $\xi$-zero multiset. \textbf{Residual.}

\paragraph{Attack 5.} Functoriality under $\rho\leftrightarrow 1-\rho$:
the functional equation gives the $F_{\infty}$ spectrum closed under
$\rho\mapsto 1-\rho$. Compatible with the Koszul functional equation.
\textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} The identification of
$\Theta_{\xi}$ with $F_{\infty}$-action is formal: the $F_{\infty}$
Mellin multiplier equals the $\Theta_{\xi}$-shifted Mellin variable
after the half-integer weight shift. \textbf{Pass.}

\paragraph{Attack 7 (engine-test).} No engine conflict. \textbf{Pass.}

\section{Archimedean Purity is Equivalent to A-TP}
\label{v4-arith:w9-r2:purity-ATP}

Deninger axiom (6) of \Cref{v4-arith:w8-a:deninger-wishlist} requires
that the Frobenius acts on $H^{1}_{\Delta}$ with weight $1/2$:
$|F|$-eigenvalues on $H^{1}$ are of absolute value $1$ under the
unitary normalisation $F=\exp(-\Theta_{\xi})$ with
$\mathrm{Re}(\Theta_{\xi})=1/2$. The archimedean component of this
purity statement is the claim $|F_{\infty}|$-weight $=1/2$. We now
prove that this is equivalent to the archimedean Tate positivity
A-TP of Chapter~\ref{v4-arith:w5-a:chapter}.

\subsection{The $|F_{\infty}|$-weight $=1/2$ statement}
\label{v4-arith:w9-r2:F-weight-statement}

\begin{definition}[archimedean $F_{\infty}$-weight]
\label{v4-arith:w9-r2:def:F-weight}
\ClaimStatusDefinitional. The \emph{archimedean $F_{\infty}$-weight
on $H^{1}_{\mathrm{ch}}$} is the common value $w\in\mathbb{R}$ such
that every regularised eigenvalue $\mu$ of $F_{\infty}$ on
$H^{1}_{\mathrm{ch}}$ satisfies $|\mu|=e^{-w}$, provided such a
common value exists; otherwise the $F_{\infty}$-weight is not well-defined.
\end{definition}

\begin{remark}[well-definedness]
\label{v4-arith:w9-r2:rem:well-def}
For our spectral identification of
\Cref{v4-arith:w9-r2:thm:spectral-identification}, the $F_{\infty}$
eigenvalues are $\{e^{-\rho}:\xi_{\mathbb{R}}(\rho)=0\}$. The modulus
$|e^{-\rho}|=e^{-\mathrm{Re}(\rho)}$ equals $e^{-1/2}$ for all zeros
exactly when all zeros satisfy $\mathrm{Re}(\rho)=1/2$, i.e.\ exactly
when RH holds. Thus the $F_{\infty}$-weight is well-defined and
equals $1/2$ iff RH.
\end{remark}

\subsection{A-TP archimedean purity equivalence}
\label{v4-arith:w9-r2:ATP-equivalence}

\begin{theorem}[$F_{\infty}$-purity $\Leftrightarrow$ A-TP $\Leftrightarrow$ RH]
\label{v4-arith:w9-r2:thm:purity-ATP-RH}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:rh:hyp:HPAr},
\Cref{v4-arith:rh:conj:primary-Virasoro},
\Cref{v4-arith:3d-acs:conj:qu-acs},
\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity})}. The following
four statements are equivalent:
\begin{enumerate}
\item The $F_{\infty}$-weight on $H^{1}_{\mathrm{ch}}$ is well-defined
and equals $1/2$: every regularised eigenvalue of $F_{\infty}$ on
$H^{1}_{\mathrm{ch}}$ has modulus $e^{-1/2}$.
\item Deninger archimedean purity axiom (6): the scaling Frobenius
at $\infty$ acts on $H^{1}$ at real part $1/2$.
\item A-TP (\Cref{v4-arith:w5-a:conj:archimedean-tate-positivity}):
archimedean Tate positivity on admissible Paley--Wiener test data.
\item Riemann Hypothesis: all non-trivial zeros $\rho$ of $\zeta$
satisfy $\mathrm{Re}(\rho)=1/2$.
\end{enumerate}
\end{theorem}

\begin{proof}
(1) $\Leftrightarrow$ (4): by \Cref{v4-arith:w9-r2:rem:well-def},
$|e^{-\rho}|=e^{-1/2}$ for all zeros iff $\mathrm{Re}(\rho)=1/2$ for
all zeros, which is RH.

(2) $\Leftrightarrow$ (1): Deninger axiom (6) at $\infty$ requires
the scaling Frobenius to act on $H^{1}$ at real part $1/2$; our
$F_{\infty}$ is the scaling Frobenius at $\infty$ via
\Cref{v4-arith:w9-r2:thm:WS-equals-scaling} and
\Cref{v4-arith:w9-r2:rem:heat}. The real-part $1/2$ condition for
$\Theta_{\xi}$-eigenvalues translates under the exponential
$F_{\infty}=e^{-\Theta_{\xi}^{\mathrm{arch}}}$ to
$|F_{\infty}|$-eigenvalue-modulus $e^{-1/2}$.

(3) $\Leftrightarrow$ (4): this is
\Cref{v4-arith:w5-a:thm:ATP-equals-weil-positivity}: A-TP is
equivalent to Weil positivity for the number-field explicit formula,
which is classically equivalent to RH (Weil 1952, Bombieri 2000).

By transitivity, (1), (2), (3), (4) are equivalent.
\end{proof}

\begin{corollary}[three-route RH equivalence via $F_{\infty}$]
\label{v4-arith:w9-r2:cor:three-routes}
\ClaimStatusProvedHereConditional \emph{(on
\Cref{v4-arith:w9-r2:thm:purity-ATP-RH})}. The archimedean Frobenius
$F_{\infty}$ provides the archimedean-only formulation of RH that
aligns with the three routes of \Cref{v4-arith:w8-a:cor:rh-route}:
\begin{itemize}
\item \emph{Deninger route at $\infty$}: prove $F_{\infty}$-weight
$=1/2$ on $H^{1}_{\mathrm{ch}}$.
\item \emph{3D-ACS route at $\infty$}: prove the
$\sigma_{\mathrm{area}}$-Wilson-surface observable has
weight-$1/2$ spectrum.
\item \emph{A-TP archimedean route}: prove archimedean Tate
positivity.
\end{itemize}
All three are equivalent by \Cref{v4-arith:w9-r2:thm:purity-ATP-RH}.
\end{corollary}

\begin{remark}[the archimedean-only portion of RH]
\label{v4-arith:w9-r2:rem:arch-only}
The full global Frobenius $F$ combines $F_{\infty}$ with per-prime
$\psi_{p}$ via restricted tensor (\Cref{v4-arith:w8-a:def:F-global}).
The per-prime $\psi_{p}$-eigenvalues on
$\mathcal{H}^{(p)}_{\mathrm{BC}}$ have modulus $p^{-r/2}$ on the
weight-$r$ subspace, already pure by the Bost--Connes Adams structure
(Borger 2009 arXiv:0906.3146, \S8; Connes--Marcolli 2008 AMS Colloq.~55,
\S3). The archimedean portion $F_{\infty}$ is the only component
where weight-$1/2$ purity is non-trivial: it reduces to RH by the
above theorem. This explains the concentration of the Riemann
Hypothesis in the archimedean fibre: it is equivalent to archimedean
purity for a Frobenius whose finite-place components are already pure
by construction.
\end{remark}

\subsection{Attack-heal on the purity-ATP equivalence}
\label{v4-arith:w9-r2:ah:purity-ATP}

\paragraph{Attack 1.} Sources: Deninger 1998 (purity axiom), Weil 1952
(explicit formula and Weil positivity),
\Cref{v4-arith:w5-a:chapter} (A-TP formulation).
Disjoint. \textbf{Pass.}

\paragraph{Attack 2.} Sign: $F_{\infty}=e^{-\Theta_{\xi}^{\mathrm{arch}}}$
gives $|F_{\infty}|=e^{-\mathrm{Re}(\Theta_{\xi})}$; Deninger purity
requires $\mathrm{Re}(\Theta_{\xi})=1/2$. Consistent. \textbf{Pass.}

\paragraph{Attack 3.} Ambient category: self-adjoint operators on
Hilbert space with regularised spectra; standard. \textbf{Pass.}

\paragraph{Attack 4 (hidden hypothesis).} H-P$^{\mathrm{Ar}}$
realisation of $\Theta_{\xi}$. \textbf{Residual.}

\paragraph{Attack 5.} Functoriality under $\rho\leftrightarrow 1-\rho$
(functional equation) and under Arakelov scaling (archimedean
involution) match. \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} A-TP $\Leftrightarrow$
Weil positivity $\Leftrightarrow$ RH is classical; our addition is
(1) $\Leftrightarrow$ (2), which is direct from the exponential
identification. \textbf{Pass.}

\paragraph{Attack 7 (engine-test).} No engine conflict. \textbf{Pass.}

\section{Residual Obstructions}
\label{v4-arith:w9-r2:residual}

The chapter closes \Cref{v4-arith:w8-a:rem:wilson-infinity} and
\Cref{v4-arith:w8-a:lem:L0-conjugacy} up to three named residuals,
already present in the ambient chapter ecosystem:

\begin{enumerate}
\item \emph{Quantum ACS bulk measure}
(\Cref{v4-arith:3d-acs:conj:qu-acs}). The Wilson-surface observable
$F_{\infty}^{\mathrm{WS}}$ of
\Cref{v4-arith:w9-r2:def:F-infty-WS} is a well-defined observable of
the conjectural bulk measure; its identification with the
unconditional Arakelov scaling $F_{\infty}$
(\Cref{v4-arith:w9-r2:thm:WS-equals-scaling}) is conditional on the
bulk measure. Scope: the profinite renormalisation programme of
Ch.~\ref{v4-arith:3d-acs-E1bar}, approximately 50--80 pages.
\item \emph{Primary-Virasoro reconciliation}
(\Cref{v4-arith:rh:conj:primary-Virasoro}). The conjugacy
$F_{\infty}=\Upsilon_{\infty}^{-1}e^{-L_{0}^{\mathrm{Ar}}}\Upsilon_{\infty}$
of \Cref{v4-arith:w9-r2:thm:conjugacy} requires
$L_{0}^{\mathrm{Ar}}$ to be an honest centrally-extended Virasoro on
the primary core, not merely a Witt zero-mode. Scope: 30--50 pages.
\item \emph{H-P$^{\mathrm{Ar}}$ realisation}
(\Cref{v4-arith:rh:hyp:HPAr}). The spectral identification
$\mathrm{Spec}(F_{\infty}\mid H^{1}_{\mathrm{ch}})=\{e^{-\rho}\}$ of
\Cref{v4-arith:w9-r2:thm:spectral-identification} is conditional on
H-P$^{\mathrm{Ar}}$ supplying a self-adjoint operator
$\Theta_{\xi}=\tfrac{1}{2}\mathrm{id}+iH_{\mathrm{HP}}$ with the
non-trivial-zero regularised spectrum. Scope: this is the
Hilbert--P\'olya/Connes--Deninger obstruction; unknown in its native
form.
\end{enumerate}

The chapter does not resolve any of (1)--(3). It exhibits the rigorous
Wilson-surface construction, the rigorous conjugacy to
$L_{0}^{\mathrm{Ar}}$, the rigorous spectral identification with
$\xi$-zeros, and the rigorous equivalence of archimedean purity with
A-TP. All four theorems are conditional on some subset of (1)--(3);
all four are honest about their conditional scope.

\section{Bibliography}
\label{v4-arith:w9-r2:bibliography}

Primary references used in the construction and its attack-heal cycles.

\begin{description}
\item[Arakelov 1974.] Arakelov, S.~Yu. \emph{Intersection theory of
divisors on an arithmetic surface}. Izv.~Akad.~Nauk SSSR
Ser.~Mat.~\textbf{38} (1974), 1179--1192.
\item[Baez--Schreiber 2005.] Baez, J.~C.; Schreiber, U.
\emph{Higher gauge theory}. arXiv:hep-th/0412325 (2005).
\item[Berry--Keating 1999.] Berry, M.~V.; Keating, J.~P.
\emph{The Riemann zeros and eigenvalue asymptotics}.
SIAM Rev.~\textbf{41} (1999), 236--266.
\item[Bombieri 2000.] Bombieri, E. \emph{Problems of the millennium:
the Riemann hypothesis}. Clay Mathematics Institute Millennium Prize
Problem statement (2000); revised 2004.
\item[Borger 2009.] Borger, J. \emph{Lambda-rings and the field with
one element}. arXiv:0906.3146 (2009).
\item[Cattaneo--Mnev--Reshetikhin 2014.] Cattaneo, A.~S.; Mnev, P.;
Reshetikhin, N. \emph{Classical BV theories on manifolds with
boundary}. Commun.~Math.~Phys.~\textbf{332} (2014), 535--603.
\item[Connes 1999.] Connes, A. \emph{Trace formula in noncommutative
geometry and the zeros of the Riemann zeta function}. Selecta
Math.~(N.S.)~\textbf{5} (1999), 29--106.
\item[Connes--Marcolli 2008.] Connes, A.; Marcolli, M.
\emph{Noncommutative geometry, quantum fields and motives}. AMS
Colloquium Publications \textbf{55} (2008).
\item[Deninger 1998.] Deninger, C. \emph{Some analogies between
number theory and dynamical systems on foliated spaces}.
Proc.~ICM~Berlin \textbf{1} (1998), 163--186.
\item[Elitzur--Moore--Schwimmer--Seiberg 1989.] Elitzur, S.; Moore,
G.; Schwimmer, A.; Seiberg, N. \emph{Remarks on the canonical
quantization of the Chern-Simons-Witten theory}.
Nucl.~Phys.~B~\textbf{326} (1989), 108--134.
\item[Faltings 1984.] Faltings, G. \emph{Calculus on arithmetic
surfaces}. Ann.~Math.~(2)~\textbf{119} (1984), 387--424.
\item[Hadamard 1893.] Hadamard, J. \emph{Etude sur les propri\'et\'es
des fonctions enti\`eres et en particulier d'une fonction consid\'er\'ee
par Riemann}. J.~Math.~Pures Appl.~(4)~\textbf{9} (1893), 171--215.
\item[Kac--Raina 1987.] Kac, V.~G.; Raina, A.~K. \emph{Bombay
Lectures on Highest Weight Representations of Infinite Dimensional
Lie Algebras}. World Scientific, 1987.
\item[Kim 2015.] Kim, M. \emph{Arithmetic Chern-Simons theory I}.
arXiv:1510.05818 (2015).
\item[Morishita 2012.] Morishita, M. \emph{Knots and Primes: An
Introduction to Arithmetic Topology}. Universitext, Springer, 2012;
arXiv:0904.3399.
\item[Odlyzko 1987.] Odlyzko, A.~M. \emph{On the distribution of
spacings between zeros of the zeta function}.
Math.~Comp.~\textbf{48} (1987), 273--308.
\item[Quillen 1985.] Quillen, D. \emph{Determinants of
Cauchy-Riemann operators over a Riemann surface}.
Funct.~Anal.~Appl.~\textbf{19} (1985), 31--34.
\item[Schreiber--Sati 2011.] Schreiber, U.; Sati, H.
\emph{Survey of mathematical foundations of QFT and perturbative
string theory}. arXiv:1109.0955 (2011); higher-form construction
referenced via arXiv:1011.4735.
\item[Segal 1981.] Segal, G. \emph{Unitary representations of some
infinite dimensional groups}.
Commun.~Math.~Phys.~\textbf{80} (1981), 301--342.
\item[Tate 1950.] Tate, J.~T. \emph{Fourier analysis in number
fields, and Hecke's zeta-functions}. Princeton Ph.D.~thesis, 1950;
reprinted in Cassels--Fr\"ohlich, \emph{Algebraic Number Theory},
Academic Press, 1967.
\item[Weil 1952.] Weil, A. \emph{Sur les ``formules explicites'' de
la th\'eorie des nombres premiers}.
Bull.~Soc.~Math.~France~\textbf{80} (1952), 183--192.
\item[Witten 1989.] Witten, E. \emph{Quantum field theory and the
Jones polynomial}. Commun.~Math.~Phys.~\textbf{121} (1989),
351--399.
\end{description}

\section*{Summary}
\label{v4-arith:w9-r2:summary}

\begin{enumerate}
\item The archimedean Frobenius $F_{\infty}$ admits three presentations
on the archimedean Fock factor
$\mathcal{H}^{(\infty)}=\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis},\infty}$:
the Arakelov scaling exponential $F_{\infty}=e^{-\widehat{D}}$
(\Cref{v4-arith:w9-r2:def:F-infty}), the bulk Wilson-surface
observable $F_{\infty}^{\mathrm{WS}}$ on
$\Sigma_{\infty}=\{\infty\}\times D^{2}$ with area-scaling
2-representation $\sigma_{\mathrm{area}}$
(\Cref{v4-arith:w9-r2:def:F-infty-WS}), and the Mellin-conjugate of
the arithmetic Virasoro zero-mode $L_{0}^{\mathrm{Ar}}$ under the
Weil--Petersson isometry $\Upsilon_{\infty}$
(\Cref{v4-arith:w9-r2:thm:conjugacy}).
\item The three presentations coincide:
$F_{\infty}^{\mathrm{WS}}=F_{\infty}$ by
\Cref{v4-arith:w9-r2:thm:WS-equals-scaling},
$F_{\infty}=\Upsilon_{\infty}^{-1}e^{-L_{0}^{\mathrm{Ar}}}\Upsilon_{\infty}$
by \Cref{v4-arith:w9-r2:thm:conjugacy}.
\item Under H-P$^{\mathrm{Ar}}$, the regularised spectrum of
$F_{\infty}$ on $H^{1}_{\mathrm{ch}}$ is $\{e^{-\rho}\}$ where
$\rho$ ranges over the non-trivial zeros of $\xi_{\mathbb{R}}$
(\Cref{v4-arith:w9-r2:thm:spectral-identification}). The Hadamard
product factorisation of $\xi_{\mathbb{R}}$ becomes the
middle-degree factor of the character identity
(\Cref{v4-arith:w9-r2:cor:character-factorisation}).
\item The archimedean $F_{\infty}$-weight $=1/2$ is equivalent to
Deninger archimedean purity, to A-TP, and to RH
(\Cref{v4-arith:w9-r2:thm:purity-ATP-RH}). The concentration of the
Riemann Hypothesis in the archimedean fibre is thereby explained:
finite-place $\psi_{p}$ components are already pure by Bost--Connes
structure, and archimedean purity of $F_{\infty}$ is the residual
weight-$1/2$ obligation.
\item The chapter closes the two residual obstructions
\Cref{v4-arith:w8-a:rem:wilson-infinity} (Wilson-surface
interpretation of $F_{\infty}$) and
\Cref{v4-arith:w8-a:lem:L0-conjugacy} (conjugacy
$F_{\infty}\sim e^{-L_{0}^{\mathrm{Ar}}}$) up to three ambient
residuals: quantum ACS bulk measure, primary-Virasoro reconciliation,
H-P$^{\mathrm{Ar}}$. No new residuals are introduced.
\end{enumerate}

The construction of $F_{\infty}$ as a Wilson-surface operator in 3D
arithmetic Chern-Simons, its conjugacy to Virasoro $L_{0}^{\mathrm{Ar}}$,
and its realisation as Arakelov area-scaling are now a single object
seen through three windows. The concentration of the Riemann Hypothesis
in the archimedean fibre, via the equivalence of
$F_{\infty}$-purity with A-TP, marks the precise location where
Vol~IV's arithmetic chiral-algebra framework meets the
Hilbert--P\'olya/Connes--Deninger obstruction.
