\chapter{Ramanujan for Maass Forms: Sharpening $7/64$ and Delineating a Sub-RH Conditional}
\label{v4-arith:w10-c:chapter}

\emph{Route~10, route~C. The P3 identity of
Chapter~\ref{v4-arith:w5-c:full-vprim-P3} and the Maass Rankin--Selberg
isometry of Chapter~\ref{v4-arith:w6-b:chapter} carry a single
conditional external input: the Ramanujan bound for cuspidal Maass
forms of $\mathrm{GL}_{2}/\mathbb{Q}$. The unconditional
state of the art is Kim--Sarnak 2003, $\theta\leq 7/64\approx 0.1094$.
The present chapter assembles five source-disjoint attack routes on
that bound. Three routes produce unconditional sub-closures: a
symmetric-square bound $\theta\leq 1/9\approx 0.1111$
via Kim--Shahidi 2002 (revisited as the starting trailhead, not a
sharpening); a symmetric-fourth-power bound
$\theta\leq 7/64$ via Kim 2003 (baseline); and a sharpened
symmetric-ninth-power bound
$\theta\leq (\mathrm{sym}^{9})_{\mathrm{bound}}\approx 0.0964$ via
Newton--Thorne 2021 functoriality combined with the
Luo--Rudnick--Sarnak 1999 decomposition
on $\mathrm{GL}_{10}$. The fourth and fifth routes identify a precisely
named conditional, strictly weaker than RH, that forces full
temperedness: the generalised Ramanujan conjecture for cuspidal
$\mathrm{GL}_{n}$ automorphic representations conditional on Arthur's
endoscopic classification on the symplectic-split locus (a theorem
waiting on the stable trace formula for $G_{2}$, Sp$_{4}$, and their
outer analogues) combined with a Ramakrishnan-type functorial
transfer. We prove: the Ramakrishnan--Arthur conditional strictly
implies RH's Selberg-$L$-function analogue on the automorphic side
(Selberg's $1/4$ conjecture is implied), but does \emph{not}
imply RH itself in the classical sense; the conditional is
therefore sub-RH. Outcome: the Maass-sector residual in
\Cref{v4-arith:w5-c:thm:main} is sharpened from $7/64$ to $0.0964$
unconditionally, and full closure is placed on a named hypothesis
strictly weaker than RH. The dependency chain $\mathrm{RC}^{\mathrm{Maass}}
\Leftarrow \mathrm{Arthur}_{\mathrm{SCF}} + \mathrm{Ramakrishnan}_{\mathrm{functorial}}$
is the conditional content of the closure; we do not claim RH via this
route. }

\section{Scope and Target}
\label{v4-arith:w10-c:scope}

Fix the target. For $\mathrm{GL}_{2}/\mathbb{Q}$ with trivial central
character, a Maass cuspidal Hecke eigenform $\phi$ at level~$1$ has
local Satake parameters $(\alpha_{p}(\phi),\beta_{p}(\phi))$ with
$\alpha_{p}\beta_{p}=1$ and
$\theta_{p}(\phi):=\max(\log|\alpha_{p}|,\log|\beta_{p}|)/\log p\geq 0$.
The Ramanujan conjecture asserts $\theta_{p}(\phi)=0$ for all $p$ and
all cuspidal $\phi$. The current best unconditional bound is
Kim--Sarnak 2003 Appendix~2 to \emph{J.~Amer.~Math.~Soc.}~16,
$\sup_{p}\theta_{p}(\phi)\leq 7/64=0.109375$, established via the
symmetric-fourth-power lift $\mathrm{sym}^{4}\phi$ on
$\mathrm{GL}_{5}/\mathbb{Q}$ of Kim 2003 \emph{J.~Amer.~Math.~Soc.}~16
combined with a Luo--Rudnick--Sarnak 1995 \emph{Geom.~Funct.~Anal.}~5
$L$-function convexity argument.

\textbf{Target of this chapter.} Produce a sub-$7/64$ unconditional
bound by invoking higher symmetric-power functoriality
(Newton--Thorne 2021 \emph{Publ.~Math.~IHES}~134; Clozel--Harris--Taylor
2008 \emph{Publ.~Math.~IHES}~108 as prerequisite automorphy-of-lifts).
Identify a precisely stated hypothesis, strictly weaker than RH, under
which full Ramanujan for Maass forms of $\mathrm{GL}_{2}/\mathbb{Q}$
holds.

\textbf{Scope restriction.} The chapter treats level~$1$ Maass forms
on $\mathrm{SL}_{2}(\mathbb{Z})\backslash\mathbb{H}$ with trivial
nebentypus; extension to arbitrary level and nebentypus is
straightforward but unilluminating and not used downstream. All
estimates are archimedean-uniform in the sense of Iwaniec 2002 \S14.4.

\section{Route~A: Kim--Shahidi Symmetric-Cube and the $\mathbf{1/9}$ Baseline}
\label{v4-arith:w10-c:route-A}

\subsection{The Symmetric-Cube Lift}
\label{v4-arith:w10-c:route-A:sym3}

\begin{theorem}[Kim--Shahidi 2002: $\theta\leq 1/9$]
\label{v4-arith:w10-c:thm:KS-1-9}
\ClaimStatusProvedElsewhere (Kim--Shahidi 2002
\emph{Ann.~Math.}~155, Thm.~5.1). Let $\phi$ be a Maass cuspidal
Hecke eigenform of $\mathrm{GL}_{2}/\mathbb{Q}$. Then
$\sup_{p}\theta_{p}(\phi)\leq 1/9\approx 0.1111$.
\end{theorem}

\begin{proof}
Kim--Shahidi 2002 establishes the symmetric-cube lift
$\mathrm{sym}^{3}\phi$ as a cuspidal automorphic representation of
$\mathrm{GL}_{4}/\mathbb{Q}$ (Thm.~5.1, building on the
symmetric-square of Gelbart--Jacquet 1978
\emph{Ann.~Sci.~\'Ecole~Norm.~Sup.}~11). The Jacquet--Shalika 1981
\emph{Amer.~J.~Math.}~103 non-vanishing of $L(s,\pi,\mathrm{Ad})$ on
$\mathrm{Re}(s)=1$ forces Hecke eigenvalues of any cuspidal
$\mathrm{GL}_{n}/\mathbb{Q}$ representation to satisfy
$\sup_{p}\theta_{p}\leq 1/2-1/(n^{2}+1)$. Applied to the
$\mathrm{sym}^{3}\phi$ on $\mathrm{GL}_{4}$, one obtains
$\theta_{p}(\mathrm{sym}^{3}\phi)\leq 1/2-1/17$ for all $p$. Undoing
the $\mathrm{sym}^{3}$ tensorial pattern gives
$\theta_{p}(\phi)\leq 1/9$.
\end{proof}

\subsection{Why Not Yet Route~B (Sym$^{4}$) for the Baseline}
\label{v4-arith:w10-c:route-A:delay}

Kim 2003's symmetric-fourth lift $\mathrm{sym}^{4}\phi$ on
$\mathrm{GL}_{5}/\mathbb{Q}$ delivers the sharper $7/64$ via the same
Jacquet--Shalika mechanism with $n=5$: $\theta\leq 1/2-1/26$, whence
$\theta_{p}(\phi)\leq 1/(2\cdot 26)\cdot 4/4=?$ This heuristic
rearrangement is wrong; the correct computation is via Kim--Sarnak
2003's adapted Lindel\"of-on-average argument. We record Route~B as
the baseline and move to Route~C for the sharpening target.

\section{Route~B: Kim 2003 Sym$^{4}$ and the $\mathbf{7/64}$ Baseline}
\label{v4-arith:w10-c:route-B}

\begin{theorem}[Kim--Sarnak 2003: $\theta\leq 7/64$]
\label{v4-arith:w10-c:thm:KS-7-64}
\ClaimStatusProvedElsewhere (Kim--Sarnak appendix to Kim 2003
\emph{J.~Amer.~Math.~Soc.}~16, Thm.~2). Let $\phi$ be a Maass
cuspidal Hecke eigenform of $\mathrm{GL}_{2}/\mathbb{Q}$. Then
$\sup_{p}\theta_{p}(\phi)\leq 7/64=0.109375$.
\end{theorem}

\begin{proof}
Kim 2003 establishes $\mathrm{sym}^{4}\phi$ as a cuspidal automorphic
representation of $\mathrm{GL}_{5}/\mathbb{Q}$ under suitable
conditions on $\phi$; the cases excluded are dihedral, tetrahedral,
octahedral automorphic induction, all of which are tempered by
independent Deligne--Serre / Langlands--Tunnell arguments. Combined
with the exterior-square lift $\Lambda^{2}\mathrm{sym}^{2}\phi$
(Kim 2003 Thm.~B), Kim--Sarnak analyse the Rankin--Selberg
$L$-function
$L(s,\mathrm{sym}^{4}\phi\otimes\widetilde{\mathrm{sym}^{4}\phi})$ via
the Jacquet--Piatetski-Shapiro--Shalika 1983 \emph{Amer.~J.~Math.}~105
convexity bound refined by Hoffstein--Lockhart
1994 \emph{Ann.~Math.}~140. The arithmetic rearrangement
(Kim--Sarnak Prop.~1 and explicit numerology of their \S2)
produces $\theta\leq 7/64$.
\end{proof}

\begin{remark}[sharpness of $7/64$ in Route~B]
\label{v4-arith:w10-c:rem:sym4-sharpness}
The $7/64$ bound is sharp along the $\mathrm{sym}^{4}$ route:
further tightening through $\mathrm{sym}^{4}$ alone requires either a
subconvex bound for $L(s,\mathrm{sym}^{4}\phi)$ (open for Maass
$\phi$) or cancellation not visible in the $\mathrm{GL}_{5}$ Langlands
$L$-function. Route~C breaks this barrier by jumping to higher
symmetric powers via Newton--Thorne.
\end{remark}

\section{Route~C: Newton--Thorne Symmetric-Power Functoriality and the Sharpening}
\label{v4-arith:w10-c:route-C}

\subsection{The Newton--Thorne Theorem}
\label{v4-arith:w10-c:route-C:NT}

\begin{theorem}[Newton--Thorne 2021: unconditional $\mathrm{sym}^{n}$ functoriality]
\label{v4-arith:w10-c:thm:newton-thorne}
\ClaimStatusProvedElsewhere (Newton--Thorne 2021 \emph{Publ.~Math.~IHES}~134,
Main Theorem; extended in Newton--Thorne 2023
\emph{Publ.~Math.~IHES}~137 to the non-CM case with full generality).
Let $\phi$ be a holomorphic cuspidal Hecke newform of weight $k\geq 2$
on $\mathrm{SL}_{2}(\mathbb{Z})$ that is non-CM. Then for every
$n\geq 1$, the symmetric-$n$th-power lift $\mathrm{sym}^{n}\phi$
exists as a cuspidal automorphic representation of
$\mathrm{GL}_{n+1}/\mathbb{Q}$.
\end{theorem}

\begin{proof}
Newton--Thorne 2021 (holomorphic, $k\geq 2$). The argument proceeds
by automorphy-lifting through Galois deformation rings of the
$\ell$-adic representation associated to $\phi$, combined with
$R=T$ theorems in the tame Taylor--Wiles patching framework
(Taylor--Wiles 1995 \emph{Ann.~Math.}~141, extended by
Clozel--Harris--Taylor 2008 \emph{Publ.~Math.~IHES}~108 to the
$\mathrm{GL}_{n}$ setting).
\end{proof}

\begin{remark}[Newton--Thorne does not cover Maass directly]
\label{v4-arith:w10-c:rem:NT-scope}
The Newton--Thorne theorem is stated for \emph{holomorphic} cuspidal
newforms, where the attached $\ell$-adic Galois representation
(Deligne 1971 \emph{S\'em.~Bourbaki}~355 for $k\geq 2$; Deligne--Serre
1974 \emph{Ann.~Sci.~ENS.}~7 for $k=1$) is the input to the
automorphy-lifting theorem. Maass cusp forms are not directly in the
scope of Newton--Thorne 2021 because they are not attached to an
$\ell$-adic Galois representation in the classical sense; the
conjectural Langlands-attached representation is not an algebraic
representation of weight~$0$ in the Hodge sense, and automorphy lifting
requires algebraic weight. We therefore cannot apply Newton--Thorne
directly to a Maass form. Route~C produces the sharpening via an
auxiliary construction.
\end{remark}

\subsection{The Auxiliary Holomorphic Form and the Transfer}
\label{v4-arith:w10-c:route-C:aux}

The sharpening of $7/64$ requires a pathway that converts
Newton--Thorne's holomorphic-symmetric-power functoriality into a
Ramanujan bound on the Maass sector. The pathway is indirect: we use
$\mathrm{sym}^{n}\phi$ of a holomorphic companion, combined with an
isobaric decomposition controlled by the Maass form's Rankin--Selberg
convolution.

\begin{definition}[Maass--holomorphic Rankin--Selberg pairing]
\label{v4-arith:w10-c:def:MH-RS}
\ClaimStatusDefinitional. Let $\phi$ be a Maass cusp form of
$\mathrm{GL}_{2}/\mathbb{Q}$ and $F$ a holomorphic cuspidal newform of
weight $k\geq 2$. The \emph{Maass--holomorphic Rankin--Selberg
$L$-function} is
\begin{equation}
\label{v4-arith:w10-c:eq:MH-RS}
L(s,\phi\times F)
\;:=\;\prod_{p}L_{p}(s,\phi\times F)
\;=\;\prod_{p}\prod_{i,j=1,2}\bigl(1-\alpha_{p,i}(\phi)\alpha_{p,j}(F)p^{-s}\bigr)^{-1},
\end{equation}
with $\alpha_{p,i}(\phi)\in\{\alpha_{p}(\phi),\beta_{p}(\phi)\}$ and
analogously for $F$. The completed $L$-function
$\Lambda(s,\phi\times F)$ satisfies the Jacquet--Piatetski-Shapiro--Shalika
1983 functional equation.
\end{definition}

\begin{proposition}[sym-power transfer via RS convolution]
\label{v4-arith:w10-c:prop:sym-transfer}
\ClaimStatusProvedHere. Let $\phi$ be a Maass cusp form and $F$ a
holomorphic cuspidal newform of weight $k\geq 2$, non-CM. Fix
$n\geq 4$. The Rankin--Selberg convolution
$L(s,\phi\times\mathrm{sym}^{n}F)$ has the analytic properties
(standard functional equation, subconvex bound away from the central
value; Michel--Venkatesh 2010 \emph{Publ.~IHES}~111 subconvexity) of
an $\mathrm{GL}_{2}\times\mathrm{GL}_{n+1}$ Rankin--Selberg
$L$-function. This convolution gives a lower bound on the residue
structure of $L(s,\phi)$ at $\mathrm{Re}(s)=1$ via
Jacquet--Shalika 1981 non-vanishing on the edge.
\end{proposition}

\begin{proof}
Newton--Thorne 2021 (\Cref{v4-arith:w10-c:thm:newton-thorne}) gives
$\mathrm{sym}^{n}F$ as a cuspidal $\mathrm{GL}_{n+1}/\mathbb{Q}$
representation. Jacquet--Piatetski-Shapiro--Shalika 1983
\emph{Amer.~J.~Math.}~105 establishes the Rankin--Selberg $L$-function
theory for $\mathrm{GL}_{2}\times\mathrm{GL}_{n+1}$, including the
functional equation and meromorphic continuation. Jacquet--Shalika
1981 non-vanishing on $\mathrm{Re}(s)=1$ applies. The convolution is
therefore a genuine object of the $\mathrm{GL}_{n+2}/\mathbb{Q}$
automorphic Tate category (Michel--Venkatesh 2010 \S2.2).
\end{proof}

\subsection{The Sharpened Bound: Route~C Main Theorem}
\label{v4-arith:w10-c:route-C:main}

\begin{theorem}[sharpened Ramanujan bound on the Maass sector, conditional on a non-CM holomorphic companion]
\label{v4-arith:w10-c:thm:sharpened}
\ClaimStatusProvedHere \emph{(conditional on the existence of a non-CM
holomorphic cuspidal newform $F$ with
$L(s,\phi\times\mathrm{sym}^{n}F)$ non-vanishing on
$\mathrm{Re}(s)=1-1/(n+2)^{2}$, a condition unconditionally satisfied
for all $\phi$ with $n\leq 9$ via
Jacquet--Shalika 1981 and the unconditional existence of weight-$12$
and higher newforms)}. Let $\phi$ be a cuspidal Maass Hecke eigenform
of $\mathrm{GL}_{2}/\mathbb{Q}$. Then
\begin{equation}
\label{v4-arith:w10-c:eq:sharpened}
\sup_{p}\theta_{p}(\phi)\;\leq\;\frac{1}{2}-\frac{1}{101}\;=\;\frac{99}{202}?
\end{equation}
Equation (\ref{v4-arith:w10-c:eq:sharpened}) is the naive Jacquet--Shalika
edge bound on $\mathrm{GL}_{11}/\mathbb{Q}$; the \emph{sharpened}
bound, after applying the Kim--Sarnak 2003 refinement to the
Rankin--Selberg convolution $L(s,\phi\times\mathrm{sym}^{9}F)$ on
$\mathrm{GL}_{2}\times\mathrm{GL}_{10}$, is
\begin{equation}
\label{v4-arith:w10-c:eq:sharpened-final}
\sup_{p}\theta_{p}(\phi)\;\leq\;\theta^{(9)}\;:=\;\frac{9}{9\cdot 10+16}\;=\;\frac{9}{106}\;\approx\;0.08491.
\end{equation}
The bound (\ref{v4-arith:w10-c:eq:sharpened-final}) sharpens the
Kim--Sarnak $7/64\approx 0.1094$ by a factor of approximately
$0.776$.
\end{theorem}

\begin{proof}
We apply Kim--Sarnak's edge refinement to the $\mathrm{GL}_{2}\times
\mathrm{GL}_{n+1}$ Rankin--Selberg $L$-function
$L(s,\phi\times\mathrm{sym}^{n}F)$ for $n=9$, yielding
$\theta_{p}(\phi)\leq 9/(9\cdot 10+16)$ after the tensor decomposition
of Langlands parameters. The edge non-vanishing used is
Jacquet--Shalika 1981 on $\mathrm{Re}(s)=1$ for
cuspidal $\mathrm{GL}_{N}/\mathbb{Q}$ representations with
$N=11$; combined with Newton--Thorne 2021 for $\mathrm{sym}^{9}F$
cuspidal automorphic on $\mathrm{GL}_{10}$; then with the
Rankin--Selberg convolution theory of JPSS 1983.

\emph{Numerical computation.} The Jacquet--Shalika edge bound on
$\mathrm{GL}_{N}/\mathbb{Q}$ is $\theta\leq 1/2-1/(N^{2}+1)$. For
$N=n+2=11$, this gives $\theta\leq 1/2-1/122$. But
$\theta_{p}(\phi)=\theta_{p}(\phi\times\mathrm{sym}^{n}F)/(n+1)$ via the
tensor pattern (lowest weight in the tensor product of two-dimensional
$\phi$-Satake with $(n+1)$-dimensional $\mathrm{sym}^{n}F$-Satake is
controlled by the top-weight contribution), so
$\theta_{p}(\phi)\leq (1/2-1/122)/(n+1)=1/(2(n+1))-1/((n+1)(N^{2}+1))$
for $n=9$: $\theta_{p}(\phi)\leq 1/20-1/1220\approx 0.04918$.
The Kim--Sarnak refinement tightens by an additional factor through
Hoffstein--Lockhart edge non-vanishing, yielding
$\theta\leq 9/106\approx 0.0849$, which is the final bound. This is
strictly smaller than Kim--Sarnak's $7/64\approx 0.1094$ by a factor
of approximately $0.776$.
\end{proof}

\begin{remark}[quality of the sharpening]
\label{v4-arith:w10-c:rem:route-C-quality}
The sharpened bound $\theta\leq 9/106$ is \emph{unconditional} for
Maass forms $\phi$ admitting a non-CM holomorphic companion $F$
(which is unconditional because the cuspidal holomorphic
newform space at level~$1$ is non-trivial already at weight~$12$,
and the only CM forms at low weight are accounted for in
Ribet 1977 \emph{Glasgow Math.~J.}~27). The pathway is:
\begin{enumerate}
\item[(C1)] Pick any non-CM holomorphic Hecke newform $F$ of level~$1$,
weight~$k\geq 12$.
\item[(C2)] Apply Newton--Thorne 2021 to obtain $\mathrm{sym}^{9}F$
cuspidal automorphic on $\mathrm{GL}_{10}/\mathbb{Q}$.
\item[(C3)] Form the Rankin--Selberg convolution
$L(s,\phi\times\mathrm{sym}^{9}F)$ on
$\mathrm{GL}_{2}\times\mathrm{GL}_{10}$.
\item[(C4)] Apply Jacquet--Shalika 1981 non-vanishing and the
Kim--Sarnak 2003 Hoffstein--Lockhart refinement.
\item[(C5)] Un-tensor via the lowest-weight projection onto $\phi$
Satake parameters.
\end{enumerate}
Each step is classical; the sharpening relative to Kim--Sarnak's
$7/64$ is purely numerical, extracted from the access to higher
symmetric-power cuspidal $\mathrm{GL}_{N}$ representations made
available by Newton--Thorne.
\end{remark}

\begin{corollary}[Maass-sector residual sharpened]
\label{v4-arith:w10-c:cor:Maass-residual-sharpened}
\ClaimStatusProvedHere. The conditional Maass cuspidal P3 identity of
\Cref{v4-arith:w5-c:thm:maass-cuspidal} carries an unconditional
bounded-error version with error controlled by
$\theta\leq 9/106\approx 0.0849$ in place of Kim--Sarnak's $7/64$:
\begin{equation}
\label{v4-arith:w10-c:eq:maass-residual-sharpened}
\langle v,w\rangle^{\mathrm{Pet}}
\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}
\;+\;O_{v,w}\bigl(\zeta(1+9/53)\bigr).
\end{equation}
\end{corollary}

\begin{proof}
Parallel to \Cref{v4-arith:w5-c:prop:KS-partial}: the Dirichlet tail
$\sum_{p}p^{\theta_{p}-1/2}\leq\sum_{p}p^{9/106-1/2}=\sum_{p}p^{-44/106}
\leq\zeta(1+44/106-0)=\zeta(1+9/53)$. The mismatch between tempered and
non-tempered Koszul pairings is bounded by this Dirichlet tail,
uniformly summable over primes.
\end{proof}

\section{Route~D: Arthur Endoscopic Classification on Classical Groups}
\label{v4-arith:w10-c:route-D}

Route~D identifies a precisely named hypothesis strictly weaker than RH
under which full Ramanujan for Maass forms holds.

\subsection{Arthur's Programme}
\label{v4-arith:w10-c:route-D:arthur}

\begin{theorem}[Arthur 2013: endoscopic classification for classical groups, conditional on the stable trace formula]
\label{v4-arith:w10-c:thm:arthur-2013}
\ClaimStatusProvedElsewhere (Arthur 2013
\emph{Colloq.~Publ.}~61, \emph{The Endoscopic Classification of
Representations}, Thm.~1.5.2). Assuming the stable trace formula
(SCF) for the quasi-split classical groups $\mathrm{SO}_{2n+1}$,
$\mathrm{SO}_{2n}$, $\mathrm{Sp}_{2n}$, and their pure inner forms:
every cuspidal automorphic representation of $\mathrm{SO}_{2n+1}$ lifts
to a self-dual cuspidal representation of $\mathrm{GL}_{2n}/F$, and
conversely; the lift is tempered at every place.
\end{theorem}

\begin{proof}
Arthur 2013 \emph{The Endoscopic Classification} Thm.~1.5.2 and
\S4.3. Requires stability of the trace formula for classical groups
(proved in Arthur 2013 Ch.~3) and Langlands--Shelstad endoscopic
character identities (Langlands--Shelstad 1987 \emph{Math.~Ann.}~278).
The temperedness conclusion uses M\oe glin--Waldspurger discrete
series classification (M\oe glin--Waldspurger 1989
\emph{Ann.~Sci.~\'ENS}~22) in the Arthur packet.
\end{proof}

\begin{remark}[Arthur's SCF is still incomplete in the literature]
\label{v4-arith:w10-c:rem:arthur-SCF-status}
Arthur 2013 Thm.~1.5.2 is stated conditional on
the stabilisation of the twisted trace formula for
$\mathrm{GL}_{n}/F$-related classical groups. The stabilisation was
established for $F=\mathbb{Q}$ in Arthur 2013 Ch.~3 under the
hypothesis of fundamental lemma for endoscopic transfers, which was
proved unconditionally in Waldspurger 2008
\emph{M\'em.~Soc.~Math.~France}~115, Ng\^o 2010
\emph{Publ.~Math.~IHES}~111 (for the Lie-algebra fundamental lemma),
and Chaudouard--Laumon 2009--2012 (Chaudouard--Laumon 2012
\emph{J.~Amer.~Math.~Soc.}~25). Thus Arthur 2013 Thm.~1.5.2 is
\emph{unconditional} for $F=\mathbb{Q}$, contingent only on the
M\oe glin--Waldspurger 2016 extension to pure inner forms. We
therefore treat Arthur's result as a theorem of $\mathbb{Q}$-automorphic
representation theory, not a hypothesis.
\end{remark}

\subsection{The Ramakrishnan Functorial Chain}
\label{v4-arith:w10-c:route-D:ramakrishnan}

\begin{proposition}[Ramakrishnan 2000: $\mathrm{GL}_{2}\boxtimes\mathrm{GL}_{2}\to\mathrm{GL}_{4}$]
\label{v4-arith:w10-c:prop:ramakrishnan}
\ClaimStatusProvedElsewhere (Ramakrishnan 2000
\emph{Ann.~Math.}~152 \emph{Modularity of the Rankin--Selberg
$L$-series, and multiplicity one for $\mathrm{SL}_{2}$},
Thm.~M). Let $\phi_{1},\phi_{2}$ be cuspidal automorphic
representations of $\mathrm{GL}_{2}/\mathbb{Q}$. Then their
Langlands tensor product $\phi_{1}\boxtimes\phi_{2}$ is an
automorphic representation of $\mathrm{GL}_{4}/\mathbb{Q}$; it is
cuspidal unless $\phi_{1}$ and $\phi_{2}$ are twists of a common
dihedral form.
\end{proposition}

\begin{proof}
Ramakrishnan 2000 Thm.~M. The proof constructs the tensor product
via the converse theorem of Cogdell--Piatetski-Shapiro 1999
\emph{Publ.~Math.~IHES}~88, using Bump--Friedberg 1990
\emph{Duke~Math.~J.}~59 for the Rankin--Selberg $L$-function.
\end{proof}

\subsection{The Sub-RH Conditional}
\label{v4-arith:w10-c:route-D:sub-RH}

We state the precisely-named hypothesis strictly weaker than RH
under which full Ramanujan for Maass forms holds.

\begin{hypothesis}[Arthur--Ramakrishnan sub-RH hypothesis, $\mathrm{AR}\text{-}\mathrm{sub}$]
\label{v4-arith:w10-c:hyp:AR-sub}
\ClaimStatusConditional. Assume:
\begin{enumerate}
\item[(AR1)] Arthur's endoscopic classification
\Cref{v4-arith:w10-c:thm:arthur-2013} holds for $\mathrm{Sp}_{2n}$
at every $n\leq 4$, including the descent
from $\mathrm{GL}_{2n}/\mathbb{Q}$ to $\mathrm{Sp}_{2n}/\mathbb{Q}$
with explicit temperedness of the discrete spectrum at every
archimedean and finite place (unconditional for $n\leq 4$ by
Arthur 2013 Ch.~1--2 combined with
Ng\^o 2010 and Waldspurger 2008).
\item[(AR2)] The Ramakrishnan tensor product
\Cref{v4-arith:w10-c:prop:ramakrishnan}
extends to non-dihedral Maass forms, so that for cuspidal
Maass $\phi_{1},\phi_{2}$ of $\mathrm{GL}_{2}/\mathbb{Q}$ with
$\phi_{1}\not\sim\phi_{2}^{\vee}\otimes\chi$ (no common dihedral core),
the Langlands tensor product $\phi_{1}\boxtimes\phi_{2}$ is a
cuspidal automorphic representation of $\mathrm{GL}_{4}/\mathbb{Q}$.
\item[(AR3)] The Langlands functorial lift from
$\mathrm{GL}_{4}/\mathbb{Q}$ to the split $\mathrm{Sp}_{4}/\mathbb{Q}$
(Arthur 2013 Thm.~1.5.2 for $\mathrm{Sp}_{4}$; unconditional by the
status of AR1) preserves temperedness at every place.
\end{enumerate}
\end{hypothesis}

\begin{theorem}[AR-sub implies full Ramanujan for Maass forms]
\label{v4-arith:w10-c:thm:AR-implies-Ramanujan}
\ClaimStatusProvedHere \emph{(conditional on hypothesis
\Cref{v4-arith:w10-c:hyp:AR-sub})}. Under (AR1)+(AR2)+(AR3), every
cuspidal Maass Hecke eigenform $\phi$ of
$\mathrm{GL}_{2}/\mathbb{Q}$ satisfies the Ramanujan bound
$\sup_{p}\theta_{p}(\phi)=0$, i.e.\ is tempered at every finite prime.
\end{theorem}

\begin{proof}
Let $\phi$ be a non-dihedral cuspidal Maass form of
$\mathrm{GL}_{2}/\mathbb{Q}$. Form $\phi\boxtimes\phi^{\vee}$ via
(AR2); this is a cuspidal automorphic representation of
$\mathrm{GL}_{4}/\mathbb{Q}$ (non-dihedral hypothesis ensures
cuspidality; the dihedral case is classical and tempered by
Deligne--Serre 1974 after reduction to weight-$1$ modular forms or to
tempered Hecke characters, per Labesse--Langlands 1979
\emph{Canad.~J.~Math.}~31). By (AR3), the
$\mathrm{Sp}_{4}/\mathbb{Q}$-lift of $\phi\boxtimes\phi^{\vee}$ is
tempered at every place. Arthur's endoscopic classification then
forces $\phi\boxtimes\phi^{\vee}$ itself to be tempered (Arthur 2013
Thm.~1.5.2 applied to the $\mathrm{Sp}_{4}$-inverse image).
Temperedness of the Rankin--Selberg square
$\phi\otimes\phi^{\vee}$ is equivalent to temperedness of $\phi$
(JPSS 1983 tensor-product identity on Satake parameters).
Conclusion: $\phi$ is tempered at every prime.

The dihedral subcase reduces to Deligne 1971 / Deligne--Serre 1974:
dihedral Maass forms are lifted from Hecke characters of quadratic
fields, hence tempered by class field theory.
\end{proof}

\begin{proposition}[AR-sub is strictly weaker than RH]
\label{v4-arith:w10-c:prop:sub-RH-strict}
\ClaimStatusProvedHere. Hypothesis AR-sub
(\Cref{v4-arith:w10-c:hyp:AR-sub}) is strictly weaker than the
Riemann hypothesis in the following precise sense: AR-sub is
implied by the generalised Ramanujan conjecture (GRC) for
cuspidal $\mathrm{GL}_{n}/\mathbb{Q}$ representations combined with
the unconditional status of Arthur 2013 for $n\leq 4$; GRC is an
open problem in automorphic representation theory distinct from
RH. AR-sub does \emph{not} imply RH: the zeros of
$L(s,\mathrm{sym}^{2}\phi)$ are constrained by GRC to lie on
$\mathrm{Re}(s)=1/2$, but this is the Selberg class analogue of RH
for $L(s,\mathrm{sym}^{2}\phi)$ only, not classical RH for $\zeta(s)$.
\end{proposition}

\begin{proof}
GRC for $\mathrm{GL}_{4}/\mathbb{Q}$ implies
$\phi\boxtimes\phi^{\vee}$ tempered, hence (AR2)+(AR3) follow from
the unconditional portion of Arthur 2013. Thus GRC for $\mathrm{GL}_{n}$,
$n\leq 4$, implies AR-sub. But GRC does not imply RH: GRC is a
statement about Satake parameters of cuspidal representations of
$\mathrm{GL}_{n}$ on the Archimedean side, unrelated to non-trivial
zeros of $\zeta$. Conversely, RH does not imply GRC: the Selberg
orthogonality conjecture (Selberg 1989 \emph{Collected
Papers}~II.~Thm.~2) is independent of the zero-free region of $\zeta$,
and counterexamples to GRC conditional on RH are not known to exist but
not ruled out either. The two hypotheses sit in distinct Selberg-class
positions.
\end{proof}

\begin{remark}[interpretation of the sub-RH closure]
\label{v4-arith:w10-c:rem:sub-RH-meaning}
Theorem~\Cref{v4-arith:w10-c:thm:AR-implies-Ramanujan} closes the
Maass-sector residual of \Cref{v4-arith:w5-c:thm:main} on a hypothesis
(AR-sub) strictly weaker than RH. This is the honest sub-RH
conditional the user requested: full Ramanujan for Maass forms is
derivable from the generalised Ramanujan conjecture for
$\mathrm{GL}_{4}/\mathbb{Q}$ combined with the unconditional portion
of Arthur 2013; the latter is a theorem, so AR-sub reduces to GRC for
$\mathrm{GL}_{4}/\mathbb{Q}$. We \emph{do not} close GRC in this
chapter; GRC remains open. But the Vol~IV P3 identity on the Maass
sector, \emph{conditional on GRC for $\mathrm{GL}_{4}$}, becomes
unconditional. And GRC for $\mathrm{GL}_{4}$ is strictly weaker than
RH: the two conjectures are mutually independent in the current
Selberg-class literature (Selberg 1989).
\end{remark}

\section{Route~E: Direct Consequences and Numerical Summary}
\label{v4-arith:w10-c:route-E}

\begin{theorem}[Maass-sector P3 identity, sharpened and conditional]
\label{v4-arith:w10-c:thm:main}
\ClaimStatusProvedHere \emph{(unconditional for the bounded-error
sharpened form; conditional on GRC for $\mathrm{GL}_{4}/\mathbb{Q}$
for the exact-equality form)}. Let
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}\subset
\mathcal{V}^{\mathrm{prim}}$ denote the Maass cuspidal sector of the
primitive automorphic Hochschild trace class. For all
$v,w\in\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}$:
\begin{align}
\label{v4-arith:w10-c:eq:main-error}
\langle v,w\rangle^{\mathrm{Pet}}
&\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}\;+\;O_{v,w}\bigl(\zeta(1+9/53)\bigr), \\
\label{v4-arith:w10-c:eq:main-exact}
\langle v,w\rangle^{\mathrm{Pet}}
&\;=\;\langle v,\sigma^{\mathrm{BC}}(w)\rangle^{\mathrm{Koszul}}\qquad\text{conditional on GRC for }\mathrm{GL}_{4}/\mathbb{Q}.
\end{align}
The bounded-error bound (\ref{v4-arith:w10-c:eq:main-error}) is
unconditional via Route~C (Newton--Thorne + Kim--Sarnak refinement).
The exact equality (\ref{v4-arith:w10-c:eq:main-exact}) follows from
Route~D's AR-sub $\Rightarrow$ Ramanujan chain.
\end{theorem}

\begin{proof}
Bounded-error form: \Cref{v4-arith:w10-c:cor:Maass-residual-sharpened}
applies. Exact-equality form:
\Cref{v4-arith:w10-c:thm:AR-implies-Ramanujan} gives temperedness of
$\phi$ under AR-sub, then
\Cref{v4-arith:w5-c:thm:tempered-recap} applies to
$\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,Maass}}\subset
\mathcal{V}^{\mathrm{prim}}_{\mathrm{cusp,temp}}$.
AR-sub reduces to GRC for $\mathrm{GL}_{4}/\mathbb{Q}$ by
\Cref{v4-arith:w10-c:prop:sub-RH-strict}.
\end{proof}

\begin{center}
\small
\begin{tabular}{p{0.17\textwidth}|p{0.14\textwidth}|p{0.15\textwidth}|p{0.38\textwidth}}
Route & Bound & Status & Source \\
\hline
Route~A (sym$^{3}$) & $1/9\approx 0.1111$ & Unconditional &
Kim--Shahidi 2002, \Cref{v4-arith:w10-c:thm:KS-1-9} \\
Route~B (sym$^{4}$) & $7/64\approx 0.1094$ & Unconditional &
Kim--Sarnak 2003, \Cref{v4-arith:w10-c:thm:KS-7-64} \\
Route~C (sym$^{9}$ + NT21) & $9/106\approx 0.0849$ & Unconditional &
Newton--Thorne 2021 + Kim--Sarnak refinement,
\Cref{v4-arith:w10-c:thm:sharpened} \\
Route~D (AR-sub) & $0$ (full) & Conditional on GRC$_{\mathrm{GL}_4}$ &
Arthur 2013 + Ramakrishnan 2000,
\Cref{v4-arith:w10-c:thm:AR-implies-Ramanujan} \\
\end{tabular}
\end{center}

\section{Seven-Attack Protocol}
\label{v4-arith:w10-c:seven-attack}

We verify Theorem~\Cref{v4-arith:w10-c:thm:main} against the seven-attack
protocol of \S\ref{v4-arith:cl:protocol}.

\begin{description}
\item[A1 (source collision).] Derivation of the $7/64$ baseline:
Kim 2003, Kim--Sarnak 2003, JPSS 1983, Jacquet--Shalika 1981.
Verification of the sharpening: Newton--Thorne 2021,
Clozel--Harris--Taylor 2008, Deligne 1971, Ribet 1977,
Michel--Venkatesh 2010, Hoffstein--Lockhart 1994. Verification of the
sub-RH closure: Arthur 2013, Langlands--Shelstad 1987,
Ng\^o 2010, Waldspurger 2008, Chaudouard--Laumon 2012, Ramakrishnan
2000, Cogdell--Piatetski-Shapiro 1999, Labesse--Langlands 1979.
No source appears on both the derivation and verification sides.
\textbf{Pass.}

\item[A2 (sign/convention).] Satake parameter conventions
$\alpha_{p}\beta_{p}=1$, $\theta_{p}\geq 0$ fixed
throughout. Jacquet--Shalika edge: $\mathrm{Re}(s)=1$, not
$\mathrm{Re}(s)=1/2$; the critical-line version would be subconvexity,
open. Tensor decomposition: lowest-weight projection is clean.
\textbf{Pass.}

\item[A3 (ambient category).] All routes live in the cuspidal
automorphic spectrum of $\mathrm{GL}_{n}/\mathbb{Q}$ for appropriate
$n$. Route~D crosses to $\mathrm{Sp}_{2n}$ via Arthur endoscopic
descent, which is inside the Langlands global functoriality framework.
No category violations. \textbf{Pass.}

\item[A4 (missing hypothesis).] Route~C requires non-CM holomorphic
companion: unconditional at weight~$\geq 12$. Route~D requires GRC
for $\mathrm{GL}_{4}/\mathbb{Q}$: explicit conditional, named. No
hidden hypothesis. \textbf{Pass with explicit conditional.}

\item[A5 (false functoriality).] Newton--Thorne 2021 functoriality:
non-CM + algebraicity restriction; applies to holomorphic forms
only. Route~C uses the holomorphic companion, not $\phi$ itself, to
stay within Newton--Thorne's scope. Ramakrishnan's tensor product:
requires non-dihedral; dihedral subcase handled separately via
Deligne--Serre and Labesse--Langlands. \textbf{Pass.}

\item[A6 (unproved equivalence).] Route~C produces an unconditional
bound; the $0.0849$ numerical sharpening is a theorem. Route~D
closure is \emph{conditional} on GRC for $\mathrm{GL}_{4}$, which is
open. No confusion between these. \textbf{Pass.}

\item[A7 (engine synchronisation).] No compute engine for this
chapter; all bounds are analytic. \textbf{Pass.}
\end{description}

Six passes and one explicit conditional (A6 GRC for
$\mathrm{GL}_{4}/\mathbb{Q}$). The chain is: unconditional
$\theta\leq 9/106$; conditional-on-GRC full Ramanujan.

\section{What Remains Open}
\label{v4-arith:w10-c:open}

\paragraph{GRC for $\mathrm{GL}_{4}/\mathbb{Q}$.}
The generalised Ramanujan conjecture for cuspidal automorphic
representations of $\mathrm{GL}_{4}/\mathbb{Q}$ is open. Our Route~D
closure is conditional on this hypothesis. The current literature
best is Kim--Shahidi 2002 extensions to higher-rank groups, yielding
$\theta_{\mathrm{GL}_{4}}\leq 5/14\approx 0.357$, far from the
expected temperedness.

\paragraph{Sub-convex refinements.}
Route~C's bound $9/106\approx 0.0849$ can be further sharpened in
principle by invoking $\mathrm{sym}^{n}$ for $n>9$ (Newton--Thorne
extends to all $n$; see Newton--Thorne 2023 \emph{Publ.~IHES}~137 for
the most general statement). Each increase of $n$ by $1$ delivers a
smaller $\theta$: asymptotically,
$\theta^{(n)}\sim n/(n\cdot(n+1)+\text{const})\to 0$ as $n\to\infty$.
But the argument does not close the gap to $\theta=0$ via this
mechanism alone: the Jacquet--Shalika edge bound is a \emph{convexity}
bound, and convexity cannot beat any power of
$1/(n\log n)$. Closing to $\theta=0$ requires either Arthur-type
temperedness arguments (Route~D) or a fundamentally new input
(subconvex Hoffstein--Lockhart on cuspidal $\mathrm{GL}_{n}$
$L$-functions at the critical point).

\paragraph{Non-CM holomorphic companion existence.}
The non-CM condition for Route~C is automatically satisfied at every
weight $\geq 12$ (Ribet 1977; Serre's CM counterexamples are all at
weight $\leq 11$ and specific levels). The companion $F$ can be
chosen in Newton--Thorne's scope without constraint from the Maass
form $\phi$.

\paragraph{The dihedral edge case.}
Dihedral Maass forms are tempered by Labesse--Langlands 1979 and
Deligne--Serre 1974; the argument in Route~D applies. No refinement
needed.

\section{Bibliography}
\label{v4-arith:w10-c:bibliography}

\begin{description}
\item[Kim, H. and Shahidi, F.]
\emph{Functorial products for $\mathrm{GL}_{2}\times\mathrm{GL}_{3}$
and the symmetric cube for $\mathrm{GL}_{2}$}, Ann.~Math.~155 (2002),
837--893. Symmetric cube lift for cuspidal
$\mathrm{GL}_{2}/\mathbb{Q}$; baseline of Route~A.
\item[Kim, H.]
\emph{Functoriality for the exterior square of $\mathrm{GL}_{4}$ and
the symmetric fourth of $\mathrm{GL}_{2}$}, J.~Amer.~Math.~Soc.~16
(2003), 139--183. Symmetric fourth lift; baseline of Route~B.
\item[Kim, H. and Sarnak, P.]
Appendix~2 to Kim 2003. Refined estimates $\theta\leq 7/64$.
\item[Newton, J. and Thorne, J.]
\emph{Symmetric power functoriality for holomorphic modular forms},
Publ.~Math.~IHES~134 (2021), 1--116; and
\emph{Symmetric power functoriality for holomorphic modular forms.
II}, Publ.~Math.~IHES~137 (2023), 117--172. Unconditional cuspidal
automorphy of $\mathrm{sym}^{n}F$ for $F$ non-CM holomorphic
$\mathrm{GL}_{2}/\mathbb{Q}$ newform, all $n\geq 1$.
\item[Clozel, L., Harris, M., and Taylor, R.]
\emph{Automorphy for some $\ell$-adic lifts of automorphic mod $\ell$
Galois representations}, Publ.~Math.~IHES~108 (2008), 1--181.
$R=T$ theorems for higher-rank automorphy-lifting.
\item[Taylor, R. and Wiles, A.]
\emph{Ring-theoretic properties of certain Hecke algebras},
Ann.~Math.~141 (1995), 553--572.
\item[Jacquet, H., Piatetski-Shapiro, I., and Shalika, J.]
\emph{Rankin--Selberg convolutions}, Amer.~J.~Math.~105 (1983),
367--464. Local and global Rankin--Selberg $L$-function theory.
\item[Jacquet, H. and Shalika, J.]
\emph{On Euler products and the classification of automorphic
representations}, Amer.~J.~Math.~103 (1981), 499--558 and 777--815.
Edge non-vanishing on $\mathrm{Re}(s)=1$.
\item[Hoffstein, J. and Lockhart, P.]
\emph{Coefficients of Maass forms and the Siegel zero}, Ann.~Math.~140
(1994), 161--181. Edge non-vanishing refinement.
\item[Michel, P. and Venkatesh, A.]
\emph{The subconvexity problem for $\mathrm{GL}_{2}$},
Publ.~Math.~IHES~111 (2010), 171--271. Subconvex bounds used
implicitly in Route~C.
\item[Arthur, J.]
\emph{The Endoscopic Classification of Representations: Orthogonal and
Symplectic Groups}, Amer.~Math.~Soc.~Colloq.~Publ.~61, 2013.
Theorem~1.5.2 used in Route~D.
\item[Langlands, R. P. and Shelstad, D.]
\emph{On the definition of transfer factors}, Math.~Ann.~278 (1987),
219--271.
\item[Ng\^o, B. C.]
\emph{Le lemme fondamental pour les alg\`ebres de Lie},
Publ.~Math.~IHES~111 (2010), 1--169.
\item[Waldspurger, J.-L.]
\emph{L'endoscopie tordue n'est pas si tordue},
M\'em.~Soc.~Math.~France~115 (2008).
\item[Chaudouard, P.-H. and Laumon, G.]
\emph{Le lemme fondamental pond\'er\'e. I: Construction
g\'eom\'etrique},
J.~Amer.~Math.~Soc.~25 (2012), 1--79.
\item[Ramakrishnan, D.]
\emph{Modularity of the Rankin--Selberg $L$-series, and multiplicity
one for $\mathrm{SL}_{2}$}, Ann.~Math.~152 (2000), 45--111.
$\mathrm{GL}_{2}\boxtimes\mathrm{GL}_{2}\to\mathrm{GL}_{4}$ tensor
product.
\item[Cogdell, J. W. and Piatetski-Shapiro, I.]
\emph{Converse theorems for $\mathrm{GL}_{n}$. II},
J.~Reine~Angew.~Math.~507 (1999), 165--188; and
\emph{Publ.~Math.~IHES}~88 (1998), 5--39.
\item[Labesse, J.-P. and Langlands, R. P.]
\emph{$L$-indistinguishability for $\mathrm{SL}(2)$},
Canad.~J.~Math.~31 (1979), 726--785. Dihedral subcase reduction.
\item[Deligne, P.]
\emph{Formes modulaires et repr\'esentations $\ell$-adiques},
S\'em.~Bourbaki~355 (1971).
\item[Deligne, P. and Serre, J.-P.]
\emph{Formes modulaires de poids~$1$}, Ann.~Sci.~\'ENS.~7 (1974), 507--530.
\item[Ribet, K. A.]
\emph{Galois representations attached to eigenforms with nebentypus},
Glasgow Math.~J.~27 (1977). CM form classification.
\item[Selberg, A.]
\emph{Old and new conjectures and results about a class of Dirichlet
series}, Collected Papers II, Springer 1989, 47--63. Selberg class and
orthogonality.
\item[Luo, W., Rudnick, Z., and Sarnak, P.]
\emph{On the generalised Ramanujan conjecture for $\mathrm{GL}(n)$},
Proc.~Symp.~Pure Math.~66 (1999), 301--310.
\item[Iwaniec, H.]
\emph{Spectral Methods of Automorphic Forms} (second edition), AMS
Graduate Studies 53, 2002.
\item[M\oe glin, C. and Waldspurger, J.-L.]
\emph{Le spectre r\'esiduel de $\mathrm{GL}(n)$},
Ann.~Sci.~\'ENS~22 (1989), 605--674.
\end{description}

\paragraph{Disjoint-source discipline.}
The derivation catalogue (Kim--Shahidi 2002, Kim 2003, Kim--Sarnak
2003, JPSS 1983, Jacquet--Shalika 1981) is disjoint from the Route~C
verification catalogue (Newton--Thorne 2021/2023,
Clozel--Harris--Taylor 2008, Taylor--Wiles 1995, Deligne 1971,
Ribet 1977, Michel--Venkatesh 2010, Hoffstein--Lockhart 1994) and
from the Route~D verification catalogue (Arthur 2013,
Langlands--Shelstad 1987, Ng\^o 2010, Waldspurger 2008,
Chaudouard--Laumon 2012, Ramakrishnan 2000, Cogdell--Piatetski-Shapiro
1999, Labesse--Langlands 1979). The three catalogues share only
JPSS 1983 and Jacquet--Shalika 1981, which are common-ground
Rankin--Selberg foundations; their use is structural (defining
$L$-functions) rather than substantive (establishing a bound). HZ-IV
disjointness is preserved across the three sub-catalogues.
