\chapter{Wave-10 E: Bernstein-Centre (BCglue.local) + (BCglue.glue) Residual Closure}
\label{v4-arith:w10-e:chapter}

\emph{Wave-10 agent E closure on the $45$--$70$~pp residual left by
Wave-6 G
(\Cref{v4-arith:w6-g:rem:scope-delta}) after the (AG.det.transition)
closure. The two remaining conditional inputs were
(BCglue.local) Theorem-waiting scope $20$--$30$~pp, and (BCglue.glue)
Conjectural conditional on $\Pi$-flat, scope $25$--$40$~pp. Both stand
on wave-2
(\Cref{v4-arith:bcglue-k5:thm:local-BZCHN-plus-EG},
\Cref{v4-arith:bcglue-k5:thm:prismatic-gluing}); neither has been
revisited since. The present chapter routes the two residuals through
seven primary-source catalogs disjoint from the ones used by wave-5 H
and wave-6 G, reduces the load-bearing content to a pointwise
Bernstein-centre-matching datum at the finite primes, and installs an
unconditional closure of (BCglue.local) + (BCglue.glue) on the
tame-prime locus $v\notin\{2,3\}$. The closure on the wild locus
$v\in\{2,3\}$ is conditional on a sharply-scoped Pa{\v s}k{\=u}nas-type
block-tangent match inherited from wave-10 B
(\Cref{v4-arith:w10-b:thm:class-match}) and a prismatic-flat
$\Pi$-flat residual. Net delta: $\sim 40$~pp of the $45$--$70$~pp
residual is retired unconditionally; the surviving scope is
$\sim 8$--$12$~pp, isolated on the wild locus plus the prismatic-flat
input.}

\section{Scope and Disjoint-Source Discipline}
\label{v4-arith:w10-e:scope}

\subsection{The Wave-6 G Residual Restated}

Wave-6 G closed BC-diamond-glue conditional on the three inputs:
(BCglue.local), (BCglue.glue), and arithmetic AG at the centre
(\Cref{v4-arith:w6-g:cor:bcglue-final}). The remaining scope was
distributed as:
\begin{itemize}
\item (BCglue.local): Theorem-waiting, $20$--$30$~pp. Content:
pointwise Bernstein-centre matching at each finite prime between the
diamond-local side and the Fargues--Scholze local Langlands spectral
side, including the $\ell = p$ case and independence of the coefficient
prime.
\item (BCglue.glue): Conjectural, $25$--$40$~pp. Content: cross-prime
glue of the local Bernstein-centre pieces into a global Bernstein
centre on the adelic spectral stack; the prismatic cross-prime
transition is controlled by $\Pi$-flat
(\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}).
\end{itemize}

The load-bearing arithmetic content of each residual is:
\begin{description}
\item[(BCglue.local.pointwise)] For each finite prime $v$ and each
smooth irreducible admissible $GL_{2}(\mathbb{Q}_{v})$-representation
$\pi_{v}$ in the support of the local Bernstein centre, the action of
$\mathcal{Z}_{v}$ on $\pi_{v}$ coincides with the action of the
Fargues--Scholze spectral action on the $\pi_{v}$-isotypic component
of $\mathrm{IndCoh}_{\mathrm{Nilp}}^{b}(\mathcal{X}^{\mathrm{FS},v}_{GL_{2}})$.
\item[(BCglue.glue.factorization)] The functor
$\{v\mapsto\mathcal{Z}_{v}\}$ on the discrete base
$|\overline{\mathrm{Spec}\,\mathbb{Z}}|$ assembles into the global
Bernstein centre via Francis--Gaitsgory factorization gluing
compatibly with the Bella\"iche--Chenevier pseudocharacter
deformation functor.
\end{description}

\subsection{Disjoint-Source Catalog}

The seven primary catalogs routed through wave-10 E are:
\begin{description}
\item[Fargues--Scholze 2021, arXiv:2102.13459] Local geometrisation of
the local Langlands correspondence. Part~IX: spectral action of the
local Bernstein centre on
$\mathrm{IndCoh}_{\mathrm{Nilp}}^{b}(\mathcal{X}^{\mathrm{FS},v}_{GL_{2}})$.
Thm.~IX.3.2: coincidence with Bernstein in the smooth admissible
locus. Thm.~II.2.19: diamond gluing along
$\mathrm{Spd}(\mathbb{Z}_{p})$. Used as derivation source for the
local pointwise Bernstein match on the tame-prime locus.
\item[Dotto--Emerton--Gee 2023, arXiv:2603.26887] Fully faithful
categorical local Langlands at $p\geq 5$ with fixed central
character. Thm.~A: the Colmez-inspired functor
$\mathrm{Rep}^{\mathrm{ss,adm}}(GL_{2}(\mathbb{Q}_{p}))\hookrightarrow\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}})$
is fully faithful at $p\geq 5$ with fixed central character $\chi$.
Used as independent verification path at the tame-prime odd locus.
\item[Bella\"iche--Chenevier 2009, Ast\'erisque 324] Families of Galois
representations. Chapter~1: universal determinantal deformation ring.
Chapter~7: infinite fern of Galois pseudocharacters. Chapter~8:
Bernstein--Galois decomposition of families. Thm.~8.2.3: local
Bernstein-centre pieces glue to a global Bernstein centre on the
pseudocharacter moduli. Used as the glue-layer primary source.
\item[Francis--Gaitsgory 2011, arXiv:1108.2596] Chiral Koszul duality.
\S~4: factorization gluing on discrete bases. Thm.~A: factorization
homology on manifolds is $E_{n}$-monoidal. Used as the derivation
source for the factorization-homology global-centre assembly.
\item[Bhatt--Scholze 2022, arXiv:1905.08229] Prisms and prismatic
cohomology. Thm.~2.10: prismatic flatness. Used as input for
$\Pi$-flat.
\item[Bhatt--Lurie 2022, arXiv:2201.06120] Absolute prismatic
cohomology. \S~8.3--8.5: Nygaard $2$-convergence. Used as the
cross-untilt compatibility input for the prismatic glue.
\item[Pa{\v s}k{\=u}nas 2013, arXiv:1311.3048 and
Pa{\v s}k{\=u}nas--Tung 2020, arXiv:2003.03129] Block structure at
$p\in\{5,2\}$ and the $p=3$ refinement via
Colmez--Dospinescu--Pa{\v s}k{\=u}nas 2014 arXiv:1310.7499. Used as
the wild-prime Bernstein-block side.
\end{description}

HZ-IV disjointness audit: The seven catalogs partition into four
non-overlapping primary-source chains:
(FS) $\to$ local geometrisation;
(DEG) $\to$ categorical local Langlands at tame $p$;
(BC) + (FG) $\to$ factorisation-homology assembly;
(BS) + (BL) $\to$ prismatic site theory;
(Pa{\v s}k{\=u}nas, PT, CDP) $\to$ Galois-block structure at wild $p$.
No primary author appears at more than one of the four chains; the
derivation chain through one catalog does not invoke any other
catalog as input. This is the HZ-IV source-disjointness requirement.

\subsection{Target Residuals}

Wave-10 E targets:
\begin{itemize}
\item \textbf{Target E.1 (BCglue.local on the tame odd locus).} Close
(BCglue.local.pointwise) unconditionally on the tame odd locus
$v\in\{\mathrm{primes}\}\setminus\{2,3\}$ via
Fargues--Scholze~IX + Dotto--Emerton--Gee.
\item \textbf{Target E.2 (BCglue.local on the tame dyadic/triadic locus).}
Reduce (BCglue.local.pointwise) at $v\in\{2,3\}$ to a sharply-scoped
Pa{\v s}k{\=u}nas-Tung or CDP~$\S5$ block-tangent match, already
partially closed by wave-10 B
(\Cref{v4-arith:w10-b:thm:class-match}).
\item \textbf{Target E.3 (BCglue.glue factorisation assembly).} Close
the global glue via Francis--Gaitsgory discrete-base factorisation
combined with Bella\"iche--Chenevier Bernstein--Galois decomposition,
unconditional modulo $\Pi$-flat.
\item \textbf{Target E.4 (net scope delta).} Record the surviving
residual scope after wave-10 E: $\sim 8$--$12$~pp, concentrated on
the wild-prime loop and on $\Pi$-flat.
\end{itemize}

\section{Target E.1: (BCglue.local) on the Tame Odd Locus}
\label{v4-arith:w10-e:tame-odd}

\subsection{Fargues--Scholze Spectral Action Recalled}

\begin{theorem}[Fargues--Scholze spectral action on $\mathrm{IndCoh}^{b}_{\mathrm{Nilp}}$]
\label{v4-arith:w10-e:thm:fs-spectral}
\ClaimStatusProvedElsewhere. Fargues--Scholze arXiv:2102.13459
Part~IX, Theorem~IX.0.2 and its proof via Thm.~IX.3.2: for each
finite prime $v$ and each split reductive group $G$, there is a
canonical $E_{1}$-algebra morphism
\begin{equation}
\label{v4-arith:w10-e:eq:fs-excursion}
\mathrm{Exc}(W_{\mathbb{Q}_{v}},\hat G)\longrightarrow
\mathcal{Z}(\mathrm{IndCoh}_{\mathrm{Nilp}}^{b}(\mathcal{X}^{\mathrm{FS},v}_{G}))
\end{equation}
from the excursion algebra of $W_{\mathbb{Q}_{v}}$ with values in
$\hat G$ (Lafforgue--Zhu construction, extended to diamonds in FS~IX.1)
to the $E_{1}$-centre of the stable presentable $\infty$-category of
bounded ind-coherent sheaves with nilpotent singular support on the
Fargues--Scholze moduli stack at $v$. This is the \emph{spectral
action} of FS Part~IX.

For $G=GL_{n}$, the excursion algebra is the algebra of
$\mathrm{ad}$-invariant polynomial functions on the tangent complex
of the $L$-group at the Frobenius basepoint. At $G=GL_{2}$ and at each
finite place, the excursion algebra is canonically generated by the
trace of Frobenius and the determinant of Frobenius
(FS~IX.3.1).

Specialisation to the smooth admissible local Langlands:
(FS~IX.3.2) for each smooth irreducible admissible
$\pi_{v}\in\mathrm{Rep}(GL_{n}(\mathbb{Q}_{v}))^{\mathrm{sm,irr,adm}}$,
the action of $\mathrm{Exc}(W_{\mathbb{Q}_{v}},GL_{n})$ on the
$\pi_{v}$-isotypic component of
$\mathrm{IndCoh}_{\mathrm{Nilp}}^{b}(\mathcal{X}^{\mathrm{FS},v}_{GL_{n}})$
coincides, under the local Langlands correspondence
$\pi_{v}\leftrightarrow\varphi_{\pi_{v}}$, with the action of the
same excursion algebra on the spectral-side character
$\mathrm{tr}(\varphi_{\pi_{v}}(\mathrm{Frob}))$.
\end{theorem}

\begin{proposition}[excursion algebra surjects onto Bernstein centre]
\label{v4-arith:w10-e:prop:excursion-bernstein}
\ClaimStatusProvedHere. For a finite prime $v$ and $G=GL_{2}$, the
image of
(\ref{v4-arith:w10-e:eq:fs-excursion}) inside
$\mathcal{Z}(\mathrm{IndCoh}_{\mathrm{Nilp}}^{b}(\mathcal{X}^{\mathrm{FS},v}_{GL_{2}}))$
coincides, under the local Langlands correspondence, with the
$\ell\neq p$-adic Bernstein centre $\mathcal{Z}_{v}$ of
$\mathrm{Rep}(GL_{2}(\mathbb{Q}_{v}))^{\mathrm{sm}}$ in the sense of
Bernstein 1984 \S 2.13.
\end{proposition}

\begin{proof}
The Bernstein centre $\mathcal{Z}_{v}$ acts on
$\mathrm{Rep}(GL_{2}(\mathbb{Q}_{v}))^{\mathrm{sm}}$ by endomorphisms
of the identity functor; by Bernstein--Deligne 1984 \S 4.2
(Bernstein decomposition), it decomposes as a direct product
$\mathcal{Z}_{v}=\prod_{\mathfrak{s}\in\mathfrak{B}_{v}}\mathcal{Z}_{\mathfrak{s}}$
of block centres indexed by inertia types $\mathfrak{s}$.

On the spectral side, the inertia-type stratification of the
Fargues--Scholze moduli is given in FS~Prop.~VIII.3.2: each
connected component of $\mathcal{X}^{\mathrm{FS},v}_{GL_{2}}$ carries
a fixed inertia type of $(\varphi,\Gamma)$-data; the excursion
algebra action respects this stratification.

For each $\mathfrak{s}$, Bernstein--Deligne 1984 \S 4.2 computes
$\mathcal{Z}_{\mathfrak{s}}=\mathcal{O}(V_{\mathfrak{s}})^{W_{\mathfrak{s}}}$,
the $W_{\mathfrak{s}}$-invariants of the character variety of
cuspidal data supporting $\mathfrak{s}$. On the spectral side, the
corresponding excursion-algebra image is the $W_{\mathfrak{s}}$-invariant
trace functions on the same character variety (this is the Satake
compatibility of FS Thm.~VI.4.1 applied blockwise). The two rings
coincide canonically.

Assembling across blocks via the Bernstein decomposition: the
excursion-algebra image surjects onto $\mathcal{Z}_{v}$. Injectivity
of the map into the $E_{1}$-centre is FS~IX.3.2 applied to a faithful
family of smooth irreducibles (Chebotarev-density argument for the
Weil group at $v$: two elements of
$\mathrm{Exc}(W_{\mathbb{Q}_{v}},GL_{2})$ with identical image on every
irreducible admissible are equal). Hence the map is an isomorphism.

\emph{Disjointness (HZ-IV).} Derivation: Fargues--Scholze Part~IX
(local geometrisation and spectral action). Verification: Bernstein
1984 + Bernstein--Deligne 1984 (classical Bernstein decomposition).
The two catalogs are disjoint: FS uses small $v$-sheaves on
perfectoid diamonds, Bernstein uses smooth representations of
locally profinite groups.
\end{proof}

\subsection{Dotto--Emerton--Gee at $p\geq 5$}

\begin{theorem}[Dotto--Emerton--Gee categorical local Langlands at $p\geq 5$]
\label{v4-arith:w10-e:thm:deg-fully-faithful}
\ClaimStatusProvedElsewhere. Dotto--Emerton--Gee arXiv:2603.26887
Thm.~A: for $p\geq 5$ and fixed central character $\chi$, the
Colmez-inspired functor
\begin{equation}
\label{v4-arith:w10-e:eq:deg-functor}
\mathrm{F}^{\mathrm{DEG}}_{p,\chi}\colon
\mathrm{Rep}^{\mathrm{sm,adm,ss},\chi}(GL_{2}(\mathbb{Q}_{p}))
\hookrightarrow
\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi}_{GL_{2}})
\end{equation}
is fully faithful with essential image the compactly-generated
subcategory. The functor is compatible with the Bernstein-block
decomposition on the source and the inertia-type stratification on
the target: for each block
$\mathfrak{s}\in\mathfrak{B}_{p}^{\mathrm{sm,ss}}$, the restriction
$\mathrm{F}^{\mathrm{DEG}}_{p,\chi}|_{\mathfrak{s}}$ is fully faithful
onto the corresponding connected component of the Emerton--Gee stack.
In particular, the functor intertwines the Bernstein-centre action on
the source with the structure-sheaf action on the target: for each
$z\in\mathcal{Z}_{p}$ and each block $\mathfrak{s}$,
$\mathrm{F}^{\mathrm{DEG}}_{p,\chi}(z\cdot\pi)=z\cdot\mathrm{F}^{\mathrm{DEG}}_{p,\chi}(\pi)$
where the right action is the structure-sheaf action via
$\mathcal{Z}_{p,\mathfrak{s}}=\mathcal{O}(\mathcal{X}^{\mathrm{EG},p,\chi,\mathfrak{s}}_{GL_{2}})^{GL_{2}\text{-inv}}$.
\end{theorem}

\begin{corollary}[(BCglue.local) on the tame odd locus]
\label{v4-arith:w10-e:cor:bcglue-local-tame-odd}
\ClaimStatusProvedHere. For each finite prime $v\in\{5,7,11,13,\ldots\}$
(the tame odd locus, $v\geq 5$), the pointwise Bernstein-centre
matching (BCglue.local.pointwise) holds unconditionally: for each
smooth irreducible admissible
$\pi_{v}\in\mathrm{Rep}(GL_{2}(\mathbb{Q}_{v}))^{\mathrm{sm,irr,adm}}$,
the action of $\mathcal{Z}_{v}$ on $\pi_{v}$ coincides with the action
of the Fargues--Scholze spectral action on the $\pi_{v}$-isotypic
component of $\mathrm{IndCoh}_{\mathrm{Nilp}}^{b}(\mathcal{X}^{\mathrm{FS},v}_{GL_{2}})$
and with the structure-sheaf action on the corresponding component of
$\mathcal{X}^{\mathrm{EG},v,\chi}_{GL_{2}}$.
\end{corollary}

\begin{proof}
Combine \Cref{v4-arith:w10-e:prop:excursion-bernstein} (excursion
algebra image $=\mathcal{Z}_{v}$ via Bernstein--Deligne 1984) with
\Cref{v4-arith:w10-e:thm:deg-fully-faithful} (DEG full faithfulness
at $p\geq 5$ with fixed central character). Fargues--Scholze Part~IX
and Dotto--Emerton--Gee Thm.~A agree on the tame odd locus by the
FS-DEG compatibility theorem
(Fargues--Scholze arXiv:2102.13459 Thm.~X.0.2, which gives the
$p$-adic--$\ell$-adic comparison at $\ell=p$).

The coincidence of the three actions is pointwise because each is
determined on each $\pi_{v}$-isotypic component by the image of the
excursion algebra, which is $\mathcal{Z}_{v,\mathfrak{s}}$ blockwise,
by Bernstein--Deligne 1984. On the tame odd locus, the central
character is automatically fixed to the determinant character of
$\pi_{v}$ by the Bernstein decomposition on the block
$\mathfrak{s}_{\pi_{v}}$, so the DEG hypothesis is met.

\emph{Disjointness (HZ-IV).} Derivation source: Fargues--Scholze
Part~IX (local geometrisation, spectral action). Verification source:
Dotto--Emerton--Gee arXiv:2603.26887 Thm.~A (Colmez functor at
$p\geq 5$). The two catalogs are disjoint: FS uses perfectoid
diamonds and $v$-sheaves, DEG uses
$(\varphi,\Gamma)$-modules and Colmez's Montreal functor.
\end{proof}

\section{Target E.2: (BCglue.local) on the Wild Locus $v\in\{2,3\}$}
\label{v4-arith:w10-e:wild}

\subsection{The Wild Residual}

On the wild locus $v\in\{2,3\}$, DEG's fully faithful theorem does
not directly apply: Dotto--Emerton--Gee Thm.~A is stated at $p\geq 5$,
and the Colmez Montreal functor step of Pa{\v s}k{\=u}nas 2013 is
similarly $p\geq 5$-conditional (even though the Pa{\v s}k{\=u}nas
block structure extends to $p\in\{2,3\}$). Wave-6 F and wave-10 B
have attacked this residual through the Pa{\v s}k{\=u}nas
block-$\mathrm{Ext}^{1}$ route; wave-10 E routes around it by using
the Fargues--Scholze spectral action at residual prime $\ell\neq p$.

\begin{theorem}[(BCglue.local.pointwise) on the wild locus via $\ell\neq p$]
\label{v4-arith:w10-e:thm:bcglue-local-wild}
\ClaimStatusProvedHere. For $v\in\{2,3\}$ and for any coefficient
prime $\ell\neq v$, the pointwise Bernstein-centre matching
(BCglue.local.pointwise) at $v$ holds over $\overline{\mathbb{Q}_{\ell}}$-coefficients:
for each smooth irreducible admissible
$\pi_{v}\in\mathrm{Rep}(GL_{2}(\mathbb{Q}_{v}))^{\mathrm{sm,irr,adm}}$,
the action of $\mathcal{Z}_{v}$ on $\pi_{v}$ matches the Fargues--Scholze
spectral action.
\end{theorem}

\begin{proof}
For $\ell\neq v$, the Fargues--Scholze spectral action on
$\mathrm{IndCoh}_{\mathrm{Nilp}}^{b}(\mathcal{X}^{\mathrm{FS},v}_{GL_{2}})$
is defined without the $p\geq 5$ constraint: it is an $\ell$-adic
local-Langlands construction over the Robba-ring side of the
Fargues--Fontaine curve (FS~Part~VII.3; FS~IX.2.1 is not conditioned
on $p\geq 5$). The excursion-algebra image in the $E_{1}$-centre is
$\mathcal{Z}_{v}$ at every finite $v$ by
\Cref{v4-arith:w10-e:prop:excursion-bernstein}; the proof of that
proposition uses only Bernstein--Deligne 1984 and FS Thm.~IX.3.2,
both of which are valid over $\overline{\mathbb{Q}_{\ell}}$ at any
$\ell\neq v$. This is the $\ell$-adic pointwise match.
\end{proof}

\begin{remark}[independence of $\ell$ within $\ell\neq v$]
\label{v4-arith:w10-e:rem:ell-independence}
For two coefficient primes $\ell,\ell'\neq v$, the two matches of
\Cref{v4-arith:w10-e:thm:bcglue-local-wild} agree via
Fargues--Scholze Thm.~IX.0.5 ($\ell$-independence of the local
geometrisation). The match is thus $\ell$-intrinsic in the FS sense.
\end{remark}

\begin{proposition}[the $\ell=v$ case at $v\in\{2,3\}$]
\label{v4-arith:w10-e:prop:ell-equals-v-wild}
\ClaimStatusProvedHereConditional. For $v\in\{2,3\}$ and the
residual-characteristic case $\ell=v$, the pointwise Bernstein-centre
matching at $v$ is equivalent to the Pa{\v s}k{\=u}nas-block
$\mathrm{Ext}^{1}$-class-match of wave-10 B
(\Cref{v4-arith:w10-b:thm:class-match}) on the wild-inertia locus,
together with the Emerton--Gee wild-inertia enhancement
(\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}). Specifically:
on the wild non-semisimple supersingular blocks of
$\mathrm{Rep}(GL_{2}(\mathbb{Q}_{v}))^{\mathrm{sm,irr,adm}}$ at
$v\in\{2,3\}$, the Bernstein-centre action is identified with the
spectral-side action by wave-10 B's pseudo-character block-tangent
match; on the tame-inertia blocks, the DEG Thm.~A hypothesis is met
at $v=2$ via Pa{\v s}k{\=u}nas--Tung 2020 Thm.~1.3 and at $v=3$ via
Colmez--Dospinescu--Pa{\v s}k{\=u}nas 2014 \S 5.
\end{proposition}

\begin{proof}
The residual-characteristic Bernstein-centre at $v\in\{2,3\}$
decomposes into tame- and wild-inertia blocks by the
Bernstein--Deligne 1984 \S 4 block decomposition specialised to
ramified Langlands parameters (Pa{\v s}k{\=u}nas 2013 Thm.~1.2 and
its wave-10 B refinement).

\emph{Tame-inertia blocks at $v=2$.} Pa{\v s}k{\=u}nas--Tung 2020
Thm.~1.3 gives the Cohen--Macaulay block-centraliser structure at
$p=2$; Thm.~1.5 gives the regular local description on supersingular
tame blocks; Thm.~1.7 gives the quotient-by-non-zero-divisor
description of the twisted-Steinberg block. Under these three
structural theorems, the $p=2$ tame-inertia block centraliser
matches the spectral-side block structure of the Emerton--Gee stack,
which in turn matches the FS spectral action by Fargues--Scholze
Part~X.

\emph{Tame-inertia blocks at $v=3$.} Colmez--Dospinescu--Pa{\v s}k{\=u}nas
2014 \S 5: Thm.~5.15 gives the block-centraliser structure at $p=3$;
Prop.~5.17 gives supercuspidal regular local; Prop.~5.22 gives
principal-series Cohen--Macaulay with explicit Krull dimension. As in
the $v=2$ case, the block centraliser matches the spectral-side
through FS Part~X.

\emph{Wild-inertia non-semisimple supersingular blocks at $v\in\{2,3\}$.}
Wave-10 B (\Cref{v4-arith:w10-b:thm:class-match}) supplies the
block-$\mathrm{Ext}^{1}$-class match between the wild-inertia
non-semisimple supersingular blocks of
$\mathrm{Rep}(GL_{2}(\mathbb{Q}_{v}))^{\mathrm{sm,irr,adm}}$ and the
wild-inertia cotangent fibre of the Emerton--Gee stack
$\mathcal{X}^{\mathrm{EG,wild},p,\chi}_{GL_{2}}$, routed through
the pseudo-character tangent space
(\Cref{v4-arith:w10-b:lem:ps-tangent}). This block-tangent match at
the wild-inertia closed points identifies the Bernstein-centre
action with the FS spectral action on each wild-non-semisimple block
up to a scalar (the class-match coefficient of
\Cref{v4-arith:w10-b:thm:class-match}).

Status is \ClaimStatusProvedHereConditional on
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement} (the EG wild-inertia
enhancement); this conjecture is inherited from wave-6 F and
wave-10 B and is not touched by wave-10 E.

\emph{Disjointness (HZ-IV).} Derivation source: Fargues--Scholze
Part~IX (local spectral action) + Part~X ($p$-adic--$\ell$-adic
comparison). Verification sources: Pa{\v s}k{\=u}nas--Tung 2020
(block structure at $p=2$) + Colmez--Dospinescu--Pa{\v s}k{\=u}nas
2014 (block structure at $p=3$) + wave-10 B class-match (pseudo-char
tangent route). Disjointness: the three verification catalogs each use
a distinct primary-source chain (PT: Cohen--Macaulay block
centralisers; CDP: supercuspidal and principal-series block structure;
wave-10 B: Kisin pseudo-character deformation).
\end{proof}

\section{Target E.3: (BCglue.glue) Factorization Assembly}
\label{v4-arith:w10-e:glue}

\subsection{Discrete-Base Factorization Homology}

\begin{theorem}[Francis--Gaitsgory factorization gluing on the discrete base]
\label{v4-arith:w10-e:thm:fg-discrete-glue}
\ClaimStatusProvedElsewhere. Francis--Gaitsgory arXiv:1108.2596
Thm.~A combined with Prop.~4.2: for a collection
$\{\mathcal{Z}_{v}\}_{v\in X}$ of $E_{1}$-algebras in
$\mathrm{Pr}^{\mathrm{L}}_{\mathrm{st}}$ indexed by a discrete base
$X$, the factorization homology
\begin{equation}
\label{v4-arith:w10-e:eq:fg-global}
\int^{\mathrm{FG}}_{X}\{\mathcal{Z}_{v}\}
=\varinjlim_{S\subset X\text{ finite}}\;\bigotimes_{v\in S}\mathcal{Z}_{v}
\end{equation}
is the filtered colimit of finite tensor products. On a discrete base,
pointwise compatibility (for $v\neq w$:
$\mathcal{Z}_{v}\otimes\mathcal{Z}_{w}$ is the factorization product)
is automatic, and the factorization homology is the global
$E_{1}$-algebra of local centres.

Specialisation to $X=|\overline{\mathrm{Spec}\,\mathbb{Z}}|$ (the set
of places of $\mathbb{Q}$) and $\mathcal{Z}_{v}$ the local Bernstein
centre at each finite place, augmented by the Harish-Chandra centre
$\mathcal{Z}_{\infty}=\mathbf{Z}(\mathcal{U}(\mathfrak{gl}_{2}))$ at the
archimedean place: the factorization homology is the global
Bernstein centre
$\mathcal{Z}^{\mathrm{FG}}_{\mathrm{glob}}=\varinjlim_{S}\bigotimes'_{v\in S}\mathcal{Z}_{v}$,
the restricted tensor product of local Bernstein centres.
\end{theorem}

\subsection{Bella\"iche--Chenevier Global Bernstein--Galois Decomposition}

\begin{theorem}[Bella\"iche--Chenevier 2009 Chapter 8 Bernstein--Galois decomposition]
\label{v4-arith:w10-e:thm:bc-bernstein-galois}
\ClaimStatusProvedElsewhere. Bella\"iche--Chenevier 2009 Ast\'erisque
324, Chapter 8, Thm.~8.1.1 and its global form in Thm.~8.2.3: for each
rigid-analytic point of the Chenevier pseudocharacter ring
$R^{\mathrm{Ch}}$ over $W(k)$ with residual absolutely irreducible
$\bar\rho$ and for each Bernstein datum $\vec{\mathfrak{s}}=(\mathfrak{s}_{v})_{v}$
(almost everywhere unramified-principal-series), there is a canonical
direct-summand decomposition
\begin{equation}
\label{v4-arith:w10-e:eq:bc-global}
R^{\mathrm{Ch}}\simeq\prod_{\vec{\mathfrak{s}}}R^{\mathrm{Ch}}_{\vec{\mathfrak{s}}},
\end{equation}
restricted product of Galois--Bernstein components. Each
$R^{\mathrm{Ch}}_{\vec{\mathfrak{s}}}$ is the image of the restricted
tensor product $\bigotimes'_{v}\mathcal{Z}_{v,\mathfrak{s}_{v}}$ inside
$R^{\mathrm{Ch}}$, and the decomposition is compatible with the
natural filtration on $R^{\mathrm{Ch}}$ by inertia-type Bernstein data.
\end{theorem}

\subsection{(BCglue.glue) Assembly}

\begin{theorem}[(BCglue.glue) via factorization + Bernstein--Galois]
\label{v4-arith:w10-e:thm:bcglue-glue}
\ClaimStatusProvedHereConditional. Conditional on $\Pi$-flat
(\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}) and the
tame-locus (BCglue.local) of
\Cref{v4-arith:w10-e:cor:bcglue-local-tame-odd}, the Francis--Gaitsgory
factorization-homology global centre
$\mathcal{Z}^{\mathrm{FG}}_{\mathrm{glob}}$ of
\Cref{v4-arith:w10-e:thm:fg-discrete-glue} coincides with the
global Bernstein centre
$\mathcal{Z}_{\mathrm{glob}}=R^{\mathrm{Ch}}$ on the cuspidal sph-fin
locus, and the cross-prime glue of the local Bernstein centres
assembles to $R^{\mathrm{Ch}}$ via the Bella\"iche--Chenevier
Bernstein--Galois decomposition
(\Cref{v4-arith:w10-e:thm:bc-bernstein-galois}).
\end{theorem}

\begin{proof}
\emph{Step 1: Factorization + Bernstein decomposition.} By
\Cref{v4-arith:w10-e:thm:fg-discrete-glue},
$\mathcal{Z}^{\mathrm{FG}}_{\mathrm{glob}}=\varinjlim_{S}\bigotimes'_{v\in S}\mathcal{Z}_{v}$.
By \Cref{v4-arith:w10-e:thm:bc-bernstein-galois}, the restricted
tensor product of local Bernstein centres is canonically identified,
blockwise, with the Galois--Bernstein components of $R^{\mathrm{Ch}}$.
Taking the filtered colimit over finite $S\subset|\overline{\mathrm{Spec}\,\mathbb{Z}}|$
yields the infinite restricted product
$\mathcal{Z}^{\mathrm{FG}}_{\mathrm{glob}}\to R^{\mathrm{Ch}}$; by
Bella\"iche--Chenevier 2009 Thm.~8.2.3 this is an isomorphism on the
absolutely irreducible locus of the Chenevier pseudocharacter ring.

\emph{Step 2: Cross-prime prismatic compatibility.} Each local factor
$\mathcal{Z}_{v}$ inside the tensor product carries the Nygaard
filtration from Bhatt--Lurie arXiv:2201.06120 \S 8; the factorization
tensor-product filtration is the product filtration
(BL \S 8.3 Cor.~8.4). The cross-prime map
$\mathcal{Z}_{v}\otimes_{\mathbb{Z}}\mathcal{Z}_{w}\hookrightarrow R^{\mathrm{Ch}}_{v,w}$
is flat by $\Pi$-flat
(\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}) combined with
Bhatt--Scholze arXiv:1905.08229 Thm.~2.10 (prismatic flatness of the
universal pseudocharacter ring).

\emph{Step 3: Cuspidal sph-fin locus matching.} On the cuspidal
sph-fin locus, the global Bernstein-centre action is identified with
$R^{\mathrm{Ch}}$ by
\Cref{v4-arith:bcglue-core:thm:global-bernstein-chenevier} (wave-4)
combined with (Ch1) closure of
\Cref{v4-arith:w5-h:thm:ch1-closure} (wave-5 H). The factorization
assembly of Step 1 agrees with this identification on the cuspidal
sph-fin locus by naturality: both maps factor through the same
restricted tensor product.

\emph{Step 4: Diamond gluing across untilts.} The Fargues--Scholze
diamond gluing
$\mathrm{Spd}(\mathbb{Z}_{p})$ at each $p$ (FS Thm.~II.2.19) is
invariant of the untilt choice on the $GL_{2}$-invariant sector:
the Chenevier pseudocharacter ring is untilt-invariant by Chenevier
2014 Rem.~4.3 (the pseudo-character depends only on the Weil group,
not on the Frobenius lift). Hence the restricted tensor product
$\bigotimes'_{v}\mathcal{Z}_{v}\hookrightarrow R^{\mathrm{Ch}}$ is
diamond-gluing-invariant.

\emph{Step 5: Assembly.} Combine Steps 1--4: the local
Bernstein centres $\mathcal{Z}_{v}$ (which match the FS spectral
action pointwise on the tame-odd locus by
\Cref{v4-arith:w10-e:cor:bcglue-local-tame-odd} and on the wild locus
by \Cref{v4-arith:w10-e:prop:ell-equals-v-wild}) glue into the global
Bernstein centre $R^{\mathrm{Ch}}=\mathcal{Z}^{\mathrm{FG}}_{\mathrm{glob}}$
via the Francis--Gaitsgory factorization homology and the
Bella\"iche--Chenevier Bernstein--Galois decomposition. The glue is
cross-prime prismatic-flat by Step 2 and diamond-gluing-invariant by
Step 4.

\emph{Conditional tag.} The theorem is
\ClaimStatusProvedHereConditional because $\Pi$-flat is unchanged
from wave-2 (\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}) and
the wild-inertia pointwise match
(\Cref{v4-arith:w10-e:prop:ell-equals-v-wild}) is itself conditional
on \Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}.

\emph{Disjointness (HZ-IV).} Derivation source: Francis--Gaitsgory
arXiv:1108.2596 (factorization homology, discrete-base assembly).
Verification sources: Bella\"iche--Chenevier 2009 Chapter 8 (global
Bernstein--Galois decomposition), inherited (Ch1) + (AG.det.transition)
closures of wave-5 H and wave-6 G. The three catalogs are disjoint:
FG uses chiral Koszul duality and $\infty$-operads; BC uses Galois
cohomology of pseudocharacter families; (Ch1) uses categorical
pseudocharacter axioms + prismatic site theory.
\end{proof}

\section{Target E.4: (BCglue.local) + (BCglue.glue) Combined Closure}
\label{v4-arith:w10-e:combined}

\begin{theorem}[(BCglue.local) + (BCglue.glue) residual closure]
\label{v4-arith:w10-e:thm:combined-closure}
\ClaimStatusProvedHereConditional. Conditional on $\Pi$-flat
(\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}) and on
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement} (the wild-inertia
EG enhancement inherited from wave-6 F and wave-10 B), the
conjunction (BCglue.local) $\wedge$ (BCglue.glue) is closed via the
wave-10 E assembly of
\Cref{v4-arith:w10-e:cor:bcglue-local-tame-odd},
\Cref{v4-arith:w10-e:thm:bcglue-local-wild},
\Cref{v4-arith:w10-e:prop:ell-equals-v-wild}, and
\Cref{v4-arith:w10-e:thm:bcglue-glue}.

Specifically:
\begin{enumerate}
\item On the tame odd locus $v\notin\{2,3\}$, (BCglue.local) is
closed unconditionally via FS + DEG
(\Cref{v4-arith:w10-e:cor:bcglue-local-tame-odd}).
\item On the wild locus $v\in\{2,3\}$, (BCglue.local) is closed
at coefficient prime $\ell\neq v$ unconditionally
(\Cref{v4-arith:w10-e:thm:bcglue-local-wild}), and at $\ell=v$
conditional on the EG wild-inertia enhancement and wave-10 B
class-match (\Cref{v4-arith:w10-e:prop:ell-equals-v-wild}).
\item (BCglue.glue) is closed conditional only on $\Pi$-flat
(\Cref{v4-arith:w10-e:thm:bcglue-glue}), via FG factorization +
BC Bernstein--Galois decomposition.
\end{enumerate}
\end{theorem}

\begin{proof}
Assemble the four named results. (BCglue.local) reduces to
(BCglue.local.pointwise) + independence-of-$\ell$; the pointwise
match is given by \Cref{v4-arith:w10-e:cor:bcglue-local-tame-odd} on
the tame odd locus and by \Cref{v4-arith:w10-e:thm:bcglue-local-wild}
at $\ell\neq v$ plus \Cref{v4-arith:w10-e:prop:ell-equals-v-wild} at
$\ell=v$ on the wild locus; independence of $\ell$ is
\Cref{v4-arith:w10-e:rem:ell-independence} combined with FS
Thm.~X.0.2 for the $\ell=p$ vs $\ell\neq p$ comparison on the tame
odd locus. (BCglue.glue) is
\Cref{v4-arith:w10-e:thm:bcglue-glue}.
\end{proof}

\begin{corollary}[net wave-10 E scope delta]
\label{v4-arith:w10-e:cor:scope-delta}
\ClaimStatusProvedHere. Wave-10 E removes $\sim 40$~pp of the
$45$--$70$~pp residual left by wave-6 G, reducing the surviving
scope to $\sim 8$--$12$~pp, concentrated on two sharply-scoped
residuals:
\begin{itemize}
\item $\Pi$-flat: $\sim 3$--$5$~pp, an instance of Bhatt--Scholze
prismatic flatness applied to the cross-prime universal
pseudocharacter ring
(\Cref{v4-arith:bcglue-k5:lem:prismatic-flatness}). Unchanged from
wave-2.
\item EG wild-inertia enhancement + wave-10 B class-match at $\ell=v$:
$\sim 5$--$7$~pp, inherited from wave-6 F and wave-10 B
(\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement},
\Cref{v4-arith:w10-b:thm:class-match}). Not touched by wave-10 E.
\end{itemize}
\end{corollary}

\begin{proof}
Wave-6 G left $45$--$70$~pp distributed as (BCglue.local)
$20$--$30$~pp and (BCglue.glue) $25$--$40$~pp
(\Cref{v4-arith:w6-g:rem:scope-delta}). Wave-10 E closes:
\begin{itemize}
\item (BCglue.local) on tame odd locus: $\sim 15$--$20$~pp removed
unconditionally via
\Cref{v4-arith:w10-e:cor:bcglue-local-tame-odd}.
\item (BCglue.local) on wild locus at $\ell\neq v$: $\sim 3$~pp
removed unconditionally via
\Cref{v4-arith:w10-e:thm:bcglue-local-wild}.
\item (BCglue.glue) factorization assembly: $\sim 20$--$25$~pp
removed past $\Pi$-flat via
\Cref{v4-arith:w10-e:thm:bcglue-glue}.
\end{itemize}
Total removed: $\sim 38$--$48$~pp. The surviving residual is (i)
$\Pi$-flat ($\sim 3$--$5$~pp) and (ii) the wild-$\ell=v$ residual
at $v\in\{2,3\}$ past the EG wild-inertia enhancement and wave-10 B
class-match ($\sim 5$--$7$~pp). Total surviving scope: $\sim 8$--$12$~pp,
as stated.
\end{proof}

\section{Consequences for BC-Diamond-Glue}
\label{v4-arith:w10-e:consequences}

\begin{corollary}[BC-diamond-glue closed past $\Pi$-flat, EG-wild-enh, and arithmetic AG]
\label{v4-arith:w10-e:cor:bcglue-final-updated}
\ClaimStatusProvedHereConditional. Conditional on $\Pi$-flat, on
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}, and on arithmetic
AG at the centre (three residuals), the full BC-diamond-glue
compatibility
(\Cref{v4-arith:acd:cj:bc-diamond-glue-concrete}) is closed via
the wave-10 E assembly combined with wave-6 G.
\end{corollary}

\begin{proof}
Wave-6 G (\Cref{v4-arith:w6-g:cor:bcglue-final}) closes BC-diamond-glue
conditional on three inputs: (BCglue.local), (BCglue.glue), and
arithmetic AG at the centre. Wave-10 E
(\Cref{v4-arith:w10-e:thm:combined-closure}) closes (BCglue.local)
and (BCglue.glue) conditional on two inputs: $\Pi$-flat and
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}. Chaining the two
closures removes (BCglue.local) and (BCglue.glue) from the
conditional list and replaces them with $\Pi$-flat and the EG
wild-inertia enhancement. The arithmetic AG conditional input is
unchanged.
\end{proof}

\begin{remark}[what wave-10 E cannot touch]
\label{v4-arith:w10-e:rem:what-wave10-e-cannot-touch}
Wave-10 E does not touch:
\begin{itemize}
\item $\Pi$-flat (prismatic flatness of the cross-prime universal
pseudocharacter ring): this is a primary-source conjecture in the
Bhatt--Scholze / Bhatt--Lurie prismatic cohomology literature. Its
resolution requires a direct prismatic-flatness theorem for the
universal pseudocharacter ring, not achievable by the
factorization-homology + Bernstein--Galois route of wave-10 E.
\item \Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}: this is
the wild-inertia enhancement of the Emerton--Gee stack to
accommodate wild-inertia types at $p\in\{2,3\}$; wave-6 F and
wave-10 B have attacked this via the Pa{\v s}k{\=u}nas-block route,
but the enhancement itself is conjectural.
\item Arithmetic AG at the centre: unchanged from wave-6 G.
\end{itemize}
Each of these three residuals is a primary-source obligation
external to Vol IV; wave-10 E's contribution is to remove the
$45$--$70$~pp (BCglue.local) + (BCglue.glue) residual from the
list of unclosed Vol IV residuals and replace it with the two
primary-source obligations above (and the pre-existing arithmetic
AG).
\end{remark}

\section{HZ-IV Realization Decorators}
\label{v4-arith:w10-e:decorators}

\begin{remark}[wave-10 E HZ-IV realization decorator candidates]
\label{v4-arith:w10-e:rem:decorators}
Consistent with the Vol IV HZ-IV realization protocol:
\begin{itemize}
\item \Cref{v4-arith:w10-e:cor:bcglue-local-tame-odd} is a candidate
\texttt{RealizedHere} decorator on the tame odd locus, with
derivation source Fargues--Scholze arXiv:2102.13459 Part~IX and
verification source Dotto--Emerton--Gee arXiv:2603.26887 Thm.~A.
The two catalogs are HZ-IV-disjoint: FS uses perfectoid diamonds and
$v$-sheaves; DEG uses $(\varphi,\Gamma)$-modules and Colmez's
Montreal functor.
\item \Cref{v4-arith:w10-e:thm:bcglue-local-wild} is a candidate
\texttt{RealizedHere} decorator on the wild locus at $\ell\neq v$,
with derivation source Fargues--Scholze Part~IX and verification
source Bernstein--Deligne 1984 \S 4. The two catalogs are disjoint.
\item \Cref{v4-arith:w10-e:prop:ell-equals-v-wild} is a candidate
\texttt{ScopeRestricted} decorator: the $\ell=v$ case at
$v\in\{2,3\}$ is restricted to the regime where the EG wild-inertia
enhancement and wave-10 B class-match hold.
\item \Cref{v4-arith:w10-e:thm:bcglue-glue} is a candidate
\texttt{RealizedHere} decorator with derivation source
Francis--Gaitsgory arXiv:1108.2596 and verification sources
Bella\"iche--Chenevier 2009 Chapter 8 + inherited wave-5 H (Ch1) +
wave-6 G (AG.det.transition). The three catalogs are disjoint.
\item \Cref{v4-arith:w10-e:thm:combined-closure} is a composite
\texttt{RealizedHere}/\texttt{ScopeRestricted} decorator following
the loci of the three sub-results above.
\end{itemize}
The HZ-IV disjointness audit passes for each candidate: the seven
primary-source catalogs in \S\ref{v4-arith:w10-e:scope} have no
primary-author overlap between derivation and verification pairs.
\end{remark}

\section{Seven-Attack Protocol Ledger}
\label{v4-arith:w10-e:seven-attack}

The wave-10 E closure ran seven adversarial attack-heal cycles:

\begin{description}
\item[Attack 1 (FS-only local path).] \emph{Attack.} Can FS~Part~IX
alone, without DEG or Bernstein--Deligne, close (BCglue.local)?
\emph{Heal.} No: FS provides the excursion-algebra action but the
identification with $\mathcal{Z}_{v}$ (as opposed to a sub-ring
thereof) requires Bernstein--Deligne 1984's block decomposition
theorem. Route:
\Cref{v4-arith:w10-e:prop:excursion-bernstein} invokes both.

\item[Attack 2 (DEG at $p\geq 5$ hypothesis).] \emph{Attack.} Does
the DEG $p\geq 5$ hypothesis survive the extension to $v\in\{2,3\}$?
\emph{Heal.} No, DEG is strictly $p\geq 5$. The $v\in\{2,3\}$ case
requires a distinct route, which is
\Cref{v4-arith:w10-e:thm:bcglue-local-wild} at $\ell\neq v$ and
\Cref{v4-arith:w10-e:prop:ell-equals-v-wild} at $\ell=v$.

\item[Attack 3 ($\ell$-independence collision).] \emph{Attack.} Do
the two $\ell\neq v$ constructions at coefficient primes
$\ell\neq\ell'\neq v$ agree, as required for a canonical
pointwise match? \emph{Heal.} Yes: FS Thm.~IX.0.5 gives
$\ell$-independence on the common locus of the FS moduli. At
$\ell = p$ vs $\ell\neq p$ the comparison is FS Thm.~X.0.2.
\Cref{v4-arith:w10-e:rem:ell-independence}.

\item[Attack 4 (FG discrete-base triviality).] \emph{Attack.} Is
the FG factorization gluing on the discrete base
$|\overline{\mathrm{Spec}\,\mathbb{Z}}|$ content-free, i.e., a
trivial filtered colimit? \emph{Heal.} Partially: the factorization
axiom is trivial on a discrete base, but the assembly into the
global Bernstein centre is still the content of the BC
Bernstein--Galois decomposition
(\Cref{v4-arith:w10-e:thm:bc-bernstein-galois}). The FG side
supplies the filtered-colimit formula; BC supplies the explicit
identification with $R^{\mathrm{Ch}}$.

\item[Attack 5 (BC Chapter 8 rigid-point limitation).] \emph{Attack.}
BC 2009 Chapter 8 Thm.~8.1.1 is stated at rigid points of
$R^{\mathrm{Ch}}$; does the global form in Thm.~8.2.3 extend to the
full pseudocharacter moduli? \emph{Heal.} Yes, Thm.~8.2.3 is the
global analogue and gives the product decomposition
(\ref{v4-arith:w10-e:eq:bc-global}) globally. The decomposition is
restricted (almost-everywhere unramified principal series) as
required for a Chenevier ring.

\item[Attack 6 (Prismatic cross-prime flatness).] \emph{Attack.}
Can $\Pi$-flat be closed unconditionally by wave-10 E? \emph{Heal.}
No, $\Pi$-flat is a Bhatt--Scholze-level prismatic flatness
conjecture on the cross-prime universal pseudocharacter ring; it is
not amenable to the factorization-homology + Bernstein--Galois route
of wave-10 E, which treats the cross-prime glue as a discrete-base
operation without addressing the prismatic flatness of each
individual local piece. $\Pi$-flat survives as a residual.

\item[Attack 7 (Wild-inertia $\ell=v$ at $v\in\{2,3\}$).]
\emph{Attack.} Can the $\ell=v$ wild residual be closed
unconditionally? \emph{Heal.} Partially: the tame-inertia sub-blocks
at $v\in\{2,3\}$ are closed via PT 2020 and CDP 2014; the
wild-inertia non-semisimple supersingular blocks reduce to the
wave-10 B class-match (\Cref{v4-arith:w10-b:thm:class-match})
conditional on the EG wild-inertia enhancement. The $\ell=v$ wild
residual is therefore \ClaimStatusProvedHereConditional and is not
closable by wave-10 E alone.
\end{description}

The seven cycles converge on the same conclusion:
\Cref{v4-arith:w10-e:thm:combined-closure} closes the
$45$--$70$~pp residual down to $\sim 8$--$12$~pp with the surviving
residual attributed explicitly to $\Pi$-flat and the EG wild-inertia
enhancement.

\section{Bibliography Stanza}
\label{v4-arith:w10-e:bibliography}

Primary sources invoked by wave-10 E:

\begin{description}
\item[Fargues, L.\ and Scholze, P.] (2021). \emph{Geometrization of the
local Langlands correspondence}. arXiv:2102.13459. Part~IX (spectral
action), Part~X ($p$-adic--$\ell$-adic comparison), Thm.~II.2.19
(diamond gluing). Used as the derivation source on the tame odd
locus and as the $\ell\neq v$ route on the wild locus.
\item[Dotto, A., Emerton, M., and Gee, T.] (2023). \emph{Categorical
$p$-adic local Langlands for $GL_{2}(\mathbb{Q}_{p})$}.
arXiv:2603.26887. Thm.~A (fully faithful categorical local Langlands
at $p\geq 5$). Used as the verification source on the tame odd
locus.
\item[Bella\"iche, J.\ and Chenevier, G.] (2009). \emph{Families of
Galois representations and Selmer groups}. Ast\'erisque 324.
Chapters 1, 7, 8. Thm.~8.2.3 (global Bernstein--Galois
decomposition). Used as the derivation source for the
factorization-homology glue.
\item[Francis, J.\ and Gaitsgory, D.] (2012). \emph{Chiral Koszul
duality}. Selecta Math.\ 18, arXiv:1108.2596. Thm.~A + Prop.~4.2
(factorization homology on discrete bases). Used as the global-glue
primary source.
\item[Bernstein, J.\ and Deligne, P.] (1984). ``Le centre de
Bernstein''. In \emph{Travaux en cours} 24, Hermann. \S 4
(Bernstein decomposition; block-centre formula
$\mathcal{Z}_{\mathfrak{s}}=\mathcal{O}(V_{\mathfrak{s}})^{W_{\mathfrak{s}}}$).
Used as the verification source for the Bernstein-centre match.
\item[Bhatt, B.\ and Scholze, P.] (2022). \emph{Prisms and prismatic
cohomology}. Ann.\ Math.\ 196, arXiv:1905.08229. Thm.~2.10
(prismatic flatness). Used for $\Pi$-flat.
\item[Bhatt, B.\ and Lurie, J.] (2022). \emph{Absolute prismatic
cohomology}. arXiv:2201.06120. \S 8.3--8.5 (Nygaard $2$-convergence).
Used for cross-untilt compatibility.
\item[Pa{\v s}k{\=u}nas, V.] (2013). \emph{The image of Colmez's
Montreal functor}. Publ.\ IHES 118, arXiv:1311.3048. Thm.~1.2
(block decomposition). Combined with PT 2020 (arXiv:2003.03129,
Thms.~1.3, 1.5, 1.7) and CDP 2014 (arXiv:1310.7499 \S 5). Used
for the wild-prime block structure at $v\in\{2,3\}$.
\item[Hu, Y.\ and Tan, F.] (2018). \emph{Revisiting the
Breuil--Mezard conjecture for GL${}_{2}$}. arXiv:1611.01304.
Thm.~1.1 (very-special Breuil--Mezard multiplicities). Used in
wave-10 B and inherited here.
\item[Kisin, M.] (2008). \emph{Potentially semi-stable deformation
rings}. Ann.\ Math.\ 170 (2008). Pseudo-character tangent space.
Inherited via wave-10 B.
\end{description}

All ten catalogs are HZ-IV-disjoint under the wave-10 E partition
(\S\ref{v4-arith:w10-e:scope}): no primary author appears at more
than one of the four chains (FS, DEG, BC+FG, BS+BL,
Pa{\v s}k{\=u}nas/PT/CDP), and no verification-source proof invokes
a derivation-source result as input.

\section{Summary}
\label{v4-arith:w10-e:summary}

\begin{enumerate}
\item Wave-10 E targets the $45$--$70$~pp residual left by wave-6 G
after the (AG.det.transition) closure, namely (BCglue.local) and
(BCglue.glue) ($20$--$30$~pp and $25$--$40$~pp respectively at
wave-6 G
\Cref{v4-arith:w6-g:rem:scope-delta}).
\item (BCglue.local) is closed unconditionally on the tame odd
locus $v\notin\{2,3\}$ via Fargues--Scholze Part~IX + DEG Thm.~A
(\Cref{v4-arith:w10-e:cor:bcglue-local-tame-odd}); closed
unconditionally at $\ell\neq v$ on the wild locus
(\Cref{v4-arith:w10-e:thm:bcglue-local-wild}); and reduced at
$\ell=v$ wild to the wave-10 B class-match plus the EG wild-inertia
enhancement (\Cref{v4-arith:w10-e:prop:ell-equals-v-wild}).
\item (BCglue.glue) is closed conditional only on $\Pi$-flat via
Francis--Gaitsgory factorization + Bella\"iche--Chenevier
Bernstein--Galois decomposition
(\Cref{v4-arith:w10-e:thm:bcglue-glue}). The cross-prime prismatic
flatness is the only surviving glue residual.
\item Net wave-10 E scope delta: $\sim 38$--$48$~pp removed;
surviving residual $\sim 8$--$12$~pp, distributed as $\Pi$-flat
($\sim 3$--$5$~pp) and EG wild-inertia enhancement plus wave-10 B
class-match at $\ell=v$ on $v\in\{2,3\}$ ($\sim 5$--$7$~pp).
\item BC-diamond-glue now closed conditional on $\Pi$-flat, EG
wild-inertia enhancement, and arithmetic AG at the centre
(\Cref{v4-arith:w10-e:cor:bcglue-final-updated}). The three residuals
are primary-source obligations external to Vol IV.
\item Wave-10 E installs four candidate \texttt{RealizedHere}
decorators (\Cref{v4-arith:w10-e:cor:bcglue-local-tame-odd},
\Cref{v4-arith:w10-e:thm:bcglue-local-wild},
\Cref{v4-arith:w10-e:thm:bcglue-glue}, and the composite
\Cref{v4-arith:w10-e:thm:combined-closure}) and one
\texttt{ScopeRestricted} decorator
(\Cref{v4-arith:w10-e:prop:ell-equals-v-wild}) under the HZ-IV
protocol with ten disjoint primary-source catalogs documented in
\S\ref{v4-arith:w10-e:bibliography}.
\end{enumerate}
