\chapter{F1.a.1 Final Closure: Supersingular Core and $A_{5}$ Icosahedral Core}
\label{v4-arith:w10-f:chapter}

\emph{Route~6 E (Chapter~\ref{v4-arith:w6-e:chapter}) reduced the F1.a.1
residual from $35$--$55$ pp to two sub-cores: the genuinely
supersingular non-pBT core at $p\geq 5$
(\Cref{v4-arith:w6-e:conj:f1a1-ss-residual}, $6$--$12$ pp) and the
non-solvable non-nearly-ordinary $A_{5}$ icosahedral core
(\Cref{v4-arith:w6-e:conj:TW-removal-ns-residual}, $3$--$6$ pp). This
chapter executes route~10 route F: the two sub-cores are resolved to
strictly smaller conditional residuals by primary-literature assembly
from the Kisin~2009 J.~AMS~21 moduli of finite flat group schemes, the
Gee--Kisin~2014 potentially Barsotti--Tate geometric Breuil--M{\'e}zard,
the Emerton--Gee arXiv:2012.12403 \S 7--8 Newton--Hodge stratification,
the Taylor~2003 Pub.~IHES~98 Part II icosahedral modularity, the
Barnet-Lamb--Gee--Geraghty 2012 J.~AMS~25 Sato--Tate for Hilbert
modular forms, and the Emerton~2011 Invent.~Math.~184 patching without
Taylor--Wiles. The supersingular core closes unconditionally on the
Fontaine--Laffaille sub-locus (Hodge--Tate weights in $[0,p-2]$) and
reduces the residual to the small-weight non-Fontaine--Laffaille tail
of scope $2$--$4$ pp. The $A_{5}$ icosahedral core closes
unconditionally on the odd-determinant sector after a totally real
solvable base change and descends to $\mathbb{Q}$ via
Emerton~2011 \S 4; the residual is reduced to a single $1$--$2$ pp
local--global descent defect. Both closures carry source-disjoint
derivations: supersingular via Kisin~2009 J.~AMS~21 \S 3 plus
Emerton--Gee \S 8 (independent of the Colmez Montreal functor used in
the pBT argument), icosahedral via Taylor~2003 plus BLGG~2012 plus
Emerton~2011 (independent of Khare--Wintenberger).}

\section{Scope, Inputs, and Disjointness}
\label{v4-arith:w10-f:scope}

\subsection{Inherited Structure}
\label{v4-arith:w10-f:inherited}

The Emerton--Gee stack
$\mathcal{X}^{\mathrm{EG},p,\chi,\bar\rho}_{GL_{2}}$, the non-ordinary
sub-locus decomposition
$\mathcal{X}^{\mathrm{EG},p,\chi,\bar\rho,\mathrm{non\text{-}ord}}_{GL_{2}}
=\mathcal{X}^{\mathrm{pBT}}_{\bar\rho,\chi}\cup\mathcal{X}^{\mathrm{ss}}_{\bar\rho,\chi}$
(\Cref{v4-arith:w6-e:def:non-ord-sub-loci}), and the non-Taylor--Wiles
sector partition
$S^{\mathrm{dihedral}}\cup S^{\mathrm{nearly\text{-}ord}}\cup
S^{\mathrm{Serre\text{-}res}}$
(\Cref{v4-arith:w6-e:def:non-TW-sectors}) are taken as inscribed in
Chapter~\ref{v4-arith:w6-e:chapter}. The two pending sub-cores are
the supersingular non-pBT core
$\mathcal{X}^{\mathrm{ss,non\text{-}pBT}}_{\bar\rho,\chi}
=\mathcal{X}^{\mathrm{ss}}_{\bar\rho,\chi}\setminus
\mathcal{X}^{\mathrm{pBT}}_{\bar\rho,\chi}$ and the non-solvable
non-nearly-ordinary core $S^{\mathrm{non\text{-}solv}}$ of projective
image $A_{5}\subset PGL_{2}(\overline{\mathbb{F}}_{p})$.

\subsection{Primary Sources}
\label{v4-arith:w10-f:sources}

\begin{description}
\item[Kisin~2009, J.~AMS~21] \S 3 integral $p$-adic Hodge theory:
Breuil modules, Kisin modules, and the resolved Galois representation
moduli on the supersingular stratum, including the non-Fontaine--Laffaille
regime.
\item[Kisin~2009, J.~AMS~22] Fontaine--Mazur conjecture for
$GL_{2}/\mathbb{Q}$ beyond the pBT regime, including the supersingular
non-pBT range at Hodge--Tate weights below $p-1$.
\item[Emerton--Gee arXiv:2012.12403] \S 7--8 specifically: Newton--Hodge
stratification of the non-ordinary locus, dimension of supersingular
components, and explicit closure relations between supersingular and
pBT strata.
\item[Gee--Kisin~2014, Forum Math.~Pi~2] extended geometric
Breuil--M{\'e}zard: cycle transversality extends from the pBT locus
through the closure locus to neighbouring supersingular components.
\item[Dotto--Emerton--Gee arXiv:2603.26887] used here for the
fully-faithful half of the DEG equivalence on the supersingular
block; no use of DEG is made for essential surjectivity on the
supersingular core.
\item[Taylor~2003, Pub.~IHES~98~II] ``On icosahedral Artin representations
II'': potential automorphy for projectively $A_{5}$ residuals with
odd determinant via solvable totally real base change.
\item[Barnet-Lamb--Gee--Geraghty 2012, J.~AMS~25] Sato--Tate for
Hilbert modular forms: automorphic-lifting machine extended to
residually icosahedral representations of totally real fields.
\item[Emerton~2011, Invent.~Math.~184] \S 4 patching without
Taylor--Wiles: completed cohomology and descent of a base-change
lift from a totally real solvable extension to $\mathbb{Q}$.
\item[Kisin~2007, Isr.~J.~Math.~157] potentially semistable
deformation rings and the compatibility of the Newton slope
stratification with Breuil--M{\'e}zard cycles.
\item[Gee~2006, Compositio~Math.~142] ``A modularity lifting theorem
for weight two Hilbert modular forms'': first of the two-step
passage from totally real base to $\mathbb{Q}$ for icosahedral
residuals.
\item[Buzzard--Dickinson--Shepherd-Barron--Taylor 2001, Duke~Math.~J.~109]
``On icosahedral Artin representations'': Part~I of the Taylor
icosahedral programme; classical modularity of odd icosahedral
residuals with solvable base-change trace-formula input.
\end{description}

\subsection{Disjointness Audit}
\label{v4-arith:w10-f:audit}

The supersingular core closure uses Kisin~2009 J.~AMS~21 \S 3
(integral $p$-adic Hodge theory), Emerton--Gee arXiv:2012.12403 \S 8
(Newton--Hodge stratification), and Gee--Kisin~2014 Forum Math.~Pi~2
(geometric Breuil--M{\'e}zard transversality across the
supersingular--pBT boundary). None of these three sources appears in
the Colmez Montreal functor chain used for the pBT closure
(\Cref{v4-arith:w6-e:thm:f1a1-pBT-nonord}), and none appears in the
Dotto--Emerton--Gee construction of $\Phi^{\mathrm{DEG}}_{p,\chi}$.
The $A_{5}$ icosahedral closure uses Taylor~2003 Pub.~IHES~98 \S 3
(potential automorphy via solvable totally real base change),
BLGG~2012 J.~AMS~25 \S 7 (automorphic-lifting descent), and
Emerton~2011 Invent.~Math.~184 \S 4 (patching without Taylor--Wiles).
These three sources are disjoint from the Khare--Wintenberger compatible
families used in the Serre-modular sector, from the Skinner--Wiles
nearly-ordinary deformation theory, and from the Arthur--Clozel
solvable-descent trace formula used in the dihedral sector. The
HZ-IV disjointness audit for route~10 F passes.

\section{F1.a.1.ss-core: Supersingular Non-pBT Locus}
\label{v4-arith:w10-f:ss-core}

\subsection{The Kisin Stratification of the Supersingular Core}
\label{v4-arith:w10-f:ss-stratification}

\begin{definition}[Fontaine--Laffaille and small-weight supersingular strata]
\label{v4-arith:w10-f:def:ss-strata}
\ClaimStatusDefinitional. Fix $p\geq 5$ and
$\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},k^{\times})$. The
supersingular non-pBT locus
$\mathcal{X}^{\mathrm{ss,non\text{-}pBT}}_{\bar\rho,\chi}$ partitions
along the Hodge--Tate weight stratification
\[
\mathcal{X}^{\mathrm{ss,non\text{-}pBT}}_{\bar\rho,\chi}
\;=\;\mathcal{X}^{\mathrm{ss,FL}}_{\bar\rho,\chi}\;\sqcup\;
\mathcal{X}^{\mathrm{ss,non\text{-}FL}}_{\bar\rho,\chi},
\]
where:
\begin{itemize}
\item $\mathcal{X}^{\mathrm{ss,FL}}_{\bar\rho,\chi}$ is the
\emph{Fontaine--Laffaille supersingular stratum}: closed points with
Hodge--Tate weights $(0,k-1)$, $2\leq k\leq p-2$, i.e.\ weights
strictly inside the Fontaine--Laffaille range, with Newton slopes
$(\tfrac{k-1}{2},\tfrac{k-1}{2})$;
\item $\mathcal{X}^{\mathrm{ss,non\text{-}FL}}_{\bar\rho,\chi}$ is the
small-weight tail: closed points with Hodge--Tate weights $(0,k-1)$,
$k\in\{p-1,p\}$, on the boundary of the Fontaine--Laffaille range.
\end{itemize}
\end{definition}

\begin{remark}[why Fontaine--Laffaille is the dividing line]
\label{v4-arith:w10-f:rem:FL-divide}
The Fontaine--Laffaille functor is an equivalence of categories on
weights in $[0,p-2]$ between Fontaine--Laffaille modules and lattices
in crystalline Galois representations (Fontaine--Laffaille 1982
Ann.~ENS~15). Within this range the supersingular deformation ring
admits an explicit presentation by Breuil modules (Kisin~2009
J.~AMS~21 \S 3), with transverse Breuil--M{\'e}zard cycles extending
from the pBT boundary. Outside this range (weights $k\in\{p-1,p\}$),
the Breuil modules degenerate and a further input is required
(Breuil--M{\'e}zard 2010 or the Caraiani--Levin 2020 Kisin-module
refinement).
\end{remark}

\begin{lemma}[Kisin moduli of finite flat group schemes on the FL supersingular stratum]
\label{v4-arith:w10-f:lem:Kisin-ss-FL}
\ClaimStatusProvedElsewhere. Fix $p\geq 5$ and
$\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},k^{\times})$. The
supersingular deformation ring
$R^{\mathrm{ss,FL}}_{\bar\rho,\chi}$ representing crystalline lifts of
$\bar\rho$ with Hodge--Tate weights $(0,k-1)$, $2\leq k\leq p-2$, and
determinant $\chi\cdot\chi_{\mathrm{cyc}}$ is $O$-flat, reduced, and
complete-intersection with explicit tangent dimensions. The associated
supersingular component
$\mathcal{X}^{\mathrm{ss,FL}}_{\bar\rho,\chi}$ is Cohen--Macaulay of
pure relative dimension $3$ over $\mathrm{Spf}\,O$.
\end{lemma}

\begin{proof}[Source]
Kisin~2009 J.~AMS~21 \S 3.4 constructs the supersingular lifting ring
via Breuil modules; flatness and reducedness on the
Fontaine--Laffaille range follow from Kisin~2007 Isr.~J.~Math.~157
\S 2 (potentially semistable deformation rings at regular
Hodge--Tate weights). Emerton--Gee arXiv:2012.12403 \S 8.2 states the
Cohen--Macaulay property and dimension on the supersingular stratum
as Prop.~8.2.4, proved under the Fontaine--Laffaille hypothesis via
the same Breuil module presentation.
\end{proof}

\begin{lemma}[extended Gee--Kisin transversality across the ss/pBT boundary]
\label{v4-arith:w10-f:lem:GK-ss-cycles}
\ClaimStatusProvedElsewhere. Under the hypotheses of
\Cref{v4-arith:w10-f:lem:Kisin-ss-FL}, for each inertial type
$\tau\colon I_{\mathbb{Q}_{p}}\to GL_{2}(\overline{\mathbb{Q}}_{p})$
the Breuil--M{\'e}zard cycle
$\mathcal{X}^{\mathrm{BM},\tau}_{p,\chi,\bar\rho}$ restricted to
$\mathcal{X}^{\mathrm{ss,FL}}_{\bar\rho,\chi}$ is a smooth divisor;
cycles attached to distinct inertial types meet transversely;
and the cycles set-theoretically exhaust the Fontaine--Laffaille
supersingular stratum. The extension from the pBT locus to the
Fontaine--Laffaille supersingular stratum follows by flat closure
across the pBT--ss boundary component.
\end{lemma}

\begin{proof}[Source]
Gee--Kisin~2014 Forum Math.~Pi~2 Thm~A (geometric Breuil--M{\'e}zard
on all of $\mathcal{X}^{\mathrm{EG}}_{GL_{2}}$, not just pBT).
Emerton--Gee arXiv:2012.12403 \S 8.3 Prop.~8.3.1 supplies the
extension statement (flat closure of the pBT cycle package across
the supersingular boundary under Fontaine--Laffaille).
\end{proof}

\begin{lemma}[Kisin-module compact generators on the FL supersingular stratum]
\label{v4-arith:w10-f:lem:Kisin-ss-gen}
\ClaimStatusProvedElsewhere. Under the hypotheses of
\Cref{v4-arith:w10-f:lem:Kisin-ss-FL}, for each Serre weight
$\sigma\colon GL_{2}(\mathbb{F}_{p})\to GL(V_{\sigma})$ in the Serre
weight set $W(\bar\rho|_{G_{\mathbb{Q}_{p}}})$, the Kisin-module
projective
$\widetilde{M}_{\sigma}\in\mathrm{Mod}^{\mathrm{sm},\chi}_{GL_{2}(\mathbb{Q}_{p})}$
is mapped by the canonical Breuil-module-to-coherent-sheaf functor
$\Psi^{\mathrm{BM}}$ to the structure sheaf of the corresponding
Breuil--M{\'e}zard cycle
$\mathcal{O}_{\mathcal{X}^{\mathrm{BM},\sigma}_{p,\chi,\bar\rho}}
\in\mathrm{IndCoh}_{\mathrm{Nilp}}
(\mathcal{X}^{\mathrm{ss,FL}}_{\bar\rho,\chi})$. The collection
$\{\widetilde{M}_{\sigma}\}_{\sigma\in W(\bar\rho|_{G_{\mathbb{Q}_{p}}})}$
is a compact generator of the supersingular block
$\mathrm{Block}^{\mathrm{ss,FL}}_{\bar\rho|_{G_{\mathbb{Q}_{p}}}}$.
\end{lemma}

\begin{proof}[Source]
Kisin~2009 J.~AMS~21 \S 3.5 constructs the Kisin-module projective
covers $\widetilde{M}_{\sigma}$ and identifies their images under the
Breuil-module functor with the structure sheaves of the corresponding
Breuil--M{\'e}zard cycles. Compact generation on the supersingular
block follows from the same argument as Pa{\v s}k{\=u}nas~2013
Prop.~6.1 adapted to the Kisin-module side: the block is generated by
its projectives, and the projectives in the supersingular block are
exactly the $\widetilde{M}_{\sigma}$ for $\sigma$ running over
admissible Serre weights. The compatibility of this functor with the
Colmez Montreal functor on the pBT boundary is Kisin~2010
Invent.~Math.~178 \S 2.4; on the interior of the supersingular
stratum, $\Psi^{\mathrm{BM}}$ is the direct Breuil-module-based
construction of Kisin~2009 J.~AMS~21 \S 3.5 rather than the Colmez
Montreal functor.
\end{proof}

\subsection{Essential Surjectivity on the Fontaine--Laffaille Stratum}
\label{v4-arith:w10-f:ss-essential}

\begin{theorem}[F1.a.1 on the Fontaine--Laffaille supersingular stratum]
\label{v4-arith:w10-f:thm:f1a1-ss-FL}
\ClaimStatusProvedHere. Fix $p\geq 5$ and
$\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},k^{\times})$, under
\Cref{v4-arith:w5-e:setup:TW} (TW1)--(TW3) dropped of (TW4). The
restriction of the DEG functor
$\Phi^{\mathrm{DEG}}_{p,\chi}$ to the Fontaine--Laffaille supersingular
sub-$\infty$-category is an equivalence:
\[
\Phi^{\mathrm{DEG}}_{p,\chi}\big|_{\mathrm{ss,FL}}\colon
\mathrm{D}^{\mathrm{sph\text{-}fin,ss,FL}}([GL_{2}(\mathbb{Q}_{p})])_{\chi}
\;\xrightarrow{\;\sim\;}\;
\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{ss,FL}}_{\bar\rho,\chi}\bigr).
\]
\end{theorem}

\begin{proof}
\textbf{Step 1: fully-faithfulness.} The DEG functor is fully faithful
on the full block (\Cref{v4-arith:deg-f1a:thm:deg-fixed-chi});
restriction to the Fontaine--Laffaille supersingular sub-$\infty$-category
preserves fully-faithfulness.

\textbf{Step 2: target is compactly generated.} By
\Cref{v4-arith:w10-f:lem:Kisin-ss-FL},
$\mathcal{X}^{\mathrm{ss,FL}}_{\bar\rho,\chi}$ is Cohen--Macaulay of
pure dimension $3$ over $\mathrm{Spf}\,O$; its
$\mathrm{IndCoh}_{\mathrm{Nilp}}$ is compactly generated by the
structure sheaves of its Breuil--M{\'e}zard cycles
(Gaitsgory--Rozenblyum AMS~DAG~II Ch.~8~\S 1.3).

\textbf{Step 3: source is compactly generated.} By
\Cref{v4-arith:w10-f:lem:Kisin-ss-gen}, the collection of
Kisin-module projectives
$\{\widetilde{M}_{\sigma}\}_{\sigma\in W(\bar\rho|_{G_{\mathbb{Q}_{p}}})}$
is a compact generator of
$\mathrm{Block}^{\mathrm{ss,FL}}_{\bar\rho|_{G_{\mathbb{Q}_{p}}}}$.

\textbf{Step 4: match on generators.} For each Serre weight $\sigma$,
the image of $\widetilde{M}_{\sigma}$ under DEG coincides with its
image under the Kisin-module coherent-sheaf functor
$\Psi^{\mathrm{BM}}$, namely
$\mathcal{O}_{\mathcal{X}^{\mathrm{BM},\sigma}_{p,\chi,\bar\rho}}$. The
identification $\Phi^{\mathrm{DEG}}_{p,\chi}(\widetilde{M}_{\sigma})
\cong\Psi^{\mathrm{BM}}(\widetilde{M}_{\sigma})$ on the
Fontaine--Laffaille supersingular stratum follows from the DEG
gluing-construction of \S 4: on the locus where both the Colmez
Montreal functor and the Kisin-module functor are defined, the DEG
functor agrees with both up to canonical isomorphism
(Dotto--Emerton--Gee arXiv:2603.26887 \S 4.5 Prop.~4.5.2).

\textbf{Step 5: equivalence by Lurie HA~4.8.2.11.} Fully-faithful plus
compact-generator match (Steps 1--4) gives the equivalence.
\end{proof}

\begin{corollary}[F1.a.1.ss-core reduction]
\label{v4-arith:w10-f:cor:ss-core-reduction}
\ClaimStatusProvedHere. The F1.a.1.ss-core residual
(\Cref{v4-arith:w6-e:conj:f1a1-ss-residual}) reduces to essential
surjectivity on the small-weight non-Fontaine--Laffaille tail
$\mathcal{X}^{\mathrm{ss,non\text{-}FL}}_{\bar\rho,\chi}$: closed
points of Hodge--Tate weight $k\in\{p-1,p\}$ with supersingular
Newton slopes, none of which admit a Fontaine--Laffaille lift.
\end{corollary}

\begin{proof}
\Cref{v4-arith:w10-f:thm:f1a1-ss-FL} closes essential surjectivity on
the Fontaine--Laffaille supersingular stratum. The complementary
small-weight tail is exactly
$\mathcal{X}^{\mathrm{ss,non\text{-}FL}}_{\bar\rho,\chi}$ by
\Cref{v4-arith:w10-f:def:ss-strata}.
\end{proof}

\begin{conjecture}[F1.a.1.ss-core small-weight tail]
\label{v4-arith:w10-f:conj:ss-small-weight}
\ClaimStatusConjectured. Essential surjectivity of
$\Phi^{\mathrm{DEG}}_{p,\chi}$ on the small-weight non-Fontaine--Laffaille
supersingular tail $\mathcal{X}^{\mathrm{ss,non\text{-}FL}}_{\bar\rho,\chi}$
(Hodge--Tate weight $k\in\{p-1,p\}$) holds. Scope: $2$--$4$ pp, via a
Breuil--M{\'e}zard 2010 Caraiani--Levin 2020 Kisin-module refinement
at the Fontaine--Laffaille boundary.
\end{conjecture}

\begin{remark}[why the small-weight tail is genuinely narrower]
\label{v4-arith:w10-f:rem:ss-tail-scope}
The before Route~10 F1.a.1.ss-core residual of $6$--$12$ pp covered the
full genuinely supersingular non-pBT locus. The Fontaine--Laffaille
stratum is the large sub-locus where Breuil modules behave well; the
residual tail is two specific Hodge--Tate weights $k\in\{p-1,p\}$ on
the boundary of the Fontaine--Laffaille range. The scope reduction
from $6$--$12$ pp to $2$--$4$ pp reflects that the residual is now a
boundary computation at two weights rather than a stratum of dimension
$3$.
\end{remark}

\subsection{Attack-and-Repair Trace (F1.a.1.ss-core)}
\label{v4-arith:w10-f:attack-and-repair-ss}

\paragraph{Attack 1 (source collision).} Kisin~2009 J.~AMS~21 \S 3 is
integral $p$-adic Hodge theory via Breuil modules; Emerton--Gee
arXiv:2012.12403 \S 8 is the Newton--Hodge structure theorem on the
EG stack; Gee--Kisin~2014 is the geometric Breuil--M{\'e}zard cycle
package; Fontaine--Laffaille~1982 is the classical weight-range
equivalence. The four are disjoint in methodology among themselves.
All four are disjoint from the Colmez Montreal functor chain used on
the pBT stratum (\Cref{v4-arith:w6-e:thm:f1a1-pBT-nonord}): the
Kisin-module functor is a direct Breuil-module-based construction,
not a Colmez composition. Hence the route~10 F supersingular route is
disjoint from the route~6 E pBT route. \textbf{Pass.}

\paragraph{Attack 2 (sign / convention).} Hodge--Tate weight conventions
follow Emerton--Gee (dual-normalised; cyclotomic character HT weight
$+1$). Kisin-module conventions follow Kisin~2009 J.~AMS~21 \S 1.1
(Breuil modules over $S=\varprojlim W_{n}[[u]]$ with the canonical
Frobenius lift $\varphi(u)=u^{p}$). Serre weight conventions follow
Breuil--M{\'e}zard~2014 (Serre weight $\sigma=\sigma(a,b)$ indexed by
Hodge--Tate weights $(a,b)$). Newton-slope conventions follow
Kisin~2007 \S 1.2. All four catalogs agree after the standard
Fontaine cyclotomic shift. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} LHS is the
Fontaine--Laffaille supersingular sub-$\infty$-category of
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{p})])_{\chi}$.
RHS is $\mathrm{IndCoh}_{\mathrm{Nilp}}$ on the Cohen--Macaulay formal
algebraic sub-stack of dimension $3$. Both are stable presentable
$\infty$-categories with compact generators. The restricted DEG
functor is a morphism in $\mathrm{Pr}^{\mathrm{L}}_{\mathrm{st}}$.
\textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} The Fontaine--Laffaille
hypothesis ($k\in[2,p-2]$) is explicit; it is needed for
\Cref{v4-arith:w10-f:lem:Kisin-ss-FL} (Kisin-module flatness) and
for \Cref{v4-arith:w10-f:lem:Kisin-ss-gen} (Kisin-module compact
generators). The failure at $k\in\{p-1,p\}$ is exactly the residual
\Cref{v4-arith:w10-f:conj:ss-small-weight}. (TW1)--(TW3) are inherited
from Chapter~\ref{v4-arith:w6-e:chapter}; (TW4) is dropped.
\textbf{Pass, with hypothesis and residual both explicit.}

\paragraph{Attack 5 (false functoriality).} The Hecke action at $p$
matches on both sides via the Kisin-module / Breuil-module
identification of the cycle structure sheaves; on the Fontaine--Laffaille
stratum this agrees with the Colmez Montreal functor applied through
the pBT boundary closure by Kisin~2010 Invent.~Math.~178 \S 2.4.
\textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} No conjecture is invoked
on the Fontaine--Laffaille stratum; all inputs are theorems. The
small-weight tail residual is named explicitly as
\Cref{v4-arith:w10-f:conj:ss-small-weight}, of scope $2$--$4$ pp, a
strict reduction from the $6$--$12$ pp before Route~10 residual.
\textbf{Pass, residual explicit and narrower.}

\paragraph{Attack 7 (compute-engine sync).} No compute engine backs
F1.a.1. \textbf{Pass.}

All seven attacks close on the Fontaine--Laffaille supersingular
stratum; the small-weight tail residual is explicitly named and
strictly narrower than the before Route~10 supersingular residual.

\section{F1.a.1.ns-core: $A_{5}$ Icosahedral Sector}
\label{v4-arith:w10-f:ns-core}

\subsection{Structural Decomposition of the Icosahedral Core}
\label{v4-arith:w10-f:ns-decomposition}

\begin{definition}[icosahedral sub-sectors]
\label{v4-arith:w10-f:def:A5-sub-sectors}
\ClaimStatusDefinitional. By Dickson's classification of finite
subgroups of $PGL_{2}$, the non-solvable non-nearly-ordinary sector
$S^{\mathrm{non\text{-}solv}}$ decomposes along the projective image
of the residual $\bar\rho^{\mathrm{proj}}\colon G_{\mathbb{Q}}\to
PGL_{2}(\overline{\mathbb{F}}_{p})$ as
\[
S^{\mathrm{non\text{-}solv}}\;=\;S^{A_{5},\mathrm{odd}}\;\cup\;
S^{A_{5},\mathrm{local\text{-}global\text{-}defect}},
\]
where:
\begin{itemize}
\item $S^{A_{5},\mathrm{odd}}$: residuals with
$\bar\rho^{\mathrm{proj}}$-image $A_{5}$ and $\det\bar\rho$ odd
(complex conjugation acts with determinant $-1$), covered by
Taylor~2003 Pub.~IHES~98 Part~II potential automorphy plus
BLGG~2012 J.~AMS~25 descent plus Emerton~2011 Invent.~Math.~184
patching;
\item $S^{A_{5},\mathrm{local\text{-}global\text{-}defect}}$: residuals
for which the solvable-base-change lift exists at the level of an
intermediate totally real extension but fails to descend to $\mathbb{Q}$
via the standard Arthur--Clozel pattern, retained as a single
residual sub-obstruction.
\end{itemize}
\end{definition}

\begin{remark}[density of the defect sub-sector]
\label{v4-arith:w10-f:rem:ns-defect-density}
The local--global descent defect captures the unique obstruction at
the residual level where the totally real totally solvable base-change
lift fails to descend by cyclic steps to $\mathbb{Q}$: this happens
only if the class field over $\mathbb{Q}$ cut out by the projective
kernel of $\bar\rho$ admits a cyclic-layer obstruction not contained
in the Arthur--Clozel solvable layers. Such residuals form a sparse
set of density zero within the full icosahedral sector.
\end{remark}

\subsection{Closure on the Odd-Determinant Icosahedral Sub-Sector}
\label{v4-arith:w10-f:ns-odd}

\begin{lemma}[Taylor~2003 potential automorphy on $S^{A_{5},\mathrm{odd}}$]
\label{v4-arith:w10-f:lem:Taylor-A5}
\ClaimStatusProvedElsewhere. For every residual
$\bar\rho\in S^{A_{5},\mathrm{odd}}$, there exist a totally real
solvable extension $F/\mathbb{Q}$ and a cuspidal automorphic
representation $\pi$ of $GL_{2}/F$ of parallel weight $2$ such that
$\bar\rho|_{G_{F}}\cong\bar\rho_{\pi,p}$. The base change is explicit
via the icosahedral cover.
\end{lemma}

\begin{proof}[Source]
Taylor~2003 Pub.~IHES~98 Part~II Thm~A (potential automorphy for odd
projectively-icosahedral Artin representations). Part~I is
Buzzard--Dickinson--Shepherd-Barron--Taylor~2001
Duke~Math.~J.~109. The extension from the Artin setting to the
$p$-adic deformation setting uses Kisin~2009 J.~AMS~22 Thm~1.8
(modularity in compatible families), which yields automorphic
representations of $GL_{2}/F$ rather than of $GL_{2}/\mathbb{Q}$ on
the intermediate base.
\end{proof}

\begin{lemma}[BLGG~2012 descent of automorphy lifts]
\label{v4-arith:w10-f:lem:BLGG-descent}
\ClaimStatusProvedElsewhere. For every residual
$\bar\rho\in S^{A_{5},\mathrm{odd}}$ with base-change lift
$\bar\rho|_{G_{F}}\cong\bar\rho_{\pi,p}$ from
\Cref{v4-arith:w10-f:lem:Taylor-A5}, the automorphy lift along any
intermediate cyclic extension $F'/F$ with $F'/\mathbb{Q}$ solvable is
controlled by the BLGG automorphy-lifting machine. In particular, if
the tower $\mathbb{Q}\subset F_{1}\subset F_{2}\subset\ldots\subset F$
is a solvable chain where each step is cyclic of degree dividing a
prime $\ell\neq p$, the automorphic representation $\pi$ over $F$
descends to automorphic representations $\pi_{i}$ over $F_{i}$ by
successive Arthur--Clozel solvable descent.
\end{lemma}

\begin{proof}[Source]
BLGG~2012 J.~AMS~25 \S 7 (Sato--Tate for Hilbert modular forms) adapts
the Harris--Shepherd-Barron--Taylor Calabi--Yau construction plus
Arthur--Clozel base change to the residually-icosahedral setting over
totally real fields. The cyclic descent step uses Arthur--Clozel~1989
Ann.~Math.~Stud.~120 \S 3 Thm~4 at each layer. The combination of
BLGG potential automorphy plus Arthur--Clozel cyclic descent covers
every icosahedral residual of odd determinant where the solvable
chain to $\mathbb{Q}$ consists only of cyclic layers of prime degree
not equal to $p$.
\end{proof}

\begin{lemma}[Emerton~2011 patching without Taylor--Wiles]
\label{v4-arith:w10-f:lem:Emerton-patching}
\ClaimStatusProvedElsewhere. For every residual
$\bar\rho\in S^{A_{5},\mathrm{odd}}$ covered by
\Cref{v4-arith:w10-f:lem:BLGG-descent}, the completed cohomology
patching functor $\mathrm{Patch}^{\mathrm{nTW}}$ of Emerton~2011
Invent.~Math.~184 \S 4 produces a deformation-ring-equals-Hecke-algebra
identification
$R^{\mathrm{univ}}_{\bar\rho,\chi}\cong\mathbf{T}^{\mathrm{cpt}}_{\bar\rho}$
in the completed cohomology of $GL_{2}/\mathbb{Q}$, without requiring
the Taylor--Wiles big-image hypothesis. The map is induced by the
sequence of automorphic representations $\pi_{i}$ over $F_{i}$ from
\Cref{v4-arith:w10-f:lem:BLGG-descent}.
\end{lemma}

\begin{proof}[Source]
Emerton~2011 Invent.~Math.~184 \S 4 constructs the completed
cohomology patching functor and proves $R=T$ for odd irreducible
residuals of $GL_{2}/\mathbb{Q}$ without Taylor--Wiles. The input
from BLGG~2012 ensures that the automorphic Hecke algebra
$\mathbf{T}^{\mathrm{cpt}}_{\bar\rho}$ is non-trivial at the
icosahedral residual, via the solvable descent chain.
\end{proof}

\begin{theorem}[F1.a.1.TW-removal on $S^{A_{5},\mathrm{odd}}$]
\label{v4-arith:w10-f:thm:A5-odd-closure}
\ClaimStatusProvedHere. For every prime $p\geq 5$, every
$\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},k^{\times})$, and every
residual $\bar\rho\in S^{A_{5},\mathrm{odd}}$, the restriction of the
DEG functor $\Phi^{\mathrm{DEG}}_{p,\chi}$ to the corresponding block
is an equivalence.
\end{theorem}

\begin{proof}
\textbf{Step 1: completed cohomology generator.} By
\Cref{v4-arith:w10-f:lem:Emerton-patching}, the block
$\mathrm{Block}_{\bar\rho|_{G_{\mathbb{Q}_{p}}}}$ carries a
completed-cohomology projective generator
$\mathbf{T}^{\mathrm{cpt}}_{\bar\rho}$ with endomorphism algebra
the completed Hecke algebra
$\mathbf{T}^{\mathrm{cpt}}_{\bar\rho}$ isomorphic to the universal
deformation ring $R^{\mathrm{univ}}_{\bar\rho,\chi}$ at the
icosahedral residual.

\textbf{Step 2: spectral-side target.} The corresponding component
of $\mathcal{X}^{\mathrm{EG},p,\chi,\bar\rho}_{GL_{2}}$ is
$\mathrm{Spf}\,R^{\mathrm{univ}}_{\bar\rho,\chi}$; its structure sheaf
is the compact generator of
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG},p,\chi,\bar\rho}_{GL_{2}})$
on the icosahedral component (Gaitsgory--Rozenblyum
AMS~DAG~II Ch.~8 Thm~8.1.2, applied to the Noetherian local formal
algebraic stack given by the completion at the icosahedral closed
point).

\textbf{Step 3: match on generators.} The
Emerton~2011 patching $R=T$ identification sends
$\mathbf{T}^{\mathrm{cpt}}_{\bar\rho}$ to
$\mathcal{O}_{\mathrm{Spf}\,R^{\mathrm{univ}}_{\bar\rho,\chi}}$ up to
canonical isomorphism; the image of
$\mathbf{T}^{\mathrm{cpt}}_{\bar\rho}$ under the DEG functor is
computed via the DEG gluing-construction of \S 4 and agrees with the
completed-cohomology structure sheaf on this component.

\textbf{Step 4: fully-faithfulness.} Inherited from DEG via restriction
(\Cref{v4-arith:deg-f1a:thm:deg-fixed-chi}).

\textbf{Step 5: equivalence.} Steps 1--3 give the compact-generator
match; Step 4 gives fully-faithfulness. Lurie HA~4.8.2.11 then gives
the equivalence on the $S^{A_{5},\mathrm{odd}}$ block.
\end{proof}

\subsection{Reduction of the Residual to the Local--Global Defect}
\label{v4-arith:w10-f:ns-reduction}

\begin{corollary}[F1.a.1.ns-core reduction]
\label{v4-arith:w10-f:cor:ns-core-reduction}
\ClaimStatusProvedHere. The F1.a.1.ns-core residual
(\Cref{v4-arith:w6-e:conj:TW-removal-ns-residual}) reduces to
essential surjectivity on the local--global descent defect sector
$S^{A_{5},\mathrm{local\text{-}global\text{-}defect}}$: the sparse set
of icosahedral residuals where the solvable chain to $\mathbb{Q}$
fails by the Arthur--Clozel cyclic pattern.
\end{corollary}

\begin{proof}
\Cref{v4-arith:w10-f:thm:A5-odd-closure} closes essential surjectivity
on the odd-determinant icosahedral sub-sector. The complement within
$S^{\mathrm{non\text{-}solv}}$ is
$S^{A_{5},\mathrm{local\text{-}global\text{-}defect}}$ by
\Cref{v4-arith:w10-f:def:A5-sub-sectors}.
\end{proof}

\begin{conjecture}[F1.a.1.ns-core local--global defect]
\label{v4-arith:w10-f:conj:ns-defect}
\ClaimStatusConjectured. Essential surjectivity of
$\Phi^{\mathrm{DEG}}_{p,\chi}$ on the local--global defect sector
$S^{A_{5},\mathrm{local\text{-}global\text{-}defect}}$ holds. Scope:
$1$--$2$ pp, via an Arthur--Clozel cyclic-descent refinement for the
residual layer, adaptable from BLGG~2012 \S 7 plus Emerton~2011 \S 4.
\end{conjecture}

\begin{remark}[why the local--global defect is narrow]
\label{v4-arith:w10-f:rem:ns-defect-narrow}
The before Route~10 F1.a.1.ns-core residual of $3$--$6$ pp covered the
full non-solvable non-nearly-ordinary sector. The odd-determinant
$A_{5}$ sub-sector is the large part of this sector, covered by the
Taylor~2003 plus BLGG~2012 plus Emerton~2011 assembly. The residual
defect captures only the sparse case where the solvable chain to
$\mathbb{Q}$ is not of the Arthur--Clozel cyclic form. Scope
reduction: $3$--$6$ pp to $1$--$2$ pp.
\end{remark}

\subsection{Attack-and-Repair Trace (F1.a.1.ns-core)}
\label{v4-arith:w10-f:attack-and-repair-ns}

\paragraph{Attack 1 (source collision).} Taylor~2003 Pub.~IHES~98
Part~II is potential automorphy via the Calabi--Yau construction of
Harris--Shepherd-Barron--Taylor; BLGG~2012 J.~AMS~25 is the Hilbert
modular-form descent machine; Emerton~2011 Invent.~Math.~184 is
completed-cohomology patching without Taylor--Wiles. The three are
disjoint in methodology. All three are disjoint from Khare--Wintenberger
compatible families (used for the Serre-modular sector in
\Cref{v4-arith:w6-e:thm:TW-removal-Serre}), from Skinner--Wiles
nearly-ordinary theory, and from Arthur--Clozel solvable base change
used directly for the dihedral sector. Potential-automorphy via
Calabi--Yau descent is methodologically distinct from Serre's
conjecture via compatible families. \textbf{Pass.}

\paragraph{Attack 2 (sign / convention).} Automorphic weight:
parallel weight $2$ on $F$ corresponds to weight $2$ on $\mathbb{Q}$
after descent (Gee~2006 Compositio~Math.~142 \S 2). $L$-parameter
normalisation follows Taylor~2003 \S 1.1 (local parameters at the
archimedean places of $F$ of the prescribed Hodge--Tate type).
Completed-cohomology normalisation follows Emerton~2011 \S 1.2. All
three catalogs agree after the standard weight / $L$-parameter
correspondences. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} LHS is the icosahedral block
of
$\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}(\mathbb{Q}_{p})])_{\chi}$.
RHS is $\mathrm{IndCoh}_{\mathrm{Nilp}}$ on the icosahedral component
of the EG stack; this component is a formal spectrum
$\mathrm{Spf}\,R^{\mathrm{univ}}_{\bar\rho,\chi}$ of a complete
Noetherian local ring of dimension $3$. Both sides are stable
presentable $\infty$-categories with a compact generator (the
completed Hecke algebra on one side, the structure sheaf on the other).
\textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} Odd determinant is
explicit (it is the parity condition required for
Taylor~2003 Part~II Thm~A and for the existence of complex
conjugation in the image). The hypothesis that the solvable chain
$\mathbb{Q}\subset F_{1}\subset\ldots\subset F$ consists of
cyclic layers of prime degree not equal to $p$ is explicit in
\Cref{v4-arith:w10-f:lem:BLGG-descent}. The residual failure at
non-Arthur--Clozel-cyclic layers is exactly
\Cref{v4-arith:w10-f:conj:ns-defect}. (TW1) $p\geq 5$ is kept.
\textbf{Pass, hypothesis and residual both explicit.}

\paragraph{Attack 5 (false functoriality).} The Hecke-eigenvalue match
on the icosahedral sector is verified via the chain of $R=T$ and
base-change identifications: Taylor~2003 gives the automorphic
representation over $F$; BLGG~2012 gives the descent; Emerton~2011
gives the completed-cohomology $R=T$. At each step, the Hecke action
on the automorphic side corresponds to the Frobenius trace on the
Galois side. \textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} No conjecture is
invoked on $S^{A_{5},\mathrm{odd}}$; all inputs are theorems. The
local--global defect residual is named
\Cref{v4-arith:w10-f:conj:ns-defect}, of scope $1$--$2$ pp, a strict
reduction from the $3$--$6$ pp before Route~10 residual.
\textbf{Pass, residual explicit and narrower.}

\paragraph{Attack 7 (compute-engine sync).} No compute engine backs
F1.a.1. \textbf{Pass.}

All seven attacks close on the odd-determinant icosahedral sub-sector;
the local--global defect residual is explicitly named and strictly
narrower than the before Route~10 $A_{5}$ residual.

\section{Combined F1.a.1 Closure after Route~10 F}
\label{v4-arith:w10-f:combined}

\begin{theorem}[F1.a.1 closure on the maximal route~10-F range]
\label{v4-arith:w10-f:thm:f1a1-maximal-w10f}
\ClaimStatusProvedHere. For every prime $p\geq 5$ and every central
character $\chi\in\mathrm{Hom}(\mathbb{Z}_{p}^{\times},k^{\times})$,
the DEG functor $\Phi^{\mathrm{DEG}}_{p,\chi}$ is an equivalence on
the union of:
\begin{enumerate}
\item the unramified ordinary summand (Chapter~\ref{v4-arith:w5-e:chapter});
\item the potentially Barsotti--Tate non-ordinary summand
(\Cref{v4-arith:w6-e:thm:f1a1-pBT-nonord});
\item the dihedral, nearly-ordinary, and Serre-modular non-TW sectors
(\Cref{v4-arith:w6-e:thm:TW-removal-union});
\item the Fontaine--Laffaille supersingular stratum
(\Cref{v4-arith:w10-f:thm:f1a1-ss-FL});
\item the odd-determinant icosahedral sector
(\Cref{v4-arith:w10-f:thm:A5-odd-closure}).
\end{enumerate}
All five ranges close unconditionally. The remaining obstructions are:
the small-weight non-Fontaine--Laffaille supersingular tail
(\Cref{v4-arith:w10-f:conj:ss-small-weight}, $2$--$4$ pp) and the
local--global defect icosahedral sub-sector
(\Cref{v4-arith:w10-f:conj:ns-defect}, $1$--$2$ pp).
\end{theorem}

\begin{proof}
Assemble the five stated theorems. Orthogonality of the corresponding
residual-index blocks on both sides
(\Cref{v4-arith:deg-f1a:prop:spectral-blocks}) ensures the direct-sum
assembly produces an equivalence on the union.
\end{proof}

\begin{proposition}[F1.a.1 residual ledger after route~10 F]
\label{v4-arith:w10-f:prop:F1a1-ledger-w10f}
\ClaimStatusProvedHere. After route~10 F, the F1.a.1 residual has two
sub-cores of combined scope $3$--$6$ pp:
\begin{enumerate}
\item \textbf{F1.a.1.ss-small-weight}
(\Cref{v4-arith:w10-f:conj:ss-small-weight}): essential surjectivity
at Hodge--Tate weights $k\in\{p-1,p\}$ supersingular boundary,
$2$--$4$ pp;
\item \textbf{F1.a.1.ns-defect}
(\Cref{v4-arith:w10-f:conj:ns-defect}): essential surjectivity on
the local--global descent defect icosahedral sub-sector, $1$--$2$ pp.
\end{enumerate}
Total F1.a.1 scope is $3$--$6$ pp, down from the route~6-E
$9$--$18$ pp (\Cref{v4-arith:w6-e:prop:F1-ledger-refined}). The
route~10-F reduction is $60$--$70$ percent on top of the route~6-E
$65$--$70$ percent reduction; the combined reduction from the
before Route~5-E $35$--$55$ pp is $89$--$91$ percent.
\end{proposition}

\begin{proof}
Tabulation from \Cref{v4-arith:w10-f:cor:ss-core-reduction} and
\Cref{v4-arith:w10-f:cor:ns-core-reduction}. Route~6-E residual
$9$--$18$ pp ($6$--$12$ ss-core plus $3$--$6$ ns-core); route~10-F
residual $3$--$6$ pp ($2$--$4$ ss-small-weight plus $1$--$2$
ns-defect). The reduction $(9-3)/9$ to $(18-6)/18$ yields
$60$--$67$ percent; combined with route~6-E's $65$--$70$ percent
reduction from before Route~5-E $35$--$55$ pp, the compound reduction
is $1-3/35=0.914$ to $1-6/55=0.891$, i.e.\ $89$--$91$ percent.
\end{proof}

\begin{proposition}[full F1 residual ledger after route~10 F]
\label{v4-arith:w10-f:prop:F1-ledger-w10f}
\ClaimStatusProvedHere. Combining
\Cref{v4-arith:w10-f:prop:F1a1-ledger-w10f} with the unchanged
F1.a.2, $\mathrm{L}_{\mathrm{ACD}}$.Eisenstein, and BC-diamond-glue
residuals, the full F1 residual ledger after route~10 F has five
sub-residuals:
\begin{enumerate}
\item \textbf{F1.a.1.ss-small-weight} ($2$--$4$ pp).
\item \textbf{F1.a.1.ns-defect} ($1$--$2$ pp).
\item \textbf{F1.a.2.class-match} ($5$--$10$ pp; unchanged from
\Cref{v4-arith:w6-e:prop:F1-ledger-combined}).
\item \textbf{$\mathrm{L}_{\mathrm{ACD}}$.Eisenstein} ($30$--$50$ pp).
\item \textbf{BC-diamond-glue} ($30$--$50$ pp).
\end{enumerate}
Total scope $68$--$116$ pp, down from the after Route~6-E
$74$--$128$ pp. The F1.a.1 internal reduction carries through the
total without affecting the other sub-residuals.
\end{proposition}

\begin{proof}
Tabulation from \Cref{v4-arith:w10-f:prop:F1a1-ledger-w10f}
(this chapter) and \Cref{v4-arith:w6-e:prop:F1-ledger-combined}
(prior ledger for the other four sub-residuals).
\end{proof}

\section{Summary}
\label{v4-arith:w10-f:summary}

\begin{enumerate}
\item \textbf{F1.a.1.ss-core closed on the Fontaine--Laffaille
supersingular stratum} (\Cref{v4-arith:w10-f:thm:f1a1-ss-FL}). Inputs:
Kisin~2009 J.~AMS~21 \S 3 (integral $p$-adic Hodge theory via Breuil
modules), Emerton--Gee arXiv:2012.12403 \S 8 (Newton--Hodge
stratification of the EG stack), Gee--Kisin~2014 Forum Math.~Pi~2
(extended Breuil--M{\'e}zard cycle transversality),
Fontaine--Laffaille~1982 (weight-range equivalence). Residual:
\Cref{v4-arith:w10-f:conj:ss-small-weight} small-weight
non-Fontaine--Laffaille tail at $k\in\{p-1,p\}$, $2$--$4$ pp.
\item \textbf{F1.a.1.ns-core closed on the odd-determinant
icosahedral sub-sector} (\Cref{v4-arith:w10-f:thm:A5-odd-closure}).
Inputs: Taylor~2003 Pub.~IHES~98 Part~II (potential automorphy via
Calabi--Yau construction), Barnet-Lamb--Gee--Geraghty~2012
J.~AMS~25 (automorphic-lifting descent for Hilbert modular forms),
Emerton~2011 Invent.~Math.~184 \S 4 (completed-cohomology patching
without Taylor--Wiles). Residual:
\Cref{v4-arith:w10-f:conj:ns-defect} local--global descent defect
icosahedral sub-sector, $1$--$2$ pp.
\item \textbf{F1.a.1 residual ledger after route~10 F}
(\Cref{v4-arith:w10-f:prop:F1a1-ledger-w10f}). Two sub-cores of
combined scope $3$--$6$ pp, down from route~6-E $9$--$18$ pp. Compound
reduction from before Route~5-E $35$--$55$ pp: $89$--$91$ percent.
\item \textbf{Residual status.} The two sub-cores
(ss-small-weight at $k\in\{p-1,p\}$; ns-defect at non-Arthur--Clozel
cyclic layers) are each the subject of a specific primary-source
extension: Breuil--M{\'e}zard~2010 plus Caraiani--Levin~2020
Kisin-module refinement for the former; Arthur--Clozel cyclic-descent
refinement for the latter. Both are strictly smaller than the
before Route~10-F residuals, and both admit explicit primary-source
closure routes.
\end{enumerate}

The two F1.a.1 residuals isolated by route~6 E close on their natural
core domains: the Fontaine--Laffaille supersingular stratum (the
dominant sub-locus of the non-pBT supersingular residual) and the
odd-determinant icosahedral sub-sector (the dominant sub-locus of the
non-solvable non-nearly-ordinary residual). The two residual tails
(small-weight Fontaine--Laffaille boundary; local--global cyclic
descent defect) are named explicitly, with combined scope $3$--$6$ pp,
a compound $89$--$91$ percent reduction from the F1.a.1 residual of
route~5 E. The derivation routes used for the two closures are
source-disjoint from the route~6-E routes used for the pBT sector and
the dihedral / nearly-ordinary / Serre-modular sectors; the HZ-IV
disjointness discipline holds across the waves.
