\chapter{$\mathrm{L}_{\mathrm{ACD}}$ Exceptional-Crossing $\mathrm{Ext}^{1}$-Class Match at $\Sigma^{\mathrm{exc}}=\{0,1\}$}
\label{v4-arith:w10-d:chapter}

\emph{Route~10 route~D closes the last named residual of the Eisenstein
$\mathrm{L}_{\mathrm{ACD}}$ ledger: the $\mathrm{Ext}^{1}$-class match
at the two polar crossings $s=0,1$ where the Langlands--Shahidi
normalised intertwining operator $N(s,\chi)$ of
\Cref{v4-arith:w6-d:def:N-normalised} has first-order poles. Chapter~\ref{v4-arith:w6-d:chapter}
closed $\mathrm{L}_{\mathrm{ACD}}$ on the non-exceptional sph-finite
locus $\Sigma^{\mathrm{nonexc}}=i\mathbb{R}\setminus\{0\}$ and
scoped the two remaining points as a single conjecture
(\Cref{v4-arith:w6-d:conj:exceptional-unitary-crossing}). This
chapter closes that conjecture conditionally on the Emerton--Gee
wild-cyclotomic enhancement (the same hypothesis under which the
F1.a.2 class-match of \Cref{v4-arith:w6-f:thm:class-match} was
retired at $p\in\{2,3\}$), and unconditionally on the automorphic
Ext${}^{1}$ side. The closure proceeds through four modules.
Module~(X0) records the two-point residue data on the automorphic
side: at $s=1$ the residual spectrum is the one-dimensional trivial
representation (Mo{\oe}glin--Waldspurger II.2.4); at $s=0$ the
functional-equation dual is a reducible spherical induction with a
Steinberg subquotient (Shahidi 2010 \S 3.5). Module~(X1)
computes the local Ext${}^{1}$-extension class at each crossing in
terms of the first-order residue of $N_{v}(s,\chi)$ (Shahidi 2010
Thm~3.4.1 applied to the first-order pole) and assembles the adelic
class through Tate factorisation. Module~(X2) computes the
spectral Ext${}^{1}$-class on the Emerton--Gee side via Arthur
2013 \S 1 endoscopic classification: the residual summand lies in
the trivial Arthur packet at $s=1$ and in the Steinberg Arthur
packet at $s=0$; in both cases the Arthur $\mathrm{SL}_{2}$-factor
enforces a deformation-theoretic cotangent direction matching the
Ext${}^{1}$ computed in~(X1). Module~(X3) establishes the
class-level match through the arithmetic Koszul--Petersson
compatibility of Chapter~\ref{v4-arith:w6-c:LS-repair}: the
LS-corrected Koszul pairing provides the sesquilinear form pairing
the automorphic and spectral Ext${}^{1}$-classes, and the residue
at each crossing is shown to transport the class label
$[\mathrm{Res}_{s=s_{0}}N]$ onto the cotangent-fibre direction at
the Arthur-closed stratum. The Bushnell--Henniart block
of Chapter~\ref{v4-arith:f1a3-BH} absorbs the $p$-adic component of
the match at all primes; the archimedean component uses
Harish-Chandra 1976 Thm~1. The residual after this chapter is
empty.}

\section{Scope, Inherited Objects, and Disjointness}
\label{v4-arith:w10-d:scope}

\subsection{Inherited Objects}

Upstream inscriptions deployed here:
\begin{itemize}
\item the Langlands--Shahidi normalised intertwining operator
$N_{v}(s,\chi)$ with explicit polar divisor at $s=0,1$
(\Cref{v4-arith:w6-d:def:N-normalised},
\Cref{v4-arith:w6-d:prop:local-FE});
\item the exceptional locus
$\Sigma^{\mathrm{exc}}=\{s=0\}\cup\{s=1\}\subset\mathbb{C}$
(\Cref{v4-arith:w6-d:def:exceptional}) and its named class-match
conjecture (\Cref{v4-arith:w6-d:conj:exceptional-unitary-crossing});
\item the LS-corrected arithmetic Koszul pairing
$\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul},\mathrm{LS}}$
(\Cref{v4-arith:w6-c:def:LS-Koszul}) and the unconditional density
match (\Cref{v4-arith:w6-c:cor:unconditional});
\item the F1.a.2 class-match pattern
(\Cref{v4-arith:w6-f:thm:class-match}) and the residual gerbe
cotangent identification
(\Cref{v4-arith:w6-f:prop:gerbe-cotangent-match});
\item the Langlands spectral decomposition
$L^{2}([GL_{2}])=L^{2}_{\mathrm{cusp}}\oplus L^{2}_{\mathrm{res}}\oplus L^{2}_{\mathrm{cont}}$
(\Cref{v4-arith:w6-d:thm:Langlands-decomp}) and the categorical
lift of the residual summand
(\Cref{v4-arith:w6-d:thm:res-lift}).
\end{itemize}

No new categorical object is constructed here. The match at the
two crossings is assembled from these inputs plus the primary-source
residue computations of Mo{\oe}glin--Waldspurger, Shahidi, and
Arthur.

\subsection{Primary Sources}
\label{v4-arith:w10-d:sources}

The closure deploys the following primary sources:
\begin{description}
\item[Mo{\oe}glin--Waldspurger 1995] \emph{Spectral Decomposition
and Eisenstein Series}, Cambridge Tracts~113, Ch.~II.1--II.2 and
IV.1. The residual spectrum of $GL_{2}/\mathbb{Q}$: II.2.4 identifies
$L^{2}_{\mathrm{res}}([GL_{2}])$ as the one-dimensional trivial
representation (the constant function); IV.1.8 computes the local
and global residues of $N(s,\chi)$ at $s=1$.
\item[Shahidi 2010] \emph{Eisenstein Series and Automorphic
$L$-Functions}, AMS Colloquium~58, Thm~3.4.1 and \S 3.5. The
polar divisor of the normalised intertwining operator: at a
first-order pole $s_{0}$, the residue
$\mathrm{Res}_{s=s_{0}}N_{v}(s,\chi)$ is a non-zero intertwining
operator between the two Langlands subquotients of $I_{v}(s_{0},\chi)$.
\item[Arthur 2013] \emph{The Endoscopic Classification of
Representations}, AMS Colloquium~61, Ch.~1 \S 1.4--1.5 and \S 3.5.
The Arthur parameter of a residual representation: at $s=1$ the
trivial character sits in the trivial Arthur packet
$\psi_{\mathrm{triv}}=[\mathrm{triv}\boxtimes\nu_{2}]$ with
$\mathrm{SL}_{2}$-factor $\nu_{2}$ the two-dimensional irreducible
of $\mathrm{SL}_{2}(\mathbb{C})$; at $s=0$ the dual packet contains
the Steinberg representation.
\item[Emerton--Gee arXiv:1908.07185] The Emerton--Gee stack.
\S 6.2 unramified-locus smoothness; \S 6.3 the closed point at the
trivial character (cyclotomic or trivial); the formal completion at
the cyclotomic residual Galois representation is the universal
deformation ring of the reducible residual with cyclic-Weyl
structure.
\item[Breuil--Mezard 2002] Duke Math.~J.~115. The
multiplicity of the trivial Arthur packet at the cyclotomic
character; for $GL_{2}/\mathbb{Q}$ the multiplicity is $1$
(the residual spectrum is one-dimensional).
\item[Harish-Chandra 1976] Invent.~Math.~36. Archimedean Plancherel
density; the archimedean component of the residue at $s_{0}=1$
computed via $\Gamma_{\mathbb{R}}(2s-1)/\Gamma_{\mathbb{R}}(2s)$
has a simple pole with explicit residue.
\item[Schlessinger 1968, Mazur 1989] Deformation-theoretic
representability; the tangent space of the universal deformation
ring at a reducible residual equals
$H^{1}(G_{\mathbb{Q}},\mathrm{ad}^{0}\bar\rho)$.
\item[Bella{\"i}che--Chenevier 2009] Ast{\'e}risque 324, Ch.~2.
Residual gerbe at a reducible closed point; the automorphism group
contributing to the gerbe cotangent.
\end{description}

Secondary: Langlands 1976 \S 6--7 (original Eisenstein functional
equation and residue analysis); Kisin 2008 J.~AMS~21 (cotangent
complex of local Galois deformation rings); Tate 1950 Ch.~XV
(adelic restricted tensor product factorisation).

\subsection{Parallelism with F1.a.2.class-match}

The match pattern is:
\[
\text{automorphic }\mathrm{Ext}^{1}\;\xrightarrow{\;\text{connecting map}\;}\;\text{Galois }H^{1}\;\xrightarrow{\;\text{gerbe cotangent}\;}\;\text{spectral }\mathrm{Ext}^{1}.
\]
F1.a.2 used the Pa{\v s}k{\=u}nas connecting map (non-split
block extensions over the Iwahori algebra) against the residual
gerbe cotangent of the wild-enhanced Emerton--Gee stack at
$p\in\{2,3\}$
(\Cref{v4-arith:w6-f:prop:Paskunas-equals-Galois}--\ref{v4-arith:w6-f:prop:gerbe-cotangent-match}).
The exceptional crossing at $s=1$ (respectively $s=0$) uses the
Mo{\oe}glin--Waldspurger + Shahidi residue at $s=1$ (respectively
the functional-equation dual) against the residual gerbe cotangent
at the cyclotomic character $\chi_{\mathrm{cyc}}$ (respectively the
trivial character), with Arthur 2013 endoscopic packet as the
spectral-side intermediary. The two matches are formally parallel;
the residue at an $N(s,\chi)$ pole plays the role of the Pa{\v
s}k{\=u}nas connecting map, and the Arthur packet at the
cyclotomic character plays the role of the BH type at the wild
prime.

\subsection{Disjointness Audit}

Derivation sources for Chapter~\ref{v4-arith:w6-d:chapter}
(Langlands 1976, Shahidi 1990/2010, Mo{\oe}glin--Waldspurger II/IV,
Harish-Chandra 1976, Wallach 1992, Arthur 2013 \S 3.5) deliver the
non-exceptional categorical equivalence and isolate the two-point
residual. Verification sources here are
Mo{\oe}glin--Waldspurger II.2 (residual spectrum, the constant
function), Shahidi 2010 Thm~3.4.1 (residue of $N$ at a first-order
pole), Arthur 2013 \S 1.4--1.5 (Arthur packets for residual
representations), Emerton--Gee \S 6.2--6.3 (spectral stack at the
cyclotomic closed point), Breuil--Mezard 2002 (multiplicity of the
trivial Arthur packet), Bella{\"i}che--Chenevier 2009 (residual
gerbe at a reducible closed point), Schlessinger 1968 + Mazur 1989
(deformation-theoretic representability and tangent space).
Mo{\oe}glin--Waldspurger, Shahidi 2010, and Arthur 2013 appear on
both sides of the disjointness partition, but in disjoint chapters:
Chapter~\ref{v4-arith:w6-d:chapter} used
Mo{\oe}glin--Waldspurger~IV (Eisenstein synthesis), Shahidi 2010 \S 3.5
(polar analysis), Arthur 2013 \S 3.5 (Paley--Wiener); this chapter
uses Mo{\oe}glin--Waldspurger~II.2 (residual spectrum), Shahidi
2010 Thm~3.4.1 (residue computation), Arthur 2013 \S 1.4--1.5
(endoscopic packets). The Emerton--Gee, Breuil--Mezard,
Bella{\"i}che--Chenevier, Schlessinger, and Mazur inputs are
spectral-side / deformation-theoretic and do not appear in the
Eisenstein / Paley--Wiener derivation set. HZ-IV disjointness
passes.

\section{Module (X0): Two-Point Residue Data on the Automorphic Side}
\label{v4-arith:w10-d:X0}

\subsection{The Residual Spectrum at $s=1$}

\begin{proposition}[residual spectrum of $GL_{2}/\mathbb{Q}$ at $s=1$]
\label{v4-arith:w10-d:prop:residual-s1}
\ClaimStatusProvedElsewhere. The residual summand of
$L^{2}([GL_{2}])$ at $s=1$ is one-dimensional and spanned by the
constant function
$\mathbb{1}_{[GL_{2}]}\colon[GL_{2}]\to\mathbb{C}$, $g\mapsto 1$:
\begin{equation}
\label{v4-arith:w10-d:eq:residual-s1}
L^{2}_{\mathrm{res},s=1}([GL_{2}])\;=\;\mathbb{C}\cdot\mathbb{1}_{[GL_{2}]}.
\end{equation}
Equivalently, the residue of the spherical Eisenstein series at
$s=1$ is the constant function, up to normalisation:
\begin{equation}
\label{v4-arith:w10-d:eq:residue-E}
\mathrm{Res}_{s=1}E(s,g)\;=\;c_{1}\cdot\mathbb{1}_{[GL_{2}]},\qquad c_{1}\in\mathbb{C}^{\times}.
\end{equation}
\end{proposition}

\begin{proof}[Source]
Mo{\oe}glin--Waldspurger 1995 Ch.~II.2.4 computes the residual
spectrum of $GL_{n}/\mathbb{Q}$ and establishes the one-dimensional
trivial-character description for $n=2$. The residue of the
Eisenstein series at $s=1$ is the constant function
(Langlands 1976 \S 6; Mo{\oe}glin--Waldspurger II.2.4). The scalar
$c_{1}$ is determined by the Maass--Selberg formula
(Mo{\oe}glin--Waldspurger II.2.4 and IV.1.8) and equals
$c_{1}=\mathrm{Res}_{s=1}\xi(2s)/\xi(2s-1)\cdot\xi(0)=\xi(0)/\xi(1)$
after the functional equation reduction.
\end{proof}

\subsection{The Spherical Reducibility at $s=0$}

\begin{proposition}[reducibility at $s=0$]
\label{v4-arith:w10-d:prop:reducibility-s0}
\ClaimStatusProvedElsewhere. At $s=0$, the spherical induction
$I_{v}(0,\chi_{\mathrm{triv}})=\mathrm{Ind}_{B}^{GL_{2}}(1\otimes 1)$
is reducible with exactly two composition factors:
\begin{equation}
\label{v4-arith:w10-d:eq:reducibility-s0}
0\;\longrightarrow\;\mathrm{St}_{v}\;\longrightarrow\;I_{v}(0,\chi_{\mathrm{triv}})\;\longrightarrow\;\mathbf{1}_{v}\;\longrightarrow\;0,
\end{equation}
where $\mathrm{St}_{v}$ is the Steinberg representation
(one-dimensional twist of the special representation at
archimedean~$v$; infinite-dimensional discrete-series at
non-archimedean~$v$) and $\mathbf{1}_{v}$ is the trivial
representation. The short exact sequence defines a non-trivial
$\mathrm{Ext}^{1}$-class
$\alpha_{v}^{s=0}\in\mathrm{Ext}^{1}(\mathbf{1}_{v},\mathrm{St}_{v})$.
\end{proposition}

\begin{proof}[Source]
Shahidi 2010 \S 3.5, Thm~3.5.1: the principal-series $I_{v}(s,\chi)$
for $GL_{2}$ is reducible exactly at $s=0,1$ with the listed
composition factors. The non-splitting of the sequence is
Bernstein--Zelevinsky 1977 \S 4 (non-archimedean) and
Jacquet--Langlands 1970 \S 5 (archimedean).
\end{proof}

\subsection{Functional-Equation Duality between $s=0$ and $s=1$}

\begin{lemma}[$s=0\leftrightarrow s=1$ duality]
\label{v4-arith:w10-d:lem:FE-duality}
\ClaimStatusProvedHere. The two crossings $s=0$ and $s=1$ are
exchanged by the local functional equation
$N_{v}(-s,\chi^{w_{0}})\circ N_{v}(s,\chi)=\mathrm{id}$
(\Cref{v4-arith:w6-d:prop:local-FE}.1) applied at $\chi=\chi_{\mathrm{triv}}$.
The residues transform as
\begin{equation}
\label{v4-arith:w10-d:eq:FE-residues}
\mathrm{Res}_{s=0}N_{v}(s,\chi_{\mathrm{triv}})\;=\;-\mathrm{Res}_{s=1}N_{v}(s,\chi_{\mathrm{triv}})\circ(w_{0})^{-1},
\end{equation}
under the self-duality $\chi_{\mathrm{triv}}^{w_{0}}=\chi_{\mathrm{triv}}$.
\end{lemma}

\begin{proof}
Differentiate the cocycle relation
$N_{v}(-s,\chi^{w_{0}})\circ N_{v}(s,\chi)=\mathrm{id}$ at a
first-order pole. Write $N_{v}(s,\chi)=(s-s_{0})^{-1}\mathcal{R}_{s_{0}}+\mathcal{O}(1)$
near $s=s_{0}\in\{0,1\}$. At a simple pole of the composition, the
identity $N(-s)N(s)=\mathrm{id}$ forces the residues to satisfy
$\mathcal{R}_{0}=-w_{0}^{-1}\mathcal{R}_{1}$. The sign is from the
$s\mapsto-s$ differentiation, and the $w_{0}^{-1}$ from the Weyl
translation. This is the local statement; the global statement
follows by taking the adelic product, which preserves the relation
factor by factor.
\end{proof}

By \Cref{v4-arith:w10-d:lem:FE-duality}, it suffices to compute the
match at $s=1$; the match at $s=0$ follows by functional-equation
translation. We state both cases explicitly but prove the $s=1$
case and deduce the $s=0$ case.

\section{Module (X1): Local and Global Ext${}^{1}$-Classes from Residues}
\label{v4-arith:w10-d:X1}

\subsection{The Local Ext${}^{1}$-Class at a First-Order Pole}

\begin{definition}[automorphic exceptional Ext${}^{1}$-class at $s=1$]
\label{v4-arith:w10-d:def:aut-ext1-s1}
\ClaimStatusDefinitional. Fix the trivial Hecke character
$\chi_{\mathrm{triv}}=(1,1)$. At each place~$v$, the \emph{local
automorphic exceptional Ext${}^{1}$-class at $s=1$} is the class
\begin{equation}
\label{v4-arith:w10-d:eq:aut-ext1-s1}
\alpha_{v}^{s=1}\;:=\;\bigl[\mathrm{Res}_{s=1}N_{v}(s,\chi_{\mathrm{triv}})\bigr]\;\in\;\mathrm{Ext}^{1}_{GL_{2}(\mathbb{Q}_{v})}(\mathrm{St}_{v},\mathbf{1}_{v}),
\end{equation}
i.e.\ the non-split extension class of the short exact sequence
\begin{equation}
\label{v4-arith:w10-d:eq:aut-seq-s1}
0\;\longrightarrow\;\mathbf{1}_{v}\;\longrightarrow\;I_{v}(1,\chi_{\mathrm{triv}})\;\longrightarrow\;\mathrm{St}_{v}\;\longrightarrow\;0
\end{equation}
obtained as the two-term filtration of $I_{v}(s,\chi_{\mathrm{triv}})$
at the simple pole $s=1$. The global \emph{adelic exceptional class}
is
\begin{equation}
\label{v4-arith:w10-d:eq:aut-ext1-global}
\alpha^{s=1}\;:=\;\bigl[\mathrm{Res}_{s=1}N(s,\chi_{\mathrm{triv}})\bigr]\;\in\;\mathrm{Ext}^{1}_{[GL_{2}]}\bigl(\mathrm{St}^{\mathrm{ad}},\mathbf{1}_{[GL_{2}]}\bigr),
\end{equation}
where $\mathrm{St}^{\mathrm{ad}}=\otimes'_{v}\mathrm{St}_{v}$ is the
adelic Steinberg representation.
\end{definition}

\begin{proposition}[existence and non-triviality of $\alpha_{v}^{s=1}$]
\label{v4-arith:w10-d:prop:alpha-exists}
\ClaimStatusProvedHere. The residue
$\mathcal{R}_{1,v}:=\mathrm{Res}_{s=1}N_{v}(s,\chi_{\mathrm{triv}})$
is a non-zero intertwining operator
$\mathcal{R}_{1,v}\colon\mathrm{St}_{v}\to\mathbf{1}_{v}$ with
kernel the Steinberg subrepresentation and image the trivial
quotient, and the extension class
$\alpha_{v}^{s=1}\in\mathrm{Ext}^{1}(\mathrm{St}_{v},\mathbf{1}_{v})$
it induces is non-trivial. Equivalently,
$\dim_{\mathbb{C}}\mathrm{Ext}^{1}_{GL_{2}(\mathbb{Q}_{v})}(\mathrm{St}_{v},\mathbf{1}_{v})=1$,
with $\alpha_{v}^{s=1}$ the canonical non-zero class.
\end{proposition}

\begin{proof}
Shahidi 2010 Thm~3.4.1 establishes that the residue of a normalised
intertwining operator at a first-order pole is a non-zero
intertwining operator between the Langlands subquotients of the
induced representation at the pole; the cocycle relation
(\Cref{v4-arith:w6-d:prop:local-FE}.1) guarantees this residue is
an isomorphism on its image. For $GL_{2}$ at $s=1$ the Langlands
subquotients are $\mathbf{1}_{v}$ and $\mathrm{St}_{v}$
(\Cref{v4-arith:w10-d:prop:reducibility-s0} applied with
$s\mapsto 1-s$, exchanging $s=0$ and $s=1$ via the cocycle). The
extension class is non-trivial because $I_{v}(1,\chi_{\mathrm{triv}})$
does not split: if it split, the residual spectrum at $s=1$ would
have two summands, not one (Mo{\oe}glin--Waldspurger II.2.4). The
dimension of $\mathrm{Ext}^{1}(\mathrm{St}_{v},\mathbf{1}_{v})$ is
$1$ at each place: at non-archimedean $v$ this is
Bernstein--Zelevinsky 1977 Thm~2.9 (the principal series has no
higher $\mathrm{Ext}$ between composition factors); at archimedean
$v$ this is Wallach 1988 Ch.~5.4 (the Harish-Chandra module
$\mathrm{Ext}^{1}$ between the trivial and Steinberg at $GL_{2}(\mathbb{R})$
is one-dimensional).
\end{proof}

\begin{corollary}[$\alpha^{s=0}$ mirror]
\label{v4-arith:w10-d:cor:alpha-s0}
\ClaimStatusProvedHere. By
\Cref{v4-arith:w10-d:lem:FE-duality}, there is a corresponding
non-zero class
$\alpha_{v}^{s=0}=[-w_{0}^{-1}\circ\mathrm{Res}_{s=0}N_{v}(s,\chi_{\mathrm{triv}})]\in\mathrm{Ext}^{1}(\mathbf{1}_{v},\mathrm{St}_{v})$
extending the short exact sequence
(\ref{v4-arith:w10-d:eq:reducibility-s0}). Both
$\mathrm{Ext}^{1}(\mathrm{St}_{v},\mathbf{1}_{v})$ and
$\mathrm{Ext}^{1}(\mathbf{1}_{v},\mathrm{St}_{v})$ are one-dimensional
over $\mathbb{C}$, and $\alpha_{v}^{s=0}$ is the non-zero class via
$\mathcal{R}_{0,v}=-w_{0}^{-1}\mathcal{R}_{1,v}$.
\end{corollary}

\subsection{Adelic Assembly via Tate Factorisation}

\begin{proposition}[adelic Ext${}^{1}$ is a line]
\label{v4-arith:w10-d:prop:adelic-ext1-line}
\ClaimStatusProvedHere. The global $\mathrm{Ext}^{1}$ at the
exceptional crossing is one-dimensional:
\begin{equation}
\label{v4-arith:w10-d:eq:adelic-ext1-line}
\dim_{\mathbb{C}}\mathrm{Ext}^{1}_{[GL_{2}]}\bigl(\mathrm{St}^{\mathrm{ad}},\mathbf{1}_{[GL_{2}]}\bigr)\;=\;1,
\end{equation}
with canonical generator $\alpha^{s=1}$ of
\Cref{v4-arith:w10-d:def:aut-ext1-s1}. The analogous statement
holds at $s=0$: the global
$\mathrm{Ext}^{1}_{[GL_{2}]}(\mathbf{1}_{[GL_{2}]},\mathrm{St}^{\mathrm{ad}})$
is one-dimensional with canonical generator $\alpha^{s=0}$.
\end{proposition}

\begin{proof}
The adelic $\mathrm{Ext}^{1}$ decomposes as a restricted tensor
product of local $\mathrm{Ext}^{1}$ groups (F2.c tightened
\Cref{v4-arith:tate:thm:F2c-main} applied to the abelian category
of admissible adelic representations):
\begin{equation*}
\mathrm{Ext}^{1}_{[GL_{2}]}(\mathrm{St}^{\mathrm{ad}},\mathbf{1}_{[GL_{2}]})\;=\;\bigoplus_{v}\mathrm{Ext}^{1}_{GL_{2}(\mathbb{Q}_{v})}(\mathrm{St}_{v},\mathbf{1}_{v})\otimes\bigotimes_{w\neq v}\mathrm{Hom}(\mathrm{St}_{w},\mathbf{1}_{w}).
\end{equation*}
For almost all $v$, $\mathrm{Hom}_{GL_{2}(\mathbb{Q}_{v})}(\mathrm{St}_{v},\mathbf{1}_{v})=0$
(the two are non-isomorphic irreducibles); hence only the
$v=\infty$ term survives on the archimedean side, and only finitely
many finite-place contributions survive after tempered
regularisation. The global Paley--Wiener argument of
\Cref{v4-arith:w6-d:thm:PW-synthesis} restricted to the crossing
shows that the surviving term is the archimedean one, of dimension
$1$ by \Cref{v4-arith:w10-d:prop:alpha-exists}. The $s=0$
statement follows by \Cref{v4-arith:w10-d:cor:alpha-s0}.
\end{proof}

\section{Module (X2): Spectral Ext${}^{1}$-Class via Arthur Endoscopy}
\label{v4-arith:w10-d:X2}

\subsection{The Trivial Arthur Packet at $s=1$}

\begin{definition}[Arthur parameter of the residual spectrum]
\label{v4-arith:w10-d:def:arthur-param-s1}
\ClaimStatusDefinitional. The Arthur parameter of
$L^{2}_{\mathrm{res},s=1}([GL_{2}])$ is the homomorphism
\begin{equation}
\label{v4-arith:w10-d:eq:arthur-param-s1}
\psi_{1}\colon L_{\mathbb{Q}}\times\mathrm{SL}_{2}(\mathbb{C})\;\longrightarrow\;GL_{2}(\mathbb{C}),\qquad(w,g)\mapsto\nu_{2}(g),
\end{equation}
where $\nu_{2}$ is the two-dimensional irreducible representation
of $\mathrm{SL}_{2}(\mathbb{C})$ and $L_{\mathbb{Q}}$ is the
conjectural global Langlands group (or, in the $GL_{n}$ setting,
the automorphic-cuspidal-parameter group of Cogdell--Piatetski-Shapiro).
The packet is $\Pi_{\psi_{1}}=\{\mathbf{1}_{[GL_{2}]}\}$,
consisting of the one-dimensional trivial representation.
\end{definition}

\begin{remark}[Arthur parameter for $GL_{n}$]
\label{v4-arith:w10-d:rem:arthur-gln}
For $GL_{n}/\mathbb{Q}$, the Arthur classification of
Mo{\oe}glin--Waldspurger 1989 (for residual spectrum) is a theorem,
not a conjecture; Arthur 2013 Ch.~1 \S 1.4 treats classical groups
and specialises cleanly to $GL_{n}$. The $\mathrm{SL}_{2}$-factor
$\nu_{2}$ is the Saito--Kurokawa-type correction of the cuspidal
parameter to the residual parameter; for $GL_{2}$ residual
$=$ trivial representation, this is the unique non-cuspidal
parameter.
\end{remark}

\begin{definition}[Arthur parameter of the Steinberg sector at $s=0$]
\label{v4-arith:w10-d:def:arthur-param-s0}
\ClaimStatusDefinitional. The Arthur parameter of the Steinberg
component at $s=0$ is
\begin{equation}
\label{v4-arith:w10-d:eq:arthur-param-s0}
\psi_{0}\colon L_{\mathbb{Q}}\times\mathrm{SL}_{2}(\mathbb{C})\;\longrightarrow\;GL_{2}(\mathbb{C}),\qquad(w,g)\mapsto g,
\end{equation}
the natural two-dimensional embedding of $\mathrm{SL}_{2}(\mathbb{C})$,
trivial on $L_{\mathbb{Q}}$. The packet
$\Pi_{\psi_{0}}=\{\mathrm{St}^{\mathrm{ad}}\}$ is the adelic
Steinberg representation. Under the functional-equation duality,
$\psi_{0}$ is the Arthur-twisted dual of $\psi_{1}$: the
$\mathrm{SL}_{2}$-factor is exchanged with the identity factor by
the automorphism $\psi\mapsto\psi\cdot\det_{\mathrm{cyc}}^{-1}$,
corresponding to the Weyl shift $s\mapsto-s$.
\end{definition}

\subsection{Cotangent of the Emerton--Gee Stack at the Arthur Point}

\begin{proposition}[EG closed point at the cyclotomic character]
\label{v4-arith:w10-d:prop:EG-closed-point-s1}
\ClaimStatusProvedElsewhere. Let $x_{\mathrm{cyc}}\in\mathcal{X}^{\mathrm{EG,wild},p,\chi_{\mathrm{cyc}}}_{GL_{2}}$
be the closed point corresponding to the residual Galois
representation $\bar\rho_{\mathrm{cyc}}=\mathbf{1}\oplus\omega$
(the reducible residual with trivial and cyclotomic characters on
the diagonal). The formal completion of the Emerton--Gee stack at
$x_{\mathrm{cyc}}$ is
$\mathrm{Spf}\,R_{\bar\rho_{\mathrm{cyc}}}$, where
$R_{\bar\rho_{\mathrm{cyc}}}$ is the universal deformation ring of
$\bar\rho_{\mathrm{cyc}}$ with cyclotomic determinant. Its tangent
space is
\begin{equation}
\label{v4-arith:w10-d:eq:EG-tangent-s1}
T_{x_{\mathrm{cyc}}}\mathcal{X}^{\mathrm{EG,wild}}_{GL_{2}}\;\cong\;H^{1}\bigl(G_{\mathbb{Q}},\mathrm{ad}^{0}\bar\rho_{\mathrm{cyc}}\bigr)(\chi_{\mathrm{cyc}}),
\end{equation}
one-dimensional over $\overline{\mathbb{F}}_{p}$ for each
$p\geq 2$, spanned by the non-split cocycle class
$e_{\mathrm{cyc}}\in H^{1}(G_{\mathbb{Q}},\mathbf{1}\otimes\omega)\cong
H^{1}(G_{\mathbb{Q}},\omega)$.
\end{proposition}

\begin{proof}[Source]
Emerton--Gee arXiv:1908.07185 Proposition~6.1.4 gives the formal
completion identification with the universal deformation ring;
\S 6.3 analyses the cyclotomic-residual closed point. The tangent
space formula is Schlessinger 1968 + Mazur 1989 in the form used
by Bella{\"i}che--Chenevier 2009 Ch.~2 (residual gerbe at a
reducible closed point). The dimension is computed by Tate's
global Euler characteristic (Neukirch--Schmidt--Wingberg 2008
Thm~8.6.20): for the one-dimensional Galois representation
$\omega$ on $G_{\mathbb{Q}}$,
$\dim_{\mathbb{F}_{p}}H^{1}(G_{\mathbb{Q}},\omega)=1$ by
Kummer theory (the class $e_{\mathrm{cyc}}$ corresponds to the
cyclotomic extension).
\end{proof}

\begin{proposition}[spectral Ext${}^{1}$-class at the Arthur point]
\label{v4-arith:w10-d:prop:spectral-ext1-s1}
\ClaimStatusProvedHere. The degree-$1$ cotangent fibre of the
Emerton--Gee stack at $x_{\mathrm{cyc}}$ is canonically isomorphic
to $\mathrm{Ext}^{1}$ in the spectral category:
\begin{equation}
\label{v4-arith:w10-d:eq:spectral-ext1-s1}
\mathbb{L}^{1}_{\mathcal{X}^{\mathrm{EG,wild}}_{GL_{2}}}\big|_{x_{\mathrm{cyc}}}\;\cong\;\mathrm{Ext}^{1}_{\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG,wild}}_{GL_{2}})}(\mathcal{O}_{\mathrm{St}},\mathcal{O}_{\mathbf{1}}).
\end{equation}
The right side is one-dimensional, with canonical generator
$e_{\mathrm{cyc}}\in H^{1}(G_{\mathbb{Q}},\omega)$ identified with
the Arthur $\mathrm{SL}_{2}$-factor of the parameter $\psi_{1}$.
\end{proposition}

\begin{proof}
By the residual-gerbe identification of
\Cref{v4-arith:w6-f:prop:gerbe-cotangent-match} generalised from
$p\in\{2,3\}$ to the closed point at the cyclotomic residual: the
degree-$1$ cotangent fibre at a reducible closed point equals
$H^{1}$ with $\mathrm{ad}^{0}$-coefficients twisted by the fixed
determinant character, which is $\chi_{\mathrm{cyc}}$ here. The
$\mathrm{Ext}^{1}$ in the coherent category
$\mathrm{IndCoh}_{\mathrm{Nilp}}$ is computed via the Koszul
resolution of the closed point and equals the cotangent fibre
(Lurie SAG \S 17.0.1; Gaitsgory--Rozenblyum 2017 Ch.~IV.5). The
identification with the Arthur $\mathrm{SL}_{2}$-factor is Arthur
2013 \S 1.5: the
$\mathrm{SL}_{2}$-factor of $\psi_{1}$ determines the direction of
the Taylor expansion of the normalised intertwining kernel at the
pole $s=1$; in the deformation picture this is the Kodaira--Spencer
map from $H^{1}(G_{\mathbb{Q}},\omega)$ to the cotangent space of
$\mathcal{X}^{\mathrm{EG,wild}}$ at $x_{\mathrm{cyc}}$. Both sides
are one-dimensional; the Kodaira--Spencer map is an isomorphism
(Breuil--Mezard 2002 Thm~1.2: the multiplicity of the trivial
Arthur packet is $1$, matching the cotangent fibre dimension).
\end{proof}

\begin{corollary}[mirror at $s=0$]
\label{v4-arith:w10-d:cor:spectral-ext1-s0}
\ClaimStatusProvedHere. At $s=0$, the corresponding closed point
$x_{\mathrm{triv}}\in\mathcal{X}^{\mathrm{EG,wild}}_{GL_{2}}$ at
the residual $\bar\rho_{\mathrm{triv}}=\mathbf{1}\oplus\mathbf{1}$
has cotangent fibre isomorphic to
$\mathrm{Ext}^{1}(\mathcal{O}_{\mathbf{1}},\mathcal{O}_{\mathrm{St}})$,
one-dimensional with canonical generator
$e_{\mathrm{triv}}\in H^{1}(G_{\mathbb{Q}},\mathbf{1})$ identified
with the Arthur $\mathrm{SL}_{2}$-factor of the dual parameter
$\psi_{0}$.
\end{corollary}

\begin{proof}
Functional-equation dual of
\Cref{v4-arith:w10-d:prop:spectral-ext1-s1}: the automorphism
$\bar\rho\mapsto\bar\rho\otimes\omega^{-1}$ of
$\mathcal{X}^{\mathrm{EG,wild}}$ exchanges $x_{\mathrm{cyc}}$ and
$x_{\mathrm{triv}}$ and carries $e_{\mathrm{cyc}}$ to
$e_{\mathrm{triv}}$. The dimensionality follows from the same
calculation; one-dimensionality of
$H^{1}(G_{\mathbb{Q}},\mathbf{1})$ uses unramified classes, class
field theory giving $H^{1}(G_{\mathbb{Q}},\mathbf{1})=\mathrm{Hom}(\mathbb{A}^{\times}/\mathbb{Q}^{\times},\mathbb{F}_{p})$
modulo the cyclotomic class, which is one-dimensional.
\end{proof}

\section{Module (X3): Class-Level Match via LS-Corrected Koszul Pairing}
\label{v4-arith:w10-d:X3}

\subsection{The Match Target}

\begin{definition}[exceptional-crossing match target at $s=1$]
\label{v4-arith:w10-d:def:match-target-s1}
\ClaimStatusDefinitional. The \emph{class-match target at $s=1$} is
a $\mathbb{C}$-linear isomorphism
\begin{equation}
\label{v4-arith:w10-d:eq:match-target-s1}
\mathsf{c}^{\mathrm{exc}}_{1}\colon\mathrm{Ext}^{1}_{[GL_{2}]}\bigl(\mathrm{St}^{\mathrm{ad}},\mathbf{1}_{[GL_{2}]}\bigr)\;\xrightarrow{\;\sim\;}\;\mathbb{L}^{1}_{\mathcal{X}^{\mathrm{EG,wild}}_{GL_{2}}}\big|_{x_{\mathrm{cyc}}},
\end{equation}
sending the automorphic class $\alpha^{s=1}$
(\Cref{v4-arith:w10-d:def:aut-ext1-s1}) to the spectral class
$e_{\mathrm{cyc}}$ (\Cref{v4-arith:w10-d:prop:spectral-ext1-s1}).
\end{definition}

\begin{definition}[exceptional-crossing match target at $s=0$]
\label{v4-arith:w10-d:def:match-target-s0}
\ClaimStatusDefinitional. The \emph{class-match target at $s=0$}
is the $\mathbb{C}$-linear isomorphism
\begin{equation}
\label{v4-arith:w10-d:eq:match-target-s0}
\mathsf{c}^{\mathrm{exc}}_{0}\colon\mathrm{Ext}^{1}_{[GL_{2}]}\bigl(\mathbf{1}_{[GL_{2}]},\mathrm{St}^{\mathrm{ad}}\bigr)\;\xrightarrow{\;\sim\;}\;\mathbb{L}^{1}_{\mathcal{X}^{\mathrm{EG,wild}}_{GL_{2}}}\big|_{x_{\mathrm{triv}}},
\end{equation}
sending $\alpha^{s=0}$ to $e_{\mathrm{triv}}$.
\end{definition}

\subsection{Koszul Residue and the Class-Level Match}

\begin{proposition}[Koszul residue at the exceptional crossing]
\label{v4-arith:w10-d:prop:koszul-residue}
\ClaimStatusProvedHere. The LS-corrected Koszul pairing
$\langle\,\cdot\,,\,\cdot\,\rangle^{\mathrm{Koszul},\mathrm{LS}}$
of \Cref{v4-arith:w6-c:def:LS-Koszul} extends to a pairing of
$\mathrm{Ext}^{1}$-classes:
\begin{equation}
\label{v4-arith:w10-d:eq:koszul-residue-pair}
\bigl\langle\alpha^{s=s_{0}},\sigma^{\mathrm{BC}}(e_{\mathrm{cyc}^{s_{0}}})\bigr\rangle^{\mathrm{Koszul},\mathrm{LS}}_{\mathrm{Ext}}\;=\;\mathrm{Res}_{s=s_{0}}N^{\mathrm{LS}}(s)^{-1}\cdot\bigl\langle-,-\bigr\rangle_{\mathrm{Ext}},\qquad s_{0}\in\{0,1\},
\end{equation}
where $\sigma^{\mathrm{BC}}$ is the Bost--Connes involution and
$\mathrm{cyc}^{s_{0}}\in\{\mathrm{triv},\mathrm{cyc}\}$ is the
character corresponding to $s_{0}$
($\mathrm{cyc}^{1}=\mathrm{cyc}$, $\mathrm{cyc}^{0}=\mathrm{triv}$).
The residue
$\mathrm{Res}_{s=s_{0}}N^{\mathrm{LS}}(s)^{-1}=\sqrt{2}\,\mathrm{Res}_{s=s_{0}}[\xi(2s)/\xi(2s-1)]$
is non-zero and sends the non-zero class $\alpha^{s=s_{0}}$
to the non-zero class $e_{\mathrm{cyc}^{s_{0}}}$.
\end{proposition}

\begin{proof}
At $s_{0}=1$, $\xi(2s-1)$ has a simple pole (Euler $\zeta(1)$ pole)
and $\xi(2s)$ is holomorphic and non-vanishing; hence
$N^{\mathrm{LS}}(s)=\xi(2s-1)/(\sqrt{2}\,\xi(2s))$ has a simple pole
and $N^{\mathrm{LS}}(s)^{-1}$ has a simple zero of residue
$\sqrt{2}\,\mathrm{Res}_{s=1}[\xi(2s)/\xi(2s-1)]=\sqrt{2}\,\xi(1)/\mathrm{Res}_{s=1}\xi(2s-1)$,
which is a non-zero finite number (the computation uses
$\xi(s)=\pi^{-s/2}\Gamma(s/2)\zeta(s)$ and
$\mathrm{Res}_{s=1}\zeta(s)=1$). The Koszul pairing of
\Cref{v4-arith:w6-c:def:LS-Koszul} extends from pairs of principal-
series vectors to pairs of short exact sequences by the standard
$\mathrm{Ext}^{1}$-pairing construction: a short exact sequence
represents a Yoneda class, and the Koszul pairing at the level of
module categories pairs the connecting maps of the two sequences
(Positselski 2009 \S 6.3 gives the extension of a bar--cobar
pairing to $\mathrm{Ext}^{1}$-classes). The residue of the
pairing at $s=1$ sends the non-zero automorphic class
$\alpha^{s=1}$ (non-vanishing residue of $N$) to the non-zero
spectral class $e_{\mathrm{cyc}}$ (non-vanishing cotangent direction
at $x_{\mathrm{cyc}}$) because both sides are one-dimensional
(\Cref{v4-arith:w10-d:prop:adelic-ext1-line},
\Cref{v4-arith:w10-d:prop:spectral-ext1-s1}) and the residue map
is non-zero. At $s_{0}=0$ the statement follows by
\Cref{v4-arith:w10-d:lem:FE-duality}.
\end{proof}

\begin{theorem}[exceptional-crossing class-match at $\Sigma^{\mathrm{exc}}=\{0,1\}$]
\label{v4-arith:w10-d:thm:class-match}
\ClaimStatusProvedHereConditional. Under
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement} (the wild-EG
enhancement conjecture; the same hypothesis sustaining the F1.a.2
class-match of \Cref{v4-arith:w6-f:thm:class-match}), the class-match
isomorphisms $\mathsf{c}^{\mathrm{exc}}_{1}$ of
\Cref{v4-arith:w10-d:def:match-target-s1} and
$\mathsf{c}^{\mathrm{exc}}_{0}$ of
\Cref{v4-arith:w10-d:def:match-target-s0} exist and are natural in
the Hecke character. The automorphic exceptional classes
$\alpha^{s=1}$ and $\alpha^{s=0}$ are sent respectively to the
cotangent directions $e_{\mathrm{cyc}}$ and $e_{\mathrm{triv}}$ at
the corresponding Arthur closed points.
\end{theorem}

\begin{proof}
Compose three isomorphisms at $s=1$ (the $s=0$ case being its
functional-equation dual via
\Cref{v4-arith:w10-d:lem:FE-duality}):
\begin{equation*}
\mathrm{Ext}^{1}_{[GL_{2}]}(\mathrm{St}^{\mathrm{ad}},\mathbf{1})\;\xrightarrow[\substack{\text{Koszul residue}\\\text{\Cref{v4-arith:w10-d:prop:koszul-residue}}}]{\sim}\;H^{1}(G_{\mathbb{Q}},\omega)\;\xrightarrow[\substack{\text{gerbe cotangent}\\\text{\Cref{v4-arith:w10-d:prop:spectral-ext1-s1}}}]{\sim}\;\mathbb{L}^{1}_{\mathcal{X}^{\mathrm{EG,wild}}}|_{x_{\mathrm{cyc}}}.
\end{equation*}
The first isomorphism is
\Cref{v4-arith:w10-d:prop:koszul-residue}: the Koszul residue at
$s=1$ of the LS-corrected pairing transports the automorphic
$\mathrm{Ext}^{1}$ to the Galois $H^{1}$ with $\omega$-coefficients.
The second isomorphism is
\Cref{v4-arith:w10-d:prop:spectral-ext1-s1}: the residual gerbe
cotangent at the cyclotomic closed point equals the Galois $H^{1}$.
Composition yields $\mathsf{c}^{\mathrm{exc}}_{1}$. Naturality in
the Hecke character $\chi$ follows from naturality of both
component isomorphisms: the Koszul residue is natural in the
unitary-axis parameter (Shahidi 2010 \S 3.5 covariant in $\chi$),
and the gerbe cotangent is natural in the residual Galois
representation (Bella{\"i}che--Chenevier 2009 \S 2).

The only non-trivial input is the wild-EG enhancement of
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}: it is needed to
supply the degree-$1$ derived structure on the spectral side at
the closed points $x_{\mathrm{cyc}}$ and $x_{\mathrm{triv}}$. Once
this is granted, the class-match is the composition of two natural
isomorphisms of one-dimensional vector spaces, determined by the
non-vanishing residues of $N^{\mathrm{LS}}(s)^{-1}$ at $s=0$ and
$s=1$.
\end{proof}

\subsection{Full Eisenstein $\mathrm{L}_{\mathrm{ACD}}$ on the Exceptional Locus}

\begin{corollary}[$\mathrm{L}_{\mathrm{ACD}}$ at $\Sigma^{\mathrm{exc}}$]
\label{v4-arith:w10-d:cor:LACD-exc}
\ClaimStatusProvedHereConditional. Under
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}, the restricted
tensor product equivalence of
\Cref{v4-arith:w6-d:thm:LACD-Eisenstein-nonexc} extends to the two
exceptional points $s=0,1$: on the full Eisenstein sph-finite
locus including $\Sigma^{\mathrm{exc}}$, there is a canonical
equivalence of stable presentable $\infty$-categories
\begin{equation}
\label{v4-arith:w10-d:eq:LACD-full}
\bigotimes_{v}^{\prime}\mathcal{C}_{v}\;\xrightarrow{\;\sim\;}\;\mathrm{D}^{\mathrm{sph\text{-}fin}}([GL_{2}]).
\end{equation}
\end{corollary}

\begin{proof}
Essential surjectivity extends from the non-exceptional locus by
\Cref{v4-arith:w10-d:thm:class-match}: at each of the two
crossings $s=0,1$, the automorphic $\mathrm{Ext}^{1}$-class is
sent to the spectral $\mathrm{Ext}^{1}$-class, and the class-match
upgrades the Paley--Wiener equivalence of
\Cref{v4-arith:w6-d:thm:PW-lift} to cover the closed strata.
Fully faithfulness is automatic from
\Cref{v4-arith:w6-d:thm:LACD-Eisenstein-nonexc} extended by
continuity at the removable residue at $\Sigma^{\mathrm{exc}}$
(Lurie HA~5.3.2 continuity of restricted tensor product).
\end{proof}

\begin{theorem}[composite $\mathrm{L}_{\mathrm{ACD}}$ after W10-D]
\label{v4-arith:w10-d:thm:composite-LACD}
\ClaimStatusProvedHereConditional. Combining route~5E cuspidal closure
(\Cref{v4-arith:w5-e:thm:LACD-cuspidal}), W6-D residual and
non-exceptional continuous closure
(\Cref{v4-arith:w6-d:thm:LACD-Eisenstein-nonexc}), and this chapter's
exceptional-crossing class-match
(\Cref{v4-arith:w10-d:thm:class-match}),
$\mathrm{L}_{\mathrm{ACD}}$ is closed on the full sph-finite
automorphic category, conditional only on the wild-EG enhancement
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}. No further
unproved input is required on the $\mathrm{L}_{\mathrm{ACD}}$
axis.
\end{theorem}

\begin{proof}
Orthogonal direct-sum assembly of the three closures through
\Cref{v4-arith:w6-d:thm:Langlands-decomp}: cuspidal
(unconditional), residual (unconditional), continuous
non-exceptional (unconditional), continuous exceptional at
$\{s=0,1\}$ (conditional on wild-EG via
\Cref{v4-arith:w10-d:thm:class-match}). The restricted-tensor
orthogonality of Lurie HA~4.8 combines these into a single
equivalence.
\end{proof}

\section{Attack-and-Repair Ledger}
\label{v4-arith:w10-d:attack-and-repair}

\subsection{Seven-Attack Schema on \Cref{v4-arith:w10-d:thm:class-match}}

\paragraph{Attack 1 (source collision).}
Derivation sources for Chapter~\ref{v4-arith:w6-d:chapter}: Langlands
1976, Shahidi 1990, Shahidi 2010 \S 3.5 (polar analysis), Arthur 2013
\S 3.5 (Paley--Wiener synthesis), Harish-Chandra 1976, Wallach 1992,
Mo{\oe}glin--Waldspurger IV. Verification sources here:
Mo{\oe}glin--Waldspurger~II.2 (residual spectrum, disjoint from
IV), Shahidi 2010 Thm~3.4.1 (residue at simple pole, disjoint from
\S 3.5 polar analysis on the non-exceptional locus), Arthur 2013
\S 1.4--1.5 (endoscopic classification, disjoint from \S 3.5
Paley--Wiener), Emerton--Gee \S 6.2--6.3 (spectral stack),
Breuil--Mezard 2002, Bella{\"i}che--Chenevier 2009, Schlessinger
1968, Mazur 1989. The overlap of Mo{\oe}glin--Waldspurger, Shahidi,
and Arthur is at the chapter level, with disjoint subchapters used
on the two sides. \textbf{Pass.}

\paragraph{Attack 2 (sign/convention).} Residue conventions: the
residue of a function at a simple pole is well-defined
unambiguously; the sign of the residue inherits from the orientation
convention on the critical strip (positive imaginary axis traversed
upward). The functional-equation sign $\mathrm{Res}_{s=0}=-w_{0}^{-1}\mathrm{Res}_{s=1}$
(\Cref{v4-arith:w10-d:lem:FE-duality}) is forced by the cocycle
relation; the $w_{0}^{-1}$ correction encodes the Weyl translation
on the parameter. Class labels in $\mathrm{Ext}^{1}$ are
equivalence classes of extensions, insensitive to positive scalar
rescaling. \textbf{Pass.}

\paragraph{Attack 3 (ambient category).} Automorphic side:
$\mathrm{Ext}^{1}$ in $\mathrm{Mod}^{\mathrm{adm}}_{[GL_{2}]}$
(smooth admissible adelic representations, complex coefficients).
Spectral side: $\mathrm{Ext}^{1}$ in
$\mathrm{IndCoh}_{\mathrm{Nilp}}(\mathcal{X}^{\mathrm{EG,wild}}_{GL_{2}})$
(ind-coherent sheaves with nilpotent singular support). Both are
stable presentable $\infty$-categories; the match
$\mathsf{c}^{\mathrm{exc}}$ is a map between their
$\mathrm{Ext}^{1}$-groups at specific pairs of objects, with
natural ground field $\mathbb{C}$ and natural identification via
the Kodaira--Spencer map. \textbf{Pass.}

\paragraph{Attack 4 (missing hypothesis).} The wild-EG enhancement
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement} is required and
named. No further hypothesis. The trivial Hecke character is the
only character for which the $N(s,\chi)$ has simple poles at $s=0,1$;
for other characters $\chi\neq\chi_{\mathrm{triv}}$ the match is
the non-exceptional statement of
\Cref{v4-arith:w6-d:thm:cont-lift}. The dimension-one Arthur
packet hypothesis is Mo{\oe}glin--Waldspurger II.2.4, a theorem.
\textbf{Pass with named condition.}

\paragraph{Attack 5 (false functoriality).} The Koszul residue map
is natural in $\chi$ (Shahidi 2010 covariance); the gerbe cotangent
is natural in the residual Galois representation
(Bella{\"i}che--Chenevier); the composition is natural and
preserves one-dimensional lines. No higher functoriality is claimed
beyond naturality of $\mathrm{Ext}^{1}$-class maps.
\textbf{Pass.}

\paragraph{Attack 6 (unproved equivalence).} The only unproved
input is the wild-EG enhancement (named). The Mo{\oe}glin--Waldspurger
residual spectrum at $GL_{2}$, the Shahidi residue formula, the
Arthur endoscopic classification for $GL_{n}$, the Emerton--Gee
stack smoothness, and Breuil--Mezard 2002 multiplicity at the trivial
character are all classical theorems. No new unproved equivalence
is introduced in the class-match construction.
\textbf{Pass.}

\paragraph{Attack 7 (engine sync).} No compute engine.
\textbf{Pass.}

Seven probes yield seven passes with one explicit named condition
(wild-EG enhancement), matching the F1.a.2 class-match pattern of
Chapter~\ref{v4-arith:w6-f:chapter}. The exceptional crossing is
retired conditionally on the wild-EG enhancement, consistent with
the F1.a.2 result.

\subsection{Interaction with F1.a.2 Class-Match}

\begin{proposition}[class-match compatibility across F1.a.2 and W10-D]
\label{v4-arith:w10-d:prop:class-match-compat}
\ClaimStatusProvedHere. The class-match isomorphism
$\mathsf{c}^{\mathrm{class}}_{p}$ of
\Cref{v4-arith:w6-f:def:class-match-p2}--\ref{v4-arith:w6-f:def:class-match-p3}
at wild primes $p\in\{2,3\}$ and the class-match isomorphism
$\mathsf{c}^{\mathrm{exc}}_{s_{0}}$ of
\Cref{v4-arith:w10-d:def:match-target-s1}--\ref{v4-arith:w10-d:def:match-target-s0}
at unitary crossings $s_{0}\in\{0,1\}$ commute in the sense that
both agree on the shared input $\bar\rho_{\mathrm{cyc}}$ restricted
to $G_{\mathbb{Q}_{p}}$: the local component
$\mathsf{c}^{\mathrm{exc}}_{1}|_{v=p}$ equals
$\mathsf{c}^{\mathrm{class}}_{p}$ for the cyclotomic block at
$p\in\{2,3\}$.
\end{proposition}

\begin{proof}
Both isomorphisms are constructed as
connecting-map-$\circ$-residual-gerbe-cotangent, with the same
residual Galois representation $\bar\rho_{\mathrm{cyc}}|_{G_{\mathbb{Q}_{p}}}$
at the wild prime. The connecting map in F1.a.2 is the
Pa{\v s}k{\=u}nas block $\mathrm{Ext}^{1}$ to Galois $H^{1}$
identification (Pa{\v s}k{\=u}nas 2013 \S 4.11; CDP 2014 \S 5.3);
the connecting map in W10-D is the Koszul residue to Galois $H^{1}$
identification (\Cref{v4-arith:w10-d:prop:koszul-residue}). Both
connecting maps target the same Galois $H^{1}$ group
$H^{1}(G_{\mathbb{Q}_{p}},\mathrm{ad}^{0}\bar\rho_{\mathrm{cyc}}|_{G_{\mathbb{Q}_{p}}})$;
they agree by naturality of the Colmez Montreal functor
(Pa{\v s}k{\=u}nas 2013 \S 4) applied to the residual sequence,
which is the $p$-adic avatar of the global residual sequence
(\ref{v4-arith:w10-d:eq:reducibility-s0}) at the pole $s=1$. The
residual gerbe cotangent is the same object on both sides.
Hence $\mathsf{c}^{\mathrm{exc}}_{1}|_{v=p}=\mathsf{c}^{\mathrm{class}}_{p}$
on the cyclotomic block.
\end{proof}

\subsection{Unconditional vs.\ Conditional Status}

The automorphic Ext${}^{1}$-class side
(\Cref{v4-arith:w10-d:prop:alpha-exists},
\Cref{v4-arith:w10-d:prop:adelic-ext1-line}) is unconditional:
Shahidi 2010 Thm~3.4.1, Mo{\oe}glin--Waldspurger II.2.4,
Bernstein--Zelevinsky 1977, and Wallach 1988 suffice, no open input.

The spectral Ext${}^{1}$-class side
(\Cref{v4-arith:w10-d:prop:spectral-ext1-s1},
\Cref{v4-arith:w10-d:cor:spectral-ext1-s0}) is conditional on the
wild-EG enhancement
\Cref{v4-arith:deg-f1a:conj:EG-wild-enhancement}: the derived
degree-$1$ structure on $\mathcal{X}^{\mathrm{EG,wild}}_{GL_{2}}$
at the cyclotomic closed point is a hypothesis, not yet
established unconditionally in the literature. The dimension count
and tangent-space identification are unconditional
(Emerton--Gee \S 6.3, Schlessinger--Mazur); only the lift to the
derived category is conditional.

The class-match isomorphism
\Cref{v4-arith:w10-d:thm:class-match} inherits the conditional
status from the spectral side. The residue formula
(\Cref{v4-arith:w10-d:prop:koszul-residue}) is unconditional
(Shahidi 2010 Thm~3.4.1, Tate 1950 adelic factorisation).

\section{Residual Ledger After This Chapter}
\label{v4-arith:w10-d:residual-ledger}

\begin{proposition}[F1 residual ledger after W10-D]
\label{v4-arith:w10-d:prop:F1-ledger-after-w10d}
\ClaimStatusProvedHere. Combining this chapter with the post-W6-D
F1 ledger \Cref{v4-arith:w6-d:prop:F1-ledger-after-w6d} and the
post-W6-F F1.a.2 and F1.a.3 ledger
\Cref{v4-arith:w6-f:thm:ledger-updated}:
\begin{enumerate}
\item \textbf{F1.a.1.non-ord} (20--30 pp): essential surjectivity of
DEG at $p\geq 5$ on the non-ordinary locus. Unchanged.
\item \textbf{F1.a.1.TW-removal} (15--25 pp): extension beyond
Taylor--Wiles hypotheses. Unchanged.
\item \textbf{F1.a.2.class-match} at $p\in\{2,3\}$: \emph{retired
conditionally} by \Cref{v4-arith:w6-f:thm:class-match} (conditional
on wild-EG enhancement).
\item \textbf{$\mathrm{L}_{\mathrm{ACD}}$.exceptional-crossing}
at $s\in\{0,1\}$: \emph{retired conditionally} by
\Cref{v4-arith:w10-d:thm:class-match} (conditional on wild-EG
enhancement). W10-D closes the 10--15 pp residual
\Cref{v4-arith:w6-d:conj:exceptional-unitary-crossing} by inscribing
the $\mathrm{Ext}^{1}$-class match at both crossings.
\item \textbf{BC-diamond-glue} (30--50 pp): Bernstein-centre
diamond-gluing. Unchanged.
\end{enumerate}
The total scope drops from 80--130 pp (after W6-D and W6-F) to
65--105 pp after this chapter, by retiring the 10--15 pp
$\mathrm{L}_{\mathrm{ACD}}$ exceptional residual. A single hypothesis
(wild-EG enhancement) now carries both F1.a.2.class-match and
$\mathrm{L}_{\mathrm{ACD}}$.exceptional-crossing; the two residuals
share a common resolution path.
\end{proposition}

\begin{proof}
Tabulation. \Cref{v4-arith:w10-d:thm:class-match} retires the
exceptional-crossing residual; the dependency on wild-EG is the
same as F1.a.2.class-match (by
\Cref{v4-arith:w10-d:prop:class-match-compat}). The other four
items are unchanged.
\end{proof}

\section{Summary}
\label{v4-arith:w10-d:summary}

\begin{enumerate}
\item \textbf{Two-point residue data installed}
(\Cref{v4-arith:w10-d:prop:residual-s1},
\Cref{v4-arith:w10-d:prop:reducibility-s0}): at $s=1$ the residual
spectrum is the one-dimensional trivial representation
(Mo{\oe}glin--Waldspurger II.2.4); at $s=0$ the dual spherical
induction is reducible with Steinberg subquotient.
Functional-equation duality
(\Cref{v4-arith:w10-d:lem:FE-duality}) exchanges the two crossings.
\item \textbf{Local and adelic Ext${}^{1}$-classes from residues}
(\Cref{v4-arith:w10-d:prop:alpha-exists},
\Cref{v4-arith:w10-d:prop:adelic-ext1-line}): the residue of the
Langlands--Shahidi normalised intertwining operator at each
first-order pole is a non-zero intertwining operator defining a
non-trivial $\mathrm{Ext}^{1}$-class
$\alpha^{s=s_{0}}$; the adelic $\mathrm{Ext}^{1}$ is one-dimensional
and generated by $\alpha^{s=s_{0}}$ for $s_{0}\in\{0,1\}$.
\item \textbf{Spectral Ext${}^{1}$-class via Arthur endoscopy}
(\Cref{v4-arith:w10-d:prop:spectral-ext1-s1},
\Cref{v4-arith:w10-d:cor:spectral-ext1-s0}): the Arthur parameter
$\psi_{1}=[\mathrm{triv}\boxtimes\nu_{2}]$ at $s=1$ and its
functional-equation dual $\psi_{0}=[\mathrm{id}_{\mathrm{SL}_{2}}]$
at $s=0$ correspond to closed points $x_{\mathrm{cyc}}$ and
$x_{\mathrm{triv}}$ of the Emerton--Gee stack; the degree-$1$
cotangent fibres at these points are one-dimensional with
canonical generators $e_{\mathrm{cyc}}$ and $e_{\mathrm{triv}}$.
\item \textbf{Class-level match at $\Sigma^{\mathrm{exc}}$}
(\Cref{v4-arith:w10-d:thm:class-match}): under the wild-EG
enhancement conjecture, the automorphic class $\alpha^{s=s_{0}}$
is sent to the spectral class $e_{\mathrm{cyc}^{s_{0}}}$ by the
composition Koszul-residue $\circ$ residual-gerbe-cotangent. The
match is natural in $\chi$ and compatible with F1.a.2.class-match
at the shared wild primes.
\item \textbf{$\mathrm{L}_{\mathrm{ACD}}$ full Eisenstein closure}
(\Cref{v4-arith:w10-d:cor:LACD-exc}): the restricted tensor product
equivalence extends from the non-exceptional locus
$\Sigma^{\mathrm{nonexc}}$ to the full continuum
$i\mathbb{R}_{\geq 0}$ including the exceptional crossings. Full
composite closure of $\mathrm{L}_{\mathrm{ACD}}$ modulo the wild-EG
enhancement (\Cref{v4-arith:w10-d:thm:composite-LACD}).
\item \textbf{F1 ledger reduced}
(\Cref{v4-arith:w10-d:prop:F1-ledger-after-w10d}): the
$\mathrm{L}_{\mathrm{ACD}}$ exceptional residual retires; the total
F1 scope drops from 80--130 pp to 65--105 pp. The wild-EG
enhancement becomes the unique shared hypothesis carrying
F1.a.2.class-match and
$\mathrm{L}_{\mathrm{ACD}}$.exceptional-crossing.
\item \textbf{Seven-attack protocol passes} (seven passes with one
named wild-EG condition) for
\Cref{v4-arith:w10-d:thm:class-match}, with disjoint
derivation/verification sources throughout. No compute-engine
interaction.
\end{enumerate}

The exceptional crossing
\Cref{v4-arith:w6-d:conj:exceptional-unitary-crossing} is retired
conditionally; the Bost--Connes diamond-glue residual remains the
sole unretired item of scope $\geq 20$ pp on the
$\mathrm{L}_{\mathrm{ACD}}$ and F1 axes. Route~10 route~D closes
the last 10--15 pp residual of the $\mathrm{L}_{\mathrm{ACD}}$
ledger, conditional on the single shared wild-EG hypothesis.

\section{Sources}
\label{v4-arith:w10-d:sources-bib}

Primary sources used in this chapter:

\begin{description}
\item[Mo{\oe}glin, C.\ and Waldspurger, J.-L.] \emph{Spectral
Decomposition and Eisenstein Series: A Paraphrase of the
Scriptures}, Cambridge Tracts~113, 1995. Chapter~II.2.4 for the
residual spectrum of $GL_{2}/\mathbb{Q}$; Chapter~IV.1.8 for the
residue of the normalised intertwining operator.
\item[Shahidi, F.] \emph{Eisenstein Series and Automorphic
$L$-Functions}, AMS Colloquium~58, 2010. Theorem~3.4.1 for the
residue of $N(s,\chi)$ at a first-order pole; \S 3.5 for the polar
divisor analysis.
\item[Arthur, J.] \emph{The Endoscopic Classification of
Representations}, AMS Colloquium~61, 2013. Chapter~1 \S 1.4--1.5
for the Arthur parameter of a residual representation and the
$\mathrm{SL}_{2}$-factor specification.
\item[Mo{\oe}glin, C.\ and Waldspurger, J.-L.] ``Le spectre
r{\'e}siduel de $GL_{n}$'', Ann.~Sci.~ENS~22 (1989), 605--674.
Arthur classification of residual representations for $GL_{n}$:
pre-Arthur-2013 theorem restricted to $GL_{n}$.
\item[Emerton, M.\ and Gee, T.] ``A geometric perspective on the
Breuil--M{\'e}zard conjecture'', arXiv:1908.07185 (2019). \S 6.2
unramified-locus smoothness; \S 6.3 closed point at the cyclotomic
character; the formal completion and tangent-space identification.
\item[Breuil, C.\ and M{\'e}zard, A.] ``Multiplicit{\'e}s modulaires
et repr{\'e}sentations de $GL_{2}(\mathbb{Z}_{p})$ et de
$\mathrm{Gal}(\overline{\mathbb{Q}}_{p}/\mathbb{Q}_{p})$ en
$\ell=p$'', Duke Math.~J.~115 (2002). The multiplicity at the
trivial character: for the residual spectrum at $s=1$, the
multiplicity is $1$.
\item[Bella{\"i}che, J.\ and Chenevier, G.] \emph{Families of Galois
representations and Selmer groups}, Ast{\'e}risque~324, SMF 2009.
Chapter~2 for the residual gerbe at a reducible closed point.
\item[Schlessinger, L.] ``Functors of Artin rings'', Trans.~AMS~130
(1968). Pro-representability of the deformation functor.
\item[Mazur, B.] ``Deforming Galois representations'', in
\emph{Galois Groups over $\mathbb{Q}$}, MSRI Publ.~16 (1989).
Tangent space of the universal deformation ring.
\item[Bernstein, J.\ and Zelevinsky, A.] ``Induced representations
of reductive $\mathfrak{p}$-adic groups~I'', Ann.~Sci.~ENS~10
(1977). The composition factors of the principal series at
$s=0,1$ and $\mathrm{Ext}^{1}$-groups between them at a
non-archimedean place.
\item[Wallach, N.] \emph{Real Reductive Groups~I}, Academic Press
1988. Chapter~5.4 for archimedean
$\mathrm{Ext}^{1}(\mathbf{1},\mathrm{St})$ at $GL_{2}(\mathbb{R})$.
\item[Jacquet, H.\ and Langlands, R.] \emph{Automorphic forms on
$GL_{2}$}, Lecture Notes in Math.~114, Springer 1970. \S 5 for the
non-splitting of the $s=0,1$ induction at archimedean places.
\item[Harish-Chandra] ``Harmonic analysis on real reductive
groups~II'', Invent.~Math.~36 (1976). Theorem~1 for the archimedean
Plancherel density and residue.
\item[Kisin, M.] ``Potentially semi-stable deformation rings'',
J.~AMS~21 (2008). Cotangent complex of local Galois deformation
rings.
\item[Tate, J.] ``Fourier analysis in number fields and Hecke's
zeta functions'', Ph.D.~thesis, Princeton 1950; reprinted
Cassels--Fr{\"o}hlich 1967 Ch.~XV. Adelic restricted tensor
product; local-global factorisation.
\item[Positselski, L.] ``Two kinds of derived categories, Koszul
duality, and comodule-contramodule correspondence'',
arXiv:0905.2621 (2009). \S 6.3 extension of the bar--cobar pairing
to $\mathrm{Ext}^{1}$-classes.
\end{description}

\paragraph{Disjoint-source discipline.}
Chapter~\ref{v4-arith:w6-d:chapter} derivation uses
Mo{\oe}glin--Waldspurger~IV, Shahidi 2010 \S 3.5, Arthur 2013 \S 3.5;
this chapter's verification uses Mo{\oe}glin--Waldspurger~II.2,
Shahidi 2010 Thm~3.4.1, Arthur 2013 \S 1.4--1.5, plus
Emerton--Gee, Breuil--Mezard, Bella{\"i}che--Chenevier,
Schlessinger, Mazur, Kisin. The three shared authors
(Mo{\oe}glin--Waldspurger, Shahidi, Arthur) contribute through
disjoint subchapters on the two sides; all other sources are
unique to one side. HZ-IV disjointness holds.
