\documentclass[11pt]{article}
\usepackage[localtheorems]{raeez-math-template}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{construction}[theorem]{Construction}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{warning}[theorem]{Warning}

\providecommand{\Zbar}{\overline{\mathrm{Spec}\,\mathbb{Z}}}
\providecommand{\HAr}{\mathsf{H}^{\mathrm{Ar}}}
\providecommand{\VAr}{\mathcal{V}^{\mathrm{prim}}}
\providecommand{\HAd}{H^{\bullet}_\Delta}
\providecommand{\HchAr}{H^{\bullet}_{\mathrm{ch}}}
\providecommand{\BAr}{B^{\mathrm{Ar}}}
\providecommand{\kAr}{\kappa^{\mathrm{Ar}}}
\providecommand{\xiR}{\xi_{\mathbb{R}}}
\providecommand{\LambdaZeta}{\Lambda_{\zeta}}
\providecommand{\ThetaAr}{\Theta_{\mathrm{Ar}}}
\providecommand{\Hch}[2]{H^{#1}_{\mathrm{ch}}\bigl(\Zbar, {#2}\bigr)}
\providecommand{\colim}{\operatorname*{colim}}

\title{Arithmetic Chiral Homology and Deninger's Motivic Cohomology over \texorpdfstring{$\Zbar$}{Spec Z bar}}
\author{Raeez Lorgat}
\date{}

\begin{document}
\maketitle

\begin{abstract}
We define a Deninger-chiral candidate for motivic cohomology on the Arakelov compactification $\Zbar$ of $\mathrm{Spec}\,\mathbb{Z}$. The candidate is built from a primary arithmetic Heisenberg coefficient datum $\HAr$ and a finite-stage Platonic arithmetic-chiral bar complex. Its stable unconditional core is the Tate-Mellin character calculation:
\[
\chi_{\VAr}(s)\;=\;\Gamma_{\mathbb{R}}(s)\prod_p(1-p^{-s})^{-1}
\;=\;\LambdaZeta(s)
\qquad(\mathrm{Re}(s)>1),
\]
with meromorphic continuation and functional equation supplied by Tate's thesis. The entire Riemann xi-function is
\[
\xiR(s)=\tfrac12 s(s-1)\LambdaZeta(s).
\]
The Deninger determinant formula, the global zero operator, and the comparison with quantum arithmetic Chern--Simons are recorded as conditional structures, not as completed theorems.

On this candidate, the Riemann Hypothesis is equivalent to the existence of a Deninger generator $\ThetaAr$ whose degree-one spectrum lies on $1/2+i\mathbb{R}$. The equivalent archimedean Tate positivity statement is isolated with the corrected sign convention
\[
W_\infty(f\ast\widetilde f)=\frac{1}{2\pi}\int_{-\infty}^{\infty}|\widehat f(1/2+it)|^2
\bigl[\mathrm{Re}\,\psi(1/4+it/2)+\log\pi\bigr]\,dt\geq 0.
\]
Several elementary test-function subclasses satisfy this inequality unconditionally; the full positivity statement remains RH-equivalent.
\end{abstract}

\section{Introduction}
\label{v4-arith-den:sec:intro}

\subsection{Deninger's dream}

The classical Weil cohomology formalism assigns to a smooth projective variety $X$ over $\mathbb{F}_q$ a graded vector space $H^{\bullet}(X_{\bar{\mathbb{F}_q}}, \mathbb{Q}_\ell)$ with a Frobenius endomorphism $F$, and recovers the congruence zeta function as
\[
Z(X, t)\;=\;\prod_{i=0}^{2\dim X}\det\!\bigl(1 - Ft\,\big|\,H^{i}\bigr)^{(-1)^{i+1}}.
\]
Deligne's theorem on the Riemann Hypothesis over finite fields states that the Frobenius eigenvalues on $H^{i}$ have archimedean absolute value $q^{i/2}$; this is the \emph{purity} of the Weil cohomology, and its consequence on zero placement is the analogue of the classical Riemann Hypothesis for $Z(X,t)$.

Deninger's programme, initiated in the 1990s, proposes an analogue of this picture on the arithmetic curve $\Zbar$: a cohomology theory $\HAd(\Zbar)$ with a Frobenius-like endomorphism $F$ whose eigenvalues on $H^{1}_\Delta$ are the non-trivial zeros of the Riemann zeta function. Under this correspondence, the Riemann Hypothesis itself becomes the purity statement: $|F|$-weight $1/2$ on $H^{1}_\Delta$ forces the zero locus to sit on the critical line.

Two obstacles have prevented the Deninger programme from being realised. First, $\Zbar$ is not a variety over a field of positive characteristic, so there is no literal Frobenius endomorphism to act on a cohomology theory. Second, no cohomology theory has ever been constructed on $\Zbar$ with the integer-graded finite-dimensional profile that a Weil cohomology demands. Each attempted construction (Deninger's foliated-dynamical systems, Connes' adele class space, Meyer's Schwartz operator) runs into the same wall: a key positivity or spectral hypothesis equivalent to the Riemann Hypothesis.

\subsection{The candidate: arithmetic chiral homology}

This paper does not claim that Deninger's missing cohomology has been constructed unconditionally. It defines a Deninger-chiral candidate: a primary arithmetic Heisenberg coefficient datum $\HAr$, a finite-stage Platonic arithmetic-chiral bar complex, and a conditional Deninger generator $\ThetaAr$ whose determinant would give the expected Lefschetz formula. The candidate has formal Tate polar lines in degrees $0$ and $2$ and a degree-one sector whose spectral interpretation is precisely the Hilbert-Polya/Deninger obstruction.

The construction is operadic rather than scheme-theoretic. The coefficient datum is assembled from an archimedean Beilinson--Drinfeld Heisenberg piece and per-prime primary Bost--Connes zero-mode pieces, combined through Tate's pointed restricted tensor product. The bar differential splits as an archimedean chiral differential, a one-dimensional Parshin--Gersten boundary, local primary $E_1$-bars, and a tame-symbol twisting cochain. On reciprocity-closed finite stages, after fixing the completed convolution Lie algebra and closed spherical units, the square-zero identity is the Maurer--Cartan form of Kato--Parshin reciprocity.

The comparison with Deninger's motivic picture and with arithmetic Chern--Simons is a conditional triangle.

\begin{conjecture}[conditional triple comparison, informal]
\label{v4-arith-den:thm:triple-informal}
Assume:
\begin{enumerate}
\item a Deninger spectral-flow operator $\ThetaAr$ on the primary degree-one sector with regularised determinant convention fixed;
\item a Beilinson--Drinfeld/Costello--Gwilliam comparison between the finite-stage ordered bar and arithmetic chiral homology;
\item a quantum arithmetic Chern--Simons boundary theory whose boundary trace is the primary class $\VAr$;
\item compatible topological completions and dualities.
\end{enumerate}
Then the following three objects should be canonically equivalent with compatible $\ThetaAr$-actions:
\begin{enumerate}
\item[(D)] the Deninger motivic target $\HAd(\Zbar)$;
\item[(O)] the operadic Deninger-chiral candidate $\Hch{\bullet}{\HAr}$;
\item[(C)] the boundary chiral homology of the conjectural 3D arithmetic Chern--Simons bulk gauge theory on the \'etale 3-space $\Zbar$.
\end{enumerate}
The finite places contribute Bost--Connes Euler factors; the archimedean place contributes the Gaussian Tate factor and the unresolved zero-side operator.
\end{conjecture}

The character-level Koszul shadow of the arithmetic Heisenberg is Tate's functional equation
\[
\LambdaZeta(s)=\LambdaZeta(1-s),
\]
rooted in Poisson summation. The Riemann Hypothesis becomes purity of the zero-side generator $\ThetaAr$ on degree one. Archimedean Tate positivity is equivalent to this purity once the determinant and spectral-flow hypotheses are imposed; it is proved only on explicit test-function subclasses.

\subsection{Roadmap}

Section~\ref{v4-arith-den:sec:arithmetic-curve} recalls the arithmetic curve $\Zbar$ as an Arakelov datum and records the \'etale dimension-three analogy. Section~\ref{v4-arith-den:sec:chiral-algebras} defines arithmetic chiral coefficient data and the primary arithmetic Heisenberg datum. Section~\ref{v4-arith-den:sec:platonic-bar} builds the finite-stage bar complex and states the square-zero result on the abelian primary scope. Section~\ref{v4-arith-den:sec:chiral-homology} defines the candidate homology and separates formal Tate polar lines from the unresolved middle spectrum. Section~\ref{v4-arith-den:sec:character-theorem} proves the Tate-Mellin character identity and states the conditional determinant formula. Section~\ref{v4-arith-den:sec:koszul} identifies the character-level Koszul shadow with Tate's functional equation. Section~\ref{v4-arith-den:sec:global-frobenius} records finite-stage Euler operators and the conditional global zero generator. Section~\ref{v4-arith-den:sec:triple-identification} states the conditional triple comparison. Section~\ref{v4-arith-den:sec:purity-RH} reformulates RH under the spectral-flow hypothesis. Section~\ref{v4-arith-den:sec:a-tp-and-subclasses} analyses archimedean Tate positivity and the elementary sub-classes. Section~\ref{v4-arith-den:sec:all-genus} records the conditional all-genus extension. Section~\ref{v4-arith-den:sec:residuals} lists closed, conditional, and open obligations.

\section{The Arithmetic Curve}
\label{v4-arith-den:sec:arithmetic-curve}

\subsection{Arakelov compactification}

Let $\mathrm{Spec}\,\mathbb{Z}$ denote the spectrum of the ring of integers. Its closed points correspond bijectively to the rational primes $p$. We write $\Zbar$ for the Arakelov datum obtained by adjoining the real archimedean place:
\[
\Zbar\;=\;\mathrm{Spec}\,\mathbb{Z}\;\sqcup\;\{\infty\}.
\]
This is not a scheme-theoretic fibre. It is $\mathrm{Spec}\,\mathbb{Z}$ together with Hermitian data at infinity. The real place carries the archimedean norm $|\cdot|_\infty$ (complexified when analytic chiral fields are used); the finite-prime fibres carry the $p$-adic norms $|\cdot|_p$; the product formula $\prod_v |x|_v = 1$ for $x \in \mathbb{Q}^\times$ realises $\Zbar$ as an Arakelov-compact analogue of a smooth projective curve.

\subsection{Etale cohomological dimension 3}

Mazur (1973, \emph{Notes on \'etale cohomology of number fields}, Ann.~Sci.~\'ENS~6) established that $\mathrm{Spec}\,\mathcal{O}_K$ for any number field $K$ has \'etale cohomological dimension $3$ (for the usual torsion coefficient range), not $1$ as one might guess from the one-dimensional scheme structure. Artin--Verdier duality supplies a dimension-three duality theory for constructible torsion sheaves, with trace/Yoneda pairings landing in $\mathbb{Q}/\mathbb{Z}$. This is the arithmetic-topological analogue of the orientation pairing of a compact oriented $3$-manifold.

This is the starting point of the Mazur--Morishita knots-and-primes dictionary (Mazur 1963 unpublished; Morishita 2002, 2012 arXiv:0904.3399): each finite prime $p \subset \mathrm{Spec}\,\mathcal{O}_K$ behaves topologically as a knot $K_p \subset \mathrm{Spec}\,\mathcal{O}_K$, whose tubular neighbourhood is the pro-\'etale fibre over $p$. Linking numbers correspond to quadratic residue symbols; knot complements correspond to ramified primes; knot Dehn surgery corresponds to \'etale covers.

\subsection{The arithmetic curve as gluing datum}

For the factorisation-algebraic constructions below, $\Zbar$ enters as a gluing datum: a set of places $|\Zbar| = \{\infty\} \cup \{\text{primes}\}$ together with
\begin{itemize}
\item local coefficient spaces per place (archimedean: $\mathbb{C}_\infty$; finite: perfectoid diamond or Iwasawa algebra);
\item pointed $E_2$-monoidal categories $\mathcal{C}_v$ per place (archimedean: chiral algebra; finite: Iwahori Hecke category);
\item pointed spherical units $u_v \in \mathcal{C}_v$ (archimedean: unit vacuum of the BD chiral algebra; finite: monoidal unit of the Hecke category);
\item boundary maps $d_{v,w}$ reflecting Parshin--Gersten tame-symbol reciprocity between places.
\end{itemize}

This stratified datum is the \emph{Platonic $2$-arithmetic surface} $\mathfrak{S}^{\mathrm{Ar}}_2$. Its operadic dimension is $2$ in the restricted-tensor model; its \'etale cohomological dimension is $3$ in the Mazur--Artin--Verdier sense. The language of an archimedean boundary circle is a heuristic dictionary, not an additional theorem about an actual compactified \'etale homotopy type.

\section{Arithmetic Chiral Algebras}
\label{v4-arith-den:sec:chiral-algebras}

\subsection{Beilinson--Drinfeld chiral algebras recalled}

A chiral algebra on a smooth complex curve $X$ is a right $\mathcal{D}_X$-module $\mathcal{A}$ equipped with a chiral multiplication
\[
\mu\colon j_\ast j^\ast(\mathcal{A}\boxtimes\mathcal{A})\;\longrightarrow\;\Delta_{!}\mathcal{A}
\]
where $j\colon (X\times X)\setminus\Delta \hookrightarrow X\times X$ is the open complement of the diagonal $\Delta\colon X \hookrightarrow X\times X$. The chiral multiplication is required to be commutative and to satisfy a Jacobi identity on $X^3$. Equivalently, a chiral algebra is a factorisation algebra on $X$: a compatible system of quasi-coherent sheaves $\mathcal{A}_S$ on the Ran space $\mathrm{Ran}(X) = \bigsqcup_n X^n/S_n$ satisfying factorisation on disjoint configurations.

A vertex algebra $V$ gives rise to a chiral algebra on $\mathbb{C}$: the $\mathcal{D}$-module $V\otimes\Omega^1_{\mathbb{C}}$ carries a chiral multiplication determined by the OPE. Beilinson and Drinfeld (2004) proved this correspondence is an equivalence of categories between vertex algebras and chiral algebras on the formal disk.

\subsection{Extension to \texorpdfstring{$\Zbar$}{the arithmetic curve}}

A classical chiral algebra requires a smooth curve over a field. The arithmetic curve $\Zbar$ fails this hypothesis: the finite fibres $\mathrm{Spec}\,\mathbb{Z}_p$ are not smooth over a base field, and there is no literal chiral OPE at a finite prime. The correct arithmetic replacement is place-by-place, with place-local chiral data assembled globally through a restricted tensor product.

\begin{definition}[arithmetic chiral coefficient datum on $\Zbar$]
\label{v4-arith-den:def:arithmetic-chiral-algebra}
An \emph{arithmetic chiral coefficient datum} on $\Zbar$ is a datum
\[
\mathsf{A}^{\mathrm{Ar}}=(\mathsf{A}_\infty,\{\mathsf{A}_p\}_p,\{u_v\}_v,\tau,\mathcal{T})
\]
consisting of:
\begin{enumerate}
\item an archimedean chiral algebra $\mathsf{A}_\infty$ in the Beilinson--Drinfeld sense on $\mathbb{C}_\infty$;
\item for each prime $p$, a locally-constant pointed $E_1$-algebra $\mathsf{A}_p$ in a chosen completed linear category over the $p$-adic chart, equipped with a continuous Euler/Frobenius endomorphism $\psi_p$;
\item for each place $v$, a pointed spherical unit $u_v \in \mathsf{A}_v$ (the monoidal unit at finite $v$; the BD vacuum at $v=\infty$);
\item a Parshin--Gersten twisting cochain $\tau$ with values in the completed convolution Lie algebra of the finite-stage local bars;
\item a filtered transition system $\mathcal{T}$ whose maps insert closed spherical units and preserve $\tau$.
\end{enumerate}
The formal global object is the pointed restricted tensor product
\[
\mathsf{A}^{\mathrm{Ar}}\;=\;\mathsf{A}_\infty\,\widehat\otimes\,\widehat\bigotimes_{p}{}'\,\mathsf{A}_p
\]
in the sense that all but finitely many tensor factors are the pointed units. Calling this object a genuine chiral algebra is conditional on a comparison theorem with arithmetic factorisation homology.
\end{definition}

\begin{remark}[what is not required]
The definition does not require a literal chiral OPE at a finite prime, and does not require a global $\mathcal{D}$-module structure. At the archimedean place the OPE is honest; at a finite prime the local structure is $E_1$ with Euler/Frobenius enhancement. The asymmetry archimedean/finite is structural and unavoidable.
\end{remark}

\subsection{The arithmetic Heisenberg}

The central example for the Deninger-chiral candidate is the arithmetic Heisenberg coefficient datum.

\begin{construction}[arithmetic Heisenberg $\HAr$]
\label{v4-arith-den:constr:arithmetic-heisenberg}
Let $\mathcal{H}_\infty$ be the standard chiral Heisenberg vertex algebra on $\mathbb{C}_\infty$: the vertex algebra freely generated by a single mode $\alpha_\infty(z)$ with OPE
\[
\alpha_\infty(z)\alpha_\infty(w)\;\sim\;\frac{1}{(z-w)^{2}},
\]
central charge $c_\infty = 1$.

For each prime $p$, take the primary unramified Bost--Connes zero-mode factor
\[
\Lambda_p \;=\;\bigoplus_{r\geq 0}\mathbb{C}\,\delta_{p^r},
\qquad
N_p\delta_{p^r}=r\log(p)\,\delta_{p^r}.
\]
Its local character is
\[
\mathrm{Tr}_{\Lambda_p}(e^{-sN_p})=\sum_{r\geq 0}p^{-rs}=(1-p^{-s})^{-1}
\qquad(\mathrm{Re}(s)>0).
\]
The endomorphism $\psi_{p,t}=e^{-tN_p}$ is the finite-place Euler flow. It is not identified here with an automorphism of the full local Iwasawa algebra $\mathbb{Z}_p[\![\mathrm{Gal}(\mathbb{Q}_p^{\mathrm{ab}}/\mathbb{Q}_p)]\!]$; ramified and wild local data require a separate comparison.

The arithmetic Heisenberg is
\[
\HAr \;=\; \mathcal{H}_\infty\,\widehat\otimes\,\widehat\bigotimes_{p}{}'\,\Lambda_p
\]
with spherical units $u_\infty = |0\rangle_\infty$ (BD vacuum of $\mathcal{H}_\infty$) and $u_p = 1_p$ (unit of $\Lambda_p$).
\end{construction}

\subsection{The primary specialisation}

The primary trace class $\VAr$ is the diagonal Tate-Mellin specialisation of $\HAr$. Its comparison with the Hochschild trace of the global arithmetic Iwahori Hecke category for $\mathrm{GL}_2/\mathbb{Q}$ is a conjectural Langlands-categorical comparison, not part of the definition used in this standalone.

\begin{definition}[primary arithmetic trace class]
\label{v4-arith-den:def:v-prim}
Let $\VAr$ denote the primary adelic Heisenberg trace candidate obtained by imposing the diagonal character:
\[
\chi_{p,s}(\delta_{p^r})=p^{-rs},\qquad
\chi_{\infty,s}(x)=e^{-\pi x^2}|x|^{s-1}\,dx.
\]
The finite character is $\prod_p(1-p^{-s})^{-1}$ and the archimedean Gaussian Mellin character is $\Gamma_{\mathbb{R}}(s)=\pi^{-s/2}\Gamma(s/2)$.
\end{definition}

\begin{remark}
$\VAr$ is not itself a vertex algebra. Its character is the meromorphic completed zeta $\LambdaZeta(s)$ before polar correction, not a rational graded dimension. The possible Hochschild-trace interpretation through the global Iwahori Hecke category remains a comparison conjecture.
\end{remark}

\section{The Platonic Arithmetic-Chiral Bar Complex}
\label{v4-arith-den:sec:platonic-bar}

The candidate chiral homology of $\HAr$ is computed by a Platonic arithmetic-chiral bar complex, assembled as a filtered colimit of finite-stage bars in the chosen completed linear category.

\subsection{Finite-stage bars}

\begin{definition}[finite-stage Platonic bar]
\label{v4-arith-den:def:finite-stage-bar}
Let $S = S_f \cup \{\infty\}$ be a finite subset of $|\Zbar|$ containing the archimedean place. Assume $S$ is closed under the Parshin--Gersten boundaries of the finite set of symbols used in the stage, and assume the transition maps insert closed spherical units. The finite-stage Platonic bar on the abelian primary scope is
\[
\BAr_S(\HAr)\;=\;
B^{\mathrm{ch}}(\mathcal{H}_\infty)\,\widehat\otimes\,C^{\bullet}_{\mathrm{PG},S}(\Zbar)\,\widehat\otimes\,\widehat\bigotimes_{p\in S_f}B^{\Lambda_p,\mathrm{prim}}_{E_1}
\]
where:
\begin{itemize}
\item $B^{\mathrm{ch}}(\mathcal{H}_\infty)$ is the Beilinson--Drinfeld chiral bar of the archimedean Heisenberg;
\item $C^{\bullet}_{\mathrm{PG},S}(\Zbar)$ is the one-dimensional Parshin--Gersten complex on $S$, with degree $0$ rational-symbol part and degree $1$ finite-place tame-symbol part;
\item $B^{\Lambda_p,\mathrm{prim}}_{E_1}$ is the primary $E_1$-bar of the local Bost--Connes zero-mode factor.
\end{itemize}
Transition maps $\BAr_S \to \BAr_{S'}$ for $S \subset S'$ insert spherical units at the new places.
\end{definition}

\subsection{The signed total differential}

Fix an order $\infty < p_1 < p_2 < \cdots < p_r$ on $S$. The signed total differential on $\BAr_S$ is
\begin{equation}
D_S \;=\; d_\infty \;+\; (-1)^{|\cdot|_\infty}\,d_{\mathrm{PG},S} \;+\; \sum_{j=1}^{r}(-1)^{|\cdot|_\infty + |\cdot|_{\mathrm{PG}} + \sum_{i<j}|\cdot|_{p_i}}\,d_{p_j}
\label{v4-arith-den:eq:bar-differential}
\end{equation}
where each $d_\bullet$ splits further as:
\begin{align*}
d_\infty &= d_{\mathrm{int}} + d_{\mathrm{res}} + d_{\mathrm{dR}}, \\
d_p &= d_{\Lambda,\mathrm{int}} + d^{\mathrm{loc}}_{\mathrm{bar},p}.
\end{align*}
The tame-symbol operator $\iota(\tau_S)$ is included in the Parshin--Gersten/local cross-term of $d_{\mathrm{PG},S}$: $\tau_S$ is a degree-one cochain in the completed convolution Lie algebra whose local component at $p$ evaluates a Steinberg symbol by the tame symbol in $k(p)^\times$.

\subsection{Square-zero by reciprocity}

\begin{proposition}[$D_S^2 = 0$ on the primary finite stage]
\label{v4-arith-den:prop:D-squared-zero}
On the abelian primary Heisenberg scope, after fixing the completed convolution Lie algebra for $\tau_S$ and closed spherical units for transitions, the differential $D_S$ in Equation~\eqref{v4-arith-den:eq:bar-differential} satisfies $D_S^{2} = 0$ on every reciprocity-closed finite stage $S$.
\end{proposition}

\begin{proof}[Proof sketch]
Expanding $D_S^{2}$ produces three families of cross-terms:
\begin{enumerate}
\item $d_\infty^2 + d_{\mathrm{PG}}^2 + \sum_p d_p^2$: vanishes term-by-term. The archimedean $d_\infty^{2} = 0$ is classical (Beilinson--Drinfeld). The Gersten $d_{\mathrm{PG}}^{2} = 0$ follows from the Gersten resolution. The local $d_p^{2} = 0$ is the primary $E_1$-bar square-zero identity.
\item Anticommutators of the local differentials from different local pieces: vanish by the Koszul signs in Equation~\eqref{v4-arith-den:eq:bar-differential}.
\item Cross-terms involving the twisting cochain $\tau_S$: assemble into the Maurer--Cartan equation
\[
d_{\mathrm{PG}}\,\tau_S + \tau_S\,d_{\mathrm{PG}} + \tfrac{1}{2}[\tau_S,\tau_S]\;=\;0.
\]
\end{enumerate}
The Maurer--Cartan equation for the tame-symbol twisting cochain is the chain-level form of Kato--Parshin reciprocity on the arithmetic curve: the boundary of a principal symbol has total tame symbol $1$ after multiplying over the places in a reciprocity-closed stage.
\end{proof}

\begin{corollary}[Platonic bar well-defined]
\label{v4-arith-den:cor:Platonic-bar-well-defined}
The filtered colimit $\BAr(\HAr) = \colim_{S} \BAr_S(\HAr)$ over reciprocity-closed finite stages $S \in \mathrm{Fin}_{\mathrm{rec}}(|\Zbar|)$ is a well-defined chain complex in the chosen completed category, with differential $D$ induced from $\{D_S\}$ by compatibility of transition maps with the closed spherical units. No exactness of completed filtered colimits is used here.
\end{corollary}

\section{Chiral Homology Functor}
\label{v4-arith-den:sec:chiral-homology}

\subsection{Definition and functoriality}

\begin{definition}[arithmetic chiral homology]
\label{v4-arith-den:def:arithmetic-chiral-homology}
For an arithmetic chiral coefficient datum $\mathsf{A}^{\mathrm{Ar}}$ on $\Zbar$, define
\[
\HchAr(\Zbar,\mathsf{A}^{\mathrm{Ar}})\;:=\;H^{\bullet}\bigl(\BAr(\mathsf{A}^{\mathrm{Ar}}),\,D\bigr).
\]
\end{definition}

$\HchAr(\Zbar, -)$ is functorial for strict morphisms of coefficient data: the local maps must preserve pointed units, finite-stage transition maps, Euler/Frobenius endomorphisms, Parshin--Gersten boundary maps, the twisting cochain, and the chosen completions. General functoriality for arbitrary local morphisms is not asserted.

\subsection{Cohomological dimension}

\begin{conjecture}[Deninger dimension profile]
\label{v4-arith-den:thm:vanishing-above-two}
On the primary arithmetic Heisenberg candidate, after replacing local bars by the bounded primary Koszul model and proving the associated spectral sequence collapses, one expects
\[
H^{i}_{\mathrm{ch}}\bigl(\Zbar,\HAr\bigr)\;=\;0\qquad\text{for all }i \geq 3.
\]
\end{conjecture}

\begin{remark}
The statement is not true for arbitrary arithmetic chiral coefficient data: ordinary $E_1$ and cyclic bars are generally unbounded. The conjecture is a bounded-primary assertion, not a formal consequence of the definition.
\end{remark}

\begin{remark}
This matches Mazur's \'etale cohomological dimension $3$: the operadic construction sees degrees $0, 1, 2$; the Artin--Verdier fundamental class sits at degree $3$ in the \'etale cohomology but is not visible operadically. The operadic theory is (after a degree shift) the \emph{degree-reduced} avatar of the \'etale cohomology.
\end{remark}

\subsection{Tate lines}

\begin{definition}[formal Tate polar lines]
\label{v4-arith-den:prop:H0-H2-Tate}
The Deninger-chiral candidate contains formal Tate polar lines
\[
\mathbb{C}\cdot|0\rangle,\qquad
\mathbb{C}\cdot|\infty\rangle,
\]
placed in degrees $0$ and $2$ and corresponding to the poles of $\LambdaZeta(s)$ at $s=0$ and $s=1$. Identifying these formal lines with actual cohomology groups is part of the Deninger dimension profile.
\end{definition}

\subsection{The degree-one bulk}

The interesting cohomology sits in degree one:
\[
H^{1}_{\mathrm{ch}}(\Zbar, \HAr)
\]
is the unresolved sector. Conditional on a Deninger/Hilbert-Polya spectral-flow operator $\ThetaAr$ and a determinant-class topology, its spectrum should be the multiset of non-trivial zeros of $\xiR$. Order-one entireness supplies a Hadamard regularisation of the determinant; it does not make the middle sector finite-dimensional.

\section{Tate--Mellin Character and the Determinant Convention}
\label{v4-arith-den:sec:character-theorem}

\subsection{Primary character identity}

The stable character calculation is Tate-Mellin, not a theorem of Zhu theory. The full Heisenberg vertex algebra has the ordinary bosonic Fock character. The zeta character appears only after passing to the primary Gaussian/Bost--Connes sector.

\begin{theorem}[primary Tate--Mellin character]
\label{v4-arith-den:thm:arithmetic-zhu}
For $\mathrm{Re}(s)>1$, the primary arithmetic trace class satisfies
\[
\chi_{\VAr}(s)\;=\;\Gamma_{\mathbb{R}}(s)\prod_p(1-p^{-s})^{-1}
\;=\;\LambdaZeta(s).
\]
Tate's thesis supplies the meromorphic continuation and the functional equation $\LambdaZeta(s)=\LambdaZeta(1-s)$. The entire function is $\xiR(s)=\tfrac12s(s-1)\LambdaZeta(s)$.
\end{theorem}

\begin{proof}
At a finite prime, Definition~\ref{v4-arith-den:def:v-prim} gives
\[
\chi_{p,s}=\mathrm{Tr}_{\Lambda_p}(e^{-sN_p})=(1-p^{-s})^{-1}.
\]
At the archimedean place, the Gaussian Mellin transform gives
\[
\chi_{\infty,s}=\int_{\mathbb{R}}e^{-\pi x^2}|x|^{s-1}\,dx
=\pi^{-s/2}\Gamma(s/2)=\Gamma_{\mathbb{R}}(s).
\]
The Euler product converges for $\mathrm{Re}(s)>1$ and equals $\LambdaZeta(s)$. Tate's Poisson summation argument gives continuation and the symmetry $s\leftrightarrow 1-s$.
\end{proof}

\begin{remark}
An arithmetic Zhu correspondence would have to compare this Mellin character with a $q$-graded trace on a suitable archimedean vertex-algebraic primary sector. That comparison is not used in the theorem above. The primary Virasoro central regularisation is a residual obligation, not part of the character proof.
\end{remark}

\subsection{Lefschetz reading}

The determinant-trace identity for the arithmetic chiral homology rewrites the character as a Lefschetz number.

\begin{conjecture}[conditional Deninger determinant identity]
\label{v4-arith-den:thm:Lefschetz-character}
Assume that the Deninger-chiral candidate carries a closed operator $\ThetaAr$ with determinant-class regularisation, with formal polar lines in degrees $0$ and $2$ and middle spectrum the zero multiset. Then
\[
\LambdaZeta(s)
\;=\;
C\,
\frac{
\det\nolimits_{\infty}\!\bigl(s-\ThetaAr\,\big|\,H^{1}_{\mathrm{ch}}(\Zbar,\HAr)\bigr)
}{
\det\nolimits_{\infty}\!\bigl(s-\ThetaAr\,\big|\,H^{0}_{\mathrm{ch}}(\Zbar,\HAr)\bigr)
\det\nolimits_{\infty}\!\bigl(s-\ThetaAr\,\big|\,H^{2}_{\mathrm{ch}}(\Zbar,\HAr)\bigr)
},
\]
with $H^0$ contributing the factor $s$ and $H^2$ contributing $s-1$ under the chosen normalisation. Equivalently,
\[
\xiR(s)=\tfrac12s(s-1)\LambdaZeta(s)
\]
is the polar-corrected entire determinant.
\end{conjecture}

\begin{remark}
The determinant convention is additive in $s-\ThetaAr$, as in Deninger's formulation. The periodic multiplicative determinant convention is not used here.
\end{remark}

\section{Koszul Duality and the Functional Equation}
\label{v4-arith-den:sec:koszul}

\subsection{Arithmetic Koszul pair}

The arithmetic Heisenberg admits a Koszul dual, the arithmetic Heisenberg cobar.

\begin{definition}[arithmetic Heisenberg Koszul dual]
\label{v4-arith-den:def:koszul-dual}
The Koszul dual of $\HAr$ is the cobar construction
\[
(\HAr)^{!}\;:=\;\Omega^{\mathrm{ch,Ar}}(\BAr(\HAr)),
\]
with structure maps inherited from the bar by the Beilinson--Drinfeld cobar procedure applied locally at each place and assembled through the Kato--Parshin twisting cochain.
\end{definition}

\begin{proposition}[primary Koszul duality, conditional]
\label{v4-arith-den:prop:koszul-duality}
On the abelian primary Heisenberg scope, assuming the completed bar/cobar categories satisfy the Positselski hypotheses, the expected equivalence has the form
\[
D^{\mathrm{b}}\bigl(\HAr\text{-}\mathrm{mod}\bigr)\;\simeq\;D^{\mathrm{b}}\bigl((\HAr)^{!}\text{-}\mathrm{comod}\bigr)^{\mathrm{op}}
\]
with shift and duality natural at each place.
\end{proposition}

\subsection{The self-duality identity}

\begin{theorem}[character-level Koszul shadow]
\label{v4-arith-den:thm:koszul-functional-equation}
On the primary diagonal, the bar character is $\LambdaZeta(s)$ and the cobar character is $\LambdaZeta(1-s)$. Therefore the character-level self-duality identity
\[
\kAr_{\mathsf{G}}\;+\;(\kappa^{!})^{\mathrm{Ar}}_{\mathsf{G}}\;=\;0
\]
is the Tate functional equation
\[
\LambdaZeta(s)\;=\;\LambdaZeta(1-s).
\]
\end{theorem}

\begin{proof}
The bar character is the Tate-Mellin character of Theorem~\ref{v4-arith-den:thm:arithmetic-zhu}. The cobar dual applies Fourier transform on $\mathbb{A}_{\mathbb{Q}}/\mathbb{Q}$ and sends the diagonal character $\chi_s$ to $\chi_{1-s}$. Tate's Poisson summation theorem gives equality of the two characters. This is a character-level identity; it does not by itself construct the Deninger zero operator.
\end{proof}

\subsection{Poincar\'e duality reading}

In the Deninger framework, the functional equation $\LambdaZeta(s) = \LambdaZeta(1-s)$ is read as Poincar\'e duality on $\Zbar$: the shift $s \mapsto 1 - s$ reflects the degree symmetry $H^i \leftrightarrow H^{2-i}$.

\begin{conjecture}[Poincar\'e duality and Koszul self-duality]
\label{v4-arith-den:prop:poincare-koszul}
Assuming a Poincar\'e pairing compatible with Tate twist and with the zero operator,
\[
\Theta_{2-i}=1-\Theta_i^\vee,
\]
the chain-level Poincar\'e duality of the candidate should be equivalent to the arithmetic Koszul self-duality $\kAr + (\kappa^{!})^{\mathrm{Ar}} = 0$.
\end{conjecture}

\section{Finite-Stage Euler Operators and the Global Zero Generator}
\label{v4-arith-den:sec:global-frobenius}

\subsection{Per-place generators}

\begin{definition}[per-place Euler operators]
\label{v4-arith-den:def:per-place-frobenius}
At each prime $p$, the primary finite-place operator is the Bost--Connes zero-mode Hamiltonian $N_p$ on $\Lambda_p$, with $N_p\delta_{p^r}=r\log(p)\delta_{p^r}$. Its semigroup $e^{-tN_p}$ gives the local Euler factor and is the finite-place input to the candidate.

At the archimedean place, the unconditional operator is the infinitesimal scaling operator entering the Gaussian Mellin transform. Any conjugacy with a Virasoro zero mode $L_0-c/24$ is conditional on the primary Virasoro comparison.
\end{definition}

\subsection{Global assembly}

\begin{definition}[finite-stage Euler operator and global hypothesis]
\label{v4-arith-den:def:global-frobenius}
For a finite stage $S=S_f\cup\{\infty\}$ define the finite-stage Euler operator
\[
N_S\;=\;N_\infty+\sum_{p\in S_f}N_p
\]
on the finite tensor product. The global Deninger generator $\ThetaAr$ is not defined as the naive infinite tensor of all local flows. It is a conditional operator obtained only after choosing a completed domain, determinant regularisation, and spectral-flow comparison to the zero side.
\end{definition}

\begin{proposition}[finite-stage chain-level commutation, conditional]
\label{v4-arith-den:prop:F-commutes-D}
Assume the local primary bars are $N_p$-equivariant, the archimedean chiral bar is scaling-equivariant, and the tame-symbol twisting cochain $\tau_S$ is equivariant under the finite-stage Euler action. Then
\[
[N_S,D_S]=0
\]
on $\BAr_S(\HAr)$.
\end{proposition}

\begin{proof}[Proof sketch]
Place-local commutation is built into the local primary bars and into the scaling equivariance of the archimedean chiral bar. The remaining term is the cross-term $\tau_S$; the stated equivariance hypothesis is exactly the assertion that the Parshin--Gersten tame-symbol operator has degree zero for the finite-stage Euler action. The signs in Equation~\eqref{v4-arith-den:eq:bar-differential} then give the displayed commutator.
\end{proof}

\begin{corollary}
Under the same hypotheses and after passing to a compatible completion, the conditional generator $\ThetaAr$ descends to the Deninger-chiral candidate homology.
\end{corollary}

\section{The Triple Identification Theorem}
\label{v4-arith-den:sec:triple-identification}

\subsection{The three readings}

On the primary Heisenberg scope, three \emph{a priori} distinct languages point to the same desired object. The comparison is conditional.

\begin{conjecture}[conditional triple identification]
\label{v4-arith-den:thm:triple-identification}
Assume the spectral-flow operator $\ThetaAr$, the ordered-bar/chiral-homology comparison, the profinite quantum arithmetic Chern--Simons boundary theory, and the necessary topological dualities. Then there should be canonical isomorphisms of graded vector spaces, compatible with $\ThetaAr$:
\[
\HAd(\Zbar)\;\cong\;\HchAr(\Zbar,\HAr)\;\cong\;\mathrm{HH}^{\mathrm{ch}}_{\bullet}\!\bigl(\partial\,\mathrm{ACS}^{\mathrm{qu}}_{k^{\mathrm{Ar}}}\bigr).
\]
The finite Euler factors are supplied by the Bost--Connes primary pieces; the zero-side spectrum and global determinant are part of the hypothesis.
\end{conjecture}

\subsection{Dependency list}

The comparison splits into three conditional chain-level identifications.

\emph{(D) $\cong$ (O)}: Deninger's programme supplies the axioms and determinant shape of the missing cohomology. The present candidate packages these axioms by the Platonic bar $\BAr(\HAr)$. The comparison becomes theorem-grade only after the spectral-flow operator and determinant-class topology are constructed.

\emph{(O) $\cong$ (C)}: The boundary chiral homology of a 3D gauge theory, in the ordered-bar presentation, is expected to be a filtered colimit of bar complexes indexed by configurations of closed points. For a quantum arithmetic Chern--Simons theory with boundary trace equal to $\VAr$, the ordered bar at each configuration should match $\BAr_S$. This is a boundary comparison hypothesis.

\emph{(D) $\cong$ (C)}: would follow by composition of the above conditional comparisons.

\subsection{Dictionary table}

\begin{table}[h]
\centering
\small
\begin{tabular}{p{0.25\linewidth}|p{0.32\linewidth}|p{0.32\linewidth}}
Deninger target & Chiral candidate & 3D ACS reading \\
\hline
$\HAd(\Zbar)$ & $\HchAr(\Zbar,\HAr)$ & $\partial\,\mathrm{ACS}^{\mathrm{qu}}$ chiral homology \\
Zero generator $\Theta$ & finite-stage $N_S$ plus $\ThetaAr$ hypothesis & Wilson loop around $K_p$; conditional surface at $\infty$ \\
Lefschetz determinant & Tate--Mellin character plus determinant hypothesis & Boundary partition function, conditional \\
Poincar\'e duality & Koszul self-duality, conditional & 3D framed bordism duality, conditional \\
Purity & $\mathrm{Spec}(\ThetaAr)\subset 1/2+i\mathbb{R}$ on $H^1$ & Partition-function spectral theorem, conditional \\
RH & Archimedean A-TP & Partition-function zeros on critical line \\
Weil $H^1$ bulk & $H^{1}_{\mathrm{ch}}$ with spectral-flow hypothesis & Bulk state space on $K_p$-complement \\
$q^{i/2}$ weights & $p^{s}$-scaling per place & Chern--Simons level $k^{\mathrm{Ar}}$ \\
Tate poles & $H^0, H^2$ Tate lines & Vacuum and conformal insertion \\
\end{tabular}
\caption{Conditional dictionary between three presentations of the desired motivic cohomology of $\Zbar$.}
\label{v4-arith-den:tab:triple-dictionary}
\end{table}

\section{The 3D Arithmetic Chern--Simons Bulk}
\label{v4-arith-den:sec:3D-ACS}

\subsection{Kim's classical arithmetic Chern--Simons}

Kim (2015, arXiv:1510.05818) constructs classical arithmetic Chern--Simons: for a finite gauge group $A$, a cocycle class $c \in H^3(BA, \mathbb{R}/\mathbb{Z})$, and a ring of integers $\mathcal{O}_K$, the classical arithmetic Chern--Simons assigns to each Galois representation $\rho\colon G_K \to A$ the phase
\[
\mathrm{ACS}_c(\rho)\;=\;\exp\!\Bigl(2\pi i\int_{\mathrm{Spec}\,\mathcal{O}_K} c(\rho)\Bigr)\;\in\;U(1).
\]
The unexponentiated action lies in $\mathbb{R}/\mathbb{Z}$. The integral is defined using the Artin--Verdier duality pairing on $\mathrm{Spec}\,\mathcal{O}_K$ (cohomological dimension $3$).

\subsection{Quantum extension}

The conditional comparison uses a quantum extension of Kim's classical theory: a 3D gauge theory with continuous gauge group $G$ (or its arithmetic avatar) whose path integral assigns to each Galois representation a complex amplitude rather than a phase.

\begin{conjecture}[quantum arithmetic CS axioms]
\label{v4-arith-den:constr:quantum-ACS}
Let $G$ be an arithmetic Langlands gauge group. A quantum arithmetic Chern--Simons extension, if it exists in the form needed here, should be a 3D topological field theory on the arithmetic 3-space whose:
\begin{itemize}
\item \emph{state space} $Z(\Sigma)$ on a 2-boundary $\Sigma$ is the arithmetic chiral algebra of the boundary WZW at level $k^{\mathrm{Ar}}$;
\item \emph{Wilson-loop operator} $W(K, \rho)$ around a link $K \subset \Zbar$ in representation $\rho$ is the holonomy of the bulk connection;
\item \emph{partition function} $Z(\Zbar)$ on the closed arithmetic 3-space is a regularised integral over connections.
\end{itemize}
For the primary Heisenberg setup, $Z(\Sigma_\infty) = \VAr$ at the archimedean boundary circle, and the partition function should recover the polar-corrected determinant $\xiR$ after the Tate-Mellin character and Deninger determinant hypotheses are imposed.
\end{conjecture}

\begin{remark}
Classical finite-gauge ACS is rigorous (Kim 2015). The quantum extension above is conjectural. It is recorded here as the gauge-theoretic side of the conditional triple comparison, not as an established construction.
\end{remark}

\subsection{Wilson-loop Frobenius identity}

\begin{proposition}[finite-level unramified Wilson insertion]
\label{v4-arith-den:thm:wilson-frobenius}
At finite level, for an unramified representation $\rho_N$ of the local Galois quotient, the Wilson insertion around the prime knot $K_p$ is the class function
\[
W_N(K_p, \rho_N)\;=\;\mathrm{tr}\,\rho_N(\mathrm{Frob}_p).
\]
\end{proposition}

This is the finite unramified holonomy statement: Wilson loops read holonomy of the bulk connection, and under the Morishita knots-and-primes dictionary the unramified holonomy around $K_p$ is $\mathrm{Frob}_p \in G_p/I_p$. The profinite, continuous, ramified, and wild statements require the quantum ACS and local epsilon-factor refinements.

\subsection{Archimedean Wilson-surface}

At the archimedean place the Frobenius is a Wilson-surface rather than a Wilson-loop.

\begin{conjecture}[archimedean Wilson-surface dictionary]
\label{v4-arith-den:constr:F-infty-wilson}
Let $\Sigma_\infty$ denote the formal archimedean boundary cell in the conjectural quantum ACS theory. The archimedean scaling operator should correspond to a Wilson-surface operator
\[
F_\infty\;=\;W(\Sigma_\infty, \sigma_{\mathrm{area}})
\]
where $\sigma_{\mathrm{area}}$ is the area-scaling 2-representation of the arithmetic Langlands gauge 2-group. Conjugacy with a Virasoro zero mode is a separate primary-Virasoro comparison.
\end{conjecture}

\section{Purity and the Riemann Hypothesis}
\label{v4-arith-den:sec:purity-RH}

\subsection{Purity defined}

\begin{definition}[Frobenius purity]
\label{v4-arith-den:def:purity}
For the Deninger-chiral candidate, purity on the middle degree means
\[
\mathrm{Spec}\bigl(\ThetaAr|H^1_{\mathrm{ch}}(\Zbar,\HAr)\bigr)
\subset \frac12+i\mathbb{R}.
\]
Finite-place Bost--Connes unitarity is a separate local statement; it is not a substitute for construction of the global zero operator $\ThetaAr$.
\end{definition}

\subsection{Finite-prime purity}

\begin{proposition}[finite-prime Bost--Connes unitarity]
\label{v4-arith-den:thm:finite-prime-purity}
For every prime $p$, the one-parameter unitary group $e^{itN_p}$ on the primary Bost--Connes zero-mode factor has spectrum contained in the unit circle. Its heat trace is the local Euler factor $(1-p^{-s})^{-1}$.
\end{proposition}

\begin{proof}
The generator $N_p$ is self-adjoint on the primary Hilbert completion with eigenvalues $r\log p$ for $r\geq 0$. Hence $e^{itN_p}$ is unitary. The heat trace is $\sum_{r\geq0}e^{-sr\log p}=(1-p^{-s})^{-1}$.
\end{proof}

\subsection{Archimedean purity}

Archimedean purity is the outstanding residual.

\begin{theorem}[RH $\Leftrightarrow$ zero-generator purity, conditional]
\label{v4-arith-den:thm:RH-purity}
Assume the Deninger determinant identity of Conjecture~\ref{v4-arith-den:thm:Lefschetz-character}: the middle operator $\ThetaAr$ is determinant-class and its spectrum is the non-trivial zero multiset of $\xiR$. Then the Riemann Hypothesis is equivalent to purity
\[
\mathrm{Spec}(\ThetaAr|H^1)\subset \frac12+i\mathbb{R}.
\]
\end{theorem}

\begin{proof}
Under the hypothesis, each eigenvalue of $\ThetaAr$ is a non-trivial zero $\rho$ of $\xiR$, with multiplicity. The displayed purity condition is exactly $\mathrm{Re}(\rho)=1/2$ for every non-trivial zero.
\end{proof}

\subsection{Archimedean purity as positivity}

Archimedean purity can be reformulated as an explicit positivity statement.

\begin{theorem}[archimedean Tate positivity]
\label{v4-arith-den:thm:A-TP}
Archimedean Frobenius purity is equivalent to the \emph{archimedean Tate positivity} (A-TP) statement:
\[
W_\infty(f\ast\widetilde f)\;\geq\;0\qquad\text{for every admissible } f \in \mathrm{PW}(\mathbb{R})
\]
where $W_\infty$ is the archimedean contribution to the Weil explicit formula,
\[
W_\infty(f\ast\widetilde f)\;=\;\frac{1}{2\pi}\int_{-\infty}^{\infty}|\widehat f(1/2+it)|^2\bigl[\mathrm{Re}\,\psi(1/4+it/2)+\log\pi\bigr]\,dt.
\]
\end{theorem}

\begin{proof}[Proof sketch]
On the scoped admissible test class, the explicit Weil distribution decomposes into finite-prime, archimedean, and polar/trivial-zero pieces. The finite-prime and polar pieces are closed by the corresponding trace-formula and boundary-term inputs on that scoped class. The remaining inequality is exactly the displayed archimedean integral. Full Weil positivity is RH-equivalent; the theorem is an equivalence of formulations, not a proof of RH.
\end{proof}

\section{A-TP and the Elementary Sub-Classes}
\label{v4-arith-den:sec:a-tp-and-subclasses}

A-TP is Riemann-Hypothesis-equivalent and thus not proved here. What is proved in the audited elementary lanes is A-TP on a catalog of explicit test-function sub-classes, each closed through a distinct instrument. The classes are not asserted to be linearly ordered by inclusion.

\subsection{The digamma kernel}

Define the digamma kernel
\[
g(t)\;:=\;\mathrm{Re}\,\psi(1/4+it/2) + \log\pi.
\]

\begin{proposition}[monotonicity + sign-change]
\label{v4-arith-den:prop:digamma-monotone}
$g$ is even, strictly increasing in $|t|$, with unique positive zero $t_\ast = 0.8506623044\ldots$.
\end{proposition}

\begin{proposition}[exact identity]
\label{v4-arith-den:prop:g-RS}
$g(t) = 2\theta'_{\mathrm{RS}}(t) + 2\log\pi$, where $\theta_{\mathrm{RS}}(t)=\mathrm{Im}\,\log\Gamma(1/4+it/2)-(t/2)\log\pi$ uses the continuous branch with $\theta_{\mathrm{RS}}(0)=0$.
\end{proposition}

\subsection{Unconditional sub-classes}

\begin{proposition}[audited A-TP sub-classes]
\label{v4-arith-den:thm:eight-subclasses}
Each of the following sub-classes of $\mathrm{PW}(\mathbb{R})$ admits an unconditional proof of A-TP on its elements:
\begin{enumerate}
\item[\textbf{HFD}] high-frequency dominance: $\int_{|t|>t_\ast}|\widehat f|^{2}\,g\geq \int_{|t|<t_\ast}|\widehat f|^{2}|g|$ (digamma Hurwitz instrument);
\item[\textbf{SHF}] Stirling-four high-frequency, $T_{\mathrm{St4}}\approx 0.873$ enlargement;
\item[\textbf{HD}] Hankel dominance via Binet--Laplace representation;
\item[\textbf{$\mathcal{C}^{+}_{\mathrm{Gauss}}$}] Gaussian positive cone at $\lambda\geq \lambda_c \approx 2.52$ (explicit $\mathrm{erfc}$ series);
\item[\textbf{VK instrument}] test functions whose support and growth allow the Vinogradov--Korobov zero-free strip of width $\eta(T)\asymp (\log T)^{-2/3}(\log\log T)^{1/3}$ to dominate the residual term;
\item[\textbf{$\mathrm{PW}^{\mathrm{TM}}$}] Tate--Mellin sub-class admitting factorisation $f_M(s) = \xiR(s)\cdot h(s)$ with Hermite symmetry;
\item[\textbf{$\mathrm{PW}^{\mathrm{CP}}$}] Burnol co-Poisson sub-class: Fourier-dual to HFD;
\item[\textbf{IE}] integral-energy sub-class: Slepian--Pollak prolate-spheroidal instrument; unconditionally covers test functions of exponential type $\leq 1/2$.
\end{enumerate}
The union is a genuine enlargement of the individually audited classes, but no quantified coverage theorem for the complement is claimed.
\end{proposition}

\subsection{The structural floor}

\begin{proposition}[structural floor diagnosis]
\label{v4-arith-den:thm:floor}
The audited elementary reductions of A-TP (digamma Hurwitz, Stirling, Binet, Mellin--Barnes, Hadamard pair-pole, Gram matrix, Guinand--Weil, Nyman--Beurling Möbius, Bost--Connes scattering) leave the same kind of residual: a compact archimedean positivity problem not removed by the elementary transform. This is a diagnosis of the audited routes, tied to the non-Hausdorff nature of the adele class space $\mathbb{A}_\mathbb{Q}/\mathbb{Q}^{\times}$; it is not a universal no-go theorem for every possible Hilbert-space construction.
\end{proposition}

\subsection{Fourier-dual obstructions}

\begin{conjecture}[Fourier-dual bounded-interval obstruction]
\label{v4-arith-den:prop:fourier-dual}
The residual of A-TP decomposes into two Fourier-dual bounded-interval obstructions:
\begin{itemize}
\item spectral-side residual on $t \in [-t_\ast, t_\ast]$ with $t_\ast \approx 0.8507$;
\item time-side residual on $y \in (0, 1/\pi)$ with $1/\pi \approx 0.318$.
\end{itemize}
The two are expected to be Fourier-dual under the Burnol co-Poisson transform. Making this a theorem requires defining the residual functional, the transform domain, and the endpoint normalisation. The full obstruction is RH-equivalent.
\end{conjecture}

\section{All-Genus Extension}
\label{v4-arith-den:sec:all-genus}

\subsection{\texorpdfstring{Arithmetic genus-$g$ data}{Arithmetic genus-g data}}

\begin{definition}[arithmetic genus-$g$ datum]
\label{v4-arith-den:def:genus-g}
For $g \geq 0$, an arithmetic genus-$g$ datum is a triple
\[
\mathcal{D}_g=(B_g,E_g,\varphi_g)
\]
where $B_g$ is the chosen arithmetic base/window, $E_g$ is the cohomological or chiral coefficient object, and $\varphi_g$ is the finite-place and archimedean Frobenius/scaling datum. Its motivic center and weight are denoted $w_{\mathcal{D}_g}$. A rank-$2g$ Heisenberg model is one realisation of $E_g$, not the definition of the datum.
\end{definition}

\subsection{All-genus character identity}

\begin{conjecture}[conditional all-genus Lefschetz character]
\label{v4-arith-den:thm:all-genus-character}
Assume the genus-$g$ Deninger package, rank-$g$ Koszul-Petersson duality, finite-place temperedness, arithmetic Chern--Simons comparison, and spectral-flow determinant. Then
\[
\chi\bigl(\mathcal{V}^{\mathrm{prim}}_g\bigr)(s)\;=\;\prod_i\det\nolimits_{\infty}\!\bigl(s-\Theta_g\,\big|\,H^{i}_{\mathrm{ch}}(B_g,E_g)\bigr)^{(-1)^{i+1}}\;=\;\Lambda_{\mathcal{D}_g}(s),
\]
where $\Lambda_{\mathcal{D}_g}$ is the completed motivic L-function of the genus-$g$ datum. For $g = 0$, this recovers Theorem~\ref{v4-arith-den:thm:Lefschetz-character} and the Riemann framework.
\end{conjecture}

\subsection{Motivic-weight RH}

\begin{conjecture}[motivic-weight Riemann Hypothesis reformulation]
\label{v4-arith-den:thm:motivic-weight-RH}
Under the same hypotheses, the motivic Riemann Hypothesis for $\mathcal{D}_g$ is equivalent to placement of the degree-one zero-generator spectrum on the critical line determined by $w_{\mathcal{D}_g}$.
\end{conjecture}

\section{Residual Obstructions}
\label{v4-arith-den:sec:residuals}

After the constructions of Sections~\ref{v4-arith-den:sec:chiral-algebras}--\ref{v4-arith-den:sec:all-genus}, the obligations separate as follows.
\[
\begin{array}{l|l}
\text{Status} & \text{Obligation}\\
\hline
\text{closed in this paper} & \text{primary finite Euler factor and Gaussian Tate factor}\\
\text{closed on finite stages} & D_S^2=0\text{ on the abelian primary reciprocity-closed bar}\\
\text{conditional} & \text{global determinant-class operator }\ThetaAr\\
\text{conditional} & \text{ordered-bar/chiral-homology comparison}\\
\text{conditional} & \text{quantum arithmetic Chern--Simons boundary theory}\\
\text{conditional} & \text{archimedean Wilson-surface dictionary and primary Virasoro comparison}\\
\text{open/RH-equivalent} & \text{Hilbert--Polya spectral flow and full A-TP}\\
\text{conditional all-genus} & \text{rank-}g\text{ Koszul-Petersson and motivic weight compatibility}
\end{array}
\]

\subsection{Path to RH}

Under the spectral-flow and determinant hypotheses, RH reduces to archimedean Tate positivity (Theorem~\ref{v4-arith-den:thm:A-TP}). A-TP is a statement about one explicit integral, the archimedean contribution $W_\infty(f\ast\widetilde f)$ against the digamma kernel $g(t) = \mathrm{Re}\,\psi(1/4+it/2) + \log\pi$. It is closed unconditionally on the audited test-function sub-classes listed above. The complement remains RH-equivalent.

The arithmetic chiral homology framework does not close A-TP. What it provides is:
\begin{itemize}
\item A precise, chain-level-explicit candidate for Deninger's wish-list.
\item A conditional triple comparison explaining how the motivic, operadic, and gauge-theoretic languages should refer to the same object.
\item An honest isolation of the residual obstruction as a single positivity statement with Fourier-dual symmetric form.
\item An audited lower bound on the unconditional sub-class: the listed instruments supply unconditional A-TP on their union.
\end{itemize}

\section{References}
\label{v4-arith-den:sec:references}

\begin{thebibliography}{99}

\bibitem{BD2004} A.~Beilinson and V.~Drinfeld, \emph{Chiral algebras}, AMS Colloquium Publications 51 (2004).

\bibitem{Bombieri1987} E.~Bombieri, \emph{The Riemann zeta function}, lecture notes (1987).

\bibitem{BostConnes1995} J.-B.~Bost and A.~Connes, \emph{Hecke algebras, Type~III factors and phase transitions with spontaneous symmetry breaking in number theory}, Selecta Math.~1 (1995), no.~3, 411--457. arXiv:math/9508003.

\bibitem{ConnesSelecta1999} A.~Connes, \emph{Trace formula in noncommutative geometry and the zeros of the Riemann zeta function}, Selecta Math.~5 (1999), no.~1, 29--106. arXiv:math/9811068.

\bibitem{deBranges1968} L.~de~Branges, \emph{Hilbert spaces of entire functions}, Prentice-Hall, 1968.

\bibitem{Deninger1998} C.~Deninger, \emph{Some analogies between number theory and dynamical systems on foliated spaces}, in Proc.~ICM~1998, Vol.~I, 163--186.

\bibitem{Deninger2002} C.~Deninger, \emph{A note on arithmetic topology and dynamical systems}, in Algebraic number theory and algebraic geometry, Contemp.~Math.~300 (2002), 99--114.

\bibitem{Francis2013} J.~Francis, \emph{The tangent complex and Hochschild cohomology of $E_n$-rings}, Compos.~Math.~149 (2013), no.~3, 430--480.

\bibitem{Kim2015} M.~Kim, \emph{Arithmetic Chern--Simons theory I}, arXiv:1510.05818.

\bibitem{Lagarias1999} J.~C.~Lagarias, \emph{On a positivity property of the Riemann $\xi$-function}, Acta Arith.~89 (1999), 217--234. arXiv:math/9805135.

\bibitem{Li1997} X.-J.~Li, \emph{The positivity of a sequence of numbers and the Riemann hypothesis}, J.~Number Theory 65 (1997), 325--333. arXiv:math/9712243.

\bibitem{Mazur1973} B.~Mazur, \emph{Notes on \'etale cohomology of number fields}, Ann.~Sci.~\'ENS~(4) 6 (1973), 521--552.

\bibitem{Meyer2005} R.~Meyer, \emph{On a representation of the idele class group related to primes and zeros of $L$-functions}, Duke Math.~J.~127 (2005), 519--595. arXiv:math/0311468.

\bibitem{Morishita2012} M.~Morishita, \emph{Knots and primes: an introduction to arithmetic topology}, Universitext, Springer, 2012. arXiv:0904.3399.

\bibitem{Positselski2011} L.~Positselski, \emph{Two kinds of derived categories, Koszul duality, and comodule-contramodule correspondence}, Mem.~AMS 212 (2011).

\bibitem{Tate1950} J.~T.~Tate, \emph{Fourier analysis in number fields and Hecke's zeta-functions}, PhD thesis, Princeton (1950).

\bibitem{Weil1952} A.~Weil, \emph{Sur les ``formules explicites'' de la th\'eorie des nombres premiers}, Meddelanden fr\aa n Lunds Univ.~Mat.~Sem., 1952 (in Oeuvres Scientifiques~II).

\bibitem{Witten1989} E.~Witten, \emph{Quantum field theory and the Jones polynomial}, Commun.~Math.~Phys.~121 (1989), 351--399.

\end{thebibliography}

\end{document}
