\chapter{Dependency Graph of the Three Closing Conjectures}
\label{v4-arith:app:three-conjectures-dep}

The three conjectures F1, F2, F3 of Chapter~\ref{v4-arith:open-frontiers}
are hierarchically ordered and mutually consistent. This appendix
records the dependency graph explicitly, the local theorems each
imports, and the global gap each fills.

\section{The Dependency Graph}
\label{v4-arith:app:C:graph}

\begin{center}
\begin{tikzcd}[row sep=large, column sep=large]
\text{F1: global arith.~AG} \ar[r] \ar[d] & \text{F2: perfectoid }E_{2} \ar[d] \\
\text{Local F1 (Fargues--Scholze)} \ar[ur, dashed] & \text{F3: arith.~Ben-Zvi--Nadler}
\end{tikzcd}
\end{center}

F1 and F2 are each theorem-locally-conjecture-globally. F3 combines
the local inputs of F1 and F2 with arithmetic Ben-Zvi--Nadler
machinery. The global identification of the Hochschild trace with
$\mathcal{V}^{\mathrm{prim}}$ remains conditional.

\section{F1: Global Arithmetic Arinkin--Gaitsgory}
\label{v4-arith:app:C:F1-details}

\begin{conjecture}[restatement of F1]
\label{v4-arith:app:C:F1-restatement}
For $G=GL_{2}$ and the Selmer-derived global spectral stack
$\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}$:
\begin{equation}
\mathrm{D}([GL_{2}])^{\mathrm{sph\text{-}fin}}\;\simeq\;\mathrm{IndCoh}_{\mathrm{Nilp}}\bigl(\mathcal{X}^{\mathrm{Sel}}_{\bar\rho,\det,\mathcal{L}}\bigr).
\end{equation}
\end{conjecture}

\paragraph{Local inputs.}
\begin{enumerate}
\item Fargues--Scholze arXiv:2102.13459 (local geometrization and
spectral action, not the displayed EG equivalence).
\item Caraiani--Scholze arXiv:1511.02418 (unitary Shimura variety case).
\item Emerton--Gee stack construction arXiv:1908.07185.
\end{enumerate}

\paragraph{Global gap (conjecture).}
\begin{itemize}
\item Proof of the local automorphic-to-Emerton--Gee
$\mathrm{IndCoh}_{\mathrm{Nilp}}$ comparison, including small primes
and central-character families.
\item Compatibility of local comparison functors under
restricted-tensor-product gluing over primes.
\item Identification of the Whittaker model across all places
simultaneously.
\item Functional-equation-level compatibility between spectral and
automorphic sides.
\end{itemize}

\paragraph{Estimated paper length.} 80--120 pages.

\section{F2: Perfectoid $E_{2}$-Enhancement}
\label{v4-arith:app:C:F2-details}

\begin{conjecture}[restatement of F2]
\label{v4-arith:app:C:F2-restatement}
The local Iwahori Hecke category $\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$
carries a canonical $E_{2}$-monoidal structure from the
perfectoid Beilinson--Drinfeld Grassmannian over $\mathrm{Spec}\,\mathbb{Z}_{p}$,
and the restricted tensor product
$\bigotimes'_{p}\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},p}$ inherits a
globally-defined $E_{2}$-monoidal structure.
\end{conjecture}

\paragraph{Local ingredients (theorem).}
\begin{enumerate}
\item Perfectoid affine Grassmannian (Fargues--Scholze, Scholze
diamonds).
\item Witt-vector affine Grassmannian (Zhu arXiv:1603.05593;
Bhatt--Scholze arXiv:1507.06490).
\item Equal-characteristic BD Grassmannian $E_{2}$-structure
(Mirkovi\'c--Vilonen + beilinson-drinfeld-grassmannian machinery).
\end{enumerate}

\paragraph{Global gap (conjecture).}
\begin{itemize}
\item Diamond-gluing of Iwahori Hecke categories across primes.
\item Compatibility with Satake and Whittaker equivalences.
\item Perfectoid Dunn-additivity argument producing $E_{1}$-algebra
structure on the Hochschild trace.
\end{itemize}

\paragraph{Estimated paper length.} 60--80 pages.

\section{F3: Arithmetic Ben-Zvi--Nadler}
\label{v4-arith:app:C:F3-details}

\begin{conjecture}[restatement of F3]
\label{v4-arith:app:C:F3-restatement}
$\mathrm{HH}_{\bullet}\bigl(\mathrm{Hk}^{\mathrm{Iw}}_{GL_{2},\mathrm{glob}}\bigr)\xrightarrow{\sim}\mathcal{V}^{\mathrm{prim}}$
as $E_{1}$-algebras.
\end{conjecture}

\paragraph{Ingredients.}
\begin{enumerate}
\item Conjecture F1 (for the spectral side identification).
\item Conjecture F2 (for $E_{2}$-enhancement of the local Hecke
factors).
\item Ben-Zvi--Nadler arXiv:0904.1247 (for the $\mathbb{C}$-version,
which F3 arithmeticises).
\item Explicit computation matching the Hochschild trace character
to $\zeta(s)$.
\end{enumerate}

\paragraph{What F3 accomplishes.}
\begin{itemize}
\item Unifies Gaiotto's CS presentation
(\Cref{v4-arith:thm:arith-CS-VA-correspondence}).
\item Unifies Bezrukavnikov--Bernstein's Hochschild presentation
(\Cref{v4-arith:thm:crowning-placement}).
\item Unifies Beilinson-solo's bar--cobar presentation
(\Cref{v4-arith:thm:bar-verifications}).
\item Proves the arithmetic six-window placement
(\Cref{v4-arith:thm:six-window-placement}).
\end{itemize}

\paragraph{Estimated paper length.} 40--60 pages.

\section{Independent Conjecture: The $\mathsf{G}$-Row Complementarity}
\label{v4-arith:app:C:G-row-independent}

\begin{conjecture}[$\kappa+\kappa^{!}=0\Leftrightarrow\xi(s)=\xi(1-s)$]
\label{v4-arith:app:C:G-row-statement}
For the arithmetic Heisenberg $\mathcal{V}^{\mathrm{prim}}_{\mathrm{Heis}}$,
the Vol~I derived-centre complementarity
$\kappa^{\mathrm{Ar}}+(\kappa^{!})^{\mathrm{Ar}}=0$ is equivalent
to the Riemann functional equation
$\xi(s)=\xi(1-s)$.
\end{conjecture}

This is \emph{independent} of F1, F2, F3: its proof proceeds
directly from the arithmetic Koszul-resolution computation of
Hochschild cochains on the arithmetic Heisenberg, using Tate's
adelic Poisson summation. A proof of this conjecture would inscribe
the arithmetic $\mathsf{G}$-row as a Vol~I Theorem~C corollary.

\paragraph{Estimated paper length.} 30--50 pages.

\section{Roadmap to Full Theorem-Status}
\label{v4-arith:app:C:roadmap}

Full theorem-status inscription of the arithmetic branch requires:

\begin{enumerate}
\item \textbf{Paper (A):} Prove the $\mathsf{G}$-row independent
conjecture
(\Cref{v4-arith:app:C:G-row-statement}). This inscribes the Riemann
functional equation as a consequence of Vol~I Koszul duality.
\item \textbf{Paper (B):} Prove F3 conditional on F1 and F2. This
unifies the three main presentations.
\item \textbf{Paper (C):} Prove F1 (global arithmetic AG).
\item \textbf{Paper (D):} Prove F2 (perfectoid $E_{2}$-enhancement).
\item \textbf{Paper (E):} Combine (B)--(D) to unconditionalise F3.
\end{enumerate}

Papers (C)--(E) are long-term (multi-year). Paper (A) is
self-contained and could be the first inscription-quality paper to
come out of the arithmetic branch.

\section{Connection to Vol~III}
\label{v4-arith:app:C:vol3-connection}

Vol~III's $\mathsf{B}$-row $\kappa+\kappa^{!}=8$ (Mukai-enhanced K3
Heisenberg via Bruinier Heegner Chern-class reciprocity) has an
arithmetic avatar (F4, Chapter~\ref{v4-arith:open-frontiers}~\S3).
The combined programme; arithmetic $\mathsf{G}$-row
(Paper~(A)) plus arithmetic $\mathsf{B}$-row (F4); would inscribe
two of the five Vol~I derived-centre-ceiling values as arithmetic
consequences of automorphic / Galois-deformation theorems. This
would move the programme from a chiral-algebra corpus to a
chiral-algebra-arithmetic corpus.

\section{Extended Graph with F-RH and Residuals}
\label{v4-arith:app:C:extended-graph}

After the structural closure of Chapter~\ref{v4-arith:closure} and
the inscription of F-RH in Chapter~\ref{v4-arith:rh-reformulation},
the dependency DAG extends as follows.

\paragraph{Spine A (six-window placement).}
\begin{center}
\begin{tikzcd}[row sep=small, column sep=small]
\text{F1.a (local comparison, TW)} \ar[dr] & \text{F1.c (Selmer target)} \ar[d] & \text{F2.a (spherical input)} \ar[d] \\
\text{L}_{\mathrm{ACD}} \ar[r] & \text{F1 conditional} \ar[r] & \text{F2 conditional} \ar[d] \\
\text{F2.c ($\infty$-Tate)} \ar[ur] & \text{F3.BZN}^{\mathrm{Ar}} \ar[r] & \text{F3 closed}
\end{tikzcd}
\end{center}

\paragraph{Spine B (RH closure).}
\begin{center}
\begin{tikzcd}[row sep=small, column sep=small]
\text{arith.~Positselski} \ar[r] & \text{P1 functional equation} \ar[dr] & \\
\text{Tate 1950} \ar[r] & \text{P2 unconditional} \ar[r] & \text{F-RH} \ar[r, "\text{VB}^{*}"] & \text{RH} \\
\text{Koszul--Pet compat} \ar[r] & \text{P3 scoped unitarity} \ar[ur] & &
\end{tikzcd}
\end{center}

The dependency partitions into two spines:

\paragraph{Spine A (six-window placement, RH-independent).}
$\mathrm{L}_{\mathrm{ACD}}$ $\to$ F1 $\to$ F3.BZN$^{\mathrm{Ar}}$
$\to$ F3; F2.c supplies only the restricted-tensor step of F2, while
the mixed-characteristic Iwahori $E_{2}$ local input remains
theorem-waiting. Closing Spine A would inscribe the six conditional
windows of $\mathcal{V}^{\mathrm{prim}}$ as theorem-grade.

\paragraph{Spine B (RH-closure spine).}
arith.~Positselski $\to$ P1 functional-equation spine; Koszul--Pet
compat $\to$ P3 scoped unitarity; (P1, P2, P3, H-P$^{\mathrm{Ar}}$)
$\to$ F-RH under VB$^{*}$; VB$^{*}$ remains the RH-equivalent
zero-mode positivity residual.
Closing Spine B closes RH within Vol~IV's chiral-algebra framework.

The two spines are independent at the residual level: a proof of
Spine A does not close Spine B, and vice versa. Partial progress
on either spine is progress on the branch; full closure of either
spine is an independent theorem.

\section{Residual Obligation Catalog}
\label{v4-arith:app:C:residual-catalog}

\begin{table}[h]
\centering
\small
\begin{tabular}{l|l|l|l}
Residual & Spine & Paper-length & Current status \\
\hline
$\mathrm{L}_{\mathrm{ACD}}$ (adelic descent) & A & 80--120 pp & Conjectural \\
F2.c ($\infty$-Tate product) & A & 20--40 pp & Proved by Ch.~\ref{v4-arith:tate-tensor} \\
F2.b (mixed-char Iwahori $E_{2}$) & A & 40--80 pp & Theorem-waiting \\
F3.BZN$^{\mathrm{Ar}}$ (arith.~BZN) & A & 40--60 pp & Conjectural \\
arith.~Positselski & B & 30--50 pp & Strict abelian Heis. model installed; full scope separate \\
Koszul--Pet compat & B & 10--20 pp & Sph-fin cuspidal core theorem \\
VB$^{*}$ (arith.~Virasoro positivity) & B & Unknown & Positive spectral package implies RH \\
\end{tabular}
\caption{Catalog of residual obligations after Chapter~\ref{v4-arith:closure}
and Chapter~\ref{v4-arith:rh-reformulation}.}
\label{v4-arith:app:C:residual-table}
\end{table}

\section{The Minimal Path to RH}
\label{v4-arith:app:C:minimal-path}

The minimal closure to RH inside Vol~IV's framework requires four
items from Spine B: the strict abelian-Heisenberg arithmetic
Positselski bar, Koszul--Pet compatibility on the normalised core,
H-P$^{\mathrm{Ar}}$, and the positive VB$^{*}$ spectral package. The
later chapters upgrade several former residuals: F2.c is theorem-grade,
the Platonic bar is a strict reciprocity-closed chain complex, and
Koszul--Pet is established on the sph-fin cuspidal core. Spectral
matching, full-sector P3, mixed-characteristic Iwahori $E_{2}$, and
VB$^{*}$ positivity remain separate obligations.

\subsection{After Route~2 Residual Catalog}
\label{v4-arith:app:C:residual-catalog-w2}

\begin{table}[h]
\centering
\small
\begin{tabular}{l|l|l|l}
Residual & Spine & Paper-length & Post-route~2 status \\
\hline
$\mathrm{L}_{\mathrm{ACD}}.0,.1,.2,.3$ & A & each 5--10 pp & Partial reductions; global glue remains conditional \\
(BC-diamond-glue).core & A & 10--15 pp & Conjectural, single cross-prime Bernstein compat \\
F2.c (pointed $E_{n}$ tightened) & A &; & Proved by \Cref{v4-arith:tate:thm:F2c-main}; pointed central-unit datum explicit \\
F3.BZN$^{\mathrm{Ar}}$ R1.fin-type & A &; & External finite-type input; arithmetic application conditional \\
F3.BZN$^{\mathrm{Ar}}$ R1.formal.a & A &; & Partial formal input; full pro-etale BZN not closed \\
F3.BZN$^{\mathrm{Ar}}$ R1.formal.b,c & A & 50--90 pp & Conjectural (ind-colimit and flat-locus matching) \\
F3.BZN$^{\mathrm{Ar}}$ R2 (Selmer target) & A & 20--40 pp & Target corrected; Noetherian/nilpotent-support checks remain theorem-waiting \\
F3.BZN$^{\mathrm{Ar}}$ R3 (loop convention) & A &; & Conditional; $B\widehat{\mathbb Z}$ loop formalism not standard BZN \\
F3.BZN$^{\mathrm{Ar}}$ R4 wild $p\in\{2,3\}$ & A &; & Local repair; global wild functoriality open \\
Wild Langlands functoriality & A &; & Conjectural, new (\Cref{v4-arith:bzn-rcompletion:conj:wild-langlands-functorial}) \\
arith.~Positselski C1--C5 & B &; & Strict completed model installed for the abelian primary bar \\
arith.~Positselski (abelian Heis.) & B &; & P1 biconditional closed on the strict primary scope \\
Koszul--Pet K5 (Godement--Jacquet) & B &; & Conditional normalisation on the sph-fin cuspidal core \\
Koszul--Pet compat & B &; & Sph-fin cuspidal core theorem; full-sector extension separate \\
H-P$^{\mathrm{Ar}}$ & B &; & Conjectural; domain theorem closes, zeta-zero spectral matching open \\
VB$^{*}$ $\Rightarrow$ F-RH & B &; & Theorem from P2, P3, H-P$^{\mathrm{Ar}}$, positive trace \\
VB$^{*}$ (main direction) & B &; & Positive spectral package; determinacy alone is insufficient \\
VB$^{*}$ converse & B &; & Strictly finer than RH; 4-way equivalence (Ch.~\ref{v4-arith:HPAr-vbconverse}) \\
\end{tabular}
\caption{Post-route~2 residual catalog.}
\label{v4-arith:app:C:residual-table-w2}
\end{table}

\subsection{After Route~2 Minimal Path}

The minimal closure to RH within Vol~IV's framework, after route~2
repairs, remains a \textbf{four-input conditional spine}:

\begin{enumerate}
\item \textbf{arith.~Positselski} (Spine B): strict completed
Gersten--Parshin bar model on the abelian primary Heisenberg scope.
\item \textbf{Koszul--Pet compat} (Spine B): stable on the normalized
sph-fin cuspidal core; full $V^{\mathrm{prim}}$ compatibility and
KMS$_1$/GNS identification remain open.
\item \textbf{H-P$^{\mathrm{Ar}}$} (Spine B): the independent
Hilbert--P\'olya spectral-matching problem.
\item \textbf{VB$^{*}$ main direction} (Spine B): the positive
Stieltjes--Hamburger zero-mode spectral package.
\end{enumerate}

Spine A remains RH-independent: (BC-diamond-glue).core, F2 trace
continuity, and arithmetic BZN formal-loop compatibility affect the
theorem-grade construction of $\mathcal{V}^{\mathrm{prim}}$, not zero
placement. VB$^{*}$ remains RH-equivalent; no framework shortens it,
but the ladder of equivalent statements (Li positivity, Weil
positivity, Hamburger determinacy, Hermite--Biehler, B\'aez-Duarte
sharp rate) is catalogued in
Chapter~\ref{v4-arith:HPAr-vbconverse}.

\section{Summary}
\label{v4-arith:app:C:summary}

Three hierarchically-ordered conjectures (F1 $\to$ F2 $\to$ F3)
plus one independent conjecture ($\mathsf{G}$-row) on the synthesis
spine; P1, P2, P3, H-P$^{\mathrm{Ar}}$, and the bootstrap
VB$^{*}$ on the RH spine. The current upgrades close the categorical
F2.c tensor product and the strict abelian primary arithmetic bar.
The arithmetic branch as inscribed (\Cref{v4-arith:closure},
\Cref{v4-arith:rh-reformulation}) reduces the remaining RH work to
H-P$^{\mathrm{Ar}}$ spectral matching plus the positive
Stieltjes--Hamburger VB$^{*}$ package.
