\chapter*{Preface}
\label{v4-ch:preface}

An inscribed theorem is not a verified theorem. A claim carrying the
tag \texttt{\textbackslash ClaimStatusProvedHere} asserts that the
reader will find, within the same file, a proof. It does not assert,
and cannot by itself assert, that the proof's internal derivation is
disjoint from the sources the author consulted to arrive at the
statement. The two are routinely identified in mathematical practice,
and for good reason: one trusts the author. The programme that
precedes this volume has earned that trust across three volumes, on
the Beilinson principle, against an explicit adversarial protocol,
with over one hundred thousand tests. Yet a trust-based corpus is not
a verified corpus.

The deficiency is concrete. Consider the inscription in Vol III of
the formula
\[
 \kappa_{\mathrm{BKM}} \;=\; c_N(0)/2
\]
for the Borcherds-Kac-Moody central charge of a frame-shape orbifold
lift. In the compute engine, $c_N(0)$ is tabulated from
\texttt{FRAME\_SHAPE\_DATA}. The hardcoded expected values in the
test file are computed by halving entries of the same table. Ninety-nine
tests pass. The derivation (via the Borcherds 1998 weight theorem
applied to the input lift) and the verification (by direct arithmetic
on the tabulated lift data) share a source. Nothing can fail. No
ninety-nine-test harness is detecting anything about the inscription
beyond the arithmetic $c_N(0)/2 = c_N(0)/2$.

This is not a local accident. The source-disjoint audit across the
programme found that every programme-wide hardcoded-table
verification was of this form: the table from which the theorem was
derived also supplied the test expectations. The programme is not
verifying that its theorems are true; it is verifying that its
arithmetic on a single source is consistent. The two are routinely
identified in mathematical practice, but they are not the same.

The deficiency admits a clean remedy: a disjointness requirement. A
theorem $T$ is verified, in the sense relevant to avoid the kind of
coincidental-agreement failure exposed by the
$\Psi = 2$ coincidence masking a cross-arity sign error), only if
there exists a test whose expected value is computed along a source
disjoint from the source used to derive $T$'s formula. Disjoint means
disjoint as a set of citations, not disjoint as a rephrasing. The
source-disjoint protocol in Vols I, II, and III
(\texttt{compute/lib/independent\_verification.py}) begins to enforce
this: every test decorated with \texttt{@independent\_verification}
must declare its \texttt{derived\_from} and \texttt{verified\_against}
sources, and the decorator raises \texttt{IndependentVerificationError}
at collection time if the two sets overlap.

What the protocol does not do, at installation, is provide coverage. The
installation snapshot across the three prior volumes was:

\begin{center}
\begin{tabular}{lcl}
Vol I & \quad & 0 of 2275 ProvedHere claims covered. \\
Vol II & \quad & 0 of 1134 ProvedHere claims covered. \\
Vol III & \quad & 2 of 283 ProvedHere claims covered. \\
\end{tabular}
\end{center}

Two claims out of 3692. The infrastructure was in place; the content
was not. A programme's claim corpus can be verified one decorator at a
time, but not by the same act that produces the theorem. The
verification must be a separate intellectual operation, carried out
with a different source catalog, and held to a different standard
than the proof that produced the theorem.

Volume IV is that separate operation.

The corpus to which \(\mathrm{Real}\) applies is no longer the
installation corpus alone. Vol~I supplies the corrected Virasoro
shadow tower: the Stokes pole is \(c_S=-218/45\), the Borel radius is
\[
 |\omega|^2(c)=\frac{c^2(5c+22)}{4(45c+218)},
\]
and the Riccati equation lives on
\(U=(\log H)'-2/t\), not on \(H\) itself. Vol~I also separates the
four conductors \(K,K^\kappa,K_c,K_g\), records the
\(p=691\) Chenevier determinant, and fixes the eight-row
Gritsenko--Cl\'ery Borcherds spread as realization input. Vol~II
supplies the \(\mathsf{SC}^{\mathrm{ch,top}}\) heptagon and the
finite-jet Khan--Zeng lane: the shifted-cotangent BV action and the
CME/PVA-Hamiltonian equivalence are constructed; the all-loop QME,
reflected weight identity, boundary vertex algebra, and \(E_3\) lift
remain conditional on analytic SDR, image-choice Stokes,
field-parity, and self-image renormalisation. Vol~III supplies the
two-stage functor
\[
 \Phi_d=\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}\circ
 \Phi^{\mathrm{FA}}_d,
\]
the K3 Hall--Drinfeld chiral-bialgebra crown, Joyce--KPS generic
compact-CY3 MNOP, \(S^3\)-framing on generic compact Calabi--Yau
threefold Lagrangians, and the \(\mathfrak{so}(4,20)\) K3 Yangian
trichotomy.

The arithmetic branch contributes a native Vol~IV residual calculus.
After the post-Tate quotient is imposed, the ordinary Meyer graph
dual does not support point or finite-jet Hadamard residue
functionals on the critical-line ordinate set
\(\Gamma_\xi^{\mathrm{crit}}\). This negative theorem does not close
the spectral-flow problem. It says exactly where a surviving route
must live: a stronger rigged, Paley--Wiener, de Branges,
reproducing-kernel, nonlocal \(L^2\), or BV--BFV boundary topology in
which Hadamard trace and jet maps are continuous and compatible with
the post-Tate quotient.

This volume does not introduce new theorems as its primary content.
It introduces a verification layer, defined precisely enough to have
its own theorems (the existence of the realization pair, its
functoriality on the non-degenerate locus, its behavior under scope
restriction). The content is the realization pair
\[
 \mathrm{Real}(X, T) \;=\; (d, e),
\]
where $d$ is a source-disjoint decorator whose derivation and verification
sources are disjoint, and $e$ is a compute engine whose hardcoded
expected values come from a source disjoint from the engine's
formula. The central theorem of Vol IV is that Real exists for every
ProvedHere claim inscribed in Vols I, II, III on the non-degenerate
locus of the programme. The non-degenerate locus is large: it
includes every generic parameter in every standard family, every
Koszul-locus claim, every chain-level result outside the admissible
logarithmic sector, every CY route outside the five unconverged
CY-C bridges. It excludes the critical level $k = -h^\vee$ for
affine Kac-Moody (where $\kappa = 0$ and Koszulness fails), the
$\Psi = 0$ locus for chiral Yangians (where the algebra is abelian),
the Creutzig-Kanade-Linshaw admissible logarithmic sector, and the
super-Yangian chain-level chiral coproduct sector.

The structure is as follows. The index part enumerates every
ProvedHere claim of Vols I--III, organized by theorem class. The
decorator part installs source-disjoint decorators. The
infrastructure part aligns compute engines. Vol IV's own theorems sit
in the realization programme chapter, which follows this preface.
Each of the three Vol IV theorems is itself realized: the decorator is
installed at inscription time; the engine backs it from a disjoint
source catalog; the reader can run the test on receipt of the
repository.

A note on what Vol IV is not. Vol IV is not a summary. The summary
role belongs to Vol I's opening part (statement of the five theorems)
and Vol I's preface (programme survey). Vol IV is not a metadata
volume. Metadata sits in \texttt{concordance.tex}, the \texttt{notes/}
directory, and the claim-status tags. Vol IV is not a second pass on
the mathematics of Vols I-III; it does not re-prove theorems. What
Vol IV is, is a functor. The functor Real from inscribed theorems to
verification pairs. The proof that Real is defined on a large locus.
The scope restriction where it is not. This is a mathematical content
claim, and this volume is organized around it.

A second note, on tone. The three prior volumes are written in the
Russian school's convergent voice: Gelfand's inevitability,
Beilinson's falsification, Drinfeld's unifying principle, Kazhdan's
compression. Vol IV inherits all four. The inevitability is that
trust-based inscription eventually produces a tautology somewhere in
the corpus; the falsification is the source-disjointness check catching
it at collection time; the unifying principle is the realization
functor Real; the compression is this preface. The fifth voice Vol IV
adds is a concession: verification is a craft, and its content is
specific. The Borcherds $c_N(0)/2$ identification is verified by a
Gritsenko-Nikulin denominator identity, not by a tabulation; the
affine Kac-Moody $\kappa = \dim(\mathfrak{g})(k + h^\vee)/(2 h^\vee)$
identification is verified at non-critical level by Feigin-Frenkel
screening cohomology, not by character arithmetic on the Sugawara
construction; the class M MC5 Wick $S_5 = -48/(c^2(5c + 22))$ is
verified by an independent Wick contraction engine built from the
Virasoro OPE axioms, not from the lambda-bracket expansion used to
derive it. Each of these is a specific mathematical act. Vol IV is
the volume in which these acts are carried out and their disjointness
recorded.

\section*{How to read this volume}

The reader with a theorem in hand from Vols I, II, or III, wishing to
know whether its realization pair is installed, consults Part A and
is directed either to a realized entry in Part B or to a
scope-restricted entry with the complementary locus explicitly marked.

The reader interested in the realization programme as a mathematical
object, independent of any particular claim, reads the realization
programme chapter (\ref{v4-ch:realization-programme}).

The reader interested in the decorator protocol and its enforcement
at import time consults
\texttt{compute/lib/realization\_registry.py} in this repository,
together with the Vol I \texttt{compute/lib/independent\_verification.py}
that this volume extends.

The programme's conventions are inherited from Vol~I and specialized
here by the prefix \texttt{v4-}, the Vol~IV registry's import-time
disjointness check against the Vol~I registry, and the coverage
protocol for Vols~I, II, and III.

\section*{Credits}

The programme is the author's own. The adversarial audits that
surfaced the verification deficiency, the source-disjoint protocol that
installed the collection-time disjointness check, and the content of
this volume's theorems are the author's responsibility. The disjoint
source catalogs are cited at the points of use:
Pridham-Toen-Vezzosi, Lurie HA 5.3, Costello-Gwilliam,
Francis-Gaitsgory, Mok 2025, Hua-Keller, Ben-Zvi-Francis-Nadler,
Schiffmann-Vasserot, Costello-Witten-Yamazaki. The mathematical text
is authored by Raeez Lorgat.
